### 2022-02-02 figures_01302022.Rmd
connect local folder to existing repo test

---
title: "Figures"
author: "Christopher Cook"
date: "1/21/2022"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(results = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r, include = FALSE}
library(tidyverse)
library(data.table)
devtools::load_all(".")
```

```{r}
#############
### histogram showing data spread for invivoPKfit cp values
#############

data.params.1 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
data.params.2 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv")

data.set.1 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
data.set.2 <- read.csv("inst/ext/processed.2comp.data.12212021.csv")

data.params.1 <- data.params.1 %>% filter(param.value.type == "Fitted geometric mean")
data.params.1$X <- NULL
data.params.1 <- data.params.1 %>% filter(Data.Analyzed != "Joint Analysis")

data.params.2 <- data.params.2 %>% filter(param.value.type == "Fitted geometric mean")
data.params.2$X <- NULL
data.params.2 <- data.params.2 %>% filter(Data.Analyzed != "Joint Analysis")

data.set.1$Reference <- as.character(data.set.1$Reference)
data.set.1$kelim <- NULL
data.set.1$Vdist <- NULL
data.set.1$Fgutabs <- NULL
data.set.1$kgutabs <- NULL

data.set.2$Reference <- as.character(data.set.2$Reference)
data.set.2$kelim <- NULL
data.set.2$Vdist <- NULL
data.set.2$Fgutabs <- NULL
data.set.2$kgutabs <- NULL

data.set.2$V1 <- NULL
data.set.2$Ralphatokelim <- NULL
data.set.2$Fbetaofalpha <- NULL

full.data.1 <- left_join(data.set.1, data.params.1, by = c("Compound", "CAS", "Reference"))
full.data.1 <- full.data.1 %>% filter(AIC != Inf)

full.data.2 <- left_join(data.set.2, data.params.2, by = c("Compound", "CAS", "Reference"))
full.data.2 <- full.data.2 %>% filter(AIC != Inf)

### function that find cp
test.1 <- function(full.data.1) {plyr::adply(full.data.1, 1, mutate, cp = cp_1comp(time = Time,
                                                                                   params = full.data.1[1,],
                                                                                   dose = Dose,
                                                                                   iv.dose = iv))}

test.2 <- function(full.data.2) {plyr::adply(full.data.2, 1, mutate, cp = cp_2comp(time = Time,
                                                                                   params = full.data.2[1,],
                                                                                   dose = Dose,
                                                                                   iv.dose = iv))}

### have to split data frame into ones with unique parameter values because cp_1comp takes constants
split_df.1 <- split(full.data.1, list(full.data.1$Compound,
                                      full.data.1$Reference,
                                      full.data.1$CAS),
                    drop = TRUE)

test_df.1 <- lapply(split_df.1, test.1)

maybe.1 <- do.call(rbind, test_df.1)

### nomralize cp by Value
maybe.1$cp_norm <- maybe.1$cp / maybe.1$Value
maybe.1$type <- "1-Compartment"

split_df.2 <- split(full.data.2, list(full.data.2$Compound,
                                      full.data.2$Reference,
                                      full.data.2$CAS),
                    drop = TRUE)

test_df.2 <- lapply(split_df.2, test.2)

maybe.2 <- do.call(rbind, test_df.2)

maybe.2$cp_norm <- maybe.2$cp / maybe.2$Value
maybe.2$type <- "2-Compartment"

# maybe.2 <- maybe.2 %>%
#   filter(cp != 1e-20)

maybe.1 <- maybe.1[, intersect(colnames(maybe.2), colnames(maybe.1))]
maybe.2 <- maybe.2[, intersect(colnames(maybe.1), colnames(maybe.2))]

maybe <- rbind(maybe.1, maybe.2)

p <- ggplot(data = maybe,
            mapping = aes(x = cp_norm)) +
  geom_histogram() +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  # xlim(0, 1e42) +
  # ylim(0, 400) +
  # scale_y_log10()+
  theme(title = element_text(size = 16),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14)) +
  scale_x_log10(limits = c(0.01, 1000))+
  theme_bw() +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  facet_wrap(. ~ type)

p
```

```{r}
### histogram of data variability

data <- as.data.table(read.csv("inst/ext/processed.1comp.data.12212021.csv"))
# data <- as.data.table(read.csv("inst/ext/processed.2comp.data.12212021.csv"))

# data <- data %>% filter(Route == "iv")

### function  that finds mean conc of each replicate timepoint
find_mean_conc <- function(data) {

  ### only use data with replicate timepoints
  data <- data[ ave(1:nrow(data), data$Time, FUN=length) > 1 , ]

  if(nrow(data) == 0) {
    return(NULL)
  } else {
    ### something that deletes replicate timepoints where all Values are NA
    time_split <- split(data, data$Time)

    # time_split_list <- keep(time_split, ~all(!is.na(.$Value)))

    time_split_list <- purrr::discard(time_split, ~all(is.na(.$Value)))
    # ~nrow(.) > 0)

    if(length(time_split_list) == 0) {
      return(NULL)
    } else {

      data <- do.call(rbind, time_split_list)
      # data$conc <- as.numeric(data$conc)
      data$Value[is.na(data$Value)] <- data$LOQ[is.na(data$Value)]

      ### take the average Value for each set of timepoints
      data <- data %>%
        group_by(Time) %>%
        do(mutate(., mean_conc = mean(.$Value, na.rm = TRUE)))

      data <- data %>%
        group_by(Time) %>%
        do(mutate(., range_conc = max(.$Value) - min(.$Value)))

      ### create normalized conc values by dividing conc by mean_conc
      data$conc_norm <- data$Value/data$mean_conc

      data <- data[order(data$Time),]

      return(data)
    }
  }
}

data.list <- list()
for(this.compound in unique(data[, Compound])) {
  this.compound.data <- data[Compound == this.compound]
  # print(this.compound)
  ### list of columns by which to split data.set
  col_list <- list(this.compound.data$Reference,
                   this.compound.data$Dose,
                   this.compound.data$Route,
                   this.compound.data$Media)

  ### split data.set into list of data.tables
  split_list <- split(this.compound.data, col_list)

  ### remove data.tables with 0 rows
  split_list <- keep(split_list, ~nrow(.) > 0)

  mean_conc <- lapply(split_list, find_mean_conc)
  test <- do.call(rbind, mean_conc)

  data.list[[this.compound]] <- test
}

### combine data.tables back into one large data.set
data.set <- do.call(rbind, data.list)

plot_fxn <- function(i){
  test_plot <- ggplot(data = i,
                      mapping = aes(x = conc_norm)) +
    # geom_histogram(aes(y = ..density..), binwidth = 0.25) +    geom_histogram(aes(y = ..density..), binwidth = 0.25) +
    # geom_density() +
    geom_histogram() +
    geom_vline(xintercept = c(0.5, 2),
               color = "Red",
               linetype = "dashed") +
    xlim(c(0, 4)) +
    theme_bw() +
    # theme(title = element_text(size = 16),
    #       axis.text = element_text(size = 12),
    #       axis.title = element_text(size = 14)) +
    labs(x = "Normalized concentration",
         y = "Number of observations")
}

my_hist <- plot_fxn(data.set)
my_hist

nrow(data.set[data.set$conc_norm > 2, ])
nrow(data.set[data.set$conc_norm < 0.5, ])

nrow(data.set[data.set$conc_norm >= 0.5 & data.set$conc_norm <= 2, ]) / nrow(data.set)

nrow(data.set)

```

```{r}

### Model Error vs Data Variability Density Plot

rownames(maybe.1) <- c()
rownames(maybe.2) <- c()

data.set$Reference <- as.character(data.set$Reference)

data.set$X <- NULL

data.set$kelim <- NULL
data.set$Vdist <- NULL
data.set$Fgutabs <- NULL
data.set$kgutabs <- NULL

data.set$type <- "1-Compartment"
test.1 <- left_join(data.set, maybe.1)

### trying to find number of points in each plot panel for 1-compartment
test.1.center <- test.1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
test.1.center <- test.1.center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio.1.center <- nrow(test.1.center)/nrow(test.1 %>% filter(!is.na(cp_norm)))

test.1.green <- test.1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
test.1.green <- test.1.green %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio.1.green <- nrow(test.1.green)/nrow(test.1 %>% filter(!is.na(cp_norm)))

test.1.gray <- test.1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
test.1.gray <- test.1.gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio.1.gray <- nrow(test.1.gray)/nrow(test.1 %>% filter(!is.na(cp_norm)))

test.1.tan <- test.1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
test.1.tan <- test.1.tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio.1.tan <- nrow(test.1.tan)/nrow(test.1 %>% filter(!is.na(cp_norm)))

###########
###########

data.set$type <- "2-Compartment"
test.2 <- left_join(data.set, maybe.2)

### trying to find number of points in each plot panel for 2-compartment
test.2.center <- test.2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
test.2.center <- test.2.center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio.2.center <- nrow(test.2.center)/nrow(test.2 %>% filter(!is.na(cp_norm)))

test.2.green <- test.2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
test.2.green <- test.2.green %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio.2.green <- nrow(test.2.green)/nrow(test.2 %>% filter(!is.na(cp_norm)))

test.2.gray <- test.2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
test.2.gray <- test.2.gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio.2.gray <- nrow(test.2.gray)/nrow(test.2 %>% filter(!is.na(cp_norm)))

test.2.tan <- test.2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
test.2.tan <- test.2.tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio.2.tan <- nrow(test.2.tan)/nrow(test.2 %>% filter(!is.na(cp_norm)))

# test.2 <- test.2 %>% filter(cp_norm > 1e-12)

test <- rbind(test.1, test.2)

p <- ggplot(data = test,
            mapping = aes(x = conc_norm, y = cp_norm)) +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#E1B07E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  # stat_density_2d() +
  geom_bin2d(bins = 100) +
  scale_fill_distiller(palette = "Blues") +
  geom_vline(xintercept = c(0.5, 2),
             linetype = "dashed") +
  geom_hline(yintercept = c(0.5, 2),
             linetype = "dashed") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Data Variability",
       y = "Model Error") +
  facet_wrap(. ~type)

p
```

```{r}

### sigma distibution histogram

data1 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv") %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

data2 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv") %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

data1 <- subset(data1, select = sigma_value)
data1$model <- 1

data2 <- subset(data2, select = sigma_value)
data2$model <- 2

data <- rbind(data1, data2)

test_plot <- ggplot(data = data,
                    mapping = aes(x = sigma_value)) +
  # geom_histogram(binwidth = 0.25) +
  geom_histogram() +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model)
  # stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

test_plot
```

```{r}

### Orders of magnitude histogram

data <- read.csv("inst/ext/processed.1comp.data.12212021.csv")

data$X <- NULL

split_df <- split(data, list(data$Compound,
                             data$Reference,
                             data$CAS,
                             data$Dose,
                             data$Species,
                             data$Route,
                             data$Media),
                  drop = TRUE)

find_mag <- function(data) {

  data$Value <- abs(data$Value)

  diff <- log10(max(data$Value, na.rm = TRUE)) - log10(min(data$Value, na.rm = TRUE))

  diff <- round(diff)

  return(diff)

}

thing <- lapply(split_df, find_mag)

thing <- pivot_longer(as.data.frame(thing), cols = everything())

p <- ggplot(data = thing, mapping = aes(x = value)) +
  geom_histogram(bins = 5, binwidth = 0.5) +
  xlab("Orders of magnitude") + theme_bw()
p
```

```{r}

### number of observations vs sigma value

one_comp_data <- read.csv("inst/ext/processed.1comp.data.12212021.csv") %>%
  filter(if_all(Value, ~!is.na(.x)))

onecomp <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv") %>%
  filter(AIC != Inf)

two_comp_data <- read.csv("inst/ext/processed.2comp.data.12212021.csv") %>%
  filter(if_all(Value, ~!is.na(.x)))

twocomp <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv") %>%
  filter(AIC != Inf)

one_comp_count <- one_comp_data %>% count(CAS, Compound, Reference, name = "Observations")

two_comp_count <- two_comp_data %>% count(CAS, Compound, Reference, name = "Observations")

#######
#######

onecomp_no_joint <- onecomp %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis" & AIC != Inf)

one_comp_count$Reference <- as.character(one_comp_count$Reference)

together_one <- left_join(one_comp_count, onecomp_no_joint, by = c("CAS", "Compound", "Reference"))

together_one <- subset(together_one, select = c(CAS, Compound, Reference, Observations, sigma_id, sigma_value))

together_one$model <- 1

twocomp_no_joint <- twocomp %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis" & AIC != Inf)

two_comp_count$Reference <- as.character(two_comp_count$Reference)

together_two <- left_join(two_comp_count, twocomp_no_joint, by = c("CAS", "Compound", "Reference"))

together_two <- subset(together_two, select = c(CAS, Compound, Reference, Observations, sigma_id, sigma_value))

together_two$model <- 2

together <- rbind(together_one, together_two)

p <- ggplot(data = together, mapping = aes(x = Observations, y = sigma_value)) +
  geom_point() +
  scale_y_log10() +
  labs(x = "Number of observations",
       y = "Sigma") +
  theme_bw() +
  facet_wrap(.~ model)

p
```

```{r}

### model error vs sigma

p <- ggplot(data = maybe, mapping = aes(x = sigma_value, y = cp_norm)) +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  labs( x = "Sigma",
        y = "Predicted/Obseved") +
  theme_bw() +
  facet_wrap(.~ model)

p

```

```{r}

### sigma estimates, joint vs individual

onecomp <- as.data.table(read.csv("inst/ext/PK.fit.table.1comp.12212021.csv") %>%
  filter(param.value.type == "Fitted geometric mean"))

twocomp <- as.data.table(read.csv("inst/ext/PK.fit.table.2comp.12212021.csv") %>%
  filter(param.value.type == "Fitted geometric mean"))

data_1 <- onecomp
data_2 <- twocomp

find_rep_sigma <- function(data) {

  ### only use data with replicate timepoints
  data <- data[ ave(1:nrow(data), data$sigma_id, FUN=length) > 1 , ]

  if(nrow(data) == 0) {
    return(NULL)
  } else {

    return(data)
  }
}

split_list_1 <- split(data_1, data_1$Compound)
rep_sigma_1 <- lapply(split_list_1, find_rep_sigma)
data_1 <- do.call(rbind, rep_sigma_1)
data_1 <- subset(data_1, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data_1$Data.Analyzed[data_1$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data_1 <- data_1 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data_1 <- data_1 %>% filter(sigma_id != "sigma2.14")
data_1$`Joint Analysis` <- as.numeric(data_1$`Joint Analysis`)
data_1$`Ind Analysis` <- as.numeric(data_1$`Ind Analysis`)
data_1$model <- "1-Compartment"

split_list_2 <- split(data_2, data_2$Compound)
rep_sigma_2 <- lapply(split_list_2, find_rep_sigma)
data_2 <- do.call(rbind, rep_sigma_2)
data_2 <- subset(data_2, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data_2$Data.Analyzed[data_2$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data_2 <- data_2 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data_2 <- data_2 %>% filter(sigma_id != "sigma2.14")
data_2$`Joint Analysis` <- as.numeric(data_2$`Joint Analysis`)
data_2$`Ind Analysis` <- as.numeric(data_2$`Ind Analysis`)
data_2$model <- "2-Compartment"

data <- rbind(data_1, data_2)

p <- ggplot(data, aes(x = `Ind Analysis`, y = `Joint Analysis`)) +
  geom_point() +
  scale_y_log10() +
  scale_x_log10() +
  geom_abline(slope = 1) +
  facet_wrap(. ~ model)
p
```

```{r}
data1 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")

data1$X <- NULL

# data1 <- data1 %>% filter(Compound == "tamoxifen")

split_df_1 <- split(data1, list(data1$Compound,
                             data1$Reference,
                             data1$CAS,
                             data1$Dose,
                             data1$Species,
                             data1$Route,
                             data1$Media),
                  drop = TRUE)

find_normalized_max <- function(data) {

  data$normalized_max <- max(data$Value, na.rm = TRUE)/data$LOQ

  return(data)

}

thing <- lapply(split_df_1, find_normalized_max)

thing <- do.call(rbind, thing)

row.names(thing) <- c()

thing <- thing %>%
  distinct(Compound,
           Reference,
           CAS,
           Dose,
           Species,
           Route,
           Media,
           normalized_max)

# thing <- pivot_longer(as.data.frame(thing), cols = everything())

p1 <- ggplot(data = thing, mapping = aes(x = normalized_max)) +
  geom_histogram(bins = 15) +
  scale_x_log10() +
  xlab("Max Concentration / LOQ") + theme_bw() +
  geom_vline(xintercept = 24.8482,
             color = "red",
             linetype = "dashed")
p1

###################################
###################################

find_normalized_mean <- function(data) {

  data$normalized_mean <- mean(data$Value, na.rm = TRUE)/data$LOQ

  return(data)

}

thing <- lapply(split_df_1, find_normalized_mean)

thing <- do.call(rbind, thing)

p2 <- ggplot(data = thing, mapping = aes(x = normalized_mean)) +
  geom_histogram(bins = 15) +
  scale_x_log10() +
  xlab("Mean Concentration / LOQ") + 
  theme_bw() +
  geom_vline(xintercept = 7.395552,
             color = "red",
             linetype = "dashed")
p2

###################################
###################################

data.params.1 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
# data.params.2 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv")

data.set.1 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
# data.set.2 <- read.csv("inst/ext/processed.2comp.data.12212021.csv")

data.params.1 <- data.params.1 %>% filter(param.value.type == "Fitted geometric mean")
data.params.1$X <- NULL
data.params.1 <- data.params.1 %>% filter(Data.Analyzed != "Joint Analysis")

# data.params.2 <- data.params.2 %>% filter(param.value.type == "Fitted geometric mean")
# data.params.2$X <- NULL
# data.params.2 <- data.params.2 %>% filter(Data.Analyzed != "Joint Analysis")

data.set.1$Reference <- as.character(data.set.1$Reference)
data.set.1$kelim <- NULL
data.set.1$Vdist <- NULL
data.set.1$Fgutabs <- NULL
data.set.1$kgutabs <- NULL

# data.set.2$Reference <- as.character(data.set.2$Reference)
# data.set.2$kelim <- NULL
# data.set.2$Vdist <- NULL
# data.set.2$Fgutabs <- NULL
# data.set.2$kgutabs <- NULL
# 
# data.set.2$V1 <- NULL
# data.set.2$Ralphatokelim <- NULL
# data.set.2$Fbetaofalpha <- NULL

full.data.1 <- left_join(data.set.1, data.params.1, by = c("Compound", "CAS", "Reference"))
full.data.1 <- full.data.1 %>% filter(AIC != Inf)

# full.data.2 <- left_join(data.set.2, data.params.2, by = c("Compound", "CAS", "Reference"))
# full.data.2 <- full.data.2 %>% filter(AIC != Inf)

split.full.data.1 <- split(full.data.1, list(full.data.1$Compound,
                             full.data.1$Reference,
                             full.data.1$CAS,
                             full.data.1$Dose,
                             full.data.1$Species.x,
                             full.data.1$Route,
                             full.data.1$Media),
                  drop = TRUE)

find_halflife_count <- function(data) {

  data_subset <- data %>% filter(!is.na(Value))

  max_time <- max(unique(data_subset$Time))

  data$halflife_count <- max_time/data$halflife

  return(data)

}

thing <- lapply(split.full.data.1, find_halflife_count)

thing <- do.call(rbind, thing)

thing <- thing %>%
  distinct(Compound,
           Reference,
           CAS,
           Dose,
           Species.x,
           Route,
           Media,
           halflife_count)

p3 <- ggplot(data = thing, mapping = aes(x = halflife_count)) +
  geom_histogram() +
  # scale_x_log10() +
  xlab("halflife count") + 
  theme_bw() +
  geom_vline(xintercept = 330.7598,
             color = "red",
             linetype = "dashed")
p3

```

```{r}

### bunch of polymeric stuff that might be useless

# data <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
# 
# data$X <- NULL
# 
# split_df <- split(data, list(data$Compound,
#                              data$Reference,
#                              data$CAS,
#                              data$Dose,
#                              data$Species,
#                              data$Route,
#                              data$Media,
#                              data$LOQ),
#                   drop = TRUE)
# 
# # split_df <- purrr::discard(split_df, ~all(is.na(.$Value)))
# 
# # split_df <- purrr::discard(split_df, ~sum(is.na(.$Value)) < 3)
# 
# fit_poly <- function(data) {
# 
#   tryCatch({
# 
#     line <- lm(data = data, formula = Value ~ poly(Time))
# 
#     RSS <- c(crossprod(line$residuals))
#     MSE <- RSS / length(line$residuals)
#     RMSE <- sqrt(MSE)
# 
#     data$RMSE <- RMSE
# 
#     return(data)
#   },
#   error = function(cond) {
#     message("poly fit failed.")
#     return(NULL)
#   })
# 
# }
# 
# work <- lapply(split_df, fit_poly)
# 
# yay <- do.call(rbind, work)
# 
# yay$Reference <- as.character(yay$Reference)
# full <- left_join(yay, maybe, by = c(c("Species" = "Species.x"),
#                                      "Compound",
#                                      "CAS",
#                                      "Reference",
#                                      "Dose",
#                                      "Route",
#                                      "Media",
#                                      "Source"))
# 
# full <- full %>%
#   filter(!is.na(type))
# just_rmse <- distinct(full, Compound, RMSE)
# #
# p1 <- ggplot(data = just_rmse, mapping = aes(x = RMSE)) +
#   geom_histogram(bins = 50) +
#   scale_x_log10() +
#   theme_bw() +
#   labs(title = "RMSE of polynomial models fit through series data")
# 
# p1
# 
# p2 <- ggplot(full, aes(x = RMSE, y = sigma_value)) +
#   geom_point() +
#   geom_abline() +
#   scale_y_log10() +
#   scale_x_log10() +
#   theme_bw() +
#   facet_wrap(.~ type)
# 
# 
# p2
# 
# 
# p3 <- ggplot(data = full, mapping = aes(x = RMSE, y = cp_norm)) +
#   # geom_point() +
#   geom_bin2d() +
#   scale_x_log10() +
#   scale_y_log10() +
#   labs(x = "RMSE",
#        y = "Predicted/Obseved") +
#   theme_bw() +
#   facet_wrap(.~ model)
# 
# p3

```

## Discussion

### 2022-02-02 figures_01312020.Rmd
connect local folder to existing repo test

---
title: "<i>invivoPKfit</i> and <i>CvTdb</i> figures"
author: "Christopher Cook"
date: "1/31/2022"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(results = TRUE)
knitr::opts_chunk$set(message = FALSE)
```

```{r}
rm(list = ls())
```

```{r, include = FALSE}
library(tidyverse)
library(data.table)
devtools::load_all(".")
```

```{r, run_invivoPKfit, eval = FALSE}

#################
#################

data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")

#################
#################

### fix compound names
data$analyte_name_original[data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
data$analyte_name_original[data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
data$analyte_name_original[data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
data$analyte_name_original[data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
data$analyte_name_original[data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"

### make fk_reference_document equal fk_extraction document if fk_reference_document is NULL
data$fk_reference_document_id[data$fk_reference_document_id == "NULL"] <- data$fk_extraction_document_id[data$fk_reference_document_id == "NULL"]

### do 1-Compartment fit
system.time(PK.fit.table.1comp <- fit_all(

  data.set = data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "fk_extraction_document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  ratio.data.to.dose = 0.001
))

### do 2-Compartment fit
system.time(PK.fit.table.2comp <- fit_all(

  data.set = data,
  model = "1compartment",
  modelfun = "analytic",
  compound.col = "analyte_name_original",
  cas.col = "dsstox_casrn",
  reference.col = "fk_reference_document_id",
  species.col = "species",
  species.weight.col = "weight_kg",
  species.weight.units.default = "kg",
  dose.col = "dose_level_normalized",
  time.col = "time_hr",
  time.units.default = "hr",
  media.col = "conc_medium_normalized",
  media.units.default = "normalized",
  value.col = "conc",
  units.default = NA,
  route.col = "administration_route_normalized",
  source.col = "fk_extraction_document_id",
  loq.default = NA,
  subject.default = NA,
  info.default = NA,
  ratio.data.to.dose = 0.001
))

write.csv(PK.fit.table.1comp[[1]] <- "inst/ext/PK.fit.table.1comp.DATE.csv")
write.csv(PK.fit.table.1comp[[2]] <- "inst/ext/processed.1comp.data.DATE.csv")

write.csv(PK.fit.table.2comp[[1]] <- "inst/ext/PK.fit.table.1comp.DATE.csv")
write.csv(PK.fit.table.2comp[[2]] <- "inst/ext/processed.1comp.data.DATE.csv")
```

```{r, make_rdata, eval = FALSE}

### save data
save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
save(pk_output_2comp_12212021, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
save(raw_2comp_12212021, file = "figures_rdata/raw_2comp_12212021.Rdata")

### save cp data
save(cp_df, file = "figures_rdata/cp_df.Rdata")
```

```{r, read_data}

### read in PK output files
pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
pk_output_2comp_12212021 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv")

### read in processed raw data files
raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
raw_2comp_12212021 <- read.csv("inst/ext/processed.2comp.data.12212021.csv")

### load all of this wonderful data
load("figures_rdata/pk_output_1comp_12212021.Rdata")
load("figures_rdata/pk_output_2comp_12212021.Rdata")
load("figures_rdata/raw_1comp_12212021.Rdata")
load("figures_rdata/raw_2comp_12212021.Rdata")
load("figures_rdata/cp_df_12212021.Rdata")
load("figures_rdata/cvt_variability_df_12212021.Rdata")
```

```{r, make_invivoPKfit_plots, eval = FALSE}

### 1 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_12212021),
                      data.set = as.data.table(raw_1comp_12212021),
                      model = "1compartment")

### 2 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_12212021),
                      data.set = as.data.table(raw_2comp_12212021),
                      model = "2compartment")

```

```{r make_cp_rdata, eval = FALSE}
################################
### histogram showing data spread of invivoPKfit cp values
################################

###########
### this is 1-compartment data
###########

###################
###################

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data1 <- pk_output_1comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data1 <- dplyr::select(raw_1comp_12212021, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs"))

###################
###################

raw_data11$Reference <- as.character(raw_data1$Reference)

full_data_1 <- left_join(raw_data1, pk_data1, by = c("Compound", "CAS", "Reference"))
full_data_1 <- full_data_1 %>% filter(AIC != Inf)

### function that finds cp
find_cp_1 <- function(full_data_1) {plyr::adply(full_data_1, 1, mutate, cp = cp_1comp(time = Time,
                                                                                      params = full_data_1[1,],
                                                                                      dose = Dose,
                                                                                      iv.dose = iv))}

### have to split data frame into ones with unique parameter values because cp_1comp takes constants
split_df_1 <- split(full_data_1, list(full_data_1$Compound,
                                      full_data_1$Reference,
                                      full_data_1$CAS),
                    drop = TRUE)

cp_df_1 <- lapply(split_df_1, find_cp_1)

cp_df_1 <- do.call(rbind, cp_df_1)

### nomralize cp by Value
cp_df_1$cp_norm <- cp_df_1$cp / cp_df_1$Value
cp_df_1$type <- "1-Compartment"

###########
### this is 2-compartment data
###########

#######################
#######################

### subset to only actual model outputs and discard "Joint Analysis" rows
pk_data2 <- pk_output_2comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

raw_data2 <- dplyr::select(raw_2comp_12212021, -c("kelim", 
                                                  "Vdist", 
                                                  "Fgutabs", 
                                                  "kgutabs",
                                                  "V1",
                                                  "Ralphatokelim",
                                                  "Fbetaofalpha"))

########################
########################

raw_data2$Reference <- as.character(raw_data2$Reference)

full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))
full_data_2 <- full_data_2 %>% filter(AIC != Inf)
split_df_2 <- split(full_data_2, list(full_data_2$Compound,
                                      full_data_2$Reference,
                                      full_data_2$CAS),
                    drop = TRUE)

### function that finds cp
find_cp_2 <- function(full_data_2) {plyr::adply(full_data_2, 1, mutate, cp = cp_2comp(time = Time,
                                                                                      params = full_data_2[1,],
                                                                                      dose = Dose,
                                                                                      iv.dose = iv))}
cp_df_2 <- lapply(split_df_2, find_cp_2)

cp_df_2 <- do.call(rbind, cp_df_2)

cp_df_2$cp_norm <- cp_df_2$cp / cp_df_2$Value
cp_df_2$type <- "2-Compartment"

# cp_df_2 <- cp_df_2 %>%
#   filter(cp != 1e-20)

### make both data.frames have the same column names so they are rbind-able
cp_df_1 <- cp_df_1[, intersect(colnames(cp_df_2), colnames(cp_df_1))]
cp_df_2 <- cp_df_2[, intersect(colnames(cp_df_1), colnames(cp_df_2))]

cp_df <- rbind(cp_df_1, cp_df_2)

cp_df_12212021 <- cp_df

save(cp_df_12212021, file = "figures_rdata/cp_df_12212021.Rdata")
```

```{r, make_cp_histogram}

##################
##################

data <- cp_df_12212021

##################
##################

p <- ggplot(data = data,
            mapping = aes(x = cp_norm)) +
  geom_histogram(bins = 30) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  # xlim(0, 1e42) +
  # ylim(0, 400) +
  # scale_y_log10()+
  theme(title = element_text(size = 16),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14)) +
  scale_x_log10(limits = c(0.01, 1000)) +
  theme_bw() +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  facet_wrap(. ~ type)

p
```

```{r, make_cvt_variability_rdata, eval = FALSE}

##################
##################

data <- as.data.table(raw_1comp_12212021)

##################
##################

### function that finds mean conc of each replicate timepoint
find_mean_conc <- function(data) {

  ### only use data with replicate timepoints
  data <- data[ ave(1:nrow(data), data$Time, fun = length) > 1 , ]

  if(nrow(data) == 0) {
    return(NULL)
  } else {

    time_split <- split(data, data$Time)

    ### discard replicate timepoints where all concentrations are NA
    time_split_list <- purrr::discard(time_split, ~all(is.na(.$Value)))

    if(length(time_split_list) == 0) {
      return(NULL)
    } else {

      data <- do.call(rbind, time_split_list)

      ### where some replicate concentration data are NA, set them equal to the LOQ
      data$Value[is.na(data$Value)] <- data$LOQ[is.na(data$Value)]

      ### take the average Value for each set of timepoints
      data <- data %>%
        group_by(Time) %>%
        do(mutate(., mean_conc = mean(.$Value, na.rm = TRUE)))

      data <- data %>%
        group_by(Time) %>%
        do(mutate(., range_conc = max(.$Value) - min(.$Value)))

      ### create normalized conc values by dividing conc by mean_conc
      data$conc_norm <- data$Value/data$mean_conc

      data <- data[order(data$Time), ]

      return(data)
    }
  }
}

data.list <- list()
for(this.compound in unique(data[, Compound])) {
  this.compound.data <- data[Compound == this.compound]

  ### list of columns by which to split data.set
  col_list <- list(this.compound.data$Reference,
                   this.compound.data$Dose,
                   this.compound.data$Route,
                   this.compound.data$Media)

  ### split data.set into list of data.tables
  split_list <- split(this.compound.data, col_list)

  ### remove data.tables with 0 rows
  split_list <- keep(split_list, ~nrow(.) > 0)

  ### use find_mean_conc fn
  mean_conc <- lapply(split_list, find_mean_conc)

  test <- do.call(rbind, mean_conc)

  data.list[[this.compound]] <- test
}

### combine data.tables back into one large data.set
cvt_variability_df_12212021 <- do.call(rbind, data.list)

save(cvt_variability_df_12212021, file = "figures_rdata/cvt_variability_df_12212021.Rdata")
```

```{r, make_cvt_variability_histogram}

#################
#################

data <- cvt_variability_df_12212021

#################
#################

p <- ggplot(data, aes(x = conc_norm)) +
  geom_histogram() +
  xlim(c(0, 4)) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  theme_bw() +
  labs(x = "Normalized concentration",
       y = "Number of observations")
p
```

```{r, make_density_plot}

##################
##################

pk_data <- cp_df_12212021

cvt_data <- cvt_variability_df_12212021

##################
##################

row.names(pk_data) <- c()

cvt_data <- dplyr::select(cvt_data, -c("X",
                                       "kelim", 
                                       "Vdist", 
                                       "Fgutabs", 
                                       "kgutabs"))

### split pk_data by model so you can properly join with raw data
model_split <- split(pk_data, pk_data$model)

cvt_data$Reference <- as.character(cvt_data$Reference)

cvt_data$type <- "1-Compartment"
full_data_1 <- left_join(cvt_data, model_split$`1compartment`)

cvt_data$type <- "2-Compartment"
full_data_2 <- left_join(cvt_data, model_split$`2compartment`)

### put data back together
full_data <- rbind(full_data_1, full_data_2)

###########
###########
###########

### Find number of points in each plot panel for 1-compartment
full_data_1_center <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
full_data_1_center <- full_data_1_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio_1_center <- nrow(full_data_1_center) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))

full_data_1_green <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_1_green <- full_data_1_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_1_green <- nrow(full_data_1_green) / nrow(full_data_1_green %>% filter(!is.na(cp_norm)))

full_data_1_gray <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_1_gray <- full_data_1_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio_1_gray <- nrow(full_data_1_gray) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))

full_data_1_tan <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
full_data_1_tan <- full_data_1_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_1_tan <- nrow(full_data_1_tan) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))

###########
###########

### Find number of points in each plot panel for 2-compartment
full_data_2_center <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
full_data_2_center <- full_data_2_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio_2_center <- nrow(full_data_2_center) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))

full_data_2_green <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_2_green <- full_data_2 %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2_green %>% filter(!is.na(cp_norm)))

full_data_2_gray <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
full_data_2_gray <- full_data_2_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
ratio_2_gray <- nrow(full_data_2_gray) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))

full_data_2_tan <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
full_data_2_tan <- full_data_2_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
ratio_2_tan <- nrow(full_data_2_tan) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))

###########
###########
###########

p <- ggplot(data = full_data,
            mapping = aes(x = conc_norm, y = cp_norm)) +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#E1B07E") +
  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  # stat_density_2d() +
  geom_bin2d(bins = 100) +
  scale_fill_distiller(palette = "Blues") +
  geom_vline(xintercept = c(0.5, 2),
             linetype = "dashed") +
  geom_hline(yintercept = c(0.5, 2),
             linetype = "dashed") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Data Variability",
       y = "Model Error") +
  facet_wrap(. ~ type)

p
```

```{r, make_sigma_distribution_histogram}

##################
##################

data1 <- pk_output_1comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

data2 <- pk_output_2comp_12212021 %>%
  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")

##################
##################

### assign new column, with either "1-Compartment" or "2-Compartment"
data1 <- subset(data1, select = sigma_value)
data1$model <- "1-Compartment"

data2 <- subset(data2, select = sigma_value)
data2$model <- "2-Compartment"

data <- rbind(data1, data2)

p <- ggplot(data = data,
            mapping = aes(x = sigma_value)) +
  geom_histogram(bins = 15) +
  # geom_density() +
  # scale_y_log10()+
  scale_x_log10() +
  theme_bw() +
  labs(x = "Sigma",
       y = "Number of observations") +
  facet_wrap(.~ model)
# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

p
```

```{r make_magnitude_histogram}

##################
##################

data <- raw_1comp_12212021

##################
##################

data$X <- NULL

split_df <- split(data, list(data$Compound,
                             data$Reference,
                             data$CAS,
                             data$Dose,
                             data$Species,
                             data$Route,
                             data$Media),
                  drop = TRUE)

### find number of orders of magnitude
find_mag <- function(data) {

  data$Value <- abs(data$Value)

  diff <- log10(max(data$Value, na.rm = TRUE)) - log10(min(data$Value, na.rm = TRUE))

  diff <- round(diff)

  return(diff)

}

data <- lapply(split_df, find_mag)

data <- pivot_longer(as.data.frame(data), cols = everything())

p <- ggplot(data = data, mapping = aes(x = value)) +
  geom_histogram(bins = 5, binwidth = 0.5) +
  xlab("Orders of magnitude") + theme_bw()

p
```

```{r make_joint_sigma_plot}

##################
##################

data1 <- as.data.table(pk_output_1comp_12212021 %>%
                         filter(param.value.type == "Fitted geometric mean"))

data2 <- as.data.table(pk_output_2comp_12212021 %>%
                         filter(param.value.type == "Fitted geometric mean"))

##################
##################

### find data with repeated sigma_id values
find_rep_sigma <- function(data) {

  data <- data[ ave(1:nrow(data), data$sigma_id, FUN=length) > 1 , ]

  if(nrow(data) == 0) {
    return(NULL)
  } else {

    return(data)
  }
}

split_list_1 <- split(data1, data1$Compound)
rep_sigma_1 <- lapply(split_list_1, find_rep_sigma)
data1 <- do.call(rbind, rep_sigma_1)
data1 <- subset(data1, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data1$Data.Analyzed[data1$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data1 <- data1 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data1 <- data1 %>% filter(sigma_id != "sigma2.14")
data1$`Joint Analysis` <- as.numeric(data1$`Joint Analysis`)
data1$`Ind Analysis` <- as.numeric(data1$`Ind Analysis`)
data1$model <- "1-Compartment"

split_list_2 <- split(data2, data2$Compound)
rep_sigma_2 <- lapply(split_list_2, find_rep_sigma)
data2 <- do.call(rbind, rep_sigma_2)
data2 <- subset(data2, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
data2$Data.Analyzed[data2$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
data2 <- data2 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
data2 <- data2 %>% filter(sigma_id != "sigma2.14")
data2$`Joint Analysis` <- as.numeric(data2$`Joint Analysis`)
data2$`Ind Analysis` <- as.numeric(data2$`Ind Analysis`)
data2$model <- "2-Compartment"

data <- rbind(data1, data2)

p <- ggplot(data, aes(x = `Ind Analysis`, y = `Joint Analysis`)) +
  geom_point() +
  scale_y_log10() +
  scale_x_log10() +
  geom_abline(slope = 1) +
  facet_wrap(. ~ model)
p
```

```{r}

###########
### one compartment
###########

##################
##################

raw_data1 <- raw_1comp_12212021

##################
##################

pk_data1 <- pk_output_1comp_12212021 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

pk_data1$X <- NULL

raw_data1$Reference <- as.character(raw_data1$Reference)

raw_data1 <- dplyr::select(raw_data1, -c("X",
                                         "kelim",
                                         "Vdist",
                                         "Fgutabs",
                                         "kgutabs"))

# pk_data2 <- pk_output_2comp_12212021

full_data_1 <- left_join(raw_data1, pk_data1, by = c("Compound", "CAS", "Reference"))

full_data_1 <- full_data_1 %>% filter(AIC != Inf)

find_halflife_count <- function(data) {

  data_subset <- data %>% filter(!is.na(Value))

  max_time <- max(unique(data_subset$Time))

  data$halflife_count <- max_time/data$halflife

  return(data)

}

split_full_data_1 <- split(full_data_1, list(full_data_1$Compound,
                                             full_data_1$Reference,
                                             full_data_1$CAS,
                                             full_data_1$Dose,
                                             full_data_1$Species.x,
                                             full_data_1$Route,
                                             full_data_1$Media),
                           drop = TRUE)

full_data_1_hl <- lapply(split_full_data_1, find_halflife_count)

full_data_1_hl <- do.call(rbind, full_data_1_hl)

full_data_1_hl <- full_data_1_hl %>%
  distinct(Compound,
           Reference,
           CAS,
           Dose,
           Species.x,
           Route,
           Media,
           halflife_count)

full_data_1_hl$model <- "1-Compartment"

###########
### two compartment
###########

##################
##################

raw_data2 <- raw_2comp_12212021

pk_data2 <- pk_output_2comp_12212021 %>% 
  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")

##################
##################

pk_data2$X <- NULL

raw_data2$Reference <- as.character(raw_data2$Reference)

raw_data2 <- dplyr::select(raw_data2, -c("kelim", 
                                         "Vdist", 
                                         "Fgutabs", 
                                         "kgutabs",
                                         "V1",
                                         "Ralphatokelim",
                                         "Fbetaofalpha"))

# pk_data2 <- pk_output_2comp_12212021

full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))

full_data_2 <- full_data_2 %>% filter(AIC != Inf)

find_halflife_count <- function(data) {

  data_subset <- data %>% filter(!is.na(Value))

  max_time <- max(unique(data_subset$Time))

  data$halflife_count <- max_time/data$halflife

  return(data)

}

split_full_data_2 <- split(full_data_2, list(full_data_2$Compound,
                                             full_data_2$Reference,
                                             full_data_2$CAS,
                                             full_data_2$Dose,
                                             full_data_2$Species.x,
                                             full_data_2$Route,
                                             full_data_2$Media),
                           drop = TRUE)

full_data_2_hl <- lapply(split_full_data_2, find_halflife_count)

full_data_2_hl <- do.call(rbind, full_data_2_hl)

full_data_2_hl <- full_data_2_hl %>%
  distinct(Compound,
           Reference,
           CAS,
           Dose,
           Species.x,
           Route,
           Media,
           halflife_count)

full_data_2_hl$model <- "2-Compartment"

###########
###########
###########

full_data_hl <- rbind(full_data_1_hl, full_data_2_hl)

###########

p <- ggplot(data = full_data_hl, mapping = aes(x = halflife_count)) +
  geom_histogram() +
  scale_x_log10() +
  xlab("halflife count") + 
  theme_bw() +
  # geom_vline(xintercept = 330.7598,
  #            color = "red",
  #            linetype = "dashed") + 
  facet_wrap(. ~ model)
p
```

### 2022-02-08 figures_01312022.Rmd
test

--- 2022-02-02 figures_01312020.Rmd
@@
 date: "1/31/2022"
-output: html_document
+output:
+  html_document: default
+  word_document: default
 ---
@@
 
-```{r}
-rm(list = ls())
-```
-
 ```{r, include = FALSE}
@@
 library(data.table)
+library(readxl)
 devtools::load_all(".")
@@
   data.set = data,
-  model = "1compartment",
+  model = "2compartment",
   modelfun = "analytic",
@@
 
+```{r, read_data}
+
+### read in PK output files
+pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
+pk_output_2comp_12212021 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv")
+
+### read in processed raw data files
+raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
+raw_2comp_12212021 <- read.csv("inst/ext/processed.2comp.data.12212021.csv")
+
+pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
+```
+
 ```{r, make_rdata, eval = FALSE}
@@
 save(raw_2comp_12212021, file = "figures_rdata/raw_2comp_12212021.Rdata")
+save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")
 
@@
 
-```{r, read_data}
-
-### read in PK output files
-pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
-pk_output_2comp_12212021 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv")
-
-### read in processed raw data files
-raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
-raw_2comp_12212021 <- read.csv("inst/ext/processed.2comp.data.12212021.csv")
+```{r, load_data}
 
@@
 load("figures_rdata/cvt_variability_df_12212021.Rdata")
+load("figures_rdata/pk_lombardo_02072022.Rdata")
 ```
@@
 
-```{r make_cp_rdata, eval = FALSE}
+```{r, make_cp_rdata, eval = FALSE}
 ################################
@@
 
-raw_data11$Reference <- as.character(raw_data1$Reference)
+raw_data1$Reference <- as.character(raw_data1$Reference)
 
@@
 full_data_1_green <- full_data_1_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_1_green <- nrow(full_data_1_green) / nrow(full_data_1_green %>% filter(!is.na(cp_norm)))
+ratio_1_green <- nrow(full_data_1_green) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
 
@@
 full_data_2_green <- full_data_2 %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2_green %>% filter(!is.na(cp_norm)))
+ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
 
@@
 ###########
+
+# rect_df1 <- data.frame(xmin = c(0, 0, 2, 2, 0, 2, 0.5, 0.5),
+#                       xmax = c(0.5, 0.5, Inf, Inf, 0.5, Inf, 2, 2),
+#                       ymin = c(2, 0, 0, 2, 0.5, 0.5, 2, 0),
+#                       ymax = c(Inf, 0.5, 0.5, Inf, 2, 2, Inf, 0.5),
+#                       panel_key = c(paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                     paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""),
+#                                           sep = " "),
+#                                     paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                     paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""),
+#                                           sep = " "),
+#                                     paste("Good Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_1_tan, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                     paste("Good Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_1_tan, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                    paste("Poor Fit, Typical Data", 
+#                                           paste("(", round(100 * ratio_1_gray, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                    paste("Poor Fit, Typical Data", 
+#                                           paste("(", round(100 * ratio_1_gray, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " ")))
+# 
+# rect_df2 <- data.frame(xmin = c(0, 0, 2, 2, 0, 2, 0.5, 0.5),
+#                       xmax = c(0.5, 0.5, Inf, Inf, 0.5, Inf, 2, 2),
+#                       ymin = c(2, 0, 0, 2, 0.5, 0.5, 2, 0),
+#                       ymax = c(Inf, 0.5, 0.5, Inf, 2, 2, Inf, 0.5),
+#                       panel_key = c(paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                     paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""),
+#                                           sep = " "),
+#                                     paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                     paste("Poor Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""),
+#                                           sep = " "),
+#                                     paste("Good Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_2_tan, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                     paste("Good Fit, Outlier Data", 
+#                                           paste("(", round(100 * ratio_2_tan, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                    paste("Poor Fit, Typical Data", 
+#                                           paste("(", round(100 * ratio_2_gray, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " "),
+#                                    paste("Poor Fit, Typical Data", 
+#                                           paste("(", round(100 * ratio_2_gray, digits = 1), "%", ")", sep = ""), 
+#                                           sep = " ")))
+# 
+# 
+# rect_p1 <- ggplot() +
+#   geom_rect(data = rect_df1, aes(xmin = xmin,
+#                                 ymin = ymin,
+#                                 xmax = xmax,
+#                                 ymax = ymax,
+#                                 fill = panel_key),
+#             alpha = 0.3, inherit.aes = FALSE) +
+#   scale_fill_manual(name = "Panel Key",
+#                     values = c("#361D2E",
+#                                "#86A397",
+#                                "#E1B07E")) +
+#   theme_bw() +
+#   theme(panel.spacing = unit(2, "lines")) +
+#   geom_vline(xintercept = c(0.5, 2),
+#              linetype = "dashed") +
+#   geom_hline(yintercept = c(0.5, 2),
+#              linetype = "dashed") +
+#   scale_x_log10() +
+#   scale_y_log10() +
+#   labs(x = "Data Variability",
+#        y = "Model Error") +
+#   guides(fill = guide_legend(override.aes = list(size = 0.1)))
+# 
+# rect_p2 <- ggplot() +
+#   geom_rect(data = rect_df2, aes(xmin = xmin,
+#                                 ymin = ymin,
+#                                 xmax = xmax,
+#                                 ymax = ymax,
+#                                 fill = panel_key),
+#             alpha = 0.3, inherit.aes = FALSE) +
+#   scale_fill_manual(name = "Panel Key",
+#                     values = c("#361D2E",
+#                                "#86A397",
+#                                "#E1B07E")) +
+#   theme_bw() +
+#   theme(panel.spacing = unit(2, "lines")) +
+#   geom_vline(xintercept = c(0.5, 2),
+#              linetype = "dashed") +
+#   geom_hline(yintercept = c(0.5, 2),
+#              linetype = "dashed") +
+#   scale_x_log10() +
+#   scale_y_log10() +
+#   labs(x = "Data Variability",
+#        y = "Model Error") +
+#   guides(fill = guide_legend(override.aes = list(size = 0.1)))
+# 
+# ###################
+# fill_legend1 <- get_legend(rect_p1)
+# fill_legend2 <- get_legend(rect_p2)
+# ##################
 
@@
   theme(panel.spacing = unit(2, "lines")) +
-  # stat_density_2d() +
   geom_bin2d(bins = 100) +
@@
 p
+
+# ##################
+# 
+# data_p_final <- data_p +
+#   # inset_element(fill_legend1, 0.1, 1, 0.5, 1) +
+#   inset_element(fill_legend2, 0.6, 0.5, 0.7, 0.2, clip = TRUE)
+#  
+# data_p_final
 ```
@@
 
-```{r}
+```{r, make_halflife_count_histogram}
 
@@
 ```
+
+```{r, make_max_loq_histogram}
+
+###############
+###############
+
+raw_data1 <- raw_1comp_12212021
+
+###############
+###############
+
+find_normalized_max <- function(data) {
+
+  data$normalized_max <- max(data$Value, na.rm = TRUE)/data$LOQ
+
+  return(data)
+
+}
+
+split_df_1 <- split(raw_data1, list(raw_data1$Compound,
+                                    raw_data1$Reference,
+                                    raw_data1$CAS,
+                                    raw_data1$Dose,
+                                    raw_data1$Species,
+                                    raw_data1$Route,
+                                    raw_data1$Media),
+                    drop = TRUE)
+
+raw_data1_normalized_max <- lapply(split_df_1, find_normalized_max)
+
+raw_data1_normalized_max <- do.call(rbind, raw_data1_normalized_max)
+
+raw_data1_normalized_max <- raw_data1_normalized_max %>%
+  distinct(Compound,
+           Reference,
+           CAS,
+           Dose,
+           Species,
+           Route,
+           Media,
+           normalized_max)
+
+p <- ggplot(data = raw_data1_normalized_max, mapping = aes(x = normalized_max)) +
+  geom_histogram(bins = 15) +
+  scale_x_log10() +
+  xlab("Max Concentration / LOQ") + 
+  theme_bw()
+# geom_vline(xintercept = 24.8482,
+#            color = "red",
+#            linetype = "dashed")
+p
+```
+
+```{r, make_mean_loq_histogram}
+
+###############
+###############
+
+raw_data1 <- raw_1comp_12212021
+
+###############
+###############
+
+find_normalized_mean <- function(data) {
+
+  data$normalized_mean <- mean(data$Value, na.rm = TRUE)/data$LOQ
+
+  return(data)
+
+}
+
+split_df_1 <- split(raw_data1, list(raw_data1$Compound,
+                                    raw_data1$Reference,
+                                    raw_data1$CAS,
+                                    raw_data1$Dose,
+                                    raw_data1$Species,
+                                    raw_data1$Route,
+                                    raw_data1$Media),
+                    drop = TRUE)
+
+raw_data1_normalized_mean <- lapply(split_df_1, find_normalized_mean)
+
+raw_data1_normalized_mean <- do.call(rbind, raw_data1_normalized_mean)
+
+raw_data1_normalized_mean <- raw_data1_normalized_mean %>%
+  distinct(Compound,
+           Reference,
+           CAS,
+           Dose,
+           Species,
+           Route,
+           Media,
+           normalized_mean)
+
+p <- ggplot(data = raw_data1_normalized_mean, mapping = aes(x = normalized_mean)) +
+  geom_histogram(bins = 15) +
+  scale_x_log10() +
+  xlab("Mean Concentration / LOQ") + 
+  theme_bw()
+# geom_vline(xintercept = 24.8482,
+#            color = "red",
+#            linetype = "dashed")
+p
+```
+
+```{r, make_model_params_table}
+
+### this code almost entirely is imported from John's bake-off RMarkdown file
+### what this produces is a table of compounds that were fit by at least one of the models
+### AICs for both models are reported, and subsequent parameter values correspond to the model with the lower AIC
+
+###################
+###################
+
+pk_data1 <- pk_output_1comp_12212021
+
+pk_data2 <- pk_output_2comp_12212021
+
+###################
+###################
+
+pk_data1$sigma_id <- NULL
+pk_data1$sigma_value <- NULL
+pk_data2$sigma_id <- NULL
+pk_data2$sigma_value <- NULL
+
+pk_data1 <- distinct(pk_data1)
+pk_data2 <- distinct(pk_data2)
+
+fits1comp <- subset(pk_data1, is.finite(AIC) & AIC < 10^4)
+fits2comp <- subset(pk_data2, is.finite(AIC) & AIC < 10^4)
+
+#How many chemicals have 1 or 2 compartment fits:
+length(unique(c(fits1comp$CAS,fits2comp$CAS)))
+
+fittable <- NULL
+for (this.cas in unique(c(fits1comp$CAS,fits2comp$CAS)))
+{
+  if (this.cas %in% fits1comp$CAS) this.compound <- fits1comp[
+    fits1comp$CAS==this.cas,"Compound"][1]
+  else this.compound <- fits2comp[
+    fits2comp$CAS==this.cas,"Compound"][1]
+
+  this.data.1comp <- subset(fits1comp,CAS==this.cas)
+  this.data.2comp <- subset(fits2comp,CAS==this.cas)
+
+  for (this.species in unique(tolower(c(
+    this.data.1comp$Species,
+    this.data.2comp$Species))))
+  {
+    Vdist.1comp <- NA
+    kelim.1comp <- NA
+    Vdist.2comp <- NA
+    kelim.2comp <- NA
+
+    this.data.1comp.species <- subset(this.data.1comp,tolower(Species)==this.species)
+    this.data.2comp.species <- subset(this.data.2comp,tolower(Species)==this.species)
+
+    this.row <- data.frame(
+      Compound=this.compound,
+      CAS=this.cas,
+      Species=this.species,
+      Reference=NA,
+      AIC.1comp=NA,
+      AIC.2comp=NA,
+      Model=NA,
+      Vdist=NA,
+      kelim=NA)
+
+    if (this.cas %in% fits1comp$CAS)
+    {
+      this.data.1comp.species <- subset(this.data.1comp.species,
+                                        param.value.type=="Fitted geometric mean")
+
+      # If more than one source, require that the joint analysis worked:
+      if (dim(this.data.1comp.species)[1]>1)
+      {
+        this.data.1comp.species<- subset(this.data.1comp.species, 
+                                         Data.Analyzed=="Joint Analysis")
+      }
+      if (dim(this.data.1comp.species)[1]>0) 
+      {
+        this.row$AIC.1comp <- this.data.1comp.species$AIC
+        Vdist.1comp <- this.data.1comp.species$Vdist
+        kelim.1comp <- this.data.1comp.species$kelim
+        this.row$Reference <- this.data.1comp.species$Reference
+      }
+    }
+
+    if (this.cas %in% fits2comp$CAS)
+    {
+      this.data.2comp.species <- subset(this.data.2comp.species,
+                                        param.value.type=="Fitted geometric mean")
+
+      # If more than one source, require that the joint analysis worked:
+      if (dim(this.data.2comp.species)[1]>1)
+      {
+        this.data.2comp.species <- subset(this.data.2comp.species, 
+                                          Data.Analyzed=="Joint Analysis")
+      }
+      if (dim(this.data.2comp.species)[1]>0) 
+      {
+        this.row$AIC.2comp <- this.data.2comp.species$AIC
+        Vdist.2comp <- this.data.2comp.species$Vss
+        kelim.2comp <- this.data.2comp.species$kelim
+        this.row$Reference <- this.data.2comp.species$Reference
+      }
+    }
+
+    if (!is.na(this.row$AIC.1comp))
+    {
+      if (!is.na(this.row$AIC.2comp))
+      {
+        if (this.row$AIC.1comp < this.row$AIC.2comp)
+        {
+          this.row$Model <- "1Comp"
+        } else this.row$Model <- "2Comp"
+      } else this.row$Model <- "1Comp"
+    } else if (!is.na(this.row$AIC.2comp))
+    {
+      this.row$Model <- "2Comp"
+    }
+
+    if (!is.na(this.row$Model))
+      if (this.row$Model == "1Comp")
+      {
+        this.row$Vdist <- Vdist.1comp
+        this.row$kelim <- kelim.1comp
+      } else 
+      {
+        this.row$Vdist <- Vdist.2comp
+        this.row$kelim <- kelim.2comp
+      }
+
+    fittable <- rbind(fittable,this.row)
+  }
+}
+fittable$halflife <- log(2)/fittable$kelim
+
+#Lets only keep chemicals where we can fit a PK model:
+fittable <- subset(fittable, !is.na(Model))
+
+for (this.col in c("AIC.1comp","AIC.2comp","Vdist","kelim","halflife"))
+  fittable[,this.col] <- signif(as.numeric(fittable[,this.col]),4)
+
+# We have parameters estimated for 86 chemicals:
+dim(fittable)[1]
+
+# write.csv(fittable, file = "inst/ext/model_params_table.csv", row.names = FALSE)
+
+```
+
+```{r, make_no_fit_table}
+
+##################
+##################
+
+pk_data1 <- as.data.table(pk_output_1comp_12212021)
+pk_data2 <- as.data.table(pk_output_2comp_12212021)
+
+##################
+##################
+
+pk_data1 <- pk_data1 %>%
+  filter(param.value.type == "Fitted geometric mean") %>%
+  dplyr::select(c("Compound", "CAS", "Reference", "AIC")) %>%
+  mutate(model = "1-Compartment")
+
+pk_data2 <- pk_data2 %>%
+  filter(param.value.type == "Fitted geometric mean") %>%
+  dplyr::select(c("Compound", "CAS", "Reference", "AIC")) %>%
+  mutate(model = "2-Compartment")
+
+pk_all <- rbind(pk_data1, pk_data2)
+
+### loop that says if a compound has any references that do not have AIC of Inf, it was a fit compound
+  this.compound.list <- list()
+  for (this.compound in unique(pk_all[, Compound])) {
+
+    this.compound.data <- pk_all[Compound == this.compound]
+
+    if(any(this.compound.data$AIC != Inf)) {
+      this.compound.data$status <- "good fit"
+    } else {
+      this.compound.data$status <- "bad fit"
+    }
+
+    this.compound.list[[this.compound]] <- this.compound.data
+
+  }
+
+  pk_all <- do.call(rbind, this.compound.list)
+
+  pk_all <- pk_all %>%
+    filter(status == "bad fit") %>% ### only want bad fit
+    mutate(status = NULL) %>% ### get rid of status column
+    group_by(Compound) %>%  
+    filter(n() == 2) %>% ### group_by compound and only keep compounds with two observations, aka neither model worked
+    mutate(model = NULL) %>% ### get ride of model column
+    distinct() ### discard repeated compound names
+
+# write.csv(pk_all, file = "inst/ext/no_fit_table_01212022.csv", row.names = FALSE)
+```
+
+```{r}
+
+##################
+##################
+
+pk_data1 <- pk_output_1comp_12212021
+
+pk_lombardo <- pk_lombardo
+
+##################
+##################
+
+pk_data1 <- pk_data1 %>%
+  filter(param.value.type == "Fitted geometric mean", Species == "human")
+
+pk_all <- left_join(pk_data1, pk_lombardo, by = c("CAS" = "CAS #"))
+
+pk_all <- pk_all %>%
+  filter(!is.na(`human VDss (L/kg)`), 
+         !is.na(`human CL (mL/min/kg)`))
+
+### volume of distribution comparison
+p1 <- ggplot(pk_all, aes(x = Vdist, y = `human VDss (L/kg)`)) +
+  geom_point() +
+  scale_x_log10() +
+  geom_abline(slope = 1, intercept = 0)
+
+p1
+
+### half-life comparision
+p2 <- ggplot(pk_all, aes(x = halflife, y = `terminal  t1/2 (h)`)) +
+  geom_point() +
+  geom_abline(slope = 1, intercept = 0)
+
+p2
+
+### clearance comparison
+
+### convert to same units
+pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000
+
+p3 <- ggplot(data = pk_all, mapping = aes(x = CLtot, y = `human CL (L/hr/kg)`)) +
+  geom_point() +
+  scale_x_log10() +
+  geom_abline(slope = 1, intercept = 0)
+
+p3
+
+```

### 2022-02-08 R/cp_2comp.R

@@ -21,44 +21,44 @@ cp_2comp <- function(params, time, dose, iv.dose)
 
   if (any(sapply(params,function(x) identical(x,numeric(0))))) return(NA)
 
-  if (is.null(params$Fgutabs)|is.na(params$Fgutabs))
+  if (is.null(params$Fgutabs) | is.na(params$Fgutabs))
   {
-    params$Fgutabs<-1
+    params$Fgutabs <- 1
   }
-  if (is.null(params$kgutabs)|is.na(params$kgutabs))
+  if (is.null(params$kgutabs) | is.na(params$kgutabs))
   {
-    params$kgutabs<-1
+    params$kgutabs <- 1
   }
-  if (is.null(params$Fbetaofalpha)) params$Fbetaofalpha<-1
-  if (is.null(params$Ralphatokelim)) params$Ralphatokelim<-1
+  if (is.null(params$Fbetaofalpha)) params$Fbetaofalpha <- 1
+  if (is.null(params$Ralphatokelim)) params$Ralphatokelim <- 1
 
-  if (is.na(params$Fbetaofalpha)) params$Fbetaofalpha<-1
-  if (is.na(params$Ralphatokelim)) params$Ralphatokelim<-1
+  if (is.na(params$Fbetaofalpha)) params$Fbetaofalpha <- 1
+  if (is.na(params$Ralphatokelim)) params$Ralphatokelim <- 1
 
-  if (params$Fgutabs>1) params$Fgutabs<-1
-  if (params$Fbetaofalpha>1) params$Fbetaofalpha<-1
-  if (params$Ralphatokelim<1) params$Ralphatokelim<-1
+  if (params$Fgutabs > 1) params$Fgutabs <- 1
+  if (params$Fbetaofalpha > 1) params$Fbetaofalpha <- 1
+  if (params$Ralphatokelim < 1) params$Ralphatokelim <- 1
 
-  alpha <- params$Ralphatokelim*(params$kelim+10^-6)
-  beta <- params$Fbetaofalpha*alpha
+  alpha <- params$Ralphatokelim * (params$kelim + 10^-6)
+  beta <- params$Fbetaofalpha * alpha
 
   # try to keep k21 and k12 positive:
-  k21 <- max(min(alpha*beta/params$kelim,alpha+beta-params$kelim),0)
+  k21 <- max(min(alpha * beta / params$kelim, alpha + beta - params$kelim), 0)
[…]

### 2022-02-16 figures_01312022.Rmd
switch branch test

@@
 
-write.csv(PK.fit.table.1comp[[1]] <- "inst/ext/PK.fit.table.1comp.DATE.csv")
-write.csv(PK.fit.table.1comp[[2]] <- "inst/ext/processed.1comp.data.DATE.csv")
-
-write.csv(PK.fit.table.2comp[[1]] <- "inst/ext/PK.fit.table.1comp.DATE.csv")
-write.csv(PK.fit.table.2comp[[2]] <- "inst/ext/processed.1comp.data.DATE.csv")
+write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
+write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)
+
+write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
+write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
 ```
@@
 pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
-pk_output_2comp_12212021 <- read.csv("inst/ext/PK.fit.table.2comp.12212021.csv")
+pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
+pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")
 
@@
 raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
-raw_2comp_12212021 <- read.csv("inst/ext/processed.2comp.data.12212021.csv")
+raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
+raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")
 
@@
 save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
-save(pk_output_2comp_12212021, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
+save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
+save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
 save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
-save(raw_2comp_12212021, file = "figures_rdata/raw_2comp_12212021.Rdata")
+save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
+save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")
 save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")
@@
 ### save cp data
-save(cp_df, file = "figures_rdata/cp_df.Rdata")
+# save(cp_df, file = "figures_rdata/cp_df.Rdata")
 ```
@@
 ### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data2 <- pk_output_2comp_12212021 %>%
+pk_data2 <- pk_output_2comp_02102022 %>%
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
 
-raw_data2 <- dplyr::select(raw_2comp_12212021, -c("kelim", 
+raw_data2 <- dplyr::select(raw_2comp_02102022, -c("kelim", 
                                                   "Vdist", 
@@
 cp_df <- rbind(cp_df_1, cp_df_2)
+
+cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
+
+cp_df <- cp_df %>% group_by(Species.x, 
+                            Compound,
+                            CAS,
+                            type) %>%
+  mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))
 
@@
 p
+```
+
+```{r, make_cp_error_histogram}
+
+##################
+##################
+
+data <- cp_df_12212021
+
+##################
+##################
+
+data <- data %>%
+  filter(cp != 1e-20)
+
+data <- data %>%
+  distinct(Species.x, Compound, CAS, cp_pred_error_range)
+
+p <- ggplot(data = data,
+            mapping = aes(x = cp_pred_error_range)) +
+  geom_histogram() +
+  scale_x_log10() +
+  facet_wrap(. ~type)
+
+p
+```
+
+```{r, make_cp_error_versus_dose}
+
+##################
+##################
+
+data <- cp_df_12212021
+
+##################
+##################
+
+data <- data %>%
+  filter(type == "1-Compartment")
+
+data <- data %>%
+  group_by(Compound, CAS, Dose) %>%
+  mutate(average = mean(cp_pred_error))
+
+p <- ggplot(data = data, mapping = aes(x = Dose, y = average)) +
+  geom_point() +
+  scale_x_log10() +
+  scale_y_log10()
+
+p
+
 ```
@@
 
-data2 <- pk_output_2comp_12212021 %>%
+data2 <- pk_output_2comp_02102022 %>%
   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
@@
        y = "Number of observations") +
-  facet_wrap(.~ model)
+  facet_wrap(.~ model) +
+  geom_vline(xintercept = 2.22e-06)
 # stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))
@@
 
-data2 <- as.data.table(pk_output_2comp_12212021 %>%
+data2 <- as.data.table(pk_output_2comp_02102022 %>%
                          filter(param.value.type == "Fitted geometric mean"))
@@
 
-raw_data2 <- raw_2comp_12212021
-
-pk_data2 <- pk_output_2comp_12212021 %>% 
+raw_data2 <- raw_2comp_02102022
+
+pk_data2 <- pk_output_2comp_02102022 %>% 
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
@@
 
-pk_data2 <- pk_output_2comp_12212021
+pk_data2 <- pk_output_2comp_02102022
 
@@
 pk_data1 <- as.data.table(pk_output_1comp_12212021)
-pk_data2 <- as.data.table(pk_output_2comp_12212021)
+pk_data2 <- as.data.table(pk_output_2comp_02102022)
 
@@
   filter(n() == 2) %>% ### group_by compound and only keep compounds with two observations, aka neither model worked
-    mutate(model = NULL) %>% ### get ride of model column
+  mutate(model = NULL) %>% ### get rid of model column
   distinct() ### discard repeated compound names
@@
 
-```{r}
+```{r, compare_AIC}
+
+##################
+##################
+
+pk_data1 <- pk_output_1comp_12212021
+
+pk_data2 <- pk_output_2comp_02102022
+
+pk_data_flat <- pk_output_flat_02102022 %>%
+  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")
+
+##################
+##################
+
+### make both data.frames have the same column names so they are rbind-able
+pk_data1 <- pk_data1[, intersect(intersect(colnames(pk_data2), colnames(pk_data_flat)), colnames(pk_data1))]
+pk_data2 <- pk_data2[, intersect(intersect(colnames(pk_data1), colnames(pk_data_flat)), colnames(pk_data2))]
+pk_data_flat <- pk_data_flat[, intersect(intersect(colnames(pk_data1), colnames(pk_data2)), colnames(pk_data_flat))]
+
+pk_data1 <- pk_data1 %>%
+  rename(LogLikelihood_1 = LogLikelihood,
+         AIC_1 = AIC,
+         sigma_value_1 = sigma_value) %>%
+  mutate(model = NULL) %>%
+  mutate(model.type = NULL)
+
+pk_data2 <- pk_data2 %>%
+  rename(LogLikelihood_2 = LogLikelihood,
+         AIC_2 = AIC,
+         sigma_value_2 = sigma_value) %>%
+  mutate(model = NULL) %>%
+  mutate(model.type = NULL)
+
+pk_data_flat <- pk_data_flat %>%
+  rename(LogLikelihood_flat = LogLikelihood,
+         AIC_flat = AIC,
+         sigma_value_flat = sigma_value) %>%
+  mutate(model = NULL) %>%
+  mutate(model.type = NULL)
+
+pk_all <- left_join(pk_data1, pk_data2, by = c("CAS",
+                                              "Species",
+                                              "param.value.type",
+                                              "sigma_id",
+                                              "Reference",
+                                              "Data.Analyzed",
+                                              "Compound"))
+
+pk_all <- left_join(pk_all, pk_data_flat, by = c("CAS",
+                                              "Species",
+                                              "param.value.type",
+                                              "sigma_id",
+                                              "Reference",
+                                              "Data.Analyzed",
+                                              "Compound"))
+
+pk_all <- subset(pk_all, select = c(CAS, Species, Compound, Reference, AIC_1, AIC_2, AIC_flat))
+
+pk_all <- distinct(pk_all)
+
+pk_all$AIC_1[pk_all$AIC_1 == Inf] <- NA
+pk_all$AIC_2[pk_all$AIC_2 == Inf] <- NA
+pk_all$AIC_flat[pk_all$AIC_flat == Inf] <- NA
+
+pk_all <- pk_all %>%
+  mutate(flat_lowest = ifelse(AIC_flat < AIC_1 & AIC_flat < AIC_2, 1, 0)) %>%
+  mutate(flat_better_than_1 = ifelse(AIC_flat < AIC_1 & AIC_flat > AIC_2, 1, 0)) %>%
+  mutate(flat_better_than_2 = ifelse(AIC_flat > AIC_1 & AIC_flat < AIC_2, 1, 0))
+
+pk_just_bad <- pk_all %>%
+  filter(flat_lowest == 1 | flat_better_than_1 == 1 | flat_better_than_2)
+```
+
+```{r, lombardo_comparisons}
 

### 2022-02-23 cook_sot_march.Rmd
copied poster files from main branch

---
title: <b>EPA's Concentration <i>versus</i> Time Database&colon; <br>
    A Resource for Extrapolating Toxicokinetic Trends Across Chemicals</b>
author:
  - name: Christopher Cook
    affil: 1,2
  - name: Lucas Albrecht
    affil: 1
  - name: Grace Cary
    affil: 1,2
  - name: Brenda Edwards
    affil: 1
  - name: Derik Haggard
    affil: 1
  - name: Nancy Hanley
    affil: 1
  - name: Michael F. Hughes
    affil: 1
  - name: Anna Jarnagin
    affil: 1,2
  - name: Tirumula D. Kodavanti
    affil: 1,2
  - name: Evgenia Koral-Bexell
    affil: 1,2
  - name: Anna Kreutz
    affil: 1,2
  - name: Mayla Ngo
    affil: 1,2
  - name: Caitlyn Patullo
    affil: 1,2
  - name: Caroline Ring
    affil: 1
  - name: Risa Sayre
    affil: 1,3
  - name: Bhaskar Sharma
    affil: 1
  - name: Jonathan Wall
    affil: 1
  - name: Hiroshi Yamazaki
    affil: 4
  - name: John Wambaugh
    affil: 1
affiliation:
  - num:
    address: "<br> ^1^Center for Computational Toxicology and Exposure, Office of Research and Development, United States Environmental Protection Agency, Durham, North Carolina"
  - num:
    address: "^2^Oak Ridge Institute for Science and Education, Oak Ridge, Tennessee"
  - num:
    address: "^3^Department of Environmental Sciences and Engineering, University of North Carolina at Chapel Hill, Chapel Hill, North Carolina"
  - num:
    address: "^4^Showa Pharmaceutical University, Tokyo, Japan"
column_numbers: 5
logoleft_name: "poster/epa_logo_white.png"
output: 
  posterdown::posterdown_html:
    self_contained: FALSE
titlebox_height: "18%"
body_textsize: "45px"
primary_colour: "#005780"
columnline_col: "#001d2b"
title_textsize: "100pt"
author_textsize: "50pt"
affilition_textsize: "30pt"
titlebox_bordercol: "##005780"
titlebox_borderwidth: "0.1in"
sectitle_bordercol: "#001d2b"
sectitle_borderwidth: "1mm"
font_family: Arimo
titletext_fontfamily: Arimo
bibliography: "poster/references.bib"
nocite: "@*"
poster_height: "43in"
poster_width: "89in"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
```

```{r, include = FALSE}
library(tidyverse)
library(data.table)
devtools::load_all(".")
```

```{r, load_data}

### load all of this wonderful data
load("figures_rdata/pk_output_1comp_12212021.Rdata")
load("figures_rdata/pk_output_2comp_12212021.Rdata")
load("figures_rdata/raw_1comp_12212021.Rdata")
load("figures_rdata/raw_2comp_12212021.Rdata")
load("figures_rdata/cp_df_12212021.Rdata")
load("figures_rdata/cvt_variability_df_12212021.Rdata")
load("figures_rdata/pk_lombardo_02072022.Rdata")
```

# 1 Expansion of the Concentration *versus* Time Database

## **1a) What is the CvTdb?**

* The Concentration *versus* Time Database  (CvTdb) is a database of standardized CvT data (time-course data of chemical compound concentrations measured *in vivo*) from hundreds of diverse publications, and serves as a platform for assessing PK/TK models on a large set of data. (Sayre, Grulke, and Wambaugh, 2020).

```{r, out.width="60%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
knitr::include_graphics("poster/tk_curve.png")
```

* The CvTdb contains 181 unique analytes, including 54 pharmaceuticals (~30%). 96 analytes are present in EPA's ToxCast dataset (~53%).

## **1b) Integration of Data Shared by Other Institutions**

* Showa Pharmaceutical University shared CvT data consisting of over 200 unique compounds (Kamiya *et al.*, 2020; Kamiya *et al.*, 2021).

* If YOU have CvT data, please consider collaborating with us! Visit [https://github.com/USEPA/CompTox-PK-CvTdb](https://github.com/USEPA/CompTox-PK-CvTdb) or email Wambaugh.John@epa.gov

## **1c) In-House Curation Workflow**
1) Identify publications with CvT data using PubMed queries

2) Manually extract CvT data using [WebPlotDigitizer](https://automeris.io/WebPlotDigitizer/)

3) Curate CvT data and metadata using EPA's *.xlsx* template

4) Screen template using *CvTdbQA*, an R Shiny application that checks template for format and reconstructs plots based on reported CvT data

5) Manually check template for format and data correctness

6) Normalize metadata units using an R script workflow, while also retaining original values

7) Push template to CvTdb

# 2 Toxicokinetic Trends Across Chemicals

* We can explore trends across chemicals and references using the CvTdb.

* "In PBPK modeling, predictions that are, on average, within a **factor of 2** of the experimental
data have frequently been considered adequate" (WHO, 2010).

* In Figure 2, 84.9% of replicate timepoint data in the CvTdb is within a factor of two of their respective mean. The "factor of two" rule may not be appropriate if the data is spread beyond a factor of two.

```{r, make_cvt_variability_histogram}

#################
#################

data <- cvt_variability_df_12212021

#################
#################

p <- ggplot(data, aes(x = conc_norm)) +
  geom_histogram() +
  xlim(c(0, 4)) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  theme_bw() +
  labs(x = "Normalized concentration",
       y = "Number of observations")
p
```

# 3 Introducing *invivoPKfit*

## **3a What is *invivoPKfit*?**

* R package that fits 1- and 2- compartment models to CvT data and extrapolates TK parameter values (e.g., half-life, elimination rate, and volume of distribution)

```{r, out.width="30%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
knitr::include_graphics("poster/pk_workflow.png")
```

## **3b TK Model Descriptions**
|    **<span style="text-decoration:underline">1-Compartment Model</span>**

```{r, fig.cap = "1-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center",  out.width = "60%"}
knitr::include_graphics("poster/1_comp.png")
```

$$
C_{iv}(dose,\ t)\ =\ \frac{dose}{V_d} e ^ {(-k_{elim}\ *\ t)}
$$

$$
C_{oral}(dose,\ t)\ =\ \frac{F_{bio}\ *\ dose}{V_{d}}\ *\ \frac{k_{abs}\ *\ (e ^ {-k_{elim}\ *\ t}\ -\ e ^ {-k_{abs}\ *\ t})}{k_{abs}\ -\ k_{elim}}   
$$

* Parameters include $V_d$ (volume of distribution), $k_{elim}$ (elimination rate), $k_{abs}$ (absorption rate; oral only), and $F_{bio}$ (fraction bioavailable; oral only).

|    **<span style="text-decoration:underline">2-Compartment Model</span>**

```{r, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "60%"}
knitr::include_graphics("poster/2_comp.png")
```

$$
C_{iv}(dose,\ t)\ =\ A\ *\ e^{-\alpha\ *\ t}\ +\ B\ *\ e^{-\beta\ *\ t}
$$  
$$
C_{oral}(dose,\ t)\ =\ A\ *\ e^{-\alpha\ *\ t}\ +\ B\ *\ e^{-\beta\ *\ t}\ +\ C\ *\ e^{-ka\ *\ t}
$$
* Parameters include $V1$ (volume of primary compartment), $k_{elim}$, $k_{12}$ (distribution rate to deep compartment), $k_{21}$ distribution rate from deep compartment), $k_{abs}$ (oral only), $F_{bio}$ (oral only).

## **3c Statistical Model Description**

* *invivoPKfit* calculates the probability of $C_{obs}$ given a PK model $M(p,\ t)$ and a statistical model $S(\sigma)$, where $P\ =\ L(C_{obs},\ M,\ S)$, and assumes that $C_{obs}$ are log-normally distributed around the concentrations predicted by $M(p,\ t)$ (Cox and Hinkley, 1979).

$$
ln\ L(x,\ \mu,\ \sigma)\ =\ \Sigma_{i=1,n}ln\frac{1}{x\sigma \sqrt{2\pi}}e^{-\frac{1}{2}\left( \frac{ln\ x\ -\ \mu)}{\sigma} \right)^2}
$$

$$
ln\ L(x,\ \mu,\ \sigma)\ =\ \Sigma_{i=1,n}ln\frac{1}{C_{obs,i}\sigma \sqrt{2\pi}}e^{-\frac{1}{2}\left( \frac{ln\ C_{obs,i}\ -\ M(p,t_i)}{\sigma} \right)^2}
$$

```{r, warning = FALSE, fig.align = "center", out.width = "60%", fig.cap = "Log-Normal Distribution"}
load(file = "poster/lognormal.Rdata")
p9
```

* The R package, [*optimx*](https://cran.r-project.org/web/packages/optimx/index.html) (Nash and Varadhan, 2011; Nash, 2014) optimizes the log-likelihood equation and estimates $p$ and $\sigma$

* We used the Hessian of the likelihood function to estimate standard deviations of the log parameter (Dovi, 1991)

# 4 ** *invivoPKfit* Analyses**

## **4a Predicted Concentrations**

* 58.4% of 12134 concentrations predicted by the 1-compartment model fit within a factor of two of the observed concentrations.

* 64.8% of 9684 concentrations predicted by the 2-compartment model fit within a factor of two of the observed concentrations.

```{r, make_cp_histogram}

##################
##################

data <- cp_df_12212021

##################
##################

p <- ggplot(data = data,
            mapping = aes(x = cp_norm)) +
  geom_histogram(bins = 30) +
  geom_vline(xintercept = c(0.5, 2),
             color = "Red",
             linetype = "dashed") +
  # xlim(0, 1e42) +
  # ylim(0, 400) +
  # scale_y_log10()+
  theme(title = element_text(size = 16),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 14)) +
  scale_x_log10(limits = c(0.01, 1000)) +
  theme_bw() +
  labs(x = "Predicted/Observed",
       y = "Number of Observations") +
  facet_wrap(. ~ type)

p
```

## **4b *invivoPKfit* Performance *versus* Data Variability**

* Can start to gauge how data variability influences the performance of a model

```{r, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "100%"}
knitr::include_graphics("poster/density_plot.png")
```

## **4c Diagnosing Poor Fits**

# What's Next?

# References

# Acknowledgements/Disclaimers

### 2022-02-23 cook_sot_march.Rmd
checking plot_conctime
skeleton of poster

@@
 
-```{r, load_data}
+```{r, load_data, include=FALSE}
 
@@
 
-```{r, out.width="60%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
+```{r, exp_plot, out.width="65%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
 knitr::include_graphics("poster/tk_curve.png")
@@
 
-## **1c) In-House Curation Workflow**
-1) Identify publications with CvT data using PubMed queries
-
-2) Manually extract CvT data using [WebPlotDigitizer](https://automeris.io/WebPlotDigitizer/)
-
-3) Curate CvT data and metadata using EPA's *.xlsx* template
-
-4) Screen template using *CvTdbQA*, an R Shiny application that checks template for format and reconstructs plots based on reported CvT data
-
-5) Manually check template for format and data correctness
-
-6) Normalize metadata units using an R script workflow, while also retaining original values
-
-7) Push template to CvTdb
-
 # 2 Toxicokinetic Trends Across Chemicals
@@
 
-```{r, make_cvt_variability_histogram}
+```{r, make_cvt_variability_histogram, out.width = "75%", fig.align = "center", fig.cap = "The CvTdb data was grouped into unique combinations of compound/reference/route/dose/timepoint.
+Groups without replicate timepoints were removed.
+If all replicate timepoints corresponded to non-detect concentration values, those data were removed.
+If some, but not all replicate timepoints corresponded to non-detect concentration values, those values were set to equal 0.45 of the minimum value.
+Each concentration was normalized by the mean concentration of each group."}
 
@@
 
-## **3a What is *invivoPKfit*?**
+## **3a) What is *invivoPKfit*?**
 
@@
 
-```{r, out.width="30%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
+```{r, workflow, out.width="30%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
 knitr::include_graphics("poster/pk_workflow.png")
@@
 
-## **3b TK Model Descriptions**
+## **3b) TK Model Descriptions**
 |    **<span style="text-decoration:underline">1-Compartment Model</span>**
 
-```{r, fig.cap = "1-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center",  out.width = "60%"}
+```{r, 1_comp, fig.cap = "1-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center",  out.width = "75%"}
 knitr::include_graphics("poster/1_comp.png")
@@
 
-```{r, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "60%"}
+```{r, 2_comp, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "75%"}
 knitr::include_graphics("poster/2_comp.png")
@@
 
-## **3c Statistical Model Description**
+## **3c) Statistical Model Description**
 
@@
 
-```{r, warning = FALSE, fig.align = "center", out.width = "60%", fig.cap = "Log-Normal Distribution"}
+```{r, log, warning = FALSE, fig.align = "center", out.width = "60%", fig.cap = "Log-Normal Distribution"}
 load(file = "poster/lognormal.Rdata")
@@
 
+|    **<span style="text-decoration:underline">Interstudy Variability</span>**
+
+```{r, interstudy, fig.align = "center", out.width = "100%", fig.cap = "Log-Normal Distribution"}
+knitr::include_graphics("poster/interstudy.png")
+```
+
 # 4 ** *invivoPKfit* Analyses**
 
-## **4a Predicted Concentrations**
+## **4a) Predicted Concentrations**
 
@@
 
-```{r, make_cp_histogram}
+```{r, make_cp_histogram, fig.align = "center", out.width = "75%", fig.cap = "Concentrations were predicted by applying estimated model parameters to the timepoints present in the data.
+Predicted concentrations were normalized by observed concentrations.
+This plot does not include 'Joint Analysis' models.
+The red dashed lines mark the 'factor of two' bounds."}
 
@@
 
-## **4b *invivoPKfit* Performance *versus* Data Variability**
+## **4b) *invivoPKfit* Performance *versus* Data Variability**
 

### 2022-02-23 figures_01312022.Rmd
skeleton of poster

@@
 ### 2 compartment
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_12212021),
-                      data.set = as.data.table(raw_2comp_12212021),
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_02102022),
+                      data.set = as.data.table(raw_2comp_02102022),
                       model = "2compartment")

### 2022-02-23 R/plot_conctime.R

@@ -138,11 +138,11 @@ plot_conctime <- function(PK.fit.table,
 
         this.medium.data <- this.reference.data[Media == this.medium]
 
-        this.medium.data[, "Value"][is.na(this.medium.data[, "Value"])] <- this.medium.data[, mean(LOQ)]
+        this.medium.data[, "Value"][is.na(this.medium.data[, "Value"])] <- 2 * this.medium.data[, mean(LOQ)]
 
         ### do this without converting to and back from a data.frame
         this.medium.data <- as.data.frame(this.medium.data)
-        this.medium.data$L.O.Q. <- ifelse(this.medium.data$Value <= mean(this.medium.data$LOQ), "Below", "Above")
+        this.medium.data$L.O.Q. <- ifelse(this.medium.data$Value <= mean(2 * this.medium.data$LOQ), "Below", "Above")
         this.medium.data <- as.data.table(this.medium.data)
         this.medium.data <- this.medium.data[, LOQ. := as.factor(L.O.Q.)]
 

### 2022-03-31 cook_sot_march.Rmd
Rmarkdown figure edits

@@
 logoleft_name: "poster/epa_logo_white.png"
+logoright_name: "poster/session_info.png"
 output: 
@@
 titlebox_height: "18%"
-body_textsize: "45px"
+body_textsize: "50px"
 primary_colour: "#005780"
@@
 author_textsize: "50pt"
-affilition_textsize: "30pt"
+affilition_textsize: "50pt"
 titlebox_bordercol: "##005780"
@@
 bibliography: "poster/references.bib"
+# csl: "poster/computational-toxicology.csl"
 nocite: "@*"
@@
 ---
+
+<style>
+body {
+text-align: left}
+</style>
 
@@
 ### load all of this wonderful data
-load("figures_rdata/pk_output_1comp_12212021.Rdata")
-load("figures_rdata/pk_output_2comp_12212021.Rdata")
-load("figures_rdata/raw_1comp_12212021.Rdata")
-load("figures_rdata/raw_2comp_12212021.Rdata")
-load("figures_rdata/cp_df_12212021.Rdata")
-load("figures_rdata/cvt_variability_df_12212021.Rdata")
-load("figures_rdata/pk_lombardo_02072022.Rdata")
+load("figures_rdata/pk_output_1comp_03012022.Rdata")
+load("figures_rdata/pk_output_2comp_03012022.Rdata")
+load("figures_rdata/pk_output_flat_03012022.Rdata")
+load("figures_rdata/raw_1comp_03012022.Rdata")
+load("figures_rdata/raw_2comp_03012022.Rdata")
+load("figures_rdata/raw_flat_03012022.Rdata")
+load("figures_rdata/cp_df_03012022.Rdata")
+load("figures_rdata/cvt_variability_df_03012022.Rdata")
 ```
@@
 
-* The Concentration *versus* Time Database  (CvTdb) is a database of standardized CvT data (time-course data of chemical compound concentrations measured *in vivo*) from hundreds of diverse publications, and serves as a platform for assessing PK/TK models on a large set of data.
+* The Concentration *versus* Time Database  (CvTdb) is a database of standardized time-course data of chemical compound concentrations measured *in vivo* from hundreds of diverse publications.
+It serves as a platform for assessing PK/TK models on a large set of data.
 (Sayre, Grulke, and Wambaugh, 2020).
 
-```{r, exp_plot, out.width="65%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
+```{r, tk-curve, out.width="60%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
 knitr::include_graphics("poster/tk_curve.png")
@@
 
-* The CvTdb contains 181 unique analytes, including 54 pharmaceuticals (~30%). 96 analytes are present in EPA's ToxCast dataset (~53%).
+* The CvTdb contains 389 unique chemicals, including 70 pharmaceuticals (~30%). 101 analytes are present in EPA's ToxCast dataset (~53%).
 
@@
 
-* In Figure 2, 84.9% of replicate timepoint data in the CvTdb is within a factor of two of their respective mean.
-The "factor of two" rule may not be appropriate if the data is spread beyond a factor of two.
+* In Figure 2, 85.1% of replicate timepoint data in the CvTdb is within a factor of two of their respective mean.
+The "factor of two" rule may not be appropriate if the data itself is spread beyond a factor of two.
 
-```{r, make_cvt_variability_histogram, out.width = "75%", fig.align = "center", fig.cap = "The CvTdb data was grouped into unique combinations of compound/reference/route/dose/timepoint.
+```{r, make-cvt-variability-histogram, out.width = "65%", fig.align="center", fig.cap = "The CvTdb data was grouped into unique combinations of compound/reference/route/dose/timepoint.
 Groups without replicate timepoints were removed.
@@
 
-data <- cvt_variability_df_12212021
+data <- cvt_variability_df_03012022
 
@@
 p <- ggplot(data, aes(x = conc_norm)) +
-  geom_histogram() +
+  geom_histogram(binwidth = 0.25) +
   xlim(c(0, 4)) +
@@
 
-```{r, workflow, out.width="30%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
+```{r, workflow, out.width="35%", fig.align="center", fig.cap="_invivoPKfit_ workflow."}
 knitr::include_graphics("poster/pk_workflow.png")
@@
 
-```{r, 1_comp, fig.cap = "1-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center",  out.width = "75%"}
+```{r, one-comp, fig.align="center", out.width = "69%", fig.cap="1-Compartment Model. Adapted from Wambaugh et al. (2018)."}
 knitr::include_graphics("poster/1_comp.png")
@@
 
-```{r, 2_comp, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "75%"}
+```{r, two-comp, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "69%"}
 knitr::include_graphics("poster/2_comp.png")
@@
 $$
+
 * Parameters include $V1$ (volume of primary compartment), $k_{elim}$, $k_{12}$ (distribution rate to deep compartment), $k_{21}$ distribution rate from deep compartment), $k_{abs}$ (oral only), $F_{bio}$ (oral only).
@@
 
-```{r, log, warning = FALSE, fig.align = "center", out.width = "60%", fig.cap = "Log-Normal Distribution"}
+```{r, lognormal, warning = FALSE, fig.align = "center", out.width = "70%", fig.cap = "Log-Normal Distribution"}
 load(file = "poster/lognormal.Rdata")
@@
 
-* The R package, [*optimx*](https://cran.r-project.org/web/packages/optimx/index.html) (Nash and Varadhan, 2011; Nash, 2014) optimizes the log-likelihood equation and estimates $p$ and $\sigma$
+* The R package, [*optimx*](https://cran.r-project.org/web/packages/optimx/index.html) (Nash and Varadhan, 2011; Nash, 2014) optimizes the log-likelihood equation and estimates $p$ and $\sigma$.
 
-* We used the Hessian of the likelihood function to estimate standard deviations of the log parameter (Dovi, 1991)
+* We used the Hessian of the likelihood function to estimate standard deviations of the log parameter (Dovi, 1991).
 
-|    **<span style="text-decoration:underline">Interstudy Variability</span>**
-
-```{r, interstudy, fig.align = "center", out.width = "100%", fig.cap = "Log-Normal Distribution"}
-knitr::include_graphics("poster/interstudy.png")
-```
-
-# 4 ** *invivoPKfit* Analyses**
+# 4 *invivoPKfit* Analyses
 
@@
 
-* 58.4% of 12134 concentrations predicted by the 1-compartment model fit within a factor of two of the observed concentrations.
+* 63.3% of 16,675 concentrations predicted by the 1-compartment model fit within a factor of two of the observed concentrations.
 
-* 64.8% of 9684 concentrations predicted by the 2-compartment model fit within a factor of two of the observed concentrations.
+* 69.1% of 13,097 concentrations predicted by the 2-compartment model fit within a factor of two of the observed concentrations.
 
-```{r, make_cp_histogram, fig.align = "center", out.width = "75%", fig.cap = "Concentrations were predicted by applying estimated model parameters to the timepoints present in the data.
-Predicted concentrations were normalized by observed concentrations.
-This plot does not include 'Joint Analysis' models.
-The red dashed lines mark the 'factor of two' bounds."}
+```{r, make-cp-histogram, out.width="65%", fig.align="center", fig.cap = "Concentrations were predicted using the estimated model parameters.
+Predicted concentrations were normalized by observed concentrations, such that C~pred~ / C~obs~ .
+The red dashed lines mark the ‘factor of two’ bounds.
+This plot does not include ‘Joint Analysis’ fits."}
 
@@
 
-data <- cp_df_12212021
+data <- cp_df_03012022
 
@@
             mapping = aes(x = cp_norm)) +
-  geom_histogram(bins = 30) +
+  geom_histogram(bins = 32) +
   geom_vline(xintercept = c(0.5, 2),
@@
              linetype = "dashed") +
-  # xlim(0, 1e42) +
-  # ylim(0, 400) +
-  # scale_y_log10()+
   theme(title = element_text(size = 16),
@@
 
-```{r, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "100%"}
-knitr::include_graphics("poster/density_plot.png")
+```{r, print-density-plot, out.width="100%", fig.align = "center", fig.cap="Predicted concentrations were normalized by observed concentrations (see Figure 7), and plotted against observed concentrations normalized by experiment-timpoint specific replicates (see Figure 2).
+The dashed lines mark the 'factor of 2' bounds for each axis.
+Sections were assigned based on both the ability of a model to accurately predict an observed concentration and the spread of the observed data.
+Points colored pink represent concentrations significantly underpredicted by the model."}
+
+knitr::include_graphics("poster/density_plot_v4.png")
 ```
 
-## **4c Diagnosing Poor Fits**
+```{r, make-density-plot, out.width = "70%", fig.align = "center", fig.cap="Predicted concentrations were normalized by observed concentrations (see Figure 7), and plotted against observed concentrations normalized by experiment-timpoint specific replicates (see Figure 2).
+The dashed lines mark the 'factor of 2' bounds for each axis.
+Sections were assigned based on both the ability of a model to accurately predict an observed concentration and the spread of the observed data.", eval = FALSE}
 
-# What's Next?
+##################
+##################
+
+pk_data <- cp_df_03012022
+
+cvt_data <- cvt_variability_df_03012022
+
+##################
+##################
+
+row.names(pk_data) <- c()
+
+cvt_data <- dplyr::select(cvt_data, -c("kelim", 
+                                       "Vdist", 
+                                       "Fgutabs", 
+                                       "kgutabs"))
+
+### split pk_data by model so you can properly join with raw data
+model_split <- split(pk_data, pk_data$model)
+
+cvt_data$Reference <- as.character(cvt_data$Reference)
+
+cvt_data$type <- "1-Compartment"
+full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
+
+cvt_data$type <- "2-Compartment"
+full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
+
+### put data back together
+full_data <- rbind(full_data_1, full_data_2)
+
+full_data <- full_data %>%
+  filter(cp != 0) %>%
+  filter(Compound != "triclosan")
+  # filter(Compound != "tamoxifen")
+
+###########
+###########
+###########
+
+### Find number of points in each plot panel for 1-compartment
+full_data_1_center <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
+full_data_1_center <- full_data_1_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
+ratio_1_center <- nrow(full_data_1_center) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
+
+full_data_1_green <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
+full_data_1_green <- full_data_1_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
+ratio_1_green <- nrow(full_data_1_green) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
+
+full_data_1_gray <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
+full_data_1_gray <- full_data_1_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
+ratio_1_gray <- nrow(full_data_1_gray) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
+
+full_data_1_tan <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
+full_data_1_tan <- full_data_1_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
+ratio_1_tan <- nrow(full_data_1_tan) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
+
+###########
+###########
+
+### Find number of points in each plot panel for 2-compartment
+full_data_2_center <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
+full_data_2_center <- full_data_2_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
+ratio_2_center <- nrow(full_data_2_center) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
+
+full_data_2_green <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
+full_data_2_green <- full_data_2_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
+ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
+
+full_data_2_gray <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
+full_data_2_gray <- full_data_2_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
+ratio_2_gray <- nrow(full_data_2_gray) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
+
+full_data_2_tan <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
+full_data_2_tan <- full_data_2_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
+ratio_2_tan <- nrow(full_data_2_tan) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
+
+outlier_df <- full_data %>%
+
+p <- ggplot() +
+  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
+  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
+  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
+  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
+  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
+  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
+  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#E1B07E") +
+  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
+  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0.5, ymax = 2.0, alpha = 0.5, fill = "black") +
+  theme_bw() +
+  theme(panel.spacing = unit(2, "lines")) +
+  geom_bin2d(data = full_data,
+            mapping = aes(x = conc_norm, y = cp_norm),
+            bins = 100) +
+  scale_fill_distiller(palette = "Blues") +
+  geom_vline(xintercept = c(0.5, 2),
+             linetype = "dashed") +
+  geom_hline(yintercept = c(0.5, 2),
+             linetype = "dashed") +
+  scale_x_log10() +
+  scale_y_log10() +
+  labs(x = "Data Variability",
+       y = "Model Performance") +
+  facet_wrap(. ~ type)
+
+p
+```
+
+## **4c) Diagnosing Poor Fits**
+
+* Plotting model predictions against observed data can help determine why a model might fit poorly.
+A poor fit could indicate 1) a deficiency in the model, 2) an inaccurate curation of data, and/or 3) a deficiency in the experimental collection of data.
+
+```{r, out.width="100%", fig.align="center", fig.cap="1-compartment model (green line) and 2-compartment model (red line) fit through CvT data (gray points) Open points represent non-detects that were below the limit of quantitation (L.O.Q.)."}
+knitr::include_graphics("poster/fits.png")
+```
+
+<!-- # Conclusions and New Goals -->
+
+<!-- * The CvTdb is useful for the calibration and validation of TK models, as evidenced by our *invivoPKfit* analyses -->
+
+<!-- * The CvTdb can help answer questions regarding the goodness of fit of a model. Preliminary analyses suggest that the **factor of two** criterion may be too strict -->
+
+<!-- * To further gauge the performance of *invivoPKfit*, we need to compare our model parameter estimates with those estimated through more chemical-specific models. -->
 
@@
 
-# Acknowledgements/Disclaimers
+<font size = "5"> <div id="refs"></div> </font>
+
+<!-- <bibliography entry-spacing = "0.5" > <font size = "5"> <div id="refs"></div> </font> <bibliography entry-spacing = "0.5" > -->
+<!-- <font size = "5">  -->
+<!-- Boxenbaum, Harold G., Sidney Riegelman, and Robert M.
+Elashoff.
+1974.
+“Statistical Estimations in Pharmacokinetics.” Journal of Pharmacokinetics and Biopharmaceutics 2 (2): 123–48.
+https://doi.org/10.1007/BF01061504.
+-->
+<!-- Cox, D. R., and D. V. Hinkley. 1979. Theoretical Statistics. CRC Press. -->
+<!-- Dovi, V.
+G., O.
+Paladino, and A.
+P.
+Reverberi.
+1991.
+“Some Remarks on the Use of the Inverse Hessian Matrix of the Likelihood Function in the Estimation of Statistical Properties of Parameters.” Applied Mathematics Letters 4 (1): 87–90.
+https://doi.org/https://doi.org/10.1016/0893-9659(91)90129-J.
+-->
+<!-- Kamiya, Yusuke, Kentaro Handa, Tomonori Miura, Junya Ohori, Makiko Shimizu, Masato Kitajima, Fumiaki Shono, Kimito Funatsu, and Hiroshi Yamazaki.
+2021.
+“An Updated in Silico Prediction Method for Volumes of Systemic Circulation of 323 Disparate Chemicals for Use in Physiologically Based Pharmacokinetic Models to Estimate Plasma and Tissue Concentrations After Oral Doses in Rats.” Chemical Research in Toxicology 34 (10): 2180–3.
+https://doi.org/10.1021/acs.chemrestox.1c00249.
+-->
+<!-- Kamiya, Yusuke, Shohei Otsuka, Tomonori Miura, Manae Yoshizawa, Ayane Nakano, Miyu Iwasaki, Yui Kobayashi, et al.
+2020.
+“Physiologically Based Pharmacokinetic Models Predicting Renal and Hepatic Concentrations of Industrial Chemicals After Virtual Oral Doses in Rats.” Chemical Research in Toxicology 33 (7): 1736–51.
+https://doi.org/10.1021/acs.chemrestox.0c00009.
+-->
+<!-- Kudo, Naomi, Masanori Katakura, Yasunori Sato, and Yoichi Kawashima.
+2002.
+“Sex Hormone-Regulated Renal Transport of Perfluorooctanoic Acid.” Chemico-Biological Interactions 139 (3): 301–16.
+https://doi.org/10.1016/s0009-2797(02)00006-6.
+-->
+<!-- Nash, John C. 2014. “On Best Practice Optimization Methods in R.” Journal of Statistical Software 60 (2): 1–14. https://doi.org/10.18637/jss.v060.i02. -->
+<!-- Nash, John C., and Ravi Varadhan.
+2011.
+“Unifying Optimization Algorithms to Aid Software System Users: optimx for R.” Journal of Statistical Software 43 (9): 1–14.
+https://doi.org/10.18637/jss.v043.i09.
+-->
+<!-- O’Flaherty, E. J. 1981. Toxicants and Drugs: Kinetics and Dynamics. John Wiley & Sons. -->
+<!-- Sayre, Risa R., John F.
+Wambaugh, and Christopher M.
+Grulke.
+2020.
+“Database of Pharmacokinetic Time-Series Data and Parameters for 144 Environmental Chemicals.” Scientific Data 7 (1): 122.
+https://doi.org/10.1038/s41597-020-0455-1.
+-->
+<!-- Sheiner, L.
+B.
+1985.
+“Analysis of Pharmacokinetic Data Using Parametric Models.
+II.
+Point Estimates of an Individual’s Parameters.” Journal of Pharmacokinetics and Biopharmaceutics 13 (5): 515–40.
+https://doi.org/10.1007/BF01059333.
+-->
+<!-- Thorne, W.
+Brent.
+2019.
+Posterdown: An R Package Built to Generate Reproducible Conference Posters for the Academic and Professional World Where Powerpoint and Pages Just Won’t Cut It.
+https://github.com/brentthorne/posterdown.
+-->
+<!-- Wakefield, Jon, Leon Aarons, and Amy Racine. 1999. “The Bayesian Approach to Population Pharmacokinetic/Pharmacodynamic Modeling.” https://doi.org/10.1007/978-1-4612-1502-8_4. -->
+<!-- Wambaugh, John F., Michael F.
+Hughes, Caroline L.
+Ring, Denise K.
+MacMillan, Jermaine Ford, Timothy R.
+Fennell, Sherry R.
+Black, et al.
+2018.
+“Evaluating in Vitro-in Vivo Extrapolation of Toxicokinetics.” Toxicological Sciences : An Official Journal of the Society of Toxicology 163 (1): 152–69.
+https://doi.org/10.1093/toxsci/kfy020.
+-->
+<!-- World Health Organization. 2010. “Characterization and Application of Physiologically Based Pharmacokinetic Models in Risk Assessment.” WHO Document Production Services, Geneva, Switzerland. -->
+
+<!-- </font> -->
+
+# Acknowledgements
+<font size = "5"> Employees of the U.S.
+EPA were funded through EPA's Office of Research and Development.
+This project was supported in part by an appointment to the Research Participation Program at the Center for Computational Toxicology, U.S.
+Environmental Protection Agency, administered by the Oak Ridge Institute for Science and Education through an interagency agreement between the U.S.
+Department of Energy and EPA.
+*This work does not necessarily reflect U.S.
+EPA policy.* </font>

### 2022-03-31 figures_01312022.Rmd
Rmarkdown figure edits

@@
 data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
+data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
 
@@
   route.col = "administration_route_normalized",
-  source.col = "fk_extraction_document_id",
+  source.col = "document_id",
   loq.default = NA,
@@
 
-write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
-write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)
-
-write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
-write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
+# write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
+# write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)
+# 
+# write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
+# write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
 ```
@@
 
+pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
+pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
+pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")
+
 ### read in processed raw data files
@@
 
+raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
+raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
+raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")
+
 pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
@@
 ### save data
-save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
-save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
-save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
-save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
-save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
-save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")
+# save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
+# save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
+# save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
+# save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
+# save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
+# save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")
+
+save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
+save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
+save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
+save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
+save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
+save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")
+
 save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")
@@
 load("figures_rdata/cvt_variability_df_12212021.Rdata")
+
+load("figures_rdata/pk_output_1comp_03012022.Rdata")
+load("figures_rdata/pk_output_2comp_03012022.Rdata")
+load("figures_rdata/pk_output_flat_03012022.Rdata")
+load("figures_rdata/raw_1comp_03012022.Rdata")
+load("figures_rdata/raw_2comp_03012022.Rdata")
+load("figures_rdata/raw_flat_03012022.Rdata")
+load("figures_rdata/cp_df_03012022.Rdata")
+load("figures_rdata/cvt_variability_df_03012022.Rdata")
+
+load("figures_rdata/cp_df_03302022.Rdata")
+
 load("figures_rdata/pk_lombardo_02072022.Rdata")
@@
 ### 1 compartment
+
+pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
+  filter(Compound == "tamoxifen") %>%
+  filter(Data.Analyzed != "Joint Analysis")
+
+raw_1comp_03012022 <- raw_1comp_03012022 %>%
+  filter(Compound == "tamoxifen")
+
 junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_12212021),
@@
 ### 2 compartment
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_02102022),
-                      data.set = as.data.table(raw_2comp_02102022),
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_03012022),
+                      data.set = as.data.table(raw_2comp_03012022),
                       model = "2compartment")
@@
 ### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data1 <- pk_output_1comp_12212021 %>%
+pk_data1 <- pk_output_1comp_03012022 %>%
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
 
-raw_data1 <- dplyr::select(raw_1comp_12212021, -c("kelim", 
+raw_data1 <- dplyr::select(raw_1comp_03012022, -c("kelim", 
                                                   "Vdist", 
@@
 ### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data2 <- pk_output_2comp_02102022 %>%
+pk_data2 <- pk_output_2comp_03012022 %>%
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
 
-raw_data2 <- dplyr::select(raw_2comp_02102022, -c("kelim", 
+raw_data2 <- dplyr::select(raw_2comp_03012022, -c("kelim", 
                                                   "Vdist", 
@@
 
-### make both data.frames have the same column names so they are rbind-able
+###########
+### this is flat data
+###########
+
+pk_data_flat <- pk_output_flat_03012022 %>%
+  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
+
+raw_data_flat <- dplyr::select(raw_flat_03012022, -c("A"))
+
+raw_data_flat$Reference <- as.character(raw_data_flat$Reference)
+
+full_data_flat <- left_join(raw_data_flat, pk_data_flat, by = c("Compound", "CAS", "Reference"))
+full_data_flat <- full_data_flat %>% filter(AIC != Inf)
+split_df_flat <- split(full_data_flat, list(full_data_flat$Compound,
+                                            full_data_flat$Reference,
+                                            full_data_flat$CAS),
+                       drop = TRUE)
+
+### function that finds cp
+find_cp_flat <- function(full_data_flat) {plyr::adply(full_data_flat, 1, mutate, cp = cp_flat(time = Time,
+                                                                                              params = full_data_flat[1,],
+                                                                                              dose = Dose,
+                                                                                              iv.dose = iv))}
+cp_df_flat <- lapply(split_df_flat, find_cp_flat)
+
+cp_df_flat <- do.call(rbind, cp_df_flat)
+
+cp_df_flat$cp_norm <- cp_df_flat$cp / cp_df_flat$Value
+cp_df_flat$type <- "Flat"
+
+#######################
+#######################
+
+### make all data.frames have the same column names so they are rbind-able
 cp_df_1 <- cp_df_1[, intersect(colnames(cp_df_2), colnames(cp_df_1))]
@@
 cp_df <- rbind(cp_df_1, cp_df_2)
+
+cp_df <- cp_df[, intersect(colnames(cp_df_flat), colnames(cp_df))]
+cp_df_flat <- cp_df_flat[, intersect(colnames(cp_df), colnames(cp_df))]
+
+cp_df <- rbind(cp_df, cp_df_flat)
 
@@
 
-cp_df_12212021 <- cp_df
-
-save(cp_df_12212021, file = "figures_rdata/cp_df_12212021.Rdata")
+cp_df_03302022 <- cp_df
+
+save(cp_df_03302022, file = "figures_rdata/cp_df_03302022.Rdata")
 ```
@@
 
-data <- cp_df_12212021
+# data <- cp_df_12212021
+data <- cp_df_03012022
 
@@
 
-data <- as.data.table(raw_1comp_12212021)
+data <- as.data.table(raw_1comp_03012022)
 
@@
   ### only use data with replicate timepoints
-  data <- data[ ave(1:nrow(data), data$Time, fun = length) > 1 , ]
+  data <- data[ ave(1:nrow(data), data$Time, FUN = length) > 1 , ]
 
@@
 ### combine data.tables back into one large data.set
-cvt_variability_df_12212021 <- do.call(rbind, data.list)
-
-save(cvt_variability_df_12212021, file = "figures_rdata/cvt_variability_df_12212021.Rdata")
+cvt_variability_df_03012022 <- do.call(rbind, data.list)
+
+save(cvt_variability_df_03012022, file = "figures_rdata/cvt_variability_df_03012022.Rdata")
 ```
@@
 
-data <- cvt_variability_df_12212021
+data <- cvt_variability_df_03012022
+# data <- cvt_variability_df_12212021
 
@@
 p <- ggplot(data, aes(x = conc_norm)) +
-  geom_histogram() +
-  xlim(c(0, 4)) +
+  geom_histogram(binwidth = 0.25) +
+  xlim(c(-0.5, 4)) +
   geom_vline(xintercept = c(0.5, 2),
@@
 
-pk_data <- cp_df_12212021
-
-cvt_data <- cvt_variability_df_12212021
+# pk_data <- cp_df_03012022
+pk_data <- cp_df_03302022
+
+cvt_data <- cvt_variability_df_03012022
 
@@
 
-cvt_data <- dplyr::select(cvt_data, -c("X",
-                                       "kelim", 
+cvt_data <- dplyr::select(cvt_data, -c("kelim", 
                                        "Vdist", 
@@
 
+cvt_data$type <- "Flat"
+full_data_flat <- left_join(cvt_data, model_split$`flat`)
+
 ### put data back together
-full_data <- rbind(full_data_1, full_data_2)
-
-###########
-###########
-###########
+full_data <- rbind(full_data_1, full_data_2, full_data_flat)
+
+full_data <- full_data %>%
+  filter(cp != 0)
+
+full_data$AIC <- round(full_data$AIC, digits = 4)
+
+full_data <- full_data %>%
+  distinct(Compound, Reference, model, conc_norm, AIC, cp_norm)
+
+### 
+full_data <- full_data %>%
+  pivot_wider(names_from = model,
+              values_from = c(AIC, cp_norm)) %>%
+  unchop(everything())
+
+full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
+                                                      AIC_1compartment < AIC_flat ~ "1compartment",
+                                                    AIC_2compartment < AIC_1compartment &
+                                                      AIC_2compartment < AIC_flat ~ "2compartment",
+                                                    AIC_flat < AIC_1compartment &
+                                                      AIC_flat < AIC_2compartment ~ "flat",
+
+                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
+                                                      is.na(AIC_flat) ~ "1compartment",
+                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
+                                                      is.na(AIC_flat) ~ "2compartment",
+                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) & 
+                                                      is.na(AIC_2compartment) ~ "flat",
+
+                                                    is.na(AIC_1compartment) &
+                                                      AIC_flat < AIC_2compartment ~ "flat",
+                                                    is.na(AIC_1compartment) &
+                                                      AIC_2compartment < AIC_flat ~ "2compartment",
+                                                    is.na(AIC_2compartment) &
+                                                      AIC_flat < AIC_1compartment ~ "flat",
+                                                    is.na(AIC_2compartment) &
+                                                      AIC_1compartment < AIC_flat ~ "1compartment",
+                                                    is.na(AIC_flat) &
+                                                      AIC_1compartment < AIC_2compartment ~"1compartment",
+                                                    is.na(AIC_flat) &
+                                                      AIC_2compartment <AIC_1compartment ~"2compartment"))
+
+full_data <- full_data %>%
+  mutate(cp_norm = case_when(model == "1compartment" ~ cp_norm_1compartment,
+                             model == "2compartment" ~ cp_norm_2compartment,
+                             model == "flat" ~ cp_norm_flat))
+
+# full_data <- full_data %>%
+#   mutate(cp_norm = case_when(model == "1comparment" ~ cp_norm_1compartment,
+#                              model == "2compartment" ~ cp_norm_2compartment))
+
+# full_data$cp_norm[full_data$model == "2compartment"] <- full_data$cp_norm_2compartment
+# full_data$cp_norm[full_data$model == "1compartment"] <- full_data$cp_norm_1compartment
+
+# full_data <- full_data %>%
+# mutate(across(everything(), ~ifelse(. == "", NA, as.character(.))))
+
+# filter(Compound != "triclosan")
+# filter(Compound != "tamoxifen")
+
+###########
+###########
+###########
+
+split_full_data <- split(full_data, full_data$model)
+
+full_data_1 <- split_full_data$`1compartment`
 
@@
 
+full_data_2 <- split_full_data$`2compartment`
+
 ### Find number of points in each plot panel for 2-compartment
@@
 full_data_2_green <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_2_green <- full_data_2 %>% filter(cp_norm < 0.5 | cp_norm > 2)
+full_data_2_green <- full_data_2_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
 ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
@@
 ratio_2_tan <- nrow(full_data_2_tan) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
+
+###########
+###########
+
+full_data_flat <- split_full_data$`flat`
+
+### Find number of points in each plot panel for 2-compartment
+full_data_flat_center <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
+full_data_flat_center <- full_data_flat_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
+ratio_flat_center <- nrow(full_data_flat_center) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
+
+full_data_flat_green <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
+full_data_flat_green <- full_data_flat_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
+ratio_flat_green <- nrow(full_data_flat_green) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
+
+full_data_flat_gray <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
+full_data_flat_gray <- full_data_flat_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
+ratio_flat_gray <- nrow(full_data_flat_gray) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
+
+full_data_flat_tan <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
+full_data_flat_tan <- full_data_flat_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
+ratio_flat_tan <- nrow(full_data_flat_tan) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
 
@@
   annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
+  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0.5, ymax = 2.0, alpha = 0.5, fill = "black") +
   theme_bw() +
@@
   labs(x = "Data Variability",
-       y = "Model Error") +
-  facet_wrap(. ~ type)
+       y = "Model Performance") +
+  facet_wrap(. ~ model)
 
@@
 
-data1 <- pk_output_1comp_12212021 %>%
+data1 <- pk_output_1comp_03012022 %>%
   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
 
-data2 <- pk_output_2comp_02102022 %>%
+data2 <- pk_output_2comp_03012022 %>%
   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
@@
   facet_wrap(.~ model) +
-  geom_vline(xintercept = 2.22e-06)
+  geom_vline(xintercept = 0.001476315)
 # stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))
@@
 
-data <- raw_1comp_12212021
+data <- raw_1comp_03012022
 
@@
 
-```{r make_joint_sigma_plot}
-
-##################
-##################
-
-data1 <- as.data.table(pk_output_1comp_12212021 %>%
+```{r make_joint_sigma_plot, eval = FALSE}
+
+##################
+##################
+
+data1 <- as.data.table(pk_output_1comp_03012022 %>%
                          filter(param.value.type == "Fitted geometric mean"))
 
-data2 <- as.data.table(pk_output_2comp_02102022 %>%
+data2 <- as.data.table(pk_output_2comp_03012022 %>%
                          filter(param.value.type == "Fitted geometric mean"))
@@
 
-raw_data1 <- raw_1comp_12212021
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp_12212021 %>% 
+raw_data1 <- raw_1comp_03012022
+
+##################
+##################
+
+pk_data1 <- pk_output_1comp_03012022 %>% 
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
@@
 
-raw_data2 <- raw_2comp_02102022
-
-pk_data2 <- pk_output_2comp_02102022 %>% 
+raw_data2 <- raw_2comp_03012022
+
+pk_data2 <- pk_output_2comp_03012022 %>% 
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
@@
 
-raw_data1 <- raw_1comp_12212021
+raw_data1 <- raw_1comp_03012022
 
@@
 
-```{r, make_model_params_table}
+```{r, make_model_params_table, eval = FALSE}
 
@@
 
+pk_data1 <- pk_output_1comp_03012022 
 pk_data1 <- pk_output_1comp_12212021
 
-pk_data2 <- pk_output_2comp_02102022
+pk_data2 <- pk_output_2comp_03012022
+pk_data2 <- pk_output_2comp_12212021
 
@@
 
-# write.csv(fittable, file = "inst/ext/model_params_table.csv", row.names = FALSE)
+write.csv(fittable, file = "inst/ext/model_params_table_03012022.csv", row.names = FALSE)
 
@@
 
-pk_data1 <- as.data.table(pk_output_1comp_12212021)
-pk_data2 <- as.data.table(pk_output_2comp_02102022)
+pk_data1 <- as.data.table(pk_output_1comp_03012022)
+pk_data2 <- as.data.table(pk_output_2comp_03012022)
 
@@
 
-# write.csv(pk_all, file = "inst/ext/no_fit_table_01212022.csv", row.names = FALSE)
+# write.csv(pk_all, file = "inst/ext/no_fit_table_03012022.csv", row.names = FALSE)
 ```
@@
 
-pk_data1 <- pk_output_1comp_12212021
-
-pk_data2 <- pk_output_2comp_02102022
-
-pk_data_flat <- pk_output_flat_02102022 %>%
+pk_data1 <- pk_output_1comp_03012022
+
+pk_data2 <- pk_output_2comp_03012022
+
+pk_data_flat <- pk_output_flat_03012022 %>%
   filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")
@@
 
-pk_data1 <- pk_output_1comp_12212021
+pk_data1 <- pk_output_1comp_03012022
 

### 2022-03-31 i.Rmd
Rmarkdown figure edits

---
title: "Untitled"
author: "Christopher Cook"
date: "3/9/2022"
output:
  word_document: default
  html_document: default
bibliography: poster/references.bib
# csl: poster/computational-toxicology.csl
nocite: '@*'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

# References

### 2022-03-31 R/fit_model.R

@@ -1,0 +1,141 @@
+fit_model <- function(data,
+                      model,
+                      model_fun,
+                      ratio_data_to_dose,
+
+                      compound_col = "compound",
+                      compound_default = NULL,
+
+                      cas_col = "cas",
+                      cas_default = NULL,
+
+                      reference_col = "reference",
+                      reference_default = NULL,
+
+                      species_col = "species",
+                      species_default = NULL,
+
+                      species_weight_col = "species_weight",
+                      species_weight_default = NULL,
+                      species_weight_units_col = "species_weight_units",
+                      species_weight_units_default = NULL,
+
+                      dose_col = "dose",
+                      dose_default = NULL,
+
+                      time_col = "time",
+                      time_default = NULL,
+                      time_units_col = "time_units",
+                      time_units_default = NULL,
+
+                      media_col = "media",
+                      media_default = NULL,
+                      media_units_col = "media_units",
+                      media_units_default = NULL,
+
+                      conc_col = "conc",
+                      conc_default = NULL,
+                      conc_units_col = "conc_units",
+                      conc_units_default = NULL,
+
+                      route_col = "route",
+                      route_default = NULL,
+
+                      loq_col = "loq",
+                      loq_default = NULL,
+
+                      loq_units_col = "loq_units",
+                      loq_units_default = NULL) {
+
+  data <- rename_columns(data,
+
+                         compound_col,
+                         compound_default,
+
+                         cas_col,
+                         cas_default,
+
+
+                         reference_col,
+                         reference_default,
+
+                         species_col,
+                         species_default,
+
+                         species_weight_col,
+                         species_weight_default,
+                         species_weight_units_col,
+                         species_weight_units_default,
+
+                         dose_col,
+                         dose_default,
+
+                         time_col,
+                         time_default,
+                         time_units_col,
+                         time_units_default,
+
+                         media_col,
+                         media_default,
+                         media_units_col,
+                         media_units_default,
+
+                         conc_col,
+                         conc_default,
+                         conc_units_col,
+                         conc_units_default,
+
+                         route_col,
+                         route_default,
+
+                         loq_col,
+                         loq_default,
+
+                         loq_units_col,
+                         loq_units_default)
+
[…]

### 2022-03-31 R/plot_conctime.R

@@ -138,11 +138,11 @@ plot_conctime <- function(PK.fit.table,
 
         this.medium.data <- this.reference.data[Media == this.medium]
 
-        this.medium.data[, "Value"][is.na(this.medium.data[, "Value"])] <- 2 * this.medium.data[, mean(LOQ)]
+        this.medium.data[, "Value"][is.na(this.medium.data[, "Value"])] <- 0.5 * this.medium.data[, mean(LOQ)]
 
         ### do this without converting to and back from a data.frame
         this.medium.data <- as.data.frame(this.medium.data)
-        this.medium.data$L.O.Q. <- ifelse(this.medium.data$Value <= mean(2 * this.medium.data$LOQ), "Below", "Above")
+        this.medium.data$L.O.Q. <- ifelse(this.medium.data$Value <= mean(this.medium.data$LOQ), "Below", "Above")
         this.medium.data <- as.data.table(this.medium.data)
         this.medium.data <- this.medium.data[, LOQ. := as.factor(L.O.Q.)]
 

### 2022-04-11 figures_01312022.Rmd
.

@@
        y = "Number of observations") +
-  facet_wrap(.~ model) +
-  geom_vline(xintercept = 0.001476315)
+  facet_wrap(.~ model)
+  # geom_vline(xintercept = 0.001476315)
 # stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))

### 2022-05-12 figures_01312022.Rmd
Chris's before leaving

@@
 
+### this block runs the model fits
+# and does some pre-processing to clean up the data
+
 #################
@@
 
-data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
-data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
+# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
+# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
+# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
+data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")
+
+### these compounds had no CAS in the cvtdb
+# double check and they should not have been added
+# so I removed them
+
+data <- data %>%
+  filter(analyte_name_original != "Methemoglobin") %>%
+  filter(analyte_name_original != "N-desmethyltamoxifen")
 
@@
 data$analyte_name_original[data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
+data$analyte_name_original[data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
 
@@
 
+### this is basically my debug line,
+# where I can focus on one problematic compound 
+# and see what's going wrong
+# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
+# data <- data %>% filter(dsstox_casrn == "123-91-1")
+
 ### do 1-Compartment fit
 system.time(PK.fit.table.1comp <- fit_all(
-
   data.set = data,
@@
   subject.default = NA,
-  info.default = NA,
-  ratio.data.to.dose = 0.001
+  info.default = NA
 ))
@@
 system.time(PK.fit.table.2comp <- fit_all(
-
   data.set = data,
@@
   route.col = "administration_route_normalized",
-  source.col = "fk_extraction_document_id",
+  source.col = "document_id",
   loq.default = NA,
   subject.default = NA,
-  info.default = NA,
-  ratio.data.to.dose = 0.001
+  info.default = NA
 ))
 
-# write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.DATE.csv", row.names = FALSE)
-# write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.DATE.csv", row.names = FALSE)
-# 
-# write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.02102022.csv", row.names = FALSE)
-# write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.02102022.csv", row.names = FALSE)
+### do flat fit
+system.time(PK.fit.table.flat <- fit_all(
+  data.set = data,
+  model = "flat",
+  modelfun = "analytic",
+  compound.col = "analyte_name_original",
+  cas.col = "dsstox_casrn",
+  reference.col = "fk_reference_document_id",
+  species.col = "species",
+  species.weight.col = "weight_kg",
+  species.weight.units.default = "kg",
+  dose.col = "dose_level_normalized",
+  time.col = "time_hr",
+  time.units.default = "hr",
+  media.col = "conc_medium_normalized",
+  media.units.default = "normalized",
+  value.col = "conc",
+  units.default = NA,
+  route.col = "administration_route_normalized",
+  source.col = "document_id",
+  loq.default = NA,
+  subject.default = NA,
+  info.default = NA
+))
+
+### uncomment below to export to CSV files
+# change the date!!
+
+write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.05092022.csv", row.names = FALSE)
+write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.05092022.csv", row.names = FALSE)
+
+write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.05092022.csv", row.names = FALSE)
+write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.05092022.csv", row.names = FALSE)
+
+write.csv(PK.fit.table.flat[[1]], "inst/ext/PK.fit.table.flat.05092022.csv", row.names = FALSE)
+write.csv(PK.fit.table.flat[[2]], "inst/ext/processed.flat.data.05092022.csv", row.names = FALSE)
 ```
@@
 
+### this block reads the exported model fit csv files from run_invivoPKfit
+
 ### read in PK output files
-pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
-pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
-pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")
-
-pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
-pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
-pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")
+# pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
+# pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
+# pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")
+
+# pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
+# pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
+# pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")
+
+pk_output_1comp_04282022 <- read.csv("inst/ext/PK.fit.table.1comp.04282022.csv")
+pk_output_2comp_04282022<- read.csv("inst/ext/PK.fit.table.2comp.04282022.csv")
+pk_output_flat_04282022 <- read.csv("inst/ext/PK.fit.table.flat.04282022.csv")
+
+pk_output_2comp_05092022 <- read.csv("inst/ext/PK.fit.table.2comp.05092022.csv")
+pk_output_flat_05092022 <- read.csv("inst/ext/PK.fit.table.flat.05092022.csv")
+pk_output_1comp_05092022 <- read.csv("inst/ext/PK.fit.table.1comp.05092022.csv")
 
 ### read in processed raw data files
-raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
-raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
-raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")
-
-raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
-raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
-raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")
+# raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
+# raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
+# raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")
+
+# raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
+# raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
+# raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")
+
+# raw_1comp_04142022 <- read.csv("inst/ext/processed.1comp.data.04142022.csv")
+# raw_2comp_04142022 <- read.csv("inst/ext/processed.2comp.data.04142022.csv")
+# raw_flat_04142022 <- read.csv("inst/ext/processed.flat.data.04142022.csv")
+
+raw_1comp_04282022 <- read.csv("inst/ext/processed.1comp.data.04282022.csv")
+raw_2comp_04282022 <- read.csv("inst/ext/processed.2comp.data.04282022.csv")
+raw_flat_04282022 <- read.csv("inst/ext/processed.flat.data.04282022.csv")
+
+raw_1comp_05092022 <- read.csv("inst/ext/processed.1comp.data.05092022.csv")
+raw_2comp_05092022 <- read.csv("inst/ext/processed.2comp.data.05092022.csv")
+raw_flat_05092022 <- read.csv("inst/ext/processed.flat.data.05092022.csv")
 
@@
 ```{r, make_rdata, eval = FALSE}
+
+### this block takes the csv files in read_data
+# and saves them as Rdata files
 
@@
 
-save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
-save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
-save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
-save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
-save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
-save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")
+# save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
+# save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
+# save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
+# save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
+# save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
+# save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")
+
+# save(pk_output_1comp_04142022, file = "figures_rdata/pk_output_1comp_04142022.Rdata")
+# save(pk_output_2comp_04142022, file = "figures_rdata/pk_output_2comp_04142022.Rdata")
+# save(pk_output_flat_04142022, file = "figures_rdata/pk_output_flat_04142022.Rdata")
+# save(raw_1comp_04142022, file = "figures_rdata/raw_1comp_04142022.Rdata")
+# save(raw_2comp_04142022, file = "figures_rdata/raw_2comp_04142022.Rdata")
+# save(raw_flat_04142022, file = "figures_rdata/raw_flat_04142022.Rdata")
+
+save(pk_output_1comp_05092022, file = "figures_rdata/pk_output_1comp_05092022.Rdata")
+save(pk_output_2comp_05092022, file = "figures_rdata/pk_output_2comp_05092022.Rdata")
+save(pk_output_flat_05092022, file = "figures_rdata/pk_output_flat_05092022.Rdata")
+save(raw_1comp_05092022, file = "figures_rdata/raw_1comp_05092022.Rdata")
+save(raw_2comp_05092022, file = "figures_rdata/raw_2comp_05092022.Rdata")
+save(raw_flat_05092022, file = "figures_rdata/raw_flat_05092022.Rdata")
 
 save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")
-
-### save cp data
-# save(cp_df, file = "figures_rdata/cp_df.Rdata")
 ```
@@
 
+### this block loads the Rdata files,
+# as well as some other files written in below code blocks
+# this saves time from having to run those below code blocks every time
+# these additional files include 'cp_df' and 'cvt_variability'
+
 ### load all of this wonderful data
-load("figures_rdata/pk_output_1comp_12212021.Rdata")
-load("figures_rdata/pk_output_2comp_12212021.Rdata")
-load("figures_rdata/raw_1comp_12212021.Rdata")
-load("figures_rdata/raw_2comp_12212021.Rdata")
-load("figures_rdata/cp_df_12212021.Rdata")
-load("figures_rdata/cvt_variability_df_12212021.Rdata")
-
-load("figures_rdata/pk_output_1comp_03012022.Rdata")
-load("figures_rdata/pk_output_2comp_03012022.Rdata")
-load("figures_rdata/pk_output_flat_03012022.Rdata")
-load("figures_rdata/raw_1comp_03012022.Rdata")
-load("figures_rdata/raw_2comp_03012022.Rdata")
-load("figures_rdata/raw_flat_03012022.Rdata")
-load("figures_rdata/cp_df_03012022.Rdata")
-load("figures_rdata/cvt_variability_df_03012022.Rdata")
-
-load("figures_rdata/cp_df_03302022.Rdata")
+# load("figures_rdata/pk_output_1comp_12212021.Rdata")
+# load("figures_rdata/pk_output_2comp_12212021.Rdata")
+# load("figures_rdata/raw_1comp_12212021.Rdata")
+# load("figures_rdata/raw_2comp_12212021.Rdata")
+# load("figures_rdata/cp_df_12212021.Rdata")
+# load("figures_rdata/cvt_variability_df_12212021.Rdata")
+
+# load("figures_rdata/pk_output_1comp_03012022.Rdata")
+# load("figures_rdata/pk_output_2comp_03012022.Rdata")
+# load("figures_rdata/pk_output_flat_03012022.Rdata")
+# load("figures_rdata/raw_1comp_03012022.Rdata")
+# load("figures_rdata/raw_2comp_03012022.Rdata")
+# load("figures_rdata/raw_flat_03012022.Rdata")
+# load("figures_rdata/cp_df_03012022.Rdata")
+# load("figures_rdata/cvt_variability_df_03012022.Rdata")
+
+# load("figures_rdata/pk_output_1comp_04142022.Rdata")
+# load("figures_rdata/pk_output_2comp_04142022.Rdata")
+# load("figures_rdata/pk_output_flat_04142022.Rdata")
+# load("figures_rdata/raw_1comp_04142022.Rdata")
+# load("figures_rdata/raw_2comp_04142022.Rdata")
+# load("figures_rdata/raw_flat_04142022.Rdata")
+# load("figures_rdata/cp_df_04142022.Rdata")
+# load("figures_rdata/cvt_variability_df_04142022.Rdata")
+# 
+# load("figures_rdata/cp_df_03302022.Rdata")
+
+# load("figures_rdata/pk_output_1comp_04282022.Rdata")
+# load("figures_rdata/pk_output_2comp_04282022.Rdata")
+# load("figures_rdata/pk_output_flat_04282022.Rdata")
+# load("figures_rdata/raw_1comp_04282022.Rdata")
+# load("figures_rdata/raw_2comp_04282022.Rdata")
+# load("figures_rdata/raw_flat_04282022.Rdata")
+# load("figures_rdata/cp_df_04282022.Rdata")
+# load("figures_rdata/cvt_variability_df_04282022.Rdata")
+# 
+# load("figures_rdata/cp_df_04282022.Rdata")
+
+load("figures_rdata/pk_output_1comp_05092022.Rdata")
+load("figures_rdata/pk_output_2comp_05092022.Rdata")
+load("figures_rdata/pk_output_flat_05092022.Rdata")
+load("figures_rdata/raw_1comp_05092022.Rdata")
+load("figures_rdata/raw_2comp_05092022.Rdata")
+load("figures_rdata/raw_flat_05092022.Rdata")
+load("figures_rdata/cp_df_05092022.Rdata")
+load("figures_rdata/cvt_variability_df_05092022.Rdata")
+
+load("figures_rdata/cp_df_05092022.Rdata")
 
@@
 
+### this block produces the pdf files of the model fits
+# plotted on top of the original data
+
 ### 1 compartment
 
-pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
-  filter(Compound == "tamoxifen") %>%
-  filter(Data.Analyzed != "Joint Analysis")
-
-raw_1comp_03012022 <- raw_1comp_03012022 %>%
-  filter(Compound == "tamoxifen")
-
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_12212021),
-                      data.set = as.data.table(raw_1comp_12212021),
+# pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
+#   filter(Compound == "tamoxifen") %>%
+#   filter(Data.Analyzed != "Joint Analysis")
+
+# raw_1comp_03012022 <- raw_1comp_03012022 %>%
+#   filter(Compound == "tamoxifen")
+
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_05092022),
+                      data.set = as.data.table(raw_1comp_05092022),
                       model = "1compartment")
@@
 ### 2 compartment
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_03012022),
-                      data.set = as.data.table(raw_2comp_03012022),
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_05092022),
+                      data.set = as.data.table(raw_2comp_05092022),
                       model = "2compartment")
 
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_flat_05092022),
+                      data.set = as.data.table(raw_flat_05092022),
+                      model = "flat")
+
 ```
@@
 ```{r, make_cp_rdata, eval = FALSE}
-################################
-### histogram showing data spread of invivoPKfit cp values
-################################
+
+### this block creates a data.frame of predicted concentrations
+# using the estimated parameters and the observed conc-time points
+
+######################
 
@@
 ### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data1 <- pk_output_1comp_03012022 %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-raw_data1 <- dplyr::select(raw_1comp_03012022, -c("kelim", 
+pk_data1 <- pk_output_1comp_05092022 %>%
+  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
+  filter(Species != "hamster")
+
+raw_data1 <- dplyr::select(raw_1comp_05092022, -c("kelim", 
                                                   "Vdist", 
                                                   "Fgutabs", 
-                                                  "kgutabs"))
+                                                  "kgutabs")) %>% 
+  filter(Species != "hamster")
 
@@
 find_cp_1 <- function(full_data_1) {plyr::adply(full_data_1, 1, mutate, cp = cp_1comp(time = Time,
-                                                                                      params = full_data_1[1,],
+                                                                                      params = full_data_1[1, ],
                                                                                       dose = Dose,
@@
                                       full_data_1$Reference,
-                                      full_data_1$CAS),
+                                      full_data_1$CAS,
+                                      full_data_1$Species.x),
                     drop = TRUE)
@@
 ### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data2 <- pk_output_2comp_03012022 %>%
+pk_data2 <- pk_output_2comp_05092022 %>%
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
 
-raw_data2 <- dplyr::select(raw_2comp_03012022, -c("kelim", 
+raw_data2 <- dplyr::select(raw_2comp_05092022, -c("kelim", 
                                                   "Vdist", 
@@
                                       full_data_2$Reference,
-                                      full_data_2$CAS),
+                                      full_data_2$CAS,
+                                      full_data_2$Species.x),
                     drop = TRUE)
@@
 find_cp_2 <- function(full_data_2) {plyr::adply(full_data_2, 1, mutate, cp = cp_2comp(time = Time,
-                                                                                      params = full_data_2[1,],
+                                                                                      params = full_data_2[1, ],
                                                                                       dose = Dose,
@@
 
-pk_data_flat <- pk_output_flat_03012022 %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-raw_data_flat <- dplyr::select(raw_flat_03012022, -c("A"))
+pk_data_flat <- pk_output_flat_05092022 %>%
+  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
+  filter(Species != "hamster")
+
+raw_data_flat <- dplyr::select(raw_flat_05092022, -c("A")) %>% 
+  filter(Species != "hamster")
 
@@
                                             full_data_flat$Reference,
-                                            full_data_flat$CAS),
+                                            full_data_flat$CAS,
+                                            full_data_flat$Species.x),
                        drop = TRUE)
@@
 find_cp_flat <- function(full_data_flat) {plyr::adply(full_data_flat, 1, mutate, cp = cp_flat(time = Time,
-                                                                                              params = full_data_flat[1,],
+                                                                                              params = full_data_flat[1, ],
                                                                                               dose = Dose,
@@
 
-cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
-
-cp_df <- cp_df %>% group_by(Species.x, 
-                            Compound,
-                            CAS,
-                            type) %>%
-  mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))
-
-cp_df_03302022 <- cp_df
-
-save(cp_df_03302022, file = "figures_rdata/cp_df_03302022.Rdata")
+# cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
+# 
+# cp_df <- cp_df %>% group_by(Species.x, 
+#                             Compound,
+#                             CAS,
+#                             type) %>%
+#   mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))
+
+cp_df_05092022 <- cp_df
+
+### here is where you save the Rdata file
+save(cp_df_05092022, file = "figures_rdata/cp_df_05092022.Rdata")
 ```
@@
 
-##################
-##################
-
-# data <- cp_df_12212021
-data <- cp_df_03012022
-
-##################
-##################
-
-p <- ggplot(data = data,
+### this block makes a histogram of the data output
+# from make_cp_rdata
+# there's a separate facet for each model type
+# only data that were best fitted by that model
+# are shown in that facet
+
+##################
+##################
+
+pk_data <- cp_df_05092022
+
+# cvt_data <- cvt_variability_df_04282022
+
+##################
+##################
+
+row.names(pk_data) <- c()
+full_data <- pk_data
+
+# cvt_data <- dplyr::select(cvt_data, -c("kelim",
+#                                        "Vdist",
+#                                        "Fgutabs",
+#                                        "kgutabs"))
+# 
+# ### split pk_data by model so you can properly join with raw data
+# model_split <- split(pk_data, pk_data$model)
+# 
+# cvt_data$Reference <- as.character(cvt_data$Reference)
+# 
+# cvt_data$type <- "1-Compartment"
+# full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
+# 
+# cvt_data$type <- "2-Compartment"
+# full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
+# 
+# cvt_data$type <- "Flat"
+# full_data_flat <- left_join(cvt_data, model_split$`flat`)
+# 
+# ### put data back together
+# full_data <- rbind(full_data_1, full_data_2, full_data_flat)
+# 
+# full_data <- full_data %>%
+#   filter(cp != 0)
+
+full_data$AIC <- round(full_data$AIC, digits = 4)
+
+### only take necessary columns to keep things clean
+full_data <- full_data %>%
+  distinct(Compound, Reference, Species.x, model, AIC, cp_norm)
+
+### this pivots the data so we have AICs and cp_norms
+# for each model row-wise
+full_data <- full_data %>%
+  group_by(Species.x, Compound, Reference, model) %>%
+  mutate(row = row_number()) %>%
+  pivot_wider(names_from = model,
+              values_from = c(AIC, cp_norm)) %>%
+  dplyr::select(-row)
+
+full_data <- as.data.table(full_data)
+
+### make model column equal a specific model based on AIC values
+full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment &
+                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
+                                                    AIC_2compartment < AIC_1compartment &
+                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
+                                                    AIC_flat < AIC_1compartment &
+                                                      AIC_flat < AIC_2compartment ~ "Null",
+
+                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
+                                                      is.na(AIC_flat) ~ "1-Compartment",
+                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) &
+                                                      is.na(AIC_flat) ~ "2-Compartment",
+                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) &
+                                                      is.na(AIC_2compartment) ~ "Null",
+
+                                                    is.na(AIC_1compartment) &
+                                                      AIC_flat < AIC_2compartment ~ "Null",
+                                                    is.na(AIC_1compartment) &
+                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
+                                                    is.na(AIC_2compartment) &
+                                                      AIC_flat < AIC_1compartment ~ "Null",
+                                                    is.na(AIC_2compartment) &
+                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
+                                                    is.na(AIC_flat) &
+                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
+                                                    is.na(AIC_flat) &
+                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
+
+### make cp_norm equal to the cp_norm that corresponds to the best fitting model
+full_data <- full_data %>%
+  mutate(cp_norm = case_when(model == "1-Compartment" ~ cp_norm_1compartment,
+                             model == "2-Compartment" ~ cp_norm_2compartment,
+                             model == "Null" ~ cp_norm_flat))
+
+full_data[, model := paste("Model:", model)]
+
+### this creates a new column that says how many unique sets of Compound, Reference,
+# and Species correspond to each model
+full_data[, chem_ref_spec_count := uniqueN(.SD), .SDcols = c("Compound", 
+                                                             "Reference",
+                                                             "Species.x"), 
+          by = "model"]
+
+full_data[, chem_ref_spec_count := paste("Chemical-Reference-Species:", chem_ref_spec_count)]
+
+### make plot, facet by model and chem_ref_spec_count
+p <- ggplot(data = full_data,
             mapping = aes(x = cp_norm)) +
-  geom_histogram(bins = 30) +
+  geom_histogram(binwidth = 0.325) +
   geom_vline(xintercept = c(0.5, 2),
@@
         axis.title = element_text(size = 14)) +
-  scale_x_log10(limits = c(0.01, 1000)) +
+  # scale_x_log10() +
+  scale_x_log10(limits = c(1e-3, 1e3), labels = scientific) +
+  scale_y_continuous(labels = scientific) +
   theme_bw() +
@@
        y = "Number of Observations") +
-  facet_wrap(. ~ type)
+  facet_wrap(. ~ model + chem_ref_spec_count)
 
@@
 
+### I think this is little outdated but whatever I'm gonna keep it here
+# Think is was just plotting Cpred - Cobs
+
 ##################
@@
 # data <- cp_df_12212021
-data <- cp_df_03012022
+# data <- cp_df_03012022
+data <- cp_df_04282022
 
@@
 
-##################
-##################
-
-data <- cp_df_03012022
+### I think this is little outdated but whatever I'm gonna keep it here
+
+##################
+##################
+
+data <- cp_df_04282022
 
@@
 
-##################
-##################
-
-data <- as.data.table(raw_1comp_03012022)
+### this block creates a data.frame that shows the 
+# spread of CvT data via across replicate timepoints 
+# for a single experiment
+# if the data isn't within 2-fold of itself
+# is it reasonable to say that a model should fit within 2-fold?
+
+##################
+##################
+
+### all the raw data for each model SHOULD be the same
+# so only need to use one
+data <- as.data.table(raw_1comp_05092022)
 
@@
 
+### this for loop applies the function 
+# at data subsets of compound, data, dose, route, media
 data.list <- list()
@@
 ### combine data.tables back into one large data.set
-cvt_variability_df_03012022 <- do.call(rbind, data.list)
-
-save(cvt_variability_df_03012022, file = "figures_rdata/cvt_variability_df_03012022.Rdata")
+cvt_variability_df_05092022 <- do.call(rbind, data.list)
+
+### SAVE the data
+save(cvt_variability_df_05092022, file = "figures_rdata/cvt_variability_df_05092022.Rdata")
 ```
@@
 ```{r, make_cvt_variability_histogram}
+
+### this block makes the histogram
+# of cvt variability using the data.frame
+# made from make_cvt_variability_rdata
 
@@
 
-data <- cvt_variability_df_03012022
+data <- cvt_variability_df_05092022
 # data <- cvt_variability_df_12212021
@@
 
+### this block makes a density plot with cvt variabity
+# and normalized predicted concentrations
+# it's basically a combination of the other two histograms
+# expect here we limit cp observations those that have replicate timepoint
+# data, so it matches the cvt variability data, thus making it 
+# comparable
+
 ##################
@@
 # pk_data <- cp_df_03012022
-pk_data <- cp_df_03302022
-
-cvt_data <- cvt_variability_df_03012022
-
-##################
-##################
-
+pk_data <- cp_df_05092022
+
+cvt_data <- cvt_variability_df_05092022
+
+##################
+##################
+
+### i hate row names
 row.names(pk_data) <- c()
 
+### making these null so I don't have to deal
+# with duplicate .x and .y's
+# only need the ones from pk_data
 cvt_data <- dplyr::select(cvt_data, -c("kelim", 
@@
 
+### References were of different classes for some reason
+# so had to change
 cvt_data$Reference <- as.character(cvt_data$Reference)
@@
 
+### not sure why there were 0s,
+# but they were screwing things up
 full_data <- full_data %>%
@@
 full_data <- full_data %>%
-  distinct(Compound, Reference, model, conc_norm, AIC, cp_norm)
-
+  distinct(Compound, Reference, model, Species.x, conc_norm, AIC, cp_norm)
+
+### 
 ### 
 full_data <- full_data %>%
+  group_by(Species.x, Compound, Reference, model) %>%
+  mutate(row = row_number()) %>%
   pivot_wider(names_from = model,
               values_from = c(AIC, cp_norm)) %>%
-  unchop(everything())
+  dplyr::select(-row)
 
 full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
-                                                      AIC_1compartment < AIC_flat ~ "1compartment",
+                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
                                                     AIC_2compartment < AIC_1compartment &
-                                                      AIC_2compartment < AIC_flat ~ "2compartment",
+                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
                                                     AIC_flat < AIC_1compartment &
-                                                      AIC_flat < AIC_2compartment ~ "flat",
+                                                      AIC_flat < AIC_2compartment ~ "Null",
 
                                                     !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
-                                                      is.na(AIC_flat) ~ "1compartment",
+                                                      is.na(AIC_flat) ~ "1-Compartment",
                                                     !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_flat) ~ "2compartment",
+                                                      is.na(AIC_flat) ~ "2-Compartment",
                                                     !is.na(AIC_flat) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_2compartment) ~ "flat",
+                                                      is.na(AIC_2compartment) ~ "Null",
 
                                                     is.na(AIC_1compartment) &
-                                                      AIC_flat < AIC_2compartment ~ "flat",
+                                                      AIC_flat < AIC_2compartment ~ "Null",
                                                     is.na(AIC_1compartment) &
-                                                      AIC_2compartment < AIC_flat ~ "2compartment",
+                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
                                                     is.na(AIC_2compartment) &
-                                                      AIC_flat < AIC_1compartment ~ "flat",
+                                                      AIC_flat < AIC_1compartment ~ "Null",
                                                     is.na(AIC_2compartment) &
-                                                      AIC_1compartment < AIC_flat ~ "1compartment",
+                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
                                                     is.na(AIC_flat) &
-                                                      AIC_1compartment < AIC_2compartment ~"1compartment",
+                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
                                                     is.na(AIC_flat) &
-                                                      AIC_2compartment <AIC_1compartment ~"2compartment"))
+                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
 
 full_data <- full_data %>%
-  mutate(cp_norm = case_when(model == "1compartment" ~ cp_norm_1compartment,
-                             model == "2compartment" ~ cp_norm_2compartment,
-                             model == "flat" ~ cp_norm_flat))
+  mutate(cp_norm = case_when(model == "1-Compartment" ~ cp_norm_1compartment,
+                             model == "2-Compartment" ~ cp_norm_2compartment,
+                             model == "Null" ~ cp_norm_flat))
+
+### remove super outlier data from triclosan, for visualization purposes
+full_data <- full_data %>%
+  filter(cp_norm > 1e-10 & cp_norm < 1e8) # also high one for the heck of it
+
+length(unique(full_data$Compound[full_data$model == "1-Compartment"]))
+length(unique(full_data$Compound[full_data$model == "2-Compartment"]))
+length(unique(full_data$Compound[full_data$model == "Null"]))
+
+null_vec <- as.vector(unique(full_data$Compound[full_data$model == "Null"]))
+
+full_data <- as.data.table(full_data)
+
+full_data[, model := paste("Model:", model)]
+
+full_data[, chem_ref_spec_count := uniqueN(.SD), .SDcols = c("Compound", 
+                                                             "Reference",
+                                                             "Species.x"), 
+          by = "model"]
+
+full_data[, chem_ref_spec_count := paste("Chemical-Reference-Species:", chem_ref_spec_count)]
 
@@
 
-full_data_1 <- split_full_data$`1compartment`
+full_data_1 <- split_full_data$`Model: 1-Compartment`
 
@@
 
-full_data_2 <- split_full_data$`2compartment`
+full_data_2 <- split_full_data$`Model: 2-Compartment`
 
@@
 
-full_data_flat <- split_full_data$`flat`
+full_data_flat <- split_full_data$`Model: Null`
 
@@
              linetype = "dashed") +
-  scale_x_log10() +
+  scale_x_log10(n.breaks = 4, labels = scientific) +
   scale_y_log10() +
@@
        y = "Model Performance") +
-  facet_wrap(. ~ model)
+  facet_wrap(. ~ model + chem_ref_spec_count) +
+  theme(strip.text.x = element_text(size = 7))
 
@@
 
-##################
-##################
-
-data1 <- pk_output_1comp_03012022 %>%
-  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
-
-data2 <- pk_output_2comp_03012022 %>%
-  filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
-
-##################
-##################
-
-### assign new column, with either "1-Compartment" or "2-Compartment"
-data1 <- subset(data1, select = sigma_value)
-data1$model <- "1-Compartment"
-
-data2 <- subset(data2, select = sigma_value)
-data2$model <- "2-Compartment"
-
-data <- rbind(data1, data2)
-
-p <- ggplot(data = data,
-            mapping = aes(x = sigma_value)) +
-  geom_histogram(bins = 15) +
+# pk_data <- cp_df_03012022
+pk_data <- cp_df_04282022
+
+cvt_data <- cvt_variability_df_04282022
+
+##################
+##################
+
+row.names(pk_data) <- c()
+
+cvt_data <- dplyr::select(cvt_data, -c("kelim", 
+                                       "Vdist", 
+                                       "Fgutabs", 
+                                       "kgutabs"))
+
+### split pk_data by model so you can properly join with raw data
+model_split <- split(pk_data, pk_data$model)
+
+cvt_data$Reference <- as.character(cvt_data$Reference)
+
+cvt_data$type <- "1-Compartment"
+full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
+
+cvt_data$type <- "2-Compartment"
+full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
+
+cvt_data$type <- "Flat"
+full_data_flat <- left_join(cvt_data, model_split$`flat`)
+
+### put data back together
+full_data <- rbind(full_data_1, full_data_2, full_data_flat)
+
+full_data <- full_data %>%
+  filter(cp != 0)
+
+# full_data$AIC <- round(full_data$AIC, digits = 4)
+
+full_data <- full_data %>%
+  pivot_wider(names_from = model,
+              values_from = c(AIC, sigma_value)) %>%
+  unchop(everything())
+
+full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
+                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
+                                                    AIC_2compartment < AIC_1compartment &
+                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
+                                                    AIC_flat < AIC_1compartment &
+                                                      AIC_flat < AIC_2compartment ~ "Null",
+
+                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
+                                                      is.na(AIC_flat) ~ "1-Compartment",
+                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
+                                                      is.na(AIC_flat) ~ "2-Compartment",
+                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) & 
+                                                      is.na(AIC_2compartment) ~ "Null",
+
+                                                    is.na(AIC_1compartment) &
+                                                      AIC_flat < AIC_2compartment ~ "Null",
+                                                    is.na(AIC_1compartment) &
+                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
+                                                    is.na(AIC_2compartment) &
+                                                      AIC_flat < AIC_1compartment ~ "Null",
+                                                    is.na(AIC_2compartment) &
+                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
+                                                    is.na(AIC_flat) &
+                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
+                                                    is.na(AIC_flat) &
+                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
+
+full_data <- full_data %>%
+  mutate(AIC = case_when(model == "1-Compartment" ~ AIC_1compartment,
+                         model == "2-Compartment" ~ AIC_2compartment,
+                         model == "Null" ~ AIC_flat))
+
+full_data <- full_data %>%
+  mutate(sigma_value = case_when(model == "1-Compartment" ~ sigma_value_1compartment,
+                                 model == "2-Compartment" ~ sigma_value_2compartment,
+                                 model == "Null" ~ sigma_value_flat))
+
+full_data <- full_data %>%
+  distinct(Compound, 
+           Reference, 
+           Route, 
+           Species,
+           Media,
+           model, 
+           sigma_id,
+           sigma_value,
+           Value,
+           AIC)
+
+full_data <- as.data.table(full_data)
+
+full_data[, sigma_norm := sigma_value / nrow(.SD), by = .(Compound, 
+                                                          Reference,
+                                                          model,
+                                                          sigma_id,
+                                                          sigma_value)]
+
+full_data <- as.data.frame(full_data)
+
+full_data <- full_data %>% distinct(Compound,
+                                    Reference,
+                                    model,
+                                    AIC,
+                                    sigma_id,
+                                    sigma_value,
+                                    sigma_norm)
+
+full_data <- full_data %>%
+  group_by(Compound, Reference, sigma_id) %>%
+  slice_min(AIC)
+
+# ##################
+# ##################
+# 
+# data1 <- pk_output_1comp_03012022 %>%
+#   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
+# 
+# data2 <- pk_output_2comp_03012022 %>%
+#   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
+# 
+# ##################
+# ##################
+# 
+# ### assign new column, with either "1-Compartment" or "2-Compartment"
+# data1 <- subset(data1, select = sigma_value)
+# data1$model <- "1-Compartment"
+# 
+# data2 <- subset(data2, select = sigma_value)
+# data2$model <- "2-Compartment"
+# 
+# data <- rbind(data1, data2)
+
+p <- ggplot(data = full_data,
+            mapping = aes(x = sigma_norm)) +
+  geom_histogram(bins = 12) +
   # geom_density() +
@@
 
-data <- raw_1comp_03012022
+data <- raw_1comp_04282022
 
@@
 
-data1 <- as.data.table(pk_output_1comp_03012022 %>%
+data1 <- as.data.table(pk_output_1comp_04282022 %>%
                          filter(param.value.type == "Fitted geometric mean"))
 
-data2 <- as.data.table(pk_output_2comp_03012022 %>%
+data2 <- as.data.table(pk_output_2comp_04282022 %>%
                          filter(param.value.type == "Fitted geometric mean"))
@@
 
-raw_data1 <- raw_1comp_03012022
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp_03012022 %>% 
+raw_data1 <- raw_1comp_04282022
+
+##################
+##################
+
+pk_data1 <- pk_output_1comp_04282022 %>% 
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
@@
 
-raw_data2 <- raw_2comp_03012022
-
-pk_data2 <- pk_output_2comp_03012022 %>% 
+raw_data2 <- raw_2comp_04282022
+
+pk_data2 <- pk_output_2comp_04282022 %>% 
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
@@
 
-raw_data1 <- raw_1comp_03012022
+raw_data1 <- raw_1comp_04282022
 
@@
 
-pk_data1 <- pk_output_1comp_03012022 
-pk_data1 <- pk_output_1comp_12212021
-
-pk_data2 <- pk_output_2comp_03012022
-pk_data2 <- pk_output_2comp_12212021
+pk_data1 <- pk_output_1comp_04282022 
+# pk_data1 <- pk_output_1comp_12212021
+
+pk_data2 <- pk_output_2comp_04282022 
+# pk_data2 <- pk_output_2comp_12212021
 
@@
 fittable <- NULL
+# test <- function(fits1comp, fits2comp) {
 for (this.cas in unique(c(fits1comp$CAS,fits2comp$CAS)))
 { 
+  # print(this.cas)
+  # if (this.cas == "123-91-1") browser()
   if (this.cas %in% fits1comp$CAS) this.compound <- fits1comp[
@@
       {
+        if (nrow(this.data.1comp.species) > 1) {
+          this.data.1comp.species <- this.data.1comp.species[1, ]
+        }
+
         this.row$AIC.1comp <- this.data.1comp.species$AIC
@@
       {
+        if(nrow(this.data.2comp.species) > 1 ) {
+          this.data.2comp.species <- this.data.2comp.species[1, ]
+        }
         this.row$AIC.2comp <- this.data.2comp.species$AIC
@@
 }
+
+# debug(test)
+# test(fits1comp, fits2comp)
 fittable$halflife <- log(2)/fittable$kelim
@@
 
-write.csv(fittable, file = "inst/ext/model_params_table_03012022.csv", row.names = FALSE)
+### compounds fit better by flat model should be removed
+# if present in fittable
+### some are only fit by the flat model,
+# but some are fit just fit better by the flat model
+
+# these are
+# hexachlorobenzene -- nevermind, for the joint 1comp does best
+# phenolphthalein glucuronide
+# tamoxifen
+# 2,3,7,8-tetrachlorodibenzo-p-dioxin
+# imidacloprid", # well this one is only fit by the flat,
+# so isn't present anyway
+
+### when I take these out, 48 1 compartment best fits, 59 2 compartment, 107 total
+
+### I also manually checked all Joint Analysis compounds 
+# to make sure no joint flat models performed better
+# none did
+
+# write.csv(fittable, file = "inst/ext/model_params_table_04182022.csv", row.names = FALSE)
 
@@
 
-pk_data1 <- as.data.table(pk_output_1comp_03012022)
-pk_data2 <- as.data.table(pk_output_2comp_03012022)
+pk_data1 <- as.data.table(pk_output_1comp_04282022)
+pk_data2 <- as.data.table(pk_output_2comp_04282022)
 
@@
 
-pk_data1 <- pk_output_1comp_03012022
-
-pk_data2 <- pk_output_2comp_03012022
-
-pk_data_flat <- pk_output_flat_03012022 %>%
+pk_data1 <- pk_output_1comp_04282022
+
+pk_data2 <- pk_output_2comp_04282022
+
+pk_data_flat <- pk_output_flat_04282022 %>%
   filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")
@@
 pk_just_bad <- pk_all %>%
-  filter(flat_lowest == 1 | flat_better_than_1 == 1 | flat_better_than_2)
+  filter(flat_lowest == 1 | flat_better_than_1 == 1 | flat_better_than_2 == 1)
 ```
@@
 
-pk_data1 <- pk_output_1comp_03012022
+pk_data1 <- pk_output_1comp_05092022
+# pk_data1 <- pk_output_1comp_04282022
+
+# pk_data1$Vdist <- log(pk_data1$Vdist)
 
@@
 pk_data1 <- pk_data1 %>%
-  filter(param.value.type == "Fitted geometric mean", Species == "human")
+  filter(param.value.type == "Fitted geometric mean")
+         # , CAS != "50-49-7", CAS != "106266-06-2")
+# , Species == "human")
 
@@
          !is.na(`human CL (mL/min/kg)`))
+
+pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000
+
+pk_all$Vdist_norm <- abs(pk_all$Vdist / pk_all$`human VDss (L/kg)`)
+pk_all$CLtot_norm <- abs(pk_all$CLtot / pk_all$`human CL (L/hr/kg)`)
+pk_all$halflife_norm <- abs(pk_all$halflife / pk_all$`terminal  t1/2 (h)`)
+
+pk_all$mae <- rowMeans(pk_all[, c("Vdist_norm", "CLtot_norm", "halflife_norm")])
 
@@
   scale_x_log10() +
+  scale_y_log10() +
   geom_abline(slope = 1, intercept = 0)
@@
   geom_point() +
+  scale_x_log10() +
+  scale_y_log10() +
   geom_abline(slope = 1, intercept = 0)
@@
 ### convert to same units
-pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000
 
@@
 ```
+
+<!-- # ```{r, make_model_params_table, eval = FALSE} -->
+<!-- #  -->
+<!-- # ### this code almost entirely is imported from John's bake-off RMarkdown file -->
+<!-- # ### what this produces is a table of compounds that were fit by at least one of the models -->
+<!-- # ### AICs for both models are reported, and subsequent parameter values correspond to the model with the lower AIC -->
+<!-- #  -->
+<!-- # ################### -->
+<!-- # ################### -->
+<!-- #  -->
+<!-- # pk_data1 <- pk_output_1comp_04142022  -->
+<!-- # # pk_data1 <- pk_output_1comp_12212021  -->
+<!-- #  -->
+<!-- # pk_data2 <- pk_output_2comp_04142022  -->
+<!-- # # pk_data2 <- pk_output_2comp_12212021  -->
+<!-- #  -->
+<!-- # pk_data_flat <- pk_output_flat_04142022 -->
+<!-- #  -->
+<!-- # ################### -->
+<!-- # ################### -->
+<!-- #  -->
+<!-- # pk_data1$sigma_id <- NULL -->
+<!-- # pk_data1$sigma_value <- NULL -->
+<!-- # pk_data2$sigma_id <- NULL -->
+<!-- # pk_data2$sigma_value <- NULL -->
+<!-- # pk_data_flat$sigma_id <- NULL -->
+<!-- # pk_data_flat$sigma_value <- NULL -->
+<!-- #  -->
+<!-- # pk_data1 <- distinct(pk_data1) -->
+<!-- # pk_data2 <- distinct(pk_data2) -->
+<!-- # pk_data_flat <- distinct(pk_data_flat) -->
+<!-- #  -->
+<!-- # fits1comp <- subset(pk_data1, is.finite(AIC) & AIC < 10^4) -->
+<!-- # fits2comp <- subset(pk_data2, is.finite(AIC) & AIC < 10^4) -->
+<!-- # fitsflat <- subset(pk_data_flat, is.finite(AIC) & AIC < 10^4) -->
+<!-- #  -->
+<!-- # #How many chemicals have 1 or 2 compartment fits: -->
+<!-- # length(unique(c(fits1comp$CAS,fits2comp$CAS,fitsflat$CAS))) -->
+<!-- #  -->
+<!-- # fittable <- NULL -->
+<!-- # # test <- function(fits1comp, fits2comp, fitsflat) { -->
+<!-- #   for (this.cas in unique(c(fits1comp$CAS,fits2comp$CAS, fitsflat$CAS))) -->
+<!-- #   { print(this.cas) -->
+<!-- #     # if (this.cas == "96-47-9") browser() -->
+<!-- #     if (this.cas %in% fits1comp$CAS) this.compound <- fits1comp[ -->
+<!-- #       fits1comp$CAS==this.cas,"Compound"][1] -->
+<!-- #     else if (this.cas %in% fits2comp$CAS) this.compound <- fits2comp[ -->
+<!-- #       fits2comp$CAS==this.cas,"Compound"][1] -->
+<!-- #     else if (this.cas %in% fitsflat$CAS) this.compound <- fitsflat[ -->
+<!-- #       fitsflat$CAS==this.cas,"Compound"][1] -->
+<!-- #      -->
+<!-- #     this.data.1comp <- subset(fits1comp,CAS==this.cas) -->
+<!-- #     this.data.2comp <- subset(fits2comp,CAS==this.cas) -->
+<!-- #     this.data.flat <- subset(fitsflat,CAS==this.cas) -->
+<!-- #      -->
+<!-- #     for (this.species in unique(tolower(c( -->
+<!-- #       this.data.1comp$Species, -->
+<!-- #       this.data.2comp$Species, -->
+<!-- #       this.data.flat$Species)))) -->
+<!-- #     { -->
+<!-- #       Vdist.1comp <- NA -->
+<!-- #       kelim.1comp <- NA -->
+<!-- #       Vdist.2comp <- NA -->
+<!-- #       kelim.2comp <- NA -->
+<!-- #       A.flat <- NA -->
+<!-- #        -->
+<!-- #       this.data.1comp.species <- subset(this.data.1comp,tolower(Species)==this.species) -->
+<!-- #       this.data.2comp.species <- subset(this.data.2comp,tolower(Species)==this.species) -->
+<!-- #       this.data.flat.species <- subset(this.data.flat, tolower(Species)==this.species) -->
+<!-- #        -->
+<!-- #       this.row <- data.frame( -->
+<!-- #         Compound=this.compound, -->
+<!-- #         CAS=this.cas, -->
+<!-- #         Species=this.species, -->
+<!-- #         Reference=NA, -->
+<!-- #         AIC.1comp=NA, -->
+<!-- #         AIC.2comp=NA, -->
+<!-- #         Model=NA, -->
+<!-- #         Vdist=NA, -->
+<!-- #         kelim=NA) -->
+<!-- #        -->
+<!-- #       if (this.cas %in% fits1comp$CAS) -->
+<!-- #       { -->
+<!-- #         this.data.1comp.species <- subset(this.data.1comp.species, -->
+<!-- #                                           param.value.type=="Fitted geometric mean") -->
+<!-- #          -->
+<!-- #         # If more than one source, require that the joint analysis worked: -->
+<!-- #         if (dim(this.data.1comp.species)[1]>1) -->
+<!-- #         { -->
+<!-- #           this.data.1comp.species<- subset(this.data.1comp.species,  -->
+<!-- #                                            Data.Analyzed=="Joint Analysis") -->
+<!-- #         } -->
+<!-- #         if (dim(this.data.1comp.species)[1]>0)  -->
+<!-- #         { -->
+<!-- #           if (nrow(this.data.1comp.species) > 1) { -->
+<!-- #             this.data.1comp.species <- this.data.1comp.species[1, ] -->
+<!-- #           } -->
+<!-- #            -->
+<!-- #           this.row$AIC.1comp <- this.data.1comp.species$AIC -->
+<!-- #           Vdist.1comp <- this.data.1comp.species$Vdist -->
+<!-- #           kelim.1comp <- this.data.1comp.species$kelim -->
+<!-- #           this.row$Reference <- this.data.1comp.species$Reference -->
+<!-- #         } -->
+<!-- #       } -->
+<!-- #        -->
+<!-- #       if (this.cas %in% fits2comp$CAS) -->
+<!-- #       { -->
+<!-- #         this.data.2comp.species <- subset(this.data.2comp.species, -->
+<!-- #                                           param.value.type=="Fitted geometric mean") -->
+<!-- #          -->
+<!-- #         # If more than one source, require that the joint analysis worked: -->
+<!-- #         if (dim(this.data.2comp.species)[1]>1) -->
+<!-- #         { -->
+<!-- #           this.data.2comp.species <- subset(this.data.2comp.species,  -->
+<!-- #                                             Data.Analyzed=="Joint Analysis") -->
+<!-- #         } -->
+<!-- #         if (dim(this.data.2comp.species)[1]>0)  -->
+<!-- #         { -->
+<!-- #           if(nrow(this.data.2comp.species) > 1 ) { -->
+<!-- #             this.data.2comp.species <- this.data.2comp.species[1, ] -->
+<!-- #           } -->
+<!-- #           this.row$AIC.2comp <- this.data.2comp.species$AIC -->
+<!-- #           Vdist.2comp <- this.data.2comp.species$Vss -->
+<!-- #           kelim.2comp <- this.data.2comp.species$kelim -->
+<!-- #           this.row$Reference <- this.data.2comp.species$Reference -->
+<!-- #         } -->
+<!-- #       } -->
+<!-- #        -->
+<!-- #       if (this.cas %in% fitsflat$CAS) -->
+<!-- #       { -->
+<!-- #         this.data.flat.species <- subset(this.data.flat.species, -->
+<!-- #                                          param.value.type=="Fitted geometric mean") -->
+<!-- #          -->
+<!-- #         # If more than one source, require that the joint analysis worked: -->
+<!-- #         if (dim(this.data.flat.species)[1]>1) -->
+<!-- #         { -->
+<!-- #           this.data.flat.species <- subset(this.data.flat.species,  -->
+<!-- #                                            Data.Analyzed=="Joint Analysis") -->
+<!-- #         } -->
+<!-- #         if (dim(this.data.flat.species)[1]>0)  -->
+<!-- #         { -->
+<!-- #           if(nrow(this.data.flat.species) > 1 ) { -->
+<!-- #             this.data.flat.species <- this.data.flat.species[1, ] -->
+<!-- #           } -->
+<!-- #           this.row$AIC.flat <- this.data.flat.species$AIC -->
+<!-- #           A.flat <- this.data.flat.species$A -->
+<!-- #           this.row$Reference <- this.data.flat.species$Reference -->
+<!-- #         } -->
+<!-- #       } -->
+<!-- #       ######################## -->
+<!-- #       ######################### -->
+<!-- #        -->
+<!-- #       if(!"AIC.flat" %in% names(this.row)) this.row <- this.row %>%  -->
+<!-- #         add_column(AIC.flat = NA) -->
+<!-- #        -->
+<!-- #       if(!"AIC.1comp" %in% names(this.row)) this.row <- this.row %>%  -->
+<!-- #         add_column(AIC.1comp = NA) -->
+<!-- #        -->
+<!-- #       if(!"AIC.2comp" %in% names(this.row)) this.row <- this.row %>%  -->
+<!-- #         add_column(AIC.2comp = NA) -->
+<!-- #        -->
+<!-- #       this.row <- this.row %>% mutate(Model = case_when(AIC.1comp < AIC.2comp &  -->
+<!-- #                                                           AIC.1comp < AIC.flat ~ "1Comp", -->
+<!-- #                                                         AIC.2comp < AIC.1comp & -->
+<!-- #                                                           AIC.2comp < AIC.flat ~ "2Comp", -->
+<!-- #                                                         AIC.flat < AIC.1comp & -->
+<!-- #                                                           AIC.flat < AIC.2comp ~ "Null", -->
+<!-- #                                                          -->
+<!-- #                                                         !is.na(AIC.1comp) & is.na(AIC.2comp) & -->
+<!-- #                                                           is.na(AIC.flat) ~ "1Comp", -->
+<!-- #                                                         !is.na(AIC.2comp) & is.na(AIC.1comp) &  -->
+<!-- #                                                           is.na(AIC.flat) ~ "2Comp", -->
+<!-- #                                                         !is.na(AIC.flat) & is.na(AIC.1comp) &  -->
+<!-- #                                                           is.na(AIC.2comp) ~ "Null", -->
+<!-- #                                                          -->
+<!-- #                                                         is.na(AIC.1comp) & -->
+<!-- #                                                           AIC.flat < AIC.2comp ~ "Null", -->
+<!-- #                                                         is.na(AIC.1comp) & -->
+<!-- #                                                           AIC.2comp < AIC.flat ~ "2Comp", -->
+<!-- #                                                         is.na(AIC.2comp) & -->
+<!-- #                                                           AIC.flat < AIC.1comp ~ "Null", -->
+<!-- #                                                         is.na(AIC.2comp) & -->
+<!-- #                                                           AIC.1comp < AIC.flat ~ "1Comp", -->
+<!-- #                                                         is.na(AIC.flat) & -->
+<!-- #                                                           AIC.1comp < AIC.2comp ~"1Comp", -->
+<!-- #                                                         is.na(AIC.flat) & -->
+<!-- #                                                           AIC.2comp <AIC.1comp ~"2Comp")) -->
+<!-- #        -->
+<!-- #        -->
+<!-- #       fittable <- rbind(fittable,this.row) -->
+<!-- #     } -->
+<!-- #   } -->
+<!-- # # } -->
+<!-- # # debug(test) -->
+<!-- # # test(fits1comp, fits2comp, fitsflat) -->
+<!-- # fittable$halflife <- log(2)/fittable$kelim -->
+<!-- #  -->
+<!-- # #Lets only keep chemicals where we can fit a PK model: -->
+<!-- # fittable <- subset(fittable, !is.na(Model)) -->
+<!-- #  -->
+<!-- # # for (this.col in c("AIC.1comp","AIC.2comp","Vdist","kelim","halflife")) -->
+<!-- # #   fittable[,this.c=-] <- signif(as.numeric(fittable[,this.col]),4) -->
+<!-- #  -->
+<!-- # # We have parameters estimated for 86 chemicals: -->
+<!-- # dim(fittable)[1] -->
+<!-- #  -->
+<!-- # # write.csv(fittable, file = "inst/ext/model_params_table_04182022.csv", row.names = FALSE) -->
+<!-- #  -->
+<!-- # ``` -->

### 2022-05-12 R/analyze_pk_data.R

@@ -27,10 +27,19 @@ analyze_pk_data <- function(fitdata,
   #take a copy of input data table so it behaves as though passed by value
   fitdata <- data.table::copy(fitdata)
 
+  # If there is no reference column, add on in:
+  if (!is.null(this.reference)) {
+    fitdata[, Reference := this.reference]
+  }
+
+  ### if the subset of data has LOQ values of 'NA', make the LOQ values = 0.45 * the minimum Value
+  fitdata[, LOQ := as.numeric(LOQ)]
+  fitdata[is.na(LOQ), LOQ := 0.45 * min(Value, na.rm = TRUE), by = .(Compound, Reference, Media)]
+
   cat(paste("Optimizing data for CAS-RN ", this.cas, "\n", sep =""))
 
   #Set a plausible upper bound for sigma:
-  TRYSIGMA <- 3 * stats::median(fitdata$Value, na.rm = T)
+  TRYSIGMA <- stats::median(fitdata$Value, na.rm = T)
   MAXSIGMA <- 100 * stats::median(fitdata$Value, na.rm = T)
 
   #Initialize output table with HTTK-predicted parameter values
@@ -38,11 +47,6 @@ analyze_pk_data <- function(fitdata,
   out.dt[, param.value.type := 'Predicted']
 
   these.params <- as.list(fitdata[1, paramnames, with = FALSE])
-
-  # If there is no reference column, add on in:
-  if (!is.null(this.reference)) {
-    fitdata[, Reference := this.reference]
-  }
 
   #Add a different sigma value for each reference
   refs <- fitdata[,
@@ -79,7 +83,7 @@ analyze_pk_data <- function(fitdata,
 
   } else if (model == 'flat') {
       opt.params <- these.params[names(these.params) %in% "A"]
-      opt.params["A"] <- mean(fitdata$Value, na.rm = TRUE)
+      opt.params["A"] <- log(mean(fitdata$Value, na.rm = TRUE))
     }
 
   if (model != 'flat') {
@@ -143,6 +147,7 @@ analyze_pk_data <- function(fitdata,
       if (length(unique(elim.data$Time)) > 3) {
 
         elim.data.test <- elim.data
+
         elim.data <- subset(elim.data,Time <= sort(unique(Time))[3]) ### added sort
         alpha <- -stats::lm(log(Value) ~ Time, data = elim.data)$coefficients["Time"]
[…]

### 2022-10-25 CreateFlatFile.Rmd
Minor bug fixes

---
title: "Create Flat File"
author: "John Wambaugh"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TKQSPR Bakeoff}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Load the curve fits from invivoPKfit (Chris Cook):
```{r load_compartmental_model_parameters, eval = TRUE}
setwd("C:/Users/jwambaug/git/tkqsars/")
fitsflat <- read.csv("PK.fit.table.flat.03012022.csv")
fits1comp <- read.csv("PK.fit.table.1comp.03012022.csv")
#fits1comp <- subset(fits1comp, is.finite(AIC) & AIC < 10^4)
fits2comp <- read.csv("PK.fit.table.2comp.03012022.csv")
#fits2comp <- subset(fits2comp, is.finite(AIC) & AIC < 10^4)
# Units on Volumes:
fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"Vdist"] <-
  fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"Vdist"] /
  1000
fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"CLtot"] <-
  fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"CLtot"] /
  1000
fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"Css"] <-
  fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"Css"] *
  1000
fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"Cpeak.oral.1mgkg"] <-
  fits1comp[regexpr("geometric mean",fits1comp$param.value.type)!=-1,"Cpeak.oral.1mgkg"] *
  1000
fits2comp[regexpr("geometric mean",fits2comp$param.value.type)!=-1,"V1"] <-
  fits2comp[regexpr("geometric mean",fits2comp$param.value.type)!=-1,"V1"] /
  1000
fits2comp[regexpr("geometric mean",fits2comp$param.value.type)!=-1,"Vss"] <-
  fits2comp[regexpr("geometric mean",fits2comp$param.value.type)!=-1,"Vss"] /
  1000
fits2comp[regexpr("geometric mean",fits2comp$param.value.type)!=-1,"CLtot"] <-
  fits2comp[regexpr("geometric mean",fits2comp$param.value.type)!=-1,"CLtot"] /
  1000
fits2comp$Css <- 1/fits2comp$CLtot

# Negative k12 indicates bad fit:
badfits <- fits2comp$k12
badfits[is.na(badfits)]<-0
badfits <- ifelse(badfits<0,TRUE,FALSE)
fits2comp[badfits,"AIC"] <- Inf

#How many chemicals have 1 or 2 compartment fits:
length(unique(c(fitsflat$CAS,fits1comp$CAS,fits2comp$CAS)))
```

# Concatanate the curve fits into a single table (should be part of invivoPKfit eventually):
```{r merge_curve_fits, eval = TRUE}
fittable <- NULL
for (this.dtxsid in unique(c(fits1comp$DTXSID,fits2comp$DTXSID,fitsflat$DTXSID)))
{
  if (this.dtxsid %in% fits1comp$DTXSID) 
  { 
    this.compound <- subset(fits1comp,DTXSID==this.dtxsid)$PREFERRED_NAME[1]
    this.cas <- subset(fits1comp,DTXSID==this.dtxsid)$CASRN[1]
  } else if (this.cas %in% fits2comp$CAS) {
    this.compound <- subset(fits2comp,DTXSID==this.dtxsid)$PREFERRED_NAME[1]
    this.cas <- subset(fits2comp,DTXSID==this.dtxsid)$CASRN[1]
  } else {
    this.compound <- subset(fitsflat,DTXSID==this.dtxsid)$PREFERRED_NAME[1]
    this.cas <- subset(fitsflat,DTXSID==this.dtxsid)$CASRN[1]
  }

  this.data.1comp <- subset(fits1comp,DTXSID==this.dtxsid)
  this.data.2comp <- subset(fits2comp,DTXSID==this.dtxsid)
  this.data.flat <- subset(fitsflat,DTXSID==this.dtxsid)

  for (this.species in unique(tolower(c(
    this.data.1comp$Species,
    this.data.2comp$Species,
    this.data.flat$Species))))
  {
    Vdist.1comp <- NA
    kelim.1comp <- NA
    Vdist.2comp <- NA
    kelim.2comp <- NA

    this.data.1comp.species <- subset(this.data.1comp,tolower(Species)==this.species)
    this.data.2comp.species <- subset(this.data.2comp,tolower(Species)==this.species)
    this.data.flat.species <- subset(this.data.flat,tolower(Species)==this.species)

    this.row <- data.frame(
      DTXSID=this.dtxsid,
      Compound=this.compound,
      CAS=this.cas,
      Species=this.species,
      Reference=NA,
      AIC.flat=NA,
      AIC.1comp=NA,
      AIC.2comp=NA,
      AIC.best=NA,
      Model=NA,
      Vdist=NA,
      kelim=NA,
      kgutabs=NA,
      Fgutabs=NA,
      Vdist.1comp=NA,
      kelim.1comp=NA,
      kgutabs.1comp=NA,
      Fgutabs.1comp=NA,
      Vdist.2comp=NA,
      V1.2comp=NA,
      k12.2comp=NA,
      k21.2comp=NA,
      kelim.2comp=NA,
      kgutabs.2comp=NA,
      Fgutabs.2comp=NA,
      Ralphatokelim.2comp=NA,
      Fbetaofalpha.2comp=NA,
      alpha.2comp=NA,
      beta.2comp=NA)

    if (this.cas %in% fitsflat$CASRN)
    {
      this.data.flat.species <- subset(this.data.flat.species,
        param.value.type=="Fitted geometric mean")

    # If more than one source, require that the joint analysis worked:
     if (dim(this.data.flat.species)[1]>1)
      {
        this.data.flat.species<- subset(this.data.flat.species, 
                                         Data.Analyzed=="Joint Analysis")[1,]
      }
      if (dim(this.data.1comp.species)[1]>0) 
      {
        this.row$AIC.flat <- this.data.flat.species$AIC
        this.row$Reference <- this.data.flat.species$Reference
      }
    }

    if (this.cas %in% fits1comp$CASRN)
    {
      this.data.1comp.species <- subset(this.data.1comp.species,
        param.value.type=="Fitted geometric mean")

    # If more than one source, require that the joint analysis worked:
     if (dim(this.data.1comp.species)[1]>1)
      {
        this.data.1comp.species<- subset(this.data.1comp.species, 
                                         Data.Analyzed=="Joint Analysis")[1,]
      }
      if (dim(this.data.1comp.species)[1]>0) 
      {
        this.row$AIC.1comp <- this.data.1comp.species$AIC
        this.row$Vdist.1comp <- this.data.1comp.species$Vdist
        this.row$kelim.1comp <- this.data.1comp.species$kelim
        this.row$kgutabs.1comp <- this.data.1comp.species$kgutabs
        this.row$Fgutabs.1comp <- this.data.1comp.species$Fgutabs
        this.row$Reference <- this.data.1comp.species$Reference
      }
    }

    if (this.cas %in% fits2comp$CASRN)
    {
      this.data.2comp.species <- subset(this.data.2comp.species,
        param.value.type=="Fitted geometric mean")

    # If more than one source, require that the joint analysis worked:
      if (dim(this.data.2comp.species)[1]>1)
      {
        this.data.2comp.species <- subset(this.data.2comp.species, 
                            Data.Analyzed=="Joint Analysis")[1,]
      }
      if (dim(this.data.2comp.species)[1]>0) 
      {
        this.row$AIC.2comp <- this.data.2comp.species$AIC
        this.row$Vdist.2comp <- this.data.2comp.species$Vss
        this.row$kelim.2comp <- this.data.2comp.species$kelim
        this.row$V1.2comp <- this.data.2comp.species$V1
        this.row$k12.2comp <- this.data.2comp.species$k12
        this.row$k21.2comp <- this.data.2comp.species$k21
        this.row$kgutabs.2comp <- this.data.2comp.species$kgutabs
        this.row$Fgutabs.2comp <- this.data.2comp.species$Fgutabs
        this.row$Ralphatokelim.2comp <- this.data.2comp.species$Ralphatokelim
        this.row$Fbetaofalpha.2comp <- this.data.2comp.species$Fbetaofalpha
        this.row$alpha.2comp <- this.data.2comp.species$alpha
        this.row$beta.2comp <- this.data.2comp.species$beta
        this.row$Reference <- this.data.2comp.species$Reference
      }
    }

    if (is.na(this.row$AIC.flat)) this.row$AIC.flat <- Inf
    if (is.na(this.row$AIC.1comp)) this.row$AIC.1comp <- Inf
    if (is.na(this.row$AIC.2comp)) this.row$AIC.2comp <- Inf

    AICs <- c(this.row$AIC.flat,this.row$AIC.1comp,this.row$AIC.2comp)
    if (all(AICs==Inf))
    {
      this.row$Model <- "None"
      this.row$AIC.best <- NA
    } else if (this.row$AIC.2comp == min(AICs))
    {
      this.row$Model <- "2Comp"
      this.row$AIC.best <- this.row$AIC.2comp
    } else if (this.row$AIC.1comp == min(AICs))
    {
      this.row$Model <- "1Comp"
      this.row$AIC.best <- this.row$AIC.1comp
    } else {
      this.row$Model <- "Flat"
      this.row$AIC.best <- this.row$AIC.flat
    }

    if (this.row$Model != "Flat")
      if (this.row$Model == "1Comp")
      {
        this.row$Vdist <- this.row$Vdist.1comp
        this.row$kelim <- this.row$kelim.1comp
        this.row$kgutabs <- this.row$kgutabs.1comp
        this.row$Fgutabs <- this.row$Fgutabs.1comp
      } else 
      {
        this.row$Vdist <- this.row$Vdist.2comp
        this.row$kelim <- this.row$kelim.2comp
        this.row$kgutabs <- this.row$kgutabs.2comp
        this.row$Fgutabs <- this.row$Fgutabs.2comp
      }

    fittable <- rbind(fittable,this.row)
  }
}
fittable$halflife <- log(2)/fittable$kelim

#Lets only keep chemicals where we can fit a PK model:
fittable <- subset(fittable, !is.na(Model))

```

# Set the signfifant digits to something reasonable:
```{r subset_cvt_data, eval = TRUE}
CvT.data$Value <- signif(CvT.data$Value,3)
CvT.data$Time <- signif(CvT.data$Time,3)
CvT.data$calc_loq <- signif(CvT.data$calc_loq,3)

for (this.col in c(
  "AIC.flat", "AIC.1comp", "AIC.2comp", "AIC.best", "Vdist", "kelim", "kgutabs",
  "Fgutabs", "kgutabs.1comp","kgutabs.2comp",    
  "Vdist.1comp", "kelim.1comp", "Fgutabs.1comp", "Vdist.2comp", "V1.2comp",
  "k12.2comp", "k21.2comp", "kelim.2comp", "Fgutabs.2comp", 
  "Ralphatokelim.2comp","Fbetaofalpha.2comp","alpha.2comp","beta.2comp",
  "halflife"))
  fittable[,this.col] <- signif(fittable[,this.col], 3)
```

# We have TK parameters estimated for 262 chemicals:
```{r load_physchem, eval = TRUE}
dim(fittable)[1]
length(unique(fittable$DTXSID))

write.csv(fittable,file="SupTable-TKFits.txt",row.names=FALSE)
```

### 2022-10-25 MainAnalysis.Rmd
Minor bug fixes

--- 2022-05-12 figures_01312022.Rmd
@@
 
-```{r, run_invivoPKfit, eval = FALSE}
+```{r, run_invivoPKfit, eval = TRUE}
+
+THIS.DATE <- "102422"
 
@@
 
-write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.05092022.csv", row.names = FALSE)
-write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.05092022.csv", row.names = FALSE)
-
-write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.05092022.csv", row.names = FALSE)
-write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.05092022.csv", row.names = FALSE)
-
-write.csv(PK.fit.table.flat[[1]], "inst/ext/PK.fit.table.flat.05092022.csv", row.names = FALSE)
-write.csv(PK.fit.table.flat[[2]], "inst/ext/processed.flat.data.05092022.csv", row.names = FALSE)
+write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+
+write.csv(PK.fit.table.2comp[[1]], paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.2comp[[2]], paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+
+write.csv(PK.fit.table.flat[[1]], paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.flat[[2]], paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
 ```

### 2022-10-25 R/plot_conctime.R

@@ -39,7 +39,8 @@ plot_conctime <- function(PK.fit.table,
                           plot.httk.pred = F,
                           omit.zero = T,
                           plot.loq = T,
-                          fit.plot.points = 200)
+                          fit.plot.points = 200,
+                          data.dose.col = "dose_level_normalized")
 {
   scientific_10 <- function(x) {
     out <- gsub("1e", "10^", scales::scientific_format()(x))
@@ -49,7 +50,7 @@ plot_conctime <- function(PK.fit.table,
   }
 
   data.set <- copy(data.set)
-  if (omit.zero) data.set <- data.set[Dose > 0, ]
+  if (omit.zero) data.set <- data.set[data.set[,data.dose.col] > 0, ]
 
   if (plot.httk.pred) {
     PK.fit.table <- copy(PK.fit.table[param.value.type %in% c("Predicted",

### 2022-10-25 MainAnalysis.Rmd
Got plot_conctime working

@@
 
-```{r, run_invivoPKfit, eval = TRUE}
-
-THIS.DATE <- "102422"
+```{r, load_cvt, eval = TRUE}
 
@@
 # data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
-data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")
+cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")
 
@@
 
-data <- data %>%
+cvt.data <- cvt.data %>%
   filter(analyte_name_original != "Methemoglobin") %>%
@@
 ### fix compound names
-data$analyte_name_original[data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
-data$analyte_name_original[data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
-data$analyte_name_original[data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
-data$analyte_name_original[data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
-data$analyte_name_original[data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
-data$analyte_name_original[data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
+cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
+cvt.data$analyte_name_original[cvt.data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
+cvt.data$analyte_name_original[cvt.data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
+cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
+cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
+cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
 
 ### make fk_reference_document equal fk_extraction document if fk_reference_document is NULL
-data$fk_reference_document_id[data$fk_reference_document_id == "NULL"] <- data$fk_extraction_document_id[data$fk_reference_document_id == "NULL"]
+cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
+  cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]
 
@@
 # data <- data %>% filter(dsstox_casrn == "123-91-1")
-
+```
+
+Calculate a limit of quantification (90% of lowest observation)
+```{r, calc_loq, eval = TRUE}
+source.col <- "fk_study_id"
+cas.col <- "dsstox_casrn"
+media.col <- "conc_medium_normalized"
+value.col <- "conc"
+for (this.study in unique(cvt.data[,source.col]))
+{
+  this.subset1 <- subset(cvt.data,cvt.data[,source.col]==this.study)
+  for (this.chem in unique(this.subset1[,cas.col]))
+  {
+    this.subset2 <- subset(this.subset1,this.subset1[,cas.col]==this.chem)
+    for (this.media in unique(this.subset2[,media.col]))
+    {
+      this.subset3 <- subset(this.subset2,this.subset2[media.col]==this.media & 
+        !is.na(this.subset2[,value.col]))
+      this.subset3 <- subset(this.subset3,this.subset3[,value.col]>0)
+      this.loq <- suppressWarnings(min(this.subset3[,value.col], na.rm=TRUE))
+      this.loq <- this.loq*0.9
+      cvt.data[
+        cvt.data[,source.col]==this.study & 
+        cvt.data[,cas.col]==this.chem & 
+        cvt.data[,media.col]==this.media,"calc_loq"] <- this.loq
+    }
+  }
+}
+cvt.data <- subset(cvt.data,!is.infinite(calc_loq))
+
+```
+
+```{r, run_invivoPKfit_1comp, eval = TRUE}
+THIS.DATE <- "102422"
 ### do 1-Compartment fit
 system.time(PK.fit.table.1comp <- fit_all(
-  data.set = data,
+  data.set = cvt.data,
   model = "1compartment",
@@
 ))
-
+```
+
+```{r, plot_1comp, eval=TRUE}
+plot_conctime(PK.fit.table.1comp[[1]],cvt.data,"1compartment")
+head(subset(PK.fit.table.1comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
+```
+
+```{r, run_invivoPKfit_2comp, eval = TRUE}
 ### do 2-Compartment fit
 system.time(PK.fit.table.2comp <- fit_all(
-  data.set = data,
+  data.set = cvt.data,
   model = "2compartment",
@@
 ))
-
+```
+
+```{r, run_invivoPKfit_flat, eval = TRUE}
 ### do flat fit
 system.time(PK.fit.table.flat <- fit_all(
-  data.set = data,
+  data.set = cvt.data,
   model = "flat",

### 2022-10-25 R/analyze_pk_data.R

@@ -51,7 +51,7 @@ analyze_pk_data <- function(fitdata,
   #Add a different sigma value for each reference
   refs <- fitdata[,
                   unique(Reference)]
-  # Initialize the standard devications to 0.2
+  # Initialize the standard deviations to 0.2
   these.params[sapply(refs,
                       function(x) paste('sigma2',
                                         x,

### 2022-10-25 merge_model_fits.R

@@ -1,0 +1,235 @@
+#' Merge tables from fit_all from different models and select best fitting model
+#'
+#' This takes multiple tables of pharmcokinetic parameters (one table per model)
+#' genetated by \code{\link{fit_all}}
+#' and merges them into a table containing one row per chemical-species 
+#' combination. Each row contains all the model
+#' parameters estimated for that model, and a set of optimal parameters as 
+#' identified from the AIC. This function assigns each chemical a column 
+#' "Model" containing the name of he winning (lowest AIC) model and, from that
+#' winning model, reports "Vdist", "kelim", "thalf", "kgutabs", "Fbioavail".
+#'
+#' @param fit_list a named list of PK parameter tables from \code{\link{fit_all}}
+#' -- the names should be the names of the models
+#'
+#' @return A data.frame with one row per chemical-species combination
+#'
+#' @author John Wambaugh
+#'
+#' @export merge_model_fits 
+function <- merge_model_fits(fit.list)
+{
+}
+  fittable <- data.frame(
+        DTXSID=NA,
+        Compound=NA,
+        CAS=NA,
+        Species=NA,
+        Reference=NA,
+        AIC.best=NA,
+        Model=NA,
+        Vdist=NA,
+        kelim=NA,
+        kgutabs=NA,
+        Fgutabs=NA)
+
+  for (this.table.name in sort(unique(names(fit.list))))
+  {
+    this.table <- fit.list[[this.table.name]]
+    this.table$Css <- 1/this.table$CLtot
+    
+    # Check for pathological fits, set AIC to Inf:
+    if ("k12" %in% colnames(this.table))
+    {
+      # Negative k12 indicates bad fit:
+      badfits <- this.table$k12
+      badfits[is.na(badfits)]<-0
+      badfits <- ifelse(badfits<0,TRUE,FALSE)
+      this.table[badfits,"AIC"] <- Inf
+    }    
+   
+    for (this.dtxsid in this.table$DTXSID) 
+    { 
+      this.compound <- subset(this.table, DTXSID==this.dtxsid)$PREFERRED_NAME[1]
+      this.cas <- subset(this.table, DTXSID==this.dtxsid)$CASRN[1]
+
+      this.subset <- subset(this.table,DTXSID == this.dtxsid)
+      
[…]

### 2022-10-26 MainAnalysis.Rmd
Most of MainAnalysis.Rmd working now

@@
 library(readxl)
-devtools::load_all(".")
+devtools::load_all("invivopkfit")
 ```
@@
 
-```{r, plot_1comp, eval=TRUE}
+```{r, plot_1comp, eval=FALSE}
 plot_conctime(PK.fit.table.1comp[[1]],cvt.data,"1compartment")
@@
 ```
+```{r, plot_2comp, eval=FALSE}
+plot_conctime(PK.fit.table.2comp[[1]],cvt.data,"2compartment")
+head(subset(PK.fit.table.2comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
+```
 
@@
 ))
-
-### uncomment below to export to CSV files
-# change the date!!
-
+```
+
+```{r, write_invivoPKfits_to_file, eval = TRUE}
 write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
@@
 
-### read in PK output files
-# pk_output_1comp_12212021 <- read.csv("inst/ext/PK.fit.table.1comp.12212021.csv")
-# pk_output_2comp_02102022 <- read.csv("inst/ext/PK.fit.table.2comp.02102022.csv")
-# pk_output_flat_02102022 <- read.csv("inst/ext/PK.fit.table.flat.02102022.csv")
-
-# pk_output_1comp_03012022 <- read.csv("inst/ext/PK.fit.table.1comp.03012022.csv")
-# pk_output_2comp_03012022<- read.csv("inst/ext/PK.fit.table.2comp.03012022.csv")
-# pk_output_flat_03012022 <- read.csv("inst/ext/PK.fit.table.flat.03012022.csv")
-
-pk_output_1comp_04282022 <- read.csv("inst/ext/PK.fit.table.1comp.04282022.csv")
-pk_output_2comp_04282022<- read.csv("inst/ext/PK.fit.table.2comp.04282022.csv")
-pk_output_flat_04282022 <- read.csv("inst/ext/PK.fit.table.flat.04282022.csv")
-
-pk_output_2comp_05092022 <- read.csv("inst/ext/PK.fit.table.2comp.05092022.csv")
-pk_output_flat_05092022 <- read.csv("inst/ext/PK.fit.table.flat.05092022.csv")
-pk_output_1comp_05092022 <- read.csv("inst/ext/PK.fit.table.1comp.05092022.csv")
-
-### read in processed raw data files
-# raw_1comp_12212021 <- read.csv("inst/ext/processed.1comp.data.12212021.csv")
-# raw_2comp_02102022 <- read.csv("inst/ext/processed.2comp.data.02102022.csv")
-# raw_flat_02102022 <- read.csv("inst/ext/processed.flat.data.02102022.csv")
-
-# raw_1comp_03012022 <- read.csv("inst/ext/processed.1comp.data.03012022.csv")
-# raw_2comp_03012022 <- read.csv("inst/ext/processed.2comp.data.03012022.csv")
-# raw_flat_03012022 <- read.csv("inst/ext/processed.flat.data.03012022.csv")
-
-# raw_1comp_04142022 <- read.csv("inst/ext/processed.1comp.data.04142022.csv")
-# raw_2comp_04142022 <- read.csv("inst/ext/processed.2comp.data.04142022.csv")
-# raw_flat_04142022 <- read.csv("inst/ext/processed.flat.data.04142022.csv")
-
-raw_1comp_04282022 <- read.csv("inst/ext/processed.1comp.data.04282022.csv")
-raw_2comp_04282022 <- read.csv("inst/ext/processed.2comp.data.04282022.csv")
-raw_flat_04282022 <- read.csv("inst/ext/processed.flat.data.04282022.csv")
-
-raw_1comp_05092022 <- read.csv("inst/ext/processed.1comp.data.05092022.csv")
-raw_2comp_05092022 <- read.csv("inst/ext/processed.2comp.data.05092022.csv")
-raw_flat_05092022 <- read.csv("inst/ext/processed.flat.data.05092022.csv")
+pk_output_2comp <- read.csv(paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""))
+pk_output_flat <- read.csv(paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""))
+pk_output_1comp <- read.csv(paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""))
+
+raw_1comp <- read.csv(paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""))
+raw_2comp <- read.csv(paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""))
+raw_flat <- read.csv(paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""))
 
@@
 ### save data
-# save(pk_output_1comp_12212021, file = "figures_rdata/pk_output_1comp_12212021.Rdata")
-# save(pk_output_2comp_02102022, file = "figures_rdata/pk_output_2comp_12212021.Rdata")
-# save(pk_output_flat_02102022, file = "figures_rdata/pk_output_flat_02102022.Rdata")
-# save(raw_1comp_12212021, file = "figures_rdata/raw_1comp_12212021.Rdata")
-# save(raw_2comp_02102022, file = "figures_rdata/raw_2comp_12212021.Rdata")
-# save(raw_flat_02102022, file = "figures_rdata/raw_flat_02102022.Rdata")
-
-# save(pk_output_1comp_03012022, file = "figures_rdata/pk_output_1comp_03012022.Rdata")
-# save(pk_output_2comp_03012022, file = "figures_rdata/pk_output_2comp_03012022.Rdata")
-# save(pk_output_flat_03012022, file = "figures_rdata/pk_output_flat_03012022.Rdata")
-# save(raw_1comp_03012022, file = "figures_rdata/raw_1comp_03012022.Rdata")
-# save(raw_2comp_03012022, file = "figures_rdata/raw_2comp_03012022.Rdata")
-# save(raw_flat_03012022, file = "figures_rdata/raw_flat_03012022.Rdata")
-
-# save(pk_output_1comp_04142022, file = "figures_rdata/pk_output_1comp_04142022.Rdata")
-# save(pk_output_2comp_04142022, file = "figures_rdata/pk_output_2comp_04142022.Rdata")
-# save(pk_output_flat_04142022, file = "figures_rdata/pk_output_flat_04142022.Rdata")
-# save(raw_1comp_04142022, file = "figures_rdata/raw_1comp_04142022.Rdata")
-# save(raw_2comp_04142022, file = "figures_rdata/raw_2comp_04142022.Rdata")
-# save(raw_flat_04142022, file = "figures_rdata/raw_flat_04142022.Rdata")
-
-save(pk_output_1comp_05092022, file = "figures_rdata/pk_output_1comp_05092022.Rdata")
-save(pk_output_2comp_05092022, file = "figures_rdata/pk_output_2comp_05092022.Rdata")
-save(pk_output_flat_05092022, file = "figures_rdata/pk_output_flat_05092022.Rdata")
-save(raw_1comp_05092022, file = "figures_rdata/raw_1comp_05092022.Rdata")
-save(raw_2comp_05092022, file = "figures_rdata/raw_2comp_05092022.Rdata")
-save(raw_flat_05092022, file = "figures_rdata/raw_flat_05092022.Rdata")
-
-save(pk_lombardo, file = "figures_rdata/pk_lombardo_02072022.Rdata")
-```
-
-```{r, load_data}
-
-### this block loads the Rdata files,
-# as well as some other files written in below code blocks
-# this saves time from having to run those below code blocks every time
-# these additional files include 'cp_df' and 'cvt_variability'
-
-### load all of this wonderful data
-# load("figures_rdata/pk_output_1comp_12212021.Rdata")
-# load("figures_rdata/pk_output_2comp_12212021.Rdata")
-# load("figures_rdata/raw_1comp_12212021.Rdata")
-# load("figures_rdata/raw_2comp_12212021.Rdata")
-# load("figures_rdata/cp_df_12212021.Rdata")
-# load("figures_rdata/cvt_variability_df_12212021.Rdata")
-
-# load("figures_rdata/pk_output_1comp_03012022.Rdata")
-# load("figures_rdata/pk_output_2comp_03012022.Rdata")
-# load("figures_rdata/pk_output_flat_03012022.Rdata")
-# load("figures_rdata/raw_1comp_03012022.Rdata")
-# load("figures_rdata/raw_2comp_03012022.Rdata")
-# load("figures_rdata/raw_flat_03012022.Rdata")
-# load("figures_rdata/cp_df_03012022.Rdata")
-# load("figures_rdata/cvt_variability_df_03012022.Rdata")
-
-# load("figures_rdata/pk_output_1comp_04142022.Rdata")
-# load("figures_rdata/pk_output_2comp_04142022.Rdata")
-# load("figures_rdata/pk_output_flat_04142022.Rdata")
-# load("figures_rdata/raw_1comp_04142022.Rdata")
-# load("figures_rdata/raw_2comp_04142022.Rdata")
-# load("figures_rdata/raw_flat_04142022.Rdata")
-# load("figures_rdata/cp_df_04142022.Rdata")
-# load("figures_rdata/cvt_variability_df_04142022.Rdata")
-# 
-# load("figures_rdata/cp_df_03302022.Rdata")
-
-# load("figures_rdata/pk_output_1comp_04282022.Rdata")
-# load("figures_rdata/pk_output_2comp_04282022.Rdata")
-# load("figures_rdata/pk_output_flat_04282022.Rdata")
-# load("figures_rdata/raw_1comp_04282022.Rdata")
-# load("figures_rdata/raw_2comp_04282022.Rdata")
-# load("figures_rdata/raw_flat_04282022.Rdata")
-# load("figures_rdata/cp_df_04282022.Rdata")
-# load("figures_rdata/cvt_variability_df_04282022.Rdata")
-# 
-# load("figures_rdata/cp_df_04282022.Rdata")
-
-load("figures_rdata/pk_output_1comp_05092022.Rdata")
-load("figures_rdata/pk_output_2comp_05092022.Rdata")
-load("figures_rdata/pk_output_flat_05092022.Rdata")
-load("figures_rdata/raw_1comp_05092022.Rdata")
-load("figures_rdata/raw_2comp_05092022.Rdata")
-load("figures_rdata/raw_flat_05092022.Rdata")
-load("figures_rdata/cp_df_05092022.Rdata")
-load("figures_rdata/cvt_variability_df_05092022.Rdata")
-
-load("figures_rdata/cp_df_05092022.Rdata")
-
-load("figures_rdata/pk_lombardo_02072022.Rdata")
-```
-
-```{r, make_invivoPKfit_plots, eval = FALSE}
+paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".RData",sep="")
+save(pk_output_1comp, file = paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
+save(pk_output_2comp, file = paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
+save(pk_output_flat, file = paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
+save(raw_1comp, file = paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
+save(raw_2comp, file = paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
+save(raw_flat, file = paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
+
+save(pk_lombardo, file = paste("figures_rdata/pk_lombardo",THIS.DATE,".RData",sep=""))
+```
+
+```{r, make_invivoPKfit_plots, eval = TRUE}
 
@@
 ### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data1 <- pk_output_1comp_05092022 %>%
+pk_data1 <- pk_output_1comp %>%
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
@@
 
-raw_data1 <- dplyr::select(raw_1comp_05092022, -c("kelim", 
+raw_data1 <- dplyr::select(raw_1comp, -c("kelim", 
                                                   "Vdist", 
@@
 
-cp_df_05092022 <- cp_df
-
 ### here is where you save the Rdata file
-save(cp_df_05092022, file = "figures_rdata/cp_df_05092022.Rdata")
+save(cp_df, file = paste(figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
+```
+
+```{r, load_data}
+
+### this block loads the Rdata files,
+# as well as some other files written in below code blocks
+# this saves time from having to run those below code blocks every time
+# these additional files include 'cp_df' and 'cvt_variability'
+
+### load all of this wonderful data
+load(paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
+load(paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
+load(paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
+load(paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
+load(paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
+load(paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
+load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
+load(paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))
+
+load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
+
+load("figures_rdata/pk_lombardo_02072022.Rdata")
 ```

### 2022-10-26 invivopkfit/R/noncomp_avg_value.R

@@ -1,0 +1,39 @@
+#' Helper function to take average value of replicate timepoints
+#'
+#' @param data A table of concentration-time data.
+#'
+#' @return A data.table with average concentration values
+#'
+#' @author Christopher Cook
+#' @importFrom magrittr "%>%"
+
+### function to take average of multiple timepoints
+noncomp_avg_value <- function(data) {
+
+  ### convert to data.frame, but fix this later because converting back and forth is silly
+  data <- as.data.frame(data)
+
+  ### if there are replicate timepoints, take the average Value for each timepoint
+  if(length(unique(data$Time)) < length(data$Time)) {
+    data <- data %>%
+      dplyr::group_by(Time) %>%
+      dplyr::do(dplyr::mutate(., mean = mean(.$Value, na.rm = TRUE)))
+
+    ### if all values are NA, output will return 'NaN's
+    ### coerces 'NaN's back to NA
+    data$mean[is.nan(data$mean)] <- NA
+
+    ### remove replicate timepoints
+    data <- data %>%
+      dplyr::distinct(Time, .keep_all = TRUE)
+
+    ### delete Value column and reassign new mean column as Value column
+    data$Value <- NULL
+    names(data)[names(data) == "mean"] <- "Value"
+  }
+
+  data <- as.data.table(data)
+
+  data
+}
+

### 2022-10-26 invivopkfit/R/plot_conctime.R

@@ -1,0 +1,412 @@
+#' plot_conctime
+#'
+#' Creates a PDF of the fits from \code{\link{fit_all}} and data together
+#'
+#'
+#' @param PK.fit.table Table of parameter estimates from \code{\link{fit_all}}
+#' @param data.set A data.table of concentration vs. time data for a given
+#' chemical
+#' @param model Analytic model to evaluate. Currently only "1compartment" or
+#' "2compartment" are implemented.
+#' @param mean.type (Defaults to fitted geometric mean)
+#' @param fit.factors Add a trend-line using the fit for each combination of
+#' the factors listed in this character vector. (defaults to Compound,
+#' Dose.nominal, Data.Analyzed, and Route)
+#' @param plot.split.factor For each compound, make a separate plot for each
+#' unique value of this factor (defaults to Route) #param shape.factor Indicate
+#' this factor by shape in the plots (defaulta to Data.Analyzed)
+#' @param color.factor Indicate this factor by color in the plots (defaults to
+#' Data.Analyzed')
+#' @param plot.httk.pred placeholder
+#' @param omit.zero Drop zero dose values from plots (default = TRUE)
+#' @param plot.loq placeholder
+#' @param fit.plot.points placeholder
+#' @return None
+#' @author Caroline Ring, John Wambaugh
+#' @export plot_conctime
+plot_conctime <- function(PK.fit.table,
+                          data.set,
+                          model,
+                          mean.type = "Fitted geometric mean",
+                          fit.factors = c("Compound",
+                                          "Data.Analyzed",
+                                          "Dose.nominal",
+                                          "Route",
+                                          "LOQ"),
+                          plot.split.factor = "Route",
+                          # shape.factor="Data.Analyzed",
+                          color.factor = "Data.Analyzed",
+                          plot.httk.pred = F,
+                          omit.zero = T,
+                          plot.loq = T,
+                          fit.plot.points = 200,
+                          data.dose.col = "dose_level_normalized",
+                          data.compound.col = "preferred_name",
+                          data.cas.col = "dsstox_casrn",
+                          data.source.col = "fk_study_id",
+                          data.route.col = "administration_route_normalized",
+                          data.reference.col = "fk_reference_document_id",
[…]

### 2022-10-26 MainAnalysis.Rmd
Everything but 2comp plots and make_joint_sigma_plot working

@@
 ### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data2 <- pk_output_2comp_05092022 %>%
+pk_data2 <- pk_output_2comp %>%
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
 
-raw_data2 <- dplyr::select(raw_2comp_05092022, -c("kelim", 
+raw_data2 <- dplyr::select(raw_2comp, -c("kelim", 
                                                   "Vdist", 
@@
 
-pk_data_flat <- pk_output_flat_05092022 %>%
+pk_data_flat <- pk_output_flat %>%
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
@@
 
-raw_data_flat <- dplyr::select(raw_flat_05092022, -c("A")) %>% 
+raw_data_flat <- dplyr::select(raw_flat, -c("A")) %>% 
   filter(Species != "hamster")
@@
 
-# cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
-# 
-# cp_df <- cp_df %>% group_by(Species.x, 
-#                             Compound,
-#                             CAS,
-#                             type) %>%
-#   mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))
+cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
+
+cp_df <- cp_df %>% group_by(Species.x, 
+                           Compound,
+                           CAS,
+                           type) %>%
+ mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))
 
 ### here is where you save the Rdata file
-save(cp_df, file = paste(figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
+save(cp_df, file = paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
+```
+
+```{r, make_cvt_variability_rdata, eval = FALSE}
+
+### this block creates a data.frame that shows the 
+# spread of CvT data via across replicate timepoints 
+# for a single experiment
+# if the data isn't within 2-fold of itself
+# is it reasonable to say that a model should fit within 2-fold?
+
+##################
+##################
+
+### all the raw data for each model SHOULD be the same
+# so only need to use one
+data <- as.data.table(raw_1comp)
+
+##################
+##################
+
+### function that finds mean conc of each replicate timepoint
+find_mean_conc <- function(data) {
+
+  ### only use data with replicate timepoints
+  data <- data[ ave(1:nrow(data), data$Time, FUN = length) > 1 , ]
+
+  if(nrow(data) == 0) {
+    return(NULL)
+  } else {
+
+    time_split <- split(data, data$Time)
+
+    ### discard replicate timepoints where all concentrations are NA
+    time_split_list <- purrr::discard(time_split, ~all(is.na(.$Value)))
+
+    if(length(time_split_list) == 0) {
+      return(NULL)
+    } else {
+
+      data <- do.call(rbind, time_split_list)
+
+      ### where some replicate concentration data are NA, set them equal to the LOQ
+      data$Value[is.na(data$Value)] <- data$LOQ[is.na(data$Value)]
+
+      ### take the average Value for each set of timepoints
+      data <- data %>%
+        group_by(Time) %>%
+        do(mutate(., mean_conc = mean(.$Value, na.rm = TRUE)))
+
+      data <- data %>%
+        group_by(Time) %>%
+        do(mutate(., range_conc = max(.$Value) - min(.$Value)))
+
+      ### create normalized conc values by dividing conc by mean_conc
+      data$conc_norm <- data$Value/data$mean_conc
+
+      data <- data[order(data$Time), ]
+
+      return(data)
+    }
+  }
+}
+
+### this for loop applies the function 
+# at data subsets of compound, data, dose, route, media
+data.list <- list()
+for(this.compound in unique(data[, Compound])) {
+  this.compound.data <- data[Compound == this.compound]
+
+  ### list of columns by which to split data.set
+  col_list <- list(this.compound.data$Reference,
+                   this.compound.data$Dose,
+                   this.compound.data$Route,
+                   this.compound.data$Media)
+
+  ### split data.set into list of data.tables
+  split_list <- split(this.compound.data, col_list)
+
+  ### remove data.tables with 0 rows
+  split_list <- keep(split_list, ~nrow(.) > 0)
+
+  ### use find_mean_conc fn
+  mean_conc <- lapply(split_list, find_mean_conc)
+
+  test <- do.call(rbind, mean_conc)
+
+  data.list[[this.compound]] <- test
+}
+
+### combine data.tables back into one large data.set
+cvt_variability_df <- do.call(rbind, data.list)
+
+### SAVE the data
+save(cvt_variability_df, file = paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))
 ```
@@
 
-pk_data <- cp_df_05092022
+pk_data <- cp_df
 
@@
 # data <- cp_df_03012022
-data <- cp_df_04282022
+data <- cp_df
 
@@
 
-data <- cp_df_04282022
+data <- cp_df
 
@@
 
-```{r, make_cvt_variability_rdata, eval = FALSE}
-
-### this block creates a data.frame that shows the 
-# spread of CvT data via across replicate timepoints 
-# for a single experiment
-# if the data isn't within 2-fold of itself
-# is it reasonable to say that a model should fit within 2-fold?
-
-##################
-##################
-
-### all the raw data for each model SHOULD be the same
-# so only need to use one
-data <- as.data.table(raw_1comp_05092022)
-
-##################
-##################
-
-### function that finds mean conc of each replicate timepoint
-find_mean_conc <- function(data) {
-
-  ### only use data with replicate timepoints
-  data <- data[ ave(1:nrow(data), data$Time, FUN = length) > 1 , ]
-
-  if(nrow(data) == 0) {
-    return(NULL)
-  } else {
-
-    time_split <- split(data, data$Time)
-
-    ### discard replicate timepoints where all concentrations are NA
-    time_split_list <- purrr::discard(time_split, ~all(is.na(.$Value)))
-
-    if(length(time_split_list) == 0) {
-      return(NULL)
-    } else {
-
-      data <- do.call(rbind, time_split_list)
-
-      ### where some replicate concentration data are NA, set them equal to the LOQ
-      data$Value[is.na(data$Value)] <- data$LOQ[is.na(data$Value)]
-
-      ### take the average Value for each set of timepoints
-      data <- data %>%
-        group_by(Time) %>%
-        do(mutate(., mean_conc = mean(.$Value, na.rm = TRUE)))
-
-      data <- data %>%
-        group_by(Time) %>%
-        do(mutate(., range_conc = max(.$Value) - min(.$Value)))
-
-      ### create normalized conc values by dividing conc by mean_conc
-      data$conc_norm <- data$Value/data$mean_conc
-
-      data <- data[order(data$Time), ]
-
-      return(data)
-    }
-  }
-}
-
-### this for loop applies the function 
-# at data subsets of compound, data, dose, route, media
-data.list <- list()
-for(this.compound in unique(data[, Compound])) {
-  this.compound.data <- data[Compound == this.compound]
-
-  ### list of columns by which to split data.set
-  col_list <- list(this.compound.data$Reference,
-                   this.compound.data$Dose,
-                   this.compound.data$Route,
-                   this.compound.data$Media)
-
-  ### split data.set into list of data.tables
-  split_list <- split(this.compound.data, col_list)
-
-  ### remove data.tables with 0 rows
-  split_list <- keep(split_list, ~nrow(.) > 0)
-
-  ### use find_mean_conc fn
-  mean_conc <- lapply(split_list, find_mean_conc)
-
-  test <- do.call(rbind, mean_conc)
-
-  data.list[[this.compound]] <- test
-}
-
-### combine data.tables back into one large data.set
-cvt_variability_df_05092022 <- do.call(rbind, data.list)
-
-### SAVE the data
-save(cvt_variability_df_05092022, file = "figures_rdata/cvt_variability_df_05092022.Rdata")
-```
-
 ```{r, make_cvt_variability_histogram}
@@
 
-data <- cvt_variability_df_05092022
+data <- cvt_variability_df
 # data <- cvt_variability_df_12212021
@@
 # pk_data <- cp_df_03012022
-pk_data <- cp_df_05092022
-
-cvt_data <- cvt_variability_df_05092022
+pk_data <- cp_df
+
+cvt_data <- cvt_variability_df
 
@@
 # pk_data <- cp_df_03012022
-pk_data <- cp_df_04282022
-
-cvt_data <- cvt_variability_df_04282022
+pk_data <- cp_df
+
+cvt_data <- cvt_variability_df
 
@@
 
-data <- raw_1comp_04282022
+data <- raw_1comp
 
@@
 
-data1 <- as.data.table(pk_output_1comp_04282022 %>%
+data1 <- as.data.table(pk_output_1comp %>%
                          filter(param.value.type == "Fitted geometric mean"))
 
-data2 <- as.data.table(pk_output_2comp_04282022 %>%
+data2 <- as.data.table(pk_output_2comp %>%
                          filter(param.value.type == "Fitted geometric mean"))
@@
 data1 <- data1 %>% filter(sigma_id != "sigma2.14")
-data1$`Joint Analysis` <- as.numeric(data1$`Joint Analysis`)
-data1$`Ind Analysis` <- as.numeric(data1$`Ind Analysis`)
+data1$`Joint Analysis` <- lapply(data1$`Joint Analysis`,as.numeric)
+data1$`Ind Analysis` <- lapply(data1$`Ind Analysis`,as.numeric)
 data1$model <- "1-Compartment"
@@
 data2 <- data2 %>% filter(sigma_id != "sigma2.14")
-data2$`Joint Analysis` <- as.numeric(data2$`Joint Analysis`)
-data2$`Ind Analysis` <- as.numeric(data2$`Ind Analysis`)
+data2$`Joint Analysis` <- lapply(data2$`Joint Analysis`,as.numeric)
+data2$`Ind Analysis` <- lapply(data2$`Ind Analysis`,as.numeric)
 data2$model <- "2-Compartment"
 
-data <- rbind(data1, data2)
+data <- as.data.table(rbind(data1, data2))
 
@@
 
-raw_data1 <- raw_1comp_04282022
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp_04282022 %>% 
+raw_data1 <- raw_1comp
+
+##################
+##################
+
+pk_data1 <- pk_output_1comp %>% 
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
@@
 
-raw_data1 <- dplyr::select(raw_data1, -c("X",
-                                         "kelim",
+raw_data1 <- dplyr::select(raw_data1, -c("kelim",
                                          "Vdist",
@@
 
-raw_data2 <- raw_2comp_04282022
-
-pk_data2 <- pk_output_2comp_04282022 %>% 
+raw_data2 <- raw_2comp
+
+pk_data2 <- pk_output_2comp %>% 
   filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
@@
 
-raw_data1 <- raw_1comp_04282022
+raw_data1 <- raw_1comp
 
@@
 
-pk_data1 <- pk_output_1comp_04282022 
+pk_data1 <- pk_output_1comp
 # pk_data1 <- pk_output_1comp_12212021
 
-pk_data2 <- pk_output_2comp_04282022 
+pk_data2 <- pk_output_2comp
 # pk_data2 <- pk_output_2comp_12212021
@@
 
-pk_data1 <- as.data.table(pk_output_1comp_04282022)
-pk_data2 <- as.data.table(pk_output_2comp_04282022)
+pk_data1 <- as.data.table(pk_output_1comp)
+pk_data2 <- as.data.table(pk_output_2comp)
 
@@
   this.compound.data <- pk_all[Compound == this.compound]
+  this.compound.data$AIC[is.na(this.compound.data$AIC)] <- Inf
 
@@
 
-pk_data1 <- pk_output_1comp_04282022
-
-pk_data2 <- pk_output_2comp_04282022
-
-pk_data_flat <- pk_output_flat_04282022 %>%
+pk_data1 <- pk_output_1comp
+
+pk_data2 <- pk_output_2comp
+
+pk_data_flat <- pk_output_flat %>%
   filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")
@@
 
-pk_data1 <- pk_output_1comp_05092022
+pk_data1 <- pk_output_1comp
 # pk_data1 <- pk_output_1comp_04282022

### 2022-10-27 MainAnalysis.Rmd
Trying to add DTXSIDs

@@
 # data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
-cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022.csv")
+cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")
 
@@
 
-```{r, run_invivoPKfit_1comp, eval = TRUE}
+```{r, set_file_timestamp, eval = TRUE}
 THIS.DATE <- "102422"
+```
+
+```{r, run_invivoPKfit_1comp, eval = FALSE}
 ### do 1-Compartment fit
@@
   compound.col = "analyte_name_original",
+  dtxsid.col = "dsstox_substance_id",
   cas.col = "dsstox_casrn",
@@
 ))
-```
-
-```{r, plot_1comp, eval=FALSE}
-plot_conctime(PK.fit.table.1comp[[1]],cvt.data,"1compartment")
-head(subset(PK.fit.table.1comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
 ```
@@
 pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
+```
+
+```{r, merge_pkfits, eval=FALSE}
+all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
+                                       "2compartment="=pk_output_2comp,
+                                       "flat"=pk_output_flat))
+
 ```

### 2022-10-29 MainAnalysis.Rmd
Switched to using DTXSIDs

@@
 ```{r, calc_loq, eval = TRUE}
-source.col <- "fk_study_id"
-cas.col <- "dsstox_casrn"
-media.col <- "conc_medium_normalized"
-value.col <- "conc"
-for (this.study in unique(cvt.data[,source.col]))
-{
-  this.subset1 <- subset(cvt.data,cvt.data[,source.col]==this.study)
-  for (this.chem in unique(this.subset1[,cas.col]))
-  {
-    this.subset2 <- subset(this.subset1,this.subset1[,cas.col]==this.chem)
-    for (this.media in unique(this.subset2[,media.col]))
-    {
-      this.subset3 <- subset(this.subset2,this.subset2[media.col]==this.media & 
-        !is.na(this.subset2[,value.col]))
-      this.subset3 <- subset(this.subset3,this.subset3[,value.col]>0)
-      this.loq <- suppressWarnings(min(this.subset3[,value.col], na.rm=TRUE))
-      this.loq <- this.loq*0.9
-      cvt.data[
-        cvt.data[,source.col]==this.study & 
-        cvt.data[,cas.col]==this.chem & 
-        cvt.data[,media.col]==this.media,"calc_loq"] <- this.loq
-    }
-  }
-}
-cvt.data <- subset(cvt.data,!is.infinite(calc_loq))
-
+cvt.data <- estimate_loq(cvt.data)
 ```
@@
 
-```{r, run_invivoPKfit_1comp, eval = FALSE}
+```{r, run_invivoPKfit_1comp, eval = TRUE}
 ### do 1-Compartment fit
@@
   subject.default = NA,
-  info.default = NA
+  info.default = NA,
+  suppress.messages = TRUE
 ))
@@
   compound.col = "analyte_name_original",
+    dtxsid.col = "dsstox_substance_id",
   cas.col = "dsstox_casrn",
@@
   subject.default = NA,
-  info.default = NA
+  info.default = NA,
+  suppress.messages=TRUE
 ))

### 2022-10-31 MainAnalysis.Rmd
DTXSID's working

@@
 
-```{r, run_invivoPKfit_1comp, eval = TRUE}
+```{r, run_invivoPKfit_1comp, eval = FALSE}
 ### do 1-Compartment fit
@@
   source.col = "document_id",
-  loq.default = NA,
+  loq.col ="calc_loq",
   subject.default = NA,
@@
 
-```{r, run_invivoPKfit_2comp, eval = TRUE}
+```{r, run_invivoPKfit_2comp, eval = FALSE}
 ### do 2-Compartment fit
@@
 ```
-```{r, plot_2comp, eval=FALSE}
-plot_conctime(PK.fit.table.2comp[[1]],cvt.data,"2compartment")
+```{r, plot_2comp, eval=TRUE}
+plot_conctime(PK.fit.table.2comp[[1]],cvt.data,model="2compartment")
 head(subset(PK.fit.table.2comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
@@
 
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp_05092022),
-                      data.set = as.data.table(raw_1comp_05092022),
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp),
+                      data.set = as.data.table(raw_1comp),
                       model = "1compartment")
@@
 ### 2 compartment
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_05092022),
-                      data.set = as.data.table(raw_2comp_05092022),
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp),
+                      data.set = as.data.table(raw_2comp),
                       model = "2compartment")
 
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_flat_05092022),
-                      data.set = as.data.table(raw_flat_05092022),
+junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_flat),
+                      data.set = as.data.table(raw_flat),
                       model = "flat")

### 2022-11-02 MainAnalysis.Rmd
Added rough draft manuscript

@@
 ```
-```{r, plot_2comp, eval=TRUE}
-plot_conctime(PK.fit.table.2comp[[1]],cvt.data,model="2compartment")
-head(subset(PK.fit.table.2comp[[1]],Vdist>10000&!is.infinite(AIC)&param.value.type=="Fitted geometric mean"))
-```
-
-```{r, run_invivoPKfit_flat, eval = TRUE}
+
+```{r, run_invivoPKfit_flat, eval = FALSE}
 ### do flat fit
@@
 
-```{r, write_invivoPKfits_to_file, eval = TRUE}
+```{r, write_invivoPKfits_to_file, eval = FALSE}
 write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
@@
                                        "2compartment="=pk_output_2comp,
-                                       "flat"=pk_output_flat))
+                                       "flat"=pk_output_flat),
+                                        dtxsid.col = "DTXSID",
+                                  species.col = "Species")
 

### 2022-11-02 invivopkfit/R/merge_model_fits.R

@@ -32,11 +32,11 @@
 #'
 #' @export merge_model_fits
 merge_model_fits <- function(fit.list,
-        compound.col="",
-        dtxsid.col="",
-        cas.col="",
-        species.col="",
-        param.value.type.col="",
+        compound.col="Compound",
+        dtxsid.col="DTXSID",
+        cas.col="CAS",
+        species.col="Species",
+        param.value.type.col="param.value.type",
         data.analyzed.col="Data.Analyzed",
         param.value.type="Fitted geometric mean")
 {
@@ -59,8 +59,14 @@ merge_model_fits <- function(fit.list,
 
     # select for the correct parameter type
     if (param.value.type.col %in% colnames(this.table))
-      this.table <- subset(this.table, this.table[,param.value.type.col] ==
-                           param.value.type)
+    {
+      this.table <- this.table[this.table[,param.value.type.col] ==
+                           param.value.type,]
+    } else stop(paste(param.value.type,
+                      "not found in column",
+                      param.value.type.col,
+                      "for table",
+                      this.table.name))
 
     # Check for pathological fits, set AIC to Inf:
     if ("kelim" %in% colnames(this.table))
@@ -96,12 +102,13 @@ merge_model_fits <- function(fit.list,
 
       for (this.species in unique(this.subset[,species.col]))
       {
-        this.species.subset < subset(this.table,this.subset[,species.col] ==
+        this.species.subset <- subset(this.subset, this.subset[,species.col] ==
                                      this.species)
 
         # If more than one source, require that the joint analysis worked:
         if (dim(this.species.subset)[1]>1)
         {
+          browser()
           if ("Joint Analysis" %in% this.species.subset[,data.analyzed.col])
           {
             this.species.subset <- subset(this.species.subset,
@@ -119,20 +126,20 @@ merge_model_fits <- function(fit.list,
         {
           this.index <- which(main.table$DTXSID == this.dtxsid)
         } else this.index <- dim(main.table)[1]+1
-        # See if this chemical-spcies combo is already in the main fittable:
-        if (this.species %in% main.table[this.index,Species])
+        # See if this chemical-species combo is already in the main fittable:
+        if (this.species %in% main.table[this.index,species.col])
         {
           this.index <- this.index & main.table$Species==this.species
         } else this.index <- dim(main.table)[1]+1
 
-        model.postfix <- substr(this.model,1,5)
+        model.postfix <- substr(this.table.name,1,5)
 
[…]

### 2022-11-02 MainAnalysis.Rmd
Making sure to separate media

@@
   source.col = "document_id",
-  loq.default = NA,
+  loq.col ="calc_loq",
   subject.default = NA,
   info.default = NA,
-  suppress.messages=TRUE
+  suppress.messages = TRUE
 ))
@@
   info.default = NA,
-  suppress.messages=TRUE
+  suppress.messages = TRUE
 ))

### 2022-11-02 MainAnalysis.Rmd
Caught error where some species were being rerun even if only one ref because other species for same chemicals had multiple refs

@@
 system.time(PK.fit.table.1comp <- fit_all(
-  data.set = cvt.data,
+  data.set = subset(cvt.data,dsstox_substance_id=="DTXSID0020442"),
   model = "1compartment",

### 2022-11-03 MainAnalysis.Rmd
Added DTXSID and got merge_model_fits working

--- 2022-11-02 MainAnalysis.Rmd
@@
 devtools::load_all("invivopkfit")
+# Clear memory:
+rm(list=ls())
 ```
@@
 
+pk_output_2comp$Vdist <- pk_output_2comp$V1*(pk_output_2comp$k12+pk_output_2comp$k21)/pk_output_2comp$k21
+
 pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
@@
 all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
-                                       "2compartment="=pk_output_2comp,
+                                       "2compartment"=pk_output_2comp,
                                        "flat"=pk_output_flat),
@@
                                   species.col = "Species")
-
 ```
@@
 save(raw_flat, file = paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
-
+save(all.fit.table, file = paste("figures_rdata/all_fit_table_",THIS.DATE,".RData",sep=""))
 save(pk_lombardo, file = paste("figures_rdata/pk_lombardo",THIS.DATE,".RData",sep=""))
@@
 
-pk_all <- left_join(pk_data1, pk_lombardo, by = c("CAS" = "CAS #"))
+pk_all <- left_join(all.fit.table, pk_lombardo, by = c("CAS" = "CAS #"))
 
@@
 pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000
-
+pk_all$CLtot <- pk_all$Vdist*pk_all$kelim
 pk_all$Vdist_norm <- abs(pk_all$Vdist / pk_all$`human VDss (L/kg)`)

### 2022-11-03 invivopkfit/R/analyze_pk_data.R

@@ -641,7 +641,7 @@ analyze_pk_data <- function(fitdata,
     {
       out.dt[ ,LogLikelihood := 0] ### replace with NA to make error more apparent
       out.dt[ ,AIC := Inf]
-      cat("Problem with Fbetaofalpha or V1 equaling optimizer bound. Returning AIC=INF.\n")
+      if (!suppress.messages) cat("Problem with Fbetaofalpha or V1 equaling optimizer bound. Returning AIC=INF.\n")
     } else {
       out.dt[, LogLikelihood := -all.data.fit$value]
       out.dt[, AIC := 2 * length(opt.params) + 2 * all.data.fit$value]
@@ -649,6 +649,7 @@ analyze_pk_data <- function(fitdata,
   } else if (model == 'flat') {
     out.dt[, LogLikelihood := -all.data.fit$value]
     out.dt[, AIC := 2 * length(opt.params) + 2 * all.data.fit$value]
+    out.dt[, Vdist := V1*(k12+k21)/k2]
   }
 
   # } else {warning("didn't converge")}

### 2022-11-03 invivopkfit/R/fit_all.R

@@ -376,10 +376,9 @@ fit_all <- function(data.set,
     #browser()
     ### Rerun subsetting per reference just for chemical/species comvbinations
     ### that have multiple references:
-    multi.ref.cas <- data.set[, MultipleReferences :=
-                                length(unique(Reference)) > 1,
-                              by = c("DTXSID", "Species")]
-    multi.ref.cas <- unique(subset(multi.ref.cas,
+    data.set[, MultipleReferences := length(unique(Reference)) > 1,
+             by = c("DTXSID", "Species")]
+    multi.ref.cas <- unique(subset(data.set,
                                    MultipleReferences == TRUE)$DTXSID)
     if (length(multi.ref.cas) > 0) {
       data.set.multi.ref <- subset(data.set, MultipleReferences == TRUE)

### 2022-11-07 MainAnalysis.Rmd
Write out CSV also

@@
                                   species.col = "Species")
+write.csv(all.fit.table, paste("inst/ext/all.fit.table.",THIS.DATE,".csv",sep=""), row.names = FALSE)
 ```

### 2022-11-08 MainAnalysis.Rmd
Cleaned up columns, added sigfigs

--- 2022-11-03 MainAnalysis.Rmd
@@
                                        "2compartment"=pk_output_2comp,
-                                       "flat"=pk_output_flat),
-                                        dtxsid.col = "DTXSID",
-                                  species.col = "Species")
+                                       "flat"=pk_output_flat))
+write.csv(all.fit.table, paste("inst/ext/all.fit.table.",THIS.DATE,".csv",sep=""), row.names = FALSE)
 ```

### 2022-11-11 MainAnalysis.Rmd
No V1 for flat model

@@
 ```{r, set_file_timestamp, eval = TRUE}
-THIS.DATE <- "102422"
+THIS.DATE <- "111022"
 ```
@@
 ))
+write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
 ```
@@
 ))
+write.csv(PK.fit.table.2comp[[1]], paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.2comp[[2]], paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
 ```
@@
 ))
-```
-
-```{r, write_invivoPKfits_to_file, eval = FALSE}
-write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-
-write.csv(PK.fit.table.2comp[[1]], paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-write.csv(PK.fit.table.2comp[[2]], paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
 

### 2022-11-11 R/cp_2comp.R

@@ -1,69 +1,0 @@
-#' Analytical 2-compartment model
-#'
-#' @param params A named list of parameter values including the following:
-#' \describe{ \item{k12}{Rate at which compound moves from central to
-#' peripheral compartment} \item{k21}{Rate at which compound moves from
-#' peripheral to central compartment} \item{kelim}{Elimination rate}
-#' \item{V1}{Apparent volume of central compartment} } For oral administration
-#' (\code{iv.dose} FALSE), \code{params} must also include: \describe{
-#' \item{Fgutabs}{Oral bioavailability} \item{kgutabs}{Rate of absorption from
-#' gut} }
-#'
-#' !author Caroline Ring, John Wambaugh
-#' @param time A vector of time values, in hours
-#' @param dose A dose in mg/kg
-#' @param iv.dose TRUE for single IV bolus dose, FALSE for single oral dose
-#' @return A vector of plasma concentration values corresponding to each value
-#' in \code{time}
-#' @export cp_2comp
-cp_2comp <- function(params, time, dose, iv.dose)
-{
-
-  if (any(sapply(params,function(x) identical(x,numeric(0))))) return(NA)
-
-  if (is.null(params$Fgutabs) | is.na(params$Fgutabs))
-  {
-    params$Fgutabs <- 1
-  }
-  if (is.null(params$kgutabs) | is.na(params$kgutabs))
-  {
-    params$kgutabs <- 1
-  }
-  if (is.null(params$Fbetaofalpha)) params$Fbetaofalpha <- 1
-  if (is.null(params$Ralphatokelim)) params$Ralphatokelim <- 1
-
-  if (is.na(params$Fbetaofalpha)) params$Fbetaofalpha <- 1
-  if (is.na(params$Ralphatokelim)) params$Ralphatokelim <- 1
-
-  if (params$Fgutabs > 1) params$Fgutabs <- 1
-  if (params$Fbetaofalpha > 1) params$Fbetaofalpha <- 1
-  if (params$Ralphatokelim < 1) params$Ralphatokelim <- 1
-
-  alpha <- params$Ralphatokelim * (params$kelim + 10^-6)
-  beta <- params$Fbetaofalpha * alpha
-
-  # try to keep k21 and k12 positive:
[…]

### 2022-11-11 R/do_noncomp_fit.R

@@ -1,204 +1,0 @@
-#' Helper function to perform noncomp fits
-#'
-#' @param data.set A table of concentration-time data.
-#'
-#' @return A data.table with average concentration values
-#'
-#' @author John Wambaugh, Caroline Ring, Christopher Cook
-#' @importFrom magrittr "%>%"
-
-do_noncomp_fit <- function(data.set) {
-
-  ### for PK package to work, have to take average of replicate timepoints
-  data.list <- list()
-  for(this.compound in unique(data.set[, Compound])) {
-    this.compound.data <- data.set[Compound == this.compound]
-
-    ### list of columns by which to split data.set
-    col_list <- list(this.compound.data$Reference,
-                     this.compound.data$Dose,
-                     this.compound.data$Route,
-                     this.compound.data$Media)
-
-    ### split data.set into list of data.tables
-    split_list <- split(this.compound.data, col_list)
-
-    ### remove data.tables with 0 rows
-    # this.medium.list <- keep(this.medium.list, ~nrow(.) > 0)
-
-    ### take average of replicate timepoints for each data.table
-    split_list_avg <- lapply(split_list, noncomp_avg_value)
-    sub_data <- do.call(rbind, split_list_avg)
-
-    data.list[[this.compound]] <- sub_data
-  }
-
-  ### combine data.tables back into one large data.set
-  data.set <- do.call(rbind, data.list)
-
-  # Normalize all concentrations by dose to fit jointly:
-  data.set[, Value.Norm := Value/Dose]
-
-  ### not sure why PK.fit.table needs to be defined as NULL right here
-  PK.fit.table <- NULL
-
-  for (this.cas in sort(unique(data.set$CAS)))
-  {
-    this.subset <- subset(data.set, CAS == this.cas & !is.na(Value.Norm))
-    for (this.species in sort(unique(this.subset$Species)))
-    {
-      # Need oral and iv to estimate bioavailability:
-      if ("po" %in% unique(this.subset$Route) & "iv" %in% unique(this.subset$Route))
-      {
-        this.iv.time.list <- list()
-        this.iv.conc.list <- list()
-        this.iv.id.list <- list()
-        this.oral.time.list <- list()
-        this.oral.conc.list <- list()
-        this.oral.id.list <- list()
-        this.row <- data.frame(Compound = this.subset$Compound[1],
-                               CAS = this.cas,
-                               Reference = NA,
-                               Source = NA,
-                               Species = this.species,
[…]

### 2022-11-11 R/prep_tk_params_table.R

@@ -1,106 +1,0 @@
-# library(tidyverse)
-#
-# ### define data
-# tk_params <- read.csv("inst/ext/tk_parameters_202202241334.csv")
-# pk_data <- pk_output_1comp_04142022
-# raw_data <- raw_1comp_04142022
-# og_raw_data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
-#
-# ### get rid of predicted parameters
-# # will just get in the way
-# raw_data <- dplyr::select(raw_data, -c("kelim",
-#                                        "Vdist",
-#                                        "Fgutabs",
-#                                        "kgutabs"))
-#
-# ### make reference column same class between both data sets before joining
-# raw_data$Reference <- as.character(raw_data$Reference)
-#
-# ### get rid of the stupid row number col
-# raw_data$X <- NULL
-# pk_data$X <- NULL
-#
-# pk_raw <- left_join(pk_data, raw_data)
-#
-# pk_raw <- pk_raw %>%
-#   filter(param.value.type == "Fitted geometric mean")
-#
-# ### right now I'm taking out
-# # joint analysis, until I
-# # figure out how to better
-# # handle it
-# pk_raw <- pk_raw %>%
-#   filter(Data.Analyzed != "Joint Analysis")
-#
-# og_raw_data$fk_reference_document_id <- as.character(og_raw_data$fk_reference_document_id)
-#
-# pk_raw_og <- left_join(pk_raw,
-#                        og_raw_data,
-#                        by = c("CAS" = "dsstox_casrn",
-#                               "Reference" = "fk_reference_document_id",
-#                               "Media" = "conc_medium_normalized",
-#                               "Species" = "species"))
-# pk_raw_og <- pk_raw_og %>%
-#   distinct(series_id, .keep_all = TRUE)
-#
-# pk_raw_og <- pk_raw_og %>% dplyr::select(series_id,
-#                                          CAS,
-#                                          Species,
-#                                          kelim,
-#                                          Vdist,
-#                                          Fgutabs,
-#                                          sigma_value,
-#                                          Reference,
-#                                          Data.Analyzed,
-#                                          Compound,
-#                                          LogLikelihood,
-#                                          AIC,
-#                                          model,
-#                                          CLtot,
-#                                          Css,
-#                                          halflife,
-#                                          tpeak.oral,
-#                                          Cpeak.oral.1mgkg)
-#
[…]

### 2022-11-15 MainAnalysis.Rmd
Making analyze_pk_data() and fit_all() more modular by splitting out functions to get starting values, get upper bounds, and get lower bounds

@@
 title: "<i>invivoPKfit</i> and <i>CvTdb</i> figures"
-author: "Christopher Cook"
-date: "1/31/2022"
+author: "Christopher Cook, John Wambaugh, Caroline Ring"
+date: "11/15/2022"
 output:
@@
 
+Read in CvTdb data.
+
 ```{r, load_cvt, eval = TRUE}
-
-### this block runs the model fits
-# and does some pre-processing to clean up the data
-
-#################
-#################
-
-# data <- read.csv("inst/ext/cvt_query_for_john_27may2021_v2.csv")
-# data <- read.csv("inst/ext/cvtdb_invivopkfit_02242022.csv")
-# data <- read.csv("inst/ext/cvtdb_invivopkfit_04142022.csv")
 cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")
-
-### these compounds had no CAS in the cvtdb
-# double check and they should not have been added
-# so I removed them
-
+```
+
+A couple of compounds had no CAS in CvTdb. Upon double checking, they should not have been added. So remove them. (CLR 2022-11-15: it doesn't look like there are any of these)
+
+```{r, cvt_remove_nocas}
 cvt.data <- cvt.data %>%
@@
   filter(analyte_name_original != "N-desmethyltamoxifen")
-
-#################
-#################
-
-### fix compound names
+```
+
+Fix a few compound names.
+```{r, cvt_fix_cpd_names}
 cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
@@
 cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
-
-### make fk_reference_document equal fk_extraction document if fk_reference_document is NULL
+```
+
+if fk_reference_document is NULL, make fk_reference_document equal fk_extraction document. (CLR 2022-11-15: it doesn't look like there are any of these)
+
+```{r}
 cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
   cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]
-
+```
+
+```{r}
 ### this is basically my debug line,
@@
 
+Set a timestamp: today's date. (I am changing this to YYYYMMDD format -- better sorting by filename. -- CLR)
+
 ```{r, set_file_timestamp, eval = TRUE}
-THIS.DATE <- "111022"
-```
+THIS.DATE <- "20221115"
+```
+
+Run a one-compartment fit on the data, and write out the results.
 
@@
 ))
+
 write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+
 write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)

### 2022-11-15 invivopkfit/R/get_starts.R

@@ -1,0 +1,147 @@
+get_starts <- function(fitdata,
+                       this.dtxsid,
+                       modelfun,
+                       model,
+                       this.reference = NULL,
+                       suppress.messages = FALSE,
+                       sig.figs = 5){
+  #Initialize starting guesses: to be refined
+  if(model %in% "flat"){
+    opt.params <- c("A" = mean(fitdata$Value, na.rm = TRUE))
+  }else{
+    #for non-flat models....
+    if (model %in% "1compartment") {
+      opt.params <- c("kelim" = 0.25,
+                      "Vdist" = 5.56)
+    }else if(model %in% "2compartment"){
+      opt.params <- c("kelim" = 0.25,
+                      "V1" = 1,
+                      "Ralphatokelim" = 1.2,
+                      "Fbetaofalpha" = 0.25)
+    }
+
+    if('po' %in% fitdata$Route){
+      #if we have oral data
+      #then add Fgutabs and kgutabs to the list
+      opt.params <- c(opt.params,
+                      c("Fgutabs" = 0.5,
+                        "kgutabs" = 2.19)
+      )
+    }
+
+    #if httk PK params exist, replace the defaults with these
+    if(this.dtxsid %in% httk::get_cheminfo(info="dtxsid")){
+      httk_params <- httk::parameterize_1comp(dtxsid = DTXSID,
+                                              default.to.human = TRUE,
+                                              suppress.messages = TRUE,
+                                              species = ifelse(tolower(Species) %in% colnames(httk::physiology.data),
+                                                               Species,
+                                                               "Human"))[c("kelim",
+                                                                           "Vdist",
+                                                                           "Fgutabs",
+                                                                           "kgutabs")]
+
+      if (model %in% "2compartment") {
+        httk_params["V1"] <- httk_params["Vdist"]
+      }
+      replace_names <- intersect(names(opt.params),
+                                 names(httk_params))
+      opt.params[replace_names] <- httk_params[replace_names]
+    }
+
+    #Go parameter by parameter
+
+    #Fgutabs
+      if('po' %in% fitdata$Route &
[…]

### 2022-11-15 invivopkfit/R/get_upper_bounds.R

@@ -1,0 +1,30 @@
+get_upper_bounds <- function(fitdata,
+                             this.dtxsid,
+                             modelfun,
+                             model,
+                             this.reference = NULL,
+                             suppress.messages = FALSE,
+                             sig.figs = 5,
+                             UPPERBOUNDARY = 1e4){
+  #specify upper bounds of params to optimize (on a log scale!!)
+  upper[] <- log(UPPERBOUNDARY)
+  TRYSIGMA <- stats::median(fitdata$Value, na.rm = TRUE)
+  upper[regexpr("sigma",names(upper)) != -1] <- log(TRYSIGMA) ### was MAXSIGMA
+  if (model == "1compartment") {
+    upper["Vdist"] <- log(max(fitdata$Dose) / min(fitdata$LOQ))
+  } else if (model == '2compartment') {
+    upper["V1"] <- log(max(fitdata$Dose) / min(fitdata$LOQ))
+    upper["Ralphatokelim"] <- log(1000)
+    upper["Fbetaofalpha"] <- log(0.75) #on a log scale!
+  }
+  if ("Fgutabs" %in% unlist(opt.params)) {
+    upper["Fgutabs"] <- log(1) #on a log scale!
+  }
+  if ("kgutabs" %in% unlist(opt.params)) {
+    upper["kgutabs"] <- log(1000)
+  }
+  # upper <- upper["Vdist"]
+  # Force initial values to be within bounds:
+  opt.params[opt.params>upper] <- upper[opt.params>upper] - 0.1
+
+}

### 2022-11-18 invivopkfit/R/analyze_subset.R
Modularized fitting code by splitting different tasks into different functions. Note: Post-processing does not work yet because format of fitting output is different now (one row for each study & parameter and one column for each estimate metric -- vs. previous format of one row for each study & metric and one column for each parameter).

@@ -17,101 +17,6 @@
 #' data point. Each reference is assumed to have its own residual error standard
 #' deviation.} }
 #'
-#' # Specifications for `fun_start`
-#'
-#' ## Arguments
-#'
-#' `fun_start` must accept the same named arguments as \code{get_starts},
-#' i.e. the parameters \code{fitdata}, \code{model}. It may
-#' accept additional arguments, to be specified in a named list in
-#' \code{fun_start_args}.
-#'
-#' ## Return value
-#'
-#' `fun_start` must return a \code{data.frame} of model parameters with the
-#' following variables: \describe{ \item{\code{param.name}}{Character: the names
-#' of the PK model parameters. Must include all of the parameter names expected
-#' by the model function defined by \code{model}, as well as
-#' all of the reference-specific error standard deviations, named as
-#' \code{paste("sigma", unique(fitdata$Reference), sep = ".)}}.
-#' \item{\code{param.value}}{Numeric: A starting value for each of the PK model
-#' parameters.} \item{\code{param.value.source}{Character: A message describing
-#' briefly how the starting value was calculated for each parameter. This may be
-#' blank or NA if you do not wish to supply any message, but the variable must
-#' be present.}} }
-#'
-#' ## Example
-#'
-#' If you want to accept the default starting values for most parameters, but
-#' you want to change the starting values for the reference-specific error SDs
-#' so that they are all fixed at some constant value (e.g., 1), you could define
-#' your own function as follows:
-#'
-#' ```{r, eval = FALSE}
-#' my_starts <- function(fitdata,
-#'                        model,
-#'                        sigma_start_const = 1){
-#'    #Get default starting values for all params
-#'    starts_df <- get_starts(fitdata, model)
-#'    #Overwrite defaults for reference-specific error SDs
-#'    starts_df[grepl(x = starts_df$param.name,
-#'                    pattern = "sigma"),
-#'                    c("param.value",
-#'                    "param.value.source")] <- list(sigma_start_const,
-#'                    "Set to constant")
-#'    return(starts_df)
-#' }
-#' ```
-#'
-#' Then when calling `analyze_subset`, you would specify `fun_start = my_starts`
-#' and `fun_start_args = list(sigma_start_const=1)`.
-#'
-#' # Specifications for `fun_lower`
-#'
-#' ## Arguments
-#'
-#' `fun_lower` must accept the same named arguments as
-#' \code{get_lower_bounds}, i.e. the parameters `par_DF`, `fitdata`, `model`. It
[…]

### 2022-11-18 invivopkfit/R/log_likelihood.R

@@ -3,8 +3,8 @@
 #' The log-likelihood function used for fitting
 #'
 #'
-#' @param params A named list of parameter values
-#' @param DT Concentration-time data for a given chemical
+#' @param params A named list of log-scaled parameter values
+#' @param DF A `data.frame` of Concentration-time data for a given chemical
 #' @param modelfun "analytic" to use the analytic model solution, "full" to use
 #' the full ODE model
 #' @param model The model to fit, either "1compartment" or "2compartment"
@@ -13,19 +13,15 @@
 #' @return A log-likelihood value for the data given the parameter values in
 #' params
 log_likelihood <- function(params,
-                           DT,
+                           DF,
                            modelfun,
                            model) {
-  # Bound the rates:
-  #  MAX.RATE <- 1000
 
-  #Take a copy of the input data table so it behaves as though passed by value
-  DT <- copy(DT)
   #Back-transform the log-transformed parameters (see analyze_pk_data) into
   #their original form
   params <- lapply(params, exp)
 
-  if (any(unlist(lapply(params, is.na)))) return(-Inf)
+  if(any(is.na(params))) return(-Inf)
 
   model <- model
 
@@ -34,26 +30,10 @@ log_likelihood <- function(params,
     if (params[["Fgutabs"]] > 1) return(-Inf)
   }
 
-  # #If a two-compartment model, then                alpha and beta must be real:
-  # if ("k12" %in% names(params))
-  # {
-  #   alphabeta.sum <- params[["kelim"]] + params[["k12"]] + params[["k21"]]
-  #   alphabeta.prod <- params[["kelim"]] * params[["k21"]]
-  #
-  #   alpha <- (alphabeta.sum + sqrt(alphabeta.sum^2 - 4*alphabeta.prod))/2
-  #   beta <- (alphabeta.sum - sqrt(alphabeta.sum^2 - 4*alphabeta.prod))/2
-  #   if (is.na(alpha) | is.na(beta)) return(-Inf)
-  # }
-
-  #Extract parameters whose names do not match 'sigma2'
+  #Extract parameters whose names do not match 'sigma'
   #(that is, all the actual model parameters)
-  model.params <- params[names(params)[regexpr(pattern = "sigma2",
-                                               text=names(params)) == -1]]
-
[…]

### 2022-11-22 MainAnalysis.Rmd
Modularized fitting code by splitting different tasks into different functions. Note: Post-processing does not work yet because format of fitting output is different now (one row for each study & parameter and one column for each estimate metric -- vs. previous format of one row for each study & metric and one column for each parameter).
Working for 1-compartment model fits (though could still fine-tune starting values, need to diagnose NaN sds, etc.)

@@
 Calculate a limit of quantification (90% of lowest observation)
+
 ```{r, calc_loq, eval = TRUE}
@@
 ```{r, set_file_timestamp, eval = TRUE}
-THIS.DATE <- "20221115"
+THIS.DATE <- "2022_11_21"
 ```
@@
 ```{r, run_invivoPKfit_1comp, eval = FALSE}
+
+devtools::load_all("invivopkfit")
+
 ### do 1-Compartment fit
@@
   info.default = NA,
-  suppress.messages = TRUE
+  suppress.messages = FALSE
 ))
 
-write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-
-write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.1comp, paste("inst/ext/PK_fit_table_1comp_",THIS.DATE,".csv",sep=""), row.names = FALSE)
+
 ```
@@
 ))
-write.csv(PK.fit.table.2comp[[1]], paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-write.csv(PK.fit.table.2comp[[2]], paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+
 ```

### 2022-11-22 invivopkfit/R/get_starts.R

@@ -79,8 +79,8 @@ get_starts <- function(par_DF = NULL,
                                          1, #V1
                                          0.2, #k12
                                          0.5, #k21
-                                         1/2.19, #Fgutabs_Vdist
-                                         1/2.19, #Fgutabs_V1
+                                         0.5/2.19, #Fgutabs_Vdist
+                                         0.51/2.19, #Fgutabs_V1
                                          100), #sigma
                          start_value_msg = "Default"
                        ),
@@ -197,8 +197,8 @@ if(is.null(par_DF)){
           mean(iv.data$Dose) / mean(oral.data$Dose)
         #if the estimated value is valid, then use it and record the source
         if (is.finite(Fgutabs_tmp) &
-            Fgutabs_tmp > 0 &
-            Fgutabs_tmp < 1){
+            Fgutabs_tmp > par_DF["Fgutabs", "lower_bound"] &
+            Fgutabs_tmp < par_DF["Fgutabs", "upper_bound"]){
           par_DF["Fgutabs",
                      "start_value"] <- Fgutabs_tmp
           par_DF["Fgutabs",
@@ -219,22 +219,29 @@ if(is.null(par_DF)){
       } #end if('po' %in% fitdata$Route & 'iv' %in% fitdata$Route) / else
       } #end if(par_DF["Fgutabs", "optimize_parambo"] %in% TRUE)
 
-      #make elim data
-      elim_data <- make_elim_data(fitdata = fitdata)
 
       #kelim
       if(par_DF["kelim", "optimize_param"] %in% TRUE){
-    #kelim can be fit from IV data if available
+        #make elim data
+        elim_data <- make_elim_data(fitdata = fitdata)
+
+        #take only the later times
+        time_split <- median(elim_data$Time)
+        elim_late <- subset(elim_data,
+                            Time >= time_split)
 
     #linear regression of log conc/dose vs. time
     elim_lm <- stats::lm(log(ValueDose) ~ Time,
                          data=elim_data)
+
     elim_coeff <- coef(elim_lm)
+
     #take negative slope
     kelim_tmp <- -elim_coeff[2]
+
     #if kelim_tmp is not NA, then use it.
     if(is.finite(kelim_tmp)){
-      if(kelim_tmp > 0.0001){
+      if(kelim_tmp > par_DF["kelim", "lower_bound"]){
       par_DF[par_DF$param_name %in% "kelim",
                  "start_value"] <- kelim_tmp
[…]

### 2022-11-28 MainAnalysis.Rmd
Updated time stamping in MainAnalysis.Rmd

@@
 
-Set a timestamp: today's date. (I am changing this to YYYYMMDD format -- better sorting by filename. -- CLR)
-
-```{r, set_file_timestamp, eval = TRUE}
-THIS.DATE <- "2022_11_21"
-```
-
-Run a one-compartment fit on the data, and write out the results.
+Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm_ss.
+
+Fit the 1-compartment model.
 
@@
 
-write.csv(PK.fit.table.1comp, paste("inst/ext/PK_fit_table_1comp_",THIS.DATE,".csv",sep=""), row.names = FALSE)
-
-```
+write.csv(PK.fit.table.1comp,
+          paste("inst/ext/PK_fit_table_1comp_",
+                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                                    ".csv",
+                                    sep=""),
+          row.names = FALSE)
+
+```
+
+Fit the 2-compartment model.
 
 ```{r, run_invivoPKfit_2comp, eval = FALSE}
+devtools::load_all("invivopkfit")
+
 ### do 2-Compartment fit
@@
   info.default = NA,
-  suppress.messages = TRUE
+  suppress.messages = FALSE
 ))
-write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
+                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                                    ".csv",
+                                    sep=""), row.names = FALSE)
 

### 2022-11-30 MainAnalysis.Rmd
Capturing output of fit_all() runs and sending to a txt file

@@
 ### do 1-Compartment fit
-system.time(PK.fit.table.1comp <- fit_all(
+system.time(
+  capture.output(
+    PK.fit.table.1comp <- fit_all(
       data.set = cvt.data,
@@
       suppress.messages = FALSE
-))
+    ),
+    file = paste0("inst/ext/PK_fit_table_1comp_output_",
+                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                  ".txt")
+  )
+)
 
@@
 ### do 2-Compartment fit
-system.time(PK.fit.table.2comp <- fit_all(
+system.time(
+  capture.output(
+    PK.fit.table.2comp <- fit_all(
       data.set = cvt.data,
@@
       suppress.messages = FALSE
-))
+    ),
+    file = paste0("inst/ext/PK_fit_table_2comp_output_",
+                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                  ".txt")
+  )
+)
+
 write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",

### 2022-11-30 MainAnalysis.Rmd
Added output of log-likelihood gradient at starting values. Tweaked get_starts.R again

@@
                 format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
-                  ".txt")
+                ".txt"),
+  type = "message"
   )
@@
                   format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
-                  ".txt")
+                  ".txt"),
+    type = "message"
   )

### 2022-12-01 MainAnalysis.Rmd
Properly vectorized cp_1comp and cp_2comp. No more need for fitfun() and analytic_model_fun() as intermediaries -- log_likelihood() now directly calls the analytic model function or httk::solve_1comp(). Also, in analyze_subset(), when repeating optimization with smaller convergence tolerance, starts from previous set of best-fit params.

--- 2022-11-28 MainAnalysis.Rmd
@@
 
+run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+
 ### do 1-Compartment fit
-system.time(PK.fit.table.1comp <- fit_all(
+system.time(
+  capture.output(
+    PK.fit.table.1comp <- fit_all(
       data.set = cvt.data,
@@
       suppress.messages = FALSE
-))
+  ),
+  file = paste0("inst/ext/PK_fit_table_1comp_output_",
+                run_timestamp,
+                ".txt"),
+  type = "message"
+  )
+)
 
@@
           paste("inst/ext/PK_fit_table_1comp_",
-                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                                    run_timestamp,
                                     ".csv",
@@
 
+run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+
 ### do 2-Compartment fit
-system.time(PK.fit.table.2comp <- fit_all(
+system.time(
+  capture.output(
+    PK.fit.table.2comp <- fit_all(
       data.set = cvt.data,
@@
       suppress.messages = FALSE
-))
+    ),
+    file = paste0("inst/ext/PK_fit_table_2comp_output_",
+                  run_timestamp,
+                  ".txt"),
+    type = "message"
+  )
+)
+
 write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
-                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                                    run_timestamp,
                                     ".csv",
@@
 ```{r, run_invivoPKfit_flat, eval = FALSE}
-### do flat fit
-system.time(PK.fit.table.flat <- fit_all(
+devtools::load_all("invivopkfit")
+
+run_timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+
+system.time(
+  capture.output(
+    PK.fit.table.flat <- fit_all(
       data.set = cvt.data,
@@
       info.default = NA,
-  suppress.messages = TRUE
-))
-
-write.csv(PK.fit.table.flat[[1]], paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-write.csv(PK.fit.table.flat[[2]], paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
+      suppress.messages = FALSE
+    ),
+    file = paste0("inst/ext/PK_fit_table_flat_output_",
+                  run_timestamp,
+                  ".txt"),
+    type = "message"
+  )
+)
+
+write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
+                                    run_timestamp,
+                                    ".csv",
+                                    sep=""), row.names = FALSE)
 ```

### 2022-12-01 invivopkfit/R/fitfun.R
Properly vectorized cp_1comp and cp_2comp. No more need for fitfun() and analytic_model_fun() as intermediaries -- log_likelihood() now directly calls the analytic model function or httk::solve_1comp(). Also, in analyze_subset(), when repeating optimization with smaller convergence tolerance, starts from previous set of best-fit params.

@@ -37,9 +37,9 @@ fitfun <- function(design.times,
                                    iv.dose=design.iv,
                                    model=model),
                      error = function(err){
-                       cat("fitfun: Error in analytic_model_fun\n")
-                       cat(paste0(err$message, "\n"))
-                       cat(paste(paste(apply(data.frame(Names=names(model.params),
+                       message("fitfun: Error in analytic_model_fun\n")
+                       message(paste0(err$message, "\n"))
+                       message(paste(paste(apply(data.frame(Names=names(model.params),
                                                         Values=model.params,
                                                         stringsAsFactors=FALSE),
                                              1,
@@ -47,6 +47,7 @@ fitfun <- function(design.times,
                                        collapse=", "),
                                  "\n",
                                  sep=""))
+                       browser()
                        out_tmp <- cbind("time" = these.times,
                                         "Ccompartment" = rep(NA_real_, length(these.times)),
                                         "AUC" = rep(NA_real_, length(these.times)))
@@ -67,9 +68,9 @@ fitfun <- function(design.times,
                            iv.dose=design.iv,
                            suppress.messages=TRUE),
                     error = function(err){
-                      cat("fitfun: Error in httk::solve_1comp()\n")
-                      cat(paste0(err$message, "\n"))
-                      cat(paste(paste(apply(data.frame(Names=names(model.params),
+                      message("fitfun: Error in httk::solve_1comp()\n")
+                      message(paste0(err$message, "\n"))
+                      message(paste(paste(apply(data.frame(Names=names(model.params),
                                                        Values=model.params,
                                                        stringsAsFactors=FALSE),
                                             1,function(x) paste(x,collapse=": ")),collapse=", "),"\n",sep=""))
@@ -94,9 +95,9 @@ fitfun <- function(design.times,
                                         suppress.messages=TRUE,
                                         atol = atol),
                       error = function(err){
-                        cat("fitfun: Error in httk::solve_1comp()\n")
-                        cat(paste0(err$message, "\n"))
-                        cat(paste(paste(apply(data.frame(Names=names(model.params),
+                        message("fitfun: Error in httk::solve_1comp()\n")
+                        message(paste0(err$message, "\n"))
+                        message(paste(paste(apply(data.frame(Names=names(model.params),
                                                          Values=model.params,
                                                          stringsAsFactors=FALSE),
                                               1,function(x) paste(x,collapse=": ")),collapse=", "),"\n",sep=""))

### 2022-12-08 MainAnalysis.Rmd
Adding new plotting function

--- 2022-11-30 MainAnalysis.Rmd
@@
 
-```{r, run_invivoPKfit_1comp, eval = FALSE}
-
-devtools::load_all("invivopkfit")
+```{r, run_invivoPKfit_1comp}
+
+run_timestamp_1comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
 
@@
 system.time(
-  capture.output(
     PK.fit.table.1comp <- fit_all(
@@
       info.default = NA,
-      suppress.messages = FALSE
-    ),
-    file = paste0("inst/ext/PK_fit_table_1comp_output_",
-                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
-                  ".txt")
+      suppress.messages = TRUE
   )
@@
           paste("inst/ext/PK_fit_table_1comp_",
-                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                                    run_timestamp_1comp,
                                     ".csv",
@@
 
-```{r, run_invivoPKfit_2comp, eval = FALSE}
-devtools::load_all("invivopkfit")
+```{r, run_invivoPKfit_2comp}
+
+run_timestamp_2comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
 
@@
 system.time(
-  capture.output(
     PK.fit.table.2comp <- fit_all(
@@
       info.default = NA,
-      suppress.messages = FALSE
-    ),
-    file = paste0("inst/ext/PK_fit_table_2comp_output_",
-                  format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
-                  ".txt")
+      suppress.messages = TRUE
     )
@@
 write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
-                                    format(Sys.time(), "%Y_%m_%d_%H_%M_%S"),
+                                    run_timestamp_2comp,
                                     ".csv",
@@
 
-```{r, run_invivoPKfit_flat, eval = FALSE}
-### do flat fit
-system.time(PK.fit.table.flat <- fit_all(
+```{r, run_invivoPKfit_flat}
+run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+
+system.time(
+    PK.fit.table.flat <- fit_all(
       data.set = cvt.data,
@@
       suppress.messages = TRUE
-))
-
-write.csv(PK.fit.table.flat[[1]], paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-write.csv(PK.fit.table.flat[[2]], paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-```
-
-```{r, read_data}
-
+    )
+)
+
+write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
+                                    run_timestamp_flat,
+                                    ".csv",
+                                    sep=""), row.names = FALSE)
+```
+
+For ease of plotting, get the pre-processed, harmonized data:
+
+```{r}
+DF <- preprocess_data(data.set = cvt.data,
+                       ratio.data.to.dose = 1,
+      compound.col = "analyte_name_original",
+      dtxsid.col = "dsstox_substance_id",
+      cas.col = "dsstox_casrn",
+      reference.col = "fk_reference_document_id",
+      species.col = "species",
+      species.weight.col = "weight_kg",
+      species.weight.units.default = "kg",
+      dose.col = "dose_level_normalized",
+      time.col = "time_hr",
+      time.units.default = "hr",
+      media.col = "conc_medium_normalized",
+      media.units.default = "normalized",
+      value.col = "conc",
+      units.default = NA,
+      route.col = "administration_route_normalized",
+      source.col = "document_id",
+      loq.col ="calc_loq",
+      subject.default = NA,
+      info.default = NA,)
+```
+
+```{r, read_data, eval = FALSE}
 ### this block reads the exported model fit csv files from run_invivoPKfit
 
-pk_output_2comp <- read.csv(paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""))
-pk_output_flat <- read.csv(paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""))
-pk_output_1comp <- read.csv(paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""))
-
-raw_1comp <- read.csv(paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""))
-raw_2comp <- read.csv(paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""))
-raw_flat <- read.csv(paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""))
-
-pk_output_2comp$Vdist <- pk_output_2comp$V1*(pk_output_2comp$k12+pk_output_2comp$k21)/pk_output_2comp$k21
+pk_output_2comp <- read.csv(paste("inst/ext/PK_fit_table_2comp_",run_timestamp_1comp,".csv",sep=""))
+pk_output_flat <- read.csv(paste("inst/ext/PK_fit_table_flat.",run_timestamp_2comp,".csv",sep=""))
+pk_output_1comp <- read.csv(paste("inst/ext/PK_fit_table_1comp_",run_timestamp_flat,".csv",sep=""))
 
 pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
+```
+
+Rowbind together all of the fitted parameter tables into one big one.
+```{r}
+pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
+                         "2comp" = PK.fit.table.2comp,
+                         "flat" = PK.fit.table.flat),
+                    idcol = "Model",
+                    use.names = TRUE,
+                    fill = TRUE)
+```
+
+Get a table of the winning model for each dataset (minimum AIC).
+
+```{r}
+setorder(pk_fit,
+         Analysis_Type,
+         DTXSID,
+         Species,
+         AIC,
+         na.last = TRUE)
+
+pk_fit_win <- unique(pk_fit[, .(Analysis_Type, DTXSID, Species, model, AIC)] )
+```
+
+Plot concentration vs time with the best-fit params by data subset (DTXSID and species).
+
+Indicate the following:
+
+- One line for each model
+- Which is the winning model
+- Dose group
+- Blood vs. plasma
+- Below LOQ vs. above LOQ (plot below-LOQ points at LOQ)
+- IV vs. oral administration
+
+Would also like to plot uncertainty in predictions based on uncertainty in parameter estimates.
+
+Plot versions:
+- Winning model only
+- One model at a time
+- All three models on same plot
+
+```{r}
+
+plot_table <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, Reference)])
+plot_table <- plot_table[Analysis_Type %in% "Joint"]
+
+tmp <- mapply(plot_fit,
+              DTXSID_in = plot_table$DTXSID,
+                     Species_in = plot_table$Species,
+                     Analysis_Type_in = plot_table$Analysis_Type,
+                     Reference_in = plot_table$Reference,
+              MoreArgs = list(
+                     model_in = c("1compartment", "2compartment", "flat"),
+                     fitdata = DF,
+                     pk_fit = pk_fit)
+                     )
     ```

### 2022-12-08 invivopkfit/R/plot_fit.R

@@ -1,0 +1,158 @@
+plot_fit <- function(DTXSID_in,
+                     Species_in,
+                     Analysis_Type_in,
+                     Reference_in,
+                     model_in = c("1compartment", "2compartment", "flat"),
+                     fitdata,
+                     pk_fit){
+  #if more than one refrence in comma separated list, get a vector of references
+  reflist <- strsplit(Reference_in,
+                      split =  ", ")[[1]]
+
+  #subset the data appropriately
+  fitsub <- subset(fitdata, DTXSID %in% DTXSID_in &
+                     Species %in% Species_in &
+                     Reference %in% reflist)
+
+  #subset the fitted parameter data appropriately
+  pksub <- subset(pk_fit, DTXSID %in% DTXSID_in &
+                    Species %in% Species_in &
+                    Reference %in% Reference_in &
+                    Analysis_Type %in% Analysis_Type_in &
+                    model %in% model_in)
+
+  #Get concentration or LOQ
+  fitsub[, Conc:=pmax(Value, LOQ, na.rm = TRUE)]
+  #Get detection flag
+  fitsub[, Detect:=!is.na(Value)]
+
+  #calculate concentration normalized to dose
+  #this allows easier visualization
+  fitsub[, ConcDose:=Conc/Dose]
+
+  fitsub[, Dose_cat:=factor(Dose)]
+
+  #Get a list of lists of model params, one for each model_in
+  params <- sapply(model_in,
+                   function(mod) {
+                     parval <- pksub[model %in% mod,
+                                     `Fitted mean`]
+                     names(parval) <- pksub[model %in% mod,
+                                            param_name]
+                     return(as.list(parval))
+                   },
+                   USE.NAMES = TRUE,
+                   simplify = FALSE)
+
+  #color will represent dose
+  #filled symbols will represent detects (>LOQ)
+  #emtpy symbols will represent nondetects (<LOQ)
+  #circles represent po, triangles represent IV
+
+  #So we need to map shape to ND
+  shapevect <- c(
+                 "FALSE" = 1, #open circle
+                 "TRUE" = 19 #filled circle
+  )
+
+
+  #plot the conc-time-dose data
+  p <- ggplot(data = fitsub,
+              aes(x = Time,
+                  y = ConcDose,
+                  color = Route,
+                  shape = Detect
+              )) +
+    geom_point()
+
+  #get a table of unique combinations of model & route
+  modelroute <- expand.grid(model = model_in,
[…]

### 2022-12-09 MainAnalysis.Rmd
Revised plotting function.

@@
 
-```{r, run_invivoPKfit_1comp}
+```{r, run_invivoPKfit_1comp, eval = FALSE}
 
@@
 
-```{r, run_invivoPKfit_2comp}
+```{r, run_invivoPKfit_2comp, eval = FALSE}
 
@@
 
-```{r, run_invivoPKfit_flat}
+Fit the flat model.
+
+```{r, run_invivoPKfit_flat, eval = FALSE}
 run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
@@
       subject.default = NA,
-      info.default = NA,)
-```
-
-```{r, read_data, eval = FALSE}
+      info.default = NA,
+      suppress.messages = FALSE)
+```
+
+```{r, read_data}
 ### this block reads the exported model fit csv files from run_invivoPKfit
 
-pk_output_2comp <- read.csv(paste("inst/ext/PK_fit_table_2comp_",run_timestamp_1comp,".csv",sep=""))
-pk_output_flat <- read.csv(paste("inst/ext/PK_fit_table_flat.",run_timestamp_2comp,".csv",sep=""))
-pk_output_1comp <- read.csv(paste("inst/ext/PK_fit_table_1comp_",run_timestamp_flat,".csv",sep=""))
-
-pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
+PK.fit.table.1comp <- fread(paste0("inst/ext/", "PK_fit_table_1comp_2022_12_08_09_44_34.csv",sep=""))
+PK.fit.table.2comp <- fread(paste0("inst/ext/", "PK_fit_table_2comp_2022_12_08_10_31_09.csv",sep=""))
+PK.fit.table.flat <- fread(paste0("inst/ext/", "PK_fit_table_flat_2022_12_08_12_03_24.csv",sep=""))
+
+#pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
 ```
@@
                          "flat" = PK.fit.table.flat),
-                    idcol = "Model",
                     use.names = TRUE,
@@
 ```{r}
-setorder(pk_fit,
-         Analysis_Type,
-         DTXSID,
-         Species,
-         AIC,
-         na.last = TRUE)
-
-pk_fit_win <- unique(pk_fit[, .(Analysis_Type, DTXSID, Species, model, AIC)] )
+tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, model, AIC)])
+setorder(tmp, DTXSID, Species, Analysis_Type, AIC, na.last = TRUE)
+model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type)]
+pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type")]
+pk_fit[, winning:=(model == winmodel)]
+
 ```
@@
 
+Get unique combinations of DTXSID and species -- each of these will be one plot.
+
 ```{r}
-
-plot_table <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, Reference)])
-plot_table <- plot_table[Analysis_Type %in% "Joint"]
-
+plot_table <- unique(pk_fit[, .(DTXSID, Species)])
+```
+
+Plot all models for the joint analysis.
+```{r}
+
+#plot all models
 tmp <- mapply(plot_fit,
@@
                      Species_in = plot_table$Species,
-                     Analysis_Type_in = plot_table$Analysis_Type,
-                     Reference_in = plot_table$Reference,
               MoreArgs = list(
-                     model_in = c("1compartment", "2compartment", "flat"),
+                     model_in = "all",
+                     Analysis_Type_in = "Joint",
+                     DF = DF,
+                     pk_fit = pk_fit,
+                     n = 101,
+                     log10_scale_time = FALSE,
+                     file_path = "inst/ext/plots/Joint Analysis/model_all/")
+                     )
+
+```
+
+Plot only the winning model
+
+```{r}
+#plot all models
+tmp <- mapply(plot_fit,
+              DTXSID_in = plot_table$DTXSID,
+                     Species_in = plot_table$Species,
+              MoreArgs = list(
+                Analysis_Type_in = c("Joint", "Separate"),
+                     model_in = "winning",
                      fitdata = DF,
-                     pk_fit = pk_fit)
+                     pk_fit = pk_fit,
+                     file_path = "inst/ext/plots/analysis_all_model_winning/",
+                log10_scale_time = TRUE)
                      )

### 2022-12-14 Working Rmds/MainAnalysis.Rmd
Add folder for working Rmds. Add Rmd to pull CvT data from database. Add updated MainAnalysis.Rmd file to use newly pulled CvT data.

--- 2022-12-09 MainAnalysis.Rmd
@@
 library(readxl)
-devtools::load_all("invivopkfit")
-# Clear memory:
-rm(list=ls())
+devtools::load_all("../invivopkfit")
 ```
@@
 ```{r, load_cvt, eval = TRUE}
-cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")
-```
-
-A couple of compounds had no CAS in CvTdb. Upon double checking, they should not have been added. So remove them. (CLR 2022-11-15: it doesn't look like there are any of these)
-
-```{r, cvt_remove_nocas}
-cvt.data <- cvt.data %>%
-  filter(analyte_name_original != "Methemoglobin") %>%
-  filter(analyte_name_original != "N-desmethyltamoxifen")
-```
-
-Fix a few compound names.
-```{r, cvt_fix_cpd_names}
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
-```
-
-if fk_reference_document is NULL, make fk_reference_document equal fk_extraction document. (CLR 2022-11-15: it doesn't look like there are any of these)
+cvt_data <- fread("../inst/ext/cvt_data_2022_12_13_17_09_45.csv")
+```
+
+Add LOQ when available.
+
+PMIDs of documents
 
 ```{r}
-cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
-  cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]
-```
+unique(cvt_data[is.na(conc_time_values.conc),
+                .(documents_extraction.pmid,
+                  documents_extraction.doi,
+                  documents_extraction.other_study_identifier,
+                  documents_extraction.url)])
+```
+
+For PMID = 1233222, the original document has the LOQ as 0.08 ug/mL.
 
 ```{r}
-### this is basically my debug line,
-# where I can focus on one problematic compound 
-# and see what's going wrong
-# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
-# data <- data %>% filter(dsstox_casrn == "123-91-1")
-```
-
-Calculate a limit of quantification (90% of lowest observation)
-
-```{r, calc_loq, eval = TRUE}
-cvt.data <- estimate_loq(cvt.data)
-```
-
-Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm_ss.
+cvt_data[documents_extraction.pmid %In% "1233222",
+         c("loq_original",
+                                                     "loq_original_units")= .(0.08,
+                                                                              "ug/mL")]
+```
+
+Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm.
+
+```{r}
+timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M")
+```
 
@@
 
-```{r, run_invivoPKfit_1comp, eval = FALSE}
-
-run_timestamp_1comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+```{r, run_invivoPKfit_1comp}
 
@@
           paste("inst/ext/PK_fit_table_1comp_",
-                                    run_timestamp_1comp,
+                                    timestamp,
                                     ".csv",
@@
 
-```{r, run_invivoPKfit_2comp, eval = FALSE}
-
-run_timestamp_2comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+```{r, run_invivoPKfit_2comp}
 
@@
 write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
-                                    run_timestamp_2comp,
+                                    timestamp,
                                     ".csv",
@@
 
-```{r, run_invivoPKfit_flat, eval = FALSE}
-run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+```{r, run_invivoPKfit_flat}
 
@@
 write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
-                                    run_timestamp_flat,
+                                    timestamp,
                                     ".csv",

### 2022-12-14 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Add folder for working Rmds. Add Rmd to pull CvT data from database. Add updated MainAnalysis.Rmd file to use newly pulled CvT data.

---
title: "Pulling oral and IV data from CvTdb"
author: "Caroline Ring"
date: "2022-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary package

```{r}
library(DBI)
library(data.table)
library(ggplot2)
```

For connection to CvTdb:

Connect to EPA VPN.

Set environment variables for the user name, password, host, and dbname that will be used to connect. In Windows 10, go to the search bar in the menu and type "environment variables." A menu item should pop up that says "Edit the system environment variables." Click it. A window should pop up. On tab "Advanced " (where you should be already), there is a button "Environment Variables" in the lower right. Click it. Under "User variables for [YOURNAME]", the top window, click the "New" button. Add a variable and value and click "OK". Repeat clicking the "New" button and adding variables. I added the following system environment variables:

cvt_user = app_cvtdb
cvt_password = Svg=ZDZkzxX7R=+J
cvt_host = ccte-postgres-res.dmap-prod.aws.epa.gov
cvt_dbname = res_cvtdb

Doing it this way allows me to not hardcode the password.

# Connect to database

Open a PostGreSQL connection.

```{r}
 con <-  dbConnect(RPostgreSQL::PostgreSQL(),
            user = Sys.getenv("cvt_user"),
            password = Sys.getenv("cvt_password"), #
            host = Sys.getenv("cvt_host"), #
            dbname = Sys.getenv("cvt_dbname"))
```

# View the available tables

```{r}
dbGetQuery(con, "SELECT * FROM pg_catalog.pg_tables WHERE schemaname != 'pg_catalog' AND schemaname != 'information_schema'")
```

I don't fully know what all of this means, but it filters out various "internal" tables that are not actually part of CvTdb, and shows only the tables that are.

See the EER diagram showing the various tables within CvtDb and the relations between them.

# Formulate a query

In PostGreSQL, you have to refer to tables as "[schema].[table]". Note that in the table above, the schema for CvT tables is always "cvt."

I don't fully understand schemas yet.

I don't have a full data dictionary so I don't yet know how to filter correctly. The most expedient way to do it for me is to pull down each table separately, then filter and merge using e.g. data.table.

Here's how to pull down each table separately.

```{r}
fpath <- "C:/Users/cring/OneDrive - Environmental Protection Agency (EPA)/CvTdb/"
this_date <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")

#list of table names to pull down
tables <- c("conc_time_values",
            "series",
            "subjects",
            "studies",
            "chemicals",
            "documents")

#loop over table names and pull down each one
for (this_table in tables){
  print(this_table)
  this_query <- paste("SELECT * FROM",
                      paste0("cvt.", this_table))
  this_item <- dbGetQuery(con, this_query)
  this_item <- as.data.table(this_item)
  assign(this_table, this_item)

  #prepend table name to all variable names in each table
  #some variable names are repeated in multiple tables
  #this will let me keep track
  these_names <- names(eval(parse(text = this_table)))
  setnames(eval(parse(text = this_table)),
           these_names,
           paste(this_table,
                 these_names,
                 sep = "."))
}
```

Disconnect from database

```{r}
dbDisconnect(con)
```

Now there are a bunch of `data.table` variables in the environment, one for each CvT table. They are `conc_time_values`, `series`, `studies`, `subjects`, `chemicals`, and `documents`.

# Merge

Merge conc_time_values with series

```{r}
tmp1 <- series[conc_time_values,
                         on = c("series.id" = "conc_time_values.fk_series_id"),
                         nomatch = NA]
```

Merge with studies

```{r}
tmp2 <- studies[tmp1,
               on = c("studies.id" = "series.fk_study_id"),
               nomatch = NA]
```

Merge in subjects info

```{r}
tmp3 <- subjects[tmp2, on = c("subjects.id" = "series.fk_subject_id"), nomatch = NA]
```

Merge in chemical info. There are two chemical ID foreign keys.

`series.fk_test_chemical_id` = chemical that was dosed

`series.fk_analyzed_chemical_id`  = chemical that was measured in body media (tissue, blood/plasma, urine, etc.) May be the same as dosed chemical, but may be different if, for example, a metabolite was measured instead of the parent chemical.

To keep track of this, let me create two copies of the `chemicals` table -- one called `chemicals_dosed` and one called `chemicals_analyzed`. That way I can get the DTXSID, CASRN, and preferred names for each one.

```{r}
chemicals_dosed <- copy(chemicals)
chemicals_analyzed <- copy(chemicals)
```

Change the variable-name prefixes from "chemicals.[var]" to "chemicals_dosed.[var]" and "chemicals_analyzed.[var]" .
```{r}
setnames(chemicals_dosed,
         names(chemicals_dosed),
         gsub(x = names(chemicals_dosed),
              pattern = "chemicals.",
              replacement = "chemicals_dosed.",
              fixed = TRUE))

setnames(chemicals_analyzed,
         names(chemicals_analyzed),
         gsub(x = names(chemicals_analyzed),
              pattern = "chemicals.",
              replacement = "chemicals_analyzed.",
              fixed = TRUE))
```

Now merge

```{r}
tmp4 <- chemicals_dosed[tmp3,
                        on = c("chemicals_dosed.id" = "series.fk_test_chemical_id"),
                        nomatch = NA]
tmp5 <- chemicals_analyzed[tmp4,
                           on = c("chemicals_analyzed.id" = "series.fk_analyzed_chemical_id"),
                           nomatch = NA]
```

Merge in documents info.

There are both extraction documents and reference documents_reference. Make two copies of documents -- one for each.

```{r}
documents_reference <- copy(documents)
documents_extraction <- copy(documents)

setnames(documents_reference,
         names(documents_reference),
         gsub(x = names(documents_reference),
              pattern = "documents.",
              replacement = "documents_reference.",
              fixed = TRUE))

setnames(documents_extraction,
         names(documents_extraction),
         gsub(x = names(documents_extraction),
              pattern = "documents.",
              replacement = "documents_extraction.",
              fixed = TRUE))
```

```{r}
tmp6 <- documents_extraction[tmp5,
                  on = c("documents_extraction.id" ="studies.fk_extraction_document_id"),
                  nomatch = NA]
tmp7 <- documents_reference[tmp6,
                  on = c("documents_reference.id" ="studies.fk_reference_document_id"),
                  nomatch = NA]
```

I think this should do it.

```{r}
cvt_data <- copy(tmp7)
rm(tmp1, tmp2, tmp3, tmp4, tmp5, tmp6, tmp7)
```

Filter down to only blood/plasma studies and to only oral/iv administration.

```{r}
cvt_data <- cvt_data[series.conc_medium_normalized %in% c("blood", "plasma") &
                       studies.administration_route_normalized %in% c("oral", "iv")]
```

# Exploring the data

How many series per study?

```{r}
n_series_per_study <- cvt_data[,
                               .(n_series = length(unique(series.id))),
                               by = studies.id]
n_series_per_study[, range(n_series)]
```

# Look at one weird case

DTXSID1034187 had a weird situation where concentrations seemed very low for the "300" dose group. Let's see what is going on there

```{r}
tmp <- cvt_data[chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187"]
```

This should have reference IDs 141 and 142 -- does it?

```{r}
tmp[, unique(documents_extraction.id)]
```

OK good, so this is the data we were expecting.

This is tamoxifen. Though it does not have much document info, I traced it to https://doi.org/10.22427/NTP-DATA-DTXSID8021301

(the only curated document info avalable is this:)

```{r}
unique(tmp[, .(documents_extraction.url, documents_extraction.other_study_identifier)])
```

That URL is now broken. But if I google "ntp S0916" I get the page at https://doi.org/10.22427/NTP-DATA-DTXSID8021301.

Though items are marked below LOD or below LOQ, the original data does not include what the LOD/LOQ actually were. I cannot find a written report with more information anywhere.

The original data does note the dose units as ug/mL and notes that 5 mL/kg were administered, and contains the initial body weight of each subject.

In fact I think these doses have *not* been correctly normalized. There should be values for `studies.dose_volume` and there are not

```{r}
tmp[, unique(studies.dose_volume)]
```

```{r}
unique(tmp[, .(studies.dose_level_original, studies.dose_level_original_units, studies.dose_level_normalized, studies.dose_volume)])
```

This apepars to be the only document where that original units of ug/mL do not get changed for normalized dose level

```{r}
cvt_data[studies.dose_level_normalized == studies.dose_level_original &
           studies.dose_level_original_units %in% "ug/mL",
         unique(documents_extraction.id)]
```

Also, there is lots and lots of below-LOD data from study S0917 oral gavage administration that is not included in CvTdb at all.

Incidentally, the one with 300 mg/kg as the original dose level also seems to be wrong. That is study S0916. Looking at the original NTP data, those units are really ug/mL.

Visualize what I mean

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc,
                 shape = factor(documents_extraction.id),
                 color = as.numeric(studies.dose_level_normalized))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c(breaks = as.numeric(unique(tmp$studies.dose_level_normalized)))
```

Or plot dose-normalized

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc/as.numeric(studies.dose_level_normalized),
                 shape = factor(documents_extraction.id),
                 color = as.numeric(studies.dose_level_normalized))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c(breaks = as.numeric(unique(tmp$studies.dose_level_normalized)))
```

We need to actually normalize the doses for these, properly. We will have to go to the original NTP data to do this, because the volumes of administration were not properly retained in CvTdb.

for study S0916, the oral gavage volume of administration was 5 mL/kg, and the IV volume of administration was 2 ml/kg.

```{r}
tmp[, correct.dose_level_normalized:=as.numeric(studies.dose_level_normalized)]

tmp[studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "oral",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]

tmp[studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

tmp[studies.dose_level_original_units %in% "mg/kg" &
      studies.dose_level_original %in% 300 &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

```

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc,
                 shape = factor(documents_extraction.id),
                 color = as.numeric(correct.dose_level_normalized))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c()
```

```{r}
ggplot(data = tmp) +
  geom_point(aes(x = conc_time_values.time_hr,
                 y = conc_time_values.conc/as.numeric(correct.dose_level_normalized),
                 shape = factor(documents_extraction.id),
                 color = as.numeric(correct.dose_level_normalized))) +
  facet_grid(rows = vars(studies.administration_route_normalized)) +
  scale_y_log10() + 
  annotation_logticks(sides = "l") +
  scale_color_viridis_c()
```

Apply dose corrections to the full data table

```{r}
cvt_data[, correct.dose_level_normalized:=as.numeric(studies.dose_level_normalized)]

cvt_data[documents_extraction.id %in% 141 &
           studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "oral",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]

cvt_data[documents_extraction.id %in% 141 &
      studies.dose_level_original_units %in% "ug/mL" &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]

cvt_data[documents_extraction.id %in% 141 &
           studies.dose_level_original_units %in% "mg/kg" &
      studies.dose_level_original %in% 300 &
      studies.administration_route_normalized %in% "iv",
    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
```

Save the pulled CVT data

```{r}
write.csv(cvt_data,
          paste0("../inst/ext/cvt_data_",
          this_date,
          ".csv"),
          row.names = FALSE)
```

### 2022-12-15 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Normalize LOQ units to mg/L.

@@
 
-Filter down to only blood/plasma studies and to only oral/iv administration.
-
-```{r}
-cvt_data <- cvt_data[series.conc_medium_normalized %in% c("blood", "plasma") &
-                       studies.administration_route_normalized %in% c("oral", "iv")]
-```
-
 # Exploring the data
@@
 ```{r}
-tmp <- cvt_data[chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187"]
+tmp <- cvt_data[chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187" &
+                  studies.administration_route_normalized %in% c("oral", "iv") &
+                  series.conc_medium_normalized %in% c("blood", "plasma")]
 ```
@@
 
+# Normalize LOQ units to mg/L
+
+```{r}
+cvt_data[, unique(series.loq_units)]
+```
+
+```{r}
+cvt_data[, series.loq := as.numeric(series.loq)]
+cvt_data[series.loq_units %in% "ug/L", series.loq_normalized := series.loq * 1e-3]
+cvt_data[trimws(series.loq_units) %in% "ug/mL", series.loq_normalized := series.loq]
+cvt_data[series.loq_units %in% "mg/L", series.loq_normalized := series.loq]
+cvt_data[series.loq_units %in% "ng/mL", series.loq_normalized := series.loq * 1e-3]
+```
+
+For that with nmol/L we will need the molecular weight.
+For items with units ug we would need the volume of media analyzed.
+Both of these are for inhalation data, though, which we are not analyzing right now.
+So I will leave it alone for now.
+
 Save the pulled CVT data

### 2022-12-20 Working Rmds/MainAnalysis.Rmd
Add analysis that showed how to impute missing SDs for multi-individual data. Add postprocessing step.

@@
 ```{r, load_cvt, eval = TRUE}
-cvt_data <- fread("../inst/ext/cvt_data_2022_12_13_17_09_45.csv")
-```
-
-Add LOQ when available.
-
-PMIDs of documents
+cvt_data <- fread("../inst/ext/cvt_data_2022_12_15_16_20_21.csv")
+```
 
 ```{r}
-unique(cvt_data[is.na(conc_time_values.conc),
-                .(documents_extraction.pmid,
-                  documents_extraction.doi,
-                  documents_extraction.other_study_identifier,
-                  documents_extraction.url)])
-```
-
-For PMID = 1233222, the original document has the LOQ as 0.08 ug/mL.
+cvt <- preprocess_data(data.set = cvt_data,
+                       names_list =list(
+                       "Compound_Dosed" = "studies.test_substance_name_original",
+                              "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                              "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                              "Compound_Analyzed" = "series.analyte_name_original",
+                              "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                              "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "correct.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq_normalized",
+                      "Subject" = "subjects.id",
+                              "N_Subjects" = "series.n_subjects_in_series",
+                              "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
+      suppress.messages = FALSE)
+```
+
+There are many, many cases where N > 1 but no SD is reported. Can we impute these based on patterns in the cases where SD is reported? Calculate mean and SD for the individual cases:
 
 ```{r}
-cvt_data[documents_extraction.pmid %In% "1233222",
-         c("loq_original",
-                                                     "loq_original_units")= .(0.08,
-                                                                              "ug/mL")]
-```
+cvt <- as.data.table(cvt)
+cvt_summarized <- cvt[N_Subjects==1,
+                      .(meanval = mean(Value, na.rm = TRUE),
+                        sdvals = sd(Value, na.rm = TRUE),
+                        n = .N),
+                      by = .(Reference, DTXSID, Media, Dose)]
+ggplot(cvt_summarized) +
+  geom_point(aes(x = meanval, y = sdvals, color = n)) +
+  scale_x_log10() + scale_y_log10() + scale_color_viridis_c(trans = "log10")
+
+summary(lm(log10(sdvals) ~ log10(meanval), data = cvt_summarized))
+```
+
+The relationship between sample SD and sample mean seems to be almost the identity line.
+
+What about the multi-subject cases with reported SD?
+
+```{r}
+ggplot(cvt[N_Subjects > 1],
+       aes(x = Value, y = Value_SD)) +
+  geom_point(aes(x = Value, y = Value_SD, color = N_Subjects))  +
+  scale_x_log10() + scale_y_log10() + geom_smooth(method = "lm")
+
+summary(lm(log10(Value_SD) ~ log10(Value), data = cvt[N_Subjects > 1]))
+```
+
+This one isn't quite the identity line but still, we can get some idea.
+
+These ones with entirely missing SDs are different from the studies where only a few SDs are missing.
+When only a few are missing, it was usually because the data were pulled from a plot where the error bars were smaller thant the plotting symbol on a few points.
+Instead of recording the size of the symbol as the error bars, the error was recorded as NA.
+But when all SDs are missing, it is usually because the study did not report the SDs in the first place.
+
+In this case, it seems like a reasonable choice to impute the mean value itself as the SD.
+This relation seems to be borne out by the individual-anumal data, and it is more conservative than the relation suggested by the (limited) multi-animal data.
+I will make that change.
 
@@
     PK.fit.table.1comp <- fit_all(
-      data.set = cvt.data,
+      data.set = cvt_data,
       model = "1compartment",
       modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
+      names_list =list(
+                      "Compound_Dosed" = "studies.test_substance_name_original",
+                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                      "Compound_Analyzed" = "series.analyte_name_original",
+                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "studies.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq",
+                      "Subject" = "subjects.id",
+                      "N_Subjects" = "series.n_subjects_in_series",
+                      "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
+      optimx_args = list(
+                      "method" = "bobyqa",
+                      "itnmax" = 1e6,
+                      "control" = list("maximize" = TRUE,
+                                       "kkt" = FALSE)
+                    ),
       suppress.messages = TRUE
@@
 
+post_1comp <- postprocess_data(PK_fit = PK.fit.table.1comp,
+                               model = "1compartment")
+
+write.csv(post_1comp,
+          paste("inst/ext/PK_fit_postprocess_1comp_",
+                                    timestamp,
+                                    ".csv",
+                                    sep=""),
+          row.names = FALSE)
+
 ```
@@
     PK.fit.table.2comp <- fit_all(
-      data.set = cvt.data,
-      model = "2compartment",
+      data.set = cvt_data,
+      model = "flat",
       modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
+      names_list =list(
+                      "Compound_Dosed" = "studies.test_substance_name_original",
+                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                      "Compound_Analyzed" = "series.analyte_name_original",
+                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "studies.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq",
+                      "Subject" = "subjects.id",
+                      "N_Subjects" = "series.n_subjects_in_series",
+                      "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
+      optimx_args = list(
+                      "method" = "bobyqa",
+                      "itnmax" = 1e6,
+                      "control" = list("maximize" = TRUE,
+                                       "kkt" = FALSE)
+                    ),
       suppress.messages = TRUE
@@
                                     sep=""), row.names = FALSE)
-
+post_2comp <- postprocess_data(PK_fit = PK.fit.table.2comp,
+                               model = "2compartment")
+
+write.csv(post_2comp,
+          paste("inst/ext/PK_fit_postprocess_2comp_",
+                                    timestamp,
+                                    ".csv",
+                                    sep=""),
+          row.names = FALSE)
 ```
@@
     PK.fit.table.flat <- fit_all(
-      data.set = cvt.data,
+     data.set = cvt_data,
       model = "flat",
       modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
+      names_list =list(
+                      "Compound_Dosed" = "studies.test_substance_name_original",
+                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                      "Compound_Analyzed" = "series.analyte_name_original",
+                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "studies.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq",
+                      "Subject" = "subjects.id",
+                      "N_Subjects" = "series.n_subjects_in_series",
+                      "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
+      optimx_args = list(
+                      "method" = "bobyqa",
+                      "itnmax" = 1e6,
+                      "control" = list("maximize" = TRUE,
+                                       "kkt" = FALSE)
+                    ),
       suppress.messages = TRUE
@@
 For ease of plotting, get the pre-processed, harmonized data:
-
-```{r}
-DF <- preprocess_data(data.set = cvt.data,
-                       ratio.data.to.dose = 1,
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
-      suppress.messages = FALSE)
-```
 

### 2022-12-20 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Normalize sample SDs to same units as concentrations (mg/L).

@@
 
+# Missing LOQs
+
+```{r}
+cvt_data[, n_obs_ref := sum(is.finite(conc_time_values.conc) & (conc_time_values.conc > 0) %in% TRUE),
+         by = .(documents_extraction.id, documents_reference.id,
+                chemicals_analyzed.dsstox_substance_id, chemicals_dosed.dsstox_substance_id,
+                series.conc_medium_normalized, subjects.species)]
+
+unique(cvt_data[n_obs_ref==0 &
+                  series.conc_medium_normalized %in% c("blood", "plasma") &
+                  studies.administration_route_normalized %in% c("oral", "iv"), 
+                  #chemicals_dosed.dsstox_substance_id == chemicals_analyzed.dsstox_substance_id,
+                .(documents_extraction.id, documents_reference.id, documents_extraction.pmid, documents_extraction.doi, documents_extraction.other_study_identifier, chemicals_analyzed.dsstox_substance_id, chemicals_dosed.dsstox_substance_id, studies.test_substance_name_original, series.analyte_name_original, series.conc_medium_normalized, studies.administration_route_normalized)])
+```
+
+# Missing LOQ for documents_extraction.id 136
+
+This is an NTP study.
+For some reason LOQs were not extracted.
+I looked up the original data and LOQs are noted.
+I will add them here.
+Source: https://cebs.niehs.nih.gov/cebs/test_article/58-08-2 click on "Individual Animal Data" to download spreadsheet.
+The LOQs are stated in comments like "XX is less than YYY, the ELOQ for [substance]."
+
+```{r}
+cvt_data[documents_extraction.id %in% 136 &
+           series.analyte_name_original %in% "Caffeine",
+         c("series.loq", "series.loq_units") := .(4.00, "ng/mL")]
+
+cvt_data[documents_extraction.id %in% 136 &
+           series.analyte_name_original %in% "L-Ephedrine",
+         c("series.loq", "series.loq_units") := .(4.44, "ng/mL")]
+
+cvt_data[documents_extraction.id %in% 136 &
+           series.analyte_name_original %in% "Pseudoephedrine",
+         c("series.loq", "series.loq_units") := .(4.43, "ng/mL")]
+```
+
+## Missing LOQ for documents_extraction.id 138
+
+```{r}
+cvt_data[documents_extraction.id %in% 138 &
+           series.analyte_name_original %in% "Pentachloroanisole",
+         c("series.loq", "series.loq_units") := .(0.05, "ug/mL")]
+
+```
+
+## Missing LOQ for documents_extraction.if 178
+
+See https://ntp.niehs.nih.gov/publications/reports/tr/500s/tr526/index.html?utm_source=direct&utm_medium=prod&utm_campaign=ntpgolinks&utm_term=tr526abs Appendix F
+
+LOQ in blood for rat was 30 pg/mL. (Individual animal data refers to plasma, but the PDF report refers to blood?)
+
+```{r}
+cvt_data[documents_extraction.id %in% 178 &
+          series.analyte_name_original %in% "2,3,4,7,8-pentachlorodibenzofuran" &
+           series.conc_medium_normalized %in% "plasma",
+         c("series.loq", "series.loq_units") := .(30, "pg/mL")]
+```
+
 # Normalize LOQ units to mg/L
@@
 cvt_data[series.loq_units %in% "ng/mL", series.loq_normalized := series.loq * 1e-3]
+cvt_data[series.loq_units %in% "pg/mL", series.loq_normalized := series.loq * 1e-6]
 ```
@@
 For items with units ug we would need the volume of media analyzed.
-Both of these are for inhalation data, though, which we are not analyzing right now.
+Both of these are for inhalation data, though, which we aare not analyzing right now.
 So I will leave it alone for now.
 
-Save the pulled CVT data
+# Concentration SD
+
+These have not been normalized so we need to do it now.
+
+```{r}
+cvt_data[!is.na(conc_time_values.conc_sd_original), unique(series.conc_units_original)]
+```
+
+```{r}
+cvt_data[series.conc_units_original == "ug/L",
+         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-3]
+
+cvt_data[series.conc_units_original == "ug/mL",
+         conc_time_values.conc_sd := conc_time_values.conc_sd_original]
+
+cvt_data[series.conc_units_original == "mg/L",
+         conc_time_values.conc_sd := conc_time_values.conc_sd_original]
+
+cvt_data[series.conc_units_original == "ug/dL",
+         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-4]
+
+cvt_data[series.conc_units_original == "ng/mL",
+         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-3]
+
+cvt_data[series.conc_units_original == "pg/mL",
+         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-6]
+
+```
+
+We don't have any cases for oral/IV in blood/plasma where concentration lower/upper bounds are given, so we won't worry about normalizing these bounds right now.
+
+```{r}
+cvt_data[!is.na(conc_time_values.conc_upper_bound_original) & studies.administration_route_normalized %in% c("oral", "iv") & series.conc_medium_normalized %in% c("blood", "plasma")]
+```
+
+Save the pulled CVT data with the edits/normalizations
 

### 2023-01-04 Working Rmds/MainAnalysis.Rmd
Split analyses for SD imputation and plotting into separate Rmd documents.

--- 2022-12-14 Working Rmds/MainAnalysis.Rmd
@@
 ---
-title: "<i>invivoPKfit</i> and <i>CvTdb</i> figures"
+title: "invivoPKfit analysis of CvTdb data"
 author: "Christopher Cook, John Wambaugh, Caroline Ring"
-date: "11/15/2022"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
 output:
@@
 
-Read in CvTdb data.
+Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.
 
 ```{r, load_cvt, eval = TRUE}
-cvt_data <- fread("../inst/ext/cvt_data_2022_12_13_17_09_45.csv")
+cvt_data <- fread("../inst/ext/cvt_data_2022_12_15_16_20_21.csv")
 ```
 
-Add LOQ when available.
-
-PMIDs of documents
-
-```{r}
-unique(cvt_data[is.na(conc_time_values.conc),
-                .(documents_extraction.pmid,
-                  documents_extraction.doi,
-                  documents_extraction.other_study_identifier,
-                  documents_extraction.url)])
-```
-
-For PMID = 1233222, the original document has the LOQ as 0.08 ug/mL.
-
-```{r}
-cvt_data[documents_extraction.pmid %In% "1233222",
-         c("loq_original",
-                                                     "loq_original_units")= .(0.08,
-                                                                              "ug/mL")]
-```
-
-Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm.
+Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.
 
@@
 timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M")
+```
+
+Fit the flat model.
+
+```{r, run_invivoPKfit_flat}
+
+system.time(
+    PK.fit.table.flat <- fit_all(
+     data.set = cvt_data,
+      model = "flat",
+      modelfun = "analytic",
+      names_list =list(
+                      "Compound_Dosed" = "studies.test_substance_name_original",
+                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                      "Compound_Analyzed" = "series.analyte_name_original",
+                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "studies.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq",
+                      "Subject" = "subjects.id",
+                      "N_Subjects" = "series.n_subjects_in_series",
+                      "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
+      optimx_args = list(
+                      "method" = "bobyqa",
+                      "itnmax" = 1e6,
+                      "control" = list("kkt" = FALSE)
+                    ),
+      suppress.messages = TRUE
+    )
+)
+
+write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
+                                    timestamp,
+                                    ".csv",
+                                    sep=""), row.names = FALSE)
+
+rm(PK.fit.table.flat)
 ```
@@
     PK.fit.table.1comp <- fit_all(
-      data.set = cvt.data,
+      data.set = cvt_data,
       model = "1compartment",
       modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
+      names_list =list(
+                      "Compound_Dosed" = "studies.test_substance_name_original",
+                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                      "Compound_Analyzed" = "series.analyte_name_original",
+                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "studies.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq",
+                      "Subject" = "subjects.id",
+                      "N_Subjects" = "series.n_subjects_in_series",
+                      "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
+      optimx_args = list(
+                      "method" = "bobyqa",
+                      "itnmax" = 1e6,
+                      "control" = list("kkt" = FALSE)
+                    ),
       suppress.messages = TRUE
@@
 write.csv(PK.fit.table.1comp,
-          paste("inst/ext/PK_fit_table_1comp_",
+          paste("../inst/ext/PK_fit_table_1comp_",
                                     timestamp,
@@
           row.names = FALSE)
+
+post_1comp <- postprocess_data(PK_fit = PK.fit.table.1comp,
+                               model = "1compartment")
+
+write.csv(post_1comp,
+          paste("../inst/ext/PK_fit_postprocess_1comp_",
+                                    timestamp,
+                                    ".csv",
+                                    sep=""),
+          row.names = FALSE)
+
+rm(PK.fit.table.1comp, post_1comp)
 
@@
 ```{r, run_invivoPKfit_2comp}
-
 ### do 2-Compartment fit
@@
     PK.fit.table.2comp <- fit_all(
-      data.set = cvt.data,
+      data.set = cvt_data,
       model = "2compartment",
       modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
+      names_list =list(
+                      "Compound_Dosed" = "studies.test_substance_name_original",
+                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                      "Compound_Analyzed" = "series.analyte_name_original",
+                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "studies.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq",
+                      "Subject" = "subjects.id",
+                      "N_Subjects" = "series.n_subjects_in_series",
+                      "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
+      optimx_args = list(
+                      "method" = "bobyqa",
+                      "itnmax" = 1e6,
+                      "control" = list("kkt" = FALSE)
+                    ),
       suppress.messages = TRUE
@@
 
-write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
+write.csv(PK.fit.table.2comp, paste("../inst/ext/PK_fit_table_2comp_",
                                     timestamp,
@@
 
-```
+post_2comp <- postprocess_data(PK_fit = PK.fit.table.2comp,
+                               model = "2compartment")
 
-Fit the flat model.
-
-```{r, run_invivoPKfit_flat}
-
-system.time(
-    PK.fit.table.flat <- fit_all(
-      data.set = cvt.data,
-      model = "flat",
-      modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
-      suppress.messages = TRUE
-    )
-)
-
-write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
+write.csv(post_2comp,
+          paste("../inst/ext/PK_fit_postprocess_2comp_",
                                     timestamp,
                                     ".csv",
-                                    sep=""), row.names = FALSE)
+                                    sep=""),
+          row.names = FALSE)
+
+rm(PK.fit.table.2comp, post_2comp)
 ```
-
-For ease of plotting, get the pre-processed, harmonized data:
-
-```{r}
-DF <- preprocess_data(data.set = cvt.data,
-                       ratio.data.to.dose = 1,
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
-      suppress.messages = FALSE)
-```
-
-```{r, read_data}
-### this block reads the exported model fit csv files from run_invivoPKfit
-
-PK.fit.table.1comp <- fread(paste0("inst/ext/", "PK_fit_table_1comp_2022_12_08_09_44_34.csv",sep=""))
-PK.fit.table.2comp <- fread(paste0("inst/ext/", "PK_fit_table_2comp_2022_12_08_10_31_09.csv",sep=""))
-PK.fit.table.flat <- fread(paste0("inst/ext/", "PK_fit_table_flat_2022_12_08_12_03_24.csv",sep=""))
-
-#pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
-```
-
-Rowbind together all of the fitted parameter tables into one big one.
-```{r}
-pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
-                         "2comp" = PK.fit.table.2comp,
-                         "flat" = PK.fit.table.flat),
-                    use.names = TRUE,
-                    fill = TRUE)
-```
-
-Get a table of the winning model for each dataset (minimum AIC).
-
-```{r}
-tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, model, AIC)])
-setorder(tmp, DTXSID, Species, Analysis_Type, AIC, na.last = TRUE)
-model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type)]
-pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type")]
-pk_fit[, winning:=(model == winmodel)]
-
-```
-
-Plot concentration vs time with the best-fit params by data subset (DTXSID and species).
-
-Indicate the following:
-
-- One line for each model
-- Which is the winning model
-- Dose group
-- Blood vs. plasma
-- Below LOQ vs. above LOQ (plot below-LOQ points at LOQ)
-- IV vs. oral administration
-
-Would also like to plot uncertainty in predictions based on uncertainty in parameter estimates.
-
-Plot versions:
-- Winning model only
-- One model at a time
-- All three models on same plot
-
-Get unique combinations of DTXSID and species -- each of these will be one plot.
-
-```{r}
-plot_table <- unique(pk_fit[, .(DTXSID, Species)])
-```
-
-Plot all models for the joint analysis.
-```{r}
-
-#plot all models
-tmp <- mapply(plot_fit,
-              DTXSID_in = plot_table$DTXSID,
-                     Species_in = plot_table$Species,
-              MoreArgs = list(
-                     model_in = "all",
-                     Analysis_Type_in = "Joint",
-                     DF = DF,
-                     pk_fit = pk_fit,
-                     n = 101,
-                     log10_scale_time = FALSE,
-                     file_path = "inst/ext/plots/Joint Analysis/model_all/")
-                     )
-
-```
-
-Plot only the winning model
-
-```{r}
-#plot all models
-tmp <- mapply(plot_fit,
-              DTXSID_in = plot_table$DTXSID,
-                     Species_in = plot_table$Species,
-              MoreArgs = list(
-                Analysis_Type_in = c("Joint", "Separate"),
-                     model_in = "winning",
-                     fitdata = DF,
-                     pk_fit = pk_fit,
-                     file_path = "inst/ext/plots/analysis_all_model_winning/",
-                log10_scale_time = TRUE)
-                     )
-```
-
-```{r, merge_pkfits, eval=FALSE}
-all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
-                                       "2compartment"=pk_output_2comp,
-                                       "flat"=pk_output_flat))
-write.csv(all.fit.table, paste("inst/ext/all.fit.table.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-```
-
-```{r, make_rdata, eval = FALSE}
-
-### this block takes the csv files in read_data
-# and saves them as Rdata files
-
-### save data
-paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".RData",sep="")
-save(pk_output_1comp, file = paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
-save(pk_output_2comp, file = paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
-save(pk_output_flat, file = paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
-save(raw_1comp, file = paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
-save(raw_2comp, file = paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
-save(raw_flat, file = paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
-save(all.fit.table, file = paste("figures_rdata/all_fit_table_",THIS.DATE,".RData",sep=""))
-save(pk_lombardo, file = paste("figures_rdata/pk_lombardo",THIS.DATE,".RData",sep=""))
-```
-
-```{r, make_invivoPKfit_plots, eval = TRUE}
-
-### this block produces the pdf files of the model fits
-# plotted on top of the original data
-
-### 1 compartment
-
-# pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
-#   filter(Compound == "tamoxifen") %>%
-#   filter(Data.Analyzed != "Joint Analysis")
-
-# raw_1comp_03012022 <- raw_1comp_03012022 %>%
-#   filter(Compound == "tamoxifen")
-
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp),
-                      data.set = as.data.table(raw_1comp),
-                      model = "1compartment")
-
-### 2 compartment
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp),
-                      data.set = as.data.table(raw_2comp),
-                      model = "2compartment")
-
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_flat),
-                      data.set = as.data.table(raw_flat),
-                      model = "flat")
-
-```
-
-```{r, make_cp_rdata, eval = FALSE}
-
-### this block creates a data.frame of predicted concentrations
-# using the estimated parameters and the observed conc-time points
-
-######################
-
-###########
-### this is 1-compartment data
-###########
-
-###################
-###################
-
-### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data1 <- pk_output_1comp %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
-  filter(Species != "hamster")
-
-raw_data1 <- dplyr::select(raw_1comp, -c("kelim", 
-                                                  "Vdist", 
-                                                  "Fgutabs", 
-                                                  "kgutabs")) %>% 
-  filter(Species != "hamster")
-
-###################
-###################
-
-raw_data1$Reference <- as.character(raw_data1$Reference)
-
-full_data_1 <- left_join(raw_data1, pk_data1, by = c("Compound", "CAS", "Reference"))
-full_data_1 <- full_data_1 %>% filter(AIC != Inf)
-
-### function that finds cp
-find_cp_1 <- function(full_data_1) {plyr::adply(full_data_1, 1, mutate, cp = cp_1comp(time = Time,
-                                                                                      params = full_data_1[1, ],
-                                                                                      dose = Dose,
-                                                                                      iv.dose = iv))}
-
-### have to split data frame into ones with unique parameter values because cp_1comp takes constants
-split_df_1 <- split(full_data_1, list(full_data_1$Compound,
-                                      full_data_1$Reference,
-                                      full_data_1$CAS,
-                                      full_data_1$Species.x),
-                    drop = TRUE)
-
-cp_df_1 <- lapply(split_df_1, find_cp_1)
-
-cp_df_1 <- do.call(rbind, cp_df_1)
-
-### nomralize cp by Value
-cp_df_1$cp_norm <- cp_df_1$cp / cp_df_1$Value
-cp_df_1$type <- "1-Compartment"
-
-###########
-### this is 2-compartment data
-###########
-
-#######################
-#######################
-
-### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data2 <- pk_output_2comp %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-raw_data2 <- dplyr::select(raw_2comp, -c("kelim", 
-                                                  "Vdist", 
-                                                  "Fgutabs", 
-                                                  "kgutabs",
-                                                  "V1",
-                                                  "Ralphatokelim",
-                                                  "Fbetaofalpha"))
-
-########################
-########################
-
-raw_data2$Reference <- as.character(raw_data2$Reference)
-
-full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))
-full_data_2 <- full_data_2 %>% filter(AIC != Inf)
-split_df_2 <- split(full_data_2, list(full_data_2$Compound,
-                                      full_data_2$Reference,
-                                      full_data_2$CAS,
-                                      full_data_2$Species.x),
-                    drop = TRUE)
-
-### function that finds cp
-find_cp_2 <- function(full_data_2) {plyr::adply(full_data_2, 1, mutate, cp = cp_2comp(time = Time,
-                                                                                      params = full_data_2[1, ],
-                                                                                      dose = Dose,
-                                                                                      iv.dose = iv))}
-cp_df_2 <- lapply(split_df_2, find_cp_2)
-
-cp_df_2 <- do.call(rbind, cp_df_2)
-
-cp_df_2$cp_norm <- cp_df_2$cp / cp_df_2$Value
-cp_df_2$type <- "2-Compartment"
-
-# cp_df_2 <- cp_df_2 %>%
-#   filter(cp != 1e-20)
-
-###########
-### this is flat data
-###########
-
-pk_data_flat <- pk_output_flat %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
-  filter(Species != "hamster")
-
-raw_data_flat <- dplyr::select(raw_flat, -c("A")) %>% 
-  filter(Species != "hamster")
-
-raw_data_flat$Reference <- as.character(raw_data_flat$Reference)
-
-full_data_flat <- left_join(raw_data_flat, pk_data_flat, by = c("Compound", "CAS", "Reference"))
-full_data_flat <- full_data_flat %>% filter(AIC != Inf)
-split_df_flat <- split(full_data_flat, list(full_data_flat$Compound,
-                                            full_data_flat$Reference,
-                                            full_data_flat$CAS,
-                                            full_data_flat$Species.x),
-                       drop = TRUE)
-
-### function that finds cp
-find_cp_flat <- function(full_data_flat) {plyr::adply(full_data_flat, 1, mutate, cp = cp_flat(time = Time,
-                                                                                              params = full_data_flat[1, ],
-                                                                                              dose = Dose,
-                                                                                              iv.dose = iv))}
-cp_df_flat <- lapply(split_df_flat, find_cp_flat)
-
-cp_df_flat <- do.call(rbind, cp_df_flat)
-
-cp_df_flat$cp_norm <- cp_df_flat$cp / cp_df_flat$Value
-cp_df_flat$type <- "Flat"
-
-#######################
-#######################
-
-### make all data.frames have the same column names so they are rbind-able
-cp_df_1 <- cp_df_1[, intersect(colnames(cp_df_2), colnames(cp_df_1))]
-cp_df_2 <- cp_df_2[, intersect(colnames(cp_df_1), colnames(cp_df_2))]
-
-cp_df <- rbind(cp_df_1, cp_df_2)
-
-cp_df <- cp_df[, intersect(colnames(cp_df_flat), colnames(cp_df))]
-cp_df_flat <- cp_df_flat[, intersect(colnames(cp_df), colnames(cp_df))]
-
-cp_df <- rbind(cp_df, cp_df_flat)
-
-cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
-
-cp_df <- cp_df %>% group_by(Species.x, 
-                           Compound,
-                           CAS,
-                           type) %>%
- mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))
-
-### here is where you save the Rdata file
-save(cp_df, file = paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
-```
-
-```{r, make_cvt_variability_rdata, eval = FALSE}
-
-### this block creates a data.frame that shows the 
-# spread of CvT data via across replicate timepoints 
-# for a single experiment
-# if the data isn't within 2-fold of itself
-# is it reasonable to say that a model should fit within 2-fold?
-
-##################
-##################
-
-### all the raw data for each model SHOULD be the same
-# so only need to use one
-data <- as.data.table(raw_1comp)
-
-##################
-##################
-
-### function that finds mean conc of each replicate timepoint
-find_mean_conc <- function(data) {
-
-  ### only use data with replicate timepoints
-  data <- data[ ave(1:nrow(data), data$Time, FUN = length) > 1 , ]
-
-  if(nrow(data) == 0) {
-    return(NULL)
-  } else {
-
-    time_split <- split(data, data$Time)
-
-    ### discard replicate timepoints where all concentrations are NA
-    time_split_list <- purrr::discard(time_split, ~all(is.na(.$Value)))
-
-    if(length(time_split_list) == 0) {
-      return(NULL)
-    } else {
-
-      data <- do.call(rbind, time_split_list)
-
-      ### where some replicate concentration data are NA, set them equal to the LOQ
-      data$Value[is.na(data$Value)] <- data$LOQ[is.na(data$Value)]
-
-      ### take the average Value for each set of timepoints
-      data <- data %>%
-        group_by(Time) %>%
-        do(mutate(., mean_conc = mean(.$Value, na.rm = TRUE)))
-
-      data <- data %>%
-        group_by(Time) %>%
-        do(mutate(., range_conc = max(.$Value) - min(.$Value)))
-
-      ### create normalized conc values by dividing conc by mean_conc
-      data$conc_norm <- data$Value/data$mean_conc
-
-      data <- data[order(data$Time), ]
-
-      return(data)
-    }
-  }
-}
-
-### this for loop applies the function 
-# at data subsets of compound, data, dose, route, media
-data.list <- list()
-for(this.compound in unique(data[, Compound])) {
-  this.compound.data <- data[Compound == this.compound]
-
-  ### list of columns by which to split data.set
-  col_list <- list(this.compound.data$Reference,
-                   this.compound.data$Dose,
-                   this.compound.data$Route,
-                   this.compound.data$Media)
-
-  ### split data.set into list of data.tables
-  split_list <- split(this.compound.data, col_list)
-
-  ### remove data.tables with 0 rows
-  split_list <- keep(split_list, ~nrow(.) > 0)
-
-  ### use find_mean_conc fn
-  mean_conc <- lapply(split_list, find_mean_conc)
-
-  test <- do.call(rbind, mean_conc)
-
-  data.list[[this.compound]] <- test
-}
-
-### combine data.tables back into one large data.set
-cvt_variability_df <- do.call(rbind, data.list)
-
-### SAVE the data
-save(cvt_variability_df, file = paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))
-```
-
-```{r, load_data}
-
-### this block loads the Rdata files,
-# as well as some other files written in below code blocks
-# this saves time from having to run those below code blocks every time
-# these additional files include 'cp_df' and 'cvt_variability'
-
-### load all of this wonderful data
-load(paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))
-
-load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
-
-load("figures_rdata/pk_lombardo_02072022.Rdata")
-```
-
-```{r, make_cp_histogram}
-
-### this block makes a histogram of the data output
-# from make_cp_rdata
-# there's a separate facet for each model type
-# only data that were best fitted by that model
-# are shown in that facet
-
-##################
-##################
-
-pk_data <- cp_df
-
-# cvt_data <- cvt_variability_df_04282022
-
-##################
-##################
-
-row.names(pk_data) <- c()
-full_data <- pk_data
-
-# cvt_data <- dplyr::select(cvt_data, -c("kelim",
-#                                        "Vdist",
-#                                        "Fgutabs",
-#                                        "kgutabs"))
-# 
-# ### split pk_data by model so you can properly join with raw data
-# model_split <- split(pk_data, pk_data$model)
-# 
-# cvt_data$Reference <- as.character(cvt_data$Reference)
-# 
-# cvt_data$type <- "1-Compartment"
-# full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
-# 
-# cvt_data$type <- "2-Compartment"
-# full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
-# 
-# cvt_data$type <- "Flat"
-# full_data_flat <- left_join(cvt_data, model_split$`flat`)
-# 
-# ### put data back together
-# full_data <- rbind(full_data_1, full_data_2, full_data_flat)
-# 
-# full_data <- full_data %>%
-#   filter(cp != 0)
-
-full_data$AIC <- round(full_data$AIC, digits = 4)
-
-### only take necessary columns to keep things clean
-full_data <- full_data %>%
-  distinct(Compound, Reference, Species.x, model, AIC, cp_norm)
-
-### this pivots the data so we have AICs and cp_norms
-# for each model row-wise
-full_data <- full_data %>%
-  group_by(Species.x, Compound, Reference, model) %>%
-  mutate(row = row_number()) %>%
-  pivot_wider(names_from = model,
-              values_from = c(AIC, cp_norm)) %>%
-  dplyr::select(-row)
-
-full_data <- as.data.table(full_data)
-
-### make model column equal a specific model based on AIC values
-full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    AIC_2compartment < AIC_1compartment &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    AIC_flat < AIC_1compartment &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-
-                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
-                                                      is.na(AIC_flat) ~ "1-Compartment",
-                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) &
-                                                      is.na(AIC_flat) ~ "2-Compartment",
-                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) &
-                                                      is.na(AIC_2compartment) ~ "Null",
-
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_flat < AIC_1compartment ~ "Null",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
-
-### make cp_norm equal to the cp_norm that corresponds to the best fitting model
-full_data <- full_data %>%
-  mutate(cp_norm = case_when(model == "1-Compartment" ~ cp_norm_1compartment,
-                             model == "2-Compartment" ~ cp_norm_2compartment,
-                             model == "Null" ~ cp_norm_flat))
-
-full_data[, model := paste("Model:", model)]
-
-### this creates a new column that says how many unique sets of Compound, Reference,
-# and Species correspond to each model
-full_data[, chem_ref_spec_count := uniqueN(.SD), .SDcols = c("Compound", 
-                                                             "Reference",
-                                                             "Species.x"), 
-          by = "model"]
-
-full_data[, chem_ref_spec_count := paste("Chemical-Reference-Species:", chem_ref_spec_count)]
-
-### make plot, facet by model and chem_ref_spec_count
-p <- ggplot(data = full_data,
-            mapping = aes(x = cp_norm)) +
-  geom_histogram(binwidth = 0.325) +
-  geom_vline(xintercept = c(0.5, 2),
-             color = "Red",
-             linetype = "dashed") +
-  # xlim(0, 1e42) +
-  # ylim(0, 400) +
-  # scale_y_log10()+
-  theme(title = element_text(size = 16),
-        axis.text = element_text(size = 12),
-        axis.title = element_text(size = 14)) +
-  # scale_x_log10() +
-  scale_x_log10(limits = c(1e-3, 1e3), labels = scientific) +
-  scale_y_continuous(labels = scientific) +
-  theme_bw() +
-  labs(x = "Predicted/Observed",
-       y = "Number of Observations") +
-  facet_wrap(. ~ model + chem_ref_spec_count)
-
-p
-```
-
-```{r, make_cp_error_histogram}
-
-### I think this is little outdated but whatever I'm gonna keep it here
-# Think is was just plotting Cpred - Cobs
-
-##################
-##################
-
-# data <- cp_df_12212021
-# data <- cp_df_03012022
-data <- cp_df
-
-##################
-##################
-
-data <- data %>%
-  filter(cp != 1e-20)
-
-data <- data %>%
-  distinct(Species.x, Compound, CAS, cp_pred_error_range)
-
-p <- ggplot(data = data,
-            mapping = aes(x = cp_pred_error_range)) +
-  geom_histogram() +
-  scale_x_log10() +
-  facet_wrap(. ~type)
-
-p
-```
-
-```{r, make_cp_error_versus_dose}
-
-### I think this is little outdated but whatever I'm gonna keep it here
-
-##################
-##################
-
-data <- cp_df
-
-##################
-##################
-
-data <- data %>%
-  filter(type == "1-Compartment")
-
-data <- data %>%
-  group_by(Compound, CAS, Dose) %>%
-  mutate(average = mean(cp_pred_error))
-
-p <- ggplot(data = data, mapping = aes(x = Dose, y = average)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10()
-
-p
-
-```
-
-```{r, make_cvt_variability_histogram}
-
-### this block makes the histogram
-# of cvt variability using the data.frame
-# made from make_cvt_variability_rdata
-
-#################
-#################
-
-data <- cvt_variability_df
-# data <- cvt_variability_df_12212021
-
-#################
-#################
-
-p <- ggplot(data, aes(x = conc_norm)) +
-  geom_histogram(binwidth = 0.25) +
-  xlim(c(-0.5, 4)) +
-  geom_vline(xintercept = c(0.5, 2),
-             color = "Red",
-             linetype = "dashed") +
-  theme_bw() +
-  labs(x = "Normalized concentration",
-       y = "Number of observations")
-p
-```
-
-```{r, make_density_plot}
-
-### this block makes a density plot with cvt variabity
-# and normalized predicted concentrations
-# it's basically a combination of the other two histograms
-# expect here we limit cp observations those that have replicate timepoint
-# data, so it matches the cvt variability data, thus making it 
-# comparable
-
-##################
-##################
-
-# pk_data <- cp_df_03012022
-pk_data <- cp_df
-
-cvt_data <- cvt_variability_df
-
-##################
-##################
-
-### i hate row names
-row.names(pk_data) <- c()
-
-### making these null so I don't have to deal
-# with duplicate .x and .y's
-# only need the ones from pk_data
-cvt_data <- dplyr::select(cvt_data, -c("kelim", 
-                                       "Vdist", 
-                                       "Fgutabs", 
-                                       "kgutabs"))
-
-### split pk_data by model so you can properly join with raw data
-model_split <- split(pk_data, pk_data$model)
-
-### References were of different classes for some reason
-# so had to change
-cvt_data$Reference <- as.character(cvt_data$Reference)
-
-cvt_data$type <- "1-Compartment"
-full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
-
-cvt_data$type <- "2-Compartment"
-full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
-
-cvt_data$type <- "Flat"
-full_data_flat <- left_join(cvt_data, model_split$`flat`)
-
-### put data back together
-full_data <- rbind(full_data_1, full_data_2, full_data_flat)
-
-### not sure why there were 0s,
-# but they were screwing things up
-full_data <- full_data %>%
-  filter(cp != 0)
-
-full_data$AIC <- round(full_data$AIC, digits = 4)
-
-full_data <- full_data %>%
-  distinct(Compound, Reference, model, Species.x, conc_norm, AIC, cp_norm)
-
-### 
-### 
-full_data <- full_data %>%
-  group_by(Species.x, Compound, Reference, model) %>%
-  mutate(row = row_number()) %>%
-  pivot_wider(names_from = model,
-              values_from = c(AIC, cp_norm)) %>%
-  dplyr::select(-row)
-
-full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    AIC_2compartment < AIC_1compartment &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    AIC_flat < AIC_1compartment &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-
-                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
-                                                      is.na(AIC_flat) ~ "1-Compartment",
-                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_flat) ~ "2-Compartment",
-                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_2compartment) ~ "Null",
-
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_flat < AIC_1compartment ~ "Null",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
-
-full_data <- full_data %>%
-  mutate(cp_norm = case_when(model == "1-Compartment" ~ cp_norm_1compartment,
-                             model == "2-Compartment" ~ cp_norm_2compartment,
-                             model == "Null" ~ cp_norm_flat))
-
-### remove super outlier data from triclosan, for visualization purposes
-full_data <- full_data %>%
-  filter(cp_norm > 1e-10 & cp_norm < 1e8) # also high one for the heck of it
-
-length(unique(full_data$Compound[full_data$model == "1-Compartment"]))
-length(unique(full_data$Compound[full_data$model == "2-Compartment"]))
-length(unique(full_data$Compound[full_data$model == "Null"]))
-
-null_vec <- as.vector(unique(full_data$Compound[full_data$model == "Null"]))
-
-full_data <- as.data.table(full_data)
-
-full_data[, model := paste("Model:", model)]
-
-full_data[, chem_ref_spec_count := uniqueN(.SD), .SDcols = c("Compound", 
-                                                             "Reference",
-                                                             "Species.x"), 
-          by = "model"]
-
-full_data[, chem_ref_spec_count := paste("Chemical-Reference-Species:", chem_ref_spec_count)]
-
-# full_data <- full_data %>%
-#   mutate(cp_norm = case_when(model == "1comparment" ~ cp_norm_1compartment,
-#                              model == "2compartment" ~ cp_norm_2compartment))
-
-# full_data$cp_norm[full_data$model == "2compartment"] <- full_data$cp_norm_2compartment
-# full_data$cp_norm[full_data$model == "1compartment"] <- full_data$cp_norm_1compartment
-
-# full_data <- full_data %>%
-# mutate(across(everything(), ~ifelse(. == "", NA, as.character(.))))
-
-# filter(Compound != "triclosan")
-# filter(Compound != "tamoxifen")
-
-###########
-###########
-###########
-
-split_full_data <- split(full_data, full_data$model)
-
-full_data_1 <- split_full_data$`Model: 1-Compartment`
-
-### Find number of points in each plot panel for 1-compartment
-full_data_1_center <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_1_center <- full_data_1_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_1_center <- nrow(full_data_1_center) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-full_data_1_green <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_1_green <- full_data_1_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_1_green <- nrow(full_data_1_green) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-full_data_1_gray <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_1_gray <- full_data_1_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_1_gray <- nrow(full_data_1_gray) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-full_data_1_tan <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_1_tan <- full_data_1_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_1_tan <- nrow(full_data_1_tan) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-###########
-###########
-
-full_data_2 <- split_full_data$`Model: 2-Compartment`
-
-### Find number of points in each plot panel for 2-compartment
-full_data_2_center <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_2_center <- full_data_2_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_2_center <- nrow(full_data_2_center) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-full_data_2_green <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_2_green <- full_data_2_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-full_data_2_gray <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_2_gray <- full_data_2_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_2_gray <- nrow(full_data_2_gray) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-full_data_2_tan <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_2_tan <- full_data_2_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_2_tan <- nrow(full_data_2_tan) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-###########
-###########
-
-full_data_flat <- split_full_data$`Model: Null`
-
-### Find number of points in each plot panel for 2-compartment
-full_data_flat_center <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_flat_center <- full_data_flat_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_flat_center <- nrow(full_data_flat_center) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-full_data_flat_green <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_flat_green <- full_data_flat_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_flat_green <- nrow(full_data_flat_green) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-full_data_flat_gray <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_flat_gray <- full_data_flat_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_flat_gray <- nrow(full_data_flat_gray) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-full_data_flat_tan <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_flat_tan <- full_data_flat_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_flat_tan <- nrow(full_data_flat_tan) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-###########
-###########
-###########
-
-# rect_df1 <- data.frame(xmin = c(0, 0, 2, 2, 0, 2, 0.5, 0.5),
-#                       xmax = c(0.5, 0.5, Inf, Inf, 0.5, Inf, 2, 2),
-#                       ymin = c(2, 0, 0, 2, 0.5, 0.5, 2, 0),
-#                       ymax = c(Inf, 0.5, 0.5, Inf, 2, 2, Inf, 0.5),
-#                       panel_key = c(paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_1_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_1_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " ")))
-# 
-# rect_df2 <- data.frame(xmin = c(0, 0, 2, 2, 0, 2, 0.5, 0.5),
-#                       xmax = c(0.5, 0.5, Inf, Inf, 0.5, Inf, 2, 2),
-#                       ymin = c(2, 0, 0, 2, 0.5, 0.5, 2, 0),
-#                       ymax = c(Inf, 0.5, 0.5, Inf, 2, 2, Inf, 0.5),
-#                       panel_key = c(paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_2_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_2_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " ")))
-# 
-# 
-# rect_p1 <- ggplot() +
-#   geom_rect(data = rect_df1, aes(xmin = xmin,
-#                                 ymin = ymin,
-#                                 xmax = xmax,
-#                                 ymax = ymax,
-#                                 fill = panel_key),
-#             alpha = 0.3, inherit.aes = FALSE) +
-#   scale_fill_manual(name = "Panel Key",
-#                     values = c("#361D2E",
-#                                "#86A397",
-#                                "#E1B07E")) +
-#   theme_bw() +
-#   theme(panel.spacing = unit(2, "lines")) +
-#   geom_vline(xintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   geom_hline(yintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   scale_x_log10() +
-#   scale_y_log10() +
-#   labs(x = "Data Variability",
-#        y = "Model Error") +
-#   guides(fill = guide_legend(override.aes = list(size = 0.1)))
-# 
-# rect_p2 <- ggplot() +
-#   geom_rect(data = rect_df2, aes(xmin = xmin,
-#                                 ymin = ymin,
-#                                 xmax = xmax,
-#                                 ymax = ymax,
-#                                 fill = panel_key),
-#             alpha = 0.3, inherit.aes = FALSE) +
-#   scale_fill_manual(name = "Panel Key",
-#                     values = c("#361D2E",
-#                                "#86A397",
-#                                "#E1B07E")) +
-#   theme_bw() +
-#   theme(panel.spacing = unit(2, "lines")) +
-#   geom_vline(xintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   geom_hline(yintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   scale_x_log10() +
-#   scale_y_log10() +
-#   labs(x = "Data Variability",
-#        y = "Model Error") +
-#   guides(fill = guide_legend(override.aes = list(size = 0.1)))
-# 
-# ###################
-# fill_legend1 <- get_legend(rect_p1)
-# fill_legend2 <- get_legend(rect_p2)
-# ##################
-
-p <- ggplot(data = full_data,
-            mapping = aes(x = conc_norm, y = cp_norm)) +
-  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
-  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
-  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#E1B07E") +
-  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
-  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0.5, ymax = 2.0, alpha = 0.5, fill = "black") +
-  theme_bw() +
-  theme(panel.spacing = unit(2, "lines")) +
-  geom_bin2d(bins = 100) +
-  scale_fill_distiller(palette = "Blues") +
-  geom_vline(xintercept = c(0.5, 2),
-             linetype = "dashed") +
-  geom_hline(yintercept = c(0.5, 2),
-             linetype = "dashed") +
-  scale_x_log10(n.breaks = 4, labels = scientific) +
-  scale_y_log10() +
-  labs(x = "Data Variability",
-       y = "Model Performance") +
-  facet_wrap(. ~ model + chem_ref_spec_count) +
-  theme(strip.text.x = element_text(size = 7))
-
-p
-
-# ##################
-# 
-# data_p_final <- data_p +
-#   # inset_element(fill_legend1, 0.1, 1, 0.5, 1) +
-#   inset_element(fill_legend2, 0.6, 0.5, 0.7, 0.2, clip = TRUE)
-#  
-# data_p_final
-```
-
-```{r, make_sigma_distribution_histogram}
-
-# pk_data <- cp_df_03012022
-pk_data <- cp_df
-
-cvt_data <- cvt_variability_df
-
-##################
-##################
-
-row.names(pk_data) <- c()
-
-cvt_data <- dplyr::select(cvt_data, -c("kelim", 
-                                       "Vdist", 
-                                       "Fgutabs", 
-                                       "kgutabs"))
-
-### split pk_data by model so you can properly join with raw data
-model_split <- split(pk_data, pk_data$model)
-
-cvt_data$Reference <- as.character(cvt_data$Reference)
-
-cvt_data$type <- "1-Compartment"
-full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
-
-cvt_data$type <- "2-Compartment"
-full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
-
-cvt_data$type <- "Flat"
-full_data_flat <- left_join(cvt_data, model_split$`flat`)
-
-### put data back together
-full_data <- rbind(full_data_1, full_data_2, full_data_flat)
-
-full_data <- full_data %>%
-  filter(cp != 0)
-
-# full_data$AIC <- round(full_data$AIC, digits = 4)
-
-full_data <- full_data %>%
-  pivot_wider(names_from = model,
-              values_from = c(AIC, sigma_value)) %>%
-  unchop(everything())
-
-full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    AIC_2compartment < AIC_1compartment &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    AIC_flat < AIC_1compartment &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-
-                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
-                                                      is.na(AIC_flat) ~ "1-Compartment",
-                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_flat) ~ "2-Compartment",
-                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_2compartment) ~ "Null",
-
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_flat < AIC_1compartment ~ "Null",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
-
-full_data <- full_data %>%
-  mutate(AIC = case_when(model == "1-Compartment" ~ AIC_1compartment,
-                         model == "2-Compartment" ~ AIC_2compartment,
-                         model == "Null" ~ AIC_flat))
-
-full_data <- full_data %>%
-  mutate(sigma_value = case_when(model == "1-Compartment" ~ sigma_value_1compartment,
-                                 model == "2-Compartment" ~ sigma_value_2compartment,
-                                 model == "Null" ~ sigma_value_flat))
-
-full_data <- full_data %>%
-  distinct(Compound, 
-           Reference, 
-           Route, 
-           Species,
-           Media,
-           model, 
-           sigma_id,
-           sigma_value,
-           Value,
-           AIC)
-
-full_data <- as.data.table(full_data)
-
-full_data[, sigma_norm := sigma_value / nrow(.SD), by = .(Compound, 
-                                                          Reference,
-                                                          model,
-                                                          sigma_id,
-                                                          sigma_value)]
-
-full_data <- as.data.frame(full_data)
-
-full_data <- full_data %>% distinct(Compound,
-                                    Reference,
-                                    model,
-                                    AIC,
-                                    sigma_id,
-                                    sigma_value,
-                                    sigma_norm)
-
-full_data <- full_data %>%
-  group_by(Compound, Reference, sigma_id) %>%
-  slice_min(AIC)
-
-# ##################
-# ##################
-# 
-# data1 <- pk_output_1comp_03012022 %>%
-#   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
-# 
-# data2 <- pk_output_2comp_03012022 %>%
-#   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
-# 
-# ##################
-# ##################
-# 
-# ### assign new column, with either "1-Compartment" or "2-Compartment"
-# data1 <- subset(data1, select = sigma_value)
-# data1$model <- "1-Compartment"
-# 
-# data2 <- subset(data2, select = sigma_value)
-# data2$model <- "2-Compartment"
-# 
-# data <- rbind(data1, data2)
-
-p <- ggplot(data = full_data,
-            mapping = aes(x = sigma_norm)) +
-  geom_histogram(bins = 12) +
-  # geom_density() +
-  # scale_y_log10()+
-  scale_x_log10() +
-  theme_bw() +
-  labs(x = "Sigma",
-       y = "Number of observations") +
-  facet_wrap(.~ model)
-# geom_vline(xintercept = 0.001476315)
-# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))
-
-p
-```
-
-```{r make_magnitude_histogram}
-
-##################
-##################
-
-data <- raw_1comp
-
-##################
-##################
-
-data$X <- NULL
-
-split_df <- split(data, list(data$Compound,
-                             data$Reference,
-                             data$CAS,
-                             data$Dose,
-                             data$Species,
-                             data$Route,
-                             data$Media),
-                  drop = TRUE)
-
-### find number of orders of magnitude
-find_mag <- function(data) {
-
-  data$Value <- abs(data$Value)
-
-  diff <- log10(max(data$Value, na.rm = TRUE)) - log10(min(data$Value, na.rm = TRUE))
-
-  diff <- round(diff)
-
-  return(diff)
-
-}
-
-data <- lapply(split_df, find_mag)
-
-data <- pivot_longer(as.data.frame(data), cols = everything())
-
-p <- ggplot(data = data, mapping = aes(x = value)) +
-  geom_histogram(bins = 5, binwidth = 0.5) +
-  xlab("Orders of magnitude") + theme_bw()
-
-p
-```
-
-```{r make_joint_sigma_plot, eval = FALSE}
-
-##################
-##################
-
-data1 <- as.data.table(pk_output_1comp %>%
-                         filter(param.value.type == "Fitted geometric mean"))
-
-data2 <- as.data.table(pk_output_2comp %>%
-                         filter(param.value.type == "Fitted geometric mean"))
-
-##################
-##################
-
-### find data with repeated sigma_id values
-find_rep_sigma <- function(data) {
-
-  data <- data[ ave(1:nrow(data), data$sigma_id, FUN=length) > 1 , ]
-
-  if(nrow(data) == 0) {
-    return(NULL)
-  } else {
-
-    return(data)
-  }
-}
-
-split_list_1 <- split(data1, data1$Compound)
-rep_sigma_1 <- lapply(split_list_1, find_rep_sigma)
-data1 <- do.call(rbind, rep_sigma_1)
-data1 <- subset(data1, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
-data1$Data.Analyzed[data1$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
-data1 <- data1 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
-data1 <- data1 %>% filter(sigma_id != "sigma2.14")
-data1$`Joint Analysis` <- lapply(data1$`Joint Analysis`,as.numeric)
-data1$`Ind Analysis` <- lapply(data1$`Ind Analysis`,as.numeric)
-data1$model <- "1-Compartment"
-
-split_list_2 <- split(data2, data2$Compound)
-rep_sigma_2 <- lapply(split_list_2, find_rep_sigma)
-data2 <- do.call(rbind, rep_sigma_2)
-data2 <- subset(data2, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
-data2$Data.Analyzed[data2$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
-data2 <- data2 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
-data2 <- data2 %>% filter(sigma_id != "sigma2.14")
-data2$`Joint Analysis` <- lapply(data2$`Joint Analysis`,as.numeric)
-data2$`Ind Analysis` <- lapply(data2$`Ind Analysis`,as.numeric)
-data2$model <- "2-Compartment"
-
-data <- as.data.table(rbind(data1, data2))
-
-p <- ggplot(data, aes(x = `Ind Analysis`, y = `Joint Analysis`)) +
-  geom_point() +
-  scale_y_log10() +
-  scale_x_log10() +
-  geom_abline(slope = 1) +
-  facet_wrap(. ~ model)
-p
-```
-
-```{r, make_halflife_count_histogram}
-
-###########
-### one compartment
-###########
-
-##################
-##################
-
-raw_data1 <- raw_1comp
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp %>% 
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-pk_data1$X <- NULL
-
-raw_data1$Reference <- as.character(raw_data1$Reference)
-
-raw_data1 <- dplyr::select(raw_data1, -c("kelim",
-                                         "Vdist",
-                                         "Fgutabs",
-                                         "kgutabs"))
-
-# pk_data2 <- pk_output_2comp_12212021
-
-full_data_1 <- left_join(raw_data1, pk_data1, by = c("Compound", "CAS", "Reference"))
-
-full_data_1 <- full_data_1 %>% filter(AIC != Inf)
-
-find_halflife_count <- function(data) {
-
-  data_subset <- data %>% filter(!is.na(Value))
-
-  max_time <- max(unique(data_subset$Time))
-
-  data$halflife_count <- max_time/data$halflife
-
-  return(data)
-
-}
-
-split_full_data_1 <- split(full_data_1, list(full_data_1$Compound,
-                                             full_data_1$Reference,
-                                             full_data_1$CAS,
-                                             full_data_1$Dose,
-                                             full_data_1$Species.x,
-                                             full_data_1$Route,
-                                             full_data_1$Media),
-                           drop = TRUE)
-
-full_data_1_hl <- lapply(split_full_data_1, find_halflife_count)
-
-full_data_1_hl <- do.call(rbind, full_data_1_hl)
-
-full_data_1_hl <- full_data_1_hl %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species.x,
-           Route,
-           Media,
-           halflife_count)
-
-full_data_1_hl$model <- "1-Compartment"
-
-###########
-### two compartment
-###########
-
-##################
-##################
-
-raw_data2 <- raw_2comp
-
-pk_data2 <- pk_output_2comp %>% 
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-##################
-##################
-
-pk_data2$X <- NULL
-
-raw_data2$Reference <- as.character(raw_data2$Reference)
-
-raw_data2 <- dplyr::select(raw_data2, -c("kelim", 
-                                         "Vdist", 
-                                         "Fgutabs", 
-                                         "kgutabs",
-                                         "V1",
-                                         "Ralphatokelim",
-                                         "Fbetaofalpha"))
-
-# pk_data2 <- pk_output_2comp_12212021
-
-full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))
-
-full_data_2 <- full_data_2 %>% filter(AIC != Inf)
-
-find_halflife_count <- function(data) {
-
-  data_subset <- data %>% filter(!is.na(Value))
-
-  max_time <- max(unique(data_subset$Time))
-
-  data$halflife_count <- max_time/data$halflife
-
-  return(data)
-
-}
-
-split_full_data_2 <- split(full_data_2, list(full_data_2$Compound,
-                                             full_data_2$Reference,
-                                             full_data_2$CAS,
-                                             full_data_2$Dose,
-                                             full_data_2$Species.x,
-                                             full_data_2$Route,
-                                             full_data_2$Media),
-                           drop = TRUE)
-
-full_data_2_hl <- lapply(split_full_data_2, find_halflife_count)
-
-full_data_2_hl <- do.call(rbind, full_data_2_hl)
-
-full_data_2_hl <- full_data_2_hl %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species.x,
-           Route,
-           Media,
-           halflife_count)
-
-full_data_2_hl$model <- "2-Compartment"
-
-###########
-###########
-###########
-
-full_data_hl <- rbind(full_data_1_hl, full_data_2_hl)
-
-###########
-
-p <- ggplot(data = full_data_hl, mapping = aes(x = halflife_count)) +
-  geom_histogram() +
-  scale_x_log10() +
-  xlab("halflife count") + 
-  theme_bw() +
-  # geom_vline(xintercept = 330.7598,
-  #            color = "red",
-  #            linetype = "dashed") + 
-  facet_wrap(. ~ model)
-p
-```
-
-```{r, make_max_loq_histogram}
-
-###############
-###############
-
-raw_data1 <- raw_1comp
-
-###############
-###############
-
-find_normalized_max <- function(data) {
-
-  data$normalized_max <- max(data$Value, na.rm = TRUE)/data$LOQ
-
-  return(data)
-
-}
-
-split_df_1 <- split(raw_data1, list(raw_data1$Compound,
-                                    raw_data1$Reference,
-                                    raw_data1$CAS,
-                                    raw_data1$Dose,
-                                    raw_data1$Species,
-                                    raw_data1$Route,
-                                    raw_data1$Media),
-                    drop = TRUE)
-
-raw_data1_normalized_max <- lapply(split_df_1, find_normalized_max)
-
-raw_data1_normalized_max <- do.call(rbind, raw_data1_normalized_max)
-
-raw_data1_normalized_max <- raw_data1_normalized_max %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species,
-           Route,
-           Media,
-           normalized_max)
-
-p <- ggplot(data = raw_data1_normalized_max, mapping = aes(x = normalized_max)) +
-  geom_histogram(bins = 15) +
-  scale_x_log10() +
-  xlab("Max Concentration / LOQ") + 
-  theme_bw()
-# geom_vline(xintercept = 24.8482,
-#            color = "red",
-#            linetype = "dashed")
-p
-```
-
-```{r, make_mean_loq_histogram}
-
-###############
-###############
-
-raw_data1 <- raw_1comp
-
-###############
-###############
-
-find_normalized_mean <- function(data) {
-
-  data$normalized_mean <- mean(data$Value, na.rm = TRUE)/data$LOQ
-
-  return(data)
-
-}
-
-split_df_1 <- split(raw_data1, list(raw_data1$Compound,
-                                    raw_data1$Reference,
-                                    raw_data1$CAS,
-                                    raw_data1$Dose,
-                                    raw_data1$Species,
-                                    raw_data1$Route,
-                                    raw_data1$Media),
-                    drop = TRUE)
-
-raw_data1_normalized_mean <- lapply(split_df_1, find_normalized_mean)
-
-raw_data1_normalized_mean <- do.call(rbind, raw_data1_normalized_mean)
-
-raw_data1_normalized_mean <- raw_data1_normalized_mean %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species,
-           Route,
-           Media,
-           normalized_mean)
-
-p <- ggplot(data = raw_data1_normalized_mean, mapping = aes(x = normalized_mean)) +
-  geom_histogram(bins = 15) +
-  scale_x_log10() +
-  xlab("Mean Concentration / LOQ") + 
-  theme_bw()
-# geom_vline(xintercept = 24.8482,
-#            color = "red",
-#            linetype = "dashed")
-p
-```
-
-```{r, make_model_params_table, eval = FALSE}
-
-### this code almost entirely is imported from John's bake-off RMarkdown file
-### what this produces is a table of compounds that were fit by at least one of the models
-### AICs for both models are reported, and subsequent parameter values correspond to the model with the lower AIC
-
-###################
-###################
-
-pk_data1 <- pk_output_1comp
-# pk_data1 <- pk_output_1comp_12212021
-
-pk_data2 <- pk_output_2comp
-# pk_data2 <- pk_output_2comp_12212021
-
-###################
-###################
-
-pk_data1$sigma_id <- NULL
-pk_data1$sigma_value <- NULL
-pk_data2$sigma_id <- NULL
-pk_data2$sigma_value <- NULL
-
-pk_data1 <- distinct(pk_data1)
-pk_data2 <- distinct(pk_data2)
-
-fits1comp <- subset(pk_data1, is.finite(AIC) & AIC < 10^4)
-fits2comp <- subset(pk_data2, is.finite(AIC) & AIC < 10^4)
-
-#How many chemicals have 1 or 2 compartment fits:
-length(unique(c(fits1comp$CAS,fits2comp$CAS)))
-
-fittable <- NULL
-# test <- function(fits1comp, fits2comp) {
-for (this.cas in unique(c(fits1comp$CAS,fits2comp$CAS)))
-{ 
-  # print(this.cas)
-  # if (this.cas == "123-91-1") browser()
-  if (this.cas %in% fits1comp$CAS) this.compound <- fits1comp[
-    fits1comp$CAS==this.cas,"Compound"][1]
-  else this.compound <- fits2comp[
-    fits2comp$CAS==this.cas,"Compound"][1]
-
-  this.data.1comp <- subset(fits1comp,CAS==this.cas)
-  this.data.2comp <- subset(fits2comp,CAS==this.cas)
-
-  for (this.species in unique(tolower(c(
-    this.data.1comp$Species,
-    this.data.2comp$Species))))
-  {
-    Vdist.1comp <- NA
-    kelim.1comp <- NA
-    Vdist.2comp <- NA
-    kelim.2comp <- NA
-
-    this.data.1comp.species <- subset(this.data.1comp,tolower(Species)==this.species)
-    this.data.2comp.species <- subset(this.data.2comp,tolower(Species)==this.species)
-
-    this.row <- data.frame(
-      Compound=this.compound,
-      CAS=this.cas,
-      Species=this.species,
-      Reference=NA,
-      AIC.1comp=NA,
-      AIC.2comp=NA,
-      Model=NA,
-      Vdist=NA,
-      kelim=NA)
-
-    if (this.cas %in% fits1comp$CAS)
-    {
-      this.data.1comp.species <- subset(this.data.1comp.species,
-                                        param.value.type=="Fitted geometric mean")
-
-      # If more than one source, require that the joint analysis worked:
-      if (dim(this.data.1comp.species)[1]>1)
-      {
-        this.data.1comp.species<- subset(this.data.1comp.species, 
-                                         Data.Analyzed=="Joint Analysis")
-      }
-      if (dim(this.data.1comp.species)[1]>0) 
-      {
-        if (nrow(this.data.1comp.species) > 1) {
-          this.data.1comp.species <- this.data.1comp.species[1, ]
-        }
-
-        this.row$AIC.1comp <- this.data.1comp.species$AIC
-        Vdist.1comp <- this.data.1comp.species$Vdist
-        kelim.1comp <- this.data.1comp.species$kelim
-        this.row$Reference <- this.data.1comp.species$Reference
-      }
-    }
-
-    if (this.cas %in% fits2comp$CAS)
-    {
-      this.data.2comp.species <- subset(this.data.2comp.species,
-                                        param.value.type=="Fitted geometric mean")
-
-      # If more than one source, require that the joint analysis worked:
-      if (dim(this.data.2comp.species)[1]>1)
-      {
-        this.data.2comp.species <- subset(this.data.2comp.species, 
-                                          Data.Analyzed=="Joint Analysis")
-      }
-      if (dim(this.data.2comp.species)[1]>0) 
-      {
-        if(nrow(this.data.2comp.species) > 1 ) {
-          this.data.2comp.species <- this.data.2comp.species[1, ]
-        }
-        this.row$AIC.2comp <- this.data.2comp.species$AIC
-        Vdist.2comp <- this.data.2comp.species$Vss
-        kelim.2comp <- this.data.2comp.species$kelim
-        this.row$Reference <- this.data.2comp.species$Reference
-      }
-    }
-
-    if (!is.na(this.row$AIC.1comp))
-    {
-      if (!is.na(this.row$AIC.2comp))
-      {
-        if (this.row$AIC.1comp < this.row$AIC.2comp)
-        {
-          this.row$Model <- "1Comp"
-        } else this.row$Model <- "2Comp"
-      } else this.row$Model <- "1Comp"
-    } else if (!is.na(this.row$AIC.2comp))
-    {
-      this.row$Model <- "2Comp"
-    }
-
-    if (!is.na(this.row$Model))
-      if (this.row$Model == "1Comp")
-      {
-        this.row$Vdist <- Vdist.1comp
-        this.row$kelim <- kelim.1comp
-      } else 
-      {
-        this.row$Vdist <- Vdist.2comp
-        this.row$kelim <- kelim.2comp
-      }
-
-    fittable <- rbind(fittable,this.row)
-  }
-}
-
-# debug(test)
-# test(fits1comp, fits2comp)
-fittable$halflife <- log(2)/fittable$kelim
-
-#Lets only keep chemicals where we can fit a PK model:
-fittable <- subset(fittable, !is.na(Model))
-
-for (this.col in c("AIC.1comp","AIC.2comp","Vdist","kelim","halflife"))
-  fittable[,this.col] <- signif(as.numeric(fittable[,this.col]),4)
-
-# We have parameters estimated for 86 chemicals:
-dim(fittable)[1]
-
-### compounds fit better by flat model should be removed
-# if present in fittable
-### some are only fit by the flat model,
-# but some are fit just fit better by the flat model
-
-# these are
-# hexachlorobenzene -- nevermind, for the joint 1comp does best
-# phenolphthalein glucuronide
-# tamoxifen
-# 2,3,7,8-tetrachlorodibenzo-p-dioxin
-# imidacloprid", # well this one is only fit by the flat,
-# so isn't present anyway
-
-### when I take these out, 48 1 compartment best fits, 59 2 compartment, 107 total
-
-### I also manually checked all Joint Analysis compounds 
-# to make sure no joint flat models performed better
-# none did
-
-# write.csv(fittable, file = "inst/ext/model_params_table_04182022.csv", row.names = FALSE)
-
-```
-
-```{r, make_no_fit_table}
-
-##################
-##################
-
-pk_data1 <- as.data.table(pk_output_1comp)
-pk_data2 <- as.data.table(pk_output_2comp)
-
-##################
-##################
-
-pk_data1 <- pk_data1 %>%
-  filter(param.value.type == "Fitted geometric mean") %>%
-  dplyr::select(c("Compound", "CAS", "Reference", "AIC")) %>%
-  mutate(model = "1-Compartment")
-
-pk_data2 <- pk_data2 %>%
-  filter(param.value.type == "Fitted geometric mean") %>%
-  dplyr::select(c("Compound", "CAS", "Reference", "AIC")) %>%
-  mutate(model = "2-Compartment")
-
-pk_all <- rbind(pk_data1, pk_data2)
-
-### loop that says if a compound has any references that do not have AIC of Inf, it was a fit compound
-this.compound.list <- list()
-for (this.compound in unique(pk_all[, Compound])) {
-
-  this.compound.data <- pk_all[Compound == this.compound]
-  this.compound.data$AIC[is.na(this.compound.data$AIC)] <- Inf
-
-  if(any(this.compound.data$AIC != Inf)) {
-    this.compound.data$status <- "good fit"
-  } else {
-    this.compound.data$status <- "bad fit"
-  }
-
-  this.compound.list[[this.compound]] <- this.compound.data
-
-}
-
-pk_all <- do.call(rbind, this.compound.list)
-
-pk_all <- pk_all %>%
-  filter(status == "bad fit") %>% ### only want bad fit
-  mutate(status = NULL) %>% ### get rid of status column
-  group_by(Compound) %>%  
-  filter(n() == 2) %>% ### group_by compound and only keep compounds with two observations, aka neither model worked
-  mutate(model = NULL) %>% ### get rid of model column
-  distinct() ### discard repeated compound names
-
-# write.csv(pk_all, file = "inst/ext/no_fit_table_03012022.csv", row.names = FALSE)
-```
-
-```{r, compare_AIC}
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp
-
-pk_data2 <- pk_output_2comp
-
-pk_data_flat <- pk_output_flat %>%
-  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")
-
-##################
-##################
-
-### make both data.frames have the same column names so they are rbind-able
-pk_data1 <- pk_data1[, intersect(intersect(colnames(pk_data2), colnames(pk_data_flat)), colnames(pk_data1))]
-pk_data2 <- pk_data2[, intersect(intersect(colnames(pk_data1), colnames(pk_data_flat)), colnames(pk_data2))]
-pk_data_flat <- pk_data_flat[, intersect(intersect(colnames(pk_data1), colnames(pk_data2)), colnames(pk_data_flat))]
-
-pk_data1 <- pk_data1 %>%
-  rename(LogLikelihood_1 = LogLikelihood,
-         AIC_1 = AIC,
-         sigma_value_1 = sigma_value) %>%
-  mutate(model = NULL) %>%
-  mutate(model.type = NULL)
-
-pk_data2 <- pk_data2 %>%
-  rename(LogLikelihood_2 = LogLikelihood,
-         AIC_2 = AIC,
-         sigma_value_2 = sigma_value) %>%
-  mutate(model = NULL) %>%
-  mutate(model.type = NULL)
-
-pk_data_flat <- pk_data_flat %>%
-  rename(LogLikelihood_flat = LogLikelihood,
-         AIC_flat = AIC,
-         sigma_value_flat = sigma_value) %>%
-  mutate(model = NULL) %>%
-  mutate(model.type = NULL)
-
-pk_all <- left_join(pk_data1, pk_data2, by = c("CAS",
-                                               "Species",
-                                               "param.value.type",
-                                               "sigma_id",
-                                               "Reference",
-                                               "Data.Analyzed",
-                                               "Compound"))
-
-pk_all <- left_join(pk_all, pk_data_flat, by = c("CAS",
-                                                 "Species",
-                                                 "param.value.type",
-                                                 "sigma_id",
-                                                 "Reference",
-                                                 "Data.Analyzed",
-                                                 "Compound"))
-
-pk_all <- subset(pk_all, select = c(CAS, Species, Compound, Reference, AIC_1, AIC_2, AIC_flat))
-
-pk_all <- distinct(pk_all)
-
-pk_all$AIC_1[pk_all$AIC_1 == Inf] <- NA
-pk_all$AIC_2[pk_all$AIC_2 == Inf] <- NA
-pk_all$AIC_flat[pk_all$AIC_flat == Inf] <- NA
-
-pk_all <- pk_all %>%
-  mutate(flat_lowest = ifelse(AIC_flat < AIC_1 & AIC_flat < AIC_2, 1, 0)) %>%
-  mutate(flat_better_than_1 = ifelse(AIC_flat < AIC_1 & AIC_flat > AIC_2, 1, 0)) %>%
-  mutate(flat_better_than_2 = ifelse(AIC_flat > AIC_1 & AIC_flat < AIC_2, 1, 0))
-
-pk_just_bad <- pk_all %>%
-  filter(flat_lowest == 1 | flat_better_than_1 == 1 | flat_better_than_2 == 1)
-```
-
-```{r, lombardo_comparisons}
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp
-# pk_data1 <- pk_output_1comp_04282022
-
-# pk_data1$Vdist <- log(pk_data1$Vdist)
-
-pk_lombardo <- pk_lombardo
-
-##################
-##################
-
-pk_data1 <- pk_data1 %>%
-  filter(param.value.type == "Fitted geometric mean")
-         # , CAS != "50-49-7", CAS != "106266-06-2")
-# , Species == "human")
-
-pk_all <- left_join(all.fit.table, pk_lombardo, by = c("CAS" = "CAS #"))
-
-pk_all <- pk_all %>%
-  filter(!is.na(`human VDss (L/kg)`), 
-         !is.na(`human CL (mL/min/kg)`))
-
-pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000
-pk_all$CLtot <- pk_all$Vdist*pk_all$kelim
-pk_all$Vdist_norm <- abs(pk_all$Vdist / pk_all$`human VDss (L/kg)`)
-pk_all$CLtot_norm <- abs(pk_all$CLtot / pk_all$`human CL (L/hr/kg)`)
-pk_all$halflife_norm <- abs(pk_all$halflife / pk_all$`terminal  t1/2 (h)`)
-
-pk_all$mae <- rowMeans(pk_all[, c("Vdist_norm", "CLtot_norm", "halflife_norm")])
-
-### volume of distribution comparison
-p1 <- ggplot(pk_all, aes(x = Vdist, y = `human VDss (L/kg)`)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  geom_abline(slope = 1, intercept = 0)
-
-p1
-
-### half-life comparision
-p2 <- ggplot(pk_all, aes(x = halflife, y = `terminal  t1/2 (h)`)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  geom_abline(slope = 1, intercept = 0)
-
-p2
-
-### clearance comparison
-
-### convert to same units
-
-p3 <- ggplot(data = pk_all, mapping = aes(x = CLtot, y = `human CL (L/hr/kg)`)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  geom_abline(slope = 1, intercept = 0)
-
-p3
-
-```
-
-<!-- # ```{r, make_model_params_table, eval = FALSE} -->
-<!-- #  -->
-<!-- # ### this code almost entirely is imported from John's bake-off RMarkdown file -->
-<!-- # ### what this produces is a table of compounds that were fit by at least one of the models -->
-<!-- # ### AICs for both models are reported, and subsequent parameter values correspond to the model with the lower AIC -->
-<!-- #  -->
-<!-- # ################### -->
-<!-- # ################### -->
-<!-- #  -->
-<!-- # pk_data1 <- pk_output_1comp_04142022  -->
-<!-- # # pk_data1 <- pk_output_1comp_12212021  -->
-<!-- #  -->
-<!-- # pk_data2 <- pk_output_2comp_04142022  -->
-<!-- # # pk_data2 <- pk_output_2comp_12212021  -->
-<!-- #  -->
-<!-- # pk_data_flat <- pk_output_flat_04142022 -->
-<!-- #  -->
-<!-- # ################### -->
-<!-- # ################### -->
-<!-- #  -->
-<!-- # pk_data1$sigma_id <- NULL -->
-<!-- # pk_data1$sigma_value <- NULL -->
-<!-- # pk_data2$sigma_id <- NULL -->
-<!-- # pk_data2$sigma_value <- NULL -->
-<!-- # pk_data_flat$sigma_id <- NULL -->
-<!-- # pk_data_flat$sigma_value <- NULL -->
-<!-- #  -->
-<!-- # pk_data1 <- distinct(pk_data1) -->
-<!-- # pk_data2 <- distinct(pk_data2) -->
-<!-- # pk_data_flat <- distinct(pk_data_flat) -->
-<!-- #  -->
-<!-- # fits1comp <- subset(pk_data1, is.finite(AIC) & AIC < 10^4) -->
-<!-- # fits2comp <- subset(pk_data2, is.finite(AIC) & AIC < 10^4) -->
-<!-- # fitsflat <- subset(pk_data_flat, is.finite(AIC) & AIC < 10^4) -->
-<!-- #  -->
-<!-- # #How many chemicals have 1 or 2 compartment fits: -->
-<!-- # length(unique(c(fits1comp$CAS,fits2comp$CAS,fitsflat$CAS))) -->
-<!-- #  -->
-<!-- # fittable <- NULL -->
-<!-- # # test <- function(fits1comp, fits2comp, fitsflat) { -->
-<!-- #   for (this.cas in unique(c(fits1comp$CAS,fits2comp$CAS, fitsflat$CAS))) -->
-<!-- #   { print(this.cas) -->
-<!-- #     # if (this.cas == "96-47-9") browser() -->
-<!-- #     if (this.cas %in% fits1comp$CAS) this.compound <- fits1comp[ -->
-<!-- #       fits1comp$CAS==this.cas,"Compound"][1] -->
-<!-- #     else if (this.cas %in% fits2comp$CAS) this.compound <- fits2comp[ -->
-<!-- #       fits2comp$CAS==this.cas,"Compound"][1] -->
-<!-- #     else if (this.cas %in% fitsflat$CAS) this.compound <- fitsflat[ -->
-<!-- #       fitsflat$CAS==this.cas,"Compound"][1] -->
-<!-- #      -->
-<!-- #     this.data.1comp <- subset(fits1comp,CAS==this.cas) -->
-<!-- #     this.data.2comp <- subset(fits2comp,CAS==this.cas) -->
-<!-- #     this.data.flat <- subset(fitsflat,CAS==this.cas) -->
-<!-- #      -->
-<!-- #     for (this.species in unique(tolower(c( -->
-<!-- #       this.data.1comp$Species, -->
-<!-- #       this.data.2comp$Species, -->
-<!-- #       this.data.flat$Species)))) -->
-<!-- #     { -->
-<!-- #       Vdist.1comp <- NA -->
-<!-- #       kelim.1comp <- NA -->
-<!-- #       Vdist.2comp <- NA -->
-<!-- #       kelim.2comp <- NA -->
-<!-- #       A.flat <- NA -->
-<!-- #        -->
-<!-- #       this.data.1comp.species <- subset(this.data.1comp,tolower(Species)==this.species) -->
-<!-- #       this.data.2comp.species <- subset(this.data.2comp,tolower(Species)==this.species) -->
-<!-- #       this.data.flat.species <- subset(this.data.flat, tolower(Species)==this.species) -->
-<!-- #        -->
-<!-- #       this.row <- data.frame( -->
-<!-- #         Compound=this.compound, -->
-<!-- #         CAS=this.cas, -->
-<!-- #         Species=this.species, -->
-<!-- #         Reference=NA, -->
-<!-- #         AIC.1comp=NA, -->
-<!-- #         AIC.2comp=NA, -->
-<!-- #         Model=NA, -->
-<!-- #         Vdist=NA, -->
-<!-- #         kelim=NA) -->
-<!-- #        -->
-<!-- #       if (this.cas %in% fits1comp$CAS) -->
-<!-- #       { -->
-<!-- #         this.data.1comp.species <- subset(this.data.1comp.species, -->
-<!-- #                                           param.value.type=="Fitted geometric mean") -->
-<!-- #          -->
-<!-- #         # If more than one source, require that the joint analysis worked: -->
-<!-- #         if (dim(this.data.1comp.species)[1]>1) -->
-<!-- #         { -->
-<!-- #           this.data.1comp.species<- subset(this.data.1comp.species,  -->
-<!-- #                                            Data.Analyzed=="Joint Analysis") -->
-<!-- #         } -->
-<!-- #         if (dim(this.data.1comp.species)[1]>0)  -->
-<!-- #         { -->
-<!-- #           if (nrow(this.data.1comp.species) > 1) { -->
-<!-- #             this.data.1comp.species <- this.data.1comp.species[1, ] -->
-<!-- #           } -->
-<!-- #            -->
-<!-- #           this.row$AIC.1comp <- this.data.1comp.species$AIC -->
-<!-- #           Vdist.1comp <- this.data.1comp.species$Vdist -->
-<!-- #           kelim.1comp <- this.data.1comp.species$kelim -->
-<!-- #           this.row$Reference <- this.data.1comp.species$Reference -->
-<!-- #         } -->
-<!-- #       } -->
-<!-- #        -->
-<!-- #       if (this.cas %in% fits2comp$CAS) -->
-<!-- #       { -->
-<!-- #         this.data.2comp.species <- subset(this.data.2comp.species, -->
-<!-- #                                           param.value.type=="Fitted geometric mean") -->
-<!-- #          -->
-<!-- #         # If more than one source, require that the joint analysis worked: -->
-<!-- #         if (dim(this.data.2comp.species)[1]>1) -->
-<!-- #         { -->
-<!-- #           this.data.2comp.species <- subset(this.data.2comp.species,  -->
-<!-- #                                             Data.Analyzed=="Joint Analysis") -->
-<!-- #         } -->
-<!-- #         if (dim(this.data.2comp.species)[1]>0)  -->
-<!-- #         { -->
-<!-- #           if(nrow(this.data.2comp.species) > 1 ) { -->
-<!-- #             this.data.2comp.species <- this.data.2comp.species[1, ] -->
-<!-- #           } -->
-<!-- #           this.row$AIC.2comp <- this.data.2comp.species$AIC -->
-<!-- #           Vdist.2comp <- this.data.2comp.species$Vss -->
-<!-- #           kelim.2comp <- this.data.2comp.species$kelim -->
-<!-- #           this.row$Reference <- this.data.2comp.species$Reference -->
-<!-- #         } -->
-<!-- #       } -->
-<!-- #        -->
-<!-- #       if (this.cas %in% fitsflat$CAS) -->
-<!-- #       { -->
-<!-- #         this.data.flat.species <- subset(this.data.flat.species, -->
-<!-- #                                          param.value.type=="Fitted geometric mean") -->
-<!-- #          -->
-<!-- #         # If more than one source, require that the joint analysis worked: -->
-<!-- #         if (dim(this.data.flat.species)[1]>1) -->
-<!-- #         { -->
-<!-- #           this.data.flat.species <- subset(this.data.flat.species,  -->
-<!-- #                                            Data.Analyzed=="Joint Analysis") -->
-<!-- #         } -->
-<!-- #         if (dim(this.data.flat.species)[1]>0)  -->
-<!-- #         { -->
-<!-- #           if(nrow(this.data.flat.species) > 1 ) { -->
-<!-- #             this.data.flat.species <- this.data.flat.species[1, ] -->
-<!-- #           } -->
-<!-- #           this.row$AIC.flat <- this.data.flat.species$AIC -->
-<!-- #           A.flat <- this.data.flat.species$A -->
-<!-- #           this.row$Reference <- this.data.flat.species$Reference -->
-<!-- #         } -->
-<!-- #       } -->
-<!-- #       ######################## -->
-<!-- #       ######################### -->
-<!-- #        -->
-<!-- #       if(!"AIC.flat" %in% names(this.row)) this.row <- this.row %>%  -->
-<!-- #         add_column(AIC.flat = NA) -->
-<!-- #        -->
-<!-- #       if(!"AIC.1comp" %in% names(this.row)) this.row <- this.row %>%  -->
-<!-- #         add_column(AIC.1comp = NA) -->
-<!-- #        -->
-<!-- #       if(!"AIC.2comp" %in% names(this.row)) this.row <- this.row %>%  -->
-<!-- #         add_column(AIC.2comp = NA) -->
-<!-- #        -->
-<!-- #       this.row <- this.row %>% mutate(Model = case_when(AIC.1comp < AIC.2comp &  -->
-<!-- #                                                           AIC.1comp < AIC.flat ~ "1Comp", -->
-<!-- #                                                         AIC.2comp < AIC.1comp & -->
-<!-- #                                                           AIC.2comp < AIC.flat ~ "2Comp", -->
-<!-- #                                                         AIC.flat < AIC.1comp & -->
-<!-- #                                                           AIC.flat < AIC.2comp ~ "Null", -->
-<!-- #                                                          -->
-<!-- #                                                         !is.na(AIC.1comp) & is.na(AIC.2comp) & -->
-<!-- #                                                           is.na(AIC.flat) ~ "1Comp", -->
-<!-- #                                                         !is.na(AIC.2comp) & is.na(AIC.1comp) &  -->
-<!-- #                                                           is.na(AIC.flat) ~ "2Comp", -->
-<!-- #                                                         !is.na(AIC.flat) & is.na(AIC.1comp) &  -->
-<!-- #                                                           is.na(AIC.2comp) ~ "Null", -->
-<!-- #                                                          -->
-<!-- #                                                         is.na(AIC.1comp) & -->
-<!-- #                                                           AIC.flat < AIC.2comp ~ "Null", -->
-<!-- #                                                         is.na(AIC.1comp) & -->
-<!-- #                                                           AIC.2comp < AIC.flat ~ "2Comp", -->
-<!-- #                                                         is.na(AIC.2comp) & -->
-<!-- #                                                           AIC.flat < AIC.1comp ~ "Null", -->
-<!-- #                                                         is.na(AIC.2comp) & -->
-<!-- #                                                           AIC.1comp < AIC.flat ~ "1Comp", -->
-<!-- #                                                         is.na(AIC.flat) & -->
-<!-- #                                                           AIC.1comp < AIC.2comp ~"1Comp", -->
-<!-- #                                                         is.na(AIC.flat) & -->
-<!-- #                                                           AIC.2comp <AIC.1comp ~"2Comp")) -->
-<!-- #        -->
-<!-- #        -->
-<!-- #       fittable <- rbind(fittable,this.row) -->
-<!-- #     } -->
-<!-- #   } -->
-<!-- # # } -->
-<!-- # # debug(test) -->
-<!-- # # test(fits1comp, fits2comp, fitsflat) -->
-<!-- # fittable$halflife <- log(2)/fittable$kelim -->
-<!-- #  -->
-<!-- # #Lets only keep chemicals where we can fit a PK model: -->
-<!-- # fittable <- subset(fittable, !is.na(Model)) -->
-<!-- #  -->
-<!-- # # for (this.col in c("AIC.1comp","AIC.2comp","Vdist","kelim","halflife")) -->
-<!-- # #   fittable[,this.c=-] <- signif(as.numeric(fittable[,this.col]),4) -->
-<!-- #  -->
-<!-- # # We have parameters estimated for 86 chemicals: -->
-<!-- # dim(fittable)[1] -->
-<!-- #  -->
-<!-- # # write.csv(fittable, file = "inst/ext/model_params_table_04182022.csv", row.names = FALSE) -->
-<!-- #  -->
-<!-- # ``` -->

### 2023-01-04 Working Rmds/impute_missing_sds.Rmd
Split analyses for SD imputation and plotting into separate Rmd documents.

---
title: "Imputing missing SDs"
author: "Caroline Ring"
date: "2023-01-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(results = TRUE)
knitr::opts_chunk$set(message = FALSE)
```

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("../invivopkfit")
```

Read in CvTdb data.

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2022_12_15_16_20_21.csv")
```

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =list(
                       "Compound_Dosed" = "studies.test_substance_name_original",
                              "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
                              "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
                              "Compound_Analyzed" = "series.analyte_name_original",
                              "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
                              "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
                      "Reference" = "documents_reference.id",
                      "Extraction" = "documents_extraction.id",
                      "Species" = "subjects.species",
                      "Weight" ="subjects.weight_kg",
                      "Weight.Units" = NULL,
                      "Dose" = "correct.dose_level_normalized",
                      "Dose.Units" = NULL,
                      "Time" = "conc_time_values.time_hr",
                      "Time.Units" = NULL,
                      "Media" = "series.conc_medium_normalized",
                      "Value" = "conc_time_values.conc",
                      "Value.Units" = NULL,
                      "Route" = "studies.administration_route_normalized",
                      "LOQ" = "series.loq_normalized",
                      "Subject" = "subjects.id",
                              "N_Subjects" = "series.n_subjects_in_series",
                              "Value_SD" = "conc_time_values.conc_sd"),
                    defaults_list =   list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "h",
                      "Value.Units" = "mg/L"),
      ratio_conc_to_dose = 1,
                    calc_loq_factor = 0.45,
                    routes_keep = c("po", "iv"),
                    media_keep = c("blood", "plasma"),
      suppress.messages = FALSE)
```

There are many, many cases where N > 1 but no SD is reported. Can we impute these based on patterns in the cases where SD is reported? Calculate mean and SD for the individual cases:

```{r}
cvt <- as.data.table(cvt)
cvt_summarized <- cvt[N_Subjects==1,
                      .(meanval = mean(Value, na.rm = TRUE),
                        sdvals = sd(Value, na.rm = TRUE),
                        n = .N),
                      by = .(Reference, DTXSID, Media, Dose)]
ggplot(cvt_summarized) +
  geom_point(aes(x = meanval, y = sdvals, color = n)) +
  scale_x_log10() + scale_y_log10() + scale_color_viridis_c(trans = "log10")

summary(lm(log10(sdvals) ~ log10(meanval), data = cvt_summarized))
```

The relationship between sample SD and sample mean seems to be almost the identity line.

What about the multi-subject cases with reported SD?

```{r}
ggplot(cvt[N_Subjects > 1],
       aes(x = Value, y = Value_SD)) +
  geom_point(aes(x = Value, y = Value_SD, color = N_Subjects))  +
  scale_x_log10() + scale_y_log10() + geom_smooth(method = "lm")

summary(lm(log10(Value_SD) ~ log10(Value), data = cvt[N_Subjects > 1]))
```

This one isn't quite the identity line but still, we can get some idea.

These ones with entirely missing SDs are different from the studies where only a few SDs are missing. When only a few are missing, it was usually because the data were pulled from a plot where the error bars were smaller thant the plotting symbol on a few points. Instead of recording the size of the symbol as the error bars, the error was recorded as NA. But when all SDs are missing, it is usually because the study did not report the SDs in the first place.

In this case, it seems like a reasonable choice to impute the mean value itself as the SD. This relation seems to be borne out by the individual-anumal data, and it is more conservative than the relation suggested by the (limited) multi-animal data.

### 2023-01-04 Working Rmds/plot_fits.Rmd
Split analyses for SD imputation and plotting into separate Rmd documents.

--- 2022-12-09 MainAnalysis.Rmd
@@
 ---
-title: "<i>invivoPKfit</i> and <i>CvTdb</i> figures"
-author: "Christopher Cook, John Wambaugh, Caroline Ring"
-date: "11/15/2022"
-output:
-  html_document: default
-  word_document: default
+title: "Plot curve fits"
+author: "Caroline Ring"
+date: "2023-01-04"
+output: html_document
 ---
@@
 library(readxl)
-devtools::load_all("invivopkfit")
-# Clear memory:
-rm(list=ls())
-```
-
-Read in CvTdb data.
-
-```{r, load_cvt, eval = TRUE}
-cvt.data <- read.csv("inst/ext/cvtdb_invivopkfit_04262022-2.csv")
-```
-
-A couple of compounds had no CAS in CvTdb. Upon double checking, they should not have been added. So remove them. (CLR 2022-11-15: it doesn't look like there are any of these)
-
-```{r, cvt_remove_nocas}
-cvt.data <- cvt.data %>%
-  filter(analyte_name_original != "Methemoglobin") %>%
-  filter(analyte_name_original != "N-desmethyltamoxifen")
-```
-
-Fix a few compound names.
-```{r, cvt_fix_cpd_names}
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Methyleugonal "] <- "Methyleugonal"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "benzo[a]pyrene"] <- "benzo(a)pyrene"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "2,4-D"] <- "2,4-Dichlorophenoxyacetic acid"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Diclofenac"] <- "Hexobarbital"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "Pentadecafluorooctanoic acid"] <- "Perfluorooctanoic acid"
-cvt.data$analyte_name_original[cvt.data$analyte_name_original == "3−hydroxybenzo[a]pyrene"] <- "3−hydroxybenzo(a)pyrene"
-```
-
-if fk_reference_document is NULL, make fk_reference_document equal fk_extraction document. (CLR 2022-11-15: it doesn't look like there are any of these)
-
-```{r}
-cvt.data$fk_reference_document_id[cvt.data$fk_reference_document_id == "NULL"] <- 
-  cvt.data$fk_extraction_document_id[cvt.data$fk_reference_document_id == "NULL"]
-```
-
-```{r}
-### this is basically my debug line,
-# where I can focus on one problematic compound 
-# and see what's going wrong
-# data <- data %>% filter(dsstox_casrn == "68291-97-4" | dsstox_casrn == "82626-48-0")
-# data <- data %>% filter(dsstox_casrn == "123-91-1")
-```
-
-Calculate a limit of quantification (90% of lowest observation)
-
-```{r, calc_loq, eval = TRUE}
-cvt.data <- estimate_loq(cvt.data)
-```
-
-Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time in format YYYY_MM_DD_hh_mm_ss.
-
-Fit the 1-compartment model.
-
-```{r, run_invivoPKfit_1comp, eval = FALSE}
-
-run_timestamp_1comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
-
-### do 1-Compartment fit
-system.time(
-    PK.fit.table.1comp <- fit_all(
-      data.set = cvt.data,
-      model = "1compartment",
-      modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
-      suppress.messages = TRUE
-  )
-)
-
-write.csv(PK.fit.table.1comp,
-          paste("inst/ext/PK_fit_table_1comp_",
-                                    run_timestamp_1comp,
-                                    ".csv",
-                                    sep=""),
-          row.names = FALSE)
-
-```
-
-Fit the 2-compartment model.
-
-```{r, run_invivoPKfit_2comp, eval = FALSE}
-
-run_timestamp_2comp <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
-
-### do 2-Compartment fit
-system.time(
-    PK.fit.table.2comp <- fit_all(
-      data.set = cvt.data,
-      model = "2compartment",
-      modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
-      suppress.messages = TRUE
-    )
-)
-
-write.csv(PK.fit.table.2comp, paste("inst/ext/PK_fit_table_2comp_",
-                                    run_timestamp_2comp,
-                                    ".csv",
-                                    sep=""), row.names = FALSE)
-
-```
-
-Fit the flat model.
-
-```{r, run_invivoPKfit_flat, eval = FALSE}
-run_timestamp_flat <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
-
-system.time(
-    PK.fit.table.flat <- fit_all(
-      data.set = cvt.data,
-      model = "flat",
-      modelfun = "analytic",
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
-      suppress.messages = TRUE
-    )
-)
-
-write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
-                                    run_timestamp_flat,
-                                    ".csv",
-                                    sep=""), row.names = FALSE)
+devtools::load_all("../invivopkfit")
 ```
@@
 ```{r}
-DF <- preprocess_data(data.set = cvt.data,
-                       ratio.data.to.dose = 1,
-      compound.col = "analyte_name_original",
-      dtxsid.col = "dsstox_substance_id",
-      cas.col = "dsstox_casrn",
-      reference.col = "fk_reference_document_id",
-      species.col = "species",
-      species.weight.col = "weight_kg",
-      species.weight.units.default = "kg",
-      dose.col = "dose_level_normalized",
-      time.col = "time_hr",
-      time.units.default = "hr",
-      media.col = "conc_medium_normalized",
-      media.units.default = "normalized",
-      value.col = "conc",
-      units.default = NA,
-      route.col = "administration_route_normalized",
-      source.col = "document_id",
-      loq.col ="calc_loq",
-      subject.default = NA,
-      info.default = NA,
+cvt <- preprocess_data(data.set = cvt_data,
+                       names_list =list(
+                       "Compound_Dosed" = "studies.test_substance_name_original",
+                              "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+                              "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+                              "Compound_Analyzed" = "series.analyte_name_original",
+                              "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+                              "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+                      "Reference" = "documents_reference.id",
+                      "Extraction" = "documents_extraction.id",
+                      "Species" = "subjects.species",
+                      "Weight" ="subjects.weight_kg",
+                      "Weight.Units" = NULL,
+                      "Dose" = "correct.dose_level_normalized",
+                      "Dose.Units" = NULL,
+                      "Time" = "conc_time_values.time_hr",
+                      "Time.Units" = NULL,
+                      "Media" = "series.conc_medium_normalized",
+                      "Value" = "conc_time_values.conc",
+                      "Value.Units" = NULL,
+                      "Route" = "studies.administration_route_normalized",
+                      "LOQ" = "series.loq_normalized",
+                      "Subject" = "subjects.id",
+                              "N_Subjects" = "series.n_subjects_in_series",
+                              "Value_SD" = "conc_time_values.conc_sd"),
+                    defaults_list =   list(
+                      "Weight.Units" = "kg",
+                      "Dose.Units" = "mg/kg",
+                      "Time.Units" = "h",
+                      "Value.Units" = "mg/L"),
+      ratio_conc_to_dose = 1,
+                    calc_loq_factor = 0.45,
+                    routes_keep = c("po", "iv"),
+                    media_keep = c("blood", "plasma"),
       suppress.messages = FALSE)
@@
 ```
-
-```{r, merge_pkfits, eval=FALSE}
-all.fit.table <- merge_model_fits(list("1compartment"=pk_output_1comp,
-                                       "2compartment"=pk_output_2comp,
-                                       "flat"=pk_output_flat))
-write.csv(all.fit.table, paste("inst/ext/all.fit.table.",THIS.DATE,".csv",sep=""), row.names = FALSE)
-```
-
-```{r, make_rdata, eval = FALSE}
-
-### this block takes the csv files in read_data
-# and saves them as Rdata files
-
-### save data
-paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".RData",sep="")
-save(pk_output_1comp, file = paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
-save(pk_output_2comp, file = paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
-save(pk_output_flat, file = paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
-save(raw_1comp, file = paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
-save(raw_2comp, file = paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
-save(raw_flat, file = paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
-save(all.fit.table, file = paste("figures_rdata/all_fit_table_",THIS.DATE,".RData",sep=""))
-save(pk_lombardo, file = paste("figures_rdata/pk_lombardo",THIS.DATE,".RData",sep=""))
-```
-
-```{r, make_invivoPKfit_plots, eval = TRUE}
-
-### this block produces the pdf files of the model fits
-# plotted on top of the original data
-
-### 1 compartment
-
-# pk_output_1comp_03012022 <- pk_output_1comp_03012022 %>%
-#   filter(Compound == "tamoxifen") %>%
-#   filter(Data.Analyzed != "Joint Analysis")
-
-# raw_1comp_03012022 <- raw_1comp_03012022 %>%
-#   filter(Compound == "tamoxifen")
-
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_1comp),
-                      data.set = as.data.table(raw_1comp),
-                      model = "1compartment")
-
-### 2 compartment
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp),
-                      data.set = as.data.table(raw_2comp),
-                      model = "2compartment")
-
-junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_flat),
-                      data.set = as.data.table(raw_flat),
-                      model = "flat")
-
-```
-
-```{r, make_cp_rdata, eval = FALSE}
-
-### this block creates a data.frame of predicted concentrations
-# using the estimated parameters and the observed conc-time points
-
-######################
-
-###########
-### this is 1-compartment data
-###########
-
-###################
-###################
-
-### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data1 <- pk_output_1comp %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
-  filter(Species != "hamster")
-
-raw_data1 <- dplyr::select(raw_1comp, -c("kelim", 
-                                                  "Vdist", 
-                                                  "Fgutabs", 
-                                                  "kgutabs")) %>% 
-  filter(Species != "hamster")
-
-###################
-###################
-
-raw_data1$Reference <- as.character(raw_data1$Reference)
-
-full_data_1 <- left_join(raw_data1, pk_data1, by = c("Compound", "CAS", "Reference"))
-full_data_1 <- full_data_1 %>% filter(AIC != Inf)
-
-### function that finds cp
-find_cp_1 <- function(full_data_1) {plyr::adply(full_data_1, 1, mutate, cp = cp_1comp(time = Time,
-                                                                                      params = full_data_1[1, ],
-                                                                                      dose = Dose,
-                                                                                      iv.dose = iv))}
-
-### have to split data frame into ones with unique parameter values because cp_1comp takes constants
-split_df_1 <- split(full_data_1, list(full_data_1$Compound,
-                                      full_data_1$Reference,
-                                      full_data_1$CAS,
-                                      full_data_1$Species.x),
-                    drop = TRUE)
-
-cp_df_1 <- lapply(split_df_1, find_cp_1)
-
-cp_df_1 <- do.call(rbind, cp_df_1)
-
-### nomralize cp by Value
-cp_df_1$cp_norm <- cp_df_1$cp / cp_df_1$Value
-cp_df_1$type <- "1-Compartment"
-
-###########
-### this is 2-compartment data
-###########
-
-#######################
-#######################
-
-### subset to only actual model outputs and discard "Joint Analysis" rows
-pk_data2 <- pk_output_2comp %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-raw_data2 <- dplyr::select(raw_2comp, -c("kelim", 
-                                                  "Vdist", 
-                                                  "Fgutabs", 
-                                                  "kgutabs",
-                                                  "V1",
-                                                  "Ralphatokelim",
-                                                  "Fbetaofalpha"))
-
-########################
-########################
-
-raw_data2$Reference <- as.character(raw_data2$Reference)
-
-full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))
-full_data_2 <- full_data_2 %>% filter(AIC != Inf)
-split_df_2 <- split(full_data_2, list(full_data_2$Compound,
-                                      full_data_2$Reference,
-                                      full_data_2$CAS,
-                                      full_data_2$Species.x),
-                    drop = TRUE)
-
-### function that finds cp
-find_cp_2 <- function(full_data_2) {plyr::adply(full_data_2, 1, mutate, cp = cp_2comp(time = Time,
-                                                                                      params = full_data_2[1, ],
-                                                                                      dose = Dose,
-                                                                                      iv.dose = iv))}
-cp_df_2 <- lapply(split_df_2, find_cp_2)
-
-cp_df_2 <- do.call(rbind, cp_df_2)
-
-cp_df_2$cp_norm <- cp_df_2$cp / cp_df_2$Value
-cp_df_2$type <- "2-Compartment"
-
-# cp_df_2 <- cp_df_2 %>%
-#   filter(cp != 1e-20)
-
-###########
-### this is flat data
-###########
-
-pk_data_flat <- pk_output_flat %>%
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis") %>% 
-  filter(Species != "hamster")
-
-raw_data_flat <- dplyr::select(raw_flat, -c("A")) %>% 
-  filter(Species != "hamster")
-
-raw_data_flat$Reference <- as.character(raw_data_flat$Reference)
-
-full_data_flat <- left_join(raw_data_flat, pk_data_flat, by = c("Compound", "CAS", "Reference"))
-full_data_flat <- full_data_flat %>% filter(AIC != Inf)
-split_df_flat <- split(full_data_flat, list(full_data_flat$Compound,
-                                            full_data_flat$Reference,
-                                            full_data_flat$CAS,
-                                            full_data_flat$Species.x),
-                       drop = TRUE)
-
-### function that finds cp
-find_cp_flat <- function(full_data_flat) {plyr::adply(full_data_flat, 1, mutate, cp = cp_flat(time = Time,
-                                                                                              params = full_data_flat[1, ],
-                                                                                              dose = Dose,
-                                                                                              iv.dose = iv))}
-cp_df_flat <- lapply(split_df_flat, find_cp_flat)
-
-cp_df_flat <- do.call(rbind, cp_df_flat)
-
-cp_df_flat$cp_norm <- cp_df_flat$cp / cp_df_flat$Value
-cp_df_flat$type <- "Flat"
-
-#######################
-#######################
-
-### make all data.frames have the same column names so they are rbind-able
-cp_df_1 <- cp_df_1[, intersect(colnames(cp_df_2), colnames(cp_df_1))]
-cp_df_2 <- cp_df_2[, intersect(colnames(cp_df_1), colnames(cp_df_2))]
-
-cp_df <- rbind(cp_df_1, cp_df_2)
-
-cp_df <- cp_df[, intersect(colnames(cp_df_flat), colnames(cp_df))]
-cp_df_flat <- cp_df_flat[, intersect(colnames(cp_df), colnames(cp_df))]
-
-cp_df <- rbind(cp_df, cp_df_flat)
-
-cp_df$cp_pred_error <- (cp_df$cp - cp_df$Value) / cp_df$Value
-
-cp_df <- cp_df %>% group_by(Species.x, 
-                           Compound,
-                           CAS,
-                           type) %>%
- mutate(cp_pred_error_range = max(cp_pred_error, na.rm = TRUE) - min(cp_pred_error, na.rm = TRUE))
-
-### here is where you save the Rdata file
-save(cp_df, file = paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
-```
-
-```{r, make_cvt_variability_rdata, eval = FALSE}
-
-### this block creates a data.frame that shows the 
-# spread of CvT data via across replicate timepoints 
-# for a single experiment
-# if the data isn't within 2-fold of itself
-# is it reasonable to say that a model should fit within 2-fold?
-
-##################
-##################
-
-### all the raw data for each model SHOULD be the same
-# so only need to use one
-data <- as.data.table(raw_1comp)
-
-##################
-##################
-
-### function that finds mean conc of each replicate timepoint
-find_mean_conc <- function(data) {
-
-  ### only use data with replicate timepoints
-  data <- data[ ave(1:nrow(data), data$Time, FUN = length) > 1 , ]
-
-  if(nrow(data) == 0) {
-    return(NULL)
-  } else {
-
-    time_split <- split(data, data$Time)
-
-    ### discard replicate timepoints where all concentrations are NA
-    time_split_list <- purrr::discard(time_split, ~all(is.na(.$Value)))
-
-    if(length(time_split_list) == 0) {
-      return(NULL)
-    } else {
-
-      data <- do.call(rbind, time_split_list)
-
-      ### where some replicate concentration data are NA, set them equal to the LOQ
-      data$Value[is.na(data$Value)] <- data$LOQ[is.na(data$Value)]
-
-      ### take the average Value for each set of timepoints
-      data <- data %>%
-        group_by(Time) %>%
-        do(mutate(., mean_conc = mean(.$Value, na.rm = TRUE)))
-
-      data <- data %>%
-        group_by(Time) %>%
-        do(mutate(., range_conc = max(.$Value) - min(.$Value)))
-
-      ### create normalized conc values by dividing conc by mean_conc
-      data$conc_norm <- data$Value/data$mean_conc
-
-      data <- data[order(data$Time), ]
-
-      return(data)
-    }
-  }
-}
-
-### this for loop applies the function 
-# at data subsets of compound, data, dose, route, media
-data.list <- list()
-for(this.compound in unique(data[, Compound])) {
-  this.compound.data <- data[Compound == this.compound]
-
-  ### list of columns by which to split data.set
-  col_list <- list(this.compound.data$Reference,
-                   this.compound.data$Dose,
-                   this.compound.data$Route,
-                   this.compound.data$Media)
-
-  ### split data.set into list of data.tables
-  split_list <- split(this.compound.data, col_list)
-
-  ### remove data.tables with 0 rows
-  split_list <- keep(split_list, ~nrow(.) > 0)
-
-  ### use find_mean_conc fn
-  mean_conc <- lapply(split_list, find_mean_conc)
-
-  test <- do.call(rbind, mean_conc)
-
-  data.list[[this.compound]] <- test
-}
-
-### combine data.tables back into one large data.set
-cvt_variability_df <- do.call(rbind, data.list)
-
-### SAVE the data
-save(cvt_variability_df, file = paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))
-```
-
-```{r, load_data}
-
-### this block loads the Rdata files,
-# as well as some other files written in below code blocks
-# this saves time from having to run those below code blocks every time
-# these additional files include 'cp_df' and 'cvt_variability'
-
-### load all of this wonderful data
-load(paste("figures_rdata/pk_output_1comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/pk_output_2comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/pk_output_flat_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/raw_1comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/raw_2comp_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/raw_flat_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
-load(paste("figures_rdata/cvt_variability_df_",THIS.DATE,".RData",sep=""))
-
-load(paste("figures_rdata/cp_df_",THIS.DATE,".RData",sep=""))
-
-load("figures_rdata/pk_lombardo_02072022.Rdata")
-```
-
-```{r, make_cp_histogram}
-
-### this block makes a histogram of the data output
-# from make_cp_rdata
-# there's a separate facet for each model type
-# only data that were best fitted by that model
-# are shown in that facet
-
-##################
-##################
-
-pk_data <- cp_df
-
-# cvt_data <- cvt_variability_df_04282022
-
-##################
-##################
-
-row.names(pk_data) <- c()
-full_data <- pk_data
-
-# cvt_data <- dplyr::select(cvt_data, -c("kelim",
-#                                        "Vdist",
-#                                        "Fgutabs",
-#                                        "kgutabs"))
-# 
-# ### split pk_data by model so you can properly join with raw data
-# model_split <- split(pk_data, pk_data$model)
-# 
-# cvt_data$Reference <- as.character(cvt_data$Reference)
-# 
-# cvt_data$type <- "1-Compartment"
-# full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
-# 
-# cvt_data$type <- "2-Compartment"
-# full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
-# 
-# cvt_data$type <- "Flat"
-# full_data_flat <- left_join(cvt_data, model_split$`flat`)
-# 
-# ### put data back together
-# full_data <- rbind(full_data_1, full_data_2, full_data_flat)
-# 
-# full_data <- full_data %>%
-#   filter(cp != 0)
-
-full_data$AIC <- round(full_data$AIC, digits = 4)
-
-### only take necessary columns to keep things clean
-full_data <- full_data %>%
-  distinct(Compound, Reference, Species.x, model, AIC, cp_norm)
-
-### this pivots the data so we have AICs and cp_norms
-# for each model row-wise
-full_data <- full_data %>%
-  group_by(Species.x, Compound, Reference, model) %>%
-  mutate(row = row_number()) %>%
-  pivot_wider(names_from = model,
-              values_from = c(AIC, cp_norm)) %>%
-  dplyr::select(-row)
-
-full_data <- as.data.table(full_data)
-
-### make model column equal a specific model based on AIC values
-full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    AIC_2compartment < AIC_1compartment &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    AIC_flat < AIC_1compartment &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-
-                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
-                                                      is.na(AIC_flat) ~ "1-Compartment",
-                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) &
-                                                      is.na(AIC_flat) ~ "2-Compartment",
-                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) &
-                                                      is.na(AIC_2compartment) ~ "Null",
-
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_flat < AIC_1compartment ~ "Null",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
-
-### make cp_norm equal to the cp_norm that corresponds to the best fitting model
-full_data <- full_data %>%
-  mutate(cp_norm = case_when(model == "1-Compartment" ~ cp_norm_1compartment,
-                             model == "2-Compartment" ~ cp_norm_2compartment,
-                             model == "Null" ~ cp_norm_flat))
-
-full_data[, model := paste("Model:", model)]
-
-### this creates a new column that says how many unique sets of Compound, Reference,
-# and Species correspond to each model
-full_data[, chem_ref_spec_count := uniqueN(.SD), .SDcols = c("Compound", 
-                                                             "Reference",
-                                                             "Species.x"), 
-          by = "model"]
-
-full_data[, chem_ref_spec_count := paste("Chemical-Reference-Species:", chem_ref_spec_count)]
-
-### make plot, facet by model and chem_ref_spec_count
-p <- ggplot(data = full_data,
-            mapping = aes(x = cp_norm)) +
-  geom_histogram(binwidth = 0.325) +
-  geom_vline(xintercept = c(0.5, 2),
-             color = "Red",
-             linetype = "dashed") +
-  # xlim(0, 1e42) +
-  # ylim(0, 400) +
-  # scale_y_log10()+
-  theme(title = element_text(size = 16),
-        axis.text = element_text(size = 12),
-        axis.title = element_text(size = 14)) +
-  # scale_x_log10() +
-  scale_x_log10(limits = c(1e-3, 1e3), labels = scientific) +
-  scale_y_continuous(labels = scientific) +
-  theme_bw() +
-  labs(x = "Predicted/Observed",
-       y = "Number of Observations") +
-  facet_wrap(. ~ model + chem_ref_spec_count)
-
-p
-```
-
-```{r, make_cp_error_histogram}
-
-### I think this is little outdated but whatever I'm gonna keep it here
-# Think is was just plotting Cpred - Cobs
-
-##################
-##################
-
-# data <- cp_df_12212021
-# data <- cp_df_03012022
-data <- cp_df
-
-##################
-##################
-
-data <- data %>%
-  filter(cp != 1e-20)
-
-data <- data %>%
-  distinct(Species.x, Compound, CAS, cp_pred_error_range)
-
-p <- ggplot(data = data,
-            mapping = aes(x = cp_pred_error_range)) +
-  geom_histogram() +
-  scale_x_log10() +
-  facet_wrap(. ~type)
-
-p
-```
-
-```{r, make_cp_error_versus_dose}
-
-### I think this is little outdated but whatever I'm gonna keep it here
-
-##################
-##################
-
-data <- cp_df
-
-##################
-##################
-
-data <- data %>%
-  filter(type == "1-Compartment")
-
-data <- data %>%
-  group_by(Compound, CAS, Dose) %>%
-  mutate(average = mean(cp_pred_error))
-
-p <- ggplot(data = data, mapping = aes(x = Dose, y = average)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10()
-
-p
-
-```
-
-```{r, make_cvt_variability_histogram}
-
-### this block makes the histogram
-# of cvt variability using the data.frame
-# made from make_cvt_variability_rdata
-
-#################
-#################
-
-data <- cvt_variability_df
-# data <- cvt_variability_df_12212021
-
-#################
-#################
-
-p <- ggplot(data, aes(x = conc_norm)) +
-  geom_histogram(binwidth = 0.25) +
-  xlim(c(-0.5, 4)) +
-  geom_vline(xintercept = c(0.5, 2),
-             color = "Red",
-             linetype = "dashed") +
-  theme_bw() +
-  labs(x = "Normalized concentration",
-       y = "Number of observations")
-p
-```
-
-```{r, make_density_plot}
-
-### this block makes a density plot with cvt variabity
-# and normalized predicted concentrations
-# it's basically a combination of the other two histograms
-# expect here we limit cp observations those that have replicate timepoint
-# data, so it matches the cvt variability data, thus making it 
-# comparable
-
-##################
-##################
-
-# pk_data <- cp_df_03012022
-pk_data <- cp_df
-
-cvt_data <- cvt_variability_df
-
-##################
-##################
-
-### i hate row names
-row.names(pk_data) <- c()
-
-### making these null so I don't have to deal
-# with duplicate .x and .y's
-# only need the ones from pk_data
-cvt_data <- dplyr::select(cvt_data, -c("kelim", 
-                                       "Vdist", 
-                                       "Fgutabs", 
-                                       "kgutabs"))
-
-### split pk_data by model so you can properly join with raw data
-model_split <- split(pk_data, pk_data$model)
-
-### References were of different classes for some reason
-# so had to change
-cvt_data$Reference <- as.character(cvt_data$Reference)
-
-cvt_data$type <- "1-Compartment"
-full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
-
-cvt_data$type <- "2-Compartment"
-full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
-
-cvt_data$type <- "Flat"
-full_data_flat <- left_join(cvt_data, model_split$`flat`)
-
-### put data back together
-full_data <- rbind(full_data_1, full_data_2, full_data_flat)
-
-### not sure why there were 0s,
-# but they were screwing things up
-full_data <- full_data %>%
-  filter(cp != 0)
-
-full_data$AIC <- round(full_data$AIC, digits = 4)
-
-full_data <- full_data %>%
-  distinct(Compound, Reference, model, Species.x, conc_norm, AIC, cp_norm)
-
-### 
-### 
-full_data <- full_data %>%
-  group_by(Species.x, Compound, Reference, model) %>%
-  mutate(row = row_number()) %>%
-  pivot_wider(names_from = model,
-              values_from = c(AIC, cp_norm)) %>%
-  dplyr::select(-row)
-
-full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    AIC_2compartment < AIC_1compartment &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    AIC_flat < AIC_1compartment &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-
-                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
-                                                      is.na(AIC_flat) ~ "1-Compartment",
-                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_flat) ~ "2-Compartment",
-                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_2compartment) ~ "Null",
-
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_flat < AIC_1compartment ~ "Null",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
-
-full_data <- full_data %>%
-  mutate(cp_norm = case_when(model == "1-Compartment" ~ cp_norm_1compartment,
-                             model == "2-Compartment" ~ cp_norm_2compartment,
-                             model == "Null" ~ cp_norm_flat))
-
-### remove super outlier data from triclosan, for visualization purposes
-full_data <- full_data %>%
-  filter(cp_norm > 1e-10 & cp_norm < 1e8) # also high one for the heck of it
-
-length(unique(full_data$Compound[full_data$model == "1-Compartment"]))
-length(unique(full_data$Compound[full_data$model == "2-Compartment"]))
-length(unique(full_data$Compound[full_data$model == "Null"]))
-
-null_vec <- as.vector(unique(full_data$Compound[full_data$model == "Null"]))
-
-full_data <- as.data.table(full_data)
-
-full_data[, model := paste("Model:", model)]
-
-full_data[, chem_ref_spec_count := uniqueN(.SD), .SDcols = c("Compound", 
-                                                             "Reference",
-                                                             "Species.x"), 
-          by = "model"]
-
-full_data[, chem_ref_spec_count := paste("Chemical-Reference-Species:", chem_ref_spec_count)]
-
-# full_data <- full_data %>%
-#   mutate(cp_norm = case_when(model == "1comparment" ~ cp_norm_1compartment,
-#                              model == "2compartment" ~ cp_norm_2compartment))
-
-# full_data$cp_norm[full_data$model == "2compartment"] <- full_data$cp_norm_2compartment
-# full_data$cp_norm[full_data$model == "1compartment"] <- full_data$cp_norm_1compartment
-
-# full_data <- full_data %>%
-# mutate(across(everything(), ~ifelse(. == "", NA, as.character(.))))
-
-# filter(Compound != "triclosan")
-# filter(Compound != "tamoxifen")
-
-###########
-###########
-###########
-
-split_full_data <- split(full_data, full_data$model)
-
-full_data_1 <- split_full_data$`Model: 1-Compartment`
-
-### Find number of points in each plot panel for 1-compartment
-full_data_1_center <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_1_center <- full_data_1_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_1_center <- nrow(full_data_1_center) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-full_data_1_green <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_1_green <- full_data_1_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_1_green <- nrow(full_data_1_green) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-full_data_1_gray <- full_data_1 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_1_gray <- full_data_1_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_1_gray <- nrow(full_data_1_gray) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-full_data_1_tan <- full_data_1 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_1_tan <- full_data_1_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_1_tan <- nrow(full_data_1_tan) / nrow(full_data_1 %>% filter(!is.na(cp_norm)))
-
-###########
-###########
-
-full_data_2 <- split_full_data$`Model: 2-Compartment`
-
-### Find number of points in each plot panel for 2-compartment
-full_data_2_center <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_2_center <- full_data_2_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_2_center <- nrow(full_data_2_center) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-full_data_2_green <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_2_green <- full_data_2_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_2_green <- nrow(full_data_2_green) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-full_data_2_gray <- full_data_2 %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_2_gray <- full_data_2_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_2_gray <- nrow(full_data_2_gray) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-full_data_2_tan <- full_data_2 %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_2_tan <- full_data_2_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_2_tan <- nrow(full_data_2_tan) / nrow(full_data_2 %>% filter(!is.na(cp_norm)))
-
-###########
-###########
-
-full_data_flat <- split_full_data$`Model: Null`
-
-### Find number of points in each plot panel for 2-compartment
-full_data_flat_center <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_flat_center <- full_data_flat_center %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_flat_center <- nrow(full_data_flat_center) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-full_data_flat_green <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_flat_green <- full_data_flat_green %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_flat_green <- nrow(full_data_flat_green) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-full_data_flat_gray <- full_data_flat %>% filter(conc_norm < 0.5 | conc_norm > 2)
-full_data_flat_gray <- full_data_flat_gray %>% filter(cp_norm >= 0.5 & cp_norm <= 2)
-ratio_flat_gray <- nrow(full_data_flat_gray) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-full_data_flat_tan <- full_data_flat %>% filter(conc_norm >= 0.5 & conc_norm <= 2)
-full_data_flat_tan <- full_data_flat_tan %>% filter(cp_norm < 0.5 | cp_norm > 2)
-ratio_flat_tan <- nrow(full_data_flat_tan) / nrow(full_data_flat %>% filter(!is.na(cp_norm)))
-
-###########
-###########
-###########
-
-# rect_df1 <- data.frame(xmin = c(0, 0, 2, 2, 0, 2, 0.5, 0.5),
-#                       xmax = c(0.5, 0.5, Inf, Inf, 0.5, Inf, 2, 2),
-#                       ymin = c(2, 0, 0, 2, 0.5, 0.5, 2, 0),
-#                       ymax = c(Inf, 0.5, 0.5, Inf, 2, 2, Inf, 0.5),
-#                       panel_key = c(paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_1_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_1_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_1_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " ")))
-# 
-# rect_df2 <- data.frame(xmin = c(0, 0, 2, 2, 0, 2, 0.5, 0.5),
-#                       xmax = c(0.5, 0.5, Inf, Inf, 0.5, Inf, 2, 2),
-#                       ymin = c(2, 0, 0, 2, 0.5, 0.5, 2, 0),
-#                       ymax = c(Inf, 0.5, 0.5, Inf, 2, 2, Inf, 0.5),
-#                       panel_key = c(paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Poor Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_green, digits = 1), "%", ")", sep = ""),
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                     paste("Good Fit, Outlier Data", 
-#                                           paste("(", round(100 * ratio_2_tan, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_2_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " "),
-#                                    paste("Poor Fit, Typical Data", 
-#                                           paste("(", round(100 * ratio_2_gray, digits = 1), "%", ")", sep = ""), 
-#                                           sep = " ")))
-# 
-# 
-# rect_p1 <- ggplot() +
-#   geom_rect(data = rect_df1, aes(xmin = xmin,
-#                                 ymin = ymin,
-#                                 xmax = xmax,
-#                                 ymax = ymax,
-#                                 fill = panel_key),
-#             alpha = 0.3, inherit.aes = FALSE) +
-#   scale_fill_manual(name = "Panel Key",
-#                     values = c("#361D2E",
-#                                "#86A397",
-#                                "#E1B07E")) +
-#   theme_bw() +
-#   theme(panel.spacing = unit(2, "lines")) +
-#   geom_vline(xintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   geom_hline(yintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   scale_x_log10() +
-#   scale_y_log10() +
-#   labs(x = "Data Variability",
-#        y = "Model Error") +
-#   guides(fill = guide_legend(override.aes = list(size = 0.1)))
-# 
-# rect_p2 <- ggplot() +
-#   geom_rect(data = rect_df2, aes(xmin = xmin,
-#                                 ymin = ymin,
-#                                 xmax = xmax,
-#                                 ymax = ymax,
-#                                 fill = panel_key),
-#             alpha = 0.3, inherit.aes = FALSE) +
-#   scale_fill_manual(name = "Panel Key",
-#                     values = c("#361D2E",
-#                                "#86A397",
-#                                "#E1B07E")) +
-#   theme_bw() +
-#   theme(panel.spacing = unit(2, "lines")) +
-#   geom_vline(xintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   geom_hline(yintercept = c(0.5, 2),
-#              linetype = "dashed") +
-#   scale_x_log10() +
-#   scale_y_log10() +
-#   labs(x = "Data Variability",
-#        y = "Model Error") +
-#   guides(fill = guide_legend(override.aes = list(size = 0.1)))
-# 
-# ###################
-# fill_legend1 <- get_legend(rect_p1)
-# fill_legend2 <- get_legend(rect_p2)
-# ##################
-
-p <- ggplot(data = full_data,
-            mapping = aes(x = conc_norm, y = cp_norm)) +
-  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#86A397") +
-  annotate(geom = "rect", xmin = 0, xmax = 0.5, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
-  annotate(geom = "rect", xmin = 2, xmax = Inf, ymin = 0.5, ymax = 2, alpha = 0.3, fill = "#361D2E") +
-  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 2, ymax = Inf, alpha = 0.3, fill = "#E1B07E") +
-  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0, ymax = 0.5, alpha = 0.3, fill = "#E1B07E") +
-  annotate(geom = "rect", xmin = 0.5, xmax = 2, ymin = 0.5, ymax = 2.0, alpha = 0.5, fill = "black") +
-  theme_bw() +
-  theme(panel.spacing = unit(2, "lines")) +
-  geom_bin2d(bins = 100) +
-  scale_fill_distiller(palette = "Blues") +
-  geom_vline(xintercept = c(0.5, 2),
-             linetype = "dashed") +
-  geom_hline(yintercept = c(0.5, 2),
-             linetype = "dashed") +
-  scale_x_log10(n.breaks = 4, labels = scientific) +
-  scale_y_log10() +
-  labs(x = "Data Variability",
-       y = "Model Performance") +
-  facet_wrap(. ~ model + chem_ref_spec_count) +
-  theme(strip.text.x = element_text(size = 7))
-
-p
-
-# ##################
-# 
-# data_p_final <- data_p +
-#   # inset_element(fill_legend1, 0.1, 1, 0.5, 1) +
-#   inset_element(fill_legend2, 0.6, 0.5, 0.7, 0.2, clip = TRUE)
-#  
-# data_p_final
-```
-
-```{r, make_sigma_distribution_histogram}
-
-# pk_data <- cp_df_03012022
-pk_data <- cp_df
-
-cvt_data <- cvt_variability_df
-
-##################
-##################
-
-row.names(pk_data) <- c()
-
-cvt_data <- dplyr::select(cvt_data, -c("kelim", 
-                                       "Vdist", 
-                                       "Fgutabs", 
-                                       "kgutabs"))
-
-### split pk_data by model so you can properly join with raw data
-model_split <- split(pk_data, pk_data$model)
-
-cvt_data$Reference <- as.character(cvt_data$Reference)
-
-cvt_data$type <- "1-Compartment"
-full_data_1 <- left_join(cvt_data, model_split$`1compartment`)
-
-cvt_data$type <- "2-Compartment"
-full_data_2 <- left_join(cvt_data, model_split$`2compartment`)
-
-cvt_data$type <- "Flat"
-full_data_flat <- left_join(cvt_data, model_split$`flat`)
-
-### put data back together
-full_data <- rbind(full_data_1, full_data_2, full_data_flat)
-
-full_data <- full_data %>%
-  filter(cp != 0)
-
-# full_data$AIC <- round(full_data$AIC, digits = 4)
-
-full_data <- full_data %>%
-  pivot_wider(names_from = model,
-              values_from = c(AIC, sigma_value)) %>%
-  unchop(everything())
-
-full_data <- full_data %>% mutate(model = case_when(AIC_1compartment < AIC_2compartment & 
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    AIC_2compartment < AIC_1compartment &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    AIC_flat < AIC_1compartment &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-
-                                                    !is.na(AIC_1compartment) & is.na(AIC_2compartment) &
-                                                      is.na(AIC_flat) ~ "1-Compartment",
-                                                    !is.na(AIC_2compartment) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_flat) ~ "2-Compartment",
-                                                    !is.na(AIC_flat) & is.na(AIC_1compartment) & 
-                                                      is.na(AIC_2compartment) ~ "Null",
-
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_flat < AIC_2compartment ~ "Null",
-                                                    is.na(AIC_1compartment) &
-                                                      AIC_2compartment < AIC_flat ~ "2-Compartment",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_flat < AIC_1compartment ~ "Null",
-                                                    is.na(AIC_2compartment) &
-                                                      AIC_1compartment < AIC_flat ~ "1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_1compartment < AIC_2compartment ~"1-Compartment",
-                                                    is.na(AIC_flat) &
-                                                      AIC_2compartment <AIC_1compartment ~"2-Compartment"))
-
-full_data <- full_data %>%
-  mutate(AIC = case_when(model == "1-Compartment" ~ AIC_1compartment,
-                         model == "2-Compartment" ~ AIC_2compartment,
-                         model == "Null" ~ AIC_flat))
-
-full_data <- full_data %>%
-  mutate(sigma_value = case_when(model == "1-Compartment" ~ sigma_value_1compartment,
-                                 model == "2-Compartment" ~ sigma_value_2compartment,
-                                 model == "Null" ~ sigma_value_flat))
-
-full_data <- full_data %>%
-  distinct(Compound, 
-           Reference, 
-           Route, 
-           Species,
-           Media,
-           model, 
-           sigma_id,
-           sigma_value,
-           Value,
-           AIC)
-
-full_data <- as.data.table(full_data)
-
-full_data[, sigma_norm := sigma_value / nrow(.SD), by = .(Compound, 
-                                                          Reference,
-                                                          model,
-                                                          sigma_id,
-                                                          sigma_value)]
-
-full_data <- as.data.frame(full_data)
-
-full_data <- full_data %>% distinct(Compound,
-                                    Reference,
-                                    model,
-                                    AIC,
-                                    sigma_id,
-                                    sigma_value,
-                                    sigma_norm)
-
-full_data <- full_data %>%
-  group_by(Compound, Reference, sigma_id) %>%
-  slice_min(AIC)
-
-# ##################
-# ##################
-# 
-# data1 <- pk_output_1comp_03012022 %>%
-#   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
-# 
-# data2 <- pk_output_2comp_03012022 %>%
-#   filter(param.value.type == "Fitted geometric mean" & AIC != Inf & Data.Analyzed != "Joint Analysis")
-# 
-# ##################
-# ##################
-# 
-# ### assign new column, with either "1-Compartment" or "2-Compartment"
-# data1 <- subset(data1, select = sigma_value)
-# data1$model <- "1-Compartment"
-# 
-# data2 <- subset(data2, select = sigma_value)
-# data2$model <- "2-Compartment"
-# 
-# data <- rbind(data1, data2)
-
-p <- ggplot(data = full_data,
-            mapping = aes(x = sigma_norm)) +
-  geom_histogram(bins = 12) +
-  # geom_density() +
-  # scale_y_log10()+
-  scale_x_log10() +
-  theme_bw() +
-  labs(x = "Sigma",
-       y = "Number of observations") +
-  facet_wrap(.~ model)
-# geom_vline(xintercept = 0.001476315)
-# stat_function(fun = dlnorm, args = list(mean = mean(log(data$sigma_value)), sd = sd(log(data$sigma_value))))
-
-p
-```
-
-```{r make_magnitude_histogram}
-
-##################
-##################
-
-data <- raw_1comp
-
-##################
-##################
-
-data$X <- NULL
-
-split_df <- split(data, list(data$Compound,
-                             data$Reference,
-                             data$CAS,
-                             data$Dose,
-                             data$Species,
-                             data$Route,
-                             data$Media),
-                  drop = TRUE)
-
-### find number of orders of magnitude
-find_mag <- function(data) {
-
-  data$Value <- abs(data$Value)
-
-  diff <- log10(max(data$Value, na.rm = TRUE)) - log10(min(data$Value, na.rm = TRUE))
-
-  diff <- round(diff)
-
-  return(diff)
-
-}
-
-data <- lapply(split_df, find_mag)
-
-data <- pivot_longer(as.data.frame(data), cols = everything())
-
-p <- ggplot(data = data, mapping = aes(x = value)) +
-  geom_histogram(bins = 5, binwidth = 0.5) +
-  xlab("Orders of magnitude") + theme_bw()
-
-p
-```
-
-```{r make_joint_sigma_plot, eval = FALSE}
-
-##################
-##################
-
-data1 <- as.data.table(pk_output_1comp %>%
-                         filter(param.value.type == "Fitted geometric mean"))
-
-data2 <- as.data.table(pk_output_2comp %>%
-                         filter(param.value.type == "Fitted geometric mean"))
-
-##################
-##################
-
-### find data with repeated sigma_id values
-find_rep_sigma <- function(data) {
-
-  data <- data[ ave(1:nrow(data), data$sigma_id, FUN=length) > 1 , ]
-
-  if(nrow(data) == 0) {
-    return(NULL)
-  } else {
-
-    return(data)
-  }
-}
-
-split_list_1 <- split(data1, data1$Compound)
-rep_sigma_1 <- lapply(split_list_1, find_rep_sigma)
-data1 <- do.call(rbind, rep_sigma_1)
-data1 <- subset(data1, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
-data1$Data.Analyzed[data1$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
-data1 <- data1 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
-data1 <- data1 %>% filter(sigma_id != "sigma2.14")
-data1$`Joint Analysis` <- lapply(data1$`Joint Analysis`,as.numeric)
-data1$`Ind Analysis` <- lapply(data1$`Ind Analysis`,as.numeric)
-data1$model <- "1-Compartment"
-
-split_list_2 <- split(data2, data2$Compound)
-rep_sigma_2 <- lapply(split_list_2, find_rep_sigma)
-data2 <- do.call(rbind, rep_sigma_2)
-data2 <- subset(data2, select = c(param.value.type, sigma_id, sigma_value, Data.Analyzed, Compound))
-data2$Data.Analyzed[data2$Data.Analyzed != "Joint Analysis"] <- "Ind Analysis"
-data2 <- data2 %>% pivot_wider(names_from = Data.Analyzed, values_from = sigma_value)
-data2 <- data2 %>% filter(sigma_id != "sigma2.14")
-data2$`Joint Analysis` <- lapply(data2$`Joint Analysis`,as.numeric)
-data2$`Ind Analysis` <- lapply(data2$`Ind Analysis`,as.numeric)
-data2$model <- "2-Compartment"
-
-data <- as.data.table(rbind(data1, data2))
-
-p <- ggplot(data, aes(x = `Ind Analysis`, y = `Joint Analysis`)) +
-  geom_point() +
-  scale_y_log10() +
-  scale_x_log10() +
-  geom_abline(slope = 1) +
-  facet_wrap(. ~ model)
-p
-```
-
-```{r, make_halflife_count_histogram}
-
-###########
-### one compartment
-###########
-
-##################
-##################
-
-raw_data1 <- raw_1comp
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp %>% 
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-pk_data1$X <- NULL
-
-raw_data1$Reference <- as.character(raw_data1$Reference)
-
-raw_data1 <- dplyr::select(raw_data1, -c("kelim",
-                                         "Vdist",
-                                         "Fgutabs",
-                                         "kgutabs"))
-
-# pk_data2 <- pk_output_2comp_12212021
-
-full_data_1 <- left_join(raw_data1, pk_data1, by = c("Compound", "CAS", "Reference"))
-
-full_data_1 <- full_data_1 %>% filter(AIC != Inf)
-
-find_halflife_count <- function(data) {
-
-  data_subset <- data %>% filter(!is.na(Value))
-
-  max_time <- max(unique(data_subset$Time))
-
-  data$halflife_count <- max_time/data$halflife
-
-  return(data)
-
-}
-
-split_full_data_1 <- split(full_data_1, list(full_data_1$Compound,
-                                             full_data_1$Reference,
-                                             full_data_1$CAS,
-                                             full_data_1$Dose,
-                                             full_data_1$Species.x,
-                                             full_data_1$Route,
-                                             full_data_1$Media),
-                           drop = TRUE)
-
-full_data_1_hl <- lapply(split_full_data_1, find_halflife_count)
-
-full_data_1_hl <- do.call(rbind, full_data_1_hl)
-
-full_data_1_hl <- full_data_1_hl %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species.x,
-           Route,
-           Media,
-           halflife_count)
-
-full_data_1_hl$model <- "1-Compartment"
-
-###########
-### two compartment
-###########
-
-##################
-##################
-
-raw_data2 <- raw_2comp
-
-pk_data2 <- pk_output_2comp %>% 
-  filter(param.value.type == "Fitted geometric mean" & Data.Analyzed != "Joint Analysis")
-
-##################
-##################
-
-pk_data2$X <- NULL
-
-raw_data2$Reference <- as.character(raw_data2$Reference)
-
-raw_data2 <- dplyr::select(raw_data2, -c("kelim", 
-                                         "Vdist", 
-                                         "Fgutabs", 
-                                         "kgutabs",
-                                         "V1",
-                                         "Ralphatokelim",
-                                         "Fbetaofalpha"))
-
-# pk_data2 <- pk_output_2comp_12212021
-
-full_data_2 <- left_join(raw_data2, pk_data2, by = c("Compound", "CAS", "Reference"))
-
-full_data_2 <- full_data_2 %>% filter(AIC != Inf)
-
-find_halflife_count <- function(data) {
-
-  data_subset <- data %>% filter(!is.na(Value))
-
-  max_time <- max(unique(data_subset$Time))
-
-  data$halflife_count <- max_time/data$halflife
-
-  return(data)
-
-}
-
-split_full_data_2 <- split(full_data_2, list(full_data_2$Compound,
-                                             full_data_2$Reference,
-                                             full_data_2$CAS,
-                                             full_data_2$Dose,
-                                             full_data_2$Species.x,
-                                             full_data_2$Route,
-                                             full_data_2$Media),
-                           drop = TRUE)
-
-full_data_2_hl <- lapply(split_full_data_2, find_halflife_count)
-
-full_data_2_hl <- do.call(rbind, full_data_2_hl)
-
-full_data_2_hl <- full_data_2_hl %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species.x,
-           Route,
-           Media,
-           halflife_count)
-
-full_data_2_hl$model <- "2-Compartment"
-
-###########
-###########
-###########
-
-full_data_hl <- rbind(full_data_1_hl, full_data_2_hl)
-
-###########
-
-p <- ggplot(data = full_data_hl, mapping = aes(x = halflife_count)) +
-  geom_histogram() +
-  scale_x_log10() +
-  xlab("halflife count") + 
-  theme_bw() +
-  # geom_vline(xintercept = 330.7598,
-  #            color = "red",
-  #            linetype = "dashed") + 
-  facet_wrap(. ~ model)
-p
-```
-
-```{r, make_max_loq_histogram}
-
-###############
-###############
-
-raw_data1 <- raw_1comp
-
-###############
-###############
-
-find_normalized_max <- function(data) {
-
-  data$normalized_max <- max(data$Value, na.rm = TRUE)/data$LOQ
-
-  return(data)
-
-}
-
-split_df_1 <- split(raw_data1, list(raw_data1$Compound,
-                                    raw_data1$Reference,
-                                    raw_data1$CAS,
-                                    raw_data1$Dose,
-                                    raw_data1$Species,
-                                    raw_data1$Route,
-                                    raw_data1$Media),
-                    drop = TRUE)
-
-raw_data1_normalized_max <- lapply(split_df_1, find_normalized_max)
-
-raw_data1_normalized_max <- do.call(rbind, raw_data1_normalized_max)
-
-raw_data1_normalized_max <- raw_data1_normalized_max %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species,
-           Route,
-           Media,
-           normalized_max)
-
-p <- ggplot(data = raw_data1_normalized_max, mapping = aes(x = normalized_max)) +
-  geom_histogram(bins = 15) +
-  scale_x_log10() +
-  xlab("Max Concentration / LOQ") + 
-  theme_bw()
-# geom_vline(xintercept = 24.8482,
-#            color = "red",
-#            linetype = "dashed")
-p
-```
-
-```{r, make_mean_loq_histogram}
-
-###############
-###############
-
-raw_data1 <- raw_1comp
-
-###############
-###############
-
-find_normalized_mean <- function(data) {
-
-  data$normalized_mean <- mean(data$Value, na.rm = TRUE)/data$LOQ
-
-  return(data)
-
-}
-
-split_df_1 <- split(raw_data1, list(raw_data1$Compound,
-                                    raw_data1$Reference,
-                                    raw_data1$CAS,
-                                    raw_data1$Dose,
-                                    raw_data1$Species,
-                                    raw_data1$Route,
-                                    raw_data1$Media),
-                    drop = TRUE)
-
-raw_data1_normalized_mean <- lapply(split_df_1, find_normalized_mean)
-
-raw_data1_normalized_mean <- do.call(rbind, raw_data1_normalized_mean)
-
-raw_data1_normalized_mean <- raw_data1_normalized_mean %>%
-  distinct(Compound,
-           Reference,
-           CAS,
-           Dose,
-           Species,
-           Route,
-           Media,
-           normalized_mean)
-
-p <- ggplot(data = raw_data1_normalized_mean, mapping = aes(x = normalized_mean)) +
-  geom_histogram(bins = 15) +
-  scale_x_log10() +
-  xlab("Mean Concentration / LOQ") + 
-  theme_bw()
-# geom_vline(xintercept = 24.8482,
-#            color = "red",
-#            linetype = "dashed")
-p
-```
-
-```{r, make_model_params_table, eval = FALSE}
-
-### this code almost entirely is imported from John's bake-off RMarkdown file
-### what this produces is a table of compounds that were fit by at least one of the models
-### AICs for both models are reported, and subsequent parameter values correspond to the model with the lower AIC
-
-###################
-###################
-
-pk_data1 <- pk_output_1comp
-# pk_data1 <- pk_output_1comp_12212021
-
-pk_data2 <- pk_output_2comp
-# pk_data2 <- pk_output_2comp_12212021
-
-###################
-###################
-
-pk_data1$sigma_id <- NULL
-pk_data1$sigma_value <- NULL
-pk_data2$sigma_id <- NULL
-pk_data2$sigma_value <- NULL
-
-pk_data1 <- distinct(pk_data1)
-pk_data2 <- distinct(pk_data2)
-
-fits1comp <- subset(pk_data1, is.finite(AIC) & AIC < 10^4)
-fits2comp <- subset(pk_data2, is.finite(AIC) & AIC < 10^4)
-
-#How many chemicals have 1 or 2 compartment fits:
-length(unique(c(fits1comp$CAS,fits2comp$CAS)))
-
-fittable <- NULL
-# test <- function(fits1comp, fits2comp) {
-for (this.cas in unique(c(fits1comp$CAS,fits2comp$CAS)))
-{ 
-  # print(this.cas)
-  # if (this.cas == "123-91-1") browser()
-  if (this.cas %in% fits1comp$CAS) this.compound <- fits1comp[
-    fits1comp$CAS==this.cas,"Compound"][1]
-  else this.compound <- fits2comp[
-    fits2comp$CAS==this.cas,"Compound"][1]
-
-  this.data.1comp <- subset(fits1comp,CAS==this.cas)
-  this.data.2comp <- subset(fits2comp,CAS==this.cas)
-
-  for (this.species in unique(tolower(c(
-    this.data.1comp$Species,
-    this.data.2comp$Species))))
-  {
-    Vdist.1comp <- NA
-    kelim.1comp <- NA
-    Vdist.2comp <- NA
-    kelim.2comp <- NA
-
-    this.data.1comp.species <- subset(this.data.1comp,tolower(Species)==this.species)
-    this.data.2comp.species <- subset(this.data.2comp,tolower(Species)==this.species)
-
-    this.row <- data.frame(
-      Compound=this.compound,
-      CAS=this.cas,
-      Species=this.species,
-      Reference=NA,
-      AIC.1comp=NA,
-      AIC.2comp=NA,
-      Model=NA,
-      Vdist=NA,
-      kelim=NA)
-
-    if (this.cas %in% fits1comp$CAS)
-    {
-      this.data.1comp.species <- subset(this.data.1comp.species,
-                                        param.value.type=="Fitted geometric mean")
-
-      # If more than one source, require that the joint analysis worked:
-      if (dim(this.data.1comp.species)[1]>1)
-      {
-        this.data.1comp.species<- subset(this.data.1comp.species, 
-                                         Data.Analyzed=="Joint Analysis")
-      }
-      if (dim(this.data.1comp.species)[1]>0) 
-      {
-        if (nrow(this.data.1comp.species) > 1) {
-          this.data.1comp.species <- this.data.1comp.species[1, ]
-        }
-
-        this.row$AIC.1comp <- this.data.1comp.species$AIC
-        Vdist.1comp <- this.data.1comp.species$Vdist
-        kelim.1comp <- this.data.1comp.species$kelim
-        this.row$Reference <- this.data.1comp.species$Reference
-      }
-    }
-
-    if (this.cas %in% fits2comp$CAS)
-    {
-      this.data.2comp.species <- subset(this.data.2comp.species,
-                                        param.value.type=="Fitted geometric mean")
-
-      # If more than one source, require that the joint analysis worked:
-      if (dim(this.data.2comp.species)[1]>1)
-      {
-        this.data.2comp.species <- subset(this.data.2comp.species, 
-                                          Data.Analyzed=="Joint Analysis")
-      }
-      if (dim(this.data.2comp.species)[1]>0) 
-      {
-        if(nrow(this.data.2comp.species) > 1 ) {
-          this.data.2comp.species <- this.data.2comp.species[1, ]
-        }
-        this.row$AIC.2comp <- this.data.2comp.species$AIC
-        Vdist.2comp <- this.data.2comp.species$Vss
-        kelim.2comp <- this.data.2comp.species$kelim
-        this.row$Reference <- this.data.2comp.species$Reference
-      }
-    }
-
-    if (!is.na(this.row$AIC.1comp))
-    {
-      if (!is.na(this.row$AIC.2comp))
-      {
-        if (this.row$AIC.1comp < this.row$AIC.2comp)
-        {
-          this.row$Model <- "1Comp"
-        } else this.row$Model <- "2Comp"
-      } else this.row$Model <- "1Comp"
-    } else if (!is.na(this.row$AIC.2comp))
-    {
-      this.row$Model <- "2Comp"
-    }
-
-    if (!is.na(this.row$Model))
-      if (this.row$Model == "1Comp")
-      {
-        this.row$Vdist <- Vdist.1comp
-        this.row$kelim <- kelim.1comp
-      } else 
-      {
-        this.row$Vdist <- Vdist.2comp
-        this.row$kelim <- kelim.2comp
-      }
-
-    fittable <- rbind(fittable,this.row)
-  }
-}
-
-# debug(test)
-# test(fits1comp, fits2comp)
-fittable$halflife <- log(2)/fittable$kelim
-
-#Lets only keep chemicals where we can fit a PK model:
-fittable <- subset(fittable, !is.na(Model))
-
-for (this.col in c("AIC.1comp","AIC.2comp","Vdist","kelim","halflife"))
-  fittable[,this.col] <- signif(as.numeric(fittable[,this.col]),4)
-
-# We have parameters estimated for 86 chemicals:
-dim(fittable)[1]
-
-### compounds fit better by flat model should be removed
-# if present in fittable
-### some are only fit by the flat model,
-# but some are fit just fit better by the flat model
-
-# these are
-# hexachlorobenzene -- nevermind, for the joint 1comp does best
-# phenolphthalein glucuronide
-# tamoxifen
-# 2,3,7,8-tetrachlorodibenzo-p-dioxin
-# imidacloprid", # well this one is only fit by the flat,
-# so isn't present anyway
-
-### when I take these out, 48 1 compartment best fits, 59 2 compartment, 107 total
-
-### I also manually checked all Joint Analysis compounds 
-# to make sure no joint flat models performed better
-# none did
-
-# write.csv(fittable, file = "inst/ext/model_params_table_04182022.csv", row.names = FALSE)
-
-```
-
-```{r, make_no_fit_table}
-
-##################
-##################
-
-pk_data1 <- as.data.table(pk_output_1comp)
-pk_data2 <- as.data.table(pk_output_2comp)
-
-##################
-##################
-
-pk_data1 <- pk_data1 %>%
-  filter(param.value.type == "Fitted geometric mean") %>%
-  dplyr::select(c("Compound", "CAS", "Reference", "AIC")) %>%
-  mutate(model = "1-Compartment")
-
-pk_data2 <- pk_data2 %>%
-  filter(param.value.type == "Fitted geometric mean") %>%
-  dplyr::select(c("Compound", "CAS", "Reference", "AIC")) %>%
-  mutate(model = "2-Compartment")
-
-pk_all <- rbind(pk_data1, pk_data2)
-
-### loop that says if a compound has any references that do not have AIC of Inf, it was a fit compound
-this.compound.list <- list()
-for (this.compound in unique(pk_all[, Compound])) {
-
-  this.compound.data <- pk_all[Compound == this.compound]
-  this.compound.data$AIC[is.na(this.compound.data$AIC)] <- Inf
-
-  if(any(this.compound.data$AIC != Inf)) {
-    this.compound.data$status <- "good fit"
-  } else {
-    this.compound.data$status <- "bad fit"
-  }
-
-  this.compound.list[[this.compound]] <- this.compound.data
-
-}
-
-pk_all <- do.call(rbind, this.compound.list)
-
-pk_all <- pk_all %>%
-  filter(status == "bad fit") %>% ### only want bad fit
-  mutate(status = NULL) %>% ### get rid of status column
-  group_by(Compound) %>%  
-  filter(n() == 2) %>% ### group_by compound and only keep compounds with two observations, aka neither model worked
-  mutate(model = NULL) %>% ### get rid of model column
-  distinct() ### discard repeated compound names
-
-# write.csv(pk_all, file = "inst/ext/no_fit_table_03012022.csv", row.names = FALSE)
-```
-
-```{r, compare_AIC}
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp
-
-pk_data2 <- pk_output_2comp
-
-pk_data_flat <- pk_output_flat %>%
-  filter(param.value.type == "Predicted" | param.value.type == "Fitted geometric mean" | param.value.type == "Fitted geometric std dev")
-
-##################
-##################
-
-### make both data.frames have the same column names so they are rbind-able
-pk_data1 <- pk_data1[, intersect(intersect(colnames(pk_data2), colnames(pk_data_flat)), colnames(pk_data1))]
-pk_data2 <- pk_data2[, intersect(intersect(colnames(pk_data1), colnames(pk_data_flat)), colnames(pk_data2))]
-pk_data_flat <- pk_data_flat[, intersect(intersect(colnames(pk_data1), colnames(pk_data2)), colnames(pk_data_flat))]
-
-pk_data1 <- pk_data1 %>%
-  rename(LogLikelihood_1 = LogLikelihood,
-         AIC_1 = AIC,
-         sigma_value_1 = sigma_value) %>%
-  mutate(model = NULL) %>%
-  mutate(model.type = NULL)
-
-pk_data2 <- pk_data2 %>%
-  rename(LogLikelihood_2 = LogLikelihood,
-         AIC_2 = AIC,
-         sigma_value_2 = sigma_value) %>%
-  mutate(model = NULL) %>%
-  mutate(model.type = NULL)
-
-pk_data_flat <- pk_data_flat %>%
-  rename(LogLikelihood_flat = LogLikelihood,
-         AIC_flat = AIC,
-         sigma_value_flat = sigma_value) %>%
-  mutate(model = NULL) %>%
-  mutate(model.type = NULL)
-
-pk_all <- left_join(pk_data1, pk_data2, by = c("CAS",
-                                               "Species",
-                                               "param.value.type",
-                                               "sigma_id",
-                                               "Reference",
-                                               "Data.Analyzed",
-                                               "Compound"))
-
-pk_all <- left_join(pk_all, pk_data_flat, by = c("CAS",
-                                                 "Species",
-                                                 "param.value.type",
-                                                 "sigma_id",
-                                                 "Reference",
-                                                 "Data.Analyzed",
-                                                 "Compound"))
-
-pk_all <- subset(pk_all, select = c(CAS, Species, Compound, Reference, AIC_1, AIC_2, AIC_flat))
-
-pk_all <- distinct(pk_all)
-
-pk_all$AIC_1[pk_all$AIC_1 == Inf] <- NA
-pk_all$AIC_2[pk_all$AIC_2 == Inf] <- NA
-pk_all$AIC_flat[pk_all$AIC_flat == Inf] <- NA
-
-pk_all <- pk_all %>%
-  mutate(flat_lowest = ifelse(AIC_flat < AIC_1 & AIC_flat < AIC_2, 1, 0)) %>%
-  mutate(flat_better_than_1 = ifelse(AIC_flat < AIC_1 & AIC_flat > AIC_2, 1, 0)) %>%
-  mutate(flat_better_than_2 = ifelse(AIC_flat > AIC_1 & AIC_flat < AIC_2, 1, 0))
-
-pk_just_bad <- pk_all %>%
-  filter(flat_lowest == 1 | flat_better_than_1 == 1 | flat_better_than_2 == 1)
-```
-
-```{r, lombardo_comparisons}
-
-##################
-##################
-
-pk_data1 <- pk_output_1comp
-# pk_data1 <- pk_output_1comp_04282022
-
-# pk_data1$Vdist <- log(pk_data1$Vdist)
-
-pk_lombardo <- pk_lombardo
-
-##################
-##################
-
-pk_data1 <- pk_data1 %>%
-  filter(param.value.type == "Fitted geometric mean")
-         # , CAS != "50-49-7", CAS != "106266-06-2")
-# , Species == "human")
-
-pk_all <- left_join(all.fit.table, pk_lombardo, by = c("CAS" = "CAS #"))
-
-pk_all <- pk_all %>%
-  filter(!is.na(`human VDss (L/kg)`), 
-         !is.na(`human CL (mL/min/kg)`))
-
-pk_all$`human CL (L/hr/kg)` <- pk_all$`human CL (mL/min/kg)` * 60 / 1000
-pk_all$CLtot <- pk_all$Vdist*pk_all$kelim
-pk_all$Vdist_norm <- abs(pk_all$Vdist / pk_all$`human VDss (L/kg)`)
-pk_all$CLtot_norm <- abs(pk_all$CLtot / pk_all$`human CL (L/hr/kg)`)
-pk_all$halflife_norm <- abs(pk_all$halflife / pk_all$`terminal  t1/2 (h)`)
-
-pk_all$mae <- rowMeans(pk_all[, c("Vdist_norm", "CLtot_norm", "halflife_norm")])
-
-### volume of distribution comparison
-p1 <- ggplot(pk_all, aes(x = Vdist, y = `human VDss (L/kg)`)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  geom_abline(slope = 1, intercept = 0)
-
-p1
-
-### half-life comparision
-p2 <- ggplot(pk_all, aes(x = halflife, y = `terminal  t1/2 (h)`)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  geom_abline(slope = 1, intercept = 0)
-
-p2
-
-### clearance comparison
-
-### convert to same units
-
-p3 <- ggplot(data = pk_all, mapping = aes(x = CLtot, y = `human CL (L/hr/kg)`)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  geom_abline(slope = 1, intercept = 0)
-
-p3
-
-```
-
-<!-- # ```{r, make_model_params_table, eval = FALSE} -->
-<!-- #  -->
-<!-- # ### this code almost entirely is imported from John's bake-off RMarkdown file -->
-<!-- # ### what this produces is a table of compounds that were fit by at least one of the models -->
-<!-- # ### AICs for both models are reported, and subsequent parameter values correspond to the model with the lower AIC -->
-<!-- #  -->
-<!-- # ################### -->
-<!-- # ################### -->
-<!-- #  -->
-<!-- # pk_data1 <- pk_output_1comp_04142022  -->
-<!-- # # pk_data1 <- pk_output_1comp_12212021  -->
-<!-- #  -->
-<!-- # pk_data2 <- pk_output_2comp_04142022  -->
-<!-- # # pk_data2 <- pk_output_2comp_12212021  -->
-<!-- #  -->
-<!-- # pk_data_flat <- pk_output_flat_04142022 -->
-<!-- #  -->
-<!-- # ################### -->
-<!-- # ################### -->
-<!-- #  -->
-<!-- # pk_data1$sigma_id <- NULL -->
-<!-- # pk_data1$sigma_value <- NULL -->
-<!-- # pk_data2$sigma_id <- NULL -->
-<!-- # pk_data2$sigma_value <- NULL -->
-<!-- # pk_data_flat$sigma_id <- NULL -->
-<!-- # pk_data_flat$sigma_value <- NULL -->
-<!-- #  -->
-<!-- # pk_data1 <- distinct(pk_data1) -->
-<!-- # pk_data2 <- distinct(pk_data2) -->
-<!-- # pk_data_flat <- distinct(pk_data_flat) -->
-<!-- #  -->
-<!-- # fits1comp <- subset(pk_data1, is.finite(AIC) & AIC < 10^4) -->
-<!-- # fits2comp <- subset(pk_data2, is.finite(AIC) & AIC < 10^4) -->
-<!-- # fitsflat <- subset(pk_data_flat, is.finite(AIC) & AIC < 10^4) -->
-<!-- #  -->
-<!-- # #How many chemicals have 1 or 2 compartment fits: -->
-<!-- # length(unique(c(fits1comp$CAS,fits2comp$CAS,fitsflat$CAS))) -->
-<!-- #  -->
-<!-- # fittable <- NULL -->
-<!-- # # test <- function(fits1comp, fits2comp, fitsflat) { -->
-<!-- #   for (this.cas in unique(c(fits1comp$CAS,fits2comp$CAS, fitsflat$CAS))) -->
-<!-- #   { print(this.cas) -->
-<!-- #     # if (this.cas == "96-47-9") browser() -->
-<!-- #     if (this.cas %in% fits1comp$CAS) this.compound <- fits1comp[ -->
-<!-- #       fits1comp$CAS==this.cas,"Compound"][1] -->
-<!-- #     else if (this.cas %in% fits2comp$CAS) this.compound <- fits2comp[ -->
-<!-- #       fits2comp$CAS==this.cas,"Compound"][1] -->
-<!-- #     else if (this.cas %in% fitsflat$CAS) this.compound <- fitsflat[ -->
-<!-- #       fitsflat$CAS==this.cas,"Compound"][1] -->
-<!-- #      -->
-<!-- #     this.data.1comp <- subset(fits1comp,CAS==this.cas) -->
-<!-- #     this.data.2comp <- subset(fits2comp,CAS==this.cas) -->
-<!-- #     this.data.flat <- subset(fitsflat,CAS==this.cas) -->
-<!-- #      -->
-<!-- #     for (this.species in unique(tolower(c( -->
-<!-- #       this.data.1comp$Species, -->
-<!-- #       this.data.2comp$Species, -->
-<!-- #       this.data.flat$Species)))) -->
-<!-- #     { -->
-<!-- #       Vdist.1comp <- NA -->
-<!-- #       kelim.1comp <- NA -->
-<!-- #       Vdist.2comp <- NA -->
-<!-- #       kelim.2comp <- NA -->
-<!-- #       A.flat <- NA -->
-<!-- #        -->
-<!-- #       this.data.1comp.species <- subset(this.data.1comp,tolower(Species)==this.species) -->
-<!-- #       this.data.2comp.species <- subset(this.data.2comp,tolower(Species)==this.species) -->
-<!-- #       this.data.flat.species <- subset(this.data.flat, tolower(Species)==this.species) -->
-<!-- #        -->
-<!-- #       this.row <- data.frame( -->
-<!-- #         Compound=this.compound, -->
-<!-- #         CAS=this.cas, -->
-<!-- #         Species=this.species, -->
-<!-- #         Reference=NA, -->
-<!-- #         AIC.1comp=NA, -->
-<!-- #         AIC.2comp=NA, -->
-<!-- #         Model=NA, -->
-<!-- #         Vdist=NA, -->
-<!-- #         kelim=NA) -->
-<!-- #        -->
-<!-- #       if (this.cas %in% fits1comp$CAS) -->
-<!-- #       { -->
-<!-- #         this.data.1comp.species <- subset(this.data.1comp.species, -->
-<!-- #                                           param.value.type=="Fitted geometric mean") -->
-<!-- #          -->
-<!-- #         # If more than one source, require that the joint analysis worked: -->
-<!-- #         if (dim(this.data.1comp.species)[1]>1) -->
-<!-- #         { -->
-<!-- #           this.data.1comp.species<- subset(this.data.1comp.species,  -->
-<!-- #                                            Data.Analyzed=="Joint Analysis") -->
-<!-- #         } -->
-<!-- #         if (dim(this.data.1comp.species)[1]>0)  -->
-<!-- #         { -->
-<!-- #           if (nrow(this.data.1comp.species) > 1) { -->
-<!-- #             this.data.1comp.species <- this.data.1comp.species[1, ] -->
-<!-- #           } -->
-<!-- #            -->
-<!-- #           this.row$AIC.1comp <- this.data.1comp.species$AIC -->
-<!-- #           Vdist.1comp <- this.data.1comp.species$Vdist -->
-<!-- #           kelim.1comp <- this.data.1comp.species$kelim -->
-<!-- #           this.row$Reference <- this.data.1comp.species$Reference -->
-<!-- #         } -->
-<!-- #       } -->
-<!-- #        -->
-<!-- #       if (this.cas %in% fits2comp$CAS) -->
-<!-- #       { -->
-<!-- #         this.data.2comp.species <- subset(this.data.2comp.species, -->
-<!-- #                                           param.value.type=="Fitted geometric mean") -->
-<!-- #          -->
-<!-- #         # If more than one source, require that the joint analysis worked: -->
-<!-- #         if (dim(this.data.2comp.species)[1]>1) -->
-<!-- #         { -->
-<!-- #           this.data.2comp.species <- subset(this.data.2comp.species,  -->
-<!-- #                                             Data.Analyzed=="Joint Analysis") -->
-<!-- #         } -->
-<!-- #         if (dim(this.data.2comp.species)[1]>0)  -->
-<!-- #         { -->
-<!-- #           if(nrow(this.data.2comp.species) > 1 ) { -->
-<!-- #             this.data.2comp.species <- this.data.2comp.species[1, ] -->
-<!-- #           } -->
-<!-- #           this.row$AIC.2comp <- this.data.2comp.species$AIC -->
-<!-- #           Vdist.2comp <- this.data.2comp.species$Vss -->
-<!-- #           kelim.2comp <- this.data.2comp.species$kelim -->
-<!-- #           this.row$Reference <- this.data.2comp.species$Reference -->
-<!-- #         } -->
-<!-- #       } -->
-<!-- #        -->
-<!-- #       if (this.cas %in% fitsflat$CAS) -->
-<!-- #       { -->
-<!-- #         this.data.flat.species <- subset(this.data.flat.species, -->
-<!-- #                                          param.value.type=="Fitted geometric mean") -->
-<!-- #          -->
-<!-- #         # If more than one source, require that the joint analysis worked: -->
-<!-- #         if (dim(this.data.flat.species)[1]>1) -->
-<!-- #         { -->
-<!-- #           this.data.flat.species <- subset(this.data.flat.species,  -->
-<!-- #                                            Data.Analyzed=="Joint Analysis") -->
-<!-- #         } -->
-<!-- #         if (dim(this.data.flat.species)[1]>0)  -->
-<!-- #         { -->
-<!-- #           if(nrow(this.data.flat.species) > 1 ) { -->
-<!-- #             this.data.flat.species <- this.data.flat.species[1, ] -->
-<!-- #           } -->
-<!-- #           this.row$AIC.flat <- this.data.flat.species$AIC -->
-<!-- #           A.flat <- this.data.flat.species$A -->
-<!-- #           this.row$Reference <- this.data.flat.species$Reference -->
-<!-- #         } -->
-<!-- #       } -->
-<!-- #       ######################## -->
-<!-- #       ######################### -->
-<!-- #        -->
-<!-- #       if(!"AIC.flat" %in% names(this.row)) this.row <- this.row %>%  -->
-<!-- #         add_column(AIC.flat = NA) -->
-<!-- #        -->
-<!-- #       if(!"AIC.1comp" %in% names(this.row)) this.row <- this.row %>%  -->
-<!-- #         add_column(AIC.1comp = NA) -->
-<!-- #        -->
-<!-- #       if(!"AIC.2comp" %in% names(this.row)) this.row <- this.row %>%  -->
-<!-- #         add_column(AIC.2comp = NA) -->
-<!-- #        -->
-<!-- #       this.row <- this.row %>% mutate(Model = case_when(AIC.1comp < AIC.2comp &  -->
-<!-- #                                                           AIC.1comp < AIC.flat ~ "1Comp", -->
-<!-- #                                                         AIC.2comp < AIC.1comp & -->
-<!-- #                                                           AIC.2comp < AIC.flat ~ "2Comp", -->
-<!-- #                                                         AIC.flat < AIC.1comp & -->
-<!-- #                                                           AIC.flat < AIC.2comp ~ "Null", -->
-<!-- #                                                          -->
-<!-- #                                                         !is.na(AIC.1comp) & is.na(AIC.2comp) & -->
-<!-- #                                                           is.na(AIC.flat) ~ "1Comp", -->
-<!-- #                                                         !is.na(AIC.2comp) & is.na(AIC.1comp) &  -->
-<!-- #                                                           is.na(AIC.flat) ~ "2Comp", -->
-<!-- #                                                         !is.na(AIC.flat) & is.na(AIC.1comp) &  -->
-<!-- #                                                           is.na(AIC.2comp) ~ "Null", -->
-<!-- #                                                          -->
-<!-- #                                                         is.na(AIC.1comp) & -->
-<!-- #                                                           AIC.flat < AIC.2comp ~ "Null", -->
-<!-- #                                                         is.na(AIC.1comp) & -->
-<!-- #                                                           AIC.2comp < AIC.flat ~ "2Comp", -->
-<!-- #                                                         is.na(AIC.2comp) & -->
-<!-- #                                                           AIC.flat < AIC.1comp ~ "Null", -->
-<!-- #                                                         is.na(AIC.2comp) & -->
-<!-- #                                                           AIC.1comp < AIC.flat ~ "1Comp", -->
-<!-- #                                                         is.na(AIC.flat) & -->
-<!-- #                                                           AIC.1comp < AIC.2comp ~"1Comp", -->
-<!-- #                                                         is.na(AIC.flat) & -->
-<!-- #                                                           AIC.2comp <AIC.1comp ~"2Comp")) -->
-<!-- #        -->
-<!-- #        -->
-<!-- #       fittable <- rbind(fittable,this.row) -->
-<!-- #     } -->
-<!-- #   } -->
-<!-- # # } -->
-<!-- # # debug(test) -->
-<!-- # # test(fits1comp, fits2comp, fitsflat) -->
-<!-- # fittable$halflife <- log(2)/fittable$kelim -->
-<!-- #  -->
-<!-- # #Lets only keep chemicals where we can fit a PK model: -->
-<!-- # fittable <- subset(fittable, !is.na(Model)) -->
-<!-- #  -->
-<!-- # # for (this.col in c("AIC.1comp","AIC.2comp","Vdist","kelim","halflife")) -->
-<!-- # #   fittable[,this.c=-] <- signif(as.numeric(fittable[,this.col]),4) -->
-<!-- #  -->
-<!-- # # We have parameters estimated for 86 chemicals: -->
-<!-- # dim(fittable)[1] -->
-<!-- #  -->
-<!-- # # write.csv(fittable, file = "inst/ext/model_params_table_04182022.csv", row.names = FALSE) -->
-<!-- #  -->
-<!-- # ``` -->

### 2023-01-05 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Change variable names for newly corrected & normalized variables to make them clearer (correct.dose_level_normalized -> studies.dose_level_normalized_corrected, conc_time_values.conc_sd -> conc_time_values.conc_sd_normalized)

@@
 ```{r}
-tmp[, correct.dose_level_normalized:=as.numeric(studies.dose_level_normalized)]
+tmp[, studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_normalized)]
 
@@
       studies.administration_route_normalized %in% "oral",
-    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]
+    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]
 
@@
       studies.administration_route_normalized %in% "iv",
-    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
+    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
 
@@
                  shape = factor(documents_extraction.id),
-                 color = as.numeric(correct.dose_level_normalized))) +
+                 color = as.numeric(studies.dose_level_normalized_corrected))) +
   facet_grid(rows = vars(studies.administration_route_normalized)) +
@@
   geom_point(aes(x = conc_time_values.time_hr,
-                 y = conc_time_values.conc/as.numeric(correct.dose_level_normalized),
+                 y = conc_time_values.conc/as.numeric(studies.dose_level_normalized_corrected),
                  shape = factor(documents_extraction.id),
-                 color = as.numeric(correct.dose_level_normalized))) +
+                 color = as.numeric(studies.dose_level_normalized_corrected))) +
   facet_grid(rows = vars(studies.administration_route_normalized)) +
@@
 ```{r}
-cvt_data[, correct.dose_level_normalized:=as.numeric(studies.dose_level_normalized)]
+cvt_data[, studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_normalized)]
 
@@
       studies.administration_route_normalized %in% "iv",
-    correct.dose_level_normalized:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
+    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
 ```
@@
 cvt_data[series.conc_units_original == "ug/L",
-         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-3]
+         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-3]
 
 cvt_data[series.conc_units_original == "ug/mL",
-         conc_time_values.conc_sd := conc_time_values.conc_sd_original]
+         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original]
 
 cvt_data[series.conc_units_original == "mg/L",
-         conc_time_values.conc_sd := conc_time_values.conc_sd_original]
+         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original]
 
 cvt_data[series.conc_units_original == "ug/dL",
-         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-4]
+         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-4]
 
 cvt_data[series.conc_units_original == "ng/mL",
-         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-3]
+         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-3]
 
 cvt_data[series.conc_units_original == "pg/mL",
-         conc_time_values.conc_sd := conc_time_values.conc_sd_original * 1e-6]
+         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-6]
 

### 2023-01-05 Working Rmds/MainAnalysis.Rmd
Read in most recent CvTdb file. Specify 'new_name' = 'old_name' list for pre-processing data ensuring that 'old_name' properly refers to corrected/normalized variables as produced in 'pulling_oral_iv_data_cvtdb.Rmd': 'Dose' = 'studies.dose_level_normalized_corrected', 'LOQ' = 'series.loq_normalized', 'Value_SD' = 'conc_time_values.conc_sd_normalized'.

@@
 
-Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.
+# Read in CvTdb data
+
+Read in CvTdb data that was pulled and normalized in `pulling_oral_iv_data_cvtdb.Rmd`.
 
 ```{r, load_cvt, eval = TRUE}
-cvt_data <- fread("../inst/ext/cvt_data_2022_12_15_16_20_21.csv")
+cvt_data <- fread("../inst/ext/cvt_data_2023_01_05_09_37_22.csv")
 ```
 
-Run a one-compartment fit on the data, and write out the results. Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.
+# Setup for model fitting
+
+## Timestamp
+Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.
 
@@
 
-Fit the flat model.
+## Settings for pre-processing data
 
-```{r, run_invivoPKfit_flat}
+List of new_name = old_name to supply for preprocessing data
 
-system.time(
-    PK.fit.table.flat <- fit_all(
-     data.set = cvt_data,
-      model = "flat",
-      modelfun = "analytic",
-      names_list =list(
+```{r}
+names_list <- list(
   "Compound_Dosed" = "studies.test_substance_name_original",
@@
   "Weight.Units" = NULL,
-                      "Dose" = "studies.dose_level_normalized",
+  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
   "Dose.Units" = NULL,
@@
   "Media" = "series.conc_medium_normalized",
-                      "Value" = "conc_time_values.conc",
+  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
   "Value.Units" = NULL,
   "Route" = "studies.administration_route_normalized",
-                      "LOQ" = "series.loq",
+  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
   "Subject" = "subjects.id",
   "N_Subjects" = "series.n_subjects_in_series",
-                      "Value_SD" = "conc_time_values.conc_sd"),
-                    defaults_list =   list(
+  "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
+  )
+```
+
+List of default values for new columns added in preprocessing data
+
+```{r}
+defaults_list <- list(
                       "Weight.Units" = "kg",
@@
                       "Time.Units" = "h",
-                      "Value.Units" = "mg/L"),
+                      "Value.Units" = "mg/L")
+```
+
+# Model fitting
+
+## Flat model
+
+```{r, run_invivoPKfit_flat}
+
+system.time(
+  PK.fit.table.flat <- fit_all(
+    data.set = cvt_data,
+    model = "flat",
+    modelfun = "analytic",
+    names_list = names_list,
+    defaults_list =  defaults_list,
     ratio_conc_to_dose = 1,
@@
 
-write.csv(PK.fit.table.flat, paste("inst/ext/PK_fit_table_flat_",
+write.csv(PK.fit.table.flat, paste("../inst/ext/PK_fit_table_flat_",
                                     timestamp,
@@
 
-Fit the 1-compartment model.
+## 1-compartment model
 
@@
       modelfun = "analytic",
-      names_list =list(
-                      "Compound_Dosed" = "studies.test_substance_name_original",
-                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
-                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
-                      "Compound_Analyzed" = "series.analyte_name_original",
-                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
-                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
-                      "Reference" = "documents_reference.id",
-                      "Extraction" = "documents_extraction.id",
-                      "Species" = "subjects.species",
-                      "Weight" ="subjects.weight_kg",
-                      "Weight.Units" = NULL,
-                      "Dose" = "studies.dose_level_normalized",
-                      "Dose.Units" = NULL,
-                      "Time" = "conc_time_values.time_hr",
-                      "Time.Units" = NULL,
-                      "Media" = "series.conc_medium_normalized",
-                      "Value" = "conc_time_values.conc",
-                      "Value.Units" = NULL,
-                      "Route" = "studies.administration_route_normalized",
-                      "LOQ" = "series.loq",
-                      "Subject" = "subjects.id",
-                      "N_Subjects" = "series.n_subjects_in_series",
-                      "Value_SD" = "conc_time_values.conc_sd"),
-                    defaults_list =   list(
-                      "Weight.Units" = "kg",
-                      "Dose.Units" = "mg/kg",
-                      "Time.Units" = "h",
-                      "Value.Units" = "mg/L"),
+        names_list = names_list,
+    defaults_list =  defaults_list,
       ratio_conc_to_dose = 1,
@@
 
-Fit the 2-compartment model.
+## 2-compartment model
 
@@
       modelfun = "analytic",
-      names_list =list(
-                      "Compound_Dosed" = "studies.test_substance_name_original",
-                      "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
-                      "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
-                      "Compound_Analyzed" = "series.analyte_name_original",
-                      "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
-                      "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
-                      "Reference" = "documents_reference.id",
-                      "Extraction" = "documents_extraction.id",
-                      "Species" = "subjects.species",
-                      "Weight" ="subjects.weight_kg",
-                      "Weight.Units" = NULL,
-                      "Dose" = "studies.dose_level_normalized",
-                      "Dose.Units" = NULL,
-                      "Time" = "conc_time_values.time_hr",
-                      "Time.Units" = NULL,
-                      "Media" = "series.conc_medium_normalized",
-                      "Value" = "conc_time_values.conc",
-                      "Value.Units" = NULL,
-                      "Route" = "studies.administration_route_normalized",
-                      "LOQ" = "series.loq",
-                      "Subject" = "subjects.id",
-                      "N_Subjects" = "series.n_subjects_in_series",
-                      "Value_SD" = "conc_time_values.conc_sd"),
-                    defaults_list =   list(
-                      "Weight.Units" = "kg",
-                      "Dose.Units" = "mg/kg",
-                      "Time.Units" = "h",
-                      "Value.Units" = "mg/L"),
+          names_list = names_list,
+    defaults_list =  defaults_list,
       ratio_conc_to_dose = 1,

### 2023-01-05 Working Rmds/plot_fits.Rmd
Read in most recent CvTdb file. Specify 'new_name' = 'old_name' list for pre-processing data ensuring that 'old_name' properly refers to corrected/normalized variables as produced in 'pulling_oral_iv_data_cvtdb.Rmd': 'Dose' = 'studies.dose_level_normalized_corrected', 'LOQ' = 'series.loq_normalized', 'Value_SD' = 'conc_time_values.conc_sd_normalized'.

@@
 
+Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.
+
+```{r, load_cvt, eval = TRUE}
+cvt_data <- fread("../inst/ext/cvt_data_2023_01_05_09_37_22.csv")
+```
+
 For ease of plotting, get the pre-processed, harmonized data:
@@
                          "Weight.Units" = NULL,
-                      "Dose" = "correct.dose_level_normalized",
+                         "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
                          "Dose.Units" = NULL,
@@
                          "Media" = "series.conc_medium_normalized",
-                      "Value" = "conc_time_values.conc",
+                         "Value" = "conc_time_values.conc", #already in mg/L units
                          "Value.Units" = NULL,
                          "Route" = "studies.administration_route_normalized",
-                      "LOQ" = "series.loq_normalized",
+                         "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
                          "Subject" = "subjects.id",
                          "N_Subjects" = "series.n_subjects_in_series",
-                              "Value_SD" = "conc_time_values.conc_sd"),
+                         "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
+                         ),
                        defaults_list =   list(
@@
                        suppress.messages = FALSE)
+cvt <- as.data.table(cvt)
 ```
 
+Read in the fitted model parameter values.
+
 ```{r, read_data}
-### this block reads the exported model fit csv files from run_invivoPKfit
-
-PK.fit.table.1comp <- fread(paste0("inst/ext/", "PK_fit_table_1comp_2022_12_08_09_44_34.csv",sep=""))
-PK.fit.table.2comp <- fread(paste0("inst/ext/", "PK_fit_table_2comp_2022_12_08_10_31_09.csv",sep=""))
-PK.fit.table.flat <- fread(paste0("inst/ext/", "PK_fit_table_flat_2022_12_08_12_03_24.csv",sep=""))
+timestamp <- "2023_01_04_10_56"
+PK.fit.table.1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
+PK.fit.table.2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
+PK.fit.table.flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))
 
@@
 
-Get a table of the winning model for each dataset (minimum AIC).
+Get a table of the winning model for each dataset (the one with minimum AIC).
 
 ```{r}
-tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, model, AIC)])
-setorder(tmp, DTXSID, Species, Analysis_Type, AIC, na.last = TRUE)
-model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type)]
-pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type")]
+tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, References.Analyzed, model, AIC)])
+
+#sort AIC from smallest to largest within each dataset, putting NAs last
+setorder(tmp, DTXSID, Species, Analysis_Type, References.Analyzed, AIC, na.last = TRUE)
+#the winning model will now be listed first within each dataset (smallest AIC)
+model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type, References.Analyzed)]
+pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type", "References.Analyzed")]
 pk_fit[, winning:=(model == winmodel)]
@@
                      Analysis_Type_in = "Joint",
-                     DF = DF,
+                     DF = cvt,
                      pk_fit = pk_fit,
                      n = 101,
+                     limit_y_axis = FALSE,
+                     log10_scale_y = FALSE,
+                     plot_errbars = TRUE,
                      log10_scale_time = FALSE,
-                     file_path = "inst/ext/plots/Joint Analysis/model_all/")
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/")
                      )
@@
 ```
+
+Problem: DTXSID0022985_rat_Joint_all does not plot any model lines. Why?
+
+```{r}
+pk_fit[DTXSID %in% "DTXSID0022985"]
+```
+
+Apparently there were no detected data points?
+
+```{r}
+cvt[DTXSID %in% "DTXSID0022985", .(Reference, Value, LOQ)]
+```
+
+Hmm. Something is very weird here. I definitely see some detected points. They are all the same reference, so it isn't that a single-reference fit did not work but a joint fit did work.
 

### 2023-01-06 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Made a change to dose units for PCB-126 study (was mg/kg; I think it should be ng/kg).

@@
 fpath <- "C:/Users/cring/OneDrive - Environmental Protection Agency (EPA)/CvTdb/"
-this_date <- format(Sys.time(), "%Y_%m_%d_%H_%M_%S")
+this_date <- format(Sys.time(), "%Y_%m_%d")
 
@@
 
+## Correcting dose level units for PCB-126
+
+Upon examining PCB-126, I think the original dose units should be ng/kg rather than mg/kg.
+If we look at https://cebs.niehs.nih.gov/cebs/study/002-02863-0008-0000-9 and look at the summary data rather than individual animal data, the dose units are listed as "ng/kg." In the rest of the studies at https://cebs.niehs.nih.gov/cebs/test_article/57465-28-8 all of the dosing units are ng/kg.
+So I think that is what it should be.
+
+```{r}
+cvt_data[chemicals_dosed.dsstox_substance_id %in% "DTXSID3032179", studies.dose_level_original := "ng/kg"]
+cvt_data[chemicals_dosed.dsstox_substance_id %in% "DTXSID3032179", studies.dose_level_normalized_corrected := as.numeric(studies.dose_level_normalized) * 1e-6] #convert to mg/kg
+```
+
 # Missing LOQs

### 2023-01-06 Working Rmds/plot_fits.Rmd
Plot most recent fits with most recent data

@@
 
+Timestamp
+
+```{r}
+timestamp <- "2023_01_05"
+```
+
 Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.
@@
 ```{r, load_cvt, eval = TRUE}
-cvt_data <- fread("../inst/ext/cvt_data_2023_01_05_09_37_22.csv")
+cvt_data <- fread(paste0("../inst/ext/cvt_data_",
+timestamp,
+".csv"))
 ```
-
-For ease of plotting, get the pre-processed, harmonized data:
+List of new_name = old_name to supply for preprocessing data
 
 ```{r}
-cvt <- preprocess_data(data.set = cvt_data,
-                       names_list =list(
+names_list <- list(
   "Compound_Dosed" = "studies.test_substance_name_original",
@@
   "Media" = "series.conc_medium_normalized",
-                         "Value" = "conc_time_values.conc", #already in mg/L units
+  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
   "Value.Units" = NULL,
@@
   "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
-                         ),
-                       defaults_list =   list(
+  )
+```
+
+List of default values for new columns added in preprocessing data
+
+```{r}
+defaults_list <- list(
                       "Weight.Units" = "kg",
@@
                       "Time.Units" = "h",
-                         "Value.Units" = "mg/L"),
+                      "Value.Units" = "mg/L")
+```
+
+For ease of plotting, get the pre-processed, harmonized data:
+
+```{r}
+cvt <- preprocess_data(data.set = cvt_data,
+                       names_list =names_list,
+                       defaults_list =   defaults_list,
                        ratio_conc_to_dose = 1,
@@
 cvt <- as.data.table(cvt)
+
+#save pre-processed data
+write.csv(cvt,
+          paste0("cvt_preprocessed_",
+                 timestamp,
+          ".csv"))
 ```
@@
 ```{r, read_data}
-timestamp <- "2023_01_04_10_56"
+
 PK.fit.table.1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
@@
                     fill = TRUE)
+
+rm(PK.fit.table.1comp,
+   PK.fit.table.2comp,
+   PK.fit.table.flat)
 ```
@@
                      log10_scale_time = FALSE,
-                     file_path = "../inst/ext/plots/Joint Analysis/model_all/")
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly")
+                     )
+
+```
+
+```{r}
+
+#plot all models
+tmp <- mapply(plot_fit,
+              DTXSID_in = plot_table$DTXSID,
+                     Species_in = plot_table$Species,
+              MoreArgs = list(
+                     model_in = "all",
+                     Analysis_Type_in = "Joint",
+                     DF = cvt,
+                     pk_fit = pk_fit,
+                     n = 101,
+                     limit_y_axis = FALSE,
+                     log10_scale_y = TRUE,
+                     plot_errbars = FALSE,
+                     log10_scale_time = FALSE,
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy")
                      )

### 2023-01-06 Working Rmds/impute_missing_sds.Rmd
Revise analysis of relation between sample mean and sample Sd (in 'impute_missing_sds.Rmd'). Implement the resulting revised relation to impute missing SDs in 'estimate_conc_sd.R'.

@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
 ```{r setup, include = FALSE}
@@
 ```{r, include = FALSE}
-library(tidyverse)
 library(data.table)
-library(readxl)
 devtools::load_all("../invivopkfit")
@@
 
-Read in CvTdb data.
+```{r}
+timestamp <- "2023_01_05"
+```
+
+Read in CvTdb data pulled in `pulling_oral_iv_data_cvtdb.Rmd`.
 
 ```{r, load_cvt, eval = TRUE}
-cvt_data <- fread("../inst/ext/cvt_data_2022_12_15_16_20_21.csv")
+cvt_data <- fread(paste0("../inst/ext/cvt_data_",
+timestamp,
+".csv"))
 ```
+List of new_name = old_name to supply for preprocessing data
 
 ```{r}
-cvt <- preprocess_data(data.set = cvt_data,
-                       names_list =list(
+names_list <- list(
   "Compound_Dosed" = "studies.test_substance_name_original",
@@
   "Weight.Units" = NULL,
-                      "Dose" = "correct.dose_level_normalized",
+  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
   "Dose.Units" = NULL,
@@
   "Media" = "series.conc_medium_normalized",
-                      "Value" = "conc_time_values.conc",
+  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
   "Value.Units" = NULL,
   "Route" = "studies.administration_route_normalized",
-                      "LOQ" = "series.loq_normalized",
+  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
   "Subject" = "subjects.id",
   "N_Subjects" = "series.n_subjects_in_series",
-                              "Value_SD" = "conc_time_values.conc_sd"),
-                    defaults_list =   list(
+  "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
+  )
+```
+
+List of default values for new columns added in preprocessing data
+
+```{r}
+defaults_list <- list(
                       "Weight.Units" = "kg",
@@
                       "Time.Units" = "h",
-                      "Value.Units" = "mg/L"),
+                      "Value.Units" = "mg/L")
+```
+
+For ease of plotting, get the pre-processed, harmonized data:
+
+```{r}
+cvt <- preprocess_data(data.set = cvt_data,
+                       names_list =names_list,
+                       defaults_list =   defaults_list,
                        ratio_conc_to_dose = 1,
@@
                        media_keep = c("blood", "plasma"),
+                       impute_loq = TRUE,
+                       impute_sd = FALSE,
                        suppress.messages = FALSE)
+cvt <- as.data.table(cvt)
 ```
 
-There are many, many cases where N > 1 but no SD is reported. Can we impute these based on patterns in the cases where SD is reported? Calculate mean and SD for the individual cases:
+There are many, many cases where N > 1 but no SD is reported. Can we impute these based on other data?
+
+# Individual subject data
+
+By chemical, species, reference, medium, dose group, and time point: calculate mean and standard deviation.
 
 ```{r}
-cvt <- as.data.table(cvt)
+
 cvt_summarized <- cvt[N_Subjects==1,
@@
                         n = .N),
-                      by = .(Reference, DTXSID, Media, Dose)]
-ggplot(cvt_summarized) +
-  geom_point(aes(x = meanval, y = sdvals, color = n)) +
-  scale_x_log10() + scale_y_log10() + scale_color_viridis_c(trans = "log10")
-
-summary(lm(log10(sdvals) ~ log10(meanval), data = cvt_summarized))
+                      by = .(Reference,
+                             DTXSID,
+                             Media,
+                             Dose,
+                             Time)]
 ```
 
-The relationship between sample SD and sample mean seems to be almost the identity line.
+Plot SD vs. mean across all chemicals, studies, media, doses, and timepoints. Is there an overall relation between SD and mean?
+
+```{r}
+
+ggplot(cvt_summarized,
+       aes(x = meanval,
+           y = sdvals)) +
+  geom_point(aes(color = n)) +
+  geom_abline(intercept = 0, slope =1 , linetype = 2) +
+  geom_smooth(method = "lm", se = FALSE, color = "black") +
+  scale_x_log10() +
+  scale_y_log10() +
+  scale_color_viridis_c(trans = "log10",
+                        name = "# subjects") +
+  annotation_logticks(sides = "bl") +
+  xlab("Mean conc., mg/kg") +
+  ylab("Sample std dev conc., mg/kg") +
+  ggtitle("Mean vs. SD for N=1 data\ngrouped by chemical, reference, medium, dose, timepoint") 
+```
+
+Linear regression of the relation:
+
+```{r}
+cvt_summarized[, log10_sdvals := log10(sdvals)]
+cvt_summarized[, log10_meanval := log10(meanval)]
+
+cvt_summarized[!is.finite(log10_sdvals), log10_sdvals := NA_real_]
+cvt_summarized[!is.finite(log10_meanval), log10_meanval := NA_real_]
+```
+
+```{r}
+summary(lm(log10_sdvals ~ log10_meanval,
+           data = cvt_summarized,
+           na.action = na.omit))
+```
 
@@
 ggplot(cvt[N_Subjects > 1],
-       aes(x = Value, y = Value_SD)) +
-  geom_point(aes(x = Value, y = Value_SD, color = N_Subjects))  +
-  scale_x_log10() + scale_y_log10() + geom_smooth(method = "lm")
-
-summary(lm(log10(Value_SD) ~ log10(Value), data = cvt[N_Subjects > 1]))
+       aes(x = Value,
+           y = Value_SD)) +
+  geom_point(aes(color = N_Subjects)) +
+  geom_abline(intercept = 0, slope =1 , linetype = 2) +
+  geom_smooth(method = "lm", se = FALSE, color = "black") +
+  scale_x_log10() +
+  scale_y_log10() +
+  scale_color_viridis_c(trans = "log10",
+                        name = "# subjects") +
+  annotation_logticks(sides = "bl") +
+  xlab("Mean conc., mg/kg") +
+  ylab("Sample std dev conc., mg/kg") +
+  ggtitle("Mean vs. SD for N>1 data") 
 ```
 
-This one isn't quite the identity line but still, we can get some idea.
+```{r}
 
-These ones with entirely missing SDs are different from the studies where only a few SDs are missing.
+summary(lm(log10(Value_SD) ~ log10(Value),
+           data = cvt[N_Subjects > 1]))
+```
+
+Studies with entirely missing SDs are different from the studies where only a few SDs are missing.
 When only a few are missing, it was usually because the data were pulled from a plot where the error bars were smaller thant the plotting symbol on a few points.
@@
 
-In this case, it seems like a reasonable choice to impute the mean value itself as the SD.
-This relation seems to be borne out by the individual-anumal data, and it is more conservative than the relation suggested by the (limited) multi-animal data.
+I suggest using the relation from the summarized individual-animal data to impute standard deviations. That is
+
+$$ \log \textrm{SD} = -0.517 + 0.953 \log \textrm{Mean} $$
+
+When translated to the natural scale (raising 10 to the power of both sides), this becomes
+
+$$ \log_{10} \textrm{SD} = -0.517 + \log_{10} \textrm{Mean}^{0.953} $$
+$$ \log_{10} \textrm{SD} = \log_{10}{ \left( 10^{-0.517} \times \textrm{Mean}^{0.953} \right)}  $$
+
+Raising 10 to the power of both sides,
+
+$$ \textrm{SD} = 10^{-0.517} \times \textrm{Mean}^{0.953} $$
+
+or approximately
+
+$$ \textrm{SD} = 0.3 \times \textrm{Mean}^{0.953} $$
+
+Very roughly, this is about a 30% coefficient of variation.

### 2023-01-06 Working Rmds/impute_missing_sds.Rmd
Fix error in computing sd vs. mean relation, and implement the fixed result when imputing missing SDs.

@@
 
-By chemical, species, reference, medium, dose group, and time point: calculate mean and standard deviation.
+By chemical, species, reference, medium, dose group, route, and time point: calculate mean and standard deviation.
 
@@
                              DTXSID,
+                             Species,
                              Media,
+                             Route,
                              Dose,
@@
   ylab("Sample std dev conc., mg/kg") +
-  ggtitle("Mean vs. SD for N=1 data\ngrouped by chemical, reference, medium, dose, timepoint") 
+  ggtitle("Mean vs. SD for N=1 data") 
 ```
@@
 cvt_summarized[!is.finite(log10_meanval), log10_meanval := NA_real_]
-```
 
-```{r}
 summary(lm(log10_sdvals ~ log10_meanval,
@@
 
-$$ \log \textrm{SD} = -0.517 + 0.953 \log \textrm{Mean} $$
+$$ \log \textrm{SD} = -0.555 + 0.939 \log \textrm{Mean} $$
 
@@
 
-$$ \log_{10} \textrm{SD} = -0.517 + \log_{10} \textrm{Mean}^{0.953} $$
-$$ \log_{10} \textrm{SD} = \log_{10}{ \left( 10^{-0.517} \times \textrm{Mean}^{0.953} \right)}  $$
+$$ \log_{10} \textrm{SD} = -0.555 + \log_{10} \textrm{Mean}^{0.939} $$
+$$ \log_{10} \textrm{SD} = \log_{10}{ \left( 10^{-0.555} \times \textrm{Mean}^{0.939} \right)}  $$
 
@@
 
-$$ \textrm{SD} = 10^{-0.517} \times \textrm{Mean}^{0.953} $$
+$$ \textrm{SD} = 10^{-0.555} \times \textrm{Mean}^{0.939} $$
 
@@
 
-$$ \textrm{SD} = 0.3 \times \textrm{Mean}^{0.953} $$
+$$ \textrm{SD} = 0.278 \times \textrm{Mean}^{0.939} $$
 

### 2023-01-06 Working Rmds/MainAnalysis.Rmd
Use most recent CVT data
Preprocess data just once, then pass it to fit_all() for each model fit.

@@
 ```{r, load_cvt, eval = TRUE}
-cvt_data <- fread("../inst/ext/cvt_data_2023_01_05_09_37_22.csv")
+cvt_data <- fread("../inst/ext/cvt_data_2023_01_05.csv")
 ```
 
-# Setup for model fitting
+# Setup for data processing and model fitting
 
@@
 ```{r}
-timestamp <- format(Sys.time(), "%Y_%m_%d_%H_%M")
+timestamp <- format(Sys.time(), "%Y_%m_%d")
 ```
@@
 
-# Model fitting
+# Preprocess data
+
+```{r}
+cvt <- preprocess_data(data.set = cvt_data,
+                       names_list =names_list,
+                       defaults_list =   defaults_list,
+                       ratio_conc_to_dose = 1,
+                       calc_loq_factor = 0.45,
+                       routes_keep = c("po", "iv"),
+                       media_keep = c("blood", "plasma"),
+                       impute_loq = TRUE,
+                       impute_sd = TRUE,
+                       suppress.messages = FALSE)
+
+#save pre-processed data
+write.csv(cvt,
+          paste0("../inst/ext/cvt_preprocessed_",
+                 timestamp,
+          ".csv"),
+          row.names = FALSE)
+```
+
+# Fit TK models to data
 
@@
   PK.fit.table.flat <- fit_all(
-    data.set = cvt_data,
+    data.set = cvt,
     model = "flat",
     modelfun = "analytic",
-    names_list = names_list,
-    defaults_list =  defaults_list,
-    ratio_conc_to_dose = 1,
-    calc_loq_factor = 0.45,
-    routes_keep = c("po", "iv"),
-    media_keep = c("blood", "plasma"),
+    preprocess = FALSE,
     optimx_args = list(
@@
     PK.fit.table.1comp <- fit_all(
-      data.set = cvt_data,
+      data.set = cvt,
       model = "1compartment",
       modelfun = "analytic",
-        names_list = names_list,
-    defaults_list =  defaults_list,
-      ratio_conc_to_dose = 1,
-                    calc_loq_factor = 0.45,
-                    routes_keep = c("po", "iv"),
-                    media_keep = c("blood", "plasma"),
+      preprocess = FALSE,
       optimx_args = list(
@@
     PK.fit.table.2comp <- fit_all(
-      data.set = cvt_data,
+      data.set = cvt,
       model = "2compartment",
       modelfun = "analytic",
-          names_list = names_list,
-    defaults_list =  defaults_list,
-      ratio_conc_to_dose = 1,
-                    calc_loq_factor = 0.45,
-                    routes_keep = c("po", "iv"),
-                    media_keep = c("blood", "plasma"),
+      preprocess = FALSE,
       optimx_args = list(

### 2023-01-10 Working Rmds/plot_fits.Rmd
Read in pre-processed data.

@@
 ```{r}
-timestamp <- "2023_01_05"
+timestamp <- "2023_01_06"
 ```
@@
 ```{r, load_cvt, eval = TRUE}
-cvt_data <- fread(paste0("../inst/ext/cvt_data_",
-timestamp,
-".csv"))
-```
-List of new_name = old_name to supply for preprocessing data
-
-```{r}
-names_list <- list(
-  "Compound_Dosed" = "studies.test_substance_name_original",
-  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
-  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
-  "Compound_Analyzed" = "series.analyte_name_original",
-  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
-  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
-  "Reference" = "documents_reference.id",
-  "Extraction" = "documents_extraction.id",
-  "Species" = "subjects.species",
-  "Weight" ="subjects.weight_kg",
-  "Weight.Units" = NULL,
-  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
-  "Dose.Units" = NULL,
-  "Time" = "conc_time_values.time_hr",
-  "Time.Units" = NULL,
-  "Media" = "series.conc_medium_normalized",
-  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
-  "Value.Units" = NULL,
-  "Route" = "studies.administration_route_normalized",
-  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
-  "Subject" = "subjects.id",
-  "N_Subjects" = "series.n_subjects_in_series",
-  "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
-  )
-```
-
-List of default values for new columns added in preprocessing data
-
-```{r}
-defaults_list <- list(
-                      "Weight.Units" = "kg",
-                      "Dose.Units" = "mg/kg",
-                      "Time.Units" = "h",
-                      "Value.Units" = "mg/L")
-```
-
-For ease of plotting, get the pre-processed, harmonized data:
-
-```{r}
-cvt <- preprocess_data(data.set = cvt_data,
-                       names_list =names_list,
-                       defaults_list =   defaults_list,
-                       ratio_conc_to_dose = 1,
-                       calc_loq_factor = 0.45,
-                       routes_keep = c("po", "iv"),
-                       media_keep = c("blood", "plasma"),
-                       suppress.messages = FALSE)
-cvt <- as.data.table(cvt)
-
-#save pre-processed data
-write.csv(cvt,
-          paste0("cvt_preprocessed_",
-                 timestamp,
-          ".csv"))
+cvt <- fread("../inst/ext/cvt_preprocessed_2023_01_06.csv")
+cvt[, Reference:=as.character(Reference)]
+cvt[, Reference_orig:=as.character(Reference_orig)]
 ```
@@
                      pk_fit = pk_fit,
-                     n = 101,
+                     n_interp_time = 10,
                      limit_y_axis = FALSE,

### 2023-01-11 Working Rmds/MainAnalysis.Rmd
Do and save postprocessing of flat model output
Now each study has its own SD, where study = chemical + species + reference + route + media

@@
                       "Dose.Units" = "mg/kg",
-                      "Time.Units" = "h",
+                      "Time.Units" = "hours",
                       "Value.Units" = "mg/L")
@@
 
-rm(PK.fit.table.flat)
+post_flat <- postprocess_data(PK_fit = PK.fit.table.flat,
+                               model = "flat")
+
+write.csv(post_flat,
+          paste("../inst/ext/PK_fit_postprocess_flat_",
+                                    timestamp,
+                                    ".csv",
+                                    sep=""),
+          row.names = FALSE)
+
+rm(PK.fit.table.flat, post_flat)
 ```
@@
 ```{r, run_invivoPKfit_1comp}
-
 ### do 1-Compartment fit

### 2023-01-11 invivopkfit/R/get_starts.R

@@ -339,7 +339,7 @@ if(is.null(par_DF)){
 
     rownames(par_DF) <- par_DF$param_name
 
-    #the abovemerge won't get reference-specific sigmas: handle them
+    #the abovemerge won't get study-specific sigmas: handle them
     for(this_sigma in grep(x = par_DF$param_name,
                            pattern= "sigma",
                            value = TRUE)){
@@ -350,7 +350,7 @@ if(is.null(par_DF)){
                              msg = "Default starting value",
                              par_DF = par_DF,
                              start_from = start_from_data)
-    } #end for loop over reference-specific sigmas
+    } #end for loop over study-specific sigmas
 
     #if httk 1-comp model params exist, replace the defaults with these
     #and mark the source accordingly
@@ -1194,16 +1194,16 @@ if(is.finite(kgutabs_po) &
   for(this_sigma in grep(x = par_DF$param_name,
                          pattern= "sigma",
                          value = TRUE)){
-    if(this_sigma == "sigma"){ #if only one sigma (one reference, or pooled)
+    if(this_sigma == "sigma"){ #if only one sigma (one study, or pooled)
       tmp_sigma <- sd(resid, na.rm = TRUE)
     }else{
-      #if multiple sigmas for multiple references
-      #get the reference
-      refid <- gsub(x = this_sigma,
-                    pattern = "sigma_ref_",
+      #if multiple sigmas for multiple studys
+      #get the study
+      studyid <- gsub(x = this_sigma,
+                    pattern = "sigma_study_",
                     replacement = "")
-      resid_ref <- resid[fitdata$Reference %in% refid]
-      tmp_sigma <- sd(resid_ref, na.rm = TRUE)
+      resid_study <- resid[fitdata$Study %in% studyid]
+      tmp_sigma <- sd(resid_study, na.rm = TRUE)
     }
 
     par_DF <- assign_start(param_name = this_sigma,

### 2023-01-12 Working Rmds/plot_fits.Rmd
Rename "Routes" and "Media" to "N_Routes" and "N_Media" to avoid collision with column names of CVT data (which contain a "Media" column that is really singular "Medium")

@@
 ```{r}
-timestamp <- "2023_01_06"
+timestamp <- "2023_01_11"
 ```
@@
 ```{r, load_cvt, eval = TRUE}
-cvt <- fread("../inst/ext/cvt_preprocessed_2023_01_06.csv")
+cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
+timestamp,
+".csv"))
 cvt[, Reference:=as.character(Reference)]
@@
 
-PK.fit.table.1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
-PK.fit.table.2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
-PK.fit.table.flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))
+DT_1comp <- fread(paste0("../inst/ext/", "PK_fit_postprocess_1comp_", timestamp, ".csv",sep=""))
+DT_2comp <- fread(paste0("../inst/ext/", "PK_fit_postprocess_2comp_", timestamp, ".csv",sep=""))
+DT_flat <- fread(paste0("../inst/ext/", "PK_fit_postprocess_flat_", timestamp, ".csv",sep=""))
+
+idcols <- c( "Analysis_Type",
+                                 "DTXSID",
+                                "Species",
+                                "References.Analyzed",
+                               "Studies.Analyzed",
+                               "N_Routes",
+                               "N_Media",
+              "time_units_reported")
+
+setnames(DT_1comp,
+         setdiff(names(DT_1comp),
+                 idcols),
+         paste(setdiff(names(DT_1comp),
+                 idcols),
+               "1compartment",
+               sep = "."))
+
+setnames(DT_2comp,
+         setdiff(names(DT_2comp),
+                 idcols),
+         paste(setdiff(names(DT_2comp),
+                 idcols),
+               "2compartment",
+               sep = "."))
+
+setnames(DT_flat,
+         setdiff(names(DT_flat),
+                 idcols),
+         paste(setdiff(names(DT_flat),
+                 idcols),
+               "flat",
+               sep = "."))
 
@@
 
-Rowbind together all of the fitted parameter tables into one big one.
+Merge these together.
+
 ```{r}
-pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
-                         "2comp" = PK.fit.table.2comp,
-                         "flat" = PK.fit.table.flat),
-                    use.names = TRUE,
-                    fill = TRUE)
-
-rm(PK.fit.table.1comp,
-   PK.fit.table.2comp,
-   PK.fit.table.flat)
+pk_fit <- merge(DT_2comp,
+               merge(DT_flat, DT_1comp, by = idcols),
+               by = idcols)
 ```
 
-Get a table of the winning model for each dataset (the one with minimum AIC).
+Find the winning model for each dataset
 
 ```{r}
-tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, References.Analyzed, model, AIC)])
+pk_AIC <- melt(pk_fit,
+     id.vars = idcols,
+     measure.vars = c("AIC.flat",
+                      "AIC.1compartment",
+                      "AIC.2compartment"),
+     value.name = "AIC",
+     variable.name = "model")
+
+pk_AIC[, model := gsub(x = model,
+                       pattern = "AIC.",
+                       replacement = "",
+                       fixed = TRUE)]
 
 #sort AIC from smallest to largest within each dataset, putting NAs last
-setorder(tmp, DTXSID, Species, Analysis_Type, References.Analyzed, AIC, na.last = TRUE)
+setorderv(pk_AIC,
+        c(idcols, "AIC"),
+         na.last = TRUE)
 #the winning model will now be listed first within each dataset (smallest AIC)
-model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type, References.Analyzed)]
-pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type", "References.Analyzed")]
-pk_fit[, winning:=(model == winmodel)]
+model_win <- pk_AIC[,
+                    .(winmodel = model[1]),
+                    by = idcols]
+pk_fit <- model_win[pk_fit,
+                    on = idcols]
+```
 
+Keep parameters only.
+
+```{r}
+all_params <- unlist(sapply(c("flat",
+         "1compartment",
+         "2compartment"),
+       function(model){
+         tmp <- get_model_paramnames(model)
+         return(paste(tmp,
+                      model,
+                      sep= "."))
+       }))
+
+pk_params <- pk_fit[, .SD, .SDcols = c(idcols, "winmodel", all_params)]
+
+#Ensure comma-separated lists of studies analyzed are properly sorted
+pk_params[, Studies.Analyzed := {
+  tmp <- strsplit(x = Studies.Analyzed,
+           split = ", ")
+  sapply(tmp,
+         function(x) paste(sort(x), collapse = ", "))
+}]
+
+# pk_params[is.na(Fgutabs_Vdist.flat),
+#           Fgutabs_Vdist.flat := Fgutabs.flat / Vdist.flat]
+# 
+# pk_params[is.na(Rblood2plasma.flat), Rblood2plasma.flat := 1]
+# pk_params[is.na(Rblood2plasma.1compartment), Rblood2plasma.1compartment := 1]
+# pk_params[is.na(Rblood2plasma.2compartment), Rblood2plasma.2compartment := 1]
+```
+
+Merge the parameter information with the original concentration-time info.
+
+```{r}
+cvt[, Study_pooled :=
+  paste(
+    sort(unique(Study)),
+    collapse = ", "
+  ),
+  by = .(DTXSID, Species)]
+
+  #Melt to longer format. The effect will be as though we row-bound two versions
+  #of DF together: one with the original single references, and one with
+  #comma-separated combined References. There is one column "Study_type" that
+  #contains either "Study" or "Study_pooled", and then one column "Study" that
+  #contains the studyID or the comma-separated list of study IDs.
+  cvt1 <- melt(cvt,
+              measure.vars = c("Study", "Study_pooled"),
+              variable.name = "Study_type",
+              value.name = "Study")
+
+  #There will be duplicated rows for single-study analyses, because
+  #"Study_pooled" (the comma-separated list of study IDs) is the same as "Study"
+  #(the individual study ID) for these analyses. Remove the duplicated rows.
+  cvt1 <- unique(cvt1[, .(DTXSID, Compound, Species, Study,Reference,
+                        Route, Dose, iv, Media, Time, Value, LOQ, Value_SD, N_Subjects)])
+
+  cvt_fit <- pk_params[cvt1, 
+                    on = c("DTXSID" = "DTXSID",
+                            "Species" = "Species",
+                            "Studies.Analyzed" = "Study"),
+                     allow.cartesian = TRUE]
 ```
@@
 ```{r}
-
-#plot all models
-tmp <- mapply(plot_fit,
-              DTXSID_in = plot_table$DTXSID,
-                     Species_in = plot_table$Species,
-              MoreArgs = list(
+cvt_fit[,
+        plot_fit(DTXSID = unique(DTXSID),
+                 Species_in = unique(Species),
+                 DFsub = .SD,
                  model_in = "all",
                  Analysis_Type_in = "Joint",
-                     DF = cvt,
-                     pk_fit = pk_fit,
                  n_interp_time = 10,
@@
                      log10_scale_time = FALSE,
-                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly")
-                     )
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly",
+                 verbose = TRUE),
+        by = .(DTXSID,
+               Species),
+        .SDcols = names(cvt_fit)]
 

### 2023-01-12 Working Rmds/MainAnalysis.Rmd
note on weird fit

@@
 ```
+
+# Test case
+
+DTXSID1022265 (Alachlor) is an example of one chemical where there is only one Reference ID, but the PO and IV data are on totally different scales -- IV concentration/dose ranges from 1e-3 to 1e-1, but PO concentration/dose ranges from 1e-5 to 1e-4.
+Now that we are fitting on natural scale, this means that with reference-specific sigma, the curve really only fits the IV data, because sigma is so large compared to the PO data scale.
+This results in a too-small Fgutabs estimate that does not fit the peak very well.
+But with "study" specific sigma -- chemical + species + reference + route + media -- the PO sigma can be on a different order than the IV sigma, and is.
+
+Another possible thing to try is to go back to fitting on the log scale.
+I had switched to the natural scale because I wasn't sure how to derive the "summary" parameterization of the residual distribution for the log scale.
+But I could try again.

### 2023-01-12 Working Rmds/MainAnalysis.Rmd
Add argument fit_conc_dose to control whether to fit dose-normalized concentrations or non-dose-normalized concentrations.

@@
     preprocess = FALSE,
+    fit_conc_dose = TRUE,
+    rescale_time = TRUE,
     optimx_args = list(
@@
       preprocess = FALSE,
+         fit_conc_dose = TRUE,
+    rescale_time = TRUE,
       optimx_args = list(

### 2023-01-12 Working Rmds/MainAnalysis.Rmd
Add argument "study_def" to allow user to specify which variables define a "study" by their unique combinations.

@@
                        impute_sd = TRUE,
+                       study_def = c("DTXSID", "Species", "Reference", "Route", "Media"),
                        suppress.messages = FALSE)

### 2023-01-17 Working Rmds/summary_loglike.Rmd
Add Rmd to explain the details of deriving the function for the summary log-likelihood

---
title: "Log-likelihood for summary data"
author: "Caroline Ring"
date: "2022-12-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

Imagine we have $N$ observations of a dependent (response) variable, $\boldsymbol{z_1}, \boldsymbol{z_2}, \ldots, \boldsymbol{z_i), \ldots, \boldsymbol{z_N}$. Each of these corresponds to one or more independent predictor variables, $\boldsymbol{x_1}, \ldots, \boldsymbol{x_i}, \ldots, \boldsymbol{x_N}$.

The $i^{th}$ observation is a summary composed of three values: the sample mean, sample standard deviation, and count of a sample of {M_i} underlying individual-subject observations.

$$ \boldsymbol{z_i} =  \left(
\begin{array}{c}
\bar{y}_i  \\
s_i \\
M_i\\
\end{array} 
\right) $$

where

$$ \boldsymbol{y_i} = \left(
\begin{array}{c}
y_{i1} \\
\cdots \\
y_{ij}\\
\cdots \\
y_{iM_i} \\
\end{array} 
\right) $$

For example, this might be a toxicokinetic study where, say, 36 rats were divided into 6 groups, and each group was dosed at a different level, resulting in 6 dose groups. Blood was drawn from the animals in each dose group at a series of time points, and the concentration of chemical X was analyzed. For each dose group and each time point, the mean and standard deviation of concentrations was reported. In this case, group $i$ represents one dose and one time point.

# Definitions of sample mean and sample variance

The sample mean and sample variance (or SD) were computed from the original individual-level data using the following definitions.

## Sample mean

$$ \bar{y}_i = \frac{1}{M_i} \sum_{j=1}^{M_i} y_{ij} $$
## Sample variance

$$ s_i^2 = \frac{1}{M_i - 1} \sum_{j=1}^{M_i} \left( y_{ij} - \bar{y}_i \right) ^2$$

# Normal log-likelihood

Assume we have a model that predicts a value $\mu_i$ for the $i^{th}$ observation, given the independent (predictor) variables $\boldsymbol{x_i}$ and some vector of parameters $\boldsymbol{\theta}$.

$$ \mu_i = f(\boldsymbol{x_i}; \boldsymbol{\theta}) $$

In the example of a TK study, $f$ might be a TK model -- e.g. a 1-compartment or 2-compartment model.

Our goal is to get the maximum-likelihood estimates of the parameters $\boldsymbol{\theta}$ -- in other words, the parameter values that make it most likely that the model would produce the data actually observed.

To do that we need to formulate the likelihood of the data given the parameters.

In this case, we assume a zero-mean normal distribution of the residual errors. This is equivalent to assuming the observed values are normally distributed around a mean given by the predicted values.

Write this likelihood function for individual $j$ in group $i$. This is just the normal probability density function.

$$ L_{ij} = \frac{1}{\sigma \sqrt{2 \pi}} \exp \left[ \frac{-1}{2} \left( \frac{y_{ij} - \mu_i}{\sigma} \right) ^2 \right] $$

## Log-likelihood for individual subjects in group i

It's usually more convenient to work with the log-likelihood, so log-transform it.

$$LL_{ij} = \log \left( \frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2} \left( \frac{y_{ij} - \mu_i}{\sigma} \right) ^2 $$
## Total log-likelihood of group i

The joint log-likelihood over all subjects in group $i$ is just the sum of individual log-likelihoods.

$$ LL_i = \sum_{j=1}^{M_i} LL_{ij} =  \sum_{j=1}^{M_i} \left[ \log \left( \frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2} \left( \frac{y_{ij} - \mu_i}{\sigma} \right) ^2 \right]$$
Breaking apart the two terms inside the summation (square brackets), and expanding the square in the second term, this becomes

$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2 \sigma^2} \left[\sum_{j=1}^{M_i} \left( y_{ij}^2 - 2 \mu_i y_{ij} + \mu_i^2  \right) \right]  $$
Further splitting apart the terms inside the summation (square brackets), this becomes

$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
\frac{-1}{2 \sigma^2} \sum_{j=1}^{M_i} y_{ij}^2 + \\
\frac{2 \mu_i}{2 \sigma^2} \sum_{j=1}^{M_i} y_{ij} + \\
\frac{-\mu_i^2 M_i}{2 \sigma^2} $$

Substitute in the definition of the sample mean:

$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
\frac{-1}{2 \sigma^2} \sum_{j=1}^{M_i} y_{ij}^2 + \\
\frac{2 \mu_i}{2 \sigma^2} M_i \bar{y}_i + \\
\frac{-\mu_i^2 M_i}{2 \sigma^2} $$

Using the definitions of the sample variance and sample mean, it can be shown (see the Appendix) that

$$ \sum_{j=1}^{M_i}  y_{ij}^2 = \left(M_i - 1 \right)  s_i^2 + M_i \bar{y}_i^2  $$
Substitute this back into the log-likelihood:

$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
\frac{-1}{2 \sigma^2} \left[ \left(M_i - 1 \right)  s_i^2 + M_i \bar{y}_i^2 \right] + \\
\frac{2 \mu_i}{2 \sigma^2} M_i \bar{y}_i + \\
\frac{-\mu_i^2 M_i}{2 \sigma^2} $$

This simplifies to

$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
\frac{-1}{2 \sigma^2} \left( \\
\left(M_i - 1 \right)  s_i^2 + M_i \bar{y}_i^2  + \\
-2 \mu_i M_i \bar{y}_i + \\
\mu_i^2 M_i \\
\right) $$

which further simplifies to

$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
\frac{-1}{2 \sigma^2} \left( \\
\left(M_i - 1 \right)  s_i^2 + \\
M_i \left( \bar{y}_i - \mu_i \right)^2 \\
\right) $$

# Appendix

How to use the definition of the sample variance and smaple mean to show that

$$ s_i^2 = \left( \frac{1}{M_i - 1} \sum_{j=1}^{M_i}  y_{ij}^2 \right) - \frac{M_i}{M_i - 1} \bar{y}_i^2 $$

Start with the definition of the sample variance

$$ s_i^2 = \frac{1}{M_i - 1} \sum_{j=1}^{M_i} \left( y_{ij} - \bar{y}_i \right) ^2$$
Expand the square

$$ s_i^2 = \frac{1}{M_i - 1} \sum_{j=1}^{M_i} \left( y_{ij}^2 - 2 y_{ij} \bar{y}_i + \bar{y}_i^2 \right) $$

Split apart the terms in the summation

$$ s_i^2 = \frac{1}{M_i - 1} \left( \sum_{j=1}^{M_i} y_{ij}^2  - 2 \bar{y}_i  \sum_{j=1}^{M_i} y_{ij} + M_i \bar{y}_i^2 \right)$$
In the second term, substitute from the definition of the sample mean, $\sum_{j=1}^{M_i} y_{ij} = M_i \bar{y}_i $

$$ s_i^2 = \frac{1}{M_i - 1} \left( \left[ \sum_{j=1}^{M_i} y_{ij}^2 \right]  - 2 M_i \bar{y}_i^2  + M_i \bar{y}_i^2 \right) $$
This then simplifies to

$$ s_i^2 = \frac{1}{M_i - 1} \left( \left[ \sum_{j=1}^{M_i} y_{ij}^2 \right]  -  M_i \bar{y}_i^2 \right) $$
We canthen solve for $\sum_{j=1}^{M_i} y_{ij}^2$

$$ \sum_{j=1}^{M_i} y_{ij}^2 = (M_i - 1) s_i^2 + M_i \bar{y}_i^2 $$

### 2023-01-17 Working Rmds/plot_fits.Rmd
Plot fits both natural and log scale, both concentration/dose and dose-faceted concentrations.

@@
 ```{r}
-timestamp <- "2023_01_11"
+timestamp <- "2023_01_13"
 ```
@@
 cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
-timestamp,
+"2023_01_13",
 ".csv"))
@@
 
-Keep parameters only.
+Keep parameters only -- that is, drop the calculated quantities like tpeak, Cpeak, Css, total clearance, etc.
 
@@
 
-pk_params <- pk_fit[, .SD, .SDcols = c(idcols, "winmodel", all_params)]
+pk_params <- pk_fit[,
+                    .SD,
+                    .SDcols = c(idcols,
+                                "winmodel",
+                                all_params)]
 
@@
 
-Merge the parameter information with the original concentration-time info.
+Merge the parameter information with the original concentration-time data.
 
@@
   #contains the studyID or the comma-separated list of study IDs.
+cvt[, Study_orig := Study]
   cvt1 <- melt(cvt,
@@
               variable.name = "Study_type",
-              value.name = "Study")
+              value.name = "Studies.Analyzed")
 
@@
   #(the individual study ID) for these analyses. Remove the duplicated rows.
-  cvt1 <- unique(cvt1[, .(DTXSID, Compound, Species, Study,Reference,
-                        Route, Dose, iv, Media, Time, Value, LOQ, Value_SD, N_Subjects)])
+  cvt1 <- unique(cvt1[, .(DTXSID, Compound, Species, Studies.Analyzed, Reference,
+                        Route, Dose, iv, Media, Study_orig, Time,
+                        Value, LOQ, Value_SD, N_Subjects,
+                        Conc, Conc_Dose, Detect, Value_Dose,
+                        Value_SD_Dose, LOQ_Dose)])
 
@@
                             "Species" = "Species",
-                            "Studies.Analyzed" = "Study"),
+                            "Studies.Analyzed" = "Studies.Analyzed"),
                      allow.cartesian = TRUE]
+```
+
+Also prepare a table of study-specific sigmas.
+
+```{r}
+DT_1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
+DT_2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
+DT_flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))
+
+idcols <- c( "Analysis_Type",
+                                 "DTXSID",
+                                "Species",
+                                "References.Analyzed",
+                               "Studies.Analyzed")
+
+DT_all <- rbindlist(list(DT_1comp, DT_2comp, DT_flat),
+                    use.names = TRUE,
+                    fill = TRUE)
+  DT_all <- DT_all[grepl(x = param_name,
+                 pattern = "sigma"),
+           .SD, .SDcols= c(idcols, "model", "param_name", "Fitted mean", "Fitted std dev")]
+  DT_melt <- dcast(DT_all,
+                   formula = Analysis_Type + DTXSID + Species + References.Analyzed + Studies.Analyzed + param_name ~ model,
+                   value.var = "Fitted mean")
+  setnames(DT_melt,
+           unique(DT_all$model),
+           paste0("sigma.", unique(DT_all$model)))
+  DT_melt[param_name %in% "sigma", sigma_studyID := Studies.Analyzed]
+  DT_melt[!(param_name %in% "sigma"), sigma_studyID := gsub(x = param_name,
+                                                            pattern = "sigma_study_",
+                                                            replacement = "",
+                                                            fixed = TRUE)]
+  DT_melt_sd <- dcast(DT_all,
+                   formula = Analysis_Type + DTXSID + Species + References.Analyzed + Studies.Analyzed + param_name ~ model,
+                   value.var = "Fitted std dev")
+   setnames(DT_melt_sd,
+           unique(DT_all$model),
+           paste0("sigma_sd.", unique(DT_all$model)))
+ DT_melt_sd[param_name %in% "sigma", sigma_studyID := Studies.Analyzed]
+  DT_melt_sd[!(param_name %in% "sigma"), sigma_studyID := gsub(x = param_name,
+                                                            pattern = "sigma_study_",
+                                                            replacement = "",
+                                                            fixed = TRUE)]
+
+  DT_melt_all <- merge(DT_melt, DT_melt_sd, by = intersect(names(DT_melt),
+                                                           names(DT_melt_sd)))
+
+```
+
+Get SD of data for each study
+
+```{r}
+cvt_sd <- cvt_fit[, .(sd_Value_Dose = sd(Value_Dose, na.rm = TRUE)),
+        by = Study_orig]
+```
+
+Merge SD of data with fitted SDs and compare
+
+```{r}
+sd_table <- cvt_sd[DT_melt_all,
+      on = c("Study_orig" = "sigma_studyID")]
 ```
@@
 
-Get unique combinations of DTXSID and species -- each of these will be one plot.
-
-```{r}
-plot_table <- unique(pk_fit[, .(DTXSID, Species)])
-```
-
 Plot all models for the joint analysis.
@@
                  Analysis_Type_in = "Joint",
+                 plot_dose_norm = TRUE,
+                 split_dose = FALSE,
                  n_interp_time = 10,
@@
                      log10_scale_time = FALSE,
-                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly",
+                 file_suffix = "errbars_naturaly_dose_norm",
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_norm",
+                 verbose = TRUE),
+        by = .(DTXSID,
+               Species),
+        .SDcols = names(cvt_fit)]
+
+```
+Do the same, but faceting by dose.
+
+```{r}
+cvt_fit[,
+        plot_fit(DTXSID = unique(DTXSID),
+                 Species_in = unique(Species),
+                 DFsub = .SD,
+                 model_in = "all",
+                 Analysis_Type_in = "Joint",
+                 plot_dose_norm = FALSE,
+                 split_dose = TRUE,
+                 n_interp_time = 10,
+                     limit_y_axis = FALSE,
+                     log10_scale_y = FALSE,
+                     plot_errbars = TRUE,
+                     log10_scale_time = FALSE,
+                 file_suffix = "errbars_naturaly_dose_norm",
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_split",
+                 verbose = TRUE),
+        by = .(DTXSID,
+               Species),
+        .SDcols = names(cvt_fit)]
+
+```
+
+Do non-dose-faceted, but log scale.
+
+```{r}
+cvt_fit[,
+        plot_fit(DTXSID = unique(DTXSID),
+                 Species_in = unique(Species),
+                 DFsub = .SD,
+                 model_in = "all",
+                 Analysis_Type_in = "Joint",
+                 plot_dose_norm = TRUE,
+                 split_dose = FALSE,
+                 n_interp_time = 10,
+                     limit_y_axis = FALSE,
+                     log10_scale_y = TRUE,
+                     plot_errbars = FALSE,
+                     log10_scale_time = FALSE,
+                 file_suffix = "errbars_naturaly_dose_norm",
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_norm",
+                 verbose = TRUE),
+        by = .(DTXSID,
+               Species),
+        .SDcols = names(cvt_fit)]
+
+```
+
+Do dose-faceted, but log scale.
+
+```{r}
+cvt_fit[,
+        plot_fit(DTXSID = unique(DTXSID),
+                 Species_in = unique(Species),
+                 DFsub = .SD,
+                 model_in = "all",
+                 Analysis_Type_in = "Joint",
+                 plot_dose_norm = FALSE,
+                 split_dose = TRUE,
+                 n_interp_time = 10,
+                     limit_y_axis = FALSE,
+                     log10_scale_y = TRUE,
+                     plot_errbars = FALSE,
+                     log10_scale_time = FALSE,
+                 file_suffix = "errbars_naturaly_dose_norm",
+                     file_path = "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_split",
                  verbose = TRUE),

### 2023-01-20 Working Rmds/MainAnalysis.Rmd
Added option to control whether to do the following: rescale time before fit; fit log-transformed or not. Retained option to fit dose-normalized or not.

--- 2023-01-12 Working Rmds/MainAnalysis.Rmd
@@
                        impute_sd = TRUE,
-                       suppress.messages = FALSE)
+                       study_def = c("DTXSID", "Species", "Reference", "Route", "Media"),
+                       suppress.messages = TRUE)
 
@@
 
-## Flat model
-
-```{r, run_invivoPKfit_flat}
-
+```{r}
+for(this_rescale_time in c(FALSE, TRUE)){
+  for(this_fit_conc_dose in c(FALSE, TRUE)){
+    for(this_fit_log_conc in c(FALSE, TRUE)){
+      if(!(this_rescale_time %in% FALSE &
+           this_fit_conc_dose %in% FALSE &
+           this_fit_log_conc %in% FALSE)){ #already did the all FALSE case
+      for (this_model in c("flat",
+                           "1compartment",
+                           "2compartment")){
+        print(paste0("model = ", this_model, "\n",
+                     "fit_log_conc = ", this_fit_log_conc, "\n",
+                     "fit_conc_dose = ", this_fit_conc_dose, "\n",
+                     "rescale_time = ", this_rescale_time))
         system.time(
-  PK.fit.table.flat <- fit_all(
+          PK.fit.table <- fit_all(
             data.set = cvt,
-    model = "flat",
+            model = this_model,
             modelfun = "analytic",
             preprocess = FALSE,
+            fit_conc_dose = this_fit_conc_dose,
+            fit_log_conc = this_fit_log_conc,
+            rescale_time = this_rescale_time,
             optimx_args = list(
@@
             ),
-    suppress.messages = TRUE
+            suppress.messages = FALSE
           )
@@
 
-write.csv(PK.fit.table.flat, paste("../inst/ext/PK_fit_table_flat_",
+        write.csv(PK.fit.table,
+                  paste("../inst/ext/PK_fit_table_",
+                        this_model,
+                        "_fit_log_conc_",
+                        this_fit_log_conc, "_",
+                        "_fit_conc_dose_",
+                        this_fit_conc_dose, "_",
+                        "_rescale_time_",
+                        this_rescale_time, "_",
                         timestamp,
@@
 
-post_flat <- postprocess_data(PK_fit = PK.fit.table.flat,
-                               model = "flat")
+        post_table <- postprocess_data(PK_fit = PK.fit.table,
+                                       model= this_model)
 
-write.csv(post_flat,
-          paste("../inst/ext/PK_fit_postprocess_flat_",
-                                    timestamp,
-                                    ".csv",
-                                    sep=""),
-          row.names = FALSE)
+        rm(PK,fit.table)
 
-rm(PK.fit.table.flat, post_flat)
-```
-
-## 1-compartment model
-
-```{r, run_invivoPKfit_1comp}
-### do 1-Compartment fit
-system.time(
-    PK.fit.table.1comp <- fit_all(
-      data.set = cvt,
-      model = "1compartment",
-      modelfun = "analytic",
-      preprocess = FALSE,
-      optimx_args = list(
-                      "method" = "bobyqa",
-                      "itnmax" = 1e6,
-                      "control" = list("kkt" = FALSE)
-                    ),
-      suppress.messages = TRUE
-  )
-)
-
-write.csv(PK.fit.table.1comp,
-          paste("../inst/ext/PK_fit_table_1comp_",
-                                    timestamp,
-                                    ".csv",
-                                    sep=""),
-          row.names = FALSE)
-
-post_1comp <- postprocess_data(PK_fit = PK.fit.table.1comp,
-                               model = "1compartment")
-
-write.csv(post_1comp,
-          paste("../inst/ext/PK_fit_postprocess_1comp_",
-                                    timestamp,
-                                    ".csv",
-                                    sep=""),
-          row.names = FALSE)
-
-rm(PK.fit.table.1comp, post_1comp)
-
-```
-
-## 2-compartment model
-
-```{r, run_invivoPKfit_2comp}
-### do 2-Compartment fit
-system.time(
-    PK.fit.table.2comp <- fit_all(
-      data.set = cvt,
-      model = "2compartment",
-      modelfun = "analytic",
-      preprocess = FALSE,
-      optimx_args = list(
-                      "method" = "bobyqa",
-                      "itnmax" = 1e6,
-                      "control" = list("kkt" = FALSE)
-                    ),
-      suppress.messages = TRUE
-    )
-)
-
-write.csv(PK.fit.table.2comp, paste("../inst/ext/PK_fit_table_2comp_",
+        write.csv(post_table,
+                  paste("../inst/ext/PK_fit_postprocess_",
+                        this_model,
+                        "_fit_log_conc_",
+                        this_fit_log_conc, "_",
+                        "_fit_conc_dose_",
+                        this_fit_conc_dose, "_",
+                        "_rescale_time_",
+                        this_rescale_time, "_",
                         timestamp,
@@
 
-post_2comp <- postprocess_data(PK_fit = PK.fit.table.2comp,
-                               model = "2compartment")
-
-write.csv(post_2comp,
-          paste("../inst/ext/PK_fit_postprocess_2comp_",
-                                    timestamp,
-                                    ".csv",
-                                    sep=""),
-          row.names = FALSE)
-
-rm(PK.fit.table.2comp, post_2comp)
+        rm(post_table)
+      } #end loop over models
+      } #end if not all FALSE
+    } #end loop over this_fit_log_conc
+  } #end loop over this_fit_conc_dose
+} #end loop over this_rescale_time
 ```
-
-# Test case
-
-DTXSID1022265 (Alachlor) is an example of one chemical where there is only one Reference ID, but the PO and IV data are on totally different scales -- IV concentration/dose ranges from 1e-3 to 1e-1, but PO concentration/dose ranges from 1e-5 to 1e-4.
-Now that we are fitting on natural scale, this means that with reference-specific sigma, the curve really only fits the IV data, because sigma is so large compared to the PO data scale.
-This results in a too-small Fgutabs estimate that does not fit the peak very well.
-But with "study" specific sigma -- chemical + species + reference + route + media -- the PO sigma can be on a different order than the IV sigma, and is.
-
-Another possible thing to try is to go back to fitting on the log scale.
-I had switched to the natural scale because I wasn't sure how to derive the "summary" parameterization of the residual distribution for the log scale.
-But I could try again.

### 2023-01-20 Working Rmds/summary_loglike_lognormal.Rmd
Added option to control whether to do the following: rescale time before fit; fit log-transformed or not. Retained option to fit dose-normalized or not.

--- 2023-01-17 Working Rmds/summary_loglike.Rmd
@@
 
-$$ L_{ij} = \frac{1}{\sigma \sqrt{2 \pi}} \exp \left[ \frac{-1}{2} \left( \frac{y_{ij} - \mu_i}{\sigma} \right) ^2 \right] $$
+$$ L_{ij} = \frac{1}{\sigma \sqrt{2 \pi}} \exp \left[ \frac{-1}{2} \left( \frac{\log y_{ij} -  \mu_i}{\sigma} \right) ^2 \right] $$
 
@@
 
-$$LL_{ij} = \log \left( \frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2} \left( \frac{y_{ij} - \mu_i}{\sigma} \right) ^2 $$
+$$LL_{ij} = \log \left( \frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2} \left( \frac{\log y_{ij} -  \mu_i}{\sigma} \right) ^2 $$
 ## Total log-likelihood of group i
@@
 
-$$ LL_i = \sum_{j=1}^{M_i} LL_{ij} =  \sum_{j=1}^{M_i} \left[ \log \left( \frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2} \left( \frac{y_{ij} - \mu_i}{\sigma} \right) ^2 \right]$$
+$$ LL_i = \sum_{j=1}^{M_i} LL_{ij} =  \sum_{j=1}^{M_i} \left[ \log \left( \frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2} \left( \frac{\log y_{ij} - \mu_i}{\sigma} \right) ^2 \right]$$
 Breaking apart the two terms inside the summation (square brackets), and expanding the square in the second term, this becomes
 
-$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2 \sigma^2} \left[\sum_{j=1}^{M_i} \left( y_{ij}^2 - 2 \mu_i y_{ij} + \mu_i^2  \right) \right]  $$
+$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \frac{-1}{2 \sigma^2} \left[\sum_{j=1}^{M_i} \left( \left( \log y_{ij} \right) ^2 - 2  \mu_i \log y_{ij} + \mu_i^2  \right) \right] $$
 Further splitting apart the terms inside the summation (square brackets), this becomes
@@
 $$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
-\frac{-1}{2 \sigma^2} \sum_{j=1}^{M_i} y_{ij}^2 + \\
-\frac{2 \mu_i}{2 \sigma^2} \sum_{j=1}^{M_i} y_{ij} + \\
+\frac{-1}{2 \sigma^2} \sum_{j=1}^{M_i} \left( \log y_{ij} \right)^2 + \\
+\frac{2 \mu_i}{2 \sigma^2} \sum_{j=1}^{M_i} \log y_{ij} + \\
 \frac{-\mu_i^2 M_i}{2 \sigma^2} $$
 
-Substitute in the definition of the sample mean:
+Here is where things get complicated with a log-normal distribution.
+With a normal distribution, we could substitute in the definition of the sample mean for $\sum y_{ij}$.
+With a log-normal distribution, we instead have $\sum \log y_{ij}$, which does not correspond to the definition of the sample mean.
+At best we could do the log of the sample mean -- but that doesn't give us what we are looking for.
+
+$$\log \bar{y}_i = \log \sum_{j=1}^{M_i} y_{ij} \neq \sum_{j=1}^{M_i} \log y_{ij}$$
+If log-scale population mean is $m_i$ and log-scale standard deviation is $s_i$, and sample mean is $\bar{y}_i$ and sample standard deviation is $S_i$, then
+
+$$ m_i = \log \frac{\bar{y}_i^2}{\sqrt{S_i^2 + \bar{y}_i^2}} = \frac{1}{M_{i}} \sum_{j=1}^{M_i} \log y_{ij}$$
+and
+
+$$ s_i = \sqrt{ \log \left( 1 + \frac{S_i^2}{\bar{y}_i^2} \right)} = \sqrt{ \frac{1}{M_i - 1} \sum_{i=1}^{M_i} (\log y_{ij} - m_i)^2}$$
+
+Substitute in the definition of the log-scale mean for $\sum_{j=1}^{M_i} \log y_{ij}$
 
 $$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
-\frac{-1}{2 \sigma^2} \sum_{j=1}^{M_i} y_{ij}^2 + \\
-\frac{2 \mu_i}{2 \sigma^2} M_i \bar{y}_i + \\
+\frac{-1}{2 \sigma^2} \sum_{j=1}^{M_i} \log y_{ij}^2 + \\
+\frac{2 \mu_i}{2 \sigma^2} M_i \log \frac{\bar{y}_i^2}{\sqrt{S_i^2 + \bar{y}_i^2}} + \\
 \frac{-\mu_i^2 M_i}{2 \sigma^2} $$
 
-Using the definitions of the sample variance and sample mean, it can be shown (see the Appendix) that
+Using the definitions of the log-scale sample variance and log-scale sample mean, it can be shown that
 
-$$ \sum_{j=1}^{M_i}  y_{ij}^2 = \left(M_i - 1 \right)  s_i^2 + M_i \bar{y}_i^2  $$
+$$ \sum_{j=1}^{M_i}  \left( \log y_{ij} \right)^2 = \left(M_i - 1 \right)  s_i^2 + M_i m_i^2 = (M_i -1) \log \left( 1 + \frac{S_i^2}{\bar{y}_i^2} \right) + M_i  \left(\log \frac{\bar{y}_i^2}{\sqrt{S_i^2 + \bar{y}_i^2}}\right)^2 $$
 Substitute this back into the log-likelihood:
@@
 $$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
-\frac{-1}{2 \sigma^2} \left[ \left(M_i - 1 \right)  s_i^2 + M_i \bar{y}_i^2 \right] + \\
-\frac{2 \mu_i}{2 \sigma^2} M_i \bar{y}_i + \\
+\frac{-1}{2 \sigma^2} \left( (M_i -1) \log \left( 1 + \frac{S_i^2}{\bar{y}_i^2} \right) + M_i  \left(\log \frac{\bar{y}_i^2}{\sqrt{S_i^2 + \bar{y}_i^2}}\right)^2 \right) + \\
+\frac{2  \mu_i}{2 \sigma^2} M_i \log \frac{\bar{y}_i^2}{\sqrt{S_i^2 + \bar{y}_i^2}} + \\
 \frac{-\mu_i^2 M_i}{2 \sigma^2} $$
 
-This simplifies to
-
-$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
-\frac{-1}{2 \sigma^2} \left( \\
-\left(M_i - 1 \right)  s_i^2 + M_i \bar{y}_i^2  + \\
--2 \mu_i M_i \bar{y}_i + \\
-\mu_i^2 M_i \\
-\right) $$
-
-which further simplifies to
-
-$$ LL_i = M_i \log \left(\frac{1}{\sigma \sqrt{2 \pi}} \right) + \\
-\frac{-1}{2 \sigma^2} \left( \\
-\left(M_i - 1 \right)  s_i^2 + \\
-M_i \left( \bar{y}_i - \mu_i \right)^2 \\
-\right) $$
+This looks horrible, but I think it is correct.
 

### 2023-01-20 Working Rmds/plot_fits.Rmd
Adding functions to evaluate goodness of fit and plot fits and residuals in various ways.

--- 2023-01-10 Working Rmds/plot_fits.Rmd
@@
 ```{r}
-timestamp <- "2023_01_06"
+timestamp <- "2023_01_17"
 ```
@@
 ```{r, load_cvt, eval = TRUE}
-cvt <- fread("../inst/ext/cvt_preprocessed_2023_01_06.csv")
+cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
+"2023_01_13",
+".csv"))
 cvt[, Reference:=as.character(Reference)]
@@
 
-PK.fit.table.1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
-PK.fit.table.2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
-PK.fit.table.flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))
+fit_1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
+fit_2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
+fit_flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))
 
 #pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
-```
-
-Rowbind together all of the fitted parameter tables into one big one.
-```{r}
-pk_fit <- rbindlist(list("1comp" = PK.fit.table.1comp,
-                         "2comp" = PK.fit.table.2comp,
-                         "flat" = PK.fit.table.flat),
-                    use.names = TRUE,
-                    fill = TRUE)
-
-rm(PK.fit.table.1comp,
-   PK.fit.table.2comp,
-   PK.fit.table.flat)
-```
-
-Get a table of the winning model for each dataset (the one with minimum AIC).
-
-```{r}
-tmp <- unique(pk_fit[, .(DTXSID, Species, Analysis_Type, References.Analyzed, model, AIC)])
-
-#sort AIC from smallest to largest within each dataset, putting NAs last
-setorder(tmp, DTXSID, Species, Analysis_Type, References.Analyzed, AIC, na.last = TRUE)
-#the winning model will now be listed first within each dataset (smallest AIC)
-model_win <- tmp[, .(winmodel = model[1]), by = .(DTXSID, Species, Analysis_Type, References.Analyzed)]
-pk_fit <- model_win[pk_fit, on = c("DTXSID", "Species", "Analysis_Type", "References.Analyzed")]
-pk_fit[, winning:=(model == winmodel)]
-
 ```
@@
 
-Would also like to plot uncertainty in predictions based on uncertainty in parameter estimates.
+Plot all models together for the joint analysis.
 
-Plot versions:
-- Winning model only
-- One model at a time
-- All three models on same plot
-
-Get unique combinations of DTXSID and species -- each of these will be one plot.
+Produce a data.table with unique combinations of DTXSID, species, analysis type, and studies analyzed.
 
 ```{r}
-plot_table <- unique(pk_fit[, .(DTXSID, Species)])
+plot_combos <- unique(fit_flat[Analysis_Type %in% "Joint", .(Analysis_Type,
+                                                             DTXSID,
+                                                             Species,
+                                                             Studies.Analyzed)])
+setnames(plot_combos,
+         names(plot_combos),
+         paste(names(plot_combos),
+               "in",
+               sep = "_"))
 ```
 
-Plot all models for the joint analysis.
+Loop over the following combinations of options:
+- Log-scale y and non-log-scale y
+- Dose-normalized and split-dose
+
 ```{r}
+opts_DT <- as.data.table(expand.grid(log10_scale_y = c(TRUE, FALSE),
+                       split_dose = c(TRUE, FALSE)))
+opts_DT[, plot_errbars := !(log10_scale_y)]
+opts_DT[, plot_dose_norm := !(split_dose)]
+opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% TRUE,
+        file_suffix := "errbars_naturaly_dose_norm"]
+opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% TRUE,
+        file_path := "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_norm"]
+opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% TRUE,
+        file_suffix := "noerrbars_logy_dose_norm"]
+opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% TRUE,
+        file_path := "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_norm"]
 
-#plot all models
-tmp <- mapply(plot_fit,
-              DTXSID_in = plot_table$DTXSID,
-                     Species_in = plot_table$Species,
-              MoreArgs = list(
+opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% FALSE,
+        file_suffix := "errbars_naturaly_dose_split"]
+opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% FALSE,
+        file_path := "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_split"]
+opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% FALSE,
+        file_suffix := "noerrbars_logy_dose_split"]
+opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% FALSE,
+        file_path := "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_split"]
+```
+
+Loop over options, and within each option, loop over datasets, to plot joint analysis with all models.
+```{r}
+junk <- mapply(function(plot_errbars,
+                       log10_scale_y,
+                       plot_dose_norm,
+                       split_dose,
+                       file_suffix,
+                       file_path){
+  print(file_suffix)
+DT_plot <- plot_combos[,
+                       .(plot_obj = list(
+                         {
+                          studies_list <- strsplit(Studies.Analyzed_in,
+                               split = ", ")[[1]]
+      #get data.table of newdata to be predicted
+      #leave out DTXSID, Species columns
+      #since these will be added back in from fit_combs
+      obs_data <- cvt[DTXSID %in% DTXSID_in &
+                           Species %in% Species_in &
+                           Study %in% studies_list]
+
+      plot_fit(fit_flat = fit_flat,
+               fit_1comp = fit_1comp,
+               fit_2comp = fit_2comp,
+               DTXSID_in = DTXSID_in,
+                 Species_in = Species_in,
+                 obs_data = obs_data,
                  model_in = "all",
                  Analysis_Type_in = "Joint",
-                     DF = cvt,
-                     pk_fit = pk_fit,
+                 plot_dose_norm = plot_dose_norm,
+                 split_dose = split_dose,
                  n_interp_time = 10,
                      limit_y_axis = FALSE,
-                     log10_scale_y = FALSE,
-                     plot_errbars = TRUE,
+                     log10_scale_y = log10_scale_y,
+                     plot_errbars = plot_errbars,
                      log10_scale_time = FALSE,
-                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly")
+                 return_plot = TRUE,
+                 save_plot = TRUE,
+                 file_suffix = file_suffix,
+                     file_path = file_path,
+                 verbose = FALSE,
+                 ggsave_args = list(scale = 1,
+                                        width = 13.33,
+                                        height = 7.5,
+                                        units = "in",
+                                        dpi = 300,
+                                        limitsize = TRUE,
+                                        bg = NULL)
                  )
+                       })),
+        by = .(DTXSID_in,
+               Species_in,
+               Analysis_Type_in,
+               Studies.Analyzed_in)]
+
+#save all plots as one big paginated file
+pdf(paste0(file_path,
+              "/all_plots_",
+              file_suffix,
+              ".pdf"),
+    width = 13.33,
+                                        height = 7.5)
+print(DT_plot$plot_obj)
+dev.off()
+
+rm(DT_plot)
+
+return(0)
+},
+plot_errbars = opts_DT$plot_errbars,
+                       log10_scale_y = opts_DT$log10_scale_y,
+                       plot_dose_norm = opts_DT$plot_dose_norm,
+                       split_dose = opts_DT$split_dose,
+file_suffix = opts_DT$file_suffix,
+file_path = opts_DT$file_path)
 
 ```
-
-```{r}
-
-#plot all models
-tmp <- mapply(plot_fit,
-              DTXSID_in = plot_table$DTXSID,
-                     Species_in = plot_table$Species,
-              MoreArgs = list(
-                     model_in = "all",
-                     Analysis_Type_in = "Joint",
-                     DF = cvt,
-                     pk_fit = pk_fit,
-                     n = 101,
-                     limit_y_axis = FALSE,
-                     log10_scale_y = TRUE,
-                     plot_errbars = FALSE,
-                     log10_scale_time = FALSE,
-                     file_path = "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy")
-                     )
-
-```
-
-Problem: DTXSID0022985_rat_Joint_all does not plot any model lines. Why?
-
-```{r}
-pk_fit[DTXSID %in% "DTXSID0022985"]
-```
-
-Apparently there were no detected data points?
-
-```{r}
-cvt[DTXSID %in% "DTXSID0022985", .(Reference, Value, LOQ)]
-```
-
-Hmm. Something is very weird here. I definitely see some detected points. They are all the same reference, so it isn't that a single-reference fit did not work but a joint fit did work.
-
-Plot only the winning model
-
-```{r}
-#plot all models
-tmp <- mapply(plot_fit,
-              DTXSID_in = plot_table$DTXSID,
-                     Species_in = plot_table$Species,
-              MoreArgs = list(
-                Analysis_Type_in = c("Joint", "Separate"),
-                     model_in = "winning",
-                     fitdata = DF,
-                     pk_fit = pk_fit,
-                     file_path = "inst/ext/plots/analysis_all_model_winning/",
-                log10_scale_time = TRUE)
-                     )
-```

### 2023-01-20 invivopkfit/R/get_error_sd.R

@@ -1,0 +1,136 @@
+get_error_sd <- function(pk_fit,
+                            newdata,
+                            DTXSID_in,
+                            Species_in,
+                            Analysis_Type_in,
+                         Studies.Analyzed_in,
+                            model_in,
+                         modelfun = "analytic",
+                         fit_conc_dose = TRUE,
+                         optimx_args = list(
+                           "method" = "bobyqa",
+                           "itnmax" = 1e6,
+                           "control" = list("kkt" = FALSE)
+                         )){
+
+  newdata <- copy(newdata)
+
+  #get appropriate subset of pk_fit
+  pk_sub <- unique(pk_fit[DTXSID %in% DTXSID_in &
+                            Species %in% Species_in &
+                            Analysis_Type %in% Analysis_Type_in &
+                            Studies.Analyzed %in% Studies.Analyzed_in, ])
+
+  #this should be a one-row subset
+  if(nrow(pk_sub)>1) {
+    stop("Selected subset of pk_fit has more than one unique row!")
+  }
+
+  #get parameter names for this model
+  param_names <- get_model_paramnames(model = model_in)
+  #get appropriate columns of pk_sub -- named [param].[model]
+  param_names_dot <- paste(param_names, model_in, sep = ".")
+  #extract appropriate columns of pk_sub
+  params <- pk_sub[, .SD, .SDcols = intersect(param_names_dot,
+                                              names(pk_sub))]
+  #rename to strip the ".[model]" part
+  setnames(params,
+           param_names_dot,
+           param_names,
+           skip_absent = TRUE)
+  #set Rblood2plasma to 1, if it is there and NA
+  if("Rblood2plasma" %in% names(params)){
+    if(is.na(params$Rblood2plasma)){
+      params$Rblood2plasma <- 1
+    }
+  }
+  #convert to list
+  params <- as.list(params)
+  #remove any NA params
+  params <- params[!(sapply(params,
+                            is.na))]
+
+
+
+  #To get starting value for params: First get model-predicted concentrations
+  newdata_pred <- get_predictions(pk_fit = pk_sub,
+                                  newdata = newdata,
+                                  DTXSID_in = DTXSID_in,
+                                  Species_in = Species_in,
+                                  Analysis_Type_in = Analysis_Type_in,
+                                  Studies.Analyzed_in = Studies.Analyzed_in,
[…]

### 2023-01-20 invivopkfit/R/plot_resids.R

@@ -1,0 +1,262 @@
+#' Plot residuals from winning model
+#'
+#' Make diagnostic plots of residuals from the winning TK model for a dataset
+#'
+#' For a given dataset (DTXSID and Species), this function calculates the
+#' predicted concentrations from the winning (best-fit by lowest AIC) TK model.
+#' Then it computes the residuals (observed - predicted), both dose-normalized
+#' and non-dose-normalized. Then it creates a grid of plots with two rows and
+#' three columns. The first row shows non-dose-normalized residuals; the second
+#' row shows dose-normalized residuals. The first column plots residuals vs.
+#' observed concentration. The second column plots residuals vs. dose. The third
+#' column plots residuals vs. time.
+#'
+#' These plots can be used to diagnose heteroscedasticity in residual errors
+#' from the best-fit model.
+#'
+#' @param cvt_pre Original concentration vs. time data, pre-processed using
+#'   `preprocess_data()`.
+#' @param fit_flat Fitting output for the flat model: the output of `fit_all()`
+#'   with `model = "flat"`
+#' @param fit_1comp Fitting output for the 1-compartment model: the output of
+#'   `fit_all()` with `model = "1compartment"`
+#' @param fit_2comp Fitting output for the 2-compartment model: the output of
+#'   `fit_all()` with `model = "2compartment"`
+#' @return A `data.table` of goodness-of-fit measures for each dataset, each
+#'   model, and each analysis (joint, separate, and pooled)
+#' @author Caroline Ring
+#' @export
+#' @import data.table patchwork
+plot_resids <- function(cvt_pre,
+                         fit_flat,
+                         fit_1comp,
+                         fit_2comp,
+                        return_plots = FALSE,
+                        save_indiv_plots = TRUE,
+                        save_combined_plots = TRUE,
+                        file_path = "../inst/ext/plots/resid_plots",
+                        file_suffix = NULL,
+                        file_format = "pdf",
+                        ggsave_args = list(scale = 1,
+                                           width = 13.33,
+                                           height = 7.5,
+                                           units = "in",
+                                           dpi = 300,
+                                           limitsize = TRUE,
+                                           bg = NULL)){
+
+ pred_DT <- get_all_predictions(cvt_pre =cvt_pre,
+                               fit_flat = fit_flat,
+                               fit_1comp = fit_1comp,
[…]

### 2023-01-23 Working Rmds/MainAnalysis.Rmd
Added several functions to evaluate fits.
preprocess_data() now retains CvTdb series and study IDs.

Updated documentation for several functions.

@@
   "N_Subjects" = "series.n_subjects_in_series",
-  "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
+  "Value_SD" = "conc_time_values.conc_sd_normalized", #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
+  "Study_ID" = "studies.id",
+  "Series_ID" = "series.id"
   )

### 2023-01-23 Working Rmds/summary_loglike_lognormal.Rmd
Added several functions to evaluate fits.
preprocess_data() now retains CvTdb series and study IDs.

Updated documentation for several functions.

@@
 This looks horrible, but I think it is correct.
-
-# Appendix
-
-How to use the definition of the sample variance and smaple mean to show that
-
-$$ s_i^2 = \left( \frac{1}{M_i - 1} \sum_{j=1}^{M_i}  y_{ij}^2 \right) - \frac{M_i}{M_i - 1} \bar{y}_i^2 $$
-
-Start with the definition of the sample variance
-
-$$ s_i^2 = \frac{1}{M_i - 1} \sum_{j=1}^{M_i} \left( y_{ij} - \bar{y}_i \right) ^2$$
-Expand the square
-
-$$ s_i^2 = \frac{1}{M_i - 1} \sum_{j=1}^{M_i} \left( y_{ij}^2 - 2 y_{ij} \bar{y}_i + \bar{y}_i^2 \right) $$
-
-Split apart the terms in the summation
-
-$$ s_i^2 = \frac{1}{M_i - 1} \left( \sum_{j=1}^{M_i} y_{ij}^2  - 2 \bar{y}_i  \sum_{j=1}^{M_i} y_{ij} + M_i \bar{y}_i^2 \right)$$
-In the second term, substitute from the definition of the sample mean, $\sum_{j=1}^{M_i} y_{ij} = M_i \bar{y}_i $
-
-$$ s_i^2 = \frac{1}{M_i - 1} \left( \left[ \sum_{j=1}^{M_i} y_{ij}^2 \right]  - 2 M_i \bar{y}_i^2  + M_i \bar{y}_i^2 \right) $$
-This then simplifies to
-
-$$ s_i^2 = \frac{1}{M_i - 1} \left( \left[ \sum_{j=1}^{M_i} y_{ij}^2 \right]  -  M_i \bar{y}_i^2 \right) $$
-We canthen solve for $\sum_{j=1}^{M_i} y_{ij}^2$
-
-$$ \sum_{j=1}^{M_i} y_{ij}^2 = (M_i - 1) s_i^2 + M_i \bar{y}_i^2 $$

### 2023-01-23 invivopkfit/R/get_predictions.R

@@ -4,9 +4,16 @@
 #' route, and medium), get predicted concentrations and AUCs.
 #'
 #' @param pk_fit A table of fitted PK parameters, as produced by
-#'   `postprocess_data()`.
-#' @param newdata A `data.table` which must contain variables named
-#'   `Time`, `Dose`, `iv`, and `Media`.
+#'   `postprocess_data()`. Must contain variables `DTXSID`, `Species`,
+#'   `Analysis_Type`, and `Studies.Analyzed`. Must also contain variables
+#'   corresponding to the parameters of the model specified in argument
+#'   `model_in`, as required for the route and media of data in `newdata` (as
+#'   given by [get_model_paramnames()]). These variables must be named as
+#'   `[param].[model]`. For example, for the 1-compartment model, if `newdata`
+#'   contains only IV-dosing data measured in plasma, then `pk_fit` must contain
+#'   variables named `kelim.1compartment` and `Vdist.1compartment`.
+#' @param newdata A `data.table` which must contain variables named `Time`,
+#'   `Dose`, `iv`, and `Media`.
 #' @param DTXSID_in The DSSTox Substance ID for which to evaluate
 #' @param Species_in The species for which to evaluate
 #' @param Analysis_Type_in The analysis type that produced the fit being
@@ -18,6 +25,8 @@
 #' @return A `data.table`, the same number of rows as `newdata`, with variables
 #'   `pred_conc` and `pred_auc` corresponding to the model-predicted
 #'   concentration and AUC.
+#' @author Caroline Ring
+#' @export
 get_predictions <- function(pk_fit,
                             newdata,
                             DTXSID_in,

### 2023-01-23 invivopkfit/R/postprocess_data.R

@@ -1,6 +1,6 @@
 #' Postprocess fitted PK models
 #'
-#' Derive quantities such as half-life, tpeak, Cpeak, Css from fitted PK models
+#' Derive quantities such as half-life, tmax, Cmax, Css from fitted PK models
 #'
 #' @param PK_fit A data.table of fitted PK parameters, as produced by `fit_all()` or `analyze_subset()`
 #' @param model The name of the relevant model: "1compartment", "2compartment", or "flat"
@@ -21,7 +21,8 @@ postprocess_data <- function(PK_fit,
                         model + References.Analyzed + Studies.Analyzed +
                         N_Routes + N_Media +
                        time_units_fitted +
-                        AIC ~ param_name,
+                        AIC +
+                       rescale_time + fit_log_conc + fit_conc_dose ~ param_name,
                       value.var = "Fitted mean")
     #also get the SD for each fitted param
     PK_flat_sd <- dcast(PK_fit[model %in% "flat" &
@@ -31,7 +32,8 @@ postprocess_data <- function(PK_fit,
                            model + References.Analyzed + Studies.Analyzed +
                            N_Routes + N_Media +
                           time_units_fitted +
-                           AIC ~ param_name,
+                           AIC+
+                          rescale_time + fit_log_conc + fit_conc_dose ~ param_name,
                          value.var = "Fitted std dev")
     #append "_sd" for these params
     setnames(PK_flat_sd,
@@ -56,7 +58,7 @@ postprocess_data <- function(PK_fit,
   }else if(model %in% "1compartment"){
   #for 1-compartment model:
 
-  #Calculate: total clearance; half-life; tpeak; Cpeak
+  #Calculate: total clearance; half-life; tmax; Cmax
   #and Css for a dose of 1 mg/kg/da
 
     #reshape wide (one column for each parameter)
@@ -67,7 +69,8 @@ postprocess_data <- function(PK_fit,
                       model + References.Analyzed + Studies.Analyzed +
                       time_units_fitted +
                       N_Routes + N_Media +
-                      AIC ~ param_name,
+                      AIC+
+                      rescale_time + fit_log_conc + fit_conc_dose ~ param_name,
                     value.var = "Fitted mean")
   #also get the SD for each fitted param
   PK_1comp_sd <- dcast(PK_fit[model %in% "1compartment" &
[…]

### 2023-01-23 Working Rmds/summary_loglike_lognormal.Rmd
Correctly log-transform predictions if log = TRUE specified when computing RMSE, R-squared, etc.
Update documentation.

@@
 This looks horrible, but I think it is correct.
+
+# Appendix: Error in log-scale moments from arithmetic moments, a simulation study
+
+How much error is there in estimating the log-scale moments (mean and SD of log-transformed observations) from the arithmetic moments (mean and SD of natural-scale observations)?
+
+We can get an idea using a simulation study.
+
+Take a log-normal distribution with known log-scale mean and SD.
+
+Draw some number of samples from this distribution.
+
+Calculate the sample mean and SD of the log-scaled samples, and of the natural-scale samples.
+
+Repeat these steps some large number of times.
+
+Compare the log-scale sample means and SDs to the natural-scale sample means and SDs.
+
+Write a function to draw the samples and calculate the sample moments:
+
+```{r}
+get_sample_moments <- function(meanlog, sdlog, n_samp){
+  #samples
+  y <- rlnorm(n = n_samp, meanlog = meanlog, sdlog = sdlog)
+  #log-transformed samples
+  ylog <- log(y)
+  return(c("sample_mean" = mean(y),
+           "sample_sd" = sd(y),
+           "sample_meanlog" = mean(ylog),
+           "sample_sdlog" = sd(ylog),
+           "sample_n" = n_samp))
+}
+```
+
+Choose values for meanlog, sdlog, and n_samp
+```{r}
+meanlog <- 0
+sdlog <- 1
+n_samp <- 7
+```
+
+Set a seed for reproducibility, and generate the values
+
+```{r}
+set.seed(42)
+n_rep <- 1000
+samp <- replicate(n = n_rep,
+          expr = get_sample_moments(meanlog = meanlog,
+                                    sdlog = sdlog,
+                                    n_samp = n_samp))
+samp <- t(samp)
+samp <- as.data.frame(samp)
+```
+
+Calculate the estimated log-scale sample moments from the arithmetic sample moments
+
+```{r}
+samp[c("est_sample_meanlog",
+       "est_sample_sdlog")] <- convert_summary_to_log(sample_mean = samp$sample_mean,
+                                                                   sample_SD = samp$sample_sd)
+```
+
+Now, plot the estimated log-scale moments vs. the "actual" log-scale moments.
+
+Log-scale sample mean. The "true" population log-scale mean (0.0) is indicated by vertical and horizontal dashed lines.
+
+```{r}
+ggplot(data = samp) +
+  geom_point(aes(x = sample_meanlog,
+                 y = est_sample_meanlog),
+             color = "gray50") +
+  geom_abline(intercept = 0, slope = 1, color = "black") +
+  geom_hline(yintercept = 0, linetype = 2) +
+  geom_vline(xintercept = 0, linetype = 2) +
+  xlab("Actual log-scale sample mean") +
+  ylab("Estimated log-scale sample mean") +
+  ggtitle("Estimated vs. actual log-scale sample mean, n = 7") +
+  theme_bw()
+```
+
+The estimated log-scale sample mean usually overestimates the "true" log-scale sample mean (most points are above the identity line).
+
+Log-scale sample SD. The "true" population log-scale SD (1.0) is indicated by vertical and horizontal dashed lines.
+
+```{r}
+ggplot(data = samp) +
+  geom_point(aes(x = sample_sdlog,
+                 y = est_sample_sdlog),
+             color = "gray50") +
+  geom_abline(intercept = 0, slope = 1, color = "black") +
+    geom_hline(yintercept = 1, linetype = 2) +
+  geom_vline(xintercept = 1, linetype = 2) +
+  xlab("Actual log-scale sample SD") +
+  ylab("Estimated log-scale sample SD") +
+  ggtitle("Estimated vs. actual log-scale sample SD, n = 7") +
+  theme_bw()
+```
+
+The estimated log-scale sample SD usually underestimates the actual log-scale sample SD (most points are below the identity line).
+
+```{r}
+summary(lm(est_sample_sdlog ~ sample_sdlog, data = samp))
+```

### 2023-01-30 Working Rmds/evaluate_fits.Rmd
Evaluating residuals by RMSE, R-squared, and overall error SD. Evaluating TK stats by tmax, Cmax, AUC. All evaluations under combinations of the following fitting conditions: log-transform TRUE/FALSE, dose-normalization TRUE/FALSE, rescale time TRUE/FALSE. Residuals for each fitting condition also calculated in all of the following combinations: log-scale residuals TRUE/FALSE, dose-normalized residuals TRUE/FALSE. This way we can compare apples to apples.

---
title: "Evaluate fits"
author: "Caroline Ring"
date: "2023-01-23"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(results = TRUE)
knitr::opts_chunk$set(message = FALSE)
```

```{r, include = FALSE}
library(tidyverse)
library(data.table)
library(readxl)
devtools::load_all("../invivopkfit")
```

# Introduction

This document contains code to evaluate the goodness-of-fit of the models fit to data in `MainAnalysis.Rmd`.

# Import and preprocess CvTdb data

## Import CvTdb data

Read in CvTdb data that was pulled and normalized in `pulling_oral_iv_data_cvtdb.Rmd`.

```{r, load_cvt, eval = TRUE}
cvt_data <- fread("../inst/ext/cvt_data_2023_01_05.csv")
```

## Timestamp
Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.

```{r}
timestamp <- format(Sys.time(), "%Y_%m_%d")
```

## Settings for pre-processing data

List of new_name = old_name to supply for preprocessing data

```{r}
names_list <- list(
  "Compound_Dosed" = "studies.test_substance_name_original",
  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
  "Compound_Analyzed" = "series.analyte_name_original",
  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
  "Reference" = "documents_reference.id",
  "Extraction" = "documents_extraction.id",
  "Species" = "subjects.species",
  "Weight" ="subjects.weight_kg",
  "Weight.Units" = NULL,
  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
  "Dose.Units" = NULL,
  "Time" = "conc_time_values.time_hr",
  "Time.Units" = NULL,
  "Media" = "series.conc_medium_normalized",
  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
  "Value.Units" = NULL,
  "Route" = "studies.administration_route_normalized",
  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Subject" = "subjects.id",
  "N_Subjects" = "series.n_subjects_in_series",
  "Value_SD" = "conc_time_values.conc_sd_normalized", #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Study_ID" = "studies.id",
  "Series_ID" = "series.id"
  )
```

List of default values for new columns added in preprocessing data

```{r}
defaults_list <- list(
                      "Weight.Units" = "kg",
                      "Dose.Units" = "mg/kg",
                      "Time.Units" = "hours",
                      "Value.Units" = "mg/L")
```

## Preprocess data

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =names_list,
                       defaults_list =   defaults_list,
                       ratio_conc_to_dose = 1,
                       calc_loq_factor = 0.45,
                       routes_keep = c("po", "iv"),
                       media_keep = c("blood", "plasma"),
                       impute_loq = TRUE,
                       impute_sd = TRUE,
                       study_def = c("DTXSID", "Species", "Reference", "Route", "Media"),
                       suppress.messages = TRUE)

#save pre-processed data
# write.csv(cvt,
#           paste0("../inst/ext/cvt_preprocessed_",
#                  timestamp,
#           ".csv"),
#           row.names = FALSE)

cvt <- as.data.table(cvt)
rm(cvt_data)
```

```{r}
cvt[, Conc_SD := Value_SD]
cvt[, Conc_SD_Dose := Value_SD_Dose]
```

# Evaluate fits

## Table of all fit options

This table defines all combinations of fitting options that were tried.

```{r}
fit_opts <- 
  as.data.table(
    expand.grid(
  rescale_time = c(FALSE, TRUE),
  fit_conc_dose = c(FALSE, TRUE),
  fit_log_conc = c(FALSE, TRUE))
  )

```

# Evaluate residuals for each set of fitting options

```{r}
eval_DT <- fit_opts[,
                  {
                    print(
                      paste("fit_log_conc = ",
                        fit_log_conc,
                        "; fit_conc_dose = ",
                        fit_conc_dose,
                        "; rescale_time = ",
                        rescale_time)
                    )

  #get fitting outputs file names
  fit_outputs <- dir(path = "../inst/ext",
      pattern = paste0("PK_fit_table_",
                       ".+",
        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "_fit_conc_dose_",
                        fit_conc_dose, "_",
                        "_rescale_time_",
                        rescale_time, "_"
                       ))

  fit_outputs <- paste0("../inst/ext/",
                        fit_outputs)

  cat(paste0(paste(fit_outputs,
              collapse = "\n"), "\n"))

  #read in fitting outputs
  #flat model
  fit_flat <- fread(grep(x = fit_outputs,
                         pattern = "flat",
                         value = TRUE))
  #1compartment model
  fit_1comp <- fread(grep(x = fit_outputs,
                         pattern = "1compartment",
                         value = TRUE))
  #2compartment model
   fit_2comp <- fread(grep(x = fit_outputs,
                         pattern = "2compartment",
                         value = TRUE))

   fit_flat[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

    fit_1comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

       fit_2comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

   cat("Evaluating residuals...\n")

   #evaluate residuals
   this_eval_DT <- evaluate_resids(cvt_pre = cvt,
                         fit_flat = fit_flat,
                         fit_1comp = fit_1comp,
                         fit_2comp = fit_2comp,
                         fit_conc_dose = fit_conc_dose,
                         fit_log_conc = fit_log_conc,
                         optimx_args = list(
                           "method" = "bobyqa",
                           "itnmax" = 1e6,
                           "control" = list("kkt" = FALSE)
                         ),
                         verbose = TRUE)

     write.csv(this_eval_DT,
                  paste("../inst/ext/evaluate_residuals_",
                        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "fit_conc_dose_",
                        fit_conc_dose, "_",
                        "rescale_time_",
                        rescale_time, "_",
                        timestamp,
                        ".csv",
                        sep=""), row.names = FALSE)

     this_eval_DT
                  },
  by = c("fit_conc_dose", "fit_log_conc", "rescale_time")]

write.csv(eval_DT,
          paste0("../inst/ext/eval_resid_",
          timestamp,
          ".csv"),
          row.names = FALSE)
```

Evalaute TK stats

```{r}
TKstats_DT <- fit_opts[,
                  {
                    print(
                      paste("fit_log_conc = ",
                        fit_log_conc,
                        "; fit_conc_dose = ",
                        fit_conc_dose,
                        "; rescale_time = ",
                        rescale_time)
                    )

  #get fitting outputs file names
  fit_outputs <- dir(path = "../inst/ext",
      pattern = paste0("PK_fit_table_",
                       ".+",
        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "_fit_conc_dose_",
                        fit_conc_dose, "_",
                        "_rescale_time_",
                        rescale_time, "_"
                       ))

  fit_outputs <- paste0("../inst/ext/",
                        fit_outputs)

  cat(paste0(paste(fit_outputs,
              collapse = "\n"), "\n"))

  #read in fitting outputs
  #flat model
  fit_flat <- fread(grep(x = fit_outputs,
                         pattern = "flat",
                         value = TRUE))
  #1compartment model
  fit_1comp <- fread(grep(x = fit_outputs,
                         pattern = "1compartment",
                         value = TRUE))
  #2compartment model
   fit_2comp <- fread(grep(x = fit_outputs,
                         pattern = "2compartment",
                         value = TRUE))

   fit_flat[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

    fit_1comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

       fit_2comp[, c("fit_conc_dose",
                "fit_log_conc",
                "rescale_time") := .(fit_conc_dose,
                                     fit_log_conc,
                                     rescale_time)]

       cat("Evaluating TK statistics...\n")
        #evaluate TK statistics & merge with postprocessed fits
   this_TKstats_DT <- evaluate_tkstats(cvt_pre = cvt,
                         fit_flat = fit_flat,
                         fit_1comp = fit_1comp,
                         fit_2comp = fit_2comp,
                         group_by = c("DTXSID",
                                          "Species",
                                          "Route",
                                          "Media"),
                         dose_norm = TRUE)

    write.csv(this_TKstats_DT,
                  paste("../inst/ext/evaluate_tkstats_",
                        "_fit_log_conc_",
                        fit_log_conc, "_",
                        "fit_conc_dose_",
                        fit_conc_dose, "_",
                        "rescale_time_",
                        rescale_time, "_",
                        timestamp,
                        ".csv",
                        sep=""), row.names = FALSE)

     this_TKstats_DT
                  },
  by = c("fit_conc_dose", "fit_log_conc", "rescale_time")]

write.csv(TKstats_DT,
          paste0("../inst/ext/eval_TKstats_",
          timestamp,
          ".csv"),
          row.names = FALSE)

```

# Visualization and analysis

Questions to answer:

Which combination of fitting parameters best fits AUC? tmax? Cmax? Take the winning model for each combination of fitting parameters and each data set.

```{r}
tk_DT <- fread(paste0("../inst/ext/eval_TKstats_",
          "2023_01_26",
          ".csv"))
```

```{r}
tk_DT[winmodel %in% "1compartment", AUC_oral_win := AUC_inf_oral_1mgkg.1compartment]
tk_DT[winmodel %in% "1compartment", AUC_iv_win := AUC_inf_IV_1mgkg.1compartment]
tk_DT[winmodel %in% "1compartment", tmax_win := tmax_oral.1compartment]
tk_DT[winmodel %in% "1compartment", Cmax_win := Cmax_oral_1mgkg.1compartment]

tk_DT[winmodel %in% "2compartment", AUC_oral_win := AUC_inf_oral_1mgkg.2compartment]
tk_DT[winmodel %in% "2compartment", AUC_iv_win := AUC_inf_iv_1mgkg.2compartment]
tk_DT[winmodel %in% "2compartment", tmax_win := tmax_oral.2compartment]
tk_DT[winmodel %in% "2compartment", Cmax_win := Cmax_oral_1mgkg.2compartment]
```

```{r}
tk_DT_sub <- tk_DT[Analysis_Type %in% "Joint", .(fit_conc_dose, fit_log_conc, rescale_time, DTXSID, Species, Route, Media, AUC_inf_1mgkg, tmax, Cmax_1mgkg, AUC_oral_win, AUC_iv_win, tmax_win, Cmax_win, winmodel)]
```

```{r}
ggplot(tk_DT_sub[rescale_time == FALSE],
       aes(x = AUC_inf_1mgkg,
           y = AUC_oral_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (oral)") +
  ylab("Winning model-predicted AUC_inf (oral)") +
  ggtitle("AUC_inf (oral), rescale_time = FALSE")
```

Fitting on the log scale seems to result in more cases of over-predicted AUC_infinity for oral dosing.

Dose-normalizing concentration before fitting doesn't seem to make a huge difference one way or another.

How about when time was rescaled?

```{r}
ggplot(tk_DT_sub[rescale_time == TRUE],
       aes(x = AUC_inf_1mgkg,
           y = AUC_oral_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (oral)") +
  ylab("Winning model-predicted AUC_inf (oral)") +
  ggtitle("AUC_inf (oral), rescale_time = TRUE")
```

Rescaling time seems to make the overpredictions worse when they happen.

```{r}
ggplot(tk_DT_sub[rescale_time == FALSE],
       aes(x = AUC_inf_1mgkg,
           y = AUC_iv_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (IV)") +
  ylab("Winning model-predicted AUC_inf (IV)") +
  ggtitle("AUC_inf (IV), rescale_time = FALSE")
```

Fitting on the log scale seems to result in a few more cases of over-predicted AUC_infinity for IV dosing. Dose-normalizing before fitting on the log scale reduces these cases.

```{r}
ggplot(tk_DT_sub[rescale_time == TRUE],
       aes(x = AUC_inf_1mgkg,
           y = AUC_iv_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10() +
  annotation_logticks() +
  xlab("Non-compartmental AUC_inf (IV)") +
  ylab("Winning model-predicted AUC_inf (IV)") +
  ggtitle("AUC_inf (IV), rescale_time = TRUE")
```

Rescaling time seems to make the overpredictions worse on the log scale (up to 1e6, rather than 1e4 without rescaling time).

```{r}
ggplot(tk_DT_sub[rescale_time == FALSE],
       aes(x = tmax,
           y = tmax_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle("Tmax, rescale_time = FALSE")
```

```{r}
ggplot(tk_DT_sub[rescale_time == TRUE],
       aes(x = tmax,
           y = tmax_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10() +
  ggtitle("Tmax, rescale_time = TRUE")
```

Note that a couple of points have appeared with tmax > 1000. These are points where the winning model was flat when time was not rescaled, but the winning model was 1- or 2-compartment when time was rescaled.

```{r}
ggplot(tk_DT_sub[rescale_time %in% FALSE],
       aes(x = Cmax_1mgkg,
           y = Cmax_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10()  +
  ggtitle("Cmax, rescale_time = FALSE") +
  annotation_logticks()
```

Overall, Cmax tends to be under-predicted, but fitting on the natural scale results in more cases of worse under-prediction. That surprises me. I would have thought the opposite, because there are so many cases where log-scaling seems to fit the late elimination tail at the expense of fitting the peak. What are some of those cases?

```{r}
tk_DT_sub[Cmax_win < 1e-4 & rescale_time %in% FALSE & !is.na(Cmax_1mgkg), ]
```

Look at the fitted parameters for these?

```{r}
tmp <- tk_DT_sub[Cmax_win < 1e-4 & rescale_time %in% FALSE & !is.na(Cmax_1mgkg), .(fit_conc_dose, fit_log_conc, rescale_time, DTXSID, Species, Route, Media)]
tmp[, Analysis_Type := "Joint"]
```

```{r}

tk_DT[tmp, on = names(tmp)][winmodel =="1compartment", .(fit_conc_dose, fit_log_conc, DTXSID, Species, Route, Media, winmodel, N_Routes, Fgutabs.1compartment, Fgutabs_Vdist.1compartment, Vdist.1compartment, kelim.1compartment, kgutabs.1compartment, AIC.1compartment, AIC.flat)]
```
Looking at plots of the fit:

DTXSID4032376 (dimethenamid) is a case where there is one very very high concentration for the oral dosing data, out of range with the others:

```{r}
cvt_sub <- cvt[DTXSID %in% "DTXSID4032376" & Species %in% "rat", .(Route, Dose, Time, Conc, Conc_Dose, Detect)]
#sort by decreasing Conc_Dose
setorder(cvt_sub, Route, -Conc_Dose)
cvt_sub[Route %in% "po"]
```
This seems like a problem with the data itself -- as in, the "non-compartmental" Cmax is probably incorrect.

DTXSID4032405 is another case where there is one very high point right at the beginning of the oral data, with nothing before it, and an awful lot of non-detects. 
```{r}
cvt_sub <- cvt[DTXSID %in% "DTXSID4032405" & Species %in% "rat", .(Route, Dose, Time, Conc, Conc_Dose, Detect)]
#sort by decreasing Conc_Dose
#setorder(cvt_sub, Route, -Conc_Dose)
cvt_sub[Route %in% "po"]
```

In fact, I don't understand how the 1-compartment model actually "won" in this case. The AIC is technically lower than the flat model, but not by much, and I really don't understand how that happened. I suppose technically, because the 1-comaprtment model predicts some ridiculously tiny value like 1e-30, it makes the likelihood slightly higher for the non-detects?

```{r}
#prediction & likelihood for flat model, for a non-detect
cp_flat(params = list(Vdist = 988, Fgutabs = 1e-4, sigma = 0.0204), time = 0.25, dose = 5, iv.dose = FALSE, medium = "plasma")
pnorm(q = 0.000738/5, mean = 5.060729e-07/5, sd = 0.0204)
```

```{r}
#prediction & likelihood for 1-compartment model, for a non-detect
cp_1comp(params = list(Fgutabs = 0.9973610551, Vdist = 175.640477, kelim = 106.112252, kgutabs = 1e4), time = 0.25, dose = 5, iv.dose = FALSE, medium = "plasma")
pnorm(q = 0.000738/5, mean = 8.646482e-14/5, sd = 0.0204)
```

Yes -- that is the situation. The lower mean produces a very slightly higher probability for the non-detects.

Should we place some lower limit on predicted values -- like anything less than machine epsilon gets truncated at machine epsilon?

```{r}
tk_DT[tmp, on = names(tmp)][winmodel =="2compartment", .(fit_conc_dose, fit_log_conc, DTXSID, Species, Route, Media, winmodel, N_Routes, Fgutabs.2compartment, Fgutabs_V1.2compartment, V1.2compartment, kelim.2compartment, kgutabs.2compartment, k12.2compartment, k21.2compartment)]
```

COmparing Cmax predictions:

```{r}
ggplot(tk_DT_sub[rescale_time %in% TRUE],
       aes(x = Cmax_1mgkg,
           y = Cmax_win)) +
  geom_point(aes(color = winmodel)) +
  geom_abline(intercept = 0, slope = 1) +
  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
             labeller = label_both) +
  scale_x_log10() +
  scale_y_log10()  +
  ggtitle("Cmax, rescale_time = TRUE")
```

# Catching pathological cases

The flat model does *not* always win in pathological cases (see above).

We could add a way to catch cases that are missing absorption phase or elimination phase for oral dosing. If there are not at least 3 detected points before the empirical tmax, flag for missing absorption phase. Or if there are not at least 3 detected points after the empirical tmax, flag for missing elimination phase. If we're fitting a 2-compartment model, I guess it should be at least 6 detected points after the empirical tmax, in order to possibly have enough data to fit both alpha and beta.

### 2023-01-30 Working Rmds/plot_fits.Rmd
Evaluating residuals by RMSE, R-squared, and overall error SD. Evaluating TK stats by tmax, Cmax, AUC. All evaluations under combinations of the following fitting conditions: log-transform TRUE/FALSE, dose-normalization TRUE/FALSE, rescale time TRUE/FALSE. Residuals for each fitting condition also calculated in all of the following combinations: log-scale residuals TRUE/FALSE, dose-normalized residuals TRUE/FALSE. This way we can compare apples to apples.

@@
 ```{r}
-timestamp <- "2023_01_17"
+timestamp <- "2023_01_23"
 ```
@@
 cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
-"2023_01_13",
+timestamp,
 ".csv"))
@@
 
-Read in the fitted model parameter values.
-
-```{r, read_data}
-
-fit_1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
-fit_2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
-fit_flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))
-
-#pk_lombardo <- read_xlsx("inst/ext/Supplemental_82966_revised_corrected.xlsx")
-```
-
-Plot concentration vs time with the best-fit params by data subset (DTXSID and species).
-
-Indicate the following:
-
-- One line for each model
-- Which is the winning model
-- Dose group
-- Blood vs. plasma
-- Below LOQ vs. above LOQ (plot below-LOQ points at LOQ)
-- IV vs. oral administration
-
-Plot all models together for the joint analysis.
-
-Produce a data.table with unique combinations of DTXSID, species, analysis type, and studies analyzed.
+# Plot fits for each combination of fitting & plotting options
 
 ```{r}
-plot_combos <- unique(fit_flat[Analysis_Type %in% "Joint", .(Analysis_Type,
+for(rescale_time in c(FALSE, TRUE)){
+  for(fit_conc_dose in c(FALSE, TRUE)){
+    for(fit_log_conc in c(FALSE, TRUE)){
+      #get fitting outputs file names
+      fit_outputs <- dir(path = "../inst/ext",
+                         pattern = paste0("PK_fit_table_",
+                                          ".+",
+                                          "_fit_log_conc_",
+                                          fit_log_conc, "_",
+                                          "_fit_conc_dose_",
+                                          fit_conc_dose, "_",
+                                          "_rescale_time_",
+                                          rescale_time, "_"
+                         ))
+
+      fit_outputs <- paste0("../inst/ext/",
+                            fit_outputs)
+
+      cat(paste0(paste(fit_outputs,
+                       collapse = "\n"), "\n"))
+
+      #read in fitting outputs
+      #flat model
+      fit_flat <- fread(grep(x = fit_outputs,
+                             pattern = "flat",
+                             value = TRUE))
+      #1compartment model
+      fit_1comp <- fread(grep(x = fit_outputs,
+                              pattern = "1compartment",
+                              value = TRUE))
+      #2compartment model
+      fit_2comp <- fread(grep(x = fit_outputs,
+                              pattern = "2compartment",
+                              value = TRUE))
+      #add in fitting options
+      fit_flat[, c("fit_conc_dose",
+                   "fit_log_conc",
+                   "rescale_time") := .(fit_conc_dose,
+                                        fit_log_conc,
+                                        rescale_time)]
+
+      fit_1comp[, c("fit_conc_dose",
+                    "fit_log_conc",
+                    "rescale_time") := .(fit_conc_dose,
+                                         fit_log_conc,
+                                         rescale_time)]
+
+      fit_2comp[, c("fit_conc_dose",
+                    "fit_log_conc",
+                    "rescale_time") := .(fit_conc_dose,
+                                         fit_log_conc,
+                                         rescale_time)]
+
+      #get unique combinations of DTXSID, Species, Analysis_Type, Studies. Analyzed
+      plot_combos <- unique(
+        fit_flat[Analysis_Type %in% "Joint",
+                 .(Analysis_Type,
                    DTXSID,
@@
                      sep = "_"))
-```
 
-Loop over the following combinations of options:
-- Log-scale y and non-log-scale y
-- Dose-normalized and split-dose
+      #now, loop over plotting options:
+      #plot log-scale, plot dose-normalized
 
-```{r}
-opts_DT <- as.data.table(expand.grid(log10_scale_y = c(TRUE, FALSE),
-                       split_dose = c(TRUE, FALSE)))
-opts_DT[, plot_errbars := !(log10_scale_y)]
-opts_DT[, plot_dose_norm := !(split_dose)]
-opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% TRUE,
-        file_suffix := "errbars_naturaly_dose_norm"]
-opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% TRUE,
-        file_path := "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_norm"]
-opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% TRUE,
-        file_suffix := "noerrbars_logy_dose_norm"]
-opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% TRUE,
-        file_path := "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_norm"]
-
-opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% FALSE,
-        file_suffix := "errbars_naturaly_dose_split"]
-opts_DT[plot_errbars %in% TRUE & plot_dose_norm %in% FALSE,
-        file_path := "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_split"]
-opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% FALSE,
-        file_suffix := "noerrbars_logy_dose_split"]
-opts_DT[plot_errbars %in% FALSE & plot_dose_norm %in% FALSE,
-        file_path := "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_split"]
-```
-
-Loop over options, and within each option, loop over datasets, to plot joint analysis with all models.
-```{r}
-junk <- mapply(function(plot_errbars,
-                       log10_scale_y,
-                       plot_dose_norm,
-                       split_dose,
-                       file_suffix,
-                       file_path){
-  print(file_suffix)
+      for(log10_scale_y in c(TRUE, FALSE)){
+        for(plot_dose_norm in c(TRUE, FALSE)){
+          cat(paste0("rescale_time = ", rescale_time,"\n",
+                     "fit_conc_dose = ", fit_conc_dose,"\n",
+                     "fit_log_conc = ", fit_log_conc,"\n",
+                     "log10_scale_y = ", log10_scale_y,"\n",
+                     "plot_dose_norm = ", plot_dose_norm,"\n"))
+          #for each row of plot_combos, create a plot
           DT_plot <- plot_combos[,
@@
                                               model_in = "all",
+                                               fit_log_conc = fit_log_conc,
+                     fit_conc_dose = fit_conc_dose,
+                     rescale_time = rescale_time,
                                               Analysis_Type_in = "Joint",
                                               plot_dose_norm = plot_dose_norm,
-                 split_dose = split_dose,
+                                              split_dose = (!plot_dose_norm),
                                               n_interp_time = 10,
@@
                                               log10_scale_y = log10_scale_y,
-                     plot_errbars = plot_errbars,
+                                              plot_errbars = (!log10_scale_y),
                                               log10_scale_time = FALSE,
                                               return_plot = TRUE,
-                 save_plot = TRUE,
-                 file_suffix = file_suffix,
-                     file_path = file_path,
-                 verbose = FALSE,
-                 ggsave_args = list(scale = 1,
-                                        width = 13.33,
-                                        height = 7.5,
-                                        units = "in",
-                                        dpi = 300,
-                                        limitsize = TRUE,
-                                        bg = NULL)
+                                              save_plot = FALSE,
+                                              file_suffix = NULL,
+                                              file_path = NULL,
+                                              verbose = FALSE
                                      )
-                       })),
+                                   }
+                                 )
+                                 ),
                                  by = .(DTXSID_in,
@@
           #save all plots as one big paginated file
-pdf(paste0(file_path,
-              "/all_plots_",
-              file_suffix,
+          pdf(paste0("../inst/ext/plots/",
+                     "plots_",
+                     "fit_log_conc_",
+                     fit_log_conc, "_",
+                     "fit_conc_dose_",
+                     fit_conc_dose, "_",
+                     "rescale_time_",
+                     rescale_time, "_",
+                     "plotlog10y_", log10_scale_y, "_",
+                     "plotdosenorm_", plot_dose_norm,
                      ".pdf"),
@@
           dev.off()
+        } #end for plot_dose_norm
+      }#end for log10_scale_y
+    } #end for fit_log_conc
+  }#end for fit_dose_norm
+}#end for rescale_time
+```
 
-rm(DT_plot)
+Tradeoffs I notice:
 
-return(0)
-},
-plot_errbars = opts_DT$plot_errbars,
-                       log10_scale_y = opts_DT$log10_scale_y,
-                       plot_dose_norm = opts_DT$plot_dose_norm,
-                       split_dose = opts_DT$split_dose,
-file_suffix = opts_DT$file_suffix,
-file_path = opts_DT$file_path)
+Fitting on the log scale gives a better fit to late elimination-phase points, sometimes at the expense of underpredicting Cmax.
+Solvent red 1 (DTXSID3061635) is a prime example.
+This happens because log-transforming observations before fitting tends to increase the scale of errors for points with small observed concentrations, and tends to decrease the scale of errors for points with large observed concentrations.
 
-```
+This effect is stronger if the range of observed concentrations is more than one order of magnitude.
+For example, for solvent red 1, concentrations range from about 0.05 down to about 1e-4.
+When fit on the natural scale, the 1-compartment model wins, because it fits the peak better.
+When fit on the log scale, the 2-compartment model wins, because it fits the tail better.
+
+Trichloroethylene (in rat) is another interesting case.
+When fitted on the natural scale without dose normalization, the 7.6 mg/kg dose is fitted well, but the 18 mg/kg dose is fitted poorly (underpredicted), and the 1-compartment model wins.
+When fitted on the log scale without dose normalization, the 18 mg/kg dose is fitted better, at the expense of overpredicting the 7.6 mg/kg dose, and the 2-compartment model wins.
+I'm not sure why the 18 mg/kg dose is underpredicted on the natural scale without dose normalization; the scale of the errors should be higher for the peak there.
+
+Questions we want to ask:
+
+- Does error vary by dose?
+- Does error vary by time (absorption, elimination phases)?
+- How well do we predict Cmax on a non-dose-normalized basis?
+- How well do we predict Cmax on a dose-normalized basis?
+- How well do we predict tmax?
+- How well do we predict AUC infinity?
+
+Probably we should do something like assess percentage error (error as a percentage of observed value).
+That corresponds to, roughly, the visual difference between fitted curves and observed points on the split-dose plots.

### 2023-01-30 Working Rmds/evaluate_fits.R

@@ -1,0 +1,339 @@
+#' ---
+#' title: "Evaluate fits"
+#' author: "Caroline Ring"
+#' date: "2023-01-23"
+#' output: html_document
+#' ---
+#' 
+## ----setup, include = FALSE----------------------------------------------
+knitr::opts_chunk$set(echo = FALSE)
+knitr::opts_chunk$set(warning = FALSE)
+knitr::opts_chunk$set(results = TRUE)
+knitr::opts_chunk$set(message = FALSE)
+
+#' 
+## ---- include = FALSE----------------------------------------------------
+library(tidyverse)
+library(data.table)
+library(readxl)
+devtools::load_all("../invivopkfit")
+
+#' 
+#' # Introduction
+#' 
+#' This document contains code to evaluate the goodness-of-fit of the models fit to data in `MainAnalysis.Rmd`.
+#' 
+#' # Import and preprocess CvTdb data
+#' 
+#' ## Import CvTdb data
+#' 
+#' Read in CvTdb data that was pulled and normalized in `pulling_oral_iv_data_cvtdb.Rmd`.
+#' 
+## ---- load_cvt, eval = TRUE----------------------------------------------
+cvt_data <- fread("../inst/ext/cvt_data_2023_01_05.csv")
+
+#' 
+#' ## Timestamp
+#' Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.
+#' 
+## ------------------------------------------------------------------------
+timestamp <- format(Sys.time(), "%Y_%m_%d")
+
+#' 
+#' ## Settings for pre-processing data
+#' 
+#' List of new_name = old_name to supply for preprocessing data
+#' 
+## ------------------------------------------------------------------------
+names_list <- list(
+  "Compound_Dosed" = "studies.test_substance_name_original",
+  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
+  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
+  "Compound_Analyzed" = "series.analyte_name_original",
+  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
+  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
+  "Reference" = "documents_reference.id",
+  "Extraction" = "documents_extraction.id",
+  "Species" = "subjects.species",
+  "Weight" ="subjects.weight_kg",
[…]

### 2023-01-30 Working Rmds/evaluate_fits.Rmd
Thoughts on errrors

@@
 
-```{r}
+```{r, eval = FALSE}
 cvt <- preprocess_data(data.set = cvt_data,
@@
 rm(cvt_data)
+```
+
+```{r}
+cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
+                 "2023_01_23",
+          ".csv"))
 ```
@@
 
-```{r}
+```{r, eval = FALSE}
 eval_DT <- fit_opts[,
@@
 
-```{r}
+```{r, eval = FALSE}
 TKstats_DT <- fit_opts[,
@@
 
+Keep only the Joint analyses, for the sake of simplicity. (These are the ones where multiple studies were fit together, but with a different error SD allowed for each study.)
+
 ```{r}
@@
 ```
+
+# AUC comparison
+
+## AUC oral
+
+### Rescale time = FALSE
 
@@
 
+### Rescale time = TRUE
+
 ```{r}
@@
 Rescaling time seems to make the overpredictions worse when they happen.
+
+## AUC IV
+
+### Rescale time = FALSE
 
@@
 
+## Tmax comparison
+
+### Rescale time = FALSE
 ```{r}
@@
 ```
+
+### Rescale time = TRUE
 
@@
 
+## Cmax comparison
+
+### Rescale time = FALSE
+
 ```{r}
 ggplot(tk_DT_sub[rescale_time %in% FALSE],
+       aes(x = Cmax_1mgkg,
+           y = Cmax_win)) +
+  geom_point(aes(color = winmodel)) +
+  geom_abline(intercept = 0, slope = 1) +
+  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
+             labeller = label_both) +
+  scale_x_log10() +
+  scale_y_log10()  +
+  ggtitle("Cmax, rescale_time = FALSE") +
+  annotation_logticks()
+```
+
+### Rescale time = TRUE
+
+```{r}
+ggplot(tk_DT_sub[rescale_time %in% TRUE],
        aes(x = Cmax_1mgkg,
@@
 I would have thought the opposite, because there are so many cases where log-scaling seems to fit the late elimination tail at the expense of fitting the peak.
+
+### Examples of bad Cmax cases
+
 What are some of those cases?
@@
 Should we place some lower limit on predicted values -- like anything less than machine epsilon gets truncated at machine epsilon?
-
-```{r}
-tk_DT[tmp, on = names(tmp)][winmodel =="2compartment", .(fit_conc_dose, fit_log_conc, DTXSID, Species, Route, Media, winmodel, N_Routes, Fgutabs.2compartment, Fgutabs_V1.2compartment, V1.2compartment, kelim.2compartment, kgutabs.2compartment, k12.2compartment, k21.2compartment)]
-```
-
-COmparing Cmax predictions:
-
-```{r}
-ggplot(tk_DT_sub[rescale_time %in% TRUE],
-       aes(x = Cmax_1mgkg,
-           y = Cmax_win)) +
-  geom_point(aes(color = winmodel)) +
-  geom_abline(intercept = 0, slope = 1) +
-  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
-             labeller = label_both) +
-  scale_x_log10() +
-  scale_y_log10()  +
-  ggtitle("Cmax, rescale_time = TRUE")
-```
+Would that make the flat model "win" in this pathological cases?
+I think it would do so only if the lower limit was equal to or higher than the fitted flat value, which it might not be.
 
@@
 
-The flat model does *not* always win in pathological cases (see above).
+The flat model does *not* always win in pathological cases (see above). So that can't be our only method of catching pathological cases.
 
@@
 If we're fitting a 2-compartment model, I guess it should be at least 6 detected points after the empirical tmax, in order to possibly have enough data to fit both alpha and beta.
+
+# Defining a 'study'
+
+Currently, I'm defining a "study" as DTXSID + Species + Reference + Route + Media. John thinks it should be DTXSID + Species + Reference.
+
+My argument is that the different dosing routes (oral vs.
+IV) might result in different levels of plasma concentration, different enough that the analytical chemistry might behave differently.
+Maybe even more strongly, different media are likely to have media-specific effects on analytical chemistry.
+
+I guess what we need is a proper model of error.
+
+Wambaugh et al. 2019 had it as the following, where $A$ is the observed peak area, $\hat{A}$ is a predicted peak area, $[x]$ is the actual concentration:
+
+$$ A \sim \textrm{Normal} (\mu = \hat{A}, \quad \sigma =  k_1 + k_2 [x]) $$
+
+$$ \hat{A} = \theta([x] - t) ([x] - t) m + b $$
+where $\theta(\cdot)$ is the Heaviside step function (1 when the argument is positive, 0 otherwise); $t$ is a threshold concentration; $m$ is the calibration; $b$ is the background noise.
+
+But that doesn't handle inter-study variability.
+
+I think what we have is something like this:
+
+$i$ indexes chemical/species.
+$j$ indexes study (whatever that ends up being).
+$k$ indexes group --  a unique combination of dose, time, route, and medium within study.
+$m$ indexes individual observations within group $k$.
+$x_{ijkm}$ is observed concentration.
+$\hat{x}_{ijk}$ is model-predicted concentration for group $k$.
+
+The residual error between $x$ and $\hat{x}$ has several components. One component is uncertainty in analytical chemistry.
+
+Wambaugh et al. (2019) cite Rocke & Lorenzato (1995), who model analytical chemistry observed concentration $x$ as the following function of true concentration $x^{\prime}$.
+
+$$ x =  x^{\prime} e^\eta + \epsilon $$
+
+Using our subscripts, I think it would be
+
+$$ x_{ijkm} = x^{\prime}_{ijkm} e^{\eta_{ijk}} + \epsilon_{ijk} $$
+Here, there are two measurement errors, $\eta$ and $\epsilon$.
+Each is zero-mean normal distributed with its own standard deviation.
+$\eta_{ijk} \sim \textrm{Normal}(0, \sigma_{\eta})$ and $\epsilon_{ijk} \sim \textrm{Normal}(0, \sigma_{\epsilon})$.
+
+$\epsilon$ represents background noise. $\eta$ represents concentration-dependent noise. 
+Both $\epsilon$ and $\eta$ are likely to be lab-dependent, because they are likely to be instrument- and run-dependent.
+
+Meanwhile, the "true" concentration $x^{\prime}_{ijkm}$ also has inter-individual variability around some group-specific mean. It could be modeled as
+
+$$ x^{\prime}_{ijkm} \sim \textrm{(Log)-Normal}(\mu = \hat{x}_{ijk}, \sigma_{\textrm{indiv}}) $$
+In this case, error is chemical- and species-specific, maybe lab-population-specific.
+
+Model-predicted concentration $\hat{x}_{ijkm}$ is the best estimate of group mean "true" concentration.
+It is a function of the model parameters for chemical/species $i$, along with dose $d$, time $t$, dosing route $r$, and analysis media $m$, for observation $m$ within group $k$ within study $j$ within chemical/species $i$.
+
+$$ \hat{x}_{ijkm} = f(\theta_i; \quad d_{ijk}, t_{ijk}, r_{ijk}, m_{ijk}) $$
+
+Could we in fact try to estimate the hyperparameters $\sigma_\eta$ and $\sigma_epsilon$?
+
+How would we write the likelihood function?
+
+Rocke & Lorenzato (1995) say "Any combination of $\eta$ and $\epsilon$ that satisfies $\epsilon = x - \x^{\prime} e^{\eta}$ is possible" (where I have substituted my notation of $x^{\prime}$ for the "true" concentration).
+
+They write the likelihood as
+
+$$ \int_{-\infty}^{\infty} \frac{1}{2 \pi \sigma_\epsilon \sigma_\eta}
+\exp \left(
+\frac{-\eta^2}
+{2 \sigma_\eta^2}
+\right)
+\exp \left(
+\frac{-(x-x^{\prime}e^\eta)^2}
+{2 \sigma_\epsilon^2}
+\right)
+d \eta $$
+
+In their Appendix 2, they explain how they implemented the numerical integration using Gauss-Hermite quadrature. This looks complicated but I think I can figure it out (?)
+
+Is there anything we can do without going to that full extent? Does log-transforming x help with this heteroscedasticity at all? At high concentrations, the errors do become approximately log-normal.
+
+$$ x =  x^{\prime} e^\eta + \epsilon $$
+
+Log-transforming, we get
+
+$$ \log x = \log(x^{\prime} e^\eta + \epsilon) $$
+
+If $\epsilon$ is small compared to $x^{\prime} e^\eta$ , then this is approximately equal to
+
+$$ \log x = \eta + \log(x^{\prime}) $$
+
+But if $\epsilon$ is not small compared to $x^{\prime} e^\eta$ -- for example, if $x^{\prime}$ is near zero -- then that approximation is not good.
+
+Could we say that likelihood is log-normal for detects, and normal for non-detects?
+And assume two different sigmas per study -- one for detects and one for non-detects?
+That would be a sort of piecewise approximation for the measurement error.

### 2023-02-01 Working Rmds/MainAnalysis.Rmd
Adding upper bounds because L-BFGS-B sometimes fails without them (returning NA for optimized param values, but not failing with an error). Adding more detail in output data.frame (including number of points in "empirical" absorption and elimination phases).

@@
                        impute_sd = TRUE,
-                       study_def = c("DTXSID", "Species", "Reference", "Route", "Media"),
+                       study_def = c("DTXSID", "Species", "Reference"),
                        suppress.messages = TRUE)
@@
 ```{r}
+for(this_method in c("bobyqa", "L-BFGS-B")){
   for(this_rescale_time in c(FALSE, TRUE)){
@@
       for(this_fit_log_conc in c(FALSE, TRUE)){
-      if(!(this_rescale_time %in% FALSE &
-           this_fit_conc_dose %in% FALSE &
-           this_fit_log_conc %in% FALSE)){ #already did the all FALSE case
           for (this_model in c("flat",
@@
                                "2compartment")){
-        print(paste0("model = ", this_model, "\n",
+            cat(paste0("method = ", this_method, "\n",
                          "fit_log_conc = ", this_fit_log_conc, "\n",
                          "fit_conc_dose = ", this_fit_conc_dose, "\n",
-                     "rescale_time = ", this_rescale_time))
+                         "rescale_time = ", this_rescale_time, "\n",
+                                     "model = ", this_model, "\n"))
             system.time(
@@
                 optimx_args = list(
-              "method" = "bobyqa",
-              "itnmax" = 1e6,
-              "control" = list("kkt" = FALSE)
+                  method = this_method,
+                  itnmax = 1e6,
+                  control = list(kkt = FALSE,
+                                 factr = 1e7)
                 ),
@@
             write.csv(PK.fit.table,
-                  paste("../inst/ext/PK_fit_table_",
-                        this_model,
-                        "_fit_log_conc_",
+                      paste0("../inst/ext/PK_fit_table_",
+                            this_model, "_",
+                            "fit_log_conc_",
                             this_fit_log_conc, "_",
-                        "_fit_conc_dose_",
+                            "fit_conc_dose_",
                             this_fit_conc_dose, "_",
-                        "_rescale_time_",
+                            "rescale_time_",
                             this_rescale_time, "_",
+                            "method_", this_method, "_",
                             timestamp,
-                        ".csv",
-                        sep=""), row.names = FALSE)
+                            ".csv"), row.names = FALSE)
 
-        post_table <- postprocess_data(PK_fit = PK.fit.table,
-                                       model= this_model)
-
-        rm(PK,fit.table)
-
-        write.csv(post_table,
-                  paste("../inst/ext/PK_fit_postprocess_",
-                        this_model,
-                        "_fit_log_conc_",
-                        this_fit_log_conc, "_",
-                        "_fit_conc_dose_",
-                        this_fit_conc_dose, "_",
-                        "_rescale_time_",
-                        this_rescale_time, "_",
-                        timestamp,
-                        ".csv",
-                        sep=""), row.names = FALSE)
-
-        rm(post_table)
           } #end loop over models
-      } #end if not all FALSE
       } #end loop over this_fit_log_conc
@@
   } #end loop over this_rescale_time
+}#end loop over this_method
 ```

### 2023-02-01 Working Rmds/MainAnalysis.R

@@ -1,48 +1,26 @@
-#' ---
-#' title: "invivoPKfit analysis of CvTdb data"
-#' author: "Christopher Cook, John Wambaugh, Caroline Ring"
-#' date: "`r format(Sys.time(), '%B %d, %Y')`"
-#' output:
-#'   html_document: default
-#'   word_document: default
-#' ---
-#' 
-## ----setup, include = FALSE--------------------------------------------------------------------------------
+## ----setup, include = FALSE-----------------------------------------------
 knitr::opts_chunk$set(echo = FALSE)
 knitr::opts_chunk$set(warning = FALSE)
 knitr::opts_chunk$set(results = TRUE)
 knitr::opts_chunk$set(message = FALSE)
 
-#' 
-## ---- include = FALSE--------------------------------------------------------------------------------------
+
+## ---- include = FALSE-----------------------------------------------------
 library(tidyverse)
 library(data.table)
 library(readxl)
 devtools::load_all("../invivopkfit")
 
-#' 
-#' # Read in CvTdb data
-#' 
-#' Read in CvTdb data that was pulled and normalized in `pulling_oral_iv_data_cvtdb.Rmd`.
-#' 
-## ---- load_cvt, eval = TRUE--------------------------------------------------------------------------------
+
+## ---- load_cvt, eval = TRUE-----------------------------------------------
 cvt_data <- fread("../inst/ext/cvt_data_2023_01_05.csv")
 
-#' 
-#' # Setup for data processing and model fitting
-#' 
-#' ## Timestamp
-#' Timestamp the file name with the current date and time (at the beginning of the runs) in format YYYY_MM_DD_hh_mm.
-#' 
-## ----------------------------------------------------------------------------------------------------------
+
+## -------------------------------------------------------------------------
 timestamp <- format(Sys.time(), "%Y_%m_%d")
 
-#' 
-#' ## Settings for pre-processing data
-#' 
-#' List of new_name = old_name to supply for preprocessing data
-#' 
-## ----------------------------------------------------------------------------------------------------------
+
+## -------------------------------------------------------------------------
 names_list <- list(
   "Compound_Dosed" = "studies.test_substance_name_original",
   "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
@@ -66,23 +44,21 @@ names_list <- list(
[…]

### 2023-02-03 Working Rmds/evaluate_fits.Rmd
Now organizing fits as S3 objects of class 'pkfit.' These are defined as a unique combination of dataset (DTXSID, Species, Study, Routes), data transformations (log-transform, dose-normalize, rescale time), fitting method (bobyqa or L-BFGS-B), and model (flat, 1-compartment, 2-compartment). They are structured as a list. Have written methods to create 'pkfit' object from fit and cvt tables, as well as methods for 'predict', 'residuals', and many other analysis tasks that are done at the single-fit level, like rmse, rsq, fractional residuals, etc.

@@
 
-# Import and preprocess CvTdb data
+# Import preprocessed CvTdb data
 
-## Import CvTdb data
-
-Read in CvTdb data that was pulled and normalized in `pulling_oral_iv_data_cvtdb.Rmd`.
-
-```{r, load_cvt, eval = TRUE}
-cvt_data <- fread("../inst/ext/cvt_data_2023_01_05.csv")
+```{r}
+cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
+                 "2023_02_01",
+          ".csv"))
 ```
@@
 timestamp <- format(Sys.time(), "%Y_%m_%d")
-```
-
-## Settings for pre-processing data
-
-List of new_name = old_name to supply for preprocessing data
-
-```{r}
-names_list <- list(
-  "Compound_Dosed" = "studies.test_substance_name_original",
-  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
-  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
-  "Compound_Analyzed" = "series.analyte_name_original",
-  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
-  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
-  "Reference" = "documents_reference.id",
-  "Extraction" = "documents_extraction.id",
-  "Species" = "subjects.species",
-  "Weight" ="subjects.weight_kg",
-  "Weight.Units" = NULL,
-  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
-  "Dose.Units" = NULL,
-  "Time" = "conc_time_values.time_hr",
-  "Time.Units" = NULL,
-  "Media" = "series.conc_medium_normalized",
-  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
-  "Value.Units" = NULL,
-  "Route" = "studies.administration_route_normalized",
-  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
-  "Subject" = "subjects.id",
-  "N_Subjects" = "series.n_subjects_in_series",
-  "Value_SD" = "conc_time_values.conc_sd_normalized", #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
-  "Study_ID" = "studies.id",
-  "Series_ID" = "series.id"
-  )
-```
-
-List of default values for new columns added in preprocessing data
-
-```{r}
-defaults_list <- list(
-                      "Weight.Units" = "kg",
-                      "Dose.Units" = "mg/kg",
-                      "Time.Units" = "hours",
-                      "Value.Units" = "mg/L")
-```
-
-## Preprocess data
-
-```{r, eval = FALSE}
-cvt <- preprocess_data(data.set = cvt_data,
-                       names_list =names_list,
-                       defaults_list =   defaults_list,
-                       ratio_conc_to_dose = 1,
-                       calc_loq_factor = 0.45,
-                       routes_keep = c("po", "iv"),
-                       media_keep = c("blood", "plasma"),
-                       impute_loq = TRUE,
-                       impute_sd = TRUE,
-                       study_def = c("DTXSID", "Species", "Reference", "Route", "Media"),
-                       suppress.messages = TRUE)
-
-#save pre-processed data
-# write.csv(cvt,
-#           paste0("../inst/ext/cvt_preprocessed_",
-#                  timestamp,
-#           ".csv"),
-#           row.names = FALSE)
-
-cvt <- as.data.table(cvt)
-rm(cvt_data)
-```
-
-```{r}
-cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
-                 "2023_01_23",
-          ".csv"))
-```
-
-```{r}
-cvt[, Conc_SD := Value_SD]
-cvt[, Conc_SD_Dose := Value_SD_Dose]
 ```
@@
   fit_conc_dose = c(FALSE, TRUE),
-  fit_log_conc = c(FALSE, TRUE))
+  fit_log_conc = c(FALSE, TRUE),
+  log_trans = c(FALSE, TRUE),
+  dose_norm = c(FALSE, TRUE),
+  method = c("bobyqa", "L-BFGS-B"),
+  model = c("flat", "1compartment", "2compartment"))
   )
-
 ```
 
-# Evaluate residuals for each set of fitting options
+# pkfit object
 
-```{r, eval = FALSE}
-eval_DT <- fit_opts[,
+One "fitted model" is defined by the following information:
+
+* Dataset used for fitting: A subset of `cvt` defined by the following information: 
+    + DTXSID
+    + Species
+    + Studies.Analyzed
+    + routes analyzed (that last one in the case when there was not enough oral absorption-phase data to fit kgutabs, but there was IV data, so we fit the IV data only)
+* Analysis Type (error model): 
+    + Joint: one set of params across all studies, but separate error SDs for each study
+    + Separate: separate params & error SDs for each study
+    + Pooled: one set of params & one error SD across all studies
+* TK model:
+    + flat
+    + 1-compartment
+    + 2-compartment
+* Transformations applied to the data before fitting:
+    + log transformation (fit_log_conc TRUE or FALSE)
+    + dose-normalization (fit_conc_dose TRUE or FALSE)
+    + rescaling time when study spanned days, weeks, months, or years (rescale_time TRUE or FALSE)
+* Fitted model parameters
+    + Name
+    + Starting values
+    + Lower & upper bounds
+    + Fitted mean
+    + Fitted standard deviation
+* Information from `optimx`
+    + Algorithm used
+    + Control parameters used
+    + Convergence code
+    + Number of function evaluations
+    + Message
+
+We can make this into an R object, essentially just a list with all of this information. Call it an object of class `pkfit` that inherits from class `list`.
+
+Then we can write methods to do things like predict, residuals, coeffs, get TK summary stats, etc. etc.
+
+We can also write a "plot" method to plot concentration vs. time with the fitted curve.
+
+## A pkanalysis object
+
+One "analysis" is a set of three "fit" objects: one for each of the three models, for the same dataset, analysis type, and fitting options.
+We can call this an object of class `pkanalysis`.
+Duplicated information (e.g.
+dataset) will be stored only once.
+
+Methods for a `pkanalysis` object include getting the winning model, and calculating the "p-value" for each model compared to the flat model (exp(AIC_model - AIC_flat)/2).
+
+We can also get predictions, coeffs, resids, etc. but these will always return a list of 3 items, one for each model.
+
+The "plot" method for a `pkanalysis` object plots concentration vs. time with all three fitted curves, or with only the winning fitted curve.
+
+## Creating fitted objects from tables of fitted parameters & of pre-processed data
+
+It would be unwieldy to save lots of R objects for each fit, especially since the fitted dataset would be the same for many fits.
+Instead, we have saved the fit output data as a table.
+To get the fitted dataset, we have to index into the appropriate pre-processed version of CvT, taking the appropriate subset of DTXSID, Species, studies analyzed, and routes analyzed.
+
+We can write a method `pkfit()` to take one row of a fit output data table, and the full CvT pre-processed table, and produce a `pkfit` object.
+
+# Evaluate residuals for each fit
+
+```{r}
+verbose <- FALSE
+timestamp <- "2023_02_01"
+resids_all <- fit_opts[,
          {
-                    print(
-                      paste("fit_log_conc = ",
-                        fit_log_conc,
-                        "; fit_conc_dose = ",
-                        fit_conc_dose,
-                        "; rescale_time = ",
-                        rescale_time)
-                    )
-
+           #Read in fits
         #get fitting outputs file names
@@
       pattern = paste0("PK_fit_table_",
-                       ".+",
-        "_fit_log_conc_",
-                        fit_log_conc, "_",
-                        "_fit_conc_dose_",
-                        fit_conc_dose, "_",
-                        "_rescale_time_",
-                        rescale_time, "_"
-                       ))
-
-  fit_outputs <- paste0("../inst/ext/",
-                        fit_outputs)
-
-  cat(paste0(paste(fit_outputs,
-              collapse = "\n"), "\n"))
-
-  #read in fitting outputs
-  #flat model
-  fit_flat <- fread(grep(x = fit_outputs,
-                         pattern = "flat",
-                         value = TRUE))
-  #1compartment model
-  fit_1comp <- fread(grep(x = fit_outputs,
-                         pattern = "1compartment",
-                         value = TRUE))
-  #2compartment model
-   fit_2comp <- fread(grep(x = fit_outputs,
-                         pattern = "2compartment",
-                         value = TRUE))
-
-   fit_flat[, c("fit_conc_dose",
-                "fit_log_conc",
-                "rescale_time") := .(fit_conc_dose,
-                                     fit_log_conc,
-                                     rescale_time)]
-
-    fit_1comp[, c("fit_conc_dose",
-                "fit_log_conc",
-                "rescale_time") := .(fit_conc_dose,
-                                     fit_log_conc,
-                                     rescale_time)]
-
-       fit_2comp[, c("fit_conc_dose",
-                "fit_log_conc",
-                "rescale_time") := .(fit_conc_dose,
-                                     fit_log_conc,
-                                     rescale_time)]
-
-   cat("Evaluating residuals...\n")
-
-   #evaluate residuals
-   this_eval_DT <- evaluate_resids(cvt_pre = cvt,
-                         fit_flat = fit_flat,
-                         fit_1comp = fit_1comp,
-                         fit_2comp = fit_2comp,
-                         fit_conc_dose = fit_conc_dose,
-                         fit_log_conc = fit_log_conc,
-                         optimx_args = list(
-                           "method" = "bobyqa",
-                           "itnmax" = 1e6,
-                           "control" = list("kkt" = FALSE)
-                         ),
-                         verbose = TRUE)
-
-     write.csv(this_eval_DT,
-                  paste("../inst/ext/evaluate_residuals_",
+                       model,
         "_fit_log_conc_",
@@
                         rescale_time, "_",
-                        timestamp,
-                        ".csv",
-                        sep=""), row.names = FALSE)
-
-     this_eval_DT
-                  },
-  by = c("fit_conc_dose", "fit_log_conc", "rescale_time")]
-
-write.csv(eval_DT,
-          paste0("../inst/ext/eval_resid_",
-          timestamp,
-          ".csv"),
-          row.names = FALSE)
-```
-
-Evalaute TK stats
-
-```{r, eval = FALSE}
-TKstats_DT <- fit_opts[,
-                  {
-                    print(
-                      paste("fit_log_conc = ",
-                        fit_log_conc,
-                        "; fit_conc_dose = ",
-                        fit_conc_dose,
-                        "; rescale_time = ",
-                        rescale_time)
-                    )
-
-  #get fitting outputs file names
-  fit_outputs <- dir(path = "../inst/ext",
-      pattern = paste0("PK_fit_table_",
-                       ".+",
-        "_fit_log_conc_",
-                        fit_log_conc, "_",
-                        "_fit_conc_dose_",
-                        fit_conc_dose, "_",
-                        "_rescale_time_",
-                        rescale_time, "_"
+        "method_", method,
+        "_", timestamp
                        ))
@@
                         fit_outputs)
-
+  if(verbose %in% TRUE){
   cat(paste0(paste(fit_outputs,
               collapse = "\n"), "\n"))
+  }
 
-  #read in fitting outputs
-  #flat model
-  fit_flat <- fread(grep(x = fit_outputs,
-                         pattern = "flat",
-                         value = TRUE))
-  #1compartment model
-  fit_1comp <- fread(grep(x = fit_outputs,
-                         pattern = "1compartment",
-                         value = TRUE))
-  #2compartment model
-   fit_2comp <- fread(grep(x = fit_outputs,
-                         pattern = "2compartment",
+  #read in fitting output table for this model
+  fit <- fread(grep(x = fit_outputs,
+                         pattern = model,
                          value = TRUE))
 
-   fit_flat[, c("fit_conc_dose",
-                "fit_log_conc",
-                "rescale_time") := .(fit_conc_dose,
+  #now: go by DTXSID, Species, Analysis Type.
+  fit[, {
+    if(verbose %in% TRUE){
+    cat(paste("DTXSID = ", DTXSID, "\n",
+              "Species = ", Species, "\n",
+              "Analysis Type = ", Analysis_Type, "\n",
+              "Studies Analyzed = ", Studies.Analyzed, "\n"))
+    }
+    obj <- pkfit(fit = .SD,
+                    dat = cvt)
+    rmse <- rmse.pkfit(obj,
+                       log_trans = log_trans,
+                       dose_norm = dose_norm)
+    rsq <- rsq.pkfit(obj,
+                       log_trans = log_trans,
+                       dose_norm = dose_norm)
+    # error_sd <- overall_error_sd.pkfit(obj,
+    #                    log_trans = log_trans,
+    #                    dose_norm = dose_norm)
+
+    #calculate residuals
+    frac_resids <- frac_resids.pkfit(obj,
+                           dose_norm = dose_norm,
+                           log_trans = log_trans)
+    #normalize residuals by 
+    list("RMSE" = rmse,
+         "rsq" = rsq,
+         # "error_sd" = error_sd,
+         "frac_resids.mean" = mean(frac_resids),
+         "frac_resids.median" = median(frac_resids),
+         "frac_resids.min" = min(frac_resids),
+         "frac_resids.max" = max(frac_resids))
+  },
+  by = .(DTXSID, Species, Analysis_Type, Studies.Analyzed, LogLikelihood, AIC),
+  .SDcols = names(fit)]
+         },
+  by = .(rescale_time,
+         fit_conc_dose,
          fit_log_conc,
-                                     rescale_time)]
+         log_trans,
+         dose_norm,
+         method,
+         model)]
+```
 
-    fit_1comp[, c("fit_conc_dose",
-                "fit_log_conc",
-                "rescale_time") := .(fit_conc_dose,
+Evaluate TK stats.
+
+This one will go a little bit differently.
+We'll loop over only the fitting options; then within that loop, we'll loop over a list of the possible models, and get the TK stats for each of those models.
+Then we'll rowbind the resulting list of three data.tables together.
+It needs to be done this way because the table of TK stats has different variable names depending on the model, so `data.table` can't row-bind them together directly inside the square brackets.
+
+```{r}
+fit_opts2 <- unique(fit_opts[, .(rescale_time,
+         fit_conc_dose,
          fit_log_conc,
-                                     rescale_time)]
+         method)])
 
-       fit_2comp[, c("fit_conc_dose",
-                "fit_log_conc",
-                "rescale_time") := .(fit_conc_dose,
-                                     fit_log_conc,
-                                     rescale_time)]
+model_list <- c("flat",
+                "1compartment",
+                "2compartment")
 
-       cat("Evaluating TK statistics...\n")
-        #evaluate TK statistics & merge with postprocessed fits
-   this_TKstats_DT <- evaluate_tkstats(cvt_pre = cvt,
-                         fit_flat = fit_flat,
-                         fit_1comp = fit_1comp,
-                         fit_2comp = fit_2comp,
-                         group_by = c("DTXSID",
-                                          "Species",
-                                          "Route",
-                                          "Media"),
-                         dose_norm = TRUE)
-
-    write.csv(this_TKstats_DT,
-                  paste("../inst/ext/evaluate_tkstats_",
+out_DT_list <- sapply(model_list,
+                      function(this_model){
+                        fit_opts2[,
+                                  {
+                                    #Read in fits
+                                    #get fitting outputs file names
+                                    fit_outputs <- dir(path = "../inst/ext",
+                                                       pattern = paste0("PK_fit_table_",
+                                                                        this_model,
                                                                         "_fit_log_conc_",
@@
                                                                         rescale_time, "_",
-                        timestamp,
-                        ".csv",
-                        sep=""), row.names = FALSE)
+                                                                        "method_", method,
+                                                                        "_", timestamp
+                                                       ))
 
-     this_TKstats_DT
+                                    fit_outputs <- paste0("../inst/ext/",
+                                                          fit_outputs)
+
+                                    if(verbose %in% TRUE){
+                                      cat(paste0(paste(fit_outputs,
+                                                       collapse = "\n"), "\n"))
+                                    }
+
+                                    #read in fitting output table for this model
+                                    fit <- fread(grep(x = fit_outputs,
+                                                      pattern = this_model,
+                                                      value = TRUE))
+
+                                    fit[, {
+                                      if(verbose %in% TRUE){
+                                        cat(paste("DTXSID = ", DTXSID, "\n",
+                                                  "Species = ", Species, "\n",
+                                                  "Analysis Type = ", Analysis_Type, "\n",
+                                                  "Studies Analyzed = ", Studies.Analyzed, "\n"))
+                                      }
+                                      #create a 'pkfit' object
+                                      obj <- pkfit(fit = .SD,
+                                                      dat = cvt)
+                                      #calculate the TK stats for this object
+                                      tk <- calc_TK_stats.pkfit(obj)
+                                      nca <- as.data.frame(
+                                        nca.pkfit(obj,
+                                                  dose_norm = TRUE)
+                                      )
+                                      cbind(tk, nca)
                                     },
-  by = c("fit_conc_dose", "fit_log_conc", "rescale_time")]
+                                    by = .(DTXSID,
+                                           Species,
+                                           Analysis_Type,
+                                           Studies.Analyzed,
+                                           LogLikelihood,
+                                           AIC),
+                                    .SDcols = names(fit)
+                                    ]
+                                  },
+                                  by = .(fit_log_conc,
+                                         fit_conc_dose,
+                                         rescale_time,
+                                         method),
+                                  .SDcols = names(fit_opts2)
+                        ]
+                      },
+                      simplify = FALSE,
+                      USE.NAMES = TRUE)
 
-write.csv(TKstats_DT,
-          paste0("../inst/ext/eval_TKstats_",
-          timestamp,
-          ".csv"),
-          row.names = FALSE)
-
+ out_DT <- rbindlist(out_DT_list,
+                     use.names = TRUE,
+                     fill = TRUE,
+                     idcol = "model")
 ```
@@
 
-```{r}
-tk_DT <- fread(paste0("../inst/ext/eval_TKstats_",
-          "2023_01_26",
-          ".csv"))
-```
-
-```{r}
-tk_DT[winmodel %in% "1compartment", AUC_oral_win := AUC_inf_oral_1mgkg.1compartment]
-tk_DT[winmodel %in% "1compartment", AUC_iv_win := AUC_inf_IV_1mgkg.1compartment]
-tk_DT[winmodel %in% "1compartment", tmax_win := tmax_oral.1compartment]
-tk_DT[winmodel %in% "1compartment", Cmax_win := Cmax_oral_1mgkg.1compartment]
-
-tk_DT[winmodel %in% "2compartment", AUC_oral_win := AUC_inf_oral_1mgkg.2compartment]
-tk_DT[winmodel %in% "2compartment", AUC_iv_win := AUC_inf_iv_1mgkg.2compartment]
-tk_DT[winmodel %in% "2compartment", tmax_win := tmax_oral.2compartment]
-tk_DT[winmodel %in% "2compartment", Cmax_win := Cmax_oral_1mgkg.2compartment]
-```
-
 Keep only the Joint analyses, for the sake of simplicity. (These are the ones where multiple studies were fit together, but with a different error SD allowed for each study.)
@@
 ```{r}
-tk_DT_sub <- tk_DT[Analysis_Type %in% "Joint", .(fit_conc_dose, fit_log_conc, rescale_time, DTXSID, Species, Route, Media, AUC_inf_1mgkg, tmax, Cmax_1mgkg, AUC_oral_win, AUC_iv_win, tmax_win, Cmax_win, winmodel)]
+tk_DT_sub <- out_DT[Analysis_Type %in% "Joint", ]
+```
+
+Get the winning model and the p-value vs. flat model.
+
+```{r}
+setorder(tk_DT_sub,
+         method,
+         rescale_time,
+         fit_conc_dose,
+         fit_log_conc,
+         DTXSID,
+         Species,
+         Studies.Analyzed,
+         AIC)
+
+tk_DT_sub[, winmodel := model[1],
+          by = .(method,
+         rescale_time,
+         fit_conc_dose,
+         fit_log_conc,
+         DTXSID,
+         Species,
+         Studies.Analyzed)]
+
+#p-value vs. flat model
+tk_DT_sub[, AIC_flat := AIC[model %in% "flat"], by = .(method,
+         rescale_time,
+         fit_conc_dose,
+         fit_log_conc,
+         DTXSID,
+         Species,
+         Studies.Analyzed)]
+tk_DT_sub[, rel_like_of_flat := exp((AIC - AIC_flat)/2)]
 ```
@@
 ```{r}
-ggplot(tk_DT_sub[rescale_time == FALSE],
-       aes(x = AUC_inf_1mgkg,
-           y = AUC_oral_win)) +
+ggplot(tk_DT_sub[rescale_time == FALSE &
+                   model == winmodel &
+                   method %in% "bobyqa"],
+       aes(x = nca.oral.AUC_inf_1mgkg,
+           y = AUC_inf_oral_1mgkg)) +
   geom_point(aes(color = winmodel)) +
@@
 ```{r}
-ggplot(tk_DT_sub[rescale_time == TRUE],
-       aes(x = AUC_inf_1mgkg,
-           y = AUC_oral_win)) +
+ggplot(tk_DT_sub[rescale_time == TRUE &
+                   model == winmodel &
+                   method %in% "bobyqa"],
+       aes(x = nca.oral.AUC_inf_1mgkg,
+           y = AUC_inf_oral_1mgkg)) +
   geom_point(aes(color = winmodel)) +
@@
 
+What are some examples when model-preidcted AUC is very big?
+
+```{r}
+tk_DT_sub[rescale_time == TRUE &
+                   model == winmodel &
+                   method %in% "bobyqa" &
+            AUC_inf_oral_1mgkg > 1e5 &
+            fit_log_conc %in% TRUE &
+            fit_conc_dose %in% FALSE,
+          .(DTXSID, Species, model, rel_like_of_flat)]
+```
+
 ## AUC IV
@@
 ```{r}
-ggplot(tk_DT_sub[rescale_time == FALSE],
-       aes(x = AUC_inf_1mgkg,
-           y = AUC_iv_win)) +
+ggplot(tk_DT_sub[rescale_time == FALSE &
+                   model == winmodel &
+                   method %in% "bobyqa"],
+       aes(x = nca.iv.AUC_tlast_1mgkg,
+           y = AUC_inf_iv_1mgkg)) +
   geom_point(aes(color = winmodel)) +
   geom_abline(intercept = 0, slope = 1) +
-  facet_grid(rows = vars(fit_conc_dose), cols = vars(fit_log_conc),
+  facet_grid(rows = vars(fit_conc_dose),
+             cols = vars(fit_log_conc),
              labeller = label_both) +

### 2023-02-03 invivopkfit/R/get_model_function.R

@@ -4,18 +4,30 @@
 #'
 #' @param model The name of a model. One of 'flat', '1compartment', or
 #'   '2compartment'.
-#' @return The function corresponding to `model`: `cp_flat()` for 'flat',
-#'   `cp_1comp()` for '1compartment', `cp_2comp()` for '2compartment'. Returned
-#'   as a function object, not as a character string.
+#' @param model.type "analytic" or "full". Default "analytic" to use the
+#'   analytic model solution. "full" to solve the ODE numerically.
+#' @return Character: The name of the function corresponding to `model`:
+#'   `cp_flat()` for 'flat', `cp_1comp()` for '1compartment', `cp_2comp()` for
+#'   '2compartment'.
 #' @author Caroline Ring
 
-get_model_function <- function(model){
+get_model_function <- function(model, model.type){
   if(model %in% "flat"){
-    modelfun <- cp_flat
+    modelfun <- "cp_flat"
   }else if(model %in% "1compartment"){
-    modelfun <- cp_1comp
+    if(model.type %in% "analytic"){
+    modelfun <- "cp_1comp"
+    }else{
+      modelfun <- "httk::solve_1comp"
+    }
   }else if(model %in% "2compartment"){
-    modelfun <- cp_2comp
+    if(model.type %in% "analytic"){
+    modelfun <- "cp_2comp"
+    }else{
+      modelfun <- stop(paste("invivopkfit::get_model_function():",
+                             "model is '2compartment' but model.type is not 'analytic'.",
+                             "Currently, only the analytic solution is implemented for the 2-compartment model."))
+    }
   }else{
     stop(paste("invivopkfit::get_model_function():",
                "model is not one of 'flat', '1compartment' or '2compartment'.",

### 2023-04-12 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
Evaluating residuals by RMSE, R-squared, and overall error SD. Evaluating TK stats by tmax, Cmax, AUC. All evaluations under combinations of the following fitting conditions: log-transform TRUE/FALSE, dose-normalization TRUE/FALSE, rescale time TRUE/FALSE. Residuals for each fitting condition also calculated in all of the following combinations: log-scale residuals TRUE/FALSE, dose-normalized residuals TRUE/FALSE. This way we can compare apples to apples.
Removing accidental inclusion of credentials (which in any case are now outdated)

@@
 Repeat clicking the "New" button and adding variables.
-I added the following system environment variables:
-
-cvt_user = app_cvtdb
-cvt_password = Svg=ZDZkzxX7R=+J
-cvt_host = ccte-postgres-res.dmap-prod.aws.epa.gov
-cvt_dbname = res_cvtdb
 
@@
 ```{r}
+this_date <- "2023_01_05"
 write.csv(cvt_data,

### 2023-05-10 invivopkfit/data-raw/pulling_oral_iv_data_cvtdb.Rmd
Workflow now functions at all steps: setup, preprocessing, prefit, fitting, summary. Methods for coef(), residuals(), predict(), logLik(), AIC(), and BIC() added, along with new method for rmse(). Built in models for flat, 1comp, and 2comp are included. (get_starts_2comp.R still needs work)

--- 2023-04-12 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
@@
 author: "Caroline Ring"
-date: "2022-12-13"
+date: "2023-05-10"
 output: html_document
@@
 
-I don't fully know what all of this means, but it filters out various "internal" tables that are not actually part of CvTdb, and shows only the tables that are.
+I don't fully know what all of this SQL query means, but it filters out various "internal" tables that are not actually part of CvTdb, and shows only the tables that are.
 
@@
 
-Save the pulled CVT data with the edits/normalizations
+To save space, filter CVT data to oral/IV routes and blood/plasma media, because nothing else is implemented right now. Also filter down to cases where administered and analyzed DTXSID are the same.
 
 ```{r}
-this_date <- "2023_01_05"
-write.csv(cvt_data,
-          paste0("../inst/ext/cvt_data_",
-          this_date,
-          ".csv"),
-          row.names = FALSE)
+cvt <- cvt_data[studies.administration_route_normalized %in% c("oral", "iv") &
+                  series.conc_medium_normalized %in% c("blood", "plasma") &
+                  chemicals_dosed.dsstox_substance_id == chemicals_analyzed.dsstox_substance_id]
 ```
+
+```{r}
+getwd()
+```
+
+Save the pulled CVT data with the edits/normalizations, andf also save the current date.
+
+```{r}
+cvt_date <- Sys.Date()
+save(cvt, file = "../data/cvt.rda", compress = "bzip2")
+save(cvt_date, file = "../data/cvt_download_date.rda")
+```

### 2023-05-10 invivopkfit/R/cp_flat.R

@@ -9,11 +9,11 @@
 #'
 #'`params` must include the following named items:
 #'   \describe{
-#'   \item{Vdist}{Apparent volume of central compartment, L/kg BW. Or see below for
+#'   \item{Vdist}{Apparent volume of central compartment, volume/unit BW. Or see below for
 #'   `Fgutabs_Vdist`}
 #'   }
 #'
-#'For oral administration (if any `iv.dose == FALSE`), `params` must also
+#'For oral administration (if any `route %in% "oral"`), `params` must also
 #'include:
 #'   \describe{
 #'   \item{Fgutabs}{Oral bioavailability, unitless fraction. Or see below for
@@ -21,14 +21,14 @@
 #'   }
 #'
 #'For oral administration, in lieu of `Vdist` and `Fgutabs`, you may instead
-#'provide `Fgutabs_Vdist`, the ratio of Fgutabs to Vdist (1/L). This is an
+#'provide `Fgutabs_Vdist`, the ratio of Fgutabs to Vdist (1/volume). This is an
 #'alternate parameterization for situations where `Fgutabs` and `Vdist` are not
 #'identifiable separately (i.e., when oral TK data are available, but IV data
 #'are not). If `Fgutabs` and `Vdist` are provided, they will override any value
 #'provided for `Fgutabs_Vdist`.
 #'
-#'If both oral and IV administration are specified (i.e., some `iv.dose == TRUE`
-#'and some `iv.dose == FALSE`), then `Vdist` is required along with either
+#'If both oral and IV administration are specified (i.e., some `route %in% "iv"`
+#'and some `route %in% "oral"`), then `Vdist` is required along with either
 #'`Fgutabs` or `Fgutabs_Vdist`. (If `Vdist` and `Fgutabs_Vdist` are provided,
 #'but `Fgutabs` is not provided, then `Fgutabs` will be calculated from `Vdist`
 #'and `Fgutabs_Vdist`.)
@@ -37,32 +37,36 @@
 #'`Rblood2plasma`, the ratio of chemical concentration in whole blood to the
 #'chemical concentration in blood plasma.
 #'
-#'@param params A named list of model parameter values. See Details for requirements.
-#'@param time A numeric vector of times in hours.
-#'@param dose A numeric vector of doses in mg/kg
-#'@param iv.dose A logical vector: TRUE for single IV bolus dose; FALSE for
-#'  single oral dose. Not used, but must be present for compatibility with other
-#'  model functions.
[…]

### 2023-05-10 invivopkfit/R/get_starts_flat.R

@@ -1,0 +1,114 @@
+get_starts_flat <- function(data,
+                            par_DF){
+
+  Vdist <- NA_real_
+  Fgutabs_Vdist <- NA_real_
+  Fgutabs <- NA_real_
+  Rblood2plasma <- 1
+
+  #Work only with detects for these rough estimates
+  tmpdat <- subset(data,
+                   Detect %in% TRUE)
+
+  #Split into IV and PO
+  ivdat <- subset(tmpdat,
+                  Route %in% "iv")
+  podat <- subset(tmpdat,
+                  Route %in% "oral")
+
+  has_iv <- any(tmpdat$Route %in% "iv")
+  has_po <- any(tmpdat$Route %in% "oral")
+  has_plasma <- any(tmpdat$Media %in% "plasma")
+  has_blood <- any(tmpdat$Media %in% "blood")
+  has_iv_plasma <- any(tmpdat$Media %in% "plasma" &
+                      tmpdat$Route %in% "iv")
+  has_iv_blood <- any(tmpdat$Media %in% "blood" &
+                         tmpdat$Route %in% "iv")
+  has_po_plasma <- any(tmpdat$Media %in% "plasma" &
+                         tmpdat$Route %in% "oral")
+  has_po_blood <- any(tmpdat$Media %in% "blood" &
+                        tmpdat$Route %in% "oral")
+
+  Vdist_plasma_log10 <- NA_real_
+  Vdist_blood_log10 <- NA_real_
+
+  Fgutabs_Vdist_plasma_log10 <- NA_real_
+  Fgutabs_Vdist_blood_log10 <- NA_real_
+
+  Rblood2plasma_iv_log10 <- NA_real_
+  Rblood2plasma_po_log10 <- NA_real_
+
+  if(has_iv %in% TRUE){
+    if(has_iv_plasma %in% TRUE){
+      #get Vdist for plasma
+      Vdist_plasma_log10 <- with(subset(ivdat,
+                               Media %in% "plasma"),
+                        -1 * mean(log10(Conc/Dose)),
+                             na.rm = TRUE)
+    }
+      if(has_iv_blood %in% TRUE){ #if both blood and plasma IV data, estimate Rblood2plasma
+        #get Vdist for blood
+        Vdist_blood_log10 <- with(subset(ivdat,
+                             Media %in% "blood"),
+                      -1 * mean(log10(Conc/Dose)),
[…]

### 2023-05-10 invivopkfit/R/pk_method_dispatch.R

@@ -13,17 +13,80 @@ pk_add.default <- function(object, pk_obj, objectname){
             object))
 }
 
-#' Preprocess data `pk` method
+#' Preprocess data
 #'
 #' @export
-preprocess_data <- function(x){
+preprocess_data <- function(x, ...){
   UseMethod("preprocess_data", x)
 }
 
 #' Preprocess_data default method
 #'
 #' @export
-preprocess_data.default <- function(x){
+preprocess_data.default <- function(x, ...){
   stop(paste("No 'preprocess_data' method exists for object of class",
              paste(class(x), collapse = ", ")))
 }
+
+#' Prefitting
+#'
+#' @export
+prefit <- function(x, ...){
+  UseMethod("prefit", x)
+}
+
+#' Prefit default method
+#'
+#' @export
+prefit.default <- function(x, ...){
+  stop(paste("No 'prefit' method exists for object of class",
+             paste(class(x), collapse = ", ")))
+}
+
+#' Fitting
+#'
+#' @export
+fit <- function(x, ...){
+  UseMethod("fit", x)
+}
+
+#' Fit default method
+#'
+#' @export
+fit.default <- function(x, ...){
+  stop(paste("No 'fit' method exists for object of class",
+             paste(class(x), collapse = ", ")))
+}
+
+#' Root mean squared error (RMSE)
+#'
+#' @export
+rmse <- function(x){
+  UseMethod("rmse", x)
+}
+
+#' Root mean squared error (RMSE) default method
+#'
+#' @export
+rmse.default <- function(x, ...){
+  stop(paste("No 'rmse' method exists for object of class",
+             paste(class(x), collapse = ", ")))
+}
+
+#' Coefficient standard deviations
+#' @param obj An object
+#' @export
+coef_sd <- function(obj,
+                    ...){
+  UseMethod("coef_sd", obj)
+}
+
+#' Coefficient standard deviation default
+#'
+#' @param obj An object
+#' @export
+coef_sd.default <- function(obj, ...){
+  stop(paste("No 'coef_sd' method exists for object of class",
+             paste(class(x), collapse = ", ")))
+}
+

### 2023-05-10 invivopkfit/R/pkproto_data_settings.R

@@ -1,23 +1,44 @@
 #' Data preprocessing settings
 #'
-
-#' @param routes_keep
-#' @param media_keep
-#' @param impute_loq
-#' @param loq_group
-#' @param calc_loq_factor
-#' @param impute_sd
-#' @param suppress.messages
+#' @param routes_keep Character: A list of routes to keep. Data will be filtered
+#'   so that the harmonized variable `Route` includes only values in
+#'   `routes_keep`. Default is `c("oral", "iv")`.
+#' @param media_keep Character: A list of media to keep. Data will be filtered
+#'   so that the harmonized variable name `Media` includes only values in
+#'   `media_keep`. Default is `c("blood", "plasma")`.
+#' @param impute_loq TRUE or FALSE: Whether to impute missing LOQ values.
+#' @param loq_group A list of variables, specified using a call to
+#'   [dplyr::vars()]. These should be harmonized variable names. Unique
+#'   combinations of these variables define groups of data. Within each group,
+#'   any missing LOQ values will be imputed as the minimum detected Value in the
+#'   group, multiplied by `calc_loq_factor`. Default is `dplyr::vars(Chemical,
+#'   Species, Reference, Media)`.
+#' @param calc_loq_factor  A numeric factor used for imputing missing LOQ.
+#'   Within each group defined in `loq_group`, any missing LOQ values will be
+#'   imputed as the minimum detected Value in the group, multiplied by
+#'   `calc_loq_factor`. Default 0.45.
+#' @param impute_sd TRUE or FALSE: Whether to impute missing SD values.
+#' @param sd_group A list of variables, specified using a call to
+#'   [dplyr::vars()]. These should be harmonized variable names. Unique
+#'   combinations of these variables define groups of data. Within each group,
+#'   any missing SD values will be imputed as the minimum non-missing SD value
+#'   in the group. Default is `dplyr::vars(Chemical, Species, Reference,
+#'   Media)`.
+#' @param suppress.messages TRUE or FALSE: Whether to suppress verbose messages.
+#'   Default FALSE.
+#' @param ... Any additional arguments. Currently ignored.
 #'
-#' @return An object of class `pk_data_settings`.
+#' @return An object of class `pk_data_settings`. This is a named list of the
+#'   arguments provided to this function and their values.
 #' @author Caroline Ring
+#' @export
 settings_data <- function(routes_keep = c("oral", "iv"),
                              media_keep = c("blood", "plasma"),
[…]

### 2023-05-10 invivopkfit/R/pkproto_stat_model.R

@@ -36,8 +36,8 @@ for(this_model in model){
 #' - `params`: A named list of parameter values
 #' - `time`: A numeric vector of time values
 #' - `dose`: A numeric vector of dose values. Currently, only a single bolus dose at time 0 is supported.
-#' - `iv.dose`: A logical vector that is TRUE if the dose was administered intravenously; FALSE if the dose was administered orally
-#' - `medium`: The tissue in which concentration is to be predicted. Currently, only `blood` and `plasma` are supported.
+#' - `route`: A character vector of the route of administration. Currently, only `'oral'` and `'iv'` are supported.
+#' - `medium`: The tissue in which concentration is to be predicted. Currently, only `'blood'` and `'plasma'` are supported.
 #'
 #'See [cp_1comp()], [cp_2comp()], [cp_flat()] for examples.
 #'
@@ -49,18 +49,20 @@ for(this_model in model){
 #'
 #'See [auc_1comp()], [auc_2comp()], [auc_flat()] for examples.
 #'
-#'# `get_params_fun` requirements
+#'# `params_fun` requirements
 #'
-#'`get_params_fun` should be a function whose first argument is a `data.frame`,
+#'`params_fun` should be a function whose first argument is a `data.frame`,
 #'which will be the pre-processed data using `invivopkfit` harmonized variable
-#'names. It should then return a `data.frame` with the following variables:
+#'names. It may take additional arguments, which can be provided in
+#'`params_fun_args`. The function should return a `data.frame` with the
+#'following variables:
 #'
 #' - `param_name`: Character vector, listing parameter names for the model
 #' - `param_units`: Character vector, listing units of each model parameter
 #' - `optimize_param`: Logical (TRUE/FALSE), whether each parameter is to be estimated given the available data
 #' - `use_param`: Logical (TRUE/FALSE), whether each parameter is to be used in the model even if it is not estimated (i.e., if a parameter value is to be held constant while the others are estimated, then `optimize_param` should be FALSE but `use_param` should be TRUE)
-#' -`lower_bound`: Numerical. Lower bounds for each parameter. May be `-Inf` if no lower bound.  If `opt_param` or `use_param` is FALSE, thenthe corresponding `lower_bound` will be ignored (because the parameter is not being estimated from the data).
-#' - `upper_bound`: Numerical. Upper bounds for each parameter. May be `Inf` if no upper bound. If `opt_param` or `use_param` is FALSE, then the corresponding `upper_bound` will be ignored (because the parameter is not being estimated from the data).
[…]

### 2023-05-10 invivopkfit/data-raw/pulling_oral_iv_data_cvtdb.Rmd
Add data-raw/ Rmd to put cleaned, filtered version of CvT data in data/

@@
 
-Save the pulled CVT data with the edits/normalizations, andf also save the current date.
+Filter out any variables that are all-NA.
+
+```{r}
+all_na <- cvt[, sapply(.SD, function(x) all(is.na(x)))]
+na_vars <- names(all_na)[all_na %in% TRUE]
+cvt[, (na_vars) := NULL]
+```
+
+Save the pulled CVT data with the edits/normalizations, and also save the current date.
 

### 2023-05-10 data-raw/how_to_norm_residus.Rmd
Reorganizing with top level directory as the R package, so I can use packages usethis and testthat properly

---
title: "How to normalize residuals?"
author: "Caroline Ring"
date: "2023-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Further thoughts (2023-01-26)

How should we "normalize" residuals in order to make comparisons?

Is a residual error of 2 the same when the observed concentration is 1 and when the observed concentration is 10?

Let's take an example. Here are two plots of the same fit to the same data: one on the natural scale and one on the log scale,

Here's a plot on the natural scale:
![Solvent red 1, non-log-transformed, non-dose-normalized]("C:\Users\cring\invivoPKfit\inst\ext\plots\Joint Analysis\plots_solventred_nonlog_nondosenorm.pdf")

Here's a plot on the log scale:
![Solvent red 1, log-transformed, non-dose-normalized]("C:\Users\cring\invivoPKfit\inst\ext\plots\Joint Analysis\plots_solventred_log_nondosenorm.pdf")

On the natural scale, residuals are large around Cmax, and small in the tail.

On the log scale, residuals are small around Cmax, and large in the tail.

Which is the better way to look at things?

Does it matter that this fit was done on the natural scale -- so the optimizer "saw" the small residuals in the tail?

How should I compare this fit to one done on the log scale?

Here's a plot of the second fit on the natural scale:
![Solvent red 1, fit on log scale, non-log-transformed, non-dose-normalized]("C:\Users\cring\invivoPKfit\inst\ext\plots\Joint Analysis\plots_solventred_fitlog_plotnonlog_nondosenorm.pdf")

Here's a plot of the second fit on the log scale:
![Solvent red 1, fit on log scale, log-transformed, non-dose-normalized]("C:\Users\cring\invivoPKfit\inst\ext\plots\Joint Analysis\plots_solventred_fitlog_plotlog_nondosenorm.pdf")

On the non-log scale, these residuals are much bigger at Cmax compared to the first fit, but still small in the tail. But on the log scale, the residuals are bigger at Cmax compared to the first fit, but smaller in the tail.

Which is the most appropriate comparison between these two fits: residuals on the log scale or on the natural scale?

For the first fit (natural-scale, non-dose-normalized fit), the natural-scale, dose-normalized RMSE is 0.007 and the log-scale, dose-normalized RMSE is 4.384. (This is for the winning model, 1-compartment.)

For the second fit (log-scale, non-dose-normalized fit), the natural-scale, non-dose-normalized RMSE is 0.146452812243452. The log-scale, dose-normalized RMSE is 1.568. (Again, this is for the winning model, 2-compartment.)

By log-scale RMSE, the log-scale fit wins. By natural-scale RMSE, the natural-scale fit wins.

This isn't exactly a shock: the log-scale fit minimizes log-scale errors, and the natural-scale fit minimizes natural-scale errors, so we would expect each fit to win on its own type of error.

But how do we compare them? Is there any basis for deciding that one fit is overall better than the other?

We could compare predictions of Cmax. By that metric, the natural-scale fit would certainly win -- the log-scale fit vastly underpredicts Cmax.

We could compare predictions of AUC. Again, by that metric, the natural-scale fit would win. This is because both Cmax and AUC really work on the natural scale. Cmean would be the same way, since it is calculated from AUC.

Css: we have no 'experimental' Css to compare to, so there is no way of judging that one.

If we look at TK summary stats -- then the natural fit really seems to win for this chemical. Is that what we should be looking at? In practice, that is usually what we want to predict with a TK model -- the blood/plasma concentration at a particular dose, whether that be peak, average, steady-state. That is what we use for reverse dosimetry.

We could check out the "factor of two" criterion. We could compute residuals as a fraction of observed concentrations, and then compute the average (absolute) fractional residual, and the max (absolute) fractional residual. We could then see if the "factor of two" criterion actually correlates with how well Cmax, tmax, AUC are predicted.

Also -- we never do that good a job of predicting Cmax. Why is that? Is it scaling issues with the optimizer? Would it help if we fit Vdist/Fgutabs, instead of Fgutabs/Vdist? Or would the scaling issue just be the same problem in the other direction?

### 2023-05-10 data-raw/summary_breusch_pagan.Rmd
Reorganizing with top level directory as the R package, so I can use packages usethis and testthat properly

---
title: "Breusch-Pagan for summary data"
author: "Caroline Ring"
date: "2023-01-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The Breusch-Pagan test is a way of testing for heteroscedasticity in residuals.

In effect, you regress the squared residuals on one or more explanatory variables (e.g. the predicted values), then take the R-squared of the regression times the number of observations, which then takes a chi-squared distribution whose degrees of freedom are equal to the number of explanatory variables.

My current problem: What to do with summary data?

# Setup

Assume data are organized into $i = 1, 2, \ldots, G$ groups, each containing $N_i$ individuals indexed as $j = 1, 2, \ldots, N_i$. A single individual observation would be indexed as $y_{ij}$.

With summary data, we don't have individual observations. Instead, for each group $i$, we have the sample mean $\bar{y}_i$, sample standard deviation $s_i$, and the number of individuals in the sample $N_i$. We also know the dose for each group, $D_i$.

We also have a TK model prediction for each group, $\mu_i$.

The total number of individuals across all groups is $N = \sum_{i=1}^G N_i$.

## If we did have individual data

The residual for individual $j$ in group $i$ would be

$$ \epsilon_{ij} = y_{ij} - \mu_{ij} $$

# Linear model of squared residuals

I'm going to leave this at one explanatory variable for the sake of simplicity. I expect to only use one in practice. Specifically, I plan to use the predicted value (by the fitted TK model).

$$ (\epsilon_{ij})^2 = \beta_0 + \beta_1 \mu_{ij} + \delta_{ij} = \widehat{(\epsilon_{ij})^2} + \delta_{ij}$$
Assume the $\delta_{ij}$ are iid zero-mean normal.

# Goal: calculate R-squared of the above linear model

$$ r^2 = 1 - \frac{
\sum_{i=1}^G \sum_{j=i}^{N_i}
\left(
(\epsilon_{ij})^2 - \widehat{(\epsilon_{ij})^2}
\right)^2 
}
{
\sum_{i=1}^G \sum_{j=i}^{N_i} \left(
(\epsilon_{ij})^2 - \overline{(\epsilon_{ij})^2}
\right)^2 
} $$

where $\overline{(\epsilon_{ij})^2}$ is the overall average squared residual across all groups:

$$ \overline{(\epsilon_{ij})^2} = \frac{1}{N} \sum_{i=1}^G \sum_{j=1}^{N_i}  (\epsilon_{ij})^2$$ 
Let's rewrite this using our definitions above

$$ r^2 = 1 - \frac{
\sum_{i=1}^G \sum_{j=i}^{N_i}
\left(
(y_{ij} - \mu_{i})^2 - \left( \beta_0 + \beta_1 \mu_{i} \right)
\right)^2 
}
{
\sum_{i=1}^G \sum_{j=1}^{N_i} \left(
(y_{ij} - \mu_{i})^2 - \frac{1}{N} \sum_{i=1}^G \sum_{j=1}^{N_i}  (y_{ij} - \mu_{i})^2
\right)^2 
} $$

## Numerator

Expand

$$ \sum_{i=1}^G \sum_{j=i}^{N_i}
\left(
y_{ij}^2 - 2 y_{ij} \mu_{i} + \mu_{i}^2 - \beta_0 - \beta_1 \mu_{i}
\right)^2 $$

I think I worked it out in `bp_rsq_summary2.py`, using SymPy. It comes to

```{r, eval = FALSE}
sum(3*N*si^4 + 2*si^2*(b0 + b1*mui - 3*(ybari - mui)^2) + (b0^2 + 2*b0*(b1*mui - si^2 - (ybari - mui)^2) + b1^2*mui^2 + 2*b1*(-si^2 - (ybari - mui)^2)*mui + 6*si^2*mui^2 + ybari^4 - 4*ybari^3*mui + ybari^2*(6*si^2 + 6*mui^2) + ybari*(-12*si^2*mui - 4*mui^3) + mui^4)*Ni)
```

# Denominator

Again, see SymPy. It comes to

```{r, eval = FALSE}
sum(3*N*si^4 + eps2bar^2*Ni + 4*eps2bar*ybari*Ni*mui - 2*eps2bar*(si^2*(Ni - 1) + ybari^2*Ni) - 2*eps2bar*Ni*mui^2 + 6*si^2*ybari^2*Ni - 6*si^2*ybari^2 + ybari^4*Ni - 4*ybari*(3*si^2*Ni - 3*si^2 + ybari^2*Ni)*mui - 4*ybari*Ni*mui^3 + 6*(si^2*(Ni - 1) + ybari^2*Ni)*mui^2 + Ni*mui^4)
```

where

```{r, eval = FALSE}
eps2bar = sum((Ni-1) * si^2 + Ni * ybari^2 - 2 * mui * Ni * ybari + Ni * mui^2)
```

Then I think we have it.

For the likelihood for fitting:

we use the same thing as the numerator

```{r}
sum(3*N*si^4 + 2*si^2*(b0 + b1*mui - 3*(ybari - mui)^2) + (b0^2 + 2*b0*(b1*mui - si^2 - (ybari - mui)^2) + b1^2*mui^2 + 2*b1*(-si^2 - (ybari - mui)^2)*mui + 6*si^2*mui^2 + ybari^4 - 4*ybari^3*mui + ybari^2*(6*si^2 + 6*mui^2) + ybari*(-12*si^2*mui - 4*mui^3) + mui^4)*Ni)
```

### 2023-05-16 R/pk.R
Changed model names from 1comp, 2comp, flat to model_1comp, model_2comp, model_flat

@@ -48,7 +48,7 @@
 #'For example, you might write at the console
 #'
 #'```
-#' my_pk <- pk(my_data) + stat_model(model = "1comp") + data_settings(impute_loq = TRUE)
+#' my_pk <- pk(my_data) + stat_model(model = model_1comp) + data_settings(impute_loq = TRUE)
 #'```
 #'
 #'This is OK even though `data_settings` provides instructions for data
@@ -59,7 +59,7 @@
 #'same data set. You can simply write
 #'
 #' ```
-#'my_pk <- my_pk + stat_model(model = "2comp")
+#'my_pk <- my_pk + stat_model(model = model_2comp)
 #' ```
 #'
 #'Then you might realize that you actually wanted to dose-normalize the

### 2023-05-16 R/pkproto_stat_model.R

@@ -1,9 +1,11 @@
 #' Add PK model(s) to be fitted
 #'
-#' @param model The name(s) of models to be fitted. These should be the names of objects of class `pk_model`. Built-in options are `"flat"`,
-#'   `"1comp"`, and `"2comp"`. You may add your own model by using [pk_model()].
+#' @param model A character vector: the name(s) of models to be fitted. These
+#'   should be the names of objects of class `pk_model`. Built-in options are
+#'   [`model_flat`], [`model_1comp`], and [`model_2comp`]. You may add your own
+#'   model by using [pk_model()].
 
-stat_model <- function(model = c("flat", "1comp", "2comp"),
+stat_model <- function(model = c("model_flat", "model_1comp", "model_2comp"),
                       ...){
   this_stat_model <- list()
   #pull pk_model objects by each name

### 2023-05-17 R/facet_by.R
Starting to sketch out faceting

@@ -1,0 +1,72 @@
+#' Facet a PK fit
+#'
+#' Create a "faceted" [pk()] object.
+#'
+#' This function automates the process of doing PK fitting in "batch mode", when
+#' you have multiple concentration-dose-time datasets to fit, and you want to
+#' fit them all using the same set of instructions.
+#'
+#' When you do something like
+#'
+#' ```
+#' pk_cvt <- pk(cvt) +
+#'  facet_by(
+#'  facets = vars(
+#'  chemicals_analyzed.dsstox_substance_id,
+#' subjects.species_harmonized
+#' )
+#' )
+#' ```
+#'
+#' Now `pk_cvt` is an object of class `pk_faceted`: under the hood, a
+#' [tibble::tibble()] with one row for each group defined by a unique
+#' combination of the faceting variables, and a `list` column containing a
+#' [pk()] object corresponding to each group.
+#'
+#' All of the [pk()] objects in the `list` column contain the same set of
+#' instructions, and they will all have the same status (*i.e.*, they are all in
+#' the same stage of the workflow at the same time). The only thing different
+#' among them is the data.
+#'
+#' If you call a `pk` method on a `pk_faceted` object, the method will be
+#' applied in turn to the [pk()] object for each group.
+#'
+#' If the method returns a [pk()] object (e.g. [preprocess_data.pk()],
+#' [data_info.pk()], [prefit.pk()], and [fit.pk()]), then the result for a
+#' `pk_faceted` object will be another `pk_faceted` object.
+#'
+#' If the method returns something other than a [pk()] object (e.g. [coef.pk()],
+#' [coef_sd.pk()], [residuals.pk()], [predict.pk()], ...) then the result for a
+#' `pk_faceted` object will simply be a [tibble::tibble()] with a `list` column
+#' containing the result for each group -- it won't have class `pk_faceted`.
+#'
+#' This function is named by analogy to [ggplot2::facet_wrap()] and
+#' [ggplot2::facet_grid()]. Those functions split up a dataset into groups by
+#' one or more `factor` variables, and produce a "faceted" grid of plots for
+#' each group of data. This function does an analogous thing for a [pk()]
+#' analysis. The dataset is split into groups by the unique combinations of
+#' variables in `facets`. For each group, a separate [pk()] object is created,
+#' using the instructions provided by the user. When methods like
+#' [preprocess_data()], [data_info()], [prefit()], and [fit()] are called on the
[…]

### 2023-05-22 R/conc_scale_use.R
All fit evaluation methods now handle argument 'exclude'. If appropriate they also take argument 'use_scale_conc' so user can specify different concentration transformation if desired (this does not apply to logLik.pk(), AIC.pk(), or BIC.pk()).

@@ -1,0 +1,47 @@
+#' Get concentration scalings
+#'
+#' A helper function to get concentration scalings
+#'
+#' In methods applied to fitted [pk()] objects that also accept `newdata`
+#' arguments, the user may specify whether to use the concentration scaling of
+#' the fitted [pk()] object, or use a different concentration scaling. This is
+#' done by specifying an argument `use_scale_conc`, which may be `TRUE` (to use
+#' the scaling from the fitted object), `FALSE` (to use no scaling), or may be a
+#' named list with elements `dose_norm` and `log10_trans` to specify
+#' scaling/transformation directly. This helper function parses the
+#' `use_scale_conc` argument.
+#'
+#' @param use_scale_conc The `use_scale_conc` argument (see Details)
+#' @param obj A [pk()] object
+#' @return A named list with elements `dose_norm` and `log10_trans`, both
+#'   logical.
+conc_scale_use <- function(use_scale_conc,
+                           obj){
+  #apply scaling or not?
+  if(is.logical(use_scale_conc) & length(use_scale_conc) %in% 1){
+    if(use_scale_conc %in% TRUE){
+      dose_norm <- obj$scales$conc$dose_norm
+      log10_trans <- obj$scales$conc$log10_trans
+    }else{
+      dose_norm <- FALSE
+      log10_trans <- FALSE
+    }}else{
+      if(!is.list(use_scale_conc)){
+        stop("use_scale_conc must be either TRUE, FALSE, or a list like `list(dose_norm = TRUE/FALSE, log10_trans = TRUE/FALSE)`")
+      }
+
+      if(!all(c("dose_norm", "log10_trans") %in% names(use_scale_conc))){
+        stop("use_scale_conc must be either TRUE, FALSE, or a list like `list(dose_norm = TRUE/FALSE, log10_trans = TRUE/FALSE)`")
+      }
+
+      if(!all(sapply(use_scale_conc[c("dose_norm", "log10_trans")], is.logical))){
+        stop("use_scale_conc must be either TRUE, FALSE, or a list like `list(dose_norm = TRUE/FALSE, log10_trans = TRUE/FALSE)`")
+      }
+
+      dose_norm <- use_scale_conc$dose_norm
+      log10_trans <- use_scale_conc$log10_trans
+    }
+
+  return(list("dose_norm" = dose_norm,
+         "log10_trans" = log10_trans))
+}

### 2023-05-22 R/pk_methods_coef.R

@@ -16,6 +16,7 @@
 #'   hyperparameters (whose names begin with "sigma").
 #' @export
 #' @author Caroline Ring
+#' @family methods for fitted pk objects
 coef.pk <- function(obj,
                     model = NULL,
                     method = NULL,

### 2023-06-08 data-raw/batchMode_trial_gpm.Rmd

---
title: "PK object batch mode trial"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj branch
library(tidyverse)
library(here)
```

## Working with one DTXSID + Species combination

```{r data_loading}
cvt %>% names()

cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>% unique() %>% length()

my_predata <- subset(cvt,
                     chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442" &
                       subjects.species_harmonized %in% "rat")

```

```{r}
my_pk <- pk(data = my_predata) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = "L-BFGS-B") +
  scale_conc(dose_norm = TRUE) +
  # scale_time() +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species))

my_pk <- preprocess_data(my_pk)

my_pk <- data_info(my_pk)

my_pk <- prefit(my_pk) 
# I get a warning here 
# "In med_y - pred : "
# "longer object length is not a multiple of shorter object length"

my_pk <- fit(my_pk)

pk_results <- coef(my_pk)

predict(my_pk) # Doesn't run rn for some reason
pred_results <- predict(my_pk)

plot_results <- plot(my_pk)
print(plot_results)

my_tkstats <- get_tkstats(my_pk)
```

### 2023-06-08 data-raw/batchMode_trial_gpm.Rmd
Generated a "wide" data.frame for the fit summaries that could perhaps be used in some downstream analyses.

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
+
+library(tidyverse, quietly = TRUE)
 devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj branch
-library(tidyverse)
-library(here)
+
 ```
@@
 
+The first step is understanding how to work with a single DTXSID + Species combination.
+Once we know how to do this, it will be easier to apply it to (potentially)
+a list of these objects in a vectorized fashion.
+Here I subset the `cvt` object and use that as my working data.
+
 ```{r data_loading}
-cvt %>% names()
-
+# There are 103 unique chemicals in this object
 cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>% unique() %>% length()
@@
 
-```{r}
+Next, I want to follow the steps required for the particular analysis I would like.
+In this instance, I set the optimizer to "L-BFGS-B" and dose-normalize the output.
+I do not scale the time or log-transform the concentration values.
+Since I would like to do a "Pooled" analysis,
+I set the `error_group = vars(Chemical, Species)`.
+
+```{r single_fit}
 my_pk <- pk(data = my_predata) +
@@
 
-my_pk <- data_info(my_pk)
+my_pk <- data_info(my_pk) # summarize error (Returning more or less than 1 row per summarize)
 
@@
 my_pk <- fit(my_pk)
+```
 
+```{r single_result_extraction}
+# A list of each fit model with the estimated parameters for that model
+# Each row has 
 pk_results <- coef(my_pk)
 
-predict(my_pk) # Doesn't run rn for some reason
 pred_results <- predict(my_pk)
@@
 plot_results <- plot(my_pk)
-print(plot_results)
 
@@
 ```
+
+```{r single_result_tidying}
+# Currently, it seems tk_stats_*() does not return dose-normalized values.
+my_tkstats %>%
+  pluck("model_1comp") %>%
+  distinct() %>% head()
+
+# Assembling the data that I want to add for a summary data.frame
+my_pk$fit$model_flat
+my_pk$settings_optimx$method
+my_pk$scales$conc$dose_norm
+my_pk$scales$conc$log10_trans
+rlang::quo_get_expr(my_pk$scales$conc$expr)
+
+# Building the wide "fit" data.frame from various parts of the `pk` object
+my_pk$fit %>%
+  as.data.frame() %>%
+  # Switches default order of 
+  rename_with(~paste0(str_extract(.,
+                                  pattern = "(?<=\\.).+$"),
+                      ".",
+                      str_extract(.,
+                                  pattern = "(?<=model_)[:alnum:]+")
+                      )
+  ) %>%
+  dplyr::select(-(starts_with(c("kkt", "xtime", "niter", "fevals", "gevals", "sigma")))) %>%
+  rownames_to_column(var = "method") %>%
+  mutate(DTXSID = unique(my_pk$data$DTXSID),
+         Species = unique(my_pk$data$Species),
+         fit_log_conc = my_pk$scales$conc$log10_trans,
+         fit_conc_dose = my_pk$scales$conc$dose_norm,
+         rescale_time = ifelse(my_pk$scales$time == "identity",
+                               FALSE, TRUE),
+         .before = method) %>%
+  View()
+
+```

### 2023-06-09 R/pk_faceted_methods_get_stat_error_model.R
Faceted analysis runs without crashing, but gives junk results.

@@ -7,6 +7,6 @@
 #'@export
 #'@author Caroline Ring
 #'@family methods for pk_faceted objects
-get_stat_error_model.pk <- function(obj, ...){
+get_stat_error_model.pk_faceted <- function(obj, ...){
 obj %>% dplyr::mutate(get_stat_error_model =purrr::map(pk_object,get_stat_error_model))
 }

### 2023-06-09 R/pk_faceted_methods_summary.R

@@ -7,6 +7,6 @@
 #'@export
 #'@author Caroline Ring
 #'@family methods for pk_faceted objects
-summary.pk <- function(obj, ...){
+summary.pk_faceted <- function(obj, ...){
 obj %>% dplyr::mutate(summary =purrr::map(pk_object,summary))
 }

### 2023-06-09 R/pkproto_facet_data.R

@@ -60,7 +60,8 @@
 #'   always added to a [pk()] object using [`+.pk`].
 #' @export
 #' @author Caroline Ring, Gilbert Padilla Mercado, Paul Kruse
-facet_data <- function(facets = vars(Chemical, Species),
+facet_data <- function(facets = vars(chemicals_analyzed.dsstox_substance_id,
+                                     subjects.species_harmonized),
                      ...){
   #get arguments and values
   argg <- c(as.list(environment()), list(...))

### 2023-06-09 data-raw/make_pk_faceted_methods.R

@@ -9,13 +9,16 @@ pk_methods_names <- gsub(x=pk_methods_names,
                          replacement = "",
                          fixed = TRUE)
 
+#these behave differently (they modify in place)
+#and I have created these manually.
 pk_methods_names <- setdiff(pk_methods_names,
                             c("preprocess_data",
                               "data_info",
                               "prefit",
-                              "fit"))
+                              "fit",
+                              "add_pkproto"))
 
-for (i in seq_along(pk_methods_list)){
+for (i in seq_along(pk_methods_names)){
   this_name <- pk_methods_names[i]
 
   #produce text of the pk_faceted script
@@ -39,7 +42,7 @@ for (i in seq_along(pk_methods_list)){
                           "@family methods for pk_faceted objects"
                           )
                         ),
-                 paste0(this_name, ".pk <- function(obj, ...){"),
+                 paste0(this_name, ".pk_faceted <- function(obj, ...){"),
                  paste0("obj %>% dplyr::mutate(",
                         this_name, " =",
                         "purrr::map(pk_object,",

### 2023-06-09 R/pk_faceted_methods_BIC.R
Faceted workflow now works from initialization, to preprocessing, to data_info, to prefitting, to fitting. Those methods have been renamed as do_[verb] to indicate they do something to modify the pk object. Post-processing methods have not been updarted to reflect new faceted workflow yet. Those are named as get_[thing] to indicate they get something from a pk object but do not modify it.

@@ -1,12 +1,0 @@
-#'BIC
-#'
-#'BIC for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` BIC ` containing the results of applying [BIC.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-BIC.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(BIC =purrr::map(pk_object,BIC))
-}

### 2023-06-09 R/pk_faceted_methods_coef_sd.R

@@ -1,12 +1,0 @@
-#'coef_sd
-#'
-#'coef_sd for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` coef_sd ` containing the results of applying [coef_sd.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-coef_sd.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(coef_sd =purrr::map(pk_object,coef_sd))
-}

### 2023-06-09 R/pk_faceted_methods_get_data_info.R

@@ -1,12 +1,0 @@
-#'get_data_info
-#'
-#'get_data_info for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` get_data_info ` containing the results of applying [get_data_info.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-get_data_info.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(get_data_info =purrr::map(pk_object,get_data_info))
-}

### 2023-06-09 R/pk_faceted_methods_get_data_sigma_group.R

@@ -1,12 +1,0 @@
-#'get_data_sigma_group
-#'
-#'get_data_sigma_group for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` get_data_sigma_group ` containing the results of applying [get_data_sigma_group.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-get_data_sigma_group.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(get_data_sigma_group =purrr::map(pk_object,get_data_sigma_group))
-}

### 2023-06-09 R/pk_faceted_methods_get_nca.R

@@ -1,12 +1,0 @@
-#'get_nca
-#'
-#'get_nca for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` get_nca ` containing the results of applying [get_nca.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-get_nca.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(get_nca =purrr::map(pk_object,get_nca))
-}

### 2023-06-09 R/pk_faceted_methods_get_prefit.R

@@ -1,12 +1,0 @@
-#'get_prefit
-#'
-#'get_prefit for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` get_prefit ` containing the results of applying [get_prefit.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-get_prefit.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(get_prefit =purrr::map(pk_object,get_prefit))
-}

### 2023-06-09 R/pk_faceted_methods_get_settings_data_info.R

@@ -1,12 +1,0 @@
-#'get_settings_data_info
-#'
-#'get_settings_data_info for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` get_settings_data_info ` containing the results of applying [get_settings_data_info.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-get_settings_data_info.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(get_settings_data_info =purrr::map(pk_object,get_settings_data_info))
-}

### 2023-06-09 R/pk_faceted_methods_get_settings_preprocess.R

@@ -1,12 +1,0 @@
-#'get_settings_preprocess
-#'
-#'get_settings_preprocess for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` get_settings_preprocess ` containing the results of applying [get_settings_preprocess.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-get_settings_preprocess.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(get_settings_preprocess =purrr::map(pk_object,get_settings_preprocess))
-}

### 2023-06-09 R/pk_faceted_methods_get_winning_model.R

@@ -1,12 +1,0 @@
-#'get_winning_model
-#'
-#'get_winning_model for pk_faceted objects
-#'
-#'@param obj An object of class `pk_faceted`
-#'@return A [tibble::tibble()] grouped by the faceting variables with a new variable ` get_winning_model ` containing the results of applying [get_winning_model.pk()] to each item in the list column of [pk()] objects, `obj$pk_object`
-#'@export
-#'@author Caroline Ring
-#'@family methods for pk_faceted objects
-get_winning_model.pk_faceted <- function(obj, ...){
-obj %>% dplyr::mutate(get_winning_model =purrr::map(pk_object,get_winning_model))
-}

### 2023-06-09 R/pk_methods_data_info.R

@@ -1,150 +1,0 @@
-#' calculate summary data info
-#'
-#' Calculate summary data information, including non-compartmental analysis.
-#'
-#'
-#' @param obj An object of class [pk()]
-#' @export
-#' @importFrom magrittr `%>%`
-#' @author Caroline Ring
-data_info.pk <- function(obj){
-
-  #check status
-  objname <- deparse(substitute(obj))
-  status <- obj$status
-  if(status >= status_data_info){
-    warning(paste0(objname,
-                   " current status is ",
-                   status,
-                   ". data_info() will reset its status to ",
-                   status_data_info,
-                   ". Any results from later workflow stages will be lost.\n"))
-  }
-
-  #if preprocessing not already done, do it
-  if(obj$status < status_preprocess){
-    obj <- preprocess_data(obj)
-  }
-
-  if(obj$settings_preprocess$suppress.messages %in% FALSE){
-    message("data_info.pk(): Getting data summary info\n")
-  }
-
-  data <- obj$data
-
-  #get data summary
-  if(obj$settings_preprocess$suppress.messages %in% FALSE){
-    message("data_info.pk(): Getting data summary statistics\n")
-  }
-
-  #grouping for data summary:
-  #data grouping, plus also Route and Media if not already included in data grouping
-  summary_group <-   unique(
-    c(obj$data_group,
-      vars(Route, Media)
-    )
-  )
-
-  data_summary_out <- data_summary(obj = obj,
-                               newdata = NULL,
-                               summary_group = summary_group
-  )
-
-  #do NCA dose-normalized
-  if(obj$settings_preprocess$suppress.messages %in% FALSE){
-    message("data_info.pk(): Doing dose-normalized non-compartmental analysis\n")
-  }
-  nca_dose_norm <- nca(obj = obj,
-                       newdata = NULL,
-                       nca_group = summary_group,
-                       exclude = TRUE,
-                       dose_norm = TRUE)
-  #pivot wider
-  #first get names of grouping vars
-  grp_vars <- sapply(summary_group,
-                     rlang::as_label)
-#then pivot wider
-  nca_dose_norm <-   nca_dose_norm %>%
-    tidyr::pivot_wider(id_cols = tidyselect::all_of(grp_vars),
-                       names_from = param_name,
-                       values_from = param_value) %>%
-    as.data.frame()
-
[…]

### 2023-06-09 R/pk_methods_do_prefit.R

@@ -1,0 +1,219 @@
+#' Do pre-fitting
+#'
+#' Do pre-fit calculations and checks
+#'
+#' This function does the following:
+#'
+#' - Based on the error model in `stat_error_model` and the pre-processed data, determines the number of residual standard deviations ("sigmas") hyperparameters to be estimated.
+#' - Determines which "sigma" hyperparameter corresponds to each observation in the data.
+#' - Calculates lower/upper bounds and starting guesses for each "sigma" hyperparameter
+#' - For each model in `stat_model`, calls its `params_fun`, the function that, based on the data, determines whether to optimize each model parameter, and calculates lower/upper bounds and starting guesses for each model parameter to be optimized. Only non-excluded observations are passed to each model's `params_fun`.
+#'
+#'
+#' Lower bounds for each "sigma" hyperparameter are set to `sqrt(.Machine$double_eps)`.
+#'
+#' Upper bounds for each "sigma" hyperparameter are calculated as the standard
+#' deviation of observations in the corresponding error SD group (see
+#' [combined_sd()]). If the combined SD is non-finite or less than the sigma
+#' lower bound, then the combined SD of all non-excluded data is substituted. If
+#' that is still non-finite or less then the sigma lower bound, then a constant
+#' value of 100 is substituted.
+#'
+#' The starting guess for each "sigma" hyperparameter is one-tenth of the upper bound.
+#'
+#' @param obj A `pk` object
+#' @return The same `pk` object, but with a new element `prefit`, containing the
+#'   results of pre-fit calculations and checks for each model and for the error
+#'   model.
+#' @export
+#' @author Caroline Ring
+do_prefit.pk <- function(obj){
+
+  objname <- deparse(substitute(obj))
+  status <- obj$status
+  if(status >= status_prefit){
+    warning(paste0(objname,
+                   " current status is ",
+                   status,
+                   ". do_prefit.pk() will reset its status to ",
+                   status_prefit,
+                   ". Any results from later workflow stages will be lost."))
+  }
+
+  #if preprocessing not already done, do it
+  if(obj$status < status_preprocess){
+    obj <- do_preprocess(obj)
+  }
+
+  if(obj$status < status_data_info){
+    obj <- do_data_info(obj)
+  }
+
+  suppress.messages <- obj$settings_preprocess$suppress.messages
+
+  data <- obj$data
+
+  if(suppress.messages %in% FALSE){
[…]

### 2023-06-13 data-raw/batchMode_trial_gpm.Rmd
Adapted coef() function using data groups and started working on predict(), which calls coef()

--- 2023-06-08 data-raw/batchMode_trial_gpm.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj branch
-library(tidyverse)
-library(here)
+knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
+
+library(tidyverse, quietly = TRUE)
+devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
+
 ```
@@
 
+The first step is understanding how to work with a single DTXSID + Species combination.
+Once we know how to do this, it will be easier to apply it to (potentially)
+a list of these objects in a vectorized fashion.
+Here I subset the `cvt` object and use that as my working data.
+
 ```{r data_loading}
-cvt %>% names()
-
-cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>% unique() %>% length()
+# There are 103 unique chemicals in this object
+cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>%
+  unique() %>%
+  length()
 
 my_predata <- subset(cvt,
-                     chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442" &
-                       subjects.species_harmonized %in% "rat")
+                     chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442")
+
+```
+
+Next, I want to follow the steps required for the particular analysis I would like.
+In this instance, I set the optimizer to "L-BFGS-B" and dose-normalize the output.
+I do not scale the time or log-transform the concentration values.
+Since I would like to do a "Pooled" analysis,
+I set the `error_group = vars(Chemical, Species)`.
+
+```{r single_fit}
+my_pk <- pk(data = my_predata) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE) +
+  # scale_time() +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species)) +
+  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
+                                     subjects.species_harmonized))
+
+my_pk <- do_preprocess(my_pk)
+
+my_pk <- do_data_info(my_pk) 
+# summarizes error (Returning more or less than 1 row per summarize)
+
+my_pk <- do_prefit(my_pk)
+
+my_pk <- do_fit(my_pk)
+```
+
+Batch mode works now I need to write a function that recapitulates `coef()` method
+
+```{r coef_function_remake}
+# A list of each fit model with the estimated parameters for that model
+pk_results <- coef(my_pk) # NAs are printed
+
+my_coefs_test <- my_pk$fit |>
+  ungroup() |>
+  tidyr::unnest(cols = fit) |>
+  tidyr::unite(sigma, starts_with("sigma_"),
+        na.rm = TRUE) |>
+  group_split(method)
+
+my_coef <- function(obj,
+                    data_group = NULL,
+                    ...) {
+  # Check fit status
+  check <- check_required_status(obj = obj,
+                                 required_status = status_fit)
+
+  if (check %in% FALSE) stop(attr(check, "msg")) # Stop if not fitted
+
+  # Assign data groups to variable
+  if (is.null(data_group)) data_group <- obj$data_group
+
+  fit_coef <- obj$fit |>
+    dplyr::ungroup() |>
+    tidyr::unnest(cols = fit) |>
+    tidyr::unite(sigma, starts_with("sigma_"),
+                 na.rm = TRUE)# |>
+    # dplyr::group_split(method)
+
+  # method_names <- purrr::map(fit_coef,
+  #     \(x) unique(x$method)) |>
+  #   unlist()
+  # 
+  # names(fit_coef) <- method_names
+
+  return(fit_coef)
+}
+
+my_coefs <- my_coef(my_pk)
+
+```
+
+```{r predict_method_remake}
+pred_results <- predict(my_pk) # Error about missing parameters
+
+my_test_data <- my_pk$data
+
+my_test_data %>%
+  group_by(!!!my_pk$data_group) %>%
+  dplyr::select(all_of(c("Time", "Time.Units", "Dose", "Route", "Media"))) %>%
+  dplyr::left_join(my_coefs,
+            relationship = "many-to-many") -> joined_test_data
+
+# Testing not complete
+joined_test_data %>%
+  relocate(method, .before = model) %>%
+  group_by(across(Chemical:model)) %>%
+  nest(.key = "coefs") %>%
+  rowwise() %>%
+  dplyr::mutate(model_fun = my_pk$stat_model[[model]]$conc_fun,
+                predicted_Value = do.call(model_fun,
+                                          args = list(
+                                            params = coefs,
+                                            dose = Dose,
+                                            time = Time,
+                                            route = Route,
+                                            medium = Media
+                                          )),
+  .after = model) %>%
+  head()
+
+my_predict <- function(obj,
+                       newdata = NULL,
+                       type = "conc",
+                       exclude = TRUE,
+                       use_scale_conc = FALSE) {
+    # Check fit status
+  check <- check_required_status(obj = obj,
+                                 required_status = status_fit)
+
+  if (check %in% FALSE) stop(attr(check, "msg")) # Stop if not fitted
+
+  if (is.null(newdata)) newdata <- obj$data
+  newdata_ok <- check_newdata(newdata = newdata,
+                              olddata = obj$data,
+                              req_vars = c("Time",
+                                           "Time.Units",
+                                           "Dose",
+                                           "Route",
+                                           "Media"),
+                              exclude = exclude)
+
+    #scale time if needed
+  if (!("Time_trans" %in% names(newdata))){
+  newdata$Time_trans <- convert_time(x = newdata$Time,
+                                     from = newdata$Time.Units,
+                                     to = obj$scales$time$new_units)
+  }
+
+  #apply transformations if so specified
+  conc_scale <- conc_scale_use(obj = obj,
+                               use_scale_conc = use_scale_conc)
+
+}
 
@@
 ```{r}
-my_pk <- pk(data = my_predata) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = "L-BFGS-B") +
-  scale_conc(dose_norm = TRUE) +
-  # scale_time() +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk <- preprocess_data(my_pk)
-
-my_pk <- data_info(my_pk)
-
-my_pk <- prefit(my_pk) 
-# I get a warning here 
-# "In med_y - pred : "
-# "longer object length is not a multiple of shorter object length"
-
-my_pk <- fit(my_pk)
-
-pk_results <- coef(my_pk)
-
-predict(my_pk) # Doesn't run rn for some reason
-pred_results <- predict(my_pk)
-
 plot_results <- plot(my_pk)
-print(plot_results)
 

### 2023-06-13 data-raw/batchMode_trial_gpm.Rmd
Trying out differnt order of operations for pk object creation

@@
 my_pk <- pk(data = my_predata) +
+  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
+                  subjects.species_harmonized)) +
   settings_preprocess(keep_data_original = TRUE) +
@@
   # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) +
-  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
-                                     subjects.species_harmonized))
+  stat_error_model(error_group = vars(Chemical, Species))
 

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
Finished coef and predict method trials

@@
 devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
-
+tidyverse_conflicts()
 ```
@@
 my_pk <- do_fit(my_pk)
+
 ```
 
-Batch mode works now I need to write a function that recapitulates `coef()` method
+Batch mode works, now I need to write a function that recapitulates `coef()` method
 
@@
 
-my_coefs_test <- my_pk$fit |>
-  ungroup() |>
-  tidyr::unnest(cols = fit) |>
-  tidyr::unite(sigma, starts_with("sigma_"),
-        na.rm = TRUE) |>
-  group_split(method)
+const_pars <- subset(my_pk$prefit$par_DF,
+       optimize_param %in% FALSE &
+         use_param %in% TRUE) %>% dplyr::select(model, Chemical, Species,
+                                         param_name, start) 
+const_pars <- const_pars %>%
+  pivot_wider(names_from = param_name,
+              values_from = start)
 
+my_fit_test <- my_pk$fit %>% unnest(cols = fit) %>%
+  group_by(model, method, Chemical, Species) %>%
+  dplyr::select(starts_with("sigma_"),
+                any_of(sapply(my_pk$stat_model, `[[`, "params") %>%
+                         unlist() %>%
+                         unique())) # need Rblood2plasma
+
+left_join(my_fit_test, const_pars)
+
+# New possible coef function!!
 my_coef <- function(obj,
@@
 
-  # Assign data groups to variable
-  if (is.null(data_group)) data_group <- obj$data_group
+  const_pars <- subset(obj$prefit$par_DF,
+                       optimize_param %in% FALSE &
+                         use_param %in% TRUE) %>% dplyr::select(model,
+                                                                !!!obj$data_group,
+                                                                param_name,
+                                                                start) 
+  const_pars <- const_pars %>%
+    pivot_wider(names_from = param_name,
+                values_from = start)
 
-  fit_coef <- obj$fit |>
-    dplyr::ungroup() |>
-    tidyr::unnest(cols = fit) |>
-    tidyr::unite(sigma, starts_with("sigma_"),
-                 na.rm = TRUE)# |>
-    # dplyr::group_split(method)
+  possible_model_params <- sapply(obj$stat_model, `[[`, "params") %>%
+    unlist() %>%
+    unique()
 
-  # method_names <- purrr::map(fit_coef,
-  #     \(x) unique(x$method)) |>
-  #   unlist()
-  # 
-  # names(fit_coef) <- method_names
+  coefs <- obj$fit %>% unnest(cols = fit) %>%
+  group_by(model, method, !!!obj$data_group) %>%
+  dplyr::select(starts_with("sigma_"),
+                any_of(possible_model_params)) %>%
+    unite(starts_with("sigma_"),
+          col = "sigma",
+          sep = "",
+          na.rm = TRUE)
 
-  return(fit_coef)
+  coefs <- left_join(coefs, const_pars)
+
+  coefs_tidy <- coefs %>%
+  nest(coefs_tibble = any_of(possible_model_params)) %>%
+  mutate(coefs_vector = map(coefs_tibble,
+                      .f = \(x){
+                        as.data.frame(x %>%
+                                    dplyr::select(!where(is.na))) %>% 
+                          unlist()
+                      })) %>%
+    unnest(coefs_tibble)
+  return(coefs_tidy)
 }
 
-my_coefs <- my_coef(my_pk)
+my_coefs <- my_coef(obj = my_pk)
 
@@
                        newdata = NULL,
+                       model = NULL,
+                       method = NULL,
                        type = "conc",
                        exclude = TRUE,
-                       use_scale_conc = FALSE) {
-    # Check fit status
+                       use_scale_conc = FALSE,
+                       ...){
+
+  #ensure that the model has been fitted
   check <- check_required_status(obj = obj,
                                  required_status = status_fit)
+  if(!(check %in% TRUE)){
+    stop(attr(check, "msg"))
+  }
 
-  if (check %in% FALSE) stop(attr(check, "msg")) # Stop if not fitted
+  if(is.null(model)) model <- names(obj$stat_model)
+  if(is.null(method)) method <- obj$settings_optimx$method
 
-  if (is.null(newdata)) newdata <- obj$data
+  method_ok <- check_method(obj = obj, method = method)
+  model_ok <- check_model(obj = obj, model = model)
+
+  coefs <- my_coef(obj = obj) %>%
+    dplyr::filter(model %in% model,
+                  method %in% method)
+
+  if(is.null(newdata)) newdata <- obj$data
+
   newdata_ok <- check_newdata(newdata = newdata,
@@
   #scale time if needed
-  if (!("Time_trans" %in% names(newdata))){
+  if(!("Time_trans" %in% names(newdata))){
     newdata$Time_trans <- convert_time(x = newdata$Time,
@@
 
+  req_vars <- c("Time",
+                "Time.Units",
+                "Dose",
+                "Route",
+                "Media",
+                "Value",
+                "Value.Units")
+
+  trans_vars <- c("Time_trans",
+                  "Time_trans.Units",
+                  "Conc_trans",
+                  "Conc_trans.Units")
+
+  newdata <- newdata %>%
+    dplyr::select(!!!obj$data_group,
+                  all_of(req_vars),
+                  any_of(trans_vars)) %>%
+    group_by(!!!obj$data_group,
+             Route, Media) %>%
+    nest(.key = "observations")
+
+  newdata <- left_join(coefs, newdata,
+                       relationship = "many-to-many")
+  # From here, trying to call map within mutate to add the prediction column by
+  # calling the appropriate model function and feeding it the parameters in coefs_vector
+
+  newdata <- newdata %>%
+    dplyr::group_by(Route, Media,
+                    .add = TRUE) %>%
+    mutate(model_fun = obj$stat_model[[model]]$conc_fun) %>%
+    reframe(predictions = 
+              map(observations,
+                  .f = \(x) {
+                    x %>%
+                      group_by(Time_trans) %>%
+                      mutate(Conc_est = sapply(coefs_vector,
+                                               FUN = model_fun,
+                                               time = Time_trans,
+                                               dose = ifelse(obj$scales$conc$dose_norm,
+                                                             1, Dose),
+                                               route = Route,
+                                               medium = Media,
+                                               simplify = TRUE,
+                                               USE.NAMES = TRUE))
+                              })) %>%
+    unnest(predictions)
+
+  return(newdata) 
 }
+
+my_pred <- my_predict(my_pk, use_scale_conc = TRUE)
+
+my_pred %>%
+  filter(model == "model_flat",
+         Route == "iv",
+         Species == "hamster",
+         method == "L-BFGS-B") %>%
+  View()
 

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
Added functionality for calculating rolling AUC

@@
 
-const_pars <- subset(my_pk$prefit$par_DF,
-       optimize_param %in% FALSE &
-         use_param %in% TRUE) %>% dplyr::select(model, Chemical, Species,
-                                         param_name, start) 
-const_pars <- const_pars %>%
-  pivot_wider(names_from = param_name,
-              values_from = start)
-
-my_fit_test <- my_pk$fit %>% unnest(cols = fit) %>%
-  group_by(model, method, Chemical, Species) %>%
-  dplyr::select(starts_with("sigma_"),
-                any_of(sapply(my_pk$stat_model, `[[`, "params") %>%
-                         unlist() %>%
-                         unique())) # need Rblood2plasma
-
-left_join(my_fit_test, const_pars)
-
 # New possible coef function!!
@@
 ```{r predict_method_remake}
-pred_results <- predict(my_pk) # Error about missing parameters
-
-my_test_data <- my_pk$data
-
-my_test_data %>%
-  group_by(!!!my_pk$data_group) %>%
-  dplyr::select(all_of(c("Time", "Time.Units", "Dose", "Route", "Media"))) %>%
-  dplyr::left_join(my_coefs,
-            relationship = "many-to-many") -> joined_test_data
-
-# Testing not complete
-joined_test_data %>%
-  relocate(method, .before = model) %>%
-  group_by(across(Chemical:model)) %>%
-  nest(.key = "coefs") %>%
-  rowwise() %>%
-  dplyr::mutate(model_fun = my_pk$stat_model[[model]]$conc_fun,
-                predicted_Value = do.call(model_fun,
-                                          args = list(
-                                            params = coefs,
-                                            dose = Dose,
-                                            time = Time,
-                                            route = Route,
-                                            medium = Media
-                                          )),
-  .after = model) %>%
-  head()
-
 my_predict <- function(obj,
@@
                     .add = TRUE) %>%
-    mutate(model_fun = obj$stat_model[[model]]$conc_fun) %>%
+    mutate(model_fun = case_when(
+      type == "conc" ~obj$stat_model[[model]]$conc_fun,
+      type == "auc"  ~obj$stat_model[[model]]$auc_fun,
+      .default = obj$stat_model[[model]]$conc_fun)) %>%
     reframe(predictions = 
@@
                       group_by(Time_trans) %>%
-                      mutate(Conc_est = sapply(coefs_vector,
+                      mutate(Estimate = sapply(coefs_vector,
                                                FUN = model_fun,
@@
 
+  if (type == "conc") newdata <- rename(newdata, Conc_est = "Estimate")
+  if (type == "auc") newdata <- rename(newdata, AUC_est = "Estimate")
+
   return(newdata) 
@@
 
-my_pred <- my_predict(my_pk, use_scale_conc = TRUE)
+my_pred <- my_predict(my_pk, type = "auc", use_scale_conc = TRUE)
 
@@
 
+```{r after_method_update}
+# Changed pk_methods coef() and predict() to those above
+# Ran the following after making the pk object:
+devtools::load_all()
+
+my_coefs_update <- coef(my_pk)
+my_pred_update <- predict(my_pk, type = "auc",
+                          use_scale_conc = TRUE)
+
+my_pred_update %>%
+  filter(model == "model_flat",
+         Route == "oral",
+         Species == "rat", # hamster has a Fgutabs of zero
+         method == "L-BFGS-B") %>%
+  View("predicted_update")
+
+my_coefs_update %>%
+  filter(model == "model_flat",
+         Species == "rat",
+         method == "L-BFGS-B") %>%
+  View("coef_update")
+
+# Seems to have worked!
+```
+
 ```{r}

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
facet_data now takes the harmonized variables as arguments for vars()

@@
 my_pk <- pk(data = my_predata) +
-  facet_data(vars(chemicals_analyzed.dsstox_substance_id,
-                  subjects.species_harmonized)) +
+  facet_data(vars(Chemical, Species)) +
   settings_preprocess(keep_data_original = TRUE) +
@@
   # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
 
@@
 
-  coefs <- my_coef(obj = obj) %>%
+  coefs <- coef(obj = obj) %>%
     dplyr::filter(model %in% model,
@@
                     x %>%
-                      group_by(Time_trans) %>%
+                      group_by(Time_trans) %>% # revise!
                       mutate(Estimate = sapply(coefs_vector,
@@
 
-my_coefs_update <- coef(my_pk)
-my_pred_update <- predict(my_pk, type = "auc",
+my_coefs_update <- coef(my_pk, model = "model_flat", drop_sigma = TRUE)
+my_pred_update <- predict(my_pk,
                           use_scale_conc = TRUE)
@@
 my_pred_update %>%
-  filter(model == "model_flat",
+  filter(model == "model_2comp",
          Route == "oral",
@@
 
-```{r}
+```{r remaining_methods}
+# rmse()
+# get_tkstats()
+# residuals()
+# plot()
+
+my_tkstats <- get_tkstats(my_pk)
+
 plot_results <- plot(my_pk)
 
-my_tkstats <- get_tkstats(my_pk)
 ```

### 2023-06-15 data-raw/batchMode_trial_gpm.Rmd
Updated the coef method to include keep_sigma, model, and method arguments. coef() now includes linked sigma_value and error_group columns

@@
 # A list of each fit model with the estimated parameters for that model
-pk_results <- coef(my_pk) # NAs are printed
+pk_results <- coef(my_pk)
 
@@
 
-my_coefs_update <- coef(my_pk, model = "model_flat", drop_sigma = TRUE)
+my_coefs_update <- coef(my_pk, drop_sigma = TRUE)
 my_pred_update <- predict(my_pk,

### 2023-06-20 data-raw/batchMode_trial_gpm.Rmd
Updated RMSE method for faceted data structure

@@
 my_predata <- subset(cvt,
-                     chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442")
+                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
+                                                                   "DTXSID2021731"))
 
@@
 
-my_coefs_update <- coef(my_pk, drop_sigma = TRUE)
+my_coefs_update <- coef(my_pk)
 my_pred_update <- predict(my_pk,
+                          exclude = TRUE, # add the "exclude" column to output
                           use_scale_conc = TRUE)
+
+my_ndf <- my_pk$data
+
+rmse(my_pk) %>% View("RMSE_test")
 

### 2023-06-20 data-raw/batchMode_trial_gpm.Rmd
Updated residuals() method, ensured predict() method was responsive to use_scale_conc argument for rmse() and residuals().

@@
   settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
   # scale_time() +
@@
                           exclude = TRUE, # add the "exclude" column to output
-                          use_scale_conc = TRUE)
+                          use_scale_conc = FALSE)
 
@@
 rmse(my_pk) %>% View("RMSE_test")
+residuals(my_pk) %>% View("Residuals_test")
 
@@
 ```{r remaining_methods}
-# rmse()
-# get_tkstats()
 # residuals()
 # plot()
+# 
+# get_tkstats()
 

### 2023-06-22 data-raw/batchMode_trial_gpm.Rmd
Revised plotting method for observations

@@
                                                                    "DTXSID2021731"))
-
 ```
@@
                           exclude = TRUE, # add the "exclude" column to output
-                          use_scale_conc = FALSE)
-
-my_ndf <- my_pk$data
+                          use_scale_conc = TRUE)
 
@@
 
-my_pred_update %>%
-  filter(model == "model_2comp",
-         Route == "oral",
-         Species == "rat", # hamster has a Fgutabs of zero
-         method == "L-BFGS-B") %>%
-  View("predicted_update")
-
-my_coefs_update %>%
-  filter(model == "model_flat",
-         Species == "rat",
-         method == "L-BFGS-B") %>%
-  View("coef_update")
-
 # Seems to have worked!
@@
 
+```{r plotting_method}
+# Experimenting with what works with my_ndf
+# 
+my_ndf <- my_pk$data
+
+my_ndf %>%
+  filter(Chemical %in% "DTXSID0020442", Species %in% "rat") %>%
+  mutate(Dose = factor(Dose),
+         Reference = factor(Reference),
+         Detect_int = as.character(Detect)
+         ) %>%
+  ggplot(aes(
+    x = Time_trans,
+    y = Conc_trans,
+    color = Dose,
+    shape = Reference
+  )) +
+  geom_point(aes(
+    fill = Dose,
+    alpha = Detect_int
+  )) +
+  geom_point() +
+  scale_shape_manual(values = 21:25) +
+  scale_alpha_manual(values = c("FALSE" = 0, "TRUE" = 1),
+                     breaks = c("TRUE", "FALSE"),
+                     name = "Detect") +
+  guides(shape = guide_legend(override.aes = list(fill = "black")),
+         alpha = guide_legend(override.aes = list(alpha = 1,
+                                                  fill = c("black", "white"),
+                                                  color = "black",
+                                                  shape = 21))) +
+  facet_grid(rows = vars(Detect), # This is just for illustrative purposes, this would be Routes
+             cols = vars(Route)) +
+  theme_bw()
+# Need to find a way to make this vectorized...
+# probably within a mutate and map function
+
+```
+
 ```{r remaining_methods}
-# residuals()
 # plot()

### 2023-06-22 data-raw/batchMode_trial_gpm.Rmd
Cleaning up the batchMode_trial_gpm.Rmd and preparing plot method to add interpolated values

@@
 my_pk <- do_fit(my_pk)
-
 ```
@@
 Batch mode works, now I need to write a function that recapitulates `coef()` method
-
-```{r coef_function_remake}
-# A list of each fit model with the estimated parameters for that model
-pk_results <- coef(my_pk)
-
-# New possible coef function!!
-my_coef <- function(obj,
-                    data_group = NULL,
-                    ...) {
-  # Check fit status
-  check <- check_required_status(obj = obj,
-                                 required_status = status_fit)
-
-  if (check %in% FALSE) stop(attr(check, "msg")) # Stop if not fitted
-
-  const_pars <- subset(obj$prefit$par_DF,
-                       optimize_param %in% FALSE &
-                         use_param %in% TRUE) %>% dplyr::select(model,
-                                                                !!!obj$data_group,
-                                                                param_name,
-                                                                start) 
-  const_pars <- const_pars %>%
-    pivot_wider(names_from = param_name,
-                values_from = start)
-
-  possible_model_params <- sapply(obj$stat_model, `[[`, "params") %>%
-    unlist() %>%
-    unique()
-
-  coefs <- obj$fit %>% unnest(cols = fit) %>%
-    group_by(model, method, !!!obj$data_group) %>%
-    dplyr::select(starts_with("sigma_"),
-                  any_of(possible_model_params)) %>%
-    unite(starts_with("sigma_"),
-          col = "sigma",
-          sep = "",
-          na.rm = TRUE)
-
-  coefs <- left_join(coefs, const_pars)
-
-  coefs_tidy <- coefs %>%
-  nest(coefs_tibble = any_of(possible_model_params)) %>%
-  mutate(coefs_vector = map(coefs_tibble,
-                      .f = \(x){
-                        as.data.frame(x %>%
-                                    dplyr::select(!where(is.na))) %>% 
-                          unlist()
-                      })) %>%
-    unnest(coefs_tibble)
-  return(coefs_tidy)
-}
-
-my_coefs <- my_coef(obj = my_pk)
-
-```
-
-```{r predict_method_remake}
-my_predict <- function(obj,
-                       newdata = NULL,
-                       model = NULL,
-                       method = NULL,
-                       type = "conc",
-                       exclude = TRUE,
-                       use_scale_conc = FALSE,
-                       ...){
-
-  #ensure that the model has been fitted
-  check <- check_required_status(obj = obj,
-                                 required_status = status_fit)
-  if(!(check %in% TRUE)){
-    stop(attr(check, "msg"))
-  }
-
-  if(is.null(model)) model <- names(obj$stat_model)
-  if(is.null(method)) method <- obj$settings_optimx$method
-
-  method_ok <- check_method(obj = obj, method = method)
-  model_ok <- check_model(obj = obj, model = model)
-
-  coefs <- coef(obj = obj) %>%
-    dplyr::filter(model %in% model,
-                  method %in% method)
-
-  if(is.null(newdata)) newdata <- obj$data
-
-  newdata_ok <- check_newdata(newdata = newdata,
-                              olddata = obj$data,
-                              req_vars = c("Time",
-                                           "Time.Units",
-                                           "Dose",
-                                           "Route",
-                                           "Media"),
-                              exclude = exclude)
-
-  #scale time if needed
-  if(!("Time_trans" %in% names(newdata))){
-    newdata$Time_trans <- convert_time(x = newdata$Time,
-                                       from = newdata$Time.Units,
-                                       to = obj$scales$time$new_units)
-  }
-
-  #apply transformations if so specified
-  conc_scale <- conc_scale_use(obj = obj,
-                               use_scale_conc = use_scale_conc)
-
-  req_vars <- c("Time",
-                "Time.Units",
-                "Dose",
-                "Route",
-                "Media",
-                "Value",
-                "Value.Units")
-
-  trans_vars <- c("Time_trans",
-                  "Time_trans.Units",
-                  "Conc_trans",
-                  "Conc_trans.Units")
-
-  newdata <- newdata %>%
-    dplyr::select(!!!obj$data_group,
-                  all_of(req_vars),
-                  any_of(trans_vars)) %>%
-    group_by(!!!obj$data_group,
-             Route, Media) %>%
-    nest(.key = "observations")
-
-  newdata <- left_join(coefs, newdata,
-                       relationship = "many-to-many")
-  # From here, trying to call map within mutate to add the prediction column by
-  # calling the appropriate model function and feeding it the parameters in coefs_vector
-
-  newdata <- newdata %>%
-    dplyr::group_by(Route, Media,
-                    .add = TRUE) %>%
-    mutate(model_fun = case_when(
-      type == "conc" ~obj$stat_model[[model]]$conc_fun,
-      type == "auc"  ~obj$stat_model[[model]]$auc_fun,
-      .default = obj$stat_model[[model]]$conc_fun)) %>%
-    reframe(predictions = 
-              map(observations,
-                  .f = \(x) {
-                    x %>%
-                      group_by(Time_trans) %>% # revise!
-                      mutate(Estimate = sapply(coefs_vector,
-                                               FUN = model_fun,
-                                               time = Time_trans,
-                                               dose = ifelse(obj$scales$conc$dose_norm,
-                                                             1, Dose),
-                                               route = Route,
-                                               medium = Media,
-                                               simplify = TRUE,
-                                               USE.NAMES = TRUE))
-                              })) %>%
-    unnest(predictions)
-
-  if (type == "conc") newdata <- rename(newdata, Conc_est = "Estimate")
-  if (type == "auc") newdata <- rename(newdata, AUC_est = "Estimate")
-
-  return(newdata) 
-}
-
-my_pred <- my_predict(my_pk, type = "auc", use_scale_conc = TRUE)
-
-my_pred %>%
-  filter(model == "model_flat",
-         Route == "iv",
-         Species == "hamster",
-         method == "L-BFGS-B") %>%
-  View()
-
-```
 
@@
 
+req_vars <- c("Time",
+              "Time.Units",
+              "Dose",
+              "Route",
+              "Media",
+              "Reference",
+              "Conc",
+              "Conc_SD",
+              "Value",
+              "Value.Units",
+              "Detect", "exclude")
+
+trans_vars <- c("Time_trans",
+                "Time_trans.Units",
+                "Conc_trans",
+                "Conc_trans.Units")
+
+my_ndf %>%
+  dplyr::select(Chemical, Species,
+                dplyr::all_of(req_vars),
+                dplyr::any_of(trans_vars)) %>%
+  mutate(Detect = ifelse(Detect, "Detect", "Non-Detect")) %>%
+  View()
+
+devtools::load_all()
+my_plot <- plot(my_pk)
+
 ```

### 2023-06-22 R/pk_methods_plot.R

@@ -58,7 +58,7 @@ plot.pk <- function(obj,
                     plot_point_aes = NULL,
                     facet_fun = NULL,
                     facet_fun_args = NULL,
-                    drop_nonDetect = TRUE,
+                    drop_nonDetect = FALSE,
                     # Predict/interpolation arguments
                     plot_fit_aes = NULL,
                     n_interp = 10,
@@ -93,8 +93,7 @@ plot.pk <- function(obj,
                                use_scale_conc = use_scale_conc)
 
   if (drop_nonDetect %in% TRUE) {
-    newdata <- subset(newdata,
-                      Detect %in% TRUE)
+    newdata <- subset(newdata, Detect %in% TRUE)
   }
 
   req_vars <- c("Time",
@@ -102,30 +101,37 @@ plot.pk <- function(obj,
                 "Dose",
                 "Route",
                 "Media",
+                "Reference",
+                "Conc",
+                "Conc_SD",
                 "Value",
-                "Value.Units")
-
-  if (!drop_nonDetect) {
-    req_vars <- c(req_vars, "Detect", "exclude")
-  }
+                "Value.Units",
+                "Detect", "exclude")
 
   trans_vars <- c("Time_trans",
                   "Time_trans.Units",
                   "Conc_trans",
                   "Conc_trans.Units")
 
+  # I think ideally there should be required variables and
+  # a way to ensure all the aes() variables get added
   newdata <- newdata %>%
     dplyr::select(!!!obj$data_group,
                   dplyr::all_of(req_vars),
                   dplyr::any_of(trans_vars)) %>%
+    dplyr::rowwise() %>%
     dplyr::mutate(Conc_set = ifelse(conc_scale$dose_norm,
                                     Conc / Dose,
                                     Conc),
                   Conc_set_SD = ifelse(conc_scale$dose_norm,
                                        Conc_SD / Dose,
-                                       Conc_SD)) %>%
-    dplyr::group_by(!!!obj$data_group,
-                    Route, Media) %>%
+                                       Conc_SD),
+                  Detect = ifelse(Detect,
+                                  "Detect",
+                                  "Non-Detect"),
+                  Dose = factor(Dose)) %>%
+    dplyr::ungroup() %>%
+    dplyr::group_by(!!!obj$data_group) %>%
     tidyr::nest(.key = "observations")
 
 
@@ -135,10 +141,10 @@ plot.pk <- function(obj,
                                         ymin = Conc_set - Conc_set_SD,
                                         ymax = Conc_set + Conc_set_SD,
[…]

### 2023-06-27 data-raw/batchMode_trial_gpm.Rmd
Updated plot function to allow predictions from time interpolation, needs data_group call flexibility

@@
 
+my_pred2 <- predict(my_pk,
+                    newdata = data.frame(Chemical = "DTXSID2021731",
+                                         Species = "rat",
+                                         Route = "iv",
+                                         Media = "plasma",
+                                         Dose = 20,
+                                         Time = 1.6,
+                                         Time.Units = "hours"),
+                    exclude = FALSE,
+                    use_scale_conc = FALSE)
+
 rmse(my_pk) %>% View("RMSE_test")
@@
                 dplyr::all_of(req_vars),
-                dplyr::any_of(trans_vars)) %>%
-  mutate(Detect = ifelse(Detect, "Detect", "Non-Detect")) %>%
+                dplyr::any_of(trans_vars)) -> my_ndf
+
+# Time interpolation
+my_ndf %>% uncount(1) %>% 
+  group_by(Dose, Route, Media) %>%
+  mutate(Time_trans = (max(Time)/(n() - 1))*(row_number() - 1)) %>%
   View()
@@
 
+my_plot[[3]][[2]] %>%
+  dplyr::select(Time, Dose, Route, Media, Reference) %>% View("reduced")
+
+my_plot[[3]][[2]] %>%
+  tidyr::uncount(3) %>%
+  arrange(Time) %>%
+  group_by(across(!starts_with("Time"))) %>% 
+  mutate(Time = seq(from = min(Time),
+                    to = max(Time),
+                    length.out = length(Time))) %>% View()
+
+# Testing the stat_function way
+# 
+my_plot$observation_plot[[2]] +
+  ggplot2::stat_function(fun = \(x) {
+    sqrt(1/x)
+    },
+    aes(linetype = "solid"),
+                         inherit.aes = FALSE)
+
+my_statfun <- ggplot2::stat_function(fun = \(x) {
+    sqrt(5*x)
+    },
+    aes(linetype = "dotted"),
+    inherit.aes = FALSE) 
+my_statfun2 <- ggplot2::stat_function(fun = \(x) {
+    0.5*x
+    },
+    aes(linetype = "solid"),
+    inherit.aes = FALSE) 
+# Note that we cannot add ggproto objects together! But I can make them into a list
+# and add that to the main object
+
+my_plot$observation_plot[[2]] + list(my_statfun, my_statfun2)
+
+my_plot$observation_plot[[2]] + my_statfun +
+  scale_linetype_identity()
 ```
@@
 # plot()
-# 
+# coef_sd
+# logLik.pk
 # get_tkstats()

### 2023-06-27 data-raw/batchMode_trial_gpm.Rmd
plot() method now also plots fits

--- 2023-06-22 data-raw/batchMode_trial_gpm.Rmd
@@
 devtools::load_all()
-my_plot <- plot(my_pk)
+my_plot <- plot(my_pk, use_scale_conc = FALSE)
 

### 2023-06-27 data-raw/batchMode_trial_gpm.Rmd
Expanded the time interpolation. Added conditional labelling legend order.

@@
 ```{r plotting_method}
-# Experimenting with what works with my_ndf
-# 
-my_ndf <- my_pk$data
-
-my_ndf %>%
-  filter(Chemical %in% "DTXSID0020442", Species %in% "rat") %>%
-  mutate(Dose = factor(Dose),
-         Reference = factor(Reference),
-         Detect_int = as.character(Detect)
-         ) %>%
-  ggplot(aes(
-    x = Time_trans,
-    y = Conc_trans,
-    color = Dose,
-    shape = Reference
-  )) +
-  geom_point(aes(
-    fill = Dose,
-    alpha = Detect_int
-  )) +
-  geom_point() +
-  scale_shape_manual(values = 21:25) +
-  scale_alpha_manual(values = c("FALSE" = 0, "TRUE" = 1),
-                     breaks = c("TRUE", "FALSE"),
-                     name = "Detect") +
-  guides(shape = guide_legend(override.aes = list(fill = "black")),
-         alpha = guide_legend(override.aes = list(alpha = 1,
-                                                  fill = c("black", "white"),
-                                                  color = "black",
-                                                  shape = 21))) +
-  facet_grid(rows = vars(Detect), # This is just for illustrative purposes, this would be Routes
-             cols = vars(Route)) +
-  theme_bw()
-# Need to find a way to make this vectorized...
-# probably within a mutate and map function
-
-req_vars <- c("Time",
-              "Time.Units",
-              "Dose",
-              "Route",
-              "Media",
-              "Reference",
-              "Conc",
-              "Conc_SD",
-              "Value",
-              "Value.Units",
-              "Detect", "exclude")
-
-trans_vars <- c("Time_trans",
-                "Time_trans.Units",
-                "Conc_trans",
-                "Conc_trans.Units")
-
-my_ndf %>%
-  dplyr::select(Chemical, Species,
-                dplyr::all_of(req_vars),
-                dplyr::any_of(trans_vars)) -> my_ndf
-
-# Time interpolation
-my_ndf %>% uncount(1) %>% 
-  group_by(Dose, Route, Media) %>%
-  mutate(Time_trans = (max(Time)/(n() - 1))*(row_number() - 1)) %>%
-  View()
 
@@
 my_plot <- plot(my_pk, use_scale_conc = FALSE)
+plot(my_pk, use_scale_conc = TRUE,
+     method = "L-BFGS-B",
+     print_out = TRUE)
+
+# This is printable into a one file, multipage pdf
+pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_OnefileTest.pdf",
+    width = 10,
+    height = 8)
+plot(my_pk, use_scale_conc = TRUE,
+     method = "L-BFGS-B",
+     print_out = TRUE)
+dev.off()
 

### 2023-06-28 data-raw/batchMode_trial_gpm.Rmd
Added new plot parameters and substituted in`reframe` for the `summarize` call in do_data_info()

@@
                      chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
-                                                                   "DTXSID2021731"))
+                                                                   "DTXSID2021731",
+                                                                   "DTXSID5034773",
+                                                                   "DTXSID5032600",
+                                                                   "DTXSID7022253"))
 ```
@@
 ```{r remaining_methods}
-# plot()
 # coef_sd

### 2023-06-28 data-raw/batchMode_trial_gpm.Rmd
Fixed function call for facetting and added a prediction value limiter when plotting model fits

@@
                                                                    "DTXSID2021731",
-                                                                   "DTXSID5034773",
                                                                    "DTXSID5032600",
@@
 devtools::load_all()
-my_plot <- plot(my_pk, use_scale_conc = FALSE)
+my_plot <- plot(my_pk, use_scale_conc = TRUE)
 plot(my_pk, use_scale_conc = TRUE,
-     method = "L-BFGS-B",
      print_out = TRUE)
@@
 # This is printable into a one file, multipage pdf
-pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_OnefileTest.pdf",
+pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_freeY.pdf",
     width = 10,
@@
 plot(my_pk, use_scale_conc = TRUE,
-     method = "L-BFGS-B",
      print_out = TRUE)

### 2023-07-06 data-raw/batchMode_trial_gpm.Rmd
Updating documentation for methods and added prediction filtering parameters for the plot.pk method
Preliminary finish for the get_tkstats method. Does need more comments and messages.

@@
                                                                    "DTXSID2021731",
-                                                                   "DTXSID5032600",
-                                                                   "DTXSID7022253"))
+                                                                   "DTXSID5032600"))
 ```
@@
 
-Batch mode works, now I need to write a function that recapitulates `coef()` method
+Batch mode works! Now, I have updated the `coef`, `predict`, `rmse`, and `residuals`
+methods.
 
@@
 my_pred_update <- predict(my_pk,
+                          exclude = TRUE, # add the "exclude" column to output
+                          use_scale_conc = TRUE)
+
+predict(my_pk,
         exclude = TRUE, # add the "exclude" column to output
@@
 
-# Seems to have worked!
 ```
@@
 
-devtools::load_all()
+plot(my_pk, use_scale_conc = TRUE,
+     print_out = TRUE, log10_C = FALSE)
+
 my_plot <- plot(my_pk, use_scale_conc = TRUE)
-plot(my_pk, use_scale_conc = TRUE,
-     print_out = TRUE)
 
@@
 
+png(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/examplePlot.png",
+    width = 8,
+    height = 6,
+    units = "in",
+    res = 150,
+    type = "cairo",
+    antialias = "none")
+plot(my_pk, use_scale_conc = TRUE,
+     method = "L-BFGS-B",
+     print_out = TRUE)[[3]]
+dev.off()
+
 ```
@@
 # get_tkstats()
-
+devtools::load_all()
+get_tkstats(my_pk) %>% head()
+get_tkstats(my_pk) %>% View("TK_test")
 my_tkstats <- get_tkstats(my_pk)
 
-plot_results <- plot(my_pk)
+# For the July 5th version where it returns a nested dataframe
+# 
+my_tkstats %>%
+  reframe(tkstats_df = purrr::map(c_data,
+                                  \(x) {
+                                    x %>%
+                                      dplyr::rowwise() %>%
+                                      dplyr::mutate(
+                                        TKstats = sapply(
+                                          coefs_vector,
+                                          FUN = tk_fun,
+                                          route = Route,
+                                          medium = Media,
+                                          dose = Dose,
+                                          time_unit = Time.Units,
+                                          conc_unit = Conc.Units,
+                                          vol_unit = "L",
+                                          simplify = FALSE,
+                                          USE.NAMES = TRUE
+                                        )
+                                      ) %>%
+                                      dplyr::ungroup()
+                                  })) -> my_tkstats
+
+my_tkstats %>% unnest(cols = c(tkstats_df)) -> my_tkstats
+
+my_tkstats %>% mutate(TKstats_wide  = map(TKstats,
+                                     \(x) {
+                                       dplyr::select(x, -param_units) %>%
+                                         tidyr::pivot_wider(names_from = param_name,
+                                                     values_from = param_value)
+                                     })) %>%
+  unnest(cols = c(TKstats_wide)) %>% View()
 

### 2023-07-10 data-raw/batchMode_trial_gpm.Rmd
Completed the logLik, AIC and BIC methods for the pk object.

@@
 
-my_predata <- subset(cvt,
-                     chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
-                                                                   "DTXSID2021731",
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
                                                               "DTXSID5032600"))
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID3061635"))
+
 ```
@@
   # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
+  stat_error_model(error_group = vars(Chemical, Species))
 
@@
 
-my_coefs_update <- coef(my_pk)
+my_coefs_update <- coef(my_pk, drop_sigma = TRUE)
 my_pred_update <- predict(my_pk,
@@
 
+```{r get_tkstats_logLik_methods}
+my_tkstats <- get_tkstats(my_pk)
+
+names(my_tkstats)
+my_tkstats
+
+my_logLike_update <- logLik(my_pk)
+
+```
+
 ```{r remaining_methods}
@@
 # logLik.pk
-# get_tkstats()
+
 devtools::load_all()
-get_tkstats(my_pk) %>% head()
-get_tkstats(my_pk) %>% View("TK_test")
-my_tkstats <- get_tkstats(my_pk)
-
-# For the July 5th version where it returns a nested dataframe
-# 
-my_tkstats %>%
-  reframe(tkstats_df = purrr::map(c_data,
-                                  \(x) {
-                                    x %>%
-                                      dplyr::rowwise() %>%
-                                      dplyr::mutate(
-                                        TKstats = sapply(
-                                          coefs_vector,
-                                          FUN = tk_fun,
-                                          route = Route,
-                                          medium = Media,
-                                          dose = Dose,
-                                          time_unit = Time.Units,
-                                          conc_unit = Conc.Units,
-                                          vol_unit = "L",
-                                          simplify = FALSE,
-                                          USE.NAMES = TRUE
-                                        )
-                                      ) %>%
-                                      dplyr::ungroup()
-                                  })) -> my_tkstats
-
-my_tkstats %>% unnest(cols = c(tkstats_df)) -> my_tkstats
-
-my_tkstats %>% mutate(TKstats_wide  = map(TKstats,
-                                     \(x) {
-                                       dplyr::select(x, -param_units) %>%
-                                         tidyr::pivot_wider(names_from = param_name,
-                                                     values_from = param_value)
-                                     })) %>%
-  unnest(cols = c(TKstats_wide)) %>% View()
+AIC(my_pk)
+BIC(my_pk)
 
 ```
+
+The purpose of the following code is to generate data.frames with information for
+all 103 chemicals in the `cvt` dataset that comes with `invivopkfit`.
+I will need to do append each dataframe to the last for the outputs of the following
+methods:
+
+- `AIC()`
+- `BIC()` left-joined with `AIC` output
+- `get_tkstats()`
+
+I will also have to fit these iteratively and manage the memory as part of the loop.
+
+```{r for_loop_allDTXSIDs}
+
+# All DTXSID
+eachDTXSID <- unique(cvt$chemicals_analyzed.dsstox_substance_id)
+
+id <- 1
+AIC_BIC <- data.frame()
+while (id <= 10) {
+  # Establishing the loop
+  DTX_set <- eachDTXSID[seq(from = id, to = id + 3)]
+  DTX_set <- DTX_set[!is.na(DTX_set)]
+  print(DTX_set)
+  id <- id + 4
+  Sys.sleep(0.5)
+
+  # Subsetting cvt
+  my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% DTX_set)
+
+  # Fitting loop
+  my_pk <- pk(data = my_predata) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time() +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species)) # Pooled model
+
+  my_pk <- do_preprocess(my_pk)
+
+  my_pk <- do_data_info(my_pk) 
+  # summarizes error (Returning more or less than 1 row per summarize)
+
+  my_pk <- do_prefit(my_pk)
+
+  my_pk <- do_fit(my_pk)
+
+  # OUTPUTS
+  # AIC/BIC
+  temp_AIC <- AIC(my_pk)
+  temp_BIC <- BIC(my_pk)
+  temp_IC <- left_join(temp_AIC, temp_BIC)
+  AIC_BIC <- bind_rows(AIC_BIC, temp_IC)
+
+} # Doesn't work because something for Solvent red 1 introduces an error
+
+```

### 2023-07-10 R/fit_group.R

@@ -21,7 +21,7 @@ fit_group <- function(data,
                       dose_norm,
                       log10_trans,
                       suppress.messages){
-  if(fit_decision %in% "continue"){
+  if (fit_decision %in% "continue") {
 
     #Rowbind par_DF and sigma_DF
     par_DF <- dplyr::bind_rows(par_DF,

### 2023-07-10 R/pk_methods_BIC.R

@@ -1,6 +1,6 @@
 #' Bayesian information criterion
 #'
-#' Get the Bayesian information criterion (AIC) for a fitted `pk` object
+#' Get the Bayesian information criterion (BIC) for a fitted `pk` object
 #'
 #' The BIC is calculated from the log-likelihood (LL) as follows:
 #' \deqn{\textrm{BIC} = -2\textrm{LL} + \log(n_{obs}) n_{par}}
@@ -49,19 +49,59 @@ BIC.pk <- function(obj,
                    exclude = TRUE){
   #ensure that the model has been fitted
   check <- check_required_status(obj = obj,
-                                 required_status = status_fit)
+                                 required_status = 5)
   if(!(check %in% TRUE)){
     stop(attr(check, "msg"))
   }
   if(is.null(model)) model <- names(obj$stat_model)
   if(is.null(method)) method <- obj$settings_optimx$method
-  if(is.null(newdata)) newdata <- obj$data
 
-  BIC <- AIC(obj = obj,
-             newdata = newdata,
-             model = model,
-             method = method,
-             exclude = exclude,
-             k = log(nrow(newdata)))
+  # Get the number of parameters
+
+  param_table <- obj$prefit$par_DF %>%
+    dplyr::filter(optimize_param %in% TRUE) %>%
+    dplyr::select(model, !!!obj$data_group, param_name, param_units)
+
+
+
+
+  sigma_table <- obj$prefit$stat_error_model$sigma_DF %>%
+    tibble::rownames_to_column("error_group") %>%
+    dplyr::select(!!!obj$data_group, param_name, param_units) %>%
+    tidyr::expand_grid(model = unique(param_table$model))
+
+  params_df <- bind_rows(param_table, sigma_table) %>%
+    dplyr::group_by(!!!obj$data_group, model) %>% dplyr::count(name = "npar")
+
+
+  #get log-likelihoods
+  ll <- logLik(obj = obj,
+               newdata = newdata,
+               model = model,
+               method = method,
+               negative = FALSE,
+               force_finite = FALSE,
+               exclude = exclude,
+               drop_obs = FALSE)
+
+  ll <- ll %>% dplyr::rowwise() %>%
+    dplyr::mutate(NROW = nrow(observations))
+
+  ll <- ll %>%
+    dplyr::select(!!!obj$data_group,
+                  model, method,
+                  log_likelihood,
+                  NROW) %>%
[…]

### 2023-07-11 data-raw/batchMode_trial_gpm.Rmd
Updated methods to work for full cvt data and ensure that Rblood2plasma was accurately passed onto coefs()

@@
   dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
-                                                              "DTXSID5032600"))
+                                                              "DTXSID5032600",
+                                                              "DTXSID2021103"))
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID5032600")
 
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID3061635"))
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID2021103")
+# Opt params not found ERROR
+# 
+#
 
@@
 ```{r single_fit}
-my_pk <- pk(data = my_predata) +
+my_pk <- pk(data = cvt) +
   facet_data(vars(Chemical, Species)) +
@@
 devtools::load_all()
+all_my_data <- my_pk$data # following the full dataset to prefit
+my_pk$data %>% filter(Chemical == "DTXSID2021103")
 
@@
 # coef_sd
-# logLik.pk
 
 devtools::load_all()
-AIC(my_pk)
+AIC(my_pk2) %>% View()
 BIC(my_pk)
@@
 
-```{r for_loop_allDTXSIDs}
+```{r allDTXSIDs_analysis}
 
-# All DTXSID
-eachDTXSID <- unique(cvt$chemicals_analyzed.dsstox_substance_id)
+# after fitting pk object for all cvt objects
+# saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
 
-id <- 1
-AIC_BIC <- data.frame()
-while (id <= 10) {
-  # Establishing the loop
-  DTX_set <- eachDTXSID[seq(from = id, to = id + 3)]
-  DTX_set <- DTX_set[!is.na(DTX_set)]
-  print(DTX_set)
-  id <- id + 4
-  Sys.sleep(0.5)
+my_tkstats <- get_tkstats(my_pk)
+my_IC <- left_join(AIC(my_pk), BIC(my_pk))
 
-  # Subsetting cvt
-  my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% DTX_set)
+my_IC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "bobyqa") %>%
+  ungroup() %>%
+  count(model)
+# model_1comp 60
+# model_2comp 48
+# model_flat   3
 
-  # Fitting loop
-  my_pk <- pk(data = my_predata) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time() +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) # Pooled model
+my_IC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>% View()
+  ungroup() %>%
+  count(model)
+# model_1comp 56
+# model_2comp 50
+# model_flat   5
 
-  my_pk <- do_preprocess(my_pk)
-
-  my_pk <- do_data_info(my_pk) 
-  # summarizes error (Returning more or less than 1 row per summarize)
-
-  my_pk <- do_prefit(my_pk)
-
-  my_pk <- do_fit(my_pk)
-
-  # OUTPUTS
-  # AIC/BIC
-  temp_AIC <- AIC(my_pk)
-  temp_BIC <- BIC(my_pk)
-  temp_IC <- left_join(temp_AIC, temp_BIC)
-  AIC_BIC <- bind_rows(AIC_BIC, temp_IC)
-
-} # Doesn't work because something for Solvent red 1 introduces an error
+all_my_data <- my_pk$data
 

### 2023-07-11 R/log_likelihood.R

@@ -302,7 +302,13 @@ log_likelihood <- function(par,
       #the result will be a matrix with as many columns as there are sigma_params,
       #and as many rows as there are observations without sigma groups
       #take the row means
-      ll_data_no_sigma <- rowMeans(ll_data_no_sigma)
+      # however, there are times there is only one value
+      # so make that just equal the mean of this
+      if (is.null(dim(ll_data_no_sigma))) {
+        ll_data_no_sigma <- mean(ll_data_no_sigma)
+      } else {
+        ll_data_no_sigma <- rowMeans(ll_data_no_sigma)
+      }
     } else{
       ll_data_no_sigma <- numeric(0)
     }

### 2023-07-11 R/pk_methods_coef.R

@@ -60,6 +60,11 @@ coef.pk <- function(obj,
 
   coefs <- dplyr::left_join(coefs, const_pars)
 
+  for (this_param in intersect(names(const_pars), possible_model_params)) {
+    coefs[this_param] <- tidyr::replace_na(coefs[[this_param]],
+                                           replace = unique(const_pars[[this_param]]))
+  }
+
   coefs_tidy <- coefs %>%
     tidyr::nest(coefs_tibble = dplyr::any_of(possible_model_params)) %>%
     dplyr::mutate(coefs_vector = map(coefs_tibble,

### 2023-07-11 data-raw/batchMode_trial_gpm.Rmd
Added figure for CVT observed variability.

@@
 # saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
+my_pk <- readRDS("data-raw/all_cvt_pk.rds")
 
@@
   filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>% View()
+         method == "L-BFGS-B") %>%
   ungroup() %>%
@@
 all_my_data <- my_pk$data
+all_my_data %>%
+  group_by(Chemical,
+           Species,
+           Reference,
+           Route,
+           Dose, Time) %>%
+  filter(n() > 1,
+         sum(is.na(Conc)) != n(),
+         LOQ < Conc) %>%
+  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
+  ungroup() %>%
+  rowwise() %>%
+  mutate(foldConc = Conc / meanConc) %>%
+  count(foldConc > 2)
+# 88.4% inside twofold
+# 2.4%  above twofold
+# 9.2%  below twofold
+
+all_my_data %>%
+  group_by(Chemical,
+           Species,
+           Reference,
+           Route,
+           Dose, Time) %>%
+  filter(n() > 1,
+         sum(is.na(Conc)) != n(),
+         LOQ < Conc) %>%
+  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
+  ungroup() %>%
+  rowwise() %>%
+  mutate(foldConc = Conc / meanConc) %>%
+  ggplot(aes(x = foldConc)) +
+  geom_histogram(binwidth = 0.1,
+                 fill = "grey5") +
+  coord_cartesian(xlim =  c(0, 4),
+                  ylim = c(0, 2000)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  expand_limits(y = 0) +
+  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
+  annotate(geom= "text",
+           x = 1.25, y = 1800,
+           label = "88.4% of Observations\n within a factor of 2") +
+  theme_classic() +
+  labs(x = "Concentration Normalized to Average",
+                y = "Number of Observations") +
+  theme(panel.border = element_rect(color = "black", fill = NA),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))
+
+ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
+              "NormalizedConcentrations_2023-07-11.png"),
+       height = 3.5,
+       width = 5.5,
+       units = "in")
+
+my_preds <- predict(my_pk)
+
+winmodels <- my_IC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>%
+  ungroup() %>%
+  dplyr::select(Chemical, Species,
+                method, model)
+
+my_preds <- inner_join(winmodels, my_preds)
+
+my_preds %>%
+  rowwise() %>%
+  mutate(Pred_Obs = Conc_trans/Conc_est) %>%
+  filter(is.finite(Pred_Obs)) %>%
+  ggplot(aes(x = Pred_Obs)) +
+  geom_histogram(
+                 fill = "grey5") +
+  coord_cartesian(xlim =  c(0.001, 1000),
+                  ylim = c(0, 2000)) +
+  scale_y_continuous() +
+  scale_x_log10()
+  expand_limits(y = 0) +
+  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
+  annotate(geom = "text",
+           x = 1.25, y = 1800,
+           label = "88.4% of Observations\n within a factor of 2") +
+  theme_classic() +
+  labs(x = "Concentration Normalized to Average",
+                y = "Number of Observations") +
+  theme(panel.border = element_rect(color = "black", fill = NA),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))
+
+# 89.9% of Pred_Obs are finite
+# 64.5% Are below two-fold
+# 26.3%  Are above two-fold
+# 9.3% Are within twofold
 

### 2023-07-13 data-raw/batchMode_trial_gpm.Rmd
Updated get_winning_model and added files of TKstats, non-compartmental analysis for Pooled and Joint analyses for full `cvt` data

@@
 knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
-
+set.seed(2023)
 library(tidyverse, quietly = TRUE)
@@
   # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) # Add Reference for Joint Analysis
 
@@
 
+get_winning_model(my_pk)
+
 ```
@@
 # saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
+# saveRDS(my_pk, file = "data-raw/all_cvt_pk_JOINT.rds")
 my_pk <- readRDS("data-raw/all_cvt_pk.rds")
-
+my_AIC <- AIC(my_pk)
 my_tkstats <- get_tkstats(my_pk)
@@
   ungroup() %>%
+  filter(model == "model_flat") %>% pull(Chemical) %>% unique()
   count(model)
@@
 
-my_preds <- predict(my_pk)
+my_preds <- predict(my_pk,
+                    use_scale_conc = TRUE)
 
@@
 my_preds <- inner_join(winmodels, my_preds)
+my_tkstats <- inner_join(winmodels, my_tkstats)
+my_nca <- get_nca(my_pk,
+                  nca_group = vars(Chemical, Species,))
+my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
+  pivot_wider(names_from = param_name,
+              values_from = param_value)
+
+# Saving some CSVs
+# my_tkstats %>% write_csv(file = "data-raw/Pooled_TKstats.csv")
+# my_nca %>% write_csv(file = "data-raw/NonCompartmentalAnalysis.csv")
 
@@
   mutate(Pred_Obs = Conc_trans/Conc_est) %>%
-  filter(is.finite(Pred_Obs)) %>%
+  filter(is.finite(Pred_Obs),
+         model %in% c("model_1comp", "model_2comp")) %>%
+  # mutate(pass = ifelse(Pred_Obs <= 2 & Pred_Obs >= 0.5, TRUE, FALSE)) %>%
+  # pull(pass) %>% table()
   ggplot(aes(x = Pred_Obs)) +
-  geom_histogram(
+  geom_histogram(binwidth = 0.4,
                  fill = "grey5") +
-  coord_cartesian(xlim =  c(0.001, 1000),
-                  ylim = c(0, 2000)) +
-  scale_y_continuous() +
-  scale_x_log10()
+  scale_x_log10(limits = c(NA, 1E6)) +
   expand_limits(y = 0) +
   geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
-  annotate(geom = "text",
-           x = 1.25, y = 1800,
-           label = "88.4% of Observations\n within a factor of 2") +
+  facet_grid(cols = vars(model),
+             rows = vars(Route)) +
+  labs(x = "Predicted/Observed",
+       y = "Number of Observations") +
   theme_classic() +
-  labs(x = "Concentration Normalized to Average",
-                y = "Number of Observations") +
-  theme(panel.border = element_rect(color = "black", fill = NA),
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA),
         panel.grid.major = element_line(color = "grey90", linewidth = 0.4))
@@
 # 89.9% of Pred_Obs are finite
-# 64.5% Are below two-fold
-# 26.3%  Are above two-fold
-# 9.3% Are within twofold
+# 19.3% Are below two-fold
+# 34.8%  Are above two-fold
+# 45.9% Are within twofold
+
+ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
+              "PredictedObserved_compartmentModels_2023-07-11.png"),
+       height = 4, width = 9)
+
+# Pooled analysis
+all_my_data %>% group_by(Chemical, Species, Reference, Media, Route) %>%
+  filter(is.finite(Conc)) %>%
+  summarise(OOM = log10(max(Conc) / min(Conc))) %>% 
+  ggplot(aes(x = OOM)) +
+  geom_histogram(bins = 15,
+                 color = NA,
+                 fill = "grey5") +
+  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
+  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5)) +
+  labs(x = "Orders of Magnitude per Series\n log10(max/min)",
+       y = "Count") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+
+ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
+              "OrdersOfMagnitude_2023-07-12.png"),
+       height = 4, width = 4)
+
+my_pk$prefit$fit_check %>% filter(fit_decision == "abort") %>%
+  dplyr::select(model, Chemical) %>% distinct()
+
+all_my_data %>%
+  filter(Chemical == "DTXSID2021781")
+
+my_AIC %>% group_by(Chemical, Species, method) %>%
+  filter(if_any(contains("AIC"), ~ . == min(.)))
 

### 2023-07-13 data-raw/batchMode_trial_gpm.Rmd
Updated the eval_tkstats method

@@
   # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) # Add Reference for Joint Analysis
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+# Add Reference for Joint Analysis
 
@@
 get_winning_model(my_pk)
+eval_tkstats(my_pk)
 
@@
 # my_nca %>% write_csv(file = "data-raw/NonCompartmentalAnalysis.csv")
+# Loading CSVs
+my_nca <- read_csv(file = "data-raw/NonCompartmentalAnalysis.csv")
 
@@
 
-ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
+ggsave(paste0("C:/Users/GPADILLA/",
+              "OneDrive - Environmental Protection Agency (EPA)/",
+              "Profile/Documents/Figures/",
               "OrdersOfMagnitude_2023-07-12.png"),
@@
 
-my_AIC %>% group_by(Chemical, Species, method) %>%
-  filter(if_any(contains("AIC"), ~ . == min(.)))
+```
+
+```{r update_eval_kstats}
+
+my_eval <- left_join(my_tkstats_red, my_nca_red) %>%
+  filter(is.finite(AUC_inf.tkstats), is.finite(AUC_inf.nca)) %>%
+  group_by(!!!my_pk$settings_data_info$nca_group)
+
+my_eval %>%
+  dplyr::select(AUC_inf.tkstats, AUC_inf.nca, Cmax.tkstats, Cmax.nca) %>%
+  ungroup(Dose) %>%
+  summarize(AUC_inf_RMSE = abs(mean(AUC_inf.tkstats) - mean(AUC_inf.nca)),
+            Cmax_RMSE = abs(mean(Cmax.tkstats) - mean(AUC_inf.nca)))
 

### 2023-07-17 data-raw/batchMode_trial_gpm.Rmd
Updated tkstats mthods default behavior

@@
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID5032600")
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID1043881")
 
@@
 #
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID2039336",
+                                                              "DTXSID7029904",
+                                                              "DTXSID1021087",
+                                                              "DTXSID2020682"))
 
@@
 ```{r single_fit}
-my_pk <- pk(data = cvt) +
+my_pk <- pk(data = my_predata) +
   facet_data(vars(Chemical, Species)) +
@@
   scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time() +
+  scale_time(new_units = "days") +
   # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+  stat_error_model(error_group = vars(Chemical, Species)) 
 # Add Reference for Joint Analysis
@@
 my_preds <- inner_join(winmodels, my_preds)
-my_tkstats <- inner_join(winmodels, my_tkstats)
+my_tkstats <- inner_join(winmodels, my_tkstats) %>%
+  dplyr::select(-TKstats, -Reference) %>% distinct()
 my_nca <- get_nca(my_pk,
@@
 ```{r update_eval_kstats}
+devtools::load_all()
+my_eval <- eval_tkstats(my_pk)
 
-my_eval <- left_join(my_tkstats_red, my_nca_red) %>%
-  filter(is.finite(AUC_inf.tkstats), is.finite(AUC_inf.nca)) %>%
-  group_by(!!!my_pk$settings_data_info$nca_group)
+# To give summary RMSEs of Cmax and AUC...
+my_eval <- my_eval %>%
+  group_by(method, model, .add = TRUE) %>%
+  ungroup(Reference) %>%
+  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
+                                             na.rm = TRUE)^2)),
+            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
+                                          na.rm = TRUE)^2)),
+            .groups = "keep")
 
-my_eval %>%
-  dplyr::select(AUC_inf.tkstats, AUC_inf.nca, Cmax.tkstats, Cmax.nca) %>%
-  ungroup(Dose) %>%
-  summarize(AUC_inf_RMSE = abs(mean(AUC_inf.tkstats) - mean(AUC_inf.nca)),
-            Cmax_RMSE = abs(mean(Cmax.tkstats) - mean(AUC_inf.nca)))
+my_eval <- my_eval %>%
+  mutate(dose_norm = TRUE,
+         log10_norm = FALSE,
+         scale_time = FALSE,
+         Analysis_Type = "Pooled")
+
+ggplot(my_eval,
+       aes(x = AUC_inf_RMSE,
+           y = Cmax_RMSE)) +
+  geom_point()
+
+ggplot(my_eval,
+       aes(x = -log10(AUC_inf_RMSE))) +
+  geom_histogram(fill = "grey5") +
+  facet_grid(cols = vars(method)) +
+  labs(x = "Accuracy of AUC",
+       y = "Observations") +
+  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
 
 ```
+
+```{r eval_Joint}
+my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
+my_eval_joint <- eval_tkstats(my_pk)
+
+# To give summary RMSEs of Cmax and AUC...
+my_eval_joint <- my_eval_joint %>%
+  group_by(method, model, .add = TRUE) %>%
+  ungroup(Reference) %>%
+  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
+                                             na.rm = TRUE)^2)),
+            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
+                                          na.rm = TRUE)^2)),
+            .groups = "keep")
+
+my_eval_joint <- my_eval_joint %>%
+  mutate(dose_norm = TRUE,
+         log10_norm = FALSE,
+         scale_time = FALSE,
+         Analysis_Type = "Joint")
+
+ggplot(my_eval_joint,
+       aes(x = AUC_inf_RMSE,
+           y = Cmax_RMSE)) +
+  geom_point()
+
+ggplot(my_eval_joint,
+       aes(x = -log10(AUC_inf_RMSE))) +
+  geom_histogram(fill = "grey5") +
+  facet_grid(cols = vars(method)) +
+  labs(x = "Accuracy of AUC",
+       y = "Observations") +
+  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+
+total_eval <- bind_rows(my_eval, my_eval_joint)
+
+ggplot(total_eval,
+       aes(x = AUC_inf_RMSE,
+           y = Cmax_RMSE)) +
+  geom_point() +
+  facet_grid(rows = vars(Analysis_Type))
+
+total_eval %>%
+  dplyr::select(!Cmax_RMSE) %>%
+  pivot_wider(names_from = Analysis_Type,
+              values_from = AUC_inf_RMSE) %>%
+  ggplot(aes(x = -log10(Pooled),
+             y = -log10(Joint),
+             color = Media)) +
+  geom_point(alpha = 0.3) +
+  geom_abline(slope = 1, linetype = "dashed") +
+  facet_grid(rows = vars(model),
+             cols = vars(method)) +
+  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+
+total_eval %>%
+  dplyr::select(!Cmax_RMSE) %>%
+  pivot_wider(names_from = Analysis_Type,
+              values_from = AUC_inf_RMSE) %>%
+  mutate(ratio = Joint/Pooled) %>%
+  filter(!(ratio == 1)) %>% pull(Chemical) %>% unique()
+  View()
+
+```

### 2023-07-19 data-raw/batchMode_trial_gpm.Rmd
Updating do_process to account for group-based Time Unit conversions and re-fitting cvt data

@@
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID1043881")
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")
 
@@
 ```{r single_fit}
+# Pooled
 my_pk <- pk(data = my_predata) +
@@
   scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  scale_time(new_units = "days") +
+  # scale_time(new_units = "auto") +
   # stat_model() + 
   stat_error_model(error_group = vars(Chemical, Species)) 
+# Add Reference for Joint Analysis
+
+my_pk <- do_preprocess(my_pk)
+
+my_pk <- do_data_info(my_pk)
+# summarizes error (Returning more or less than 1 row per summarize)
+
+my_pk <- do_prefit(my_pk)
+
+my_pk <- do_fit(my_pk)
+
+# Joint
+my_pk <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
 # Add Reference for Joint Analysis
@@
   count(model)
-# model_1comp 60
-# model_2comp 48
-# model_flat   3
+# model_1comp 59
+# model_2comp 50
+# model_flat   2
 
@@
   ungroup() %>%
-  filter(model == "model_flat") %>% pull(Chemical) %>% unique()
+  # filter(model == "model_flat") %>% pull(Chemical) %>% unique()
   count(model)
-# model_1comp 56
+# model_1comp 57
 # model_2comp 50
-# model_flat   5
+# model_flat   4
 
@@
 
+all_my_data %>%
+  group_by(Chemical,
+           Species,
+           Reference,
+           Route,
+           Dose, Time) %>%
+  filter(n() > 1,
+         sum(is.na(Conc)) != n(),
+         exclude == FALSE) %>%
+  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
+  ungroup() %>%
+  rowwise() %>%
+  mutate(foldConc = Conc / meanConc) %>%
+  inner_join(my_tkstats %>%
+              dplyr::select(Chemical, Species,
+                            Route, Media,
+                            tmax) %>%
+              filter(!is.na(tmax))) %>%
+  group_by(Chemical,
+           Species,
+           Reference,
+           Route,
+           Media,
+           Dose) %>%
+  mutate(
+         normTime = ifelse(
+           Route == "iv",
+           1 + Time/max(Time),
+           ifelse(
+             Time > tmax,
+             ((Time - tmax)/max(Time)) + 1,
+             0.5 + Time/(2*tmax)
+           )
+         )) %>%
+  ggplot(aes(
+    x = normTime,
+    y = foldConc
+  )) +
+  geom_point(alpha = 0.2) +
+  geom_vline(xintercept = 1, color = "blue", linetype = "dashed") +
+  geom_vline(xintercept = 2, color = "green4", linetype = "dashed") +
+  geom_hline(yintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
+  facet_grid(cols = vars(Route),
+             scales = "free_x") +
+  labs(x = "ADME-Normalized Time",
+       y = "Mean-Normalized Concentration") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text.x = element_blank())
+
+ggsave(paste0("C:/Users/GPADILLA/",
+              "OneDrive - Environmental Protection Agency (EPA)/",
+              "Profile/Documents/Figures/",
+              "ADME_NormalizedTime-NormalizedConcentrations_2023-07-19.png"),
+       height = 4,
+       width = 6,
+       units = "in")
+
+my_tkstats %>%
+              dplyr::select(Chemical, Species,
+                            Route, Media, model, method,
+                            tmax) %>%
+              filter(!is.na(tmax))
+
+all_my_data %>%
+              dplyr::select(Chemical, Species,
+                            Route, Media, Dose,
+                            Reference) %>%
+  distinct() %>% nrow()
+
 my_preds <- predict(my_pk,
@@
 my_tkstats <- inner_join(winmodels, my_tkstats) %>%
-  dplyr::select(-TKstats, -Reference) %>% distinct()
+  dplyr::select(-TKstats) %>% distinct()
 my_nca <- get_nca(my_pk,
@@
          model %in% c("model_1comp", "model_2comp")) %>%
-  # mutate(pass = ifelse(Pred_Obs <= 2 & Pred_Obs >= 0.5, TRUE, FALSE)) %>%
+  # mutate(pass = ifelse(Pred_Obs < 0.5, TRUE, FALSE)) %>%
   # pull(pass) %>% table()
@@
 
-# 89.9% of Pred_Obs are finite
-# 19.3% Are below two-fold
-# 34.8%  Are above two-fold
-# 45.9% Are within twofold
+# 91.1% of Pred_Obs are finite
+# 16.6% Are below two-fold
+# 33.2%  Are above two-fold
+# 50.2% Are within twofold
 
-ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
+ggsave(paste0("C:/Users/GPADILLA/",
+              "OneDrive - Environmental Protection Agency (EPA)/",
+              "Profile/Documents/Figures/",
               "PredictedObserved_compartmentModels_2023-07-11.png"),
-       height = 4, width = 9)
+       height = 6, width = 7)
 
@@
 
-```{r update_eval_kstats}
+```{r update_eval_tkstats}
 devtools::load_all()
+my_pk <- readRDS("data-raw/all_cvt_pk.rds")
 my_eval <- eval_tkstats(my_pk)
@@
            y = Cmax_RMSE)) +
-  geom_point()
+  geom_point() +
+  geom_abline(slope = 1) +
+  scale_y_log10() +
+  scale_x_log10()
 
@@
 ```{r eval_Joint}
-my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
-my_eval_joint <- eval_tkstats(my_pk)
+my_pk2 <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
+my_eval_joint <- eval_tkstats(my_pk2)
 
@@
               values_from = AUC_inf_RMSE) %>%
-  ggplot(aes(x = -log10(Pooled),
-             y = -log10(Joint),
+  ggplot(aes(x = log10(Pooled),
+             y = log10(Joint),
              color = Media)) +
@@
   mutate(ratio = Joint/Pooled) %>%
-  filter(!(ratio == 1)) %>% pull(Chemical) %>% unique()
-  View()
+  # filter(!(ratio == 1)) %>% 
+  # View()
+  pull(Chemical) %>%
+  # unique()
+  length()
 

### 2023-07-21 data-raw/batchMode_trial_gpm.Rmd
Plotting data variability and model performance.

@@
 
+my_preds <- predict(my_pk,
+                    use_scale_conc = TRUE)
+
+winmodels <- my_IC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>%
+  ungroup() %>%
+  dplyr::select(Chemical, Species,
+                method, model)
+
+my_preds <- inner_join(winmodels, my_preds)
+my_tkstats <- inner_join(winmodels, my_tkstats) %>%
+  dplyr::select(-TKstats) %>% distinct()
+my_nca <- get_nca(my_pk,
+                  nca_group = vars(Chemical, Species,))
+my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
+  pivot_wider(names_from = param_name,
+              values_from = param_value)
+
 all_my_data <- my_pk$data
@@
   filter(n() > 1,
-         sum(is.na(Conc)) != n(),
+         sum(is.na(Conc_trans)) != n(),
          exclude == FALSE) %>%
-  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
+  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
   ungroup() %>%
   rowwise() %>%
-  mutate(foldConc = Conc / meanConc) %>%
+  mutate(foldConc = Conc_trans / meanConc) %>%
   inner_join(my_tkstats %>%
@@
   )) +
-  geom_point(alpha = 0.2) +
+  geom_point(alpha = 0.2,
+             aes(color = Chemical)) +
   geom_vline(xintercept = 1, color = "blue", linetype = "dashed") +
@@
   facet_grid(cols = vars(Route),
+             rows = vars(Species),
              scales = "free_x") +
@@
               "Profile/Documents/Figures/",
-              "ADME_NormalizedTime-NormalizedConcentrations_2023-07-19.png"),
+              "ADME_NormalizedTime-NormalizedConcentrations_onlyDetects_2023-07-19.png"),
        height = 4,
@@
        units = "in")
+
+# Per chemical + Species average mean normalized concentration variability over time
+all_my_data %>%
+  group_by(Chemical,
+           Species,
+           Reference,
+           Route,
+           Dose, Time) %>%
+  filter(n() > 1,
+         sum(is.na(Conc)) != n(),
+         LOQ < Conc,
+         exclude == FALSE) %>%
+  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
+  ungroup() %>%
+  rowwise() %>%
+  mutate(foldConc = Conc / meanConc) %>%
+  inner_join(my_tkstats %>%
+              dplyr::select(Chemical, Species,
+                            Route, Media,
+                            tmax) %>%
+              filter(!is.na(tmax))) %>%
+  group_by(Chemical, Species, Route, Media, Dose) %>%
+  summarize(sdFC = sd(foldConc)) %>%
+  mutate(maxDose = max(Dose),
+         minDose = min(Dose)) %>%
+  ungroup() %>%
+  add_count(Dose, name = "Unique_Doses") %>%
+  filter(Unique_Doses == 1) %>%
+  arrange(desc(sdFC))
 
@@
               values_from = param_value)
+
+my_preds %>%
+  group_by(Chemical,
+           Species,
+           Route,
+           Dose, Time) %>%
+  filter(n() > 1,
+         sum(is.na(Conc_trans)) != n(),
+         exclude == FALSE,
+         Detect == TRUE) %>%
+  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
+  ungroup() %>%
+  rowwise() %>%
+  mutate(foldConc = Conc_trans / meanConc,
+         foldPred = Conc_est / Conc_trans) %>% 
+  # filter(model == "model_2comp") %>%
+  mutate(VAR_DATA = ifelse(
+    (foldPred > 2 | foldPred < 0.5) & (foldConc <= 2 & foldConc >= 0.5),
+    TRUE, FALSE
+  )) %>%
+  filter(VAR_DATA == TRUE) %>%
+  pull(VAR_DATA) %>% table()
+  ggplot(aes(
+    y = foldPred,
+    x = foldConc
+  )) +
+  geom_bin2d(bins = 40, color = NA) +
+  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
+  geom_vline(xintercept = c(0.5, 2), linetype = "dashed") +
+  facet_grid(cols = vars(model)) +
+  scale_x_log10(limits = c(0.0001, 50)) +
+  scale_y_log10(limits = c(0.001, 1000)) +
+  scale_fill_viridis_c(option = "cividis",
+                       limits = c(1, 100),
+                       oob = oob_squish) +
+  labs(y = "Model Performance",
+       x = "Data Variability") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+
+ggsave(paste0("C:/Users/GPADILLA/",
+              "OneDrive - Environmental Protection Agency (EPA)/",
+              "Profile/Documents/Figures/",
+              "ModelPerformance_vDataVariability_2023-07-20.png"),
+       height = 3.5,
+       width = 7,
+       units = "in")
+
+# Why are 38-39% of adequate data have models that are too variable?
+# 
+my_preds %>%
+  group_by(Chemical,
+           Species,
+           Route,
+           Dose, Time) %>%
+  filter(n() > 1,
+         sum(is.na(Conc_trans)) != n(),
+         exclude == FALSE,
+         Detect == TRUE) %>%
+  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
+  ungroup() %>%
+  rowwise() %>%
+  mutate(foldConc = Conc_trans / meanConc,
+         foldPred = Conc_est / Conc_trans) %>% 
+  # filter(model == "model_2comp") %>%
+  mutate(VAR_DATA = ifelse(
+    (foldPred > 2 | foldPred < 0.5) & (foldConc <= 2 & foldConc >= 0.5),
+    TRUE, FALSE
+  )) %>%
+  group_by(Chemical, Species) %>%
+  mutate(VAR_TRUE = sum(VAR_DATA %in% TRUE),
+         VAR_FALSE = sum(VAR_DATA %in% FALSE)) %>%
+  dplyr::select(-VAR_DATA) %>% distinct() %>%
+  mutate(PERCENT_TRUE = VAR_TRUE/(VAR_TRUE + VAR_FALSE),
+         MAJOR_TRUE = ifelse(PERCENT_TRUE > 0.6, TRUE, FALSE)) %>%
+  # View("Count")
+  ggplot(aes(
+    x = Time,
+    y = Conc_est,
+    color = paste(Chemical, Species),
+    group = paste(Chemical, Species)
+  )) +
+  geom_point() +
+  geom_line() +
+  facet_grid(cols = vars(MAJOR_TRUE),
+             rows = vars(Route)) +
+  labs(y = "Predicted Concentrations",
+       x = "Time") +
+  # xlim(0, 2000) +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        legend.position = "none",
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
 

### 2023-07-21 data-raw/batchMode_trial_gpm.Rmd
Plotting data variability and model performance.

@@
   facet_grid(cols = vars(MAJOR_TRUE),
-             rows = vars(Route)) +
+             rows = vars(model)) +
   labs(y = "Predicted Concentrations",
        x = "Time") +
-  # xlim(0, 2000) +
+  xlim(0, 78) +
   theme(aspect.ratio = 1,

### 2023-07-24 data-raw/batchMode_trial_gpm.Rmd
Updated summarize to reframe()

@@
 my_pk <- do_data_info(my_pk)
-# summarizes error (Returning more or less than 1 row per summarize)
 
@@
        x = "Time") +
-  xlim(0, 78) +
+  # xlim(0, 2000) +
   theme(aspect.ratio = 1,

### 2023-07-25 data-raw/batchMode_trial_gpm.Rmd
Updating residuals method and plotting residuals over ADME-normalized time.

@@
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
-                                                              "DTXSID5032600",
-                                                              "DTXSID2021103"))
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID8031865"),
+                subjects.species_harmonized %in% "rat",
+                studies.administration_route_normalized %in% "iv")
 my_predata <- cvt %>%
@@
 
+plot(my_pk,
+     method = "L-BFGS-B",
+     print_out = TRUE)
 # Joint
@@
   mutate(foldConc = Conc / meanConc) %>%
-  count(foldConc > 2)
+  count(foldConc < 2 & foldConc > 0.5)
 # 88.4% inside twofold
@@
 ```
+
+```{r PredictionVariability_overtime}
+my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+winmodels <- AIC(my_pk) %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>%
+  ungroup() %>%
+  dplyr::select(Chemical, Species,
+                method, model)
+my_preds <- inner_join(winmodels,
+                       predict(my_pk,
+                               use_scale_conc = TRUE))
+
+my_tkstats <- inner_join(winmodels, get_tkstats(my_pk))
+my_residuals <- residuals(my_pk, use_scale_conc = TRUE)
+
+# my_preds %>%
+#   group_by(Chemical,
+#            Species,
+#            Route,
+#            Dose, Time) %>%
+#   filter(sum(is.na(Conc_trans)) != n(),
+#          exclude == FALSE,
+#          Detect %in% TRUE) %>%
+#          
+my_residuals %>%
+  filter(exclude == FALSE) %>%
+  inner_join(winmodels) %>%
+  inner_join(my_tkstats %>%
+              dplyr::select(Chemical, Species,
+                            Route, Media,
+                            tmax) %>%
+              filter(!is.na(tmax))) %>%
+  group_by(Chemical,
+           Species,
+           Route,
+           Media,
+           Dose) %>%
+  mutate(
+         normTime = ifelse(
+           Route == "iv",
+           1 + Time/max(Time),
+           ifelse(
+             Time > tmax,
+             ((Time - tmax)/max(Time)) + 1,
+             0.5 + Time/(2*tmax)
+           )
+         )) %>%
+  distinct() %>%
+  filter(Detect %in% TRUE) %>%
+  # filter(Route == "iv") %>% View()
+  ggplot(aes(
+    x = normTime,
+    y = Residuals
+  )) +
+  geom_point(alpha = 0.2, size = 0.5) +
+  geom_vline(xintercept = 1, color = "blue", linetype = "dashed") +
+  geom_vline(xintercept = 2, color = "green4", linetype = "dashed") +
+  facet_grid(cols = vars(Route),
+             # rows = vars(model),
+             scales = "free_x") +
+  labs(x = "ADME-Normalized Time",
+       y = "Winning Model Residuals") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text.x = element_blank())
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "ADME_NormalizedTime-WinModelResiduals_onlyDetects_2023-07-19.png"),
+       height = 4,
+       width = 6,
+       units = "in")
+```

### 2023-07-28 data-raw/batchMode_trial_gpm.Rmd
Updated plotting method interpolation

--- 2023-07-24 data-raw/batchMode_trial_gpm.Rmd
@@
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
-                                                              "DTXSID5032600",
-                                                              "DTXSID2021103"))
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
+                subjects.species_harmonized %in% "hamster",
+                studies.administration_route_normalized %in% "iv")
 my_predata <- cvt %>%
@@
 my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+my_coefs <- coef(my_pk, drop_sigma = FALSE)
+get_winning_model(my_pk) %>%
+  filter(model %in% c("model_2comp"),
+         method == "L-BFGS-B") %>%
+  dplyr::select(Chemical, Species) %>% distinct() %>% nrow()
+all_my_data  %>% dplyr::select(Chemical, Species) %>% distinct() %>% nrow()
 my_AIC <- AIC(my_pk)
@@
 all_my_data %>%
+  filter(Detect %in% TRUE,
+         exclude %in% FALSE,
+         Dose > 0) %>%
   group_by(Chemical,
@@
            Route, 
+           Media,
            Dose, Time) %>%
@@
   mutate(foldConc = Conc / meanConc) %>%
-  count(foldConc > 2)
-# 88.4% inside twofold
-# 2.4%  above twofold
-# 9.2%  below twofold
+  filter(Route == "iv") %>%
+  count(foldConc >= 0.5 & foldConc <= 2) %>%
+  {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
+# 88.9% inside twofold
+# 2.2%  above twofold 
+# 8.8%  below twofold
+# 
+#
 
 all_my_data %>%
+  filter(Detect %in% TRUE,
+         exclude %in% FALSE,
+         Dose > 0) %>%
   group_by(Chemical,
@@
   geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
-  annotate(geom= "text",
-           x = 1.25, y = 1800,
-           label = "88.4% of Observations\n within a factor of 2") +
+  # annotate(geom= "text",
+  #          x = 1.25, y = 1800,
+  #          label = "88.9% of Observations\n within a factor of 2") +
   theme_classic() +
@@
 
-winmodels <- my_IC %>% group_by(Chemical, Species, method) %>%
+winmodels <- AIC(my_pk) %>% group_by(Chemical, Species, method) %>%
   filter(AIC == min(AIC),
@@
            Species,
-           Route,
+           Route, Media,
            Dose, Time) %>%
@@
          sum(is.na(Conc_trans)) != n(),
-         exclude == FALSE,
-         Detect == TRUE) %>%
+         model %in% c("model_flat"),
+         exclude %in% FALSE,
+         Detect %in% TRUE) %>%
   mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
@@
          foldPred = Conc_est / Conc_trans) %>% 
-  # filter(model == "model_2comp") %>%
-  mutate(VAR_DATA = ifelse(
-    (foldPred > 2 | foldPred < 0.5) & (foldConc <= 2 & foldConc >= 0.5),
-    TRUE, FALSE
-  )) %>%
-  filter(VAR_DATA == TRUE) %>%
-  pull(VAR_DATA) %>% table()
+  # For percentages
+  ungroup() %>%
+  count(!(foldPred >= 0.5 & foldPred <= 2) &
+          !(foldConc >= 0.5 & foldConc <= 2)) %>%
+  {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
+  # For Plotting
   ggplot(aes(
@@
 
+my_coefs %>% inner_join(get_winning_model(my_pk)) -> my_coefs
+my_coefs %>% inner_join(get_data_summary(my_pk)) -> my_coefs
+
+my_coefs %>%
+  mutate(model = 
+           case_when(
+             model == "model_1comp" ~ "1-compartment",
+             model == "model_2comp" ~ "2-compartment",
+             model == "model_flat"  ~ "Null"
+           )) %>%
+  ggplot(aes(x = sigma_value/n_obs)) +
+  geom_histogram(bins = 15,
+                 color = NA, fill = "grey5") +
+  scale_x_log10(labels = label_log()) +
+  facet_grid(cols = vars(model)) +
+  labs(x = "Size-normalized Sigma Value",
+       y = "Number of Observations",
+       title = "Distribution of Sigmas in CvTdb data") +
+  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        plot.title = element_text(hjust = 0.5),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "NormalizedSigma_Distributions_2023-07.png"),
+       height = 3, width = 5)
 ```
@@
 ```
+
+```{r PredictionVariability_overtime}
+my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+winmodels <- AIC(my_pk) %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>%
+  ungroup() %>%
+  dplyr::select(Chemical, Species,
+                method, model)
+my_preds <- inner_join(winmodels,
+                       predict(my_pk,
+                               use_scale_conc = TRUE))
+
+my_tkstats <- inner_join(winmodels, get_tkstats(my_pk))
+my_residuals <- residuals(my_pk, use_scale_conc = FALSE)
+
+my_residuals %>%
+  filter(exclude == FALSE) %>%
+  inner_join(winmodels) %>%
+  inner_join(my_tkstats %>%
+              dplyr::select(Chemical, Species,
+                            Route, Media,
+                            tmax) %>%
+              filter(!is.na(tmax))) %>%
+  group_by(Chemical,
+           Species,
+           Route,
+           Media,
+           Dose) %>%
+  mutate(
+         normTime = ifelse(
+           Route == "iv",
+           1 + Time/max(Time),
+           ifelse(
+             Time > tmax,
+             ((Time - tmax)/max(Time)) + 1,
+             0.5 + Time/(2*tmax)
+           )
+         )) %>%
+  distinct() %>%
+  filter(Detect %in% TRUE) -> my_residuals2
+my_residuals2 %>%
+  # filter(Route == "oral") %>% View()
+  ggplot(aes(
+    x = normTime,
+    y = Residuals
+  )) +
+  geom_point(alpha = 0.2, size = 0.5) +
+  geom_point(data = filter(my_residuals2,
+                           Chemical %in% "DTXSID4020533",
+                           Species %in% "rat"),
+             color = "orange2", size = 0.5) +
+  geom_point(data = filter(my_residuals2,
+                           Chemical %in% "DTXSID8031865",
+                           Species %in% "rat"),
+             color = "magenta4", size = 0.5) +
+  geom_point(data = filter(my_residuals2,
+                           Chemical %in% "DTXSID8025337",
+                           Species %in% "rat"),
+             color = "green2", size = 0.5) +
+  geom_vline(xintercept = 1, color = "blue", linetype = "dashed") +
+  geom_vline(xintercept = 2, color = "green4", linetype = "dashed") +
+  facet_grid(cols = vars(Route),
+             # rows = vars(model),
+             scales = "free_x") +
+  labs(x = "ADME-Normalized Time",
+       y = "Winning Model Residuals") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text.x = element_blank())
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "ADME_NormalizedTime-WinModelResiduals_onlyDetects_Highlighted_2023-07-19.png"),
+       height = 4,
+       width = 6,
+       units = "in")
+```
+
+```{r log10_Pooled}
+devtools::load_all()
+
+my_log10pk <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species)) 
+# Add Reference for Joint Analysis
+
+my_log10pk <- do_preprocess(my_log10pk)
+
+my_log10pk <- do_data_info(my_log10pk)
+
+my_log10pk <- do_prefit(my_log10pk)
+
+my_log10pk <- do_fit(my_log10pk)
+# saveRDS(my_log10pk, file = "data-raw/all_cvt_pklog10.rds")
+
+my_AIC <- AIC(my_log10pk)
+my_tkstats <- get_tkstats(my_log10pk)
+
+my_AIC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "bobyqa") %>%
+  ungroup() %>%
+  count(model)
+# model_1comp 69
+# model_2comp 35
+# model_flat   7
+
+my_AIC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>%
+  ungroup() %>%
+  count(model)
+# model_1comp 77
+# model_2comp 25
+# model_flat   9
+
+# To give summary RMSEs of Cmax and AUC...
+my_eval <- eval_tkstats(my_log10pk) %>%
+  group_by(method, model, .add = TRUE) %>%
+  ungroup(Reference) %>%
+  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
+                                             na.rm = TRUE)^2)),
+            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
+                                          na.rm = TRUE)^2)),
+            .groups = "keep")
+
+my_eval %>%
+  group_by(method) %>%
+  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
+            AUC_mediRMSE = median(AUC_inf_RMSE),
+            AUC_sdRMSE = sd(AUC_inf_RMSE),
+            Cmax_meanRMSE = mean(Cmax_RMSE),
+            Cmax_mediRMSE = median(Cmax_RMSE),
+            Cmax_sdRMSE = sd(Cmax_RMSE)) %>% as.data.frame()
+
+```
+
+```{r log10_Joint}
+my_log10pk <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+# Add Reference for Joint Analysis
+
+my_log10pk <- do_preprocess(my_log10pk)
+
+my_log10pk <- do_data_info(my_log10pk)
+
+my_log10pk <- do_prefit(my_log10pk)
+
+my_log10pk <- do_fit(my_log10pk)
+
+my_AIC <- AIC(my_log10pk)
+
+my_AIC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "bobyqa") %>%
+  ungroup() %>%
+  count(model)
+# model_1comp 56
+# model_2comp 54
+# model_flat  1
+
+my_AIC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>%
+  ungroup() %>%
+  count(model)
+# model_1comp 63
+# model_2comp 48
+# model_flat  0
+
+my_eval <- eval_tkstats(my_log10pk)
+
+# To give summary RMSEs of Cmax and AUC...
+my_eval <- my_eval %>%
+  group_by(method, model, .add = TRUE) %>%
+  ungroup(Reference) %>%
+  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
+                                             na.rm = TRUE)^2)),
+            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
+                                          na.rm = TRUE)^2)),
+            .groups = "keep")
+
+my_eval %>%
+  group_by(method) %>%
+  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
+            AUC_mediRMSE = median(AUC_inf_RMSE),
+            AUC_sdRMSE = sd(AUC_inf_RMSE),
+            Cmax_meanRMSE = mean(Cmax_RMSE),
+            Cmax_mediRMSE = median(Cmax_RMSE),
+            Cmax_sdRMSE = sd(Cmax_RMSE)) %>%
+  as.data.frame()
+
+```
+
+```{r boilerplate_RMSE_analysis}
+my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+my_AIC <- AIC(my_pk)
+
+my_AIC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "bobyqa") %>%
+  ungroup() %>%
+  count(model)
+
+my_AIC %>% group_by(Chemical, Species, method) %>%
+  filter(AIC == min(AIC),
+         method == "L-BFGS-B") %>%
+  ungroup() %>%
+  count(model)
+
+my_eval <- eval_tkstats(my_pk)
+
+# To give summary RMSEs of Cmax and AUC...
+my_eval <- my_eval %>%
+  group_by(method, model, .add = TRUE) %>%
+  ungroup(Reference) %>%
+  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
+                                             na.rm = TRUE)^2)),
+            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
+                                          na.rm = TRUE)^2)),
+            .groups = "keep")
+
+my_eval %>%
+  group_by(method) %>%
+  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
+            AUC_mediRMSE = median(AUC_inf_RMSE),
+            AUC_sdRMSE = sd(AUC_inf_RMSE),
+            Cmax_meanRMSE = mean(Cmax_RMSE),
+            Cmax_mediRMSE = median(Cmax_RMSE),
+            Cmax_sdRMSE = sd(Cmax_RMSE)) %>%
+  as.data.frame()
+```
+
+```{r bad_fits}
+predata_chemical <- my_pk$prefit$fit_check %>%
+  filter(fit_decision == "abort") %>%
+  pull(Chemical) %>%
+  unique()
+
+my_pk <- pk(data = cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% predata_chemical)) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species)) 
+# Add Reference for Joint Analysis
+
+my_pk <- do_preprocess(my_pk)
+
+get_data(my_pk) %>% View()
+
+plot(my_pk, print_out = TRUE)[[1]] +
+  labs(subtitle = "Dibutyl phthalate (DBP)") +
+  theme(aspect.ratio = 1,
+        plot.subtitle = element_text(hjust = 0.5))
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "DTXSID20211781_rat_badFit.png"),
+       width = 6,
+       height = 4,
+       units = "in")
+
+my_pk <- pk(data = cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID2021315")) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk <- do_fit(my_pk)
+
+plot(my_pk,
+     method = "L-BFGS-B",
+     n_interp = 10,
+     print_out = TRUE)[[1]] +
+  labs(subtitle = "2,3,7,8-tetrachlorodibenzo-p-dioxin") +
+  scale_x_continuous(breaks = c(0, (1:4)*(24*7*4)),
+                     labels = c(0, 1:4),
+                     name = "Time (months)") +
+  guides(color = "none",
+         shape = "none") +
+  theme(aspect.ratio = 1,
+        plot.subtitle = element_text(hjust = 0.5))
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "DTXSID2021315_rat_badFit.png"),
+       width = 8,
+       height = 5,
+       units = "in")
+
+my_pk <- pk(data = cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk <- do_fit(my_pk)
+
+plot(my_pk,
+     method = "L-BFGS-B",
+     use_scale_conc = FALSE,
+     log10_C = FALSE,
+     n_interp = 50,
+     print_out = TRUE)[[1]] +
+  labs(subtitle = "3,3',4,4',5-pentachlorobiphenyl (without Dose-Normalized Fit)") +
+  scale_x_continuous(breaks = c(0, (1:14)*(24*7*4)),
+                     labels = c(0, 1:14),
+                     name = "Time (months)") +
+  guides(color = "none",
+         shape = "none") +
+  theme(aspect.ratio = 1,
+        plot.subtitle = element_text(hjust = 0.5))
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "DTXSID3032179_rat_badFit_noDoseNorm.png"),
+       width = 7.5,
+       height = 5,
+       units = "in")
+
+my_pk <- pk(data = cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk <- do_fit(my_pk)
+
+plot(my_pk,
+     method = "L-BFGS-B",
+     use_scale_conc = FALSE,
+     log10_C = FALSE,
+     n_interp = 50,
+     print_out = TRUE)[[1]] +
+  labs(subtitle = "3,3',4,4',5-pentachlorobiphenyl (Dose-Normalized Fit)") +
+  scale_x_continuous(breaks = c(0, (1:14)*(24*7*4)),
+                     labels = c(0, 1:14),
+                     name = "Time (months)") +
+  guides(color = "none",
+         shape = "none") +
+  theme(aspect.ratio = 1,
+        plot.subtitle = element_text(hjust = 0.5))
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "DTXSID3032179_rat_badFit_DoseNorm.png"),
+       width = 7.5,
+       height = 5,
+       units = "in")
+
+my_pk <- pk(data = cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187")) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk <- do_fit(my_pk)
+
+get_data(my_pk) %>% View()
+plot(my_pk,
+     method = "L-BFGS-B",
+     use_scale_conc = TRUE,
+     log10_C = FALSE,
+     n_interp = 100,
+     print_out = TRUE)[[1]] +
+  labs(subtitle = "Tamoxifen") +
+  theme(aspect.ratio = 1,
+        plot.subtitle = element_text(hjust = 0.5))
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "DTXSID1034187_rat_badFit_.png"),
+       width = 7,
+       height = 7,
+       units = "in")
+# Fit is actually ok, but there are lot's of non-Detects in the data
+# There are many doses that are fully non-Detects.
+
+problem_dose <- all_my_data %>%
+  group_by(Chemical, Species, Route, Media, Dose) %>%
+  filter(sum(Detect) == 0) %>%
+  dplyr::select(Chemical, Species, Route, Media, Dose) %>%
+  rename(chemicals_analyzed.dsstox_substance_id = Chemical,
+         subjects.species_harmonized = Species,
+         series.conc_medium_normalized = Media,
+         studies.administration_route_normalized = Route,
+         studies.dose_level_normalized_corrected = Dose) %>%
+  distinct()
+
+problem_dose_DTX <- all_my_data %>%
+  group_by(Chemical, Species, Route, Media, Dose) %>%
+  filter(sum(Detect) == 0) %>%
+  ungroup() %>%
+  pull(1) %>% unique()
+
+# Figure out if the fits improve if we exclude Dose groups that do not have
+# any Detects
+
+my_pk_full <- pk(data = cvt %>%
+                   dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% 
+                                   "DTXSID1034187")) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_full <- do_preprocess(my_pk_full)
+my_pk_full <- do_fit(my_pk_full)
+
+plot(my_pk_full,
+     n_interp = 50,
+     use_scale_conc = TRUE,
+     print_out = TRUE)
+
+my_pk_trimmed <- pk(data = cvt %>%
+                      dplyr::filter(chemicals_analyzed.dsstox_substance_id %in%
+                                      "DTXSID1034187") %>%
+                      anti_join(problem_dose)) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_trimmed <- do_preprocess(my_pk_trimmed)
+my_pk_trimmed <- do_fit(my_pk_trimmed)
+
+AIC(my_pk_full) %>% View("full")
+AIC(my_pk_trimmed) %>% View("trimmed")
+
+get_winning_model(my_pk_full)
+get_winning_model(my_pk_trimmed)
+
+eval_tkstats(my_pk_full) %>% View("full_tkstats")
+eval_tkstats(my_pk_trimmed) %>% View("trimmed_tkstats")
+get_tkstats(my_pk_trimmed) %>% View()
+
+plot(my_pk_trimmed,
+     n_interp = 50,
+     method = "L-BFGS-B",
+     print_out = TRUE)
+
+```

### 2023-07-28 R/pk_methods_plot.R

@@ -77,7 +77,7 @@ plot.pk <- function(obj,
                     drop_nonDetect = FALSE,
                     # Predict/interpolation arguments
                     plot_fit_aes = NULL,
-                    n_interp = 10,
+                    n_interp = 100,
                     fit_limits = NULL,
                     print_out = FALSE,
                     ...){
@@ -294,7 +294,7 @@ plot.pk <- function(obj,
   if (get_status(obj = obj) == 5) {
     interp_data <- newdata
     interp_data <- interp_data %>%
-      mutate(interpolated = map(observations,
+      dplyr::mutate(interpolated = purrr::map(observations,
                                 \(x) {
                                   t_units <- unique(x[["Time_trans.Units"]])
                                   x %>%
@@ -304,15 +304,15 @@ plot.pk <- function(obj,
                                                    Time_trans.Units) %>%
                                     dplyr::mutate(maxTime = max(Time),
                                                   Time.Units = unique(Time_trans.Units)) %>%
-                                    tidyr::uncount(n_interp * maxTime) %>%
+                                    tidyr::uncount(n_interp) %>%
                                     dplyr::group_by(Dose, Route, Media) %>%
                                     dplyr::mutate(Time_trans = (maxTime / (n() - 1)) *
                                                     (row_number() - 1))
                                 }))
     interp_data <- interp_data %>%
       dplyr::select(!!!obj$data_group, interpolated) %>%
-      unnest(cols = c(interpolated)) %>%
-      ungroup()
+      tidyr::unnest(cols = c(interpolated)) %>%
+      dplyr::ungroup()
 
     interp_data <- predict(obj = obj,
                            newdata = interp_data,
@@ -320,36 +320,36 @@ plot.pk <- function(obj,
                            model = model,
                            method = method,
                            exclude = FALSE) %>%
-      group_by(!!!obj$data_group) %>%
-      nest(.key = "predicted")
+      dplyr::group_by(!!!obj$data_group) %>%
+      tidyr::nest(.key = "predicted")
 
-    newdata <- left_join(newdata, interp_data)
+    newdata <- dplyr::left_join(newdata, interp_data)
 
     if (limit_predicted) {
       if (log10_C) {
         newdata <- newdata %>%
-          mutate(predicted = map2(observations, predicted,
+          dplyr::mutate(predicted = purrr::map2(observations, predicted,
                                   \(x, y) {
-                                    filter(y,
+                                    dplyr::filter(y,
[…]

### 2023-08-01 data-raw/batchMode_trial_gpm.Rmd
Updated coef_sd method for batch mode.

@@
 # This is printable into a one file, multipage pdf
-pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_freeY.pdf",
+pdf(file = paste0(Sys.getenv("FIG_DIR"), "plotMethod_freeY.pdf"),
     width = 10,
@@
 
-png(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/examplePlot.png",
-    width = 8,
-    height = 6,
-    units = "in",
-    res = 150,
-    type = "cairo",
-    antialias = "none")
-plot(my_pk, use_scale_conc = TRUE,
-     method = "L-BFGS-B",
-     print_out = TRUE)[[3]]
-dev.off()
-
 ```
@@
 eval_tkstats(my_pk)
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442")
+my_pk <- pk(data = my_predata) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species)) 
+my_pk <- do_fit(my_pk)
+
+my_hess <- coef_sd(my_pk)
+
+my_hess %>%
+  rowwise() %>%
+  mutate(sds = list(sds))
 
@@
 
-ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
+ggsave(paste0(Sys.getenv("FIG_DIR"),
               "NormalizedConcentrations_2023-07-11.png"),
@@
 
-ggsave(paste0("C:/Users/GPADILLA/",
-              "OneDrive - Environmental Protection Agency (EPA)/",
-              "Profile/Documents/Figures/",
+ggsave(paste0(Sys.getenv("FIG_DIR"),
               "ADME_NormalizedTime-NormalizedConcentrations_onlyDetects_2023-07-19.png"),
@@
 
-ggsave(paste0("C:/Users/GPADILLA/",
-              "OneDrive - Environmental Protection Agency (EPA)/",
-              "Profile/Documents/Figures/",
+ggsave(paste0(Sys.getenv("FIG_DIR"),
               "ModelPerformance_vDataVariability_2023-07-20.png"),
@@
 
-ggsave(paste0("C:/Users/GPADILLA/",
-              "OneDrive - Environmental Protection Agency (EPA)/",
-              "Profile/Documents/Figures/",
+ggsave(paste0(Sys.getenv("FIG_DIR"),
               "PredictedObserved_compartmentModels_2023-07-11.png"),
@@
 
-ggsave(paste0("C:/Users/GPADILLA/",
-              "OneDrive - Environmental Protection Agency (EPA)/",
-              "Profile/Documents/Figures/",
+ggsave(paste0(Sys.getenv("FIG_DIR"),
               "OrdersOfMagnitude_2023-07-12.png"),

### 2023-08-01 R/pk_methods_coef_sd.R

@@ -58,74 +58,120 @@ coef_sd.pk <- function(obj,
   method_ok <- check_method(obj = obj, method = method)
   model_ok <- check_model(obj = obj, model = model)
 
-  sapply(model,
-         function(this_model){
-           npar <- attr(obj$fit[[this_model]], "npar")
-           fit_par <- as.matrix(obj$fit[[this_model]][method, 1:npar])
-           #Add any "constant" params
-           if(any(obj$prefit[[this_model]]$par_DF$optimize_param %in% FALSE &
-                  obj$prefit[[this_model]]$par_DF$use_param %in% TRUE)){
-             const_parDF <- subset(obj$prefit[[this_model]]$par_DF,
-                                   optimize_param %in% FALSE &
-                                     use_param %in% TRUE)[c("param_name",
-                                                            "start")]
-             const_par <- const_parDF[["start"]]
-             names(const_par) <- const_parDF[["param_name"]]
-           }else{
-             const_par <- NULL
-           }
+  noptim_params <- obj$prefit$par_DF %>%
+    dplyr::filter(optimize_param == FALSE,
+                  use_param == TRUE) %>%
+    dplyr::pull(param_name) %>%
+    unique()
 
-         t(
-           apply(fit_par,
-                 1,
-                 function(this_par){
-                   #Evaluate the Hessian
-                   numhess <- numDeriv::hessian(func = function(x){
-                     log_likelihood(x,
-                                    const_params = const_par,
-                                    data = obj$data,
-                                    data_sigma_group =obj$prefit$stat_error_model$data_sigma_group,
-                                    modelfun = obj$stat_model[[this_model]]$conc_fun,
-                                    dose_norm = obj$scales$conc$dose_norm,
-                                    log10_trans = obj$scales$conc$log10_trans,
-                                    negative = TRUE,
-                                    force_finite = TRUE)
-                   },
-                   x = this_par,
-                   method = 'Richardson')
+  other_vars <- ggplot2::vars(
+    Value,
+    Value.Units,
+    Time_trans.Units,
+    Conc_trans,
+    Conc_trans.Units,
+    data_sigma_group,
+    exclude
+  )
 
-                   #Invert the Hessian to get the SDs
-                   sds <- tryCatch(diag(solve(numhess)) ^ (1/2),
-                                   error = function(err){
-                                     #if hessian can't be inverted
-                                     if (!suppress.messages) {
-                                       message(paste0("Hessian can't be inverted, ",
[…]

### 2023-08-01 data-raw/batchMode_trial_gpm.Rmd
Added alerts column and table_format argument to coef_sd()

@@
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")
 
@@
 
-my_hess <- coef_sd(my_pk)
+my_hess <- coef_sd(my_pk, table_format = TRUE)
 
 my_hess %>%
-  rowwise() %>%
-  mutate(sds = list(sds))
+  dplyr::mutate(sds_tibble = purrr::map(sds, \(x) as.list(x) %>% as.data.frame)) %>% 
+  tidyr::unnest(sds_tibble) %>%
+  tidyr::pivot_longer(cols = starts_with("sigma_"),
+                      names_to = "error_group",
+                      values_to = "sigma.value_sd") %>%
+  dplyr::filter(!is.na(sigma.value_sd)) %>%
+  dplyr::mutate(coefs_tibble = purrr::map(coefs_vector, \(x) as.list(x) %>% as.data.frame)) %>% 
+  tidyr::unnest(coefs_tibble) %>%
+  tidyr::pivot_longer(cols = starts_with("sigma_"),
+                      names_to = "error_group_value",
+                      values_to = "sigma.value") %>%
+  dplyr::filter(!is.na(sigma.value)) %>%
+  dplyr::filter(paste0(error_group_value, "_sd") == error_group) %>%
+  dplyr::select(-coefs_vector, -sds, -error_group_value) %>%
+  dplyr::relocate(error_group, sigma.value, sigma.value_sd, .after = method) %>%
+  View()
 

### 2023-08-02 data-raw/batchMode_trial_gpm.Rmd
Updated several methods to work with data_groups that were unable to be fit. Some methods ignore these (get_tkstats) while others are supplied NAs (plot)

--- 2023-08-01 data-raw/batchMode_trial_gpm.Rmd
@@
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9021924")
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")
 
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID2021103")
-# Opt params not found ERROR
-# 
-#
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9030258")
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID7030066",
+                                                              "DTXSID0020442",
+                                                              "DTXSID2021315"),
+                subjects.species_harmonized %in% "rat")
 
@@
 ```{r remaining_methods}
-# coef_sd
-
 devtools::load_all()
@@
 
-my_hess <- coef_sd(my_pk)
-
-my_hess %>%
-  rowwise() %>%
-  mutate(sds = list(sds))
+my_hess <- coef_sd(my_pk, table_format = TRUE)
+
+ggplot(inner_join(get_winning_model(my_pk), my_hess),
+       aes(x = Fgutabs,
+           y = V1)) +
+  geom_point() +
+  facet_grid(cols = vars(model))
 

### 2023-08-02 R/pk_methods_predict.R

@@ -55,6 +55,8 @@ predict.pk <- function(obj,
                        type = "conc",
                        exclude = TRUE,
                        use_scale_conc = FALSE,
+                       suppress_messages = TRUE,
+                       include_NAs = FALSE,
                        ...) {
   #ensure that the model has been fitted
   check <- check_required_status(obj = obj,
@@ -75,7 +77,8 @@ predict.pk <- function(obj,
     obj = obj,
     model = model,
     method = method,
-    drop_sigma = TRUE
+    drop_sigma = TRUE,
+    include_NAs = include_NAs
   )
 
   other_vars <- NULL
@@ -164,17 +167,30 @@ predict.pk <- function(obj,
                                   x %>%
                                     dplyr::rowwise() %>%
                                     dplyr::mutate(
-                                      Estimate = sapply(
-                                        coefs_vector,
-                                        FUN = model_fun,
-                                        time = Time_trans,
-                                        dose = ifelse(conc_scale$dose_norm,
-                                                      1, Dose),
-                                        route = Route,
-                                        medium = Media,
-                                        simplify = TRUE,
-                                        USE.NAMES = TRUE
-                                      )
+                                      Estimate = tryCatch(
+                                        sapply(
+                                          coefs_vector,
+                                          FUN = model_fun,
+                                          time = Time_trans,
+                                          dose = ifelse(conc_scale$dose_norm,
+                                                        1, Dose),
+                                          route = Route,
+                                          medium = Media,
+                                          simplify = TRUE,
+                                          USE.NAMES = TRUE
+                                        ),
+                                        error = function(err) {
+                                          if (!suppress_messages) {
+                                            message(paste("Unable to run",
+                                                          model_fun, "for",
+                                                          Chemical, Species,
+                                                          "data grouping.",
+                                                          "Likely an aborted fit,",
+                                                          "it is missing estimated parameters."))
+                                          }
+                                          # Return Value
+                                          NA
+                                        })
                                     )
                                 })) %>%
     tidyr::unnest(predictions)

### 2023-08-09 data-raw/batchMode_trial_gpm.Rmd
Created testing vignette, updated rsq and fold_error for batch mode

@@
 ```
+
+```{r function_connections}
+fw <- mvbutils::foodweb(where = asNamespace("invivoPKfit"),
+                        border = TRUE, cex = 0.6, lwd = 1.5)
+fun_mat <- fw$funmat
+
+mvbutils::foodweb(where = asNamespace("invivoPKfit"),
+                  prune = "bp_test",
+                  border = TRUE, cex = 1, lwd = 1.5)
+
+fun_mat2 <- fun_mat[rowSums(fun_mat) > 0, ]
+
+library(ComplexHeatmap)
+ComplexHeatmap::Heatmap(fun_mat2, row_names_side = "left", column_names_side = "top",
+                        row_names_gp = gpar(fontsize = 10),
+                        column_names_gp = gpar(fontsize = 10),
+                        col = circlize::colorRamp2(c(0, 1), colors = c("white", "green4")),
+                        rect_gp = gpar(col = "black", lwd = 1),
+                        show_row_dend = FALSE,
+                        show_column_dend = FALSE)
+
+fun_mat %>%
+  as_tibble(rownames = NA) %>%
+  rownames_to_column(var = "from") %>%
+  pivot_longer(cols = !from,
+               names_to = "to",
+               values_to = "Call") %>%
+   mutate(
+    from = str_remove(from, pattern = ".pk"),
+    to = str_remove(to, pattern = ".pk")
+  ) %>%
+  filter(from %in% "residuals") %>% View()
+
+fun_mat2 %>%
+  as_tibble(rownames = NA) %>%
+  rownames_to_column(var = "from") %>%
+  pivot_longer(cols = !from,
+               names_to = "to",
+               values_to = "Call") %>%
+  filter(Call != 0) %>% 
+  transmute(
+    from = str_remove(from, pattern = ".pk"),
+    to = str_remove(to, pattern = ".pk")
+  ) %>%
+  filter(from %in% c("residuals"),
+         !(to %in% c("check_model",
+                     "check_method",
+                     "check_newdata",
+                     "check_required_status"))) %>%
+  ggflowchart::ggflowchart(horizontal = TRUE)
+```

### 2023-08-10 data-raw/batchMode_trial_gpm.Rmd
Updating summary method and finalizing the testing vignette.

@@
   length()
+
+# easy fit
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID5020732")
 
@@
 my_pk <- do_preprocess(my_pk)
+plot(my_pk, print_out = TRUE)
 
@@
 mvbutils::foodweb(where = asNamespace("invivoPKfit"),
-                  prune = "bp_test",
+                  prune = "compare_models",
                   border = TRUE, cex = 1, lwd = 1.5)
@@
   ggflowchart::ggflowchart(horizontal = TRUE)
-```
+
+# Random Bits
+# 
+rmse(my_pk) %>%
+  group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
+  mutate(avg_rmse = mean(RMSE)) %>%
+  nest(full_rmse = c(Time, RMSE))
+
+fold_errors(my_pk) %>%
+  group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
+  mutate(avg_FoldErr = mean(Fold_Error),
+         median_FoldErr = median(Fold_Error),
+         within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error)) %>%
+  dplyr::select(Time, Fold_Error, avg_FoldErr, median_FoldErr, within_2fold) %>%
+  nest(full_fold_errors = c(Time, Fold_Error))
+
+```

### 2023-08-10 R/pk_methods_summary.R
Updated coefs method string matching

@@ -147,7 +147,7 @@ summary.pk <- function(obj){
   #things that require pre-fitting (status 4):
   #stat_error_model
   message("Error Model Variables Specified: ")
-  print(as.character(get_error_group(my_pk))[-1])
+  print(as.character(get_error_group(obj))[-1])
   #stat_model par_DFs
   prefit_DF <- obj$prefit$par_DF
 
@@ -156,8 +156,8 @@ summary.pk <- function(obj){
   #things that require fitting (status 5):
   #coefficients
   #get model coefficients
-  outDF <- suppressMessages(left_join(coef(my_pk, include_NAs = TRUE),
-                     coef_sd(my_pk, table_format = TRUE)))
+  outDF <- suppressMessages(left_join(coef(obj, include_NAs = TRUE),
+                     coef_sd(obj, table_format = TRUE)))
 
   #goodness of fit metrics
   aic_all <- suppressMessages(AIC(obj)) # Already includes logLik

### 2023-08-11 data-raw/batchMode_trial_gpm.Rmd
Bug fix for fold error function and downstream summary function

@@
 ```
+
+```{r questions}
+my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+
+pk_summary <- summary(my_pk)
+
+# Q: What do "bad" fits have in common?
+gof_df <- pk_summary$goodness_of_fit %>%
+  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
+  filter(method == "L-BFGS-B") %>%
+  ungroup()
+
+## Find the within_2fold for each data_group
+gof_df %>%
+  dplyr::select(Chemical, Species, full_fold_errors) %>%
+  unnest(full_fold_errors) %>%
+  group_by(Chemical, Species) %>%
+  summarize(within_2fold = sum(
+    Fold_Error >= 0.5 & Fold_Error <= 2, na.rm = TRUE
+    ) / length(na.omit(Fold_Error))) %>%
+  filter(within_2fold == 0) %>% pull(Chemical) %>% unique()
+  arrange(within_2fold) %>%
+  View()
+
+gof_df %>%
+  ggplot(aes(
+    x = log2(avg_FoldErr),
+    y = log10(avg_rmse))) +
+  geom_point() +
+  geom_vline(color = "red3", xintercept = c(-1, 1))
+
+fe_df <- fold_errors(my_pk)
+# Something wrong with the summary method... maybe only use detects?
+fold_errors_all <- fe_df %>%
+  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
+  dplyr::filter(Detect %in% TRUE) %>%
+  dplyr::group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
+  dplyr::mutate(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
+                median_FoldErr = median(Fold_Error, na.rm = TRUE),
+                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error)) %>%
+  dplyr::select(Time, Fold_Error,
+                avg_FoldErr, median_FoldErr, within_2fold) %>%
+  tidyr::nest(full_fold_errors = c(Time, Fold_Error))
+
+fold_errors_all %>% 
+  ggplot(aes(x = within_2fold)) +
+  geom_histogram(binwidth = 0.1) +
+  facet_grid(cols = vars(model))
+
+fe_df %>%
+  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
+  dplyr::filter(Detect %in% TRUE) %>%
+  ggplot(aes(x = log2(Fold_Error))) +
+  xlim(-4, 4) +
+  geom_histogram(binwidth = 0.1) +
+  facet_grid(cols = vars(model))
+
+# Q: What do "great" fits have in common?
+
+# Q: Does the dataset have a bias?
+```

### 2023-08-16 data-raw/batchMode_trial_gpm.Rmd
Plots for R-squared, fold errors, and RMSEs

@@
 my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID8025337")
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9022360")
+
+my_predata <- cvt %>%
   dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
@@
                 studies.administration_route_normalized %in% "iv")
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID1043881",
+                                                              "DTXSID8020541",
+                                                              "DTXSID6034849"),
+                subjects.species_harmonized %in% "rat")
+
 my_predata <- cvt %>%
@@
                                                               "DTXSID2020682"))
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID1034187",
+                                                              "DTXSID2021315",
+                                                              "DTXSID3032179",
+                                                              "DTXSID4020533"))
 
@@
 
+plot(my_pk, method = "L-BFGS-B",
+     n_interp = 50) -> pl
+
 plot(my_pk,
      method = "L-BFGS-B",
+     n_interp = 50,
+
      print_out = TRUE)
@@
 
-fe_df <- fold_errors(my_pk)
+winning_model <- get_winning_model(my_pk)
+fe_df <- fold_errors(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
+# May need to change the use_scale_conc defaults
+r2_df <- rsq(my_pk, method = "L-BFGS-B", use_scale_conc = FALSE) %>%
+  inner_join(winning_model)
+myAIC <- AIC(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
+myRMSE <- rmse(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
+
 # Something wrong with the summary method... maybe only use detects?
 fold_errors_all <- fe_df %>%
-  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
   dplyr::filter(Detect %in% TRUE) %>%
-  dplyr::group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
-  dplyr::mutate(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
+  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
+  dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
                 median_FoldErr = median(Fold_Error, na.rm = TRUE),
-                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error)) %>%
-  dplyr::select(Time, Fold_Error,
-                avg_FoldErr, median_FoldErr, within_2fold) %>%
-  tidyr::nest(full_fold_errors = c(Time, Fold_Error))
+                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error))
+
+myRMSE <- myRMSE %>%
+  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
+  dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE),
+                median_MSE = median(RMSE^2, na.rm = TRUE))
+
+my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE)
+mypl <- ggplot(data = my_df,
+               aes(
+                 x = within_2fold,
+                 y = Rsq,
+                 color = model
+               )) + geom_point() +
+  geom_abline(slope = 1, color = "red4", linetype = "longdash") +
+  scale_color_manual(values = c("#0398FC", "#D68E09", "black")) +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        legend.position = "bottom",
+        legend.title = element_blank())
+ggExtra::ggMarginal(mypl, groupFill = TRUE,
+                    type = "histogram",
+                    xparams = list(binwidth = 0.05),
+                    yparams = list(binwidth = 0.05))
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "R2_within2fold_comparison.png"),
+       plot = ggExtra::ggMarginal(mypl, groupFill = TRUE,
+                    type = "histogram",
+                    xparams = list(binwidth = 0.05),
+                    yparams = list(binwidth = 0.05)),
+       height = 5,
+       width = 5,
+       units = "in")
+
+ggplot(data = rmse(my_pk, method = "L-BFGS-B",
+                   rmse_group = vars(Route, Media, Dose),
+                   use_scale_conc = FALSE) %>%
+         inner_join(winning_model) %>%
+         mutate(RMSE = ifelse(RMSE == 0, 1E-6, RMSE)),
+               aes(
+                 x = log10(RMSE),
+                 color = model,
+                 fill = model
+               )) + 
+  geom_histogram(bins = 100) +
+  # geom_freqpoly(aes(groups = paste(Chemical, Species)),
+  #               color = "black",
+  #               bins = 5) +
+  scale_color_manual(values = c("#0398FC", "#D68E09", "grey10")) +
+  scale_fill_manual(values = c("#0398FC", "#D68E09", "grey10")) +
+  scale_y_continuous(breaks = scales::pretty_breaks()) +
+  facet_grid(rows = vars(model),
+             cols = vars(Route)) +
+  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        strip.background = element_blank(),
+        legend.position = "bottom",
+        legend.title = element_blank())
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RMSEs_winningmodel_LBFGSB_zero1E-6_RouteFacet_notNormalized.png"),
+       height = 4,
+       width = 6,
+       units = "in")
+
+ rmse(my_pk, method = "L-BFGS-B",
+      rmse_group = vars(Route, Media, Dose)) %>%
+   inner_join(get_winning_model(my_pk, method = "L-BFGS-B")) %>%
+   count(model)
+
+rmse(my_pk, method = "L-BFGS-B",
+                   rmse_group = vars(Route, Media, Dose)) %>%
+  inner_join(winning_model) %>%
+  filter(RMSE < 0.01, RMSE > 0.0001, Route == "oral", model == "model_1comp") %>%
+  group_by(Chemical, Species, Route, Media) %>%
+  mutate(group_size = n(),
+         logRMSE = log10(RMSE)) %>%
+  arrange(Chemical, Species, Route, Media, RMSE) %>%
+  View()
 
@@
   facet_grid(cols = vars(model))
+
+ggplot() +
+  geom_histogram(data = fold_errors_all, 
+                 aes(x = within_2fold),
+                 bins = 100) +
+  geom_vline(xintercept = fold_errors_all %>%
+               filter(Chemical == "DTXSID8025337") %>%
+               pull(within_2fold)) +
+  scale_x_log10()
+
+fold_errors_all %>% ungroup() %>%
+  mutate(per_rank = rank(within_2fold)/n()) %>%
+  filter(Chemical == "DTXSID8025337") %>%
+  dplyr::select(-full_fold_errors)
 
@@
 
+# Evaluate at level of Cmax and AUC RMSE
+my_tkstats <- eval_tkstats(my_pk, method = "L-BFGS-B")
+my_tkstats %>%
+  dplyr::select(Chemical, Species, Route, Media, model, method,
+                starts_with("Cmax"),
+                starts_with("AUC")) %>%
+  distinct() %>% 
+  filter(is.finite(Cmax.tkstats), is.finite(AUC_inf.tkstats),
+         is.finite(Cmax.nca), is.finite(AUC_inf.nca)) %>%
+  ggplot(aes(x = Cmax.tkstats/Cmax.nca,
+             y = AUC_inf.tkstats/AUC_inf.nca)) +
+  geom_point() +
+  geom_abline(slope = 1, color = "red4")
+
 # Q: What do "great" fits have in common?

### 2023-08-18 data-raw/batchMode_trial_gpm.Rmd
Rid of get_nca duplicate method and updated tkstats and do_data_info methods to work with this change

@@
 mvbutils::foodweb(where = asNamespace("invivoPKfit"),
-                  prune = "compare_models",
+                  prune = "get_nca",
                   border = TRUE, cex = 1, lwd = 1.5)
@@
 
-winning_model <- get_winning_model(my_pk)
+winning_model <- get_winning_model(my_pk, method = "L-BFGS-B")
 fe_df <- fold_errors(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
@@
   inner_join(winning_model)
-myAIC <- AIC(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
-myRMSE <- rmse(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
+myAIC <- AIC(my_pk, method = "L-BFGS-B") %>%
+  inner_join(winning_model)
+myRMSE <- rmse(my_pk, method = "L-BFGS-B",
+               rmse_group = vars(Route, Media, Dose),
+               use_scale_conc = FALSE) %>% 
+  inner_join(winning_model)
 
@@
 
-myRMSE <- myRMSE %>%
+myRMSE_all <- myRMSE %>%
   dplyr::group_by(!!!my_pk$data_group, model, method) %>%
@@
 
-my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE)
+my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE_all)
 mypl <- ggplot(data = my_df,
@@
                  color = model
-               )) + geom_point() +
+               )) +
+  geom_point() +
   geom_abline(slope = 1, color = "red4", linetype = "longdash") +
   scale_color_manual(values = c("#0398FC", "#D68E09", "black")) +
+  labs(x = "% Fold Error within 2-fold",
+       y = "R-squared value") +
   theme(aspect.ratio = 1,
@@
         legend.position = "bottom",
-        legend.title = element_blank())
-ggExtra::ggMarginal(mypl, groupFill = TRUE,
+        legend.title = element_blank(),
+        legend.key = element_blank())
+panelA_plot <- ggExtra::ggMarginal(mypl, groupFill = TRUE,
                     type = "histogram",
@@
 
-ggplot(data = rmse(my_pk, method = "L-BFGS-B",
-                   rmse_group = vars(Route, Media, Dose),
-                   use_scale_conc = FALSE) %>%
+panelB_plot <- ggplot(data = myRMSE %>%
          inner_join(winning_model) %>%
-         mutate(RMSE = ifelse(RMSE == 0, 1E-6, RMSE)),
+         mutate(RMSE = ifelse(RMSE == 0, NA, RMSE)),
                aes(
@@
   geom_histogram(bins = 100) +
-  # geom_freqpoly(aes(groups = paste(Chemical, Species)),
-  #               color = "black",
-  #               bins = 5) +
+  labs(y = "Count") +
   scale_color_manual(values = c("#0398FC", "#D68E09", "grey10")) +
@@
              cols = vars(Route)) +
-  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+  theme(aspect.ratio = 0.5,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
         panel.background = element_blank(),
@@
        width = 6,
+       units = "in")
+
+cowplot::plot_grid(panelA_plot, panelB_plot, labels = c("A", "B"))
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "CombinedPlot_Rsquared_RMSE.png"),
+       height = 5,
+       width = 7.45,
+       bg = "white",
        units = "in")
@@
 ```
+
+```{r ALL_fitting_choices}
+# This chunk is to run all the options through a
+# standard pipeline that calculates RMSE for Cmax and AUC_inf
+# for the Chemical Species Route Media grouping...
+
+# Types of Choices:
+## Dose Normalized
+## Log10 transform
+## Scale time
+
+# Pooled
+my_pk_000p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_100p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_110p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_111p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_010p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_011p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_001p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_101p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+## Do fits
+my_pk_000p <- do_fit(my_pk_000p)
+my_pk_100p <- do_fit(my_pk_100p)
+my_pk_110p <- do_fit(my_pk_110p)
+my_pk_111p <- do_fit(my_pk_111p)
+my_pk_010p <- do_fit(my_pk_010p)
+my_pk_011p <- do_fit(my_pk_011p)
+my_pk_001p <- do_fit(my_pk_001p)
+my_pk_101p <- do_fit(my_pk_101p)
+
+my_pk_111p <- do_data_info(my_pk_111p)
+my_nca1 <- get_nca(my_pk_111p)
+
+# Joint
+my_pk_000j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_100j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_110j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_111j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_010j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_011j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_001j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_101j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+## Do fits
+my_pk_000j <- do_fit(my_pk_000j)
+my_pk_100j <- do_fit(my_pk_100j)
+my_pk_110j <- do_fit(my_pk_110j)
+my_pk_111j <- do_fit(my_pk_111j)
+my_pk_010j <- do_fit(my_pk_010j)
+my_pk_011j <- do_fit(my_pk_011j)
+my_pk_001j <- do_fit(my_pk_001j)
+my_pk_101j <- do_fit(my_pk_101j)
+
+```
+
+```{r Evaluating_Choices}
+# Evaluation
+# Current: my_pk_111p
+
+# Number of model fits
+winning_model <- get_winning_model(my_pk_111p)
+winning_model %>%
+  group_by(method, model) %>%
+  count() %>%
+  mutate(Options = "111 Pooled") %>%
+  clipr::write_clip(col.names = FALSE)
+
+clipr::clear_clip()
+
+# TKstats/Cmax/AUC analysis... combined!
+final_tkstats <- eval_tkstats(my_pk_111p) %>%
+  mutate(Options = "111 Pooled")
+# Will need to evaluate the best model + method + options
+
+# RMSEs for Cmax and AUC_inf
+final_tkstats %>%
+  dplyr::select(Options,
+                Chemical, Species,
+                Route, Media, Reference,
+                method, model,
+                starts_with("Cmax"),
+                starts_with("AUC_inf")) %>%
+  rowwise() %>%
+  mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
+         SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
+  filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
+  group_by(Options, method, model) %>%
+  summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
+                             na.rm = FALSE)),
+            RMSE_AUC = sqrt(mean(SE_AUC_inf,
+                            na.rm = FALSE))) %>%
+  clipr::write_clip(col.names = FALSE)
+
+clipr::clear_clip()
+
+# Other metrics (Rsq, Fold-Error, prediction RMSE)
+# May need to change the use_scale_conc defaults
+r2_df <- rsq(my_pk_111p, use_scale_conc = FALSE) %>%
+  inner_join(winning_model)
+myAIC <- AIC(my_pk_111p) %>%
+  inner_join(winning_model)
+fold_errors_all <- fold_errors(my_pk_111p) %>%
+  inner_join(winning_model) %>%
+  dplyr::filter(Detect %in% TRUE) %>%
+  dplyr::group_by(!!!my_pk_111p$data_group, model, method) %>%
+  dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
+                median_FoldErr = median(Fold_Error, na.rm = TRUE),
+                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error))
+
+myRMSE_all <- rmse(my_pk_111p,
+               rmse_group = vars(Route, Media, Dose),
+               use_scale_conc = FALSE) %>% 
+  inner_join(winning_model) %>%
+  dplyr::group_by(!!!my_pk_111p$data_group, model, method) %>%
+  dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE),
+                median_MSE = median(RMSE^2, na.rm = TRUE))
+
+my_df <- left_join(fold_errors_all, r2_df) %>%
+  inner_join(myAIC) %>%
+  inner_join(myRMSE_all) %>%
+  mutate(Options = "111 Pooled", .before = Chemical)
+
+my_df %>% clipr::write_clip(col.names = FALSE)
+
+clipr::clear_clip()
+
+hist(my_df$within_2fold)
+
+rm(my_pk_111p)
+gc()
+
+# Last one was 111p
+```

### 2023-08-23 data-raw/batchMode_trial_gpm.Rmd
New parallelized tidy version of do_fit

--- 2023-08-16 data-raw/batchMode_trial_gpm.Rmd
@@
   dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9022360")
+
+# Reasonable fits... multiple species
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
+                                                              "DTXSID8025337"))
 
@@
   facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = TRUE) +
   settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
@@
 
-my_pk <- do_prefit(my_pk)
-
+my_pk <- do_prefit(my_pk) # needs reframe somewhere
+# Timing for normal fit sapply
+{
+  start_t <- Sys.time()
+  normal_fit <- do_fit(my_pk)
+  round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
+} 
+# Timing for multidplyr
+{
+  start_t <- Sys.time()
+  party_fit <- do_fit(my_pk)
+  round(Sys.time() - start_t, 3) # 2.514min (5 data_groups)
+}
 my_pk <- do_fit(my_pk)
@@
      method = "L-BFGS-B",
-     n_interp = 50,
-
+     n_interp = 20,
      print_out = TRUE)
@@
         strip.background = element_blank(),
-        legend.position = "bottom",
+        legend.position = "none",
         legend.title = element_blank())
@@
 ```
+
+This chunk is to run all the options through a
+standard pipeline that calculates RMSE for Cmax and AUC_inf
+for the Chemical Species Route Media grouping...
+
+```{r pooled_fitting_choices}
+# Types of Choices:
+## Dose Normalized
+## Log10 transform
+## Scale time
+
+# Pooled
+my_pk_000p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_100p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_110p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_111p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_010p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_011p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_001p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_101p <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+```
+
+```{r joint_fitting_choices}
+# Joint
+my_pk_000j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_100j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_110j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_111j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_010j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_011j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_001j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_101j <- pk(data = cvt) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+```
+
+```{r}
+## Do fits
+my_pk_000p <- do_fit(my_pk_000p)
+my_pk_100p <- do_fit(my_pk_100p)
+my_pk_110p <- do_fit(my_pk_110p)
+my_pk_111p <- do_fit(my_pk_111p)
+my_pk_010p <- do_fit(my_pk_010p)
+my_pk_011p <- do_fit(my_pk_011p)
+my_pk_001p <- do_fit(my_pk_001p)
+my_pk_101p <- do_fit(my_pk_101p)
+
+## Do fits
+my_pk_000j <- do_fit(my_pk_000j)
+my_pk_100j <- do_fit(my_pk_100j)
+my_pk_110j <- do_fit(my_pk_110j)
+my_pk_111j <- do_fit(my_pk_111j)
+my_pk_010j <- do_fit(my_pk_010j)
+my_pk_011j <- do_fit(my_pk_011j)
+my_pk_001j <- do_fit(my_pk_001j)
+my_pk_101j <- do_fit(my_pk_101j)
+```
+
+```{r Evaluating_Choices}
+# Evaluation
+# Current: my_pk_111p
+
+get_choices <- function(obj, PJ = "Pooled") {
+  dose_norm <- obj$scales$conc$dose_norm
+  log10_norm <- obj$scales$conc$log10_trans
+  time_scale <- ifelse(obj$scales$time$new_units == "identity", FALSE, TRUE)
+
+  my_choices <- paste0(dose_norm+0,
+                       log10_norm+0,
+                       time_scale+0,
+                       " ", PJ)
+  return(my_choices)
+}
+
+# Write into package
+evaluate_choices <- function(obj) {
+  pk_name <- get_choices(obj)
+
+  cli::cli_progress_step("Winning Model...")
+  # Wide winning model
+  suppressMessages({
+    winning_model <- get_winning_model(obj = obj) %>%
+      group_by(method, model) %>%
+      count() %>%
+      pivot_wider(names_from = model, values_from = n) %>%
+      mutate(Options = pk_name)
+  })
+
+  cli::cli_progress_step("Cmax and AUC_inf RMSEs...")
+  # Cmax and AUC_inf RMSEs
+  suppressMessages({
+    RMSE_eval <- eval_tkstats(obj = obj) %>%
+    mutate(Options = pk_name) %>%
+    dplyr::select(Options,
+                Chemical, Species,
+                Route, Media, Reference,
+                method, model,
+                starts_with("Cmax"),
+                starts_with("AUC_inf")) %>%
+  rowwise() %>%
+  mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
+         SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
+  filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
+  group_by(Options, method) %>%
+  summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
+                             na.rm = FALSE)) %>% signif(digits = 4),
+            RMSE_AUC = sqrt(mean(SE_AUC_inf,
+                            na.rm = FALSE)) %>% signif(digits = 4))
+  })
+
+  cli::cli_progress_step("More detailed metrics...")
+  # Other metrics (detailed)
+  suppressMessages({
+    r2_df <- rsq(obj, use_scale_conc = FALSE) %>%
+    inner_join(winning_model)
+  myAIC <- AIC(obj) %>%
+    inner_join(winning_model)
+  fold_errors_all <- fold_errors(obj) %>%
+    inner_join(winning_model) %>%
+    dplyr::filter(Detect %in% TRUE) %>%
+    dplyr::group_by(!!!obj$data_group, model, method) %>%
+    dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE) %>%
+                       signif(digits = 4),
+                     median_FoldErr = median(Fold_Error, na.rm = TRUE) %>%
+                       signif(digits = 4),
+                     within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error) %>%
+                       signif(digits = 4))
+
+  myRMSE_all <- rmse(obj,
+                     rmse_group = vars(Route, Media, Dose),
+                     use_scale_conc = FALSE) %>% 
+    inner_join(winning_model) %>%
+    dplyr::group_by(!!!obj$data_group, model, method) %>%
+    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
+                       signif(digits = 4),
+                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
+                       signif(digits = 4))
+
+  my_df <- left_join(fold_errors_all, r2_df) %>%
+    inner_join(myAIC) %>%
+    inner_join(myRMSE_all) %>%
+    mutate(Options = pk_name, .before = Chemical)
+
+  full_list <- list(winning_model, RMSE_eval, my_df)
+  })
+
+  return(full_list)
+}
+gc()
+
+my_pk_000p <- evaluate_choices(my_pk_000p) # Done
+my_pk_100p <- evaluate_choices(my_pk_100p) # Done
+my_pk_110p <- do_fit(my_pk_110p) %>% evaluate_choices() # Done
+my_pk_111p <- do_fit(my_pk_111p) %>% evaluate_choices() # Done
+my_pk_010p <- do_fit(my_pk_010p) %>% evaluate_choices() # Done
+my_pk_011p <- do_fit(my_pk_011p) %>% evaluate_choices() # Done (took 1.807 hrs)
+my_pk_001p <- do_fit(my_pk_001p) %>% evaluate_choices() # Done
+
+my_pk_101p <- do_data_info(my_pk_101p) # This took 13 min
+
+my_pk_101p <- do_fit(my_pk_101p) %>% evaluate_choices()
+
+# Run after each evaluation
+# initialization (only run once)
+winning_model_final <- NULL
+rmse_summary <- NULL
+detail_stats <- NULL
+
+# Run all at once
+{
+current_pk <- my_pk_101p # Define current evaluated pk object here
+winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])
+rmse_summary <- bind_rows(rmse_summary, current_pk[[2]])
+detail_stats <- bind_rows(detail_stats, current_pk[[3]])
+rm(current_pk)
+gc()
+}
+
+# For copy + pasting into Excel workbook
+winning_model_final %>% clipr::write_clip(col.names = FALSE)
+clipr::clear_clip()
+rmse_summary %>% clipr::write_clip(col.names = FALSE)
+clipr::clear_clip()
+detail_stats %>% clipr::write_clip(col.names = FALSE)
+clipr::clear_clip()
+gc()
+```

### 2023-08-24 data-raw/batchMode_trial_gpm.Rmd
Added explicit dplyr::n() call to fit_group so it works with multidplyr parallelization and adding explicit definitions

@@
 devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
+library(multidplyr)
 tidyverse_conflicts()
@@
 # Write into package
-evaluate_choices <- function(obj) {
-  pk_name <- get_choices(obj)
+evaluate_choices <- function(obj, PJ = "Pooled") {
+  pk_name <- get_choices(obj, PJ = PJ)
 
@@
 
-my_pk_101p <- do_fit(my_pk_101p) %>% evaluate_choices()
+my_pk_101p <- do_fit(my_pk_101p) %>% evaluate_choices() # Done
+
+my_pk_000j <- do_prefit(my_pk_000j)
+my_pk_000j <- do_fit(my_pk_000j) %>% evaluate_choices() # Done (took 16 minutes)
+# WOW! A 2-3X speedup from the previous sapply() implementation
+my_pk_100j <- do_fit(my_pk_100j) %>% evaluate_choices(PJ = "Joint") 
+my_pk_110j <- do_fit(my_pk_110j) %>% evaluate_choices()
+my_pk_111j <- do_fit(my_pk_111j) %>% evaluate_choices()
+my_pk_010j <- do_fit(my_pk_010j) %>% evaluate_choices()
+my_pk_011j <- do_fit(my_pk_011j) %>% evaluate_choices()
+my_pk_001j <- do_fit(my_pk_001j) %>% evaluate_choices()
+my_pk_101j <- do_fit(my_pk_101j) %>% evaluate_choices()
 
@@
 {
-current_pk <- my_pk_101p # Define current evaluated pk object here
+current_pk <- my_pk_000j # Define current evaluated pk object here
 winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])

### 2023-09-07 data-raw/batchMode_trial_gpm.Rmd
Updating changes to data analysis vignette, requires cleaning in the near future.

--- 2023-08-23 data-raw/batchMode_trial_gpm.Rmd
@@
 
+# A PFAS chemical?
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3031860")
+# All long lived chemicals
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c(long_lived_chem[3:5],
+                                                              "DTXSID0020442"))
+do_preprocess(my_pk_001p) %>% get_data() %>% filter(Time.Units != Time_trans.Units) %>%
+  pull(Chemical) %>% unique() -> long_lived_chem
+
 # Reasonable fits... multiple species
@@
   dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
-                                                              "DTXSID8025337"))
+                                                              "DTXSID2039336"))
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% (over1Ref %>%
+                                                               pull(Chemical)),
+                subjects.species_harmonized %in% "rat")
 
@@
 my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9030258")
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID4023917")
 
@@
   facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE,
-                      suppress.messages = TRUE) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = FALSE) +
   settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
   scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
+  scale_time(new_units = "auto") +
   # stat_model() + 
@@
 my_pk <- do_preprocess(my_pk)
-plot(my_pk, print_out = TRUE)
 
@@
   start_t <- Sys.time()
-  normal_fit <- do_fit(my_pk)
+  my_pk <- do_fit(my_pk, n_cores = 6)
   round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
 }
-# Timing for multidplyr
-{
-  start_t <- Sys.time()
-  party_fit <- do_fit(my_pk)
-  round(Sys.time() - start_t, 3) # 2.514min (5 data_groups)
-}
-my_pk <- do_fit(my_pk)
+# my_pk <- do_fit(my_pk)
 
 plot(my_pk, method = "L-BFGS-B",
-     n_interp = 50) -> pl
+     n_interp = 12) -> pl
 
@@
 my_pk <- do_fit(my_pk)
-```
-
-Batch mode works! Now, I have updated the `coef`, `predict`, `rmse`, and `residuals`
-methods.
-
-```{r after_method_update}
-# Changed pk_methods coef() and predict() to those above
-# Ran the following after making the pk object:
-devtools::load_all()
-all_my_data <- my_pk$data # following the full dataset to prefit
-my_pk$data %>% filter(Chemical == "DTXSID2021103")
-
-my_coefs_update <- coef(my_pk, drop_sigma = TRUE)
-my_pred_update <- predict(my_pk,
-                          exclude = TRUE, # add the "exclude" column to output
-                          use_scale_conc = TRUE)
-
-predict(my_pk,
-        exclude = TRUE, # add the "exclude" column to output
-        use_scale_conc = TRUE)
-
-my_pred2 <- predict(my_pk,
-                    newdata = data.frame(Chemical = "DTXSID2021731",
-                                         Species = "rat",
-                                         Route = "iv",
-                                         Media = "plasma",
-                                         Dose = 20,
-                                         Time = 1.6,
-                                         Time.Units = "hours"),
-                    exclude = FALSE,
-                    use_scale_conc = FALSE)
-
-rmse(my_pk) %>% View("RMSE_test")
-residuals(my_pk) %>% View("Residuals_test")
-
-```
-
-```{r plotting_method}
-
-plot(my_pk, use_scale_conc = TRUE,
-     print_out = TRUE, log10_C = FALSE)
-
-my_plot <- plot(my_pk, use_scale_conc = TRUE)
-
-# This is printable into a one file, multipage pdf
-pdf(file = paste0(Sys.getenv("FIG_DIR"), "plotMethod_freeY.pdf"),
-    width = 10,
-    height = 8)
-plot(my_pk, use_scale_conc = TRUE,
-     print_out = TRUE)
-dev.off()
-
-```
-
-```{r get_tkstats_logLik_methods}
-my_tkstats <- get_tkstats(my_pk)
-
-names(my_tkstats)
-my_tkstats
-
-my_logLike_update <- logLik(my_pk)
-
-```
-
-```{r remaining_methods}
-devtools::load_all()
-AIC(my_pk2) %>% View()
-BIC(my_pk)
-
-get_winning_model(my_pk)
-eval_tkstats(my_pk)
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442")
-my_pk <- pk(data = my_predata) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) 
-my_pk <- do_fit(my_pk)
-
-my_hess <- coef_sd(my_pk, table_format = TRUE)
-
-ggplot(inner_join(get_winning_model(my_pk), my_hess),
-       aes(x = Fgutabs,
-           y = V1)) +
-  geom_point() +
-  facet_grid(cols = vars(model))
+
+my_df %>%
+  ggplot(aes(x = maxT/(24)
+             )) +
+  geom_histogram(fill = "grey5") +
+  scale_x_log10() +
+  scale_y_continuous(expand = c(0, 0), limits = c(0, 30)) +
+  expand_limits(y = 0) +
+  labs(x = "Day of final Timepoint",
+       y = "Count") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text = element_text(face = "bold"))
 
@@
 # after fitting pk object for all cvt objects
-# saveRDS(my_pk, file = "data-raw/all_cvt_pk.rds")
+# saveRDS(my_pk_100p, file = "data-raw/all_cvt_pk.rds")
 # saveRDS(my_pk, file = "data-raw/all_cvt_pk_JOINT.rds")
@@
 
+This next set of code is a preliminary attempt at summarizing the TK statistics
+for Pooled and Joint analyses.
+
 ```{r update_eval_tkstats}
 devtools::load_all()
-my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+my_pk <- readRDS("data-raw/all_cvt_pk.rds") # This no longer works somehow
 my_eval <- eval_tkstats(my_pk)
@@
 ```
+
+Here I introduce the notion whether the data is variable compared across time.
 
@@
 
-```{r log10_Pooled}
-devtools::load_all()
-
-my_log10pk <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) 
-# Add Reference for Joint Analysis
-
-my_log10pk <- do_preprocess(my_log10pk)
-
-my_log10pk <- do_data_info(my_log10pk)
-
-my_log10pk <- do_prefit(my_log10pk)
-
-my_log10pk <- do_fit(my_log10pk)
-# saveRDS(my_log10pk, file = "data-raw/all_cvt_pklog10.rds")
-
-my_AIC <- AIC(my_log10pk)
-my_tkstats <- get_tkstats(my_log10pk)
-
-my_AIC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "bobyqa") %>%
-  ungroup() %>%
-  count(model)
-# model_1comp 69
-# model_2comp 35
-# model_flat   7
-
-my_AIC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>%
-  ungroup() %>%
-  count(model)
-# model_1comp 77
-# model_2comp 25
-# model_flat   9
-
-# To give summary RMSEs of Cmax and AUC...
-my_eval <- eval_tkstats(my_log10pk) %>%
-  group_by(method, model, .add = TRUE) %>%
-  ungroup(Reference) %>%
-  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
-                                             na.rm = TRUE)^2)),
-            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
-                                          na.rm = TRUE)^2)),
-            .groups = "keep")
-
-my_eval %>%
-  group_by(method) %>%
-  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
-            AUC_mediRMSE = median(AUC_inf_RMSE),
-            AUC_sdRMSE = sd(AUC_inf_RMSE),
-            Cmax_meanRMSE = mean(Cmax_RMSE),
-            Cmax_mediRMSE = median(Cmax_RMSE),
-            Cmax_sdRMSE = sd(Cmax_RMSE)) %>% as.data.frame()
-
-```
-
-```{r log10_Joint}
-my_log10pk <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
-# Add Reference for Joint Analysis
-
-my_log10pk <- do_preprocess(my_log10pk)
-
-my_log10pk <- do_data_info(my_log10pk)
-
-my_log10pk <- do_prefit(my_log10pk)
-
-my_log10pk <- do_fit(my_log10pk)
-
-my_AIC <- AIC(my_log10pk)
-
-my_AIC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "bobyqa") %>%
-  ungroup() %>%
-  count(model)
-# model_1comp 56
-# model_2comp 54
-# model_flat  1
-
-my_AIC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>%
-  ungroup() %>%
-  count(model)
-# model_1comp 63
-# model_2comp 48
-# model_flat  0
-
-my_eval <- eval_tkstats(my_log10pk)
-
-# To give summary RMSEs of Cmax and AUC...
-my_eval <- my_eval %>%
-  group_by(method, model, .add = TRUE) %>%
-  ungroup(Reference) %>%
-  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
-                                             na.rm = TRUE)^2)),
-            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
-                                          na.rm = TRUE)^2)),
-            .groups = "keep")
-
-my_eval %>%
-  group_by(method) %>%
-  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
-            AUC_mediRMSE = median(AUC_inf_RMSE),
-            AUC_sdRMSE = sd(AUC_inf_RMSE),
-            Cmax_meanRMSE = mean(Cmax_RMSE),
-            Cmax_mediRMSE = median(Cmax_RMSE),
-            Cmax_sdRMSE = sd(Cmax_RMSE)) %>%
-  as.data.frame()
-
-```
+This is another preliminary attempt to summarize RMSEs of each fit
+(Predictions - Observed Values)
 
@@
 ```
+
+Here I explore some bad-fitting chemicals using the dose-normalized pooled analysis.
 
@@
 
+# PFAS Chemical
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID80108992")
+my_pk <- pk(data = my_predata) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species)) 
+my_pk <- do_fit(my_pk)
+plot(my_pk, n_interp = 20,
+     method = "L-BFGS-B", print_out = TRUE)
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "DTXSID80108992_noTimeScaling.png"),
+       height = 3,
+       width = 5.5,
+       units = "in")
+# Time-scaled!
+my_pk <- pk(data = my_predata) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species)) 
+my_pk <- do_data_info(my_pk)
+my_pk <- do_fit(my_pk)
+dplot(my_pk, n_interp = 20,
+     method = "L-BFGS-B", print_out = TRUE)
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "PerluorodeconoicAcid_noTimeScaling.png"),
+       height = 4,
+       width = 5.5,
+       units = "in")
+
 ```
+
+I try to find the connections between functions in _invivoPKfit_ to best understand
+and represent the structure of the package.
 
@@
 mvbutils::foodweb(where = asNamespace("invivoPKfit"),
-                  prune = "get_nca",
+                  prune = "get_tkstats",
+                  # descendents = FALSE,
+                  ancestors = FALSE,
                   border = TRUE, cex = 1, lwd = 1.5)
+
+# Predict dependents: rmse, residuals, rsq, calc_auc, fold_errors, plot
+# Coef dependents: calc_auc, predict, get_tkstats, summary,log_Lik, coef_sd
 
@@
 
-# Random Bits
-# 
-rmse(my_pk) %>%
-  group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
-  mutate(avg_rmse = mean(RMSE)) %>%
-  nest(full_rmse = c(Time, RMSE))
-
-fold_errors(my_pk) %>%
-  group_by(!!!my_pk$data_group, model, method, Route, Media, Dose) %>%
-  mutate(avg_FoldErr = mean(Fold_Error),
-         median_FoldErr = median(Fold_Error),
-         within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error)) %>%
-  dplyr::select(Time, Fold_Error, avg_FoldErr, median_FoldErr, within_2fold) %>%
-  nest(full_fold_errors = c(Time, Fold_Error))
-
 ```
+
+## Q & A
+
+Here I try asking the remaining questions for the paper/presentation.
 
@@
 my_pk <- readRDS("data-raw/all_cvt_pk.rds")
-
-pk_summary <- summary(my_pk)
+pk_summary <- summary(my_pk) # Testing the summary functionality
 
@@
 
-```{r}
-## Do fits
-my_pk_000p <- do_fit(my_pk_000p)
-my_pk_100p <- do_fit(my_pk_100p)
-my_pk_110p <- do_fit(my_pk_110p)
-my_pk_111p <- do_fit(my_pk_111p)
-my_pk_010p <- do_fit(my_pk_010p)
-my_pk_011p <- do_fit(my_pk_011p)
-my_pk_001p <- do_fit(my_pk_001p)
-my_pk_101p <- do_fit(my_pk_101p)
-
-## Do fits
-my_pk_000j <- do_fit(my_pk_000j)
-my_pk_100j <- do_fit(my_pk_100j)
-my_pk_110j <- do_fit(my_pk_110j)
-my_pk_111j <- do_fit(my_pk_111j)
-my_pk_010j <- do_fit(my_pk_010j)
-my_pk_011j <- do_fit(my_pk_011j)
-my_pk_001j <- do_fit(my_pk_001j)
-my_pk_101j <- do_fit(my_pk_101j)
-```
+Here I evaluate the choices of the fits in a streamlined way.
 
@@
                 starts_with("Cmax"),
-                starts_with("AUC_inf")) %>%
+                starts_with("AUC_")) %>%
+      filter(abs(AUC_inf.nca / AUC_tlast.nca) < 10,
+             is.finite(AUC_inf.nca), is.finite(AUC_inf.tkstats),
+             AUC_inf.nca > 0, AUC_inf.tkstats > 0) %>%
       rowwise() %>%
@@
     inner_join(myRMSE_all) %>%
-    mutate(Options = pk_name, .before = Chemical)
+    mutate(Options = pk_name, .before = Chemical) %>%
+    dplyr::select(!c("model_1comp", "model_2comp", "model_flat"))
 
@@
 
-my_pk_000p <- evaluate_choices(my_pk_000p) # Done
-my_pk_100p <- evaluate_choices(my_pk_100p) # Done
-my_pk_110p <- do_fit(my_pk_110p) %>% evaluate_choices() # Done
-my_pk_111p <- do_fit(my_pk_111p) %>% evaluate_choices() # Done
-my_pk_010p <- do_fit(my_pk_010p) %>% evaluate_choices() # Done
-my_pk_011p <- do_fit(my_pk_011p) %>% evaluate_choices() # Done (took 1.807 hrs)
-my_pk_001p <- do_fit(my_pk_001p) %>% evaluate_choices() # Done
-
-my_pk_101p <- do_data_info(my_pk_101p) # This took 13 min
-
-my_pk_101p <- do_fit(my_pk_101p) %>% evaluate_choices()
+my_pk_000p <- do_fit(my_pk_000p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_100p <- do_fit(my_pk_100p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_110p <- do_fit(my_pk_110p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_111p <- do_fit(my_pk_111p, n_cores = 12) #%>% evaluate_choices() # Done
+my_pk_010p <- do_fit(my_pk_010p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_011p <- do_fit(my_pk_011p, n_cores = 8) %>% evaluate_choices() # Done 
+my_pk_001p <- do_fit(my_pk_001p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_101p <- do_fit(my_pk_101p, n_cores = 8) %>% evaluate_choices() # Done
+
+my_pk_000j <- do_fit(my_pk_000j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done 
+my_pk_100j <- do_fit(my_pk_100j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_110j <- do_fit(my_pk_110j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_111j <- do_fit(my_pk_111j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_010j <- do_fit(my_pk_010j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_011j <- do_fit(my_pk_011j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done 
+my_pk_001j <- do_fit(my_pk_001j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done 
+my_pk_101j <- do_fit(my_pk_101j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
 
@@
 # initialization (only run once)
+{
 winning_model_final <- NULL
@@
 detail_stats <- NULL
+start_time <- Sys.time()
+}
 
@@
 {
-current_pk <- my_pk_101p # Define current evaluated pk object here
+current_pk <- my_pk_111p # Define current evaluated pk object here
 winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])
@@
 gc()
+
+### Workshopping
+evaluated_tkstats %>%
+  mutate(Options = "Pooled") %>%
+    dplyr::select(Options,
+                Chemical, Species,
+                Route, Media, Reference,
+                method, model,
+                starts_with("Cmax"),
+                starts_with("AUC_")) %>%
+      filter(abs(AUC_inf.nca / AUC_tlast.nca) < 10,
+             is.finite(AUC_inf.nca), is.finite(AUC_inf.tkstats),
+             AUC_inf.nca > 0, AUC_inf.tkstats > 0) %>%
+      rowwise() %>%
+      mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
+             SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
+      filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
+  dplyr::select(Chemical, Species, Route, Media, method, Options,
+                SE_Cmax, SE_AUC_inf) %>%
+  distinct() %>%
+  group_by(Options, method) %>%
+      summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
+                                      na.rm = FALSE)) %>% signif(digits = 4),
+                RMSE_AUC = sqrt(mean(SE_AUC_inf,
+                                     na.rm = FALSE)) %>% signif(digits = 4))
+  View()
+
+eval_tkstats(obj = my_pk_111p) %>%
+  filter(Chemical == "DTXSID0021125") %>%
+    mutate(Options = "Pooled") %>%
+    dplyr::select(Options,
+                Chemical, Species,
+                Route, Media, Reference,
+                method, model,
+                starts_with("Cmax"),
+                starts_with("AUC_")) %>%
+      filter(abs(AUC_inf.nca / AUC_tlast.nca) < 10,
+             is.finite(AUC_inf.nca), is.finite(AUC_inf.tkstats),
+             AUC_inf.nca > 0, AUC_inf.tkstats > 0) %>%
+      rowwise() %>%
+      mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
+             SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
+      filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
+      group_by(Options, method) %>%
+      summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
+                                      na.rm = FALSE)) %>% signif(digits = 4),
+                RMSE_AUC = sqrt(mean(SE_AUC_inf,
+                                     na.rm = FALSE)) %>% signif(digits = 4))
+
 ```
+
+```{r Plotting_Summary}
+
+readxl::excel_sheets("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/DataSummary_8_18_2023.xlsx") # Predictions Evaluation
+
+preval <- readxl::read_xlsx(paste("C:/Users/GPADILLA",
+                                  "OneDrive - Environmental Protection Agency (EPA)",
+                                  "DataSummary_8_18_2023.xlsx",
+                                  sep = "/"),
+                            sheet = "Predictions Evaluation") %>%
+  dplyr::select(-model_1comp, -model_2comp, -model_flat) %>%
+  distinct()
+
+library(broom)
+
+filtered_preval <- preval %>%
+  filter(if_all(where(is.numeric), is.finite))
+
+filtered_preval %>%
+  dplyr::select(Chemical, Species, model, method, Options, Rsq) %>%
+  mutate(time_scaled = ifelse(str_detect(Options,
+                                         pattern = "^\\d\\d1"),
+                              "Time_Scaled",
+                              "notTime_Scaled"),
+         Options = str_remove(Options, pattern = "\\d(?=[:blank:])")) %>%
+  # dplyr::select(-Options) %>%
+  pivot_wider(names_from = time_scaled, values_from = Rsq) %>% 
+  mutate(differ = Time_Scaled - notTime_Scaled) %>%
+  View()
+
+fit <- lm(within_2fold ~ avg_FoldErr, data = filtered_preval)
+summary(fit)
+tidy(fit)
+head(augment(fit))
+glance(fit)
+
+filtered_preval %>% group_by(Options) %>%
+  nest() %>%
+  mutate(fit = map(data, \(x) {
+    lm(within_2fold ~ avg_FoldErr, data = x)
+    }),
+    tidy_fit = map(fit, tidy)) %>%
+  unnest(tidy_fit) %>%
+  dplyr::select(Options, term, estimate, std.error, statistic) %>%
+  View()
+
+Cmax_AUC <- readxl::read_xlsx(paste("C:/Users/GPADILLA",
+                                  "OneDrive - Environmental Protection Agency (EPA)",
+                                  "DataSummary_8_18_2023.xlsx",
+                                  sep = "/"),
+                            sheet = "Cmax and AUC_inf Evaluation") %>%
+  dplyr::select(1:4) %>%
+  distinct()
+
+Cmax_AUC %>%
+  mutate(DFO = rank(sqrt(RMSE_Cmax^2 + signif(RMSE_AUC, 5)^2)),
+         OLS = rank(abs(RMSE_Cmax + signif(RMSE_AUC, 5))/sqrt(2))) %>%
+  #filter(DFO < 11 | OLS < 11) %>%
+  arrange(DFO, OLS) %>%
+  dplyr::select(-RMSE_Cmax, -RMSE_AUC) %>% View()
+  clipr::write_clip()
+
+Cmax_AUC %>%
+  mutate(DFO = rank(sqrt(RMSE_Cmax^2 + RMSE_AUC^2)),
+         OLS = rank(abs(RMSE_Cmax + RMSE_AUC)/sqrt(2))) %>%
+  ggplot(aes(
+    x = DFO,
+    y = OLS,
+    fill = Options
+  )) + geom_point(shape = 21)
+
+```
+
+Here I do a bit of benchmarking for the parallel-ized version of do_fit
+
+```{r do_fit-benchmarking}
+
+# Set to 
+single_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 1), times = 3)
+four_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 4), times = 3)
+# eight_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 8), times = 3) # Only for four_DG
+ten_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 10), times = 3)
+fourteen_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 14), times = 3)
+
+single_core
+four_core
+# eight_core
+ten_core
+fourteen_core
+
+four_DG <- bind_rows(summary(single_core),
+                     summary(four_core),
+                     summary(eight_core),
+                     summary(ten_core),
+                     summary(fourteen_core)) # Done ~ 140s
+
+eight_DG <- bind_rows(summary(single_core),
+                      summary(four_core),
+                      summary(ten_core),
+                      summary(fourteen_core)) # Done
+
+sixteen_DG <- bind_rows(summary(single_core),
+                        summary(four_core),
+                        summary(ten_core),
+                        summary(fourteen_core)) # Done
+
+my_pk %>% get_data() %>% dplyr::select(Chemical, Species) %>%
+  distinct() %>% nrow()
+my_pk %>% get_data() %>% pull(Chemical) %>% unique() -> used_chemicals
+
+unused_cvt <- cvt %>%
+  dplyr::filter(!(chemicals_analyzed.dsstox_substance_id %in% used_chemicals))
+
+new_chemicals <- sample(unique(unused_cvt$chemicals_analyzed.dsstox_substance_id),
+                       size = 8)
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% union(used_chemicals,
+                                                                  new_chemicals))
+my_predata %>%
+  dplyr::select(chemicals_analyzed.dsstox_substance_id, subjects.species_harmonized) %>%
+  distinct() %>% nrow()
+
+my_pk <- pk(data = my_predata) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+my_pk <- do_prefit(my_pk) # Then run again
+
+##
+##
+# After getting all of them
+full_df <- bind_rows(
+  four_DG %>% mutate(data_group_N = 4),
+  eight_DG %>% mutate(data_group_N = 8),
+  sixteen_DG %>% mutate(data_group_N = 16)
+)
+
+full_df <- full_df %>%
+  mutate(N_cores = as.numeric(str_extract(expr, pattern = "[:digit:]+")))
+
+full_long <- full_df %>% 
+         dplyr::select(expr, N_cores, data_group_N, min, median, max) %>%
+         pivot_longer(cols = c(min, median, max)) %>%
+  dplyr::select(-name)
+
+df_long <- full_df %>% 
+         dplyr::select(expr, N_cores, data_group_N, min, median, max) %>%
+         pivot_longer(cols = c(min, median, max)) %>%
+  dplyr::select(-name) %>% group_by(N_cores, data_group_N) %>%
+  summarize(avg_val = mean(value),
+            sd_val = sd(value))
+
+ggplot(full_long,
+       aes(x = N_cores,
+           y = value,
+           color = factor(data_group_N))) +
+
+  geom_point() +
+  geom_line(data = df_long,
+            aes(x = N_cores,
+                y = avg_val)) +
+  scale_x_continuous(breaks = c(0, 1, 4, 8, 10, 14)) +
+  labs(x = "Number of Cores",
+       y = "Runtime (seconds)",
+       color = "Data Groups",
+       title = "Parallelization diminishes runtime at scale") +
+  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        legend.key = element_rect(fill = "white"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "Parallelization_Benchmarking.png"),
+       width = 4.5,
+       height = 3.5,
+       units = "in")
+
+```

### 2023-09-08 data-raw/batchMode_trial_gpm.Rmd
Starting some code optimizations (avoiding redundancy)

@@
 mvbutils::foodweb(where = asNamespace("invivoPKfit"),
-                  prune = "get_tkstats",
+                  prune = "transformed_params_2comp",
                   # descendents = FALSE,
-                  ancestors = FALSE,
+                  # ancestors = FALSE,
                   border = TRUE, cex = 1, lwd = 1.5)

### 2023-09-08 data-raw/batchMode_trial_gpm.Rmd
Redesigned the convert_time() function by adding a convert_time_table() sub-function which pre-generates a conversion table for all time units. Utilizes updated lubridate functions for conversions.

--- 2023-09-07 data-raw/batchMode_trial_gpm.Rmd
@@
   # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) 
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
 # Add Reference for Joint Analysis
@@
 # my_pk <- do_fit(my_pk)
+{
+  start_t <- Sys.time()
+  my_pk_time_scaling <- do_fit(my_pk_time_scaling, n_cores = 10)
+  round(Sys.time() - start_t, 3) # w/ Time scaling 36mins!
+}
+
+profvis::profvis(
+  plot(my_pk,
+     n_interp = 10)
+)
 
 plot(my_pk, method = "L-BFGS-B",
-     n_interp = 12) -> pl
+     n_interp = 5) -> pl
 
@@
 mvbutils::foodweb(where = asNamespace("invivoPKfit"),
-                  prune = "get_tkstats",
+                  prune = "time_units",
                   # descendents = FALSE,
-                  ancestors = FALSE,
+                  # ancestors = FALSE,
                   border = TRUE, cex = 1, lwd = 1.5)
@@
 ```
+
+### Time table (refactoring convert_time)
+
+```{r convert_time_table}
+
+expand_grid(TimeA = time_units, TimeB = time_units) %>%
+  mutate(A_fun = paste0("d", TimeA), B_fun = paste0("d", TimeB)) %>%
+  rowwise() %>%
+  mutate(conversion = 
+           do.call(A_fun, list(1))/do.call(B_fun, list(1))) %>%
+  dplyr::select(!c(A_fun, B_fun))
+
+```

### 2023-09-08 R/convert_time.R

@@ -31,44 +31,57 @@
 convert_time <- function(x,
                          from = "hours",
                          to = "identity",
-                         inverse = FALSE){
+                         inverse = FALSE,
+                         cct = NULL) {
 
   period_units <- time_units
 
-  if(to %in% "auto"){
+  if (to %in% "auto") {
     #select units automatically
     to <- auto_units(y = x,
                      from = from)
   }
 
 
-  if(to != "identity"){
-
-    if(inverse %in% TRUE){
-      y <- 1/x
-    }else{y <- x}
-
-  if(to %in% period_units){
-  y_new <- as.numeric(
-   lubridate::duration(num = y,
-                       units = from),
-   to)
-    }else{
-      y_new <- NA_real_
-      message(paste("invivopkfit::convert_time(): Allowable values for 'to' are",
-                    paste(c(period_units,
-                            ),
-                          collapse = ", "),
-                    ", but 'to' =", to,
-                    ". Returning NA_real_ for converted times."))
+  if (to != "identity") {
+    if (inverse %in% TRUE) {
+      y <- 1 / x
+    } else{
+      y <- x
     }
 
-  if(inverse %in% TRUE){
-    yout <- 1/y_new
-  }else{
-    yout <- y_new
-  }
-  }else{
+    if (to %in% period_units) {
+      # Legacy Code
+      # y_new <- as.numeric(lubridate::duration(num = y, units = from), to)
+      # New Code (needs to be vectorized)
+      # test with convert_time(c(1, 2, 10), from = "minutes", to = "hours")
+      if (is.null(cct)) {
+        cct <- convert_time_table()
+      }
+      ctt <- cct %>%
+        filter(to == TimeB && unique(from) == TimeA)
+      y_new <- y * ctt$conversion
+
+    } else{
+      y_new <- NA_real_
+      message(
+        paste(
+          "invivopkfit::convert_time(): Allowable values for 'to' are",
+          paste(c(period_units,),
+                collapse = ", "),
+          ", but 'to' =",
+          to,
+          ". Returning NA_real_ for converted times."
+        )
+      )
+    }
+
+    if (inverse %in% TRUE) {
+      yout <- 1 / y_new
+    } else{
+      yout <- y_new
+    }
+  } else{
     #if to == "identity", then just return the input as-is
     yout <- x
   }
@@ -76,3 +89,16 @@ convert_time <- function(x,
   return(yout)
 }
 
[…]

### 2023-09-08 R/pk_methods_plot.R

@@ -77,7 +77,7 @@ plot.pk <- function(obj,
                     drop_nonDetect = FALSE,
                     # Predict/interpolation arguments
                     plot_fit_aes = NULL,
-                    n_interp = 100,
+                    n_interp = 10,
                     fit_limits = NULL,
                     print_out = FALSE,
                     ...){
@@ -323,12 +323,22 @@ plot.pk <- function(obj,
                            model = model,
                            method = method,
                            exclude = FALSE,
-                           include_NAs = TRUE) %>%
-      rowwise()
+                           include_NAs = TRUE)
+
+    # rowwise can be taxing for function calls
+    # This process is inefficient, need to rewrite using a simple
+    # JOIN -> MUTATE -> SELECT
+    cct <- convert_time_table() %>%
+      filter(TimeA %in% interp_data$Time.Units,
+             TimeB %in% interp_data$Time_trans.Units) %>%
+      rename(Time.Units = "TimeA",
+             Time_trans.Units = "TimeB")
+
     interp_data <- interp_data %>%
-      mutate(Time_trans = convert_time(Time,
-                                       from = Time.Units,
-                                       to = Time_trans.Units))
+      dplyr::left_join(cct, by = dplyr::join_by(Time.Units,
+                                                Time_trans.Units)) %>%
+      dplyr::mutate(Time_trans = Time * conversion) %>%
+      dplyr::select(!conversion)
 
     interp_data <- interp_data %>%
       dplyr::group_by(!!!obj$data_group) %>%

### 2023-09-11 data-raw/batchMode_trial_gpm.Rmd
Added a time conversion table and made slight optimizations to the parameter assignment for the functions doing tkstat, concentration, or auc calculations.

@@
   start_t <- Sys.time()
-  my_pk <- do_fit(my_pk, n_cores = 6)
+  my_pk <- do_fit(my_pk, n_cores = 3)
   round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
-}
+} # 1.639min with only one dataset
 # my_pk <- do_fit(my_pk)
@@
 mvbutils::foodweb(where = asNamespace("invivoPKfit"),
-                  prune = "time_units",
+                  prune = "convert_time",
                   # descendents = FALSE,
@@
                        signif(digits = 4))
-
+  browser()
   my_df <- left_join(fold_errors_all, r2_df) %>%
@@
 
+time_table <- convert_time_table()
+
+time_table$TimeA %>% clipr::write_clip()
+time_table$TimeB %>% clipr::write_clip()
+time_table$conversion %>% MASS::fractions(max.denominator = 1000000000000000)
+
+### Plotting for all (2GB file)
+pdf(file = paste0(Sys.getenv("FIG_DIR"),
+              "DoseNormalized_Joint_AllFits.pdf"))
+for (i in 1:nrow(pl)) {
+  print(pl$final_plot[[i]])
+}
+dev.off()
+
 ```

### 2023-09-11 R/auto_units.R

@@ -30,8 +30,7 @@
 auto_units <- function(y,
                        from,
                        target = 10,
-                       period_units = time_units,
-                       cct = convert_time_table()){
+                       period_units = time_units){
 
 
   #auto-select units based on the midpoint of x
@@ -52,52 +51,48 @@ auto_units <- function(y,
   target_dist <- abs(y_mid - target_log10)
 
   #first we choose a direction -- up or down
-  if(i == 1){
+  if (i == 1) {
     #if we're at the low end we can only go up
     dir <- 1
     y_mid_up <- midpt_log10(
-        convert_time(y,
-                     from = from,
-                     to = period_units[i+1],
-                     cct = cct)
+      convert_time(y,
+                   from = from,
+                   to = period_units[i+1])
     )
 
     target_dist_new <- abs(y_mid_up - target_log10)
-  }else if(i == length(period_units)){
+  } else if (i == length(period_units)) {
     #if we're at the high end we can only go down
     dir <- -1
     y_mid_down <- midpt_log10(
-        convert_time(y,
-                     from = from,
-                     to = period_units[i-1],
-                     cct = cct)
+      convert_time(y,
+                   from = from,
+                   to = period_units[i-1])
     )
 
     target_dist_new <- abs(y_mid_down - target_log10)
-  }else{
+  } else {
     #try both ways and see which one gets closer to a midpoint of target
     y_mid_up <- midpt_log10(
-        convert_time(y,
-                     from = from,
-                   to = period_units[i+1],
-                   cct = cct)
+      convert_time(y,
+                   from = from,
+                   to = period_units[i+1])
     )
     target_dist_up <- abs(y_mid_up - target_log10)
 
     y_mid_down <- midpt_log10(
-        convert_time(y,
-                     from = from,
-                     to = period_units[i-1],
-                     cct = cct)
+      convert_time(y,
+                   from = from,
+                   to = period_units[i-1])
     )
 
     target_dist_down <- abs(y_mid_down - target_log10)
 
-    if(target_dist_up < target_dist_down){
+    if (target_dist_up < target_dist_down) {
       #if up gets closer to target than down does
       dir <- 1
       target_dist_new <- target_dist_up
-    }else if(target_dist_down < target_dist_up){
+    } else if (target_dist_down < target_dist_up) {
       #if down gets closer to target than up does
       dir <- -1
       target_dist_new <- target_dist_down
[…]

### 2023-09-11 R/pk_methods_do_preprocess.R

@@ -82,15 +82,11 @@ do_preprocess.pk <- function(obj){
 
 
 
-browser()
     #Check to make sure there is only one value for each set of units
     time_units <- unique(data$Time.Units)
     value_units <- unique(data$Value.Units)
     weight_units <- unique(data$Weight.Units)
     dose_units <- unique(data$Dose.Units)
-
-    this_cct <- convert_time_table() %>%
-      dplyr::filter(TimeA %in% time_units)
 
     if(any(sapply(list(time_units,
                        value_units,
@@ -656,8 +652,7 @@ browser()
       to_units <- data %>%
         group_by(!!!data_group) %>%
         mutate(AUTO_UNITS = auto_units(y = Time,
-                             from = Time.Units_orig,
-                             cct = this_cct)) %>%
+                             from = Time.Units_orig)) %>%
         pull(AUTO_UNITS)
     }
 
@@ -679,8 +674,7 @@ browser()
         dplyr::mutate(Time_trans = tryCatch(convert_time(x = Time,
                                          from = from_units,
                                          to = NEW_UNITS,
-                                         inverse = FALSE,
-                                         cct = this_cct),
+                                         inverse = FALSE),
                                      error = function(err){
                                        warning(paste("invivopkfit::do_preprocess.pk():",
                                                      "Error in transforming time using convert_time():",

### 2023-09-12 data-raw/batchMode_trial_gpm.Rmd
Removed a browser() call in plot.pk() and added definitions for time units

@@
   scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  scale_time(new_units = "auto") +
+  # scale_time(new_units = "auto") +
   # stat_model() + 
@@
                        signif(digits = 4))
-  browser()
+
   my_df <- left_join(fold_errors_all, r2_df) %>%
@@
 
-### Plotting for all (2GB file)
+### Plotting for all (2.5MB file)
+pl <- plot(my_pk, n_interp = 8, use_scale_conc = TRUE)
 pdf(file = paste0(Sys.getenv("FIG_DIR"),
-              "DoseNormalized_Joint_AllFits.pdf"))
+              "DoseNormalized_Pooled_AllFits.pdf"),
+    height = 6, width = 10)
 for (i in 1:nrow(pl)) {
@@
 
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "DoseNormalized_DTXSID8025337.png"),
+       units = "in",
+       height = 5.05,
+       width = 5.55,
+       dpi = 200)
+
 ```

### 2023-09-12 R/pk_methods_plot.R

@@ -328,7 +328,6 @@ plot.pk <- function(obj,
     # rowwise can be taxing for function calls
     # This process is inefficient, need to rewrite using a simple
     # JOIN -> MUTATE -> SELECT
-    browser()
     conversion_table <- time_conversions %>%
       filter(TimeFrom %in% interp_data$Time.Units,
              TimeTo %in% interp_data$Time_trans.Units) %>%

### 2023-09-25 data-raw/batchMode_trial_gpm.Rmd
Updating vignette to prepare for publication, included a TOC for figure's produced.

@@
 devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
+library(DBI)
 tidyverse_conflicts()
@@
 
-## Working with one DTXSID + Species combination
+# TOC
+
+1. Pulling Data from CvTdb  
+  - Minimal `pk` object  
+2. Running all possible fitting options  
+  - Evaluating fitting options  
+  - Head-to-head comparison of pooled vs joint models  
+3. Running dose-normalized joint fits  
+4. Analysis Plots  
+  - CvTdb replicate variation (Figure 5)  
+  - CvTdb replicate variation over ADME-normalized time (Figure 5B)  
+  - CvTdb concentration and final time-point distributions (Supplementary Figure 1)  
+  - invivoPKfit fit option selection (Figure 6)  
+  - invivoPKfit model performance (Supplementary Figure 2)  
+  - Model performance vs Data variability (Figure 7A)  
+  - Goodness of fit plots (Figure 7B)  
+  - Fits that may be improved (Supplementary Figure 3)  
+5. Lombardo Analysis  
+  - Chemicals included  
+  - Comparison of derived TK stats  (Figure 8)
+6. Benchmarking invivoPKfit
+  - Parallelization speeds up the process of fitting (Supplementary Figure 4)
+
+## Pulling data from CvTdb
+This is largely taken from a `Querying CvTdb` vignette from Taylor Wall.
+
+```{r query_functions}
+
+postgreSQL_connection <- function() {
+  return(
+    dbConnect(RPostgreSQL::PostgreSQL(),
+              user = Sys.getenv("CVT_USER"),
+              password = Sys.getenv("CVT_PASS"),
+              host = Sys.getenv("CVT_HOST"),
+              dbname = Sys.getenv("CVT_DB_NAME"))
+  )
+}
+
+query_db <- function(query = NULL, schema) {
+  if (is.null(query)) return(cat("\nMust provide a query to send"))
+  con <- postgreSQL_connection()
+
+  query_result <- tryCatch(
+    return(dbGetQuery(con, query %>%
+                        gsub("FROM ", paste0("FROM ", schema, "."), .) %>%
+                        gsub("JOIN ", paste0("JOIN ", schema, "."), .))),
+  error = function(cond){ 
+    cat(paste0("\nError message: ", cond))
+    return(NULL)
+  },
+  finally = { 
+    dbDisconnect(con)
+    }
+    )
+  return(query_result)
+}
+
+```
+
+The following is the new SQL query, this will eventually be moved another vignette.
+
+```{r SQL_queries}
+# Sample query of CvTdb Documents SQL
+# query <- "SELECT pmid, year, first_author, title FROM documents LIMIT 10"
+# query <- "SELECT count(*) FROM studies"
+# query <- "SELECT DISTINCT administration_route_normalized FROM studies"
+
+# Need to make this in a specified ordered
+# First all IDs (so I can check them quickly)
+# Note that this uses an ALIAS for each table which is later specified in
+# the FROM and LEFT JOIN statments
+query <- paste0(
+  "SELECT distinct ",
+  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
+  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
+  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
+  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
+  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
+  "b.loq, b.loq_units, b.n_subjects_in_series, ",
+  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
+  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
+  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
+  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
+  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",
+
+  # Main Table
+  "FROM conc_time_values a ",
+
+  # Join with series table by series ID
+  "LEFT JOIN series b ON b.id = a.fk_series_id ",
+
+  # Join to studies table by study ID
+  "LEFT JOIN studies c ON c.id = b.fk_study_id ",
+
+  # Join to subjects table by subject ID
+  "LEFT JOIN subjects d ON d.id = b.fk_subject_id ",
+
+  # Join to documents table by extraction document ID
+  "LEFT JOIN documents e ON e.id = c.fk_extraction_document_id ",
+
+  # Filtering steps
+  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
+  "c.administration_route_normalized IN ('iv', 'oral')"
+)
+
+sql_query <- query_db(query = query,
+         schema = "cvt")
+
+names(sql_query)
+# Need to change column names for this
+{
+  names(sql_query)[1] <- "conc_time_id"
+  names(sql_query)[8] <- "series_id"
+  names(sql_query)[22] <- "study_id"
+  names(sql_query)[34] <- "subject_id"
+  names(sql_query)[41] <- "document_id"
+}
+
+# Harmonize values for easier analysis
+sql_query <- sql_query %>%
+  mutate(
+    species = tolower(species),
+    sex = tolower(sex),
+    loq = as.numeric(loq),
+    n_subjects_in_series = as.numeric(n_subjects_in_series),
+    dose_level_normalized = as.numeric(dose_level_normalized),
+    dose_level_original = as.numeric(dose_level_original),
+    dose_volume_units = str_extract(dose_volume,
+                                    pattern = "(?<=[:space:]).+"),
+    dose_volume = as.numeric(str_extract(dose_volume,
+                                         pattern = "^(\\d|\\.)*")),
+    dose_duration_units = str_extract(dose_duration,
+                                      pattern = "(?<=[space]).+"),
+    dose_duration = as.numeric(str_extract(dose_duration,
+                                pattern = "^\\d"))
+  )
+sql_query <- sql_query %>%
+  rename_with(~gsub(pattern = "fk_", replacement = "",
+                         .x), .cols = contains("fk_"))
+
+# Copying
+cvt_df <- sql_query # Copy so I don't have to do query again to reset any errors
+
+# Check other_study_identifier == S0916 so that it has dose_level_original_units == ug/mL
+cvt_df %>% filter(other_study_identifier == "S0916") %>%
+  pull(dose_level_original_units) %>% unique()
+# There are still columns that are mg/kg... changing these to ug/mL
+cvt_df <- cvt_df %>% mutate(
+  dose_level_original_units = ifelse(
+    other_study_identifier == "S0916",
+    "ug/mL",
+    dose_level_original_units
+  )
+)
+
+# Need to convert the units to mg/kg
+# In pulling_oral_iv_data_cvtdb.Rmd, it is noted that oral was 5mL/kg and iv 2mL/kg
+# So I need to do ug/mL * mL/kg * 1mg/1000ug = mg/kg
+cvt_df <- cvt_df %>%
+  mutate(
+    dose_level_corrected = ifelse(
+      other_study_identifier %in% "S0916",
+      ifelse(administration_route_normalized %in% "oral",
+             dose_level_original * 5/1000,
+             dose_level_original * 2/1000),
+      dose_level_normalized),
+    dose_level_corrected_units = "mg/kg",
+    .after = dose_level_original_units)
+
+# For this study, it was in ng/kg not mg/kg
+cvt_df <- cvt_df %>%
+  mutate(
+    dose_level_corrected = ifelse(
+      other_study_identifier %in% "S0624",
+      dose_level_original * 1E-6,
+      dose_level_normalized),
+    .after = dose_level_original_units)
+
+# The following measured C-14/H-3 but are indicators for the following Chemicals
+# document_id = 65, DTXSID = DTXSID7031290, name = Isocyclemone E or beta-OTNE
+# document_id = 61, DTXSID = DTXSID4022527, DTXSID3020209,
+### name(s) = propylparaben, butylparaben, missing...methylparaben
+# Propylparaben SERIES_ID = 110, Butylparaben SERIES_ID = 112
+# For above, HPLC reviealed a single peak corresponding with p-hydroxybenzoic acid (PHBA, DTXSID3026647)
+# document_id = 46, DTXSID = DTXSID2020139, name = benzo[a]pyrene
+# document_id = 31, DTXSID = DTXSID2020139, name = benzo[a]pyrene
+
+# However, now would be good time to eliminate any ones where they analyte != test chemical
+# Some studies may have dosed with multiple chemicals... important to note
+# cvt_df <- cvt_df %>% filter(analyzed_chemical_id == test_chemical_id)
+# For now, I will change the chemical name and dtxsid
+cvt_df <- cvt_df %>%
+  mutate(analyte_dtxsid = ifelse(document_id %in% 65, "DTXSID7031290",
+                                 analyte_dtxsid),
+         analyte_name_original = ifelse(document_id %in% 65, "beta-OTNE",
+                                        analyte_name_original)) %>%
+  mutate(analyte_dtxsid = ifelse(document_id %in% 61,
+                                 case_when(
+                                   series_id %in% 110 ~ "DTXSID4022527",
+                                   series_id %in% 112 ~ "DTXSID3020209",
+                                   .default = analyte_dtxsid
+                                 ),
+                                 analyte_dtxsid),
+         analyte_name_original = ifelse(document_id %in% 61,
+                                 case_when(
+                                   series_id %in% 110 ~ "Propylparaben",
+                                   series_id %in% 112 ~ "Butylparaben",
+                                   .default = analyte_name_original
+                                 ),
+                                 analyte_name_original)
+         ) %>%
+  mutate(analyte_dtxsid = ifelse(document_id %in% c(46, 31),
+                                 "DTXSID2020139",
+                                 analyte_dtxsid),
+         analyte_name_original = ifelse(document_id %in% c(46, 31),
+                                        "benzo[a]pyrene",
+                                        analyte_name_original))
+
+# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine were dosed
+cvt_df <- cvt_df %>%
+  mutate(loq = ifelse(
+    other_study_identifier %in% "S0976",
+    case_when(
+      analyte_name_original %in% "Caffeine" ~ 4.00,
+      analyte_name_original %in% "L-Ephedrine" ~ 4.44,
+      analyte_name_original %in% "Pseudoephedrine" ~ 4.43
+    ),
+    loq),
+    loq_units = ifelse(
+      other_study_identifier %in% "S0976",
+      "ng/mL",
+      loq_units
+    ))
+
+# Some pentachloranisole studies
+# S0361 seems to have some data that has not been extracted (also for mouse)
+cvt_df <- cvt_df %>%
+  mutate(loq = case_when(
+    other_study_identifier %in% "S0361" ~ 0.05,
+    other_study_identifier %in% "S0328" ~ 1, # This is inferred
+    # Highest value under loq is 0.9
+    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
+    .default = loq
+  ),
+  loq_units = case_when(
+    other_study_identifier %in% "S0361" ~ "ug/mL",
+    other_study_identifier %in% "S0328" ~ "ug/mL",
+    .default = loq_units
+  ))
+
+# Checking if entire groups of data are NA for conc and loq
+# Really only eliminates Tamoxifen
+# cvt_df %>%
+#   # filter(analyte_dtxsid %in% "DTXSID1034187") %>%
+#   group_by(analyte_dtxsid, document_id, 
+#                     administration_route_normalized,
+#                     conc_medium_normalized,
+#                     species, dose_level_corrected) %>%
+#   filter(all(is.na(conc) & is.na(loq))) %>% 
+#   distinct(analyte_dtxsid, document_id, analyte_name_original,
+#                     administration_route_normalized,
+#                     conc_medium_normalized,
+#                     species, dose_level_corrected) %>% View()
+
+# Checking individual chemicals
+# cvt_df %>%
+#   filter(analyte_dtxsid %in% "DTXSID2020682") %>%
+#   distinct(analyte_dtxsid, document_id, 
+#                     administration_route_normalized,
+#                     conc_medium_normalized,
+#                     species, dose_level_corrected)
+
+# PMID 6310077 is a tritium tracing of B[a]P and these were given as % of Dose
+# The initial dose was 117 nmol, 2 mCi/kg
+# Molecular Mass of benzo[a]pyrene (C20H12) is 252.316 g/mol
+# The initial dose *I think* is in dose_level_normalized
+cvt_df <- cvt_df %>%
+  mutate(conc = ifelse(document_id %in% 38,
+                       conc_original*dose_level_corrected,
+                       conc))
+
+# NTP-CEB C96019 just has a lot of data below LOQ
+# For S0916, there is no > LOQ data for anything but Tamoxifen
+# N-di-butyl phthalate is only good at the iv dose
+# DTXSID2021315 is only good at 1E-4 Dose
+# S0623 Doesn't have any plasma data
+# There is a maybe control sample for hexachlorobenzene (Dose = 0.0 ) ?
+
+# Filter by whether at each dose, there are no LOQ or Concentration value reported
+# This is the threshold for Minimally Informative Data in our use case.
+cvt_df %>%
+  group_by(analyte_dtxsid, document_id, 
+                    administration_route_normalized,
+                    conc_medium_normalized,
+                    species, dose_level_corrected) %>%
+  filter(!all(is.na(conc) & is.na(loq))) %>%
+  distinct(analyte_dtxsid, species,) %>% nrow() # Says there are 433 distinct
+
+cvt_df <- cvt_df %>%
+  group_by(analyte_dtxsid, document_id, 
+                    administration_route_normalized,
+                    conc_medium_normalized,
+                    species, dose_level_corrected) %>%
+  filter(!all(is.na(conc) & is.na(loq)))
+
+# Give N-desmethyltamoxifen it's due DTXSID501315924
+cvt_df <- cvt_df %>%
+  mutate(analyte_dtxsid = ifelse(
+    analyte_name_original %in% "N-desmethyltamoxifen",
+    "DTXSID501315924",
+    analyte_dtxsid
+  ))
+
+cvt_df <- cvt_df %>%
+  mutate(analyte_dtxsid = ifelse(
+    analyte_name_original %in% "Methemoglobin",
+    "DTXSID301056085",
+    analyte_dtxsid
+  ))
+
+# Standardizing the names (example: glucuronide had two entries)
+cvt_df <- cvt_df %>%
+  mutate(analyte_name_original = tolower(analyte_name_original))
+
+# Eliminate study that gave chemical each day, not single dose
+# This may be used in another type of model, but right now we deal with single bolus
+# Only include those that have NA or 1 for dose frequency
+cvt_df <- cvt_df %>%
+  filter(dose_frequency %in% c("1", NA))
+
+# Normalize LOQ units
+cvt_df <- cvt_df %>%
+  mutate(loq = ifelse(
+    loq_units %in% c("ug/L", "ng/mL"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
+# Normalize conc_sd and conc units manually
+cvt_df <- cvt_df %>%
+  mutate(conc_sd_normalized = case_when(
+    conc_units_original %in% c("ug/L", "ng/mL", "ng-Eq/mL", "ng/g tissue") ~ conc_sd_original*1E-3,
+    conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
+    conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
+    .default = conc_sd_original
+  ))
+# Need to normalize the ng-eq/mL sample, conc is generally already normalized
+cvt_df <- cvt_df %>%
+  mutate(conc = case_when(
+    conc_units_original %in% c("ng-eq/mL") ~ conc_original*1E-3,
+    .default = conc
+  ))
+
+cvt_df <- cvt_df %>%
+  dplyr::filter(!(analyte_dtxsid %in% c("DTXSID501315924",
+                                      "DTXSID10169854",
+                                      "DTXSID2021103") )) # These only have 1 or 2 values
+
+# More notes:
+# DTXSID6020438 & DTXSID0020868 rat is from water (top) and oil (bottom curve) gavage
+
+```
+
+```{r pk_obj_fromSQL}
+
+### PK OBJECT ###----
+# Minimum pk object, add options later
+minimal_pk <- pk(data = cvt_df,
+                 mapping = ggplot2::aes(
+                   Chemical = analyte_dtxsid,
+                   Chemical_Name = analyte_name_original,
+                   DTXSID = analyte_dtxsid,
+                   CASRN = analyte_casrn,
+                   Species = species,
+                   Reference = document_id,
+                   Media = conc_medium_normalized,
+                   Route = administration_route_normalized,
+                   Dose = dose_level_normalized,
+                   Dose.Units = "mg/kg",
+                   Subject_ID = subject_id,
+                   Series_ID = series_id,
+                   Study_ID = study_id,
+                   ConcTime_ID = conc_time_id,
+                   N_Subjects = n_subjects_in_series,
+                   Weight = weight_kg,
+                   Weight.Units = "kg",
+                   Time = time_hr,
+                   Time.Units = "hours",
+                   Value = conc,
+                   Value.Units = "mg/L",
+                   Value_SD = conc_sd_normalized,
+                   LOQ = loq
+                 ))
+```
+
+## Running all possible fitting options
+
+This chunk is to run all the options through a
+standard pipeline that calculates RMSE for Cmax and AUC_inf
+for the Chemical Species Route Media grouping...
+
+```{r pooled_fitting_choices}
+# Types of Choices:
+## Dose Normalized
+## Log10 transform
+## Scale time
+
+# Pooled
+my_pk_000p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_100p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_110p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_111p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_010p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_011p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_001p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+my_pk_101p <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+
+```
+
+```{r joint_fitting_choices}
+# Joint
+my_pk_000j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_100j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_110j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_111j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_010j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_011j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_001j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference))
+
+my_pk_101j <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = FALSE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+```
+
+### Evaluating fitting options
+
+```{r Evaluating_Choices}
+# Evaluation
+# Current: my_pk_111p
+
+get_choices <- function(obj, PJ = "Pooled") {
+  dose_norm <- obj$scales$conc$dose_norm
+  log10_norm <- obj$scales$conc$log10_trans
+  time_scale <- ifelse(obj$scales$time$new_units == "identity", FALSE, TRUE)
+
+  my_choices <- paste0(dose_norm+0,
+                       log10_norm+0,
+                       time_scale+0,
+                       " ", PJ)
+  return(my_choices)
+}
+
+# Write into package
+evaluate_choices <- function(obj, PJ = "Pooled") {
+  pk_name <- get_choices(obj, PJ = PJ)
+
+  cli::cli_progress_step("Winning Model...")
+  # Wide winning model
+  suppressMessages({
+    winning_model <- get_winning_model(obj = obj) 
+    wide_winning_model <- winning_model %>%
+      group_by(method, model) %>%
+      count() %>%
+      pivot_wider(names_from = model, values_from = n) %>%
+      mutate(Options = pk_name)
+  })
+
+  cli::cli_progress_step("Cmax and AUC_inf RMSEs...")
+  # Cmax and AUC_inf RMSEs
+  suppressMessages({
+    RMSE_eval <- eval_tkstats(obj = obj) %>%
+    mutate(Options = pk_name) %>%
+    dplyr::select(Options,
+                Chemical, Species,
+                Route, Media, Reference,
+                method, model,
+                starts_with("Cmax"),
+                starts_with("AUC_")) %>%
+      filter(abs(AUC_inf.nca / AUC_tlast.nca) < 10,
+             is.finite(AUC_inf.nca), is.finite(AUC_inf.tkstats),
+             AUC_inf.nca > 0, AUC_inf.tkstats > 0) %>%
+      rowwise() %>%
+      mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
+             SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
+      filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
+      group_by(Options, method) %>%
+      summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
+                                      na.rm = FALSE)) %>% signif(digits = 4),
+                RMSE_AUC = sqrt(mean(SE_AUC_inf,
+                                     na.rm = FALSE)) %>% signif(digits = 4))
+  })
+
+  cli::cli_progress_step("More detailed metrics...")
+  # Other metrics (detailed)
+  suppressMessages({
+    r2_df <- rsq(obj, use_scale_conc = FALSE) %>%
+    inner_join(winning_model)
+  myAIC <- AIC(obj) %>%
+    inner_join(winning_model)
+  fold_errors_all <- fold_errors(obj) %>%
+    inner_join(winning_model) %>%
+    dplyr::filter(Detect %in% TRUE) %>%
+    dplyr::group_by(!!!obj$data_group, model, method) %>%
+    dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE) %>%
+                       signif(digits = 4),
+                     median_FoldErr = median(Fold_Error, na.rm = TRUE) %>%
+                       signif(digits = 4),
+                     within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error) %>%
+                       signif(digits = 4))
+
+  myRMSE_all <- rmse(obj,
+                     rmse_group = vars(Route, Media, Dose),
+                     use_scale_conc = FALSE) %>% 
+    inner_join(winning_model) %>%
+    dplyr::group_by(!!!obj$data_group, model, method) %>%
+    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
+                       signif(digits = 4),
+                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
+                       signif(digits = 4))
+
+  my_df <- left_join(fold_errors_all, r2_df) %>%
+    inner_join(myAIC) %>%
+    inner_join(myRMSE_all) %>%
+    mutate(Options = pk_name, .before = Chemical)
+
+  full_list <- list(wide_winning_model, RMSE_eval, my_df)
+  })
+
+  return(full_list)
+}
+gc()
+
+### Evaluations-----
+my_pk_000p <- do_fit(my_pk_000p, n_cores = 14) 
+my_pk_000p <- my_pk_000p %>% evaluate_choices() # Done
+my_pk_100p <- do_fit(my_pk_100p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_110p <- do_fit(my_pk_110p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_111p <- do_fit(my_pk_111p, n_cores = 8) %>% evaluate_choices() # Done
+rm(my_pk_100p,my_pk_110p,my_pk_111p)
+gc()
+my_pk_010p <- do_fit(my_pk_010p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_011p <- do_fit(my_pk_011p, n_cores = 8) %>% evaluate_choices() # Done 
+my_pk_001p <- do_fit(my_pk_001p, n_cores = 8) %>% evaluate_choices() # Done
+my_pk_101p <- do_fit(my_pk_101p, n_cores = 8) %>% evaluate_choices() # Done
+
+my_pk_000j <- do_fit(my_pk_000j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_100j <- do_fit(my_pk_100j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_110j <- do_fit(my_pk_110j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_111j <- do_fit(my_pk_111j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+rm(my_pk_000j, my_pk_100j, my_pk_110j, my_pk_111j)
+gc()
+my_pk_010j <- do_fit(my_pk_010j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_011j <- do_fit(my_pk_011j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_001j <- do_fit(my_pk_001j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+my_pk_101j <- do_fit(my_pk_101j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
+
+# Run after each evaluation
+# initialization (only run once)
+{
+winning_model_final <- NULL
+rmse_summary <- NULL
+detail_stats <- NULL
+}
+
+# Run all at once
+{
+current_pk <- my_pk_101j # Define current evaluated pk object here
+winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])
+rmse_summary <- bind_rows(rmse_summary, current_pk[[2]])
+detail_stats <- bind_rows(detail_stats, current_pk[[3]])
+rm(current_pk)
+gc()
+}
+
+# For copy + pasting into Excel workbook
+winning_model_final %>% clipr::write_clip(col.names = FALSE)
+clipr::clear_clip()
+rmse_summary %>% clipr::write_clip(col.names = FALSE)
+clipr::clear_clip()
+detail_stats %>% clipr::write_clip(col.names = FALSE)
+clipr::clear_clip()
+gc()
+
+```
+
+## Head-to-head comparison of pooled vs joint models
+
+Now I need to go back and re-analyze the data only for 100, 101, and 000
+Pooled and Joint, L-BFGS-B only. I need to filter the cvt_df to only include Chem + Species combinations
+with multiple references. Then I will join them with the excel sheet of already collected data.
+
+```{r load_multirefs}
+# Reference Multiples
+multiRef_ChemSpec <- cvt_df %>%
+  ungroup() %>%
+  distinct(analyte_dtxsid, species, document_id) %>%
+  group_by(analyte_dtxsid, species) %>%
+  count() %>%
+  arrange(desc(n)) %>%
+  filter(n > 1) %>%
+  dplyr::select(!n)
+multiRef_ChemSpec %>% nrow() # Surprisingly only 13 Chem + Species have multiple references
+
+```
+
+```{r Plotting_Summary}
+finalist_options <- c("000 Pooled", "000 Joint",
+                      "100 Pooled", "100 Joint",
+                      "101 Pooled", "101 Joint")
+
+readxl::excel_sheets(paste(Sys.getenv("OD_DIR"),
+                           "DataSummary_9_21_2023.xlsx",
+                           sep = "/")) # Predictions Evaluation
+
+preval <- readxl::read_xlsx(paste(Sys.getenv("OD_DIR"),
+                                  "DataSummary_9_21_2023.xlsx",
+                                  sep = "/"),
+                            sheet = "Predictions Evaluation") %>%
+  left_join(multiRef_ChemSpec,
+            by = join_by(Chemical == analyte_dtxsid,
+                         Species == species)) %>%
+  filter(method %in% "L-BFGS-B", 
+         Options %in% finalist_options) %>%
+  distinct()
+
+preval %>%
+  separate(Options, sep = " ",
+           into = c("Options", "Error_Model")) %>%
+  ggplot(aes(x = avg_FoldErr,
+             color = Options)) +
+  geom_freqpoly(bins = 10) +
+  facet_grid(cols = vars(Error_Model))
+
+preval %>% 
+  separate(Options, sep = " ",
+           into = c("Options", "Error_Model")) %>%
+  group_by(Options, Error_Model) %>%
+  summarize(totalFoldError = sum(avg_FoldErr))
+
+readxl::read_xlsx(paste(Sys.getenv("OD_DIR"),
+                                  "DataSummary_9_21_2023.xlsx",
+                                  sep = "/"),
+                            sheet = "Fit_Counts") %>%
+  filter(Options %in% finalist_options, method %in% "L-BFGS-B")
+
+readxl::read_xlsx(paste(Sys.getenv("OD_DIR"),
+                                  "DataSummary_9_21_2023.xlsx",
+                                  sep = "/"),
+                            sheet = "Cmax and AUC_inf Evaluation") %>%
+  filter(Options %in% finalist_options, method %in% "L-BFGS-B")
+
+library(broom)
+
+filtered_preval <- preval %>%
+  filter(if_all(where(is.numeric), is.finite))
+
+filtered_preval %>%
+  dplyr::select(Chemical, Species, model, method, Options, Rsq) %>%
+  mutate(time_scaled = ifelse(str_detect(Options,
+                                         pattern = "^\\d\\d1"),
+                              "Time_Scaled",
+                              "notTime_Scaled"),
+         Options = str_remove(Options, pattern = "\\d(?=[:blank:])")) %>%
+  # dplyr::select(-Options) %>%
+  pivot_wider(names_from = time_scaled, values_from = Rsq) %>% 
+  mutate(differ = Time_Scaled - notTime_Scaled) %>%
+  View()
+
+fit <- lm(within_2fold ~ avg_FoldErr, data = filtered_preval)
+summary(fit)
+tidy(fit)
+head(augment(fit))
+glance(fit)
+
+filtered_preval %>% group_by(Options) %>%
+  nest() %>%
+  mutate(fit = map(data, \(x) {
+    lm(within_2fold ~ avg_FoldErr, data = x)
+    }),
+    tidy_fit = map(fit, tidy)) %>%
+  unnest(tidy_fit) %>%
+  dplyr::select(Options, term, estimate, std.error, statistic) %>%
+  View()
+
+Cmax_AUC <- readxl::read_xlsx(paste("C:/Users/GPADILLA",
+                                  "OneDrive - Environmental Protection Agency (EPA)",
+                                  "DataSummary_8_18_2023.xlsx",
+                                  sep = "/"),
+                            sheet = "Cmax and AUC_inf Evaluation") %>%
+  dplyr::select(1:4) %>%
+  distinct()
+
+Cmax_AUC %>%
+  mutate(DFO = rank(sqrt(RMSE_Cmax^2 + signif(RMSE_AUC, 5)^2)),
+         OLS = rank(abs(RMSE_Cmax + signif(RMSE_AUC, 5))/sqrt(2))) %>%
+  #filter(DFO < 11 | OLS < 11) %>%
+  arrange(DFO, OLS) %>%
+  dplyr::select(-RMSE_Cmax, -RMSE_AUC) %>% View()
+  clipr::write_clip()
+
+Cmax_AUC %>%
+  mutate(DFO = rank(sqrt(RMSE_Cmax^2 + RMSE_AUC^2)),
+         OLS = rank(abs(RMSE_Cmax + RMSE_AUC)/sqrt(2))) %>%
+  ggplot(aes(
+    x = DFO,
+    y = OLS,
+    fill = Options
+  )) + geom_point(shape = 21)
+
+```
+
+## Running dose-normalized joint fits
+
+Dose-normalization and a hierarchical model were the options that produced the least
+amount of error in predictions and derived TK stats.
+
+```{r Standard_Settings}
+# Full option setting
+my_pk <- pk(data = cvt_df,
+            mapping = ggplot2::aes(
+              Chemical = analyte_dtxsid,
+              Chemical_Name = analyte_name_original,
+              DTXSID = analyte_dtxsid,
+              CASRN = analyte_casrn,
+              Species = species,
+              Reference = document_id,
+              Media = conc_medium_normalized,
+              Route = administration_route_normalized,
+              Dose = dose_level_normalized,
+              Dose.Units = "mg/kg",
+              Subject_ID = subject_id,
+              Series_ID = series_id,
+              Study_ID = study_id,
+              ConcTime_ID = conc_time_id,
+              N_Subjects = n_subjects_in_series,
+              Weight = weight_kg,
+              Weight.Units = "kg",
+              Time = time_hr,
+              Time.Units = "hours",
+              Value = conc,
+              Value.Units = "mg/L",
+              Value_SD = conc_sd_normalized,
+              LOQ = loq
+            )) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+my_pk <- do_preprocess(my_pk)
+my_data <- get_data(my_pk)
+
+```
+
+An aside: working with one DTXSID + Species combination
 
@@
 
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID8025337")
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID9022360")
-
-# A PFAS chemical?
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3031860")
-# All long lived chemicals
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c(long_lived_chem[3:5],
-                                                              "DTXSID0020442"))
-do_preprocess(my_pk_001p) %>% get_data() %>% filter(Time.Units != Time_trans.Units) %>%
-  pull(Chemical) %>% unique() -> long_lived_chem
-
-# Reasonable fits... multiple species
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442",
-                                                              "DTXSID2039336"))
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% (over1Ref %>%
-                                                               pull(Chemical)),
-                subjects.species_harmonized %in% "rat")
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID0020442"),
-                subjects.species_harmonized %in% "hamster",
-                studies.administration_route_normalized %in% "iv")
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID1043881",
-                                                              "DTXSID8020541",
-                                                              "DTXSID6034849"),
-                subjects.species_harmonized %in% "rat")
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID4023917")
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID7030066",
-                                                              "DTXSID0020442",
-                                                              "DTXSID2021315"),
-                subjects.species_harmonized %in% "rat")
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID2039336",
-                                                              "DTXSID7029904",
-                                                              "DTXSID1021087",
-                                                              "DTXSID2020682"))
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% c("DTXSID1034187",
-                                                              "DTXSID2021315",
-                                                              "DTXSID3032179",
-                                                              "DTXSID4020533"))
-
 ```
@@
 ```{r single_fit}
-# Pooled
-my_pk <- pk(data = my_predata) +
+my_pk_original <- minimal_pk +
   facet_data(vars(Chemical, Species)) +
@@
 
-my_pk <- do_preprocess(my_pk)
+my_pk_original <- do_preprocess(my_pk_original)
 
@@
 # Timing for normal fit sapply
-{
-  start_t <- Sys.time()
-  my_pk <- do_fit(my_pk, n_cores = 3)
-  round(Sys.time() - start_t, 3) # 5.741min (5 data_groups)
-} # 1.639min with only one dataset
-# my_pk <- do_fit(my_pk)
-{
-  start_t <- Sys.time()
-  my_pk_time_scaling <- do_fit(my_pk_time_scaling, n_cores = 10)
-  round(Sys.time() - start_t, 3) # w/ Time scaling 36mins!
-}
-
-profvis::profvis(
-  plot(my_pk,
-     n_interp = 10)
-)
-
-plot(my_pk, method = "L-BFGS-B",
-     n_interp = 5) -> pl
-
-plot(my_pk,
-     method = "L-BFGS-B",
-     n_interp = 20,
-     print_out = TRUE)
-# Joint
-my_pk <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
-# Add Reference for Joint Analysis
-
-my_pk <- do_preprocess(my_pk)
-
-my_pk <- do_data_info(my_pk) 
-# summarizes error (Returning more or less than 1 row per summarize)
-
-my_pk <- do_prefit(my_pk)
-
+my_pk <- do_fit(my_pk, 
+                n_cores = 12)
 my_pk <- do_fit(my_pk)
 
+```
+
+## Analysis Plots
+
+### Figure 5A: Replicated timepoint variation in CvTdb
+
+### Figure 5B: Variation over time in CvTdb data
+
+### Supplementary Figure 1: Concentration and final time-points have wide range
+
+### Figure 6: Selecting best fitting options for CvTdb data
+
+### Supp Figure 2: invivoPKfit model performance
+
+### Figure 7A: Model performance vs Data Variability
+
+### Figure 7B: Multiple goodness-of-fit metrics validate model performance
+
+### Supp. Fig. 3: Fits that may be improved with other settings
+
+### Figure 8: Comparing derived TK stats with human TK stats from Lombardo et al.
+
+### Supp. Fig. 4: Parallelization decreases runtime of invivoPKfit
+
+```{r cvt_analysis}
 my_df %>%
@@
 
-all_my_data <- my_pk$data
+all_my_data <- get_data(my_pk)
 all_my_data %>%
@@
   filter(Route == "iv") %>%
-  count(foldConc >= 0.5 & foldConc <= 2) %>%
+  count(foldConc < 0.5) %>%
   {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
-# 88.9% inside twofold
-# 2.2%  above twofold 
-# 8.8%  below twofold
+# 88.9% inside twofold ## New CvT extraction: 91.3%
+# 2.2%  above twofold  ## 1.7%
+# 8.8%  below twofold  ## 7.0%
 # 
@@
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "NormalizedConcentrations_2023-07-11.png"),
+              "NormalizedConcentrations_2023-09-21.png"),
        height = 3.5,
@@
   )) +
-  geom_point(alpha = 0.2,
-             aes(color = Chemical)) +
-  geom_vline(xintercept = 1, color = "blue", linetype = "dashed") +
-  geom_vline(xintercept = 2, color = "green4", linetype = "dashed") +
-  geom_hline(yintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
+  geom_point(alpha = 0.1, size = 0.7) +
+  geom_vline(xintercept = 1, color = "blue",
+             size = 1, linetype = "dashed") +
+  geom_vline(xintercept = 2, color = "green4",
+             size = 1, linetype = "dashed") +
+  geom_hline(yintercept = c(0.5, 2), color = "red3",
+             size = 1, linetype = "dashed") +
   facet_grid(cols = vars(Route),
@@
         axis.line = element_blank(),
-        axis.text.x = element_blank())
+        axis.text.x = element_blank(),
+        legend.position = "none")
 
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "ADME_NormalizedTime-NormalizedConcentrations_onlyDetects_2023-07-19.png"),
+              "ADME_NormalizedTime-NormalizedConcentrations_onlyDetects_2023-09-21.png"),
        height = 4,
        width = 6,
-       units = "in")
+       units = "in",
+       dpi = 300)
 
@@
 
-winmodels <- AIC(my_pk) %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>%
-  ungroup() %>%
-  dplyr::select(Chemical, Species,
-                method, model)
+winmodels <- get_winning_model(my_pk)
 
@@
          sum(is.na(Conc_trans)) != n(),
-         model %in% c("model_flat"),
+         # model %in% c("model_flat"),
          exclude %in% FALSE,
@@
   # For percentages
-  ungroup() %>%
-  count(!(foldPred >= 0.5 & foldPred <= 2) &
-          !(foldConc >= 0.5 & foldConc <= 2)) %>%
-  {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
+  # ungroup() %>%
+  # count(!(foldPred >= 0.5 & foldPred <= 2) &
+  #         !(foldConc >= 0.5 & foldConc <= 2)) %>%
+  # {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
   # For Plotting
@@
   facet_grid(cols = vars(model)) +
-  scale_x_log10(limits = c(0.0001, 50)) +
+  scale_x_log10(limits = c(0.0001, 100)) +
   scale_y_log10(limits = c(0.001, 1000)) +
@@
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "ModelPerformance_vDataVariability_2023-07-20.png"),
+              "ModelPerformance_vDataVariability_2023-09-21.png"),
        height = 3.5,
@@
 
-This chunk is to run all the options through a
-standard pipeline that calculates RMSE for Cmax and AUC_inf
-for the Chemical Species Route Media grouping...
-
-```{r pooled_fitting_choices}
-# Types of Choices:
-## Dose Normalized
-## Log10 transform
-## Scale time
-
-# Pooled
-my_pk_000p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_100p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_110p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_111p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_010p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_011p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_001p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_101p <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-```
-
-```{r joint_fitting_choices}
-# Joint
-my_pk_000j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
-
-my_pk_100j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
-
-my_pk_110j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
-
-my_pk_111j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
-
-my_pk_010j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
-
-my_pk_011j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = TRUE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
-
-my_pk_001j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference))
-
-my_pk_101j <- pk(data = cvt) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
-```
-
-Here I evaluate the choices of the fits in a streamlined way.
-
-```{r Evaluating_Choices}
-# Evaluation
-# Current: my_pk_111p
-
-get_choices <- function(obj, PJ = "Pooled") {
-  dose_norm <- obj$scales$conc$dose_norm
-  log10_norm <- obj$scales$conc$log10_trans
-  time_scale <- ifelse(obj$scales$time$new_units == "identity", FALSE, TRUE)
-
-  my_choices <- paste0(dose_norm+0,
-                       log10_norm+0,
-                       time_scale+0,
-                       " ", PJ)
-  return(my_choices)
-}
-
-# Write into package
-evaluate_choices <- function(obj, PJ = "Pooled") {
-  pk_name <- get_choices(obj, PJ = PJ)
-
-  cli::cli_progress_step("Winning Model...")
-  # Wide winning model
-  suppressMessages({
-    winning_model <- get_winning_model(obj = obj) %>%
-      group_by(method, model) %>%
-      count() %>%
-      pivot_wider(names_from = model, values_from = n) %>%
-      mutate(Options = pk_name)
-  })
-
-  cli::cli_progress_step("Cmax and AUC_inf RMSEs...")
-  # Cmax and AUC_inf RMSEs
-  suppressMessages({
-    RMSE_eval <- eval_tkstats(obj = obj) %>%
-    mutate(Options = pk_name) %>%
-    dplyr::select(Options,
-                Chemical, Species,
-                Route, Media, Reference,
-                method, model,
-                starts_with("Cmax"),
-                starts_with("AUC_")) %>%
-      filter(abs(AUC_inf.nca / AUC_tlast.nca) < 10,
-             is.finite(AUC_inf.nca), is.finite(AUC_inf.tkstats),
-             AUC_inf.nca > 0, AUC_inf.tkstats > 0) %>%
-      rowwise() %>%
-      mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
-             SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
-      filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
-      group_by(Options, method) %>%
-      summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
-                                      na.rm = FALSE)) %>% signif(digits = 4),
-                RMSE_AUC = sqrt(mean(SE_AUC_inf,
-                                     na.rm = FALSE)) %>% signif(digits = 4))
-  })
-
-  cli::cli_progress_step("More detailed metrics...")
-  # Other metrics (detailed)
-  suppressMessages({
-    r2_df <- rsq(obj, use_scale_conc = FALSE) %>%
-    inner_join(winning_model)
-  myAIC <- AIC(obj) %>%
-    inner_join(winning_model)
-  fold_errors_all <- fold_errors(obj) %>%
-    inner_join(winning_model) %>%
-    dplyr::filter(Detect %in% TRUE) %>%
-    dplyr::group_by(!!!obj$data_group, model, method) %>%
-    dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE) %>%
-                       signif(digits = 4),
-                     median_FoldErr = median(Fold_Error, na.rm = TRUE) %>%
-                       signif(digits = 4),
-                     within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error) %>%
-                       signif(digits = 4))
-
-  myRMSE_all <- rmse(obj,
-                     rmse_group = vars(Route, Media, Dose),
-                     use_scale_conc = FALSE) %>% 
-    inner_join(winning_model) %>%
-    dplyr::group_by(!!!obj$data_group, model, method) %>%
-    dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE) %>%
-                       signif(digits = 4),
-                     median_MSE = median(RMSE^2, na.rm = TRUE) %>%
-                       signif(digits = 4))
-
-  my_df <- left_join(fold_errors_all, r2_df) %>%
-    inner_join(myAIC) %>%
-    inner_join(myRMSE_all) %>%
-    mutate(Options = pk_name, .before = Chemical) %>%
-    dplyr::select(!c("model_1comp", "model_2comp", "model_flat"))
-
-  full_list <- list(winning_model, RMSE_eval, my_df)
-  })
-
-  return(full_list)
-}
-gc()
-
-my_pk_000p <- do_fit(my_pk_000p, n_cores = 8) %>% evaluate_choices() # Done
-my_pk_100p <- do_fit(my_pk_100p, n_cores = 8) %>% evaluate_choices() # Done
-my_pk_110p <- do_fit(my_pk_110p, n_cores = 8) %>% evaluate_choices() # Done
-my_pk_111p <- do_fit(my_pk_111p, n_cores = 12) #%>% evaluate_choices() # Done
-my_pk_010p <- do_fit(my_pk_010p, n_cores = 8) %>% evaluate_choices() # Done
-my_pk_011p <- do_fit(my_pk_011p, n_cores = 8) %>% evaluate_choices() # Done 
-my_pk_001p <- do_fit(my_pk_001p, n_cores = 8) %>% evaluate_choices() # Done
-my_pk_101p <- do_fit(my_pk_101p, n_cores = 8) %>% evaluate_choices() # Done
-
-my_pk_000j <- do_fit(my_pk_000j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done 
-my_pk_100j <- do_fit(my_pk_100j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
-my_pk_110j <- do_fit(my_pk_110j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
-my_pk_111j <- do_fit(my_pk_111j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
-my_pk_010j <- do_fit(my_pk_010j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
-my_pk_011j <- do_fit(my_pk_011j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done 
-my_pk_001j <- do_fit(my_pk_001j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done 
-my_pk_101j <- do_fit(my_pk_101j, n_cores = 8) %>% evaluate_choices(PJ = "Joint") # Done
-
-# Run after each evaluation
-# initialization (only run once)
-{
-winning_model_final <- NULL
-rmse_summary <- NULL
-detail_stats <- NULL
-start_time <- Sys.time()
-}
-
-# Run all at once
-{
-current_pk <- my_pk_111p # Define current evaluated pk object here
-winning_model_final <- bind_rows(winning_model_final, current_pk[[1]])
-rmse_summary <- bind_rows(rmse_summary, current_pk[[2]])
-detail_stats <- bind_rows(detail_stats, current_pk[[3]])
-rm(current_pk)
-gc()
-}
-
-# For copy + pasting into Excel workbook
-winning_model_final %>% clipr::write_clip(col.names = FALSE)
-clipr::clear_clip()
-rmse_summary %>% clipr::write_clip(col.names = FALSE)
-clipr::clear_clip()
-detail_stats %>% clipr::write_clip(col.names = FALSE)
-clipr::clear_clip()
-gc()
-
-### Workshopping
-evaluated_tkstats %>%
-  mutate(Options = "Pooled") %>%
-    dplyr::select(Options,
-                Chemical, Species,
-                Route, Media, Reference,
-                method, model,
-                starts_with("Cmax"),
-                starts_with("AUC_")) %>%
-      filter(abs(AUC_inf.nca / AUC_tlast.nca) < 10,
-             is.finite(AUC_inf.nca), is.finite(AUC_inf.tkstats),
-             AUC_inf.nca > 0, AUC_inf.tkstats > 0) %>%
-      rowwise() %>%
-      mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
-             SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
-      filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
-  dplyr::select(Chemical, Species, Route, Media, method, Options,
-                SE_Cmax, SE_AUC_inf) %>%
-  distinct() %>%
-  group_by(Options, method) %>%
-      summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
-                                      na.rm = FALSE)) %>% signif(digits = 4),
-                RMSE_AUC = sqrt(mean(SE_AUC_inf,
-                                     na.rm = FALSE)) %>% signif(digits = 4))
-  View()
-
-eval_tkstats(obj = my_pk_111p) %>%
-  filter(Chemical == "DTXSID0021125") %>%
-    mutate(Options = "Pooled") %>%
-    dplyr::select(Options,
-                Chemical, Species,
-                Route, Media, Reference,
-                method, model,
-                starts_with("Cmax"),
-                starts_with("AUC_")) %>%
-      filter(abs(AUC_inf.nca / AUC_tlast.nca) < 10,
-             is.finite(AUC_inf.nca), is.finite(AUC_inf.tkstats),
-             AUC_inf.nca > 0, AUC_inf.tkstats > 0) %>%
-      rowwise() %>%
-      mutate(SE_Cmax = (Cmax.tkstats - Cmax.nca)^2,
-             SE_AUC_inf = (AUC_inf.tkstats - AUC_inf.nca)^2) %>%
-      filter(!is.na(SE_Cmax), !is.na(SE_AUC_inf)) %>%
-      group_by(Options, method) %>%
-      summarize(RMSE_Cmax = sqrt(mean(SE_Cmax,
-                                      na.rm = FALSE)) %>% signif(digits = 4),
-                RMSE_AUC = sqrt(mean(SE_AUC_inf,
-                                     na.rm = FALSE)) %>% signif(digits = 4))
-
-```
-
-```{r Plotting_Summary}
-
-readxl::excel_sheets("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/DataSummary_8_18_2023.xlsx") # Predictions Evaluation
-
-preval <- readxl::read_xlsx(paste("C:/Users/GPADILLA",
-                                  "OneDrive - Environmental Protection Agency (EPA)",
-                                  "DataSummary_8_18_2023.xlsx",
-                                  sep = "/"),
-                            sheet = "Predictions Evaluation") %>%
-  dplyr::select(-model_1comp, -model_2comp, -model_flat) %>%
-  distinct()
-
-library(broom)
-
-filtered_preval <- preval %>%
-  filter(if_all(where(is.numeric), is.finite))
-
-filtered_preval %>%
-  dplyr::select(Chemical, Species, model, method, Options, Rsq) %>%
-  mutate(time_scaled = ifelse(str_detect(Options,
-                                         pattern = "^\\d\\d1"),
-                              "Time_Scaled",
-                              "notTime_Scaled"),
-         Options = str_remove(Options, pattern = "\\d(?=[:blank:])")) %>%
-  # dplyr::select(-Options) %>%
-  pivot_wider(names_from = time_scaled, values_from = Rsq) %>% 
-  mutate(differ = Time_Scaled - notTime_Scaled) %>%
-  View()
-
-fit <- lm(within_2fold ~ avg_FoldErr, data = filtered_preval)
-summary(fit)
-tidy(fit)
-head(augment(fit))
-glance(fit)
-
-filtered_preval %>% group_by(Options) %>%
-  nest() %>%
-  mutate(fit = map(data, \(x) {
-    lm(within_2fold ~ avg_FoldErr, data = x)
-    }),
-    tidy_fit = map(fit, tidy)) %>%
-  unnest(tidy_fit) %>%
-  dplyr::select(Options, term, estimate, std.error, statistic) %>%
-  View()
-
-Cmax_AUC <- readxl::read_xlsx(paste("C:/Users/GPADILLA",
-                                  "OneDrive - Environmental Protection Agency (EPA)",
-                                  "DataSummary_8_18_2023.xlsx",
-                                  sep = "/"),
-                            sheet = "Cmax and AUC_inf Evaluation") %>%
-  dplyr::select(1:4) %>%
-  distinct()
-
-Cmax_AUC %>%
-  mutate(DFO = rank(sqrt(RMSE_Cmax^2 + signif(RMSE_AUC, 5)^2)),
-         OLS = rank(abs(RMSE_Cmax + signif(RMSE_AUC, 5))/sqrt(2))) %>%
-  #filter(DFO < 11 | OLS < 11) %>%
-  arrange(DFO, OLS) %>%
-  dplyr::select(-RMSE_Cmax, -RMSE_AUC) %>% View()
-  clipr::write_clip()
-
-Cmax_AUC %>%
-  mutate(DFO = rank(sqrt(RMSE_Cmax^2 + RMSE_AUC^2)),
-         OLS = rank(abs(RMSE_Cmax + RMSE_AUC)/sqrt(2))) %>%
-  ggplot(aes(
-    x = DFO,
-    y = OLS,
-    fill = Options
-  )) + geom_point(shape = 21)
-
-```
-
 Here I do a bit of benchmarking for the parallel-ized version of do_fit
@@
 
+# From my new SQL pull
+pl <- plot(my_pk, n_interp = 8, use_scale_conc = TRUE)
+pdf(file = paste0(Sys.getenv("FIG_DIR"),
+              "NormalizedUpdate_NewCvT_SQLquery.pdf"),
+    height = 6, width = 10)
+for (i in 1:nrow(pl)) {
+  print(pl$final_plot[[i]])
+}
+dev.off()
+
 ggsave(paste0(Sys.getenv("FIG_DIR"),

### 2023-09-29 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Save cvt data with harmonized (lower case) species variable subjects.species_harmonized
Updated the 'cvt' data included with invivoPKfit and the associated vignette.

--- 2023-04-12 Working Rmds/pulling_oral_iv_data_cvtdb.Rmd
@@
 title: "Pulling oral and IV data from CvTdb"
-author: "Caroline Ring"
-date: "2022-12-13"
+author: "Caroline Ring, Gilberto Padilla Mercado"
+date: "2023-09-29"
 output: html_document
@@
 library(DBI)
-library(data.table)
-library(ggplot2)
+library(dplyr)
+library(tidyr)
 ```
@@
 
-Open a PostGreSQL connection.
+This is largely taken from a `Querying CvTdb` vignette from Taylor Wall and a previous version
+of this vignette authored by Caroline Ring.
 
-```{r}
- con <-  dbConnect(RPostgreSQL::PostgreSQL(),
-            user = Sys.getenv("cvt_user"),
-            password = Sys.getenv("cvt_password"), #
-            host = Sys.getenv("cvt_host"), #
-            dbname = Sys.getenv("cvt_dbname"))
-```
+The following are some helpter functions for the database connection
+```{r query_functions}
+postgreSQL_connection <- function() {
+  return(
+    dbConnect(RPostgreSQL::PostgreSQL(),
+              user = Sys.getenv("CVT_USER"),
+              password = Sys.getenv("CVT_PASS"),
+              host = Sys.getenv("CVT_HOST"),
+              dbname = Sys.getenv("CVT_DB_NAME"))
+  )
+}
 
-# View the available tables
+query_db <- function(query = NULL, schema) {
+  if (is.null(query)) return(cat("\nMust provide a query to send"))
+  con <- postgreSQL_connection()
 
-```{r}
-dbGetQuery(con, "SELECT * FROM pg_catalog.pg_tables WHERE schemaname != 'pg_catalog' AND schemaname != 'information_schema'")
-```
-
-I don't fully know what all of this means, but it filters out various "internal" tables that are not actually part of CvTdb, and shows only the tables that are.
-
-See the EER diagram showing the various tables within CvtDb and the relations between them.
-
-# Formulate a query
-
-In PostGreSQL, you have to refer to tables as "[schema].[table]". Note that in the table above, the schema for CvT tables is always "cvt."
-
-I don't fully understand schemas yet.
-
-I don't have a full data dictionary so I don't yet know how to filter correctly.
-The most expedient way to do it for me is to pull down each table separately, then filter and merge using e.g.
-data.table.
-
-Here's how to pull down each table separately.
-
-```{r}
-fpath <- "C:/Users/cring/OneDrive - Environmental Protection Agency (EPA)/CvTdb/"
-this_date <- format(Sys.time(), "%Y_%m_%d")
-
-#list of table names to pull down
-tables <- c("conc_time_values",
-            "series",
-            "subjects",
-            "studies",
-            "chemicals",
-            "documents")
-
-#loop over table names and pull down each one
-for (this_table in tables){
-  print(this_table)
-  this_query <- paste("SELECT * FROM",
-                      paste0("cvt.", this_table))
-  this_item <- dbGetQuery(con, this_query)
-  this_item <- as.data.table(this_item)
-  assign(this_table, this_item)
-
-  #prepend table name to all variable names in each table
-  #some variable names are repeated in multiple tables
-  #this will let me keep track
-  these_names <- names(eval(parse(text = this_table)))
-  setnames(eval(parse(text = this_table)),
-           these_names,
-           paste(this_table,
-                 these_names,
-                 sep = "."))
+  query_result <- tryCatch(
+    return(dbGetQuery(con, query %>%
+                        gsub("FROM ", paste0("FROM ", schema, "."), .) %>%
+                        gsub("JOIN ", paste0("JOIN ", schema, "."), .))),
+  error = function(cond){ 
+    cat(paste0("\nError message: ", cond))
+    return(NULL)
+  },
+  finally = { 
+    dbDisconnect(con)
     }
-```
-
-Disconnect from database
-
-```{r}
-dbDisconnect(con)
-```
-
-Now there are a bunch of `data.table` variables in the environment, one for each CvT table. They are `conc_time_values`, `series`, `studies`, `subjects`, `chemicals`, and `documents`.
-
-# Merge
-
-Merge conc_time_values with series
-
-```{r}
-tmp1 <- series[conc_time_values,
-                         on = c("series.id" = "conc_time_values.fk_series_id"),
-                         nomatch = NA]
-```
-
-Merge with studies
-
-```{r}
-tmp2 <- studies[tmp1,
-               on = c("studies.id" = "series.fk_study_id"),
-               nomatch = NA]
-```
-
-Merge in subjects info
-
-```{r}
-tmp3 <- subjects[tmp2, on = c("subjects.id" = "series.fk_subject_id"), nomatch = NA]
-```
-
-Merge in chemical info. There are two chemical ID foreign keys.
-
-`series.fk_test_chemical_id` = chemical that was dosed
-
-`series.fk_analyzed_chemical_id`  = chemical that was measured in body media (tissue, blood/plasma, urine, etc.) May be the same as dosed chemical, but may be different if, for example, a metabolite was measured instead of the parent chemical.
-
-To keep track of this, let me create two copies of the `chemicals` table -- one called `chemicals_dosed` and one called `chemicals_analyzed`.
-That way I can get the DTXSID, CASRN, and preferred names for each one.
-
-```{r}
-chemicals_dosed <- copy(chemicals)
-chemicals_analyzed <- copy(chemicals)
-```
-
-Change the variable-name prefixes from "chemicals.[var]" to "chemicals_dosed.[var]" and "chemicals_analyzed.[var]" .
-```{r}
-setnames(chemicals_dosed,
-         names(chemicals_dosed),
-         gsub(x = names(chemicals_dosed),
-              pattern = "chemicals.",
-              replacement = "chemicals_dosed.",
-              fixed = TRUE))
-
-setnames(chemicals_analyzed,
-         names(chemicals_analyzed),
-         gsub(x = names(chemicals_analyzed),
-              pattern = "chemicals.",
-              replacement = "chemicals_analyzed.",
-              fixed = TRUE))
-```
-
-Now merge
-
-```{r}
-tmp4 <- chemicals_dosed[tmp3,
-                        on = c("chemicals_dosed.id" = "series.fk_test_chemical_id"),
-                        nomatch = NA]
-tmp5 <- chemicals_analyzed[tmp4,
-                           on = c("chemicals_analyzed.id" = "series.fk_analyzed_chemical_id"),
-                           nomatch = NA]
-```
-
-Merge in documents info.
-
-There are both extraction documents and reference documents_reference. Make two copies of documents -- one for each.
-
-```{r}
-documents_reference <- copy(documents)
-documents_extraction <- copy(documents)
-
-setnames(documents_reference,
-         names(documents_reference),
-         gsub(x = names(documents_reference),
-              pattern = "documents.",
-              replacement = "documents_reference.",
-              fixed = TRUE))
-
-setnames(documents_extraction,
-         names(documents_extraction),
-         gsub(x = names(documents_extraction),
-              pattern = "documents.",
-              replacement = "documents_extraction.",
-              fixed = TRUE))
-```
-
-```{r}
-tmp6 <- documents_extraction[tmp5,
-                  on = c("documents_extraction.id" ="studies.fk_extraction_document_id"),
-                  nomatch = NA]
-tmp7 <- documents_reference[tmp6,
-                  on = c("documents_reference.id" ="studies.fk_reference_document_id"),
-                  nomatch = NA]
-```
-
-I think this should do it.
-
-```{r}
-cvt_data <- copy(tmp7)
-rm(tmp1, tmp2, tmp3, tmp4, tmp5, tmp6, tmp7)
-```
-
-# Exploring the data
-
-How many series per study?
-
-```{r}
-n_series_per_study <- cvt_data[,
-                               .(n_series = length(unique(series.id))),
-                               by = studies.id]
-n_series_per_study[, range(n_series)]
-```
-
-# Look at one weird case
-
-DTXSID1034187 had a weird situation where concentrations seemed very low for the "300" dose group. Let's see what is going on there
-
-```{r}
-tmp <- cvt_data[chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187" &
-                  studies.administration_route_normalized %in% c("oral", "iv") &
-                  series.conc_medium_normalized %in% c("blood", "plasma")]
-```
-
-This should have reference IDs 141 and 142 -- does it?
-
-```{r}
-tmp[, unique(documents_extraction.id)]
-```
-
-OK good, so this is the data we were expecting.
-
-This is tamoxifen. Though it does not have much document info, I traced it to https://doi.org/10.22427/NTP-DATA-DTXSID8021301
-
-(the only curated document info avalable is this:)
-
-```{r}
-unique(tmp[, .(documents_extraction.url, documents_extraction.other_study_identifier)])
-```
-
-That URL is now broken. But if I google "ntp S0916" I get the page at https://doi.org/10.22427/NTP-DATA-DTXSID8021301.
-
-Though items are marked below LOD or below LOQ, the original data does not include what the LOD/LOQ actually were. I cannot find a written report with more information anywhere.
-
-The original data does note the dose units as ug/mL and notes that 5 mL/kg were administered, and contains the initial body weight of each subject.
-
-In fact I think these doses have *not* been correctly normalized. There should be values for `studies.dose_volume` and there are not
-
-```{r}
-tmp[, unique(studies.dose_volume)]
-```
-
-```{r}
-unique(tmp[, .(studies.dose_level_original, studies.dose_level_original_units, studies.dose_level_normalized, studies.dose_volume)])
-```
-
-This apepars to be the only document where that original units of ug/mL do not get changed for normalized dose level
-
-```{r}
-cvt_data[studies.dose_level_normalized == studies.dose_level_original &
-           studies.dose_level_original_units %in% "ug/mL",
-         unique(documents_extraction.id)]
-```
-
-Also, there is lots and lots of below-LOD data from study S0917 oral gavage administration that is not included in CvTdb at all.
-
-Incidentally, the one with 300 mg/kg as the original dose level also seems to be wrong. That is study S0916. Looking at the original NTP data, those units are really ug/mL.
-
-Visualize what I mean
-
-```{r}
-ggplot(data = tmp) +
-  geom_point(aes(x = conc_time_values.time_hr,
-                 y = conc_time_values.conc,
-                 shape = factor(documents_extraction.id),
-                 color = as.numeric(studies.dose_level_normalized))) +
-  facet_grid(rows = vars(studies.administration_route_normalized)) +
-  scale_y_log10() + 
-  annotation_logticks(sides = "l") +
-  scale_color_viridis_c(breaks = as.numeric(unique(tmp$studies.dose_level_normalized)))
-```
-
-Or plot dose-normalized
-
-```{r}
-ggplot(data = tmp) +
-  geom_point(aes(x = conc_time_values.time_hr,
-                 y = conc_time_values.conc/as.numeric(studies.dose_level_normalized),
-                 shape = factor(documents_extraction.id),
-                 color = as.numeric(studies.dose_level_normalized))) +
-  facet_grid(rows = vars(studies.administration_route_normalized)) +
-  scale_y_log10() + 
-  annotation_logticks(sides = "l") +
-  scale_color_viridis_c(breaks = as.numeric(unique(tmp$studies.dose_level_normalized)))
-```
-
-We need to actually normalize the doses for these, properly. We will have to go to the original NTP data to do this, because the volumes of administration were not properly retained in CvTdb.
-
-for study S0916, the oral gavage volume of administration was 5 mL/kg, and the IV volume of administration was 2 ml/kg.
-
-```{r}
-tmp[, studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_normalized)]
-
-tmp[studies.dose_level_original_units %in% "ug/mL" &
-      studies.administration_route_normalized %in% "oral",
-    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]
-
-tmp[studies.dose_level_original_units %in% "ug/mL" &
-      studies.administration_route_normalized %in% "iv",
-    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
-
-tmp[studies.dose_level_original_units %in% "mg/kg" &
-      studies.dose_level_original %in% 300 &
-      studies.administration_route_normalized %in% "iv",
-    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
+    )
+  return(query_result)
+}
 
@@
 
-```{r}
-ggplot(data = tmp) +
-  geom_point(aes(x = conc_time_values.time_hr,
-                 y = conc_time_values.conc,
-                 shape = factor(documents_extraction.id),
-                 color = as.numeric(studies.dose_level_normalized_corrected))) +
-  facet_grid(rows = vars(studies.administration_route_normalized)) +
-  scale_y_log10() + 
-  annotation_logticks(sides = "l") +
-  scale_color_viridis_c()
+The following is the new SQL query.
+
+```{r SQL_queries}
+# Need to make this in a specified ordered
+# First all IDs (so I can check them quickly)
+# Note that this uses an ALIAS for each table which is later specified in
+# the FROM and LEFT JOIN statments
+query <- paste0(
+  "SELECT distinct ",
+  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
+  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
+  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
+  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
+  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
+  "b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
+  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
+  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
+  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
+  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
+  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",
+
+  # Main Table
+  "FROM conc_time_values a ",
+
+  # Join with series table by series ID
+  "LEFT JOIN series b ON b.id = a.fk_series_id ",
+
+  # Join to studies table by study ID
+  "LEFT JOIN studies c ON c.id = b.fk_study_id ",
+
+  # Join to subjects table by subject ID
+  "LEFT JOIN subjects d ON d.id = b.fk_subject_id ",
+
+  # Join to documents table by extraction document ID
+  "LEFT JOIN documents e ON e.id = c.fk_extraction_document_id ",
+
+  # Filtering steps
+  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
+  "c.administration_route_normalized IN ('iv', 'oral')"
+)
+
+sql_query <- query_db(query = query,
+         schema = "cvt")
+
+names(sql_query)
+# Need to change column names for this
+{
+  names(sql_query)[1] <- "conc_time_id"
+  names(sql_query)[8] <- "series_id"
+  names(sql_query)[23] <- "study_id"
+  names(sql_query)[35] <- "subject_id"
+  names(sql_query)[42] <- "document_id"
+}
+
+# Harmonize values for easier analysis
+sql_query <- sql_query %>%
+  mutate(
+    species = tolower(species),
+    sex = tolower(sex),
+    loq = as.numeric(loq),
+    n_subjects_in_series = as.numeric(n_subjects_in_series),
+    dose_level_normalized = as.numeric(dose_level_normalized),
+    dose_level_original = as.numeric(dose_level_original),
+    dose_volume_units = str_extract(dose_volume,
+                                    pattern = "(?<=[:space:]).+"),
+    dose_volume = as.numeric(str_extract(dose_volume,
+                                         pattern = "^(\\d|\\.)*")),
+    dose_duration_units = str_extract(dose_duration,
+                                      pattern = "(?<=[space]).+"),
+    dose_duration = as.numeric(str_extract(dose_duration,
+                                pattern = "^\\d")),
+    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE)
+  )
+sql_query <- sql_query %>%
+  rename_with(~gsub(pattern = "fk_", replacement = "",
+                         .x), .cols = contains("fk_"))
+
+# Copying
+cvt_df <- sql_query # Copy so I don't have to do query again to reset any errors
 ```
 
-```{r}
-ggplot(data = tmp) +
-  geom_point(aes(x = conc_time_values.time_hr,
-                 y = conc_time_values.conc/as.numeric(studies.dose_level_normalized_corrected),
-                 shape = factor(documents_extraction.id),
-                 color = as.numeric(studies.dose_level_normalized_corrected))) +
-  facet_grid(rows = vars(studies.administration_route_normalized)) +
-  scale_y_log10() + 
-  annotation_logticks(sides = "l") +
-  scale_color_viridis_c()
-```
+# Validating data
 
-Apply dose corrections to the full data table
+This step in the loading process allows us to correct some mis-annotations in the
+data, without directly changing CvTdb (the review process there is more rigorous).
+Some of these changes will be sent as a ticket item for the CvTdb team.
+Other times, the annotation is correct, it's just that units need to be standardized
+for `invivoPKfit` specifically.
 
-```{r}
-cvt_data[, studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_normalized)]
+To summarize the changes:
 
-cvt_data[documents_extraction.id %in% 141 &
-           studies.dose_level_original_units %in% "ug/mL" &
-      studies.administration_route_normalized %in% "oral",
-    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 5 * subjects.weight_kg/1000]
+-  Change original dose units for study _S0916_ and convert to mg/kg.  
+-  Change original dose units for study _S0642_ and convert to mg/kg.  
+-  Include a series of isotope tracing experiments from documents _65_, _61_, _46_, and _31_.  
+-  Input the LOQ for studies _S0976_ & _S0361_.  
+-  Infer the LOQ for study _S0328_ as 1, given the values near it deemed above and below LOQ.  
+-  Extraction from PMID:6310077 reflects a _% of Dose_, so we converted this to mg/kg.  
+-  Input DTXSIDs for chemicals that did not have them but were available via CompTox dashboard.  
+-  Standardize all Doses, LOQs, Concentrations, and Concentration standard deviations.  
+-  Filter out chemicals dosed multiple times throughout the experiment.  
+-  Filter out chemicals with very limited information.
 
-cvt_data[documents_extraction.id %in% 141 &
-      studies.dose_level_original_units %in% "ug/mL" &
-      studies.administration_route_normalized %in% "iv",
-    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
+```{r data_validation}
+# Check other_study_identifier == S0916 so that it has dose_level_original_units == ug/mL
+cvt_df %>% filter(other_study_identifier == "S0916") %>%
+  pull(dose_level_original_units) %>% unique()
+# There are still columns that are mg/kg... changing these to ug/mL
+cvt_df <- cvt_df %>% mutate(
+  dose_level_original_units = ifelse(
+    other_study_identifier == "S0916",
+    "ug/mL",
+    dose_level_original_units
+  )
+)
 
-cvt_data[documents_extraction.id %in% 141 &
-           studies.dose_level_original_units %in% "mg/kg" &
-      studies.dose_level_original %in% 300 &
-      studies.administration_route_normalized %in% "iv",
-    studies.dose_level_normalized_corrected:=as.numeric(studies.dose_level_original) * 2 * subjects.weight_kg/1000]
-```
+# Need to convert the units to mg/kg
+# In pulling_oral_iv_data_cvtdb.Rmd, it is noted that oral was 5mL/kg and iv 2mL/kg
+# So I need to do ug/mL * mL/kg * 1mg/1000ug = mg/kg
+cvt_df <- cvt_df %>%
+  mutate(
+    dose_level_corrected = ifelse(
+      other_study_identifier %in% "S0916",
+      ifelse(administration_route_normalized %in% "oral",
+             dose_level_original * 5/1000,
+             dose_level_original * 2/1000),
+      dose_level_normalized),
+    dose_level_corrected_units = "mg/kg",
+    .after = dose_level_original_units)
 
-## Correcting dose level units for PCB-126
+# For this study, it was in ng/kg not mg/kg
+cvt_df <- cvt_df %>%
+  mutate(
+    dose_level_corrected = ifelse(
+      other_study_identifier %in% "S0624",
+      dose_level_original * 1E-6,
+      dose_level_normalized),
+    .after = dose_level_original_units)
 
-Upon examining PCB-126, I think the original dose units should be ng/kg rather than mg/kg.
-If we look at https://cebs.niehs.nih.gov/cebs/study/002-02863-0008-0000-9 and look at the summary data rather than individual animal data, the dose units are listed as "ng/kg." In the rest of the studies at https://cebs.niehs.nih.gov/cebs/test_article/57465-28-8 all of the dosing units are ng/kg.
-So I think that is what it should be.
+# The following measured C-14/H-3 but are indicators for the following Chemicals
+# document_id = 65, DTXSID = DTXSID7031290, name = Isocyclemone E or beta-OTNE
+# document_id = 61, DTXSID = DTXSID4022527, DTXSID3020209,
+### name(s) = propylparaben, butylparaben, missing...methylparaben
+# Propylparaben SERIES_ID = 110, Butylparaben SERIES_ID = 112
+# For above, HPLC reviealed a single peak corresponding with p-hydroxybenzoic acid (PHBA, DTXSID3026647)
+# document_id = 46, DTXSID = DTXSID2020139, name = benzo[a]pyrene
+# document_id = 31, DTXSID = DTXSID2020139, name = benzo[a]pyrene
 
-```{r}
-cvt_data[chemicals_dosed.dsstox_substance_id %in% "DTXSID3032179", studies.dose_level_original := "ng/kg"]
-cvt_data[chemicals_dosed.dsstox_substance_id %in% "DTXSID3032179", studies.dose_level_normalized_corrected := as.numeric(studies.dose_level_normalized) * 1e-6] #convert to mg/kg
-```
+# However, now would be good time to eliminate any ones where they analyte != test chemical
+# Some studies may have dosed with multiple chemicals... important to note
+# cvt_df <- cvt_df %>% filter(analyzed_chemical_id == test_chemical_id)
+# For now, I will change the chemical name and dtxsid
+cvt_df <- cvt_df %>%
+  mutate(analyte_dtxsid = ifelse(document_id %in% 65, "DTXSID7031290",
+                                 analyte_dtxsid),
+         analyte_name_original = ifelse(document_id %in% 65, "beta-OTNE",
+                                        analyte_name_original)) %>%
+  mutate(analyte_dtxsid = ifelse(document_id %in% 61,
+                                 case_when(
+                                   series_id %in% 110 ~ "DTXSID4022527",
+                                   series_id %in% 112 ~ "DTXSID3020209",
+                                   .default = analyte_dtxsid
+                                 ),
+                                 analyte_dtxsid),
+         analyte_name_original = ifelse(document_id %in% 61,
+                                 case_when(
+                                   series_id %in% 110 ~ "Propylparaben",
+                                   series_id %in% 112 ~ "Butylparaben",
+                                   .default = analyte_name_original
+                                 ),
+                                 analyte_name_original)
+         ) %>%
+  mutate(analyte_dtxsid = ifelse(document_id %in% c(46, 31),
+                                 "DTXSID2020139",
+                                 analyte_dtxsid),
+         analyte_name_original = ifelse(document_id %in% c(46, 31),
+                                        "benzo[a]pyrene",
+                                        analyte_name_original))
 
-# Missing LOQs
+# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine were dosed
+cvt_df <- cvt_df %>%
+  mutate(loq = ifelse(
+    other_study_identifier %in% "S0976",
+    case_when(
+      analyte_name_original %in% "Caffeine" ~ 4.00,
+      analyte_name_original %in% "L-Ephedrine" ~ 4.44,
+      analyte_name_original %in% "Pseudoephedrine" ~ 4.43
+    ),
+    loq),
+    loq_units = ifelse(
+      other_study_identifier %in% "S0976",
+      "ng/mL",
+      loq_units
+    ))
 
-```{r}
-cvt_data[, n_obs_ref := sum(is.finite(conc_time_values.conc) & (conc_time_values.conc > 0) %in% TRUE),
-         by = .(documents_extraction.id, documents_reference.id,
-                chemicals_analyzed.dsstox_substance_id, chemicals_dosed.dsstox_substance_id,
-                series.conc_medium_normalized, subjects.species)]
+# Some pentachloranisole studies
+# S0361 seems to have some data that has not been extracted (also for mouse)
+cvt_df <- cvt_df %>%
+  mutate(loq = case_when(
+    other_study_identifier %in% "S0361" ~ 0.05,
+    other_study_identifier %in% "S0328" ~ 1, # This is inferred
+    # Highest value under loq is 0.9
+    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
+    .default = loq
+  ),
+  loq_units = case_when(
+    other_study_identifier %in% "S0361" ~ "ug/mL",
+    other_study_identifier %in% "S0328" ~ "ug/mL",
+    .default = loq_units
+  ))
 
-unique(cvt_data[n_obs_ref==0 &
-                  series.conc_medium_normalized %in% c("blood", "plasma") &
-                  studies.administration_route_normalized %in% c("oral", "iv"), 
-                  #chemicals_dosed.dsstox_substance_id == chemicals_analyzed.dsstox_substance_id,
-                .(documents_extraction.id, documents_reference.id, documents_extraction.pmid, documents_extraction.doi, documents_extraction.other_study_identifier, chemicals_analyzed.dsstox_substance_id, chemicals_dosed.dsstox_substance_id, studies.test_substance_name_original, series.analyte_name_original, series.conc_medium_normalized, studies.administration_route_normalized)])
-```
+# PMID 6310077 is a tritium tracing of B[a]P and these were given as % of Dose
+# The initial dose was 117 nmol, 2 mCi/kg
+# Molecular Mass of benzo[a]pyrene (C20H12) is 252.316 g/mol
+# The initial dose *I think* is in dose_level_normalized
+cvt_df <- cvt_df %>%
+  mutate(conc = ifelse(document_id %in% 38,
+                       conc_original*dose_level_corrected,
+                       conc))
 
-# Missing LOQ for documents_extraction.id 136
+# NTP-CEB C96019 just has a lot of data below LOQ
+# For S0916, there is no > LOQ data for anything but Tamoxifen
+# N-di-butyl phthalate is only good at the iv dose
+# DTXSID2021315 is only good at 1E-4 Dose
+# S0623 Doesn't have any plasma data
+# There is a maybe control sample for hexachlorobenzene (Dose = 0.0 ) ?
 
-This is an NTP study.
-For some reason LOQs were not extracted.
-I looked up the original data and LOQs are noted.
-I will add them here.
-Source: https://cebs.niehs.nih.gov/cebs/test_article/58-08-2 click on "Individual Animal Data" to download spreadsheet.
-The LOQs are stated in comments like "XX is less than YYY, the ELOQ for [substance]."
+# Give N-desmethyltamoxifen it's due DTXSID501315924
+cvt_df <- cvt_df %>%
+  mutate(analyte_dtxsid = ifelse(
+    analyte_name_original %in% "N-desmethyltamoxifen",
+    "DTXSID501315924",
+    analyte_dtxsid
+  ))
 
-```{r}
-cvt_data[documents_extraction.id %in% 136 &
-           series.analyte_name_original %in% "Caffeine",
-         c("series.loq", "series.loq_units") := .(4.00, "ng/mL")]
+cvt_df <- cvt_df %>%
+  mutate(analyte_dtxsid = ifelse(
+    analyte_name_original %in% "Methemoglobin",
+    "DTXSID301056085",
+    analyte_dtxsid
+  ))
 
-cvt_data[documents_extraction.id %in% 136 &
-           series.analyte_name_original %in% "L-Ephedrine",
-         c("series.loq", "series.loq_units") := .(4.44, "ng/mL")]
+# Standardizing the names (example: glucuronide had two entries)
+cvt_df <- cvt_df %>%
+  mutate(analyte_name_original = tolower(analyte_name_original))
 
-cvt_data[documents_extraction.id %in% 136 &
-           series.analyte_name_original %in% "Pseudoephedrine",
-         c("series.loq", "series.loq_units") := .(4.43, "ng/mL")]
-```
+# Eliminate study that gave chemical each day, not single dose
+# This may be used in another type of model, but right now we deal with single bolus
+# Only include those that have NA or 1 for dose frequency
+cvt_df <- cvt_df %>%
+  filter(dose_frequency %in% c("1", NA))
 
-## Missing LOQ for documents_extraction.id 138
+# Normalize LOQ units
+cvt_df <- cvt_df %>%
+  mutate(loq = ifelse(
+    loq_units %in% c("ug/L", "ng/mL"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
+# Normalize conc_sd and conc units manually
+cvt_df <- cvt_df %>%
+  mutate(conc_sd_normalized = case_when(
+    conc_units_original %in% c("ug/L", "ng/mL", "ng-Eq/mL", "ng/g tissue") ~ conc_sd_original*1E-3,
+    conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
+    conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
+    .default = conc_sd_original
+  ))
+# Need to normalize the ng-eq/mL sample, conc is generally already normalized
+cvt_df <- cvt_df %>%
+  mutate(conc = case_when(
+    conc_units_original %in% c("ng-eq/mL") ~ conc_original*1E-3,
+    .default = conc
+  ))
 
-```{r}
-cvt_data[documents_extraction.id %in% 138 &
-           series.analyte_name_original %in% "Pentachloroanisole",
-         c("series.loq", "series.loq_units") := .(0.05, "ug/mL")]
+cvt_df <- cvt_df %>%
+  dplyr::filter(!(analyte_dtxsid %in% c("DTXSID501315924",
+                                      "DTXSID10169854",
+                                      "DTXSID2021103") )) # These only have 1 or 2 values
+
+# More notes:
+# DTXSID6020438 & DTXSID0020868 rat is from water (top) and oil (bottom curve) gavage
 
@@
 
-## Missing LOQ for documents_extraction.if 178
-
-See https://ntp.niehs.nih.gov/publications/reports/tr/500s/tr526/index.html?utm_source=direct&utm_medium=prod&utm_campaign=ntpgolinks&utm_term=tr526abs Appendix F
-
-LOQ in blood for rat was 30 pg/mL. (Individual animal data refers to plasma, but the PDF report refers to blood?)
+Save the pulled CVT data with the edits/normalizations, and also save the current date.
 
 ```{r}
-cvt_data[documents_extraction.id %in% 178 &
-          series.analyte_name_original %in% "2,3,4,7,8-pentachlorodibenzofuran" &
-           series.conc_medium_normalized %in% "plasma",
-         c("series.loq", "series.loq_units") := .(30, "pg/mL")]
+cvt_date <- Sys.Date()
+save(cvt_df, file = "data/cvt.rda", compress = "bzip2")
+save(cvt_date, file = "data/cvt_download_date.rda")
 ```
-
-# Normalize LOQ units to mg/L
-
-```{r}
-cvt_data[, unique(series.loq_units)]
-```
-
-```{r}
-cvt_data[, series.loq := as.numeric(series.loq)]
-cvt_data[series.loq_units %in% "ug/L", series.loq_normalized := series.loq * 1e-3]
-cvt_data[trimws(series.loq_units) %in% "ug/mL", series.loq_normalized := series.loq]
-cvt_data[series.loq_units %in% "mg/L", series.loq_normalized := series.loq]
-cvt_data[series.loq_units %in% "ng/mL", series.loq_normalized := series.loq * 1e-3]
-cvt_data[series.loq_units %in% "pg/mL", series.loq_normalized := series.loq * 1e-6]
-```
-
-For that with nmol/L we will need the molecular weight.
-For items with units ug we would need the volume of media analyzed.
-Both of these are for inhalation data, though, which we aare not analyzing right now.
-So I will leave it alone for now.
-
-# Concentration SD
-
-These have not been normalized so we need to do it now.
-
-```{r}
-cvt_data[!is.na(conc_time_values.conc_sd_original), unique(series.conc_units_original)]
-```
-
-```{r}
-cvt_data[series.conc_units_original == "ug/L",
-         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-3]
-
-cvt_data[series.conc_units_original == "ug/mL",
-         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original]
-
-cvt_data[series.conc_units_original == "mg/L",
-         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original]
-
-cvt_data[series.conc_units_original == "ug/dL",
-         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-4]
-
-cvt_data[series.conc_units_original == "ng/mL",
-         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-3]
-
-cvt_data[series.conc_units_original == "pg/mL",
-         conc_time_values.conc_sd_normalized := conc_time_values.conc_sd_original * 1e-6]
-
-```
-
-We don't have any cases for oral/IV in blood/plasma where concentration lower/upper bounds are given, so we won't worry about normalizing these bounds right now.
-
-```{r}
-cvt_data[!is.na(conc_time_values.conc_upper_bound_original) & studies.administration_route_normalized %in% c("oral", "iv") & series.conc_medium_normalized %in% c("blood", "plasma")]
-```
-
-Save the pulled CVT data with the edits/normalizations
-
-```{r}
-this_date <- "2023_01_05"
-write.csv(cvt_data,
-          paste0("../inst/ext/cvt_data_",
-          this_date,
-          ".csv"),
-          row.names = FALSE)
-```

### 2023-10-05 data-raw/batchMode_trial_gpm.Rmd
Major reorganization of vignette to specify how each figure in manuscript was made.

@@
 devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
-library(DBI)
+library(cowplot)
+library(RColorBrewer)
 tidyverse_conflicts()
+# Note I have now saved the RDS file for JOINT model with L-BFGS-B
+my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
 ```
@@
 4. Analysis Plots  
-  - CvTdb replicate variation (Figure 5)  
-  - CvTdb replicate variation over ADME-normalized time (Figure 5B)  
+  - CvTdb replicate variation (Figure 4A)  
+  - CvTdb replicate variation over ADME-normalized time (Figure 4B)  
   - CvTdb concentration and final time-point distributions (Supplementary Figure 1)  
-  - invivoPKfit fit option selection (Figure 6)  
+  - invivoPKfit fit option selection (Supplementary Table 1)  
   - invivoPKfit model performance (Supplementary Figure 2)  
-  - Model performance vs Data variability (Figure 7A)  
-  - Goodness of fit plots (Figure 7B)  
+  - Model performance vs Data variability (Figure 5)  
+  - Goodness of fit plots (Figure 6)  
   - Fits that may be improved (Supplementary Figure 3)  
@@
   - Chemicals included  
-  - Comparison of derived TK stats  (Figure 8)
+  - Comparison of derived TK stats  (Figure 7A)  
+  - Histograms for Steady-state Volume of Dist. and Total Clearance (Supplemental Figure 4)
 6. Benchmarking invivoPKfit
-  - Parallelization speeds up the process of fitting (Supplementary Figure 4)
+  - Parallelization speeds up the process of fitting (Supplementary Figure 5)
 
 ## Pulling data from CvTdb
-This is largely taken from a `Querying CvTdb` vignette from Taylor Wall.
-
-```{r query_functions}
-
-postgreSQL_connection <- function() {
-  return(
-    dbConnect(RPostgreSQL::PostgreSQL(),
-              user = Sys.getenv("CVT_USER"),
-              password = Sys.getenv("CVT_PASS"),
-              host = Sys.getenv("CVT_HOST"),
-              dbname = Sys.getenv("CVT_DB_NAME"))
-  )
-}
-
-query_db <- function(query = NULL, schema) {
-  if (is.null(query)) return(cat("\nMust provide a query to send"))
-  con <- postgreSQL_connection()
-
-  query_result <- tryCatch(
-    return(dbGetQuery(con, query %>%
-                        gsub("FROM ", paste0("FROM ", schema, "."), .) %>%
-                        gsub("JOIN ", paste0("JOIN ", schema, "."), .))),
-  error = function(cond){ 
-    cat(paste0("\nError message: ", cond))
-    return(NULL)
-  },
-  finally = { 
-    dbDisconnect(con)
-    }
-    )
-  return(query_result)
-}
-
-```
-
-The following is the new SQL query, this will eventually be moved another vignette.
-
-```{r SQL_queries}
-# Sample query of CvTdb Documents SQL
-# query <- "SELECT pmid, year, first_author, title FROM documents LIMIT 10"
-# query <- "SELECT count(*) FROM studies"
-# query <- "SELECT DISTINCT administration_route_normalized FROM studies"
-
-# Need to make this in a specified ordered
-# First all IDs (so I can check them quickly)
-# Note that this uses an ALIAS for each table which is later specified in
-# the FROM and LEFT JOIN statments
-query <- paste0(
-  "SELECT distinct ",
-  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
-  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
-  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
-  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
-  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
-  "b.loq, b.loq_units, b.n_subjects_in_series, ",
-  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
-  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
-  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
-  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
-  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",
-
-  # Main Table
-  "FROM conc_time_values a ",
-
-  # Join with series table by series ID
-  "LEFT JOIN series b ON b.id = a.fk_series_id ",
-
-  # Join to studies table by study ID
-  "LEFT JOIN studies c ON c.id = b.fk_study_id ",
-
-  # Join to subjects table by subject ID
-  "LEFT JOIN subjects d ON d.id = b.fk_subject_id ",
-
-  # Join to documents table by extraction document ID
-  "LEFT JOIN documents e ON e.id = c.fk_extraction_document_id ",
-
-  # Filtering steps
-  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
-  "c.administration_route_normalized IN ('iv', 'oral')"
-)
-
-sql_query <- query_db(query = query,
-         schema = "cvt")
-
-names(sql_query)
-# Need to change column names for this
-{
-  names(sql_query)[1] <- "conc_time_id"
-  names(sql_query)[8] <- "series_id"
-  names(sql_query)[22] <- "study_id"
-  names(sql_query)[34] <- "subject_id"
-  names(sql_query)[41] <- "document_id"
-}
-
-# Harmonize values for easier analysis
-sql_query <- sql_query %>%
-  mutate(
-    species = tolower(species),
-    sex = tolower(sex),
-    loq = as.numeric(loq),
-    n_subjects_in_series = as.numeric(n_subjects_in_series),
-    dose_level_normalized = as.numeric(dose_level_normalized),
-    dose_level_original = as.numeric(dose_level_original),
-    dose_volume_units = str_extract(dose_volume,
-                                    pattern = "(?<=[:space:]).+"),
-    dose_volume = as.numeric(str_extract(dose_volume,
-                                         pattern = "^(\\d|\\.)*")),
-    dose_duration_units = str_extract(dose_duration,
-                                      pattern = "(?<=[space]).+"),
-    dose_duration = as.numeric(str_extract(dose_duration,
-                                pattern = "^\\d"))
-  )
-sql_query <- sql_query %>%
-  rename_with(~gsub(pattern = "fk_", replacement = "",
-                         .x), .cols = contains("fk_"))
-
-# Copying
-cvt_df <- sql_query # Copy so I don't have to do query again to reset any errors
-
-# Check other_study_identifier == S0916 so that it has dose_level_original_units == ug/mL
-cvt_df %>% filter(other_study_identifier == "S0916") %>%
-  pull(dose_level_original_units) %>% unique()
-# There are still columns that are mg/kg... changing these to ug/mL
-cvt_df <- cvt_df %>% mutate(
-  dose_level_original_units = ifelse(
-    other_study_identifier == "S0916",
-    "ug/mL",
-    dose_level_original_units
-  )
-)
-
-# Need to convert the units to mg/kg
-# In pulling_oral_iv_data_cvtdb.Rmd, it is noted that oral was 5mL/kg and iv 2mL/kg
-# So I need to do ug/mL * mL/kg * 1mg/1000ug = mg/kg
-cvt_df <- cvt_df %>%
-  mutate(
-    dose_level_corrected = ifelse(
-      other_study_identifier %in% "S0916",
-      ifelse(administration_route_normalized %in% "oral",
-             dose_level_original * 5/1000,
-             dose_level_original * 2/1000),
-      dose_level_normalized),
-    dose_level_corrected_units = "mg/kg",
-    .after = dose_level_original_units)
-
-# For this study, it was in ng/kg not mg/kg
-cvt_df <- cvt_df %>%
-  mutate(
-    dose_level_corrected = ifelse(
-      other_study_identifier %in% "S0624",
-      dose_level_original * 1E-6,
-      dose_level_normalized),
-    .after = dose_level_original_units)
-
-# The following measured C-14/H-3 but are indicators for the following Chemicals
-# document_id = 65, DTXSID = DTXSID7031290, name = Isocyclemone E or beta-OTNE
-# document_id = 61, DTXSID = DTXSID4022527, DTXSID3020209,
-### name(s) = propylparaben, butylparaben, missing...methylparaben
-# Propylparaben SERIES_ID = 110, Butylparaben SERIES_ID = 112
-# For above, HPLC reviealed a single peak corresponding with p-hydroxybenzoic acid (PHBA, DTXSID3026647)
-# document_id = 46, DTXSID = DTXSID2020139, name = benzo[a]pyrene
-# document_id = 31, DTXSID = DTXSID2020139, name = benzo[a]pyrene
-
-# However, now would be good time to eliminate any ones where they analyte != test chemical
-# Some studies may have dosed with multiple chemicals... important to note
-# cvt_df <- cvt_df %>% filter(analyzed_chemical_id == test_chemical_id)
-# For now, I will change the chemical name and dtxsid
-cvt_df <- cvt_df %>%
-  mutate(analyte_dtxsid = ifelse(document_id %in% 65, "DTXSID7031290",
-                                 analyte_dtxsid),
-         analyte_name_original = ifelse(document_id %in% 65, "beta-OTNE",
-                                        analyte_name_original)) %>%
-  mutate(analyte_dtxsid = ifelse(document_id %in% 61,
-                                 case_when(
-                                   series_id %in% 110 ~ "DTXSID4022527",
-                                   series_id %in% 112 ~ "DTXSID3020209",
-                                   .default = analyte_dtxsid
-                                 ),
-                                 analyte_dtxsid),
-         analyte_name_original = ifelse(document_id %in% 61,
-                                 case_when(
-                                   series_id %in% 110 ~ "Propylparaben",
-                                   series_id %in% 112 ~ "Butylparaben",
-                                   .default = analyte_name_original
-                                 ),
-                                 analyte_name_original)
-         ) %>%
-  mutate(analyte_dtxsid = ifelse(document_id %in% c(46, 31),
-                                 "DTXSID2020139",
-                                 analyte_dtxsid),
-         analyte_name_original = ifelse(document_id %in% c(46, 31),
-                                        "benzo[a]pyrene",
-                                        analyte_name_original))
-
-# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine were dosed
-cvt_df <- cvt_df %>%
-  mutate(loq = ifelse(
-    other_study_identifier %in% "S0976",
-    case_when(
-      analyte_name_original %in% "Caffeine" ~ 4.00,
-      analyte_name_original %in% "L-Ephedrine" ~ 4.44,
-      analyte_name_original %in% "Pseudoephedrine" ~ 4.43
-    ),
-    loq),
-    loq_units = ifelse(
-      other_study_identifier %in% "S0976",
-      "ng/mL",
-      loq_units
-    ))
-
-# Some pentachloranisole studies
-# S0361 seems to have some data that has not been extracted (also for mouse)
-cvt_df <- cvt_df %>%
-  mutate(loq = case_when(
-    other_study_identifier %in% "S0361" ~ 0.05,
-    other_study_identifier %in% "S0328" ~ 1, # This is inferred
-    # Highest value under loq is 0.9
-    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
-    .default = loq
-  ),
-  loq_units = case_when(
-    other_study_identifier %in% "S0361" ~ "ug/mL",
-    other_study_identifier %in% "S0328" ~ "ug/mL",
-    .default = loq_units
-  ))
-
-# Checking if entire groups of data are NA for conc and loq
-# Really only eliminates Tamoxifen
-# cvt_df %>%
-#   # filter(analyte_dtxsid %in% "DTXSID1034187") %>%
-#   group_by(analyte_dtxsid, document_id, 
-#                     administration_route_normalized,
-#                     conc_medium_normalized,
-#                     species, dose_level_corrected) %>%
-#   filter(all(is.na(conc) & is.na(loq))) %>% 
-#   distinct(analyte_dtxsid, document_id, analyte_name_original,
-#                     administration_route_normalized,
-#                     conc_medium_normalized,
-#                     species, dose_level_corrected) %>% View()
-
-# Checking individual chemicals
-# cvt_df %>%
-#   filter(analyte_dtxsid %in% "DTXSID2020682") %>%
-#   distinct(analyte_dtxsid, document_id, 
-#                     administration_route_normalized,
-#                     conc_medium_normalized,
-#                     species, dose_level_corrected)
-
-# PMID 6310077 is a tritium tracing of B[a]P and these were given as % of Dose
-# The initial dose was 117 nmol, 2 mCi/kg
-# Molecular Mass of benzo[a]pyrene (C20H12) is 252.316 g/mol
-# The initial dose *I think* is in dose_level_normalized
-cvt_df <- cvt_df %>%
-  mutate(conc = ifelse(document_id %in% 38,
-                       conc_original*dose_level_corrected,
-                       conc))
-
-# NTP-CEB C96019 just has a lot of data below LOQ
-# For S0916, there is no > LOQ data for anything but Tamoxifen
-# N-di-butyl phthalate is only good at the iv dose
-# DTXSID2021315 is only good at 1E-4 Dose
-# S0623 Doesn't have any plasma data
-# There is a maybe control sample for hexachlorobenzene (Dose = 0.0 ) ?
-
-# Filter by whether at each dose, there are no LOQ or Concentration value reported
-# This is the threshold for Minimally Informative Data in our use case.
-cvt_df %>%
-  group_by(analyte_dtxsid, document_id, 
-                    administration_route_normalized,
-                    conc_medium_normalized,
-                    species, dose_level_corrected) %>%
-  filter(!all(is.na(conc) & is.na(loq))) %>%
-  distinct(analyte_dtxsid, species,) %>% nrow() # Says there are 433 distinct
-
-cvt_df <- cvt_df %>%
-  group_by(analyte_dtxsid, document_id, 
-                    administration_route_normalized,
-                    conc_medium_normalized,
-                    species, dose_level_corrected) %>%
-  filter(!all(is.na(conc) & is.na(loq)))
-
-# Give N-desmethyltamoxifen it's due DTXSID501315924
-cvt_df <- cvt_df %>%
-  mutate(analyte_dtxsid = ifelse(
-    analyte_name_original %in% "N-desmethyltamoxifen",
-    "DTXSID501315924",
-    analyte_dtxsid
-  ))
-
-cvt_df <- cvt_df %>%
-  mutate(analyte_dtxsid = ifelse(
-    analyte_name_original %in% "Methemoglobin",
-    "DTXSID301056085",
-    analyte_dtxsid
-  ))
-
-# Standardizing the names (example: glucuronide had two entries)
-cvt_df <- cvt_df %>%
-  mutate(analyte_name_original = tolower(analyte_name_original))
-
-# Eliminate study that gave chemical each day, not single dose
-# This may be used in another type of model, but right now we deal with single bolus
-# Only include those that have NA or 1 for dose frequency
-cvt_df <- cvt_df %>%
-  filter(dose_frequency %in% c("1", NA))
-
-# Normalize LOQ units
-cvt_df <- cvt_df %>%
-  mutate(loq = ifelse(
-    loq_units %in% c("ug/L", "ng/mL"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
-# Normalize conc_sd and conc units manually
-cvt_df <- cvt_df %>%
-  mutate(conc_sd_normalized = case_when(
-    conc_units_original %in% c("ug/L", "ng/mL", "ng-Eq/mL", "ng/g tissue") ~ conc_sd_original*1E-3,
-    conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
-    conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
-    .default = conc_sd_original
-  ))
-# Need to normalize the ng-eq/mL sample, conc is generally already normalized
-cvt_df <- cvt_df %>%
-  mutate(conc = case_when(
-    conc_units_original %in% c("ng-eq/mL") ~ conc_original*1E-3,
-    .default = conc
-  ))
-
-cvt_df <- cvt_df %>%
-  dplyr::filter(!(analyte_dtxsid %in% c("DTXSID501315924",
-                                      "DTXSID10169854",
-                                      "DTXSID2021103") )) # These only have 1 or 2 values
-
-# More notes:
-# DTXSID6020438 & DTXSID0020868 rat is from water (top) and oil (bottom curve) gavage
-
-```
+
+See `pulling_iv_oral_cvtdb.Rmd`.
 
@@
 
-### PK OBJECT ###----
+### Minimal PK Object ###----
 # Minimum pk object, add options later
+# Note that these mappings are now a default mappings, just being verbose here.
 minimal_pk <- pk(data = cvt_df,
@@
 ### Evaluations-----
-my_pk_000p <- do_fit(my_pk_000p, n_cores = 14) 
-my_pk_000p <- my_pk_000p %>% evaluate_choices() # Done
+my_pk_000p <- do_fit(my_pk_000p, n_cores = 14)  %>% evaluate_choices() # Done
 my_pk_100p <- do_fit(my_pk_100p, n_cores = 8) %>% evaluate_choices() # Done
@@
 amount of error in predictions and derived TK stats.
-
-```{r Standard_Settings}
-# Full option setting
-my_pk <- pk(data = cvt_df,
-            mapping = ggplot2::aes(
-              Chemical = analyte_dtxsid,
-              Chemical_Name = analyte_name_original,
-              DTXSID = analyte_dtxsid,
-              CASRN = analyte_casrn,
-              Species = species,
-              Reference = document_id,
-              Media = conc_medium_normalized,
-              Route = administration_route_normalized,
-              Dose = dose_level_normalized,
-              Dose.Units = "mg/kg",
-              Subject_ID = subject_id,
-              Series_ID = series_id,
-              Study_ID = study_id,
-              ConcTime_ID = conc_time_id,
-              N_Subjects = n_subjects_in_series,
-              Weight = weight_kg,
-              Weight.Units = "kg",
-              Time = time_hr,
-              Time.Units = "hours",
-              Value = conc,
-              Value.Units = "mg/L",
-              Value_SD = conc_sd_normalized,
-              LOQ = loq
-            )) +
+In addition, _L-GFGS-B_ was the optimizer of choice
+
+```{r Final_Options}
+my_pk <- minimal_pk +
   facet_data(vars(Chemical, Species)) +
   settings_preprocess(keep_data_original = TRUE,
-                      suppress.messages = FALSE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B")) +
   scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
   stat_error_model(error_group = vars(Chemical, Species, Reference))
+
 my_pk <- do_preprocess(my_pk)
-my_data <- get_data(my_pk)
-
-```
-
-An aside: working with one DTXSID + Species combination
-
-The first step is understanding how to work with a single DTXSID + Species combination.
-Once we know how to do this, it will be easier to apply it to (potentially)
-a list of these objects in a vectorized fashion.
-Here I subset the `cvt` object and use that as my working data.
-
-```{r data_loading}
-# There are 103 unique chemicals in this object
-cvt %>% pull(chemicals_analyzed.dsstox_substance_id) %>%
-  unique() %>%
-  length()
-
-# easy fit
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID5020732")
-
-```
-
-Next, I want to follow the steps required for the particular analysis I would like.
-In this instance, I set the optimizer to "L-BFGS-B" and dose-normalize the output.
-I do not scale the time or log-transform the concentration values.
-Since I would like to do a "Pooled" analysis,
-I set the `error_group = vars(Chemical, Species)`.
-
-```{r single_fit}
-my_pk_original <- minimal_pk +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = FALSE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
-# Add Reference for Joint Analysis
-
-my_pk_original <- do_preprocess(my_pk_original)
+cvt_DTXSIDs <- unique(my_pk$data$Chemical)
 
@@
 my_pk <- do_prefit(my_pk) # needs reframe somewhere
-# Timing for normal fit sapply
+
+{
+  start <- Sys.time()
   my_pk <- do_fit(my_pk, 
                   n_cores = 12)
-my_pk <- do_fit(my_pk)
+  round(Sys.time() - start, 4)
+}
 
@@
 
-### Figure 5A: Replicated timepoint variation in CvTdb
-
-### Figure 5B: Variation over time in CvTdb data
-
-### Supplementary Figure 1: Concentration and final time-points have wide range
-
-### Figure 6: Selecting best fitting options for CvTdb data
-
-### Supp Figure 2: invivoPKfit model performance
-
-### Figure 7A: Model performance vs Data Variability
-
-### Figure 7B: Multiple goodness-of-fit metrics validate model performance
-
-### Supp. Fig. 3: Fits that may be improved with other settings
-
-### Figure 8: Comparing derived TK stats with human TK stats from Lombardo et al.
-
-### Supp. Fig. 4: Parallelization decreases runtime of invivoPKfit
-
-```{r cvt_analysis}
-my_df %>%
-  ggplot(aes(x = maxT/(24)
-             )) +
-  geom_histogram(fill = "grey5") +
-  scale_x_log10() +
-  scale_y_continuous(expand = c(0, 0), limits = c(0, 30)) +
-  expand_limits(y = 0) +
-  labs(x = "Day of final Timepoint",
-       y = "Count") +
-  theme(aspect.ratio = 1,
-        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        strip.background = element_rect(fill = "white"),
-        strip.text = element_text(face = "bold"),
-        axis.ticks = element_blank(),
-        axis.line = element_blank(),
-        axis.text = element_text(face = "bold"))
-
-```
-
-The purpose of the following code is to generate data.frames with information for
-all 103 chemicals in the `cvt` dataset that comes with `invivopkfit`.
-I will need to do append each dataframe to the last for the outputs of the following
-methods:
-
-- `AIC()`
-- `BIC()` left-joined with `AIC` output
-- `get_tkstats()`
-
-I will also have to fit these iteratively and manage the memory as part of the loop.
-
-```{r allDTXSIDs_analysis}
-
-# after fitting pk object for all cvt objects
-# saveRDS(my_pk_100p, file = "data-raw/all_cvt_pk.rds")
-# saveRDS(my_pk, file = "data-raw/all_cvt_pk_JOINT.rds")
-my_pk <- readRDS("data-raw/all_cvt_pk.rds")
-my_coefs <- coef(my_pk, drop_sigma = FALSE)
-get_winning_model(my_pk) %>%
-  filter(model %in% c("model_2comp"),
-         method == "L-BFGS-B") %>%
-  dplyr::select(Chemical, Species) %>% distinct() %>% nrow()
-all_my_data  %>% dplyr::select(Chemical, Species) %>% distinct() %>% nrow()
-my_AIC <- AIC(my_pk)
-my_tkstats <- get_tkstats(my_pk)
-my_IC <- left_join(AIC(my_pk), BIC(my_pk))
-
-my_IC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "bobyqa") %>%
-  ungroup() %>%
-  count(model)
-# model_1comp 59
-# model_2comp 50
-# model_flat   2
-
-my_IC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>%
-  ungroup() %>%
-  # filter(model == "model_flat") %>% pull(Chemical) %>% unique()
-  count(model)
-# model_1comp 57
-# model_2comp 50
-# model_flat   4
-
-my_preds <- predict(my_pk,
-                    use_scale_conc = TRUE)
-
-winmodels <- my_IC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>%
-  ungroup() %>%
-  dplyr::select(Chemical, Species,
-                method, model)
-
-my_preds <- inner_join(winmodels, my_preds)
-my_tkstats <- inner_join(winmodels, my_tkstats) %>%
-  dplyr::select(-TKstats) %>% distinct()
-my_nca <- get_nca(my_pk,
-                  nca_group = vars(Chemical, Species,))
-my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
-  pivot_wider(names_from = param_name,
-              values_from = param_value)
-
+```{r data_aggregation}
+# Need the following data for any of the subsequent plots
+
+# after fitting pk object for all cvt objects or reading the fitted pk object in `setup`
+winmodel <- get_winning_model(my_pk)
+my_preds <- inner_join(predict(my_pk, use_scale_conc = TRUE), winmodel)
+my_residuals <- residuals(my_pk, use_scale_conc = FALSE) %>%
+  inner_join(winmodel)
+my_tkstats <- eval_tkstats(my_pk)
+my_nca <- get_nca(my_pk)
 all_my_data <- get_data(my_pk)
+
+fe_df <- fold_errors(my_pk, method = "L-BFGS-B") %>% inner_join(winmodel)
+# May need to change the use_scale_conc defaults
+r2_df <- rsq(my_pk, method = "L-BFGS-B", use_scale_conc = FALSE) %>%
+  inner_join(winmodel)
+myAIC <- AIC(my_pk, method = "L-BFGS-B") %>%
+  inner_join(winmodel)
+myRMSE <- rmse(my_pk, method = "L-BFGS-B",
+               rmse_group = vars(Route, Media, Dose),
+               use_scale_conc = FALSE) %>% 
+  inner_join(winmodel)
+
+# Something wrong with the summary method... maybe only use detects?
+fold_errors_all <- fe_df %>%
+  dplyr::filter(Detect %in% TRUE) %>%
+  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
+  dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
+                median_FoldErr = median(Fold_Error, na.rm = TRUE),
+                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error))
+
+myRMSE_all <- myRMSE %>%
+  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
+  dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE),
+                median_MSE = median(RMSE^2, na.rm = TRUE))
+
+```
+
+### Figure 4A: Replicated timepoint variation in CvTdb
+```{r fig4A}
+
 all_my_data %>%
@@
   {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
-# 88.9% inside twofold ## New CvT extraction: 91.3%
-# 2.2%  above twofold  ## 1.7%
-# 8.8%  below twofold  ## 7.0%
-# 
-#
-
-all_my_data %>%
+# Stats for ALL | ORAL | IV
+# 88.64% inside twofold | 87.20%  | 91.23%
+# 2.23%  above twofold  | 2.52%   | 1.70%
+# 9.11%  below twofold  | 10.25%  | 7.04%
+
+pl5A <- all_my_data %>%
   filter(Detect %in% TRUE,
@@
   ggplot(aes(x = foldConc)) +
-  geom_histogram(binwidth = 0.1,
-                 fill = "grey5") +
+  geom_histogram(binwidth = 0.2,
+                 fill = "grey5",
+                 color = "grey5",
+                 linewidth = 0.4) +
   coord_cartesian(xlim =  c(0, 4),
-                  ylim = c(0, 2000)) +
-  scale_y_continuous(expand = c(0, 0)) +
+                  ylim = c(0, 4000)) +
+  scale_y_continuous(expand = c(0, 0),
+                     breaks = c(0, 1000, 2000, 3000),
+                     labels = c("0", "1", "2", "3")) +
   expand_limits(y = 0) +
   geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
-  # annotate(geom= "text",
-  #          x = 1.25, y = 1800,
-  #          label = "88.9% of Observations\n within a factor of 2") +
   theme_classic() +
-  labs(x = "Concentration Normalized to Average",
-                y = "Number of Observations") +
-  theme(panel.border = element_rect(color = "black", fill = NA),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))
+  labs(x = "Mean-normalized\nconcentration",
+                y = "Observations\n(thousands)") +
+  theme(text = element_text(size = 10),
+        panel.border = element_rect(color = "black", linewidth = 1, fill = NA),
+        panel.background = element_blank(),
+        panel.grid.major.y = element_line(color = "grey90", linewidth = 0.4),
+        axis.title = element_text(face = "bold"),
+        axis.line = element_blank(),
+        plot.background = element_blank(),
+        axis.ticks.y = element_blank())
 
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "NormalizedConcentrations_2023-09-21.png"),
-       height = 3.5,
-       width = 5.5,
-       units = "in")
-
-all_my_data %>%
+              "NormalizedConcentrations_2023-09-29.png"),
+       plot = pl5A,
+       height = 2.2,
+       width = 2.5,
+       units = "in",
+       device = "png",
+       dpi = 300)
+
+```
+
+### Figure 4B: Variation over time in CvTdb data
+
+```{r fig4B-cowplot}
+
+pl5B <- all_my_data %>%
   group_by(Chemical,
@@
                             Route, Media,
-                            tmax) %>%
+                            tmax = tmax.nca) %>%
               filter(!is.na(tmax))) %>%
@@
   geom_vline(xintercept = 1, color = "blue",
-             size = 1, linetype = "dashed") +
+             linewidth = 0.8, linetype = "dashed") +
   geom_vline(xintercept = 2, color = "green4",
-             size = 1, linetype = "dashed") +
+             linewidth = 0.8, linetype = "dashed") +
   geom_hline(yintercept = c(0.5, 2), color = "red3",
-             size = 1, linetype = "dashed") +
+             linewidth = 0.8, linetype = "dashed") +
   facet_grid(cols = vars(Route),
-             rows = vars(Species),
              scales = "free_x") +
   labs(x = "ADME-Normalized Time",
-       y = "Mean-Normalized Concentration") +
-  theme(aspect.ratio = 1,
-        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+       y = "Mean-Normalized\nConcentration") +
+  theme(text = element_text(size = 10),
+        panel.border = element_rect(color = "black", fill = NA, size = 1),
         panel.background = element_blank(),
@@
         axis.text.x = element_blank(),
+        axis.title = element_text(face = "bold"),
+        panel.spacing = unit(0.125, units = "in"),
+        plot.background = element_blank(),
         legend.position = "none")
@@
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "ADME_NormalizedTime-NormalizedConcentrations_onlyDetects_2023-09-21.png"),
+              "ADME_NormTime-NormConcs_onlyDetects_2023-09-29.png"),
        height = 4,
+       width = 5,
+       units = "in",
+       dpi = 300)
+
+# Make the Combination Plot----
+
+plot_grid(pl5A, pl5B, labels = c("A", "B"),
+                     align = "h", axis = "bt", rel_widths = c(1, 1.5))
+
+figure5 <- plot_grid(pl5A, pl5B, labels = c("A", "B"),
+                     align = "h", axis = "bt", rel_widths = c(1, 1.5))
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "Figure5_onlyDetects_2023-10-02.png"),
+       plot = figure5,
+       bg = "white",
+       height = 3.25,
+       width = 6.5,
+       units = "in",
+       dpi = 300)
+
+```
+
+### Supp. Figure 1: Concentration and final time-points have wide range
+
+```{r cvt_analysis}
+data_range <- all_my_data %>%
+  filter(Detect) %>%
+  group_by(Chemical, Species, Reference, Media, Route, Dose, Dose.Units) %>%
+  summarize(maxT = max(Time)/24,
+         concRange = log10(max(Conc)/min(Conc))) %>%
+  ungroup()
+
+sf_2B <- data_range %>%
+  ggplot(aes(x = maxT)) +
+  geom_histogram(fill = "grey5",
+                 bins = 40,
+                 color = "grey5") +
+  scale_x_log10(labels = scales::number,
+                breaks = c(0.1, 1, 7, 30, 365)) +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 60),
+                     breaks = c(0, 10, 20, 30, 40, 50)) +
+  labs(x = "Day of final Timepoint",
+       y = "Count") +
+  theme(aspect.ratio = 1,
+        text = element_text(size = 10),
+        panel.border = element_rect(color = "black", fill = NA, size = 1),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "SFig2B_TimePoints_2023-10-02.png"),
+       height = 4,
+       width = 4,
+       units = "in",
+       dpi = 300)
+
+sf_2A <- data_range %>%
+  ggplot(aes(x = concRange)) +
+  geom_histogram(fill = "grey5",
+                 bins = 40,
+                 color = "grey5") +
+  scale_y_continuous(expand = c(0, 0),
+                     limits = c(0, 25),
+                     breaks = c(0, 5, 10, 15, 20)) +
+  labs(x = "log10(Concentration Range)",
+       y = "Count") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 11))
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "SFig2A_ConcRange_2023-09-29.png"),
+       height = 4,
+       width = 4,
+       units = "in",
+       dpi = 300)
+
+plot_grid(sf_2A, sf_2B, labels = "AUTO", align = "h", axis = "bt")
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "SFig2_ConcTimeRanges_2023-10-02.png"),
+       height = 3.25,
        width = 6,
@@
 
-# Per chemical + Species average mean normalized concentration variability over time
-all_my_data %>%
-  group_by(Chemical,
-           Species,
-           Reference,
-           Route,
-           Dose, Time) %>%
-  filter(n() > 1,
-         sum(is.na(Conc)) != n(),
-         LOQ < Conc,
-         exclude == FALSE) %>%
-  mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%
-  ungroup() %>%
+```
+
+### Supp Figure 2: invivoPKfit model performance
+
+```{r sFig2-model_performance}
+my_preds %>%
+  right_join(winmodel) %>%
   rowwise() %>%
-  mutate(foldConc = Conc / meanConc) %>%
-  inner_join(my_tkstats %>%
-              dplyr::select(Chemical, Species,
-                            Route, Media,
-                            tmax) %>%
-              filter(!is.na(tmax))) %>%
-  group_by(Chemical, Species, Route, Media, Dose) %>%
-  summarize(sdFC = sd(foldConc)) %>%
-  mutate(maxDose = max(Dose),
-         minDose = min(Dose)) %>%
-  ungroup() %>%
-  add_count(Dose, name = "Unique_Doses") %>%
-  filter(Unique_Doses == 1) %>%
-  arrange(desc(sdFC))
-
-my_tkstats %>%
-              dplyr::select(Chemical, Species,
-                            Route, Media, model, method,
-                            tmax) %>%
-              filter(!is.na(tmax))
-
-all_my_data %>%
-              dplyr::select(Chemical, Species,
-                            Route, Media, Dose,
-                            Reference) %>%
-  distinct() %>% nrow()
-
-my_preds <- predict(my_pk,
-                    use_scale_conc = TRUE)
-
-winmodels <- get_winning_model(my_pk)
-
-my_preds <- inner_join(winmodels, my_preds)
-my_tkstats <- inner_join(winmodels, my_tkstats) %>%
-  dplyr::select(-TKstats) %>% distinct()
-my_nca <- get_nca(my_pk,
-                  nca_group = vars(Chemical, Species,))
-my_nca <- my_nca %>% dplyr::select(-param_sd_z, -param_units) %>%
-  pivot_wider(names_from = param_name,
-              values_from = param_value)
-
-my_preds %>%
+  mutate(Pred_Obs = Conc_trans/Conc_est) %>%
+  filter(is.finite(Pred_Obs),
+         model %in% c("model_1comp", "model_2comp")) %>%
+  # mutate(pass = ifelse(Pred_Obs < 0.5, TRUE, FALSE)) %>%
+  # pull(pass) %>% table()
+  ggplot(aes(x = Pred_Obs)) +
+  geom_histogram(binwidth = 0.5,
+                 fill = "grey5") +
+  scale_x_log10(limits = c(NA, 1E6)) +
+  expand_limits(y = 0) +
+  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
+  facet_grid(cols = vars(model),
+             rows = vars(Route)) +
+  labs(x = "Dose-normalized\nPredicted/Observed",
+       y = "Number of Observations") +
+  theme_classic() +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))
+
+# 91.1% of Pred_Obs are finite
+# 16.6% Are below two-fold
+# 33.2%  Are above two-fold
+# 50.2% Are within twofold
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "PredictedObserved_compartmentModels_2023-10-02.png"),
+       height = 6, width = 6)
+
+```
+
+### Figure 5: Model performance vs Data Variability
+
+```{r fig5-modelPerform-v-dataVar}
+
+pl_7A <- my_preds %>%
   group_by(Chemical,
@@
   # ungroup() %>%
-  # count(!(foldPred >= 0.5 & foldPred <= 2) &
-  #         !(foldConc >= 0.5 & foldConc <= 2)) %>%
-  # {.[[2,2]]/(.[[1,2]] + .[[2,2]])}
+  # filter(model %in% c("model_flat")) %>%
+  # count((foldPred >= 0.5 & foldPred <= 2) & !(foldConc >= 0.5 & foldConc <= 2)) %>%
+  # {100*.[[2,2]]/(.[[1,2]] + .[[2,2]])}
   # For Plotting
@@
                        oob = oob_squish) +
-  labs(y = "Model Performance",
+  labs(y = "Model Error",
        x = "Data Variability") +
@@
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "ModelPerformance_vDataVariability_2023-09-21.png"),
-       height = 3.5,
-       width = 7,
+              "ModelPerformance_vDataVariability_2023-10-02.png"),
+       height = 3,
+       width = 6.5,
+       device = "png",
+       dpi = 300,
        units = "in")
 
-# Why are 38-39% of adequate data have models that are too variable?
-# 
-my_preds %>%
-  group_by(Chemical,
-           Species,
-           Route,
-           Dose, Time) %>%
-  filter(n() > 1,
-         sum(is.na(Conc_trans)) != n(),
-         exclude == FALSE,
-         Detect == TRUE) %>%
-  mutate(meanConc = mean(Conc_trans, na.rm = TRUE)) %>%
-  ungroup() %>%
-  rowwise() %>%
-  mutate(foldConc = Conc_trans / meanConc,
-         foldPred = Conc_est / Conc_trans) %>% 
-  # filter(model == "model_2comp") %>%
-  mutate(VAR_DATA = ifelse(
-    (foldPred > 2 | foldPred < 0.5) & (foldConc <= 2 & foldConc >= 0.5),
-    TRUE, FALSE
-  )) %>%
-  group_by(Chemical, Species) %>%
-  mutate(VAR_TRUE = sum(VAR_DATA %in% TRUE),
-         VAR_FALSE = sum(VAR_DATA %in% FALSE)) %>%
-  dplyr::select(-VAR_DATA) %>% distinct() %>%
-  mutate(PERCENT_TRUE = VAR_TRUE/(VAR_TRUE + VAR_FALSE),
-         MAJOR_TRUE = ifelse(PERCENT_TRUE > 0.6, TRUE, FALSE)) %>%
-  # View("Count")
-  ggplot(aes(
-    x = Time,
-    y = Conc_est,
-    color = paste(Chemical, Species),
-    group = paste(Chemical, Species)
+my_table <- data.frame(
+  c("Both within a factor of 2",
+    "Model too variable",
+    "Data too variable",
+    "Both outside a factor of 2"),
+  c(46.3, 39.5, 2.3, 12),
+  c(46, 44, 1.8, 7.4),
+  c(26, 60, 5, 8.5),
+  c(45, 42.7, 2.3, 10))
+
+names(my_table) <- c(" ","1-compartment (%)", "2-compartment (%)", "Flat (%)", "Overall (%)")
+
+library(flextable)
+library(officer)
+
+flextable(my_table) %>%
+  border_inner() %>%
+  fontsize(part = "all", size = 11) %>%
+  bold(part = "all", j = 5)
+
+table_plot <- gen_grob(flextable(my_table) %>%
+                         border_inner() %>%
+                         fontsize(part = "all", size = 10) %>%
+                         bold(part = "all", j = 5) %>%
+                         autofit())
+
+dual_plot <- plot_grid(pl_7A, table_plot, ncol = 1, align = "v",
+          rel_heights = c(1, 0.5))
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "ModelPerformance_vDataVariability_wTable_2023-10-02.png"),
+       plot = dual_plot,
+       height = 4.5,
+       width = 6.5,
+       device = "png",
+       bg = "white",
+       dpi = 300,
+       units = "in")  
+```
+
+### Figure 6: Multiple goodness-of-fit metrics validate model performance
+This should be it's own figure
+
+```{r fig6-goodness-of-fit}
+
+my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE_all)
+
+mypl <- ggplot(data = my_df,
+               aes(
+                 x = within_2fold,
+                 y = Rsq,
+                 color = model
                )) +
   geom_point() +
-  geom_line() +
-  facet_grid(cols = vars(MAJOR_TRUE),
-             rows = vars(model)) +
-  labs(y = "Predicted Concentrations",
-       x = "Time") +
-  # xlim(0, 2000) +
+  geom_abline(slope = 1, color = "red4", linetype = "longdash") +
+  scale_color_manual(values = c("#0398FC", "#D68E09", "black")) +
+  labs(x = "% Fold Error within 2-fold",
+       y = "R-squared value") +
   theme(aspect.ratio = 1,
-        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        strip.background = element_rect(fill = "white"),
-        strip.text = element_text(face = "bold"),
-        legend.position = "none",
-        axis.ticks = element_blank(),
-        axis.line = element_blank())
-
-# Saving some CSVs
-# my_tkstats %>% write_csv(file = "data-raw/Pooled_TKstats.csv")
-# my_nca %>% write_csv(file = "data-raw/NonCompartmentalAnalysis.csv")
-# Loading CSVs
-my_nca <- read_csv(file = "data-raw/NonCompartmentalAnalysis.csv")
-
-my_preds %>%
-  rowwise() %>%
-  mutate(Pred_Obs = Conc_trans/Conc_est) %>%
-  filter(is.finite(Pred_Obs),
-         model %in% c("model_1comp", "model_2comp")) %>%
-  # mutate(pass = ifelse(Pred_Obs < 0.5, TRUE, FALSE)) %>%
-  # pull(pass) %>% table()
-  ggplot(aes(x = Pred_Obs)) +
-  geom_histogram(binwidth = 0.4,
-                 fill = "grey5") +
-  scale_x_log10(limits = c(NA, 1E6)) +
-  expand_limits(y = 0) +
-  geom_vline(xintercept = c(0.5, 2), color = "red3", linetype = "dashed") +
-  facet_grid(cols = vars(model),
-             rows = vars(Route)) +
-  labs(x = "Predicted/Observed",
-       y = "Number of Observations") +
-  theme_classic() +
-  theme(aspect.ratio = 1,
-        panel.border = element_rect(color = "black", fill = NA),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.4))
-
-# 91.1% of Pred_Obs are finite
-# 16.6% Are below two-fold
-# 33.2%  Are above two-fold
-# 50.2% Are within twofold
-
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "PredictedObserved_compartmentModels_2023-07-11.png"),
-       height = 6, width = 7)
-
-# Pooled analysis
-all_my_data %>% group_by(Chemical, Species, Reference, Media, Route) %>%
-  filter(is.finite(Conc)) %>%
-  summarise(OOM = log10(max(Conc) / min(Conc))) %>% 
-  ggplot(aes(x = OOM)) +
-  geom_histogram(bins = 15,
-                 color = NA,
-                 fill = "grey5") +
-  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
-  scale_x_continuous(breaks = c(0, 1, 2, 3, 4, 5)) +
-  labs(x = "Orders of Magnitude per Series\n log10(max/min)",
-       y = "Count") +
-  theme(aspect.ratio = 1,
-        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.border = element_rect(color = "black", fill = NA, size = 1),
         panel.background = element_blank(),
@@
         axis.ticks = element_blank(),
-        axis.line = element_blank())
-
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "OrdersOfMagnitude_2023-07-12.png"),
-       height = 4, width = 4)
-
-my_pk$prefit$fit_check %>% filter(fit_decision == "abort") %>%
-  dplyr::select(model, Chemical) %>% distinct()
-
-all_my_data %>%
-  filter(Chemical == "DTXSID2021781")
-
-my_coefs %>% inner_join(get_winning_model(my_pk)) -> my_coefs
+        axis.line = element_blank(),
+        legend.position = "none",
+        legend.title = element_blank(),
+        legend.key = element_blank())
+panelA_plot <- ggExtra::ggMarginal(mypl, groupFill = TRUE,
+                    type = "histogram",
+                    xparams = list(binwidth = 0.05),
+                    yparams = list(binwidth = 0.05))
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "R2_within2fold_comparison.png"),
+       plot = ggExtra::ggMarginal(mypl, groupFill = TRUE,
+                    type = "histogram",
+                    xparams = list(binwidth = 0.05),
+                    yparams = list(binwidth = 0.05)),
+       height = 5,
+       width = 5,
+       units = "in")
+
+panelB_plot <- ggplot(data = myRMSE %>%
+         mutate(RMSE = ifelse(RMSE == 0, NA, RMSE)),
+               aes(
+                 x = log10(RMSE),
+                 color = model,
+                 fill = model
+               )) + 
+  geom_histogram(bins = 100) +
+  labs(y = "Count") +
+  scale_color_manual(values = c("#0398FC", "#D68E09", "grey10")) +
+  scale_fill_manual(values = c("#0398FC", "#D68E09", "grey10")) +
+  scale_y_continuous(breaks = scales::pretty_breaks(n = 4),
+                     expand = c(0,NA)) +
+  facet_grid(rows = vars(model),
+             cols = vars(Route)) +
+  theme(text = element_text(size = 10),
+        aspect.ratio = 0.6,
+    panel.border = element_rect(color = "black", fill = NA, size = 1),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        strip.background = element_blank(),
+    panel.spacing.y = unit(0.125, units = "in"),
+        legend.position = "bottom",
+        legend.title = element_blank())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RMSEs_winningmodel_LBFGSB_zero1E-6_RouteFacet_notNormalized.png"),
+       height = 4,
+       width = 6,
+       units = "in")
+
+legend <- get_legend(panelB_plot)
+
+plot_grid(plot_grid(panelA_plot,
+                   panelB_plot + theme(legend.position = "none"), labels = c("A", "B"),
+                   axis = "tb", align = "h", rel_heights = c(1,1)), legend,
+          ncol = 1,
+          rel_heights = c(1, 0.1))
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "CombinedPlot_Rsquared_RMSE.png"),
+       height = 4,
+       width = 6.5,
+       bg = "white",
+       units = "in")
+```
+
+### Supp. Fig. 3: Distribution of Sigmas in CvTdb data
+
+```{r sFig3-sigmaDistribution}
+
+my_coefs <- inner_join(get_winning_model(my_pk), coef(my_pk))
 my_coefs %>% inner_join(get_data_summary(my_pk)) -> my_coefs
@@
   labs(x = "Size-normalized Sigma Value",
-       y = "Number of Observations",
-       title = "Distribution of Sigmas in CvTdb data") +
+       y = "Number of Observations") +
   theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
@@
        height = 3, width = 5)
-```
-
-This next set of code is a preliminary attempt at summarizing the TK statistics
-for Pooled and Joint analyses.
-
-```{r update_eval_tkstats}
-devtools::load_all()
-my_pk <- readRDS("data-raw/all_cvt_pk.rds") # This no longer works somehow
-my_eval <- eval_tkstats(my_pk)
-
-# To give summary RMSEs of Cmax and AUC...
-my_eval <- my_eval %>%
-  group_by(method, model, .add = TRUE) %>%
-  ungroup(Reference) %>%
-  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
-                                             na.rm = TRUE)^2)),
-            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
-                                          na.rm = TRUE)^2)),
-            .groups = "keep")
-
-my_eval <- my_eval %>%
-  mutate(dose_norm = TRUE,
-         log10_norm = FALSE,
-         scale_time = FALSE,
-         Analysis_Type = "Pooled")
-
-ggplot(my_eval,
-       aes(x = AUC_inf_RMSE,
-           y = Cmax_RMSE)) +
+
+```
+
+### Figure 7: Comparing derived TK stats with human TK stats from Lombardo et al.
+
+```{r Lombardo_Comparison}
+cvt_DTXSIDs <- unique(my_pk$data$Chemical)
+# First things first, let's load the data from Lombardo et al.
+lombardo <- readxl::read_xlsx(
+  paste0(Sys.getenv("FIG_DIR"),
+         "Lombardo2018-Supplemental_82966_revised_corrected.xlsx"),
+  skip = 8)
+
+l_batch_search <- readxl::read_xlsx(
+  paste0(Sys.getenv("FIG_DIR"),
+         "LombardoBatchSearch_Name.xlsx"),
+  sheet = "Main Data"
+)
+
+l_batch_search <- l_batch_search[c("INPUT", "CASRN","DTXSID")] %>%
+  distinct() %>%
+  right_join(lombardo[c("Name", "CAS #")], by = c("CASRN" = "CAS #", "INPUT" = "Name"))
+
+l_noNamesCASRN <- readxl::read_xlsx(
+  paste0(Sys.getenv("FIG_DIR"),
+         "LombardoBatchSearch_CASRNnoName.xlsx"),
+  sheet = "Main Data"
+) %>%
+  dplyr::select(CASRN = INPUT, DTXSID)
+
+l_curatedDTX <- read_tsv(paste0(Sys.getenv("FIG_DIR"),
+                         "CuratedIDs_lombardo.txt")) %>%
+  rename(INPUT = Name)
+
+l_batch_search <- l_batch_search %>%
+  left_join(l_noNamesCASRN, by = "CASRN") %>%
+  mutate(DTXSID = coalesce(DTXSID.x, DTXSID.y)) %>%
+  dplyr::select(-DTXSID.x, -DTXSID.y) %>%
+  left_join(l_curatedDTX, by = "INPUT") %>%
+  mutate(DTXSID = coalesce(DTXSID.x, DTXSID.y)) %>%
+  dplyr::select(-DTXSID.x, -DTXSID.y)
+# Now all but two of the IDs are unidentified
+
+lombardo <- lombardo %>%
+  right_join(l_batch_search, by = c("Name" = "INPUT"))
+
+lombard_abbr <- lombardo %>% dplyr::select(DTXSID,
+                                           hVss = `human VDss (L/kg)`,
+                                           hCltot = `human CL (mL/min/kg)`,
+                                           halflife = `terminal  t1/2 (h)` ) %>%
+  filter(DTXSID %in% cvt_DTXSIDs)
+
+# 15 chemicals in common with values for both
+lombardo_comparison <- my_tkstats %>%
+  dplyr::select(DTXSID = Chemical, Species,
+                model, Vss.tkstats, CLtot.tkstats) %>%
+  distinct() %>%
+  inner_join(lombard_abbr, by = "DTXSID") %>%
+  filter(!is.na(Vss.tkstats)) %>%
+  arrange(halflife)
+
+comparable_ids <- lombardo_comparison %>% pull(DTXSID)
+
+lombard_abbr <- lombard_abbr %>%
+  mutate(Species = "human", model = "lombardo") %>%
+  rename(Vss = hVss, CLtot = hCltot) %>%
+  mutate(CLtot = CLtot*60/1000) %>% # Lombardo reports this as mL/min/kg, need L/h/kg
+  filter(DTXSID %in% comparable_ids)
+
+lombardo_comparison <- my_tkstats %>%
+  dplyr::select(DTXSID = Chemical, Species,
+                model, Vss.tkstats, CLtot.tkstats, halflife.tkstats) %>%
+  filter(DTXSID %in% comparable_ids) %>%
+  distinct() %>%
+  rename(Vss = Vss.tkstats, CLtot = CLtot.tkstats, halflife = halflife.tkstats) %>%
+  bind_rows(lombard_abbr) %>%
+  mutate(model = ifelse(str_detect(model, "^model"), "invivoPKfit", model),
+         DTXSID = factor(DTXSID, levels = unique(comparable_ids)))
+
+lombardo_comparison %>%
+  pivot_longer(cols = c("Vss", "CLtot", "halflife")) %>%
+  mutate(name = factor(name, levels = c("halflife", "Vss", "CLtot"))) %>%
+  ggplot(mapping = aes(
+    x = value,
+    y = DTXSID
+  )) +
+  geom_point(aes(color = model,
+                 shape = Species),
+             position = position_dodge(0.7),
+             size = 5/.pt, stroke = 2.5/.pt) +
+  facet_grid(cols = vars(name),
+             scales = "free_x") +
+  scale_shape_manual(values = c(21, 22, 24),
+                     breaks = c("human", "dog", "rat")) +
+  scale_color_manual(values = c("black", "#1064c9")) +
+  guides(color = guide_legend(override.aes = list(shape = 21),
+                              nrow = 2,
+                              title.position = "top",
+                              title.hjust = 0.5),
+         shape = guide_legend(nrow = 1,
+                              title.position = "top",
+                              title.hjust = 0.5)) +
+  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold", size = 12),
+        text = element_text(size = 10),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text = element_text(face = "bold"),
+        axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        legend.position = "bottom",
+        legend.key = element_blank(),
+        legend.title = element_text(face = "bold"),
+        legend.text = element_text())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "lombardoComparison_Figure8.png"),
+       height = 4,
+       width = 6.5,
+       device = "png", dpi = 300)
+
+```
+
+### Supp. Fig. 4 Histogram of Lombardo Vss and InvivoPKfit & another meta-analysis
+
+```{r otherMeta-analysis}
+
+# Histograms
+lombardo_hist <- data.frame(Chemical = c(lombardo$DTXSID,
+                              my_tkstats$Chemical),
+                            Vss = c(lombardo$`human VDss (L/kg)`,
+                              my_tkstats$Vss.tkstats),
+                            halflife = c(lombardo$`terminal  t1/2 (h)`,
+                              my_tkstats$halflife.tkstats),
+                            Source = c(rep_len("lombardo",
+                                    length.out = nrow(lombardo)),
+                              rep_len("invivoPKfit",
+                                      length.out = nrow(my_tkstats))))
+
+sfig4A <- lombardo_hist %>% ggplot(aes(x = log2(Vss), color = Source,
+                             group = Source)) +
+  geom_freqpoly(aes(y = after_stat(ndensity)),
+                linewidth = 2/.pt,
+                bins = 20) +
+  labs(y = "Scaled Frequency") +
+  scale_color_manual(values = c("black", "#1064c9")) +
+  guides(color = guide_legend(nrow = 2, linewidth = 1)) +
+  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold", size = 12),
+        text = element_text(size = 10),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text = element_text(face = "bold"),
+        legend.position = "bottom",
+        legend.key = element_blank(),
+        legend.title = element_text(face = "bold"),
+        legend.text = element_text())
+
+other_meta <- read_csv(
+  file = paste0(Sys.getenv("FIG_DIR"), "SupTableInVivoDatandPreds.csv")) %>%
+  dplyr::select(DTXSID, fbioh, fbior) %>%
+  filter(DTXSID %in% my_tkstats$Chemical)
+
+sfig4B <- other_meta %>% left_join(my_tkstats, by = c("DTXSID" = "Chemical")) %>%
+  filter(Species %in% c("rat")) %>%
+  filter(!is.na(Fgutabs.tkstats),
+         !is.na(fbior)) %>%
+  distinct(DTXSID, Species,
+           Fgutabs.tkstats, fbior) %>%
+  pivot_longer(cols = c(Fgutabs.tkstats, fbior),
+               names_to = "Source",
+               values_to = "Fgutabs") %>%
+    mutate(Source = ifelse(str_detect(Source, "tkstats"), "invivoPKfit",
+                           "Caco-2 Paper")) %>%
+    ggplot(mapping = aes(
+      x = Fgutabs,
+      y = reorder(DTXSID, Fgutabs)
+    )) +
+    geom_point(aes(color = Source),
+               shape = 24,
+               position = position_dodge(0.7),
+               size = 5/.pt, stroke = 2.5/.pt) +
+    scale_color_manual(values = c("black", "green4"),
+                       breaks = c("invivoPKfit", "Caco-2 Paper")) +
+  guides(color = guide_legend(nrow = 2)) +
+    theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
+          panel.background = element_blank(),
+          panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+          strip.background = element_rect(fill = "white"),
+          strip.text = element_text(face = "bold", size = 12),
+          text = element_text(size = 10),
+          axis.ticks = element_blank(),
+          axis.line = element_blank(),
+          axis.text = element_text(face = "bold"),
+          axis.title.y = element_blank(),
+          legend.position = "bottom",
+          legend.key = element_blank(),
+          legend.title = element_text(face = "bold"),
+          legend.text = element_text())
+
+plot_grid(sfig4A, sfig4B, align = "h", axis = "bt")
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "metaAnalysis_Comparisons_SuppFigure4.png"),
+       height = 3,
+       width = 5,
+       device = "png", dpi = 300)
+
+```
+
+### Supp. Fig. 5: Parallelization decreases runtime of invivoPKfit
+
+Here I do a bit of benchmarking for the parallel-ized version of do_fit
+
+```{r do_fit-benchmarking}
+
+# Set to 
+single_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 1), times = 3)
+four_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 4), times = 3)
+# eight_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 8), times = 3) # Only for four_DG
+ten_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 10), times = 3)
+fourteen_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 14), times = 3)
+
+single_core
+four_core
+# eight_core
+ten_core
+fourteen_core
+
+four_DG <- bind_rows(summary(single_core),
+                     summary(four_core),
+                     summary(eight_core),
+                     summary(ten_core),
+                     summary(fourteen_core)) # Done ~ 140s
+
+eight_DG <- bind_rows(summary(single_core),
+                      summary(four_core),
+                      summary(ten_core),
+                      summary(fourteen_core)) # Done
+
+sixteen_DG <- bind_rows(summary(single_core),
+                        summary(four_core),
+                        summary(ten_core),
+                        summary(fourteen_core)) # Done
+
+my_pk %>% get_data() %>% dplyr::select(Chemical, Species) %>%
+  distinct() %>% nrow()
+my_pk %>% get_data() %>% pull(Chemical) %>% unique() -> used_chemicals
+
+unused_cvt <- cvt %>%
+  dplyr::filter(!(chemicals_analyzed.dsstox_substance_id %in% used_chemicals))
+
+new_chemicals <- sample(unique(unused_cvt$chemicals_analyzed.dsstox_substance_id),
+                       size = 8)
+
+my_predata <- cvt %>%
+  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% union(used_chemicals,
+                                                                  new_chemicals))
+my_predata %>%
+  dplyr::select(chemicals_analyzed.dsstox_substance_id, subjects.species_harmonized) %>%
+  distinct() %>% nrow()
+
+my_pk <- pk(data = my_predata) +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = TRUE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  # scale_time(new_units = "auto") +
+  # stat_model() + 
+  stat_error_model(error_group = vars(Chemical, Species))
+my_pk <- do_prefit(my_pk) # Then run again
+
+##
+##
+# After getting all of them
+full_df <- bind_rows(
+  four_DG %>% mutate(data_group_N = 4),
+  eight_DG %>% mutate(data_group_N = 8),
+  sixteen_DG %>% mutate(data_group_N = 16)
+)
+
+full_df <- full_df %>%
+  mutate(N_cores = as.numeric(str_extract(expr, pattern = "[:digit:]+")))
+
+full_long <- full_df %>% 
+         dplyr::select(expr, N_cores, data_group_N, min, median, max) %>%
+         pivot_longer(cols = c(min, median, max)) %>%
+  dplyr::select(-name)
+
+df_long <- full_df %>% 
+         dplyr::select(expr, N_cores, data_group_N, min, median, max) %>%
+         pivot_longer(cols = c(min, median, max)) %>%
+  dplyr::select(-name) %>% group_by(N_cores, data_group_N) %>%
+  summarize(avg_val = mean(value),
+            sd_val = sd(value))
+
+ggplot(full_long,
+       aes(x = N_cores,
+           y = value,
+           color = factor(data_group_N))) +
+
   geom_point() +
-  geom_abline(slope = 1) +
-  scale_y_log10() +
-  scale_x_log10()
-
-ggplot(my_eval,
-       aes(x = -log10(AUC_inf_RMSE))) +
-  geom_histogram(fill = "grey5") +
-  facet_grid(cols = vars(method)) +
-  labs(x = "Accuracy of AUC",
-       y = "Observations") +
+  geom_line(data = df_long,
+            aes(x = N_cores,
+                y = avg_val)) +
+  scale_x_continuous(breaks = c(0, 1, 4, 8, 10, 14)) +
+  labs(x = "Number of Cores",
+       y = "Runtime (seconds)",
+       color = "Data Groups",
+       title = "Parallelization diminishes runtime at scale") +
   theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
@@
         panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        strip.background = element_rect(fill = "white"),
+        legend.key = element_rect(fill = "white"),
         axis.ticks = element_blank(),
         axis.line = element_blank())
-
-```
-
-```{r eval_Joint}
-my_pk2 <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
-my_eval_joint <- eval_tkstats(my_pk2)
-
-# To give summary RMSEs of Cmax and AUC...
-my_eval_joint <- my_eval_joint %>%
-  group_by(method, model, .add = TRUE) %>%
-  ungroup(Reference) %>%
-  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
-                                             na.rm = TRUE)^2)),
-            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
-                                          na.rm = TRUE)^2)),
-            .groups = "keep")
-
-my_eval_joint <- my_eval_joint %>%
-  mutate(dose_norm = TRUE,
-         log10_norm = FALSE,
-         scale_time = FALSE,
-         Analysis_Type = "Joint")
-
-ggplot(my_eval_joint,
-       aes(x = AUC_inf_RMSE,
-           y = Cmax_RMSE)) +
-  geom_point()
-
-ggplot(my_eval_joint,
-       aes(x = -log10(AUC_inf_RMSE))) +
-  geom_histogram(fill = "grey5") +
-  facet_grid(cols = vars(method)) +
-  labs(x = "Accuracy of AUC",
-       y = "Observations") +
-  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        strip.background = element_rect(fill = "white"),
-        axis.ticks = element_blank(),
-        axis.line = element_blank())
-
-total_eval <- bind_rows(my_eval, my_eval_joint)
-
-ggplot(total_eval,
-       aes(x = AUC_inf_RMSE,
-           y = Cmax_RMSE)) +
-  geom_point() +
-  facet_grid(rows = vars(Analysis_Type))
-
-total_eval %>%
-  dplyr::select(!Cmax_RMSE) %>%
-  pivot_wider(names_from = Analysis_Type,
-              values_from = AUC_inf_RMSE) %>%
-  ggplot(aes(x = log10(Pooled),
-             y = log10(Joint),
-             color = Media)) +
-  geom_point(alpha = 0.3) +
-  geom_abline(slope = 1, linetype = "dashed") +
-  facet_grid(rows = vars(model),
-             cols = vars(method)) +
-  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        strip.background = element_rect(fill = "white"),
-        axis.ticks = element_blank(),
-        axis.line = element_blank())
-
-total_eval %>%
-  dplyr::select(!Cmax_RMSE) %>%
-  pivot_wider(names_from = Analysis_Type,
-              values_from = AUC_inf_RMSE) %>%
-  mutate(ratio = Joint/Pooled) %>%
-  # filter(!(ratio == 1)) %>% 
-  # View()
-  pull(Chemical) %>%
-  # unique()
-  length()
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "Parallelization_Benchmarking.png"),
+       width = 4.5,
+       height = 3.5,
+       units = "in")
+
+```
+
+### Supp. Fig. 6: Example plots for data fits
+
+```{r sfig6-examples-of-fits}
+pl <- plot(my_pk, use_scale_conc = TRUE, n_interp = 10)
+names(pl) # Chemical Species observations oservation_plot predicted predicted_plot final_plot
+
+s6_plA <- pl %>% filter(Chemical %in% "DTXSID90382620") %>%
+  pull(observation_plot) %>% .[[1]]
+s6_plB_mouse <- pl %>% filter(Chemical %in% "DTXSID4020533",
+                              Species %in% "mouse") %>% pull(final_plot) %>% .[[1]]
+s6_plB_rat <- pl %>% filter(Chemical %in% "DTXSID4020533",
+                              Species %in% "rat") %>% pull(final_plot) %>% .[[1]]
+s6_plC <- pl %>% filter(Chemical %in% "DTXSID8021359") %>%
+  pull(final_plot) %>% .[[1]]
+s6_plD <- pl %>% filter(Chemical %in% "DTXSID8025337") %>%
+  pull(final_plot) %>% .[[1]]
+
+# Set colors palletes for each
+# panel A : Oranges
+panelA_cols <- brewer.pal(8, "Oranges")[3:8]
+# panel B : Greens
+panelB_cols <- brewer.pal(9, "Greens")[2:9]
+# panel C : Blue (only 2 values) 
+# panel D : Purple (6 values)
+panelD_cols <- brewer.pal(9, "Purples")[4:9]
+
+s6_plA <- s6_plA + 
+  labs(title = "fluorotelomer acid 7+3") +
+  scale_color_manual(values = panelA_cols, aesthetics = c("color", "fill")) +
+  theme(text = element_text(size = 20),
+        legend.position = "none",
+        strip.background = element_rect(fill = "white"))
+
+s6_plB_mouse <- s6_plB_mouse + 
+  labs(title = "1,4-dioxane\nMouse") +
+  scale_color_manual(values = panelB_cols[c(5,8)],
+                     aesthetics = c("color", "fill")) +
+  theme(text = element_text(size = 20),
+        legend.position = "none",
+        strip.background = element_rect(fill = "white"))
+
+s6_plB_rat <- s6_plB_rat + 
+  labs(title = "1,4-dioxane\nRat") +
+  scale_color_manual(values = panelB_cols[c(1, 2, 3, 4, 6,8)],
+                     aesthetics = c("color", "fill")) +
+  theme(text = element_text(size = 20),
+        legend.position = "none",
+        strip.background = element_rect(fill = "white"))
+
+s6_plC <- s6_plC +
+  labs(title = "tolbutamide") +
+  scale_color_manual(values = c("#6BAED6", "#08519C"),
+                     aesthetics = c("color", "fill")) +
+  theme(text = element_text(size = 20),
+        legend.position = "none",
+        strip.background = element_rect(fill = "white"))
+
+s6_plD <- s6_plD +
+  labs(title = "formamide") +
+  scale_color_manual(values = panelD_cols,
+                     aesthetics = c("color", "fill")) +
+  theme(text = element_text(size = 20),
+        legend.position = "none",
+        strip.background = element_rect(fill = "white"))
+
+# Put it all together
+s6_plB <- plot_grid(s6_plB_mouse, s6_plB_rat,
+            align = "h", axis = "bt",
+           rel_widths = c(1.2,2))
+
+s6_plCD <- plot_grid(s6_plC, s6_plD, labels = c("C", "D"), label_size = 24)
+
+plot_grid(
+  s6_plA,
+  s6_plB,
+  s6_plCD,
+  align = "v",
+  ncol = 1,
+  rel_heights = c(1.25, 1, 1.25),
+  labels = c("A", "B", ""),
+  label_size = 24
+)
+
+# Am making this 2X the size I need it to be 
+# so the points are a reasonable size when I scale it down
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "ExampleFitsPlots.png"),
+       width = 13,
+       height = 14,
+       units = "in")
+
+```
+
+The purpose of the following code is to generate data.frames with information for
+all 103 chemicals in the `cvt` dataset that comes with `invivopkfit`.
+I will need to do append each dataframe to the last for the outputs of the following
+methods:
+
+- `AIC()`
+- `BIC()` left-joined with `AIC` output
+- `get_tkstats()`
+
+I will also have to fit these iteratively and manage the memory as part of the loop.
+
+```{r more_analysis}
+
+my_pk$prefit$fit_check %>% filter(fit_decision == "abort") %>%
+  dplyr::select(model, Chemical) %>% distinct()
+
+all_my_data %>%
+  filter(Chemical == "DTXSID2021315")
+
+# On average, how many time-points before tmax (empirical)?
+my_nca %>% filter(param_name %in% "tmax") %>%
+  dplyr::select(Chemical, Species, Route, Media, tmax.nca = param_value) %>%
+  left_join(all_my_data) %>%
+  filter(Route %in% "oral", Time < tmax.nca) %>%
+  distinct(Chemical, Chemical_Name, Species, Route, Media, Detect, Time) %>%
+  group_by(Chemical, Chemical_Name, Species, Route, Media, Detect) %>%
+  count(name = "tp_before_tmax") %>%
+  ungroup() %>% 
+  filter(Detect == TRUE) %>%
+  dplyr::select(!Detect) %>%
+  arrange(tp_before_tmax) %>%
+  count(tp_before_tmax > 1)
 
@@
 ```{r PredictionVariability_overtime}
-my_pk <- readRDS("data-raw/all_cvt_pk.rds")
-winmodels <- AIC(my_pk) %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>%
-  ungroup() %>%
-  dplyr::select(Chemical, Species,
-                method, model)
-my_preds <- inner_join(winmodels,
-                       predict(my_pk,
-                               use_scale_conc = TRUE))
-
-my_tkstats <- inner_join(winmodels, get_tkstats(my_pk))
-my_residuals <- residuals(my_pk, use_scale_conc = FALSE)
-
 my_residuals %>%
   filter(exclude == FALSE) %>%
-  inner_join(winmodels) %>%
+  inner_join(winmodel) %>%
   inner_join(my_tkstats %>%
@@
                             Route, Media,
-                            tmax) %>%
+                            tmax = tmax.tkstats) %>%
               filter(!is.na(tmax))) %>%
@@
 
-This is another preliminary attempt to summarize RMSEs of each fit
-(Predictions - Observed Values)
-
-```{r boilerplate_RMSE_analysis}
-my_pk <- readRDS("data-raw/all_cvt_pk.rds")
-my_AIC <- AIC(my_pk)
-
-my_AIC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "bobyqa") %>%
-  ungroup() %>%
-  count(model)
-
-my_AIC %>% group_by(Chemical, Species, method) %>%
-  filter(AIC == min(AIC),
-         method == "L-BFGS-B") %>%
-  ungroup() %>%
-  count(model)
-
-my_eval <- eval_tkstats(my_pk)
-
-# To give summary RMSEs of Cmax and AUC...
-my_eval <- my_eval %>%
-  group_by(method, model, .add = TRUE) %>%
-  ungroup(Reference) %>%
-  summarize(AUC_inf_RMSE = sqrt((1/n())*(sum(AUC_inf.tkstats - AUC_inf.nca,
-                                             na.rm = TRUE)^2)),
-            Cmax_RMSE = sqrt((1/n())*(sum(Cmax.tkstats - Cmax.nca,
-                                          na.rm = TRUE)^2)),
-            .groups = "keep")
-
-my_eval %>%
-  group_by(method) %>%
-  summarize(AUC_meanRMSE = mean(AUC_inf_RMSE),
-            AUC_mediRMSE = median(AUC_inf_RMSE),
-            AUC_sdRMSE = sd(AUC_inf_RMSE),
-            Cmax_meanRMSE = mean(Cmax_RMSE),
-            Cmax_mediRMSE = median(Cmax_RMSE),
-            Cmax_sdRMSE = sd(Cmax_RMSE)) %>%
-  as.data.frame()
-```
-
-Here I explore some bad-fitting chemicals using the dose-normalized pooled analysis.
-
-```{r bad_fits}
-predata_chemical <- my_pk$prefit$fit_check %>%
-  filter(fit_decision == "abort") %>%
-  pull(Chemical) %>%
-  unique()
-
-my_pk <- pk(data = cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% predata_chemical)) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) 
-# Add Reference for Joint Analysis
-
-my_pk <- do_preprocess(my_pk)
-
-get_data(my_pk) %>% View()
-
-plot(my_pk, print_out = TRUE)[[1]] +
-  labs(subtitle = "Dibutyl phthalate (DBP)") +
-  theme(aspect.ratio = 1,
-        plot.subtitle = element_text(hjust = 0.5))
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "DTXSID20211781_rat_badFit.png"),
-       width = 6,
-       height = 4,
-       units = "in")
-
-my_pk <- pk(data = cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID2021315")) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk <- do_fit(my_pk)
-
-plot(my_pk,
-     method = "L-BFGS-B",
-     n_interp = 10,
-     print_out = TRUE)[[1]] +
-  labs(subtitle = "2,3,7,8-tetrachlorodibenzo-p-dioxin") +
-  scale_x_continuous(breaks = c(0, (1:4)*(24*7*4)),
-                     labels = c(0, 1:4),
-                     name = "Time (months)") +
-  guides(color = "none",
-         shape = "none") +
-  theme(aspect.ratio = 1,
-        plot.subtitle = element_text(hjust = 0.5))
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "DTXSID2021315_rat_badFit.png"),
-       width = 8,
-       height = 5,
-       units = "in")
-
-my_pk <- pk(data = cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk <- do_fit(my_pk)
-
-plot(my_pk,
-     method = "L-BFGS-B",
-     use_scale_conc = FALSE,
-     log10_C = FALSE,
-     n_interp = 50,
-     print_out = TRUE)[[1]] +
-  labs(subtitle = "3,3',4,4',5-pentachlorobiphenyl (without Dose-Normalized Fit)") +
-  scale_x_continuous(breaks = c(0, (1:14)*(24*7*4)),
-                     labels = c(0, 1:14),
-                     name = "Time (months)") +
-  guides(color = "none",
-         shape = "none") +
-  theme(aspect.ratio = 1,
-        plot.subtitle = element_text(hjust = 0.5))
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "DTXSID3032179_rat_badFit_noDoseNorm.png"),
-       width = 7.5,
-       height = 5,
-       units = "in")
-
-my_pk <- pk(data = cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID3032179")) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk <- do_fit(my_pk)
-
-plot(my_pk,
-     method = "L-BFGS-B",
-     use_scale_conc = FALSE,
-     log10_C = FALSE,
-     n_interp = 50,
-     print_out = TRUE)[[1]] +
-  labs(subtitle = "3,3',4,4',5-pentachlorobiphenyl (Dose-Normalized Fit)") +
-  scale_x_continuous(breaks = c(0, (1:14)*(24*7*4)),
-                     labels = c(0, 1:14),
-                     name = "Time (months)") +
-  guides(color = "none",
-         shape = "none") +
-  theme(aspect.ratio = 1,
-        plot.subtitle = element_text(hjust = 0.5))
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "DTXSID3032179_rat_badFit_DoseNorm.png"),
-       width = 7.5,
-       height = 5,
-       units = "in")
-
-my_pk <- pk(data = cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID1034187")) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk <- do_fit(my_pk)
-
-get_data(my_pk) %>% View()
-plot(my_pk,
-     method = "L-BFGS-B",
-     use_scale_conc = TRUE,
-     log10_C = FALSE,
-     n_interp = 100,
-     print_out = TRUE)[[1]] +
-  labs(subtitle = "Tamoxifen") +
-  theme(aspect.ratio = 1,
-        plot.subtitle = element_text(hjust = 0.5))
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "DTXSID1034187_rat_badFit_.png"),
-       width = 7,
-       height = 7,
-       units = "in")
-# Fit is actually ok, but there are lot's of non-Detects in the data
-# There are many doses that are fully non-Detects.
-
-problem_dose <- all_my_data %>%
-  group_by(Chemical, Species, Route, Media, Dose) %>%
-  filter(sum(Detect) == 0) %>%
-  dplyr::select(Chemical, Species, Route, Media, Dose) %>%
-  rename(chemicals_analyzed.dsstox_substance_id = Chemical,
-         subjects.species_harmonized = Species,
-         series.conc_medium_normalized = Media,
-         studies.administration_route_normalized = Route,
-         studies.dose_level_normalized_corrected = Dose) %>%
-  distinct()
-
-problem_dose_DTX <- all_my_data %>%
-  group_by(Chemical, Species, Route, Media, Dose) %>%
-  filter(sum(Detect) == 0) %>%
-  ungroup() %>%
-  pull(1) %>% unique()
-
-# Figure out if the fits improve if we exclude Dose groups that do not have
-# any Detects
-
-my_pk_full <- pk(data = cvt %>%
-                   dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% 
-                                   "DTXSID1034187")) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_full <- do_preprocess(my_pk_full)
-my_pk_full <- do_fit(my_pk_full)
-
-plot(my_pk_full,
-     n_interp = 50,
-     use_scale_conc = TRUE,
-     print_out = TRUE)
-
-my_pk_trimmed <- pk(data = cvt %>%
-                      dplyr::filter(chemicals_analyzed.dsstox_substance_id %in%
-                                      "DTXSID1034187") %>%
-                      anti_join(problem_dose)) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  stat_error_model(error_group = vars(Chemical, Species))
-
-my_pk_trimmed <- do_preprocess(my_pk_trimmed)
-my_pk_trimmed <- do_fit(my_pk_trimmed)
-
-AIC(my_pk_full) %>% View("full")
-AIC(my_pk_trimmed) %>% View("trimmed")
-
-get_winning_model(my_pk_full)
-get_winning_model(my_pk_trimmed)
-
-eval_tkstats(my_pk_full) %>% View("full_tkstats")
-eval_tkstats(my_pk_trimmed) %>% View("trimmed_tkstats")
-get_tkstats(my_pk_trimmed) %>% View()
-
-plot(my_pk_trimmed,
-     n_interp = 50,
-     method = "L-BFGS-B",
-     print_out = TRUE)
-
-# PFAS Chemical
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID80108992")
-my_pk <- pk(data = my_predata) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE,
-                      suppress.messages = FALSE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) 
-my_pk <- do_fit(my_pk)
-plot(my_pk, n_interp = 20,
-     method = "L-BFGS-B", print_out = TRUE)
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "DTXSID80108992_noTimeScaling.png"),
-       height = 3,
-       width = 5.5,
-       units = "in")
-# Time-scaled!
-my_pk <- pk(data = my_predata) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = FALSE,
-                      suppress.messages = FALSE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species)) 
-my_pk <- do_data_info(my_pk)
-my_pk <- do_fit(my_pk)
-dplot(my_pk, n_interp = 20,
-     method = "L-BFGS-B", print_out = TRUE)
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "PerluorodeconoicAcid_noTimeScaling.png"),
-       height = 4,
-       width = 5.5,
-       units = "in")
-
-```
-
 I try to find the connections between functions in _invivoPKfit_ to best understand
@@
 
-fun_mat2 <- fun_mat[rowSums(fun_mat) > 0, ]
-
-library(ComplexHeatmap)
-ComplexHeatmap::Heatmap(fun_mat2, row_names_side = "left", column_names_side = "top",
-                        row_names_gp = gpar(fontsize = 10),
-                        column_names_gp = gpar(fontsize = 10),
-                        col = circlize::colorRamp2(c(0, 1), colors = c("white", "green4")),
-                        rect_gp = gpar(col = "black", lwd = 1),
-                        show_row_dend = FALSE,
-                        show_column_dend = FALSE)
-
-fun_mat %>%
-  as_tibble(rownames = NA) %>%
-  rownames_to_column(var = "from") %>%
-  pivot_longer(cols = !from,
-               names_to = "to",
-               values_to = "Call") %>%
-   mutate(
-    from = str_remove(from, pattern = ".pk"),
-    to = str_remove(to, pattern = ".pk")
-  ) %>%
-  filter(from %in% "residuals") %>% View()
-
-fun_mat2 %>%
-  as_tibble(rownames = NA) %>%
-  rownames_to_column(var = "from") %>%
-  pivot_longer(cols = !from,
-               names_to = "to",
-               values_to = "Call") %>%
-  filter(Call != 0) %>% 
-  transmute(
-    from = str_remove(from, pattern = ".pk"),
-    to = str_remove(to, pattern = ".pk")
-  ) %>%
-  filter(from %in% c("residuals"),
-         !(to %in% c("check_model",
-                     "check_method",
-                     "check_newdata",
-                     "check_required_status"))) %>%
-  ggflowchart::ggflowchart(horizontal = TRUE)
-
-```
-
-## Q & A
-
-Here I try asking the remaining questions for the paper/presentation.
-
-```{r questions}
-my_pk <- readRDS("data-raw/all_cvt_pk.rds")
-pk_summary <- summary(my_pk) # Testing the summary functionality
-
-# Q: What do "bad" fits have in common?
-gof_df <- pk_summary$goodness_of_fit %>%
-  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
-  filter(method == "L-BFGS-B") %>%
-  ungroup()
-
-## Find the within_2fold for each data_group
-gof_df %>%
-  dplyr::select(Chemical, Species, full_fold_errors) %>%
-  unnest(full_fold_errors) %>%
-  group_by(Chemical, Species) %>%
-  summarize(within_2fold = sum(
-    Fold_Error >= 0.5 & Fold_Error <= 2, na.rm = TRUE
-    ) / length(na.omit(Fold_Error))) %>%
-  filter(within_2fold == 0) %>% pull(Chemical) %>% unique()
-  arrange(within_2fold) %>%
-  View()
-
-gof_df %>%
-  ggplot(aes(
-    x = log2(avg_FoldErr),
-    y = log10(avg_rmse))) +
-  geom_point() +
-  geom_vline(color = "red3", xintercept = c(-1, 1))
-
-winning_model <- get_winning_model(my_pk, method = "L-BFGS-B")
-fe_df <- fold_errors(my_pk, method = "L-BFGS-B") %>% inner_join(winning_model)
-# May need to change the use_scale_conc defaults
-r2_df <- rsq(my_pk, method = "L-BFGS-B", use_scale_conc = FALSE) %>%
-  inner_join(winning_model)
-myAIC <- AIC(my_pk, method = "L-BFGS-B") %>%
-  inner_join(winning_model)
-myRMSE <- rmse(my_pk, method = "L-BFGS-B",
-               rmse_group = vars(Route, Media, Dose),
-               use_scale_conc = FALSE) %>% 
-  inner_join(winning_model)
-
-# Something wrong with the summary method... maybe only use detects?
-fold_errors_all <- fe_df %>%
-  dplyr::filter(Detect %in% TRUE) %>%
-  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
-  dplyr::summarize(avg_FoldErr = mean(Fold_Error, na.rm = TRUE),
-                median_FoldErr = median(Fold_Error, na.rm = TRUE),
-                within_2fold = sum(Fold_Error >= 0.5 & Fold_Error <= 2)/length(Fold_Error))
-
-myRMSE_all <- myRMSE %>%
-  dplyr::group_by(!!!my_pk$data_group, model, method) %>%
-  dplyr::summarize(avg_MSE = mean(RMSE^2, na.rm = TRUE),
-                median_MSE = median(RMSE^2, na.rm = TRUE))
-
-my_df <- left_join(fold_errors_all, r2_df) %>% inner_join(myAIC) %>% inner_join(myRMSE_all)
-mypl <- ggplot(data = my_df,
-               aes(
-                 x = within_2fold,
-                 y = Rsq,
-                 color = model
-               )) +
-  geom_point() +
-  geom_abline(slope = 1, color = "red4", linetype = "longdash") +
-  scale_color_manual(values = c("#0398FC", "#D68E09", "black")) +
-  labs(x = "% Fold Error within 2-fold",
-       y = "R-squared value") +
-  theme(aspect.ratio = 1,
-        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        axis.ticks = element_blank(),
-        axis.line = element_blank(),
-        legend.position = "bottom",
-        legend.title = element_blank(),
-        legend.key = element_blank())
-panelA_plot <- ggExtra::ggMarginal(mypl, groupFill = TRUE,
-                    type = "histogram",
-                    xparams = list(binwidth = 0.05),
-                    yparams = list(binwidth = 0.05))
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "R2_within2fold_comparison.png"),
-       plot = ggExtra::ggMarginal(mypl, groupFill = TRUE,
-                    type = "histogram",
-                    xparams = list(binwidth = 0.05),
-                    yparams = list(binwidth = 0.05)),
-       height = 5,
-       width = 5,
-       units = "in")
-
-panelB_plot <- ggplot(data = myRMSE %>%
-         inner_join(winning_model) %>%
-         mutate(RMSE = ifelse(RMSE == 0, NA, RMSE)),
-               aes(
-                 x = log10(RMSE),
-                 color = model,
-                 fill = model
-               )) + 
-  geom_histogram(bins = 100) +
-  labs(y = "Count") +
-  scale_color_manual(values = c("#0398FC", "#D68E09", "grey10")) +
-  scale_fill_manual(values = c("#0398FC", "#D68E09", "grey10")) +
-  scale_y_continuous(breaks = scales::pretty_breaks()) +
-  facet_grid(rows = vars(model),
-             cols = vars(Route)) +
-  theme(aspect.ratio = 0.5,
-        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        axis.ticks = element_blank(),
-        axis.line = element_blank(),
-        strip.background = element_blank(),
-        legend.position = "none",
-        legend.title = element_blank())
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RMSEs_winningmodel_LBFGSB_zero1E-6_RouteFacet_notNormalized.png"),
-       height = 4,
-       width = 6,
-       units = "in")
-
-cowplot::plot_grid(panelA_plot, panelB_plot, labels = c("A", "B"))
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "CombinedPlot_Rsquared_RMSE.png"),
-       height = 5,
-       width = 7.45,
-       bg = "white",
-       units = "in")
-
- rmse(my_pk, method = "L-BFGS-B",
-      rmse_group = vars(Route, Media, Dose)) %>%
-   inner_join(get_winning_model(my_pk, method = "L-BFGS-B")) %>%
-   count(model)
-
-rmse(my_pk, method = "L-BFGS-B",
-                   rmse_group = vars(Route, Media, Dose)) %>%
-  inner_join(winning_model) %>%
-  filter(RMSE < 0.01, RMSE > 0.0001, Route == "oral", model == "model_1comp") %>%
-  group_by(Chemical, Species, Route, Media) %>%
-  mutate(group_size = n(),
-         logRMSE = log10(RMSE)) %>%
-  arrange(Chemical, Species, Route, Media, RMSE) %>%
-  View()
-
-fold_errors_all %>% 
-  ggplot(aes(x = within_2fold)) +
-  geom_histogram(binwidth = 0.1) +
-  facet_grid(cols = vars(model))
-
-ggplot() +
-  geom_histogram(data = fold_errors_all, 
-                 aes(x = within_2fold),
-                 bins = 100) +
-  geom_vline(xintercept = fold_errors_all %>%
-               filter(Chemical == "DTXSID8025337") %>%
-               pull(within_2fold)) +
-  scale_x_log10()
-
-fold_errors_all %>% ungroup() %>%
-  mutate(per_rank = rank(within_2fold)/n()) %>%
-  filter(Chemical == "DTXSID8025337") %>%
-  dplyr::select(-full_fold_errors)
-
-fe_df %>%
-  inner_join(suppressMessages(get_winning_model(my_pk))) %>%
-  dplyr::filter(Detect %in% TRUE) %>%
-  ggplot(aes(x = log2(Fold_Error))) +
-  xlim(-4, 4) +
-  geom_histogram(binwidth = 0.1) +
-  facet_grid(cols = vars(model))
-
-# Evaluate at level of Cmax and AUC RMSE
-my_tkstats <- eval_tkstats(my_pk, method = "L-BFGS-B")
-my_tkstats %>%
-  dplyr::select(Chemical, Species, Route, Media, model, method,
-                starts_with("Cmax"),
-                starts_with("AUC")) %>%
-  distinct() %>% 
-  filter(is.finite(Cmax.tkstats), is.finite(AUC_inf.tkstats),
-         is.finite(Cmax.nca), is.finite(AUC_inf.nca)) %>%
-  ggplot(aes(x = Cmax.tkstats/Cmax.nca,
-             y = AUC_inf.tkstats/AUC_inf.nca)) +
-  geom_point() +
-  geom_abline(slope = 1, color = "red4")
-
-# Q: What do "great" fits have in common?
-
-# Q: Does the dataset have a bias?
-```
-
-Here I do a bit of benchmarking for the parallel-ized version of do_fit
-
-```{r do_fit-benchmarking}
-
-# Set to 
-single_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 1), times = 3)
-four_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 4), times = 3)
-# eight_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 8), times = 3) # Only for four_DG
-ten_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 10), times = 3)
-fourteen_core <- microbenchmark::microbenchmark(do_fit(my_pk, n_cores = 14), times = 3)
-
-single_core
-four_core
-# eight_core
-ten_core
-fourteen_core
-
-four_DG <- bind_rows(summary(single_core),
-                     summary(four_core),
-                     summary(eight_core),
-                     summary(ten_core),
-                     summary(fourteen_core)) # Done ~ 140s
-
-eight_DG <- bind_rows(summary(single_core),
-                      summary(four_core),
-                      summary(ten_core),
-                      summary(fourteen_core)) # Done
-
-sixteen_DG <- bind_rows(summary(single_core),
-                        summary(four_core),
-                        summary(ten_core),
-                        summary(fourteen_core)) # Done
-
-my_pk %>% get_data() %>% dplyr::select(Chemical, Species) %>%
-  distinct() %>% nrow()
-my_pk %>% get_data() %>% pull(Chemical) %>% unique() -> used_chemicals
-
-unused_cvt <- cvt %>%
-  dplyr::filter(!(chemicals_analyzed.dsstox_substance_id %in% used_chemicals))
-
-new_chemicals <- sample(unique(unused_cvt$chemicals_analyzed.dsstox_substance_id),
-                       size = 8)
-
-my_predata <- cvt %>%
-  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% union(used_chemicals,
-                                                                  new_chemicals))
-my_predata %>%
-  dplyr::select(chemicals_analyzed.dsstox_substance_id, subjects.species_harmonized) %>%
-  distinct() %>% nrow()
-
-my_pk <- pk(data = my_predata) +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE,
-                      suppress.messages = TRUE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
-  # stat_model() + 
-  stat_error_model(error_group = vars(Chemical, Species))
-my_pk <- do_prefit(my_pk) # Then run again
-
-##
-##
-# After getting all of them
-full_df <- bind_rows(
-  four_DG %>% mutate(data_group_N = 4),
-  eight_DG %>% mutate(data_group_N = 8),
-  sixteen_DG %>% mutate(data_group_N = 16)
-)
-
-full_df <- full_df %>%
-  mutate(N_cores = as.numeric(str_extract(expr, pattern = "[:digit:]+")))
-
-full_long <- full_df %>% 
-         dplyr::select(expr, N_cores, data_group_N, min, median, max) %>%
-         pivot_longer(cols = c(min, median, max)) %>%
-  dplyr::select(-name)
-
-df_long <- full_df %>% 
-         dplyr::select(expr, N_cores, data_group_N, min, median, max) %>%
-         pivot_longer(cols = c(min, median, max)) %>%
-  dplyr::select(-name) %>% group_by(N_cores, data_group_N) %>%
-  summarize(avg_val = mean(value),
-            sd_val = sd(value))
-
-ggplot(full_long,
-       aes(x = N_cores,
-           y = value,
-           color = factor(data_group_N))) +
-
-  geom_point() +
-  geom_line(data = df_long,
-            aes(x = N_cores,
-                y = avg_val)) +
-  scale_x_continuous(breaks = c(0, 1, 4, 8, 10, 14)) +
-  labs(x = "Number of Cores",
-       y = "Runtime (seconds)",
-       color = "Data Groups",
-       title = "Parallelization diminishes runtime at scale") +
-  theme(panel.border = element_rect(color = "black", fill = NA, size = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        legend.key = element_rect(fill = "white"),
-        axis.ticks = element_blank(),
-        axis.line = element_blank())
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "Parallelization_Benchmarking.png"),
-       width = 4.5,
-       height = 3.5,
-       units = "in")
-
-```
-
-### Time table (refactoring convert_time)
-
-```{r convert_time_table}
-
-expand_grid(TimeA = time_units, TimeB = time_units) %>%
-  mutate(A_fun = paste0("d", TimeA), B_fun = paste0("d", TimeB)) %>%
-  rowwise() %>%
-  mutate(conversion = 
-           do.call(A_fun, list(1))/do.call(B_fun, list(1))) %>%
-  dplyr::select(!c(A_fun, B_fun))
-
-time_table <- convert_time_table()
-
-time_table$TimeA %>% clipr::write_clip()
-time_table$TimeB %>% clipr::write_clip()
-time_table$conversion %>% MASS::fractions(max.denominator = 1000000000000000)
-
+```
+
+## Other Plots
+
+### Plotting ALL fits for Dose-normalized Joint fits (L-BFGS-B)
+
+```{r plotting_all_Fits}
 ### Plotting for all (2.5MB file)
@@
 pdf(file = paste0(Sys.getenv("FIG_DIR"),
-              "DoseNormalized_Pooled_AllFits.pdf"),
+              "DoseNormalized_Joint_AllFits_Final.pdf"),
     height = 6, width = 10)
@@
 
-ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "DoseNormalized_DTXSID8025337.png"),
+```
+
+### Figure 2
+```{r Explain-Heirarchical-Model}
+# Note that the data will run one "Series" of time point at a time
+my_1comp <- function(t, F_V, kelim, kabs, sd = 0) {
+  sd + (F_V * (kabs * (exp(-kelim * t) - exp(-kabs * t))) / (kabs - kelim))
+}
+
+my_cdata <- data.frame(
+  Reference = rep(rep(c("X", "O"), each = 3), 6),
+  Time = rep(c(0, 2, 4, 6, 8, 12), each = 6),
+  Concentration = c(
+    4, 5, 6.5,
+    4.5, 5, 6,
+    8, 9, 9.5,
+    7.5, 8, 8.5,
+    3, 4.5, 6,
+    3.5, 4, 5,
+    2, 2.5, 4,
+    1, 1.5, 2.25,
+    0.4, 1, 2,
+    0.4, 0.8, 1,
+    0.2, 0.5, 1,
+    0.25, 0.4, 0.5
+  ) 
+)
+
+pl_pool <- ggplot() +
+  geom_point(data = my_cdata,
+             mapping = aes(
+               x = Time,
+               y = Concentration,
+               color = Reference
+             ),
+             position = position_dodge(width = 0.4),
+             size = 2) +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8),
+    linewidth = 1) +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8, sd = 1),
+    linewidth = 0.5, linetype = "dashed") +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8, sd = -1),
+    linewidth = 0.5, linetype = "dashed") +
+  scale_y_continuous(breaks = scales::pretty_breaks(10)) +
+  scale_x_continuous(breaks = scales::pretty_breaks(13)) +
+  scale_color_manual(values = c("black", "black")) +
+  theme_classic() +
+  theme(axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        axis.title = element_text(size = 12, face = "bold"),
+        axis.line = element_line(linewidth = 1, lineend = "square"),
+        legend.position = "none")
+ggsave(paste0(Sys.getenv("FIG_DIR"), "PooledExampleFigure.png"),
        units = "in",
-       height = 5.05,
-       width = 5.55,
-       dpi = 200)
-
-```
+       height = 4,
+       width = 5,
+       device = "png",
+       dpi = 300)
+
+# Change shape(s) from circles
+pl_joint <- ggplot() +
+  geom_point(data = my_cdata,
+             mapping = aes(
+               x = Time,
+               y = Concentration,
+               color = Reference,
+               shape = Reference
+             ),
+             position = position_dodge(width = 0.4),
+             size = 2) +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8),
+    linewidth = 1) +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8, sd = 1.3),
+    linewidth = 0.6, linetype = "dashed", color = "green4") +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8, sd = -1.3),
+    linewidth = 0.6, linetype = "dashed", color = "green4") +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8, sd = 0.7),
+    linewidth = 0.6, linetype = "dashed", color = "magenta3") +
+  stat_function(
+    fun = my_1comp,
+    args = list(F_V = 20, kelim = 0.6, kabs = 0.8, sd = -0.7),
+    linewidth = 0.6, linetype = "dashed", color = "magenta3") +
+  scale_y_continuous(breaks = scales::pretty_breaks(10)) +
+  scale_x_continuous(breaks = scales::pretty_breaks(13)) +
+  scale_color_manual(values = c("magenta3", "green4")) +
+  scale_shape_manual(values = c(15, 17)) +
+  theme_classic() +
+  theme(axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        axis.title = element_text(size = 12, face = "bold"),
+        axis.line = element_line(linewidth = 1, lineend = "square"),
+        axis.title.y = element_blank(),
+        legend.position = "none")
+
+pl_joint
+ggsave(paste0(Sys.getenv("FIG_DIR"), "JointExampleFigure.png"),
+       units = "in",
+       height = 4,
+       width = 5,
+       device = "png",
+       dpi = 300)
+
+plot_grid(pl_pool, pl_joint,
+          align = "h", axis = "bt")
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "Pooled_Joint_ExampleFigure.png"),
+       units = "in",
+       height = 3.4,
+       width = 6.5,
+       device = "png",
+       dpi = 300)
+
+ggplot(data.frame(point_size = seq(0.2, 3, by = 0.2)),
+       aes(x = as.factor(point_size), size = point_size)) +
+  geom_point(y = 0) +
+  scale_y_continuous(limits = c(-1, 1)) +
+  theme_bw() +
+  theme(legend.position = "none")
+
+ggsave(paste0(Sys.getenv("FIG_DIR"), "Point_Reference_3x5.png"),
+       units = "in",
+       height = 3,
+       width = 5,
+       device = "png",
+       dpi = 300)
+
+```
+
+# Notes
+
+Specify that favorable gains in Cmax RMSE not accompanied by gains in AUC RMSE.
+Histogram of Volume of Distributions and half-lifes... other TKstats... Lombardo comparison
+- Stratified on species... then chemical class (pharma vs non-pharma, Pharmapendium)
+- Classyfier for chemical superclass (talk to Paul) Ranges and Mean for each class...

### 2023-10-10 data-raw/batchMode_trial_gpm.Rmd
Updating vignette to increase detail to readers.

@@
 
-```{r Evaluating_Choices}
+Here I evaluate the various fitting options by counting the number of fits 
+for each model that "won" based on AIC. This is given by the `get_winning_model`
+method. Furthermore, I also calculate the root mean squared error (RMSE)
+for AUC~inf~ and C~max~ values. The _observed_ values in this calculation are
+the results of the non-compartmental analysis. Importantly,
+all Chemical, Species, Reference, Route, Media, Dose data groups with
+AUC~inf~ values that are non-finite or zero in either
+non-compartmental or _invivoPKfit_ analysis are not included in the 
+calculation for RMSE (of AUC or C~max~). This is to exclude the "incalculable"
+RMSEs such that they won't impact our assessment of each set of options'
+_goodness-of-fit_. Lastly, we calculate more detailed statistics such as R^2^
+and average fold error for each model, method, and set **data_group** for downstream
+analyses.
+
+```{r Evaluation-helpers}
 # Evaluation
-# Current: my_pk_111p
+# Current:
 
@@
 gc()
+```
+
+```{r Evaluating choices}
 
@@
 
+These finalists will be compared based on their more detailed statistics.
+
 ```{r Plotting_Summary}
@@
 
+# What are the sheets names
 readxl::excel_sheets(paste(Sys.getenv("OD_DIR"),
@@
 amount of error in predictions and derived TK stats.
-In addition, _L-GFGS-B_ was the optimizer of choice
+In addition, _L-BFGS-B_ was the optimizer of choice due to some marginally better fits
+(I will note that the run-time for _L-BFGS-B_ is significantly faster).
 
@@
 ## Analysis Plots
+
+Next I will generate the figures for the paper.
 
@@
 
-The purpose of the following code is to generate data.frames with information for
-all 103 chemicals in the `cvt` dataset that comes with `invivopkfit`.
-I will need to do append each dataframe to the last for the outputs of the following
-methods:
-
-- `AIC()`
-- `BIC()` left-joined with `AIC` output
-- `get_tkstats()`
-
-I will also have to fit these iteratively and manage the memory as part of the loop.
+Here I decide to investigate data where fits were aborted and how many 
+time-points occurred before non-compartmental t~max~, which essentially
+asks whether there are enough detectable (above LOQ) data points to model absorption.
+As a threshold for whether absorption can be modeled, I count those that have at least
+more than one data point prior to the empirical t~max~. With at least three points
+(including t~max~) we can reasonably begin to assess the absorption of a compound.
 
@@
 
+Here is the code used to generate the CvT data and _invivoPKfit_ fits
+for each chemical, species data group.
+
 ```{r plotting_all_Fits}
@@
        dpi = 300)
-
-```
-
-# Notes
-
-Specify that favorable gains in Cmax RMSE not accompanied by gains in AUC RMSE.
-Histogram of Volume of Distributions and half-lifes... other TKstats... Lombardo comparison
+```
+
+# Notes and future directions
 - Stratified on species... then chemical class (pharma vs non-pharma, Pharmapendium)

### 2023-10-12 data-raw/Manuscript2023_Workflow.Rmd
Renamed batchMode_trial_gpm.Rmd to Manuscript2023_Workflow.Rmd

--- 2023-10-10 data-raw/batchMode_trial_gpm.Rmd
@@
 
-# Notes and future directions
-- Stratified on species... then chemical class (pharma vs non-pharma, Pharmapendium)
-- Classyfier for chemical superclass (talk to Paul) Ranges and Mean for each class...
+# Preparing results for CvTdb
+
+```{r cvtdb-prep}
+
+my_cvt <- cvt
+my_tkstats <- eval_tkstats(my_pk)
+
+my_cvt_unique <- my_cvt %>% dplyr::mutate(
+  preprocess_data_flags = 
+    case_when(
+      (other_study_identifier %in% "S0916") ~ paste("Adjusted dose_level_original_units",
+                                                              "adjusted dose_level_normalized.",
+                                                              sep = " and "),
+      (other_study_identifier %in% "S0624") ~ paste("Adjusted dose_level_normalized."),
+      (document_id %in% c("65", "61", "46", "31")) ~ paste("Adjusted analyte_dtxsid",
+                                                           "adjusted analyte_name_original.",
+                                                           sep = " and "),
+      (other_study_identifier %in% c("S0976",
+                                     "S0361",
+                                     "S0328")) ~ paste("Adjusted loq and loq_units."),
+      (document_id %in% "38") ~ paste("Adjusted conc."),
+      (analyte_name_original %in% c("n-desmethyltamoxifen",
+                                    "methemoglobin")) ~ paste("Adjusted analyte_dtxsid."),
+      .default = NA_character_
+    )) %>%
+  group_by(analyte_dtxsid, species,
+    administration_route_normalized, conc_medium_normalized, preprocess_data_flags) %>%
+  summarize(document_ids = paste0(unique(document_id), collapse = ","))
+
+# Non-compartmental analysis
+my_nca <- get_nca(my_pk) %>% dplyr::select(-param_units) %>%
+  mutate(param_name = paste0(param_name, ".nca")) %>%
+  group_by(Chemical, Species,
+           Route, Media, design) %>%
+  pivot_wider(names_from = param_name,
+              values_from = c(param_value, param_sd_z)) %>%
+  distinct() %>%
+  arrange(Chemical) %>%
+  rename_with(.fn = ~gsub("param_", "", .x)) %>%
+  rename_with(.fn = ~gsub("value_", "", .x)) %>%
+  rename(analyte_dtxsid = Chemical,
+         species = Species,
+         administration_route_normalized = Route,
+         conc_medium_normalized = Media)
+
+my_cvt %>%
+  dplyr::select(analyte_dtxsid, species, radiolabeled) %>%
+  distinct() %>%
+  filter(analyte_dtxsid %in% (cvt %>% filter(radiolabeled) %>% pull(analyte_dtxsid)))
+
+# Writing to file
+left_join(my_nca, my_cvt_unique) %>%
+  ungroup() %>%
+  filter(!is.infinite(AUC_infinity.nca), !is.infinite(AUMC_infinity.nca)) %>%
+  distinct() %>%
+  mutate(nca_id = row_number(),
+         .before = analyte_dtxsid) %>% View("NCA-CvTdb")
+  # write_tsv("data-raw/NCA_CvTdb.tsv")
+# Note that this will have more numbers because it still includes AUC_infinity == NA
+
+# TK stats
+my_tkstats <- my_tkstats %>%
+  dplyr::select(analyte_dtxsid = Chemical, species = Species,
+                administration_route_normalized = Route, 
+                conc_medium_normalized = Media, 
+                Reference,
+                model, method,
+                ends_with("tkstats")) %>%
+  group_by(across(everything())) %>%
+  ungroup(Reference) %>%
+  summarize(document_ids = paste0(unique(Reference), collapse = ",")) %>%
+  ungroup() %>%
+  distinct() %>%
+  arrange(analyte_dtxsid)
+
+prefit_df <- my_pk$prefit$fit_check %>% inner_join(get_winning_model(my_pk)) %>%
+  dplyr::select(analyte_dtxsid = Chemical, species = Species, model, method, 
+                fit_decision, fit_reason)
+
+left_join(my_tkstats, my_cvt_unique) %>%
+  left_join(prefit_df) %>%
+  ungroup() %>%
+  distinct() %>%
+  mutate(tkstats_id = row_number(), .before = analyte_dtxsid) %>% View("TKstats-CvTdb")
+  # write_tsv("data-raw/tkstats_CvTdb.tsv")
+
+```

### 2023-10-12 data-raw/Manuscript2023_Workflow.Rmd
Updating vignettes and some mapping variable names

@@
 ---
-title: "PK object batch mode trial"
+title: "Figures and Analysis for 2023 Manuscript"
 author: "Gilberto Padilla Mercado"
@@
 # Note that these mappings are now a default mappings, just being verbose here.
-minimal_pk <- pk(data = cvt_df,
+minimal_pk <- pk(data = cvt,
                  mapping = ggplot2::aes(

### 2023-10-12 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Updated some methods and data

@@
     dose_level_original = as.numeric(dose_level_original),
-    dose_volume_units = str_extract(dose_volume,
+    dose_volume_units = stringr::str_extract(dose_volume,
                                     pattern = "(?<=[:space:]).+"),
-    dose_volume = as.numeric(str_extract(dose_volume,
+    dose_volume = as.numeric(stringr::str_extract(dose_volume,
                                          pattern = "^(\\d|\\.)*")),
-    dose_duration_units = str_extract(dose_duration,
+    dose_duration_units = stringr::str_extract(dose_duration,
                                       pattern = "(?<=[space]).+"),
-    dose_duration = as.numeric(str_extract(dose_duration,
+    dose_duration = as.numeric(stringr::str_extract(dose_duration,
                                 pattern = "^\\d")),
@@
 sql_query <- sql_query %>%
-  rename_with(~gsub(pattern = "fk_", replacement = "",
+  dplyr::rename_with(~gsub(pattern = "fk_", replacement = "",
                          .x), .cols = contains("fk_"))
@@
 cvt_date <- Sys.Date()
-save(cvt_df, file = "data/cvt.rda", compress = "bzip2")
-save(cvt_date, file = "data/cvt_download_date.rda")
+cvt <- cvt_df
+save(cvt, file = "data/cvt.rda", compress = "bzip2")
+save(cvt_date, file = "data/cvt_date.rda")
 ```

### 2023-10-12 R/data.R

@@ -68,7 +68,7 @@
 #' Concentration vs. time data from CvTdb
 #'
 #' This is concentration vs. time data from CvTdb, most recently downloaded as
-#' of the date in [`cvt_download_date`].
+#' of the date in [`cvt_date`].
 #'
 #' These data have been filtered to retain only oral and intravenous
 #' administration, and only measurements in blood and plasma. They have also

### 2023-10-13 R/pk_methods_AIC.R
Updated vignettes and methods. Included the proper namespaces for tidyverse functions

@@ -75,8 +75,9 @@ AIC.pk <- function(obj,
     dplyr::select(!!!obj$data_group, param_name, param_units) %>%
     tidyr::expand_grid(model = unique(param_table$model))
 
-  params_df <- bind_rows(param_table, sigma_table) %>%
-    dplyr::group_by(!!!obj$data_group, model) %>% dplyr::count(name = "npar")
+  params_df <- dplyr::bind_rows(param_table, sigma_table) %>%
+    dplyr::group_by(!!!obj$data_group, model) %>%
+    dplyr::count(name = "npar")
 
 
   #get log-likelihoods
@@ -93,13 +94,13 @@ AIC.pk <- function(obj,
     dplyr::select(!!!obj$data_group,
                   model, method,
                   log_likelihood) %>%
-    left_join(params_df))
+    dplyr::left_join(params_df))
 
 
   #get number of parameters (excluding any constant, non-optimized parameters)
 
   AIC <- ll %>% dplyr::group_by(!!!obj$data_group, model) %>%
-    mutate(AIC = (k * npar) - (2 * log_likelihood))
+    dplyr::mutate(AIC = (k * npar) - (2 * log_likelihood))
 
 
   return(AIC)

### 2023-10-13 R/pk_methods_BIC.R

@@ -66,7 +66,7 @@ BIC.pk <- function(obj,
     dplyr::select(!!!obj$data_group, param_name, param_units) %>%
     tidyr::expand_grid(model = unique(param_table$model))
 
-  params_df <- bind_rows(param_table, sigma_table) %>%
+  params_df <- dplyr::bind_rows(param_table, sigma_table) %>%
     dplyr::group_by(!!!obj$data_group, model) %>% dplyr::count(name = "npar")
 
 
@@ -95,7 +95,7 @@ BIC.pk <- function(obj,
 
   BIC <- ll %>%
     dplyr::group_by(!!!obj$data_group, model, method) %>%
-    mutate(BIC = (log(NROW) * npar) - (2 * log_likelihood))
+    dplyr::mutate(BIC = (log(NROW) * npar) - (2 * log_likelihood))
 
 
   return(BIC)

### 2023-10-13 R/pk_methods_coef_sd.R

@@ -127,16 +127,16 @@ coef_sd.pk <- function(obj,
 
   newdata <- suppressMessages(
     newdata %>%
-      rowwise() %>%
-      filter(!is.null(observations)) %>%
-      mutate(model_fun = obj$stat_model[[model]]$conc_fun) %>%
-      left_join(obj$prefit$par_DF %>%
-                  filter(param_name %in% noptim_params) %>%
+      dplyr::rowwise() %>%
+      dplyr::filter(!is.null(observations)) %>%
+      dplyr::mutate(model_fun = obj$stat_model[[model]]$conc_fun) %>%
+      dplyr::left_join(obj$prefit$par_DF %>%
+                  dplyr::filter(param_name %in% noptim_params) %>%
                   dplyr::select(!!!obj$data_group, param_name, start)) %>%
-      distinct() %>%
-      mutate(const_pars = setNames(start, param_name)) %>%
-      ungroup() %>%
-      distinct())
+      dplyr::distinct() %>%
+      dplyr::mutate(const_pars = setNames(start, param_name)) %>%
+      dplyr::ungroup() %>%
+      dplyr::distinct())
 
   newdata <- newdata %>%
     dplyr::rowwise() %>%
@@ -153,8 +153,8 @@ coef_sd.pk <- function(obj,
     },
     x = coefs_vector,
     method = 'Richardson'))) %>%
-    ungroup() %>%
-    mutate(sds = map2(hessian_mat, coefs_vector, \(x, y) {
+    dplyr::ungroup() %>%
+    dplyr::mutate(sds = purrr::map2(hessian_mat, coefs_vector, \(x, y) {
       tryCatch(diag(solve(x))^(1/2) %>% as.numeric(),
                error = function(err){
                  if (!suppress.messages) {
@@ -177,7 +177,7 @@ coef_sd.pk <- function(obj,
                }) %>%
         set_names(nm = paste0(names(y), "_sd"))
     }),
-    alerts = map2(hessian_mat, coefs_vector, \(x, y) {
+    alerts = purrr::map2(hessian_mat, coefs_vector, \(x, y) {
       tryCatch({
         diag(solve(x))^(1/2) %>% as.numeric()
         return(paste0("Hessian successfully inverted"))
@@ -204,13 +204,13 @@ coef_sd.pk <- function(obj,
     dplyr::mutate(sds_tibble = purrr::map(sds,
                                           \(x) as.list(x) %>% as.data.frame)) %>%
       tidyr::unnest(sds_tibble) %>%
[…]

### 2023-10-13 R/pk_methods_get_tkstats.R

@@ -58,7 +58,7 @@
 #'   (For the built-in models `model_flat`, `model_1comp`, and `model_2comp`, these
 #'   variables are `param_name` and `param_value`.)
 #' @export
-#' @author Caroline Ring
+#' @author Caroline Ring, Gilberto Padilla Mercado
 #' @family methods for fitted pk objects
 get_tkstats.pk <- function(obj,
                            newdata = NULL,
@@ -158,7 +158,7 @@ get_tkstats.pk <- function(obj,
     tidyr::nest(.key = "c_data")
 
   tkstats_all <- tkstats_all %>%
-    reframe(tkstats_df = purrr::map(c_data,
+    dplyr::reframe(tkstats_df = purrr::map(c_data,
                                     \(x) {
                                       x %>%
                                         dplyr::rowwise() %>%

### 2023-10-17 data-raw/Manuscript2023_Workflow.Rmd
Added import and importFrom tags to functions

@@
 mvbutils::foodweb(where = asNamespace("invivoPKfit"),
-                  prune = "convert_time",
-                  # descendents = FALSE,
+                  prune = "calc_auc",
+                  # descendants = FALSE,
                   # ancestors = FALSE,
@@
 # Coef dependents: calc_auc, predict, get_tkstats, summary,log_Lik, coef_sd
+
+# list of all functions and methods
+fm <- ls(asNamespace("invivoPKfit"))
+fm <- fm[!grepl(".default", x = fm)]
+
+pdf(file = paste0(Sys.getenv("FIG_DIR"),
+              "NonDefaultFunction_Connections.pdf"),
+    height = 8, width = 8)
+for (i in fm) {
+  mvbutils::foodweb(where = asNamespace("invivoPKfit"),
+                  prune = i,
+                  # descendants = FALSE,
+                  # ancestors = FALSE,
+                  border = TRUE, cex = 1, lwd = 1.5)
+}
+dev.off()
 

### 2023-10-19 data-raw/Manuscript2023_Workflow.Rmd
Minor descriptors added to workflow document

@@
   mutate(foldConc = Conc / meanConc) %>%
+  # Plotting
   ggplot(aes(x = foldConc)) +
@@
         axis.ticks.y = element_blank())
+
+pl5A
 

### 2023-10-20 data-raw/Manuscript2023_Workflow.Rmd
Added label expressions 10^ and 2^ for plots on poster.

@@
   facet_grid(cols = vars(model)) +
-  scale_x_log10(limits = c(0.0001, 100)) +
-  scale_y_log10(limits = c(0.001, 1000)) +
+  scale_x_log10(labels = scales::label_math(format = log10),
+                limits = c(0.001, 100)) +
+  scale_y_log10(labels = scales::label_math(format = log10),
+                limits = c(0.001, 1000)) +
   scale_fill_viridis_c(option = "cividis",
                        limits = c(1, 100),
-                       oob = oob_squish) +
+                       oob = scales::oob_squish) +
   labs(y = "Model Error",
@@
 
+pl_7A
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "ModelPerformance_vDataVariability_2023-10-02.png"),
+              "ModelPerformance_vDataVariability_2023-10-19.png"),
        height = 3,
@@
 lombard_abbr <- lombard_abbr %>%
-  mutate(Species = "human", model = "lombardo") %>%
+  mutate(Species = "human", model = "Lombardo et al.") %>%
   rename(Vss = hVss, CLtot = hCltot) %>%
@@
 
-sfig4A <- lombardo_hist %>% ggplot(aes(x = log2(Vss), color = Source,
+sfig4A <- lombardo_hist %>% 
+  ggplot(aes(x = log2(Vss), color = Source,
              group = Source)) +
@@
                 bins = 20) +
-  labs(y = "Scaled Frequency") +
+  labs(y = "Scaled Frequency",
+       x = "Vss") +
+  scale_x_continuous(labels = scales::label_math(expr = 2^.x)) +
   scale_color_manual(values = c("black", "#1064c9")) +
@@
 
+sfig4A
 other_meta <- read_csv(
@@
     mutate(Source = ifelse(str_detect(Source, "tkstats"), "invivoPKfit",
-                           "Caco-2 Paper")) %>%
+                           "Honda et al.")) %>%
     ggplot(mapping = aes(
@@
     scale_color_manual(values = c("black", "green4"),
-                       breaks = c("invivoPKfit", "Caco-2 Paper")) +
+                       breaks = c("invivoPKfit", "Honda et al.")) +
+  labs(x = "Oral Bioavailability") +
   guides(color = guide_legend(nrow = 2)) +

### 2023-10-24 data-raw/Manuscript2023_Workflow.Rmd
Markdown changes and calculating proportion of timepoints that are replicated vs non-replicated per data series.

@@
        dpi = 300)
+
+all_my_data %>%
+  filter(Detect %in% TRUE,
+         exclude %in% FALSE,
+         Dose > 0) %>%
+  group_by(Chemical,
+           Species,
+           Reference,
+           Route, 
+           Media,
+           Dose, Time) %>%
+  count() %>%
+  mutate(Replicated = ifelse(n > 1, TRUE, FALSE)) %>%
+  distinct() %>% .$Replicated %>% table()
+  ggplot(aes(fill = Replicated)) +
+  geom_bar(position = "stack",
+           color = "black")
+  labs(x = "", y = "Timepoints") +
+  scale_fill_manual(values = c("black", "white")) +
+  scale_y_continuous(expand = c(0, NA)) +
+  theme_void() +
+  theme(legend.position = "bottom")
 

### 2023-11-02 data-raw/Manuscript2023_Workflow.Rmd
Ensure all imports are declared and fixing some tests

@@
 
+my_coefs <- coef(my_pk) %>% inner_join(winmodel) %>% inner_join(myAIC)
+
+my_coefs %>% dplyr::select(-sigma_value, -error_group, -coefs_vector) %>%
+  ungroup() %>%
+  distinct() %>%
+  inner_join(other_coefs %>% dplyr::select(model, method, Chemical, Species)) ->
+  my_coefs
+
+other_coefs <- read_csv(
+  "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/CvTdb_fullCoefs_20230906.csv")
+
+other_coefs %>% dplyr::select(model, method, Chemical, Species)
+
+write_csv(my_coefs, "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/CvTdb_fullCoefsAIC_2023.10.30.csv")
+
 ```
@@
          sum(is.na(Conc)) != n(),
-         LOQ < Conc) %>%
+         Conc > LOQ) %>% nrow()
   mutate(meanConc = mean(Conc, na.rm = TRUE)) %>%

### 2023-11-02 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Ensure all imports are declared and fixing some tests

@@
 
+```{r counting-replicates}
+count_query <- paste0(
+  "SELECT DISTINCT ",
+  "a.id, a.time_hr, a.conc, ",
+  "b.id, b.analyte_dtxsid, ",
+  "b.test_substance_dtxsid, b.conc_medium_normalized, ",
+  "c.id, c.administration_route_normalized, ",
+  "c.fk_extraction_document_id, c.dose_level_normalized, ",
+  "d.id, d.species ",
+
+  # Main Table
+  "FROM conc_time_values a ",
+
+  # Join with series table by series ID
+  "LEFT JOIN series b ON b.id = a.fk_series_id ",
+
+  # Join to studies table by study ID
+  "LEFT JOIN studies c ON c.id = b.fk_study_id ",
+
+  # Join to subjects table by subject ID
+  "LEFT JOIN subjects d ON d.id = b.fk_subject_id ",
+
+  # Filtering steps
+  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
+  "c.administration_route_normalized IN ('iv', 'oral')"
+)
+
+query_db(query = count_query,
+         schema = "cvt") %>%
+  select(-id) %>% 
+  filter(!is.na(analyte_dtxsid),
+         analyte_dtxsid == test_substance_dtxsid,
+         conc > 0) %>%
+  distinct() %>%
+  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
+           administration_route_normalized, species, fk_extraction_document_id,
+           dose_level_normalized) %>%
+  count() %>%
+  pull(n) %>% table()
+```
+
 # Validating data
@@
 -  Change original dose units for study _S0916_ and convert to mg/kg.  
--  Change original dose units for study _S0642_ and convert to mg/kg.  
+-  Change original dose units for study _S0624_ and convert to mg/kg.  
 -  Include a series of isotope tracing experiments from documents _65_, _61_, _46_, and _31_.  

### 2023-11-02 tests/testthat/test-pkproto_scale_data.R

@@ -22,8 +22,7 @@ test_that("scale_conc() returns an object with the expected names in its element
             obj <- scale_conc()
             expect_true(
               all(
-                c("ratio_conc_dose",
-                  "dose_norm",
+                c("dose_norm",
                   "log10_trans",
                   "expr") %in%
                   names(obj$value)

### 2023-11-07 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Slightly more stringent filtering for the creation of the cvt data set and adjusting the calc_loq_factor for imputed LOQs

@@
   mutate(loq = case_when(
-    other_study_identifier %in% "S0361" ~ 0.05,
-    other_study_identifier %in% "S0328" ~ 1, # This is inferred
+    # here omitted a change to a value for LOQ that doubles the minimum detected limit
+    other_study_identifier %in% "S0328" ~ 1, # This is inferred from the data
     # Highest value under loq is 0.9
     # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
+    # The method of imputation for loq may yet need to be improved
     .default = loq
@@
 
+# This is the final filtering so that the dataset is most consistent with the
+# most current near future pull in the new year
+cvt_df <- cvt_df %>%
+  filter(!is.na(analyte_dtxsid),
+         analyte_dtxsid == test_substance_dtxsid,
+         !(document_id %in% c(38, 65, 110, 112, 46, 31)),
+         !(other_study_identifier %in% c("S0916")),
+         !(analyte_name_original %in% "Methemoglobin"),
+         is.na(radiolabeled))
+
+cvt_df %>%
+  filter(conc > 0) %>%
+  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
+           administration_route_normalized, species, document_id,
+           dose_level_normalized) %>%
+  distinct() %>%
+  count() %>% 
+  ungroup() %>%
+  filter(n >= 10) %>% 
+  distinct(analyte_dtxsid, conc_medium_normalized,
+           administration_route_normalized, species, document_id,
+           dose_level_normalized) %>%
+  arrange(analyte_dtxsid, species, document_id) %>%
+  left_join(cvt_df) %>% 
+  View()
+
+cvt_df %>%
+  filter(conc > 0) %>%
+  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
+           administration_route_normalized, species, document_id,
+           dose_level_normalized) %>%
+  distinct() %>%
+  count() %>%
+  ungroup() %>%
+  count(n)
 ```
+
+This filtered and transformed dataset has 14,486 observations.
 

### 2023-11-08 data-raw/Manuscript2023_Workflow.Rmd
Updating pk object

@@
 # Note I have now saved the RDS file for JOINT model with L-BFGS-B
+# saveRDS(my_pk_100j, "data-raw/all_cvt_pk_JOINT.rds")
 my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")

### 2023-11-14 data-raw/Manuscript2023_Workflow.Rmd
Added alternate figures and data variability calculations

@@
   settings_preprocess(keep_data_original = TRUE,
-                      suppress.messages = TRUE) +
+                      suppress.messages = FALSE) +
   settings_optimx(method = c("L-BFGS-B")) +
@@
   theme(legend.position = "bottom")
+
+```
+
+### Figure 4A-2: Alternate version of Figure 4A
+
+This alternate version of Figure 4A aims to simplify the assessment of replication
+of datasets in invivoPKfit. In contrast to the original 4A, this will also result
+in the inclusion of datasets with recorded standard deviation values
+(i.e. non-indivudual animal data/summarized data).
+
+The way this will work is by calculating the average and standard deviations
+of individual animal data
+(eliminating individual animal data that does not have replicates)
+then testing the following:
+
+$$
+\frac{\mu + 2\sigma}{\mu} \leq 2
+$$
+
+Which essentially tests whether, at least 95% of data is within a factor of 2.
+The result is a bar chart that shows how many timepoints with replicate values
+passed this test. It minimizes the double (or more) counting of timepoints with
+multiple replicates from individual animal data.
+
+```{r fig4A-2-alt}
+iad_summary <- cvt %>% filter(conc > 0, n_subjects_in_series == 1) %>%
+  group_by(analyte_dtxsid, species, administration_route_normalized,
+           conc_medium_normalized, dose_level_corrected, document_id,
+           time_hr) %>%
+  filter(n() > 1) %>%
+  summarize(conc_sd_calc = sd(conc),
+            conc_avg_calc = mean(conc),
+            n_subjects_in_series = n())
+
+sud_summary <- cvt %>% filter(conc > 0,
+                              n_subjects_in_series > 1,
+                              !is.na(conc_sd_normalized)) %>%
+  mutate(conc_sd_calc = conc_sd_normalized,
+         conc_avg_calc = conc) %>%
+  distinct(analyte_dtxsid, species, administration_route_normalized,
+           conc_medium_normalized, dose_level_corrected, document_id,
+           time_hr, conc_sd_calc, conc_avg_calc, n_subjects_in_series)
+
+combined_summary <- bind_rows(sud_summary, iad_summary) %>%
+  rowwise() %>%
+  mutate(twofold_95 = ifelse((conc_avg_calc + (2*conc_sd_calc))/conc_avg_calc < 2,
+                             TRUE, FALSE))
+
+# With the mapped column names
+
+iad_summary <- all_my_data %>% filter(Conc > 0, N_Subjects == 1, Dose > 0) %>%
+  group_by(Chemical, Species, Route, Media, Dose, Reference, Time) %>%
+  filter(n() > 1) %>%
+  summarize(conc_sd_calc = sd(Conc),
+            conc_avg_calc = mean(Conc),
+            n_subjects_in_series = n())
+
+sud_summary <- all_my_data %>% filter(Conc > 0, N_Subjects > 1,
+                                      !is.na(Conc_SD), Dose > 0) %>%
+  mutate(conc_sd_calc = Conc_SD,
+         conc_avg_calc = Conc,
+         n_subjects_in_series = N_Subjects) %>%
+  distinct(Chemical, Species, Route, Media, Dose, Reference, Time,
+           conc_sd_calc, conc_avg_calc, n_subjects_in_series)
+
+combined_summary <- bind_rows(sud_summary, iad_summary) %>%
+  rowwise() %>%
+  mutate(twofold_95 = ifelse((conc_avg_calc + (2*conc_sd_calc))/conc_avg_calc < 2,
+                             TRUE, FALSE))
 
@@
 
+### Figure 5Alt
+
+```{r fig5Alt}
+this_preds <- inner_join(predict(my_pk), winmodel) %>%
+  rowwise() %>% mutate(foldPred = Conc_est/Conc) %>%
+  distinct(model, method, Chemical, Species, Route, Media, Dose, Time, foldPred) %>%
+  group_by(model, method, Chemical, Species, Route, Media, Dose, Time) %>%
+  summarize(avgFE = mean(foldPred, na.rm = TRUE))
+this_preds %>%
+  inner_join(combined_summary, by = join_by(Chemical, Species,
+                                            Route, Media,
+                                            Dose, Time)) %>%
+  filter(!is.na(model), avgFE > 0) %>% 
+  # For percentages
+  # ungroup() %>%
+  # filter(model %in% c("model_flat")) %>%
+  # count((foldPred >= 0.5 & foldPred <= 2) & !(foldConc >= 0.5 & foldConc <= 2)) %>%
+  # {100*.[[2,2]]/(.[[1,2]] + .[[2,2]])}
+  # For Plotting
+  ggplot(aes(
+    y = avgFE,
+    x = twofold_95
+  )) +
+  geom_bin2d(bins = 40, color = NA) +
+  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
+  scale_y_log10(labels = scales::label_math(format = log10),
+                limits = c(0.0001, 10000)) +
+  scale_fill_viridis_c(option = "cividis",
+                       limits = c(1, 200),
+                       oob = scales::oob_squish) +
+  labs(y = "Model Error",
+       x = "95% of data within 2-fold") +
+  theme(aspect.ratio = 1,
+        panel.border = element_rect(color = "black", fill = NA, size = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        axis.ticks = element_blank(),
+        axis.line = element_blank())
+
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "ModelPerformance_vDataVariability_2023-11-14.png"),
+       height = 4.5,
+       width = 4.5,
+       device = "png",
+       bg = "white",
+       dpi = 300,
+       units = "in")
+
+```
+
 ### Figure 6: Multiple goodness-of-fit metrics validate model performance

### 2023-11-16 data-raw/Manuscript2023_Workflow.Rmd
Updated with filtered cvt data.

@@
   mutate(nca_id = row_number(),
-         .before = analyte_dtxsid) %>% View("NCA-CvTdb")
-  # write_tsv("data-raw/NCA_CvTdb.tsv")
+         .before = analyte_dtxsid) %>%
+  # View("NCA-CvTdb")
+  write_tsv("data-raw/NCA_CvTdb.tsv")
 # Note that this will have more numbers because it still includes AUC_infinity == NA
@@
   distinct() %>%
-  mutate(tkstats_id = row_number(), .before = analyte_dtxsid) %>% View("TKstats-CvTdb")
-  # write_tsv("data-raw/tkstats_CvTdb.tsv")
-
-```
+  mutate(tkstats_id = row_number(), .before = analyte_dtxsid) %>%
+  # View("TKstats-CvTdb")
+  write_tsv("data-raw/tkstats_CvTdb.tsv")
+
+```

### 2023-11-30 R/pk_methods_do_fit.R
Fix typos in documentation and consolidating vignettes

@@ -24,6 +24,8 @@
 #' values.
 #'
 #' @param obj A [pk] object.
+#' @param n_cores Number of cores used for parallel computing.
+#' @param rate_names The names of the rate units. Leave NULL to utilize default 1/hour.
 #' @return The same [pk] object, with element `fit` containing the fitted
 #'   results for each model in `stat_model`.
 #' @export

### 2023-11-30 data-raw/TKstatsForCompTox_vignette.Rmd
Vignette for CompTox TK stats predictions needed

---
title: "Updated invivoPKfit predictions"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
set.seed(2023)
library(tidyverse, quietly = TRUE)
devtools::load_all() # Loads the invivopkfit package in feature/pkS3obj_facet branch
library(cowplot)
library(RColorBrewer)
tidyverse_conflicts()
# Note I have now saved the RDS file for JOINT model with L-BFGS-B optimization
my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
```

First we explore the different _settings_ used. These fits were generated using a 
hierarchical error model. The data group was Chemical and Species and the error
group additionally included Reference. The optimization algorithm used was **L-BFGS-B**.

```{r settings_output}
my_pk$settings_preprocess
my_pk$settings_data_info
my_pk$settings_optimx
my_pk$stat_error_model
my_pk$stat_model
my_pk$data_group
```

The following chunk pulls the *winning model* (with the lowest AIC)
and pulls the predicted TKstats from this for each chemical and species listed.
This results in 109 unique observations.

```{r tkstats_predictions}
winmodel <- get_winning_model(my_pk)
all_tkstats <- get_tkstats(my_pk) %>% inner_join(winmodel)

all_tkstats <- all_tkstats %>% ungroup() %>%
  dplyr::select(Chemical, Species, Vdist, V1, Vss, halflife, model) %>%
  distinct()

```

### 2023-12-01 data-raw/Manuscript2023_Workflow.Rmd
Added the alternative (new) figures to vignette and fixed lack of exclusion criteria for plot method

@@
   my_coefs
-
-other_coefs <- read_csv(
-  "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/CvTdb_fullCoefs_20230906.csv")
-
-other_coefs %>% dplyr::select(model, method, Chemical, Species)
-
-write_csv(my_coefs, "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/CvTdb_fullCoefsAIC_2023.10.30.csv")
 
@@
                              TRUE, FALSE))
+
+table(combined_summary$twofold_95)
+
+pl5A <- combined_summary %>% ungroup() %>%
+  count(twofold_95) %>%
+  ggplot(aes(x = twofold_95, fill = twofold_95, y = n)) +
+  geom_col(position = position_stack(),
+           color = "black", linewidth = 1) +
+  coord_cartesian(ylim = c(0, 4000)) +
+  scale_y_continuous(expand = c(0, 0),
+                     breaks = c(0, 1000, 2000, 3000),
+                     labels = c("0", "1", "2", "3")) +
+  scale_fill_manual(values = c("black", "white")) +
+  theme_classic() +
+  labs(x = "95% of observations\nwithin factor of 2",
+                y = "Observations\n(thousands)") +
+  theme(text = element_text(size = 10),
+        panel.border = element_rect(color = "black", linewidth = 1, fill = NA),
+        panel.background = element_blank(),
+        panel.grid.major.y = element_line(color = "grey90", linewidth = 0.4),
+        axis.title = element_text(face = "bold"),
+        axis.line = element_blank(),
+        plot.background = element_blank(),
+        axis.ticks.y = element_blank(),
+        legend.position = "none")
 
@@
 plot_grid(pl5A, pl5B, labels = c("A", "B"),
-                     align = "h", axis = "bt", rel_widths = c(1, 1.5))
+                     align = "h", axis = "bt", rel_widths = c(1, 2))
 
 figure5 <- plot_grid(pl5A, pl5B, labels = c("A", "B"),
-                     align = "h", axis = "bt", rel_widths = c(1, 1.5))
+                     align = "h", axis = "bt", rel_widths = c(1, 1.75))
 
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "Figure5_onlyDetects_2023-10-02.png"),
+              "Figure5alt_onlyDetects_2023-10-02.png"),
        plot = figure5,
@@
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "PredictedObserved_compartmentModels_2023-10-02.png"),
+              "PredictedObserved_compartmentModels_2023-11-30.png"),
        height = 6, width = 6)
@@
 ```{r fig5Alt}
+# Redo combined summary
+combined_summary <- bind_rows(sud_summary, iad_summary) %>%
+  rowwise() %>%
+  mutate(twofold_95 = ifelse((conc_avg_calc + (2*conc_sd_calc))/conc_avg_calc < 2,
+                             TRUE, FALSE))
+
+# Now
 this_preds <- inner_join(predict(my_pk), winmodel) %>%
@@
   summarize(avgFE = mean(foldPred, na.rm = TRUE))
-this_preds %>%
+
+pl_7Alt <- this_preds %>%
   inner_join(combined_summary, by = join_by(Chemical, Species,
@@
   filter(!is.na(model), avgFE > 0) %>% 
-  # For percentages
-  # ungroup() %>%
-  # filter(model %in% c("model_flat")) %>%
-  # count((foldPred >= 0.5 & foldPred <= 2) & !(foldConc >= 0.5 & foldConc <= 2)) %>%
-  # {100*.[[2,2]]/(.[[1,2]] + .[[2,2]])}
+  # 
   # For Plotting
@@
   geom_bin2d(bins = 40, color = NA) +
-  geom_hline(yintercept = c(0.5, 2), linetype = "dashed") +
+  geom_hline(yintercept = c(0.5, 2), linetype = "dashed", linewidth = 1, color = "red3") +
   scale_y_log10(labels = scales::label_math(format = log10),
@@
        width = 4.5,
+       device = "png",
+       bg = "white",
+       dpi = 300,
+       units = "in")
+
+this_preds %>%
+  inner_join(combined_summary, by = join_by(Chemical, Species,
+                                            Route, Media,
+                                            Dose, Time)) %>%
+  filter(!is.na(model), avgFE > 0) %>% ungroup() %>%
+  filter(model == "model_2comp") %>%
+  count(!(avgFE >= 0.5 & avgFE <= 2) & !twofold_95) %>%
+  {100*.[[2,2]]/(.[[1,2]] + .[[2,2]])} %>% round(digits = 1)
+
+# Table
+
+my_table <- data.frame(
+  c("Reasonable model error and observed variability",
+    "Data variability high, model error reasonable",
+    "Model error high, data variation reasonable",
+    "Both model error and data variability are high"),
+  c(37.2, 6.5,  41.4, 14.8),
+  c(53.6, 3.5,  32.4, 10.4),
+  c(11.0, 16.4, 46.6, 26.0),
+  c(44.2, 5.4,  37.4, 13.0))
+
+names(my_table) <- c(" ","1-compartment (%)", "2-compartment (%)", "Flat (%)", "Overall (%)")
+
+library(flextable)
+library(officer)
+
+flextable(my_table) %>%
+  border_inner() %>%
+  fontsize(part = "all", size = 11) %>%
+  bold(part = "all", j = 5)
+
+table_plot <- gen_grob(flextable(my_table) %>%
+                         border_inner() %>%
+                         fontsize(part = "all", size = 10) %>%
+                         bold(part = "all", j = 5) %>%
+                         autofit())
+
+dual_plot <- plot_grid(pl_7Alt, table_plot, ncol = 1, align = "v",
+          rel_heights = c(1, 0.5))
+
+dual_plot
+ggsave(paste0(Sys.getenv("FIG_DIR"),
+              "ModelPerformance_vDataVariability_wTable_2023-11-30.png"),
+       plot = dual_plot,
+       height = 4.5,
+       width = 6.5,
        device = "png",
@@
                  color = NA, fill = "grey5") +
-  scale_x_log10(labels = label_log()) +
+  scale_x_log10(labels = scales::label_math(format = log10)) +
   facet_grid(cols = vars(model)) +
@@
 pl <- plot(my_pk, use_scale_conc = TRUE, n_interp = 10)
-names(pl) # Chemical Species observations oservation_plot predicted predicted_plot final_plot
-
-s6_plA <- pl %>% filter(Chemical %in% "DTXSID90382620") %>%
+names(pl) # Chemical Species observations observation_plot predicted predicted_plot final_plot
+
+s6_plA <- pl %>% filter(Chemical %in% "DTXSID3031860") %>%
   pull(observation_plot) %>% .[[1]]
@@
 
-# Set colors palletes for each
+# Set colors palettes for each
 # panel A : Oranges
@@
 s6_plA <- s6_plA + 
-  labs(title = "fluorotelomer acid 7+3") +
+  labs(title = "perfluorodecanoic acid") +
   scale_color_manual(values = panelA_cols, aesthetics = c("color", "fill")) +
@@
 ggsave(paste0(Sys.getenv("FIG_DIR"),
-              "ExampleFitsPlots.png"),
+              "ExampleFitsPlots_11.30.2023.png"),
        width = 13,

### 2023-12-01 data-raw/Manuscript2023_Workflow.Rmd
Made sure not to evaluate chunks

@@
 
-```{r pooled_fitting_choices}
+```{r pooled_fitting_choices, eval=FALSE}
 # Types of Choices:
@@
 
-```{r joint_fitting_choices}
+```{r joint_fitting_choices, eval=FALSE}
 # Joint
@@
 
-```{r Evaluation-helpers}
+```{r Evaluation-helpers, eval=FALSE}
 # Evaluation
@@
 
-```{r Evaluating choices}
+```{r Evaluating choices, eval=FALSE}
 
@@
 
-```{r load_multirefs}
+```{r load_multirefs, eval=FALSE}
 # Reference Multiples
@@
 
-```{r Plotting_Summary}
+```{r Plotting_Summary, eval=FALSE}
 finalist_options <- c("000 Pooled", "000 Joint",
@@
 
-```{r Final_Options}
+```{r Final_Options, eval=FALSE}
 my_pk <- minimal_pk +
@@
 
-```{r data_aggregation}
+```{r data_aggregation, eval=FALSE}
 # Need the following data for any of the subsequent plots
@@
 ### Figure 4A: Replicated timepoint variation in CvTdb
-```{r fig4A}
+```{r fig4A, eval=FALSE}
 
@@
 
-```{r fig4A-2-alt}
+```{r fig4A-2-alt, eval=FALSE}
 iad_summary <- cvt %>% filter(conc > 0, n_subjects_in_series == 1) %>%
@@
 
-```{r fig4B-cowplot}
+```{r fig4B-cowplot, eval=FALSE}
 
@@
 
-```{r cvt_analysis}
+```{r cvt_analysis, eval=FALSE}
 data_range <- all_my_data %>%
@@
 
-```{r sFig2-model_performance}
+```{r sFig2-model_performance, eval=FALSE}
 my_preds %>%
@@
 
-```{r fig5-modelPerform-v-dataVar}
+```{r fig5-modelPerform-v-dataVar, eval=FALSE}
 
@@
 
-```{r fig5Alt}
+```{r fig5Alt, eval=FALSE}
 # Redo combined summary
@@
 
-```{r fig6-goodness-of-fit}
+```{r fig6-goodness-of-fit, eval=FALSE}
 
@@
 
-```{r sFig3-sigmaDistribution}
+```{r sFig3-sigmaDistribution, eval=FALSE}
 
@@
 
-```{r Lombardo_Comparison}
+```{r Lombardo_Comparison, eval=FALSE}
 cvt_DTXSIDs <- unique(my_pk$data$Chemical)
@@
 
-```{r otherMeta-analysis}
+```{r otherMeta-analysis, eval=FALSE}
 
@@
 
-```{r do_fit-benchmarking}
+```{r do_fit-benchmarking, eval=FALSE}
 
@@
 
-```{r sfig6-examples-of-fits}
+```{r sfig6-examples-of-fits, eval=FALSE}
 pl <- plot(my_pk, use_scale_conc = TRUE, n_interp = 10)
@@
 
-```{r more_analysis}
+```{r more_analysis, eval=FALSE}
 
@@
 
-```{r PredictionVariability_overtime}
+```{r PredictionVariability_overtime, eval=FALSE}
 my_residuals %>%
@@
 
-```{r function_connections}
+```{r function_connections, eval=FALSE}
 fw <- mvbutils::foodweb(where = asNamespace("invivoPKfit"),
@@
 
-```{r plotting_all_Fits}
+```{r plotting_all_Fits, eval=FALSE}
 ### Plotting for all (2.5MB file)
@@
 ### Figure 2
-```{r Explain-Heirarchical-Model}
+```{r Explain-Heirarchical-Model, eval=FALSE}
 # Note that the data will run one "Series" of time point at a time
@@
 
-```{r cvtdb-prep}
+```{r cvtdb-prep, eval=FALSE}
 

### 2023-12-05 data-raw/Manuscript2023_Workflow.Rmd
Expanded documentation for Manuscript Vignette

@@
 4. Analysis Plots  
-  - CvTdb replicate variation (Figure 4A)  
+  - CvTdb replicate variation (Figure 4A & Alternative)  
   - CvTdb replicate variation over ADME-normalized time (Figure 4B)  
@@
   - invivoPKfit model performance (Supplementary Figure 2)  
-  - Model performance vs Data variability (Figure 5)  
+  - Model performance vs Data variability (Figure 5 and Alternative)  
   - Goodness of fit plots (Figure 6)  
@@
 
-```{r pk_obj_fromSQL}
+The following chunk shows the column/field mapping from the `cvt` object and
+the `pk` object needed for invivoPKfit analysis.
+
+```{r pk_obj_fromSQL, eval=FALSE}
 
@@
 ### Figure 4A: Replicated timepoint variation in CvTdb
+
 ```{r fig4A, eval=FALSE}
@@
 
-### Figure 2
+### Figure 2: Example Fits to Explain Joint vs Pooled Models
+
 ```{r Explain-Heirarchical-Model, eval=FALSE}

### 2024-01-25 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Fixing dose_level_units_original to account for name change in CvTdb table.

@@
   "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
-  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
+  "c.dose_level_normalized, c.dose_level_original, c.dose_level_units_original, ",
   "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
@@
 cvt <- cvt_df
+cvt <- cvt %>% mutate(conc_normalized_units = "mg/L")
 save(cvt, file = "data/cvt.rda", compress = "bzip2")

### 2024-01-29 R/invivoPKfit-package.R
Add imports and adjusting method documentation to be in line with S3 generics. 0 errors 0 warnings 4 notes on CRAN check

@@ -6,7 +6,8 @@
 #'
 #' @name invivoPKfit
 #'
-#' @docType _PACKAGE
+#' @keywords internal
+"_PACKAGE"
 #'
 #' @author Caroline Ring, Chris Cook, John Wambaugh, Mitchell Teague, Gilberto Padilla Mercado
 NULL

### 2024-01-31 R/get_params_2comp.R
Changed the lower bound of F_abs to 1%

@@ -74,7 +74,7 @@
 #'
 #' ## Default lower and upper bounds for `Fgutabs`
 #'
-#' By default, the lower bound for `Fgutabs` is 0, and the upper bound for
+#' By default, the lower bound for `Fgutabs` is 0.01, and the upper bound for
 #' `Fgutabs` is 1. These are simply the bounds of the physically-meaningful
 #' range for a fraction.
 #'
@@ -123,7 +123,7 @@ get_params_2comp <- function(data,
                                                         k12 = log(2)/(2*max(Time_trans)),
                                                         k21 = log(2)/(2*max(Time_trans)),
                                                         V1 = 0.01,
-                                                        Fgutabs = 0,
+                                                        Fgutabs = 0.01,
                                                         kgutabs = log(2)/(2*max(Time_trans)),
                                                         Fgutabs_V1 = 0.01,
                                                         Rblood2plasma = 1e-2),

### 2024-01-31 R/get_params_2comp.R
Fgutabs changed back to zero

@@ -74,7 +74,7 @@
 #'
 #' ## Default lower and upper bounds for `Fgutabs`
 #'
-#' By default, the lower bound for `Fgutabs` is 0.01, and the upper bound for
+#' By default, the lower bound for `Fgutabs` is 0.0, and the upper bound for
 #' `Fgutabs` is 1. These are simply the bounds of the physically-meaningful
 #' range for a fraction.
 #'
@@ -126,7 +126,7 @@ get_params_2comp <- function(data,
                                                         k12 = log(2)/(2*max(Time_trans)),
                                                         k21 = log(2)/(2*max(Time_trans)),
                                                         V1 = 0.01,
-                                                        Fgutabs = 0.01,
+                                                        Fgutabs = 0.0,
                                                         kgutabs = log(2)/(2*max(Time_trans)),
                                                         Fgutabs_V1 = 0.01,
                                                         Rblood2plasma = 1e-2),

### 2024-03-05 data-raw/RestrictiveClearance_comparison.Rmd
Preliminary comparative analysis on restrictive vs non-restrictive clearance from httk and the values estimated by invivoPKfit

---
title: "Restrictive Clearance Comparison"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette describes comparisons between invivoPKfit predicted and those from httk.

```{r library_loading}
devtools::load_all()
library(httk)
my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
```

The first thing I need to do is get the chemicals included in both the CvTdb subset
and the httk empirical data for pbpk.

```{r chems_in_common}
common_chems <- cvt %>%
  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "pbtk")) %>%
  pull(analyte_dtxsid) %>%
  unique()

```

Next I need to get the clearances using the `calc_total_clearance(dtxsid, restrictive.clearance)`
function from httk. Also need the clearances from invivoPKfit's winning models.

```{r get_clearances}
clearance_df <- data.frame(Chemical = common_chems) %>%
  rowwise() %>%
  mutate(Restrict_Cl = calc_total_clearance(dtxsid = Chemical,
                                            restrictive.clearance = TRUE,
                                            suppress.messages = TRUE),
         nonRestrict_Cl = calc_total_clearance(dtxsid = Chemical,
                                            restrictive.clearance = FALSE,
                                            suppress.messages = TRUE)) %>%
  ungroup()

my_tkstats <- eval_tkstats(my_pk) %>%
  dplyr::select(Chemical, Species, CLtot.tkstats, CLtot.nca) %>%
  distinct() %>%
  filter(Chemical %in% common_chems,
         !is.na(CLtot.tkstats), !is.na(CLtot.nca)) %>%
  group_by(Chemical, Species, CLtot.tkstats) %>%
  summarize(CLtot.nca_mean = mean(CLtot.nca),
            CLtot.nca_sd = sd(CLtot.nca))

# Combine these two
combined_clearance_df <- my_tkstats %>% inner_join(clearance_df)

```

Finally, let's visualize where the tkstats predictions land.

```{r viz}

# Preliminary viz, plot all clearances
combined_clearance_df %>%
  relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
  pivot_longer(cols = 3:6,
               names_to = "Clearance_Source",
               values_to = "Value") %>%
  ggplot(aes(x = Value,
             y = Chemical,
             fill = Clearance_Source)) +
  geom_point(shape = 21, alpha = 0.7) +
  scale_x_log10() +
  scale_fill_manual(breaks = c("nonRestrict_Cl", "CLtot.tkstats",
                               "CLtot.nca_mean",
                               "Restrict_Cl"),
                    labels = c("non-restrictive clearance (httk)",
                               "predicted clearance (invivoPKfit)",
                               "mean non-compartmental total clearance (invivoPKfit)",
                               "restrictive clearance (httk)"),
                    values = c("orange2", "grey5", "skyblue3",  "green4")) +
  facet_grid(rows = vars(Species), scales = "free", space = "free") +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.position = "bottom",
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "initial_tkClearance_comparison_httk.png"),
       height = 14,
       width = 5,
       device = "png")
```

### 2024-03-21 data-raw/RestrictiveClearance_comparison.Rmd
Update using gas_pbpk for initial comparison. Total clearance for 3 more chemicals-species groups are able to be compared for a total of 36

@@
 common_chems <- cvt %>%
-  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "pbtk")) %>%
+  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk")) %>%
   pull(analyte_dtxsid) %>%
@@
 
+common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "pbtk"))] %>% unique() %>% sort()
 ```
@@
 ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "initial_tkClearance_comparison_httk.png"),
+                         "tkClearance_comparison_httk_gasPBPK.png"),
        height = 14,

### 2024-03-27 data-raw/RestrictiveClearance_comparison.Rmd
Preparation for implementation of static restrictive vs non-restrictive total clearance models

@@
 
-common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "pbtk"))] %>% unique() %>% sort()
+common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk"))] %>%
+  unique() %>%
+  sort()
 ```
@@
          nonRestrict_Cl = calc_total_clearance(dtxsid = Chemical,
+                                            restrictive.clearance = FALSE,
+                                            suppress.messages = TRUE)) %>%
+  ungroup()
+
+hep_clearance_df <- data.frame(Chemical = common_chems) %>%
+  rowwise() %>%
+  mutate(Restrict_Cl = calc_hep_clearance(dtxsid = Chemical,
+                                            restrictive.clearance = TRUE,
+                                            suppress.messages = TRUE),
+         nonRestrict_Cl = calc_hep_clearance(dtxsid = Chemical,
                                             restrictive.clearance = FALSE,
@@
 ```
+
+Finally, what I want to analyze is how good the fits for these chemicals are relative to the rest of the chemicals.
+
+```{r fit_analysis}
+wm <- get_winning_model(my_pk)
+ingroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
+  filter(Chemical %in% combined_clearance_df$Chemical) %>%
+  mutate(Group = "in httk")
+
+outgroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
+  filter(!(Chemical %in% combined_clearance_df$Chemical)) %>%
+  mutate(Group = "not in httk")
+
+all_group_rmse <- bind_rows(ingroup_rmse, outgroup_rmse)
+
+all_group_rmse %>%
+  filter(Species == "rat") %>%
+  ggplot(aes(x = Rsq, y = Chemical,
+             shape = Group)) +
+  geom_point() +
+  facet_grid(rows = vars(Group), scales = "free", space = "free") +
+  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        legend.direction = "vertical",
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text.y = element_blank())
+
+ggsave(paste0(Sys.getenv("FIG_DIR"), "Rsq_gaspbtk.png"),
+       height = 5,
+       width = 5)
+
+```
+
+## Exploring _httk_ parameters and solved values for `gas_pbtk`
+
+```{r httk_solution}
+httk::calc_tkstats(dtxsid = unique(combined_clearance_df$Chemical)[[5]])
+httk::parameterize_gas_pbtk(restrictive.clearance = TRUE,
+                            dtxsid = unique(combined_clearance_df$Chemical)[[5]])
+
+httk::solve_gas_pbtk(dtxsid = unique(combined_clearance_df$Chemical)[[5]],
+                     parameters = httk::parameterize_gas_pbtk(
+                       restrictive.clearance = TRUE,
+                       dtxsid = unique(combined_clearance_df$Chemical)[[5]]
+                       ),
+                     dose = 10,
+                     exp.conc = 0,
+                     input.units = "mg",
+                     output.units = "mg",
+                     days = 3,
+                     plots = TRUE)
+
+```

### 2024-03-29 data-raw/RestrictiveClearance_comparison.Rmd
New restrictive clearance updates.

@@
 
+# For the invivoPKfit functions, we will hold kelim constant
+# This constant will be calculated as CLtot/Vdist (or V1, if 2-compartment)
+# This constant is derived by httk in the following way:
+calc_total_clearance(dtxsid = common_chems[[10]],
+                             restrictive.clearance = FALSE) /
+  calc_vdist(dtxsid = common_chems[[10]])
+
 ```
+
+I have modified the starts of the 1- and 2-compartment models,
+as well as adding a restrictive_clearance argument in stat_model.
+
+```{r running-invivoPKfit}
+minimal_pk <- pk(data = cvt %>%
+                   filter(analyte_dtxsid %in% unique(combined_clearance_df$Chemical)),
+                 mapping = ggplot2::aes(
+                   Chemical = analyte_dtxsid,
+                   Chemical_Name = analyte_name_original,
+                   DTXSID = analyte_dtxsid,
+                   CASRN = analyte_casrn,
+                   Species = species,
+                   Reference = document_id,
+                   Media = conc_medium_normalized,
+                   Route = administration_route_normalized,
+                   Dose = dose_level_normalized,
+                   Dose.Units = "mg/kg",
+                   Subject_ID = subject_id,
+                   Series_ID = series_id,
+                   Study_ID = study_id,
+                   ConcTime_ID = conc_time_id,
+                   N_Subjects = n_subjects_in_series,
+                   Weight = weight_kg,
+                   Weight.Units = "kg",
+                   Time = time_hr,
+                   Time.Units = "hours",
+                   Value = conc,
+                   Value.Units = "mg/L",
+                   Value_SD = conc_sd_normalized,
+                   LOQ = loq
+                 ))
+
+new_pk <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = FALSE) +
+  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+new_pk <- do_data_info(new_pk)
+
+rest_pk <- do_prefit(new_pk, restrictive_clearance = TRUE)
+rest_pk <- do_fit(rest_pk, n_cores = 6) # Worked!
+
+nonrest_pk <- do_prefit(new_pk, restrictive_clearance = FALSE)
+nonrest_pk <- do_fit(nonrest_pk, n_cores = 6) # Worked!
+
+old_pk <- do_prefit(new_pk, restrictive_clearance = NULL)
+old_pk <- do_fit(old_pk, n_cores = 6)
+
+# Unfortunately, it seems the optimizer fails 
+# Need to investigate why!!
+# Are the kelims calculated too far from those estimated from the data?
+
+rest_wm <- get_winning_model(rest_pk)
+rest_AIC <- AIC(rest_pk)
+rest_rsq <- rsq(rest_pk)
+
+eval_tkstats(rest_pk) %>% View()
+residuals(rest_pk) %>% View()
+
+pl <- plot(rest_pk, n_interp = 12, use_scale_conc = TRUE)
+pdf(file = paste0(Sys.getenv("FIG_DIR"),
+              "RestrictiveCL_AllFits_Final_202402_08.pdf"),
+    height = 6, width = 10)
+for (i in 1:nrow(pl)) {
+  print(pl$final_plot[[i]])
+}
+dev.off()
+
+# Non-restrictive fits (constant kelim)
+
+pl <- plot(nonrest_pk, n_interp = 12, use_scale_conc = TRUE)
+pdf(file = paste0(Sys.getenv("FIG_DIR"),
+              "Non-restrictiveCL_AllFits_Final_202402_08.pdf"),
+    height = 6, width = 10)
+for (i in 1:nrow(pl)) {
+  print(pl$final_plot[[i]])
+}
+dev.off()
+
+# try dawson
+httk::load_dawson2021()
+
+```

### 2024-04-04 data-raw/RestrictiveClearance_comparison.Rmd
Added a kelim comparison for "old fits" and the newer restrictive vs non-restrictive fits to diagnose an issue with fitting algorithm.

@@
 minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% unique(combined_clearance_df$Chemical)),
+                   filter(analyte_dtxsid %in% "DTXSID0020442"),
                  mapping = ggplot2::aes(
@@
 
+```
+
+Why are so many fits failing?
+Well, we should take a look at the parameter which we are holding constant,
+`kelim` and whether the new starting points vastly differ from those in the
+starting points based on the data.
+
+For this I will just use the PK object I have saved `my_pk` and take the
+_prefit_ parameter estimations and first compare that with eventual optimized `kelim`.
+
+```{r kelim-questions}
+
+# Original data, filtered for common_chems
+# par_DF
+my_kelim_prefit <- my_pk$prefit$par_DF %>%
+  filter(param_name %in% "kelim",
+         Chemical %in% common_chems) %>%
+  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)
+
+my_kelim_fit <- coef(my_pk) %>%
+  inner_join(get_winning_model(my_pk)) %>%
+  ungroup() %>%
+  distinct(model, Chemical, Species, kelim) %>%
+  rename(fit_kelim = "kelim") %>%
+  filter(Chemical %in% common_chems)
+
+my_kelim_df <- inner_join(my_kelim_fit, my_kelim_prefit)
+
+httk_df <- rest_pk$prefit$par_DF %>%
+  filter(param_name %in% "kelim") %>%
+  distinct(Chemical, Species, param_name, start) %>%
+  rename(init_restrictive = "start") %>%
+  inner_join(
+    nonrest_pk$prefit$par_DF %>%
+  filter(param_name %in% "kelim") %>%
+  distinct(Chemical, Species, param_name, start) %>%
+  rename(init_nonrestrictive = "start"))
+
+full_df <- inner_join(my_kelim_df, httk_df) %>%
+  relocate(fit_kelim, .after = last_col())
+
+full_df %>%
+  ggplot(aes(x = Chemical)) +
+  geom_hline(yintercept = 1, linetype = "dashed", color = "grey30") +
+  geom_errorbar(aes(ymax = upper_bound, ymin = lower_bound)) +
+  geom_point(aes(y = fit_kelim, color = "Original Optimized")) +
+  geom_point(aes(y = init_restrictive, color = "Restrictive")) +
+  geom_point(aes(y = init_nonrestrictive, color = "Non-restrictive")) +
+  geom_point(aes(y = start, shape = "Original Initialized")) +
+  facet_grid(rows = vars(Species), scales = "free", space = "free") +
+  scale_color_manual(name = "kelim",
+                     breaks = c("Original Optimized", "Restrictive", "Non-restrictive"),
+                     values = c("Original Optimized" = "skyblue4", 
+                                "Restrictive" = "orange2",
+                                "Non-restrictive" = "green4")) +
+  scale_shape_manual(name = "",
+                     values = 4) +
+  coord_flip() +
+  scale_y_log10(labels = scales::label_math(format = log10)) +
+  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
+        panel.background = element_blank(),
+        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
+        strip.background = element_rect(fill = "white"),
+        strip.text = element_text(face = "bold"),
+        legend.direction = "vertical",
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        axis.text.y = element_blank(),
+        strip.text.y = element_text(angle = 0))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare_2024_0329.png"),
+       height = 11,
+       width = 8.5)
+```
+
+```{r testing_optimx}
+test_optimx <- do.call(
+          optimx::optimx,
+          args = c(
+            list(par = opt_params,
+                 fn = log_likelihood,
+                 lower = lower_params,
+                 upper = upper_params),
+            #method and control
+            settings_optimx,
+            #... additional args to log_likelihood
+            list(
+              const_params = const_params,
+              data = data,
+              data_sigma_group = data$data_sigma_group,
+              modelfun = modelfun,
+              dose_norm = dose_norm,
+              log10_trans = log10_trans,
+              negative = TRUE,
+              force_finite = TRUE,
+              suppress.messages = FALSE
+            ) #end list()
+          ) #end args = c()
+        ) #end do.call
+```
+
+```{r}
+
 rest_wm <- get_winning_model(rest_pk)

### 2024-04-04 data-raw/RestrictiveClearance_comparison.Rmd
Added restrictive and non-restrictive, constant kelim versions of 1-/2-compartment models

@@
 minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% "DTXSID0020442"),
+                   filter(analyte_dtxsid %in% common_chems[1:8]),
                  mapping = ggplot2::aes(
@@
   scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
+  stat_model(model = c("model_flat", "model_1comp",
+                       "model_1comp_rest", "model_1comp_nonrest"))
 new_pk <- do_data_info(new_pk)
 
-rest_pk <- do_prefit(new_pk, restrictive_clearance = TRUE)
-rest_pk <- do_fit(rest_pk, n_cores = 6) # Worked!
+new_pk <- do_prefit(new_pk)
 
-nonrest_pk <- do_prefit(new_pk, restrictive_clearance = FALSE)
-nonrest_pk <- do_fit(nonrest_pk, n_cores = 6) # Worked!
+new_pk$prefit$par_DF %>% View()
 
-old_pk <- do_prefit(new_pk, restrictive_clearance = NULL)
-old_pk <- do_fit(old_pk, n_cores = 6)
+new_pk <- do_fit(new_pk) # For troubleshooting
 
-# Unfortunately, it seems the optimizer fails 
-# Need to investigate why!!
-# Are the kelims calculated too far from those estimated from the data?
+new_pk <- do_fit(new_pk, n_cores = 6) 
+# Multidplyr error because of forgotten browser() call within log_likelihood
+new_pk$fit %>% unnest(fit) %>% View()
+
+coef(new_pk) %>% View()
+eval_tkstats(new_pk) %>% View()
+
+AIC(new_pk) %>% filter(method %in% "L-BFGS-B") %>% arrange(Chemical, Species) %>%
+  View()
+
+pl <- plot(new_pk, use_scale_conc = TRUE, method = "L-BFGS-B", n_interp = 10)
 

### 2024-04-04 R/get_params_2comp_nonrest.R

@@ -1,4 +1,4 @@
-#' Get parameters for 2-compartment model
+#' Get parameters for 2-compartment model (non-restrictive)
 #'
 #' Get parameters for 2-compartment model and determine whether each is to be
 #' estimated from the data
@@ -124,8 +124,8 @@
 #' @family get_params functions
 #' @family built-in model functions
 
-get_params_2comp <- function(data,
-                             lower_bound = ggplot2::aes(kelim = log(2)/(2*max(Time_trans)),
+get_params_2comp_nonrest <- function(data,
+                             lower_bound = ggplot2::aes(kelim = 0,
                                                         k12 = log(2)/(2*max(Time_trans)),
                                                         k21 = log(2)/(2*max(Time_trans)),
                                                         V1 = 0.01,
@@ -133,7 +133,7 @@ get_params_2comp <- function(data,
                                                         kgutabs = log(2)/(2*max(Time_trans)),
                                                         Fgutabs_V1 = 0.01,
                                                         Rblood2plasma = 1e-2),
-                             upper_bound = ggplot2::aes(kelim = log(2)/(0.5*min(Time_trans[Time_trans>0])),
+                             upper_bound = ggplot2::aes(kelim = 1E6,
                                                         k12 = log(2)/(0.5*min(Time_trans[Time_trans>0])),
                                                         k21 = log(2)/(0.5*min(Time_trans[Time_trans>0])),
                                                         V1 = 100,
@@ -142,45 +142,45 @@ get_params_2comp <- function(data,
                                                         Fgutabs_V1 = 1e2,
                                                         Rblood2plasma = 100),
                              param_units = ggplot2::aes(kelim = paste0("1/", #kelim
-                                                         unique(Time_trans.Units)),
-                                          V1 = paste0("(", #V1
-                                                         unique(Dose.Units),
-                                                         ")",
-                                                         "/",
-                                                         "(",
-                                                         unique(Conc.Units),
-                                                         ")"),
-                                          k21 = paste0("1/", #k21
-                                                         unique(Time_trans.Units)),
-                                          k12 = paste0("1/", #k12
-                                                         unique(Time_trans.Units)),
-                                          Fgutabs = "unitless fraction", #Fgutabs
-                                          kgutabs = paste0("1/", #kgutabs
-                                                           unique(Time_trans.Units)),
-                                          Fgutabs_V1 = paste0("(", #Fgutabs_V1
-                                                                 unique(Conc.Units),
[…]

### 2024-04-04 R/get_starts_2comp_rest.R

@@ -39,22 +39,9 @@
 #'
 #'# Starting value for `kelim`
 #'
-#'If IV data exist, then only IV data are used to derive starting estimates for
-#'`kelim`, even if oral data also exist.
-#'
-#'If only oral data exist, then the oral data are used to derive a starting
-#'estimate for `kelim`.
-#'
-#'Whichever data set is used (IV or oral), the starting value for `kelim` is
-#'derived by assuming that the range of observed time values in the data set
-#'spans two elimination half-lives. This implies that the elimination half-life
-#'is equal to the midpoint of observed time values, and that the starting value
-#'for the elimination time constant `kelim` is therefore `log(2)` divided by the
-#'midpoint of observed time values.
-#'
-#'Of course, this assumption is unlikely to be correct. However, we hope that it
-#'will yield a starting guess for `kelim` that is at least on the right order of
-#'magnitude.
+#'This value is held constant such that it equals `CLtot`/`Vdist` as calculated
+#'by _httk_. It is not optimized in this case and `CLtot` is calculated assuming
+#'`restrictive.clearance = TRUE`.
 #'
 #' # Starting value for `V1`
 #'
@@ -155,10 +142,14 @@
 #' @family 2-compartment model functions
 #' @family get_starts functions
 #' @family built-in model functions
-get_starts_2comp <- function(data,
+get_starts_2comp_rest <- function(data,
                              par_DF){
 
-  kelim <- NA_real_
+  kelim <- httk::calc_total_clearance(dtxsid = unique(data$Chemical),
+                                      restrictive.clearance = TRUE,
+                                      suppress.messages = TRUE) /
+    httk::calc_vdist(dtxsid = unique(data$Chemical),
+                     suppress.messages = TRUE)
   kgutabs <- NA_real_
   V1 <- NA_real_
   Fgutabs_V1 <- NA_real_
@@ -169,7 +160,6 @@ get_starts_2comp <- function(data,
 
   # Get starting Concs from data
 
-  # Get starting Concs from data
 
   #Work only with detects for these rough estimates
   tmpdat <- subset(data,
@@ -184,11 +174,6 @@ get_starts_2comp <- function(data,
   # Quick and dirty:
   #IV data estimates, if IV data exist
   if(nrow(ivdat)>0){
-
[…]

### 2024-04-04 R/pk_methods_do_prefit.R
Added restrictive and non-restrictive, constant kelim versions of 1-/2-compartment models. Added RData files for some models.

@@ -141,8 +141,7 @@ sigma_DF <- do.call(dplyr::group_by,
                               !!!obj$data_group) %>%
       dplyr::reframe(do.call(obj$stat_model[[this_model]]$params_fun,
                                args = c(list(dplyr::cur_data_all()),
-                                        obj$stat_model[[this_model]]$params_fun_args,
-                                        restrictive_clearance = restrictive_clearance)
+                                        obj$stat_model[[this_model]]$params_fun_args)
                                )
       ) %>% as.data.frame()
 

### 2024-04-04 data-raw/RestrictiveClearance_comparison.Rmd
Finishing the preliminary implementation of restrictive/non-restrictive clearance models

@@
                       suppress.messages = FALSE) +
-  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
+  settings_optimx(method = c("L-BFGS-B")) +
   scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
   stat_error_model(error_group = vars(Chemical, Species, Reference)) +
-  stat_model(model = c("model_flat", "model_1comp",
-                       "model_1comp_rest", "model_1comp_nonrest"))
+  stat_model(model = c("model_flat", "model_1comp", "model_2comp",
+                       "model_1comp_rest", "model_1comp_nonrest",
+                       "model_2comp_rest", "model_2comp_nonrest"))
 new_pk <- do_data_info(new_pk)
@@
 
-new_pk$prefit$par_DF %>% View()
+new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "kelim") %>%
+  View()
 
@@
 
-pl <- plot(new_pk, use_scale_conc = TRUE, method = "L-BFGS-B", n_interp = 10)
+pl2comp <- plot(new_pk, use_scale_conc = FALSE,
+           model = "model_2comp_nonrest",
+           n_interp = 10)
 
+pl2comp %>%
+  filter(Chemical %in% "DTXSID0021383") %>% pull(final_plot) %>% .[[1]]
 ```

### 2024-04-05 data-raw/RestrictiveClearance_comparison.Rmd
Clarified some functions, added systematic comparisons between constant and optimized kelim models

@@
 library(httk)
+library(tidyverse)
 my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
@@
 minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% common_chems[1:8]),
+                   filter(analyte_dtxsid %in% common_chems),
                  mapping = ggplot2::aes(
@@
 
-new_pk <- do_fit(new_pk, n_cores = 6) 
+new_pk <- do_fit(new_pk, n_cores = 10) 
 # Multidplyr error because of forgotten browser() call within log_likelihood
@@
 coef(new_pk) %>% View()
-eval_tkstats(new_pk) %>% View()
+eval_tkstats(new_pk, finite_only = FALSE) %>% View()
+get_winning_model(new_pk) %>% View("winning_model")
 
@@
        width = 8.5)
-```
 
-```{r testing_optimx}
-test_optimx <- do.call(
-          optimx::optimx,
-          args = c(
-            list(par = opt_params,
-                 fn = log_likelihood,
-                 lower = lower_params,
-                 upper = upper_params),
-            #method and control
-            settings_optimx,
-            #... additional args to log_likelihood
-            list(
-              const_params = const_params,
-              data = data,
-              data_sigma_group = data$data_sigma_group,
-              modelfun = modelfun,
-              dose_norm = dose_norm,
-              log10_trans = log10_trans,
-              negative = TRUE,
-              force_finite = TRUE,
-              suppress.messages = FALSE
-            ) #end list()
-          ) #end args = c()
-        ) #end do.call
 ```
@@
 
-rest_wm <- get_winning_model(rest_pk)
-rest_AIC <- AIC(rest_pk)
-rest_rsq <- rsq(rest_pk)
+new_wm <- get_winning_model(new_pk)
+new_AIC <- AIC(new_pk)
+new_rsq <- rsq(new_pk)
 
-eval_tkstats(rest_pk) %>% View()
-residuals(rest_pk) %>% View()
+new_tkstats <- eval_tkstats(new_pk, finite_only = FALSE)
 
-pl <- plot(rest_pk, n_interp = 12, use_scale_conc = TRUE)
+residuals(new_pk) %>% View()
+
+pl <- plot(new_pk, n_interp = 12, use_scale_conc = TRUE, best_fit = TRUE)
 pdf(file = paste0(Sys.getenv("FIG_DIR"),
-              "RestrictiveCL_AllFits_Final_202402_08.pdf"),
+              "BestFits_Final_2024_0405.pdf"),
     height = 6, width = 10)
@@
 
-# Non-restrictive fits (constant kelim)
+```
 
-pl <- plot(nonrest_pk, n_interp = 12, use_scale_conc = TRUE)
-pdf(file = paste0(Sys.getenv("FIG_DIR"),
-              "Non-restrictiveCL_AllFits_Final_202402_08.pdf"),
-    height = 6, width = 10)
-for (i in 1:nrow(pl)) {
-  print(pl$final_plot[[i]])
-}
-dev.off()
+Comparing total clearance estimates for those where a restrictive or non-restrictive model
+was the "best fit" as determined by AIC.
 
+```{r cltot-comparison}
+new_cltot2 <- new_tkstats %>% 
+  # filter(str_detect(model, "rest")) %>%
+  select(Chemical, Species, Media, Route, 
+         model, method,
+         CLtot.tkstats, CLtot.nca) %>%
+  filter(!is.na(CLtot.tkstats)) %>%
+  mutate(clearance_type = ifelse(str_detect(model, "nonrest"),
+                                "NonRestrictive",
+                                ifelse(str_detect(model, "rest"),
+                                       "Restrictive",
+                                       "optimized kelim"))) %>%
+  rowwise() %>%
+  mutate(CLtot.httk_rest = calc_total_clearance(dtxsid = Chemical,
+                                           restrictive.clearance = TRUE),
+         CLtot.httk_nonrest = calc_total_clearance(dtxsid = Chemical,
+                                           restrictive.clearance = FALSE))
+
+new_cltot2 %>%
+  ggplot(aes(x = Chemical)) +
+  geom_point(aes(y = CLtot.httk_rest),shape = 19, size = 2, color = "green4") +
+  geom_point(aes(y = CLtot.httk_nonrest),shape = 19, size = 2, color = "orange2") +
+  geom_point(aes(y = CLtot.tkstats), shape = 1, size = 3, color = "black", stroke = 1) +
+  scale_y_log10(labels = scales::label_math(format = log10)) +
+  geom_hline(yintercept = c(0.01, 0.1, 1, 10)) +
+  coord_flip() +
+  facet_grid(rows = vars(clearance_type),
+             scales = "free", space = "free") +
+  labs(title = "Total Clearance for constant kelim \"best fits\" (empty)\nand httk calculations (filled)") +
+  theme_bw() +
+  theme(axis.line = element_line(linewidth = 1),
+        axis.text = element_text(size = 12),
+        axis.title = element_blank(),
+        plot.title = element_text(hjust = 0.5),
+        plot.background = element_rect(fill = "white"))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_backcompare_2024_0405.png"),
+       height = 4,
+       width = 6)
+
+```
+
+```{r chemical-correlation}
+new_AIC %>%
+  ungroup() %>%
+  filter(model %in% c("model_1comp", "model_2comp"),
+         Species %in% "rat") %>%
+  group_by(Chemical) %>%
+  filter(AIC == min(AIC)) %>%
+  mutate(estimate = "nonConst") %>%
+  distinct(Chemical, model, estimate) -> nAIC_nonConst
+new_AIC %>%
+  ungroup() %>%
+  filter(model %in% c("model_1comp_rest", "model_2comp_rest"),
+         Species %in% "rat") %>%
+  group_by(Chemical) %>%
+  filter(AIC == min(AIC)) %>%
+  mutate(estimate = "Rest") %>%
+  distinct(Chemical, model, estimate) -> nAIC_rest
+new_AIC %>%
+  ungroup() %>%
+  filter(model %in% c("model_1comp_nonrest", "model_2comp_nonrest"),
+         Species %in% "rat") %>%
+  group_by(Chemical) %>%
+  filter(AIC == min(AIC)) %>%
+  mutate(estimate = "nonRest") %>%
+  distinct(Chemical, model, estimate) -> nAIC_nonrest
+
+full_nAIC <- bind_rows(nAIC_nonConst, nAIC_rest) %>%
+  bind_rows(nAIC_nonrest)
+
+new_tkstats_full <- get_tkstats(new_pk)
+
+new_tkstats_full %>%
+  filter(Species %in% "rat", !(model %in% "model_flat")) %>%
+  distinct(Chemical, model, CLtot) %>%
+  inner_join(full_nAIC) %>%
+  na.omit() %>% 
+  distinct(Chemical, estimate, CLtot) %>%
+  pivot_wider(names_from = estimate,
+              values_from = CLtot) %>%
+  rowwise() %>%
+  mutate(CLtot.httk_rest = calc_total_clearance(dtxsid = Chemical,
+                                           restrictive.clearance = TRUE),
+         CLtot.httk_nonrest = calc_total_clearance(dtxsid = Chemical,
+                                           restrictive.clearance = FALSE)) %>%
+  ungroup() %>%
+  mutate(A_rest = log(nonConst) - log(CLtot.httk_rest),
+         A_nonrest = log(nonConst) - log(CLtot.httk_nonrest),
+         B_rest = log(Rest) - log(CLtot.httk_rest),
+         B_nonrest = log(Rest) - log(CLtot.httk_nonrest),
+         C_rest = log(nonRest) - log(CLtot.httk_rest),
+         C_nonrest = log(nonRest) - log(CLtot.httk_nonrest)) %>%
+  select(Chemical, A_rest:C_nonrest) -> df_valcomp
+
+df_valcomp %>% 
+  column_to_rownames(var = "Chemical") %>%
+  t() %>%
+  as.matrix() %>%
+  cor() %>%
+  round(digits = 3) -> val_cormat
+
+hclust(d = as.dist(1-abs(val_cormat)), method = "complete") %>% plot()
+
+hclust(d = as.dist(1-abs(val_cormat)), method = "complete") -> val_hclust
+
+corrplot::corrplot(abs(val_cormat))
+
+#reorder the Chemical names prior to plotting
+df_valcomp %>%
+  mutate(Chemical = factor(x = Chemical,
+                           levels = val_hclust$labels[val_hclust$order])) %>%
+  pivot_longer(cols = A_rest:C_nonrest,
+               names_to = "comparison", values_to = "logres") %>%
+  mutate(comparison = case_when(
+    comparison == "A_nonrest" ~ "free kelim vs httk nonrestrictive",
+    comparison == "A_rest" ~ "free kelim vs httk restrictive",
+    comparison == "B_nonrest" ~ "restrictive kelim vs httk nonrestrictive",
+    comparison == "B_rest" ~ "restrictive kelim vs httk restrictive",
+    comparison == "C_nonrest" ~ "nonrestrictive kelim vs httk nonrestrictive",
+    comparison == "C_rest" ~ "nonrestrictive kelim vs httk restrictive",
+  ),
+  comparison = factor(comparison,
+  levels = c("free kelim vs httk nonrestrictive",
+             "free kelim vs httk restrictive",
+             "restrictive kelim vs httk nonrestrictive",
+             "restrictive kelim vs httk restrictive",
+             "nonrestrictive kelim vs httk nonrestrictive",
+             "nonrestrictive kelim vs httk restrictive"))) %>%
+  ggplot(aes(x = comparison, y = Chemical, fill = logres)) +
+  geom_tile() +
+  scale_fill_gradient2(mid = "grey5", high = "magenta", low = "green",
+                       name = "Total Clearance\nlog-scale difference") +
+  coord_fixed(ratio = 0.3) +
+  theme_bw() +
+  theme(axis.text.x = element_text(hjust = 1, angle = 45),
+        axis.ticks.y = element_blank(),
+        panel.grid = element_blank(),
+        axis.title.x = element_blank())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_compare_heatmap_2024_0405.png"),
+       height = 14,
+       width = 8)
+
+```
+
+```{r dawson}
 # try dawson

### 2024-04-18 data-raw/RestrictiveClearance_comparison.Rmd
An early beginning to a re-parametrized restrictive vs non-restrictive one-compartment model

@@
   sort()
+```
+
+```{r dawson}
+# try dawson
+httk::load_dawson2021()
+
+common_chems_dawson <- cvt %>%
+  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk")) %>%
+  pull(analyte_dtxsid) %>%
+  unique()
+
+cvt %>%
+  subset(!(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk"))) %>%
+  dplyr::distinct(analyte_dtxsid, analyte_name_original)
+
+# Test which analyte_dtxsid don't have a clearance or vdist
+
+data.frame(Chemical = unique(cvt$analyte_dtxsid)) %>%
+  rowwise() %>%
+  mutate(needs_RestCL = ifelse(
+    (class(try(calc_total_clearance(dtxsid = Chemical,
+                     restrictive.clearance = TRUE,
+                     suppress.messages = TRUE))) == "try-error"),
+    TRUE, FALSE),
+    needs_nonRestCL = ifelse(
+      (class(try(calc_total_clearance(dtxsid = Chemical,
+                     restrictive.clearance = FALSE,
+                     suppress.messages = TRUE))) == "try-error"),
+    TRUE, FALSE),
+    needs_Vdist = ifelse(
+      (class(try(calc_vdist(dtxsid = Chemical,
+                     suppress.messages = TRUE))) == "try-error"),
+    TRUE, FALSE)) %>%
+  ungroup() -> has_all_needed_df
+
+has_all_needed_df %>%
+  filter(!(needs_RestCL | needs_nonRestCL | needs_Vdist)) %>%
+  pull(Chemical) %>% unique() -> common_chems_dawson
+
 ```
@@
 ```{r running-invivoPKfit}
+# This is now updated to use dawson chem table
 minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% common_chems),
+                   filter(analyte_dtxsid %in% common_chems_dawson),
                  mapping = ggplot2::aes(
@@
 
-new_pk <- do_fit(new_pk) # For troubleshooting
+new_pk <- do_fit(new_pk) # For troubleshooting only
 
-new_pk <- do_fit(new_pk, n_cores = 10) 
+new_pk <- do_fit(new_pk, n_cores = 12)
+
 # Multidplyr error because of forgotten browser() call within log_likelihood
 new_pk$fit %>% unnest(fit) %>% View()
+
+saveRDS(new_pk, "data-raw/someCVT_wHTTK_JOINT.rds")
 
@@
 
-```{r}
+```{r new_analysis}
+# Loading the new data
+new_pk <- readRDS("data-raw/someCVT_wHTTK_JOINT.rds")
 
@@
 new_rsq <- rsq(new_pk)
+new_rmse <- rmse(new_pk, use_scale_conc = FALSE)
 
@@
 
-residuals(new_pk) %>% View()
+new_resid <- residuals(new_pk)
 
-pl <- plot(new_pk, n_interp = 12, use_scale_conc = TRUE, best_fit = TRUE)
+my_data <- get_data(new_pk) %>%
+  distinct(Chemical, Species, Reference, Route, Media, Dose, Time, Conc) %>%
+  right_join(new_resid)
+
+pl <- plot(new_pk, n_interp = 12, use_scale_conc = FALSE)
 pdf(file = paste0(Sys.getenv("FIG_DIR"),
-              "BestFits_Final_2024_0405.pdf"),
+              "AllFits_noScaleConc_newPK_2024_0412.pdf"),
     height = 6, width = 10)
@@
 new_cltot2 <- new_tkstats %>% 
-  # filter(str_detect(model, "rest")) %>%
+  filter(str_detect(model, "rest")) %>%
   select(Chemical, Species, Media, Route, 
@@
   geom_point(aes(y = CLtot.httk_nonrest),shape = 19, size = 2, color = "orange2") +
-  geom_point(aes(y = CLtot.tkstats), shape = 1, size = 3, color = "black", stroke = 1) +
+  geom_point(aes(y = CLtot.tkstats, shape = Species), size = 3, color = "black", stroke = 1) +
   scale_y_log10(labels = scales::label_math(format = log10)) +
   geom_hline(yintercept = c(0.01, 0.1, 1, 10)) +
+  scale_shape_manual(values = c(0,1,2,5,6)) +
   coord_flip() +
@@
              scales = "free", space = "free") +
-  labs(title = "Total Clearance for constant kelim \"best fits\" (empty)\nand httk calculations (filled)") +
+  labs(title = "CLtot for constant kelim \"best fits\" (empty)\nand httk calculations (filled)") +
   theme_bw() +
@@
         plot.title = element_text(hjust = 0.5),
-        plot.background = element_rect(fill = "white"))
+        plot.background = element_rect(fill = "white"),
+        strip.text.y = element_text(angle = 0),
+        strip.background = element_blank(),
+        legend.position = "none")
 
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_backcompare_2024_0405.png"),
-       height = 4,
-       width = 6)
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_backcompare_wDawson_2024_0416.png"),
+       height = 8,
+       width = 9)
 
@@
   cor() %>%
-  round(digits = 3) -> val_cormat
+  signif() -> val_cormat
 
-hclust(d = as.dist(1-abs(val_cormat)), method = "complete") %>% plot()
+hclust(d = as.dist((1+val_cormat)/2), method = "average") %>% plot()
 
-hclust(d = as.dist(1-abs(val_cormat)), method = "complete") -> val_hclust
+hclust(d = as.dist((1+val_cormat)/2), method = "average") -> val_hclust
 
@@
   comparison = factor(comparison,
-  levels = c("free kelim vs httk nonrestrictive",
-             "free kelim vs httk restrictive",
-             "restrictive kelim vs httk nonrestrictive",
+  levels = c("free kelim vs httk restrictive",
+             "free kelim vs httk nonrestrictive",
              "restrictive kelim vs httk restrictive",
              "nonrestrictive kelim vs httk nonrestrictive",
-             "nonrestrictive kelim vs httk restrictive"))) %>%
+             "nonrestrictive kelim vs httk restrictive",
+             "restrictive kelim vs httk nonrestrictive"))) %>%
   ggplot(aes(x = comparison, y = Chemical, fill = logres)) +
   geom_tile() +
-  scale_fill_gradient2(mid = "grey5", high = "magenta", low = "green",
-                       name = "Total Clearance\nlog-scale difference") +
+  scale_fill_gradient2(mid = "grey5", high = "orange", low = "green3",
+                       name = "Total Clearance\nlog10-scale difference",
+                       limits = c(-4, 4),
+                       oob = scales::oob_squish) +
   coord_fixed(ratio = 0.3) +
@@
 
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_compare_heatmap_2024_0405.png"),
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_compare_heatmap_2024_0409.png"),
        height = 14,
@@
 
-```{r dawson}
-# try dawson
-httk::load_dawson2021()
+# Winning models - An aside
+
+I am a little worried that I am not selecting the best fit model for each
+chemical all the time. Ultimately, the consequences for this being having parameters
+for chemicals with rather poor fits in general, when there is a better fitting
+model available. Here I want to do a quick analysis of the chemical
+*DTXSID3022405* in mouse. The one compartment fits best in the original data
+(by visual inspection) but the 2-compartment wins out in minimizing AIC.
+
+For each model, I can find how many distinct experimental timepoints have the minimum
+RMSE then investigate whether the model with the most _minimum RMSE_ timepoint
+corresponds to the winning model by AIC.
+
+*Update*: About half do not correspond. However, the lack of correspondance doesn't
+mean there is bad fits declared winning model. To address this I need to understand 
+_how_ different the AIC-based winning model and the RMSE-based winning models
+are and whether the data leaves something to be desired.
+This may be as simple as a Pearson correlation between residual values.
+The output of this analysis is how related both
+
+Another thing I am noticing in oral data: the constant _kelim_ fits sometimes are very similar
+to their respective non-constant _kelim_ fits and they actually intersect/cross over.
+I wonder if there is something special about the timepoints at which they intersect.
+For example, a restrictive fit will reach a slightly higher Cmax, but then
+dive below the fully optimized fit during elimination phase before crossing over
+again near the second inflection point.
+
+```{r oxybenzene-test}
+old_AIC <- AIC(my_pk) %>%
+  filter(Chemical %in% "DTXSID3022405",
+         Species %in% "mouse")
+
+new_AIC <- new_AIC %>%
+  filter(Chemical %in% "DTXSID3022405",
+         Species %in% "mouse")
+
+plot(new_pk, model = c("model_2comp",
+                       "model_1comp", "model_1comp_nonrest"),
+     use_scale_conc = FALSE) %>%
+  filter(Chemical %in% "DTXSID3022405",
+         Species %in% "mouse") %>%
+  pull(final_plot) %>% .[[1]]
+
+old_rsquared <- rmse(my_pk) %>%
+  filter(Chemical %in% "DTXSID3022405",
+         Species %in% "mouse")
+
+# Only test residual correlations with those not the same
+
+winmodel_conflict <- rmse(new_pk, use_scale_conc = FALSE) %>%
+  group_by(Chemical, Species, Route, Media, Dose, Time) %>%
+  filter(RMSE == min(RMSE)) %>%
+  group_by(Chemical, Species) %>%
+  count(model) %>%
+  filter(n == max(n)) %>%
+  inner_join(new_wm %>% rename("winmodel" = "model")) %>%
+  filter(!(model == winmodel))
+
+# need to map2 then have `residuals.pk(model = .x)` and .y
+# then correlate these values for each data group
+winmodel_conflict %>% names()
+
+mod_red <- winmodel_conflict %>%
+  dplyr::select(Chemical, Species, model) %>%
+  left_join(new_resid,
+            by = join_by(Chemical, Species, model)) %>%
+  rename("mod_residuals" = "Residuals") %>%
+  select(Chemical, Species, Route, Media, Time, Detect, exclude,
+         model, mod_residuals)
+
+wm_red <- winmodel_conflict %>%
+  dplyr::select(Chemical, Species, winmodel) %>%
+  left_join(new_resid,
+            by = join_by(Chemical, Species, "winmodel" == "model")) %>%
+  rename("wm_residuals" = "Residuals") %>%
+  select(Chemical, Species, Route, Media, Time, Detect, exclude,
+         winmodel, wm_residuals)
+sum_red <- new_resid %>%
+  group_by(Chemical, Species, model) %>%
+  summarize(MSE = sum(Residuals^2)/n())
+
+cor_mod <- mod_red %>% inner_join(wm_red) %>%
+  select(Chemical, Species, model, mod_residuals, winmodel, wm_residuals) %>%
+  group_by(Chemical, Species, model, winmodel) %>%
+  summarize(cor_mods = cor(x = mod_residuals, y = wm_residuals)) %>%
+  left_join(sum_red, by = join_by(Chemical, Species, model)) %>%
+  rename("mod_MSE" = "MSE") %>%
+  left_join(sum_red, by = join_by(Chemical, Species, "winmodel" == "model")) %>%
+  rename("wm_MSE" = "MSE")
+
+my_pl_1comp <- plot(new_pk, n_interp = 11, use_scale_conc = FALSE,
+                    model = c("model_1comp",
+                              "model_1comp_rest",
+                              "model_1comp_nonrest"))
+
+my_pl_2comp <- plot(new_pk, n_interp = 11, use_scale_conc = FALSE,
+                    model = c("model_2comp",
+                              "model_2comp_rest",
+                              "model_2comp_nonrest"))
+
+# General trends about residual correlation and MSE
+cor_mod %>%
+  mutate(cor_bin = ifelse(abs(cor_mods) >= 0.60,
+                          "Taking win_model",
+                          "Taking low RMSE model")) %>% na.omit() %>%
+  ggplot() +
+  geom_point(aes(x = mod_MSE, y = wm_MSE)) +
+  scale_x_log10() +
+  scale_y_log10() +
+  geom_abline(slope = 1, intercept = 0, linetype = "dotted") +
+  facet_grid(rows = vars(cor_bin))
+
+cor_mod %>%
+  filter(!(model %in% "model_flat")) %>%
+  mutate(cor_bin = ifelse(abs(cor_mods) >= 0.60,
+                          "Taking win_model",
+                          "Taking low RMSE model")) %>% na.omit() %>%
+  ggplot() +
+  geom_histogram(aes(x = cor_mods, fill = model),
+                 binwidth = 0.05) +
+  facet_grid(rows = vars(winmodel)) +
+  scale_fill_viridis_d() +
+  theme_bw() +
+  theme(strip.text.y = element_text(angle = 0)) +
+  labs(x = "Correlation of Residuals",
+       fill = "model by grouped RMSE")
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "winModel_correlations_changes",
+                         "_2024_Apr_16.png"),
+       height = 6,
+       width = 8)
+
+# Try oxybenzone fitting without dose-norm
+minimal_pk <- pk(data = cvt %>%
+                   filter(analyte_dtxsid %in% "DTXSID3022405"),
+                 mapping = ggplot2::aes(
+                   Chemical = analyte_dtxsid,
+                   Chemical_Name = analyte_name_original,
+                   DTXSID = analyte_dtxsid,
+                   CASRN = analyte_casrn,
+                   Species = species,
+                   Reference = document_id,
+                   Media = conc_medium_normalized,
+                   Route = administration_route_normalized,
+                   Dose = dose_level_normalized,
+                   Dose.Units = "mg/kg",
+                   Subject_ID = subject_id,
+                   Series_ID = series_id,
+                   Study_ID = study_id,
+                   ConcTime_ID = conc_time_id,
+                   N_Subjects = n_subjects_in_series,
+                   Weight = weight_kg,
+                   Weight.Units = "kg",
+                   Time = time_hr,
+                   Time.Units = "hours",
+                   Value = conc,
+                   Value.Units = "mg/L",
+                   Value_SD = conc_sd_normalized,
+                   LOQ = loq
+                 ))
+new_pk <- minimal_pk +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = FALSE) +
+  settings_optimx(method = c("L-BFGS-B")) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
+  stat_model(model = c("model_flat", "model_1comp", "model_2comp",
+                       "model_1comp_rest", "model_1comp_nonrest",
+                       "model_2comp_rest", "model_2comp_nonrest"))
+
+new_pk <- do_fit(new_pk, n_cores = 3) 
+get_winning_model(new_pk)
+plot(new_pk, best_fit = TRUE) %>% pull(final_plot)
+```
+
+# Categorizing chemicals
+
+I first need to find the winning model for constant kelims and optimized kelims
+
+```{r categorization}
+
+grouped_wm <- new_AIC %>%
+  mutate(model_type = case_when(
+    str_detect(model, "_nonrest$") ~ "Nonrestrictive",
+    str_detect(model, "_rest$") ~ "Restrictive",
+    .default = "Free_kelim"
+  )) %>%
+  group_by(Chemical, Species, model_type) %>%
+  filter(AIC == min(AIC)) %>% 
+  ungroup() %>%
+  arrange(Chemical, Species, model_type) %>%
+  select(Chemical, Species, model, method, model_type)
+
+grouped_tkstats <- get_tkstats(new_pk) %>%
+  inner_join(grouped_wm)
+
+grouped_tkstats %>%
+  select(Chemical, Species, Reference,
+         Route, Media, model_type,
+         CLtot) %>%
+  pivot_wider(names_from = model_type, values_from = CLtot) %>%
+  mutate(low_invivo_CL = ifelse(
+    Free_kelim < Nonrestrictive/2 | Free_kelim < Restrictive/2,
+    TRUE, FALSE),
+    high_extra_hepCL = ifelse(
+      Free_kelim > 1.5*Nonrestrictive | Free_kelim > 1.5*Restrictive,
+      TRUE, FALSE),
+    rest_metabol = ifelse(
+      Free_kelim > Restrictive/2 & Free_kelim < 1.5*Nonrestrictive,
+      TRUE, FALSE),
+    combo_cat = paste0(low_invivo_CL + 0,
+                       high_extra_hepCL + 0,
+                       rest_metabol + 0)) %>%
+  count(combo_cat)
+  arrange(Chemical, combo_cat) %>%
+  na.omit() %>%
+  View()
 
 ```
+
+```{r}
+my_tkstats <- eval_tkstats(my_pk, finite_only = FALSE)
+
+my_tkstats %>% filter(Species %in% "rat",
+                      Route %in% "oral") %>%
+  distinct(Chemical, Species, Route, Media, model, Fgutabs.tkstats) %>%
+  filter(Fgutabs.tkstats > 0) %>%
+  left_join(distinct(cas_convert)) %>% 
+  arrange(Chemical) %>% clipr::write_clip()
+
+pesticides <- read_csv("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Chemical List EPAPCS-2024-04-17.csv") %>%
+  pull(DTXSID) %>% str_extract("DTXSID\\d+")
+
+unique(my_tkstats$Chemical)[unique(my_tkstats$Chemical) %in% pesticides]
+
+```

### 2024-04-18 R/get_params_1comp_cl.R

@@ -1,0 +1,315 @@
+#' Get parameters for 1-compartment model with clearance assumption
+#'
+#' Get parameters for 1-compartment model and determine whether each is to be
+#'estimated from the data
+#'
+#'The full set of model parameters for the 1-compartment model includes `Vdist`,
+#'`Clint`, `kgutabs`, `Fgutabs`, `Q_totli`, `Q_gfr`, `Fup`, and `Rblood2plasma`.
+#'Whether each one can be estimated from the data depends on which routes of administration
+#'are included in the data.
+#'
+#'# Constant parameters from `httk`
+#'`Q_totli` is the flow through the portal vein from the gut to the liver
+#'and is estimated in this model via [httk::tissue.data] in a species-specific manner.
+#'`Q_gfr` is the glomular filtration rate of kidneys. It is estimated via
+#'[httk::physiology.data] in a species specific manner.
+#'`Fup` and `Rblood2plasma` are both calculated in [httk::parameterize_1comp()]
+#' For each of these parameters default lower bounds are 10% and 110% of the starting value
+#'
+#'# IV data, no oral data
+#'
+#'If IV dosing data are available, but no oral dosing data are available, then
+#'only the parameters `Vdist` and `kelim` will be estimated from the data. The
+#'parameters `kgutabs` and `Fgutabs` cannot be estimated from IV data alone, and
+#'will not be used in evaluating the model.
+#'
+#'# Oral data, no IV data
+#'
+#'If oral dosing data are available, but no IV dosing data are available, then
+#'the parameters `kelim` and `kgutabs` can be estimated from the data. However,
+#'the parameters `Fgutabs` and `Vdist` cannot be identified separately. From
+#'oral data alone, only the ratio `Fgutabs/Vdist` can be identified. This ratio
+#'is represented by a single parameter named `Fgutabs_Vdist`. `Fgutabs` and
+#'`Vdist` will not be used to evaluate the model nor be estimated from data, but
+#'`Fgutabs_Vdist` will be estimated from data, along with `kelim` and `kgutabs`.
+#'
+#'# Oral data and IV data
+#'
+#'If both oral and IV dosing data are available, then `Vdist`, `kelim`,
+#'`kgutabs`, and `Fgutabs` will all be estimated from the data.
+#'
+#'# Blood and plasma data
+#'
+#'If both blood and plasma data are available, then `Rblood2plasma` will be
+#'estimated from the data.
+#'
[…]

### 2024-04-24 data-raw/RestrictiveClearance_comparison.Rmd
Complete re-parameterized 1-compartment models for restrictive and non-restrictive assumptions which use httk-derived values to calculate hepatic clearance and parameter starts

@@
   settings_optimx(method = c("L-BFGS-B")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
   stat_error_model(error_group = vars(Chemical, Species, Reference)) +
-  stat_model(model = c("model_flat", "model_1comp", "model_2comp",
-                       "model_1comp_rest", "model_1comp_nonrest",
-                       "model_2comp_rest", "model_2comp_nonrest"))
+  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
 new_pk <- do_data_info(new_pk)
@@
 
-new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "kelim") %>%
+new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Clint") %>%
   View()
@@
 pl2comp <- plot(new_pk, use_scale_conc = FALSE,
-           model = "model_2comp_nonrest",
+           # model = "model_2comp_nonrest",
            n_interp = 10)
@@
 pl2comp %>%
-  filter(Chemical %in% "DTXSID0021383") %>% pull(final_plot) %>% .[[1]]
+  filter(Chemical %in% "DTXSID1043881") %>% pull(final_plot) %>% .[[1]]
 ```
@@
 pdf(file = paste0(Sys.getenv("FIG_DIR"),
-              "AllFits_noScaleConc_newPK_2024_0412.pdf"),
+              "AllFits_nonDoseNorm_newPK_reParametizedModels_2024_0412.pdf"),
     height = 6, width = 10)
@@
 ```
+
+## New reformulated models that estimate Clint!
+
+```{r reformMod}
+new_pk$fit %>% unnest(fit) %>%
+  mutate(Clint = ifelse(model == "model_1comp", kelim/Vdist, Clint)) %>%
+  select(Chemical, Species, model, Clint) %>%
+  pivot_wider(names_from = model, values_from = Clint) %>%
+  left_join(new_pk$prefit$par_DF %>%
+              filter(param_name == "Clint") %>%
+              select(Chemical, Species, model, start) %>%
+              mutate(model = paste0("start_", model)) %>%
+              pivot_wider(names_from = model,
+                          values_from = start)) %>% View()
+
+get_tkstats(new_pk)
+
+```

### 2024-05-15 data-raw/RestrictiveClearance_comparison.Rmd
Changes to cvt object to include Showa, and new selection of fitting options has been done.

@@
   settings_optimx(method = c("L-BFGS-B")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
   stat_error_model(error_group = vars(Chemical, Species, Reference)) +
@@
 # Multidplyr error because of forgotten browser() call within log_likelihood
-new_pk$fit %>% unnest(fit) %>% View()
+new_pk$fit %>% unnest(fit) %>% select(!starts_with("sigma_")) %>% View()
 
-saveRDS(new_pk, "data-raw/someCVT_wHTTK_JOINT.rds")
+saveRDS(new_pk, "data-raw/someCVT_wHTTK_reform_JOINT.rds")
 
@@
 pl2comp <- plot(new_pk, use_scale_conc = FALSE,
-           # model = "model_2comp_nonrest",
            n_interp = 10)
@@
   filter(param_name %in% "kelim",
-         Chemical %in% common_chems) %>%
+         Chemical %in% common_chems_dawson) %>%
   distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)
@@
   rename(fit_kelim = "kelim") %>%
-  filter(Chemical %in% common_chems)
+  filter(Chemical %in% common_chems_dawson)
 
@@
 
-httk_df <- rest_pk$prefit$par_DF %>%
+httk_df <- new_pk$prefit$par_DF %>%
   filter(param_name %in% "kelim") %>%
@@
 
-```{r}
-my_tkstats <- eval_tkstats(my_pk, finite_only = FALSE)
-
-my_tkstats %>% filter(Species %in% "rat",
-                      Route %in% "oral") %>%
-  distinct(Chemical, Species, Route, Media, model, Fgutabs.tkstats) %>%
-  filter(Fgutabs.tkstats > 0) %>%
-  left_join(distinct(cas_convert)) %>% 
-  arrange(Chemical) %>% clipr::write_clip()
-
-pesticides <- read_csv("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Chemical List EPAPCS-2024-04-17.csv") %>%
-  pull(DTXSID) %>% str_extract("DTXSID\\d+")
-
-unique(my_tkstats$Chemical)[unique(my_tkstats$Chemical) %in% pesticides]
-
-```
-
 ## New reformulated models that estimate Clint!
@@
 ```{r reformMod}
-new_pk$fit %>% unnest(fit) %>%
-  mutate(Clint = ifelse(model == "model_1comp", kelim/Vdist, Clint)) %>%
-  select(Chemical, Species, model, Clint) %>%
-  pivot_wider(names_from = model, values_from = Clint) %>%
+get_tkstats(new_pk) %>% 
+  distinct(Chemical, Species, model, CLtot) %>%
+  pivot_wider(names_from = model, values_from = CLtot) %>%
   left_join(new_pk$prefit$par_DF %>%
-              filter(param_name == "Clint") %>%
+              filter(param_name == "CLtot") %>%
               select(Chemical, Species, model, start) %>%
@@
               pivot_wider(names_from = model,
-                          values_from = start)) %>% View()
+                          values_from = start)) %>% View("Clearance")
 
-get_tkstats(new_pk)
+new_cl_tkstats <- get_tkstats(new_pk)
+my_tkstats <- my_pk %>%
+  get_winning_model() %>%
+  left_join(coef(my_pk)) %>%
+  left_join(rsq(my_pk)) %>% distinct()
+my_tkstats %>% select(-coefs_vector) %>% clipr::write_clip()
+#Send the R2 too.
 
+## Need to parameterize with gas_pbpk or new 3compartment
+## To add into total clearance 
+# Rb2p * Qalv/Kblood2air
 ```

### 2024-05-15 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Changes to cvt object to include Showa, and new selection of fitting options has been done.

@@
   "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
-  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
-  "b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
+  "b.conc_medium_normalized, b.conc_medium_original, b.time_units_original, b.conc_units_original, ",
+  "b.conc_units_normalized, b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
   "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
   "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
-  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
+  "c.dose_level_normalized, c.dose_level_original, c.dose_level_units_original, ",
   "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
-  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",
+  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted, e.curation_set_tag ",
 
@@
   # Filtering steps
-  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
+  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') OR ",
+  "b.conc_medium_original IN ('blood', 'plasma') AND ",
   "c.administration_route_normalized IN ('iv', 'oral')"
@@
 
+dtxsid_query <- paste0(
+  "SELECT distinct * FROM chemicals"
+)
+
+dtxsid_query <- query_db(query = dtxsid_query,
+         schema = "cvt")
+
+dq_cols <- dtxsid_query %>%
+  dplyr::select("analyte_dtxsid2" = "dsstox_substance_id",
+         "fk_analyzed_chemical_id" = "id",
+         "analyte_name_original" = "chemical_name_original") %>%
+  distinct()
+
+glimpse(dq_cols)
+
 names(sql_query)
@@
   names(sql_query)[8] <- "series_id"
-  names(sql_query)[23] <- "study_id"
-  names(sql_query)[35] <- "subject_id"
-  names(sql_query)[42] <- "document_id"
+  names(sql_query)[25] <- "study_id"
+  names(sql_query)[37] <- "subject_id"
+  names(sql_query)[44] <- "document_id"
 }
 
+full_set <- sql_query %>%
+  left_join(dq_cols, 
+            by = join_by("fk_analyzed_chemical_id", "analyte_name_original")) %>%
+  mutate(analyte_dtxsid = ifelse(is.na(analyte_dtxsid), analyte_dtxsid2, analyte_dtxsid)) %>%
+  select(-analyte_dtxsid2)
+
 # Harmonize values for easier analysis
-sql_query <- sql_query %>%
+cvt_df <- full_set %>%
+  filter(administration_route_normalized %in% c("iv", "oral")) %>%
   mutate(
@@
   )
-sql_query <- sql_query %>%
-  dplyr::rename_with(~gsub(pattern = "fk_", replacement = "",
-                         .x), .cols = contains("fk_"))
 
-# Copying
-cvt_df <- sql_query # Copy so I don't have to do query again to reset any errors
-```
-
-```{r counting-replicates}
-count_query <- paste0(
-  "SELECT DISTINCT ",
-  "a.id, a.time_hr, a.conc, ",
-  "b.id, b.analyte_dtxsid, ",
-  "b.test_substance_dtxsid, b.conc_medium_normalized, ",
-  "c.id, c.administration_route_normalized, ",
-  "c.fk_extraction_document_id, c.dose_level_normalized, ",
-  "d.id, d.species ",
-
-  # Main Table
-  "FROM conc_time_values a ",
-
-  # Join with series table by series ID
-  "LEFT JOIN series b ON b.id = a.fk_series_id ",
-
-  # Join to studies table by study ID
-  "LEFT JOIN studies c ON c.id = b.fk_study_id ",
-
-  # Join to subjects table by subject ID
-  "LEFT JOIN subjects d ON d.id = b.fk_subject_id ",
-
-  # Filtering steps
-  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
-  "c.administration_route_normalized IN ('iv', 'oral')"
-)
-
-query_db(query = count_query,
-         schema = "cvt") %>%
-  select(-id) %>% 
-  filter(!is.na(analyte_dtxsid),
-         analyte_dtxsid == test_substance_dtxsid,
-         conc > 0) %>%
-  distinct() %>%
-  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, fk_extraction_document_id,
-           dose_level_normalized) %>%
-  count() %>%
-  pull(n) %>% table()
+cvt_df <- cvt_df %>%
+  mutate(conc_medium_normalized = ifelse(is.na(conc_medium_normalized),
+                                         conc_medium_original,
+                                         conc_medium_normalized))
 ```
@@
 ```{r data_validation}
-# Check other_study_identifier == S0916 so that it has dose_level_original_units == ug/mL
+# Check other_study_identifier == S0916 so that it has dose_level_units_original == ug/mL
 cvt_df %>% filter(other_study_identifier == "S0916") %>%
-  pull(dose_level_original_units) %>% unique()
+  pull(dose_level_units_original) %>% unique()
 # There are still columns that are mg/kg... changing these to ug/mL
 cvt_df <- cvt_df %>% mutate(
-  dose_level_original_units = ifelse(
+  dose_level_units_original = ifelse(
     other_study_identifier == "S0916",
     "ug/mL",
-    dose_level_original_units
+    dose_level_units_original
   )
 )
+cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
 
@@
     dose_level_corrected_units = "mg/kg",
-    .after = dose_level_original_units)
+    .after = dose_level_units_original)
 
@@
       dose_level_normalized),
-    .after = dose_level_original_units)
+    .after = dose_level_units_original)
+
+cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
 
@@
       analyte_name_original %in% "Caffeine" ~ 4.00,
-      analyte_name_original %in% "L-Ephedrine" ~ 4.44,
+      analyte_name_original %in% "L-Ephedrine" ~ 3.39,
       analyte_name_original %in% "Pseudoephedrine" ~ 4.43
@@
       loq_units
-    ))
+    ),
+    conc_units_original = ifelse(other_study_identifier %in% "S0976", "mg/L", conc_units_original))
 
@@
   ))
-
+cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
 # PMID 6310077 is a tritium tracing of B[a]P and these were given as % of Dose
@@
 cvt_df <- cvt_df %>%
+  mutate(conc = as.numeric(conc),
+         conc_original = as.numeric(conc)) %>%
   mutate(conc = ifelse(document_id %in% 38,
@@
   filter(dose_frequency %in% c("1", NA))
+cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
 
+cvt_df$loq_units %>% unique()
 # Normalize LOQ units
@@
   mutate(loq = ifelse(
-    loq_units %in% c("ug/L", "ng/mL"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
+    loq_units %in% c("ug/L", "ng/mL", "ng/g"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
 # Normalize conc_sd and conc units manually
 cvt_df <- cvt_df %>%
+  mutate(conc_sd_original = as.numeric(conc_sd_original)) %>%
   mutate(conc_sd_normalized = case_when(
-    conc_units_original %in% c("ug/L", "ng/mL", "ng-Eq/mL", "ng/g tissue") ~ conc_sd_original*1E-3,
+    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml", "ng/g", "ng/g tissue", "ug/L") ~ conc_sd_original*1E-3,
     conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
@@
   mutate(conc = case_when(
-    conc_units_original %in% c("ng-eq/mL") ~ conc_original*1E-3,
+    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
+                               "ng/g", "ng/g tissue", "ug/L") ~ conc_original*1E-3,
+    conc_units_original %in% c("g/dL") ~ conc_original*1E-4,
+    conc_units_original %in% c("pg/mL") ~ conc_original*1E-6,
     .default = conc
   ))
-
+cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
+# Some chemicals have very few values
 cvt_df <- cvt_df %>%
@@
                                       "DTXSID10169854",
-                                      "DTXSID2021103") )) # These only have 1 or 2 values
-
+                                      "DTXSID2021103",
+                                      "DTXSID6038299") ),
+                administration_route_normalized %in% c("iv", "oral"))
+cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
 # More notes:
 # DTXSID6020438 & DTXSID0020868 rat is from water (top) and oil (bottom curve) gavage
+cvt_df %>% count(curation_set_tag)
 
@@
   filter(!is.na(analyte_dtxsid),
-         analyte_dtxsid == test_substance_dtxsid,
+         fk_analyzed_chemical_id == fk_dosed_chemical_id, # sometimes test chemical id is not filled out :/
          !(document_id %in% c(38, 65, 110, 112, 46, 31)),
          !(other_study_identifier %in% c("S0916")),
-         !(analyte_name_original %in% "Methemoglobin"),
-         is.na(radiolabeled))
+         !(analyte_name_original %in% "methemoglobin"),
+         radiolabeled %in% c(NA, FALSE) # Legacy left as NA, other curations explicitly state FALSE
+         )
+cvt_df %>% distinct(analyte_dtxsid, curation_set_tag) %>% count(curation_set_tag)
+cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()
 
 cvt_df %>%
-  filter(conc > 0) %>%
-  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, document_id,
-           dose_level_normalized) %>%
-  distinct() %>%
-  count() %>% 
-  ungroup() %>%
-  filter(n >= 10) %>% 
-  distinct(analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, document_id,
-           dose_level_normalized) %>%
-  arrange(analyte_dtxsid, species, document_id) %>%
-  left_join(cvt_df) %>% 
-  View()
+  pull(conc_units_original) %>%
+  table()
+cvt_df %>%
+  filter(conc_units_original %in% "molar percentage") %>% View()
 
-cvt_df %>%
-  filter(conc > 0) %>%
-  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, document_id,
-           dose_level_normalized) %>%
-  distinct() %>%
-  count() %>%
-  ungroup() %>%
-  count(n)
+cvt_df <- cvt_df %>%
+  filter(!is.na(conc)) %>%
+  mutate(conc = case_when(
+    conc_units_original %in% "umol/kg" ~ conc * dose_level_corrected,
+    # Some concentration values are in uM
+    document_id %in% 62 ~ conc * 179.219/1E3,
+    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc * 88.15/1E3,
+    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc * 102.177/1E3,
+    .default = conc
+  )) %>%
+    mutate(conc_sd_normalized = case_when(
+    conc_units_original %in% "umol/kg" ~ conc_sd_original * dose_level_corrected,
+    # Some concentration values are in uM
+    document_id %in% 62 ~ conc_sd_original * 179.219/1E3,
+    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc_sd_original * 88.15/1E3,
+    document_id %in% 51 & analyte_dtxsid %in% "DTXSID3020833" ~ conc_sd_original * 102.177/1E3,
+    .default = conc_sd_original
+  ))
+cvt_df %>% distinct(analyte_dtxsid, curation_set_tag) %>% count(curation_set_tag)
 ```

### 2024-08-01 data-raw/pulling_oral_iv_data_cvtdb.Rmd

@@
          !(document_id %in% c(38, 65, 110, 112, 46, 31)),
-         !(other_study_identifier %in% c("S0916")),
+         !(other_study_identifier %in% c("S0916") & is.na(conc)),
          !(analyte_name_original %in% "methemoglobin"),
@@
 cvt_df %>%
-  filter(conc_units_original %in% "molar percentage") %>% View()
+  filter(conc_units_original %in% "molar percentage") %>%
 
@@
 
-This filtered and transformed dataset has 14,486 observations.
+This filtered and transformed dataset has 14,152 observations.
 

### 2024-08-16 data-raw/RestrictiveClearance_comparison.Rmd
Added new method twofold_test, updated manuscript vignette and a few methods. Notably, rsq

@@
 # Test which analyte_dtxsid don't have a clearance or vdist
-
 data.frame(Chemical = unique(cvt$analyte_dtxsid)) %>%
@@
   facet_grid(rows = vars(Species), scales = "free", space = "free") +
+  labs(x = "Total Clearance") +
   theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
@@
   settings_optimx(method = c("L-BFGS-B")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
   stat_error_model(error_group = vars(Chemical, Species, Reference)) +
@@
 
+new_pk <- new_pk + settings_optimx(method = c("bobyqa"))
 new_pk <- do_prefit(new_pk)
 
-new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Clint") %>%
+unique(new_pk$prefit$par_DF$param_name)
+new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Fup") %>%
   View()
-
-new_pk <- do_fit(new_pk) # For troubleshooting only
 
@@
 
-# Multidplyr error because of forgotten browser() call within log_likelihood
 new_pk$fit %>% unnest(fit) %>% select(!starts_with("sigma_")) %>% View()

### 2024-08-16 R/pk_methods_do_data_info.R

@@ -65,10 +65,11 @@ do_data_info.pk <- function(obj, ...){
     message("do_data_info.pk(): Doing dose-normalized non-compartmental analysis\n")
   }
   nca_dose_norm_long <- nca(obj = obj,
-                       newdata = NULL,
-                       nca_group = summary_group,
-                       exclude = TRUE,
-                       dose_norm = TRUE)
+                            newdata = NULL,
+                            nca_group = summary_group,
+                            exclude = TRUE,
+                            dose_norm = TRUE,
+                            n_cores = n_cores)
   #pivot wider
   #first get names of grouping vars
   grp_vars <- sapply(summary_group,

### 2024-08-16 R/pk_methods_rsq.R

@@ -121,6 +121,10 @@
 #'   R-squared is computed. If `use_scale_conc = list(dose_norm = ...,
 #'   log10_trans = ...)`, then the specified dose normalization and/or
 #'   log10-transformation will be applied.
+#' @param rsq_group Default: Chemical, Species. Determines what the data
+#' grouping that is used to calculate R-squared value. Should be set to lowest number
+#' of variables that still would return unique experimental conditions.
+#' Input in the form of `ggplot2::vars(Chemical, Species, Route, Media, Dose)`.
 #' @param ... Additional arguments. Not currently in use.
 #' @return  A dataframe with one row for each `data_group`, `model` and `method`.
 #'   The final column contains the R-squared of the model fitted by the corresponding
@@ -135,6 +139,7 @@ rsq.pk <- function(obj,
                    method = NULL,
                    exclude = TRUE,
                    use_scale_conc = TRUE,
+                   rsq_group = ggplot2::vars(Chemical, Species),
                    ...){
   #ensure that the model has been fitted
   check <- check_required_status(obj = obj,
@@ -172,6 +177,12 @@ rsq.pk <- function(obj,
           "Dose-normalization ", conc_scale$dose_norm, "\n",
           "log-transformation ", conc_scale$log10_trans)
 
+  if (is.null(rsq_group)) {
+    rsq_group <- obj$data_group
+  }
+  rsq_group_char <- sapply(rsq_group, rlang::as_label)
+
+
   #Get predictions
   preds <- predict(obj,
                    newdata = newdata,
@@ -190,7 +201,7 @@ rsq.pk <- function(obj,
     }
   }
 
-  req_vars <- c(names(preds),
+  req_vars <- c(union(names(preds),rsq_group_char),
                 "Conc",
                 "Conc_SD",
                 "N_Subjects",
@@ -216,7 +227,7 @@ rsq.pk <- function(obj,
                            Conc_SD / Dose,
                            Conc_SD)) %>%
     dplyr::ungroup() %>%
-    dplyr::group_by(!!!obj$data_group,
+    dplyr::group_by(!!!rsq_group,
                     model, method) %>%
     dplyr::summarize(
       Rsq = calc_rsq(obs = Conc_set,
@@ -229,7 +240,7 @@ rsq.pk <- function(obj,
     dplyr::ungroup()
 
   message("Groups: \n",
-          paste(sapply(unlist(obj$data_group), rlang::as_label),
[…]

### 2024-08-30 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Update: data-raw/pulling_oral_iv_data_cvtdb.Rmd has been made more verbose. cvt.rda and cvt_data.rda have been updated.

--- 2024-01-26 data-raw/pulling_oral_iv_data_cvtdb.Rmd
@@
 date: "2023-09-29"
-output: html_document
+output: 
+  html_document:
+    toc: true
+  pdf_document:
+    toc: true
+    toc_depth: 3
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE,
+                      comment = NA,
+                      tidy.opts = list(width.cutoff = 75),
+                      tidy = TRUE)
 ```
 
-Load necessary package
+Load necessary packages: **DBI, dplyr, tidyr**
 
@@
 
+# Connect to database
+
+This section is largely taken from a `Querying CvTdb` vignette from Taylor Wall 
+and a previous version of this vignette authored by Caroline Ring.
+
 For connection to CvTdb:
@@
 
-Set environment variables for the user name, password, host, and dbname that will be used to connect.
-In Windows 10, go to the search bar in the menu and type "environment variables." A menu item should pop up that says "Edit the system environment variables." Click it.
-A window should pop up.
-On tab "Advanced " (where you should be already), there is a button "Environment Variables" in the lower right.
-Click it.
-Under "User variables for [YOURNAME]", the top window, click the "New" button.
-Add a variable and value and click "OK".
-Repeat clicking the "New" button and adding variables.
+Set environment variables for the user name, password, host, and dbname that will be used to connect. Doing it this way allows us to not hardcode the password.
 
-Doing it this way allows me to not hardcode the password.
+The following are some helper functions for the database connection.
 
-# Connect to database
-
-This is largely taken from a `Querying CvTdb` vignette from Taylor Wall and a previous version
-of this vignette authored by Caroline Ring.
-
-The following are some helpter functions for the database connection
 ```{r query_functions}
@@
 
-The following is the new SQL query.
+```{r quick_message_funtion}
+quick_message <- function(text = character()) {
+  stopifnot(length(text) > 0)
 
-```{r SQL_queries}
+  cli::cli_par()
+  cli::cli_text(paste("{.strong [i]}  ", text[1], sep = "\t"))
+  text <- text[-1]
+
+  for (this_text in seq_along(text)) {
+    cli::cli_li(text[this_text])
+  }
+  cli::cli_end()
+
+}
+
+quick_stats <- function(.data) {
+  stopifnot(is.data.frame(.data))
+  cli::cli_h2("Statistics on the current data")
+  message(paste0("Total number of data points: ", nrow(.data)))
+  message("Unique Species and data counts:")
+  print(table(.data$species))
+  message(paste0("Number of unique studies: ", length(unique(.data$fk_study_id))))
+  message(paste0("Number of unique series: ", length(unique(.data$fk_series_id))))
+  message(paste0("Number of unique chemicals: ", length(unique(.data$analyte_dtxsid))))
+  message(paste0("Unique Dose units: ", paste(unique(.data$dose_level_units_original), collapse = ", ")))
+  message(paste0("Unique Concentration units: ", paste(unique(.data$conc_units_original), collapse = ", ")))
+  message("Data by unique route of administration:")
+  print(table(.data$administration_route_normalized))
+  message("Data by medium collected:")
+  print(table(.data$conc_medium_normalized))
+  message("Data by curation set:")
+  print(table(.data$curation_set_tag))
+}
+
+```
+
+# SQL Query
+
+The SQL query result is built by left joining onto the `conc_time_values` table.
+Additionally, because _invivoPKfit_ uses DTXSID as the standard chemical identifier,
+it is important to repair some missing values for DTXSID. To do this, I 
+make a separate query `SELECT distinct * FROM chemicals` and making the chemical
+names to lowercase and by specifically taking the columns for name (now lowercase)
+and DTXSID, I can see there are many instances of duplicated chemical entries
+(which means they have separate `chemical.id` key values in this table). I then
+"fill in" the DTXSID when they are missing and if any other instance of that
+chemical name in the table has a DTXSID. I fill in DTXSIDs in the main
+query result that I will be using using some joins with this repaired table.
+
+## Suggestions for CvTdb
+
+Repairing duplication in the chemicals table should be a priority
+that would benefit all current and future users of _CvTdb_. It would repair other
+missing identifying chemical information as well as truly have unique rows per chemical.
+Here this repair is done by making names lowercase to avoid capitalization, but there
+may be other issues arise with spaces that should be parsed prior to input into 
+the database record.
+
+The other suggestion would be to have a filled out `conc_units_normalized` column in
+the `series` table. Although it is assumed to be _mg/kg_, it would be nice to have this
+confirmed. Here `conc_units_original` is compared with the ratio of `conc` to `conc_original`
+to get a sense of whether the units for `conc` were reasonably converted to
+_mg/kg_. This seems like it could reasonably be a part of the QA process.
+
+Besides these two suggestions, there are only a couple other changes in the data that 
+are made throughout this document but these pertain to specific records rather than
+the entire database, so I think they are a little bit lower on the priority list.
+
+```{r SQL_queries, warning=FALSE}
 # Need to make this in a specified ordered
@@
   "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
-  "b.id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
+  #
+  "a.fk_series_id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
   "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
   "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
-  "b.conc_medium_normalized, b.time_units_original, b.conc_units_original, ",
-  "b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
-  "c.id, c.administration_route_normalized, c.fk_dosed_chemical_id, c.dose_volume, c.dose_vehicle, ",
+  "b.conc_medium_normalized, b.conc_medium_original, b.time_units_original, b.conc_units_original, ",
+  "b.conc_units_normalized, b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
+  #
+  "b.fk_study_id, c.administration_route_normalized, c.fk_dosed_chemical_id, ",
+  "c.dose_volume, c.dose_volume_units, c.dose_vehicle, ",
   "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
-  "c.dose_level_normalized, c.dose_level_original, c.dose_level_original_units, ",
-  "d.id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
-  "e.id, e.pmid, e.year, e.other_study_identifier, e.url, e.doi, e.extracted ",
+  "c.dose_level_normalized, c.dose_level_original, c.dose_level_units_original, ",
+  #
+  "b.fk_subject_id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
+  #
+  "c.fk_extraction_document_id, e.pmid, e.year, e.other_study_identifier, ",
+  "e.url, e.doi, e.extracted, e.curation_set_tag ",
 
@@
   # Join with series table by series ID
-  "LEFT JOIN series b ON b.id = a.fk_series_id ",
+  "LEFT JOIN series b ON a.fk_series_id = b.id ",
 
   # Join to studies table by study ID
-  "LEFT JOIN studies c ON c.id = b.fk_study_id ",
+  "LEFT JOIN studies c ON b.fk_study_id = c.id ",
 
   # Join to subjects table by subject ID
-  "LEFT JOIN subjects d ON d.id = b.fk_subject_id ",
+  "LEFT JOIN subjects d ON b.fk_subject_id = d.id ",
 
   # Join to documents table by extraction document ID
-  "LEFT JOIN documents e ON e.id = c.fk_extraction_document_id ",
+  "LEFT JOIN documents e ON c.fk_extraction_document_id = e.id ",
 
   # Filtering steps
-  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
-  "c.administration_route_normalized IN ('iv', 'oral')"
+  "WHERE c.administration_route_normalized IN ('iv', 'oral') AND ",
+  "(b.conc_medium_normalized IN ('blood', 'plasma') OR ",
+  "b.conc_medium_original IN ('blood', 'plasma'))"
 )
@@
 
-names(sql_query)
 # Need to change column names for this
@@
   names(sql_query)[1] <- "conc_time_id"
-  names(sql_query)[8] <- "series_id"
-  names(sql_query)[23] <- "study_id"
-  names(sql_query)[35] <- "subject_id"
-  names(sql_query)[42] <- "document_id"
 }
@@
 # Harmonize values for easier analysis
-sql_query <- sql_query %>%
+cvt_df <- sql_query %>%
   mutate(
+    across(ends_with("id"), as.character),
+    # Note that sometimes fk_test_chemical_id is NA
+    across(all_of(c("time_original",
+                    "time_hr",
+                    "conc_original",
+                    "conc_sd_original",
+                    "conc",
+                    "conc_sd",
+                    "dose_level_original",
+                    "dose_level_normalized",
+                    "loq")), as.numeric),
+    # conc, conc_sd_original, and conc_original have NA/NE/ND values that are coerced to NAs
+    year = as.character(year),
     species = tolower(species),
     sex = tolower(sex),
-    loq = as.numeric(loq),
-    n_subjects_in_series = as.numeric(n_subjects_in_series),
-    dose_level_normalized = as.numeric(dose_level_normalized),
-    dose_level_original = as.numeric(dose_level_original),
+    analyte_name_original = tolower(analyte_name_original),
     dose_volume_units = stringr::str_extract(dose_volume,
@@
                                 pattern = "^\\d")),
-    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE)
-  )
-sql_query <- sql_query %>%
-  dplyr::rename_with(~gsub(pattern = "fk_", replacement = "",
-                         .x), .cols = contains("fk_"))
-
-# Copying
-cvt_df <- sql_query # Copy so I don't have to do query again to reset any errors
-```
-
-```{r counting-replicates}
-count_query <- paste0(
-  "SELECT DISTINCT ",
-  "a.id, a.time_hr, a.conc, ",
-  "b.id, b.analyte_dtxsid, ",
-  "b.test_substance_dtxsid, b.conc_medium_normalized, ",
-  "c.id, c.administration_route_normalized, ",
-  "c.fk_extraction_document_id, c.dose_level_normalized, ",
-  "d.id, d.species ",
-
-  # Main Table
-  "FROM conc_time_values a ",
-
-  # Join with series table by series ID
-  "LEFT JOIN series b ON b.id = a.fk_series_id ",
-
-  # Join to studies table by study ID
-  "LEFT JOIN studies c ON c.id = b.fk_study_id ",
-
-  # Join to subjects table by subject ID
-  "LEFT JOIN subjects d ON d.id = b.fk_subject_id ",
-
-  # Filtering steps
-  "WHERE b.conc_medium_normalized IN ('blood', 'plasma') AND ",
-  "c.administration_route_normalized IN ('iv', 'oral')"
+    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE),
+    n_subjects_normalized = ifelse(n_subjects_in_series %in% "NR", NA_real_,
+      as.numeric(stringr::str_extract(n_subjects_in_series,
+                                                 pattern = "\\d+")))
   )
 
-query_db(query = count_query,
-         schema = "cvt") %>%
-  select(-id) %>% 
-  filter(!is.na(analyte_dtxsid),
-         analyte_dtxsid == test_substance_dtxsid,
-         conc > 0) %>%
-  distinct() %>%
-  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, fk_extraction_document_id,
-           dose_level_normalized) %>%
-  count() %>%
-  pull(n) %>% table()
+cvt_df <- cvt_df %>%
+  mutate(conc_medium_normalized = ifelse(is.na(conc_medium_normalized),
+                                         conc_medium_original,
+                                         conc_medium_normalized))
+
+# There are some missing DTXSIDs that we need to fix
+# cvt_df %>%
+#   distinct(analyte_dtxsid, analyte_name_original, fk_analyzed_chemical_id) %>%
+#   filter(is.na(analyte_dtxsid)) %>% nrow()
+
+dtxsid_query <- paste0(
+  "SELECT distinct * FROM chemicals"
+)
+
+dtxsid_query <- query_db(query = dtxsid_query,
+         schema = "cvt")
+
+dq_cols <- dtxsid_query %>%
+  select("analyte_dtxsid2" = "dsstox_substance_id",
+         "fk_analyzed_chemical_id" = "id",
+         "analyte_name_original" = "chemical_name_original") %>%
+  mutate(analyte_name_original =  tolower(analyte_name_original)) %>%
+  distinct()
+
+dq_cols <- dq_cols %>% distinct(analyte_dtxsid2, analyte_name_original) %>%
+  group_by(analyte_name_original) %>%
+  summarize(analyte_dtxsid2 = if_else(any(complete.cases(analyte_dtxsid2)),
+                                      first(analyte_dtxsid2[!is.na(analyte_dtxsid2)]),
+                                      NA)) %>%
+  left_join(dq_cols %>% select(-analyte_dtxsid2),
+            join_by(analyte_name_original)) %>%
+  mutate(fk_analyzed_chemical_id = as.character(fk_analyzed_chemical_id))
+
+# glimpse(dq_cols)
+
+# names(cvt_df)
+
+study_query <- query_db(query = "SELECT distinct * FROM studies",
+         schema = "cvt")
+
+# Here we join to make sure all chemical ids are represented
+full_set <- cvt_df %>%
+  left_join(dq_cols, 
+            by = join_by("fk_analyzed_chemical_id", "analyte_name_original")) %>%
+  mutate(analyte_dtxsid = coalesce(analyte_dtxsid, analyte_dtxsid2)) %>%
+  select(-analyte_dtxsid2)
+
+cvt_df <- full_set
+quick_stats(cvt_df)
+
+# For figuring out whether there was a change from the original units to reported conc
+# And only keep non-radiolabeling experiments, where analyte_dtxsid is known
+# and where analyzed chemical is equivalent to the dosed chemical
+cvt_df <- cvt_df %>% mutate(conc_unit_norm_factor = signif(conc/conc_original, 1),
+                            .after = conc_units_normalized) %>%
+  filter(!(radiolabeled %in% TRUE),
+         !is.na(analyte_dtxsid),
+         fk_analyzed_chemical_id == fk_dosed_chemical_id)
+
+quick_message(text = c("Filtering out:",
+                       "Missing {.code analyte_dtxsid}",
+                       "Radiolabeling experiments",
+                       "Data where the analyzed chemicals and dosed chemicals are different"))
 ```
@@
 
-To summarize the changes:
+There are some procedures needed to be taken to standardized some of this data
+such that dose units are all in mg/kg of bodyweight and concentration units are in
+ug/L.
 
--  Change original dose units for study _S0916_ and convert to mg/kg.  
--  Change original dose units for study _S0624_ and convert to mg/kg.  
--  Include a series of isotope tracing experiments from documents _65_, _61_, _46_, and _31_.  
--  Input the LOQ for studies _S0976_ & _S0361_.  
--  Infer the LOQ for study _S0328_ as 1, given the values near it deemed above and below LOQ.  
--  Extraction from PMID:6310077 reflects a _% of Dose_, so we converted this to mg/kg.  
--  Input DTXSIDs for chemicals that did not have them but were available via CompTox dashboard.  
--  Standardize all Doses, LOQs, Concentrations, and Concentration standard deviations.  
--  Filter out chemicals dosed multiple times throughout the experiment.  
--  Filter out chemicals with very limited information.
+## Preliminary Filtering
 
-```{r data_validation}
-# Check other_study_identifier == S0916 so that it has dose_level_original_units == ug/mL
-cvt_df %>% filter(other_study_identifier == "S0916") %>%
-  pull(dose_level_original_units) %>% unique()
-# There are still columns that are mg/kg... changing these to ug/mL
+I begin with a couple of filtering steps:
+
++ Exclude data without any concentration value  
++ Exclude data with only one observation per *study_id*
+
+```{r preliminary_filtering}
+# Dose Units: Need mg/kg... = ug/mg = ng/ug, and kg = L
+# Conc Units: Need mg/L... = ug/mL = ng/uL = pg/nL, and kg = L, g = mL
 cvt_df <- cvt_df %>% mutate(
-  dose_level_original_units = ifelse(
-    other_study_identifier == "S0916",
-    "ug/mL",
-    dose_level_original_units
+  invivPK_dose_level_units = "mg/kg",
+  invivPK_conc_units = "ug/mL",
+  invivPK_conc = NA_real_,
+  invivPK_dose_level = NA_real_
+  )
+# Set the equivalent units
+equiv_mgkg <- c("mg/kg", "ug/g", "ng/mg")
+equiv_mgL <- c("mg/L", "ug/mL", "ng/uL", "mg/kg", "mg/g", "ug/mg")
+
+cvt_df <- cvt_df %>%
+  filter(!(is.na(conc) & is.na(conc_original))) %>%
+  group_by(fk_study_id) %>%
+  filter(n() > 1) %>%
+  ungroup()
+###
+```
+
+## Specific Data Changes
+
+To summarize these changes:
+
++  Convert original dose units for CEBS study _S0916_ to mg/kg.  
++  ~~Convert original dose units for CEBS study _S0624_ to mg/kg.~~ Data got corrected in CEBS, trusting that.  
++  Input the LOQ for studies _S0976_.  
++  Infer the LOQ for study _S0328_ as 1, given the values near it deemed above and below LOQ.
+
+```{r specific_data_validation}
+# Looking for suspect dose levels
+quick_message(paste0("Looking at dose units not equivalent to mg/kg where ",
+                     "dose_level_original and dose_level_normalized ",
+                     "{.emph remain the same}"))
+cvt_df %>% filter(!(dose_level_units_original %in% equiv_mgkg),
+                  dose_level_normalized == dose_level_original) %>%
+  distinct(fk_study_id, 
+           dose_level_original, dose_level_normalized,
+           dose_level_units_original,
+           pmid,
+           other_study_identifier)
+
+# Checking other_study_identifier == S0916
+quick_message(text = c(
+  "Data Modification:",
+  paste("For study 1713 and 1714, tamoxifen was administered at 5mL/kg, ",
+        "meaning these doses are 5/1000th of current value to convert ug/mL -> mg/kg.")
+))
+# In CEBS "S0916" the Dose is 300,100 ug/mL with 5mL/kg administered by gavage (the only data left)
+# Making it 5/1000 mg/kg x either doses in study_ids 1714,1713 (the latter was filtered out prior to this)
+cvt_df <- cvt_df %>%
+  mutate(
+    invivPK_dose_level = if_else(
+      fk_study_id %in% c("1714", "1713"),
+      5/1000 * dose_level_normalized,
+      invivPK_dose_level
     )
@@
 
-# Need to convert the units to mg/kg
-# In pulling_oral_iv_data_cvtdb.Rmd, it is noted that oral was 5mL/kg and iv 2mL/kg
-# So I need to do ug/mL * mL/kg * 1mg/1000ug = mg/kg
+# In CEBS "S0624" it was in ng/kg not mg/kg in the summary, but that has been deleted from CEBS
+# Assuming that was a error of record
+
+quick_message("CEBS datasets S0976 and S0328 contain data on LOQ or ELOQ")
+# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine 
+quick_message(c(
+  "Data Modification:",
+  "Adjusting LOQ values for L-ephedrine to 3.39 as stated in CEBS study S0976.",
+  "Set LOQ units to ng/mL as detailed in the same CEBS study"
+))
+# Here I create new columns for loq and loq_units b/c I have modified them.
 cvt_df <- cvt_df %>%
-  mutate(
-    dose_level_corrected = ifelse(
-      other_study_identifier %in% "S0916",
-      ifelse(administration_route_normalized %in% "oral",
-             dose_level_original * 5/1000,
-             dose_level_original * 2/1000),
-      dose_level_normalized),
-    dose_level_corrected_units = "mg/kg",
-    .after = dose_level_original_units)
-
-# For this study, it was in ng/kg not mg/kg
-cvt_df <- cvt_df %>%
-  mutate(
-    dose_level_corrected = ifelse(
-      other_study_identifier %in% "S0624",
-      dose_level_original * 1E-6,
-      dose_level_normalized),
-    .after = dose_level_original_units)
-
-# The following measured C-14/H-3 but are indicators for the following Chemicals
-# document_id = 65, DTXSID = DTXSID7031290, name = Isocyclemone E or beta-OTNE
-# document_id = 61, DTXSID = DTXSID4022527, DTXSID3020209,
-### name(s) = propylparaben, butylparaben, missing...methylparaben
-# Propylparaben SERIES_ID = 110, Butylparaben SERIES_ID = 112
-# For above, HPLC reviealed a single peak corresponding with p-hydroxybenzoic acid (PHBA, DTXSID3026647)
-# document_id = 46, DTXSID = DTXSID2020139, name = benzo[a]pyrene
-# document_id = 31, DTXSID = DTXSID2020139, name = benzo[a]pyrene
-
-# However, now would be good time to eliminate any ones where they analyte != test chemical
-# Some studies may have dosed with multiple chemicals... important to note
-# cvt_df <- cvt_df %>% filter(analyzed_chemical_id == test_chemical_id)
-# For now, I will change the chemical name and dtxsid
-cvt_df <- cvt_df %>%
-  mutate(analyte_dtxsid = ifelse(document_id %in% 65, "DTXSID7031290",
-                                 analyte_dtxsid),
-         analyte_name_original = ifelse(document_id %in% 65, "beta-OTNE",
-                                        analyte_name_original)) %>%
-  mutate(analyte_dtxsid = ifelse(document_id %in% 61,
-                                 case_when(
-                                   series_id %in% 110 ~ "DTXSID4022527",
-                                   series_id %in% 112 ~ "DTXSID3020209",
-                                   .default = analyte_dtxsid
-                                 ),
-                                 analyte_dtxsid),
-         analyte_name_original = ifelse(document_id %in% 61,
-                                 case_when(
-                                   series_id %in% 110 ~ "Propylparaben",
-                                   series_id %in% 112 ~ "Butylparaben",
-                                   .default = analyte_name_original
-                                 ),
-                                 analyte_name_original)
-         ) %>%
-  mutate(analyte_dtxsid = ifelse(document_id %in% c(46, 31),
-                                 "DTXSID2020139",
-                                 analyte_dtxsid),
-         analyte_name_original = ifelse(document_id %in% c(46, 31),
-                                        "benzo[a]pyrene",
-                                        analyte_name_original))
-
-# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine were dosed
-cvt_df <- cvt_df %>%
-  mutate(loq = ifelse(
+  mutate(invivPK_loq = if_else(
     other_study_identifier %in% "S0976",
     case_when(
-      analyte_name_original %in% "Caffeine" ~ 4.00,
-      analyte_name_original %in% "L-Ephedrine" ~ 4.44,
-      analyte_name_original %in% "Pseudoephedrine" ~ 4.43
+      analyte_name_original %in% "caffeine" ~ 4.00,
+      analyte_name_original %in% "l-ephedrine" ~ 3.39,
+      analyte_name_original %in% "pseudoephedrine" ~ 4.43
     ),
     loq),
-    loq_units = ifelse(
+    invivPK_loq_units = if_else(
       other_study_identifier %in% "S0976",
@@
 
-# Some pentachloranisole studies
-# S0361 seems to have some data that has not been extracted (also for mouse)
-cvt_df <- cvt_df %>%
-  mutate(loq = case_when(
-    # here omitted a change to a value for LOQ that doubles the minimum detected limit
-    other_study_identifier %in% "S0328" ~ 1, # This is inferred from the data
-    # Highest value under loq is 0.9
-    # Lowest value above loq is 1.263, but there are differences in GC-EC and HPLC methods
-    # The method of imputation for loq may yet need to be improved
-    .default = loq
-  ),
-  loq_units = case_when(
-    other_study_identifier %in% "S0361" ~ "ug/mL",
-    other_study_identifier %in% "S0328" ~ "ug/mL",
-    .default = loq_units
-  ))
-
-# PMID 6310077 is a tritium tracing of B[a]P and these were given as % of Dose
-# The initial dose was 117 nmol, 2 mCi/kg
-# Molecular Mass of benzo[a]pyrene (C20H12) is 252.316 g/mol
-# The initial dose *I think* is in dose_level_normalized
-cvt_df <- cvt_df %>%
-  mutate(conc = ifelse(document_id %in% 38,
-                       conc_original*dose_level_corrected,
-                       conc))
-
-# NTP-CEB C96019 just has a lot of data below LOQ
-# For S0916, there is no > LOQ data for anything but Tamoxifen
-# N-di-butyl phthalate is only good at the iv dose
-# DTXSID2021315 is only good at 1E-4 Dose
-# S0623 Doesn't have any plasma data
-# There is a maybe control sample for hexachlorobenzene (Dose = 0.0 ) ?
-
-# Give N-desmethyltamoxifen it's due DTXSID501315924
-cvt_df <- cvt_df %>%
-  mutate(analyte_dtxsid = ifelse(
-    analyte_name_original %in% "N-desmethyltamoxifen",
-    "DTXSID501315924",
-    analyte_dtxsid
+# Some pentachlorophenol studies
+quick_message(c(
+  "Data Modification:",
+  "Looked at ELOQ in CEBS study S0328 and found it to be around 1",
+  "This only is relevant for {.code study_id} 1779"
 ))
@@
 cvt_df <- cvt_df %>%
-  mutate(analyte_dtxsid = ifelse(
-    analyte_name_original %in% "Methemoglobin",
-    "DTXSID301056085",
-    analyte_dtxsid
+  mutate(
+  invivPK_loq = if_else(
+    fk_study_id %in% "1779",
+    1, invivPK_loq),
+  invivPK_loq_units = if_else(
+    other_study_identifier %in% "S0328",
+    "ug/mL",
+    invivPK_loq_units
   ))
 
-# Standardizing the names (example: glucuronide had two entries)
-cvt_df <- cvt_df %>%
-  mutate(analyte_name_original = tolower(analyte_name_original))
+# quick_stats(cvt_df)
 
+```
+
+## Routine Unit Conversions and final filtering steps
+
+Here I converted units for concentration, concentration standard deviation,
+and LOQ to *ug/mL* and dose units to *mg/kg*. There is a special case for records
+in series 23340 and 23380 where the `conc_original` value is already in *mg/kg*
+but is somehow rounded in `conc`, which gives zero values for the final timepoints in this series
+even when these are not below LOQ.
+
+ There are some final filtering steps as well:
+
++  Filter out chemicals dosed multiple times throughout the experiment.  
++  Filter out chemicals with very limited information.
+
+```{r general_unit_conversions}
+quick_message(c(
+  "Filtering data:",
+  "Only including data with a single dose.",
+  "{.code dose_frequency} of {.code NA} is assumed to be single bolus dose."
+))
 # Eliminate study that gave chemical each day, not single dose
@@
 
+# quick_stats(cvt_df)
+quick_message("Uniqe LOQ units:")
+table(cvt_df$invivPK_loq_units)
+
+quick_message(c(
+  "Modifying Data:",
+  "Converting loq units to concentration unit standard mg/L",
+  "Converting concentration units to standard mg/L",
+  "Converting concentration sd units to the standard mg/L",
+  "Keeping concentration values for series 23340 and 23380 to original records"
+))
 # Normalize LOQ units
 cvt_df <- cvt_df %>%
-  mutate(loq = ifelse(
-    loq_units %in% c("ug/L", "ng/mL"), loq * 1E-3, loq)) # mg/L and ug/mL are same scale
+  mutate(invivPK_loq = if_else(
+    invivPK_loq_units %in% c("ug/L", "ng/mL", "ng/g"),
+    invivPK_loq * 1E-3, invivPK_loq)) # mg/L and ug/mL are same scale
 # Normalize conc_sd and conc units manually
+
+# Some concentrations are already normalized
 cvt_df <- cvt_df %>%
-  mutate(conc_sd_normalized = case_when(
-    conc_units_original %in% c("ug/L", "ng/mL", "ng-Eq/mL", "ng/g tissue") ~ conc_sd_original*1E-3,
+  mutate(invivPK_conc_sd = case_when(
+    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
+                               "ng/g", "ng/g tissue", "ug/L") ~ conc_sd_original*1E-3,
     conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
     conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
+    !is.na(conc_sd) ~ conc_sd, 
     .default = conc_sd_original
@@
 # Need to normalize the ng-eq/mL sample, conc is generally already normalized
+# 
 cvt_df <- cvt_df %>%
-  mutate(conc = case_when(
-    conc_units_original %in% c("ng-eq/mL") ~ conc_original*1E-3,
+  mutate(invivPK_conc = case_when(
+    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
+                               "ng/g", "ng/g tissue", "ug/L") ~ conc_original*1E-3,
+    conc_units_original %in% c("g/dL") ~ conc_original*1E-4,
+    conc_units_original %in% c("pg/mL") ~ conc_original*1E-6,
+    fk_series_id %in% c("23340", "23380") ~ conc_original, # Special case of rounding errors
     .default = conc
@@
 
+quick_message("Are there chemicals with very few (less than 5) observations still?")
+cvt_df %>% count(analyte_dtxsid) %>% arrange(n) %>% head()
+
+quick_message(c(
+  "Filtering Data:",
+  "Removing DTXSID6038299 due to insufficient data",
+  "Removing all data points that still have recorded concentrations of zero"
+))
 cvt_df <- cvt_df %>%
-  dplyr::filter(!(analyte_dtxsid %in% c("DTXSID501315924",
-                                      "DTXSID10169854",
-                                      "DTXSID2021103") )) # These only have 1 or 2 values
+  dplyr::filter(!(analyte_dtxsid %in% "DTXSID6038299"))
+
+# This is the final filtering so that the dataset is most consistent with the
+# most current near future pull in the new year
+cvt_df <- cvt_df %>%
+  filter(invivPK_conc > 0)
 
@@
 
-# This is the final filtering so that the dataset is most consistent with the
-# most current near future pull in the new year
-cvt_df <- cvt_df %>%
-  filter(!is.na(analyte_dtxsid),
-         analyte_dtxsid == test_substance_dtxsid,
-         !(document_id %in% c(38, 65, 110, 112, 46, 31)),
-         !(other_study_identifier %in% c("S0916")),
-         !(analyte_name_original %in% "Methemoglobin"),
-         is.na(radiolabeled))
-
-cvt_df %>%
-  filter(conc > 0) %>%
-  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, document_id,
-           dose_level_normalized) %>%
-  distinct() %>%
-  count() %>% 
-  ungroup() %>%
-  filter(n >= 10) %>% 
-  distinct(analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, document_id,
-           dose_level_normalized) %>%
-  arrange(analyte_dtxsid, species, document_id) %>%
-  left_join(cvt_df) %>% 
-  View()
-
-cvt_df %>%
-  filter(conc > 0) %>%
-  group_by(time_hr, analyte_dtxsid, conc_medium_normalized,
-           administration_route_normalized, species, document_id,
-           dose_level_normalized) %>%
-  distinct() %>%
-  count() %>%
-  ungroup() %>%
-  count(n)
+glimpse(cvt_df, width = 80)
 ```
 
-This filtered and transformed dataset has 14,486 observations.
+Note the columns prefixed by _invivPK_. These are generated as a non-destructive form
+of modifying the data that we will use for _invivoPKfit_. The only column from the
+SQL query result of CvTdb that is actually changed is the `analyte_dtxsid` as 
+described earlier.
+
+```{r}
+quick_stats(cvt_df)
+```
 
@@
 
-```{r}
+```{r saving_data, include=FALSE, eval=FALSE}
 cvt_date <- Sys.Date()
 cvt <- cvt_df
-cvt <- cvt %>% mutate(conc_normalized_units = "mg/L")
 save(cvt, file = "data/cvt.rda", compress = "bzip2")

### 2024-09-10 data-raw/testing_summary.Rmd
Added a function/method testing vignette in data-raw/ which aims to test all package methods systematically. Useful when optimizing code and making any changes to core methods.

---
title: "testing_summary"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
today <- format(Sys.Date(), "%d%B%Y")
set.seed(as.numeric(Sys.Date()))
options(digits = 10, warnPartialMatchDollar = TRUE)
```

## Purpose

The pupose of this document is to test all functions in invivoPKfit and
assist with debugging. No function will remain unturned. Perhaps some of these
examples will be formalized into unit tests included in the package.

The first step is loading some basic packages: _magrittr_ and _devtools_

```{r libraries}
library(devtools)
load_all()
library(magrittr)
```

Now the first thing we could do is get a list of all the functions.
Since we are in a project-based development environment, we are already in the
necessary working directory. We can inquire all the _.R_ files in the Terminal as so:

```
ls R/*.R
ls -l R/*.R | wc -l
```

We have 111 functions and methods in this package! This will be a lot of work to get
through, hence the inspiration for this document. First things first, make a 
"small" version of `cvt` that we can quickly fit. For the purposes of this
document, I will take 5% of CVT_Legacy data.
I will also add a few chemicals + species' data that I know will fail or
be skipped, so that these features may be tested.

```{r tiny-cvt}
tiny_cvt <- cvt %>%
  dplyr::filter(curation_set_tag == "CVT_Legacy") %>%
  dplyr::distinct(analyte_dtxsid, species) %>%
  dplyr::slice_sample(prop = 0.05) %>%
  dplyr::bind_rows(
    data.frame(
      analyte_dtxsid = c("DTXSID00861411", "DTXSID6023577", 
                         "DTXSID1043881", "DTXSID3061635",
                         "DTXSID1021116", "DTXSID2020139"),
      species = rep("rat", 6)
    )) %>%
  dplyr::distinct() %>%
  dplyr::left_join(cvt, by = dplyr::join_by(analyte_dtxsid, species))

length(unique(tiny_cvt$analyte_dtxsid))
length(unique(tiny_cvt$administration_route_normalized)) # Should be two
length(unique(tiny_cvt$conc_medium_normalized)) # Should be two
tiny_cvt %>% 
  dplyr::distinct(analyte_dtxsid, species, n_subjects_normalized, curation_set_tag)
```

The next step is to create a minimal PK object like in the main vignette.

```{r minimal-pk}
minimal_pk <- pk(data = tiny_cvt %>%
                   mutate(n_subjects_normalized = if_else(
                     n_subjects_normalized > 1 & is.na(invivPK_conc_sd),
                     min(n_subjects_normalized, 6), n_subjects_normalized)),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = fk_extraction_document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = invivPK_dose_level,
                   Dose.Units = "mg/kg",
                   Subject_ID = fk_subject_id,
                   Series_ID = fk_series_id,
                   Study_ID = fk_study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_normalized,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = invivPK_conc,
                   Value.Units = "mg/L",
                   Value_SD = invivPK_conc_sd,
                   LOQ = invivPK_loq
                 ))

testthat::expect_identical(length(minimal_pk), 10L)
```

From here I need to set up the pk object settings. I will be using the dose-normalization only,
then re-run using all settings at the end.

```{r pk-settings}
my_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("bobyqa", "L-BFGS-B")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  stat_error_model(error_group = vars(Chemical, Species, Reference))
```

## Setting Getters Test

Below are just a few checks for the settings I changed above.

```{r setting-getters}
get_data_group(my_pk) # Modified to follow output from get_error_group
get_error_group(my_pk)

get_mapping(my_pk)
get_settings_data_info(my_pk) # Removed nca_group
get_settings_preprocess(my_pk)
get_scale_time(my_pk)
get_scale_conc(my_pk)
get_stat_error_model(my_pk) # Removed Chemical <- NULL
get_stat_model(my_pk)

get_status(my_pk)
get_status(my_pk, suppress.messages = TRUE)

testthat::expect_identical(get_status(my_pk), 1L)
```

Now we can do the pre-processing steps. Important to note that there is actually
an impute_sd setting that is on by default but has been commented out.

I need to figure out what the effect of the 30% is on calculating sigma.

```{r pre-process}
my_pk <- do_preprocess(my_pk)
my_data <- get_data(my_pk)
# Showing that Chemical + Species + Route + Media + Dose defines
# A CvT experiment, not necessarily Study_ID
my_data %>% dplyr::distinct(Study_ID,
                            Chemical, Species, Route, Media, Dose)

```

Next I will go through the data info function. Implicitly, this tests
the `nca` and `calc_nca`

```{r data-info}
my_pk <- do_data_info(my_pk)
get_status(my_pk)
```

Next is pre-fitting. Here, the upper/lower bounds & starts for the parameters.
Here is also where sigma values are initialized.

```{r prefit}
my_pk <- do_prefit(my_pk)
get_prefit(my_pk) # This has some odd outputs :/
get_status(my_pk)
get_data_summary(my_pk)
get_settings_optimx(my_pk)
```

Finally do the fitting, here is where most of the functions come to play,
including the model functions. Walk through the main function and set `browser()`
markers in the concentration prediction functions.

```{r fit}
thispk_profvis <- profvis::profvis(do_fit(my_pk))
system.time(my_pk <- do_fit(my_pk)) # 72 seconds, 11 data_groups

```

After some optimization of the fitting functions... now it's time
to optimize some of the downstream analysis functions and make sure they work
as intended! Firstly, I changed the way fit object _look_ so I need to change how
it interfaces with the coef method.

I have also found a _safer_ way to select the model functions in `predict.pk()`
that is based on joins and creating a data.frame of model names and functions
ahead of time.

```{r coef-preds}
my_coefs <- coef(my_pk)
my_preds <- predict(my_pk)
my_logLik <- logLik(my_pk)
```

There are a bunch of methods that call these three...  
For coef.pk() :

+ coef_sd.pk()  
+ get_tkstats.pk()  
+ _logLik.pk()_  
+ _predict.pk()_  
+ summary.pk()

For predict.pk() :

+ fold_errors.pk()  
+ residuals.pk()  
+ rsq.pk()  
+ rmse.pk()

For logLik.pk() :

+ AIC.pk()  
+ BIC.pk()  
+ get_winning_model.pk()

I will start with adjusting the `predict.pk()`-dependent methods.
Since most of these simply use the results from `predict.pk()`, it should
be simple.

```{r}
my_residuals <- residuals(my_pk)
my_fes <- fold_errors(my_pk)
my_rmse <- rmse(my_pk)
my_rmsle <- rmse(my_pk, use_scale_conc = list(dose_norm = FALSE,
                                              log10_trans = TRUE))

my_rsq <- rsq(my_pk)
```

Next lets address `logLik.pk()`-dependent methods. Generally, what I did here
is let `logLik.pk()` take the responsibility of checking that the methods
and models were alright. This was done more for efficiency in reading the code.
One important consideration for `get_winning_model.pk()` is what happens
when there are ties? This is probably unlikely to be the case, but we
need to account for it nonetheless.

```{r}
my_AIC <- AIC(my_pk)
my_BIC <- BIC(my_pk)
my_wm <- get_winning_model(my_pk)
```

Lastly, let's take a look at the remaining `coef.pk()`-dependent methods.
To make more efficient use of the results, I modified the output of
`coef_sd.pk` to look like `coef`, removing the table_format option.
`get_tkstats(my_pk)` has some nested operations that I think can be optimized
further.

```{r}
my_coefsd <- coef_sd(my_pk)
my_tkstats <- get_tkstats(my_pk)
best_tkstats <- eval_tkstats(my_pk)
```

### 2024-09-20 data-raw/testing_summary.Rmd
Updated vignettes and saved fitted pk object, changed twofold_test.pk filename and method dispatch documentation.

@@
 library(magrittr)
+library(ggplot2)
 ```
@@
 "small" version of `cvt` that we can quickly fit. For the purposes of this
-document, I will take 5% of CVT_Legacy data.
+document, I will take 20% of CVT_Legacy data.
 I will also add a few chemicals + species' data that I know will fail or
@@
   dplyr::distinct(analyte_dtxsid, species) %>%
-  dplyr::slice_sample(prop = 0.05) %>%
+  dplyr::slice_sample(prop = 0.20) %>%
   dplyr::bind_rows(
@@
                          "DTXSID1043881", "DTXSID3061635",
-                         "DTXSID1021116", "DTXSID2020139"),
-      species = rep("rat", 6)
+                         "DTXSID1021116", "DTXSID2020139",
+                         "DTXSID3031862"),
+      species = rep("rat", 7)
     )) %>%
@@
 ```{r minimal-pk}
-minimal_pk <- pk(data = tiny_cvt %>%
+flat_chems <- paste0("DTXSID",
+                     c(2020139,
+                       5037523,
+                       8020541,
+                       8025337,
+                       5034773,
+                       4021268))
+
+minimal_pk <- pk(data = cvt %>%
+                   # filter(analyte_dtxsid %in% flat_chems) %>%
                    mutate(n_subjects_normalized = if_else(
@@
 
-From here I need to set up the pk object settings. I will be using the dose-normalization only,
-then re-run using all settings at the end.
+From here I need to set up the pk object settings.
+I will be using all settings as TRUE.
 
@@
                       suppress.messages = FALSE) +
-  settings_optimx(method = c("bobyqa", "L-BFGS-B")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  # scale_time(new_units = "auto") +
+  settings_optimx(method = c(
+    "bobyqa",
+    "L-BFGS-B")) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  scale_time(new_units = "auto") +
   stat_error_model(error_group = vars(Chemical, Species, Reference))
@@
 my_data <- get_data(my_pk)
-# Showing that Chemical + Species + Route + Media + Dose defines
-# A CvT experiment, not necessarily Study_ID
-my_data %>% dplyr::distinct(Study_ID,
-                            Chemical, Species, Route, Media, Dose)
-
+my_data %>% dplyr::distinct(Chemical, Species) %>% NROW()
 ```
@@
 thispk_profvis <- profvis::profvis(do_fit(my_pk))
-system.time(my_pk <- do_fit(my_pk)) # 72 seconds, 11 data_groups
+system.time(my_pk <- do_fit(my_pk))
+system.time(my_pk <- do_fit(my_pk, n_cores = 10))
+my_pk <- do_fit(my_pk)
+# 100 seconds, 11 data_groups
+# 270 seconds, 25 data_groups
+# 12 cores, full dataset:  489 seconds
 
+get_winning_model(my_pk) %>% View()
 ```
@@
 my_rsq <- rsq(my_pk)
+
+plot(my_rsq$Rsq, my_rmsle$RMSLE)
 ```
@@
 my_wm <- get_winning_model(my_pk)
+table(my_wm$model)
+
 ```
@@
 ```
+
+Plotting is of the important outputs of _invivoPKfit_, as it allows
+people to visualize the predictions and form a second opinion on the
+fits.
+
+```{r}
+mypl <- plot(my_pk, best_fit = TRUE)
+```

### 2024-10-15 data-raw/pulling_oral_iv_data_cvtdb.Rmd

@@
       5/1000 * dose_level_normalized,
-      invivPK_dose_level
+      dose_level_normalized
     )

### 2024-10-15 data-raw/testing_summary.Rmd

@@
 
-minimal_pk <- pk(data = cvt %>%
+minimal_pk <- pk(data = tiny_cvt %>%
                    # filter(analyte_dtxsid %in% flat_chems) %>%
@@
   scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  scale_time(new_units = "auto") +
+  # scale_time(new_units = "auto") +
   stat_error_model(error_group = vars(Chemical, Species, Reference))
@@
 ```{r}
-mypl <- plot(my_pk, best_fit = TRUE)
+mypl <- plot(my_pk, log10_C = TRUE)
+mypl %>% pull(final_plot) %>% .[[13]]
 ```

### 2024-11-04 data-raw/RestrictiveClearance_comparison.Rmd
Updated object 'cvt' and related documentation. invivPK_loq_units were not ug/mL as intended. Added description of each column of the data. Added description for fup-optimizing clearance aware 1-compartment model in data.R

--- 2024-05-15 data-raw/RestrictiveClearance_comparison.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
 ```
@@
 library(tidyverse)
-my_pk <- readRDS("data-raw/all_cvt_pk_JOINT.rds")
-```
+my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+httk::load_dawson2021()
+```
+
+Steps in the analysis:
+
+1. Get chemicals + species combinations in CvTdb that have _httk_ predictions.
+2. Safely get parameters, clearance, and solutions for each of these groups.
+3. Compare clearances from _httk_ with those from _invivoPKfit_.
+4. Compare $f_{up}$ for subset of data with total values available via _httk_.
+5. Use new _clearance-aware_ optimization of 1-compartment parameters to
+benchmark _httk_ solutions.
+6. Estimate the fraction unbound in plasma for chemicals with rat data,
+for those same chemicals with human data for Clint and Fup. 
+Begin with the assumption that there is restrictive clearance, those chemicals
+that do not change when optimized (and produce reasonable fits) are likely to
+be _restrictively cleared_, whereas those that increase Fup during maximum
+likelihood estimation are _possibly non-restrictively clearaed_. 
+7. Other factors such as renal clearance may play a role in those cases.
+Validate the clearance estimate by measuring changes in predicted clearance.
+Important to identify whether there seems to be a "fraction missing".
+8. Wrap the previous steps into attempts to identify true positive
+categorizations for Restrictive and Potentially Non-Restrictively metabolized
+chemicals (include Lipinski's Rule of 5 too).
 
@@
 
-```{r chems_in_common}
-common_chems <- cvt %>%
-  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk")) %>%
+```{r dawson}
+# try dawson
+# can also be run as background job (see data-raw/RC_comparison_bkgd.R)
+
+human_chems_gas <- get_cheminfo(info = "DTXSID",
+                                species = "Human",
+                                model = "gas_pbtk",
+                                median.only = TRUE,
+                                physchem.exclude = TRUE,
+                                suppress.messages = TRUE)
+
+common_chems_dawson <- cvt %>%
+  filter(species %in% c("human", "rat", "mouse"),
+         analyte_dtxsid %in% human_chems_gas) %>%
   pull(analyte_dtxsid) %>%
@@
 
-common_chems[!(common_chems %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk"))] %>%
-  unique() %>%
-  sort()
-```
-
-```{r dawson}
-# try dawson
-httk::load_dawson2021()
-
-common_chems_dawson <- cvt %>%
-  subset(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk")) %>%
+rat_chems_gas <- get_cheminfo(info = "DTXSID",
+                                species = "Rat",
+                                model = "gas_pbtk",
+                                median.only = TRUE,
+                                physchem.exclude = TRUE,
+                                suppress.messages = TRUE)
+
+common_chems_rat <- cvt %>%
+  filter(species %in% "rat",
+         analyte_dtxsid %in% rat_chems_gas) %>%
   pull(analyte_dtxsid) %>%
@@
 
-cvt %>%
-  subset(!(analyte_dtxsid %in% get_cheminfo(info = "DTXSID", model = "gas_pbtk"))) %>%
-  dplyr::distinct(analyte_dtxsid, analyte_name_original)
-
-# Test which analyte_dtxsid don't have a clearance or vdist
-
-data.frame(Chemical = unique(cvt$analyte_dtxsid)) %>%
-  rowwise() %>%
-  mutate(needs_RestCL = ifelse(
-    (class(try(calc_total_clearance(dtxsid = Chemical,
-                     restrictive.clearance = TRUE,
-                     suppress.messages = TRUE))) == "try-error"),
-    TRUE, FALSE),
-    needs_nonRestCL = ifelse(
-      (class(try(calc_total_clearance(dtxsid = Chemical,
-                     restrictive.clearance = FALSE,
-                     suppress.messages = TRUE))) == "try-error"),
-    TRUE, FALSE),
-    needs_Vdist = ifelse(
-      (class(try(calc_vdist(dtxsid = Chemical,
-                     suppress.messages = TRUE))) == "try-error"),
-    TRUE, FALSE)) %>%
-  ungroup() -> has_all_needed_df
-
-has_all_needed_df %>%
-  filter(!(needs_RestCL | needs_nonRestCL | needs_Vdist)) %>%
-  pull(Chemical) %>% unique() -> common_chems_dawson
-
+remove(list = c("human_chems_gas", "rat_chems_gas"))
+
+# How many are in the previous invivoPKfit analysis?
+length(common_chems_dawson %in% unique(my_pk$fit %>%
+                                         filter(convcode == 0) %>%
+                                         pull(Chemical)))
+
+test_parameterization <- function(dtxsid, species = "Human") {
+  is(
+    tryCatch(
+      {
+        parameterize_gas_pbtk(dtxsid = dtxsid,
+                              species = species,
+                              supress.messages = TRUE)  
+      }, error = function(e) {
+        NULL
+      }
+    ),
+    "list"
+  )
+}
+
+parameterize_all_gas <- function(dtxsid, species = "Human") {
+  # Note that Clint is given in uL/min, which must be converted to L/h
+  params <- httk::parameterize_gas_pbtk(dtxsid = dtxsid,
+                                        species = species,
+                                        default.to.human = FALSE)
+  paramdf <- data.frame(Chemical = dtxsid, Species = tolower(species),
+                        Qliverf = params$Qliverf,
+                        Funbound.plasma = params$Funbound.plasma,
+                        Clint = params$Clint*60/1e+6)
+  paramdf$fupClint <- paramdf$Funbound.plasma * paramdf$Clint
+  paramdf$ExtEff <- paramdf$fupClint/(paramdf$Qliverf + paramdf$fupClint)
+  paramdf$Q_Clint <- paramdf$Qliverf/paramdf$Clint
+  return(paramdf)
+}
+
+if (all(vapply(common_chems_rat, test_parameterization,
+               FUN.VALUE = logical(1), species = "Rat"))) {
+  rat_params <- do.call(rbind, lapply(common_chems_rat,
+                                      parameterize_all_gas,
+                                      species = "Rat"))
+}
+
+if (all(vapply(common_chems_dawson, test_parameterization,
+               FUN.VALUE = logical(1), species = "Human"))) {
+  human_params <- do.call(rbind, lapply(common_chems_dawson,
+                                        parameterize_all_gas,
+                                        species = "Human"))
+}
 ```
@@
 ```{r get_clearances}
-clearance_df <- data.frame(Chemical = common_chems) %>%
-  rowwise() %>%
-  mutate(Restrict_Cl = calc_total_clearance(dtxsid = Chemical,
-                                            restrictive.clearance = TRUE,
-                                            suppress.messages = TRUE),
-         nonRestrict_Cl = calc_total_clearance(dtxsid = Chemical,
-                                            restrictive.clearance = FALSE,
-                                            suppress.messages = TRUE)) %>%
-  ungroup()
-
-hep_clearance_df <- data.frame(Chemical = common_chems) %>%
-  rowwise() %>%
-  mutate(Restrict_Cl = calc_hep_clearance(dtxsid = Chemical,
-                                            restrictive.clearance = TRUE,
-                                            suppress.messages = TRUE),
-         nonRestrict_Cl = calc_hep_clearance(dtxsid = Chemical,
-                                            restrictive.clearance = FALSE,
-                                            suppress.messages = TRUE)) %>%
-  ungroup()
+params_dtxsid <- function(dtxsid, species) {
+  httk::parameterize_gas_pbtk(dtxsid = dtxsid,
+                              species = species,
+                              default.to.human = FALSE,
+                              suppress.messages = TRUE)
+}
+
+make_clearance_df <- function(dtxsid, species) {
+  tmp_df <- data.frame(Chemical = dtxsid)
+  tmp_params <- lapply(dtxsid, params_dtxsid, species = species)
+  tmp_df$restrict_cl <- vapply(tmp_params,
+                               \(x) {
+                                 calc_total_clearance(
+                                   parameters = x,species = species,
+                                   suppress.messages = TRUE,
+                                   restrictive.clearance = TRUE
+                                 )
+                               },
+                               FUN.VALUE = double(1L)
+  )
+  tmp_df$nonrestrict_cl <- vapply(tmp_params,
+                                  \(x) {
+                                    calc_total_clearance(
+                                      parameters = x,species = species,
+                                      suppress.messages = TRUE,
+                                      restrictive.clearance = FALSE
+                                    )
+                                  },
+                                  FUN.VALUE = double(1L)
+  )
+  return(tmp_df)
+}
+clearance_df <- make_clearance_df(dtxsid = common_chems_rat, species = "rat")
+```
+
+```{r combine_tkstats}
+# Start Here if you ran the background job
 
 my_tkstats <- eval_tkstats(my_pk) %>%
+  filter(Media %in% "plasma") %>%
   dplyr::select(Chemical, Species, CLtot.tkstats, CLtot.nca) %>%
   distinct() %>%
-  filter(Chemical %in% common_chems,
-         !is.na(CLtot.tkstats), !is.na(CLtot.nca)) %>%
+  filter(
+    Species %in% "rat",
+    Chemical %in% common_chems_rat,
+    !is.na(CLtot.tkstats), !is.na(CLtot.nca)
+  ) %>%
   group_by(Chemical, Species, CLtot.tkstats) %>%
-  summarize(CLtot.nca_mean = mean(CLtot.nca),
-            CLtot.nca_sd = sd(CLtot.nca))
+  summarize(
+    CLtot.nca_mean = mean(CLtot.nca),
+    CLtot.nca_sd = sd(CLtot.nca)
+  )
 
@@
 combined_clearance_df <- my_tkstats %>% inner_join(clearance_df)
-
 ```
@@
 
-```{r viz}
+```{r clearance_viz}
+combined_clearance_df %>%
+  mutate(AD_restrictive = abs(CLtot.tkstats - restrict_cl),
+         AD_nonrestrictive = abs(CLtot.tkstats - nonrestrict_cl),
+         rough_determination = ifelse(
+           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
+             CLtot.tkstats < nonrestrict_cl,
+           "Restrictive", "Possibly non-Restrictive"
+         )) %>% 
+  dplyr::distinct(Chemical, rough_determination) %>%
+  View()
 
 # Preliminary viz, plot all clearances
-combined_clearance_df %>%
+ccd <- combined_clearance_df %>%
   relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
-  pivot_longer(cols = 3:6,
+  pivot_longer(
+    cols = 3:6,
     names_to = "Clearance_Source",
-               values_to = "Value") %>%
-  ggplot(aes(x = Value,
+    values_to = "Value"
+  ) %>%
+  mutate(
+    Chemical = factor(Chemical),
+    Clearance_Source = factor(
+      Clearance_Source,
+      levels = c(
+        "CLtot.tkstats", "CLtot.nca_mean",
+        "nonrestrict_cl", "restrict_cl"
+      )
+    )
+  ) %>%
+  transform(
+    Chemical = fct_reorder(Chemical, Value, max)
+  ) %>% 
+  as_tibble()
+
+ccd %>%
+  ggplot(aes(
+    x = Value,
     y = Chemical,
-             fill = Clearance_Source)) +
+    fill = Clearance_Source
+  )) +
   geom_point(shape = 21, alpha = 0.7) +
   scale_x_log10() +
-  scale_fill_manual(breaks = c("nonRestrict_Cl", "CLtot.tkstats",
+  scale_fill_manual(
+    breaks = c(
+      "nonrestrict_cl", "CLtot.tkstats",
       "CLtot.nca_mean",
-                               "Restrict_Cl"),
-                    labels = c("non-restrictive clearance (httk)",
+      "restrict_cl"
+    ),
+    labels = c(
+      "non-restrictive clearance (httk)",
       "predicted clearance (invivoPKfit)",
       "mean non-compartmental total clearance (invivoPKfit)",
-                               "restrictive clearance (httk)"),
-                    values = c("orange2", "grey5", "skyblue3",  "green4")) +
+      "restrictive clearance (httk)"
+    ),
+    values = c("orange2", "grey5", "skyblue3", "green4")
+  ) +
   facet_grid(rows = vars(Species), scales = "free", space = "free") +
-  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
+  labs(
+    x = "Total Clearance",
+    y = "Chemical"
+  ) +
+  theme(
+    panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
     panel.background = element_blank(),
@@
     strip.background = element_rect(fill = "white"),
-        strip.text = element_text(face = "bold"),
-        legend.position = "bottom",
+    strip.text = element_text(face = "bold", angle = 0),
+    # axis.text.y = element_blank(),
+    axis.title.y = element_blank(),
+    legend.position = "right",
     legend.direction = "vertical",
     axis.ticks = element_blank(),
-        axis.line = element_blank())
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "tkClearance_comparison_httk_gasPBPK.png"),
-       height = 14,
-       width = 5,
-       device = "png")
-```
-
-Finally, what I want to analyze is how good the fits for these chemicals are relative to the rest of the chemicals.
-
-```{r fit_analysis}
-wm <- get_winning_model(my_pk)
-ingroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
-  filter(Chemical %in% combined_clearance_df$Chemical) %>%
-  mutate(Group = "in httk")
-
-outgroup_rmse <- rsq(my_pk) %>% inner_join(wm) %>%
-  filter(!(Chemical %in% combined_clearance_df$Chemical)) %>%
-  mutate(Group = "not in httk")
-
-all_group_rmse <- bind_rows(ingroup_rmse, outgroup_rmse)
-
-all_group_rmse %>%
-  filter(Species == "rat") %>%
-  ggplot(aes(x = Rsq, y = Chemical,
-             shape = Group)) +
-  geom_point() +
-  facet_grid(rows = vars(Group), scales = "free", space = "free") +
-  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
-        panel.background = element_blank(),
-        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-        strip.background = element_rect(fill = "white"),
-        strip.text = element_text(face = "bold"),
-        legend.direction = "vertical",
-        axis.ticks = element_blank(),
-        axis.line = element_blank(),
-        axis.text.y = element_blank())
-
-ggsave(paste0(Sys.getenv("FIG_DIR"), "Rsq_gaspbtk.png"),
+    axis.line = element_blank()
+  )
+
+clear_chem_levels <- levels(ccd$Chemical)
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
+    "rat_tkClearance_comparison_httk_PBPK.png"
+  ),
+  height = 8,
+  width = 8,
+  device = "png"
+)
+```
+
+I would also like to know, how does the $f_{up}$ of this set of chemicals
+compare to that of all chemicals in `httk` (Dawson 2021).
+
+```{r fup_comparison}
+fup_df <- data.frame(
+  Chemical = get_cheminfo("DTXSID", species = "Rat"),
+  fup = as.numeric(vapply(get_cheminfo("Funbound.plasma", species = "Rat"),
+                          gsub, pattern = ",.+", replacement = "",
+                          FUN.VALUE = character(1)
+  ))
+)
+
+fup_df %>%
+  ggplot(aes(x = fup)) +
+  geom_histogram(
+    # aes(y = after_stat(density)),
+    binwidth = 0.03,
+    color = "grey5", fill = "grey5"
+  ) +
+  geom_histogram(
+    data = fup_df %>%
+      filter(Chemical %in% common_chems_rat),
+    # aes(y = after_stat(density)),
+    fill = NA,
+    color = "darkgreen", binwidth = 0.03
+  ) +
+  expand_limits(expand = c(0,0)) +
+  # geom_vline(xintercept = 0.05, linetype = "dashed") +
+  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
+  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
+  labs(
+    title = "Distribution of Funbound.plasma values",
+    subtitle = "(chemicals fit by invivoPKfit in dark green)"
+  ) +
+  coord_cartesian(clip = "off") +
+  theme_bw()
+
+ggsave(paste0(Sys.getenv("FIG_DIR"), "fup_density_plots.png"),
        height = 5,
-       width = 5)
-
+       width = 6,
+       device = ragg::agg_png,
+       units = "in"
+)
+
+test_fup <- fup_df %>%
+  # filter(Chemical %in% common_chems_dawson) %>%
+  pull(fup)
+for (i in seq(0, 0.5, by = 1e-9)) {
+  if (sum(test_fup > i) == sum(test_fup <= i)) {
+    print(i)
+    break
+  }
+}
 ```
@@
 
+Note that this is only for rats. This is supposed to be the best case,
+but of course _httk_ is "made" for predicting **human exposures**. Also,
+I will try to order some of this data the same way as the clearance figures.
+
+This will ultimately help understand whether Total Clearance
+differences and prediction differences relate. Of course it would
+be possible to do a formal test for correlation but that overdoes what we need
+to build this relationship for with the rather limited _rat_ data we have
+in both _httk_ and _invivoPKfit_.
+
+```{r rat_invivo_comparison}
+
+solve_gas_pbtk(
+  dtxsid = common_chems_dawson[10],
+  dose = 1, exp.conc = 0,
+  iv.dose = FALSE,
+  input.units = "mg/kg",
+  output.units = "mg/L",
+  suppress.messages = TRUE
+) %>%
+  ggplot(aes(x = time)) +
+  geom_line(aes(y = Cplasma)) +
+  geom_line(aes(y = Crest), color = "blue4") +
+  geom_line(aes(y = Cgut), color = "goldenrod") +
+  geom_line(aes(y = Cliver), color = "darkgreen") +
+  geom_line(aes(y = Clung), color = "hotpink") +
+  geom_line(aes(y = Ckidney), color = "purple4")
+
+# Functions wrapping httk single dose evaluation
+httk_bolus_gas_pbtk <- function(dtxsid, species = "Human",
+                                dose, times, iv.dose, LOQ) {
+  tmp_solution <- solve_gas_pbtk(
+    dtxsid = unique(dtxsid),
+    dose = unique(dose),
+    exp.conc = 0,
+    iv.dose = unique(iv.dose),
+    times = unique(c(0, times/24)),
+    input.units = "mg/kg",
+    output.units = "mg/L",
+    species = unique(stringr::str_to_title(species)),
+    default.to.human = TRUE,
+    suppress.messages = TRUE
+  )
+  # Remove the 0.0001 intermediate time value that is returned
+  retdf <- tibble(
+    Time = round(tmp_solution[, "time"]*24, digits = 3),
+    httk_Preds = tmp_solution[, "Cplasma"]
+  )
+  retdf[which(retdf$Time %in% unique(round(times, 3))), ]
+}
+```
+
+We need to put the _in vivo_ data in an amenable format.
+For this I will limit the species to "rat", the chemicals to
+`common_chems_rat`, and the medium to "plasma".
+
+```{r rat_data}
+my_data <- get_data(my_pk)
+
+rat_df <- my_data %>%
+  distinct(Chemical, Species, Dose, Route, Media, Time, Conc, exclude, Detect,
+           pLOQ) %>%
+  filter(Species %in% "rat", Media %in% "plasma",
+         Chemical %in% common_chems_rat, !exclude, Detect) %>%
+  mutate(iv_dose = (Route == "iv"),
+         Time = round(Time, 3)) %>%
+  group_by(Chemical, Species, Dose, Route, Media) %>%
+  filter(n() > 4) %>%
+  nest(.key = "CvT") %>%
+  rowwise() %>%
+  mutate(
+    httk_solved = list(
+      tryCatch(
+        expr = do.call(httk_bolus_gas_pbtk,
+                       list(
+                         dtxsid = Chemical,
+                         species = Species,
+                         dose = Dose,
+                         times = CvT$Time,
+                         iv.dose = CvT$iv_dose,
+                         LOQ = CvT$pLOQ
+                       )
+        ) %>%
+          inner_join(tibble(Time = CvT$Time, Conc = CvT$Conc, pLOQ = CvT$pLOQ),
+                     by = join_by(Time)),
+        error = function(err) {
+          message(paste0("Unable to get solution for ", Chemical))
+          print(err)
+        } 
+      )
+    )
+  ) %>% filter(Chemical %in% clear_chem_levels)
+
+length(unique(rat_df$Chemical))
+
+rat_df$Chemical <- factor(rat_df$Chemical, levels = clear_chem_levels)
+
+rat_df <- rat_df %>%
+  dplyr::select(Chemical, Species, Dose, Route, Media, httk_solved) %>%
+  unnest(cols = httk_solved)
+
+rat_out <- rat_df %>%
+  mutate(httk_Preds = ifelse(httk_Preds < pLOQ, pLOQ, httk_Preds)) %>% 
+  mutate(SLE = (log2(Conc) - log2(httk_Preds))^2,
+         AE = abs(Conc - httk_Preds)) %>%
+  summarize(
+    RMSLE = sqrt(mean(SLE, na.rm = TRUE)),
+    MAE = mean(AE, na.rm = TRUE)
+   ) %>% pivot_longer(cols = c(RMSLE, MAE),
+                      names_to = "metric",
+                      values_to = "value")
+
+rat_out %>%
+  na.omit() %>%
+  ggplot() +
+  geom_tile(data = rat_out %>% na.omit() %>%
+              filter(metric %in% "RMSLE"),
+            aes(x = metric, y = Chemical, fill = value)) +
+  scale_fill_gradient(low = "grey5", high = "grey90",
+                      name = "RMSLE") +
+  ggnewscale::new_scale_fill() +
+  geom_tile(data = rat_out %>% na.omit() %>%
+              filter(metric %in% "MAE"),
+            aes(x = metric, y = Chemical, fill = value)) +
+  scale_fill_gradient(low = "darkgreen", high = "seagreen1",
+                      limits = c(0, 80),
+                      labels = c("0", "20",
+                                 "40", "60",
+                                 "80+"),
+                      oob = scales::squish,
+                      name = "MAE") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(hjust = 1, angle = 50),
+        legend.title = element_text(hjust = 0.5)) +
+  coord_fixed(ratio = 0.75)
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
+    "rat_httk_predictionRMSLE.png"
+  ),
+  height = 8.1,
+  width = 4,
+  device = "png"
+)
+
+rat_out2 <- rat_df %>%
+  group_by(Chemical, Species, Route, Dose) %>% nest() %>%
+  summarize(plot = map(
+    data,
+    \(d){
+      ggplot(d, aes(x = Time)) +
+        geom_point(aes(y = Conc)) +
+        geom_line(aes(y = httk_Preds),
+                    color = "forestgreen") +
+        geom_point(aes(y = httk_Preds),
+                   color = "forestgreen",
+                   shape = 1) +
+        labs(title = Chemical,
+             subtitle = paste(Dose, "mg/kg given via",
+                               Route, "bolus"),
+             y = "Plasma Concentration (mg/L)",
+             x = "Time (hrs)") +
+        theme_bw() +
+        theme(plot.title = element_text(hjust = 0.5),
+              plot.subtitle = element_text(hjust = 0.5))
+    }
+  ))
+```
+
 ```{r httk_solution}
-httk::calc_tkstats(dtxsid = unique(combined_clearance_df$Chemical)[[5]])
-httk::parameterize_gas_pbtk(restrictive.clearance = TRUE,
-                            dtxsid = unique(combined_clearance_df$Chemical)[[5]])
-
-httk::solve_gas_pbtk(dtxsid = unique(combined_clearance_df$Chemical)[[5]],
+
+rat_params %>%
+  ggplot(aes(y = fupClint)) + 
+  geom_point(aes(x = Clint), color = "darkred", shape = 1) +
+  geom_abline(slope = 1, intercept = 0, color = "darkblue",
+              linetype = "dashed")
+
+rat_params %>%
+  mutate(fup_z = scale(Funbound.plasma),
+         clint_z = scale(Clint)) %>%
+  dplyr::select(Chemical, fup_z, clint_z) %>%
+  pivot_longer(cols = c(fup_z, clint_z),
+               names_to = "pars", values_to = "vals") %>%
+  ggplot(aes(x = pars, y = vals, group = Chemical)) +
+  geom_line()
+
+httk::calc_tkstats(dtxsid = unique(rat_out$Chemical)[[5]])
+httk::parameterize_gas_pbtk(
+  restrictive.clearance = TRUE,
+  dtxsid = unique(rat_out$Chemical)[[5]]
+)
+
+httk::solve_gas_pbtk(
+  dtxsid = unique(combined_clearance_df$Chemical)[[5]],
   parameters = httk::parameterize_gas_pbtk(
@@
   days = 3,
-                     plots = TRUE)
+  plots = TRUE
+)
 
@@
 # This constant is derived by httk in the following way:
-calc_total_clearance(dtxsid = common_chems[[10]],
-                             restrictive.clearance = FALSE) /
+calc_total_clearance(
+  dtxsid = common_chems[[10]],
+  restrictive.clearance = FALSE
+) /
   calc_vdist(dtxsid = common_chems[[10]])
-
 ```
@@
 minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% common_chems_dawson),
-                 mapping = ggplot2::aes(
-                   Chemical = analyte_dtxsid,
-                   Chemical_Name = analyte_name_original,
-                   DTXSID = analyte_dtxsid,
-                   CASRN = analyte_casrn,
-                   Species = species,
-                   Reference = document_id,
-                   Media = conc_medium_normalized,
-                   Route = administration_route_normalized,
-                   Dose = dose_level_normalized,
-                   Dose.Units = "mg/kg",
-                   Subject_ID = subject_id,
-                   Series_ID = series_id,
-                   Study_ID = study_id,
-                   ConcTime_ID = conc_time_id,
-                   N_Subjects = n_subjects_in_series,
-                   Weight = weight_kg,
-                   Weight.Units = "kg",
-                   Time = time_hr,
-                   Time.Units = "hours",
-                   Value = conc,
-                   Value.Units = "mg/L",
-                   Value_SD = conc_sd_normalized,
-                   LOQ = loq
-                 ))
+                   filter(analyte_dtxsid %in% common_chems_rat,
+                          species %in% "rat"))
 
@@
   facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE,
-                      suppress.messages = FALSE) +
+  settings_preprocess(
+    keep_data_original = TRUE,
+    suppress.messages = FALSE
+  ) +
   settings_optimx(method = c("L-BFGS-B")) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
-  stat_model(model = c("model_1comp", "model_1comp_cl_rest", "model_1comp_cl_nonrest"))
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  stat_error_model(error_group = vars(Chemical, Species)) +
+  stat_model(model = c(
+    "model_1comp", "model_1comp_cl_rest", 
+    "model_1comp_cl_nonrest", "model_1comp_fup",
+    "model_flat")) +
+  settings_optimx(method = c("bobyqa"))
+
 new_pk <- do_data_info(new_pk)
@@
 new_pk <- do_prefit(new_pk)
-
-new_pk$prefit$par_DF %>% arrange(Chemical, Species) %>% filter(param_name == "Clint") %>%
+gc()
+
+unique(new_pk$prefit$par_DF$param_name)
+
+new_pk$prefit$par_DF %>%
+  arrange(Chemical, Species) %>%
+  filter(param_name == "Fup") %>%
   View()
 
-new_pk <- do_fit(new_pk) # For troubleshooting only
-
-new_pk <- do_fit(new_pk, n_cores = 12)
-
-# Multidplyr error because of forgotten browser() call within log_likelihood
-new_pk$fit %>% unnest(fit) %>% select(!starts_with("sigma_")) %>% View()
-
-saveRDS(new_pk, "data-raw/someCVT_wHTTK_reform_JOINT.rds")
+new_pk <- do_fit(new_pk, n_cores = 14)
+gc()
+
+new_pk$fit %>%
+  View()
+
+saveRDS(new_pk, "data-raw/ratCVT_wHTTK_reformulated.rds")
+```
+
+```{r begin_analysis}
+new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
 
@@
 eval_tkstats(new_pk, finite_only = FALSE) %>% View()
-get_winning_model(new_pk) %>% View("winning_model")
-
-AIC(new_pk) %>% filter(method %in% "L-BFGS-B") %>% arrange(Chemical, Species) %>%
-  View()
-
-pl2comp <- plot(new_pk, use_scale_conc = FALSE,
-           n_interp = 10)
+get_winning_model(new_pk) %>%
+  count(model)
+
+AIC(new_pk) %>%
+  arrange(Chemical, Species) %>%
+  group_by(model, method) %>% 
+  count(is.finite(AIC))
+
+pl2comp <- plot(new_pk,
+                use_scale_conc = FALSE,
+                n_interp = 12
+)
 
 pl2comp %>%
-  filter(Chemical %in% "DTXSID1043881") %>% pull(final_plot) %>% .[[1]]
+  filter(Chemical %in% "DTXSID4020533") %>%
+  pull(final_plot)
+
+rel_ll <- AIC(new_pk) %>% 
+  filter(is.finite(AIC)) %>% 
+  dplyr::select(-c(log_likelihood, npar)) %>% 
+  pivot_wider(names_from = model,
+              values_from = AIC) %>% 
+  rowwise() %>% 
+  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(across(starts_with("model_"), \(x) {
+    signif(exp((minAIC - x)/2) * 100, 4)
+  }))
+
+# Test whether the flat model has lowest relative likelihood
+rel_ll %>%
+  dplyr::select(-c(Species, method))
+# We can inspect this visually
+rel_ll %>% arrange(desc(model_flat)) %>% head()
+rel_ll %>%
+  dplyr::select(-c(Species, method)) %>% 
+  rowwise() %>% 
+  mutate(across(contains("_1comp"),
+                \(x) {
+                  ifelse(
+                    x < model_flat | x < 1,
+                    NA_real_,
+                    x
+                  )
+                })) %>% 
+  filter(!if_all(contains("_1comp_"), is.na)) %>%
+  clipr::write_clip()
+
+rel_ll %>%
+  rowwise() %>% 
+  mutate(across(contains("_1comp"),
+                \(x) {
+                  ifelse(
+                    x < model_flat | x < 1,
+                    NA_real_,
+                    x
+                  )
+                })) %>% 
+  drop_na(model_1comp_fup)
+
+new_pk$fit %>%
+  filter(param_name %in% "Fup",
+         model %in% "model_1comp_fup") %>%
+  ggplot(aes(x = estimate, y = start)) +
+  geom_point(size = 2) +
+  theme_bw() +
+  coord_equal(xlim = c(0,1), ylim = c(0,1),
+              expand = TRUE)
+
+new_pk$fit %>%
+  filter(param_name %in% "Fup",
+         model %in% "model_1comp_fup") %>%
+  distinct(Chemical, Species, method, model,
+           param_name, estimate, start) %>%
+  mutate(direction = ifelse(abs(estimate - start) < 0.1,
+                            "similar (less than 10% difference)",
+                            ifelse(estimate > start,
+                                   "increase",
+                                   "decrease"))) %>%
+  pivot_longer(cols = c(estimate, start),
+               names_to = "parameterization",
+               values_to = "value") %>%
+  mutate(parameterization = factor(parameterization,
+                                   levels = c("start", "estimate"))) %>%
+  ggplot(aes(x = parameterization, y = value)) +
+  geom_point() +
+  geom_line(aes(group = Chemical)) +
+  facet_grid(cols = vars(direction)) +
+  labs(title = "Optimization of fraction unbound in plasma") +
+  theme_bw()
+
+ggsave(filename = paste0(
+  Sys.getenv("FIG_DIR"),
+  format(today(), '%d%b%Y'),
+  "fup_optimization_generalFits"
+))
+
 ```
@@
 ```{r kelim-questions}
-
 # Original data, filtered for common_chems
@@
 my_kelim_prefit <- my_pk$prefit$par_DF %>%
-  filter(param_name %in% "kelim",
-         Chemical %in% common_chems_dawson) %>%
+  filter(
+    param_name %in% "kelim",
+    Chemical %in% common_chems_dawson
+  ) %>%
   distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)
@@
       distinct(Chemical, Species, param_name, start) %>%
-  rename(init_nonrestrictive = "start"))
+      rename(init_nonrestrictive = "start")
+  )
 
@@
   facet_grid(rows = vars(Species), scales = "free", space = "free") +
-  scale_color_manual(name = "kelim",
+  scale_color_manual(
+    name = "kelim",
     breaks = c("Original Optimized", "Restrictive", "Non-restrictive"),
-                     values = c("Original Optimized" = "skyblue4", 
+    values = c(
+      "Original Optimized" = "skyblue4",
       "Restrictive" = "orange2",
-                                "Non-restrictive" = "green4")) +
-  scale_shape_manual(name = "",
-                     values = 4) +
+      "Non-restrictive" = "green4"
+    )
+  ) +
+  scale_shape_manual(
+    name = "",
+    values = 4
+  ) +
   coord_flip() +
   scale_y_log10(labels = scales::label_math(format = log10)) +
-  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
+  theme(
+    panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
     panel.background = element_blank(),
@@
     axis.text.y = element_blank(),
-        strip.text.y = element_text(angle = 0))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare_2024_0329.png"),
+    strip.text.y = element_text(angle = 0)
+  )
+
+ggsave(
+  filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare_2024_0329.png"),
   height = 11,
-       width = 8.5)
-
+  width = 8.5
+)
 ```
@@
 pl <- plot(new_pk, n_interp = 12, use_scale_conc = FALSE)
-pdf(file = paste0(Sys.getenv("FIG_DIR"),
-              "AllFits_nonDoseNorm_newPK_reParametizedModels_2024_0412.pdf"),
-    height = 6, width = 10)
-for (i in 1:nrow(pl)) {
+pdf(
+  file = paste0(
+    Sys.getenv("FIG_DIR"),
+    "AllFits_nonDoseNorm_newPK_reParametizedModels_2024_0412.pdf"
+  ),
+  height = 6, width = 10
+)
+for (i in seq_len(nrow(pl))) {
   print(pl$final_plot[[i]])
@@
 dev.off()
-
 ```
@@
   filter(str_detect(model, "rest")) %>%
-  select(Chemical, Species, Media, Route, 
+  select(
+    Chemical, Species, Media, Route,
     model, method,
-         CLtot.tkstats, CLtot.nca) %>%
+    CLtot.tkstats, CLtot.nca
+  ) %>%
   filter(!is.na(CLtot.tkstats)) %>%
@@
                                         "Restrictive",
-                                       "optimized kelim"))) %>%
+                                        "optimized kelim"
+                                 )
+  )) %>%
   rowwise() %>%
-  mutate(CLtot.httk_rest = calc_total_clearance(dtxsid = Chemical,
-                                           restrictive.clearance = TRUE),
-         CLtot.httk_nonrest = calc_total_clearance(dtxsid = Chemical,
-                                           restrictive.clearance = FALSE))
+  mutate(
+    CLtot.httk_rest = calc_total_clearance(
+      dtxsid = Chemical,
+      restrictive.clearance = TRUE
+    ),
+    CLtot.httk_nonrest = calc_total_clearance(
+      dtxsid = Chemical,
+      restrictive.clearance = FALSE
+    )
+  )
 
@@
   ggplot(aes(x = Chemical)) +
-  geom_point(aes(y = CLtot.httk_rest),shape = 19, size = 2, color = "green4") +
-  geom_point(aes(y = CLtot.httk_nonrest),shape = 19, size = 2, color = "orange2") +
-  geom_point(aes(y = CLtot.tkstats, shape = Species), size = 3, color = "black", stroke = 1) +
+  geom_point(aes(y = CLtot.httk_rest),
+             shape = 19, size = 2, color = "green4") +
+  geom_point(aes(y = CLtot.httk_nonrest),
+             shape = 19, size = 2, color = "orange2") +
+  geom_point(aes(y = CLtot.tkstats,
+                 shape = Species), size = 3, color = "black", stroke = 1) +
   scale_y_log10(labels = scales::label_math(format = log10)) +
   geom_hline(yintercept = c(0.01, 0.1, 1, 10)) +
-  scale_shape_manual(values = c(0,1,2,5,6)) +
+  scale_shape_manual(values = c(0, 1, 2, 5, 6)) +
   coord_flip() +
-  facet_grid(rows = vars(clearance_type),
-             scales = "free", space = "free") +
-  labs(title = "CLtot for constant kelim \"best fits\" (empty)\nand httk calculations (filled)") +
+  facet_grid(
+    rows = vars(clearance_type),
+    scales = "free", space = "free"
+  ) +
+  labs(title = paste(
+    "CLtot for constant kelim \"best fits\" (empty)",
+    "and httk calculations (filled)",
+    sep = "\n"
+  )) +
   theme_bw() +
-  theme(axis.line = element_line(linewidth = 1),
+  theme(
+    axis.line = element_line(linewidth = 1),
     axis.text = element_text(size = 12),
@@
     strip.background = element_blank(),
-        legend.position = "none")
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_backcompare_wDawson_2024_0416.png"),
+    legend.position = "none"
+  )
+
+ggsave(
+  filename = paste0(Sys.getenv("FIG_DIR"),
+                    "Cltot_backcompare_wDawson_2024_0416.png"),
   height = 8,
-       width = 9)
-
+  width = 9
+)
 ```
@@
   ungroup() %>%
-  filter(model %in% c("model_1comp", "model_2comp"),
-         Species %in% "rat") %>%
+  filter(
+    model %in% c("model_1comp", "model_2comp"),
+    Species %in% "rat"
+  ) %>%
   group_by(Chemical) %>%
@@
   ungroup() %>%
-  filter(model %in% c("model_1comp_rest", "model_2comp_rest"),
-         Species %in% "rat") %>%
+  filter(
+    model %in% c("model_1comp_rest", "model_2comp_rest"),
+    Species %in% "rat"
+  ) %>%
   group_by(Chemical) %>%
@@
   ungroup() %>%
-  filter(model %in% c("model_1comp_nonrest", "model_2comp_nonrest"),
-         Species %in% "rat") %>%
+  filter(
+    model %in% c("model_1comp_nonrest", "model_2comp_nonrest"),
+    Species %in% "rat"
+  ) %>%
   group_by(Chemical) %>%
@@
   distinct(Chemical, estimate, CLtot) %>%
-  pivot_wider(names_from = estimate,
-              values_from = CLtot) %>%
+  pivot_wider(
+    names_from = estimate,
+    values_from = CLtot
+  ) %>%
   rowwise() %>%
-  mutate(CLtot.httk_rest = calc_total_clearance(dtxsid = Chemical,
-                                           restrictive.clearance = TRUE),
-         CLtot.httk_nonrest = calc_total_clearance(dtxsid = Chemical,
-                                           restrictive.clearance = FALSE)) %>%
+  mutate(
+    CLtot.httk_rest = calc_total_clearance(
+      dtxsid = Chemical,
+      restrictive.clearance = TRUE
+    ),
+    CLtot.httk_nonrest = calc_total_clearance(
+      dtxsid = Chemical,
+      restrictive.clearance = FALSE
+    )
+  ) %>%
   ungroup() %>%
-  mutate(A_rest = log(nonConst) - log(CLtot.httk_rest),
+  mutate(
+    A_rest = log(nonConst) - log(CLtot.httk_rest),
     A_nonrest = log(nonConst) - log(CLtot.httk_nonrest),
@@
     C_rest = log(nonRest) - log(CLtot.httk_rest),
-         C_nonrest = log(nonRest) - log(CLtot.httk_nonrest)) %>%
+    C_nonrest = log(nonRest) - log(CLtot.httk_nonrest)
+  ) %>%
   select(Chemical, A_rest:C_nonrest) -> df_valcomp
@@
 
-hclust(d = as.dist((1+val_cormat)/2), method = "average") %>% plot()
-
-hclust(d = as.dist((1+val_cormat)/2), method = "average") -> val_hclust
+hclust(d = as.dist((1 + val_cormat) / 2), method = "average") %>% plot()
+
+hclust(d = as.dist((1 + val_cormat) / 2), method = "average") -> val_hclust
 
@@
 
-#reorder the Chemical names prior to plotting
+# reorder the Chemical names prior to plotting
 df_valcomp %>%
-  mutate(Chemical = factor(x = Chemical,
-                           levels = val_hclust$labels[val_hclust$order])) %>%
-  pivot_longer(cols = A_rest:C_nonrest,
-               names_to = "comparison", values_to = "logres") %>%
-  mutate(comparison = case_when(
+  mutate(Chemical = factor(
+    x = Chemical,
+    levels = val_hclust$labels[val_hclust$order]
+  )) %>%
+  pivot_longer(
+    cols = A_rest:C_nonrest,
+    names_to = "comparison", values_to = "logres"
+  ) %>%
+  mutate(
+    comparison = case_when(
       comparison == "A_nonrest" ~ "free kelim vs httk nonrestrictive",
@@
     comparison = factor(comparison,
-  levels = c("free kelim vs httk restrictive",
+                        levels = c(
+                          "free kelim vs httk restrictive",
                           "free kelim vs httk nonrestrictive",
@@
                           "nonrestrictive kelim vs httk restrictive",
-             "restrictive kelim vs httk nonrestrictive"))) %>%
+                          "restrictive kelim vs httk nonrestrictive"
+                        )
+    )
+  ) %>%
   ggplot(aes(x = comparison, y = Chemical, fill = logres)) +
   geom_tile() +
-  scale_fill_gradient2(mid = "grey5", high = "orange", low = "green3",
+  scale_fill_gradient2(
+    mid = "grey5", high = "orange", low = "green3",
     name = "Total Clearance\nlog10-scale difference",
     limits = c(-4, 4),
-                       oob = scales::oob_squish) +
+    oob = scales::oob_squish
+  ) +
   coord_fixed(ratio = 0.3) +
   theme_bw() +
-  theme(axis.text.x = element_text(hjust = 1, angle = 45),
+  theme(
+    axis.text.x = element_text(hjust = 1, angle = 45),
     axis.ticks.y = element_blank(),
     panel.grid = element_blank(),
-        axis.title.x = element_blank())
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_compare_heatmap_2024_0409.png"),
+    axis.title.x = element_blank()
+  )
+
+ggsave(
+  filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_compare_heatmap_2024_0409.png"),
   height = 14,
-       width = 8)
-
+  width = 8
+)
 ```
@@
 old_AIC <- AIC(my_pk) %>%
-  filter(Chemical %in% "DTXSID3022405",
-         Species %in% "mouse")
+  filter(
+    Chemical %in% "DTXSID3022405",
+    Species %in% "mouse"
+  )
 
 new_AIC <- new_AIC %>%
-  filter(Chemical %in% "DTXSID3022405",
-         Species %in% "mouse")
-
-plot(new_pk, model = c("model_2comp",
-                       "model_1comp", "model_1comp_nonrest"),
-     use_scale_conc = FALSE) %>%
-  filter(Chemical %in% "DTXSID3022405",
-         Species %in% "mouse") %>%
-  pull(final_plot) %>% .[[1]]
+  filter(
+    Chemical %in% "DTXSID3022405",
+    Species %in% "mouse"
+  )
+
+plot(new_pk,
+     model = c(
+       "model_2comp",
+       "model_1comp", "model_1comp_nonrest"
+     ),
+     use_scale_conc = FALSE
+) %>%
+  filter(
+    Chemical %in% "DTXSID3022405",
+    Species %in% "mouse"
+  ) %>%
+  pull(final_plot) %>%
+  .[[1]]
 
 old_rsquared <- rmse(my_pk) %>%
-  filter(Chemical %in% "DTXSID3022405",
-         Species %in% "mouse")
+  filter(
+    Chemical %in% "DTXSID3022405",
+    Species %in% "mouse"
+  )
 
@@
   left_join(new_resid,
-            by = join_by(Chemical, Species, model)) %>%
+            by = join_by(Chemical, Species, model)
+  ) %>%
   rename("mod_residuals" = "Residuals") %>%
-  select(Chemical, Species, Route, Media, Time, Detect, exclude,
-         model, mod_residuals)
+  select(
+    Chemical, Species, Route, Media, Time, Detect, exclude,
+    model, mod_residuals
+  )
 
@@
   left_join(new_resid,
-            by = join_by(Chemical, Species, "winmodel" == "model")) %>%
+            by = join_by(Chemical, Species, "winmodel" == "model")
+  ) %>%
   rename("wm_residuals" = "Residuals") %>%
-  select(Chemical, Species, Route, Media, Time, Detect, exclude,
-         winmodel, wm_residuals)
+  select(
+    Chemical, Species, Route, Media, Time, Detect, exclude,
+    winmodel, wm_residuals
+  )
 sum_red <- new_resid %>%
   group_by(Chemical, Species, model) %>%
-  summarize(MSE = sum(Residuals^2)/n())
-
-cor_mod <- mod_red %>% inner_join(wm_red) %>%
+  summarize(MSE = sum(Residuals^2) / n())
+
+cor_mod <- mod_red %>%
+  inner_join(wm_red) %>%
   select(Chemical, Species, model, mod_residuals, winmodel, wm_residuals) %>%
@@
 
-my_pl_1comp <- plot(new_pk, n_interp = 11, use_scale_conc = FALSE,
-                    model = c("model_1comp",
+my_pl_1comp <- plot(new_pk,
+                    n_interp = 11, use_scale_conc = FALSE,
+                    model = c(
+                      "model_1comp",
                       "model_1comp_rest",
-                              "model_1comp_nonrest"))
-
-my_pl_2comp <- plot(new_pk, n_interp = 11, use_scale_conc = FALSE,
-                    model = c("model_2comp",
+                      "model_1comp_nonrest"
+                    )
+)
+
+my_pl_2comp <- plot(new_pk,
+                    n_interp = 11, use_scale_conc = FALSE,
+                    model = c(
+                      "model_2comp",
                       "model_2comp_rest",
-                              "model_2comp_nonrest"))
+                      "model_2comp_nonrest"
+                    )
+)
 
@@
                           "Taking win_model",
-                          "Taking low RMSE model")) %>% na.omit() %>%
+                          "Taking low RMSE model"
+  )) %>%
+  na.omit() %>%
   ggplot() +
@@
                           "Taking win_model",
-                          "Taking low RMSE model")) %>% na.omit() %>%
+                          "Taking low RMSE model"
+  )) %>%
+  na.omit() %>%
   ggplot() +
   geom_histogram(aes(x = cor_mods, fill = model),
-                 binwidth = 0.05) +
+                 binwidth = 0.05
+  ) +
   facet_grid(rows = vars(winmodel)) +
@@
   theme(strip.text.y = element_text(angle = 0)) +
-  labs(x = "Correlation of Residuals",
-       fill = "model by grouped RMSE")
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "winModel_correlations_changes",
-                         "_2024_Apr_16.png"),
+  labs(
+    x = "Correlation of Residuals",
+    fill = "model by grouped RMSE"
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"), "winModel_correlations_changes",
+    "_2024_Apr_16.png"
+  ),
   height = 6,
-       width = 8)
+  width = 8
+)
 
 # Try oxybenzone fitting without dose-norm
-minimal_pk <- pk(data = cvt %>%
+minimal_pk <- pk(
+  data = cvt %>%
     filter(analyte_dtxsid %in% "DTXSID3022405"),
@@
     LOQ = loq
-                 ))
+  )
+)
 new_pk <- minimal_pk +
   facet_data(vars(Chemical, Species)) +
-  settings_preprocess(keep_data_original = TRUE,
-                      suppress.messages = FALSE) +
+  settings_preprocess(
+    keep_data_original = TRUE,
+    suppress.messages = FALSE
+  ) +
   settings_optimx(method = c("L-BFGS-B")) +
@@
   stat_error_model(error_group = vars(Chemical, Species, Reference)) +
-  stat_model(model = c("model_flat", "model_1comp", "model_2comp",
+  stat_model(model = c(
+    "model_flat", "model_1comp", "model_2comp",
     "model_1comp_rest", "model_1comp_nonrest",
-                       "model_2comp_rest", "model_2comp_nonrest"))
+    "model_2comp_rest", "model_2comp_nonrest"
+  ))
 
@@
 ```{r categorization}
-
 grouped_wm <- new_AIC %>%
@@
 grouped_tkstats %>%
-  select(Chemical, Species, Reference,
+  select(
+    Chemical, Species, Reference,
     Route, Media, model_type,
-         CLtot) %>%
+    CLtot
+  ) %>%
   pivot_wider(names_from = model_type, values_from = CLtot) %>%
-  mutate(low_invivo_CL = ifelse(
-    Free_kelim < Nonrestrictive/2 | Free_kelim < Restrictive/2,
-    TRUE, FALSE),
+  mutate(
+    low_invivo_CL = ifelse(
+      Free_kelim < Nonrestrictive / 2 | Free_kelim < Restrictive / 2,
+      TRUE, FALSE
+    ),
     high_extra_hepCL = ifelse(
-      Free_kelim > 1.5*Nonrestrictive | Free_kelim > 1.5*Restrictive,
-      TRUE, FALSE),
+      Free_kelim > 1.5 * Nonrestrictive | Free_kelim > 1.5 * Restrictive,
+      TRUE, FALSE
+    ),
     rest_metabol = ifelse(
-      Free_kelim > Restrictive/2 & Free_kelim < 1.5*Nonrestrictive,
-      TRUE, FALSE),
-    combo_cat = paste0(low_invivo_CL + 0,
+      Free_kelim > Restrictive / 2 & Free_kelim < 1.5 * Nonrestrictive,
+      TRUE, FALSE
+    ),
+    combo_cat = paste0(
+      low_invivo_CL + 0,
       high_extra_hepCL + 0,
-                       rest_metabol + 0)) %>%
+      rest_metabol + 0
+    )
+  ) %>%
   count(combo_cat)
@@
   View()
-
 ```
@@
               mutate(model = paste0("start_", model)) %>%
-              pivot_wider(names_from = model,
-                          values_from = start)) %>% View("Clearance")
+              pivot_wider(
+                names_from = model,
+                values_from = start
+              )) %>%
+  View("Clearance")
 
@@
   left_join(coef(my_pk)) %>%
-  left_join(rsq(my_pk)) %>% distinct()
-my_tkstats %>% select(-coefs_vector) %>% clipr::write_clip()
-#Send the R2 too.
+  left_join(rsq(my_pk)) %>%
+  distinct()
+my_tkstats %>%
+  select(-coefs_vector) %>%
+  clipr::write_clip()
+# Send the R2 too.
 

### 2024-11-04 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Updated object 'cvt' and related documentation. invivPK_loq_units were not ug/mL as intended. Added description of each column of the data. Added description for fup-optimizing clearance aware 1-compartment model in data.R

@@
     invivPK_loq_units %in% c("ug/L", "ng/mL", "ng/g"),
-    invivPK_loq * 1E-3, invivPK_loq)) # mg/L and ug/mL are same scale
+    invivPK_loq * 1E-3, invivPK_loq)) %>% 
+  mutate(ivivPK_loq_units = "ug/mL") # mg/L and ug/mL are same scale
 # Normalize conc_sd and conc units manually

### 2024-11-05 R/conc_scale_use.R
Minor code style update using suggestions from `lintr` for improved readability. Minor typo fixes to the manuscript vignette.

@@ -27,15 +27,21 @@ conc_scale_use <- function(use_scale_conc,
       log10_trans <- FALSE
     }}else{
       if(!is.list(use_scale_conc)){
-        stop("use_scale_conc must be either TRUE, FALSE, or a list like `list(dose_norm = TRUE/FALSE, log10_trans = TRUE/FALSE)`")
+        stop("use_scale_conc must be either TRUE, FALSE, ",
+             "or a list like `list(dose_norm = TRUE/FALSE, ",
+             "log10_trans = TRUE/FALSE)`")
       }
 
       if(!all(c("dose_norm", "log10_trans") %in% names(use_scale_conc))){
-        stop("use_scale_conc must be either TRUE, FALSE, or a list like `list(dose_norm = TRUE/FALSE, log10_trans = TRUE/FALSE)`")
+        stop("use_scale_conc must be either TRUE, FALSE, ",
+             "or a list like `list(dose_norm = TRUE/FALSE, ",
+             "log10_trans = TRUE/FALSE)`")
       }
 
       if(!all(sapply(use_scale_conc[c("dose_norm", "log10_trans")], is.logical))){
-        stop("use_scale_conc must be either TRUE, FALSE, or a list like `list(dose_norm = TRUE/FALSE, log10_trans = TRUE/FALSE)`")
+        stop("use_scale_conc must be either TRUE, FALSE, ",
+             "or a list like `list(dose_norm = TRUE/FALSE, ",
+             "log10_trans = TRUE/FALSE)`")
       }
 
       dose_norm <- use_scale_conc$dose_norm

### 2024-11-05 R/fit_group.R

@@ -54,8 +54,11 @@ fit_group <- function(data,
     if (any(par_DF$optimize_param %in% FALSE & par_DF$use_param %in% TRUE)) {
       const_params <- par_DF[which(!par_DF$optimize_param & par_DF$use_param),
                              "start", drop = TRUE]
-      names(const_params) <- par_DF[which(!par_DF$optimize_param & par_DF$use_param),
-                                    "param_name", drop = TRUE]
+      names(const_params) <- par_DF[
+        which(!par_DF$optimize_param & par_DF$use_param),
+        "param_name",
+        drop = TRUE
+      ]
     } else {
       const_params <- NULL
     }
@@ -114,7 +117,7 @@ fit_group <- function(data,
                           "xtime")
 
           tmp <- data.frame(as.list(tmp)) %>%
-            dplyr::slice(rep(1:dplyr::n(),
+            dplyr::slice(rep(seq_len(dplyr::n()),
                              each = length(method)))
 
           rownames(tmp) <- method
@@ -149,7 +152,7 @@ fit_group <- function(data,
                     "kkt1", "kkt2",
                     "xtime")
     tmp <- data.frame(as.list(tmp)) %>%
-      dplyr::slice(rep(1:dplyr::n(),
+      dplyr::slice(rep(seq_len(dplyr::n()),
                        each = length(method)))
     rownames(tmp) <- method
     tmp$method <- rownames(tmp)
@@ -157,7 +160,6 @@ fit_group <- function(data,
     attr(tmp, "maximize") <- FALSE
     attr(tmp, "npar") <- length(opt_params)
     attr(tmp, "follow.on") <- FALSE
-    # method <- settings_optimx$method
     details <- as.data.frame(
       cbind(method = as.list(method),
             ngatend = as.list(rep(NA_real_, length(method))),

### 2024-11-05 R/pk_methods_nca.R

@@ -74,8 +74,7 @@ nca.pk <- function(obj,
              grp_vars))){
       stop(paste0("When dose_norm == TRUE, nca_group must include all of Route, Media.\n",
                   "nca_group is: ",
-                  paste(grp_vars,
-                        collapse = ", ")
+                  toString(grp_vars)
       ))
     }
   }else{
@@ -87,8 +86,7 @@ nca.pk <- function(obj,
              grp_vars))){
       stop(paste0("When dose_norm == FALSE, nca_group must include all of Dose, Route, Media.\n",
                  "nca_group is: ",
-                 paste(grp_vars,
-                       collapse = ", ")
+                 toString(grp_vars)
       ))
     }
   }
@@ -153,7 +151,7 @@ nca.pk <- function(obj,
                                          "dose-normalized",
                                          "non-dose-normalized"),
                                   "NCA by the following grouping:",
-                  paste(grp_vars, collapse = ", ")
+                  toString(grp_vars)
                   )
             )
   }

### 2024-11-05 R/calc_rsq.R
Minor code style update using suggestions from `lintr` for improved readability. Minor typo fixes to the manuscript vignette.

@@ -156,7 +156,7 @@ calc_rsq <- function(pred,
     2 * x_bar * sum(n_subj * obs) +
     sum(n_subj) * x_bar^2)
   #Calculate second denominator term of Pearson correlation coefficient
-  r_denom_2 <- sqrt(pmax(0,sum(n_subj * pred^2) -
+  r_denom_2 <- sqrt(pmax(0, sum(n_subj * pred^2) -
                       2 * pred_bar * sum(n_subj * pred) +
                       sum(n_subj) * pred_bar^2))
 

### 2024-11-05 R/check_params_2comp.R

@@ -24,8 +24,6 @@ check_params_2comp <- function(params,
 
   msg <- "Parameters OK"
 
-  # params <- fill_params_2comp(params)
-
   #check for any missing parameters
   #required params for oral dose
   if(any(route %in% "oral")){
@@ -38,7 +36,7 @@ check_params_2comp <- function(params,
     if(length(missing_params)>0){
       msg <- (paste("Error: For 2-compartment oral model,",
                  "missing parameters:",
-                 paste(missing_params, collapse = ", ")))
+                 toString(missing_params)))
     }
   }
 
@@ -52,7 +50,7 @@ check_params_2comp <- function(params,
     if(length(missing_params)>0){
       msg <- (paste("Error: For 2-compartment IV model,",
                  "missing parameters:",
-                 paste(missing_params, collapse = ", ")))
+                 toString(missing_params)))
     }
   }
 

### 2024-11-05 R/get_starts_flat.R

@@ -132,8 +132,8 @@ get_starts_flat <- function(data,
   if (has_po %in% TRUE) {
     if (has_po_plasma %in% TRUE) {
       #get Fgutabs_Vdist for plasma
-      Fgutabs_Vdist_plasma_log10 <- with(subset(podat,Media %in% "plasma"),
-                                         mean(log10(Conc/Dose),na.rm = TRUE))
+      Fgutabs_Vdist_plasma_log10 <- with(subset(podat, Media %in% "plasma"),
+                                         mean(log10(Conc/Dose), na.rm = TRUE))
     }
     if (has_po_blood %in% TRUE) {
       #get Fgutabs_Vdist for blood

### 2024-11-05 R/pk_methods_coef_sd.R

@@ -141,9 +141,10 @@ coef_sd.pk <- function(obj,
       tryCatch(diag(solve(x))^(1/2) %>% as.numeric(),
                error = function(err){
                  if (!suppress.messages) {
-                   message(paste0("Hessian can't be inverted, ",
-                                  "using pseudovariance matrix ",
-                                  "to estimate parameter uncertainty."))
+                   message("Hessian can't be inverted, ",
+                           "using pseudovariance matrix ",
+                           "to estimate parameter uncertainty."
+                   )
                  }
                  # pseudovariance matrix
                  # see http://gking.harvard.edu/files/help.pdf
@@ -152,8 +153,9 @@ coef_sd.pk <- function(obj,
                              pivot = TRUE))^(1/2)),
                    error = function(err){
                      if (!suppress.messages) {
-                       message(paste0("Pseudovariance matrix failed,",
-                                      " returning NAs"))
+                       message("Pseudovariance matrix failed, ",
+                               "returning NAs"
+                               )
                      }
                      rep(NA_real_, nrow(x))
                    })
@@ -170,14 +172,17 @@ coef_sd.pk <- function(obj,
           suppressWarnings(diag(chol(MASS::ginv(x),
                                      pivot = TRUE))^(1/2)),
           error = function(err){
-            paste0("Pseudovariance matrix failed,",
-                   " returning NAs")
+            message("Pseudovariance matrix failed, ",
+                    "returning NAs")
           })
-        paste0("Hessian can't be inverted, ",
-               "using pseudovariance matrix ",
-               "to estimate parameter uncertainty.")
-      })
-    })))
+        message("Hessian can't be inverted, ",
+                "using pseudovariance matrix ",
+                "to estimate parameter uncertainty.")
+      }
+      )
+    }
+    ))
+  )
 
   # Limit data.frame columns to those that unique identify needed values
   newdata <- newdata %>%

### 2024-11-05 R/pk_methods_get_data_group.R
Bug fixes and documentation updates. Passing R CMD check.

@@ -8,9 +8,11 @@ get_data_group.pk <- function(obj, ...){
   out <- rlang::parse_expr(
     paste0("vars(",
            paste(
-             toString(obj$data_group,
-                      rlang::as_label),
-             ")"
+             toString(
+               sapply(obj$data_group,
+                      rlang::as_label)
+             ),
+           ")"
            )
     )
   )

### 2024-11-05 data-raw/RestrictiveClearance_comparison.Rmd
Adding new data-raw/ files prior to merge

@@
 httk::load_dawson2021()
+source("data-raw/RC_comparison_bkgd.R")
 ```
@@
 
-```{r dawson}
-# try dawson
-# can also be run as background job (see data-raw/RC_comparison_bkgd.R)
-
-human_chems_gas <- get_cheminfo(info = "DTXSID",
-                                species = "Human",
-                                model = "gas_pbtk",
-                                median.only = TRUE,
-                                physchem.exclude = TRUE,
-                                suppress.messages = TRUE)
-
-common_chems_dawson <- cvt %>%
-  filter(species %in% c("human", "rat", "mouse"),
-         analyte_dtxsid %in% human_chems_gas) %>%
-  pull(analyte_dtxsid) %>%
-  unique()
-
-rat_chems_gas <- get_cheminfo(info = "DTXSID",
-                                species = "Rat",
-                                model = "gas_pbtk",
-                                median.only = TRUE,
-                                physchem.exclude = TRUE,
-                                suppress.messages = TRUE)
-
-common_chems_rat <- cvt %>%
-  filter(species %in% "rat",
-         analyte_dtxsid %in% rat_chems_gas) %>%
-  pull(analyte_dtxsid) %>%
-  unique()
-
-remove(list = c("human_chems_gas", "rat_chems_gas"))
-
-# How many are in the previous invivoPKfit analysis?
-length(common_chems_dawson %in% unique(my_pk$fit %>%
-                                         filter(convcode == 0) %>%
-                                         pull(Chemical)))
-
-test_parameterization <- function(dtxsid, species = "Human") {
-  is(
-    tryCatch(
-      {
-        parameterize_gas_pbtk(dtxsid = dtxsid,
-                              species = species,
-                              supress.messages = TRUE)  
-      }, error = function(e) {
-        NULL
-      }
-    ),
-    "list"
-  )
-}
-
-parameterize_all_gas <- function(dtxsid, species = "Human") {
-  # Note that Clint is given in uL/min, which must be converted to L/h
-  params <- httk::parameterize_gas_pbtk(dtxsid = dtxsid,
-                                        species = species,
-                                        default.to.human = FALSE)
-  paramdf <- data.frame(Chemical = dtxsid, Species = tolower(species),
-                        Qliverf = params$Qliverf,
-                        Funbound.plasma = params$Funbound.plasma,
-                        Clint = params$Clint*60/1e+6)
-  paramdf$fupClint <- paramdf$Funbound.plasma * paramdf$Clint
-  paramdf$ExtEff <- paramdf$fupClint/(paramdf$Qliverf + paramdf$fupClint)
-  paramdf$Q_Clint <- paramdf$Qliverf/paramdf$Clint
-  return(paramdf)
-}
-
-if (all(vapply(common_chems_rat, test_parameterization,
-               FUN.VALUE = logical(1), species = "Rat"))) {
-  rat_params <- do.call(rbind, lapply(common_chems_rat,
-                                      parameterize_all_gas,
-                                      species = "Rat"))
-}
-
-if (all(vapply(common_chems_dawson, test_parameterization,
-               FUN.VALUE = logical(1), species = "Human"))) {
-  human_params <- do.call(rbind, lapply(common_chems_dawson,
-                                        parameterize_all_gas,
-                                        species = "Human"))
-}
-```
-
 Next I need to get the clearances using the `calc_total_clearance(dtxsid, restrictive.clearance)`
 function from httk. Also need the clearances from invivoPKfit's winning models.
-
-```{r get_clearances}
-params_dtxsid <- function(dtxsid, species) {
-  httk::parameterize_gas_pbtk(dtxsid = dtxsid,
-                              species = species,
-                              default.to.human = FALSE,
-                              suppress.messages = TRUE)
-}
-
-make_clearance_df <- function(dtxsid, species) {
-  tmp_df <- data.frame(Chemical = dtxsid)
-  tmp_params <- lapply(dtxsid, params_dtxsid, species = species)
-  tmp_df$restrict_cl <- vapply(tmp_params,
-                               \(x) {
-                                 calc_total_clearance(
-                                   parameters = x,species = species,
-                                   suppress.messages = TRUE,
-                                   restrictive.clearance = TRUE
-                                 )
-                               },
-                               FUN.VALUE = double(1L)
-  )
-  tmp_df$nonrestrict_cl <- vapply(tmp_params,
-                                  \(x) {
-                                    calc_total_clearance(
-                                      parameters = x,species = species,
-                                      suppress.messages = TRUE,
-                                      restrictive.clearance = FALSE
-                                    )
-                                  },
-                                  FUN.VALUE = double(1L)
-  )
-  return(tmp_df)
-}
-clearance_df <- make_clearance_df(dtxsid = common_chems_rat, species = "rat")
-```
 

### 2024-11-20 data-raw/RestrictiveClearance_comparison.Rmd

@@
 devtools::load_all()
-library(httk)
 library(tidyverse)
 my_pk <- readRDS("data-raw/all_cvt_pk.rds")
-httk::load_dawson2021()
-source("data-raw/RC_comparison_bkgd.R")
+source("data-raw/RC_comparison_bkgd.R") # httk loaded here
 ```
@@
     Species %in% "rat",
-    Chemical %in% common_chems_rat,
+    Chemical %in% rat_pars_rat$clearance_df$Chemical,
     !is.na(CLtot.tkstats), !is.na(CLtot.nca)
@@
 # Combine these two
-combined_clearance_df <- my_tkstats %>% inner_join(clearance_df)
+combined_clearance_df <- my_tkstats %>% inner_join(rat_pars_rat$clearance_df)
 ```
@@
 combined_clearance_df %>%
-  mutate(AD_restrictive = abs(CLtot.tkstats - restrict_cl),
-         AD_nonrestrictive = abs(CLtot.tkstats - nonrestrict_cl),
+  mutate(AD_restrictive = abs(CLtot.tkstats - restrictive_clearance),
+         AD_nonrestrictive = abs(CLtot.tkstats - nonrestrictive_clearance),
          rough_determination = ifelse(
            min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
-             CLtot.tkstats < nonrestrict_cl,
+             CLtot.tkstats < nonrestrictive_clearance,
            "Restrictive", "Possibly non-Restrictive"
@@
   dplyr::distinct(Chemical, rough_determination) %>%
-  View()
+  tally()
 
@@
         "CLtot.tkstats", "CLtot.nca_mean",
-        "nonrestrict_cl", "restrict_cl"
+        "nonrestrictive_clearance", "restrictive_clearance"
       )
@@
     breaks = c(
-      "nonrestrict_cl", "CLtot.tkstats",
+      "nonrestrictive_clearance", "CLtot.tkstats",
       "CLtot.nca_mean",
-      "restrict_cl"
+      "restrictive_clearance"
     ),

### 2024-12-19 data-raw/RestrictiveClearance_comparison.Rmd
Added uncertainty estimation section to data-raw/RestrictiveClearance_comparison.Rmd and updated a few of the visualizations.

@@
 ```{r library_loading}
+today <- format(Sys.Date(), "%d%b%Y")
 devtools::load_all()
 library(tidyverse)
+library(ctxR)
 my_pk <- readRDS("data-raw/all_cvt_pk.rds")
@@
 be _restrictively cleared_, whereas those that increase Fup during maximum
-likelihood estimation are _possibly non-restrictively clearaed_. 
+likelihood estimation are _possibly non-restrictively cleared_. 
 7. Other factors such as renal clearance may play a role in those cases.
@@
 chemicals (include Lipinski's Rule of 5 too).
+9. Implement a _slow_ PBPK model that optimizes $f_{up}$ and $CL_{int}$ under
+restrictive and non-restrictive clearance conditions. Test whether these have a
+substantial difference from initial values. Use `coef_sd()` to evaluate
+uncertainty of these parameter estimates for a larger share of chemicals.
+10. Compare the results of 9 with the putative/predicted clearance from 1-6.
 
@@
 ```{r clearance_viz}
-combined_clearance_df %>%
+clearance_guess <- combined_clearance_df %>%
   mutate(AD_restrictive = abs(CLtot.tkstats - restrictive_clearance),
@@
          )) %>% 
+  dplyr::ungroup()
+clearance_guess %>%
   dplyr::distinct(Chemical, rough_determination) %>%
+  group_by(rough_determination) %>%
   tally()
@@
     x = "Total Clearance",
-    y = "Chemical"
+    y = "Chemical",
+    title = "Comparing clearance estimates of chemicals with rat CvT data"
   ) +
@@
   filename = paste0(
-    Sys.getenv("FIG_DIR"),
+    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
+    today,
     "rat_tkClearance_comparison_httk_PBPK.png"
@@
     data = fup_df %>%
-      filter(Chemical %in% common_chems_rat),
+      filter(Chemical %in% rat_pars_rat$param_df$Chemical),
     # aes(y = after_stat(density)),
@@
 }
+
+httk_preds_rat <- get_httk_preds(rat_pars_rat, my_pk, species = "rat")
+
 ```
@@
 ```{r rat_data}
-my_data <- get_data(my_pk)
-
-rat_df <- my_data %>%
-  distinct(Chemical, Species, Dose, Route, Media, Time, Conc, exclude, Detect,
-           pLOQ) %>%
-  filter(Species %in% "rat", Media %in% "plasma",
-         Chemical %in% common_chems_rat, !exclude, Detect) %>%
-  mutate(iv_dose = (Route == "iv"),
-         Time = round(Time, 3)) %>%
-  group_by(Chemical, Species, Dose, Route, Media) %>%
-  filter(n() > 4) %>%
-  nest(.key = "CvT") %>%
-  rowwise() %>%
-  mutate(
-    httk_solved = list(
-      tryCatch(
-        expr = do.call(httk_bolus_gas_pbtk,
-                       list(
-                         dtxsid = Chemical,
-                         species = Species,
-                         dose = Dose,
-                         times = CvT$Time,
-                         iv.dose = CvT$iv_dose,
-                         LOQ = CvT$pLOQ
-                       )
-        ) %>%
-          inner_join(tibble(Time = CvT$Time, Conc = CvT$Conc, pLOQ = CvT$pLOQ),
-                     by = join_by(Time)),
-        error = function(err) {
-          message(paste0("Unable to get solution for ", Chemical))
-          print(err)
+rat_df <- httk_preds_rat %>%
+  left_join(predict(my_pk)) %>%
+  semi_join(get_winning_model(my_pk))
+
+rat_df <- ggplot(mapping = aes(
+    x = Conc_est,
+    y = httk_Preds,
+    color = interaction(Route, Media)
+  )) +
+  geom_point() +
+  geom_line(mapping = aes(
+    group = interaction(Chemical, Media, Route, Reference)
+  )
+  ) +
+  geom_abline(slope = 1, intercept = 0, color = "black") +
+  coord_equal(ylim = c(0, 200), xlim = c(0, 200))
+
+rat_plots <- rat_df %>%
+  distinct(Chemical, Species, Dose, Route, Media, Reference,
+           Time, httk_Preds, Conc, Conc_est, pLOQ) %>%
+  mutate(Dose = as.factor(Dose)) %>%
+  group_by(Chemical, Species, Route, Media, Reference) %>%
+  nest(.key = "data_pl")
+
+rat_plots <- rat_plots %>%
+  reframe(plots = purrr::map(data_pl,
+                             \(x) {
+                               cowplot::plot_grid(
+                               ggplot(data = x %>%
+                                        group_by(Time, Dose) %>%
+                                        mutate(meanConc = mean(Conc,
+                                                           na.rm = TRUE)) %>%
+                                        select(-Conc) %>% distinct() %>%
+                                        pivot_longer(cols = c(httk_Preds,
+                                                              meanConc,
+                                                              Conc_est),
+                                                     names_to = "Measurement",
+                                                     values_to = "Concentration"
+                                                     ), 
+                                      mapping = aes(
+                                        x = Time,
+                                        y = Concentration,
+                                        color = Measurement,
+                                        shape = Dose
+                                      )) +
+                                 geom_point() +
+                                 geom_line(
+                                   aes(group = interaction(Measurement, Dose))
+                                   ) +
+                                 theme_bw() +
+                                 labs(
+                                   title = paste(Chemical, Species),
+                                   subtitle = paste(Route, Media)
+                                 ),
+                               ggplot(data = x) +
+                                 geom_point(aes(x = Conc_est, httk_Preds,
+                                                shape = Dose)) +
+                                 geom_abline(slope = 1, intercept = 0,
+                                             linetype = "dashed") +
+                                 theme_bw()
+                               )
+                             })
+  )
+
+pdf(file = paste0(Sys.getenv("FIG_DIR"), "RC_comparison_CvTplots.pdf"),
+    onefile = TRUE,
+    height = 7,
+    width = 10,
+    bg = "white")
+
+for (i in 1L:NROW(rat_plots)) {
+  message("Now plotting: ", i)
+  print(rat_plots %>% pull(plots) %>% .[[i]])
 }
-      )
-    )
-  ) %>% filter(Chemical %in% clear_chem_levels)
+
+dev.off()
 
@@
 
-rat_df <- rat_df %>%
-  dplyr::select(Chemical, Species, Dose, Route, Media, httk_solved) %>%
-  unnest(cols = httk_solved)
-
 rat_out <- rat_df %>%
+  filter(Chemical %in% clear_chem_levels) %>%
+  group_by(Chemical, Species, Route, Reference, Media) %>%
   mutate(httk_Preds = ifelse(httk_Preds < pLOQ, pLOQ, httk_Preds)) %>% 
@@
               linetype = "dashed")
-
 rat_params %>%
@@
 minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% common_chems_rat,
+                   filter(analyte_dtxsid %in% rat_pars_rat$param_df$Chemical,
                           species %in% "rat"))
@@
 
-new_pk <- do_fit(new_pk, n_cores = 14)
+new_pk <- do_fit(new_pk, n_cores = 12)
 gc()
@@
 ```
+
+Here we begin the analysis by estimating the relative likelihood of
+"clearance aware" models. This provides an additional evaluation of the evidence
+that points towards a restrictive or non-restrictively cleared model.
 
@@
                 })) %>% 
-  drop_na(model_1comp_fup)
+  # drop_na(model_1comp_fup) %>%
+  filter(Chemical %in% clear_chem_levels) %>% View()
+  glimpse()
 
@@
                                    "decrease"))) %>%
+  filter(Chemical %in% clear_chem_levels, direction %in% "similar (less than 10% difference)")
   pivot_longer(cols = c(estimate, start),
@@
 ggsave(filename = paste0(
-  Sys.getenv("FIG_DIR"),
-  format(today(), '%d%b%Y'),
-  "fup_optimization_generalFits"
-))
+  Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
+  today, "fup_optimization_generalFits.png"),
+  height = 5, width = 7)
 
@@
 # Loading the new data
-new_pk <- readRDS("data-raw/someCVT_wHTTK_JOINT.rds")
 
@@
 
-## New reformulated models that estimate Clint!
+## New reformulated models that estimate Fup!
 
@@
 ```
+
+# Calculating uncertainty of parameter estimation
+
+Below I will use the `coef_sd` method to estimate standard deviation of
+the fraction unbound parameter and assess whether this may contribute
+to the uncertainty of 'declaration' of clearance for chemicals that have
+CvT data documented.
+
+```{r uncertainty_estimation}
+this_coefsd <- coef_sd(new_pk)
+
+this_coefsd %>% filter(param_name == "Clint", Chemical %in% clear_chem_levels) %>%
+  ggplot(aes(x = factor(Chemical, levels = clear_chem_levels), 
+             y = param_value,
+             color = model)) +
+  geom_point(alpha = 0.5) +
+  geom_linerange(aes(ymin = param_value-param_sd,
+                    ymax = param_value+param_sd),
+                 alpha = 0.5) +
+  theme_bw() +
+  coord_flip() +
+  scale_y_log10()
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
+    today,
+    "fup_sd_estimates.png"
+  ),
+  height = 8,
+  width = 8,
+  device = "png"
+)
+
+this_loglikelihood <- AIC(new_pk) %>%
+  filter(Chemical %in% clear_chem_levels) %>%
+  mutate(Chemical = factor(Chemical, levels = clear_chem_levels))
+
+this_loglikelihood %>%
+  ggplot(aes(x = model, y = Chemical, fill = log10(AIC))) +
+  geom_tile() +
+  scale_fill_viridis_c(option = "mako", direction = -1) +
+  coord_fixed() +
+  theme(axis.text.x = element_text(angle = 60, hjust = 1))
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
+    today,
+    "fup_AIC_heatmap.png"
+  ),
+  height = 10,
+  width = 4,
+  device = "png"
+)
+
+select_chem_info <- get_chem_info_batch(clear_chem_levels)
+
+select_chem_info %>%
+  filter(propertyId == "logkow-octanol-water") %>%
+  mutate(dtxsid = factor(dtxsid, levels = clear_chem_levels)) %>%
+  ggplot(aes(x = value, y = dtxsid, color = source)) +
+  geom_point() +
+  labs(title = "logKow") +
+  geom_vline(xintercept = 5)
+
+# Also check whether the Fup or CLint are at their respective extremes (1, 0)
+# If they are, it will be difficult to tell whether a chemical is cleared in a
+# particular way
+
+```
+
+# Slow PBPK model optimization of fup for more chemicals
+
+There may also be an opportunity to evaluate chemicals without _in vivo_ data
+by comparing them to those that do. Effectively, we can look at the uncertainty
+in the call between restrictive/non-restrictive and further look at estimates
+from PBPK models where $f_{up}$ is optimized and it is run through `solve_pbtk`.
+
+```{r slow_pbpk_optimizations}
+
+```
+
+```{r}
+sessionInfo()
+```

### 2024-12-23 R/pk_method_dispatch.R
Added `return` tag to default methods in pk_method_dispatch, resulting in \value in documentation files.

@@ -10,6 +10,7 @@
   #' do_preprocess default method
   #' @param obj an object
   #' @param ... Additional arguments currently not in use.
+  #' @return An error, when a non-pk object is used for the first argument.
   #' @export
   do_preprocess.default <- function(obj, ...) {
     stop("No 'do_preprocess' method exists for object of class",
@@ -29,6 +30,7 @@
   #' do_data_info default method
   #' @param obj an object
   #' @param ... Additional arguments currently not in use.
+  #' @return An error, when a non-pk object is used for the first argument.
   #' @export
   do_data_info.default <- function(obj, ...) {
     stop("No 'do_data_info' method exists for object of class",
@@ -48,6 +50,7 @@
   #' do_prefit default method
   #' @param obj an object
   #' @param ... Additional arguments currently not in use.
+  #' @return An error, when a non-pk object is used for the first argument.
   #'
   #' @export
   do_prefit.default <- function(obj, ...) {
@@ -70,6 +73,7 @@
   #' do_fit default method
   #' @param obj an object
   #' @param ... Additional arguments currently not in use.
+  #' @return An error, when a non-pk object is used for the first argument.
   #' @export
   do_fit.default <- function(obj, ...) {
     stop("No 'do_fit' method exists for object of class",
@@ -91,6 +95,7 @@
   #' Root mean squared error (RMSE) default method
   #' @param obj an object
   #' @param ... Additional arguments.
+  #' @return An error, when a non-pk object is used for the first argument.
   #' @export
   rmse.default <- function(obj, ...) {
     stop("No 'rmse' method exists for object of class",
@@ -121,6 +126,7 @@
   #'
   #' @param obj An object
   #' @param ... Additional arguments currently not in use.
+  #' @return An error, when a non-pk object is used for the first argument.
   #' @export
   coef_sd.default <- function(obj, ...) {
     stop("No 'coef_sd' method exists for object of class",
@@ -143,6 +149,7 @@
   #' Default method for getting status
   #' @param obj an object
   #' @param ... Additional arguments currently not in use.
+  #' @return An error, when a non-pk object is used for the first argument.
   #' @export
   get_status.default <- function(obj, ...) {
     stop("No 'get_status' method exists for object of class",
@@ -164,6 +171,7 @@
   #' fold_error default method
   #' @param obj an object
   #' @param ... Additional arguments currently not in use.
+  #' @return An error, when a non-pk object is used for the first argument.
   #' @export
[…]

### 2025-01-08 data-raw/RestrictiveClearance_comparison.Rmd
Changes to Restrictive Clearance analysis document

@@
 library(ctxR)
-my_pk <- readRDS("data-raw/all_cvt_pk.rds")
+library(ggvenn)
 source("data-raw/RC_comparison_bkgd.R") # httk loaded here
+# Only use plasma 
+this_pk <- pk(cvt) +
+  settings_optimx(method = "bobyqa") +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(
+    keep_data_original = TRUE,
+    suppress.messages = FALSE
+  ) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
+  stat_error_model(error_group = vars(Chemical, Species))
+this_pk <- do_fit(this_pk, n_cores = 12)
 ```
@@
 
+Note: There is about 50 chemicals with rat data for both, but 3X that when
+we allow substitution of human numbers. However, this does not necessarily mean
+that we will get appropriate fits with the human numbers.
+The aforementioned set of rat data, for example, 33 of 51 chemicals find
+appropriate fits with invivoPKfit + httk.
+
+```{r selecting_chemical_params}
+chosen_list <- rat_pars_human
+# The following are derived from the above selected list (see environment)
+this_chem_v <- unique(chosen_list$param_df$Chemical)
+this_param_list <- chosen_list$named_params
+this_param_df <- chosen_list$param_df
+this_httk_clearance_df <- chosen_list$clearance_df
+this_species_v <- c("rat", "human")
+```
+
+We first want to see how many chemicals are in either _httk_ or _invivoPKfit_
+
+```{r venn_diagrams}
+member_list <- list(
+  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
+                                species = "human",
+                                model = "gas_pbtk",
+                                median.only = TRUE,
+                                physchem.exclude = TRUE,
+                                suppress.messages = TRUE)) %>% 
+    suppressWarnings(),
+  cvt = cvt %>% filter(species %in% c("human", "rat")) %>% pull(analyte_dtxsid)
+)
+
+ggvenn(member_list, fill_color = c("white", "white"))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         today, "httk_vs_CvT_VennDiagram_human.png"),
+       bg = "white",
+       height = 4, width = 6
+)
+
+member_list <- list(
+  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
+                                species = "rat",
+                                model = "gas_pbtk",
+                                median.only = TRUE,
+                                physchem.exclude = TRUE,
+                                suppress.messages = TRUE)) %>% 
+    suppressWarnings(),
+  cvt = cvt %>% filter(species %in% c("rat")) %>% pull(analyte_dtxsid)
+)
+
+ggvenn(member_list, fill_color = c("white", "white"))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         today, "httk_vs_CvT_VennDiagram_ratOnly.png"),
+       bg = "white",
+       height = 4, width = 6
+)
+
+new_chems <- clipr::read_clip()
+length(unique(new_chems %in% setdiff(member_list$cvt, member_list$httk_gas_pbtk)))
+length(unique(new_chems %in% member_list$cvt))
+
+intersect(setdiff(member_list$cvt, member_list$httk_gas_pbtk), new_chems)
+```
+
 ```{r combine_tkstats}
@@
 
-my_tkstats <- eval_tkstats(my_pk) %>%
-  filter(Media %in% "plasma") %>%
+my_tkstats <- eval_tkstats(my_pk, finite_only = FALSE) %>%
+  filter(Media %in% "plasma",
+         Chemical %in% this_chem_v,
+         Species %in% this_species_v) %>%
+  semi_join(get_winning_model(my_pk)) %>%
   dplyr::select(Chemical, Species, CLtot.tkstats, CLtot.nca) %>%
@@
   filter(
-    Species %in% "rat",
-    Chemical %in% rat_pars_rat$clearance_df$Chemical,
     !is.na(CLtot.tkstats), !is.na(CLtot.nca)
@@
 # Combine these two
-combined_clearance_df <- my_tkstats %>% inner_join(rat_pars_rat$clearance_df)
+combined_clearance_df <- this_httk_clearance_df %>%
+  inner_join(my_tkstats) %>%
+  distinct()
+
+length(unique(combined_clearance_df$Chemical))
 ```
@@
   dplyr::ungroup()
+
 clearance_guess %>%
@@
 # Preliminary viz, plot all clearances
-ccd <- combined_clearance_df %>%
+ccd <- clearance_guess %>%
   relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
   pivot_longer(
-    cols = 3:6,
+    cols = tidyselect::all_of(c("CLtot.tkstats", "CLtot.nca_mean",
+                              "restrictive_clearance", "nonrestrictive_clearance")),
     names_to = "Clearance_Source",
@@
       )
-    )
+    ),
+    label_cols = ifelse(rough_determination == "Restrictive",
+                     "green4", "orange3")
   ) %>%
@@
     strip.text = element_text(face = "bold", angle = 0),
-    # axis.text.y = element_blank(),
     axis.title.y = element_blank(),
@@
     today,
-    "rat_tkClearance_comparison_httk_PBPK.png"
+    "all_tkClearance_comparison_httk_PBPK.png"
   ),
@@
 ```{r fup_comparison}
-fup_df <- data.frame(
-  Chemical = get_cheminfo("DTXSID", species = "Rat"),
-  fup = as.numeric(vapply(get_cheminfo("Funbound.plasma", species = "Rat"),
-                          gsub, pattern = ",.+", replacement = "",
-                          FUN.VALUE = character(1)
+fup_df <- this_param_df %>%
+  distinct(Chemical, Species, forced_human_values,
+           Funbound.plasma, Funbound.plasma.adjustment, 
+           Funbound.plasma.dist) %>%
+  mutate(
+    Funbound.plasma.median = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "^\\d+\\.?\\d+e?-?\\d+(?=,)"
+    )),
+    Funbound.plasma.lower95 = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d+(?=,)"
+    )),
+    Funbound.plasma.upper95 = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d$"
     ))
@@
 fup_df %>%
-  ggplot(aes(x = fup)) +
-  geom_histogram(
-    # aes(y = after_stat(density)),
-    binwidth = 0.03,
-    color = "grey5", fill = "grey5"
-  ) +
+  ggplot(aes(x = Funbound.plasma.adjustment)) +
   geom_histogram(
     data = fup_df %>%
-      filter(Chemical %in% rat_pars_rat$param_df$Chemical),
+      filter(Chemical %in% this_httk_clearance_df$Chemical),
     # aes(y = after_stat(density)),
-    fill = NA,
+    fill = "white",
     color = "darkgreen", binwidth = 0.03
@@
   expand_limits(expand = c(0,0)) +
-  # geom_vline(xintercept = 0.05, linetype = "dashed") +
+  geom_vline(xintercept = 0.05, linetype = "dashed") +
   scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
@@
 test_fup <- fup_df %>%
-  # filter(Chemical %in% common_chems_dawson) %>%
-  pull(fup)
+  pull(Funbound.plasma)
 for (i in seq(0, 0.5, by = 1e-9)) {
@@
 }
+
+fup_df %>%
+  ggplot(aes(x = Funbound.plasma, y = Funbound.plasma.adjustment)) +
+  geom_point()
+
 ```
@@
 minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% rat_pars_rat$param_df$Chemical,
-                          species %in% "rat"))
+                   filter(analyte_dtxsid %in% this_chem_v,
+                          species %in% "rat",
+                          administration_route_normalized == "iv"))
 
@@
   ) +
-  settings_optimx(method = c("L-BFGS-B")) +
   scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
@@
 
-unique(new_pk$prefit$par_DF$param_name)
-
-new_pk$prefit$par_DF %>%
-  arrange(Chemical, Species) %>%
-  filter(param_name == "Fup") %>%
-  View()
-
-new_pk <- do_fit(new_pk, n_cores = 12)
+unique(new_pk$prefit$par_DF$param_name) # Check all parameters are there
+length(unique(new_pk$data$Chemical)) 
+length(unique(this_chem_v))
+
+new_pk <- do_fit(new_pk, n_cores = 14)
 gc()
@@
   count(is.finite(AIC))
+
+new_tkstats <- eval_tkstats(new_pk, finite_only = TRUE)
 
@@
                 })) %>% 
+  count(is.na(model_1comp_fup))
   # drop_na(model_1comp_fup) %>%
-  filter(Chemical %in% clear_chem_levels) %>% View()
+  # filter(Chemical %in% clear_chem_levels) %>% View()
   glimpse()
@@
   ggplot(aes(x = estimate, y = start)) +
-  geom_point(size = 2) +
+  geom_point(size = 1.25) +
+  geom_point(data = new_pk$fit %>%
+               filter(param_name %in% "Fup",
+                      model %in% "model_1comp_fup",
+                      Chemical %in% combined_clearance_df$Chemical),
+             size = 1.5, color = "green4") +
   theme_bw() +
   coord_equal(xlim = c(0,1), ylim = c(0,1),
-              expand = TRUE)
+              expand = TRUE) +
+  coord_flip()
+
+ggsave(filename = paste0(
+  Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
+  today, "fup_optimization_allowingHuman.png"),
+  height = 5, width = 5)
 
@@
                                    "decrease"))) %>%
-  filter(Chemical %in% clear_chem_levels, direction %in% "similar (less than 10% difference)")
+  # filter(direction %in% "similar (less than 10% difference)") %>%
   pivot_longer(cols = c(estimate, start),
@@
   Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
-  today, "fup_optimization_generalFits.png"),
+  today, "fup_optimization_generalFits_allowingHuman.png"),
   height = 5, width = 7)
@@
     param_name %in% "kelim",
-    Chemical %in% common_chems_dawson
   ) %>%
@@
 
-my_kelim_fit <- coef(my_pk) %>%
-  inner_join(get_winning_model(my_pk)) %>%
+my_kelim_fit <- get_fit(my_pk) %>%
+  semi_join(get_winning_model(my_pk)) %>%
   ungroup() %>%
-  distinct(model, Chemical, Species, kelim) %>%
-  rename(fit_kelim = "kelim") %>%
-  filter(Chemical %in% common_chems_dawson)
+  filter(param_name == "kelim") %>%
+  distinct(model, Chemical, Species, param_name, value)
 
@@
 ggsave(
-  filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare_2024_0329.png"),
+  filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare.png"),
   height = 11,

### 2025-01-10 data-raw/RestrictiveClearance_comparison.Rmd
Added diagrams for chemical list overlap.

@@
 library(ggvenn)
+library(ggalluvial)
+library(reticulate)
 source("data-raw/RC_comparison_bkgd.R") # httk loaded here
+```
+
+```{r quick-fit}
 # Only use plasma 
@@
 
-member_list <- list(
-  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
-                                species = "rat",
-                                model = "gas_pbtk",
-                                median.only = TRUE,
-                                physchem.exclude = TRUE,
-                                suppress.messages = TRUE)) %>% 
-    suppressWarnings(),
-  cvt = cvt %>% filter(species %in% c("rat")) %>% pull(analyte_dtxsid)
-)
-
-ggvenn(member_list, fill_color = c("white", "white"))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         today, "httk_vs_CvT_VennDiagram_ratOnly.png"),
-       bg = "white",
-       height = 4, width = 6
-)
-
-new_chems <- clipr::read_clip()
-length(unique(new_chems %in% setdiff(member_list$cvt, member_list$httk_gas_pbtk)))
-length(unique(new_chems %in% member_list$cvt))
-
-intersect(setdiff(member_list$cvt, member_list$httk_gas_pbtk), new_chems)
-```
+# new_chems <- clipr::read_clip()
+# length(unique(new_chems %in% setdiff(member_list$cvt, member_list$httk_gas_pbtk)))
+# length(unique(new_chems %in% member_list$cvt))
+
+# intersect(setdiff(member_list$cvt, member_list$httk_gas_pbtk), new_chems)
+
+target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
+```
+
+Here I quickly check a few additional chemicals that will be added to _httk_.
+
+```{r new_httk_chems}
+new_chems_clint <- readxl::read_xlsx(path = paste0(Sys.getenv("OD_DIR"),
+                                             "162Clint_Com_ChemID_DTXSID.xlsx"))
+new_smiles <- readxl::read_xlsx(path = paste0(Sys.getenv("OD_DIR"),
+                                             "127NewSMILES_Caco2_Cyprotex_7.23.24.xlsx"))
+# New Clint
+intersect(
+  member_list$cvt[which(!(member_list$cvt %in% member_list$httk_gas_pbtk))], new_chems_clint$DTXSID
+  )
+
+# New SMILES
+intersect(
+  member_list$cvt[which(!(member_list$cvt %in% member_list$httk_gas_pbtk))], new_smiles$DTXSID
+  )
+```
+
+## Lipinski's Rules
+
+Here I will look at the whether chemicals are "drug-like" by evaluating if:
+
+1. Molecular weight less than 500 Da.  
+2. logP (octanol-water partitioning coefficient) no greater than 5.  
+3. Less than 5 hydrogen bond donors and less than 10 acceptors.
+
+```{r lipinksi_test_data}
+target_chem_info <- get_chemical_details_batch(DTXSID = target_chems,
+                                               rate_limit = 1L)
+target_chem_properties <- get_chem_info_batch(DTXSID = target_chems, 
+                                              rate_limit = 1L) %>%
+  filter(name == "LogKow: Octanol-Water") %>% distinct()
+
+target_chem_properties %>%
+  ggplot(aes(x = source, y = value)) +
+  geom_point() +
+  geom_line(aes(group = dtxsid), color = "grey10", alpha = 0.1) +
+  geom_hline(yintercept = 5, linetype = "longdash") +
+  facet_grid(cols = vars(propType), scales = "free_x") +
+  theme_bw() +
+  theme(axis.text.x = element_text(hjust = 1, angle = 45))
+
+target_chem_properties %>%
+  count(source)
+
+target_chem_info %>%
+  ggplot(aes(x = monoisotopicMass)) +
+  geom_histogram(binwidth = 20, fill = "grey5") +
+  geom_vline(xintercept = 500, linetype = "longdash") +
+  theme_bw()
+
+target_chem_info %>%
+  count(monoisotopicMass <= 500)
+
+```
+
+```{r reticulate-prep}
+smiles_list <- target_chem_info %>% pull(smiles) %>% unique()
+mykit <- import("rdkit")
+```
+
+```{python get_H_bonds}
+import rdkit
+from rdkit import Chem
+from rdkit.Chem import Descriptors
+
+py_smiles_list = r.smiles_list
+mol_from_smiles = [Chem.MolFromSmiles(x) for x in py_smiles_list]
+
+py_h_donors = [Chem.Descriptors.NOCount(x) for x in mol_from_smiles]
+py_h_acceptors = [Chem.Descriptors.NHOHCount(x) for x in mol_from_smiles]
+```
+
+```{r lipinksi_alluvial}
+target_chem_summary <- target_chem_info %>%
+  distinct(dtxsid, monoisotopicMass, smiles) %>%
+  right_join(data.frame(smiles = smiles_list)) %>%
+  bind_cols(data.frame(H_donors = py_to_r(py$py_h_donors),
+                       H_acceptors = py_to_r(py$py_h_acceptors))
+            ) %>%
+  left_join(
+    target_chem_properties %>%
+      filter(source == "ACD/Labs Consensus") %>%
+      distinct(dtxsid, source, value)
+  ) %>%
+  rename(LogKow = value)
+
+target_chem_lipinski <- target_chem_summary %>%
+  select(-c(smiles, source)) %>%
+  group_by(dtxsid) %>%
+  mutate("Mass <= 500 Da" = (monoisotopicMass <= 500),
+          "H-donors < 5" = (H_donors < 5),
+          "H-acceptors < 10" = (H_acceptors < 10),
+          "logP < 5" = (LogKow < 5),
+          .keep = "none") %>%
+  ungroup() %>%
+  mutate(Lipinski = rowSums(dplyr::select(., where(is.logical))) >= 3)
+
+target_chem_lipinski %>%
+  group_by(Lipinski) %>%
+  count(`Mass <= 500 Da`, `H-donors < 5`, `H-acceptors < 10`, `logP < 5`,
+        name = "Count") %>%
+  ggplot(aes(
+    axis3 = `Mass <= 500 Da`,
+    axis4 = `logP < 5`,
+    axis2 = `H-donors < 5`,
+    axis1 = `H-acceptors < 10`,
+    y = Count
+  )) +
+  geom_alluvium(aes(fill = Lipinski)) +
+  geom_stratum() +
+  scale_x_discrete(limits = c( 
+    "H-acceptors < 10",
+    "H-donors < 5",
+    "<= 500 Da",
+    "logP < 5"
+  ),
+  position = "top",
+  expand = c(.2, .05)) +
+  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
+  labs(title = "Overwhelmingly, this subset of chemicals passes Lipinksi's Rules of 5") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(face = "bold", color = "black"),
+        panel.grid = element_blank())
+
+```
+
+Overwhelmingly, we see that chemicals (by Lipinski's rules of 5) are "drug-like".
+While this may not matter effectively for clearance, it may be nice to look 
+at whether chemicals deemed not "drug-like" (11 total) are more likely to be
+restrictively or non-restrictively cleared.
 
@@
 # Start Here if you ran the background job
-
-my_tkstats <- eval_tkstats(my_pk, finite_only = FALSE) %>%
+this_winmodel <- get_winning_model(this_pk)
+this_tkstats <- inner_join(this_winmodel %>% filter(model != "model_flat"),
+                          eval_tkstats(this_pk, finite_only = TRUE)) %>%
   filter(Media %in% "plasma",
          Chemical %in% this_chem_v,
-         Species %in% this_species_v) %>%
-  semi_join(get_winning_model(my_pk)) %>%
+         Species %in% this_species_v,
+         !is.na(CLtot.tkstats)) %>%
+  semi_join(get_winning_model(this_pk)) %>%
   dplyr::select(Chemical, Species, CLtot.tkstats, CLtot.nca) %>%
   distinct() %>%
-  filter(
-    !is.na(CLtot.tkstats), !is.na(CLtot.nca)
-  ) %>%
   group_by(Chemical, Species, CLtot.tkstats) %>%
   summarize(
-    CLtot.nca_mean = mean(CLtot.nca),
-    CLtot.nca_sd = sd(CLtot.nca)
-  )
+    CLtot.nca_mean = mean(CLtot.nca, na.rm = TRUE),
+    CLtot.nca_sd = sd(CLtot.nca, na.rm = TRUE)
+  )
+message(length(unique(this_tkstats$Chemical)),
+        " unique chemicals with finite clearance.")
 
@@
 combined_clearance_df <- this_httk_clearance_df %>%
-  inner_join(my_tkstats) %>%
+  inner_join(this_tkstats) %>%
   distinct()
@@
 
-httk_preds_rat <- get_httk_preds(rat_pars_rat, my_pk, species = "rat")
+httk_preds_rat <- get_httk_preds(rat_pars_rat, this_pk, species = "rat")
 
@@
 rat_df <- httk_preds_rat %>%
-  left_join(predict(my_pk)) %>%
-  semi_join(get_winning_model(my_pk))
-
-rat_df <- ggplot(mapping = aes(
+  left_join(predict(this_pk)) %>%
+  semi_join(this_winmodel)
+
+rat_df %>% ggplot(mapping = aes(
     x = Conc_est,
     y = httk_Preds,
-    color = interaction(Route, Media)
+    color = interaction(Route)
   )) +
   geom_point() +
-  geom_line(mapping = aes(
-    group = interaction(Chemical, Media, Route, Reference)
-  )
-  ) +
   geom_abline(slope = 1, intercept = 0, color = "black") +
-  coord_equal(ylim = c(0, 200), xlim = c(0, 200))
+  scale_x_log10() + scale_y_log10() +
+  facet_wrap(~Route)
 
@@
 
-saveRDS(new_pk, "data-raw/ratCVT_wHTTK_reformulated.rds")
+# saveRDS(new_pk, "data-raw/ratCVT_wHTTK_reformulated.rds")
 ```
@@
 ```{r begin_analysis}
-new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
-
+# new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
 coef(new_pk) %>% View()
-eval_tkstats(new_pk, finite_only = FALSE) %>% View()
-get_winning_model(new_pk) %>%
-  count(model)
+new_winmodel <- get_winning_model(new_pk)
+eval_tkstats(new_pk, finite_only = TRUE) %>% 
+  semi_join(new_winmodel) %>%
+  View()
 
@@
   # filter(Chemical %in% clear_chem_levels) %>% View()
-  glimpse()
 
@@
   geom_point(size = 1.25) +
-  geom_point(data = new_pk$fit %>%
-               filter(param_name %in% "Fup",
-                      model %in% "model_1comp_fup",
-                      Chemical %in% combined_clearance_df$Chemical),
-             size = 1.5, color = "green4") +
   theme_bw() +
@@
 
-For this I will just use the PK object I have saved `my_pk` and take the
+For this I will just use the PK object I have saved `this_pk` and take the
 _prefit_ parameter estimations and first compare that with eventual optimized `kelim`.
@@
 # par_DF
-my_kelim_prefit <- my_pk$prefit$par_DF %>%
+this_kelim_prefit <- this_pk$prefit$par_DF %>%
   filter(
@@
 
-my_kelim_fit <- get_fit(my_pk) %>%
-  semi_join(get_winning_model(my_pk)) %>%
+this_kelim_fit <- get_fit(this_pk) %>%
+  semi_join(get_winning_model(this_pk)) %>%
   ungroup() %>%
@@
 
-my_kelim_df <- inner_join(my_kelim_fit, my_kelim_prefit)
+this_kelim_df <- inner_join(this_kelim_fit, this_kelim_prefit)
 
@@
 
-full_df <- inner_join(my_kelim_df, httk_df) %>%
+full_df <- inner_join(this_kelim_df, httk_df) %>%
   relocate(fit_kelim, .after = last_col())
@@
 
-my_data <- get_data(new_pk) %>%
+this_data <- get_data(new_pk) %>%
   distinct(Chemical, Species, Reference, Route, Media, Dose, Time, Conc) %>%
@@
 ```{r oxybenzene-test}
-old_AIC <- AIC(my_pk) %>%
+old_AIC <- AIC(this_pk) %>%
   filter(
@@
 
-old_rsquared <- rmse(my_pk) %>%
+old_rsquared <- rmse(this_pk) %>%
   filter(
@@
 
-my_pl_1comp <- plot(new_pk,
+this_pl_1comp <- plot(new_pk,
                     n_interp = 11, use_scale_conc = FALSE,
@@
 
-my_pl_2comp <- plot(new_pk,
+this_pl_2comp <- plot(new_pk,
                     n_interp = 11, use_scale_conc = FALSE,
@@
 new_cl_tkstats <- get_tkstats(new_pk)
-my_tkstats <- my_pk %>%
+this_tkstats <- this_pk %>%
   get_winning_model() %>%
-  left_join(coef(my_pk)) %>%
-  left_join(rsq(my_pk)) %>%
+  left_join(coef(this_pk)) %>%
+  left_join(rsq(this_pk)) %>%
   distinct()
-my_tkstats %>%
+this_tkstats %>%
   select(-coefs_vector) %>%

### 2025-01-10 data-raw/pulling_oral_iv_data_cvtdb.Rmd

@@
   print(table(.data$species))
-  message(paste0("Number of unique studies: ", length(unique(.data$fk_study_id))))
-  message(paste0("Number of unique series: ", length(unique(.data$fk_series_id))))
-  message(paste0("Number of unique chemicals: ", length(unique(.data$analyte_dtxsid))))
-  message(paste0("Unique Dose units: ", paste(unique(.data$dose_level_units_original), collapse = ", ")))
-  message(paste0("Unique Concentration units: ", paste(unique(.data$conc_units_original), collapse = ", ")))
+
+  message(paste0("Number of unique studies: ",
+                 length(unique(.data$fk_study_id))))
+  message(paste0("Number of unique series: ",
+                 length(unique(.data$fk_series_id))))
+  message(paste0("Number of unique chemicals: ",
+                 length(unique(.data$analyte_dtxsid))))
+  message(paste0("Unique Dose units: ",
+                 toString(unique(.data$dose_level_units_original))))
+  message(paste0("Unique Concentration units: ", 
+                 toString(unique(.data$conc_units_original))))
   message("Data by unique route of administration:")
@@
                     "loq")), as.numeric),
-    # conc, conc_sd_original, and conc_original have NA/NE/ND values that are coerced to NAs
+    # conc, conc_sd_original, and conc_original
+    # have NA/NE/ND values that are coerced to NAs
     year = as.character(year),
@@
 glimpse(cvt_df, width = 80)
+quick_stats(cvt_df)
 ```
@@
 
-```{r}
-quick_stats(cvt_df)
+```{r diff_log_function}
+# Now I want to write a quick function that will log relevant changes
+# from previous 'cvt' objects
+devtools::load_all() # So this loads the previous cvt object
+diff_log_cvt <- function(new_cvt,
+                         key_id = "conc_time_id",
+                         grp_ids = c("analyte_dtxsid",
+                                     "species")) {
+  stopifnot(
+    key_id %in% colnames(cvt),
+    key_id %in% colnames(new_cvt),
+    all(grp_ids %in% colnames(cvt)),
+    all(grp_ids %in% colnames(new_cvt))
+  )
+  if (length(unique(new_cvt[[key_id]])) != NROW(new_cvt)) {
+    stop("key_id is not not a column that uniquely identifies this data.")
+  }
+
+  # Prepare some vectors:
+  grp_strings_new <- unique(do.call("paste", new_cvt[grp_ids]))
+  grp_strings_old <- unique(do.call("paste", cvt[grp_ids]))
+
+  msg_to_write <- paste0("\n\n======== ", round(Sys.time()))
+
+  if (identical(new_cvt, cvt)) {
+    msg_to_write <- paste(msg_to_write, "No changes.", sep = "\t")
+    message("There are no changes from previous `cvt` data.frame, ",
+            "are you sure you want to save this?")
+  } else {
+    msg_to_write <- paste(msg_to_write, "Changes detected.", sep = "\t")
+
+    ###---- Check key_id changes (usually conc_time_id)
+    diff_row_add <- setdiff(new_cvt[[key_id]], cvt[[key_id]])
+    diff_row_sub <- setdiff(cvt[[key_id]], new_cvt[[key_id]])
+    diff_row_common <- intersect(cvt[[key_id]], new_cvt[[key_id]])
+    # Nature of data changes:
+    added_grps <- unique(
+      do.call("paste",
+              new_cvt[which(new_cvt[[key_id]] %in% diff_row_add), grp_ids]
+              )
+      )
+    removed_grps <- unique(
+      do.call("paste",
+              cvt[which(cvt[[key_id]] %in% diff_row_sub), grp_ids]
+              )
+      )
+
+    added_new_grps <- setdiff(added_grps, grp_strings_old)
+    added_existing_grps <- intersect(added_grps, grp_strings_old)
+    removed_new_grps <- setdiff(removed_grps, grp_strings_new)
+    removed_existing_grps <- intersect(removed_grps, grp_strings_new)
+
+    msg_to_write <- c(
+      msg_to_write,
+      paste("Rows added:", length(diff_row_add)),
+      paste("Rows removed:", length(diff_row_sub))
+    )
+
+    limit_grp_output <- function(grp_vector) {
+      if (length(grp_vector) > 0) {
+        if (length(grp_vector) > 6) {
+          grp_vector <- c(grp_vector[c(1,2)],
+                              paste0("... [",
+                                     length(grp_vector) - 3,
+                                     "] more!"),
+                              grp_vector[c(length(grp_vector) - 1)]
+          )
+        }
+      return(grp_vector)
+    }
+      msg_to_write <- c(msg_to_write,
+                        "New Groups added (not in previous data):",
+                        paste0("\t", limit_grp_output(added_new_grps)),
+                        "Groups with new observations (group present in previous data)",
+                        paste0("\t", limit_grp_output(added_existing_grps)),
+                        "Groups removed that no longer have data present:",
+                        paste0("\t", limit_grp_output(removed_new_grps)),
+                        "Groups removed that still have some data present:",
+                        paste0("\t", limit_grp_output(removed_existing_grps)),
+                        "-----------------------------------"
+                        )
+    }
+
+    ### -----Checking columns
+    diff_col_add <- setdiff(names(new_cvt), names(cvt)) # Columns added in new_cvt
+    diff_col_sub <- setdiff(names(cvt), names(new_cvt)) # Columns removed in new_cvt
+    diff_col_common <- intersect(names(cvt), names(new_cvt))
+
+    # Left off here TODO
+    if (length(c(diff_col_add, diff_col_sub)) == 0) {
+      msg_to_write <- c(msg_to_write,
+                        "No changes in column names.")
+    } else if (length(diff_col_add) > 0 && length(diff_col_sub) > 0) {
+      # Check renaming
+      common_row_cvt <- cvt[diff_row_common, ]
+      common_row_new <- new_cvt[diff_row_common, ]
+
+      diff_columns <- function(x, y) {
+        out_list <- character()
+        for (ix in names(x)) {
+          for (iy in names(y)) {
+            if (identical(x[[c(key_id,ix)]], y[[c(key_id, iy)]])) {
+              out_list <- c(out_list, paste0(ix, " -> ", iy))
+            }
+          }
+        }
+        return(out_list)
+      }
+
+      renamed_cols <- diff_columns(common_row_cvt[diff_col_sub],
+                                   common_row_new[diff_col_add])
+      if (length(renamed_cols) > 0) {
+        msg_to_write <- c(msg_to_write,
+                          "Renamed columns (non-exhaustive):",
+                          renamed_cols)
+      } else {
+        msg_to_write <- c(msg_to_write,
+                          "No renamed columns found.")
+      }
+    }
+    if (length(diff_col_add) > 0) {
+      msg_to_write <- c(msg_to_write,
+                        "--------------",
+                        "Columns added:",
+                        diff_col_add)
+    }
+    if (length(diff_col_sub) > 0) {
+      msg_to_write <- c(msg_to_write,
+                        "______________",
+                        "Columns removed (from previous data):",
+                        diff_col_sub)
+    }
+
+    if (!identical(common_row_cvt[diff_col_common],
+                   common_row_new[diff_col_common])) {
+      msg_to_write <- c(msg_to_write,
+                        "Data for same observation key_ids have changed.")
+    }
+    msg_to_write <- c(msg_to_write,
+                      "================================\n")
+  }
+  return(cat(msg_to_write, sep = "\n"))
+}
 ```

### 2025-01-10 data-raw/summary_loglike_lognormal.Rmd

--- 2023-01-23 Working Rmds/summary_loglike_lognormal.Rmd
@@
   #log-transformed samples
-  ylog <- log(y)
+  ylog <- log10(y)
   return(c("sample_mean" = mean(y),
@@
 samp[c("est_sample_meanlog",
-       "est_sample_sdlog")] <- convert_summary_to_log(sample_mean = samp$sample_mean,
+       "est_sample_sdlog")] <- convert_summary_to_log10(sample_mean = samp$sample_mean,
                                                                    sample_SD = samp$sample_sd)
@@
 
-Log-scale sample SD. The "true" population log-scale SD (1.0) is indicated by vertical and horizontal dashed lines.
+Sampling error:
+
+```{r}
+ggplot(data = samp) +
+  geom_histogram(aes(x = est_sample_meanlog - sample_meanlog))
+```
+
+Log-scale sample SD. The "true" population log-scale SD (`log10(exp(1))`) is indicated by vertical and horizontal dashed lines.
 
@@
   geom_abline(intercept = 0, slope = 1, color = "black") +
-    geom_hline(yintercept = 1, linetype = 2) +
-  geom_vline(xintercept = 1, linetype = 2) +
+    geom_hline(yintercept = log10(exp(1)), linetype = 2) +
+  geom_vline(xintercept = log10(exp(1)), linetype = 2) +
   xlab("Actual log-scale sample SD") +
@@
 
-The estimated log-scale sample SD usually underestimates the actual log-scale sample SD (most points are below the identity line).
+The estimated log-scale sample SD usually overestimates the actual log-scale sample SD (most points are above the identity line).
 

### 2025-01-23 data-raw/RestrictiveClearance_comparison.Rmd
Re-structured analysis to fit new httk release and ensured that restrictive and non-restrictive estimates & parameterization are being appropriately handled.

@@
 library(ggalluvial)
+library(flextable)
 library(reticulate)
-source("data-raw/RC_comparison_bkgd.R") # httk loaded here
-```
+source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
+```
+
+I select which parameterization (based on species) that I will use.
+
+```{r selecting_chemical_params}
+chosen_list <- rat_pars_human
+# The following are derived from the above selected list (see environment)
+this_chem_v <- unique(chosen_list$param_df$Chemical)
+this_param_rest_l <- chosen_list$named_params_restrictive
+this_param_nrest_l <- chosen_list$named_params_nonrestrictive
+this_param_df <- chosen_list$param_df
+this_httk_clearance_df <- chosen_list$clearance_df
+this_species_v <- c("rat", "human")
+# Testing to make sure there are some chemicals that have different clearances
+count(this_httk_clearance_df, restrictive_clearance == nonrestrictive_clearance)
+# The majority (140) do!
+```
+
+Here I do a quick fit of the CvT data only for those that have plasma measurements.
 
 ```{r quick-fit}
-# Only use plasma 
-this_pk <- pk(cvt) +
+# Only use plasma for simplicity
+this_pk <- pk(cvt %>% filter(conc_medium_normalized == "plasma")) +
   settings_optimx(method = "bobyqa") +
@@
     keep_data_original = TRUE,
-    suppress.messages = FALSE
-  ) +
+    suppress.messages = FALSE) +
   scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
   stat_error_model(error_group = vars(Chemical, Species))
-this_pk <- do_fit(this_pk, n_cores = 12)
-```
+
+this_pk <- do_prefit(this_pk)
+this_pk <- do_fit(this_pk, n_cores = 14)
+```
+
+Relationships in the mathematical PK models:
+
+- When there is only oral data available, `Fgutabs_Vdist` and `CLtot_Fgutabs`
+will be calculated instead of the numerator alone.  
+- $C_{ss} \cdot CL_{tot} = C_{H,u}\cdot CL{int}$ (Bennet & Sodhi 2024)  
+- [Add More Here]
 
@@
 
-```{r selecting_chemical_params}
-chosen_list <- rat_pars_human
-# The following are derived from the above selected list (see environment)
-this_chem_v <- unique(chosen_list$param_df$Chemical)
-this_param_list <- chosen_list$named_params
-this_param_df <- chosen_list$param_df
-this_httk_clearance_df <- chosen_list$clearance_df
-this_species_v <- c("rat", "human")
-```
-
 We first want to see how many chemicals are in either _httk_ or _invivoPKfit_
@@
     suppressWarnings(),
-  cvt = cvt %>% filter(species %in% c("human", "rat")) %>% pull(analyte_dtxsid)
+  cvt = cvt %>% 
+    filter(species %in% c("human", "rat"),
+           conc_medium_normalized == "plasma") %>%
+    pull(analyte_dtxsid)
 )
@@
                          "RestrictiveClearance_Analysis/",
-                         today, "httk_vs_CvT_VennDiagram_human.png"),
+                         "CURRENT_", "httk_vs_CvT_VennDiagram_human.png"),
        bg = "white",
-       height = 4, width = 6
-)
-
-# new_chems <- clipr::read_clip()
-# length(unique(new_chems %in% setdiff(member_list$cvt, member_list$httk_gas_pbtk)))
-# length(unique(new_chems %in% member_list$cvt))
-
-# intersect(setdiff(member_list$cvt, member_list$httk_gas_pbtk), new_chems)
+       height = 3, width = 5
+)
 
 target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
-```
-
-Here I quickly check a few additional chemicals that will be added to _httk_.
-
-```{r new_httk_chems}
-new_chems_clint <- readxl::read_xlsx(path = paste0(Sys.getenv("OD_DIR"),
-                                             "162Clint_Com_ChemID_DTXSID.xlsx"))
-new_smiles <- readxl::read_xlsx(path = paste0(Sys.getenv("OD_DIR"),
-                                             "127NewSMILES_Caco2_Cyprotex_7.23.24.xlsx"))
-# New Clint
-intersect(
-  member_list$cvt[which(!(member_list$cvt %in% member_list$httk_gas_pbtk))], new_chems_clint$DTXSID
-  )
-
-# New SMILES
-intersect(
-  member_list$cvt[which(!(member_list$cvt %in% member_list$httk_gas_pbtk))], new_smiles$DTXSID
-  )
 ```
@@
   ggplot(aes(x = monoisotopicMass)) +
-  geom_histogram(binwidth = 20, fill = "grey5") +
+  geom_histogram(binwidth = 50, fill = "grey5",
+                 boundary = 0) +
   geom_vline(xintercept = 500, linetype = "longdash") +
+  scale_x_continuous(limits = c(0, 1000),
+                     breaks = seq(0, 1000, 100)) +
   theme_bw()
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "target_chems_molmass.png"),
+       bg = "white",
+       height = 3, width = 5
+)
 
@@
   geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  labs(title = "Overwhelmingly, this subset of chemicals passes Lipinksi's Rules of 5") +
+  labs(title = "Overwhelmingly, these chemicals passes Lipinksi's Rules of 5",
+       fill = "Passes Lipinksi's Rules?") +
+  scale_fill_manual(values = c("grey20", "green4")) +
   theme_minimal() +
-  theme(axis.text.x = element_text(face = "bold", color = "black"),
-        panel.grid = element_blank())
-
+  theme(axis.text.x = element_text(face = "bold", color = "black", size = 10),
+        panel.grid = element_blank(),
+        plot.title = element_text(hjust = 0.5),
+        legend.position = "bottom")
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Alluvium_Lipinski.png"),
+       bg = "white",
+       height = 4, width = 6
+)
 ```
@@
 
+We also want to assess whether the "winning" _invivoPKfit_ fits are better than
+the chosen _httk_ fit. This is a bit of a pre-requisite to our analysis of the
+clearances and whether they are more or less reasonable in their reflection of
+the reality. The metric used here will be RMSLE.
+
+```{r httk_predictions}
+restrictive_preds <- get_httk_preds(
+  parameters = this_param_rest_l,
+  pk_obj = this_pk,
+  species = c("rat", "human")
+) %>% rename_with(
+  .fn = ~paste0(.x, "_restrictive"),
+  .cols = starts_with("httk_")
+)
+
+nonrestrictive_preds <- get_httk_preds(
+  parameters = this_param_nrest_l,
+  pk_obj = this_pk,
+  species = c("rat", "human")
+) %>% rename_with(
+  .fn = ~paste0(.x, "_nonrestrictive"),
+  .cols = starts_with("httk_")
+)
+
+all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds)
+
+this_nonflat_winmodel <- get_winning_model(this_pk) %>%
+  filter(model %in% c("model_1comp", "model_2comp"))
+
+winning_preds <- predict(this_pk) %>%
+  semi_join(this_nonflat_winmodel) %>%
+  distinct(Chemical, Species, Chemical_Name,
+           model, method, Dose, Media, Route, Reference, pLOQ, Time,
+           N_Subjects, Conc, Conc_est)
+
+# RMSLE formula
+# LE = log1p(Conc_est) - log1p(Conc)
+# SLE = LE^2
+# RMSLE = sqrt(mean(SLE, na.rm = TRUE))
+
+combined_preds <- all_httk_preds %>%
+  left_join(winning_preds) %>%
+  filter(!is.na(model))
+
+combined_RMSLE <- combined_preds %>%
+  ungroup() %>%
+  mutate(
+    restrictive_SLE = (log1p(httk_Preds_restrictive) - log1p(Conc))^2,
+    nonrestrictive_SLE = (log1p(httk_Preds_nonrestrictive) - log1p(Conc))^2,
+    invivoPK_SLE =  (log1p(Conc_est) - log1p(Conc))^2 
+  ) %>%
+  group_by(Chemical, Species) %>%
+  summarize(RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
+            RMSLE_nonrestrictive = sqrt(mean(nonrestrictive_SLE, na.rm = TRUE)),
+            RMSLE_invivoPKfit = sqrt(mean(invivoPK_SLE, na.rm = TRUE)))
+
+combined_RMSLE %>%
+  ungroup() %>%
+  pivot_longer(cols = starts_with("RMSLE_"),
+               names_to = "Source",
+               values_to = "RMSLE") %>%
+  mutate(Source = factor(Source,
+                         levels = c("RMSLE_nonrestrictive",
+                                    "RMSLE_invivoPKfit",
+                                    "RMSLE_restrictive")
+  )) %>%
+  ggplot(aes(x = Source, y = RMSLE, group = Chemical)) +
+  geom_point(alpha = 0.5) +
+  geom_line(alpha = 0.5) +
+  theme_bw()
+
+combined_RMSLE %>%
+  ungroup() %>%
+  mutate(comparison_group = case_when(
+    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
+     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
+    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
+      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
+    RMSLE_invivoPKfit > RMSLE_restrictive &
+      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
+  )) %>% 
+  ggplot(aes(x = Chemical, y = RMSLE_invivoPKfit)) +
+  geom_point(color = "green4") +
+  geom_point(aes(y = RMSLE_nonrestrictive), shape = 4, size = 0.5) +
+  geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
+  geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
+  facet_grid(~factor(comparison_group,
+                     levels = c("Less than", "Between", "More than")),
+             scales = "free_x", space = "free_x") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid = element_blank())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "RMSLE_comparison_fullChart.png"),
+       bg = "white",
+       height = 4, width = 8
+)
+
+```
+
+Another weight that we may consider is relative log-likelihood. This can be
+calculated using AIC, compared to the the flat model.
+
+```{r relative-likelihood}
+this_rll_probs <- AIC(this_pk) %>%
+  distinct(Chemical, Species, model, AIC) %>%
+  pivot_wider(names_from = model, values_from = AIC) %>%
+  rowwise() %>% 
+  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(across(starts_with("model_"), \(x) {
+    signif(exp((minAIC - x)/2) * 100, 4)
+  })) %>%
+  mutate(across(starts_with("model_"), \(x) {
+    ifelse(x < 1E-6, 0, x)
+  })) %>%
+  inner_join(this_nonflat_winmodel %>% distinct(Chemical, Species, model)) %>%
+  ungroup() %>%
+  filter(model_1comp >= 99 | model_2comp >= 99,
+        model_flat < 1, Chemical %in% target_chems)
+
+this_rll_probs %>%
+  count(model_1comp >= 99, model_2comp >= 99)
+
+```
+
+The weights to be applied are calculated as such:
+
+$$
+\gamma = \frac{100\cdot \rm{RMSLE}}{\theta}
+$$
+Where $\theta$ is the relative log-likelihood. The smaller number the better.
+If the RMSLE is zero, then it means that it is a "perfect" fit and we are highly
+confident in using other metrics to gauge clearance. Below I put these together.
+
+```{r model_weighting}
+combined_model_weights <- combined_RMSLE %>%
+  left_join(this_rll_probs) %>%
+  ungroup() %>%
+  pivot_longer(cols = starts_with("model_"),
+               names_to = "all_models",
+               values_to = "relative_likelihood") %>%
+  filter(all_models == model) %>%
+  ungroup() %>%
+  mutate(gamma_weight = 100 * RMSLE_invivoPKfit / relative_likelihood,
+         rmsle_comparison_group = case_when(
+    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
+     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
+    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
+      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
+    RMSLE_invivoPKfit > RMSLE_restrictive &
+      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than")
+  ) %>%
+  mutate(rmsle_comparison_group = factor(rmsle_comparison_group,
+                                         levels = c("Less than", "Between",
+                                                    "More than"))) %>%
+  select(-all_models) %>% distinct()
+
+```
+
+Next we need to compare clearances. Sometimes this is difficult as the overlap
+with certain calculations will be defined by the type of experimental data
+available. For instance, if there is only oral data available, `CLtot.tkstats`
+will _not_ be calculated and instead `CLtot/Fgutabs.tkstats` will be available.
+
 ```{r combine_tkstats}
-# Start Here if you ran the background job
-this_winmodel <- get_winning_model(this_pk)
-this_tkstats <- inner_join(this_winmodel %>% filter(model != "model_flat"),
-                          eval_tkstats(this_pk, finite_only = TRUE)) %>%
-  filter(Media %in% "plasma",
-         Chemical %in% this_chem_v,
-         Species %in% this_species_v,
-         !is.na(CLtot.tkstats)) %>%
-  semi_join(get_winning_model(this_pk)) %>%
-  dplyr::select(Chemical, Species, CLtot.tkstats, CLtot.nca) %>%
-  distinct() %>%
-  group_by(Chemical, Species, CLtot.tkstats) %>%
-  summarize(
-    CLtot.nca_mean = mean(CLtot.nca, na.rm = TRUE),
-    CLtot.nca_sd = sd(CLtot.nca, na.rm = TRUE)
-  )
-message(length(unique(this_tkstats$Chemical)),
-        " unique chemicals with finite clearance.")
+# Get the winning model and only include chemicals in target_chems
+this_winmodel <- get_winning_model(this_pk) %>%
+    filter(Chemical %in% target_chems)
+# How many overlapping chemicals have winning models that aren't flat?
+count(
+  this_winmodel,
+  model
+) # 153 = 97 1-compartment + 56 2-compartment
+
+this_tkstats <- eval_tkstats(this_pk,
+                             model = c("model_1comp", "model_2comp"),
+                             finite_only = TRUE,
+                             dose_norm = TRUE
+) %>%
+  rename(CLtot_Fgutabs.tkstats = `CLtot/Fgutabs.tkstats`) %>%
+  distinct(Chemical, Species, method, model, Dose, Route, Media,
+           CLtot.tkstats, CLtot_Fgutabs.tkstats, halflife.tkstats, Css.tkstats) %>%
+  inner_join(this_winmodel)
+
+count(
+  this_tkstats,
+  # model,
+  !is.na(CLtot.tkstats),
+  !is.na(CLtot_Fgutabs.tkstats),
+  !is.na(halflife.tkstats)
+) %>% flextable() %>%
+  set_header_labels(
+    `!is.na(CLtot.tkstats)` = "Valid Total Clearance",
+    `!is.na(CLtot_Fgutabs.tkstats)` = "Valid Total Clearance/Fgutabs",
+    `!is.na(halflife.tkstats)` = "Valid halflife",
+    n = "Number of Chemicals"
+    )
+# 46 chemicals have valid total clearance
+# 144 chemicals have valid total clearance/Fgutabs
+# 5 chemicals have only valid total clearance and no valid total clearance/Fgutabs
+
+count(this_tkstats, is.na(Css.tkstats))
+
+```
+
+Here I will evaluate $C_{SS}$, the steady-state concentration to get some
+understanding of whether chemicals may be likely restrictive or non-restrictive.
+
+```{r Css_assessment}
+
+css_httk_batch <- function(param_list,
+                           restrictive = TRUE) {
+  stopifnot(is.logical(restrictive))
+
+  css_list_r <- vapply(
+    param_list,
+    \(x) {
+      calc_analytic_css_3comp2(parameters = x,
+                               restrictive.clearance = restrictive)
+    },
+    FUN.VALUE = numeric(1L)
+  )
+  css_list_names <- names(param_list)
+
+  css_df <- data.frame(Chemical = css_list_names,
+                       Css_httk = css_list_r)
+  if (restrictive) {
+    css_df <- rename(css_df, Css_httk_r = Css_httk)
+  } else {
+    css_df <- rename(css_df, Css_httk_nr = Css_httk)
+  }
+  return(css_df)
+}
+
+this_css_df <- inner_join(
+  css_httk_batch(this_param_rest_l, restrictive = TRUE),
+  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
+) %>%
+  inner_join(this_tkstats) %>%
+  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
+  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
+  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
+  mutate(comparison_group_Css = factor(
+    case_when(
+      between(Css.tkstats, Css_httk_r, Css_httk_nr) |
+        between(Css.tkstats, Css_httk_nr, Css_httk_r) ~ "Between",
+      Css.tkstats < Css_httk_r & Css.tkstats < Css_httk_nr ~ "Below",
+      Css.tkstats > Css_httk_r & Css.tkstats > Css_httk_nr ~ "Above"),
+    levels = c("Above", "Between", "Below")
+  ), Chemical = factor(Chemical) %>% fct_reorder(Css_httk_r)
+  )
+
+this_css_df %>%
+  ggplot(aes(x = Chemical)) +
+  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
+  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
+  geom_linerange(aes(ymin = Css_httk_r,
+                     ymax = Css_httk_nr)
+  ) +
+  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
+  facet_grid(rows = vars(comparison_group_Css),
+             scales = "free_x",
+             space = "free_x") +
+  scale_y_log10(name = "Css") +
+  scale_shape_manual(values = c(0,1)) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid = element_blank())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Css_comparison_fullChart.png"),
+       bg = "white",
+       height = 4, width = 8
+)
+
+```
+
+```{r}
+this_css_df %>%
+  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
+  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
+  left_join(data.frame(Chemical = names(this_param_rest_l),
+                       CLint = vapply(names(this_param_rest_l),
+                                      \(x) {
+                                        this_param_rest_l[[x]][["Clint"]]
+                                      },
+                                      FUN.VALUE = numeric(1L)
+                       ))) %>%
+  mutate(CLint = log10(CLint + 1)) %>%
+  ggplot(aes(x = CLint)) +
+  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
+  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
+  geom_linerange(aes(ymin = Css_httk_r,
+                     ymax = Css_httk_nr)
+  ) +
+  scale_y_log10(name = "C<sub>SS</sub>") + 
+  labs(x = "CL<sub>int</sub>") +
+  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
+  scale_shape_manual(values = c(0,1)) +
+  theme_bw() +
+  theme(axis.title = ggtext::element_markdown())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Css_x_CLint.png"),
+       bg = "white",
+       height = 4, width = 8
+)
+```
+
+Now I will try to triangulate the model weights witht the Css estimates.
+
+```{r weighted_Css}
+combined_model_weights %>%
+  inner_join(this_css_df) %>%
+  ggplot(aes(x = fct_reorder(Chemical, Css_httk_r))) +
+  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
+  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
+  geom_linerange(aes(ymin = Css_httk_r,
+                     ymax = Css_httk_nr)
+  ) +
+  geom_point(aes(y = Css.tkstats, shape = Route, color = gamma_weight)) +
+  facet_grid(rows = vars(comparison_group_Css),
+             cols = vars(rmsle_comparison_group),
+             scales = "free_x",
+             space = "free_x") +
+  scale_y_log10(name = "Css") +
+  scale_shape_manual(values = c(0,1)) +
+  scale_color_viridis_b(option = "viridis", 
+                        guide = guide_colorbar(position = "bottom")) +
+  labs(subtitle = "RMSLE for invivoPKfit compared to httk predictions",
+       x = "Chemical\n(ordered by increasing restrictive Css prediction)",
+       y = "Css",
+       color = "Inverse Confidence") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.subtitle = element_text(hjust = 0.5),
+        panel.grid = element_blank(),
+        legend.title = element_text(vjust = 0.8))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Css_withRMSLEweights.png"),
+       bg = "white",
+       height = 5, width = 10
+)
+
+```
+
+```{r calc_CLtot_Fgutabs}
+this_tkstats2 <- this_tkstats %>%
+  left_join(
+    this_param_df %>%
+      distinct(Chemical, Species, Fabsgut.restrictive)
+  ) %>%
+  mutate(CLtot_calc = CLtot_Fgutabs.tkstats * Fabsgut.restrictive)
+
+ggplot(data = this_httk_clearance_df,
+       aes(x = Chemical)) +
+  geom_point(aes(y = restrictive_clearance), color = "green4") +
+  geom_point(aes(y = nonrestrictive_clearance), color = "orange2") +
+  geom_point(data = this_tkstats2,
+             aes(y = CLtot_calc)) +
+  scale_y_log10() +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank())
 
@@
 Finally, let's visualize where the tkstats predictions land.
+Because there are only a handful of chemicals which _invivoPKfit_ can calculate
+`CLtot` for, I will employ two strategies to gauge how different these estimates
+are in reality.
+
+1. Visualize differences in half-life.  
+2. Multiply `CLtot_Fgutabs` by the `Fabsgut` value parameterized in _httk_ to
+get a clearance value.
+
+```{r half-life}
+combined_clearance_df %>%
+  ggplot(aes(x = halflife.tkstats)) +
+  geom_point(aes(y = restrictive_halflife), color = "magenta2") +
+  geom_point(aes(y = nonrestrictive_halflife), color = "green4") +
+  coord_equal(xlim = c(0, 200), y = c(0, 200))
+```
+
+Notes:
+Look at Css values for restrictive/nonrestrictive (httk solutions)
+AICs for models
 
 ```{r clearance_viz}
+
+this_param_df %>%
+  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
+  inner_join(combined_clearance_df) %>%
+  mutate(CLtot.nonrest = CLtot_Fgutabs.tkstats * Fabsgut.nonrestrictive,
+         CLtot.rest = CLtot_Fgutabs.tkstats * Fabsgut.restrictive) %>%
+  pivot_longer(cols = c(restrictive_clearance, nonrestrictive_clearance,
+                        CLtot.nonrest, CLtot.rest),
+               names_to = "Source",
+               values_to = "Clearance") %>%
+  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
+  geom_point() +
+  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
+  theme_bw() +
+  coord_cartesian(xlim = c(0.0001, 1000)) +
+  scale_x_log10()
+
+this_param_df %>%
+  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
+  inner_join(combined_clearance_df) %>%
+  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
+         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
+  pivot_longer(cols = c(CLtot_Fgutabs.tkstats,
+                        rest_fgutabs, nonrest_fgutabs),
+               names_to = "Source",
+               values_to = "Clearance") %>%
+  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
+  geom_point() +
+  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
+  theme_bw() +
+  coord_cartesian(xlim = c(0.000001, 100000)) +
+  scale_x_log10()
+
+this_param_df %>%
+  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
+  inner_join(combined_clearance_df) %>%
+  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
+         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
+   mutate(AD_restrictive = abs(CLtot_Fgutabs.tkstats - rest_fgutabs),
+         AD_nonrestrictive = abs(CLtot_Fgutabs.tkstats - nonrest_fgutabs),
+         rough_determination = ifelse(
+           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
+             CLtot.tkstats <= nonrest_fgutabs,
+           "Restrictive", "Possibly non-Restrictive"
+         )) %>% 
+  dplyr::ungroup() %>% View()
+
 clearance_guess <- combined_clearance_df %>%

### 2025-01-30 data-raw/RestrictiveClearance_comparison.Rmd
Added relative difference for Css figures and comments to RestrictiveClearance_comparison.Rmd

@@
 devtools::load_all()
-library(tidyverse)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
 library(ctxR)
@@
 library(reticulate)
+library(patchwork)
 source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
+```
+
+We first want to see how many chemicals are in either _httk_ or _invivoPKfit_
+
+```{r venn_diagrams}
+member_list <- list(
+  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
+                                species = "human",
+                                model = "gas_pbtk",
+                                median.only = TRUE,
+                                physchem.exclude = TRUE,
+                                suppress.messages = TRUE)) %>% 
+    suppressWarnings(),
+  cvt = cvt %>% 
+    filter(species %in% c("human", "rat"),
+           conc_medium_normalized == "plasma") %>%
+    pull(analyte_dtxsid)
+)
+
+ggvenn(member_list, fill_color = c("white", "white"))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "httk_vs_CvT_VennDiagram_human.png"),
+       bg = "white",
+       height = 3, width = 5
+)
+
+target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
+
+filter_targets <- function(.data) {
+  stopifnot("Chemical" %in% names(.data))
+  dplyr::filter(.data = .data, Chemical %in% target_chems)
+}
 ```
@@
 ```{r quick-fit}
+
 # Only use plasma for simplicity
-this_pk <- pk(cvt %>% filter(conc_medium_normalized == "plasma")) +
+this_pk <- pk(cvt %>% 
+                dplyr::filter(conc_medium_normalized == "plasma")
+              ) +
   settings_optimx(method = "bobyqa") +
@@
 
-We first want to see how many chemicals are in either _httk_ or _invivoPKfit_
-
-```{r venn_diagrams}
-member_list <- list(
-  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
-                                species = "human",
-                                model = "gas_pbtk",
-                                median.only = TRUE,
-                                physchem.exclude = TRUE,
-                                suppress.messages = TRUE)) %>% 
-    suppressWarnings(),
-  cvt = cvt %>% 
-    filter(species %in% c("human", "rat"),
-           conc_medium_normalized == "plasma") %>%
-    pull(analyte_dtxsid)
-)
-
-ggvenn(member_list, fill_color = c("white", "white"))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "httk_vs_CvT_VennDiagram_human.png"),
-       bg = "white",
-       height = 3, width = 5
-)
-
-target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
-```
-
 ## Lipinski's Rules
@@
 ```{r lipinksi_alluvial}
+
 target_chem_summary <- target_chem_info %>%
@@
 
-all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds)
+all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
+  filter_targets()
 
 this_nonflat_winmodel <- get_winning_model(this_pk) %>%
-  filter(model %in% c("model_1comp", "model_2comp"))
+  filter(model %in% c("model_1comp", "model_2comp")) %>%
+  filter_targets()
 
 winning_preds <- predict(this_pk) %>%
-  semi_join(this_nonflat_winmodel) %>%
+  semi_join(this_nonflat_winmodel) %>% # The targets already filtered here
   distinct(Chemical, Species, Chemical_Name,
@@
   geom_point(color = "green4") +
-  geom_point(aes(y = RMSLE_nonrestrictive), shape = 4, size = 0.5) +
+  geom_point(aes(y = RMSLE_nonrestrictive), shape = 6, size = 0.5) +
   geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
@@
              scales = "free_x", space = "free_x") +
+  labs(y = "RMSLE") +
   theme_bw() +
@@
 
+# Number of chemicals we have RMSLE's for
+combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()
+
 ```
@@
 this_rll_probs <- AIC(this_pk) %>%
+  filter_targets() %>%
   distinct(Chemical, Species, model, AIC) %>%
@@
 this_winmodel <- get_winning_model(this_pk) %>%
-    filter(Chemical %in% target_chems)
+    filter_targets()
 # How many overlapping chemicals have winning models that aren't flat?
@@
 ) %>%
+  filter_targets() %>%
   rename(CLtot_Fgutabs.tkstats = `CLtot/Fgutabs.tkstats`) %>%
@@
     )
-# 46 chemicals have valid total clearance
-# 144 chemicals have valid total clearance/Fgutabs
+# 83 chemicals have valid total clearance
+# 180 chemicals have valid total clearance/Fgutabs
 # 5 chemicals have only valid total clearance and no valid total clearance/Fgutabs
@@
   css_httk_batch(this_param_nrest_l, restrictive = FALSE)
-) %>%
+)
+# Chart with relative differences (think steps) of Css between clearance types
+this_css_df %>%
+  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
+  count(relative_difference == 0, Css_httk_r == 0) # 31 Chemicals have zero difference
+###
+this_css_df %>%
+  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
+  filter(relative_difference > 0) %>%
+  ggplot(aes(x = forcats::fct_reorder(Chemical,
+                                      relative_difference, .desc = FALSE))) +
+  geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r)) +
+  labs(title = "Differences between restrictive & nonrestrictive clearance",
+       y = "Css\n(mg/L)", x = "Chemicals") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks = element_blank(),
+        panel.grid.major.x = element_blank(),
+        plot.title = element_text(hjust = 0.5))
+
+this_css_df %>%
+  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
+  filter(relative_difference > 0) %>%
+  ggplot(aes(x = forcats::fct_reorder(Chemical,
+                                      relative_difference))) +
+  geom_point(aes(size = relative_difference), y = 0, alpha = 0.2, shape = 16) +
+  annotate(x = 1, y = 150 ,label = "Min: 0 mg/L\n31 Chemicals", geom = "text") +
+  annotate(x = 140, y = 150 ,label = "Max: 30 mg/L\n", geom = "text") +
+  scale_y_continuous(limits = c(-150,150)) +
+  scale_size_area(max_size = 40) +
+  coord_cartesian(clip = "off") +
+  theme_void() +
+  theme(legend.position = "none",
+        plot.margin = unit(c(2,2,1,2), units = "inches"))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Css_difference_httk_inkblot.png"),
+       bg = "white",
+       height = 5, width = 7)
+###
+
+this_css_df <- this_css_df %>%
   inner_join(this_tkstats) %>%
@@
     levels = c("Above", "Between", "Below")
-  ), Chemical = factor(Chemical) %>% fct_reorder(Css_httk_r)
-  )
+  ), Chemical = factor(Chemical) %>% forcats::fct_reorder(Css_httk_r)
+  ) %>%
+  mutate(nearest_clearance = factor(
+    case_when(
+      between(log2(Css.tkstats),
+              log2(Css_httk_r)-1, log2(Css_httk_r)+1) |
+        (comparison_group_Css == "Above" &
+           log2(Css.tkstats) <= log2(Css_httk_r)+2) ~ "Restrictive",
+      between(log2(Css.tkstats),
+              log2(Css_httk_nr)-1, log2(Css_httk_nr)+1) |
+        comparison_group_Css == "Below" ~ "NonRestrictive",
+      .default = "Out of Range"
+    )
+  ))
 
@@
   ) +
-  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
+  geom_point(aes(y = Css.tkstats, shape = Route,
+                 color = nearest_clearance)) +
   facet_grid(rows = vars(comparison_group_Css),
@@
   scale_shape_manual(values = c(0,1)) +
+  scale_color_manual(values = c("magenta3", "green4", "black"),
+                     name = "Within 2-fold\nof clearance:",
+                     ) +
   theme_bw() +
@@
         axis.ticks.x = element_blank(),
-        panel.grid = element_blank())
+        panel.grid = element_blank()) +
+  guide_area() +
+  plot_layout(widths = c(8,1))
 
@@
                          "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_comparison_fullChart.png"),
+                         "CURRENT_", "Css_comparison_2foldclearancefullChart.png"),
        bg = "white",
-       height = 4, width = 8
-)
-
-```
-
-```{r}
+       height = 5, width = 10
+)
+
 this_css_df %>% 
-  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
+  group_by(Chemical) %>%
+  count(nearest_clearance) %>%
+  filter(nearest_clearance != "Out of Range") %>% View()
+
+```
+
+Overwhelmingly, the results of this is a Restrictive clearance model...
+however it is important to flag
+
+```{r Css_CLint}
+this_css_clint_df <- this_css_df %>%
+  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats,
+           nearest_clearance, comparison_group_Css) %>%
   filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
@@
                        ))) %>%
-  mutate(CLint = log10(CLint + 1)) %>%
+  dplyr::filter(CLint > 0)
+
+this_css_clint_df %>%
+  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
   ggplot(aes(x = CLint)) +
@@
   ) +
-  scale_y_log10(name = "C<sub>SS</sub>") + 
-  labs(x = "CL<sub>int</sub>") +
-  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
-  scale_shape_manual(values = c(0,1)) +
+  scale_y_log10(name = "C<sub>ss</sub>") + 
+  scale_x_log10(name = "CL<sub>int</sub>") +
+  geom_point(aes(y = Css.tkstats, 
+                 fill = `Mass <= 500 Da`,
+                 shape = Route,
+                 color = nearest_clearance)) +
+  facet_grid(rows = vars(nearest_clearance)) +
+  scale_color_manual(values = c("magenta3", "green4", "black"),
+                     guide = "none") +
+  scale_shape_manual(values = c(21,22)) +
+  scale_fill_manual(values = c("white", "grey5")) +
+  guides(fill = guide_legend(override.aes = list(shape = 21))) +
   theme_bw() +
@@
                          "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_x_CLint.png"),
+                         "CURRENT_", "Css_x_CLint_wNearestClearanceGrid.png"),
        bg = "white",
-       height = 4, width = 8
-)
+       height = 6, width = 10
+)
+
+this_css_clint_df %>%
+  # group_by(Route) %>%
+  group_modify(~broom::tidy(lm(Css.tkstats ~ nearest_clearance + CLint, data = .x)))
+
 ```
@@
   inner_join(this_css_df) %>%
-  ggplot(aes(x = fct_reorder(Chemical, Css_httk_r))) +
+  filter_targets() %>%
+  ggplot(aes(x = forcats::fct_reorder(Chemical, Css_httk_r))) +
   geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
@@
   scale_shape_manual(values = c(0,1)) +
-  scale_color_viridis_b(option = "viridis", 
-                        guide = guide_colorbar(position = "bottom")) +
+  scale_color_viridis_b(option = "viridis") +
   labs(subtitle = "RMSLE for invivoPKfit compared to httk predictions",
@@
         panel.grid = element_blank(),
-        legend.title = element_text(vjust = 0.8))
+        legend.title = element_text(vjust = 0.8)) +
+  guide_area() +
+  plot_layout(widths = c(8,1))
 
@@
        height = 5, width = 10
+)
+
+```
+
+First, there are about 80 chemicals which have a `CLtot.tkstats` which may
+give us some idea of the clearance alongside the _inverse confidence_ metric.
+
+```{r CLtot_subset}
+
+this_tkstats %>%
+  inner_join(this_httk_clearance_df) %>%
+  inner_join(combined_model_weights) %>%
+  filter(!is.na(CLtot.tkstats)) %>%
+  mutate(comparison_CLtot = factor(
+    case_when(
+    between(log2(CLtot.tkstats), 
+            log2(restrictive_clearance)-1,
+            log2(restrictive_clearance)+1) ~ "Restrictive",
+    between(log2(CLtot.tkstats), 
+            log2(nonrestrictive_clearance)-1,
+            log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
+    between(CLtot.tkstats,
+            restrictive_clearance, nonrestrictive_clearance) ~ "Between",
+    .default = "Out of Range"
+  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of Range")
+  )) %>%
+  ggplot(aes(forcats::fct_reorder(Chemical,
+                          gamma_weight))) +
+  geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
+             shape = 21) +
+  geom_linerange(aes(ymin = restrictive_clearance, 
+                     ymax = nonrestrictive_clearance)) +
+  geom_point(aes(y = restrictive_clearance),
+             shape = 2, size = 0.8) + # Note that this is the lower value
+  geom_point(aes(y = nonrestrictive_clearance),
+             shape = 6, size = 0.8) +
+  scale_fill_viridis_b(option = "viridis", 
+                        guide = guide_colorbar(position = "bottom"),
+                       limits = c(0,1.5)) +
+  scale_y_log10() +
+  facet_grid(cols = vars(comparison_CLtot),
+             scales = "free_x",
+             space = "free_x") +
+  labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.title = element_text(vjust = 0.8))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
+       bg = "white",
+       height = 4, width = 8
+)
+
+```
+
+```{r CLtot_subset_withCss}
+
+this_tkstats %>%
+  inner_join(this_httk_clearance_df) %>%
+  inner_join(combined_model_weights) %>%
+  left_join(this_css_df) %>%
+  filter(!is.na(CLtot.tkstats)) %>%
+  mutate(comparison_CLtot = factor(
+    case_when(
+      between(log2(CLtot.tkstats),log2(restrictive_clearance)-1,
+              log2(restrictive_clearance)+1) ~ "Restrictive",
+      between(log2(CLtot.tkstats),log2(nonrestrictive_clearance)-1,
+              log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
+      between(CLtot.tkstats,
+              restrictive_clearance, nonrestrictive_clearance) ~ "Between",
+      .default = "Out of range"
+  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of range"))) %>%
+  ggplot(aes(forcats::fct_reorder(Chemical,
+                          gamma_weight))) +
+  geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
+             shape = 21) +
+  geom_linerange(aes(ymin = restrictive_clearance, 
+                     ymax = nonrestrictive_clearance)) +
+  geom_point(aes(y = restrictive_clearance),
+             shape = 4, size = 0.8) + # Note that this is the lower value
+  geom_point(aes(y = nonrestrictive_clearance),
+             shape = 4, size = 0.8) +
+  scale_fill_viridis_b(option = "viridis", 
+                        guide = guide_colorbar(position = "bottom")) +
+  scale_y_log10() +
+  facet_grid(cols = vars(comparison_CLtot),
+             scales = "free_x") +
+  labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence",
+       subtitle = "Estimates within 20% of in vitro modelled predictions") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.title = element_text(vjust = 0.8))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
+       bg = "white",
+       height = 4, width = 8
 )
@@
 
-Notes:
+## Notes:
 Look at Css values for restrictive/nonrestrictive (httk solutions)
 AICs for models
+Important to look for potential reflective metrics and find associations 
+(CLtot, Css, fup) and also look at physiochemical properties that may create
+some distinctions once a prediction of clearance type is made.
+
+So the model will be something like `CLtot ~ Css + fup + Clearance_Type + GFR`
+and we can re-simplify certain things into `halflife` and `kelim` to see
+how likely this would be in a simple, classical PK model.
 

### 2025-02-07 data-raw/RestrictiveClearance_comparison.Rmd
Added clustering chunk and began re-writing analysis steps alongside the respective chunk.

@@
 this_pk <- do_prefit(this_pk)
-this_pk <- do_fit(this_pk, n_cores = 14)
+this_pk <- do_fit(this_pk, n_cores = 12)
 ```
@@
 - [Add More Here]
-
-Steps in the analysis:
-
-1. Get chemicals + species combinations in CvTdb that have _httk_ predictions.
-2. Safely get parameters, clearance, and solutions for each of these groups.
-3. Compare clearances from _httk_ with those from _invivoPKfit_.
-4. Compare $f_{up}$ for subset of data with total values available via _httk_.
-5. Use new _clearance-aware_ optimization of 1-compartment parameters to
-benchmark _httk_ solutions.
-6. Estimate the fraction unbound in plasma for chemicals with rat data,
-for those same chemicals with human data for Clint and Fup. 
-Begin with the assumption that there is restrictive clearance, those chemicals
-that do not change when optimized (and produce reasonable fits) are likely to
-be _restrictively cleared_, whereas those that increase Fup during maximum
-likelihood estimation are _possibly non-restrictively cleared_. 
-7. Other factors such as renal clearance may play a role in those cases.
-Validate the clearance estimate by measuring changes in predicted clearance.
-Important to identify whether there seems to be a "fraction missing".
-8. Wrap the previous steps into attempts to identify true positive
-categorizations for Restrictive and Potentially Non-Restrictively metabolized
-chemicals (include Lipinski's Rule of 5 too).
-9. Implement a _slow_ PBPK model that optimizes $f_{up}$ and $CL_{int}$ under
-restrictive and non-restrictive clearance conditions. Test whether these have a
-substantial difference from initial values. Use `coef_sd()` to evaluate
-uncertainty of these parameter estimates for a larger share of chemicals.
-10. Compare the results of 9 with the putative/predicted clearance from 1-6.
 
@@
        bg = "white",
-       height = 4, width = 6
+       height = 5, width = 6
 )
@@
        bg = "white",
-       height = 4, width = 8
+       height = 4.5, width = 8
 )
@@
         plot.title = element_text(hjust = 0.5))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Css_difference_httk_lineplot.png"),
+       bg = "white",
+       height = 5, width = 7)
 
@@
 
-Now I will try to triangulate the model weights witht the Css estimates.
+Now I will try to triangulate the model weights with the Css estimates.
 
@@
 ```{r CLtot_subset}
-
-this_tkstats %>%
+enhanced_tkstats <- this_tkstats %>%
   inner_join(this_httk_clearance_df) %>%
@@
   ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of Range")
-  )) %>%
+  ))
+enhanced_tkstats %>%
   ggplot(aes(forcats::fct_reorder(Chemical,
@@
   labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence",
-       subtitle = "Estimates within 20% of in vitro modelled predictions") +
+       subtitle = "Estimates within 2-fold of in vitro modelled predictions") +
   theme_bw() +
@@
 )
+
+```
+
+```{r rudimentary_clustering}
+
+# Set up a data.frame that has chemical, Css difference, Funbound z-score,
+# nearest_clearance (using Css), and model weight
+this_fupZ_df <- this_param_df %>% select(Chemical, Funbound.plasma.restrictive) %>%
+  mutate(Fup_Z = as.vector(scale(sqrt(Funbound.plasma.restrictive))),
+         .keep = "unused")
+
+this_dist_prepdf <- this_css_df %>% select(Chemical, model, Route,
+                       nearest_clearance, comparison_group_Css,
+                       Css_httk_r, Css_httk_nr) %>%
+  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr),
+         .keep = "unused") %>%
+  inner_join(combined_model_weights %>%
+               select(Chemical, Species, gamma_weight)) %>%
+  inner_join(enhanced_tkstats %>%
+               select(Chemical, Species, comparison_CLtot)) %>%
+  inner_join(this_fupZ_df) %>%
+  distinct() %>%
+  mutate(ID = paste(Chemical, Species, model, Route, sep = "."), .keep = "unused")
+
+this_dist_prepdf %>%
+ggplot(aes(x = gamma_weight, y = Fup_Z, color = relative_difference)) + 
+  geom_point() +
+  scale_color_viridis_c() +
+  facet_grid(cols = vars(comparison_CLtot))
 

### 2025-02-11 data-raw/RestrictiveClearance_comparison.Rmd
Included pka into ctxR data loading. Also loaded RData for binding affinity.

@@
 
+```{r load_Kd}
+load(paste0(Sys.getenv("OD_DIR"),
+            "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
+)
+```
+
 ## Lipinski's Rules
@@
                                               rate_limit = 1L) %>%
-  filter(name == "LogKow: Octanol-Water") %>% distinct()
+  filter(name %in% c("LogKow: Octanol-Water",
+                     "pKa Acidic Apparent",
+                     "pKa Basic Apparent")) %>% distinct()
 
@@
   ggplot(aes(x = source, y = value)) +
-  geom_point() +
+  geom_violin() +
   geom_line(aes(group = dtxsid), color = "grey10", alpha = 0.1) +
   geom_hline(yintercept = 5, linetype = "longdash") +
-  facet_grid(cols = vars(propType), scales = "free_x") +
+  facet_grid(cols = vars(propType), scales = "free_x",
+             rows = vars(name)) +
+  scale_y_log10() +
   theme_bw() +
@@
 
+target_chem_pw_predicted <- target_chem_properties %>%
+  filter(source == "ACD/Labs") %>%
+  distinct(propertyId, value, dtxsid) %>%
+  pivot_wider(names_from = propertyId,
+              values_from = value)
+
 ```
@@
 py_h_acceptors = [Chem.Descriptors.NHOHCount(x) for x in mol_from_smiles]
+py_tpsa = [Chem.Descriptors.TPSA(x) for x in mol_from_smiles]
 ```

### 2025-02-18 data-raw/RestrictiveClearance_comparison.Rmd
Added diff_log_cvt() call for oral and iv. Included Kd affinity plots in main Rmd.

@@
             "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
+)
+new.raw.httk.data %>%
+  distinct(DTXSID, Affinity.Kd.Med, Affinity.Kd.Low, Affinity.Kd.High,
+           Fit) %>%
+  na.omit() %>%
+  mutate(Target_Chemical = (DTXSID %in% target_chems)) %>%
+ggplot(
+       aes(
+         x = forcats::fct_reorder(DTXSID, Affinity.Kd.Low)
+         )) +
+  geom_linerange(aes(
+    ymin  = Affinity.Kd.Low,
+    ymax = Affinity.Kd.High,
+    color = Target_Chemical
+  ), alpha = 0.4) +
+  geom_point(aes(
+    y = Affinity.Kd.Med, color = Target_Chemical
+  ), size = 0.75) +
+  # facet_grid(cols = vars(Fit), space = "free_x", scales = "free_x") +
+  scale_y_log10(labels = scales::label_log(digits = 1)) +
+  scale_color_manual(values = c("black", "green4")) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid = element_blank(),
+        plot.title = element_text(hjust = 0.5, face = "bold"),
+        legend.position = "bottom") +
+  labs(title = "Kd estimates across chemicals", x = NULL)
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Kd_estimates_initialsummary.png"),
+       bg = "white",
+       height = 4, width = 9
 )

### 2025-02-18 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Added diff_log_cvt() call for oral and iv. Included Kd affinity plots in main Rmd.

@@
 }
+diff_log_cvt(cvt_df)
 ```

### 2025-02-21 data-raw/RestrictiveClearance_comparison.Rmd
Included additional chemical descriptors and added relative log-likelihood calculations for restrictive/non-restrictive httk predictions.

--- 2025-02-07 data-raw/RestrictiveClearance_comparison.Rmd
@@
 library(tidyr)
+library(stringr)
 library(ggplot2)
@@
 member_list <- list(
-  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
+  httk_3comp2 = unique(get_cheminfo(info = "DTXSID",
                                 species = "human",
-                                model = "gas_pbtk",
+                                model = "3compartment2",
                                 median.only = TRUE,
@@
 
-target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
+target_chems <- intersect(member_list$cvt, member_list$httk_3comp2)
 
@@
 this_pk <- do_prefit(this_pk)
-this_pk <- do_fit(this_pk, n_cores = 12)
+this_pk <- do_fit(this_pk, n_cores = 14)
+```
+
+```{r load-other}
+# Here I want to load all other data and setup other data objects
+# Kd/binding affinity data
+load(paste0(Sys.getenv("OD_DIR"),
+            "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
+)
+
+# Chemical info and properties (averaging the latter by chemical and experimental/predicted)
+target_chem_info <- get_chemical_details_batch(DTXSID = target_chems,
+                                               rate_limit = 1L)
+target_chem_properties <- get_chem_info_batch(DTXSID = target_chems, 
+                                              rate_limit = 1L) %>%
+  filter(name %in% c("LogKow: Octanol-Water",
+                     "pKa Acidic Apparent",
+                     "pKa Basic Apparent")) %>% 
+  group_by(dtxsid, propType, propertyId) %>%
+  summarize(Mean = mean(value, na.rm = TRUE),
+            StDev = sd(value, na.rm = TRUE)) %>%
+  ungroup() %>%
+  distinct()
+
+# Bring together all chemical properties
+target_chem_pw_predicted <- target_chem_properties %>%
+  filter(propType == "predicted") %>%
+  pivot_wider(names_from = propertyId,
+              names_prefix = "pr_",
+              id_cols = dtxsid,
+              values_from = c("Mean", "StDev"))
+target_chem_pw_experimental <- target_chem_properties %>%
+  filter(propType == "experimental") %>%
+  pivot_wider(names_from = propertyId,
+              names_prefix = "ex_",
+              values_from = c("Mean", "StDev"),
+              id_cols = dtxsid)
+
+target_chem_pw_full <- full_join(
+  target_chem_pw_experimental,
+  target_chem_pw_predicted
+) %>%
+  janitor::clean_names() %>%
+  mutate(dtxsid,
+         type_logkow = ifelse(is.na(mean_ex_logkow_octanol_water),
+                              NA, "experimental"),
+         logkow = ifelse(is.na(mean_ex_logkow_octanol_water),
+                         mean_pr_logkow_octanol_water,
+                         mean_ex_logkow_octanol_water),
+         type_apKa = ifelse(is.na(mean_ex_pka_acidic_apparent),
+                            NA, "experimental"),
+         apKa = ifelse(is.na(mean_ex_pka_acidic_apparent),
+                       mean_pr_pka_acidic_apparent,
+                       mean_ex_pka_acidic_apparent),
+         type_bpKa = ifelse(is.na(mean_ex_pka_basic_apparent),
+                            NA, "experimental"),
+         bpKa = ifelse(is.na(mean_ex_pka_basic_apparent),
+                       mean_pr_pka_basic_apparent,
+                       mean_ex_pka_basic_apparent),
+         .keep = "unused") %>%
+  mutate(type_logkow = ifelse(!is.na(logkow) & is.na(type_logkow),
+                              "predicted",
+                              ifelse(type_logkow == "experimental",
+                                     "experimental", NA)),
+         type_apKa = ifelse(!is.na(apKa) & is.na(type_apKa),
+                            "predicted",
+                            ifelse(type_apKa == "experimental",
+                                     "experimental", NA)),
+         type_bpKa = ifelse(!is.na(bpKa) & is.na(type_bpKa),
+                            "predicted",
+                            ifelse(type_bpKa == "experimental",
+                                     "experimental", NA))) %>%
+  mutate(logkow_sd = ifelse(type_logkow == "experimental",
+                            st_dev_ex_logkow_octanol_water,
+                            st_dev_pr_logkow_octanol_water),
+         apKa_sd = ifelse(type_apKa == "experimental",
+                          st_dev_ex_pka_acidic_apparent,
+                          st_dev_pr_pka_acidic_apparent),
+         bpKa_sd = ifelse(type_bpKa == "experimental",
+                          st_dev_ex_pka_basic_apparent,
+                          st_dev_pr_pka_basic_apparent)) %>%
+  select(-starts_with("st_dev")) %>%
+  distinct()
+# Remove the parts of this final dataset
+rm(target_chem_pw_experimental, target_chem_pw_predicted)
+
+# Predictions from httk(code retained but not run after 2.20.2025)
+restrictive_preds <- get_httk_preds(
+  parameters = this_param_rest_l,
+  pk_obj = this_pk,
+  species = c("rat", "human")
+) %>% rename_with(
+  .fn = ~paste0(.x, "_restrictive"),
+  .cols = starts_with("httk_")
+)
+
+nonrestrictive_preds <- get_httk_preds(
+  parameters = this_param_nrest_l,
+  pk_obj = this_pk,
+  species = c("rat", "human")
+) %>% rename_with(
+  .fn = ~paste0(.x, "_nonrestrictive"),
+  .cols = starts_with("httk_")
+)
+
+names(restrictive_preds)
+
+all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
+  filter_targets()
+rm(restrictive_preds, nonrestrictive_preds)
+# 
+readr::write_csv(all_httk_preds,
+                 file = paste0(Sys.getenv("FIG_DIR"),
+                               "RestrictiveClearance_Analysis/",
+                               "CURRENT_all_httk_preds.csv"))
+
+all_httk_preds <- readr::read_csv(file = paste0(Sys.getenv("FIG_DIR"), 
+                                                "RestrictiveClearance_Analysis/",
+                                                "CURRENT_all_httk_preds.csv"))
+
+this_nonflat_winmodel <- get_winning_model(this_pk) %>%
+  filter(model %in% c("model_1comp", "model_2comp")) %>%
+  filter_targets()
+
+# Get the winning model (including flats) and only include chemicals in target_chems
+this_winmodel <- get_winning_model(this_pk) %>%
+    filter_targets()
+
+winning_preds <- predict(this_pk) %>%
+  semi_join(this_nonflat_winmodel) %>% # The targets already filtered here
+  distinct(Chemical, Species, Chemical_Name,
+           model, method, Dose, Media, Route, Reference, pLOQ, Time,
+           N_Subjects, Conc, Conc_est)
+
+# TKstats for 1-/2-compartment model
+this_tkstats <- eval_tkstats(this_pk,
+                             model = c("model_1comp", "model_2comp"),
+                             finite_only = TRUE,
+                             dose_norm = TRUE
+) %>%
+  filter_targets()
+colnames(this_tkstats) <- gsub("/", "_", colnames(this_tkstats))
+this_tkstats <- this_tkstats %>%
+  inner_join(this_winmodel)
+
 ```
@@
 
+```{r load_Kd}
+new.raw.httk.data %>%
+  distinct(DTXSID, Affinity.Kd.Med, Affinity.Kd.Low, Affinity.Kd.High,
+           Fit) %>%
+  na.omit() %>%
+  mutate(Target_Chemical = (DTXSID %in% target_chems)) %>%
+ggplot(
+       aes(
+         x = forcats::fct_reorder(DTXSID, Affinity.Kd.Low)
+         )) +
+  geom_linerange(aes(
+    ymin  = Affinity.Kd.Low,
+    ymax = Affinity.Kd.High,
+    color = Target_Chemical
+  ), alpha = 0.4) +
+  geom_point(aes(
+    y = Affinity.Kd.Med, color = Target_Chemical
+  ), size = 0.75) +
+  # facet_grid(cols = vars(Fit), space = "free_x", scales = "free_x") +
+  scale_y_log10(labels = scales::label_log(digits = 1)) +
+  scale_color_manual(values = c("black", "green4")) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid = element_blank(),
+        plot.title = element_text(hjust = 0.5, face = "bold"),
+        legend.position = "bottom") +
+  labs(title = "Kd estimates across chemicals", x = NULL)
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Kd_estimates_initialsummary.png"),
+       bg = "white",
+       height = 4, width = 9
+)
+```
+
 ## Lipinski's Rules
@@
 ```{r lipinksi_test_data}
-target_chem_info <- get_chemical_details_batch(DTXSID = target_chems,
-                                               rate_limit = 1L)
-target_chem_properties <- get_chem_info_batch(DTXSID = target_chems, 
-                                              rate_limit = 1L) %>%
-  filter(name == "LogKow: Octanol-Water") %>% distinct()
 
 target_chem_properties %>%
-  ggplot(aes(x = source, y = value)) +
-  geom_point() +
+  ggplot(aes(x = propType, y = Mean)) +
+  geom_violin() +
   geom_line(aes(group = dtxsid), color = "grey10", alpha = 0.1) +
   geom_hline(yintercept = 5, linetype = "longdash") +
-  facet_grid(cols = vars(propType), scales = "free_x") +
+  facet_grid(scales = "free_x",
+             rows = vars(propertyId)) +
+  scale_y_log10() +
   theme_bw() +
@@
 
+target_chem_pw_full %>%
+  ggplot(aes(x = forcats::fct_reorder(dtxsid, logkow))) +
+  geom_pointrange(aes(y = logkow, ymin = logkow - logkow_sd,
+                      ymax = logkow + logkow_sd), size = 0.1) +
+  facet_grid(cols = vars(type_logkow)) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank())
+target_chem_pw_full %>%
+  ggplot(aes(x = logkow)) +
+  geom_histogram(color = "grey50", fill = "grey5",
+                 binwidth = 1) +
+  theme_bw()
+
 ```
@@
 from rdkit.Chem import Descriptors
+from rdkit.Chem import rdMolDescriptors
 
@@
 
-py_h_donors = [Chem.Descriptors.NOCount(x) for x in mol_from_smiles]
-py_h_acceptors = [Chem.Descriptors.NHOHCount(x) for x in mol_from_smiles]
+py_h_donors = [Chem.rdMolDescriptors.CalcNumLipinskiHBD(x) for x in mol_from_smiles]
+py_h_acceptors = [Chem.rdMolDescriptors.CalcNumLipinskiHBA(x) for x in mol_from_smiles]
+py_tpsa = [Chem.rdMolDescriptors.CalcTPSA(x, False, True) for x in mol_from_smiles]
+py_rotbonds = [Chem.rdMolDescriptors.CalcNumRotatableBonds(x) for x in mol_from_smiles]
 ```
@@
   bind_cols(data.frame(H_donors = py_to_r(py$py_h_donors),
-                       H_acceptors = py_to_r(py$py_h_acceptors))
+                       H_acceptors = py_to_r(py$py_h_acceptors),
+                       TPSA = py_to_r(py$py_tpsa),
+                       Rot_Bonds = py_to_r(py$py_rotbonds))
             ) %>%
   left_join(
-    target_chem_properties %>%
-      filter(source == "ACD/Labs Consensus") %>%
-      distinct(dtxsid, source, value)
-  ) %>%
-  rename(LogKow = value)
+    target_chem_pw_full
+  ) %>%
+  rowwise() %>%
+  mutate(logD_7.4 = httk::calc_dow(dtxsid = dtxsid, pH = 7.4))
 
 target_chem_lipinski <- target_chem_summary %>%
-  select(-c(smiles, source)) %>%
+  select(-c(smiles)) %>%
   group_by(dtxsid) %>%
@@
           "H-acceptors < 10" = (H_acceptors < 10),
-          "logP < 5" = (LogKow < 5),
+          "logP < 5" = (logkow < 5),
           .keep = "none") %>%
@@
 )
+
+# Molecular descriptors in bins
+bin_size <- 2
+logP_plot <- target_chem_summary %>%
+  distinct(dtxsid, logkow) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(logP_bin = factor(logkow %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = logP_bin, y = Funbound.plasma)) +
+  labs(x = "logKow", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 50
+TPSA_plot <- target_chem_summary %>%
+  distinct(dtxsid, TPSA) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(TPSA_bin = factor(TPSA %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = TPSA_bin, y = Funbound.plasma)) +
+  labs(x = "Topological Polar Surface Area", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 2
+RotBond_plot <- target_chem_summary %>%
+  distinct(dtxsid, Rot_Bonds) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(Rot_Bonds_bin = factor(Rot_Bonds %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = Rot_Bonds_bin, y = Funbound.plasma)) +
+  labs(x = "Rotatable Bonds", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 150
+MW_plot <- target_chem_summary %>%
+  distinct(dtxsid, monoisotopicMass) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(MW_bin = factor(monoisotopicMass %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = MW_bin, y = Funbound.plasma)) +
+  labs(x = "Molecular Mass", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 4
+HBA_plot <- target_chem_summary %>%
+  distinct(dtxsid, H_acceptors) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(HBA_bin = factor(H_acceptors %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = HBA_bin, y = Funbound.plasma)) +
+  labs(x = "Hydrogen bond acceptors", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 2
+HBD_plot <- target_chem_summary %>%
+  distinct(dtxsid, H_donors) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(HBD_bin = factor(H_donors %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = HBD_bin, y = Funbound.plasma)) +
+  labs(x = "Hydrogen bond donors", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 200
+target_chem_summary %>%
+  distinct(dtxsid, logD_7.4) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(logD_bin =  factor(logD_7.4 %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = logD_bin, y = Funbound.plasma)) +
+  labs(x = "logD_7.4", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+(MW_plot + TPSA_plot + HBA_plot) / (logP_plot + RotBond_plot + HBD_plot)
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "PhysChemProperties_rdkit.png"),
+       bg = "white",
+       height = 6, width = 8
+)
+
 ```
@@
 
-```{r httk_predictions}
-restrictive_preds <- get_httk_preds(
-  parameters = this_param_rest_l,
-  pk_obj = this_pk,
-  species = c("rat", "human")
-) %>% rename_with(
-  .fn = ~paste0(.x, "_restrictive"),
-  .cols = starts_with("httk_")
-)
-
-nonrestrictive_preds <- get_httk_preds(
-  parameters = this_param_nrest_l,
-  pk_obj = this_pk,
-  species = c("rat", "human")
-) %>% rename_with(
-  .fn = ~paste0(.x, "_nonrestrictive"),
-  .cols = starts_with("httk_")
-)
-
-all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
-  filter_targets()
-
-this_nonflat_winmodel <- get_winning_model(this_pk) %>%
-  filter(model %in% c("model_1comp", "model_2comp")) %>%
-  filter_targets()
-
-winning_preds <- predict(this_pk) %>%
-  semi_join(this_nonflat_winmodel) %>% # The targets already filtered here
-  distinct(Chemical, Species, Chemical_Name,
-           model, method, Dose, Media, Route, Reference, pLOQ, Time,
-           N_Subjects, Conc, Conc_est)
+```{r httk_pr_rmsle}
 
@@
 combined_preds <- all_httk_preds %>%
+  mutate(Reference = as.character(Reference)) %>%
   left_join(winning_preds) %>%
@@
   ) %>%
-  group_by(Chemical, Species) %>%
+  group_by(Chemical, Species, Route) %>%
   summarize(RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
@@
         axis.ticks.x = element_blank(),
-        panel.grid = element_blank())
+        panel.grid = element_blank(),
+        axis.title = element_text(size = 14),
+        strip.text = element_text(size = 12))
 
@@
        bg = "white",
-       height = 4.5, width = 8
-)
-
-# Number of chemicals we have RMSLE's for
+       height = 3.8, width = 10
+)# Number of chemicals we have RMSLE's for
 combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()
@@
 ```{r relative-likelihood}
+
+# AIC and relative likelihood
 this_rll_probs <- AIC(this_pk) %>%
@@
 
+# LL from pre-calculated httk predictions
+restrictive_ll <- all_httk_preds %>% 
+  rename(Conc_est = httk_Preds_restrictive,
+         Time_trans = Time) %>%
+  select(!httk_Preds_nonrestrictive) %>%
+  distinct() %>%
+  group_by(Chemical, Species) %>%
+  nest(.key = "observations") %>%
+  inner_join(coef(this_pk) %>% semi_join(this_winmodel) %>% distinct()) %>%
+  rowwise() %>%
+  mutate(log_likelihood = log_likelihood(
+    par = coefs_vector,
+    data = observations,
+    data_sigma_group = observations$data_sigma_group,
+    dose_norm = FALSE,
+    log10_trans = FALSE,
+    negative = FALSE,
+    includes_preds = TRUE,
+    detect
+  )) %>%
+  select(!observations) %>%
+  mutate(model = "httk_3comp2_restrictive",
+         AIC = -2 * log_likelihood)
+
+nonrestrictive_ll <- all_httk_preds %>% 
+  rename(Conc_est = httk_Preds_nonrestrictive,
+         Time_trans = Time) %>%
+  select(!httk_Preds_restrictive) %>%
+  distinct() %>%
+  group_by(Chemical, Species) %>%
+  nest(.key = "observations") %>%
+  inner_join(coef(this_pk) %>% semi_join(this_winmodel) %>% distinct()) %>%
+  rowwise() %>%
+  mutate(log_likelihood = log_likelihood(
+    par = coefs_vector,
+    data = observations,
+    data_sigma_group = observations$data_sigma_group,
+    dose_norm = FALSE,
+    log10_trans = FALSE,
+    negative = FALSE,
+    includes_preds = TRUE,
+    detect
+  )) %>%
+  select(!observations) %>%
+  mutate(model = "httk_3comp2_nonrestrictive",
+         AIC = -2 * log_likelihood) # Simple formula when there are no optimized params
+
+httk_AIC <- bind_rows(restrictive_ll, nonrestrictive_ll)
+
+httk_AIC %>%
+  distinct(Chemical, Species, model, AIC) %>%
+  pivot_wider(names_from = model, values_from = AIC) %>%
+  rowwise() %>% 
+  mutate(minAIC = min(c_across(starts_with("httk_")), na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(across(starts_with("httk_"), \(x) {
+    signif(exp((minAIC - x)/2) * 100, 4)
+  })) %>%
+  mutate(across(starts_with("httk_"), \(x) {
+    ifelse(x < 1E-6, 0, x)
+  })) %>% View()
+
 ```
@@
 
+combined_model_weights %>%
+  ggplot(aes(x = gamma_weight, color = rmsle_comparison_group)) +
+  geom_freqpoly() +
+  labs(x = "Inverse Confidence",
+       color = "RMSLE relative to httk predictions") +
+  facet_grid(rows = vars(rmsle_comparison_group)) +
+  theme_bw()
+
 ```
@@
 ```{r combine_tkstats}
-# Get the winning model and only include chemicals in target_chems
-this_winmodel <- get_winning_model(this_pk) %>%
-    filter_targets()
 # How many overlapping chemicals have winning models that aren't flat?
@@
 ) # 153 = 97 1-compartment + 56 2-compartment
-
-this_tkstats <- eval_tkstats(this_pk,
-                             model = c("model_1comp", "model_2comp"),
-                             finite_only = TRUE,
-                             dose_norm = TRUE
-) %>%
-  filter_targets() %>%
-  rename(CLtot_Fgutabs.tkstats = `CLtot/Fgutabs.tkstats`) %>%
-  distinct(Chemical, Species, method, model, Dose, Route, Media,
-           CLtot.tkstats, CLtot_Fgutabs.tkstats, halflife.tkstats, Css.tkstats) %>%
-  inner_join(this_winmodel)
 
@@
 )
+
+# Table
+this_css_df %>%
+  count(Css_httk_r == Css_httk_nr,
+        Css_httk_r - Css_httk_nr < 0.1 & Css_httk_r - Css_httk_nr > 0,
+        Css_httk_r - Css_httk_nr >= 0.1) %>%
+  rename("No difference" = "Css_httk_r == Css_httk_nr",
+         "Less than 0.1" = "Css_httk_r - Css_httk_nr < 0.1 & Css_httk_r - Css_httk_nr > 0",
+         "At least 0.1" = "Css_httk_r - Css_httk_nr >= 0.1")
+
 # Chart with relative differences (think steps) of Css between clearance types
@@
                                       relative_difference, .desc = FALSE))) +
-  geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r)) +
+  geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r),
+                 linewidth = 1.25) +
   labs(title = "Differences between restrictive & nonrestrictive clearance",
-       y = "Css\n(mg/L)", x = "Chemicals") +
+       y = "Difference in Css\n(mg/L)", x = "Chemicals") +
   theme_bw() +
@@
         panel.grid.major.x = element_blank(),
-        plot.title = element_text(hjust = 0.5))
+        plot.title = element_text(hjust = 0.5, size = 18),
+        axis.title = element_text(size = 14),
+        axis.text.y = element_text(size = 10, color = "black"))
 
@@
        bg = "white",
-       height = 5, width = 7)
+       height = 3.5, width = 11.5)
 
@@
 ###
-
-this_css_df <- this_css_df %>%
-  inner_join(this_tkstats) %>%
-  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
-  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
-  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
-  mutate(comparison_group_Css = factor(
-    case_when(
-      between(Css.tkstats, Css_httk_r, Css_httk_nr) |
-        between(Css.tkstats, Css_httk_nr, Css_httk_r) ~ "Between",
-      Css.tkstats < Css_httk_r & Css.tkstats < Css_httk_nr ~ "Below",
-      Css.tkstats > Css_httk_r & Css.tkstats > Css_httk_nr ~ "Above"),
-    levels = c("Above", "Between", "Below")
-  ), Chemical = factor(Chemical) %>% forcats::fct_reorder(Css_httk_r)
-  ) %>%
-  mutate(nearest_clearance = factor(
-    case_when(
+```
+
+The next step is to assess Css, halflife, and total clearance
+deciding whether the invivoPKfit evidence points to more restrictive or non-restrictive
+clearance. To do this we will create a dummy variable that will accumulate
+the information.
+
+  Restrictive  = -1  
+  Nonrestrictive = +1  
+  Undetermined = 0
+
+We will keep track of this with labeled columns and sum at the end.
+
+```{r full-eval}
+this_evaluated_df <- this_css_df %>%
+  inner_join(this_tkstats) %>% # Css
+  inner_join(this_httk_clearance_df) %>% # CLtot and halflife
+  inner_join(data.frame(Chemical = names(this_param_rest_l),
+                        CLint = vapply(names(this_param_rest_l),
+                                       \(x) {
+                                         this_param_rest_l[[x]][["Clint"]]
+                                       },
+                                       FUN.VALUE = numeric(1L)
+                        ))) %>%
+  mutate(Css_clear = case_when(
     between(log2(Css.tkstats),
-              log2(Css_httk_r)-1, log2(Css_httk_r)+1) |
-        (comparison_group_Css == "Above" &
-           log2(Css.tkstats) <= log2(Css_httk_r)+2) ~ "Restrictive",
+            log2(Css_httk_r)-1, log2(Css_httk_r)+1) &
+      abs(log2(Css.tkstats/Css_httk_r)) < abs(log2(Css.tkstats/Css_httk_nr))~ -1,
     between(log2(Css.tkstats),
-              log2(Css_httk_nr)-1, log2(Css_httk_nr)+1) |
-        comparison_group_Css == "Below" ~ "NonRestrictive",
-      .default = "Out of Range"
-    )
-  ))
+            log2(Css_httk_nr)-1, log2(Css_httk_nr)+1) ~ 1,
+    .default = 0),
+    halflife_clear = case_when(
+      between(log2(halflife.tkstats),
+              log2(restrictive_halflife)-1,
+              log2(restrictive_halflife)+1) &
+        abs(
+          log2(halflife.tkstats/restrictive_halflife)
+        ) < abs(
+          log2(halflife.tkstats/nonrestrictive_halflife)
+        ) | (nonrestrictive_halflife == restrictive_halflife) ~ -1,
+      (log2(halflife.tkstats) < log2(nonrestrictive_halflife)+1) ~ 1,
+      .default = 0
+    ),
+    CLtot_clear = case_when(
+      between(log2(CLtot.tkstats),
+              log2(restrictive_clearance)-1,
+              log2(restrictive_clearance)+1) &
+        abs(
+          log2(CLtot.tkstats/restrictive_clearance)
+        ) < abs(
+          log2(CLtot.tkstats/nonrestrictive_clearance)
+        ) ~ -1,
+      between(log2(CLtot.tkstats),
+              log2(nonrestrictive_clearance)-1,
+              log2(nonrestrictive_clearance)+1) ~ 1,
+      .default = 0
+    )
+  )
+
+evaluated_df_summary <- this_evaluated_df %>%
+  group_by(Chemical) %>%
+  summarize(CLtot_clear = median(CLtot_clear),
+            halflife_clear = median(halflife_clear),
+            Css_clear = median(Css_clear)) %>%
+  rowwise() %>%
+  mutate(clearance_sum = sum(CLtot_clear, halflife_clear, Css_clear)) %>%
+  ungroup()
+
+count(evaluated_df_summary, clearance_sum < 0, clearance_sum > 0)
 
@@
 this_css_clint_df %>%
-  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
   ggplot(aes(x = CLint)) +
@@
   geom_point(aes(y = Css.tkstats,
-                 fill = `Mass <= 500 Da`,
                  shape = Route,

### 2025-02-24 data-raw/RestrictiveClearance_comparison.Rmd
Adjusted fraction unbound comparison. Began moving some data wrangling code to beginning of document RestrictiveClearance_comparison.Rmd

@@
 
+# Fraction unbound data for target chemicals
+fup_df <- this_param_df %>%
+  distinct(Chemical, Species, forced_human_values,
+           Funbound.plasma, Funbound.plasma.adjustment, 
+           Funbound.plasma.dist) %>%
+  mutate(
+    Funbound.plasma.median = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "^\\d+\\.?\\d+e?-?\\d+(?=,)"
+    )),
+    Funbound.plasma.lower95 = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d+(?=,)"
+    )),
+    Funbound.plasma.upper95 = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d$"
+    ))
+    )
+
+human_chems <- httk::get_cheminfo(info = "DTXSID",
+                                species = "human",
+                                model = "3compartment2",
+                                median.only = TRUE,
+                                physchem.exclude = TRUE,
+                                suppress.messages = TRUE)
+human_chems <- intersect(human_chems, new.raw.httk.data$DTXSID)
+
+all_hum_rat_fups <- chem.physical_and_invitro.data %>%
+  filter(DTXSID %in% human_chems) %>%
+  select(DTXSID, Human.Funbound.plasma, Rat.Funbound.plasma) %>%
+  mutate(Rat.Funbound.plasma = as.numeric(str_extract(Rat.Funbound.plasma,
+                                                      "^([^,]+)")),
+         Human.Funbound.plasma = as.numeric(str_extract(Human.Funbound.plasma,
+                                                        "^([^,]+)"))
+         )
+
+# Get restrictive and non-restrictive parameters
+human_chems_fup <- data.frame(
+  Chemical = human_chems,
+  fup_restrictive = chem.physical_and_invitro.data$Human.Funbound.plasma[],
+                              fup_nonrestrictive = params_nr)
 ```
@@
 )
+
+kd_v_fup_plot <- new.raw.httk.data %>%
+  inner_join(all_hum_rat_fups) %>%
+  pivot_longer(cols = Human.Funbound.plasma:Rat.Funbound.plasma,
+               names_to = "Species", values_to = "httk_fup_med") %>%
+  ggplot(aes(x = Affinity.Kd.Med, y = httk_fup_med, color = Species)) +
+  geom_point(alpha = 0.5) +
+  scale_color_manual(values = c("green4", "purple2"),
+                     labels = c("Human", "Rat")) +
+  scale_x_log10(labels = scales::label_log(digits = 2)) +
+  labs(x = "Binding affinity ratio", y = "Fraction unbound\nin plasma") +
+  theme_bw() +
+  theme(legend.position = "top",
+        legend.text = element_text(size = 10),
+        legend.title = element_blank(),
+        axis.title = element_text(size = 12),
+        axis.text = element_text(size = 10))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Kd_estimates_vs_fup_multispecies.png"),
+       bg = "white",
+       height = 3, width = 5
+)
+
 ```
@@
 
-target_chem_lipinski %>%
+lipinski_plot <- target_chem_lipinski %>%
   group_by(Lipinski) %>%
@@
   expand = c(.2, .05)) +
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  labs(title = "Overwhelmingly, these chemicals passes Lipinksi's Rules of 5",
+  geom_text(stat = "stratum", aes(label = after_stat(stratum)),
+            size = 2) +
+  labs(title = "Target chemicals passing Lipinksi's Rules of 5",
        fill = "Passes Lipinksi's Rules?") +
@@
 
+lipinski_plot
 ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
@@
        bg = "white",
-       height = 5, width = 6
-)
+       height = 4, width = 5
+)
+
+chem_rell_label <- total_rel_evaluation_df %>% distinct(Chemical, ll_label) %>%
+  filter(ll_label %in% c("Restrictive", "Nonrestrictive"))
 
 # Molecular descriptors in bins
-bin_size <- 2
+bin_size <- 10
 logP_plot <- target_chem_summary %>%
+  inner_join(chem_rell_label, by = join_by(dtxsid == Chemical)) %>%
   distinct(dtxsid, logkow) %>% 
@@
   ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+target_chem_summary %>%
+  inner_join(chem_rell_label, by = join_by(dtxsid == Chemical)) %>%
+  distinct(dtxsid, logkow, TPSA, Rot_Bonds, ll_label) %>% 
+  pivot_longer(cols = c(logkow, TPSA),
+               names_to = "Parameter", values_to = "Value") %>%
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  ggplot(aes(x = Value, y = Funbound.plasma)) +
+  labs(x = "", y = "fup") +
+  facet_grid(cols = vars(Parameter),
+             rows = vars(ll_label),
+             scales = "free_x") +
+  geom_point() +
   theme_bw()
@@
   )) %>%
-  select(!observations) %>%
-  mutate(model = "httk_3comp2_restrictive",
+  select(!c(observations, coefs_vector, Time.Units, Time_trans.Units)) %>%
+  mutate(model = "model_3comp2_restrictive",
          AIC = -2 * log_likelihood)
@@
   )) %>%
-  select(!observations) %>%
-  mutate(model = "httk_3comp2_nonrestrictive",
+  select(!c(observations, coefs_vector, Time.Units, Time_trans.Units)) %>%
+  mutate(model = "model_3comp2_nonrestrictive",
          AIC = -2 * log_likelihood) # Simple formula when there are no optimized params
 
-httk_AIC <- bind_rows(restrictive_ll, nonrestrictive_ll)
-
-httk_AIC %>%
+httk_AIC <- bind_rows(restrictive_ll,
+                      nonrestrictive_ll,
+                      AIC(this_pk) %>% filter(model == "model_flat") %>%
+                        filter_targets())
+
+httk_rel_ll <- httk_AIC %>%
   distinct(Chemical, Species, model, AIC) %>%
@@
   rowwise() %>% 
-  mutate(minAIC = min(c_across(starts_with("httk_")), na.rm = TRUE)) %>% 
+  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
   ungroup() %>%
-  mutate(across(starts_with("httk_"), \(x) {
+  mutate(across(starts_with("model_"), \(x) {
     signif(exp((minAIC - x)/2) * 100, 4)
   })) %>%
-  mutate(across(starts_with("httk_"), \(x) {
+  mutate(across(starts_with("model_"), \(x) {
     ifelse(x < 1E-6, 0, x)
-  })) %>% View()
-
+  })) %>%
+  mutate(ll_label = factor(
+    case_when(model_flat > 95 ~ "Undetermined",
+              model_3comp2_nonrestrictive > 95 &
+                model_3comp2_restrictive > 95 ~ "Undetermined (non-flat)",
+              model_3comp2_nonrestrictive > 95 ~ "Nonrestrictive",
+              model_3comp2_restrictive > 95 ~ "Restrictive")
+  ))
+
+httk_rel_ll %>%
+  count(model_flat > 95, model_3comp2_nonrestrictive > 95,
+        model_3comp2_restrictive > 95)
+
+httk_rel_ll %>%
+  select(!minAIC) %>%
+  mutate(Chemical = forcats::fct_reorder2(Chemical,
+                                          model_3comp2_nonrestrictive,
+                                          model_flat,
+                                          .fun = mean)) %>%
+  pivot_longer(cols = starts_with("model_"),
+               names_to = "model", values_to = "relative_likelihood") %>%
+  ggplot(aes(x = Chemical, y = model)) +
+  geom_tile(aes(fill = relative_likelihood)) +
+  scale_fill_viridis_b(option = "cividis", breaks = c(0, 50, 80, 100)) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.text.y = element_text(size = 12, color = "black"),
+        axis.ticks = element_blank(),
+        panel.grid = element_blank(),
+        panel.border = element_blank())
+
+total_rel_evaluation_df <- httk_rel_ll %>%
+  inner_join(this_evaluated_df) %>%
+  inner_join(this_param_df %>% distinct(Chemical, forced_human_values)) %>%
+  distinct()
+
+total_rel_evaluation_df %>%
+  distinct(Chemical, Species, Css.tkstats, Css_httk_nr, Css_httk_r, Css_clear,
+         ll_label) %>%
+  filter(ll_label %in% c("Nonrestrictive", "Restrictive", "Undetermined")) %>%
+  ggplot(aes(x = forcats::fct_reorder(Chemical, Css_httk_r))) +
+  geom_pointrange(aes(y = Css.tkstats, ymin = Css_httk_nr, ymax = Css_httk_r),
+                  size = 0.1) +
+  facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
+  scale_y_log10() +
+  labs(x = 'Chemicals', y = "Css") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        strip.text = element_blank())
+
+total_rel_evaluation_df %>%
+  distinct(Chemical, Species, Css_httk_r,
+           halflife.tkstats, restrictive_halflife,
+           nonrestrictive_halflife, halflife_clear,
+           ll_label) %>%
+    filter(ll_label %in% c("Nonrestrictive", "Restrictive", "Undetermined")) %>%
+  ggplot(aes(x = forcats::fct_reorder(Chemical, restrictive_halflife))) +
+  geom_pointrange(aes(y = halflife.tkstats, 
+                      ymin = nonrestrictive_halflife,
+                      ymax = restrictive_halflife),
+                  size = 0.1) +
+  facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
+  scale_y_log10() +
+  labs(x = "Chemicals", y = "halflife") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        strip.text = element_blank(),
+        strip.background = element_blank(),
+        axis.text.y = element_text(color = "black", size = 10),
+        axis.title = element_text(size = 14))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "halflife_fullChart.png"),
+       bg = "white",
+       height = 3, width = 12
+)
 ```
@@
 ```{r fup_comparison}
-fup_df <- this_param_df %>%
-  distinct(Chemical, Species, forced_human_values,
-           Funbound.plasma, Funbound.plasma.adjustment, 
-           Funbound.plasma.dist) %>%
-  mutate(
-    Funbound.plasma.median = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "^\\d+\\.?\\d+e?-?\\d+(?=,)"
-    )),
-    Funbound.plasma.lower95 = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d+(?=,)"
-    )),
-    Funbound.plasma.upper95 = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d$"
-    ))
-    )
 

### 2025-03-11 data-raw/ClearanceProject-1-DataRmd.Rmd
Renamed and initialized 4 analysis documents for clearance project.

---
title: "Clearance Project - 1 - Data Generation"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

This vignette creates and describes data for downstream analysis.

```{r library_loading}
today <- format(Sys.Date(), "%d%b%Y")
devtools::load_all()
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ctxR)
library(ggvenn)
library(ggalluvial)
library(flextable)
library(reticulate)
library(patchwork)
source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
```

```{r chemical-lists}
member_list <- list(
  httk_3comp2 = unique(get_cheminfo(info = "DTXSID",
                                species = "human",
                                model = "3compartment2",
                                median.only = TRUE,
                                physchem.exclude = TRUE,
                                suppress.messages = TRUE)) %>% 
    suppressWarnings(),
  cvt = cvt %>% 
    filter(species %in% c("human", "rat"),
           conc_medium_normalized == "plasma") %>%
    pull(analyte_dtxsid)
)
# These are the chemicals we can evaluate!
target_chems <- intersect(member_list$cvt, member_list$httk_3comp2)
all_chems <- member_list$httk_3comp2

# save in an .Rdata file
save(target_chems, all_chems,
     file = "data-raw/chem_lists.RData")

```

```{r external_data}
# Here we load Kd/binding affinity data
red_assay_res <- readRDS("data-raw/2019-05-06-REDassay_HTTK.rds")

# ctxR download of all chemicals in 3comp2 model
# Chemical info and properties (averaging the latter by chemical and experimental/predicted)
chem_info <- get_chemical_details_batch(DTXSID = all_chems,
                                               rate_limit = 0L) %>%
  filter(!is.na(smiles))
# 9086 total unique chemicals with SMILES data

chem_properties <- get_chem_info_batch(
  DTXSID = chem_info$dtxsid,
  type = '', 
  rate_limit = 0L,
  verbose = TRUE
) 
# This takes a minute or so... save a reference RDS file to load
# Also get rid of any that don't have SMILES
chem_info %>% distinct(dtxsid, preferredName,
                              qsarReadySmiles, monoisotopicMass) %>%
  right_join(chem_properties) %>%
  filter(!is.na(qsarReadySmiles)) %>%
  saveRDS(file = "data-raw/ctxR_3comp2_cheminfo.rds")

functional_uses_all <- readr::read_csv(paste0(
  Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
  "ChemExpo_bulk_functional_uses_20250304.csv"
))

```

```{r inivopkfit}
# Here we fit CvTdb data that has plasma measurements
# Only use plasma for simplicity
this_pk <- pk(cvt %>% 
                dplyr::filter(conc_medium_normalized == "plasma")
              ) +
  settings_optimx(method = "bobyqa") +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = FALSE) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  stat_error_model(error_group = vars(Chemical, Species))

this_pk <- do_prefit(this_pk)
this_pk <- do_fit(this_pk, n_cores = 14)
saveRDS(this_pk, "data-raw/plasma_CvTfits.rds")

# Related files for pre-calculated:
# tkstats, winning model, AIC, coef_sd, predictions, etc...
this_winmodel <- get_winning_model(this_pk)

this_tkstats <- eval_tkstats(this_pk,
                             model = c("model_1comp", "model_2comp"),
                             finite_only = TRUE,
                             dose_norm = TRUE) %>%
  inner_join(this_winmodel)
colnames(this_tkstats) <- gsub("/", "_", colnames(this_tkstats))

winning_preds <- predict(this_pk) %>%
  semi_join(this_winmodel) %>%
  distinct(Chemical, Species, Chemical_Name,
           model, method, Dose, Media, Route, Reference, pLOQ, Time,
           N_Subjects, Conc, Conc_est)
this_AIC <- AIC(this_pk)
this_coef_win <- coef(this_pk) %>% semi_join(this_winmodel)
this_coef_fit <- this_pk$fit %>% semi_join(this_winmodel)
this_coef_sd_win <- coef_sd(this_pk) %>% semi_join(this_winmodel)

save(this_winmodel, this_tkstats, winning_preds,
     this_AIC, this_coef_win, this_coef_fit, this_coef_sd_win,
     file = "data-raw/plasma_CvTfits_data.RData")
```

```{r getting_curent_params}

# rat_pars_rat <- parameterize_rat()
rat_pars_human <- parameterize_rat(human_clint_fup = TRUE)
#human_pars_human <- parameterize_human()
chosen_list <- rat_pars_human
# The following are derived from the above selected list (see environment)
this_param_rest_l <- chosen_list$named_params_restrictive
this_param_nrest_l <- chosen_list$named_params_nonrestrictive
this_param_df <- chosen_list$param_df
this_httk_clearance_df <- chosen_list$clearance_df

# HTTK predictions

# Predictions from httk(code retained but not run after 2.20.2025)
restrictive_preds <- get_httk_preds(
  parameters = this_param_rest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_restrictive"),
  .cols = starts_with("httk_")
)

nonrestrictive_preds <- get_httk_preds(
  parameters = this_param_nrest_l,
  pk_obj = this_pk,
  species = c("rat", "human")
) %>% rename_with(
  .fn = ~paste0(.x, "_nonrestrictive"),
  .cols = starts_with("httk_")
)

names(restrictive_preds)

all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
  filter_targets()
rm(restrictive_preds, nonrestrictive_preds)

this_css_df <- inner_join(
  css_httk_batch(this_param_rest_l, restrictive = TRUE),
  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
) %>% filter_targets()

this_clint_df <- data.frame(Chemical = names(this_param_rest_l),
                            CLint = vapply(names(this_param_rest_l),
                                           \(x) {
                                             this_param_rest_l[[x]][["Clint"]]
                                           },
                                           FUN.VALUE = numeric(1L)
                            ))

save(this_param_rest_l, this_param_nrest_l,
     this_param_df, this_httk_clearance_df,
     all_httk_preds, this_css_df, this_clint_df,
     file = "data-raw/rat_pars_human.RData")
```

### 2025-03-11 data-raw/ClearanceProject-3-TKstats.Rmd
Renamed and initialized 4 analysis documents for clearance project.

---
title: "Clearance Project - 3 - TKstats"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 2025-03-11 data-raw/ClearanceProject-4-PhysChemClustering.Rmd
Renamed and initialized 4 analysis documents for clearance project.

--- 2025-02-18 data-raw/RestrictiveClearance_comparison.Rmd
@@
 ---
-title: "Restrictive Clearance Comparison"
+title: "Clearance Project - 4 - PhysChem Clustering"
 author: "Gilberto Padilla Mercado"
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
+knitr::opts_chunk$set(echo = TRUE)
 ```
 
-This vignette describes comparisons between invivoPKfit predicted and those from httk.
-
-```{r library_loading}
-today <- format(Sys.Date(), "%d%b%Y")
-devtools::load_all()
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(ctxR)
-library(ggvenn)
-library(ggalluvial)
-library(flextable)
-library(reticulate)
-library(patchwork)
-source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
-```
-
-We first want to see how many chemicals are in either _httk_ or _invivoPKfit_
-
-```{r venn_diagrams}
-member_list <- list(
-  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
-                                species = "human",
-                                model = "gas_pbtk",
-                                median.only = TRUE,
-                                physchem.exclude = TRUE,
-                                suppress.messages = TRUE)) %>% 
-    suppressWarnings(),
-  cvt = cvt %>% 
-    filter(species %in% c("human", "rat"),
-           conc_medium_normalized == "plasma") %>%
-    pull(analyte_dtxsid)
-)
-
-ggvenn(member_list, fill_color = c("white", "white"))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "httk_vs_CvT_VennDiagram_human.png"),
-       bg = "white",
-       height = 3, width = 5
-)
-
-target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
-
-filter_targets <- function(.data) {
-  stopifnot("Chemical" %in% names(.data))
-  dplyr::filter(.data = .data, Chemical %in% target_chems)
-}
-```
-
-I select which parameterization (based on species) that I will use.
-
-```{r selecting_chemical_params}
-chosen_list <- rat_pars_human
-# The following are derived from the above selected list (see environment)
-this_chem_v <- unique(chosen_list$param_df$Chemical)
-this_param_rest_l <- chosen_list$named_params_restrictive
-this_param_nrest_l <- chosen_list$named_params_nonrestrictive
-this_param_df <- chosen_list$param_df
-this_httk_clearance_df <- chosen_list$clearance_df
-this_species_v <- c("rat", "human")
-# Testing to make sure there are some chemicals that have different clearances
-count(this_httk_clearance_df, restrictive_clearance == nonrestrictive_clearance)
-# The majority (140) do!
-```
-
-Here I do a quick fit of the CvT data only for those that have plasma measurements.
-
-```{r quick-fit}
-
-# Only use plasma for simplicity
-this_pk <- pk(cvt %>% 
-                dplyr::filter(conc_medium_normalized == "plasma")
-              ) +
-  settings_optimx(method = "bobyqa") +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(
-    keep_data_original = TRUE,
-    suppress.messages = FALSE) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  stat_error_model(error_group = vars(Chemical, Species))
-
-this_pk <- do_prefit(this_pk)
-this_pk <- do_fit(this_pk, n_cores = 12)
-```
-
-Relationships in the mathematical PK models:
-
-- When there is only oral data available, `Fgutabs_Vdist` and `CLtot_Fgutabs`
-will be calculated instead of the numerator alone.  
-- $C_{ss} \cdot CL_{tot} = C_{H,u}\cdot CL{int}$ (Bennet & Sodhi 2024)  
-- [Add More Here]
-
-The first thing I need to do is get the chemicals included in both the CvTdb subset
-and the httk empirical data for pbpk.
-
-Next I need to get the clearances using the `calc_total_clearance(dtxsid, restrictive.clearance)`
-function from httk. Also need the clearances from invivoPKfit's winning models.
-
-Note: There is about 50 chemicals with rat data for both, but 3X that when
-we allow substitution of human numbers. However, this does not necessarily mean
-that we will get appropriate fits with the human numbers.
-The aforementioned set of rat data, for example, 33 of 51 chemicals find
-appropriate fits with invivoPKfit + httk.
-
-```{r load_Kd}
-load(paste0(Sys.getenv("OD_DIR"),
-            "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
-)
-new.raw.httk.data %>%
-  distinct(DTXSID, Affinity.Kd.Med, Affinity.Kd.Low, Affinity.Kd.High,
-           Fit) %>%
-  na.omit() %>%
-  mutate(Target_Chemical = (DTXSID %in% target_chems)) %>%
-ggplot(
-       aes(
-         x = forcats::fct_reorder(DTXSID, Affinity.Kd.Low)
-         )) +
-  geom_linerange(aes(
-    ymin  = Affinity.Kd.Low,
-    ymax = Affinity.Kd.High,
-    color = Target_Chemical
-  ), alpha = 0.4) +
-  geom_point(aes(
-    y = Affinity.Kd.Med, color = Target_Chemical
-  ), size = 0.75) +
-  # facet_grid(cols = vars(Fit), space = "free_x", scales = "free_x") +
-  scale_y_log10(labels = scales::label_log(digits = 1)) +
-  scale_color_manual(values = c("black", "green4")) +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        panel.grid = element_blank(),
-        plot.title = element_text(hjust = 0.5, face = "bold"),
-        legend.position = "bottom") +
-  labs(title = "Kd estimates across chemicals", x = NULL)
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Kd_estimates_initialsummary.png"),
-       bg = "white",
-       height = 4, width = 9
-)
+```{r data_loading}
+target_chem_properties <- readRDS("data-raw/ctxR_3comp2_cheminfo.rds")
+new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
+red_assay_res <- readRDS("data-raw/2019-05-06-REDassay_HTTK.rds")
 ```
@@
 ```{r lipinksi_test_data}
-target_chem_info <- get_chemical_details_batch(DTXSID = target_chems,
-                                               rate_limit = 1L)
-target_chem_properties <- get_chem_info_batch(DTXSID = target_chems, 
-                                              rate_limit = 1L) %>%
-  filter(name %in% c("LogKow: Octanol-Water",
-                     "pKa Acidic Apparent",
-                     "pKa Basic Apparent")) %>% distinct()
 
 target_chem_properties %>%
-  ggplot(aes(x = source, y = value)) +
-  geom_violin() +
-  geom_line(aes(group = dtxsid), color = "grey10", alpha = 0.1) +
-  geom_hline(yintercept = 5, linetype = "longdash") +
-  facet_grid(cols = vars(propType), scales = "free_x",
-             rows = vars(name)) +
-  scale_y_log10() +
-  theme_bw() +
-  theme(axis.text.x = element_text(hjust = 1, angle = 45))
-
-target_chem_properties %>%
-  count(source)
-
-target_chem_info %>%
+  rename(Chemical = dtxsid) %>%
+  filter_targets() %>%
+  distinct(Chemical, monoisotopicMass) %>%
   ggplot(aes(x = monoisotopicMass)) +
@@
 
-target_chem_pw_predicted <- target_chem_properties %>%
-  filter(source == "ACD/Labs") %>%
-  distinct(propertyId, value, dtxsid) %>%
-  pivot_wider(names_from = propertyId,
-              values_from = value)
+target_chem_pw_full %>%
+  ggplot(aes(x = forcats::fct_reorder(dtxsid, logkow))) +
+  geom_pointrange(aes(y = logkow, ymin = logkow - logkow_sd,
+                      ymax = logkow + logkow_sd), size = 0.1) +
+  facet_grid(cols = vars(type_logkow)) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank())
+target_chem_pw_full %>%
+  ggplot(aes(x = logkow)) +
+  geom_histogram(color = "grey50", fill = "grey5",
+                 binwidth = 1) +
+  theme_bw()
 
@@
 ```{r reticulate-prep}
-smiles_list <- target_chem_info %>% pull(smiles) %>% unique()
+smiles_list <- target_chem_properties %>% 
+  rename(Chemical = dtxsid) %>%
+  filter_targets() %>%
+  pull(qsarReadySmiles) %>% unique()
 mykit <- import("rdkit")
@@
 
-py_h_donors = [Chem.Descriptors.NOCount(x) for x in mol_from_smiles]
-py_h_acceptors = [Chem.Descriptors.NHOHCount(x) for x in mol_from_smiles]
-py_tpsa = [Chem.Descriptors.TPSA(x) for x in mol_from_smiles]
+py_h_donors = [Chem.rdMolDescriptors.CalcNumLipinskiHBD(x) for x in mol_from_smiles]
+py_h_acceptors = [Chem.rdMolDescriptors.CalcNumLipinskiHBA(x) for x in mol_from_smiles]
+py_tpsa = [Chem.rdMolDescriptors.CalcTPSA(x, False, True) for x in mol_from_smiles]
+py_rotbonds = [Chem.rdMolDescriptors.CalcNumRotatableBonds(x) for x in mol_from_smiles]
 ```
 
-```{r lipinksi_alluvial}
+```{r chemical_summary_matrix}
 
-target_chem_summary <- target_chem_info %>%
-  distinct(dtxsid, monoisotopicMass, smiles) %>%
-  right_join(data.frame(smiles = smiles_list)) %>%
-  bind_cols(data.frame(H_donors = py_to_r(py$py_h_donors),
-                       H_acceptors = py_to_r(py$py_h_acceptors))
+target_chem_summary <- target_chem_properties %>%
+  filter(propertyId == "logkow-octanol-water", source == "ACD/Labs") %>%
+  pivot_wider(names_from = propertyId, values_from = value) %>%
+  rename(logkow = `logkow-octanol-water`) %>%
+  distinct(dtxsid, monoisotopicMass, qsarReadySmiles, logkow) %>%
+  filter(qsarReadySmiles %in% smiles_list) %>%
+  right_join(data.frame(qsarReadySmiles = smiles_list,
+                        H_donors = py_to_r(py$py_h_donors),
+                        H_acceptors = py_to_r(py$py_h_acceptors),
+                        TPSA = py_to_r(py$py_tpsa),
+                        Rot_Bonds = py_to_r(py$py_rotbonds))
             ) %>%
-  left_join(
-    target_chem_properties %>%
-      filter(source == "ACD/Labs Consensus") %>%
-      distinct(dtxsid, source, value)
-  ) %>%
-  rename(LogKow = value)
+  rowwise() %>%
+  mutate(logD_7.4 = httk::calc_dow(dtxsid = dtxsid, pH = 7.4)) %>%
+  left_join(red_assay_res %>%
+              distinct(DTXSID, Affinity.Kd.Med) %>%
+              na.omit(),
+            by = join_by(dtxsid == DTXSID)) %>%
+  distinct() %>%
+  left_join(cyp_data, join_by(dtxsid == Chemical))
+
+# Make a matrix of all properties so far
+tcs_mat <- target_chem_summary %>% 
+  select(dtxsid, monoisotopicMass, Affinity.Kd.Med,
+         H_donors:Rot_Bonds, logkow, apKa, bpKa, logD_7.4,
+         starts_with("CYP")) %>%
+  distinct()
+tcs_mat <- column_to_rownames(tcs_mat, var = "dtxsid") %>% as.matrix()
+
+# z-score all properties
+# Margin = 2 is columns
+tcs_mat_z <- apply(tcs_mat, MARGIN = 2, FUN = scale)
+rownames(tcs_mat_z) <- rownames(tcs_mat)
+summary(tcs_mat_z[, 1])
+summary(tcs_mat_z[(rownames(tcs_mat_z) %in% target_chems), 1])
+tcs_mat_z[is.na(tcs_mat_z)] <- 0
+pca_tcs <- prcomp(tcs_mat_z, scale = FALSE)
+
+pca_df <- pca_tcs$x %>% as.data.frame() %>% rownames_to_column(var = "Chemical")
+
+ggplot(data = pca_df %>% mutate(Target = (Chemical %in% target_chems)) %>%
+         left_join(target_chem_summary, by = join_by(Chemical == dtxsid)),
+       aes(x = PC1, y = PC2)) +
+  geom_point(aes(color = TPSA), alpha = 0.8) +
+  scale_color_viridis_c(option = "magma") +
+  facet_wrap(~Target) +
+  theme_bw()
 
 target_chem_lipinski <- target_chem_summary %>%
-  select(-c(smiles, source)) %>%
+  select(-c(qsarReadySmiles)) %>%
   group_by(dtxsid) %>%
@@
   expand = c(.2, .05)) +
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  labs(title = "Overwhelmingly, these chemicals passes Lipinksi's Rules of 5",
+  geom_text(stat = "stratum", aes(label = after_stat(stratum)),
+            size = 1.5) +
+  labs(title = "Target chemicals passing Lipinksi's Rules of 5",
        fill = "Passes Lipinksi's Rules?") +
@@
   theme_minimal() +
-  theme(axis.text.x = element_text(face = "bold", color = "black", size = 10),
+  theme(axis.text.x = element_text(face = "bold", color = "black", size = 8),
         panel.grid = element_blank(),
-        plot.title = element_text(hjust = 0.5),
+        plot.title = element_text(hjust = 0.5, size = 10),
+        axis.title = element_text(size = 8),
+        legend.title = element_text(size = 8),
+        legend.text = element_text(size = 8),
+        axis.title.x = element_blank(),
         legend.position = "bottom")
 
+lipinski_plot
 ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
@@
        bg = "white",
-       height = 5, width = 6
+       height = 3, width = 4
 )
+
+chem_rell_label <- total_rel_evaluation_df %>% distinct(Chemical, ll_label) %>%
+  filter(ll_label %in% c("Restrictive", "Nonrestrictive"))
+
+# Molecular descriptors in bins
+bin_size <- 10
+logP_plot <- target_chem_summary %>%
+  inner_join(chem_rell_label, by = join_by(dtxsid == Chemical)) %>%
+  distinct(dtxsid, logkow) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(logP_bin = factor(logkow %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = logP_bin, y = Funbound.plasma)) +
+  labs(x = "logKow", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+target_chem_summary %>%
+  inner_join(chem_rell_label, by = join_by(dtxsid == Chemical)) %>%
+  distinct(dtxsid, logkow, TPSA, Rot_Bonds, ll_label) %>% 
+  pivot_longer(cols = c(logkow, TPSA),
+               names_to = "Parameter", values_to = "Value") %>%
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  ggplot(aes(x = Value, y = Funbound.plasma)) +
+  labs(x = "", y = "fup") +
+  facet_grid(cols = vars(Parameter),
+             rows = vars(ll_label),
+             scales = "free_x") +
+  geom_point() +
+  theme_bw()
+
+bin_size <- 50
+TPSA_plot <- target_chem_summary %>%
+  distinct(dtxsid, TPSA) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(TPSA_bin = factor(TPSA %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = TPSA_bin, y = Funbound.plasma)) +
+  labs(x = "Topological Polar Surface Area", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 2
+RotBond_plot <- target_chem_summary %>%
+  distinct(dtxsid, Rot_Bonds) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(Rot_Bonds_bin = factor(Rot_Bonds %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = Rot_Bonds_bin, y = Funbound.plasma)) +
+  labs(x = "Rotatable Bonds", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 150
+MW_plot <- target_chem_summary %>%
+  distinct(dtxsid, monoisotopicMass) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(MW_bin = factor(monoisotopicMass %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = MW_bin, y = Funbound.plasma)) +
+  labs(x = "Molecular Mass", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 4
+HBA_plot <- target_chem_summary %>%
+  distinct(dtxsid, H_acceptors) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(HBA_bin = factor(H_acceptors %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = HBA_bin, y = Funbound.plasma)) +
+  labs(x = "Hydrogen bond acceptors", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 2
+HBD_plot <- target_chem_summary %>%
+  distinct(dtxsid, H_donors) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(HBD_bin = factor(H_donors %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = HBD_bin, y = Funbound.plasma)) +
+  labs(x = "Hydrogen bond donors", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+bin_size <- 200
+target_chem_summary %>%
+  distinct(dtxsid, logD_7.4) %>% 
+  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
+  mutate(logD_bin =  factor(logD_7.4 %/% bin_size * bin_size)) %>%
+  ggplot(aes(x = logD_bin, y = Funbound.plasma)) +
+  labs(x = "logD_7.4", y = "fup") +
+  ggbeeswarm::geom_beeswarm() +
+  theme_bw()
+
+(MW_plot + TPSA_plot + HBA_plot) / (logP_plot + RotBond_plot + HBD_plot)
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "PhysChemProperties_rdkit.png"),
+       bg = "white",
+       height = 6, width = 8
+)
+
 ```
@@
 restrictively or non-restrictively cleared.
-
-We also want to assess whether the "winning" _invivoPKfit_ fits are better than
-the chosen _httk_ fit. This is a bit of a pre-requisite to our analysis of the
-clearances and whether they are more or less reasonable in their reflection of
-the reality. The metric used here will be RMSLE.
-
-```{r httk_predictions}
-restrictive_preds <- get_httk_preds(
-  parameters = this_param_rest_l,
-  pk_obj = this_pk,
-  species = c("rat", "human")
-) %>% rename_with(
-  .fn = ~paste0(.x, "_restrictive"),
-  .cols = starts_with("httk_")
-)
-
-nonrestrictive_preds <- get_httk_preds(
-  parameters = this_param_nrest_l,
-  pk_obj = this_pk,
-  species = c("rat", "human")
-) %>% rename_with(
-  .fn = ~paste0(.x, "_nonrestrictive"),
-  .cols = starts_with("httk_")
-)
-
-all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
-  filter_targets()
-
-this_nonflat_winmodel <- get_winning_model(this_pk) %>%
-  filter(model %in% c("model_1comp", "model_2comp")) %>%
-  filter_targets()
-
-winning_preds <- predict(this_pk) %>%
-  semi_join(this_nonflat_winmodel) %>% # The targets already filtered here
-  distinct(Chemical, Species, Chemical_Name,
-           model, method, Dose, Media, Route, Reference, pLOQ, Time,
-           N_Subjects, Conc, Conc_est)
-
-# RMSLE formula
-# LE = log1p(Conc_est) - log1p(Conc)
-# SLE = LE^2
-# RMSLE = sqrt(mean(SLE, na.rm = TRUE))
-
-combined_preds <- all_httk_preds %>%
-  left_join(winning_preds) %>%
-  filter(!is.na(model))
-
-combined_RMSLE <- combined_preds %>%
-  ungroup() %>%
-  mutate(
-    restrictive_SLE = (log1p(httk_Preds_restrictive) - log1p(Conc))^2,
-    nonrestrictive_SLE = (log1p(httk_Preds_nonrestrictive) - log1p(Conc))^2,
-    invivoPK_SLE =  (log1p(Conc_est) - log1p(Conc))^2 
-  ) %>%
-  group_by(Chemical, Species) %>%
-  summarize(RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
-            RMSLE_nonrestrictive = sqrt(mean(nonrestrictive_SLE, na.rm = TRUE)),
-            RMSLE_invivoPKfit = sqrt(mean(invivoPK_SLE, na.rm = TRUE)))
-
-combined_RMSLE %>%
-  ungroup() %>%
-  pivot_longer(cols = starts_with("RMSLE_"),
-               names_to = "Source",
-               values_to = "RMSLE") %>%
-  mutate(Source = factor(Source,
-                         levels = c("RMSLE_nonrestrictive",
-                                    "RMSLE_invivoPKfit",
-                                    "RMSLE_restrictive")
-  )) %>%
-  ggplot(aes(x = Source, y = RMSLE, group = Chemical)) +
-  geom_point(alpha = 0.5) +
-  geom_line(alpha = 0.5) +
-  theme_bw()
-
-combined_RMSLE %>%
-  ungroup() %>%
-  mutate(comparison_group = case_when(
-    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
-     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
-    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
-      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
-    RMSLE_invivoPKfit > RMSLE_restrictive &
-      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
-  )) %>% 
-  ggplot(aes(x = Chemical, y = RMSLE_invivoPKfit)) +
-  geom_point(color = "green4") +
-  geom_point(aes(y = RMSLE_nonrestrictive), shape = 6, size = 0.5) +
-  geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
-  facet_grid(~factor(comparison_group,
-                     levels = c("Less than", "Between", "More than")),
-             scales = "free_x", space = "free_x") +
-  labs(y = "RMSLE") +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        panel.grid = element_blank())
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "RMSLE_comparison_fullChart.png"),
-       bg = "white",
-       height = 4.5, width = 8
-)
-
-# Number of chemicals we have RMSLE's for
-combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()
-
-```
-
-Another weight that we may consider is relative log-likelihood. This can be
-calculated using AIC, compared to the the flat model.
-
-```{r relative-likelihood}
-this_rll_probs <- AIC(this_pk) %>%
-  filter_targets() %>%
-  distinct(Chemical, Species, model, AIC) %>%
-  pivot_wider(names_from = model, values_from = AIC) %>%
-  rowwise() %>% 
-  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(across(starts_with("model_"), \(x) {
-    signif(exp((minAIC - x)/2) * 100, 4)
-  })) %>%
-  mutate(across(starts_with("model_"), \(x) {
-    ifelse(x < 1E-6, 0, x)
-  })) %>%
-  inner_join(this_nonflat_winmodel %>% distinct(Chemical, Species, model)) %>%
-  ungroup() %>%
-  filter(model_1comp >= 99 | model_2comp >= 99,
-        model_flat < 1, Chemical %in% target_chems)
-
-this_rll_probs %>%
-  count(model_1comp >= 99, model_2comp >= 99)
-
-```
-
-The weights to be applied are calculated as such:
-
-$$
-\gamma = \frac{100\cdot \rm{RMSLE}}{\theta}
-$$
-Where $\theta$ is the relative log-likelihood. The smaller number the better.
-If the RMSLE is zero, then it means that it is a "perfect" fit and we are highly
-confident in using other metrics to gauge clearance. Below I put these together.
-
-```{r model_weighting}
-combined_model_weights <- combined_RMSLE %>%
-  left_join(this_rll_probs) %>%
-  ungroup() %>%
-  pivot_longer(cols = starts_with("model_"),
-               names_to = "all_models",
-               values_to = "relative_likelihood") %>%
-  filter(all_models == model) %>%
-  ungroup() %>%
-  mutate(gamma_weight = 100 * RMSLE_invivoPKfit / relative_likelihood,
-         rmsle_comparison_group = case_when(
-    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
-     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
-    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
-      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
-    RMSLE_invivoPKfit > RMSLE_restrictive &
-      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than")
-  ) %>%
-  mutate(rmsle_comparison_group = factor(rmsle_comparison_group,
-                                         levels = c("Less than", "Between",
-                                                    "More than"))) %>%
-  select(-all_models) %>% distinct()
-
-```
-
-Next we need to compare clearances. Sometimes this is difficult as the overlap
-with certain calculations will be defined by the type of experimental data
-available. For instance, if there is only oral data available, `CLtot.tkstats`
-will _not_ be calculated and instead `CLtot/Fgutabs.tkstats` will be available.
-
-```{r combine_tkstats}
-# Get the winning model and only include chemicals in target_chems
-this_winmodel <- get_winning_model(this_pk) %>%
-    filter_targets()
-# How many overlapping chemicals have winning models that aren't flat?
-count(
-  this_winmodel,
-  model
-) # 153 = 97 1-compartment + 56 2-compartment
-
-this_tkstats <- eval_tkstats(this_pk,
-                             model = c("model_1comp", "model_2comp"),
-                             finite_only = TRUE,
-                             dose_norm = TRUE
-) %>%
-  filter_targets() %>%
-  rename(CLtot_Fgutabs.tkstats = `CLtot/Fgutabs.tkstats`) %>%
-  distinct(Chemical, Species, method, model, Dose, Route, Media,
-           CLtot.tkstats, CLtot_Fgutabs.tkstats, halflife.tkstats, Css.tkstats) %>%
-  inner_join(this_winmodel)
-
-count(
-  this_tkstats,
-  # model,
-  !is.na(CLtot.tkstats),
-  !is.na(CLtot_Fgutabs.tkstats),
-  !is.na(halflife.tkstats)
-) %>% flextable() %>%
-  set_header_labels(
-    `!is.na(CLtot.tkstats)` = "Valid Total Clearance",
-    `!is.na(CLtot_Fgutabs.tkstats)` = "Valid Total Clearance/Fgutabs",
-    `!is.na(halflife.tkstats)` = "Valid halflife",
-    n = "Number of Chemicals"
-    )
-# 83 chemicals have valid total clearance
-# 180 chemicals have valid total clearance/Fgutabs
-# 5 chemicals have only valid total clearance and no valid total clearance/Fgutabs
-
-count(this_tkstats, is.na(Css.tkstats))
-
-```
-
-Here I will evaluate $C_{SS}$, the steady-state concentration to get some
-understanding of whether chemicals may be likely restrictive or non-restrictive.
-
-```{r Css_assessment}
-
-css_httk_batch <- function(param_list,
-                           restrictive = TRUE) {
-  stopifnot(is.logical(restrictive))
-
-  css_list_r <- vapply(
-    param_list,
-    \(x) {
-      calc_analytic_css_3comp2(parameters = x,
-                               restrictive.clearance = restrictive)
-    },
-    FUN.VALUE = numeric(1L)
-  )
-  css_list_names <- names(param_list)
-
-  css_df <- data.frame(Chemical = css_list_names,
-                       Css_httk = css_list_r)
-  if (restrictive) {
-    css_df <- rename(css_df, Css_httk_r = Css_httk)
-  } else {
-    css_df <- rename(css_df, Css_httk_nr = Css_httk)
-  }
-  return(css_df)
-}
-
-this_css_df <- inner_join(
-  css_httk_batch(this_param_rest_l, restrictive = TRUE),
-  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
-)
-# Chart with relative differences (think steps) of Css between clearance types
-this_css_df %>%
-  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
-  count(relative_difference == 0, Css_httk_r == 0) # 31 Chemicals have zero difference
-###
-this_css_df %>%
-  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
-  filter(relative_difference > 0) %>%
-  ggplot(aes(x = forcats::fct_reorder(Chemical,
-                                      relative_difference, .desc = FALSE))) +
-  geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r)) +
-  labs(title = "Differences between restrictive & nonrestrictive clearance",
-       y = "Css\n(mg/L)", x = "Chemicals") +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks = element_blank(),
-        panel.grid.major.x = element_blank(),
-        plot.title = element_text(hjust = 0.5))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_difference_httk_lineplot.png"),
-       bg = "white",
-       height = 5, width = 7)
-
-this_css_df %>%
-  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
-  filter(relative_difference > 0) %>%
-  ggplot(aes(x = forcats::fct_reorder(Chemical,
-                                      relative_difference))) +
-  geom_point(aes(size = relative_difference), y = 0, alpha = 0.2, shape = 16) +
-  annotate(x = 1, y = 150 ,label = "Min: 0 mg/L\n31 Chemicals", geom = "text") +
-  annotate(x = 140, y = 150 ,label = "Max: 30 mg/L\n", geom = "text") +
-  scale_y_continuous(limits = c(-150,150)) +
-  scale_size_area(max_size = 40) +
-  coord_cartesian(clip = "off") +
-  theme_void() +
-  theme(legend.position = "none",
-        plot.margin = unit(c(2,2,1,2), units = "inches"))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_difference_httk_inkblot.png"),
-       bg = "white",
-       height = 5, width = 7)
-###
-
-this_css_df <- this_css_df %>%
-  inner_join(this_tkstats) %>%
-  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
-  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
-  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
-  mutate(comparison_group_Css = factor(
-    case_when(
-      between(Css.tkstats, Css_httk_r, Css_httk_nr) |
-        between(Css.tkstats, Css_httk_nr, Css_httk_r) ~ "Between",
-      Css.tkstats < Css_httk_r & Css.tkstats < Css_httk_nr ~ "Below",
-      Css.tkstats > Css_httk_r & Css.tkstats > Css_httk_nr ~ "Above"),
-    levels = c("Above", "Between", "Below")
-  ), Chemical = factor(Chemical) %>% forcats::fct_reorder(Css_httk_r)
-  ) %>%
-  mutate(nearest_clearance = factor(
-    case_when(
-      between(log2(Css.tkstats),
-              log2(Css_httk_r)-1, log2(Css_httk_r)+1) |
-        (comparison_group_Css == "Above" &
-           log2(Css.tkstats) <= log2(Css_httk_r)+2) ~ "Restrictive",
-      between(log2(Css.tkstats),
-              log2(Css_httk_nr)-1, log2(Css_httk_nr)+1) |
-        comparison_group_Css == "Below" ~ "NonRestrictive",
-      .default = "Out of Range"
-    )
-  ))
-
-this_css_df %>%
-  ggplot(aes(x = Chemical)) +
-  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
-  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = Css_httk_r,
-                     ymax = Css_httk_nr)
-  ) +
-  geom_point(aes(y = Css.tkstats, shape = Route,
-                 color = nearest_clearance)) +
-  facet_grid(rows = vars(comparison_group_Css),
-             scales = "free_x",
-             space = "free_x") +
-  scale_y_log10(name = "Css") +
-  scale_shape_manual(values = c(0,1)) +
-  scale_color_manual(values = c("magenta3", "green4", "black"),
-                     name = "Within 2-fold\nof clearance:",
-                     ) +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        panel.grid = element_blank()) +
-  guide_area() +
-  plot_layout(widths = c(8,1))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_comparison_2foldclearancefullChart.png"),
-       bg = "white",
-       height = 5, width = 10
-)
-
-this_css_df %>% 
-  group_by(Chemical) %>%
-  count(nearest_clearance) %>%
-  filter(nearest_clearance != "Out of Range") %>% View()
-
-```
-
-Overwhelmingly, the results of this is a Restrictive clearance model...
-however it is important to flag
-
-```{r Css_CLint}
-this_css_clint_df <- this_css_df %>%
-  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats,
-           nearest_clearance, comparison_group_Css) %>%
-  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
-  left_join(data.frame(Chemical = names(this_param_rest_l),
-                       CLint = vapply(names(this_param_rest_l),
-                                      \(x) {
-                                        this_param_rest_l[[x]][["Clint"]]
-                                      },
-                                      FUN.VALUE = numeric(1L)
-                       ))) %>%
-  dplyr::filter(CLint > 0)
-
-this_css_clint_df %>%
-  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
-  ggplot(aes(x = CLint)) +
-  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
-  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = Css_httk_r,
-                     ymax = Css_httk_nr)
-  ) +
-  scale_y_log10(name = "C<sub>ss</sub>") + 
-  scale_x_log10(name = "CL<sub>int</sub>") +
-  geom_point(aes(y = Css.tkstats, 
-                 fill = `Mass <= 500 Da`,
-                 shape = Route,
-                 color = nearest_clearance)) +
-  facet_grid(rows = vars(nearest_clearance)) +
-  scale_color_manual(values = c("magenta3", "green4", "black"),
-                     guide = "none") +
-  scale_shape_manual(values = c(21,22)) +
-  scale_fill_manual(values = c("white", "grey5")) +
-  guides(fill = guide_legend(override.aes = list(shape = 21))) +
-  theme_bw() +
-  theme(axis.title = ggtext::element_markdown())
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_x_CLint_wNearestClearanceGrid.png"),
-       bg = "white",
-       height = 6, width = 10
-)
-
-this_css_clint_df %>%
-  # group_by(Route) %>%
-  group_modify(~broom::tidy(lm(Css.tkstats ~ nearest_clearance + CLint, data = .x)))
-
-```
-
-Now I will try to triangulate the model weights with the Css estimates.
-
-```{r weighted_Css}
-combined_model_weights %>%
-  inner_join(this_css_df) %>%
-  filter_targets() %>%
-  ggplot(aes(x = forcats::fct_reorder(Chemical, Css_httk_r))) +
-  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
-  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = Css_httk_r,
-                     ymax = Css_httk_nr)
-  ) +
-  geom_point(aes(y = Css.tkstats, shape = Route, color = gamma_weight)) +
-  facet_grid(rows = vars(comparison_group_Css),
-             cols = vars(rmsle_comparison_group),
-             scales = "free_x",
-             space = "free_x") +
-  scale_y_log10(name = "Css") +
-  scale_shape_manual(values = c(0,1)) +
-  scale_color_viridis_b(option = "viridis") +
-  labs(subtitle = "RMSLE for invivoPKfit compared to httk predictions",
-       x = "Chemical\n(ordered by increasing restrictive Css prediction)",
-       y = "Css",
-       color = "Inverse Confidence") +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        plot.subtitle = element_text(hjust = 0.5),
-        panel.grid = element_blank(),
-        legend.title = element_text(vjust = 0.8)) +
-  guide_area() +
-  plot_layout(widths = c(8,1))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_withRMSLEweights.png"),
-       bg = "white",
-       height = 5, width = 10
-)
-
-```
-
-First, there are about 80 chemicals which have a `CLtot.tkstats` which may
-give us some idea of the clearance alongside the _inverse confidence_ metric.
-
-```{r CLtot_subset}
-enhanced_tkstats <- this_tkstats %>%
-  inner_join(this_httk_clearance_df) %>%
-  inner_join(combined_model_weights) %>%
-  filter(!is.na(CLtot.tkstats)) %>%
-  mutate(comparison_CLtot = factor(
-    case_when(
-    between(log2(CLtot.tkstats), 
-            log2(restrictive_clearance)-1,
-            log2(restrictive_clearance)+1) ~ "Restrictive",
-    between(log2(CLtot.tkstats), 
-            log2(nonrestrictive_clearance)-1,
-            log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
-    between(CLtot.tkstats,
-            restrictive_clearance, nonrestrictive_clearance) ~ "Between",
-    .default = "Out of Range"
-  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of Range")
-  ))
-enhanced_tkstats %>%
-  ggplot(aes(forcats::fct_reorder(Chemical,
-                          gamma_weight))) +
-  geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
-             shape = 21) +
-  geom_linerange(aes(ymin = restrictive_clearance, 
-                     ymax = nonrestrictive_clearance)) +
-  geom_point(aes(y = restrictive_clearance),
-             shape = 2, size = 0.8) + # Note that this is the lower value
-  geom_point(aes(y = nonrestrictive_clearance),
-             shape = 6, size = 0.8) +
-  scale_fill_viridis_b(option = "viridis", 
-                        guide = guide_colorbar(position = "bottom"),
-                       limits = c(0,1.5)) +
-  scale_y_log10() +
-  facet_grid(cols = vars(comparison_CLtot),
-             scales = "free_x",
-             space = "free_x") +
-  labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence") +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        plot.subtitle = element_text(hjust = 0.5),
-        legend.title = element_text(vjust = 0.8))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
-       bg = "white",
-       height = 4, width = 8
-)
-
-```
-
-```{r CLtot_subset_withCss}
-
-this_tkstats %>%
-  inner_join(this_httk_clearance_df) %>%
-  inner_join(combined_model_weights) %>%
-  left_join(this_css_df) %>%
-  filter(!is.na(CLtot.tkstats)) %>%
-  mutate(comparison_CLtot = factor(
-    case_when(
-      between(log2(CLtot.tkstats),log2(restrictive_clearance)-1,
-              log2(restrictive_clearance)+1) ~ "Restrictive",
-      between(log2(CLtot.tkstats),log2(nonrestrictive_clearance)-1,
-              log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
-      between(CLtot.tkstats,
-              restrictive_clearance, nonrestrictive_clearance) ~ "Between",
-      .default = "Out of range"
-  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of range"))) %>%
-  ggplot(aes(forcats::fct_reorder(Chemical,
-                          gamma_weight))) +
-  geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
-             shape = 21) +
-  geom_linerange(aes(ymin = restrictive_clearance, 
-                     ymax = nonrestrictive_clearance)) +
-  geom_point(aes(y = restrictive_clearance),
-             shape = 4, size = 0.8) + # Note that this is the lower value
-  geom_point(aes(y = nonrestrictive_clearance),
-             shape = 4, size = 0.8) +
-  scale_fill_viridis_b(option = "viridis", 
-                        guide = guide_colorbar(position = "bottom")) +
-  scale_y_log10() +
-  facet_grid(cols = vars(comparison_CLtot),
-             scales = "free_x") +
-  labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence",
-       subtitle = "Estimates within 2-fold of in vitro modelled predictions") +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        plot.subtitle = element_text(hjust = 0.5),
-        legend.title = element_text(vjust = 0.8))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
-       bg = "white",
-       height = 4, width = 8
-)
-
-```
-
-```{r rudimentary_clustering}
-
-# Set up a data.frame that has chemical, Css difference, Funbound z-score,
-# nearest_clearance (using Css), and model weight
-this_fupZ_df <- this_param_df %>% select(Chemical, Funbound.plasma.restrictive) %>%
-  mutate(Fup_Z = as.vector(scale(sqrt(Funbound.plasma.restrictive))),
-         .keep = "unused")
-
-this_dist_prepdf <- this_css_df %>% select(Chemical, model, Route,
-                       nearest_clearance, comparison_group_Css,
-                       Css_httk_r, Css_httk_nr) %>%
-  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr),
-         .keep = "unused") %>%
-  inner_join(combined_model_weights %>%
-               select(Chemical, Species, gamma_weight)) %>%
-  inner_join(enhanced_tkstats %>%
-               select(Chemical, Species, comparison_CLtot)) %>%
-  inner_join(this_fupZ_df) %>%
-  distinct() %>%
-  mutate(ID = paste(Chemical, Species, model, Route, sep = "."), .keep = "unused")
-
-this_dist_prepdf %>%
-ggplot(aes(x = gamma_weight, y = Fup_Z, color = relative_difference)) + 
-  geom_point() +
-  scale_color_viridis_c() +
-  facet_grid(cols = vars(comparison_CLtot))
-
-```
-
-```{r calc_CLtot_Fgutabs}
-this_tkstats2 <- this_tkstats %>%
-  left_join(
-    this_param_df %>%
-      distinct(Chemical, Species, Fabsgut.restrictive)
-  ) %>%
-  mutate(CLtot_calc = CLtot_Fgutabs.tkstats * Fabsgut.restrictive)
-
-ggplot(data = this_httk_clearance_df,
-       aes(x = Chemical)) +
-  geom_point(aes(y = restrictive_clearance), color = "green4") +
-  geom_point(aes(y = nonrestrictive_clearance), color = "orange2") +
-  geom_point(data = this_tkstats2,
-             aes(y = CLtot_calc)) +
-  scale_y_log10() +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank())
-
-# Combine these two
-combined_clearance_df <- this_httk_clearance_df %>%
-  inner_join(this_tkstats) %>%
-  distinct()
-
-length(unique(combined_clearance_df$Chemical))
-```
-
-Finally, let's visualize where the tkstats predictions land.
-Because there are only a handful of chemicals which _invivoPKfit_ can calculate
-`CLtot` for, I will employ two strategies to gauge how different these estimates
-are in reality.
-
-1. Visualize differences in half-life.  
-2. Multiply `CLtot_Fgutabs` by the `Fabsgut` value parameterized in _httk_ to
-get a clearance value.
-
-```{r half-life}
-combined_clearance_df %>%
-  ggplot(aes(x = halflife.tkstats)) +
-  geom_point(aes(y = restrictive_halflife), color = "magenta2") +
-  geom_point(aes(y = nonrestrictive_halflife), color = "green4") +
-  coord_equal(xlim = c(0, 200), y = c(0, 200))
-```
-
-## Notes:
-Look at Css values for restrictive/nonrestrictive (httk solutions)
-AICs for models
-Important to look for potential reflective metrics and find associations 
-(CLtot, Css, fup) and also look at physiochemical properties that may create
-some distinctions once a prediction of clearance type is made.
-
-So the model will be something like `CLtot ~ Css + fup + Clearance_Type + GFR`
-and we can re-simplify certain things into `halflife` and `kelim` to see
-how likely this would be in a simple, classical PK model.
-
-```{r clearance_viz}
-
-this_param_df %>%
-  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
-  inner_join(combined_clearance_df) %>%
-  mutate(CLtot.nonrest = CLtot_Fgutabs.tkstats * Fabsgut.nonrestrictive,
-         CLtot.rest = CLtot_Fgutabs.tkstats * Fabsgut.restrictive) %>%
-  pivot_longer(cols = c(restrictive_clearance, nonrestrictive_clearance,
-                        CLtot.nonrest, CLtot.rest),
-               names_to = "Source",
-               values_to = "Clearance") %>%
-  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
-  geom_point() +
-  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
-  theme_bw() +
-  coord_cartesian(xlim = c(0.0001, 1000)) +
-  scale_x_log10()
-
-this_param_df %>%
-  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
-  inner_join(combined_clearance_df) %>%
-  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
-         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
-  pivot_longer(cols = c(CLtot_Fgutabs.tkstats,
-                        rest_fgutabs, nonrest_fgutabs),
-               names_to = "Source",
-               values_to = "Clearance") %>%
-  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
-  geom_point() +
-  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
-  theme_bw() +
-  coord_cartesian(xlim = c(0.000001, 100000)) +
-  scale_x_log10()
-
-this_param_df %>%
-  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
-  inner_join(combined_clearance_df) %>%
-  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
-         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
-   mutate(AD_restrictive = abs(CLtot_Fgutabs.tkstats - rest_fgutabs),
-         AD_nonrestrictive = abs(CLtot_Fgutabs.tkstats - nonrest_fgutabs),
-         rough_determination = ifelse(
-           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
-             CLtot.tkstats <= nonrest_fgutabs,
-           "Restrictive", "Possibly non-Restrictive"
-         )) %>% 
-  dplyr::ungroup() %>% View()
-
-clearance_guess <- combined_clearance_df %>%
-  mutate(AD_restrictive = abs(CLtot.tkstats - restrictive_clearance),
-         AD_nonrestrictive = abs(CLtot.tkstats - nonrestrictive_clearance),
-         rough_determination = ifelse(
-           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
-             CLtot.tkstats < nonrestrictive_clearance,
-           "Restrictive", "Possibly non-Restrictive"
-         )) %>% 
-  dplyr::ungroup()
-
-clearance_guess %>%
-  dplyr::distinct(Chemical, rough_determination) %>%
-  group_by(rough_determination) %>%
-  tally()
-
-# Preliminary viz, plot all clearances
-ccd <- clearance_guess %>%
-  relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
-  pivot_longer(
-    cols = tidyselect::all_of(c("CLtot.tkstats", "CLtot.nca_mean",
-                              "restrictive_clearance", "nonrestrictive_clearance")),
-    names_to = "Clearance_Source",
-    values_to = "Value"
-  ) %>%
-  mutate(
-    Chemical = factor(Chemical),
-    Clearance_Source = factor(
-      Clearance_Source,
-      levels = c(
-        "CLtot.tkstats", "CLtot.nca_mean",
-        "nonrestrictive_clearance", "restrictive_clearance"
-      )
-    ),
-    label_cols = ifelse(rough_determination == "Restrictive",
-                     "green4", "orange3")
-  ) %>%
-  transform(
-    Chemical = fct_reorder(Chemical, Value, max)
-  ) %>% 
-  as_tibble()
-
-ccd %>%
-  ggplot(aes(
-    x = Value,
-    y = Chemical,
-    fill = Clearance_Source
-  )) +
-  geom_point(shape = 21, alpha = 0.7) +
-  scale_x_log10() +
-  scale_fill_manual(
-    breaks = c(
-      "nonrestrictive_clearance", "CLtot.tkstats",
-      "CLtot.nca_mean",
-      "restrictive_clearance"
-    ),
-    labels = c(
-      "non-restrictive clearance (httk)",
-      "predicted clearance (invivoPKfit)",
-      "mean non-compartmental total clearance (invivoPKfit)",
-      "restrictive clearance (httk)"
-    ),
-    values = c("orange2", "grey5", "skyblue3", "green4")
-  ) +
-  facet_grid(rows = vars(Species), scales = "free", space = "free") +
-  labs(
-    x = "Total Clearance",
-    y = "Chemical",
-    title = "Comparing clearance estimates of chemicals with rat CvT data"
-  ) +
-  theme(
-    panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
-    panel.background = element_blank(),
-    panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-    strip.background = element_rect(fill = "white"),
-    strip.text = element_text(face = "bold", angle = 0),
-    axis.title.y = element_blank(),
-    legend.position = "right",
-    legend.direction = "vertical",
-    axis.ticks = element_blank(),
-    axis.line = element_blank()
-  )
-
-clear_chem_levels <- levels(ccd$Chemical)
-
-ggsave(
-  filename = paste0(
-    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
-    today,
-    "all_tkClearance_comparison_httk_PBPK.png"
-  ),
-  height = 8,
-  width = 8,
-  device = "png"
-)
-```
-
-I would also like to know, how does the $f_{up}$ of this set of chemicals
-compare to that of all chemicals in `httk` (Dawson 2021).
-
-```{r fup_comparison}
-fup_df <- this_param_df %>%
-  distinct(Chemical, Species, forced_human_values,
-           Funbound.plasma, Funbound.plasma.adjustment, 
-           Funbound.plasma.dist) %>%
-  mutate(
-    Funbound.plasma.median = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "^\\d+\\.?\\d+e?-?\\d+(?=,)"
-    )),
-    Funbound.plasma.lower95 = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d+(?=,)"
-    )),
-    Funbound.plasma.upper95 = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d$"
-    ))
-    )
-
-fup_df %>%
-  ggplot(aes(x = Funbound.plasma.adjustment)) +
-  geom_histogram(
-    data = fup_df %>%
-      filter(Chemical %in% this_httk_clearance_df$Chemical),
-    # aes(y = after_stat(density)),
-    fill = "white",
-    color = "darkgreen", binwidth = 0.03
-  ) +
-  expand_limits(expand = c(0,0)) +
-  geom_vline(xintercept = 0.05, linetype = "dashed") +
-  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
-  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
-  labs(
-    title = "Distribution of Funbound.plasma values",
-    subtitle = "(chemicals fit by invivoPKfit in dark green)"
-  ) +
-  coord_cartesian(clip = "off") +
-  theme_bw()
-
-ggsave(paste0(Sys.getenv("FIG_DIR"), "fup_density_plots.png"),
-       height = 5,
-       width = 6,
-       device = ragg::agg_png,
-       units = "in"
-)
-
-test_fup <- fup_df %>%
-  pull(Funbound.plasma)
-for (i in seq(0, 0.5, by = 1e-9)) {
-  if (sum(test_fup > i) == sum(test_fup <= i)) {
-    print(i)
-    break
-  }
-}
-
-fup_df %>%
-  ggplot(aes(x = Funbound.plasma, y = Funbound.plasma.adjustment)) +
-  geom_point()
-
-```
-
-## Exploring _httk_ parameters and solved values for `gas_pbtk`
-
-Note that this is only for rats. This is supposed to be the best case,
-but of course _httk_ is "made" for predicting **human exposures**. Also,
-I will try to order some of this data the same way as the clearance figures.
-
-This will ultimately help understand whether Total Clearance
-differences and prediction differences relate. Of course it would
-be possible to do a formal test for correlation but that overdoes what we need
-to build this relationship for with the rather limited _rat_ data we have
-in both _httk_ and _invivoPKfit_.
-
-```{r rat_invivo_comparison}
-
-solve_gas_pbtk(
-  dtxsid = common_chems_dawson[10],
-  dose = 1, exp.conc = 0,
-  iv.dose = FALSE,
-  input.units = "mg/kg",
-  output.units = "mg/L",
-  suppress.messages = TRUE
-) %>%
-  ggplot(aes(x = time)) +
-  geom_line(aes(y = Cplasma)) +
-  geom_line(aes(y = Crest), color = "blue4") +
-  geom_line(aes(y = Cgut), color = "goldenrod") +
-  geom_line(aes(y = Cliver), color = "darkgreen") +
-  geom_line(aes(y = Clung), color = "hotpink") +
-  geom_line(aes(y = Ckidney), color = "purple4")
-
-# Functions wrapping httk single dose evaluation
-httk_bolus_gas_pbtk <- function(dtxsid, species = "Human",
-                                dose, times, iv.dose, LOQ) {
-  tmp_solution <- solve_gas_pbtk(
-    dtxsid = unique(dtxsid),
-    dose = unique(dose),
-    exp.conc = 0,
-    iv.dose = unique(iv.dose),
-    times = unique(c(0, times/24)),
-    input.units = "mg/kg",
-    output.units = "mg/L",
-    species = unique(stringr::str_to_title(species)),
-    default.to.human = TRUE,
-    suppress.messages = TRUE
-  )
-  # Remove the 0.0001 intermediate time value that is returned
-  retdf <- tibble(
-    Time = round(tmp_solution[, "time"]*24, digits = 3),
-    httk_Preds = tmp_solution[, "Cplasma"]
-  )
-  retdf[which(retdf$Time %in% unique(round(times, 3))), ]
-}
-
-httk_preds_rat <- get_httk_preds(rat_pars_rat, this_pk, species = "rat")
-
-```
-
-We need to put the _in vivo_ data in an amenable format.
-For this I will limit the species to "rat", the chemicals to
-`common_chems_rat`, and the medium to "plasma".
-
-```{r rat_data}
-rat_df <- httk_preds_rat %>%
-  left_join(predict(this_pk)) %>%
-  semi_join(this_winmodel)
-
-rat_df %>% ggplot(mapping = aes(
-    x = Conc_est,
-    y = httk_Preds,
-    color = interaction(Route)
-  )) +
-  geom_point() +
-  geom_abline(slope = 1, intercept = 0, color = "black") +
-  scale_x_log10() + scale_y_log10() +
-  facet_wrap(~Route)
-
-rat_plots <- rat_df %>%
-  distinct(Chemical, Species, Dose, Route, Media, Reference,
-           Time, httk_Preds, Conc, Conc_est, pLOQ) %>%
-  mutate(Dose = as.factor(Dose)) %>%
-  group_by(Chemical, Species, Route, Media, Reference) %>%
-  nest(.key = "data_pl")
-
-rat_plots <- rat_plots %>%
-  reframe(plots = purrr::map(data_pl,
-                             \(x) {
-                               cowplot::plot_grid(
-                               ggplot(data = x %>%
-                                        group_by(Time, Dose) %>%
-                                        mutate(meanConc = mean(Conc,
-                                                           na.rm = TRUE)) %>%
-                                        select(-Conc) %>% distinct() %>%
-                                        pivot_longer(cols = c(httk_Preds,
-                                                              meanConc,
-                                                              Conc_est),
-                                                     names_to = "Measurement",
-                                                     values_to = "Concentration"
-                                                     ), 
-                                      mapping = aes(
-                                        x = Time,
-                                        y = Concentration,
-                                        color = Measurement,
-                                        shape = Dose
-                                      )) +
-                                 geom_point() +
-                                 geom_line(
-                                   aes(group = interaction(Measurement, Dose))
-                                   ) +
-                                 theme_bw() +
-                                 labs(
-                                   title = paste(Chemical, Species),
-                                   subtitle = paste(Route, Media)
-                                 ),
-                               ggplot(data = x) +
-                                 geom_point(aes(x = Conc_est, httk_Preds,
-                                                shape = Dose)) +
-                                 geom_abline(slope = 1, intercept = 0,
-                                             linetype = "dashed") +
-                                 theme_bw()
-                               )
-                             })
-  )
-
-pdf(file = paste0(Sys.getenv("FIG_DIR"), "RC_comparison_CvTplots.pdf"),
-    onefile = TRUE,
-    height = 7,
-    width = 10,
-    bg = "white")
-
-for (i in 1L:NROW(rat_plots)) {
-  message("Now plotting: ", i)
-  print(rat_plots %>% pull(plots) %>% .[[i]])
-}
-
-dev.off()
-
-length(unique(rat_df$Chemical))
-
-rat_df$Chemical <- factor(rat_df$Chemical, levels = clear_chem_levels)
-
-rat_out <- rat_df %>%
-  filter(Chemical %in% clear_chem_levels) %>%
-  group_by(Chemical, Species, Route, Reference, Media) %>%
-  mutate(httk_Preds = ifelse(httk_Preds < pLOQ, pLOQ, httk_Preds)) %>% 
-  mutate(SLE = (log2(Conc) - log2(httk_Preds))^2,
-         AE = abs(Conc - httk_Preds)) %>%
-  summarize(
-    RMSLE = sqrt(mean(SLE, na.rm = TRUE)),
-    MAE = mean(AE, na.rm = TRUE)
-   ) %>% pivot_longer(cols = c(RMSLE, MAE),
-                      names_to = "metric",
-                      values_to = "value")
-
-rat_out %>%
-  na.omit() %>%
-  ggplot() +
-  geom_tile(data = rat_out %>% na.omit() %>%
-              filter(metric %in% "RMSLE"),
-            aes(x = metric, y = Chemical, fill = value)) +
-  scale_fill_gradient(low = "grey5", high = "grey90",
-                      name = "RMSLE") +
-  ggnewscale::new_scale_fill() +
-  geom_tile(data = rat_out %>% na.omit() %>%
-              filter(metric %in% "MAE"),
-            aes(x = metric, y = Chemical, fill = value)) +
-  scale_fill_gradient(low = "darkgreen", high = "seagreen1",
-                      limits = c(0, 80),
-                      labels = c("0", "20",
-                                 "40", "60",
-                                 "80+"),
-                      oob = scales::squish,
-                      name = "MAE") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(hjust = 1, angle = 50),
-        legend.title = element_text(hjust = 0.5)) +
-  coord_fixed(ratio = 0.75)
-
-ggsave(
-  filename = paste0(
-    Sys.getenv("FIG_DIR"),
-    "rat_httk_predictionRMSLE.png"
-  ),
-  height = 8.1,
-  width = 4,
-  device = "png"
-)
-
-rat_out2 <- rat_df %>%
-  group_by(Chemical, Species, Route, Dose) %>% nest() %>%
-  summarize(plot = map(
-    data,
-    \(d){
-      ggplot(d, aes(x = Time)) +
-        geom_point(aes(y = Conc)) +
-        geom_line(aes(y = httk_Preds),
-                    color = "forestgreen") +
-        geom_point(aes(y = httk_Preds),
-                   color = "forestgreen",
-                   shape = 1) +
-        labs(title = Chemical,
-             subtitle = paste(Dose, "mg/kg given via",
-                               Route, "bolus"),
-             y = "Plasma Concentration (mg/L)",
-             x = "Time (hrs)") +
-        theme_bw() +
-        theme(plot.title = element_text(hjust = 0.5),
-              plot.subtitle = element_text(hjust = 0.5))
-    }
-  ))
-```
-
-```{r httk_solution}
-
-rat_params %>%
-  ggplot(aes(y = fupClint)) + 
-  geom_point(aes(x = Clint), color = "darkred", shape = 1) +
-  geom_abline(slope = 1, intercept = 0, color = "darkblue",
-              linetype = "dashed")
-rat_params %>%
-  mutate(fup_z = scale(Funbound.plasma),
-         clint_z = scale(Clint)) %>%
-  dplyr::select(Chemical, fup_z, clint_z) %>%
-  pivot_longer(cols = c(fup_z, clint_z),
-               names_to = "pars", values_to = "vals") %>%
-  ggplot(aes(x = pars, y = vals, group = Chemical)) +
-  geom_line()
-
-httk::calc_tkstats(dtxsid = unique(rat_out$Chemical)[[5]])
-httk::parameterize_gas_pbtk(
-  restrictive.clearance = TRUE,
-  dtxsid = unique(rat_out$Chemical)[[5]]
-)
-
-httk::solve_gas_pbtk(
-  dtxsid = unique(combined_clearance_df$Chemical)[[5]],
-  parameters = httk::parameterize_gas_pbtk(
-    restrictive.clearance = TRUE,
-    dtxsid = unique(combined_clearance_df$Chemical)[[5]]
-  ),
-  dose = 10,
-  exp.conc = 0,
-  input.units = "mg",
-  output.units = "mg",
-  days = 3,
-  plots = TRUE
-)
-
-# For the invivoPKfit functions, we will hold kelim constant
-# This constant will be calculated as CLtot/Vdist (or V1, if 2-compartment)
-# This constant is derived by httk in the following way:
-calc_total_clearance(
-  dtxsid = common_chems[[10]],
-  restrictive.clearance = FALSE
-) /
-  calc_vdist(dtxsid = common_chems[[10]])
-```
-
-I have modified the starts of the 1- and 2-compartment models,
-as well as adding a restrictive_clearance argument in stat_model.
-
-```{r running-invivoPKfit}
-# This is now updated to use dawson chem table
-minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% this_chem_v,
-                          species %in% "rat",
-                          administration_route_normalized == "iv"))
-
-new_pk <- minimal_pk +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(
-    keep_data_original = TRUE,
-    suppress.messages = FALSE
-  ) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  stat_error_model(error_group = vars(Chemical, Species)) +
-  stat_model(model = c(
-    "model_1comp", "model_1comp_cl_rest", 
-    "model_1comp_cl_nonrest", "model_1comp_fup",
-    "model_flat")) +
-  settings_optimx(method = c("bobyqa"))
-
-new_pk <- do_data_info(new_pk)
-
-new_pk <- do_prefit(new_pk)
-gc()
-
-unique(new_pk$prefit$par_DF$param_name) # Check all parameters are there
-length(unique(new_pk$data$Chemical)) 
-length(unique(this_chem_v))
-
-new_pk <- do_fit(new_pk, n_cores = 14)
-gc()
-
-new_pk$fit %>%
-  View()
-
-# saveRDS(new_pk, "data-raw/ratCVT_wHTTK_reformulated.rds")
-```
-
-Here we begin the analysis by estimating the relative likelihood of
-"clearance aware" models. This provides an additional evaluation of the evidence
-that points towards a restrictive or non-restrictively cleared model.
-
-```{r begin_analysis}
-# new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
-coef(new_pk) %>% View()
-new_winmodel <- get_winning_model(new_pk)
-eval_tkstats(new_pk, finite_only = TRUE) %>% 
-  semi_join(new_winmodel) %>%
-  View()
-
-AIC(new_pk) %>%
-  arrange(Chemical, Species) %>%
-  group_by(model, method) %>% 
-  count(is.finite(AIC))
-
-new_tkstats <- eval_tkstats(new_pk, finite_only = TRUE)
-
-pl2comp <- plot(new_pk,
-                use_scale_conc = FALSE,
-                n_interp = 12
-)
-
-pl2comp %>%
-  filter(Chemical %in% "DTXSID4020533") %>%
-  pull(final_plot)
-
-rel_ll <- AIC(new_pk) %>% 
-  filter(is.finite(AIC)) %>% 
-  dplyr::select(-c(log_likelihood, npar)) %>% 
-  pivot_wider(names_from = model,
-              values_from = AIC) %>% 
-  rowwise() %>% 
-  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(across(starts_with("model_"), \(x) {
-    signif(exp((minAIC - x)/2) * 100, 4)
-  }))
-
-# Test whether the flat model has lowest relative likelihood
-rel_ll %>%
-  dplyr::select(-c(Species, method))
-# We can inspect this visually
-rel_ll %>% arrange(desc(model_flat)) %>% head()
-rel_ll %>%
-  dplyr::select(-c(Species, method)) %>% 
-  rowwise() %>% 
-  mutate(across(contains("_1comp"),
-                \(x) {
-                  ifelse(
-                    x < model_flat | x < 1,
-                    NA_real_,
-                    x
-                  )
-                })) %>% 
-  filter(!if_all(contains("_1comp_"), is.na)) %>%
-  clipr::write_clip()
-
-rel_ll %>%
-  rowwise() %>% 
-  mutate(across(contains("_1comp"),
-                \(x) {
-                  ifelse(
-                    x < model_flat | x < 1,
-                    NA_real_,
-                    x
-                  )
-                })) %>% 
-  count(is.na(model_1comp_fup))
-  # drop_na(model_1comp_fup) %>%
-  # filter(Chemical %in% clear_chem_levels) %>% View()
-
-new_pk$fit %>%
-  filter(param_name %in% "Fup",
-         model %in% "model_1comp_fup") %>%
-  ggplot(aes(x = estimate, y = start)) +
-  geom_point(size = 1.25) +
-  theme_bw() +
-  coord_equal(xlim = c(0,1), ylim = c(0,1),
-              expand = TRUE) +
-  coord_flip()
-
-ggsave(filename = paste0(
-  Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
-  today, "fup_optimization_allowingHuman.png"),
-  height = 5, width = 5)
-
-new_pk$fit %>%
-  filter(param_name %in% "Fup",
-         model %in% "model_1comp_fup") %>%
-  distinct(Chemical, Species, method, model,
-           param_name, estimate, start) %>%
-  mutate(direction = ifelse(abs(estimate - start) < 0.1,
-                            "similar (less than 10% difference)",
-                            ifelse(estimate > start,
-                                   "increase",
-                                   "decrease"))) %>%
-  # filter(direction %in% "similar (less than 10% difference)") %>%
-  pivot_longer(cols = c(estimate, start),
-               names_to = "parameterization",
-               values_to = "value") %>%
-  mutate(parameterization = factor(parameterization,
-                                   levels = c("start", "estimate"))) %>%
-  ggplot(aes(x = parameterization, y = value)) +
-  geom_point() +
-  geom_line(aes(group = Chemical)) +
-  facet_grid(cols = vars(direction)) +
-  labs(title = "Optimization of fraction unbound in plasma") +
-  theme_bw()
-
-ggsave(filename = paste0(
-  Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
-  today, "fup_optimization_generalFits_allowingHuman.png"),
-  height = 5, width = 7)
-
-```
-
-Why are so many fits failing?
-Well, we should take a look at the parameter which we are holding constant,
-`kelim` and whether the new starting points vastly differ from those in the
-starting points based on the data.
-
-For this I will just use the PK object I have saved `this_pk` and take the
-_prefit_ parameter estimations and first compare that with eventual optimized `kelim`.
-
-```{r kelim-questions}
-# Original data, filtered for common_chems
-# par_DF
-this_kelim_prefit <- this_pk$prefit$par_DF %>%
-  filter(
-    param_name %in% "kelim",
-  ) %>%
-  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)
-
-this_kelim_fit <- get_fit(this_pk) %>%
-  semi_join(get_winning_model(this_pk)) %>%
-  ungroup() %>%
-  filter(param_name == "kelim") %>%
-  distinct(model, Chemical, Species, param_name, value)
-
-this_kelim_df <- inner_join(this_kelim_fit, this_kelim_prefit)
-
-httk_df <- new_pk$prefit$par_DF %>%
-  filter(param_name %in% "kelim") %>%
-  distinct(Chemical, Species, param_name, start) %>%
-  rename(init_restrictive = "start") %>%
-  inner_join(
-    nonrest_pk$prefit$par_DF %>%
-      filter(param_name %in% "kelim") %>%
-      distinct(Chemical, Species, param_name, start) %>%
-      rename(init_nonrestrictive = "start")
-  )
-
-full_df <- inner_join(this_kelim_df, httk_df) %>%
-  relocate(fit_kelim, .after = last_col())
-
-full_df %>%
-  ggplot(aes(x = Chemical)) +
-  geom_hline(yintercept = 1, linetype = "dashed", color = "grey30") +
-  geom_errorbar(aes(ymax = upper_bound, ymin = lower_bound)) +
-  geom_point(aes(y = fit_kelim, color = "Original Optimized")) +
-  geom_point(aes(y = init_restrictive, color = "Restrictive")) +
-  geom_point(aes(y = init_nonrestrictive, color = "Non-restrictive")) +
-  geom_point(aes(y = start, shape = "Original Initialized")) +
-  facet_grid(rows = vars(Species), scales = "free", space = "free") +
-  scale_color_manual(
-    name = "kelim",
-    breaks = c("Original Optimized", "Restrictive", "Non-restrictive"),
-    values = c(
-      "Original Optimized" = "skyblue4",
-      "Restrictive" = "orange2",
-      "Non-restrictive" = "green4"
-    )
-  ) +
-  scale_shape_manual(
-    name = "",
-    values = 4
-  ) +
-  coord_flip() +
-  scale_y_log10(labels = scales::label_math(format = log10)) +
-  theme(
-    panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
-    panel.background = element_blank(),
-    panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-    strip.background = element_rect(fill = "white"),
-    strip.text = element_text(face = "bold"),
-    legend.direction = "vertical",
-    axis.ticks = element_blank(),
-    axis.line = element_blank(),
-    axis.text.y = element_blank(),
-    strip.text.y = element_text(angle = 0)
-  )
-
-ggsave(
-  filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare.png"),
-  height = 11,
-  width = 8.5
-)
-```
-
-```{r new_analysis}
-# Loading the new data
-
-new_wm <- get_winning_model(new_pk)
-new_AIC <- AIC(new_pk)
-new_rsq <- rsq(new_pk)
-new_rmse <- rmse(new_pk, use_scale_conc = FALSE)
-
-new_tkstats <- eval_tkstats(new_pk, finite_only = FALSE)
-
-new_resid <- residuals(new_pk)
-
-this_data <- get_data(new_pk) %>%
-  distinct(Chemical, Species, Reference, Route, Media, Dose, Time, Conc) %>%
-  right_join(new_resid)
-
-pl <- plot(new_pk, n_interp = 12, use_scale_conc = FALSE)
-pdf(
-  file = paste0(
-    Sys.getenv("FIG_DIR"),
-    "AllFits_nonDoseNorm_newPK_reParametizedModels_2024_0412.pdf"
-  ),
-  height = 6, width = 10
-)
-for (i in seq_len(nrow(pl))) {
-  print(pl$final_plot[[i]])
-}
-dev.off()
-```
-
-Comparing total clearance estimates for those where a restrictive or non-restrictive model
-was the "best fit" as determined by AIC.
-
-```{r cltot-comparison}
-new_cltot2 <- new_tkstats %>%
-  filter(str_detect(model, "rest")) %>%
-  select(
-    Chemical, Species, Media, Route,
-    model, method,
-    CLtot.tkstats, CLtot.nca
-  ) %>%
-  filter(!is.na(CLtot.tkstats)) %>%
-  mutate(clearance_type = ifelse(str_detect(model, "nonrest"),
-                                 "NonRestrictive",
-                                 ifelse(str_detect(model, "rest"),
-                                        "Restrictive",
-                                        "optimized kelim"
-                                 )
-  )) %>%
-  rowwise() %>%
-  mutate(
-    CLtot.httk_rest = calc_total_clearance(
-      dtxsid = Chemical,
-      restrictive.clearance = TRUE
-    ),
-    CLtot.httk_nonrest = calc_total_clearance(
-      dtxsid = Chemical,
-      restrictive.clearance = FALSE
-    )
-  )
-
-new_cltot2 %>%
-  ggplot(aes(x = Chemical)) +
-  geom_point(aes(y = CLtot.httk_rest),
-             shape = 19, size = 2, color = "green4") +
-  geom_point(aes(y = CLtot.httk_nonrest),
-             shape = 19, size = 2, color = "orange2") +
-  geom_point(aes(y = CLtot.tkstats,
-                 shape = Species), size = 3, color = "black", stroke = 1) +
-  scale_y_log10(labels = scales::label_math(format = log10)) +
-  geom_hline(yintercept = c(0.01, 0.1, 1, 10)) +
-  scale_shape_manual(values = c(0, 1, 2, 5, 6)) +
-  coord_flip() +
-  facet_grid(
-    rows = vars(clearance_type),
-    scales = "free", space = "free"
-  ) +
-  labs(title = paste(
-    "CLtot for constant kelim \"best fits\" (empty)",
-    "and httk calculations (filled)",
-    sep = "\n"
-  )) +
-  theme_bw() +
-  theme(
-    axis.line = element_line(linewidth = 1),
-    axis.text = element_text(size = 12),
-    axis.title = element_blank(),
-    plot.title = element_text(hjust = 0.5),
-    plot.background = element_rect(fill = "white"),
-    strip.text.y = element_text(angle = 0),
-    strip.background = element_blank(),
-    legend.position = "none"
-  )
-
-ggsave(
-  filename = paste0(Sys.getenv("FIG_DIR"),
-                    "Cltot_backcompare_wDawson_2024_0416.png"),
-  height = 8,
-  width = 9
-)
-```
-
-```{r chemical-correlation}
-new_AIC %>%
-  ungroup() %>%
-  filter(
-    model %in% c("model_1comp", "model_2comp"),
-    Species %in% "rat"
-  ) %>%
-  group_by(Chemical) %>%
-  filter(AIC == min(AIC)) %>%
-  mutate(estimate = "nonConst") %>%
-  distinct(Chemical, model, estimate) -> nAIC_nonConst
-new_AIC %>%
-  ungroup() %>%
-  filter(
-    model %in% c("model_1comp_rest", "model_2comp_rest"),
-    Species %in% "rat"
-  ) %>%
-  group_by(Chemical) %>%
-  filter(AIC == min(AIC)) %>%
-  mutate(estimate = "Rest") %>%
-  distinct(Chemical, model, estimate) -> nAIC_rest
-new_AIC %>%
-  ungroup() %>%
-  filter(
-    model %in% c("model_1comp_nonrest", "model_2comp_nonrest"),
-    Species %in% "rat"
-  ) %>%
-  group_by(Chemical) %>%
-  filter(AIC == min(AIC)) %>%
-  mutate(estimate = "nonRest") %>%
-  distinct(Chemical, model, estimate) -> nAIC_nonrest
-
-full_nAIC <- bind_rows(nAIC_nonConst, nAIC_rest) %>%
-  bind_rows(nAIC_nonrest)
-
-new_tkstats_full <- get_tkstats(new_pk)
-
-new_tkstats_full %>%
-  filter(Species %in% "rat", !(model %in% "model_flat")) %>%
-  distinct(Chemical, model, CLtot) %>%
-  inner_join(full_nAIC) %>%
-  na.omit() %>%
-  distinct(Chemical, estimate, CLtot) %>%
-  pivot_wider(
-    names_from = estimate,
-    values_from = CLtot
-  ) %>%
-  rowwise() %>%
-  mutate(
-    CLtot.httk_rest = calc_total_clearance(
-      dtxsid = Chemical,
-      restrictive.clearance = TRUE
-    ),
-    CLtot.httk_nonrest = calc_total_clearance(
-      dtxsid = Chemical,
-      restrictive.clearance = FALSE
-    )
-  ) %>%
-  ungroup() %>%
-  mutate(
-    A_rest = log(nonConst) - log(CLtot.httk_rest),
-    A_nonrest = log(nonConst) - log(CLtot.httk_nonrest),
-    B_rest = log(Rest) - log(CLtot.httk_rest),
-    B_nonrest = log(Rest) - log(CLtot.httk_nonrest),
-    C_rest = log(nonRest) - log(CLtot.httk_rest),
-    C_nonrest = log(nonRest) - log(CLtot.httk_nonrest)
-  ) %>%
-  select(Chemical, A_rest:C_nonrest) -> df_valcomp
-
-df_valcomp %>%
-  column_to_rownames(var = "Chemical") %>%
-  t() %>%
-  as.matrix() %>%
-  cor() %>%
-  signif() -> val_cormat
-
-hclust(d = as.dist((1 + val_cormat) / 2), method = "average") %>% plot()
-
-hclust(d = as.dist((1 + val_cormat) / 2), method = "average") -> val_hclust
-
-corrplot::corrplot(abs(val_cormat))
-
-# reorder the Chemical names prior to plotting
-df_valcomp %>%
-  mutate(Chemical = factor(
-    x = Chemical,
-    levels = val_hclust$labels[val_hclust$order]
-  )) %>%
-  pivot_longer(
-    cols = A_rest:C_nonrest,
-    names_to = "comparison", values_to = "logres"
-  ) %>%
-  mutate(
-    comparison = case_when(
-      comparison == "A_nonrest" ~ "free kelim vs httk nonrestrictive",
-      comparison == "A_rest" ~ "free kelim vs httk restrictive",
-      comparison == "B_nonrest" ~ "restrictive kelim vs httk nonrestrictive",
-      comparison == "B_rest" ~ "restrictive kelim vs httk restrictive",
-      comparison == "C_nonrest" ~ "nonrestrictive kelim vs httk nonrestrictive",
-      comparison == "C_rest" ~ "nonrestrictive kelim vs httk restrictive",
-    ),
-    comparison = factor(comparison,
-                        levels = c(
-                          "free kelim vs httk restrictive",
-                          "free kelim vs httk nonrestrictive",
-                          "restrictive kelim vs httk restrictive",
-                          "nonrestrictive kelim vs httk nonrestrictive",
-                          "nonrestrictive kelim vs httk restrictive",
-                          "restrictive kelim vs httk nonrestrictive"
-                        )
-    )
-  ) %>%
-  ggplot(aes(x = comparison, y = Chemical, fill = logres)) +
-  geom_tile() +
-  scale_fill_gradient2(
-    mid = "grey5", high = "orange", low = "green3",
-    name = "Total Clearance\nlog10-scale difference",
-    limits = c(-4, 4),
-    oob = scales::oob_squish
-  ) +
-  coord_fixed(ratio = 0.3) +
-  theme_bw() +
-  theme(
-    axis.text.x = element_text(hjust = 1, angle = 45),
-    axis.ticks.y = element_blank(),
-    panel.grid = element_blank(),
-    axis.title.x = element_blank()
-  )
-
-ggsave(
-  filename = paste0(Sys.getenv("FIG_DIR"), "Cltot_compare_heatmap_2024_0409.png"),
-  height = 14,
-  width = 8
-)
-```
-
-# Winning models - An aside
-
-I am a little worried that I am not selecting the best fit model for each
-chemical all the time. Ultimately, the consequences for this being having parameters
-for chemicals with rather poor fits in general, when there is a better fitting
-model available. Here I want to do a quick analysis of the chemical
-*DTXSID3022405* in mouse. The one compartment fits best in the original data
-(by visual inspection) but the 2-compartment wins out in minimizing AIC.
-
-For each model, I can find how many distinct experimental timepoints have the minimum
-RMSE then investigate whether the model with the most _minimum RMSE_ timepoint
-corresponds to the winning model by AIC.
-
-*Update*: About half do not correspond. However, the lack of correspondance doesn't
-mean there is bad fits declared winning model. To address this I need to understand 
-_how_ different the AIC-based winning model and the RMSE-based winning models
-are and whether the data leaves something to be desired.
-This may be as simple as a Pearson correlation between residual values.
-The output of this analysis is how related both
-
-Another thing I am noticing in oral data: the constant _kelim_ fits sometimes are very similar
-to their respective non-constant _kelim_ fits and they actually intersect/cross over.
-I wonder if there is something special about the timepoints at which they intersect.
-For example, a restrictive fit will reach a slightly higher Cmax, but then
-dive below the fully optimized fit during elimination phase before crossing over
-again near the second inflection point.
-
-```{r oxybenzene-test}
-old_AIC <- AIC(this_pk) %>%
-  filter(
-    Chemical %in% "DTXSID3022405",
-    Species %in% "mouse"
-  )
-
-new_AIC <- new_AIC %>%
-  filter(
-    Chemical %in% "DTXSID3022405",
-    Species %in% "mouse"
-  )
-
-plot(new_pk,
-     model = c(
-       "model_2comp",
-       "model_1comp", "model_1comp_nonrest"
-     ),
-     use_scale_conc = FALSE
-) %>%
-  filter(
-    Chemical %in% "DTXSID3022405",
-    Species %in% "mouse"
-  ) %>%
-  pull(final_plot) %>%
-  .[[1]]
-
-old_rsquared <- rmse(this_pk) %>%
-  filter(
-    Chemical %in% "DTXSID3022405",
-    Species %in% "mouse"
-  )
-
-# Only test residual correlations with those not the same
-
-winmodel_conflict <- rmse(new_pk, use_scale_conc = FALSE) %>%
-  group_by(Chemical, Species, Route, Media, Dose, Time) %>%
-  filter(RMSE == min(RMSE)) %>%
-  group_by(Chemical, Species) %>%
-  count(model) %>%
-  filter(n == max(n)) %>%
-  inner_join(new_wm %>% rename("winmodel" = "model")) %>%
-  filter(!(model == winmodel))
-
-# need to map2 then have `residuals.pk(model = .x)` and .y
-# then correlate these values for each data group
-winmodel_conflict %>% names()
-
-mod_red <- winmodel_conflict %>%
-  dplyr::select(Chemical, Species, model) %>%
-  left_join(new_resid,
-            by = join_by(Chemical, Species, model)
-  ) %>%
-  rename("mod_residuals" = "Residuals") %>%
-  select(
-    Chemical, Species, Route, Media, Time, Detect, exclude,
-    model, mod_residuals
-  )
-
-wm_red <- winmodel_conflict %>%
-  dplyr::select(Chemical, Species, winmodel) %>%
-  left_join(new_resid,
-            by = join_by(Chemical, Species, "winmodel" == "model")
-  ) %>%
-  rename("wm_residuals" = "Residuals") %>%
-  select(
-    Chemical, Species, Route, Media, Time, Detect, exclude,
-    winmodel, wm_residuals
-  )
-sum_red <- new_resid %>%
-  group_by(Chemical, Species, model) %>%
-  summarize(MSE = sum(Residuals^2) / n())
-
-cor_mod <- mod_red %>%
-  inner_join(wm_red) %>%
-  select(Chemical, Species, model, mod_residuals, winmodel, wm_residuals) %>%
-  group_by(Chemical, Species, model, winmodel) %>%
-  summarize(cor_mods = cor(x = mod_residuals, y = wm_residuals)) %>%
-  left_join(sum_red, by = join_by(Chemical, Species, model)) %>%
-  rename("mod_MSE" = "MSE") %>%
-  left_join(sum_red, by = join_by(Chemical, Species, "winmodel" == "model")) %>%
-  rename("wm_MSE" = "MSE")
-
-this_pl_1comp <- plot(new_pk,
-                    n_interp = 11, use_scale_conc = FALSE,
-                    model = c(
-                      "model_1comp",
-                      "model_1comp_rest",
-                      "model_1comp_nonrest"
-                    )
-)
-
-this_pl_2comp <- plot(new_pk,
-                    n_interp = 11, use_scale_conc = FALSE,
-                    model = c(
-                      "model_2comp",
-                      "model_2comp_rest",
-                      "model_2comp_nonrest"
-                    )
-)
-
-# General trends about residual correlation and MSE
-cor_mod %>%
-  mutate(cor_bin = ifelse(abs(cor_mods) >= 0.60,
-                          "Taking win_model",
-                          "Taking low RMSE model"
-  )) %>%
-  na.omit() %>%
-  ggplot() +
-  geom_point(aes(x = mod_MSE, y = wm_MSE)) +
-  scale_x_log10() +
-  scale_y_log10() +
-  geom_abline(slope = 1, intercept = 0, linetype = "dotted") +
-  facet_grid(rows = vars(cor_bin))
-
-cor_mod %>%
-  filter(!(model %in% "model_flat")) %>%
-  mutate(cor_bin = ifelse(abs(cor_mods) >= 0.60,
-                          "Taking win_model",
-                          "Taking low RMSE model"
-  )) %>%
-  na.omit() %>%
-  ggplot() +
-  geom_histogram(aes(x = cor_mods, fill = model),
-                 binwidth = 0.05
-  ) +
-  facet_grid(rows = vars(winmodel)) +
-  scale_fill_viridis_d() +
-  theme_bw() +
-  theme(strip.text.y = element_text(angle = 0)) +
-  labs(
-    x = "Correlation of Residuals",
-    fill = "model by grouped RMSE"
-  )
-
-ggsave(
-  filename = paste0(
-    Sys.getenv("FIG_DIR"), "winModel_correlations_changes",
-    "_2024_Apr_16.png"
-  ),
-  height = 6,
-  width = 8
-)
-
-# Try oxybenzone fitting without dose-norm
-minimal_pk <- pk(
-  data = cvt %>%
-    filter(analyte_dtxsid %in% "DTXSID3022405"),
-  mapping = ggplot2::aes(
-    Chemical = analyte_dtxsid,
-    Chemical_Name = analyte_name_original,
-    DTXSID = analyte_dtxsid,
-    CASRN = analyte_casrn,
-    Species = species,
-    Reference = document_id,
-    Media = conc_medium_normalized,
-    Route = administration_route_normalized,
-    Dose = dose_level_normalized,
-    Dose.Units = "mg/kg",
-    Subject_ID = subject_id,
-    Series_ID = series_id,
-    Study_ID = study_id,
-    ConcTime_ID = conc_time_id,
-    N_Subjects = n_subjects_in_series,
-    Weight = weight_kg,
-    Weight.Units = "kg",
-    Time = time_hr,
-    Time.Units = "hours",
-    Value = conc,
-    Value.Units = "mg/L",
-    Value_SD = conc_sd_normalized,
-    LOQ = loq
-  )
-)
-new_pk <- minimal_pk +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(
-    keep_data_original = TRUE,
-    suppress.messages = FALSE
-  ) +
-  settings_optimx(method = c("L-BFGS-B")) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE) +
-  stat_error_model(error_group = vars(Chemical, Species, Reference)) +
-  stat_model(model = c(
-    "model_flat", "model_1comp", "model_2comp",
-    "model_1comp_rest", "model_1comp_nonrest",
-    "model_2comp_rest", "model_2comp_nonrest"
-  ))
-
-new_pk <- do_fit(new_pk, n_cores = 3)
-get_winning_model(new_pk)
-plot(new_pk, best_fit = TRUE) %>% pull(final_plot)
-```
-
-# Categorizing chemicals
-
-I first need to find the winning model for constant kelims and optimized kelims
-
-```{r categorization}
-grouped_wm <- new_AIC %>%
-  mutate(model_type = case_when(
-    str_detect(model, "_nonrest$") ~ "Nonrestrictive",
-    str_detect(model, "_rest$") ~ "Restrictive",
-    .default = "Free_kelim"
-  )) %>%
-  group_by(Chemical, Species, model_type) %>%
-  filter(AIC == min(AIC)) %>%
-  ungroup() %>%
-  arrange(Chemical, Species, model_type) %>%
-  select(Chemical, Species, model, method, model_type)
-
-grouped_tkstats <- get_tkstats(new_pk) %>%
-  inner_join(grouped_wm)
-
-grouped_tkstats %>%
-  select(
-    Chemical, Species, Reference,
-    Route, Media, model_type,
-    CLtot
-  ) %>%
-  pivot_wider(names_from = model_type, values_from = CLtot) %>%
-  mutate(
-    low_invivo_CL = ifelse(
-      Free_kelim < Nonrestrictive / 2 | Free_kelim < Restrictive / 2,
-      TRUE, FALSE
-    ),
-    high_extra_hepCL = ifelse(
-      Free_kelim > 1.5 * Nonrestrictive | Free_kelim > 1.5 * Restrictive,
-      TRUE, FALSE
-    ),
-    rest_metabol = ifelse(
-      Free_kelim > Restrictive / 2 & Free_kelim < 1.5 * Nonrestrictive,
-      TRUE, FALSE
-    ),
-    combo_cat = paste0(
-      low_invivo_CL + 0,
-      high_extra_hepCL + 0,
-      rest_metabol + 0
-    )
-  ) %>%
-  count(combo_cat)
-arrange(Chemical, combo_cat) %>%
-  na.omit() %>%
-  View()
-```
-
-## New reformulated models that estimate Fup!
-
-```{r reformMod}
-get_tkstats(new_pk) %>%
-  distinct(Chemical, Species, model, CLtot) %>%
-  pivot_wider(names_from = model, values_from = CLtot) %>%
-  left_join(new_pk$prefit$par_DF %>%
-              filter(param_name == "CLtot") %>%
-              select(Chemical, Species, model, start) %>%
-              mutate(model = paste0("start_", model)) %>%
-              pivot_wider(
-                names_from = model,
-                values_from = start
-              )) %>%
-  View("Clearance")
-
-new_cl_tkstats <- get_tkstats(new_pk)
-this_tkstats <- this_pk %>%
-  get_winning_model() %>%
-  left_join(coef(this_pk)) %>%
-  left_join(rsq(this_pk)) %>%
-  distinct()
-this_tkstats %>%
-  select(-coefs_vector) %>%
-  clipr::write_clip()
-# Send the R2 too.
-
-## Need to parameterize with gas_pbpk or new 3compartment
-## To add into total clearance
-# Rb2p * Qalv/Kblood2air
-```
-
-# Calculating uncertainty of parameter estimation
-
-Below I will use the `coef_sd` method to estimate standard deviation of
-the fraction unbound parameter and assess whether this may contribute
-to the uncertainty of 'declaration' of clearance for chemicals that have
-CvT data documented.
-
-```{r uncertainty_estimation}
-this_coefsd <- coef_sd(new_pk)
-
-this_coefsd %>% filter(param_name == "Clint", Chemical %in% clear_chem_levels) %>%
-  ggplot(aes(x = factor(Chemical, levels = clear_chem_levels), 
-             y = param_value,
-             color = model)) +
-  geom_point(alpha = 0.5) +
-  geom_linerange(aes(ymin = param_value-param_sd,
-                    ymax = param_value+param_sd),
-                 alpha = 0.5) +
-  theme_bw() +
-  coord_flip() +
-  scale_y_log10()
-
-ggsave(
-  filename = paste0(
-    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
-    today,
-    "fup_sd_estimates.png"
-  ),
-  height = 8,
-  width = 8,
-  device = "png"
-)
-
-this_loglikelihood <- AIC(new_pk) %>%
-  filter(Chemical %in% clear_chem_levels) %>%
-  mutate(Chemical = factor(Chemical, levels = clear_chem_levels))
-
-this_loglikelihood %>%
-  ggplot(aes(x = model, y = Chemical, fill = log10(AIC))) +
-  geom_tile() +
-  scale_fill_viridis_c(option = "mako", direction = -1) +
-  coord_fixed() +
-  theme(axis.text.x = element_text(angle = 60, hjust = 1))
-
-ggsave(
-  filename = paste0(
-    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
-    today,
-    "fup_AIC_heatmap.png"
-  ),
-  height = 10,
-  width = 4,
-  device = "png"
-)
-
-select_chem_info <- get_chem_info_batch(clear_chem_levels)
-
-select_chem_info %>%
-  filter(propertyId == "logkow-octanol-water") %>%
-  mutate(dtxsid = factor(dtxsid, levels = clear_chem_levels)) %>%
-  ggplot(aes(x = value, y = dtxsid, color = source)) +
-  geom_point() +
-  labs(title = "logKow") +
-  geom_vline(xintercept = 5)
-
-# Also check whether the Fup or CLint are at their respective extremes (1, 0)
-# If they are, it will be difficult to tell whether a chemical is cleared in a
-# particular way
-
-```
-
-# Slow PBPK model optimization of fup for more chemicals
-
-There may also be an opportunity to evaluate chemicals without _in vivo_ data
-by comparing them to those that do. Effectively, we can look at the uncertainty
-in the call between restrictive/non-restrictive and further look at estimates
-from PBPK models where $f_{up}$ is optimized and it is run through `solve_pbtk`.
-
-```{r slow_pbpk_optimizations}
-
-```
-
-```{r}
-sessionInfo()
-```

### 2025-03-12 data-raw/ClearanceProject-3-TKstats.Rmd
Implemented bootstrapping-like analysis of steady state concentration values.

@@
 ```
+
+```{r library-loading}
+today <- format(Sys.Date(), "%d%b%Y")
+devtools::load_all()
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(ctxR)
+library(patchwork)
+```
+
+```{r data-loading}
+this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
+load("data-raw/chem_lists.RData")
+load("data-raw/plasma_CvTfits_data.RData")
+load("data-raw/rat_pars_human.RData")
+all_chem_properties <- readRDS("data-raw/ctxR_3comp2_cheminfo.rds")
+```
+
+```{r combination-function}
+combo_gen_splitter <- function(df, N = 3L, split_col) {
+  # Checks
+  stopifnot(
+    is.character(split_col),
+    is.data.frame(df),
+    is.integer(N)
+  )
+
+  # arrange by split_col and make ID column (row number)
+  df <- arrange(df, split_col)
+  df$ID <- 1:NROW(df)
+
+  # Split the data.frames (both combo sets)
+  df_split <- split(df, df[[split_col]])
+  # full_combos <- expand.grid(
+  #   lapply(df_split,
+  #          \(x) {
+  #            tmp_combos <- combn(x[['ID']], N)
+  #            apply(tmp_combos, MARGIN = 2, paste, collapse = ".")
+  #          })
+  # ) |> apply(1, paste, collapse = ".")
+
+  internal_combos <- lapply(df_split,
+           \(x) {
+             tmp_combos <- combn(x[['ID']], N)
+             apply(tmp_combos, MARGIN = 2, paste, collapse = ".")
+           })
+
+  # Check to see if full sampling will cause vector length issues
+  # Max length = 2^30 so we will set it to something comfortably below this
+  max_length = 14
+  prob_vectors <- sum(log2(vapply(internal_combos, length, numeric(1L)))
+  )
+
+  if (prob_vectors > max_length) {
+    message("Full sampling too memory intensive, performing random sampling")
+
+    for (i in rev(seq(0.001, 0.6, by = 0.001))) {
+      npv <- sum(log2(floor(i * vapply(internal_combos, length, numeric(1L)))))
+
+      if (npv < max_length) {
+        print(paste("Proportion that works: ", i))
+        print(paste("Number of full combinations expected: ", 2^npv))
+
+        internal_combos <- lapply(
+          internal_combos, \(x) {
+            prop_len = floor(length(x) * i)
+            sample(x, size = prop_len)
+          }
+        )
+        break
+      }
+    }
+  }
+
+  full_combos <- expand.grid(internal_combos)
+
+  full_combos <- apply(full_combos,1, paste, collapse = ".")
+
+  # Generate list of numeric for row filtering
+  split_combos <- strsplit(full_combos, split = "\\.")
+
+  # Generate list of sampled data sets
+  full_df_combos <- lapply(split_combos,
+         \(x) {
+           df[x,]
+         })
+
+  message(paste("Unique dataset samples: ", length(full_df_combos)))
+
+  invisible(full_df_combos)
+}
+
+```
+
+```{r example_chemical}
+# Using the example chemical
+full_pk <- readRDS("data-raw/all_cvt_pk.rds")
+full_tkstats <- get_tkstats(full_pk)
+
+get_data(full_pk) %>% filter(Conc > pLOQ) %>% count(Chemical, Species, Reference, Route, Dose, Time) %>% arrange(-n) %>%
+  mutate(combos = choose(n,3)) %>%
+  group_by(Chemical, Species, Reference, Route, Dose) %>%
+  summarize(TotalnCr = sum(combos)) %>% arrange(-TotalnCr) %>% 
+  right_join(full_pk$fit) %>% View()
+
+test_chem <- "DTXSID6073499"
+full_tkstats %>% filter(Chemical == test_chem) %>% glimpse()
+
+test_chem_data <- get_data(full_pk) %>%
+  filter(Chemical == test_chem)
+
+test_chem_data %>%
+  ggplot(aes(Time, Conc)) +
+  geom_point() +
+  facet_wrap(~Route+Dose+Media) +
+  theme_bw()
+
+test_chem_data_listsplits <- combo_gen_splitter(
+  test_chem_data,
+  4L,
+  'Time'
+)
+
+# Takes way too long, parallelize it
+
+clust <- parallel::makeCluster(parallel::detectCores()-2L)
+parallel::clusterCall(clust, function() devtools::load_all())
+system.time(
+  Css_list <- parallel::parLapply(clust, test_chem_data_listsplits,
+                                  \(x) {
+                                    tmp_pk <- pk(x,
+                                                 mapping = ggplot2::aes(
+                                                   Chemical = Chemical,
+                                                   Chemical_Name = Chemical_Name,
+                                                   DTXSID = DTXSID,
+                                                   CASRN = CASRN,
+                                                   Species = Species,
+                                                   Reference = Reference,
+                                                   Media = Media,
+                                                   Route = Route,
+                                                   Dose = Dose,
+                                                   Dose.Units = "mg/kg",
+                                                   Subject_ID = Subject_ID,
+                                                   Series_ID = Series_ID,
+                                                   Study_ID = Study_ID,
+                                                   ConcTime_ID = ConcTime_ID,
+                                                   N_Subjects = N_Subjects,
+                                                   Weight = Weight,
+                                                   Weight.Units = "kg",
+                                                   Time = Time,
+                                                   Time.Units = "hours",
+                                                   Value = Value,
+                                                   Value.Units = "mg/L",
+                                                   Value_SD = Value_SD,
+                                                   LOQ = LOQ
+                                                 )
+                                    ) +
+                                      scale_conc(dose_norm = TRUE,
+                                                 log10_trans = TRUE) +
+                                      settings_optimx(method = c(
+                                        "bobyqa"
+                                      ))
+
+                                    tmp_pk <- do_fit(tmp_pk)
+                                    tmp_tkstats <- get_tkstats(tmp_pk) %>%
+                                      distinct(Chemical, Species, Reference,
+                                               Route, Media,
+                                               model, method,
+                                               Css, CLtot, halflife)
+
+                                    return(tmp_tkstats)
+                                  })
+)
+parallel::stopCluster(clust)
+
+Css_df_full <- bind_rows(Css_list)
+
+```
+
+```{r}
+num_samples <- length(Css_list)
+
+test_chem_full_tkstats <- full_tkstats %>%
+  filter(Chemical == test_chem, model != "model_flat") %>%
+  distinct(Chemical, Species, model, Css)
+
+css_hist <- Css_df_full %>%
+  filter(model != "model_flat") %>%
+  ggplot(aes(x = Css)) +
+  geom_histogram(fill = "grey5", binwidth = 0.2) +
+  geom_vline(data = test_chem_full_tkstats,
+             aes(xintercept = Css),
+             color = "green4",
+             linetype = "dashed") +
+  facet_grid(rows = vars(model)) +
+  labs(title = unique(test_chem_data$Chemical_Name),
+       subtitle = paste("Number of samples: ", num_samples)) +
+  scale_x_log10() +
+  xlim(0,50) +
+  theme_bw() +
+  theme(plot.title = element_text(hjust = 1),
+        plot.subtitle = element_text(hjust = 1))
+
+css_lines <- Css_df_full %>%
+  filter(model != "model_flat") %>%
+  group_by(model) %>%
+  mutate(grouping = row_number()) %>%
+  ggplot(aes(x = model, y = Css)) +
+  geom_point(alpha = 0.4) +
+  geom_line(aes(group=grouping), alpha = 0.02) +
+  scale_y_log10() +
+  labs(subtitle = "N per timepoint: 4") +
+  theme_bw()
+
+get_winning_model(full_pk) %>% filter(Chemical == test_chem) %>% glimpse()
+
+css_hist + css_lines
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", test_chem,
+                         "_Css_pseudobootstrapping.png"),
+       bg = "white",
+       height = 3, width = 5
+)
+```

### 2025-03-14 data-raw/ClearanceProject-3-TKstats.Rmd
Fixed sampling to be a classical bootstrapping procedure.

--- 2025-03-11 data-raw/ClearanceProject-3-TKstats.Rmd
@@
 ```
+
+```{r library-loading}
+today <- format(Sys.Date(), "%d%b%Y")
+devtools::load_all()
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(ctxR)
+library(ggdist)
+library(patchwork)
+```
+
+```{r data-loading}
+this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
+load("data-raw/chem_lists.RData")
+load("data-raw/plasma_CvTfits_data.RData")
+load("data-raw/rat_pars_human.RData")
+all_chem_properties <- readRDS("data-raw/ctxR_3comp2_cheminfo.rds")
+full_pk <- readRDS("data-raw/all_cvt_pk.rds")
+full_tkstats <- get_tkstats(full_pk)
+```
+
+```{r combination-function}
+# Only need a simple bootstrapping method
+combo_gen_splitter <- function(df, num = 1000L) {
+  # Checks
+  num = as.integer(num)
+  stopifnot(
+    is.data.frame(df),
+    !is.na(num)
+  )
+
+  start <- 100L
+  end <- 100L+num
+  seed_seq <- seq.int(start, end)
+  full_df_combos <- lapply(
+    seed_seq,
+    \(x) {
+      set.seed(x)
+      sample_df <- df %>%
+        group_by(Chemical, Species, Reference, Route, Media, Dose, Time) %>%
+        slice_sample(prop = 1, replace = TRUE) %>%
+        ungroup()
+      return(sample_df)
+    }
+  )
+
+  message(paste("Samples: ", num))
+  set.seed(NULL)
+  invisible(full_df_combos)
+}
+
+```
+
+```{r example_chemical}
+# Using the example chemical
+trial_coefsd <- coef_sd(full_pk)
+trial_coefsd_reduced <- trial_coefsd %>% 
+  filter(param_name %in% c("kelim", "Vdist", "V1")) %>%
+  distinct()
+
+trial_coefsd_reduced %>%
+  filter(is.na(param_sd), model == "model_1comp") %>%
+  distinct(Chemical, Species) -> selected_trial
+
+test_chem_data <- get_data(full_pk) %>% filter(Conc > pLOQ) %>%
+  count(Chemical, Species, Reference, Route, Media, Dose, Time) %>% arrange(-n) %>%
+  filter(n > 4) %>%
+  inner_join(selected_trial) %>%
+  distinct(Chemical, Species, Reference, Route, Media, Dose) %>%
+  inner_join(get_data(full_pk))
+
+# Make 1000 sample data sets
+system.time(
+  test_chem_data_listsplits <- combo_gen_splitter(test_chem_data)
+)
+
+# Takes way too long, parallelize it
+
+clust <- parallel::makeCluster(parallel::detectCores()-4L)
+parallel::clusterCall(clust, function() devtools::load_all())
+system.time(
+  Css_list <- parallel::parLapply(
+    clust,
+    test_chem_data_listsplits,
+    \(x) {
+      tmp_pk <- pk(x,
+                   mapping = ggplot2::aes(
+                     Chemical = Chemical,
+                     Chemical_Name = Chemical_Name,
+                     DTXSID = DTXSID,
+                     CASRN = CASRN,
+                     Species = Species,
+                     Reference = Reference,
+                     Media = Media,
+                     Route = Route,
+                     Dose = Dose,
+                     Dose.Units = "mg/kg",
+                     Subject_ID = Subject_ID,
+                     Series_ID = Series_ID,
+                     Study_ID = Study_ID,
+                     ConcTime_ID = ConcTime_ID,
+                     N_Subjects = N_Subjects,
+                     Weight = Weight,
+                     Weight.Units = "kg",
+                     Time = Time,
+                     Time.Units = "hours",
+                     Value = Value,
+                     Value.Units = "mg/L",
+                     Value_SD = Value_SD,
+                     LOQ = LOQ
+                   )
+      ) +
+        scale_conc(dose_norm = TRUE,
+                   log10_trans = TRUE) +
+        settings_optimx(method = c(
+          "bobyqa"
+        ))
+
+      tmp_pk <- do_fit(tmp_pk)
+      tmp_tkstats <- get_tkstats(tmp_pk) %>%
+        distinct(Chemical, Species, Reference,
+                 Route, Media,
+                 model, method,
+                 Css, CLtot, halflife)
+
+      return(tmp_tkstats)
+    })
+)
+parallel::stopCluster(clust)
+
+Css_df_full <- bind_rows(Css_list)
+
+```
+
+```{r plotting-bootstraps}
+num_samples <- length(Css_list)
+
+test_chem_full_tkstats <- full_tkstats %>%
+  filter(model != "model_flat") %>%
+  inner_join(selected_trial) %>%
+  distinct(Chemical, Species, model, Css)
+
+Css_df_full %>%
+  filter(model != "model_flat") %>%
+  left_join(this_winmodel %>% 
+              mutate(winmodel = TRUE) %>%
+              select(-c(near_flat, preds_below_loq))) %>% 
+  mutate(winmodel = ifelse(is.na(winmodel), FALSE, winmodel)) %>%
+  ggplot(aes(x = halflife, y = Chemical, fill = winmodel)) +
+  stat_slab() +
+  # xlim(0,40) +
+  scale_x_log10() +
+  facet_grid(rows = vars(model),
+             cols = vars(Route)) +
+  scale_fill_manual(values = c("grey5", "green3")) +
+  theme_bw() +
+  labs(title = "halflife (hours)") +
+  theme(
+    axis.text.y = element_text(size = 6),
+    axis.text.x = element_text(size = 10),
+    plot.title = element_text(hjust = 0.5, size = 12),
+    axis.title = element_blank()
+  )
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "select_",
+                         "halflife_bootstrapping.png"),
+       bg = "white",
+       height = 4, width = 6
+)
+
+css_hist <- Css_df_full %>%
+  filter(model != "model_flat") %>%
+  ggplot(aes(x = Css)) +
+  geom_histogram(fill = "grey5", binwidth = 0.2) +
+  geom_vline(data = test_chem_full_tkstats,
+             aes(xintercept = Css),
+             color = "green4",
+             linetype = "dashed") +
+  facet_grid(rows = vars(model)) +
+  labs(title = unique(test_chem_data$Chemical_Name),
+       subtitle = paste("Number of samples: ", num_samples)) +
+  scale_x_log10() +
+  xlim(0,50) +
+  theme_bw() +
+  theme(plot.title = element_text(hjust = 1),
+        plot.subtitle = element_text(hjust = 1))
+
+css_lines <- Css_df_full %>%
+  filter(model != "model_flat") %>%
+  group_by(model) %>%
+  mutate(grouping = row_number()) %>%
+  ggplot(aes(x = model, y = Css)) +
+  geom_point(alpha = 0.4) +
+  geom_line(aes(group=grouping), alpha = 0.02) +
+  scale_y_log10() +
+  labs(subtitle = "N per timepoint: 4") +
+  theme_bw()
+
+get_winning_model(full_pk) %>% filter(Chemical == test_chem) %>% glimpse()
+
+css_hist + css_lines
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", test_chem,
+                         "_Css_pseudobootstrapping.png"),
+       bg = "white",
+       height = 3, width = 5
+)
+```

### 2025-03-17 data-raw/ClearanceProject-1-DataRmd.Rmd
Updated some data scripts and files to ensure we have both rat and human fup and Clint data.

@@
 ```{r chemical-lists}
-member_list <- list(
-  httk_3comp2 = unique(get_cheminfo(info = "DTXSID",
+human_3compchems <- unique(get_cheminfo(info = "DTXSID",
                                 species = "human",
@@
                                 suppress.messages = TRUE)) %>% 
-    suppressWarnings(),
-  cvt = cvt %>% 
+    suppressWarnings()
+
+rat_3compchems <- unique(get_cheminfo(info = "DTXSID",
+                                species = "rat",
+                                model = "3compartment2",
+                                median.only = TRUE,
+                                physchem.exclude = TRUE,
+                                suppress.messages = TRUE)) %>% 
+    suppressWarnings()
+
+cvt_plasma_chems <-  cvt %>% 
     filter(species %in% c("human", "rat"),
@@
     pull(analyte_dtxsid)
-)
+
 # These are the chemicals we can evaluate!
-target_chems <- intersect(member_list$cvt, member_list$httk_3comp2)
-all_chems <- member_list$httk_3comp2
+target_chems_human <- intersect(cvt_plasma_chems,
+                                human_3compchems)
+target_chems_rat <- intersect(cvt_plasma_chems,
+                              rat_3compchems)
 
 # save in an .Rdata file
-save(target_chems, all_chems,
+save(target_chems_human, target_chems_rat, 
+     human_3compchems, rat_3compchems,
      file = "data-raw/chem_lists.RData")
@@
 
-```{r getting_curent_params}
+```{r getting_curent_params_rpr}
 
-# rat_pars_rat <- parameterize_rat()
-rat_pars_human <- parameterize_rat(human_clint_fup = TRUE)
-#human_pars_human <- parameterize_human()
-chosen_list <- rat_pars_human
-# The following are derived from the above selected list (see environment)
-this_param_rest_l <- chosen_list$named_params_restrictive
-this_param_nrest_l <- chosen_list$named_params_nonrestrictive
-this_param_df <- chosen_list$param_df
-this_httk_clearance_df <- chosen_list$clearance_df
+rat_pars_rat <- parameterize_rat(human_clint_fup = FALSE)
+
+rpr_param_rest_l <- rat_pars_rat$named_params_restrictive
+rpr_param_nrest_l <- rat_pars_rat$named_params_nonrestrictive
+rpr_param_df <- rat_pars_rat$param_df
+rpr_httk_clearance_df <- rat_pars_rat$clearance_df
 
 # HTTK predictions
-
 # Predictions from httk(code retained but not run after 2.20.2025)
 restrictive_preds <- get_httk_preds(
-  parameters = this_param_rest_l,
+  parameters = rpr_param_rest_l,
   pk_obj = this_pk,
@@
 nonrestrictive_preds <- get_httk_preds(
-  parameters = this_param_nrest_l,
+  parameters = rpr_param_nrest_l,
   pk_obj = this_pk,
@@
 
-all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
-  filter_targets()
+rpr_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) 
 rm(restrictive_preds, nonrestrictive_preds)
 
-this_css_df <- inner_join(
-  css_httk_batch(this_param_rest_l, restrictive = TRUE),
-  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
-) %>% filter_targets()
+rpr_css_df <- inner_join(
+  css_httk_batch(rpr_param_rest_l, restrictive = TRUE),
+  css_httk_batch(rpr_param_nrest_l, restrictive = FALSE)
+)
 
-this_clint_df <- data.frame(Chemical = names(this_param_rest_l),
-                            CLint = vapply(names(this_param_rest_l),
+rpr_clint_df <- data.frame(Chemical = names(rpr_param_rest_l),
+                           CLint = vapply(names(rpr_param_rest_l),
                                           \(x) {
-                                             this_param_rest_l[[x]][["Clint"]]
+                                            rpr_param_rest_l[[x]][["Clint"]]
                                           },
@@
 
-save(this_param_rest_l, this_param_nrest_l,
-     this_param_df, this_httk_clearance_df,
-     all_httk_preds, this_css_df, this_clint_df,
+save(rpr_param_rest_l, rpr_param_nrest_l,
+     rpr_param_df, rpr_httk_clearance_df,
+     rpr_httk_preds, rpr_css_df, rpr_clint_df,
+     file = "data-raw/rat_pars_rat.RData")
+```
+
+```{r getting_current_params_rph}
+
+rat_pars_human <- parameterize_rat(human_clint_fup = TRUE)
+#human_pars_human <- parameterize_human()
+# The following are derived from the above selected list (see environment)
+rph_param_rest_l <- rat_pars_human$named_params_restrictive
+rph_param_nrest_l <- rat_pars_human$named_params_nonrestrictive
+rph_param_df <- rat_pars_human$param_df
+rph_httk_clearance_df <- rat_pars_human$clearance_df
+
+# HTTK predictions
+# Predictions from httk(code retained but not run after 2.20.2025)
+restrictive_preds <- get_httk_preds(
+  parameters = rph_param_rest_l,
+  pk_obj = this_pk,
+  species = c("rat", "human")
+) %>% rename_with(
+  .fn = ~paste0(.x, "_restrictive"),
+  .cols = starts_with("httk_")
+)
+
+nonrestrictive_preds <- get_httk_preds(
+  parameters = rph_param_nrest_l,
+  pk_obj = this_pk,
+  species = c("rat", "human")
+) %>% rename_with(
+  .fn = ~paste0(.x, "_nonrestrictive"),
+  .cols = starts_with("httk_")
+)
+
+names(restrictive_preds)
+
+rph_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds)
+rm(restrictive_preds, nonrestrictive_preds)
+
+rph_css_df <- inner_join(
+  css_httk_batch(rph_param_rest_l, restrictive = TRUE),
+  css_httk_batch(rph_param_nrest_l, restrictive = FALSE)
+)
+
+rph_clint_df <- data.frame(Chemical = names(rph_param_rest_l),
+                            CLint = vapply(names(rph_param_rest_l),
+                                           \(x) {
+                                             rph_param_rest_l[[x]][["Clint"]]
+                                           },
+                                           FUN.VALUE = numeric(1L)
+                            ))
+
+save(rph_param_rest_l, rph_param_nrest_l,
+     rph_param_df, rph_httk_clearance_df,
+     rph_httk_preds, rph_css_df, rph_clint_df,
      file = "data-raw/rat_pars_human.RData")

### 2025-03-19 data-raw/ClearanceProject-1-DataRmd.Rmd
Updated parameter collating functions to use chemical DTXSIDs and merges to maintain correct order.

@@
   filter(!is.na(qsarReadySmiles)) %>%
-  saveRDS(file = "data-raw/ctxR_3comp2_cheminfo.rds")
+  saveRDS(file = "data-raw/RCdata/ctxR_3comp2_cheminfo.rds")
 
@@
                            ))
+rownames(rpr_clint_df) <- NULL
+rpr_param_df <- merge(rpr_param_df, rpr_clint_df)
+rpr_httk_clearance_df <- merge(rpr_httk_clearance_df, rpr_css_df)
 
@@
      rpr_param_df, rpr_httk_clearance_df,
-     rpr_httk_preds, rpr_css_df, rpr_clint_df,
-     file = "data-raw/rat_pars_rat.RData")
+     rpr_httk_preds, file = "data-raw/RCdata/rat_pars_rat.RData")
 ```
@@
 
+rownames(rph_clint_df) <- NULL
+rph_param_df <- merge(rph_param_df, rph_clint_df)
+rph_httk_clearance_df <- merge(rph_httk_clearance_df, rph_css_df)
+
 save(rph_param_rest_l, rph_param_nrest_l,
      rph_param_df, rph_httk_clearance_df,
-     rph_httk_preds, rph_css_df, rph_clint_df,
-     file = "data-raw/rat_pars_human.RData")
+     rph_httk_preds,
+     file = "data-raw/RCdata/rat_pars_human.RData")
 ```

### 2025-03-19 data-raw/ClearanceProject-3-TKstats.Rmd
Analyzed interspecies differences for fup, CLint, and httk estimates compared to in vivo data.

@@
 library(patchwork)
+library(httk)
+.onUnload <- function(libpath) {
+  library.dynam.unload("httk", libpath)
+}
 ```
@@
 ```{r data-loading}
+# Note that you should run ...-1-Data.Rmd before this
+# RCdata/ is a directory that is not tracked by git because it contains
+# large files 
 this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
-load("data-raw/chem_lists.RData")
+load("data-raw/RCdata/chem_lists.RData")
 load("data-raw/plasma_CvTfits_data.RData")
-load("data-raw/rat_pars_human.RData")
-all_chem_properties <- readRDS("data-raw/ctxR_3comp2_cheminfo.rds")
+load("data-raw/RCdata/rat_pars_human.RData")
+load("data-raw/RCdata/rat_pars_rat.RData")
+all_chem_properties <- readRDS("data-raw/RCdata/ctxR_3comp2_cheminfo.rds")
 full_pk <- readRDS("data-raw/all_cvt_pk.rds")
 full_tkstats <- get_tkstats(full_pk)
+```
+
+## Species-specific differences in fraction unbound and intrinsic clearance
+
+We first want to establish that there is a difference between human and rat
+parameterization. Because one of our `param_df`s is only rat and the other has
+substituted human parameters (scaled to a rat).
+
+```{r rat_human_diff_fupClint}
+fup_rh <- rpr_param_df %>% 
+  distinct(Chemical, MW,
+           Clint, Funbound.plasma) %>% 
+  rename_with(\(x) {paste0(x, "_rat")},
+              .cols = c(Clint, Funbound.plasma)) %>%
+  left_join(
+    rph_param_df %>%
+      distinct(Chemical, MW,
+               Clint, Funbound.plasma) %>% 
+      rename_with(\(x) {paste0(x, "_human")},
+                  .cols = c(Clint, Funbound.plasma))
+    )
+
+species_fup_pl <- fup_rh %>%
+  ggplot(aes(
+    Funbound.plasma_human,
+    Funbound.plasma_rat
+  )) +
+  geom_abline(slope = 1) +
+  geom_point() +
+  geom_smooth(method = "lm", linetype = "dashed",
+              color = "forestgreen") +
+  labs(title = expression(f[up]),
+       x = "Human", y = "Rat") +
+  theme_bw() +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  coord_equal(xlim = c(0,1), ylim = c(0,1), expand = TRUE)
+
+fup_pl <- ggExtra::ggMarginal(
+  species_fup_pl,
+  type = "histogram",
+  binwidth = 0.025,
+  fill = "white"
+)
+
+lm(
+  Funbound.plasma_rat ~ Funbound.plasma_human,
+  data = fup_rh
+)
+
+cor.test(fup_rh$Funbound.plasma_human,
+            fup_rh$Funbound.plasma_rat)
+
+## Clint
+species_clint_pl <- subset(
+  fup_rh, Clint_human < 500, Clint_rat < 500
+) %>%
+  ggplot(aes(
+    Clint_human,
+    Clint_rat
+  )) +
+  geom_abline(slope = 1) +
+  geom_abline(slope = 1, intercept = c(-50,50), linetype = "longdash") +
+  geom_point() +
+  # geom_smooth(method = "lm", linetype = "dashed", color = "forestgreen") +
+  labs(title = expression(CL[int]),
+       x = "Human", y = "Rat") +
+  coord_equal(xlim = c(0,500), ylim = c(0,500)) +
+  theme_bw() +
+  theme(plot.title = element_text(hjust = 0.5,vjust = -1))
+
+clint_pl <- ggExtra::ggMarginal(
+  species_clint_pl,
+  type = "histogram",
+  fill = "white"
+)
+
+lm(
+  Clint_rat ~ Clint_human,
+  data = fup_rh
+)
+
+cor.test(fup_rh$Clint_human,
+            fup_rh$Clint_rat)
+
+# Both plots
+species_fup_pl + species_clint_pl +
+  plot_layout(axis_titles = "collect")
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
+                         "Rat_Human_Interspecies_FupCLint_compare.png"),
+       height = 3, width = 6)
+
+# Get the "close" estimates (+/-50)
+close_clint <- fup_rh %>%
+  filter(between(Clint_rat, Clint_human - 50, Clint_human + 50)) %>%
+  pull(Chemical)
+
+rph_rmsle <- rph_httk_preds %>%
+  mutate(fupSpecies = "human",
+         rest_sqerror = (log10(httk_Preds_restrictive) - log10(Conc))^2,
+         nonrest_sqerror = (log10(httk_Preds_nonrestrictive) - log10(Conc))^2) %>%
+  group_by(
+    Chemical, Species, fupSpecies
+  ) %>%
+  summarize(rest_rmsle = sqrt(sum(rest_sqerror)/n()),
+            nonrest_rmsle = sqrt(sum(nonrest_sqerror)/n())
+  ) %>%
+  ungroup()
+
+rpr_rmsle <- rpr_httk_preds %>%
+  mutate(fupSpecies = "rat",
+        rest_sqerror = (log10(httk_Preds_restrictive) - log10(Conc))^2,
+         nonrest_sqerror = (log10(httk_Preds_nonrestrictive) - log10(Conc))^2) %>%
+  group_by(
+    Chemical, Species, fupSpecies
+  ) %>%
+  summarize(rest_rmsle = sqrt(sum(rest_sqerror)/n()),
+            nonrest_rmsle = sqrt(sum(nonrest_sqerror)/n())
+  ) %>%
+  ungroup()
+
+bind_rows(rpr_rmsle, rph_rmsle) %>%
+  mutate(close_clint = ifelse(Chemical %in% close_clint,
+                              "|CLint| within 50", "|CLint| > 50")
+  ) %>% 
+  filter(Chemical %in% unique(rpr_rmsle$Chemical)) %>%
+  ggplot(aes(nonrest_rmsle, rest_rmsle)) +
+  geom_abline(slope = 1, color = "blue") +
+  geom_point(aes(color = fupSpecies), shape = 21) +
+  scale_color_manual(values = c("green4", "magenta3")) +
+  facet_grid(cols = vars(close_clint)) +
+  geom_line(aes(group = paste0(Chemical)),
+            alpha = 0.4) +
+  labs(x = "Nonrestrictive RMSLE", y = "Restrictive RMSLE") +
+  theme_bw() +
+  coord_equal()
+
+interspecies_rmsle_trends <- bind_rows(rpr_rmsle, rph_rmsle) %>%
+  mutate(
+    close_clint = ifelse(Chemical %in% close_clint,
+                         "|\U0394 CLint| within 50", "|\U0394 CLint| > 50")
+  ) %>% 
+  filter(Chemical %in% unique(rpr_rmsle$Chemical)) %>% 
+  pivot_longer(cols = contains("_rmsle"),
+               names_to = "clearance_type",
+               values_to = "RMSLE") %>%
+  pivot_wider(names_from = fupSpecies,
+              values_from = RMSLE) %>%
+  mutate(norm_diff = (human - rat)/rat) %>%
+  filter(!is.na(norm_diff)) %>% 
+  group_by(Chemical, close_clint, clearance_type) %>%
+  ggplot(aes(x = forcats::fct_reorder(Chemical, norm_diff, mean),
+             y = norm_diff,
+             fill = clearance_type)) +
+  geom_col(
+    width = 0.6,
+    # fill = "grey5", 
+    position = position_dodge(),
+    color = NA
+    ) +
+  labs(
+    x = "Chemical",
+    y = "Fold Change RMSLE\nHuman more accurate <<     >> Rat more accurate"
+  ) +
+  scale_fill_manual(values = c("grey20", "seagreen"),
+                    breaks = c("nonrest_rmsle", "rest_rmsle"),
+                    labels = c("Nonrestrictive", "Restrictive"),
+                    name = "Clearance") +
+  geom_hline(yintercept = 0) +
+  theme_minimal() + 
+  facet_grid(cols = vars(close_clint),
+             # rows = vars(clearance_type),
+             space = "free_x", scales = "free_x") +
+  theme(axis.text.x = element_blank(),
+        axis.ticks = element_blank(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.major.y = element_line(color = "grey5"),
+        panel.background = element_rect(color = "grey5"),
+        axis.title = element_text(size = 10),
+        legend.position = "bottom")
+
+species_clint_pl + interspecies_rmsle_trends +
+  plot_layout(widths = c(5,8))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
+                         "Rat_Human_Interspecies_RMSLE_trends.png"),
+       height = 5, width = 7,
+       bg = "white")
+```
+
+Next what we want to do is get httk predictions for nonrestrictive & 
+restrictive chemicals, but going from
+
+```{r}
+
 ```

### 2025-03-19 data-raw/testing_summary.Rmd

@@
 
-+ fold_errors.pk()  
++ fold_error.pk()  
 + residuals.pk()  
@@
 my_residuals <- residuals(my_pk)
-my_fes <- fold_errors(my_pk)
+my_fes <- fold_error(my_pk)
 my_rmse <- rmse(my_pk)

### 2025-03-19 data-raw/ClearanceProject-1-DataRmd.Rmd
Merge feature/Rclearance_comparison to dev (#22)
* Added diff_log_cvt() call for oral and iv.

* Changed log_likelihood() to work with pre-calculated predictions from other sources. Still requires sigma.

* Quick fix to get_fit.pk which no longer needs unnesting.

* Renamed and initialized 4 analysis documents for clearance project.

* Added data associated with clearance project for efficient loading.

* Organized ongoing hepatic clearance project files in data-raw/

@@
      rpr_param_df, rpr_httk_clearance_df,
-     rpr_httk_preds, file = "data-raw/RCdata/rat_pars_rat.RData")
+     rpr_httk_preds, file = "data-raw/rat_pars_rat.RData")
 ```
@@
      rph_httk_preds,
-     file = "data-raw/RCdata/rat_pars_human.RData")
+     file = "data-raw/rat_pars_human.RData")
 ```

### 2025-03-19 data-raw/ClearanceProject-2-RelativeLikelihood.Rmd
Merge feature/Rclearance_comparison to dev (#22)
* Added diff_log_cvt() call for oral and iv.

* Changed log_likelihood() to work with pre-calculated predictions from other sources. Still requires sigma.

* Quick fix to get_fit.pk which no longer needs unnesting.

* Renamed and initialized 4 analysis documents for clearance project.

* Added data associated with clearance project for efficient loading.

* Organized ongoing hepatic clearance project files in data-raw/

--- 2025-02-18 data-raw/RestrictiveClearance_comparison.Rmd
@@
 
+```{r data_loading}
+this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
+load("data-raw/chem_lists.RData")
+load("data-raw/plasma_CvTfits_data.RData")
+load("data-raw/rat_pars_human.RData")
+all_chem_properties <- readRDS("data-raw/ctxR_3comp2_cheminfo.rds")
+
+# Sipes 2017 data
+cyp_data <- readr::read_csv(paste0(
+  Sys.getenv("FIG_DIR"),
+  "RestrictiveClearance_Analysis/",
+  "CLint_CYP_Sipes2017.csv"
+)) %>%
+  left_join(
+    chem.physical_and_invitro.data %>%
+      select(CAS = CAS, Chemical = DTXSID) %>%
+      distinct()
+  ) %>%
+  select(Chemical, CAS, starts_with("MET_")) %>%
+  filter(!is.na(Chemical))
+names(cyp_data) <- c("Chemical", "CAS", "CYP1A2",
+                     "CYP2C9", "CYP2C19", "CYP2D6", "CYP3A4")
+# Functional use categories from CPdat
+functional_uses_all <- readr::read_csv(paste0(
+  Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
+  "ChemExpo_bulk_functional_uses_20250304.csv"
+))
+```
+
 We first want to see how many chemicals are in either _httk_ or _invivoPKfit_
@@
 ```{r venn_diagrams}
-member_list <- list(
-  httk_gas_pbtk = unique(get_cheminfo(info = "DTXSID",
-                                species = "human",
-                                model = "gas_pbtk",
-                                median.only = TRUE,
-                                physchem.exclude = TRUE,
-                                suppress.messages = TRUE)) %>% 
-    suppressWarnings(),
-  cvt = cvt %>% 
-    filter(species %in% c("human", "rat"),
-           conc_medium_normalized == "plasma") %>%
-    pull(analyte_dtxsid)
-)
-
-ggvenn(member_list, fill_color = c("white", "white"))
+
+ggvenn(member_list, fill_color = c("white", "white"), auto_scale = FALSE)
 
@@
 
-target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
-
-filter_targets <- function(.data) {
-  stopifnot("Chemical" %in% names(.data))
-  dplyr::filter(.data = .data, Chemical %in% target_chems)
-}
+```
+
+```{r httk_pr_rmsle}
+
+# RMSLE formula
+# LE = log1p(Conc_est) - log1p(Conc)
+# SLE = LE^2
+# RMSLE = sqrt(mean(SLE, na.rm = TRUE))
+
+combined_preds <- all_httk_preds %>%
+  mutate(Reference = as.character(Reference)) %>%
+  left_join(winning_preds) %>%
+  filter(!is.na(model))
+
+combined_RMSLE <- combined_preds %>%
+  ungroup() %>%
+  mutate(
+    restrictive_SLE = (log1p(httk_Preds_restrictive) - log1p(Conc))^2,
+    nonrestrictive_SLE = (log1p(httk_Preds_nonrestrictive) - log1p(Conc))^2,
+    invivoPK_SLE =  (log1p(Conc_est) - log1p(Conc))^2 
+  ) %>%
+  group_by(Chemical, Species, Route) %>%
+  summarize(RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
+            RMSLE_nonrestrictive = sqrt(mean(nonrestrictive_SLE, na.rm = TRUE)),
+            RMSLE_invivoPKfit = sqrt(mean(invivoPK_SLE, na.rm = TRUE))) %>%
+  ungroup() %>%
+  mutate(comparison_group = case_when(
+    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
+     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
+    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
+      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
+    RMSLE_invivoPKfit > RMSLE_restrictive &
+      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
+  ))
+
+combined_RMSLE %>%
+  ungroup() %>%
+  pivot_longer(cols = starts_with("RMSLE_"),
+               names_to = "Source",
+               values_to = "RMSLE") %>%
+  mutate(Source = factor(Source,
+                         levels = c("RMSLE_nonrestrictive",
+                                    "RMSLE_invivoPKfit",
+                                    "RMSLE_restrictive")
+  )) %>%
+  ggplot(aes(x = Source, y = RMSLE, group = Chemical)) +
+  geom_point(alpha = 0.5) +
+  geom_line(alpha = 0.5) +
+  theme_bw()
+
+combined_RMSLE %>%
+  ggplot(aes(x = Chemical, y = RMSLE_invivoPKfit)) +
+  geom_point(color = "green4") +
+  geom_point(aes(y = RMSLE_nonrestrictive), shape = 6, size = 0.5) +
+  geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
+  geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
+  facet_grid(~factor(comparison_group,
+                     levels = c("Less than", "Between", "More than")),
+             scales = "free_x", space = "free_x") +
+  labs(y = "RMSLE") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        panel.grid = element_blank(),
+        axis.title = element_text(size = 14),
+        strip.text = element_text(size = 12))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "RMSLE_comparison_fullChart.png"),
+       bg = "white",
+       height = 3.8, width = 10
+)# Number of chemicals we have RMSLE's for
+combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()
+
+```
+
+Another weight that we may consider is relative log-likelihood. This can be
+calculated using AIC, compared to the the flat model.
+
+```{r relative-likelihood}
+
+# AIC and relative likelihood
+# LL from pre-calculated httk predictions
+restrictive_ll <- all_httk_preds %>% 
+  rename(Conc_est = httk_Preds_restrictive,
+         Time_trans = Time) %>%
+  select(!httk_Preds_nonrestrictive) %>%
+  distinct() %>%
+  group_by(Chemical, Species) %>%
+  nest(.key = "observations") %>%
+  inner_join(coef(this_pk) %>% semi_join(this_winmodel) %>% distinct()) %>%
+  rowwise() %>%
+  mutate(log_likelihood = log_likelihood(
+    par = coefs_vector,
+    data = observations,
+    data_sigma_group = observations$data_sigma_group,
+    dose_norm = FALSE,
+    log10_trans = FALSE,
+    negative = FALSE,
+    includes_preds = TRUE,
+    detect
+  )) %>%
+  select(!c(observations, coefs_vector, Time.Units, Time_trans.Units)) %>%
+  mutate(model = "model_3comp2_restrictive",
+         AIC = -2 * log_likelihood)
+
+nonrestrictive_ll <- all_httk_preds %>% 
+  rename(Conc_est = httk_Preds_nonrestrictive,
+         Time_trans = Time) %>%
+  select(!httk_Preds_restrictive) %>%
+  distinct() %>%
+  group_by(Chemical, Species) %>%
+  nest(.key = "observations") %>%
+  inner_join(coef(this_pk) %>% semi_join(this_winmodel) %>% distinct()) %>%
+  rowwise() %>%
+  mutate(log_likelihood = log_likelihood(
+    par = coefs_vector,
+    data = observations,
+    data_sigma_group = observations$data_sigma_group,
+    dose_norm = FALSE,
+    log10_trans = FALSE,
+    negative = FALSE,
+    includes_preds = TRUE,
+    detect
+  )) %>%
+  select(!c(observations, coefs_vector, Time.Units, Time_trans.Units)) %>%
+  mutate(model = "model_3comp2_nonrestrictive",
+         AIC = -2 * log_likelihood) # Simple formula when there are no optimized params
+
+httk_AIC <- bind_rows(restrictive_ll,
+                      nonrestrictive_ll,
+                      this_AIC %>% filter(model == "model_flat") %>%
+                        filter_targets())
+
+httk_rel_ll <- httk_AIC %>%
+  distinct(Chemical, Species, model, AIC) %>%
+  pivot_wider(names_from = model, values_from = AIC) %>%
+  rowwise() %>% 
+  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
+  ungroup() %>%
+  mutate(across(starts_with("model_"), \(x) {
+    signif(exp((minAIC - x)/2) * 100, 4)
+  })) %>%
+  mutate(across(starts_with("model_"), \(x) {
+    ifelse(x < 1E-6, 0, x)
+  })) %>%
+  mutate(ll_label = factor(
+    case_when(model_flat > 95 ~ "Undetermined",
+              model_3comp2_nonrestrictive > 95 &
+                model_3comp2_restrictive > 95 ~ "Undetermined (non-flat)",
+              model_3comp2_nonrestrictive > 95 ~ "Nonrestrictive",
+              model_3comp2_restrictive > 95 ~ "Restrictive")
+  ))
+
+this_rel_evaluated_df <- this_css_df %>%
+  inner_join(httk_rel_ll %>% distinct(Chemical, Species, ll_label)) %>%
+  inner_join(this_tkstats) %>% # Css
+  inner_join(this_httk_clearance_df) %>% # CLtot and halflife
+  inner_join(data.frame(this_clint_df)) %>%
+  inner_join(this_param_df %>% 
+               distinct(Chemical,
+                        forced_human_values,
+                        Fabsgut.restrictive,
+                        Fabsgut.nonrestrictive)) %>%
+  mutate(Chemical = forcats::fct_reorder(Chemical, restrictive_halflife)) %>%
+  ungroup() %>%
+  distinct()
+
+halflife_pl <- this_rel_evaluated_df %>%
+  distinct(Chemical, Species, Css_httk_r,
+           halflife.tkstats, restrictive_halflife,
+           nonrestrictive_halflife,
+           ll_label) %>%
+  ggplot(aes(x = Chemical)) +
+  geom_pointrange(aes(y = halflife.tkstats, 
+                      ymin = nonrestrictive_halflife,
+                      ymax = restrictive_halflife),
+                  size = 0.1, shape = 23) +
+  facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
+  scale_y_log10() +
+  labs(x = "Chemicals", y = "halflife (hours)") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        strip.text = element_blank(),
+        strip.background = element_blank(),
+        axis.text.y = element_text(color = "black", size = 10),
+        axis.title = element_text(size = 10))
+
+ggsave(halflife_pl, filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "halflife_fullChart.png"),
+       bg = "white",
+       height = 3, width = 12
+)
+
+css_pl <- this_rel_evaluated_df %>%
+  distinct(Chemical, Species, Css.tkstats, Css_httk_nr, Css_httk_r,
+         ll_label) %>%
+  ggplot(aes(x = Chemical)) +
+  geom_pointrange(aes(y = Css.tkstats, ymin = Css_httk_nr, ymax = Css_httk_r),
+                  size = 0.1, shape = 23) +
+  facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
+  scale_y_log10() +
+  labs(x = 'Chemicals', y = "Css") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        strip.text = element_blank(),
+        strip.background = element_blank(),
+        axis.text.y = element_text(color = "black", size = 10),
+        axis.title = element_text(size = 10))
+
+cltot_pl <- this_rel_evaluated_df %>%
+  distinct(Chemical, Species, CLtot_Fgutabs.tkstats,
+           restrictive_clearance, nonrestrictive_clearance, 
+           Fabsgut.restrictive, Fabsgut.nonrestrictive,
+         ll_label) %>%
+  ggplot(aes(x = Chemical)) +
+  geom_pointrange(aes(y = CLtot_Fgutabs.tkstats,
+                      ymin = restrictive_clearance/Fabsgut.restrictive,
+                      ymax = nonrestrictive_clearance/Fabsgut.nonrestrictive),
+                  size = 0.1, shape = 23) +
+  facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
+  scale_y_log10() +
+  labs(x = 'Chemicals', y = "CLtot/Fabsgut") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        strip.text = element_blank(),
+        strip.background = element_blank(),
+        axis.text.y = element_text(color = "black", size = 10),
+        axis.title = element_text(size = 10))
+
+(halflife_pl + theme(axis.title.x = element_blank())) /
+  (css_pl+ theme(axis.title.x = element_blank())) /
+  cltot_pl
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "tkcomparisons_fullChart.png"),
+       bg = "white",
+       height = 4.5, width = 12
+)
+
+```
+
+This is the enrichment analysis for functional use categories.
+
+```{r functional}
+all_chem_functions <- functional_uses_all %>%
+  filter(DTXSID %in% all_chems, !is.na(`Harmonized Functional Use`)) %>% 
+  group_by(`Harmonized Functional Use`) %>% 
+  count() %>% arrange(-n) %>% head(20) %>% pull(1)
+target_chem_functions <- functional_uses_all %>%
+  filter(DTXSID %in% target_chems, !is.na(`Harmonized Functional Use`)) %>% 
+  group_by(`Harmonized Functional Use`) %>% 
+  count() %>% arrange(-n) %>% head(20) %>% pull(1)
+
+combined_function_list <- union(all_chem_functions,
+                                target_chem_functions) # 25 total
+
+pre_enrichment_mat <- inner_join(
+  functional_uses_all %>%
+    filter(
+      DTXSID %in% all_chems, !(DTXSID %in% target_chems), # all non-targets
+      `Harmonized Functional Use` %in% combined_function_list
+    ) %>% distinct(DTXSID, `Harmonized Functional Use`) %>%
+    count(`Harmonized Functional Use`, name = "n_nontargets"),
+  functional_uses_all %>%
+    filter(
+      DTXSID %in% target_chems, 
+      `Harmonized Functional Use` %in% combined_function_list
+    ) %>% distinct(DTXSID, `Harmonized Functional Use`) %>%
+    count(`Harmonized Functional Use`, name = "n_targets")
+) %>%
+  janitor::clean_names() %>%
+  mutate(n_total_targets = length(target_chems),
+         n_total_nontargets = length(all_chems) - n_total_targets,
+         n_nontargets_out = n_total_nontargets - n_nontargets,
+         n_targets_out = n_total_targets - n_targets) %>%
+  select(!c(n_total_nontargets, n_total_targets))
+
+quick_enrich <- pre_enrichment_mat %>%
+  rowwise() %>%
+  mutate(odds_ratio = fisher.test(
+    matrix(c(n_targets, n_nontargets,
+             n_targets_out, n_nontargets_out),
+           nrow = 2),
+    alternative = "greater")$estimate,
+    pval = fisher.test(
+    matrix(c(n_targets, n_nontargets,
+             n_targets_out, n_nontargets_out),
+           nrow = 2),
+    alternative = "greater")$p.value
+  ) %>%
+  ungroup() %>%
+  mutate(padj = 0.05/n()) %>%
+  arrange(pval)
+
+# Makeshift upset plot
+upset_pl <- this_rel_evaluated_df %>%
+  distinct(Chemical, Species, Css_httk_r,
+           halflife.tkstats, restrictive_halflife,
+           nonrestrictive_halflife,
+           ll_label) %>%
+left_join(functional_uses_all %>%
+            distinct(DTXSID, `Harmonized Functional Use`) %>%
+            rename(Chemical = DTXSID) %>%
+            filter(`Harmonized Functional Use` %in% c(
+              "Biocide",
+              "Pharmaceutical (EPA)",
+              "Degradant/impurity (EPA)"))
+          ) %>%
+  # filter(!is.na(`Harmonized Functional Use`)) %>%
+  mutate(val = ifelse(is.na(`Harmonized Functional Use`), NA, "Present")) %>%
+  distinct(Chemical, ll_label, `Harmonized Functional Use`, val) %>%
+  ggplot(aes(x = Chemical, y = `Harmonized Functional Use`, color = val)) + 
+  geom_point() +
+  scale_color_manual(values = "black") +
+  facet_grid(cols = vars(ll_label), scales = "free_x", space = "free_x") +
+  theme_minimal() +
+  theme(axis.text.x = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        plot.background = element_rect(color = "white"),
+        strip.text = element_blank(),
+        legend.title = element_blank(), axis.title.y = element_blank())
+
+(halflife_pl + theme(axis.title = element_blank())) /
+  (css_pl + theme(axis.title = element_blank())) /
+  upset_pl
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "tkcomparisons_withUpset.png"),
+       bg = "white",
+       height = 4.5, width = 12
+)
+
+quick_enrich$padj_val <- p.adjust(quick_enrich$pval, "bonferroni")
+
+# Enrichment plot
+quick_enrich %>%
+  mutate(
+    harmonized_functional_use = forcats::fct_reorder(
+      harmonized_functional_use, odds_ratio)
+    ) %>%
+  filter(padj_val <= 0.5) %>%
+  ggplot() +
+  geom_col(aes(x = odds_ratio, 
+               y = harmonized_functional_use,
+                fill = padj_val),
+           color = "black", linewidth = 0.2,
+           width = 0.75) +
+  scale_fill_viridis_b(option = "viridis", direction = -1,
+                       breaks = c(0, 0.05, 0.1, 0.5),
+                       limits = c(0, 0.5)
+                       ) +
+  scale_x_continuous(limits = c(0, 12),
+                     expand = expansion()) +
+  labs(x = "Enrichment Score", y = "",
+       title = "Enrichment of Functional Use Categories",
+       fill = "adjusted p-value") +
+  theme_bw() +
+  theme(legend.title = element_text(hjust = 0.5),
+        axis.text = element_text(color = "black"),
+        axis.text.y = element_text(face = "bold", size = 10),
+        plot.title = element_text(hjust = 0.5))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "FunctionalUse_Enrichment.png"),
+       bg = "white",
+       height = 5, width = 6.5
+)
+
 ```
@@
 ```{r selecting_chemical_params}
-chosen_list <- rat_pars_human
-# The following are derived from the above selected list (see environment)
-this_chem_v <- unique(chosen_list$param_df$Chemical)
-this_param_rest_l <- chosen_list$named_params_restrictive
-this_param_nrest_l <- chosen_list$named_params_nonrestrictive
-this_param_df <- chosen_list$param_df
-this_httk_clearance_df <- chosen_list$clearance_df
-this_species_v <- c("rat", "human")
+
 # Testing to make sure there are some chemicals that have different clearances
@@
 # The majority (140) do!
-```
-
-Here I do a quick fit of the CvT data only for those that have plasma measurements.
-
-```{r quick-fit}
-
-# Only use plasma for simplicity
-this_pk <- pk(cvt %>% 
-                dplyr::filter(conc_medium_normalized == "plasma")
-              ) +
-  settings_optimx(method = "bobyqa") +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(
-    keep_data_original = TRUE,
-    suppress.messages = FALSE) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  stat_error_model(error_group = vars(Chemical, Species))
-
-this_pk <- do_prefit(this_pk)
-this_pk <- do_fit(this_pk, n_cores = 12)
+
+```
+
+```{r load-other}
+
+# Check to see how much of the full dataset is available
+length(intersect(unique(new.raw.httk.data$DTXSID), full_list))
+
+focus_chems <- union(new.raw.httk.data$DTXSID, target_chems)
+
+all_chem_properties %>%
+  filter(propertyId %in% c("logkow-octanol-water",
+                     "pka-acidic-apparent",
+                     "pka-basic-apparent",
+                     "water-solubility",
+                     "logkoa-octanol-air",
+                     "henrys-law",
+                     "boiling-point")) %>%
+  glimpse()
+
+# Fraction unbound data for target chemicals
+fup_df <- this_param_df %>%
+  distinct(Chemical, Species, forced_human_values,
+           Funbound.plasma, Funbound.plasma.adjustment, 
+           Funbound.plasma.dist) %>%
+  mutate(
+    Funbound.plasma.median = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "^\\d+\\.?\\d+e?-?\\d+(?=,)"
+    )),
+    Funbound.plasma.lower95 = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d+(?=,)"
+    )),
+    Funbound.plasma.upper95 = as.numeric(str_extract(
+      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d$"
+    ))
+    )
+
+all_hum_rat_fups <- chem.physical_and_invitro.data %>%
+  filter(DTXSID %in% all_chems) %>%
+  select(DTXSID, Human.Funbound.plasma, Rat.Funbound.plasma) %>%
+  mutate(Rat.Funbound.plasma = as.numeric(str_extract(Rat.Funbound.plasma,
+                                                      "^([^,]+)")),
+         Human.Funbound.plasma = as.numeric(str_extract(Human.Funbound.plasma,
+                                                        "^([^,]+)"))
+         )
+
+# Get restrictive and non-restrictive parameters
+
 ```
@@
 ```{r load_Kd}
-load(paste0(Sys.getenv("OD_DIR"),
-            "Profile/Documents/New-HTTK-raw-2019-05-06.RData")
-)
 new.raw.httk.data %>%
@@
 )
-```
-
-## Lipinski's Rules
-
-Here I will look at the whether chemicals are "drug-like" by evaluating if:
-
-1. Molecular weight less than 500 Da.  
-2. logP (octanol-water partitioning coefficient) no greater than 5.  
-3. Less than 5 hydrogen bond donors and less than 10 acceptors.
-
-```{r lipinksi_test_data}
-target_chem_info <- get_chemical_details_batch(DTXSID = target_chems,
-                                               rate_limit = 1L)
-target_chem_properties <- get_chem_info_batch(DTXSID = target_chems, 
-                                              rate_limit = 1L) %>%
-  filter(name %in% c("LogKow: Octanol-Water",
-                     "pKa Acidic Apparent",
-                     "pKa Basic Apparent")) %>% distinct()
-
-target_chem_properties %>%
-  ggplot(aes(x = source, y = value)) +
-  geom_violin() +
-  geom_line(aes(group = dtxsid), color = "grey10", alpha = 0.1) +
-  geom_hline(yintercept = 5, linetype = "longdash") +
-  facet_grid(cols = vars(propType), scales = "free_x",
-             rows = vars(name)) +
-  scale_y_log10() +
+
+kd_v_fup_plot <- new.raw.httk.data %>%
+  inner_join(all_hum_rat_fups) %>%
+  pivot_longer(cols = Human.Funbound.plasma:Rat.Funbound.plasma,
+               names_to = "Species", values_to = "httk_fup_med") %>%
+  ggplot(aes(x = Affinity.Kd.Med, y = httk_fup_med, color = Species)) +
+  geom_point(alpha = 0.5) +
+  scale_color_manual(values = c("green4", "purple2"),
+                     labels = c("Human", "Rat")) +
+  scale_x_log10(labels = scales::label_log(digits = 2)) +
+  labs(x = "Dissociation constant Kd\n(uM, from in vitro RED assay)",
+       y = "Fraction unbound\nin plasma") +
   theme_bw() +
-  theme(axis.text.x = element_text(hjust = 1, angle = 45))
-
-target_chem_properties %>%
-  count(source)
-
-target_chem_info %>%
-  ggplot(aes(x = monoisotopicMass)) +
-  geom_histogram(binwidth = 50, fill = "grey5",
-                 boundary = 0) +
-  geom_vline(xintercept = 500, linetype = "longdash") +
-  scale_x_continuous(limits = c(0, 1000),
-                     breaks = seq(0, 1000, 100)) +
-  theme_bw()
+  theme(legend.position = "left",
+        legend.text = element_text(size = 8),
+        legend.title = element_blank(),
+        axis.title = element_text(size = 10),
+        axis.text = element_text(size = 8, color = "black"))
+
+kd_v_fup_plot
 
@@
                          "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "target_chems_molmass.png"),
+                         "CURRENT_", "Kd_estimates_vs_fup_multispecies.png"),
        bg = "white",
-       height = 3, width = 5
-)
-
-target_chem_info %>%
-  count(monoisotopicMass <= 500)
-
-target_chem_pw_predicted <- target_chem_properties %>%
-  filter(source == "ACD/Labs") %>%
-  distinct(propertyId, value, dtxsid) %>%
-  pivot_wider(names_from = propertyId,
-              values_from = value)
-
-```
-
-```{r reticulate-prep}
-smiles_list <- target_chem_info %>% pull(smiles) %>% unique()
-mykit <- import("rdkit")
-```
-
-```{python get_H_bonds}
-import rdkit
-from rdkit import Chem
-from rdkit.Chem import Descriptors
-
-py_smiles_list = r.smiles_list
-mol_from_smiles = [Chem.MolFromSmiles(x) for x in py_smiles_list]
-
-py_h_donors = [Chem.Descriptors.NOCount(x) for x in mol_from_smiles]
-py_h_acceptors = [Chem.Descriptors.NHOHCount(x) for x in mol_from_smiles]
-py_tpsa = [Chem.Descriptors.TPSA(x) for x in mol_from_smiles]
-```
-
-```{r lipinksi_alluvial}
-
-target_chem_summary <- target_chem_info %>%
-  distinct(dtxsid, monoisotopicMass, smiles) %>%
-  right_join(data.frame(smiles = smiles_list)) %>%
-  bind_cols(data.frame(H_donors = py_to_r(py$py_h_donors),
-                       H_acceptors = py_to_r(py$py_h_acceptors))
-            ) %>%
-  left_join(
-    target_chem_properties %>%
-      filter(source == "ACD/Labs Consensus") %>%
-      distinct(dtxsid, source, value)
-  ) %>%
-  rename(LogKow = value)
-
-target_chem_lipinski <- target_chem_summary %>%
-  select(-c(smiles, source)) %>%
-  group_by(dtxsid) %>%
-  mutate("Mass <= 500 Da" = (monoisotopicMass <= 500),
-          "H-donors < 5" = (H_donors < 5),
-          "H-acceptors < 10" = (H_acceptors < 10),
-          "logP < 5" = (LogKow < 5),
-          .keep = "none") %>%
-  ungroup() %>%
-  mutate(Lipinski = rowSums(dplyr::select(., where(is.logical))) >= 3)
-
-target_chem_lipinski %>%
-  group_by(Lipinski) %>%
-  count(`Mass <= 500 Da`, `H-donors < 5`, `H-acceptors < 10`, `logP < 5`,
-        name = "Count") %>%
-  ggplot(aes(
-    axis3 = `Mass <= 500 Da`,
-    axis4 = `logP < 5`,
-    axis2 = `H-donors < 5`,
-    axis1 = `H-acceptors < 10`,
-    y = Count
-  )) +
-  geom_alluvium(aes(fill = Lipinski)) +
-  geom_stratum() +
-  scale_x_discrete(limits = c( 
-    "H-acceptors < 10",
-    "H-donors < 5",
-    "<= 500 Da",
-    "logP < 5"
-  ),
-  position = "top",
-  expand = c(.2, .05)) +
-  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
-  labs(title = "Overwhelmingly, these chemicals passes Lipinksi's Rules of 5",
-       fill = "Passes Lipinksi's Rules?") +
-  scale_fill_manual(values = c("grey20", "green4")) +
-  theme_minimal() +
-  theme(axis.text.x = element_text(face = "bold", color = "black", size = 10),
-        panel.grid = element_blank(),
-        plot.title = element_text(hjust = 0.5),
-        legend.position = "bottom")
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Alluvium_Lipinski.png"),
-       bg = "white",
-       height = 5, width = 6
-)
-```
-
-Overwhelmingly, we see that chemicals (by Lipinski's rules of 5) are "drug-like".
-While this may not matter effectively for clearance, it may be nice to look 
-at whether chemicals deemed not "drug-like" (11 total) are more likely to be
-restrictively or non-restrictively cleared.
+       height = 2.8, width = 5
+)
+
+```
 
@@
 the reality. The metric used here will be RMSLE.
-
-```{r httk_predictions}
-restrictive_preds <- get_httk_preds(
-  parameters = this_param_rest_l,
-  pk_obj = this_pk,
-  species = c("rat", "human")
-) %>% rename_with(
-  .fn = ~paste0(.x, "_restrictive"),
-  .cols = starts_with("httk_")
-)
-
-nonrestrictive_preds <- get_httk_preds(
-  parameters = this_param_nrest_l,
-  pk_obj = this_pk,
-  species = c("rat", "human")
-) %>% rename_with(
-  .fn = ~paste0(.x, "_nonrestrictive"),
-  .cols = starts_with("httk_")
-)
-
-all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
-  filter_targets()
-
-this_nonflat_winmodel <- get_winning_model(this_pk) %>%
-  filter(model %in% c("model_1comp", "model_2comp")) %>%
-  filter_targets()
-
-winning_preds <- predict(this_pk) %>%
-  semi_join(this_nonflat_winmodel) %>% # The targets already filtered here
-  distinct(Chemical, Species, Chemical_Name,
-           model, method, Dose, Media, Route, Reference, pLOQ, Time,
-           N_Subjects, Conc, Conc_est)
-
-# RMSLE formula
-# LE = log1p(Conc_est) - log1p(Conc)
-# SLE = LE^2
-# RMSLE = sqrt(mean(SLE, na.rm = TRUE))
-
-combined_preds <- all_httk_preds %>%
-  left_join(winning_preds) %>%
-  filter(!is.na(model))
-
-combined_RMSLE <- combined_preds %>%
-  ungroup() %>%
-  mutate(
-    restrictive_SLE = (log1p(httk_Preds_restrictive) - log1p(Conc))^2,
-    nonrestrictive_SLE = (log1p(httk_Preds_nonrestrictive) - log1p(Conc))^2,
-    invivoPK_SLE =  (log1p(Conc_est) - log1p(Conc))^2 
-  ) %>%
-  group_by(Chemical, Species) %>%
-  summarize(RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
-            RMSLE_nonrestrictive = sqrt(mean(nonrestrictive_SLE, na.rm = TRUE)),
-            RMSLE_invivoPKfit = sqrt(mean(invivoPK_SLE, na.rm = TRUE)))
-
-combined_RMSLE %>%
-  ungroup() %>%
-  pivot_longer(cols = starts_with("RMSLE_"),
-               names_to = "Source",
-               values_to = "RMSLE") %>%
-  mutate(Source = factor(Source,
-                         levels = c("RMSLE_nonrestrictive",
-                                    "RMSLE_invivoPKfit",
-                                    "RMSLE_restrictive")
-  )) %>%
-  ggplot(aes(x = Source, y = RMSLE, group = Chemical)) +
-  geom_point(alpha = 0.5) +
-  geom_line(alpha = 0.5) +
-  theme_bw()
-
-combined_RMSLE %>%
-  ungroup() %>%
-  mutate(comparison_group = case_when(
-    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
-     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
-    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
-      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
-    RMSLE_invivoPKfit > RMSLE_restrictive &
-      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
-  )) %>% 
-  ggplot(aes(x = Chemical, y = RMSLE_invivoPKfit)) +
-  geom_point(color = "green4") +
-  geom_point(aes(y = RMSLE_nonrestrictive), shape = 6, size = 0.5) +
-  geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
-  facet_grid(~factor(comparison_group,
-                     levels = c("Less than", "Between", "More than")),
-             scales = "free_x", space = "free_x") +
-  labs(y = "RMSLE") +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        panel.grid = element_blank())
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "RMSLE_comparison_fullChart.png"),
-       bg = "white",
-       height = 4.5, width = 8
-)
-
-# Number of chemicals we have RMSLE's for
-combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()
-
-```
-
-Another weight that we may consider is relative log-likelihood. This can be
-calculated using AIC, compared to the the flat model.
-
-```{r relative-likelihood}
-this_rll_probs <- AIC(this_pk) %>%
-  filter_targets() %>%
-  distinct(Chemical, Species, model, AIC) %>%
-  pivot_wider(names_from = model, values_from = AIC) %>%
-  rowwise() %>% 
-  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
-  ungroup() %>%
-  mutate(across(starts_with("model_"), \(x) {
-    signif(exp((minAIC - x)/2) * 100, 4)
-  })) %>%
-  mutate(across(starts_with("model_"), \(x) {
-    ifelse(x < 1E-6, 0, x)
-  })) %>%
-  inner_join(this_nonflat_winmodel %>% distinct(Chemical, Species, model)) %>%
-  ungroup() %>%
-  filter(model_1comp >= 99 | model_2comp >= 99,
-        model_flat < 1, Chemical %in% target_chems)
-
-this_rll_probs %>%
-  count(model_1comp >= 99, model_2comp >= 99)
-
-```
 
@@
 
-css_httk_batch <- function(param_list,
-                           restrictive = TRUE) {
-  stopifnot(is.logical(restrictive))
-
-  css_list_r <- vapply(
-    param_list,
-    \(x) {
-      calc_analytic_css_3comp2(parameters = x,
-                               restrictive.clearance = restrictive)
-    },
-    FUN.VALUE = numeric(1L)
-  )
-  css_list_names <- names(param_list)
-
-  css_df <- data.frame(Chemical = css_list_names,
-                       Css_httk = css_list_r)
-  if (restrictive) {
-    css_df <- rename(css_df, Css_httk_r = Css_httk)
-  } else {
-    css_df <- rename(css_df, Css_httk_nr = Css_httk)
-  }
-  return(css_df)
-}
-
-this_css_df <- inner_join(
-  css_httk_batch(this_param_rest_l, restrictive = TRUE),
-  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
-)
+# Table
+this_css_df %>%
+  count(Css_httk_r == Css_httk_nr,
+        Css_httk_r - Css_httk_nr < 0.1 & Css_httk_r - Css_httk_nr > 0,
+        Css_httk_r - Css_httk_nr >= 0.1) %>%
+  rename("No difference" = "Css_httk_r == Css_httk_nr",
+         "Less than 0.1" = "Css_httk_r - Css_httk_nr < 0.1 & Css_httk_r - Css_httk_nr > 0",
+         "At least 0.1" = "Css_httk_r - Css_httk_nr >= 0.1")
+
 # Chart with relative differences (think steps) of Css between clearance types
 this_css_df %>%
-  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
+  mutate(relative_difference = (Css_httk_r - Css_httk_nr)/Css_httk_nr) %>%
   count(relative_difference == 0, Css_httk_r == 0) # 31 Chemicals have zero difference
@@
 this_css_df %>%
-  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
+  mutate(relative_difference = (Css_httk_r - Css_httk_nr)/Css_httk_nr) %>%
   filter(relative_difference > 0) %>%
@@
                                       relative_difference, .desc = FALSE))) +
-  geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r)) +
-  labs(title = "Differences between restrictive & nonrestrictive clearance",
+  geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r),
+                 linewidth = 1.25) +
+  labs(title = "Css differences between restrictive & nonrestrictive clearance",
        y = "Css\n(mg/L)", x = "Chemicals") +
@@
         panel.grid.major.x = element_blank(),
-        plot.title = element_text(hjust = 0.5))
+        plot.title = element_text(hjust = 0.5, size = 10),
+        axis.title = element_text(size = 10),
+        axis.text.y = element_text(size = 8, color = "black"))
 
@@
        bg = "white",
-       height = 5, width = 7)
+       height = 3, width = 8)
+
+this_css_df %>%
+  mutate(relative_difference = log1p((Css_httk_r - Css_httk_nr)/Css_httk_nr)) %>%
+  filter(relative_difference > 0) %>%
+  ggplot(aes(x = forcats::fct_reorder(Chemical,
+                                      relative_difference, .desc = FALSE))) +
+  geom_linerange(aes(ymin = 0,
+                     ymax = 0 + relative_difference),
+                 linewidth = 1) +
+  labs(
+    title = paste0("Relative Css differences between\n",
+                   "restrictive & nonrestrictive clearance"),
+       y = "log10 Css\n(relative difference, mg/L)", x = "Chemicals") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks = element_blank(),
+        panel.grid.major.x = element_blank(),
+        plot.title = element_text(hjust = 0.5, size = 10),
+        axis.title = element_text(size = 10),
+        axis.text.y = element_text(size = 8, color = "black"))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Css_relativedifference_httk_lineplot.png"),
+       bg = "white",
+       height = 3, width = 5.75)
 
@@
 ###
-
-this_css_df <- this_css_df %>%
-  inner_join(this_tkstats) %>%
-  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
-  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
-  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
-  mutate(comparison_group_Css = factor(
-    case_when(
-      between(Css.tkstats, Css_httk_r, Css_httk_nr) |
-        between(Css.tkstats, Css_httk_nr, Css_httk_r) ~ "Between",
-      Css.tkstats < Css_httk_r & Css.tkstats < Css_httk_nr ~ "Below",
-      Css.tkstats > Css_httk_r & Css.tkstats > Css_httk_nr ~ "Above"),
-    levels = c("Above", "Between", "Below")
-  ), Chemical = factor(Chemical) %>% forcats::fct_reorder(Css_httk_r)
-  ) %>%
-  mutate(nearest_clearance = factor(
-    case_when(
-      between(log2(Css.tkstats),
-              log2(Css_httk_r)-1, log2(Css_httk_r)+1) |
-        (comparison_group_Css == "Above" &
-           log2(Css.tkstats) <= log2(Css_httk_r)+2) ~ "Restrictive",
-      between(log2(Css.tkstats),
-              log2(Css_httk_nr)-1, log2(Css_httk_nr)+1) |
-        comparison_group_Css == "Below" ~ "NonRestrictive",
-      .default = "Out of Range"
-    )
-  ))
-
-this_css_df %>%
-  ggplot(aes(x = Chemical)) +
-  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
-  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = Css_httk_r,
-                     ymax = Css_httk_nr)
-  ) +
-  geom_point(aes(y = Css.tkstats, shape = Route,
-                 color = nearest_clearance)) +
-  facet_grid(rows = vars(comparison_group_Css),
-             scales = "free_x",
-             space = "free_x") +
-  scale_y_log10(name = "Css") +
-  scale_shape_manual(values = c(0,1)) +
-  scale_color_manual(values = c("magenta3", "green4", "black"),
-                     name = "Within 2-fold\nof clearance:",
-                     ) +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        panel.grid = element_blank()) +
-  guide_area() +
-  plot_layout(widths = c(8,1))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_comparison_2foldclearancefullChart.png"),
-       bg = "white",
-       height = 5, width = 10
-)
-
-this_css_df %>% 
-  group_by(Chemical) %>%
-  count(nearest_clearance) %>%
-  filter(nearest_clearance != "Out of Range") %>% View()
-
-```
-
-Overwhelmingly, the results of this is a Restrictive clearance model...
-however it is important to flag
-
-```{r Css_CLint}
-this_css_clint_df <- this_css_df %>%
-  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats,
-           nearest_clearance, comparison_group_Css) %>%
-  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
-  left_join(data.frame(Chemical = names(this_param_rest_l),
-                       CLint = vapply(names(this_param_rest_l),
-                                      \(x) {
-                                        this_param_rest_l[[x]][["Clint"]]
-                                      },
-                                      FUN.VALUE = numeric(1L)
-                       ))) %>%
-  dplyr::filter(CLint > 0)
-
-this_css_clint_df %>%
-  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
-  ggplot(aes(x = CLint)) +
-  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
-  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = Css_httk_r,
-                     ymax = Css_httk_nr)
-  ) +
-  scale_y_log10(name = "C<sub>ss</sub>") + 
-  scale_x_log10(name = "CL<sub>int</sub>") +
-  geom_point(aes(y = Css.tkstats, 
-                 fill = `Mass <= 500 Da`,
-                 shape = Route,
-                 color = nearest_clearance)) +
-  facet_grid(rows = vars(nearest_clearance)) +
-  scale_color_manual(values = c("magenta3", "green4", "black"),
-                     guide = "none") +
-  scale_shape_manual(values = c(21,22)) +
-  scale_fill_manual(values = c("white", "grey5")) +
-  guides(fill = guide_legend(override.aes = list(shape = 21))) +
-  theme_bw() +
-  theme(axis.title = ggtext::element_markdown())
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_x_CLint_wNearestClearanceGrid.png"),
-       bg = "white",
-       height = 6, width = 10
-)
-
-this_css_clint_df %>%
-  # group_by(Route) %>%
-  group_modify(~broom::tidy(lm(Css.tkstats ~ nearest_clearance + CLint, data = .x)))
-
-```
-
-Now I will try to triangulate the model weights with the Css estimates.
-
-```{r weighted_Css}
-combined_model_weights %>%
-  inner_join(this_css_df) %>%
-  filter_targets() %>%
-  ggplot(aes(x = forcats::fct_reorder(Chemical, Css_httk_r))) +
-  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
-  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
-  geom_linerange(aes(ymin = Css_httk_r,
-                     ymax = Css_httk_nr)
-  ) +
-  geom_point(aes(y = Css.tkstats, shape = Route, color = gamma_weight)) +
-  facet_grid(rows = vars(comparison_group_Css),
-             cols = vars(rmsle_comparison_group),
-             scales = "free_x",
-             space = "free_x") +
-  scale_y_log10(name = "Css") +
-  scale_shape_manual(values = c(0,1)) +
-  scale_color_viridis_b(option = "viridis") +
-  labs(subtitle = "RMSLE for invivoPKfit compared to httk predictions",
-       x = "Chemical\n(ordered by increasing restrictive Css prediction)",
-       y = "Css",
-       color = "Inverse Confidence") +
-  theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank(),
-        plot.subtitle = element_text(hjust = 0.5),
-        panel.grid = element_blank(),
-        legend.title = element_text(vjust = 0.8)) +
-  guide_area() +
-  plot_layout(widths = c(8,1))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
-                         "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_withRMSLEweights.png"),
-       bg = "white",
-       height = 5, width = 10
-)
-
 ```

### 2025-03-19 data-raw/ClearanceProject-3-TKstats.Rmd
Merge feature/Rclearance_comparison to dev (#22)
* Added diff_log_cvt() call for oral and iv.

* Changed log_likelihood() to work with pre-calculated predictions from other sources. Still requires sigma.

* Quick fix to get_fit.pk which no longer needs unnesting.

* Renamed and initialized 4 analysis documents for clearance project.

* Added data associated with clearance project for efficient loading.

* Organized ongoing hepatic clearance project files in data-raw/

@@
 this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
-load("data-raw/RCdata/chem_lists.RData")
+load("data-raw/chem_lists.RData")
 load("data-raw/plasma_CvTfits_data.RData")
-load("data-raw/RCdata/rat_pars_human.RData")
-load("data-raw/RCdata/rat_pars_rat.RData")
+load("data-raw/rat_pars_human.RData")
+load("data-raw/rat_pars_rat.RData")
 all_chem_properties <- readRDS("data-raw/RCdata/ctxR_3comp2_cheminfo.rds")

### 2025-03-19 R/log_likelihood.R

@@ -124,6 +124,7 @@
 #' @param max_multiplier Numeric, but NULL by default. Determines which multiple
 #'  of the maximum concentration to use to limit possible predictions.
 #'  Note: only use this as part of the fitting function.
+#' @param includes_preds Logical: whether `data` includes predictions.
 #' @param suppress.messages Logical.
 #' @return A log-likelihood value for the data given the parameter values in
 #'  params
@@ -139,15 +140,9 @@ log_likelihood <- function(par,
                            negative = TRUE,
                            force_finite = FALSE,
                            max_multiplier = NULL,
+                           includes_preds = FALSE,
                            suppress.messages = TRUE) {
 
-  # combine parameters to be optimized and held constant
-  params <- c(par, const_params)
-
-  # Extract parameters whose names do not match 'sigma'
-  # (that is, all the actual model parameters)
-  sigma_index <- startsWith(names(params), prefix = "sigma")
-  model.params <- params[!sigma_index]
 
   # Used variables such that there is no need to reference 'data'
   Time_trans <- data$Time_trans
@@ -161,19 +156,34 @@ log_likelihood <- function(par,
   Detect <- data$Detect
   pLOQ <- data$pLOQ
 
+  # combine parameters to be optimized and held constant
+  params <- c(par, const_params)
 
-  # get un-transformed predicted plasma concentration vs. time for the current parameter
-  # values, by dose and route
-  pred <- do.call(
-    modelfun,
-    args = list(
-      params = model.params,
-      time = Time_trans,
-      dose = Dose,
-      route = Route,
-      medium = Media
+  # Extract parameters whose names do not match 'sigma'
+  # (that is, all the actual model parameters)
+  sigma_index <- startsWith(names(params), prefix = "sigma")
+  model.params <- params[!sigma_index]
+
+  if (includes_preds) {
+
+    stopifnot("data must have Conc_est column." = "Conc_est" %in% names(data))
+    pred <- data$Conc_est
+
+  } else {
+
+    # get un-transformed predicted plasma concentration vs. time for the current parameter
+    # values, by dose and route
+    pred <- do.call(
+      modelfun,
+      args = list(
+        params = model.params,
+        time = Time_trans,
+        dose = Dose,
+        route = Route,
+        medium = Media
+      )
     )
-  )
+  }
 
   pred[which(pred < pLOQ)] <- pLOQ[which(pred < pLOQ)]
 

### 2025-03-19 data-raw/ClearanceProject-1-DataRmd.Rmd
Updated DESCRIPTION and data.

@@
 ```
+
+This code chunk creates and `.RData` file that contains character vectors
+of DTXSIDs for:
+
+1. All chemicals with human parameterization available for a 3-compartment model w/ inhalation.  
+2. All chemicals with rat parameterization available for a 3-compartment model w/ inhalation.  
+3. All chemicals with human and rat plasma concentration over time data.
 
@@
 
+Below read in some external data which is publicly available already.
+
+- `red_assay_res` is the named object that contains the data from the RED assay
+including the dissociation constant $K_d$ for plasma protein binding.  
+- `chem_info` is a combined data.frame from calls to `get_chemical_details_batch`
+and `get_chem_info_batch`. This uses the `ctxR` API to fetch chemical information
+such as physio-chemical properties and SMILES from the CompTox dashboard.  
+- `cyp_data` is data from Sipes 2017 predicting the CLint fraction for each CYP enzyme.
+- `functional_uses_all` is a list of functional use categories for each chemical
+from the Chemical and Products Database.
+
 ```{r external_data}
@@
 # Chemical info and properties (averaging the latter by chemical and experimental/predicted)
-chem_info <- get_chemical_details_batch(DTXSID = all_chems,
+chem_info <- get_chemical_details_batch(DTXSID = human_3compchems,
                                                rate_limit = 0L) %>%
@@
 
+# Sipes 2017 data
+cyp_data <- readr::read_csv(paste0(
+  Sys.getenv("FIG_DIR"),
+  "RestrictiveClearance_Analysis/",
+  "CLint_CYP_Sipes2017.csv"
+)) %>%
+  left_join(
+    chem.physical_and_invitro.data %>%
+      select(CAS = CAS, Chemical = DTXSID) %>%
+      distinct()
+  ) %>%
+  select(Chemical, CAS, starts_with("MET_")) %>%
+  filter(!is.na(Chemical))
+names(cyp_data) <- c("Chemical", "CAS", "CYP1A2",
+                     "CYP2C9", "CYP2C19", "CYP2D6", "CYP3A4")
+# Functional use categories from CPdat
 functional_uses_all <- readr::read_csv(paste0(
@@
 
+save(cyp_data,
+     file = "data-raw/CYP_Sipes2017.Rdata")
+
 ```
+
+Next we fit the plasma data from CvTdb, which we already have in the `invivoPKfit`
+package using `cvt` object. We also get a few downstream statistics and save them
+in an `.RData` file.
 
@@
 ```
+
+The next two chunks take a while. These will parameterize the `3compartment2`
+`httk` model with restrictive and nonrestrictive clearance.
+It also creates data.frames for evaluating predictions, steady-state concentration,
+and other PK statistics.
+In the first chunk rats are limited parameterized as rats (for _fup_ and _CLint_), and in
+the second chunk human parameterization of _fup_ and _CLint_ are allowed.
 

### 2025-03-19 data-raw/ClearanceProject-1-DataRmd.Rmd
Updating data.

@@
            conc_medium_normalized == "plasma") %>%
-    pull(analyte_dtxsid)
+    pull(analyte_dtxsid) %>% unique()
 
@@
      human_3compchems, rat_3compchems,
+     cvt_plasma_chems,
      file = "data-raw/chem_lists.RData")

### 2025-03-20 data-raw/ClearanceProject-2-RelativeLikelihood.Rmd
Ensured in-progress analysis scripts were able to run sequentially. Further refinement expected in the future.

@@
 
+Here I load all the data
+
 ```{r data_loading}
@@
 load("data-raw/rat_pars_human.RData")
-all_chem_properties <- readRDS("data-raw/ctxR_3comp2_cheminfo.rds")
-
-# Sipes 2017 data
-cyp_data <- readr::read_csv(paste0(
-  Sys.getenv("FIG_DIR"),
-  "RestrictiveClearance_Analysis/",
-  "CLint_CYP_Sipes2017.csv"
-)) %>%
-  left_join(
-    chem.physical_and_invitro.data %>%
-      select(CAS = CAS, Chemical = DTXSID) %>%
-      distinct()
-  ) %>%
-  select(Chemical, CAS, starts_with("MET_")) %>%
-  filter(!is.na(Chemical))
-names(cyp_data) <- c("Chemical", "CAS", "CYP1A2",
-                     "CYP2C9", "CYP2C19", "CYP2D6", "CYP3A4")
+load("data-raw/rat_pars_rat.RData")
+all_chem_properties <- readRDS("data-raw/RCdata/ctxR_3comp2_cheminfo.rds")
+# Here we load Kd/binding affinity data
+red_assay_res <- readRDS("data-raw/2019-05-06-REDassay_HTTK.rds")
+
 # Functional use categories from CPdat
@@
 ```{r venn_diagrams}
+member_list <- list(cvt = cvt_plasma_chems,
+                    httk_3comp2 = human_3compchems)
 
@@
 )
-
 ```
@@
 
-combined_preds <- all_httk_preds %>%
-  mutate(Reference = as.character(Reference)) %>%
+combined_preds <- rph_httk_preds %>%
   left_join(winning_preds) %>%
@@
        height = 3.8, width = 10
-)# Number of chemicals we have RMSLE's for
+)
+
+# Number of chemicals we have RMSLE's for
 combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()
@@
 # LL from pre-calculated httk predictions
-restrictive_ll <- all_httk_preds %>% 
+restrictive_ll <- rph_httk_preds %>% 
+  select(!httk_Preds_nonrestrictive) %>%
   rename(Conc_est = httk_Preds_restrictive,
          Time_trans = Time) %>%
-  select(!httk_Preds_nonrestrictive) %>%
   distinct() %>%
@@
 
-nonrestrictive_ll <- all_httk_preds %>% 
+nonrestrictive_ll <- rph_httk_preds %>% 
+  select(!httk_Preds_restrictive) %>%
   rename(Conc_est = httk_Preds_nonrestrictive,
          Time_trans = Time) %>%
-  select(!httk_Preds_restrictive) %>%
   distinct() %>%
@@
                       this_AIC %>% filter(model == "model_flat") %>%
-                        filter_targets())
+                        filter_targets()
+                      )
 
@@
 
-this_rel_evaluated_df <- this_css_df %>%
+this_rel_evaluated_df <- rph_httk_clearance_df %>%
   inner_join(httk_rel_ll %>% distinct(Chemical, Species, ll_label)) %>%
   inner_join(this_tkstats) %>% # Css
-  inner_join(this_httk_clearance_df) %>% # CLtot and halflife
-  inner_join(data.frame(this_clint_df)) %>%
-  inner_join(this_param_df %>% 
+  inner_join(rph_param_df %>% 
                distinct(Chemical,
@@
                         Fabsgut.restrictive,
-                        Fabsgut.nonrestrictive)) %>%
-  mutate(Chemical = forcats::fct_reorder(Chemical, restrictive_halflife)) %>%
+                        Fabsgut.nonrestrictive,
+                        CLint)) %>%
+  mutate(Chemical = forcats::fct_reorder(Chemical, halflife_restrictive)) %>%
   ungroup() %>%
@@
   distinct(Chemical, Species, Css_httk_r,
-           halflife.tkstats, restrictive_halflife,
-           nonrestrictive_halflife,
+           halflife.tkstats, halflife_restrictive,
+           halflife_nonrestrictive,
            ll_label) %>%
@@
   geom_pointrange(aes(y = halflife.tkstats, 
-                      ymin = nonrestrictive_halflife,
-                      ymax = restrictive_halflife),
+                      ymin = halflife_nonrestrictive,
+                      ymax = halflife_restrictive),
                   size = 0.1, shape = 23) +
@@
   distinct(Chemical, Species, CLtot_Fgutabs.tkstats,
-           restrictive_clearance, nonrestrictive_clearance, 
+           CLtot_restrictive, CLtot_nonrestrictive, 
            Fabsgut.restrictive, Fabsgut.nonrestrictive,
@@
   geom_pointrange(aes(y = CLtot_Fgutabs.tkstats,
-                      ymin = restrictive_clearance/Fabsgut.restrictive,
-                      ymax = nonrestrictive_clearance/Fabsgut.nonrestrictive),
+                      ymin = CLtot_restrictive/Fabsgut.restrictive,
+                      ymax = CLtot_nonrestrictive/Fabsgut.nonrestrictive),
                   size = 0.1, shape = 23) +
@@
 all_chem_functions <- functional_uses_all %>%
-  filter(DTXSID %in% all_chems, !is.na(`Harmonized Functional Use`)) %>% 
+  filter(DTXSID %in% human_3compchems, !is.na(`Harmonized Functional Use`)) %>% 
   group_by(`Harmonized Functional Use`) %>% 
@@
 target_chem_functions <- functional_uses_all %>%
-  filter(DTXSID %in% target_chems, !is.na(`Harmonized Functional Use`)) %>% 
+  filter(DTXSID %in% target_chems_human, !is.na(`Harmonized Functional Use`)) %>% 
   group_by(`Harmonized Functional Use`) %>% 
@@
     filter(
-      DTXSID %in% all_chems, !(DTXSID %in% target_chems), # all non-targets
+      DTXSID %in% human_3compchems, !(DTXSID %in% target_chems_human), # all non-targets
       `Harmonized Functional Use` %in% combined_function_list
@@
     filter(
-      DTXSID %in% target_chems, 
+      DTXSID %in% target_chems_human, 
       `Harmonized Functional Use` %in% combined_function_list
@@
   janitor::clean_names() %>%
-  mutate(n_total_targets = length(target_chems),
-         n_total_nontargets = length(all_chems) - n_total_targets,
+  mutate(n_total_targets = length(target_chems_human),
+         n_total_nontargets = length(human_3compchems) - n_total_targets,
          n_nontargets_out = n_total_nontargets - n_nontargets,
@@
 # Testing to make sure there are some chemicals that have different clearances
-count(this_httk_clearance_df, restrictive_clearance == nonrestrictive_clearance)
+count(rph_httk_clearance_df, CLtot_restrictive == CLtot_nonrestrictive)
 # The majority (140) do!
-
-```
-
-```{r load-other}
-
-# Check to see how much of the full dataset is available
-length(intersect(unique(new.raw.httk.data$DTXSID), full_list))
-
-focus_chems <- union(new.raw.httk.data$DTXSID, target_chems)
-
-all_chem_properties %>%
-  filter(propertyId %in% c("logkow-octanol-water",
-                     "pka-acidic-apparent",
-                     "pka-basic-apparent",
-                     "water-solubility",
-                     "logkoa-octanol-air",
-                     "henrys-law",
-                     "boiling-point")) %>%
-  glimpse()
-
-# Fraction unbound data for target chemicals
-fup_df <- this_param_df %>%
-  distinct(Chemical, Species, forced_human_values,
-           Funbound.plasma, Funbound.plasma.adjustment, 
-           Funbound.plasma.dist) %>%
-  mutate(
-    Funbound.plasma.median = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "^\\d+\\.?\\d+e?-?\\d+(?=,)"
-    )),
-    Funbound.plasma.lower95 = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d+(?=,)"
-    )),
-    Funbound.plasma.upper95 = as.numeric(str_extract(
-      Funbound.plasma.dist, pattern = "(?<=,)\\d+\\.?\\d+e?-?\\d$"
-    ))
-    )
-
-all_hum_rat_fups <- chem.physical_and_invitro.data %>%
-  filter(DTXSID %in% all_chems) %>%
-  select(DTXSID, Human.Funbound.plasma, Rat.Funbound.plasma) %>%
-  mutate(Rat.Funbound.plasma = as.numeric(str_extract(Rat.Funbound.plasma,
-                                                      "^([^,]+)")),
-         Human.Funbound.plasma = as.numeric(str_extract(Human.Funbound.plasma,
-                                                        "^([^,]+)"))
-         )
-
-# Get restrictive and non-restrictive parameters
 
@@
 ```{r load_Kd}
-new.raw.httk.data %>%
+
+red_assay_res %>%
   distinct(DTXSID, Affinity.Kd.Med, Affinity.Kd.Low, Affinity.Kd.High,
@@
   na.omit() %>%
-  mutate(Target_Chemical = (DTXSID %in% target_chems)) %>%
+  mutate(Target_Chemical = (DTXSID %in% target_chems_human)) %>%
 ggplot(
@@
 
-kd_v_fup_plot <- new.raw.httk.data %>%
+all_hum_rat_fups <- chem.physical_and_invitro.data %>%
+  filter(DTXSID %in% human_3compchems) %>%
+  select(DTXSID, Human.Funbound.plasma, Rat.Funbound.plasma) %>%
+  mutate(Rat.Funbound.plasma = as.numeric(str_extract(Rat.Funbound.plasma,
+                                                      "^([^,]+)")),
+         Human.Funbound.plasma = as.numeric(str_extract(Human.Funbound.plasma,
+                                                        "^([^,]+)"))
+         )
+
+kd_v_fup_plot <- red_assay_res %>%
   inner_join(all_hum_rat_fups) %>%
@@
 $$
+
 Where $\theta$ is the relative log-likelihood. The smaller number the better.
@@
 combined_model_weights <- combined_RMSLE %>%
-  left_join(this_rll_probs) %>%
+  left_join(httk_rel_ll) %>%
   ungroup() %>%
@@
                values_to = "relative_likelihood") %>% 
-  filter(all_models == model) %>%
   ungroup() %>%
@@
 count(
-  this_winmodel,
+  this_winmodel %>% filter_targets(),
   model
@@
 count(
-  this_tkstats,
+  this_tkstats %>% filter_targets(),
   # model,
@@
     )
-# 83 chemicals have valid total clearance
-# 180 chemicals have valid total clearance/Fgutabs
-# 5 chemicals have only valid total clearance and no valid total clearance/Fgutabs
-
-count(this_tkstats, is.na(Css.tkstats))
+
+count(this_tkstats %>% filter_targets(), is.na(Css.tkstats))
 
@@
 # Table
-this_css_df %>%
+rph_httk_clearance_df %>%
   count(Css_httk_r == Css_httk_nr,
@@
 # Chart with relative differences (think steps) of Css between clearance types
-this_css_df %>%
+rph_httk_clearance_df %>%
   mutate(relative_difference = (Css_httk_r - Css_httk_nr)/Css_httk_nr) %>%
@@
 ###
-this_css_df %>%
+rph_httk_clearance_df %>%
   mutate(relative_difference = (Css_httk_r - Css_httk_nr)/Css_httk_nr) %>%
@@
   ggplot(aes(x = forcats::fct_reorder(Chemical,
-                                      relative_difference, .desc = FALSE))) +
+                                      relative_difference, 
+                                      max,
+                                      .desc = FALSE))) +
   geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r),
@@
 
-this_css_df %>%
+rph_httk_clearance_df %>%
   mutate(relative_difference = log1p((Css_httk_r - Css_httk_nr)/Css_httk_nr)) %>%
@@
   ggplot(aes(x = forcats::fct_reorder(Chemical,
-                                      relative_difference, .desc = FALSE))) +
+                                      relative_difference,
+                                      max,
+                                      .desc = FALSE))) +
   geom_linerange(aes(ymin = 0,
@@
 
-this_css_df %>%
+rph_httk_clearance_df %>%
   mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
@@
 enhanced_tkstats <- this_tkstats %>%
-  inner_join(this_httk_clearance_df) %>%
+  inner_join(rph_httk_clearance_df) %>%
   inner_join(combined_model_weights) %>%
@@
     between(log2(CLtot.tkstats), 
-            log2(restrictive_clearance)-1,
-            log2(restrictive_clearance)+1) ~ "Restrictive",
+            log2(CLtot_restrictive)-1,
+            log2(CLtot_restrictive)+1) ~ "Restrictive",
     between(log2(CLtot.tkstats), 
-            log2(nonrestrictive_clearance)-1,
-            log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
+            log2(CLtot_nonrestrictive)-1,
+            log2(CLtot_nonrestrictive)+1) ~ "Nonrestrictive",
     between(CLtot.tkstats,
-            restrictive_clearance, nonrestrictive_clearance) ~ "Between",
+            CLtot_restrictive, CLtot_nonrestrictive) ~ "Between",
     .default = "Out of Range"
@@
              shape = 21) +
-  geom_linerange(aes(ymin = restrictive_clearance, 
-                     ymax = nonrestrictive_clearance)) +
-  geom_point(aes(y = restrictive_clearance),
+  geom_linerange(aes(ymin = CLtot_restrictive, 
+                     ymax = CLtot_nonrestrictive)) +
+  geom_point(aes(y = CLtot_restrictive),
              shape = 2, size = 0.8) + # Note that this is the lower value
-  geom_point(aes(y = nonrestrictive_clearance),
+  geom_point(aes(y = CLtot_nonrestrictive),
              shape = 6, size = 0.8) +
@@
 this_tkstats %>%
-  inner_join(this_httk_clearance_df) %>%
+  inner_join(rph_httk_clearance_df) %>%
   inner_join(combined_model_weights) %>%
-  left_join(this_css_df) %>%
+  left_join(rph_httk_clearance_df) %>%
   filter(!is.na(CLtot.tkstats)) %>%
@@
     case_when(
-      between(log2(CLtot.tkstats),log2(restrictive_clearance)-1,
-              log2(restrictive_clearance)+1) ~ "Restrictive",
-      between(log2(CLtot.tkstats),log2(nonrestrictive_clearance)-1,
-              log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
+      between(log2(CLtot.tkstats),log2(CLtot_restrictive)-1,
+              log2(CLtot_restrictive)+1) ~ "Restrictive",
+      between(log2(CLtot.tkstats),log2(CLtot_nonrestrictive)-1,
+              log2(CLtot_nonrestrictive)+1) ~ "Nonrestrictive",
       between(CLtot.tkstats,
-              restrictive_clearance, nonrestrictive_clearance) ~ "Between",
+              CLtot_restrictive, CLtot_nonrestrictive) ~ "Between",
       .default = "Out of range"
@@
              shape = 21) +
-  geom_linerange(aes(ymin = restrictive_clearance, 
-                     ymax = nonrestrictive_clearance)) +
-  geom_point(aes(y = restrictive_clearance),
+  geom_linerange(aes(ymin = CLtot_restrictive, 
+                     ymax = CLtot_nonrestrictive)) +
+  geom_point(aes(y = CLtot_restrictive),
              shape = 4, size = 0.8) + # Note that this is the lower value
-  geom_point(aes(y = nonrestrictive_clearance),
+  geom_point(aes(y = CLtot_nonrestrictive),
              shape = 4, size = 0.8) +
@@
 # nearest_clearance (using Css), and model weight
-this_fupZ_df <- this_param_df %>% select(Chemical, Funbound.plasma.restrictive) %>%
-  mutate(Fup_Z = as.vector(scale(sqrt(Funbound.plasma.restrictive))),
+this_fupZ_df <- rph_param_df %>% select(Chemical, Funbound.plasma) %>%
+  mutate(Fup_Z = as.vector(scale(sqrt(Funbound.plasma))),
          .keep = "unused")
-
-this_dist_prepdf <- this_css_df %>% select(Chemical, model, Route,
-                       nearest_clearance, comparison_group_Css,
-                       Css_httk_r, Css_httk_nr) %>%
-  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr),
-         .keep = "unused") %>%
-  inner_join(combined_model_weights %>%
-               select(Chemical, Species, gamma_weight)) %>%
-  inner_join(enhanced_tkstats %>%
-               select(Chemical, Species, comparison_CLtot)) %>%
-  inner_join(this_fupZ_df) %>%
-  distinct() %>%
-  mutate(ID = paste(Chemical, Species, model, Route, sep = "."), .keep = "unused")
-
-this_dist_prepdf %>%
-ggplot(aes(x = gamma_weight, y = Fup_Z, color = relative_difference)) + 
-  geom_point() +
-  scale_color_viridis_c() +
-  facet_grid(cols = vars(comparison_CLtot))
 
@@
   left_join(
-    this_param_df %>%
-      distinct(Chemical, Species, Fabsgut.restrictive)
+    rph_param_df %>%
+      distinct(Chemical, Fabsgut.restrictive)
   ) %>%
@@
 
-ggplot(data = this_httk_clearance_df,
+ggplot(data = rph_httk_clearance_df,
        aes(x = Chemical)) +
-  geom_point(aes(y = restrictive_clearance), color = "green4") +
-  geom_point(aes(y = nonrestrictive_clearance), color = "orange2") +
+  geom_point(aes(y = CLtot_restrictive), color = "green4") +
+  geom_point(aes(y = CLtot_nonrestrictive), color = "orange2") +
   geom_point(data = this_tkstats2,
@@
 # Combine these two
-combined_clearance_df <- this_httk_clearance_df %>%
+combined_clearance_df <- rph_httk_clearance_df %>%
   inner_join(this_tkstats) %>%
@@
   ggplot(aes(x = halflife.tkstats)) +
-  geom_point(aes(y = restrictive_halflife), color = "magenta2") +
-  geom_point(aes(y = nonrestrictive_halflife), color = "green4") +
+  geom_point(aes(y = halflife_restrictive), color = "magenta2") +
+  geom_point(aes(y = halflife_nonrestrictive), color = "green4") +
   coord_equal(xlim = c(0, 200), y = c(0, 200))
@@
 
-```{r clearance_viz}
-
-this_param_df %>%
-  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
-  inner_join(combined_clearance_df) %>%
-  mutate(CLtot.nonrest = CLtot_Fgutabs.tkstats * Fabsgut.nonrestrictive,
-         CLtot.rest = CLtot_Fgutabs.tkstats * Fabsgut.restrictive) %>%
-  pivot_longer(cols = c(restrictive_clearance, nonrestrictive_clearance,
-                        CLtot.nonrest, CLtot.rest),
-               names_to = "Source",
-               values_to = "Clearance") %>%
-  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
-  geom_point() +
-  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
-  theme_bw() +
-  coord_cartesian(xlim = c(0.0001, 1000)) +
-  scale_x_log10()
-
-this_param_df %>%
-  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
-  inner_join(combined_clearance_df) %>%
-  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
-         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
-  pivot_longer(cols = c(CLtot_Fgutabs.tkstats,
-                        rest_fgutabs, nonrest_fgutabs),
-               names_to = "Source",
-               values_to = "Clearance") %>%
-  ggplot(aes(y = Chemical, x = Clearance, color = Source)) +
-  geom_point() +
-  labs(title = "comparison of restrictive and non-restrictive clearance estimates") +
-  theme_bw() +
-  coord_cartesian(xlim = c(0.000001, 100000)) +
-  scale_x_log10()
-
-this_param_df %>%
-  distinct(Chemical, Species, Fabsgut.restrictive, Fabsgut.nonrestrictive) %>%
-  inner_join(combined_clearance_df) %>%
-  mutate(nonrest_fgutabs = nonrestrictive_clearance / Fabsgut.nonrestrictive,
-         rest_fgutabs = nonrestrictive_clearance / Fabsgut.restrictive) %>%
-   mutate(AD_restrictive = abs(CLtot_Fgutabs.tkstats - rest_fgutabs),
-         AD_nonrestrictive = abs(CLtot_Fgutabs.tkstats - nonrest_fgutabs),
-         rough_determination = ifelse(
-           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
-             CLtot.tkstats <= nonrest_fgutabs,
-           "Restrictive", "Possibly non-Restrictive"
-         )) %>% 
-  dplyr::ungroup() %>% View()
-
-clearance_guess <- combined_clearance_df %>%
-  mutate(AD_restrictive = abs(CLtot.tkstats - restrictive_clearance),
-         AD_nonrestrictive = abs(CLtot.tkstats - nonrestrictive_clearance),
-         rough_determination = ifelse(
-           min(AD_restrictive, AD_nonrestrictive) == AD_restrictive &
-             CLtot.tkstats < nonrestrictive_clearance,
-           "Restrictive", "Possibly non-Restrictive"
-         )) %>% 
-  dplyr::ungroup()
-
-clearance_guess %>%
-  dplyr::distinct(Chemical, rough_determination) %>%
-  group_by(rough_determination) %>%
-  tally()
-
-# Preliminary viz, plot all clearances
-ccd <- clearance_guess %>%
-  relocate(CLtot.nca_mean, CLtot.nca_sd, .after = tidyselect::last_col()) %>%
-  pivot_longer(
-    cols = tidyselect::all_of(c("CLtot.tkstats", "CLtot.nca_mean",
-                              "restrictive_clearance", "nonrestrictive_clearance")),
-    names_to = "Clearance_Source",
-    values_to = "Value"
-  ) %>%
-  mutate(
-    Chemical = factor(Chemical),
-    Clearance_Source = factor(
-      Clearance_Source,
-      levels = c(
-        "CLtot.tkstats", "CLtot.nca_mean",
-        "nonrestrictive_clearance", "restrictive_clearance"
-      )
-    ),
-    label_cols = ifelse(rough_determination == "Restrictive",
-                     "green4", "orange3")
-  ) %>%
-  transform(
-    Chemical = fct_reorder(Chemical, Value, max)
-  ) %>% 
-  as_tibble()
-
-ccd %>%
-  ggplot(aes(
-    x = Value,
-    y = Chemical,
-    fill = Clearance_Source
-  )) +
-  geom_point(shape = 21, alpha = 0.7) +
-  scale_x_log10() +
-  scale_fill_manual(
-    breaks = c(
-      "nonrestrictive_clearance", "CLtot.tkstats",
-      "CLtot.nca_mean",
-      "restrictive_clearance"
-    ),
-    labels = c(
-      "non-restrictive clearance (httk)",
-      "predicted clearance (invivoPKfit)",
-      "mean non-compartmental total clearance (invivoPKfit)",
-      "restrictive clearance (httk)"
-    ),
-    values = c("orange2", "grey5", "skyblue3", "green4")
-  ) +
-  facet_grid(rows = vars(Species), scales = "free", space = "free") +
-  labs(
-    x = "Total Clearance",
-    y = "Chemical",
-    title = "Comparing clearance estimates of chemicals with rat CvT data"
-  ) +
-  theme(
-    panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
-    panel.background = element_blank(),
-    panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
-    strip.background = element_rect(fill = "white"),
-    strip.text = element_text(face = "bold", angle = 0),
-    axis.title.y = element_blank(),
-    legend.position = "right",
-    legend.direction = "vertical",
-    axis.ticks = element_blank(),
-    axis.line = element_blank()
-  )
-
-clear_chem_levels <- levels(ccd$Chemical)
-
-ggsave(
-  filename = paste0(
-    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
-    today,
-    "all_tkClearance_comparison_httk_PBPK.png"
-  ),
-  height = 8,
-  width = 8,
-  device = "png"
-)
-```
-
-I would also like to know, how does the $f_{up}$ of this set of chemicals
-compare to that of all chemicals in `httk` (Dawson 2021).
-
-```{r fup_comparison}
-
-fup_df %>%
-  ggplot(aes(x = Funbound.plasma.adjustment)) +
-  geom_histogram(
-    data = fup_df %>%
-      filter(Chemical %in% this_httk_clearance_df$Chemical),
-    # aes(y = after_stat(density)),
-    fill = "white",
-    color = "darkgreen", binwidth = 0.03
-  ) +
-  expand_limits(expand = c(0,0)) +
-  geom_vline(xintercept = 0.05, linetype = "dashed") +
-  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
-  scale_x_continuous(expand = expansion(mult = c(0.01, 0.01))) +
-  labs(
-    title = "Distribution of Funbound.plasma values",
-    subtitle = "(chemicals fit by invivoPKfit in dark green)"
-  ) +
-  coord_cartesian(clip = "off") +
-  theme_bw()
-
-ggsave(paste0(Sys.getenv("FIG_DIR"), "fup_density_plots.png"),
-       height = 5,
-       width = 6,
-       device = ragg::agg_png,
-       units = "in"
-)
-
-test_fup <- fup_df %>%
-  pull(Funbound.plasma)
-for (i in seq(0, 0.5, by = 1e-9)) {
-  if (sum(test_fup > i) == sum(test_fup <= i)) {
-    print(i)
-    break
-  }
-}
-
-fup_df %>%
-  ggplot(aes(x = Funbound.plasma, y = Funbound.plasma.adjustment)) +
-  geom_point()
-
-```
-
-## Exploring _httk_ parameters and solved values for `gas_pbtk`
+## Exploring _httk_ parameters and solved values for `3compartment2`
 
@@
 
-solve_gas_pbtk(
-  dtxsid = common_chems_dawson[10],
+solve_3comp2(
+  dtxsid = target_chems_rat[10],
   dose = 1, exp.conc = 0,
@@
   geom_line(aes(y = Cplasma)) +
-  geom_line(aes(y = Crest), color = "blue4") +
-  geom_line(aes(y = Cgut), color = "goldenrod") +
-  geom_line(aes(y = Cliver), color = "darkgreen") +
-  geom_line(aes(y = Clung), color = "hotpink") +
-  geom_line(aes(y = Ckidney), color = "purple4")
-
-# Functions wrapping httk single dose evaluation
-httk_bolus_gas_pbtk <- function(dtxsid, species = "Human",
-                                dose, times, iv.dose, LOQ) {
-  tmp_solution <- solve_gas_pbtk(
-    dtxsid = unique(dtxsid),
-    dose = unique(dose),
-    exp.conc = 0,
-    iv.dose = unique(iv.dose),
-    times = unique(c(0, times/24)),
-    input.units = "mg/kg",
-    output.units = "mg/L",
-    species = unique(stringr::str_to_title(species)),
-    default.to.human = TRUE,
-    suppress.messages = TRUE
-  )
-  # Remove the 0.0001 intermediate time value that is returned
-  retdf <- tibble(
-    Time = round(tmp_solution[, "time"]*24, digits = 3),
-    httk_Preds = tmp_solution[, "Cplasma"]
-  )
-  retdf[which(retdf$Time %in% unique(round(times, 3))), ]
-}
-
-httk_preds_rat <- get_httk_preds(rat_pars_rat, this_pk, species = "rat")
-
-```
-
-We need to put the _in vivo_ data in an amenable format.
-For this I will limit the species to "rat", the chemicals to
-`common_chems_rat`, and the medium to "plasma".
-
-```{r rat_data}
-rat_df <- httk_preds_rat %>%
-  left_join(predict(this_pk)) %>%
-  semi_join(this_winmodel)
-
-rat_df %>% ggplot(mapping = aes(
-    x = Conc_est,
-    y = httk_Preds,
-    color = interaction(Route)
-  )) +
-  geom_point() +
-  geom_abline(slope = 1, intercept = 0, color = "black") +
-  scale_x_log10() + scale_y_log10() +
-  facet_wrap(~Route)
-
-rat_plots <- rat_df %>%
-  distinct(Chemical, Species, Dose, Route, Media, Reference,
-           Time, httk_Preds, Conc, Conc_est, pLOQ) %>%
-  mutate(Dose = as.factor(Dose)) %>%
-  group_by(Chemical, Species, Route, Media, Reference) %>%
-  nest(.key = "data_pl")
-
-rat_plots <- rat_plots %>%
-  reframe(plots = purrr::map(data_pl,
-                             \(x) {
-                               cowplot::plot_grid(
-                               ggplot(data = x %>%
-                                        group_by(Time, Dose) %>%
-                                        mutate(meanConc = mean(Conc,
-                                                           na.rm = TRUE)) %>%
-                                        select(-Conc) %>% distinct() %>%
-                                        pivot_longer(cols = c(httk_Preds,
-                                                              meanConc,
-                                                              Conc_est),
-                                                     names_to = "Measurement",
-                                                     values_to = "Concentration"
-                                                     ), 
-                                      mapping = aes(
-                                        x = Time,
-                                        y = Concentration,
-                                        color = Measurement,
-                                        shape = Dose
-                                      )) +
-                                 geom_point() +
-                                 geom_line(
-                                   aes(group = interaction(Measurement, Dose))
-                                   ) +
-                                 theme_bw() +
-                                 labs(
-                                   title = paste(Chemical, Species),
-                                   subtitle = paste(Route, Media)
-                                 ),
-                               ggplot(data = x) +
-                                 geom_point(aes(x = Conc_est, httk_Preds,
-                                                shape = Dose)) +
-                                 geom_abline(slope = 1, intercept = 0,
-                                             linetype = "dashed") +
-                                 theme_bw()
-                               )
-                             })
-  )
-
-pdf(file = paste0(Sys.getenv("FIG_DIR"), "RC_comparison_CvTplots.pdf"),
-    onefile = TRUE,
-    height = 7,
-    width = 10,
-    bg = "white")
-
-for (i in 1L:NROW(rat_plots)) {
-  message("Now plotting: ", i)
-  print(rat_plots %>% pull(plots) %>% .[[i]])
-}
-
-dev.off()
-
-length(unique(rat_df$Chemical))
-
-rat_df$Chemical <- factor(rat_df$Chemical, levels = clear_chem_levels)
-
-rat_out <- rat_df %>%
-  filter(Chemical %in% clear_chem_levels) %>%
-  group_by(Chemical, Species, Route, Reference, Media) %>%
-  mutate(httk_Preds = ifelse(httk_Preds < pLOQ, pLOQ, httk_Preds)) %>% 
-  mutate(SLE = (log2(Conc) - log2(httk_Preds))^2,
-         AE = abs(Conc - httk_Preds)) %>%
-  summarize(
-    RMSLE = sqrt(mean(SLE, na.rm = TRUE)),
-    MAE = mean(AE, na.rm = TRUE)
-   ) %>% pivot_longer(cols = c(RMSLE, MAE),
-                      names_to = "metric",
-                      values_to = "value")
-
-rat_out %>%
-  na.omit() %>%
-  ggplot() +
-  geom_tile(data = rat_out %>% na.omit() %>%
-              filter(metric %in% "RMSLE"),
-            aes(x = metric, y = Chemical, fill = value)) +
-  scale_fill_gradient(low = "grey5", high = "grey90",
-                      name = "RMSLE") +
-  ggnewscale::new_scale_fill() +
-  geom_tile(data = rat_out %>% na.omit() %>%
-              filter(metric %in% "MAE"),
-            aes(x = metric, y = Chemical, fill = value)) +
-  scale_fill_gradient(low = "darkgreen", high = "seagreen1",
-                      limits = c(0, 80),
-                      labels = c("0", "20",
-                                 "40", "60",
-                                 "80+"),
-                      oob = scales::squish,
-                      name = "MAE") +
-  theme_minimal() +
-  theme(axis.text.x = element_text(hjust = 1, angle = 50),
-        legend.title = element_text(hjust = 0.5)) +
-  coord_fixed(ratio = 0.75)
-
-ggsave(
-  filename = paste0(
-    Sys.getenv("FIG_DIR"),
-    "rat_httk_predictionRMSLE.png"
-  ),
-  height = 8.1,
-  width = 4,
-  device = "png"
-)
-
-rat_out2 <- rat_df %>%
-  group_by(Chemical, Species, Route, Dose) %>% nest() %>%
-  summarize(plot = map(
-    data,
-    \(d){
-      ggplot(d, aes(x = Time)) +
-        geom_point(aes(y = Conc)) +
-        geom_line(aes(y = httk_Preds),
-                    color = "forestgreen") +
-        geom_point(aes(y = httk_Preds),
-                   color = "forestgreen",
-                   shape = 1) +
-        labs(title = Chemical,
-             subtitle = paste(Dose, "mg/kg given via",
-                               Route, "bolus"),
-             y = "Plasma Concentration (mg/L)",
-             x = "Time (hrs)") +
-        theme_bw() +
-        theme(plot.title = element_text(hjust = 0.5),
-              plot.subtitle = element_text(hjust = 0.5))
-    }
-  ))
-```
-
-```{r httk_solution}
-
-rat_params %>%
-  ggplot(aes(y = fupClint)) + 
-  geom_point(aes(x = Clint), color = "darkred", shape = 1) +
-  geom_abline(slope = 1, intercept = 0, color = "darkblue",
-              linetype = "dashed")
-rat_params %>%
-  mutate(fup_z = scale(Funbound.plasma),
-         clint_z = scale(Clint)) %>%
-  dplyr::select(Chemical, fup_z, clint_z) %>%
-  pivot_longer(cols = c(fup_z, clint_z),
-               names_to = "pars", values_to = "vals") %>%
-  ggplot(aes(x = pars, y = vals, group = Chemical)) +
-  geom_line()
-
-httk::calc_tkstats(dtxsid = unique(rat_out$Chemical)[[5]])
-httk::parameterize_gas_pbtk(
-  restrictive.clearance = TRUE,
-  dtxsid = unique(rat_out$Chemical)[[5]]
-)
-
-httk::solve_gas_pbtk(
-  dtxsid = unique(combined_clearance_df$Chemical)[[5]],
-  parameters = httk::parameterize_gas_pbtk(
-    restrictive.clearance = TRUE,
-    dtxsid = unique(combined_clearance_df$Chemical)[[5]]
-  ),
-  dose = 10,
-  exp.conc = 0,
-  input.units = "mg",
-  output.units = "mg",
-  days = 3,
-  plots = TRUE
-)
-
-# For the invivoPKfit functions, we will hold kelim constant
-# This constant will be calculated as CLtot/Vdist (or V1, if 2-compartment)
-# This constant is derived by httk in the following way:
-calc_total_clearance(
-  dtxsid = common_chems[[10]],
-  restrictive.clearance = FALSE
-) /
-  calc_vdist(dtxsid = common_chems[[10]])
-```
-
-I have modified the starts of the 1- and 2-compartment models,
-as well as adding a restrictive_clearance argument in stat_model.
-
-```{r running-invivoPKfit}
-# This is now updated to use dawson chem table
-minimal_pk <- pk(data = cvt %>%
-                   filter(analyte_dtxsid %in% this_chem_v,
-                          species %in% "rat",
-                          administration_route_normalized == "iv"))
-
-new_pk <- minimal_pk +
-  facet_data(vars(Chemical, Species)) +
-  settings_preprocess(
-    keep_data_original = TRUE,
-    suppress.messages = FALSE
-  ) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
-  stat_error_model(error_group = vars(Chemical, Species)) +
-  stat_model(model = c(
-    "model_1comp", "model_1comp_cl_rest", 
-    "model_1comp_cl_nonrest", "model_1comp_fup",
-    "model_flat")) +
-  settings_optimx(method = c("bobyqa"))
-
-new_pk <- do_data_info(new_pk)
-
-new_pk <- do_prefit(new_pk)
-gc()
-
-unique(new_pk$prefit$par_DF$param_name) # Check all parameters are there
-length(unique(new_pk$data$Chemical)) 
-length(unique(this_chem_v))
-
-new_pk <- do_fit(new_pk, n_cores = 14)
-gc()
-
-new_pk$fit %>%
-  View()
-
-# saveRDS(new_pk, "data-raw/ratCVT_wHTTK_reformulated.rds")
+  geom_line(aes(y = Csyscomp), color = "blue4") +
+  geom_line(aes(y = Cliver), color = "darkgreen")
+
 ```
@@
 
+**At this time this analysis is still in development**
+
 ```{r begin_analysis}
-# new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
-coef(new_pk) %>% View()
+new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
+
 new_winmodel <- get_winning_model(new_pk)
-eval_tkstats(new_pk, finite_only = TRUE) %>% 
-  semi_join(new_winmodel) %>%
-  View()
 

### 2025-03-20 data-raw/ClearanceProject-4-PhysChemClustering.Rmd
Ensured in-progress analysis scripts were able to run sequentially. Further refinement expected in the future.

@@
 ```{r data_loading}
-target_chem_properties <- readRDS("data-raw/ctxR_3comp2_cheminfo.rds")
+target_chem_properties <- readRDS("data-raw/RCdata/ctxR_3comp2_cheminfo.rds")
 new_pk <- readRDS("data-raw/ratCVT_wHTTK_reformulated.rds")
 red_assay_res <- readRDS("data-raw/2019-05-06-REDassay_HTTK.rds")
+load("data-raw/CYP_Sipes2017.RData")
 ```
@@
 
-target_chem_pw_full %>%
+target_chem_properties %>%
   ggplot(aes(x = forcats::fct_reorder(dtxsid, logkow))) +
@@
                       ymax = logkow + logkow_sd), size = 0.1) +
-  facet_grid(cols = vars(type_logkow)) +
+  # facet_grid(cols = vars(type_logkow)) +
   theme_bw() +
@@
 tcs_mat <- target_chem_summary %>% 
-  select(dtxsid, monoisotopicMass, Affinity.Kd.Med,
-         H_donors:Rot_Bonds, logkow, apKa, bpKa, logD_7.4,
+  select(dtxsid, monoisotopicMass, logkow:Affinity.Kd.Med,
          starts_with("CYP")) %>%
@@
 summary(tcs_mat_z[, 1])
-summary(tcs_mat_z[(rownames(tcs_mat_z) %in% target_chems), 1])
+summary(tcs_mat_z[(rownames(tcs_mat_z) %in% target_chems_human), 1])
 tcs_mat_z[is.na(tcs_mat_z)] <- 0
@@
 
-ggplot(data = pca_df %>% mutate(Target = (Chemical %in% target_chems)) %>%
+ggplot(data = pca_df %>% mutate(Target = (Chemical %in% target_chems_human)) %>%
          left_join(target_chem_summary, by = join_by(Chemical == dtxsid)),
@@
 
-chem_rell_label <- total_rel_evaluation_df %>% distinct(Chemical, ll_label) %>%
+chem_rell_label <- this_rel_evaluated_df %>% distinct(Chemical, ll_label) %>%
   filter(ll_label %in% c("Restrictive", "Nonrestrictive"))
 
+fup_df <- rph_param_df %>% distinct(Chemical, Funbound.plasma)
 # Molecular descriptors in bins
@@
   ggbeeswarm::geom_beeswarm() +
-  theme_bw()
-
-target_chem_summary %>%
-  inner_join(chem_rell_label, by = join_by(dtxsid == Chemical)) %>%
-  distinct(dtxsid, logkow, TPSA, Rot_Bonds, ll_label) %>% 
-  pivot_longer(cols = c(logkow, TPSA),
-               names_to = "Parameter", values_to = "Value") %>%
-  left_join(fup_df, by = join_by(dtxsid == Chemical)) %>%
-  ggplot(aes(x = Value, y = Funbound.plasma)) +
-  labs(x = "", y = "fup") +
-  facet_grid(cols = vars(Parameter),
-             rows = vars(ll_label),
-             scales = "free_x") +
-  geom_point() +
   theme_bw()

### 2025-03-20 data-raw/ClearanceProject-2-RelativeLikelihood.Rmd

@@
 )
+
 ```
@@
 ```{r load_Kd}
-
 red_assay_res %>%
@@
   mutate(Target_Chemical = (DTXSID %in% target_chems_human)) %>%
+
 ggplot(
@@
 $$
-
 Where $\theta$ is the relative log-likelihood. The smaller number the better.
@@
 ```{r rat_invivo_comparison}
-
 solve_3comp2(

### 2025-03-20 data-raw/ClearanceProject-3-TKstats.Rmd

@@
 
-Next what we want to do is get httk predictions for nonrestrictive & 
-restrictive chemicals, but going from
-
-```{r}
-
-```
+This next analysis looks at bootstrapping to look at specific variation in downstream
+parameters (like Css and halflife) which depend on _kelim_ which cannot be estimated
+at times. However, it is noted that even this method does not provide much more information.
 

### 2025-03-24 data-raw/ClearanceProject-3-TKstats.Rmd
Added figure investigating interspecies trends in fup and CLint.

@@
               values_from = RMSLE) %>%
-  mutate(norm_diff = (human - rat)/rat) %>%
+  mutate(norm_diff = (human - rat)/rat)
+
+irt_pl <- interspecies_rmsle_trends %>%
   filter(!is.na(norm_diff)) %>% 
-  group_by(Chemical, close_clint, clearance_type) %>%
   ggplot(aes(x = forcats::fct_reorder(Chemical, norm_diff, mean),
@@
 
-species_clint_pl + interspecies_rmsle_trends +
+species_clint_pl + irt_pl +
   plot_layout(widths = c(5,8))
@@
        bg = "white")
+```
+
+From this we notice that CLint specifically can have drastic differences which
+we want to explore. We also glean that there are potential drastic improvements
+in model accuracy. We next want to compare how a changing human CLint towards rat
+CLint by 1% steps changes RMSE.
+
+```{r}
+combo_clint <- rpr_param_df %>%
+  select(Chemical, rCLint = CLint) %>% 
+  left_join(rph_param_df %>%
+              select(Chemical, hCLint = CLint)) %>%
+  mutate(hclint_1p = (1/10)*hCLint, 
+         direction = sign(hCLint - rCLint)) %>%
+  mutate(Nstep = ifelse(direction == 0, 
+                        0, abs(hCLint - rCLint) %/% hclint_1p))
+
+combo_clint %>%
+  left_join(interspecies_rmsle_trends) %>%
+  ggplot(aes(Nstep, norm_diff)) +
+  geom_point() +
+  scale_x_log10() +
+  theme_bw()
 ```

### 2025-04-02 data-raw/ClearanceProject-2-RelativeLikelihood.Rmd
Updated relative loglikelihood analysis based on predictions from latest httk-dev and included best fit empirical compartmental model in the calculation.

@@
 # LL from pre-calculated httk predictions
-restrictive_ll <- rph_httk_preds %>% 
-  select(!httk_Preds_nonrestrictive) %>%
-  rename(Conc_est = httk_Preds_restrictive,
-         Time_trans = Time) %>%
-  distinct() %>%
-  group_by(Chemical, Species) %>%
-  nest(.key = "observations") %>%
-  inner_join(coef(this_pk) %>% semi_join(this_winmodel) %>% distinct()) %>%
-  rowwise() %>%
-  mutate(log_likelihood = log_likelihood(
-    par = coefs_vector,
-    data = observations,
-    data_sigma_group = observations$data_sigma_group,
-    dose_norm = FALSE,
-    log10_trans = FALSE,
-    negative = FALSE,
-    includes_preds = TRUE,
-    detect
-  )) %>%
-  select(!c(observations, coefs_vector, Time.Units, Time_trans.Units)) %>%
-  mutate(model = "model_3comp2_restrictive",
-         AIC = -2 * log_likelihood)
-
-nonrestrictive_ll <- rph_httk_preds %>% 
-  select(!httk_Preds_restrictive) %>%
-  rename(Conc_est = httk_Preds_nonrestrictive,
-         Time_trans = Time) %>%
-  distinct() %>%
-  group_by(Chemical, Species) %>%
-  nest(.key = "observations") %>%
-  inner_join(coef(this_pk) %>% semi_join(this_winmodel) %>% distinct()) %>%
-  rowwise() %>%
-  mutate(log_likelihood = log_likelihood(
-    par = coefs_vector,
-    data = observations,
-    data_sigma_group = observations$data_sigma_group,
-    dose_norm = FALSE,
-    log10_trans = FALSE,
-    negative = FALSE,
-    includes_preds = TRUE,
-    detect
-  )) %>%
-  select(!c(observations, coefs_vector, Time.Units, Time_trans.Units)) %>%
-  mutate(model = "model_3comp2_nonrestrictive",
-         AIC = -2 * log_likelihood) # Simple formula when there are no optimized params
-
-httk_AIC <- bind_rows(restrictive_ll,
-                      nonrestrictive_ll,
-                      this_AIC %>% filter(model == "model_flat") %>%
-                        filter_targets()
+this_pk <- this_pk %>% fit_sigma.pk(preds = rpr_httk_preds,
+                                    pred_col = "httk_Preds_restrictive")
+this_pk <- this_pk %>% fit_sigma.pk(preds = rpr_httk_preds,
+                                    pred_col = "httk_Preds_nonrestrictive")
+
+restrictive_ll <- this_pk$ext_fits.httk_Preds_restrictive$sigma_AIC
+
+nonrestrictive_ll <- this_pk$ext_fits.httk_Preds_nonrestrictive$sigma_AIC
+
+# Get NULL models and winning models AICs (call them empirical model)
+invivoPKfit_AIC <- bind_rows(
+  this_AIC %>% semi_join(this_winmodel) %>%
+    mutate(model = "model_empirical"),
+  this_AIC %>% filter(model == "model_flat")
+) %>% distinct()
+
+httk_AIC <- bind_rows(
+  restrictive_ll %>% mutate(model = "model_3comp2_restrictive"),
+  nonrestrictive_ll %>% mutate(model = "model_3comp2_nonrestrictive"),
+  invivoPKfit_AIC
 )
@@
   pivot_wider(names_from = model, values_from = AIC) %>%
+  filter(!is.na(model_3comp2_nonrestrictive)) %>%
   rowwise() %>% 
-  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
+  mutate(minAIC = min(c_across(starts_with("model_")), 
+                      na.rm = TRUE)) %>%
   ungroup() %>%
@@
     case_when(model_flat > 95 ~ "Undetermined",
-              model_3comp2_nonrestrictive > 95 &
-                model_3comp2_restrictive > 95 ~ "Undetermined (non-flat)",
-              model_3comp2_nonrestrictive > 95 ~ "Nonrestrictive",
-              model_3comp2_restrictive > 95 ~ "Restrictive")
+              model_3comp2_nonrestrictive > 50 &
+                model_3comp2_restrictive > 50 ~ "Undetermined (non-flat)",
+              model_3comp2_nonrestrictive > 50 ~ "Nonrestrictive",
+              model_3comp2_restrictive > 50 ~ "Restrictive")
   ))
+
+httk_rel_ll %>% 
+  select(Chemical, Species, starts_with("model_"), minAIC) %>%
+  mutate(Chemical = forcats::fct_reorder2(Chemical,
+                                         model_flat,
+                                         minAIC,
+                                         mean)
+         ) %>%
+  pivot_longer(cols = starts_with("model_"),
+               names_to = "model", values_to = "relative_ll") %>%
+  mutate(
+    source = ifelse(grepl("_3comp2_", model), "httk", "invivoPKfit")
+  ) %>%
+  ggplot(aes(x = Chemical, y = relative_ll, color = model, shape = source)) +
+  geom_point(size = 0.75, alpha = 0.9) +
+  scale_color_manual(
+    values = c('#33a02c', '#cc88ff', '#7b3294', 'orange'),
+    breaks = c('model_empirical',
+               'model_3comp2_restrictive',
+               'model_3comp2_nonrestrictive',
+               'model_flat')
+  ) +
+  scale_shape_manual(values = c(2, 3)) +
+  labs(
+    title = "Relative likelihoods",
+    subtitle = "(rat parameterized with human CLint and fup values)",
+    y = "More Likely Model >>>",
+    color = ''
+  ) +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        legend.position = "bottom",
+        plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "AIC_comparisons.png"),
+       bg = "white",
+       height = 5, width = 10
+)
 

### 2025-04-02 data-raw/ClearanceProject-3-TKstats.Rmd
Updated relative loglikelihood analysis based on predictions from latest httk-dev and included best fit empirical compartmental model in the calculation.

@@
 library(httk)
-.onUnload <- function(libpath) {
-  library.dynam.unload("httk", libpath)
-}
 ```
@@
 
+Next I want to categorize each chemical based on putative hepatic extraction ratio.
+This is calculated as:
+$$
+E_H = \frac{f_{up}\cdot CL_{int}}{Q_{hep} + f_{up}\cdot CL_{int}}
+$$
+```{r extraction_ratio}
+rat_er <- rpr_param_df %>%
+  group_by(Chemical) %>%
+  reframe(fupClint = (Funbound.plasma * Clint),
+          Qhep = (Qcardiacc*Qliverf)) %>%
+  mutate(extraction_ratio = fupClint/(Qhep + fupClint),
+         clearance_type_by_er = case_when(
+           extraction_ratio >= 0.7 ~ "Nonrestrictive",
+           extraction_ratio < 0.3 ~ "Restrictive",
+           between(extraction_ratio, 0.3, 0.7) ~ "Ambiguous"
+         )
+  )
+
+human_er <- rph_param_df %>%
+  group_by(Chemical) %>%
+  reframe(fupClint = (Funbound.plasma * Clint),
+          Qhep = (Qcardiacc*Qliverf)) %>%
+  mutate(extraction_ratio = fupClint/(Qhep + fupClint),
+         clearance_type_by_er = case_when(
+           extraction_ratio >= 0.7 ~ "Nonrestrictive",
+           extraction_ratio < 0.3 ~ "Restrictive",
+           between(extraction_ratio, 0.3, 0.7) ~ "Ambiguous"
+         )
+  )
+
+combo_pretable <- inner_join(
+  rat_er %>% select(Chemical,
+                    "rat_er" = extraction_ratio, 
+                    "rat_cl" = clearance_type_by_er),
+  human_er %>% select(Chemical,
+                    "human_er" = extraction_ratio, 
+                    "human_cl" = clearance_type_by_er)
+)
+# Row, Columns
+# In this case, rat is rows, human is columns
+clearance_contingency_tbl <- table(combo_pretable$rat_cl, combo_pretable$human_cl)
+addmargins(clearance_contingency_tbl)
+
+```
+
 This next analysis looks at bootstrapping to look at specific variation in downstream

### 2025-04-03 data-raw/ClearanceProject-3-TKstats.Rmd
Added hepatic blood flow sensitivity analysis as a possible test for restrictive/nonrestrictive clearance assumption.

@@
 library(httk)
+load_dawson2021()
+
 ```
@@
 This is calculated as:
+
 $$
@@
 ```
+
+I want to do some sensitivity analysis for hepatic blood flow.
+The logic here is that, with nonrestrictive clearance, the clearance is
+flow-dependent and therefore would be sensitive to increases in hepatic
+blood flow. Restrictive compounds should not.
+
+For rats, the default hepatic blood flow (in mL/min/kg^(3/4)) is 33.38.
+I will increase this by 1% (i.e. 0.3338) and look at the sensitivity of
+steady-state concentration and total clearance.
+
+```{r hbf_sensitivity}
+# Find 1% increment
+liver_tissue_new <- subset(tissue.data,
+                           Tissue == "liver" &
+                             Species == "Rat")
+
+new_hepblfl_increment <- liver_tissue_new[
+  liver_tissue_new$variable == "Flow (mL/min/kg^(3/4))",
+  "value"
+] * (1/100) # Get the increment amount (this is delta r)
+# Calculate numerator for normalized sensitivity coefficient, 1%
+drr <- new_hepblfl_increment/liver_tissue_new[
+  liver_tissue_new$variable == "Flow (mL/min/kg^(3/4))",
+  "value"
+]
+
+# Decrease "rest" of body blood flow
+tissue.data[
+  tissue.data$Tissue == "rest" &
+    tissue.data$Species == "Rat" &
+    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
+  "value"
+  ] <- tissue.data[
+  tissue.data$Tissue == "rest" &
+    tissue.data$Species == "Rat" &
+    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
+  "value"
+  ] - new_hepblfl_increment
+# Increase hepatic blood flow
+tissue.data[
+  tissue.data$Tissue == "liver" &
+    tissue.data$Species == "Rat" &
+    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
+  "value"
+  ] <- 
+  tissue.data[
+  tissue.data$Tissue == "liver" &
+    tissue.data$Species == "Rat" &
+    tissue.data$variable == "Flow (mL/min/kg^(3/4))",
+  "value"
+  ] + new_hepblfl_increment
+```
+
+```{r}
+# Next we need to re-parameterize the chemicals...
+# I only need to do this under the assumption of restrictive clearance.
+# The test is that under this assumption these chemicals should NOT be sensitive
+# to the changes in hepatic blood flow.
+
+rpr_sparams_rest <- tryCatch(
+  expr = {
+    sapply(
+      target_chems_rat,
+      \(x) {
+        httk::parameterize_3comp2(
+          dtxsid = x,
+          species = "Rat",
+          restrictive.clearance = TRUE,
+          default.to.human = FALSE,
+          force.human.clint.fup = FALSE,
+          suppress.messages = TRUE
+        )
+      },
+      simplify = FALSE,
+      USE.NAMES = TRUE
+    )
+  }, error = function(msg) {
+    message("Not possible to parameterize_3comp2 for all dtxsid ",
+            "try to use default.to.human = TRUE.")
+  }
+)
+# For these same chemicals, I also want to test sensitivity
+# when parameterized as human for fup and Clint
+rph_sparams_rest <- tryCatch(
+  expr = {
+    sapply(
+      target_chems_rat,
+      \(x) {
+        httk::parameterize_3comp2(
+          dtxsid = x,
+          species = "Rat",
+          restrictive.clearance = TRUE,
+          default.to.human = TRUE,
+          force.human.clint.fup = TRUE,
+          suppress.messages = TRUE
+        )
+      },
+      simplify = FALSE,
+      USE.NAMES = TRUE
+    )
+  }, error = function(msg) {
+    message("Not possible to parameterize_3comp2 for all dtxsid ",
+            "try to use default.to.human = TRUE.")
+  }
+)
+
+# Copied from RC_comparison_bkgd.R
+css_httk_batch <- function(param_list,
+                           restrictive = TRUE) {
+  stopifnot(is.logical(restrictive))
+
+  css_list_r <- vapply(
+    param_list,
+    \(x) {
+      calc_analytic_css_3comp2(parameters = x,
+                               restrictive.clearance = restrictive)
+    },
+    FUN.VALUE = numeric(1L)
+  )
+  css_list_names <- names(param_list)
+
+  css_df <- data.frame(Chemical = css_list_names,
+                       Css_httk_r.1p = css_list_r)
+  return(css_df)
+}
+
+rpr_css_sensitivity <- css_httk_batch(rpr_sparams_rest)
+rph_css_sensitivity <- css_httk_batch(rph_sparams_rest)
+
+rpr_cltot_sensitivity <- data.frame(
+      Chemical = names(rpr_sparams_rest),
+      CLtot_restrictive.1p = vapply(
+        rpr_sparams_rest,
+        \(x) {
+          httk::calc_total_clearance(
+            parameters = x,
+            species = "Rat",
+            model = "3compartment2",
+            suppress.messages = TRUE,
+            restrictive.clearance = TRUE
+          )
+        },
+        FUN.VALUE = double(1)
+      ),
+      halflife_restrictive.1p = vapply(
+        rpr_sparams_rest,
+        \(x) {
+          httk::calc_half_life(
+            parameters = x,
+            species = "Rat",
+            model = "3compartment2",
+            suppress.messages = TRUE,
+            restrictive.clearance = TRUE
+          )
+        },
+        FUN.VALUE = double(1)
+      )
+)
+
+rph_cltot_sensitivity <- data.frame(
+      Chemical = names(rph_sparams_rest),
+      CLtot_restrictive.1p = vapply(
+        rph_sparams_rest,
+        \(x) {
+          httk::calc_total_clearance(
+            parameters = x,
+            species = "Rat",
+            model = "3compartment2",
+            suppress.messages = TRUE,
+            restrictive.clearance = TRUE
+          )
+        },
+        FUN.VALUE = double(1)
+      ),
+      halflife_restrictive.1p = vapply(
+        rph_sparams_rest,
+        \(x) {
+          httk::calc_half_life(
+            parameters = x,
+            species = "Rat",
+            model = "3compartment2",
+            suppress.messages = TRUE,
+            restrictive.clearance = TRUE
+          )
+        },
+        FUN.VALUE = double(1)
+      )
+)
+
+rpr_sensitivity <- merge(rpr_cltot_sensitivity,
+                         rpr_css_sensitivity)
+
+rph_sensitivity <- merge(rph_cltot_sensitivity,
+                         rph_css_sensitivity)
+
+rpr_sensitivity <- rpr_sensitivity %>%
+  merge(rpr_httk_clearance_df) %>%
+  mutate(
+    nsc_css = ((Css_httk_r.1p - 
+                  Css_httk_r)/Css_httk_r)/drr,
+    nsc_cltot = ((CLtot_restrictive.1p -
+                    CLtot_restrictive)/CLtot_restrictive)/drr,
+    nsc_halflife = ((halflife_restrictive.1p -
+                       halflife_restrictive)/halflife_restrictive)/drr
+  ) %>%
+  select(Chemical, Species, starts_with("nsc_"))
+
+rph_sensitivity <- rph_sensitivity %>%
+  merge(rpr_httk_clearance_df) %>%
+  mutate(
+    nsc_css = ((Css_httk_r.1p - 
+                  Css_httk_r)/Css_httk_r)/drr,
+    nsc_cltot = ((CLtot_restrictive.1p -
+                    CLtot_restrictive)/CLtot_restrictive)/drr,
+    nsc_halflife = ((halflife_restrictive.1p -
+                       halflife_restrictive)/halflife_restrictive)/drr
+  ) %>%
+  select(Chemical, Species, starts_with("nsc_"))
+
+rpr_sensitivity %>%
+  mutate(across(starts_with("nsc_"),
+                \(x) {
+                  factor(
+                    case_when(
+                      abs(x) < 0.2 ~ 'Low',
+                      between(abs(x), 0.2, 0.5) ~ 'Medium',
+                      abs(x) > 0.5 ~ 'High'
+                    ), levels = c('High', 'Medium', 'Low')
+                  )
+                })) %>% 
+  count(nsc_css, nsc_cltot, nsc_halflife)
+
+addmargins(clearance_contingency_tbl)
+
+rph_sense_tables <- rph_sensitivity %>%
+  mutate(across(starts_with("nsc_"),
+                \(x) {
+                  factor(
+                    case_when(
+                      abs(x) < 0.2 ~ 'Low',
+                      between(abs(x), 0.2, 0.5) ~ 'Medium',
+                      abs(x) > 0.5 ~ 'High'
+                    ), levels = c('High', 'Medium', 'Low')
+                  )
+                })) %>%
+  rename_with(\(x) {paste0(x, "_h")}, .cols = starts_with("nsc_"))
+
+rpr_sense_tables <- rpr_sensitivity %>%
+  mutate(across(starts_with("nsc_"),
+                \(x) {
+                  factor(
+                    case_when(
+                      abs(x) < 0.2 ~ 'Low',
+                      between(abs(x), 0.2, 0.5) ~ 'Medium',
+                      abs(x) > 0.5 ~ 'High'
+                    ), levels = c('High', 'Medium', 'Low')
+                  )
+                })) %>% 
+  left_join(combo_pretable) %>% 
+  arrange(nsc_css, nsc_cltot, nsc_halflife) %>%
+  relocate(rat_cl, human_cl, .after = Species) %>%
+  mutate(
+    cl = paste0("Rat:", rat_cl, "/Human:", human_cl),
+  .keep = "unused", .after = Species) %>%
+  left_join(rph_sense_tables) %>%
+  left_join(fup_rh)
+
+with(rpr_sense_tables,
+     table(cl, nsc_halflife))
+
+rpr_sense_tables %>%
+  mutate(Rat_ambi = str_detect(cl, "Rat:Ambi")) %>%
+  filter(!is.na(nsc_css)) %>%
+  ggplot(aes(x = Clint_human, 
+             y = Clint_rat, 
+             color=cl)) +
+  geom_point(alpha = 0.7, aes(shape = Rat_ambi)) +
+  scale_shape_manual(values = c(16,21)) +
+  scale_color_manual(
+    values = c(
+      "#d6604d", "red2", "#b2182b",
+      "#fdb863", "#e08214", "#b35806",
+      "#b2abd2", "#8073ac", "#542788")
+  ) +
+  labs(x = "Human", y = "Rat",
+       title = "CL<sub>int</sub>",
+       color = "Clearance Determination\nby Hepatic Extraction",
+       shape = "Rat Clearance\ndetermined Ambiguous?") +
+  facet_grid(rows = vars(nsc_halflife),
+             scales = "free",
+             space = "free_x") +
+  geom_abline(slope = 1, color = "grey20") +
+  theme_bw() +
+  theme(plot.title = ggtext::element_markdown(hjust = 0.5))
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "Rat_Human_Clint_Clearance_by_extractionRatio.png"),
+       height = 7, width = 8,
+       bg = "white")
+
+```
+
+Unfortunately, it seems that the sensitivity for Css, CLtot, and halflife
+when parameterized with human fup and CLint values is quite high,
+meaning they don't provide as much information as other metrics.
 

### 2025-04-11 data-raw/pulling_oral_iv_data_cvtdb.Rmd

--- 2025-01-10 data-raw/pulling_oral_iv_data_cvtdb.Rmd
@@
   print(table(.data$curation_set_tag))
+}
+
+```
+
+```{r diff_log_function}
+# Now I want to write a quick function that will log relevant changes
+# from previous 'cvt' objects
+devtools::load_all() # So this loads the previous cvt object
+diff_log_cvt <- function(new_cvt,
+                         key_id = "conc_time_id",
+                         grp_ids = c("analyte_dtxsid",
+                                     "species"),
+                         notes = character(0L)) {
+  stopifnot(
+    key_id %in% colnames(cvt),
+    key_id %in% colnames(new_cvt),
+    all(grp_ids %in% colnames(cvt)),
+    all(grp_ids %in% colnames(new_cvt))
+  )
+  if (length(unique(new_cvt[[key_id]])) != NROW(new_cvt)) {
+    stop("key_id is not not a column that uniquely identifies this data.")
+  }
+
+  # Prepare some vectors:
+  grp_strings_new <- unique(do.call("paste", new_cvt[grp_ids]))
+  grp_strings_old <- unique(do.call("paste", cvt[grp_ids]))
+
+  msg_to_write <- paste0("\n\n======== ", round(Sys.time()))
+
+  if (identical(new_cvt, cvt)) {
+    msg_to_write <- paste(msg_to_write, "No changes.", sep = "\t")
+    message("There are no changes from previous `cvt` data.frame, ",
+            "are you sure you want to save this?")
+  } else {
+    msg_to_write <- paste(msg_to_write, "Changes detected.", sep = "\t")
+
+    ###---- Check key_id changes (usually conc_time_id)
+    diff_row_add <- setdiff(new_cvt[[key_id]], cvt[[key_id]])
+    diff_row_sub <- setdiff(cvt[[key_id]], new_cvt[[key_id]])
+    diff_row_common <- intersect(cvt[[key_id]], new_cvt[[key_id]])
+    # Nature of data changes:
+    added_grps <- unique(
+      do.call("paste",
+              new_cvt[which(new_cvt[[key_id]] %in% diff_row_add), grp_ids]
+              )
+      )
+    removed_grps <- unique(
+      do.call("paste",
+              cvt[which(cvt[[key_id]] %in% diff_row_sub), grp_ids]
+              )
+      )
+
+    added_new_grps <- setdiff(added_grps, grp_strings_old)
+    added_existing_grps <- intersect(added_grps, grp_strings_old)
+    removed_new_grps <- setdiff(removed_grps, grp_strings_new)
+    removed_existing_grps <- intersect(removed_grps, grp_strings_new)
+
+    msg_to_write <- c(
+      msg_to_write,
+      paste("Rows added:", length(diff_row_add)),
+      paste("Rows removed:", length(diff_row_sub))
+    )
+
+    limit_grp_output <- function(grp_vector) {
+      if (length(grp_vector) > 0) {
+        if (length(grp_vector) > 6) {
+          grp_vector <- c(grp_vector[c(1,2)],
+                              paste0("... [",
+                                     length(grp_vector) - 3,
+                                     "] more!"),
+                              grp_vector[c(length(grp_vector) - 1)]
+          )
+        }
+      return(grp_vector)
+    }
+      msg_to_write <- c(msg_to_write,
+                        "New Groups added (not in previous data):",
+                        paste0("\t", limit_grp_output(added_new_grps)),
+                        "Groups with new observations (group present in previous data)",
+                        paste0("\t", limit_grp_output(added_existing_grps)),
+                        "Groups removed that no longer have data present:",
+                        paste0("\t", limit_grp_output(removed_new_grps)),
+                        "Groups removed that still have some data present:",
+                        paste0("\t", limit_grp_output(removed_existing_grps)),
+                        "-----------------------------------"
+                        )
+    }
+
+    ### -----Checking columns
+    diff_col_add <- setdiff(names(new_cvt), names(cvt)) # Columns added in new_cvt
+    diff_col_sub <- setdiff(names(cvt), names(new_cvt)) # Columns removed in new_cvt
+    diff_col_common <- intersect(names(cvt), names(new_cvt))
+    common_row_cvt <- cvt[cvt[[key_id]] %in% diff_row_common, ]
+
+    common_row_cvt <- common_row_cvt[order(common_row_cvt[[key_id]]), ]
+
+    common_row_new <- new_cvt[new_cvt[[key_id]] %in% diff_row_common, ]
+    common_row_new <- common_row_new[order(common_row_new[[key_id]]), ]
+
+    if (length(c(diff_col_add, diff_col_sub)) == 0) {
+      msg_to_write <- c(msg_to_write,
+                        "No changes in column names.")
+    } else if (length(diff_col_add) > 0 && length(diff_col_sub) > 0) {
+      # Check renaming
+
+      diff_columns <- function(x, y) {
+        out_list <- character()
+        for (ix in names(x)) {
+          for (iy in names(y)) {
+            if (identical(x[[c(key_id,ix)]], y[[c(key_id, iy)]])) {
+              out_list <- c(out_list, paste0(ix, " -> ", iy))
+            }
+          }
+        }
+        return(out_list)
+      }
+
+      renamed_cols <- diff_columns(common_row_cvt[diff_col_sub],
+                                   common_row_new[diff_col_add])
+      if (length(renamed_cols) > 0) {
+        msg_to_write <- c(msg_to_write,
+                          "Renamed columns (non-exhaustive):",
+                          renamed_cols)
+      } else {
+        msg_to_write <- c(msg_to_write,
+                          "No renamed columns found.")
+      }
+    }
+    if (length(diff_col_add) > 0) {
+      msg_to_write <- c(msg_to_write,
+                        "--------------",
+                        "Columns added:",
+                        diff_col_add)
+    }
+    if (length(diff_col_sub) > 0) {
+      msg_to_write <- c(msg_to_write,
+                        "______________",
+                        "Columns removed (from previous data):",
+                        diff_col_sub)
+    }
+
+    if ((NROW(
+      setdiff(
+        common_row_cvt[diff_col_common], common_row_new[diff_col_common]
+      )) > 0
+    ) ||  (NROW(
+      setdiff(
+        common_row_new[diff_col_common], common_row_cvt[diff_col_common]
+      )) > 0
+    )) {
+      msg_to_write <- c(msg_to_write,
+                        "Data for same observation key_ids have changed.")
+
+      # Which columns have different data?
+      test_cols <- setdiff(diff_col_common, key_id)
+      for (i in test_cols) {
+        this_diff <- setdiff(common_row_new[c(key_id, i)],
+                             common_row_cvt[c(key_id, i)])
+        that_diff <- setdiff(common_row_cvt[c(key_id, i)],
+                             common_row_new[c(key_id, i)])
+
+        if (NROW(this_diff) > 0) {
+          msg_to_write <- c(
+            msg_to_write,
+            paste0(c(i, "had", NROW(this_diff), "differences."), collapse = " ")
+          )
+
+          this_grp <- dplyr::distinct(common_row_new[
+            common_row_new[[key_id]] %in% this_diff[[key_id]],
+            grp_ids
+          ])
+          this_grp <- paste0(this_grp[1,1:2], collapse = " ")
+
+          # Print the differences (if below a certain number of rows)
+          msg_to_write <- c(
+            msg_to_write,
+            paste0(
+              "Example:",
+              paste(this_grp, collapse = " "),
+              collapse = " "
+            ),
+            paste0(c(i, "\t new:", this_diff[1,2], "<--\t old:", that_diff[1,2]),
+                   collapse = " "), "\n"
+          )
+        }
+      }
+    }
+    msg_to_write <- c(msg_to_write,
+                      notes,
+                      "================================\n")
+  }
+  return(cat(msg_to_write, sep = "\n"))
 }
@@
                        "Data where the analyzed chemicals and dosed chemicals are different"))
+diff_log_cvt(cvt_df)
 ```
@@
 
+# Filtering out entries with no concentration information available
 cvt_df <- cvt_df %>%
@@
 
+cvt_df <- cvt_df %>%
+  mutate(invivPK_dose_level = dose_level_normalized,
+         invivPK_loq = loq,
+         invivPK_loq_units = loq_units,
+         invivPK_conc_sd = conc_sd,
+         invivPK_conc = conc)
+diff_log_cvt(cvt_df)
+
 # Checking other_study_identifier == S0916
@@
   paste("For study 1713 and 1714, tamoxifen was administered at 5mL/kg, ",
-        "meaning these doses are 5/1000th of current value to convert ug/mL -> mg/kg.")
-))
+        "meaning these doses are 5/1000th of current value to convert ug/mL -> mg/kg."
+),
+ "This entry has since been removed from CvT as of April 2025"
+)
+)
+
 # In CEBS "S0916" the Dose is 300,100 ug/mL with 5mL/kg administered by gavage (the only data left)
 # Making it 5/1000 mg/kg x either doses in study_ids 1714,1713 (the latter was filtered out prior to this)
-cvt_df <- cvt_df %>%
-  mutate(
-    invivPK_dose_level = if_else(
-      fk_study_id %in% c("1714", "1713"),
-      5/1000 * dose_level_normalized,
-      dose_level_normalized
-    )
-  )
+# cvt_df <- cvt_df %>%
+#   mutate(
+#     invivPK_dose_level = if_else(
+#       fk_study_id %in% c("1714", "1713"),
+#       5/1000 * dose_level_normalized,
+#       dose_level_normalized
+#     )
+#   )
 
@@
   "Adjusting LOQ values for L-ephedrine to 3.39 as stated in CEBS study S0976.",
-  "Set LOQ units to ng/mL as detailed in the same CEBS study"
+  "Set LOQ units to ng/mL as detailed in the same CEBS study.",
+  "Caffeine and Pseudoephedine have been removed as of April 2025."
 ))
@@
     case_when(
-      analyte_name_original %in% "caffeine" ~ 4.00,
+      # analyte_name_original %in% "caffeine" ~ 4.00,
       analyte_name_original %in% "l-ephedrine" ~ 3.39,
-      analyte_name_original %in% "pseudoephedrine" ~ 4.43
+      # analyte_name_original %in% "pseudoephedrine" ~ 4.43
     ),
@@
   "Looked at ELOQ in CEBS study S0328 and found it to be around 1",
-  "This only is relevant for {.code study_id} 1779"
+  "This only is relevant for {.code study_id} 1779.",
+  "This record is no longer present as of April 2025."
 ))
 
-cvt_df <- cvt_df %>%
-  mutate(
-  invivPK_loq = if_else(
-    fk_study_id %in% "1779",
-    1, invivPK_loq),
-  invivPK_loq_units = if_else(
-    other_study_identifier %in% "S0328",
-    "ug/mL",
-    invivPK_loq_units
-  ))
+# cvt_df <- cvt_df %>%
+#   mutate(
+#   invivPK_loq = if_else(
+#     fk_study_id %in% "1779",
+#     1, invivPK_loq),
+#   invivPK_loq_units = if_else(
+#     other_study_identifier %in% "S0328",
+#     "ug/mL",
+#     invivPK_loq_units
+#   ))
 
 # quick_stats(cvt_df)
-
+diff_log_cvt(cvt_df)
 ```
@@
 table(cvt_df$invivPK_loq_units)
+diff_log_cvt(cvt_df)
 
@@
 # most current near future pull in the new year
+# This will include some zero values, but should work itself out during preprocessing
 cvt_df <- cvt_df %>%
-  filter(invivPK_conc > 0)
+  filter(invivPK_conc >= 0)
 
@@
 quick_stats(cvt_df)
+diff_log_cvt(cvt_df, 
+             notes = "Relaxed conc > 0 filter to conc >= 0.")
+
 ```
@@
 
-```{r diff_log_function}
-# Now I want to write a quick function that will log relevant changes
-# from previous 'cvt' objects
-devtools::load_all() # So this loads the previous cvt object
-diff_log_cvt <- function(new_cvt,
-                         key_id = "conc_time_id",
-                         grp_ids = c("analyte_dtxsid",
-                                     "species")) {
-  stopifnot(
-    key_id %in% colnames(cvt),
-    key_id %in% colnames(new_cvt),
-    all(grp_ids %in% colnames(cvt)),
-    all(grp_ids %in% colnames(new_cvt))
-  )
-  if (length(unique(new_cvt[[key_id]])) != NROW(new_cvt)) {
-    stop("key_id is not not a column that uniquely identifies this data.")
-  }
-
-  # Prepare some vectors:
-  grp_strings_new <- unique(do.call("paste", new_cvt[grp_ids]))
-  grp_strings_old <- unique(do.call("paste", cvt[grp_ids]))
-
-  msg_to_write <- paste0("\n\n======== ", round(Sys.time()))
-
-  if (identical(new_cvt, cvt)) {
-    msg_to_write <- paste(msg_to_write, "No changes.", sep = "\t")
-    message("There are no changes from previous `cvt` data.frame, ",
-            "are you sure you want to save this?")
-  } else {
-    msg_to_write <- paste(msg_to_write, "Changes detected.", sep = "\t")
-
-    ###---- Check key_id changes (usually conc_time_id)
-    diff_row_add <- setdiff(new_cvt[[key_id]], cvt[[key_id]])
-    diff_row_sub <- setdiff(cvt[[key_id]], new_cvt[[key_id]])
-    diff_row_common <- intersect(cvt[[key_id]], new_cvt[[key_id]])
-    # Nature of data changes:
-    added_grps <- unique(
-      do.call("paste",
-              new_cvt[which(new_cvt[[key_id]] %in% diff_row_add), grp_ids]
-              )
-      )
-    removed_grps <- unique(
-      do.call("paste",
-              cvt[which(cvt[[key_id]] %in% diff_row_sub), grp_ids]
-              )
-      )
-
-    added_new_grps <- setdiff(added_grps, grp_strings_old)
-    added_existing_grps <- intersect(added_grps, grp_strings_old)
-    removed_new_grps <- setdiff(removed_grps, grp_strings_new)
-    removed_existing_grps <- intersect(removed_grps, grp_strings_new)
-
-    msg_to_write <- c(
-      msg_to_write,
-      paste("Rows added:", length(diff_row_add)),
-      paste("Rows removed:", length(diff_row_sub))
-    )
-
-    limit_grp_output <- function(grp_vector) {
-      if (length(grp_vector) > 0) {
-        if (length(grp_vector) > 6) {
-          grp_vector <- c(grp_vector[c(1,2)],
-                              paste0("... [",
-                                     length(grp_vector) - 3,
-                                     "] more!"),
-                              grp_vector[c(length(grp_vector) - 1)]
-          )
-        }
-      return(grp_vector)
-    }
-      msg_to_write <- c(msg_to_write,
-                        "New Groups added (not in previous data):",
-                        paste0("\t", limit_grp_output(added_new_grps)),
-                        "Groups with new observations (group present in previous data)",
-                        paste0("\t", limit_grp_output(added_existing_grps)),
-                        "Groups removed that no longer have data present:",
-                        paste0("\t", limit_grp_output(removed_new_grps)),
-                        "Groups removed that still have some data present:",
-                        paste0("\t", limit_grp_output(removed_existing_grps)),
-                        "-----------------------------------"
-                        )
-    }
-
-    ### -----Checking columns
-    diff_col_add <- setdiff(names(new_cvt), names(cvt)) # Columns added in new_cvt
-    diff_col_sub <- setdiff(names(cvt), names(new_cvt)) # Columns removed in new_cvt
-    diff_col_common <- intersect(names(cvt), names(new_cvt))
-
-    # Left off here TODO
-    if (length(c(diff_col_add, diff_col_sub)) == 0) {
-      msg_to_write <- c(msg_to_write,
-                        "No changes in column names.")
-    } else if (length(diff_col_add) > 0 && length(diff_col_sub) > 0) {
-      # Check renaming
-      common_row_cvt <- cvt[diff_row_common, ]
-      common_row_new <- new_cvt[diff_row_common, ]
-
-      diff_columns <- function(x, y) {
-        out_list <- character()
-        for (ix in names(x)) {
-          for (iy in names(y)) {
-            if (identical(x[[c(key_id,ix)]], y[[c(key_id, iy)]])) {
-              out_list <- c(out_list, paste0(ix, " -> ", iy))
-            }
-          }
-        }
-        return(out_list)
-      }
-
-      renamed_cols <- diff_columns(common_row_cvt[diff_col_sub],
-                                   common_row_new[diff_col_add])
-      if (length(renamed_cols) > 0) {
-        msg_to_write <- c(msg_to_write,
-                          "Renamed columns (non-exhaustive):",
-                          renamed_cols)
-      } else {
-        msg_to_write <- c(msg_to_write,
-                          "No renamed columns found.")
-      }
-    }
-    if (length(diff_col_add) > 0) {
-      msg_to_write <- c(msg_to_write,
-                        "--------------",
-                        "Columns added:",
-                        diff_col_add)
-    }
-    if (length(diff_col_sub) > 0) {
-      msg_to_write <- c(msg_to_write,
-                        "______________",
-                        "Columns removed (from previous data):",
-                        diff_col_sub)
-    }
-
-    if (!identical(common_row_cvt[diff_col_common],
-                   common_row_new[diff_col_common])) {
-      msg_to_write <- c(msg_to_write,
-                        "Data for same observation key_ids have changed.")
-    }
-    msg_to_write <- c(msg_to_write,
-                      "================================\n")
-  }
-  return(cat(msg_to_write, sep = "\n"))
-}
-```
-
 Save the pulled CVT data with the edits/normalizations, and also save the current date.
@@
 cvt_date <- Sys.Date()
+cat(diff_log_cvt(cvt_df,
+                 notes = "Relaxed conc > 0 filter to conc >= 0."),
+    file = "data-raw/cvt_changelog.txt",
+    append = TRUE)
+
 cvt <- cvt_df
@@
 save(cvt_date, file = "data/cvt_date.rda")
+
 ```

### 2025-04-17 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Secondary update to cvt object and related files.

@@
         out_list <- character()
-        for (ix in names(x)) {
-          for (iy in names(y)) {
-            if (identical(x[[c(key_id,ix)]], y[[c(key_id, iy)]])) {
+        for (ix in setdiff(names(x), key_id)) {
+          for (iy in setdiff(names(y), key_id)) {
+            tmp <- merge(x[c(key_id,ix)], y[c(key_id, iy)], by=key_id)
+            if (identical(tmp[[2]], tmp[[3]])) {
               out_list <- c(out_list, paste0(ix, " -> ", iy))
@@
 
-      renamed_cols <- diff_columns(common_row_cvt[diff_col_sub],
-                                   common_row_new[diff_col_add])
+      renamed_cols <- diff_columns(common_row_cvt[c(key_id,diff_col_sub)],
+                                   common_row_new[c(key_id, diff_col_add)])
       if (length(renamed_cols) > 0) {
@@
 
+# Unfortunately, there are some "fancy" or curly quotes that need to be replaced
+# with "straight" quotes to be more machine read-able
+force_straight_quotes <- function(x) {
+  temp <- gsub("(’|′)", "'", x)
+  temp <- gsub("(, | ,)", ",", temp)
+  return(temp)
+}
+force_straight_quotes("3,3’,4,4’-tetrachloro-5-biphenylol")
+
 # Harmonize values for easier analysis
@@
     sex = tolower(sex),
-    analyte_name_original = tolower(analyte_name_original),
+    analyte_name_original = force_straight_quotes(tolower(analyte_name_original)),
+    analyte_name_secondary_original = force_straight_quotes(tolower(
+      analyte_name_secondary_original
+      )),
     dose_volume_units = stringr::str_extract(dose_volume,
@@
                                 pattern = "^\\d")),
-    radiolabeled = ifelse(radiolabeled == 1, TRUE, FALSE),
+    radiolabeled = ifelse(is.na(radiolabeled), FALSE, as.logical(radiolabeled)),
     n_subjects_normalized = ifelse(n_subjects_in_series %in% "NR", NA_real_,
@@
 # There are some missing DTXSIDs that we need to fix
-# cvt_df %>%
-#   distinct(analyte_dtxsid, analyte_name_original, fk_analyzed_chemical_id) %>%
-#   filter(is.na(analyte_dtxsid)) %>% nrow()
+cvt_df %>% 
+    filter(is.na(analyte_dtxsid),
+           !(radiolabeled %in% TRUE)) %>%
+  distinct(fk_analyzed_chemical_id,fk_dosed_chemical_id,
+           analyte_dtxsid, analyte_name_original,
+           analyte_name_secondary_original) %>%
+  View("NA_dtxsid")
 
@@
 
-dq_cols <- dtxsid_query %>%
-  select("analyte_dtxsid2" = "dsstox_substance_id",
-         "fk_analyzed_chemical_id" = "id",
-         "analyte_name_original" = "chemical_name_original") %>%
-  mutate(analyte_name_original =  tolower(analyte_name_original)) %>%
+dtxsid_query <- dtxsid_query %>%
+  filter(id %in% as.numeric(
+    union(cvt_df$fk_analyzed_chemical_id, cvt_df$fk_dosed_chemical_id))
+  ) %>%
+  mutate(id = as.character(id),
+         chemical_name_original = force_straight_quotes(tolower(
+           chemical_name_original
+         )),
+         chemical_name_secondary_original = force_straight_quotes(tolower(
+           chemical_name_secondary_original
+         ))
+  )
+
+cvt_df %>% 
+  filter(fk_analyzed_chemical_id != fk_dosed_chemical_id,
+         !(radiolabeled %in% TRUE)) %>%
+  distinct(fk_analyzed_chemical_id,fk_dosed_chemical_id,fk_test_chemical_id) %>%
+  left_join(dtxsid_query %>%
+              select("fk_analyzed_chemical_id" = "id",
+                     "analyzed_chemical_name" = "chemical_name_original")) %>%
+  left_join(dtxsid_query %>%
+              select("fk_dosed_chemical_id" = "id",
+                     "dosed_chemical_name" = "chemical_name_original")) %>%
+  View("errors")
+
+# Rather than hope most of these chemicals have dtxsids within CvTdb,
+# I cross-referenced it with the CompTox database batch search.
+dtxsid_batch_idless <- readr::read_csv(
+  "data-raw/CCD-Batch-Search_2025-04-17_DTXSIDless.csv",
+  na = "N/A"
+) %>% filter(!is.na(DTXSID)) %>%
+  select("dsstox_substance_id" = "DTXSID",
+         "chemical_name_original" = "INPUT") %>%
   distinct()
 
-dq_cols <- dq_cols %>% distinct(analyte_dtxsid2, analyte_name_original) %>%
-  group_by(analyte_name_original) %>%
-  summarize(analyte_dtxsid2 = if_else(any(complete.cases(analyte_dtxsid2)),
-                                      first(analyte_dtxsid2[!is.na(analyte_dtxsid2)]),
-                                      NA)) %>%
-  left_join(dq_cols %>% select(-analyte_dtxsid2),
-            join_by(analyte_name_original)) %>%
-  mutate(fk_analyzed_chemical_id = as.character(fk_analyzed_chemical_id))
+quick_message(c(
+  "Erroneous DTXSID assignments (identified via duplication):",
+  "perfluorohexanesulfonate == DTXSID80873012",
+  "tacrolimus == DTXSID5046354",
+  "hippuric acid == DTXSID9046073"
+))
+
+dtxsid_batch_idless <- dtxsid_batch_idless %>%
+  mutate(dsstox_substance_id = case_when(
+    chemical_name_original == "perfluorohexanesulfonate" ~ "DTXSID80873012",
+    chemical_name_original == "tacrolimus" ~ "DTXSID5046354",
+    chemical_name_original == "hippuric acid" ~ "DTXSID9046073",
+    .default = dsstox_substance_id
+  )) %>% distinct()
+
+# Fixing the missing DTXSID to prevent premature filtering
+cvt_df <- cvt_df %>%
+  left_join(
+    dtxsid_batch_idless,
+    by = join_by(analyte_name_original == chemical_name_original)
+  ) %>%
+  mutate(analyte_dtxsid = coalesce(analyte_dtxsid, dsstox_substance_id)) %>%
+  select(!dsstox_substance_id)
+
+quick_stats(cvt_df)
+
+# Now we need to pre-emptively address the chemicals that have different
+# dosed_id and analyzed_ids but are actually the same chemical
+quick_message(c(
+  "The following have resolvable errors:",
+  "If dosed chemical id is 47, change this to 46 to match analyte id. tamoxifen, salt dosed.",
+  "If dosed chemical id is 893, change this to 929 to match analyte id. trichloroethylene, duplicate.",
+  "If dosed chemical id is 671, change to 672 to match analyte id. PFHS, salt dosed.",
+  "If dosed chemical id is 673, change to 675 to match analyte id. PFNA, capitalization.",
+  "If dosed chemical id is 674, change to 676 to match analyte id, PFDA, capitalization."
+))
+
+cvt_df <- cvt_df %>%
+  rowwise() %>%
+  mutate(fk_dosed_chemical_id = case_when(
+    fk_dosed_chemical_id == "47" &&
+      fk_analyzed_chemical_id == "46" ~ "46",
+    fk_dosed_chemical_id == "893" &&
+      fk_analyzed_chemical_id == "929" ~ "929",
+    fk_dosed_chemical_id == "671" &&
+      fk_analyzed_chemical_id == "672" ~ "672",
+    fk_dosed_chemical_id == "673" &&
+      fk_analyzed_chemical_id == "673" ~ "673",
+    fk_dosed_chemical_id == "674" &&
+      fk_analyzed_chemical_id == "676" ~ "676",
+    .default = fk_dosed_chemical_id
+  )) %>%
+  ungroup()
 
@@
 
-study_query <- query_db(query = "SELECT distinct * FROM studies",
-         schema = "cvt")
+# study_query <- query_db(query = "SELECT distinct * FROM studies",
+#          schema = "cvt")
 
-# Here we join to make sure all chemical ids are represented
-full_set <- cvt_df %>%
-  left_join(dq_cols, 
-            by = join_by("fk_analyzed_chemical_id", "analyte_name_original")) %>%
-  mutate(analyte_dtxsid = coalesce(analyte_dtxsid, analyte_dtxsid2)) %>%
-  select(-analyte_dtxsid2)
-
-cvt_df <- full_set
 quick_stats(cvt_df)
@@
 cvt_df <- cvt_df %>% mutate(conc_unit_norm_factor = signif(conc/conc_original, 1),
-                            .after = conc_units_normalized) %>%
+                            .after = conc_units_normalized)
+
+cat("Current # chemicals: ", length(unique(cvt_df$analyte_dtxsid)), "\n")
+cat("Number of chemicals where analyte_dtxsid is NA: ",
+    sum(is.na(unique(cvt_df[c("fk_analyzed_chemical_id",
+                               "analyte_dtxsid")])$analyte_dtxsid)),
+    "\n")
+
+cat("Number of radiolabelling experiments: ",
+    sum(distinct(cvt_df, analyte_dtxsid, radiolabeled) %>% pull(radiolabeled) %>%
+          {. %in% TRUE}
+        )
+    )
+distinct(cvt_df, analyte_dtxsid, analyte_name_original, radiolabeled) %>%
+  filter(radiolabeled %in% TRUE, !is.na(analyte_dtxsid))
+
+cat("Number of chemicals with non-matching ids ",
+    cvt_df %>%
+      filter(!is.na(analyte_dtxsid),
+             !(radiolabeled %in% TRUE),
+             fk_analyzed_chemical_id != fk_dosed_chemical_id) %>%
+      distinct(analyte_dtxsid) %>%
+      NROW()
+)
+
+cvt_df <- cvt_df %>%
   filter(!(radiolabeled %in% TRUE),
          !is.na(analyte_dtxsid),
-         fk_analyzed_chemical_id == fk_dosed_chemical_id)
+         (fk_analyzed_chemical_id == fk_dosed_chemical_id)) %>%
+  distinct()
 
@@
                        "Data where the analyzed chemicals and dosed chemicals are different"))
+quick_stats(cvt_df)
 diff_log_cvt(cvt_df)
@@
 ###
+quick_stats(cvt_df)
 ```
@@
 +  Convert original dose units for CEBS study _S0916_ to mg/kg.  
-+  ~~Convert original dose units for CEBS study _S0624_ to mg/kg.~~ Data got corrected in CEBS, trusting that.  
++  Convert original dose units for CEBS study _S0624_ to mg/kg. Data got corrected in CEBS, trusting that.  
 +  Input the LOQ for studies _S0976_.  
@@
                      "{.emph remain the same}"))
+
 cvt_df %>% filter(!(dose_level_units_original %in% equiv_mgkg),
@@
   "Set LOQ units to ng/mL as detailed in the same CEBS study.",
-  "Caffeine and Pseudoephedine have been removed as of April 2025."
+  "S0976 has been removed as of April 2025."
 ))
 # Here I create new columns for loq and loq_units b/c I have modified them.
-cvt_df <- cvt_df %>%
-  mutate(invivPK_loq = if_else(
-    other_study_identifier %in% "S0976",
-    case_when(
+# cvt_df <- cvt_df %>%
+#   mutate(invivPK_loq = if_else(
+#     other_study_identifier %in% "S0976",
+#     case_when(
 #       analyte_name_original %in% "caffeine" ~ 4.00,
-      analyte_name_original %in% "l-ephedrine" ~ 3.39,
+#       analyte_name_original %in% "l-ephedrine" ~ 3.39,
 #       analyte_name_original %in% "pseudoephedrine" ~ 4.43
-    ),
-    loq),
-    invivPK_loq_units = if_else(
-      other_study_identifier %in% "S0976",
-      "ng/mL",
-      loq_units
-    ))
+#     ),
+#     loq),
+#     invivPK_loq_units = if_else(
+#       other_study_identifier %in% "S0976",
+#       "ng/mL",
+#       loq_units
+#     ))
 
@@
 
-# quick_stats(cvt_df)
+quick_stats(cvt_df)
 diff_log_cvt(cvt_df)
@@
 diff_log_cvt(cvt_df)
+quick_stats(cvt_df)
 
@@
 cvt_df %>% count(analyte_dtxsid) %>% arrange(n) %>% head()
-
-quick_message(c(
-  "Filtering Data:",
-  "Removing DTXSID6038299 due to insufficient data",
-  "Removing all data points that still have recorded concentrations of zero"
-))
-cvt_df <- cvt_df %>%
-  dplyr::filter(!(analyte_dtxsid %in% "DTXSID6038299"))
+# This has been resolved now
+# quick_message(c(
+#   "Filtering Data:",
+#   "Removing DTXSID6038299 due to insufficient data",
+#   "Removing all data points that still have recorded concentrations of zero"
+# ))
+# cvt_df <- cvt_df %>%
+#   dplyr::filter(!(analyte_dtxsid %in% "DTXSID6038299"))
 
@@
 
-glimpse(cvt_df, width = 80)
+glimpse(cvt_df)
 quick_stats(cvt_df)
+
 diff_log_cvt(cvt_df, 
-             notes = "Relaxed conc > 0 filter to conc >= 0.")
+             notes = c("Used CompTox name - DTXSID matching to fill in NAs.",
+                       "Fixed names that used non-standard single quotes.")
+)
 
@@
 cat(diff_log_cvt(cvt_df, 
-                 notes = "Relaxed conc > 0 filter to conc >= 0."),
+             notes = c("Used CompTox name - DTXSID matching to fill in NAs.",
+                       "Fixed names that used non-standard single quotes.")
+),
     file = "data-raw/cvt_changelog.txt",

### 2025-05-06 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Updated CvTdb SQL query and helper function.

@@
                         gsub("FROM ", paste0("FROM ", schema, "."), .) %>%
-                        gsub("JOIN ", paste0("JOIN ", schema, "."), .))),
+                        gsub("JOIN (?=\\w)", paste0("JOIN ", schema, "."), ., perl = TRUE))),
   error = function(cond){ 
@@
   "SELECT distinct ",
-  "a.id, a.time_original,  a.time_hr, a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
-  #
-  "a.fk_series_id, b.analyte_name_original, b.analyte_dtxsid, b.analyte_casrn, ",
-  "b.fk_analyzed_chemical_id, b.fk_test_chemical_id, ",
-  "b.test_substance_dtxsid, b.analyte_name_secondary_original, ",
-  "b.conc_medium_normalized, b.conc_medium_original, b.time_units_original, b.conc_units_original, ",
-  "b.conc_units_normalized, b.loq, b.loq_units, b.n_subjects_in_series, b.radiolabeled, ",
-  #
-  "b.fk_study_id, c.administration_route_normalized, c.fk_dosed_chemical_id, ",
+  # Conc_Time_Values table fields
+  "a.id, a.fk_series_id, a.time_original, a.time_hr, ",
+  "a.conc_original, a.conc_sd_original, a.conc, a.conc_sd, ",
+
+  # Series table fields
+  "b.fk_analyzed_chemical_id, ",
+  ## Chemical dictionary fields (analyzed chemical information)
+  "l.analyzed_chem_dtxsid, l.analyzed_chem_name_original, ",
+  "l.analyzed_chem_casrn, l.analyzed_chem_name, ",
+
+  "b.time_units_original, b.conc_units_original, ",
+  "b.conc_units_normalized, b.loq, b.loq_units, ",
+  "b.n_subjects_in_series, b.radiolabeled, b.fk_study_id, ",
+
+  # Studies table fields
+  "c.fk_dosed_chemical_id, ",
+  ## Chemical dictionary fields (dosed chemical information)
+  "k.dosed_chem_dtxsid, k.dosed_chem_name_original, ",
+  "k.dosed_chem_casrn, k.dosed_chem_name, ",
+
   "c.dose_volume, c.dose_volume_units, c.dose_vehicle, ",
-  "c.dose_duration, c.dose_duration_units, c.dose_frequency, c.fasting_period, ",
+  "c.dose_duration, c.dose_duration_units, ",
+  ## dose_frequency dictionary fields
+  "j.dose_frequency_original, j.dose_frequency_normalized, ",
+  "c.fasting_period, ",
   "c.dose_level_normalized, c.dose_level_original, c.dose_level_units_original, ",
-  #
+  ## conc_medium dictionary fields
+  "i.conc_medium_original, i.conc_medium_normalized, ", 
+  ## administration_route dictionary fields
+  "h.administration_route_original, h.administration_route_normalized, ",
+  ## administration_method dictionary fields
+  "g.administration_method_original, g.administration_method_normalized, ",
+  ## administration_form dictionary fields
+  "f.administration_form_original, f.administration_form_normalized, ",
+
+  # Subjects table fields
   "b.fk_subject_id, d.weight_kg, d.species, d.sex, d.age, d.age_units, d.age_category, ",
-  #
+  # Documents table fields
   "c.fk_extraction_document_id, e.pmid, e.year, e.other_study_identifier, ",
@@
 
+  # Join to dictionary tables
+  "LEFT JOIN administration_form_dict f ON c.fk_administration_form_id = f.id ",
+  "LEFT JOIN administration_method_dict g ON c.fk_administration_method_id = g.id ",
+  "LEFT JOIN administration_route_dict h ON c.fk_administration_route_id = h.id ",
+  "LEFT JOIN conc_medium_dict i ON b.fk_conc_medium_id = i.id ",
+  "LEFT JOIN dose_frequency_dict j ON c.fk_dose_frequency_id = j.id ",
+
+  # Rename chemical fields for dosed vs. analyzed chemical record foreign keys
+  "LEFT JOIN (SELECT id, dsstox_substance_id as dosed_chem_dtxsid, ",
+  "chemical_name_original as dosed_chem_name_original, ", 
+  "dsstox_casrn as dosed_chem_casrn, preferred_name as dosed_chem_name ",
+  "FROM chemicals) as k ON c.fk_dosed_chemical_id = k.id ",
+  "LEFT JOIN (SELECT id, dsstox_substance_id as analyzed_chem_dtxsid, ",
+  "chemical_name_original as analyzed_chem_name_original, ",
+  "dsstox_casrn as analyzed_chem_casrn, preferred_name as analyzed_chem_name ",
+  "FROM chemicals) as l ON b.fk_analyzed_chemical_id = l.id ",
+
   # Filtering steps
-  "WHERE c.administration_route_normalized IN ('iv', 'oral') AND ",
-  "(b.conc_medium_normalized IN ('blood', 'plasma') OR ",
-  "b.conc_medium_original IN ('blood', 'plasma'))"
+  "WHERE h.administration_route_normalized IN ('iv', 'oral') AND ",
+  "(i.conc_medium_normalized IN ('blood', 'plasma', 'excreta') OR ",
+  "i.conc_medium_original IN ('blood', 'plasma', 'excreta'))"
 )

### 2025-05-20 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Updating data-raw with changes to vignettes and built-in model function arguments.

@@
 library(DBI)
+devtools::load_all() # So this loads the previous cvt object
 library(dplyr)
 library(tidyr)
+library(readr)
 ```
@@
                         gsub("FROM ", paste0("FROM ", schema, "."), .) %>%
-                        gsub("JOIN (?=\\w)", paste0("JOIN ", schema, "."), ., perl = TRUE))),
+                        gsub("JOIN (?=\\w)", paste0("JOIN ", schema, "."), ., 
+                             perl = TRUE))),
   error = function(cond){ 
@@
 
-quick_stats <- function(.data) {
+quick_stats <- function(.data, old_version = FALSE) {
   stopifnot(is.data.frame(.data))
+
   cli::cli_h2("Statistics on the current data")
@@
 
-  message(paste0("Number of unique studies: ",
-                 length(unique(.data$fk_study_id))))
-  message(paste0("Number of unique series: ",
-                 length(unique(.data$fk_series_id))))
-  message(paste0("Number of unique chemicals: ",
-                 length(unique(.data$analyte_dtxsid))))
-  message(paste0("Unique Dose units: ",
-                 toString(unique(.data$dose_level_units_original))))
-  message(paste0("Unique Concentration units: ", 
-                 toString(unique(.data$conc_units_original))))
+  message("Number of unique studies: ",
+          length(unique(.data$fk_study_id)))
+  message("Number of unique series: ",
+          length(unique(.data$fk_series_id)))
+
+  if (old_version) {
+    message("Number of unique chemicals: ",
+          length(unique(.data$analyte_dtxsid)),
+          "\n")
+    chem_by_medium <- .data[c("conc_medium_normalized", "analyte_dtxsid")] %>%
+      filter(!is.na(analyte_dtxsid)) %>%
+      distinct()
+    chem_by_curset <- .data[c("curation_set_tag", "analyte_dtxsid")] %>%
+      filter(!is.na(analyte_dtxsid)) %>%
+      distinct()
+  } else {
+    message("Number of unique chemicals: ",
+          length(unique(.data$analyzed_chem_dtxsid)),
+          "\n")
+    chem_by_medium <- .data[c("conc_medium_normalized", "analyzed_chem_dtxsid")] %>%
+      filter(!is.na(analyzed_chem_dtxsid)) %>%
+      distinct()
+    chem_by_curset <- .data[c("curation_set_tag", "analyzed_chem_dtxsid")] %>%
+      filter(!is.na(analyzed_chem_dtxsid)) %>%
+      distinct()
+  }
+
+  message("Unique Dose units: ",
+          toString(unique(.data$dose_level_units_original)),
+          "\n")
+  if (all(is.na(.data$conc_units_normalized))) {
+    message("Unique Concentration units: ", 
+            toString(unique(.data$conc_units_original)),
+            "\n")
+  } else {
+    message("Unique Concentration units: ", 
+            toString(unique(.data$conc_units_normalized)),
+            "\n")
+  }
   message("Data by unique route of administration:")
@@
   print(table(.data$curation_set_tag))
+  message("\n\nUnique chemicals per medium:")
+  print(table(chem_by_medium$conc_medium_normalized))
+  message("Unique chemicals per curation set:")
+  print(table(chem_by_curset$curation_set_tag))
 }
@@
 # from previous 'cvt' objects
-devtools::load_all() # So this loads the previous cvt object
 diff_log_cvt <- function(new_cvt,
                          key_id = "conc_time_id",
-                         grp_ids = c("analyte_dtxsid",
+                         grp_ids = c("analyzed_chem_dtxsid",
                                      "species"),
@@
 # Note that this uses an ALIAS for each table which is later specified in
-# the FROM and LEFT JOIN statments
+# the FROM and LEFT JOIN statements
+series_chems <- paste0(
+  "SELECT DISTINCT a.id, a.fk_analyzed_chemical_id, ",
+  "b.analyzed_chem_dtxsid, b.analyzed_chem_name_original, ",
+  "b.analyzed_chem_name_secondary_original, ",
+  "b.analyzed_chem_casrn, b.analyzed_chem_name, ",
+  "a.time_units_original, a.conc_units_original, ",
+  "a.conc_units_normalized, a.loq, a.loq_units, ",
+  "a.n_subjects_in_series, a.radiolabeled, a.fk_study_id, ",
+  "a.qc_notes, a.qc_status, a.qc_flags, c.conc_medium_normalized ",
+  "FROM series a ",
+  "LEFT JOIN (SELECT id, dsstox_substance_id as analyzed_chem_dtxsid, ",
+  "chemical_name_original as analyzed_chem_name_original, ",
+  "chemical_name_secondary_original as analyzed_chem_name_secondary_original, ",
+  "dsstox_casrn as analyzed_chem_casrn, preferred_name as analyzed_chem_name ",
+  "FROM chemicals) as b ON a.fk_analyzed_chemical_id = b.id ",
+  "LEFT JOIN conc_medium_dict as c ON a.fk_conc_medium_id = c.id"
+)
+
+study_docs <- paste0(
+  "SELECT a.id, a.fk_extraction_document_id, a.fk_dosed_chemical_id, ",
+  "b.pmid, b.doi, b.year, b.other_study_identifier, ",
+  "b.url, b.extracted, b.curation_set_tag ",
+  "FROM studies a ",
+  "LEFT JOIN documents b ON a.fk_extraction_document_id = b.id"
+)
+
+audit_query <- query_db(paste0("SELECT DISTINCT * FROM cvt_audit ",
+                               "WHERE fk_table_name IN ('documents', 'series', 'studies')"),
+                        "cvt")
+study_query <- query_db(study_docs, "cvt")
+series_query <- query_db(series_chems, "cvt")
+dtxsid_query <- query_db("SELECT DISTINCT * FROM chemicals", "cvt") %>%
+  mutate(
+    across(ends_with("id"), as.character),
+    across(contains("chemical_name"), \(x) {
+      tolower(force_ascii_quotes(x))
+    })
+  )
+
+# There are a lot of duplicate DTXSIDs
 query <- paste0(
@@
   ## administration_method dictionary fields
-  "g.administration_method_original, g.administration_method_normalized, ",
+  # "g.administration_method_original, g.administration_method_normalized, ",
   ## administration_form dictionary fields
-  "f.administration_form_original, f.administration_form_normalized, ",
+  # "f.administration_form_original, f.administration_form_normalized, ",
 
@@
 
-  # Join to dictionary tables
-  "LEFT JOIN administration_form_dict f ON c.fk_administration_form_id = f.id ",
-  "LEFT JOIN administration_method_dict g ON c.fk_administration_method_id = g.id ",
+  # # Join to dictionary tables
+  # "LEFT JOIN administration_form_dict f ON c.fk_administration_form_id = f.id ",
+  # "LEFT JOIN administration_method_dict g ON c.fk_administration_method_id = g.id ",
   "LEFT JOIN administration_route_dict h ON c.fk_administration_route_id = h.id ",
@@
   "chemical_name_original as dosed_chem_name_original, ", 
+  "chemical_name_secondary_original as dosed_chem_name_secondary_original, ",
   "dsstox_casrn as dosed_chem_casrn, preferred_name as dosed_chem_name ",
@@
   "chemical_name_original as analyzed_chem_name_original, ",
+  "chemical_name_secondary_original as analyzed_chem_name_secondary_original, ",
   "dsstox_casrn as analyzed_chem_casrn, preferred_name as analyzed_chem_name ",
@@
   "WHERE h.administration_route_normalized IN ('iv', 'oral') AND ",
-  "(i.conc_medium_normalized IN ('blood', 'plasma', 'excreta') OR ",
-  "i.conc_medium_original IN ('blood', 'plasma', 'excreta'))"
-)
-
-sql_query <- query_db(query = query,
-         schema = "cvt")
-
-# Need to change column names for this
-{
+  "(i.conc_medium_normalized IN ('blood', 'plasma') OR ",
+  "i.conc_medium_original IN ('blood', 'plasma')) AND ",
+  "(j.dose_frequency_normalized IN ('Once') OR e.curation_set_tag IN ('CVT_Showa'))"
+)
+
+sql_query <- query_db(query = query, schema = "cvt")
+
+# Need to change the column name for this
 names(sql_query)[1] <- "conc_time_id"
-}
-
-# Unfortunately, there are some "fancy" or curly quotes that need to be replaced
-# with "straight" quotes to be more machine read-able
-force_straight_quotes <- function(x) {
-  temp <- gsub("(’|′)", "'", x)
-  temp <- gsub("(, | ,)", ",", temp)
-  return(temp)
-}
-force_straight_quotes("3,3’,4,4’-tetrachloro-5-biphenylol")
+
+# cvtdb_original <- sql_query
+# save(cvtdb_original, file = "data/cvtdb_original.rda", compress = "bzip2")
+```
+
+```{r harmonizing}
+load("data/cvtdb_original.rda")
+sql_query <- cvtdb_original
+rm(cvtdb_original)
 
@@
     sex = tolower(sex),
-    analyte_name_original = force_straight_quotes(tolower(analyte_name_original)),
-    analyte_name_secondary_original = force_straight_quotes(tolower(
-      analyte_name_secondary_original
+    across(contains("chem_name"), \(x) {
+      tolower(force_ascii_quotes(x))
+    }),
+    dose_volume_units = ifelse(
+      dose_volume_units %in% c("NR", "ND"),
+      NA_character_,
+      gsub(" / ", "/", gsub("ml", "mL", dose_volume_units))
+      ),
+    dose_volume = signif(as.numeric(dose_volume), digits = 7),
+    dose_duration_units = trimws(dose_duration_units),
+    dose_duration = as.numeric(stringr::str_extract(dose_duration,
+                                pattern = "^\\d+")),
+    dose_frequency_normalized = "Once", # Showa is not annotated
+    radiolabeled = ifelse(is.na(radiolabeled), FALSE, as.logical(radiolabeled)),
+    # for n_subject ranges, take integer value of median 
+    # otherwise pull number or NA
+    n_subjects_normalized = case_when(
+      n_subjects_in_series %in% "NR" ~ NA_real_,
+      grepl("-", n_subjects_in_series) ~ floor(mean(
+        as.numeric(unlist(strsplit(n_subjects_in_series, split = "-"))),
+        na.rm = TRUE
         )),
-    dose_volume_units = stringr::str_extract(dose_volume,
-                                    pattern = "(?<=[:space:]).+"),
-    dose_volume = as.numeric(stringr::str_extract(dose_volume,
-                                         pattern = "^(\\d|\\.)*")),
-    dose_duration_units = stringr::str_extract(dose_duration,
-                                      pattern = "(?<=[space]).+"),
-    dose_duration = as.numeric(stringr::str_extract(dose_duration,
-                                pattern = "^\\d")),
-    radiolabeled = ifelse(is.na(radiolabeled), FALSE, as.logical(radiolabeled)),
-    n_subjects_normalized = ifelse(n_subjects_in_series %in% "NR", NA_real_,
-      as.numeric(stringr::str_extract(n_subjects_in_series,
-                                                 pattern = "\\d+")))
-  )
-
-cvt_df <- cvt_df %>%
-  mutate(conc_medium_normalized = ifelse(is.na(conc_medium_normalized),
-                                         conc_medium_original,
-                                         conc_medium_normalized))
-
-# There are some missing DTXSIDs that we need to fix
+      .default = as.numeric(
+        stringr::str_extract(n_subjects_in_series, pattern = "\\d+")
+        )
+      )
+  )
+
+```
+
+## Some data malformations
+
+There are some duplications in chemical entries such that not all unique chemical ids
+represent a unique DTXSID, but rather a unique original name entry.
+To fix this, when DTXSIDs for dosed and analyzed chemicals match, I will
+be setting `fk_dosed_chemical_id` to `fk_analyzed_chemical_id`.
+
+There is also some radiolabeling experiments that aren't described as such.
+We can use `stringr::str_detect(x,"(13|14)c")` to recode `radiolabeled = TRUE`
+for these.
+
+Then we should address the fact that the `invivoPKfit_2.0.0` version of the `cvt`
+object has 228 chemicals, while the recent query only has 145. This is a
+difference of 83.
+
+By hand, I can add back the DTXSIDs for about 15 chemicals. Some of these will
+be ChEMBLIDs actually.
+
+```{r malformed_data}
+# First quick check to see if any chemical_ids are NA
+any(is.na(cvt_df$fk_analyzed_chemical_id))
+any(is.na(cvt_df$fk_dosed_chemical_id))
+length(unique(cvt_df$analyzed_chem_dtxsid))
+
+cvt_df <- cvt_df %>%
+  rowwise() %>%
+  mutate(fk_dosed_chemical_id = ifelse(
+    identical(analyzed_chem_dtxsid, dosed_chem_dtxsid),
+    fk_analyzed_chemical_id,
+    fk_dosed_chemical_id
+  )) %>%
+  ungroup()
+
 cvt_df %>%
-    filter(is.na(analyte_dtxsid),
-           !(radiolabeled %in% TRUE)) %>%
-  distinct(fk_analyzed_chemical_id,fk_dosed_chemical_id,
-           analyte_dtxsid, analyte_name_original,
-           analyte_name_secondary_original) %>%
-  View("NA_dtxsid")
-
-dtxsid_query <- paste0(
-  "SELECT distinct * FROM chemicals"
-)
-
-dtxsid_query <- query_db(query = dtxsid_query,
-         schema = "cvt")
-
-dtxsid_query <- dtxsid_query %>%
-  filter(id %in% as.numeric(
-    union(cvt_df$fk_analyzed_chemical_id, cvt_df$fk_dosed_chemical_id))
+  distinct(analyzed_chem_name_original, dosed_chem_name_original, radiolabeled) %>%
+  filter(!radiolabeled) %>%
+  filter(stringr::str_detect(dosed_chem_name_original, "(13|14)c"))
+
+cvt_df <- cvt_df %>%
+  mutate(
+    radiolabeled = ifelse(
+      stringr::str_detect(dosed_chem_name_original, "(13|14)c"),
+      TRUE,
+      radiolabeled
+    )
+  )
+
+quick_stats(cvt_df)
+quick_stats(cvt_2.0.0, old_version = TRUE)
+# Note unique chemical counts
+
+# Rather than hope most of these chemicals have dtxsids within CvTdb,
+# I cross-referenced it with the CompTox database batch search.
+# Here I have curated the input by hand
+dtxsid_byhand_idless <- data.frame(
+  chem_name_original = c(
+    "paracetmol", #misspelling
+    "antipyrene", #synonym phenazone
+    "r-(+)-metoprolol", # using R/S and +/- confused search
+    "s-(-)-metoprolol",
+    "deacetyl diltiazem", # should be desacetyl
+    "valproate (vpa)", # valproic acid
+    "valproic acid",
+    "clotiapine", # clothiapine
+    "padsevonil", # found a ChEMBL_ID...
+    "2,2',4,4',5,'5-hexachlorobiphenyl",
+    "2,4,5,2',4','5-hexachlorobiphenyl", # number/prime order confused
+    "quinidine sulfate",
+    "quinidine",
+    "quinidine gluconate",
+    "furosemide",
+    "theophylline",
+    "fentanyl",
+    "ammonium perfluorooctonoate",
+    "perfluorohexanesulfonate anion", # anion confused search
+    "3'-azido-3'-deoxythymidine (aids)", # parenthetical confuses search
+    "3'-azido-3'-deoxythymidine", # repeat/duplicate of above
+    "2,4,5,2'5'-pentachlorobiphenyl", # number/prime order incorrect
+    "4,4'-sufonylbisphenol-d8", # deuterium but same as bisphenol S
+    "hydroxy-tebuconazole", # CAS 212267-64-6
+    "3'-amino-3'-deoxythimidine",
+    "bosentan sodium salt",
+    "bosentan micronized free sulfonamide",
+    "dichloroacetate",
+    "fluorotelomer acid 7+3",
+    "furosemide",
+    "morphine hydrochloride",
+    "perfluorohexanesulfonate,potassium salt",
+    "potassium perfluorooctane",
+    "sodium hexobarbital"
+  ),
+  comptox_dtxsid = c(
+    "DTXSID2020006",
+    "DTXSID6021117",
+    "DTXSID20230862",
+    "DTXSID20230861",
+    "DTXSID00881093",
+    "DTXSID6023733",
+    "DTXSID6023733",
+    "DTXSID5022851",
+    "CHEMBL4297521",
+    "DTXSID2032180",
+    "DTXSID2032180",
+    "DTXSID101017271",
+    "DTXSID4023549",
+    "DTXSID80102749",
+    "DTXSID6020648",
+    "DTXSID5021336",
+    "DTXSID9023049",
+    "DTXSID8037708",
+    "DTXSID80873012",
+    "DTXSID8020127",
+    "DTXSID8020127",
+    "DTXSID8038304",
+    "DTXSID3022409",
+    "DTXSID50891627",
+    "DTXSID00966879",
+    "DTXSID7046627",
+    "DTXSID7046627",
+    "DTXSID2020428",
+    "DTXSID90382620",
+    "DTXSID6020648",
+    "DTXSID9023336",
+    "DTXSID3037709",
+    "DTXSID0059794",
+    "DTXSID9023122"
+  )
 ) %>%
-  mutate(id = as.character(id),
-         chemical_name_original = force_straight_quotes(tolower(
-           chemical_name_original
-         )),
-         chemical_name_secondary_original = force_straight_quotes(tolower(
-           chemical_name_secondary_original
-         ))
-  )
-
+  distinct()
+
+# Fill in the missing DTXSIDs for these
+cvt_df <- cvt_df %>%
+  # Fill for analyzed chemicals
+  left_join(
+    dtxsid_byhand_idless %>%
+      inner_join(cvt_df %>%
+                   distinct(analyzed_chem_name_original, fk_analyzed_chemical_id),
+                 by = join_by(chem_name_original == analyzed_chem_name_original)),
+    by = join_by(fk_analyzed_chemical_id,
+                 analyzed_chem_name_original == chem_name_original)
+  ) %>%
+  mutate(analyzed_chem_dtxsid = coalesce(analyzed_chem_dtxsid, comptox_dtxsid)) %>%
+  select(!comptox_dtxsid) %>%
+  # Now do the same for dosed chemical
+  left_join(
+    dtxsid_byhand_idless %>%
+      inner_join(
+        cvt_df %>%
+          distinct(dosed_chem_name_original, fk_dosed_chemical_id),
+        by = join_by(chem_name_original == dosed_chem_name_original)
+      ),
+    by = join_by(fk_dosed_chemical_id,
+                 dosed_chem_name_original == chem_name_original)
+  ) %>%
+  mutate(dosed_chem_dtxsid = coalesce(dosed_chem_dtxsid, comptox_dtxsid)) %>%
+  select(!comptox_dtxsid)
+
+# Now that we've added some missing DTXSIDs, redo the chemical id 
+cvt_df <- cvt_df %>%
+  rowwise() %>%
+  mutate(fk_dosed_chemical_id = ifelse(
+    identical(analyzed_chem_dtxsid, dosed_chem_dtxsid),
+    fk_analyzed_chemical_id,
+    fk_dosed_chemical_id
+  )) %>%
+  ungroup()
+
+any(is.na(cvt_df$fk_analyzed_chemical_id))
+any(is.na(cvt_df$fk_dosed_chemical_id))
+
+quick_stats(cvt_df)
+
+# Now we need to pre-emptively address the chemicals that have different
+# dosed_id and analyzed_ids but are actually the same chemical
 cvt_df %>%
   filter(fk_analyzed_chemical_id != fk_dosed_chemical_id, 
-         !(radiolabeled %in% TRUE)) %>%
-  distinct(fk_analyzed_chemical_id,fk_dosed_chemical_id,fk_test_chemical_id) %>%
-  left_join(dtxsid_query %>%
-              select("fk_analyzed_chemical_id" = "id",
-                     "analyzed_chemical_name" = "chemical_name_original")) %>%
-  left_join(dtxsid_query %>%
-              select("fk_dosed_chemical_id" = "id",
-                     "dosed_chemical_name" = "chemical_name_original")) %>%
-  View("errors")
-
-# Rather than hope most of these chemicals have dtxsids within CvTdb,
-# I cross-referenced it with the CompTox database batch search.
-dtxsid_batch_idless <- readr::read_csv(
-  "data-raw/CCD-Batch-Search_2025-04-17_DTXSIDless.csv",
-  na = "N/A"
-) %>% filter(!is.na(DTXSID)) %>%
-  select("dsstox_substance_id" = "DTXSID",
-         "chemical_name_original" = "INPUT") %>%
-  distinct()
-
-quick_message(c(
-  "Erroneous DTXSID assignments (identified via duplication):",
-  "perfluorohexanesulfonate == DTXSID80873012",
-  "tacrolimus == DTXSID5046354",
-  "hippuric acid == DTXSID9046073"
-))
-
-dtxsid_batch_idless <- dtxsid_batch_idless %>%
-  mutate(dsstox_substance_id = case_when(
-    chemical_name_original == "perfluorohexanesulfonate" ~ "DTXSID80873012",
-    chemical_name_original == "tacrolimus" ~ "DTXSID5046354",
-    chemical_name_original == "hippuric acid" ~ "DTXSID9046073",
-    .default = dsstox_substance_id
-  )) %>% distinct()
-
-# Fixing the missing DTXSID to prevent premature filtering
-cvt_df <- cvt_df %>%
-  left_join(
-    dtxsid_batch_idless,
-    by = join_by(analyte_name_original == chemical_name_original)
-  ) %>%
-  mutate(analyte_dtxsid = coalesce(analyte_dtxsid, dsstox_substance_id)) %>%
-  select(!dsstox_substance_id)
-
-quick_stats(cvt_df)
-
-# Now we need to pre-emptively address the chemicals that have different
-# dosed_id and analyzed_ids but are actually the same chemical
-quick_message(c(
-  "The following have resolvable errors:",
-  "If dosed chemical id is 47, change this to 46 to match analyte id. tamoxifen, salt dosed.",
-  "If dosed chemical id is 893, change this to 929 to match analyte id. trichloroethylene, duplicate.",
-  "If dosed chemical id is 671, change to 672 to match analyte id. PFHS, salt dosed.",
-  "If dosed chemical id is 673, change to 675 to match analyte id. PFNA, capitalization.",
-  "If dosed chemical id is 674, change to 676 to match analyte id, PFDA, capitalization."
-))
-
-cvt_df <- cvt_df %>%
-  rowwise() %>%
-  mutate(fk_dosed_chemical_id = case_when(
-    fk_dosed_chemical_id == "47" &&
-      fk_analyzed_chemical_id == "46" ~ "46",
-    fk_dosed_chemical_id == "893" &&
-      fk_analyzed_chemical_id == "929" ~ "929",
-    fk_dosed_chemical_id == "671" &&
-      fk_analyzed_chemical_id == "672" ~ "672",
-    fk_dosed_chemical_id == "673" &&
-      fk_analyzed_chemical_id == "673" ~ "673",
-    fk_dosed_chemical_id == "674" &&
-      fk_analyzed_chemical_id == "676" ~ "676",
+         analyzed_chem_dtxsid != dosed_chem_dtxsid) %>%
+  distinct(analyzed_chem_name_original, dosed_chem_name_original,
+           fk_analyzed_chemical_id, fk_dosed_chemical_id,
+           analyzed_chem_dtxsid, dosed_chem_dtxsid) %>%
+  arrange(analyzed_chem_name_original) %>%
+  head()
+  # View()
+
+# TO FIX: SALTS
+# perfluorooctanesulfonate 692 -> 694, 763 -> 764
+# perfluorooctanoate 761 -> 762
+# phenobarbital 1147 -> 291
+# perfluorobutyrate (two different salts, could be interesting but removing for now)
+# perfluorobutanesulfonate 679 -> 680, 777 -> 778
+# perfluorohexanesulfonate 671 -> 672, 791 -> 792, 681 -> 682
+# tamoxifen 1008 -> 1010
+# thiopenal 1148 -> 1150
+# imipramine 1158 -> 1159, 1154 -> 1159
+# valproate 1163 -> 1164
+# nitrite 1013 -> 1014
+# odansetron 1117 -> 1118
+
+cvt_df <- cvt_df %>%
+  mutate(
+    fk_dosed_chemical_id = case_when(
+      fk_dosed_chemical_id %in% "692" &
+        fk_analyzed_chemical_id %in% "694" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "763" &
+        fk_analyzed_chemical_id %in% "764" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "761" &
+        fk_analyzed_chemical_id %in% "762" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1147" &
+        fk_analyzed_chemical_id %in% "291" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "679" &
+        fk_analyzed_chemical_id %in% "680" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "777" &
+        fk_analyzed_chemical_id %in% "778" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "671" &
+        fk_analyzed_chemical_id %in% "672" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "791" &
+        fk_analyzed_chemical_id %in% "792" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "681" &
+        fk_analyzed_chemical_id %in% "682" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1008" &
+        fk_analyzed_chemical_id %in% "1010" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1148" &
+        fk_analyzed_chemical_id %in% "1150" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1158" &
+        fk_analyzed_chemical_id %in% "1159" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1154" &
+        fk_analyzed_chemical_id %in% "1159" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1163" &
+        fk_analyzed_chemical_id %in% "1164" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1013" &
+        fk_analyzed_chemical_id %in% "1014" ~ fk_analyzed_chemical_id,
+      fk_dosed_chemical_id %in% "1117" &
+        fk_analyzed_chemical_id %in% "1118" ~ fk_analyzed_chemical_id,
       .default = fk_dosed_chemical_id
-  )) %>%
-  ungroup()
-
-# glimpse(dq_cols)
-
-# names(cvt_df)
-
-# study_query <- query_db(query = "SELECT distinct * FROM studies",
-#          schema = "cvt")
-
-quick_stats(cvt_df)
+    )
+  )
 
@@
 
-cat("Current # chemicals: ", length(unique(cvt_df$analyte_dtxsid)), "\n")
-cat("Number of chemicals where analyte_dtxsid is NA: ",
+cat("Current # chemicals: ", length(unique(cvt_df$analyzed_chem_dtxsid)), "\n")
+cat("Number of chemicals where analyzed_chem_dtxsid is NA: ",
     sum(is.na(unique(cvt_df[c("fk_analyzed_chemical_id",
-                               "analyte_dtxsid")])$analyte_dtxsid)),
+                               "analyzed_chem_dtxsid")])$analyzed_chem_dtxsid)),
     "\n")
@@
 cat("Number of radiolabelling experiments: ",
-    sum(distinct(cvt_df, analyte_dtxsid, radiolabeled) %>% pull(radiolabeled) %>%
+    sum(distinct(cvt_df, analyzed_chem_dtxsid, radiolabeled) %>%
+          pull(radiolabeled) %>%
           {. %in% TRUE}
@@
     )
-distinct(cvt_df, analyte_dtxsid, analyte_name_original, radiolabeled) %>%
-  filter(radiolabeled %in% TRUE, !is.na(analyte_dtxsid))
+distinct(cvt_df, analyzed_chem_dtxsid,
+         analyzed_chem_name_original, radiolabeled) %>%
+  filter(radiolabeled %in% TRUE, !is.na(analyzed_chem_dtxsid))
 
@@
     cvt_df %>%
-      filter(!is.na(analyte_dtxsid),
+      filter(!is.na(analyzed_chem_dtxsid),
              !(radiolabeled %in% TRUE),
              fk_analyzed_chemical_id != fk_dosed_chemical_id) %>%
-      distinct(analyte_dtxsid) %>%
+      distinct(analyzed_chem_dtxsid) %>%
       NROW()
@@
 
-cvt_df <- cvt_df %>%
-  filter(!(radiolabeled %in% TRUE),
-         !is.na(analyte_dtxsid),
-         (fk_analyzed_chemical_id == fk_dosed_chemical_id)) %>%
-  distinct()
-
-quick_message(text = c("Filtering out:",
-                       "Missing {.code analyte_dtxsid}",
-                       "Radiolabeling experiments",
-                       "Data where the analyzed chemicals and dosed chemicals are different"))
 quick_stats(cvt_df)
-diff_log_cvt(cvt_df)
+# This should be the base CvTdb prior to filtering steps
+
 ```
@@
 ```{r preliminary_filtering}
+
+cvt_df <- cvt_df %>%
+  filter(!(radiolabeled %in% TRUE),
+         !is.na(analyzed_chem_dtxsid),
+         (fk_analyzed_chemical_id == fk_dosed_chemical_id)) %>%
+  distinct()
+
+quick_message(text = c("Filtering out:",
+                       "Missing {.code analyzed_chem_dtxsid}",
+                       "Radiolabeling experiments",
+                       "Data where the analyzed chemicals and dosed chemicals are different"))
+
+quick_stats(cvt_df)
+
+# Filtering out non-circulation mediums (these are retained in cvtdb_original)
+cvt_df <- cvt_df %>%
+  filter(conc_medium_normalized %in% c("blood", "plasma"))
+
+quick_message(text = c("Filtering out:",
+                       "Non-plasma/blood medium collected."))
+
+# Filter out where all values in experiment are missing values/below LOQ
+# Also filter out observations where 
+cvt_df <- cvt_df %>%
+  mutate(
+    conc = ifelse(conc < 0, NA_real_, conc),
+    conc_original = ifelse(conc_original < 0, NA_real_, conc_original)
+  ) %>%
+  group_by(analyzed_chem_dtxsid, species, fk_extraction_document_id,
+           administration_route_normalized, conc_medium_normalized) %>%
+  filter(
+    !(if_all(conc, is.na) & if_all(conc_original, is.na))
+  ) %>%
+  ungroup() %>%
+  distinct()
+
+quick_message(text = c("Filtering out:",
+                       "Experiments missing concentration values altogether."))
+
+quick_stats(cvt_df)
+
 # Dose Units: Need mg/kg... = ug/mg = ng/ug, and kg = L
@@
 cvt_df <- cvt_df %>% mutate(
+  conc_units_normalized = stringr::str_replace(
+    conc_units_original, "(?<=/m?)l", "L"
+  ),
+  loq_units = stringr::str_replace(loq_units, "(?<=/m?)l", "L"),
   invivPK_dose_level_units = "mg/kg",
-  invivPK_conc_units = "ug/mL",
-  invivPK_conc = NA_real_,
-  invivPK_dose_level = NA_real_
+  invivPK_conc_units = "ug/mL"
   )
@@
 
-# Filtering out entries with no concentration information available
-cvt_df <- cvt_df %>%
-  filter(!(is.na(conc) & is.na(conc_original))) %>%
+quick_stats(cvt_df)
+
+# Filtering out entries with only single observations per study_id
+cvt_df <- cvt_df %>%
   group_by(fk_study_id) %>%
@@
   ungroup()
-###
+
 quick_stats(cvt_df)
+
 ```
@@
            dose_level_units_original,
-           pmid,
-           other_study_identifier)
-
+           administration_route_normalized,
+           pmid, fk_extraction_document_id,
+           other_study_identifier) %>%
+  glimpse()
+
+# Set units
+# Fix some dosing units which are not weight normalized
 cvt_df <- cvt_df %>%
@@
          invivPK_conc = conc)
-diff_log_cvt(cvt_df)
-
-# Checking other_study_identifier == S0916
-quick_message(text = c(
-  "Data Modification:",
-  paste("For study 1713 and 1714, tamoxifen was administered at 5mL/kg, ",
-        "meaning these doses are 5/1000th of current value to convert ug/mL -> mg/kg."
+
+# Now only a few studies need "extra" normalizing
+quick_message(c(
+  "Data Modification: Changing `conc` for following chemicals",
+  "hexobarbital, phenobarbital, thiopental"
+))
+quick_message(c(
+  "Data Modification: Changing `conc_units_normalized` for following chemicals",
+  "hexobarbital, phenobarbital, thiopental, TAME, chlorpyrifos, benzo(a)pyrene",
+  "phenacetin, perfluorononanoic acid, perfluorodecanoic acid, perfluorooctanoic acid"
+))
+quick_message(c(
+  "Data Modification: Changing `invivPK_loq` for following chemicals",
+  "TAME"
+))
+quick_message(c(
+  "Data Modification: Changing `invivPK_loq_units` for following chemicals",
+  "TAME",
+  "Any NA value for invivPK_loq_units to 'ug/mL'",
+  "Any 'ng' value to 'ng/mL'"
+))
+
+cvt_df <- cvt_df %>%
+  mutate(
+    invivPK_conc = case_when(
+      # TAME OK
+      # chlorpyrifos OK
+      # benzo(a)pyrene OK
+      # hexobarbital
+      conc_units_normalized %in% "x 10^-3 M" &
+        analyzed_chem_dtxsid %in% "DTXSID9023122" ~ conc_original * 0.23611,
+      # phenobarbital
+      conc_units_normalized %in% "x 10^-3 M" &
+        analyzed_chem_dtxsid %in% "DTXSID5021122" ~ conc_original * 0.23208,
+      # thiopental
+      conc_units_normalized %in% "x 10^-3 M" &
+        analyzed_chem_dtxsid %in% "DTXSID1023653" ~ conc_original * 0.24211,
+      .default = invivPK_conc
     ),
- "This entry has since been removed from CvT as of April 2025"
-)
-)
-
-# In CEBS "S0916" the Dose is 300,100 ug/mL with 5mL/kg administered by gavage (the only data left)
-# Making it 5/1000 mg/kg x either doses in study_ids 1714,1713 (the latter was filtered out prior to this)
-# cvt_df <- cvt_df %>%
-#   mutate(
-#     invivPK_dose_level = if_else(
-#       fk_study_id %in% c("1714", "1713"),
-#       5/1000 * dose_level_normalized,
-#       dose_level_normalized
-#     )
-#   )
-
-# In CEBS "S0624" it was in ng/kg not mg/kg in the summary, but that has been deleted from CEBS
-# Assuming that was a error of record
-
-quick_message("CEBS datasets S0976 and S0328 contain data on LOQ or ELOQ")
-# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine 
-quick_message(c(
-  "Data Modification:",
-  "Adjusting LOQ values for L-ephedrine to 3.39 as stated in CEBS study S0976.",
-  "Set LOQ units to ng/mL as detailed in the same CEBS study.",
-  "S0976 has been removed as of April 2025."
-))
-# Here I create new columns for loq and loq_units b/c I have modified them.
-# cvt_df <- cvt_df %>%
-#   mutate(invivPK_loq = if_else(
-#     other_study_identifier %in% "S0976",
-#     case_when(
-#       analyte_name_original %in% "caffeine" ~ 4.00,
-#       analyte_name_original %in% "l-ephedrine" ~ 3.39,
-#       analyte_name_original %in% "pseudoephedrine" ~ 4.43
-#     ),
-#     loq),
-#     invivPK_loq_units = if_else(
-#       other_study_identifier %in% "S0976",
-#       "ng/mL",
-#       loq_units
-#     ))
-
-# Some pentachlorophenol studies
-quick_message(c(
-  "Data Modification:",
-  "Looked at ELOQ in CEBS study S0328 and found it to be around 1",
-  "This only is relevant for {.code study_id} 1779.",
-  "This record is no longer present as of April 2025."
-))
-
-# cvt_df <- cvt_df %>%
-#   mutate(
-#   invivPK_loq = if_else(
-#     fk_study_id %in% "1779",
-#     1, invivPK_loq),
-#   invivPK_loq_units = if_else(
-#     other_study_identifier %in% "S0328",
-#     "ug/mL",
-#     invivPK_loq_units
-#   ))
+    conc_units_normalized = case_match(
+      analyzed_chem_dtxsid,
+      c("DTXSID9023122",
+        "DTXSID5021122",
+        "DTXSID1023653",
+        "DTXSID8024521",
+        "DTXSID4020458",
+        "DTXSID2020139",
+        "DTXSID1021116",
+        "DTXSID8031865",
+        "DTXSID3031860",
+        "DTXSID8031863"
+        ) ~ "ug/mL",
+      .default = conc_units_normalized
+    ),
+    invivPK_loq = case_when(
+      # TAME
+      invivPK_loq_units %in% "nmol/mL" &
+        analyzed_chem_dtxsid %in% "DTXSID8024521" ~ loq * 0.102,
+      .default = invivPK_loq
+    ),
+    invivPK_loq_units = case_when(
+      invivPK_loq_units %in% "nmol/mL" &
+        analyzed_chem_dtxsid %in% "DTXSID8024521" ~ "ug/mL",
+      is.na(invivPK_loq_units) ~ "ug/mL",
+      other_study_identifier %in% "K02922" ~ "ng/mL", # incorrect extraction
+      invivPK_loq_units %in% "ng" ~ "ng/mL",
+      .default = invivPK_loq_units
+    ),
+    weight_kg = case_when(
+      fk_subject_id %in% "41249" ~ 76, # extraction typo
+      .default = weight_kg
+    )
+  )
+
+# Fixing DOSE units
+unique(cvt_df$dose_level_units_original)
+
+cvt_df %>% 
+  filter(!(dose_level_units_original %in% equiv_mgkg),
+                  dose_level_normalized == dose_level_original) %>%
+  distinct(fk_study_id, 
+           dose_level_original, dose_level_normalized,
+           dose_level_units_original,
+           administration_route_normalized, fk_extraction_document_id)
+
+# Adjust invivPK_dose_level for non-standard units
+cvt_df %>% filter(is.na(invivPK_dose_level)) %>% count(dose_level_units_original)
+
+cvt_df <- cvt_df %>% 
+  mutate(
+    invivPK_dose_level = case_when(
+      # Standard weight of human (75kg)
+      is.na(invivPK_dose_level) &
+        is.na(weight_kg) &
+        species %in% "human" &
+        dose_level_units_original %in% "mg" ~ dose_level_original / 75,
+      dose_level_units_original %in% "mg" ~ signif(
+        invivPK_dose_level / weight_kg, digits = 5
+      ),
+      dose_level_units_original %in% "g" ~ signif(
+        1E3 * invivPK_dose_level / weight_kg, digits = 5
+      ),
+      dose_level_units_original %in% "ug" ~ signif(
+        1E-3 * invivPK_dose_level / weight_kg, digits = 5
+      ),
+      is.na(invivPK_dose_level) &
+        dose_level_units_original %in% "ug/kg" ~ dose_level_original * 1E-3,
+      is.na(invivPK_dose_level) &
+        dose_level_units_original %in% "ng/kg" ~ dose_level_original * 1E-6,
+      is.na(invivPK_dose_level) &
+        dose_level_units_original %in% c("mg/kg", "ug/mL") ~ dose_level_original,
+      .default = invivPK_dose_level
+    )
+  )
+
+cvt_df %>% filter(is.na(invivPK_dose_level)) %>% count(dose_level_units_original)
+cvt_df %>% filter(is.na(invivPK_dose_level)) %>% glimpse()
 
 quick_stats(cvt_df)
-diff_log_cvt(cvt_df)
 ```
@@
 ```{r general_unit_conversions}
-quick_message(c(
-  "Filtering data:",
-  "Only including data with a single dose.",
-  "{.code dose_frequency} of {.code NA} is assumed to be single bolus dose."
-))
-# Eliminate study that gave chemical each day, not single dose
-# This may be used in another type of model, but right now we deal with single bolus
-# Only include those that have NA or 1 for dose frequency
-cvt_df <- cvt_df %>%
-  filter(dose_frequency %in% c("1", NA))
+apply(cvt_df, 2, \(x) {
+  sum(is.na(x))
+})
 
 # quick_stats(cvt_df)
-quick_message("Uniqe LOQ units:")
-table(cvt_df$invivPK_loq_units)
-diff_log_cvt(cvt_df)
-quick_stats(cvt_df)
+quick_message("Unique LOQ units:")
+print(table(cvt_df$invivPK_loq_units))
 
@@
   "Converting concentration units to standard mg/L",
-  "Converting concentration sd units to the standard mg/L",
-  "Keeping concentration values for series 23340 and 23380 to original records"
+  "Converting concentration sd units to the standard mg/L"
 ))
@@
 cvt_df <- cvt_df %>%
-  mutate(invivPK_loq = if_else(
-    invivPK_loq_units %in% c("ug/L", "ng/mL", "ng/g"),
-    invivPK_loq * 1E-3, invivPK_loq)) %>% 
-  mutate(ivivPK_loq_units = "ug/mL") # mg/L and ug/mL are same scale
+  mutate(invivPK_loq = case_match(
+    invivPK_loq_units,
+    c("ug/L", "ng/mL", "ng/g") ~ invivPK_loq * 1E-3,
+    c("pg/mL") ~ invivPK_loq * 1E-6,
+    .default = invivPK_loq
+    )) %>% 
+  mutate(invivPK_loq_units = "ug/mL") # mg/L and ug/mL are same scale
+
 # Normalize conc_sd and conc units manually
+quick_message("Unique conc units:")
+print(table(cvt_df$conc_units_normalized))
 
@@
 cvt_df <- cvt_df %>%
+  filter(!(conc_units_normalized %in% "molar percentage")) %>%
   mutate(invivPK_conc_sd = case_when(
-    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
-                               "ng/g", "ng/g tissue", "ug/L") ~ conc_sd_original*1E-3,
-    conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
-    conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
-    !is.na(conc_sd) ~ conc_sd, 
-    .default = conc_sd_original
+    conc_units_normalized %in% c("ng/mL", "ng/g", "ug/L") ~ conc_sd_original*1E-3,
+    conc_units_normalized %in% c("g/dL") ~ conc_sd_original*1E-4,
+    conc_units_normalized %in% c("pg/mL") ~ conc_sd_original*1E-6,
+    conc_units_normalized %in% "percent of dose" ~ conc_sd_original * 
+      invivPK_dose_level/100,
+    .default = invivPK_conc_sd
   ))
@@
   mutate(invivPK_conc = case_when(
-    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
-                               "ng/g", "ng/g tissue", "ug/L") ~ conc_original*1E-3,
-    conc_units_original %in% c("g/dL") ~ conc_original*1E-4,
-    conc_units_original %in% c("pg/mL") ~ conc_original*1E-6,
-    fk_series_id %in% c("23340", "23380") ~ conc_original, # Special case of rounding errors
-    .default = conc
+    conc_units_normalized %in% c("ng/mL", "ng/g", "ug/L") ~ conc_original*1E-3,
+    conc_units_normalized %in% c("g/dL") ~ conc_original*1E-4,
+    conc_units_normalized %in% c("pg/mL") ~ conc_original*1E-6,
+    conc_units_normalized %in% "percent of dose" ~ conc_original * invivPK_dose_level/100,
+    is.na(invivPK_conc) ~ conc_original,
+    .default = invivPK_conc
   ))
@@
 quick_message("Are there chemicals with very few (less than 5) observations still?")
-cvt_df %>% count(analyte_dtxsid) %>% arrange(n) %>% head()
-# This has been resolved now
-# quick_message(c(
-#   "Filtering Data:",
-#   "Removing DTXSID6038299 due to insufficient data",
-#   "Removing all data points that still have recorded concentrations of zero"
-# ))
-# cvt_df <- cvt_df %>%
-#   dplyr::filter(!(analyte_dtxsid %in% "DTXSID6038299"))
-
-# This is the final filtering so that the dataset is most consistent with the
-# most current near future pull in the new year
-# This will include some zero values, but should work itself out during preprocessing
-cvt_df <- cvt_df %>%
-  filter(invivPK_conc >= 0)
+cvt_df %>% count(analyzed_chem_dtxsid) %>% arrange(n) %>% head()
+# No
 
@@
 
+cvt_df <- cvt_df %>%
+  mutate(time_hr = case_when(
+    is.na(time_hr) &
+      !is.na(time_original) & 
+      time_units_original %in% c("hours", "hour") ~ time_original,
+    .default = time_hr
+  ))
+
+# Filter out negative timepoints
+# Set subjects to 1 if conc_sd is NA
+cvt_df <- cvt_df %>%
+  filter(time_hr >= 0) %>%
+  mutate(
+    n_subjects_normalized = case_when(
+      is.na(invivPK_conc_sd) ~ 1,
+      is.na(n_subjects_normalized) ~ 1,
+      .default = n_subjects_normalized
+    )
+  )
+
+quick_message(c(
+  "Modifying dataset:",
+  "Set missing time_hr to time_original if these are in hour(s).",
+  "Filter out negative timepoints.",
+  "Set n_subjects_normalized to 1 if conc_sd or n_subjects_normalized is missing."
+))
+
 glimpse(cvt_df)
+apply(cvt_df, 2, \(x) {
+  sum(is.na(x))
+})
+
 quick_stats(cvt_df)
-
-diff_log_cvt(cvt_df, 
-             notes = c("Used CompTox name - DTXSID matching to fill in NAs.",
-                       "Fixed names that used non-standard single quotes.")
-)
 
@@
 of modifying the data that we will use for _invivoPKfit_. The only column from the
-SQL query result of CvTdb that is actually changed is the `analyte_dtxsid` as 
+SQL query result of CvTdb that is actually changed is the `analyzed_chem_dtxsid` as 
 described earlier.
+
+```{r plot_by_dtxsid}
+
+cvt_df %>%
+  ggplot(aes(x = time_hr, y = invivPK_conc, group = analyzed_chem_dtxsid,
+             color = analyzed_chem_dtxsid)) +
+  geom_point() +
+  geom_smooth(se = FALSE) +
+  theme_bw() +
+  scale_y_log10() +
+  theme(legend.position = "none")
+```
+
+```{r final_checks}
+
+cvt_df %>%
+  count(is.na(dose_level_normalized), 
+        is.na(invivPK_dose_level),
+        is.na(dose_level_original)) %>% glimpse()
+
+cvt_df %>%
+  count(is.na(invivPK_conc_sd) & n_subjects_normalized > 1)
+
+cvt_df %>%
+  count(is.na(n_subjects_normalized))
+
+```
 
@@
 cvt_date <- Sys.Date()
+
 cat(diff_log_cvt(cvt_df, 
-             notes = c("Used CompTox name - DTXSID matching to fill in NAs.",
-                       "Fixed names that used non-standard single quotes.")
+                 notes = c(
+                   ""
+                 )
 ),
 file = "data-raw/cvt_changelog.txt",
-    append = TRUE)
+append = TRUE
+)
 
@@
 ```
+
+# QSAR Bakeoff Run
+
+```{r running}
+my_pk <- pk(cvt,
+            mapping = ggplot2::aes(
+              Chemical = analyzed_chem_dtxsid,
+              Chemical_Name = analyzed_chem_name_original,
+              DTXSID = analyzed_chem_dtxsid,
+              CASRN = analyzed_chem_casrn,
+              Species = species,
+              Reference = fk_extraction_document_id,
+              Media = conc_medium_normalized,
+              Route = administration_route_normalized,
+              Dose = invivPK_dose_level,
+              Dose.Units = "mg/kg",
+              Subject_ID = fk_subject_id,
+              Series_ID = fk_series_id,
+              Study_ID = fk_study_id,
+              ConcTime_ID = conc_time_id,
+              N_Subjects = n_subjects_normalized,
+              Weight = weight_kg,
+              Weight.Units = "kg",
+              Time = time_hr,
+              Time.Units = "hours",
+              Value = invivPK_conc,
+              Value.Units = "mg/L",
+              Value_SD = invivPK_conc_sd,
+              LOQ = invivPK_loq
+            ))
+
+my_pk <- my_pk +
+  stat_error_model(error_group = vars(Chemical, Species)) +
+  settings_optimx(method = "bobyqa") +
+  facet_data(vars(Chemical, Species)) +
+  settings_preprocess(keep_data_original = TRUE,
+                      suppress.messages = TRUE) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE)
+
+my_pk <- do_preprocess(my_pk)
+apply(my_pk$data, 2, \(x) { any(is.na(x)) })
+
+my_pk <- do_data_info(my_pk)
+my_pk <- do_prefit(my_pk)
+
+my_pk <- do_fit(my_pk, n_cores = 12)
+
+fit_pl <- plot(my_pk, best_fit = TRUE, log10_C = FALSE, use_scale_conc = TRUE)
+
+fit_pl %>% filter(Chemical %in% "DTXSID1021116", Species %in% "human") %>%
+  pull(final_plot) %>% .[[1]]
+fit_pl %>% filter(Chemical %in% "DTXSID9025617", Species %in% "mouse") %>%
+  pull(final_plot) %>% .[[1]]
+fit_pl %>% filter(Chemical %in% "DTXSID9025617", Species %in% "rat") %>%
+  pull(final_plot) %>% .[[1]]
+fit_pl %>% filter(Chemical %in% "DTXSID2021781", Species %in% "mouse") %>%
+  pull(final_plot) %>% .[[1]]
+
+save(my_pk, file = "data-raw/temp_pk.rda")
+
+```

### 2025-05-20 data-raw/pk_models.R

@@ -51,7 +51,7 @@ model_1comp_cl_rest <- pk_model(name = "model_1comp_cl_rest",
                              auc_fun = "auc_1comp_cl",
                              params_fun = "get_params_1comp_cl",
                              tkstats_fun = "tkstats_1comp_cl",
-                             conc_fun_args = NULL,
+                             conc_fun_args = list(restrictive = TRUE),
                              auc_fun_args = NULL,
                              params_fun_args = list(restrictive = TRUE),
                              tkstats_fun_args = NULL)
@@ -69,7 +69,7 @@ model_1comp_cl_nonrest <- pk_model(name = "model_1comp_cl_nonrest",
                                 auc_fun = "auc_1comp_cl",
                                 params_fun = "get_params_1comp_cl",
                                 tkstats_fun = "tkstats_1comp_cl",
-                                conc_fun_args = NULL,
+                                conc_fun_args = list(restrictive = FALSE),
                                 auc_fun_args = NULL,
                                 params_fun_args = list(restrictive = FALSE),
                                 tkstats_fun_args = NULL)
@@ -87,7 +87,7 @@ model_1comp_fup <- pk_model(name = "model_1comp_fup",
                              auc_fun = "auc_1comp_cl",
                              params_fun = "get_params_1comp_fup",
                              tkstats_fun = "tkstats_1comp_cl",
-                             conc_fun_args = NULL,
+                             conc_fun_args = list(restrictive = TRUE),
                              auc_fun_args = NULL,
                              params_fun_args = NULL,
                              tkstats_fun_args = NULL)

### 2025-05-21 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Updated data objects to reflect fixes to dose values for tamoxifen and MTBE data.

@@
 quick_stats(cvt_df)
-quick_stats(cvt_2.0.0, old_version = TRUE)
+# quick_stats(cvt_2.0.0, old_version = TRUE)
 # Note unique chemical counts
@@
 # Conc Units: Need mg/L... = ug/mL = ng/uL = pg/nL, and kg = L, g = mL
+
 cvt_df <- cvt_df %>% mutate(
@@
            dose_level_units_original,
+           administration_route_normalized,
+           pmid, fk_extraction_document_id,
+           other_study_identifier) %>%
+  glimpse()
+
+cvt_df %>% filter(stringr::str_detect(dose_level_units_original, "L")) %>%
+  distinct(analyzed_chem_dtxsid, analyzed_chem_name_original,
+           dose_level_original, dose_level_normalized,
+           dose_level_units_original,
+           dose_volume, dose_volume_units,
            administration_route_normalized,
@@
 
-cvt_df %>% 
-  filter(!(dose_level_units_original %in% equiv_mgkg),
-                  dose_level_normalized == dose_level_original) %>%
-  distinct(fk_study_id, 
-           dose_level_original, dose_level_normalized,
-           dose_level_units_original,
-           administration_route_normalized, fk_extraction_document_id)
-
 # Adjust invivPK_dose_level for non-standard units
@@
         dose_level_units_original %in% "ng/kg" ~ dose_level_original * 1E-6,
+      # There are some cases where there is a volume given (not mass normalized)
       is.na(invivPK_dose_level) &
-        dose_level_units_original %in% c("mg/kg", "ug/mL") ~ dose_level_original,
+        dose_level_units_original %in% "ug/mL" &
+        !is.na(dose_volume) & 
+        dose_volume_units %in% "mL/kg" ~ dose_level_original * dose_volume / 1E3,
+      is.na(invivPK_dose_level) &
+        dose_level_units_original %in% "ug/mL" &
+        !is.na(dose_volume) & 
+        dose_volume_units %in% "mL" &
+        species %in% "human" ~ dose_level_original * dose_volume / (75E3),
+      is.na(invivPK_dose_level) &
+        dose_level_units_original %in% "mg/kg" ~ dose_level_original,
       .default = invivPK_dose_level
@@
 
-fit_pl <- plot(my_pk, best_fit = TRUE, log10_C = FALSE, use_scale_conc = TRUE)
+fit_pl <- plot(my_pk, log10_C = FALSE, use_scale_conc = TRUE)
 
@@
   pull(final_plot) %>% .[[1]]
+fit_pl %>% filter(Chemical %in% "DTXSID1034187") %>% # Tamoxifen sanity check
+  pull(final_plot) %>% .[[1]]
+
+get_winning_model(my_pk) %>% filter(Chemical %in% "DTXSID1034187")
 

### 2025-05-27 data-raw/optimizing_httk_model.Rmd
Updating data-raw files

---
title: "Optimizing httk's 3comp2 model"
author: "Gilberto Padilla Mercado"
date: "2025-05-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
devtools::load_all()
library(httk)
```

# Purpose

This documents how to optimize `Clint` and `Funbound.plasma` using
_invivoPKfit_ and _httk_'s `3compartment2` model. There are
a couple of issues mainly stemming from the fact that the solver often
returns an error from the underlying FORTRAN code used in `deSolve` in
multiple iterations of the optimization procedure.

```{r}
load_dawson2021()
schems <- httk::get_cheminfo("dtxsid", species = "rat",
                             model = "3compartment2")[50:65] |>
  suppressWarnings()

sum(unique(cvt$analyzed_chem_dtxsid) %in% schems)

minicvt <- subset(
  cvt,
  species == "rat" &
    analyzed_chem_dtxsid %in% schems
)

table(minicvt$analyzed_chem_dtxsid)
```

First I want to try just the clearance-aware 1-compartment models

```{r}
test_pk <- pk(data = minicvt) + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  stat_model(model = c("model_flat", "model_1comp_cl_rest",
                       "model_1comp_cl_nonrest", "model_1comp_fup")) +
  settings_optimx(hessian = TRUE) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE)

test_pk <- do_prefit(test_pk)
test_pk
gc()

test_fit <- do_fit(test_pk)
winmodel <- get_winning_model(test_fit)
View(winmodel)

pl <- plot(test_fit, use_scale_conc = TRUE, method = "bobyqa",best_fit = TRUE)
pl$final_plot[[1]]
pl$final_plot[[2]]
pl$final_plot[[3]]
pl$final_plot[[4]]

get_fit(test_fit) |> dplyr::filter(Chemical == "DTXSID4020458",
                                   param_name %in% c("Fup", "Clint"),
                                   model != "model_flat",
                                   convcode == 0) |>
  View()

```

We have a list of things to try:

[] Are the timepoints causing issues? Run and stop with initial parameters.
[] Should we only optimize one parameter? Modify `get_params_httk_3comp2` function.

```{r}

test_pk <- pk(data = minicvt) + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  stat_model(model = c("model_flat", "model_httk_3comp2")) +
  settings_optimx(hessian = TRUE) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE)

test_pk <- do_prefit(test_pk)
test_pk
gc()

test_fit <- do_fit(test_pk)

```

```{r}
preds <- predict(test_fit)

my_fit <- get_fit(test_fit) |>
  dplyr::filter(optimize_param)

View(transform(my_fit, opt_diff = start - estimate))

```

### 2025-05-27 data-raw/pk_models.R

@@ -112,20 +112,53 @@ model_1comp_rad <- pk_model(name = "model_1comp_rad",
                              tkstats_fun_args = NULL)
 
 model_httk_3comp2 <- pk_model(name = "model_httk_3comp2",
-                            params = c("Clint",
-                                       "Funbound.plasma"),
-                            conc_fun = "cp_httk_3comp2",
-                            auc_fun = "auc_httk_3comp2",
-                            params_fun = "get_params_httk_3comp2",
-                            tkstats_fun = "tkstats_httk_3comp2",
-                            conc_fun_args = list(restrictive = TRUE,
-                                                 this_chem = quote(Chemical),
-                                                 this_species = quote(Species)),
-                            auc_fun_args = NULL,
-                            params_fun_args = list(restrictive = TRUE,
+                              params = c("BW",
+                                         "Caco2.Pab",
+                                         "Caco2.Pab.dist",
+                                         "Clint",
+                                         "Clint.dist",
+                                         "Clmetabolismc",
+                                         "Funbound.plasma",
+                                         "Funbound.plasma.dist",
+                                         "Funbound.plasma.adjustment",
+                                         "Fabsgut",
+                                         "Fhep.assay.correction",
+                                         "hematocrit",
+                                         "Kgut2pu",
+                                         "Krbc2pu",
+                                         "kgutabs",
+                                         "Kliver2pu",
+                                         "Krest2pu",
+                                         "Kblood2air",
+                                         "liver.density",
+                                         "logHenry",
+                                         "million.cells.per.gliver",
+                                         "MW",
+                                         "Pow",
+                                         # pKa values are added in get_params
+                                         "MA",
+                                         "Qcardiacc",
+                                         "Qgfrc",
+                                         "Qgutf",
+                                         "Qliverf",
+                                         "Qalvc",
+                                         "Rblood2plasma",
+                                         "Vgutc",
+                                         "Vliverc",
+                                         "Vrestc"
+                              ),
+                              conc_fun = "cp_httk_3comp2",
+                              auc_fun = "auc_httk_3comp2",
+                              params_fun = "get_params_httk_3comp2",
+                              tkstats_fun = "tkstats_httk_3comp2",
+                              conc_fun_args = list(restrictive = TRUE,
                                                    this_chem = quote(Chemical),
                                                    this_species = quote(Species)),
-                            tkstats_fun_args = NULL)
+                              auc_fun_args = NULL,
[…]

### 2025-05-27 data-raw/qb_filter_tracking.R

@@ -1,4 +1,5 @@
 # qb_df is the CSV file that contains the tested chemicals for the QSAR bakeoff
+qb_df <- paste0(Sys.getenv("TKQSAR_DIR"), "TestChemsDashboardInfo.csv")
 qb_dtxsid <- qb_df$DTXSID
 
 table(qb_dtxsid %in% cvt_df$analyzed_chem_dtxsid)

### 2025-05-27 data-raw/optimizing_httk_model.Rmd
Updated README.

@@
 devtools::load_all()
+library(dplyr)
 library(httk)
@@
 schems <- httk::get_cheminfo("dtxsid", species = "rat",
-                             model = "3compartment2")[50:65] |>
+                             model = "3compartment2") |>
   suppressWarnings()
@@
   settings_optimx(hessian = TRUE) +
-  scale_conc(dose_norm = TRUE, log10_trans = FALSE)
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE)
 
+test_pk <- do_data_info(test_pk)
 test_pk <- do_prefit(test_pk)
@@
 
-test_fit <- do_fit(test_pk)
+test_pk$prefit$par_DF |> View()
+
+test_fit <- do_fit(test_pk, n_cores = 8)
 winmodel <- get_winning_model(test_fit)
 View(winmodel)
+winmodel %>% ungroup() %>% count(method, model)
+get_fit(test_fit) %>%
+  filter(convcode == 0) %>%
+  ungroup() %>%
+  distinct(Chemical, Species, model, method) %>% View()
 
-pl <- plot(test_fit, use_scale_conc = TRUE, method = "bobyqa",best_fit = TRUE)
-pl$final_plot[[1]]
-pl$final_plot[[2]]
-pl$final_plot[[3]]
-pl$final_plot[[4]]
+pl <- plot(test_fit, use_scale_conc = TRUE,best_fit = FALSE, log10_C = TRUE,
+           method = "bobyqa", fit_limits = 10)
+pl %>%
+  filter(Chemical == "DTXSID0020442") %>%
+  pull(final_plot) %>% .[[1]]
 
-get_fit(test_fit) |> dplyr::filter(Chemical == "DTXSID4020458",
-                                   param_name %in% c("Fup", "Clint"),
-                                   model != "model_flat",
-                                   convcode == 0) |>
-  View()
+pl %>%
+  filter(Chemical == "DTXSID1022265") %>%
+  pull(final_plot) %>% .[[1]]
+
+get_fit(test_fit) %>%
+  filter(Chemical == "DTXSID0020442", model == "model_1comp_cl_nonrest",
+         param_name == "Clint", method == "L-BFGS-B") %>% View()
 

### 2025-06-02 data-raw/optimizing_httk_model.Rmd
Fixing total liver flow, renal and hepatic clearance definition in 1comp_cl model functions. Added liver_mass as a parameter to facilitate hepatic clearance calculations.

@@
   settings_optimx(hessian = TRUE) +
-  scale_conc(dose_norm = FALSE, log10_trans = FALSE)
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE)
 
@@
 
-test_pk$prefit$par_DF |> View()
-
-test_fit <- do_fit(test_pk, n_cores = 8)
+test_fit <- do_fit(test_pk, n_cores = 4)
 winmodel <- get_winning_model(test_fit)
+winmodel %>% ungroup() %>% count(method, model)
 View(winmodel)
-winmodel %>% ungroup() %>% count(method, model)
 get_fit(test_fit) %>%
@@
 
-pl <- plot(test_fit, use_scale_conc = TRUE,best_fit = FALSE, log10_C = TRUE,
-           method = "bobyqa", fit_limits = 10)
+pl <- plot(test_fit, use_scale_conc = FALSE,
+           best_fit = FALSE, log10_C = FALSE,
+           method = "L-BFGS-B")
+
+winmodel %>%
+  filter(model != "model_flat") %>%
+  distinct(Chemical, model)
+
 pl %>%
   filter(Chemical == "DTXSID0020442") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID2020139") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID4020458") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID4022527") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID4032405") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID5023320") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID6022923") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID7046627") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID8020541") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID8032673") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID9020584") %>%
+  pull(final_plot) %>% .[[1]]
+
+pl %>%
+  filter(Chemical == "DTXSID9032329") %>%
   pull(final_plot) %>% .[[1]]
@@
          param_name == "Clint", method == "L-BFGS-B") %>% View()
+
+get_fit(test_fit) %>%
+  semi_join(winmodel) %>%
+  filter(model != "model_flat", optimize_param) %>%
+  mutate(diff_est = estimate - start) %>%
+  View("diffs")
+
+get_fit(test_fit) %>%
+  semi_join(winmodel) %>%
+  filter(model != "model_flat", optimize_param,
+         convcode == 0) %>%
+  mutate(diff_est = estimate - start) %>%
+  filter(stringr::str_detect(param_name, "sigma_", negate = TRUE)) %>%
+  group_by(model, method, param_name) %>%
+  summarize(avg_diff = mean(diff_est),
+            min_diff = min(diff_est),
+            max_diff = max(diff_est))
 

### 2025-06-02 data-raw/optimizing_httk_model.Rmd
Fixing total liver flow, renal and hepatic clearance definition in 1comp_cl model functions.

@@
            best_fit = FALSE, log10_C = FALSE,
-           method = "L-BFGS-B")
+           method = "L-BFGS-B", fit_limits = 10)
 
@@
 pl %>%
-  filter(Chemical == "DTXSID7046627") %>%
-  pull(final_plot) %>% .[[1]]
-
-pl %>%
   filter(Chemical == "DTXSID8020541") %>%
@@
   filter(Chemical == "DTXSID9020584") %>%
-  pull(final_plot) %>% .[[1]]
-
-pl %>%
-  filter(Chemical == "DTXSID9032329") %>%
   pull(final_plot) %>% .[[1]]

### 2025-07-08 data-raw/ClearanceProject-0-Distinguishability.Rmd
Updated Rmarkdown files and moved some RDS data files used.

---
title: "Sampling Clint and Funbound.plasma"
author: "Gilberto Padilla Mercado"
date: "2025-06-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library_loading}
# June 6, 2025 8AM: Using httk-dev/HTTK-293 branch
# June 6, 2025 3PM: Using httk-dev/dev branch
source("data-raw/RC_comparison_bkgd.R")
library(dplyr)
library(tidyselect)
library(ggplot2)
library(patchwork)
library(parallel)
```

# Purpose

```{r set_parameters}
THIS_CHEMICAL = "DTXSID3024289" # A chemical to test
# THIS_CHEMICAL = "DTXSID50873382" # Warfarin
DOSE = 25
SPECIES = "Rat"
ROUTE = "oral"
TIMES = c(seq(0, 23.75, by = 0.25), seq(24, 72, by = 6),
          seq(96, 120, by = 24))/24
SAMPLES = 1000
VARPARS = list(Clint = 0.1)
CENSORPARS = list(Funbound.plasma = list(cv = 0.1, lod = 1E-5))
HUMAN_CLINT_FUP = TRUE
SPECIES_TEXT <- ifelse(SPECIES != "Human" && HUMAN_CLINT_FUP,
                       paste0(SPECIES, "_parHuman"),
                       SPECIES)
INVITROUV = NULL
INVITROUV_TEXT = NULL
if (!is.null(INVITROUV)) {
  INVITROUV_TEXT = "_usedINVITRO"
}
```

```{r get_chems}
chems_available <- get_cheminfo(info = "dtxsid", species = SPECIES,
                                model = "gas_pbtk") |> suppressWarnings()
```

```{r helper_functions}
# Get all simulations (restrictive and nonrestrictive)
conc_fun_wsamples <- function(
    # Parameterizing args
    dtxsid,
    species = "Human",
    default_to_human = FALSE,
    force_human = FALSE,
    # Solving args
    dose = 20, 
    route = "iv",
    times = seq(0, 48, by = 1)/24,
    # MC sampler args
    vary.params = NULL,
    censored.params = NULL,
    samples = 1000
) {
  # Decided to do both Clearances in one go
  # parameterization to be able to explicitly force human clint and fup

  # Parameterize
  gas_pars <- standard_parameterization(
    dtxsid = dtxsid,
    species = species,
    default_to_human = default_to_human,
    force_human = force_human
  )

  # SOLVE NUMERICALLY
  numerical_solution <- standard_httk_preds(parameters = gas_pars,
                                            species = species,
                                            default_to_human = default_to_human,
                                            force_human = force_human,
                                            dose = dose,
                                            route = route,
                                            times = times)

  mc_solutions <- standard_httk_mc(parameters = gas_pars,
                                   species = species,
                                   default_to_human = default_to_human,
                                   force_human = force_human,
                                   dose = dose,
                                   route = route,
                                   times = times,
                                   vary.params = vary.params,
                                   censored.params = censored.params,
                                   samples = samples)

  # Merge the solutions
  tmp <- merge(numerical_solution, mc_solutions)
  tmp <- subset(tmp, Time %in% times)

  # Time from days to hours
  tmp$Time <- janitor::round_to_fraction(tmp$Time * 24, denominator = 60)

  return(tmp)
}

```

```{r runs}

# system.time(
  test_mc_fun <- conc_fun_wsamples(
    dtxsid = "DTXSID3024289",
    times = TIMES,
    species = SPECIES,
    route = ROUTE,
    samples = SAMPLES,
    dose = DOSE,
    vary.params = VARPARS,
    censored.params = CENSORPARS,
    force_human = HUMAN_CLINT_FUP
  )
# )

# What is happening now is with parameterization, solution is higher than MC!
# But Solution is correct... MC has decreased!!!

Sys.sleep(5)
gc()

```

```{r test_plots}
# How do restrictive vs non-restrictive compare?
ggplot(test_mc_fun, aes(x = Time)) +
  geom_line(mapping = aes(y = MED_R), color = "magenta4",
            linewidth = 1, linetype = "76") +
  geom_ribbon(mapping = aes( ymin = l95_R, ymax = u95_R), linetype = "dotted",
              fill = NA, color = "magenta4") +
  geom_line(mapping = aes(y = MED_N), color = "cyan4",
            linewidth = 1, linetype = "76") +
  geom_ribbon(mapping = aes(ymin = l95_N, ymax = u95_N), linetype = "dotted",
              fill = NA, color = "cyan4") +
  geom_line(aes(y = Sol_N), linetype = "55") +
  geom_line(aes(y = Sol_R), linetype = "solid") +
  labs(y = "Concentration (mg/L)",x = "Time (hrs)",
       title = paste0(THIS_CHEMICAL, " (", DOSE, "mg/kg)"),
       subtitle = paste0("Samples: ", SAMPLES)) +
  coord_cartesian(xlim = c(0,24)) +
  theme_bw()

ggplot(test_mc_fun,
  mapping = aes(
    x = MED_N,
    y = MED_R
  )
) +
  geom_ribbon(aes(ymin = l95_R, ymax = u95_R),
              fill = "magenta4", alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0) +
  geom_ribbon(aes(ymin = l95_N, ymax = u95_N),
              fill = "cyan4", alpha = 0.5) +
  theme_bw()

```

## Overlaps of confidence intervals

A confidence interval represents our *confidence*
that the mean value of a distribution is within a
particular range. Thus when we take the *overlap*
of these intervals and divide it by the
non-overlapping areas, it is a rough representation
of how *confident* we would be in distinguishing
two sets of TK curves. I will call this the
**distinguishability**.

```{r testing_overlap}
# Overlap testing
# mat must have rownames and first row must be "Time"
args(calc_overlap)

# Test matrices
## Simple Triangle
mat_st <- matrix(c(0,0,0,2,0,4,5,0,0), nrow = 3)
rownames(mat_st) <- c("Time", "UL", "BL")
mat_st
calc_overlap(mat_st)

## Diamond (undetermined midpoint)
mat_dd <- matrix(c(0,10,0,
                   2,0,10,
                   10,10,0),
                 nrow = 3)
rownames(mat_dd) <- c("Time", "UL", "BL")
mat_dd
calc_overlap(mat_dd)
```

```{r diagnosing}
# Checking that the medians/means of samples are consistent with numerical solution
TEST_CHEMICALS <- paste0("DTXSID",
                         c("0020232", "4020458",
                           "8020541", "4022529",
                           "6022923", "3024289"))

for (this_chem in TEST_CHEMICALS) {
  solved_mc_fun <- conc_fun_wsamples(this_chem,
                                     species = SPECIES,
                                     default_to_human = FALSE,
                                     force_human = HUMAN_CLINT_FUP,
                                     vary.params = VARPARS,
                                     censored.params = CENSORPARS,
                                     dose = DOSE,
                                     route = ROUTE,
                                     times = TIMES)
  print(
    ggplot(solved_mc_fun, aes(x = Time)) +
      geom_line(mapping = aes(y = MED_R), color = "magenta4",
                linewidth = 1, linetype = "76") +
      geom_ribbon(mapping = aes( ymin = l95_R, ymax = u95_R), linetype = "dotted",
                  fill = NA, color = "magenta4") +
      geom_line(mapping = aes(y = MED_N), color = "cyan4",
                linewidth = 1, linetype = "76") +
      geom_ribbon(mapping = aes(ymin = l95_N, ymax = u95_N), linetype = "dotted",
                  fill = NA, color = "cyan4") +
      geom_line(aes(y = Sol_N), linetype = "55") +
      geom_line(aes(y = Sol_R), linetype = "solid") +
      labs(y = "Concentration (mg/L)",x = "Time (hrs)",
           title = paste0(this_chem, " (", DOSE, "mg/kg)"),
           subtitle = paste0("Samples: ", SAMPLES)) +
      theme_bw()
  )
  Sys.sleep(10)
}

```

We need to assess the distinguishability in a standard manner, with a few 
considerations. We can assess human and rat at arbitrary doses and coefficients
of variation for `Clint` and `Funbound.plasma`. However, there may be specific
doses and CVs for which we want to test. Note that there are

```{r all_chems_fun}

assessment_fun <- function(
    x,
    species = SPECIES,
    dose = DOSE,
    route = ROUTE,
    times = TIMES,
    samples = SAMPLES,
    vary.params = VARPARS,
    censored.params = CENSORPARS,
    force_human = HUMAN_CLINT_FUP
) {
  p_df <- conc_fun_wsamples(
    dtxsid = x,
    species = species,
    dose = dose,
    route = route,
    times = times,
    samples = samples,
    vary.params = vary.params,
    censored.params = censored.params,
    force_human = force_human
  ) |> try()

  if (inherits(p_df, "try-error")) return("Error at solving")

  p_df <- p_df[-2, ] # Remove small time increment

  if (identical(p_df[["Sol_R"]], p_df[["Sol_N"]])) {
    # Not distinguishable by numerical solution
    hep_extr <- parameterize_gas_pbtk(
      dtxsid = x,
      species = species,
      restrictive.clearance = TRUE,
      force.human.clint.fup = force_human,
      Caco2.options = list(overwrite.invivo = TRUE)
    ) |> try()

    if (inherits(hep_extr, "try-error")) return("Error at  parameterizing")

    hep_extr <- with(
      hep_extr, 
      Clmetabolismc / (Qcardiacc * Qliverf)
    )
    if (hep_extr < 0.3) {
      return(setNames("ND_SO_low", x))
    } else if (hep_extr > 0.7) {
      return(setNames("ND_SO_hi", x))
    } else {
      return(setNames("ND_SO_mid", x))
    }
  } else if (all(with(p_df, u95_N <= l95_R))) {
    # Distinguishable, non-overlapping at all
    # Change to "Identifiable"
    return(setNames("Distinguished", x))
  } else if (any(with(p_df, u95_N > l95_R))) {
    mcmat <- data.matrix(p_df[c("Time", 
                                  "l95_R", "u95_R",
                                  "l95_N", "u95_N")])

    this_auc_R <- calc_overlap(mcmat[, c("Time", "l95_R", "u95_R")])
    this_auc_N <- calc_overlap(mcmat[, c("Time", "l95_N", "u95_N")])
    this_auc_B <- min(
      calc_overlap(mcmat[, c("Time", "l95_R", "u95_N")]),
      calc_overlap(mcmat[, c("Time", "l95_R", "u95_N")])
    )
    prob_auc <- signif(this_auc_B / (this_auc_R + this_auc_N - this_auc_B), 4)

    if (!is.nan(prob_auc) && prob_auc > 0.1) {
      # Not distinguishable by Monte Carlo simulations
      hep_extr <- parameterize_gas_pbtk(
        dtxsid = x,
        species = species,
        restrictive.clearance = TRUE,
        force.human.clint.fup = force_human,
        Caco2.options = list(overwrite.invivo = TRUE)
      ) |> try()

      if (inherits(hep_extr, "try-error")) return("Error at parameterizing")

      hep_extr <- with(
        hep_extr, 
        Clmetabolismc / (Qcardiacc * Qliverf)
      )
      if (hep_extr < 0.3) {
        return(setNames("ND_MC_low", x))
      } else if (hep_extr > 0.7) {
        return(setNames("ND_MC_hi", x))
      } else {
        return(setNames("ND_MC_mid", x))
      }
    } else {
      # Distinguishable
      return(setNames("Distinguished", x))
    }
  }
}

# PLOTTING FUNCTION
plotting_fun <- function(
    x,
    species = SPECIES,
    dose = DOSE,
    route = ROUTE,
    times = TIMES,
    samples = SAMPLES,
    vary.params = VARPARS,
    censored.params = CENSORPARS,
    force_human = HUMAN_CLINT_FUP  
) {
  p_df <- conc_fun_wsamples(
    dtxsid = x,
    species = species,
    dose = dose,
    route = route,
    times = times,
    samples = samples,
    vary.params = vary.params,
    censored.params = censored.params,
    force_human = force_human
  )
  p_df <- p_df[-2, ] # Remove small time increment
  p_df_rmse <- signif(sum(with(p_df, (Sol_R - MED_R)^2)) / NROW(p_df), 3)
  title_txt <- paste(unlist(get_chem_id(dtxsid = x))[2:3], collapse = "\n")

  if (identical(p_df[["Sol_R"]], p_df[["Sol_N"]])) {

    pl <- ggplot(p_df, aes(x = Time)) +
      geom_line(aes(y = Sol_R)) +
      geom_line(aes(y = MED_R), linetype = "44", color = "purple") +
      labs(title = title_txt,
           subtitle = paste("RMSE:", signif(p_df_rmse, 5)),
           y = "Concentration (mg/L)") +
      scale_x_continuous(breaks = seq(0,120, by = 12)) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5))

  } else {
    mcmat <- data.matrix(p_df[c("Time", 
                                  "l95_R", "u95_R",
                                  "l95_N", "u95_N")])

    this_auc_R <- calc_overlap(mcmat[, c("Time", "l95_R", "u95_R")])
    this_auc_N <- calc_overlap(mcmat[, c("Time", "l95_N", "u95_N")])
    this_auc_B <- min(
      calc_overlap(mcmat[, c("Time", "l95_R", "u95_N")]),
      calc_overlap(mcmat[, c("Time", "l95_R", "u95_N")])
    )
    prob_auc <- signif(this_auc_B / (this_auc_R + this_auc_N - this_auc_B), 4)
    pl <- ggplot(p_df, aes(x = Time)) +
      geom_ribbon(aes(ymin = l95_R, ymax = u95_R),
                  linetype = "44", fill = "magenta3", alpha = 0.3) +
      geom_ribbon(aes(ymin = l95_N, ymax = u95_N),
                  linetype = "44", fill = "cyan3", alpha = 0.3) +
      geom_line(aes(y = Sol_R)) +
      geom_line(aes(y = Sol_N)) +
      geom_line(aes(y = MED_R),
                linetype = "44", color = "purple") +
      geom_line(aes(y = MED_N),
                linetype = "44", color = "cyan4") +
      labs(title = title_txt,
           subtitle = paste0(paste("Overlap:", round(prob_auc*100, 3), "%"),
                            "\n",
                            paste("RMSE:", signif(p_df_rmse, 5))),
           y = "Concentration (mg/L)") +
      scale_x_continuous(breaks = seq(0,120, by = 12)) +
      theme_bw() +
      theme(plot.title = element_text(hjust = 0.5))
  }
  return(pl)

}

```

```{r parallel_sims}
# Parallelized simulation assessment
detectCores() # 16 cores, use 12
gc()

clust <- makeCluster(14L)
clusterEvalQ(clust, library("httk"))
clusterExport(clust, c("get_95CI_mc", "conc_fun_wsamples", "calc_overlap"))
clusterExport(clust, c("standard_parameterization", "standard_httk_preds",
                       "standard_httk_mc"))
clusterExport(clust, c("chem.physical_and_invitro.data"))
clusterExport(clust, c("ROUTE", "DOSE", "SAMPLES", "SPECIES", "TIMES", 
                       "VARPARS",
                       "CENSORPARS",
                       "HUMAN_CLINT_FUP"))

system.time(
  sim_bins <- unlist(parLapply(cl = clust, chems_available, assessment_fun))
)
stopCluster(clust)

table(sim_bins)
table(grepl("ND_SO_", sim_bins))
sum(table(sim_bins))
bindf <- data.frame(DTXSID = names(sim_bins), Bin = sim_bins,
                    CV_Clint = 0.1, CV_Funbound.plasma = 0.1, Dose = 25)
head(bindf)
rownames(bindf) <- NULL

saveRDS(bindf,
        paste0("data-raw/", SPECIES_TEXT, "_", ROUTE, INVITROUV_TEXT,
               "_simulation_bins.rds")
)

rm(clust)
rm(bindf)
gc()
```

```{r plot_all_chems}
# Parallelized simulation assessment
clust <- makeCluster(12L)
clusterEvalQ(clust, library("httk"))
clusterEvalQ(clust, library("ggplot2"))
clusterExport(clust, c("get_95CI_mc", "conc_fun_wsamples", "calc_overlap"))
clusterExport(clust, c("standard_parameterization", "standard_httk_preds",
                       "standard_httk_mc"))
clusterExport(clust, c("chem.physical_and_invitro.data"))
clusterExport(clust, c("ROUTE", "DOSE", "SAMPLES", "SPECIES", "TIMES", 
                       "VARPARS",
                       "CENSORPARS",
                       "HUMAN_CLINT_FUP"))

sim_pls <- parLapply(cl = clust, chems_available, plotting_fun)
stopCluster(clust)
length(seq_along(sim_pls))
gc()

pdf(file = paste0(Sys.getenv("FIG_DIR"), "RestNonRest_",SPECIES_TEXT,
                  ROUTE,"_Comparison_gasPBTK.pdf"),
    paper = "usr", bg = "white")
for (i in seq_along(sim_pls)) {
  print(sim_pls[[i]])
}
dev.off()
rm(sim_pls)
gc()

```

## Metabolism Landscape Tree

The goal is to find a tree structure that defines the above bins using the following data:

- Lombardo:
  - Total Clearance (human)
  - Ion state at pH 7.4
- CvT/invivoPKfit:
  - Total Clearance (from best fit, mostly rat)
- HTTK:
  - Total Clearance (human & rat)
  - Funbound.plasma and Clint (human & rat)
  - Clearance fractions (liver, kidney, lung... human & rat, in PFAS branch)
  - Distinguishable or Non-Distinguishable bins (human & rat)

Then feature engineer the following:

- HTTK vs CvT clearances in Rat (over- or under-estimating)
- Differences in Human and Rat Clearance, Funbound.plasma, and Clint
- Closest Restrictive/Nonrestrictive based on invivoPKfit best fit.

While some missing data will be incorporated in this analysis,
this will not include data where Total Clearance is not known for 2 of 3 sources.

```{r}
lombardo <- readxl::read_xlsx(
  paste0(Sys.getenv("FIG_DIR"),
         "Lombardo2018-Supplemental_82966_revised_corrected.xlsx"),
  skip = 8) |> janitor::clean_names()

table(
  lombardo$cas_number %in% suppressWarnings(get_cheminfo("CAS", model = "gas_pbtk"))
)

```

What I want to do next is directly compare the _in vivo_ data to predictions.

```{r cvt_object}
temp_data <- get_data(do_preprocess(pk(cvt)))
temp_data <- subset(temp_data, select = c("DTXSID",
                                          "Chemical_Name",
                                          "CASRN",
                                          "Species",
                                          "Media",
                                          "Route",
                                          "Dose",
                                          "Dose.Units",
                                          "N_Subjects",
                                          "Time",
                                          "Conc",
                                          "Conc_SD",
                                          "Conc.Units")) |>
  distinct()
```

```{r data-specific-parameterization}
# Each x is a grouped split of a data.frame
# Using a factor of DTXSID, Species, Media, Route, Dose
invivo_prediction <- function(
    x,
    vary.params = VARPARS,
    censored.params = CENSORPARS,
    force_human = HUMAN_CLINT_FUP
) {
  dtxsid <- unique(x[["DTXSID"]])
  species <- tools::toTitleCase(unique(x[['Species']]))
  media <- unique(x[['Media']])
  route <- unique(x[['Route']])
  dose <- unique(x[['Dose']])
  times <- unique(x[['Time']])/24 # Multiple values (in hours)

  invivo_preds <- conc_fun_wsamples(
    dtxsid = dtxsid,
    species = species,
    dose = dose,
    route = route,
    times = times,
    samples = 1000,
    force_human = force_human,
    vary.params = vary.params,
    censored.params = censored.params
  ) |> try()

  if (inherits(invivo_preds, "try-error")) return(NULL)

  # If measured media is blood need to divide CPLASMA results by Rblood2plasma
  if (media == "blood") {
    Rb2p <- standard_parameterization(
      dtxsid = dtxsid, 
      species = species,
      force_human = force_human
    )[['par_rest']][['Rblood2plasma']]

    browser()
    cols2convert <- apply(
      expand.grid(c("Sol", "l95", "MED", "u95"), c("_R", "_N")),
      MARGIN = 1,
      paste0, collapse = ""
      )

    invivo_preds <- invivo_preds |>
      dplyr::mutate(dplyr::across(dplyr::all_of(cols2convert), function(x) x / Rb2p))
  }

  cbind(
    data.frame(
    DTXSID = dtxsid,
    Species = tolower(species),
    Dose = dose,
    Route = route,
    Media = media
    ),
    as.data.frame(censored.params),
    as.data.frame(vary.params),
    invivo_preds
  )
}

```

```{r run_invivo_preds}
temp_data2 <- subset(temp_data, DTXSID %in% chems_available & Species == "rat")

split_factor <- with(
  temp_data2,
  factor(paste0(DTXSID, Species, Dose, Route, Media))
)
temp_lst <- split(temp_data2, split_factor)

# Run the cluster
clust <- makeCluster(12L)
clusterEvalQ(clust, library("httk"))
clusterEvalQ(clust, library("dplyr"))
clusterExport(clust, c("get_95CI_mc", "conc_fun_wsamples", "calc_overlap"))
clusterExport(clust, c("standard_parameterization", "standard_httk_preds",
                       "standard_httk_mc"))
clusterExport(clust, c("chem.physical_and_invitro.data"))
clusterExport(clust, c("VARPARS", "CENSORPARS", "HUMAN_CLINT_FUP"))

system.time(
  temp_lst <- parLapply(clust, temp_lst, invivo_prediction)
)
stopCluster(clust)

rm(clust)
gc()

temp_lst <- do.call(rbind, temp_lst)

temp_data3 <- left_join(temp_data2, temp_lst, relationship = "many-to-one")
saveRDS(temp_data3,
        paste0("data-raw/", SPECIES_TEXT, "_HTTK_preds_CvTdata.rds")
)
```

```{r bin-compare}
# Get the bins
bindf_rat <- readRDS("data-raw/Rat_oral_simulation_bins.rds") |>
  subset(select = c("DTXSID", "Bin"))
bindf_rat_parhuman <- readRDS("data-raw/Rat_parHuman_oral_simulation_bins.rds") |>
  subset(select = c("DTXSID", "Bin"))

afe_formula <- expression(
  paste("Average fold error: ", 10^{frac(1,n)*sum(log[10](frac(y, x)))})
)

temp_data3 |>
  filter(Sol_R > 0, Sol_N > 0) |>
  mutate(FE_R = log10(Sol_R / Conc), FE_N = log10(Sol_N / Conc)) |>
  group_by(DTXSID, Species, Media, Route, Dose) |>
  summarize(AFE_R = 10^(mean(FE_R)), AFE_N = 10^(mean(FE_N)), N_Obs = n()) |>
  ungroup() |>
  left_join(bindf_rat_parhuman) |>
  mutate(Bin = ifelse(Bin == "Distinguished", "Distinguishable", Bin)) |>
  arrange(DTXSID, Species, Media, Route, Dose) |>
  ggplot(aes(x = AFE_N, y = AFE_R)) +
  geom_point(aes(fill = log10(Dose)), shape = 21, color = "black", size = 1.2, alpha = 0.6) +
  geom_abline(slope = 1, intercept = 0) +
  geom_vline(xintercept = 1, linetype = "22", color = "grey20") +
  geom_hline(yintercept = 1, linetype = "22", color = "grey20") +
  facet_wrap(~Bin) +
  scale_fill_viridis_c() +
  labs(x = "Nonrestrictive Solution", y = "Restrictive Solution", 
       title = afe_formula) +
  scale_x_log10(labels = scales::label_log()) + scale_y_log10(labels = scales::label_log()) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "bottom",
        legend.title.position = "top")

ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "AFE_CvT_HTTK_predictions_",
                         SPECIES_TEXT, INVITROUV_TEXT,
                         ".png"),
       width = 5, height = 5)

```

### 2025-07-08 data-raw/ClearanceProject-1-DataRmd.Rmd
Updated Rmarkdown files and moved some RDS data files used.

@@
                                 species = "human",
-                                model = "3compartment2",
+                                model = "gas_pbtk",
                                 median.only = TRUE,
@@
                                 species = "rat",
-                                model = "3compartment2",
+                                model = "gas_pbtk",
                                 median.only = TRUE,

### 2025-07-08 data-raw/qb_filter_tracking.R

@@ -47,7 +47,7 @@ congruent_chems <- cvt_df |>
   ) |>
   pull(analyzed_chem_dtxsid) |> unique()
 
-incongruent_chems <- setdiff(incongruent_chems, congruent_chems)
+incongruent_chems <- base::setdiff(incongruent_chems, congruent_chems)
 
 
 qb_df_tracker <- qb_df_tracker |>
@@ -91,7 +91,7 @@ good_conc_chems <- cvt_df_qb |>
   filter(!(is.na(conc) & is.na(conc_original))) |>
   pull(analyzed_chem_dtxsid) |> unique()
 
-na_conc_chems <- setdiff(na_conc_chems, good_conc_chems)
+na_conc_chems <- base::setdiff(na_conc_chems, good_conc_chems)
 
 negative_conc_chems <- cvt_df_qb |>
   filter(!((conc < 0 | conc_original < 0) %in% FALSE)) |>
@@ -101,7 +101,7 @@ positive_conc_chems <- cvt_df_qb |>
   filter(!((conc >= 0 & conc_original >= 0) %in% FALSE)) |>
   pull(analyzed_chem_dtxsid) |> unique()
 
-negative_conc_chems <- setdiff(negative_conc_chems, positive_conc_chems)
+negative_conc_chems <- base::setdiff(negative_conc_chems, positive_conc_chems)
 
 qb_df_tracker <- qb_df_tracker |>
   mutate(
@@ -135,7 +135,7 @@ cvt_df_qb |>
   pull(analyzed_chem_dtxsid) |>
   unique() -> plbl_chem
 
-plbl_chem <- setdiff(
+plbl_chem <- base::setdiff(
   plbl_chem,
   subset(cvt_df_qb,
          subset = (conc_medium_normalized %in% c("plasma", "blood")))[["analyzed_chem_dtxsid"]]
@@ -170,7 +170,7 @@ qb_df_tracker[qb_df_tracker$include, ][["DTXSID"]] -> included_dtxsid
 winmodels <- get_winning_model(my_pk)
 count(winmodels, model)
 
-nofit_chems <- setdiff(
+nofit_chems <- base::setdiff(
   intersect(
     included_dtxsid,
     my_pk$prefit$fit_check |>
@@ -184,7 +184,7 @@ nofit_chems <- setdiff(
 )
 
 
-flat_chems <- setdiff(
+flat_chems <- base::setdiff(
   winmodels |>
[…]

### 2025-07-08 data-raw/optimizing_httk_model.Rmd

--- 2025-06-02 data-raw/optimizing_httk_model.Rmd
@@
 schems <- httk::get_cheminfo("dtxsid", species = "rat",
-                             model = "3compartment2") |>
+                             model = "gas_pbtk") |>
   suppressWarnings()
@@
 table(minicvt$analyzed_chem_dtxsid)
+```
+
+Initial test with regular models.
+
+```{r}
+test_pk2 <- pk(data = minicvt) + 
+  stat_error_model(error_group = vars(Chemical, Species)) +
+  scale_conc(dose_norm = TRUE, log10_trans = FALSE)
+
+test_pk2 <- do_data_info(test_pk)
+test_pk2 <- do_prefit(test_pk)
+test_fit2 <- do_fit(test_pk, n_cores = 4)
+winmodel2 <- get_winning_model(test_fit)
+
 ```

### 2025-08-01 data-raw/ClearanceProject-2-RelativeLikelihood.Rmd
updating data files

@@
   filter(
-    param_name %in% "kelim",
+    param_name %in% "kelim"
   ) %>%
@@
       comparison == "C_nonrest" ~ "nonrestrictive kelim vs httk nonrestrictive",
-      comparison == "C_rest" ~ "nonrestrictive kelim vs httk restrictive",
+      comparison == "C_rest" ~ "nonrestrictive kelim vs httk restrictive"
     ),

### 2025-08-01 data-raw/ClearanceProject-0-Distinguishability.Rmd

@@
 library(parallel)
+library(mirai)
+library(ctxR)
 ```
@@
 THIS_CHEMICAL = "DTXSID3024289" # A chemical to test
-# THIS_CHEMICAL = "DTXSID50873382" # Warfarin
 DOSE = 25
@@
 INVITROUV = NULL
+
 INVITROUV_TEXT = NULL
@@
 chems_available <- get_cheminfo(info = "dtxsid", species = SPECIES,
-                                model = "gas_pbtk") |> suppressWarnings()
+                                model = "gas_pbtk", suppress.messages = TRUE)
 ```
@@
 ```
+
+#### Testing
 
@@
 
+#### Testing
+
 ```{r testing_overlap}
@@
 ```
+
+#### Set-up assessment functions
 
@@
 
-```{r}
+```{r lombardo_sipes}
+
+load(file = "data-raw/CYP_Sipes2017.Rdata")
+
 lombardo <- readxl::read_xlsx(
@@
          "Lombardo2018-Supplemental_82966_revised_corrected.xlsx"),
-  skip = 8) |> janitor::clean_names()
+  skip = 8) |> 
+  janitor::clean_names() |>
+  left_join(chem.physical_and_invitro.data[c("CAS", "DTXSID")],
+            by = join_by(cas_number == CAS))
 
 table(
-  lombardo$cas_number %in% suppressWarnings(get_cheminfo("CAS", model = "gas_pbtk"))
+  lombardo$DTXSID %in% suppressWarnings(get_cheminfo("DTXSID", model = "gas_pbtk"))
 )
@@
 saveRDS(temp_data3,
-        paste0("data-raw/", SPECIES_TEXT, "_HTTK_preds_CvTdata.rds")
+        paste0("data-raw/RCdata/", SPECIES_TEXT, "_HTTK_preds_CvTdata.rds")
 )
@@
 # Get the bins
-bindf_rat <- readRDS("data-raw/Rat_oral_simulation_bins.rds") |>
+bindf_rat <- readRDS("data-raw/RCdata/Rat_oral_simulation_bins.rds") |>
   subset(select = c("DTXSID", "Bin"))
-bindf_rat_parhuman <- readRDS("data-raw/Rat_parHuman_oral_simulation_bins.rds") |>
+bindf_rat_parhuman <- readRDS("data-raw/RCdata/Rat_parHuman_oral_simulation_bins.rds") |>
   subset(select = c("DTXSID", "Bin"))
@@
   theme_bw() +
-  theme(plot.title = element_text(hjust = 0.5),
+  theme(
+    plot.title = element_text(hjust = 0.5),
     legend.position = "bottom",
-        legend.title.position = "top")
+    legend.title.position = "top",
+    legend.title = element_text(hjust = 0.5)
+  )
+
+# For this figure, try reducing bins to Distinguishable and Not Distinguishable
 
@@
 ```
+
+```{r}
+rat_physchem <- filter(
+  chem.physical_and_invitro.data,
+  DTXSID %in% bindf_rat$DTXSID
+) |>
+  select(
+    DTXSID,
+    logHenry, logMA, logP, logPwa, logWSol,
+    Rat.Clint, Rat.Funbound.plasma,
+    # pKa_Accept, pKa_Donor, Chemical.Class,
+    MP, MW
+  ) |>
+  mutate(
+    across(starts_with("Rat."), as.numeric)
+  )
+
+lombardo_trim <- lombardo |>
+  filter(!is.na(DTXSID)) |>
+  select(
+    DTXSID,
+    human_v_dss_l_kg,
+    human_cl_m_l_min_kg,
+    terminal_t1_2_h,
+    hba, hbd,
+    moka_ion_state7_4
+  ) |>
+  mutate(moka_ion_state7_4 = factor(moka_ion_state7_4))
+
+tree_rat <- bindf_rat |>
+  left_join(cyp_data, by = join_by(DTXSID == Chemical)) |>
+  left_join(rat_physchem, by = join_by(DTXSID)) |>
+  # left_join(lombardo_trim, by = join_by(DTXSID)) |>
+  select(-c(DTXSID, CAS)) |>
+  filter(!Bin %in% "ND_MC_mid") |> # Only one observation, don't want it to throw of tree
+  mutate(
+    Bin = factor(Bin),
+    Bin = forcats::fct_other(
+      Bin,
+      keep = "Distinguished", 
+      other_level = "Not Distinguishable" 
+    )
+  )
+
+table(tree_rat$Bin) 
+# Quite unbalanced, by we can try to upsampling/downsampling
+
+fit_tree_rat <- rpart::rpart(Bin ~ ., data = tree_rat)
+rpart.plot::rpart.plot(fit_tree_rat)
+preds_tree <- predict(fit_tree_rat, tree_rat, type = "class")
+caret::confusionMatrix(preds_tree, tree_rat$Bin, positive = 'Distinguished')
+
+# adjusted Clint   = Clint / Fu_hep... make sure I am using this value
+# randomForest < TRY
+# Potentially, add uncertainty factor for bins (Rest vs Non)
+
+```

### 2025-08-01 data-raw/pulling_oral_iv_data_cvtdb.Rmd

--- 2025-05-06 data-raw/pulling_oral_iv_data_cvtdb.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE,
+knitr::opts_chunk$set(
+  echo = FALSE,
   comment = NA,
   tidy.opts = list(width.cutoff = 75),
-                      tidy = TRUE)
+  tidy = TRUE
+)
 ```
@@
       host = Sys.getenv("CVT_HOST"),
-              dbname = Sys.getenv("CVT_DB_NAME"))
+      dbname = Sys.getenv("CVT_DB_NAME")
+    )
   )
@@
 query_db <- function(query = NULL, schema) {
-  if (is.null(query)) return(cat("\nMust provide a query to send"))
+  if (is.null(query)) {
+    return(cat("\nMust provide a query to send"))
+  }
   con <- postgreSQL_connection()
@@
       gsub("FROM ", paste0("FROM ", schema, "."), .) %>%
-                        gsub("JOIN (?=\\w)", paste0("JOIN ", schema, "."), ., perl = TRUE))),
-  error = function(cond){ 
+      gsub("JOIN (?=\\w)", paste0("JOIN ", schema, "."), .,
+        perl = TRUE
+      ))),
+    error = function(cond) {
       cat(paste0("\nError message: ", cond))
@@
 }
-
 ```
@@
   cli::cli_end()
-
-}
-
-quick_stats <- function(.data) {
+}
+
+quick_stats <- function(.data, old_version = FALSE) {
   stopifnot(is.data.frame(.data))
+
   cli::cli_h2("Statistics on the current data")
@@
 
-  message(paste0("Number of unique studies: ",
-                 length(unique(.data$fk_study_id))))
-  message(paste0("Number of unique series: ",
-                 length(unique(.data$fk_series_id))))
-  message(paste0("Number of unique chemicals: ",
-                 length(unique(.data$analyte_dtxsid))))
-  message(paste0("Unique Dose units: ",
-                 toString(unique(.data$dose_level_units_original))))
-  message(paste0("Unique Concentration units: ", 
-                 toString(unique(.data$conc_units_original))))
+  message(
+    "Number of unique studies: ",
+    length(unique(.data$fk_study_id))
+  )
+  message(
+    "Number of unique series: ",
+    length(unique(.data$fk_series_id))
+  )
+
+  if (old_version) {
+    message(
+      "Number of unique chemicals: ",
+      length(unique(.data$analyte_dtxsid)),
+      "\n"
+    )
+    chem_by_medium <- .data[c("conc_medium_normalized", "analyte_dtxsid")] %>%
+      filter(!is.na(analyte_dtxsid)) %>%
+      distinct()
+    chem_by_curset <- .data[c("curation_set_tag", "analyte_dtxsid")] %>%
+      filter(!is.na(analyte_dtxsid)) %>%
+      distinct()
+  } else {
+    message(
+      "Number of unique chemicals: ",
+      length(unique(.data$analyzed_chem_dtxsid)),
+      "\n"
+    )
+    chem_by_medium <- .data[c("conc_medium_normalized", "analyzed_chem_dtxsid")] %>%
+      filter(!is.na(analyzed_chem_dtxsid)) %>%
+      distinct()
+    chem_by_curset <- .data[c("curation_set_tag", "analyzed_chem_dtxsid")] %>%
+      filter(!is.na(analyzed_chem_dtxsid)) %>%
+      distinct()
+  }
+
+  message(
+    "Unique Dose units: ",
+    toString(unique(.data$dose_level_units_original)),
+    "\n"
+  )
+  if (all(is.na(.data$conc_units_normalized))) {
+    message(
+      "Unique Concentration units: ",
+      toString(unique(.data$conc_units_original)),
+      "\n"
+    )
+  } else {
+    message(
+      "Unique Concentration units: ",
+      toString(unique(.data$conc_units_normalized)),
+      "\n"
+    )
+  }
   message("Data by unique route of administration:")
@@
   print(table(.data$curation_set_tag))
-}
+  message("\n\nUnique chemicals per medium:")
+  print(table(chem_by_medium$conc_medium_normalized))
+  message("Unique chemicals per curation set:")
+  print(table(chem_by_curset$curation_set_tag))
+}
+
+chem_id_cols <- rlang::quos(
+  fk_analyzed_chemical_id, fk_dosed_chemical_id,
+  analyzed_chem_dtxsid, dosed_chem_dtxsid,
+  analyzed_chem_name, dosed_chem_name,
+  analyzed_chem_name_original, dosed_chem_name_original,
+  analyzed_chem_name_secondary_original, 
+  dosed_chem_name_secondary_original
+)
+
+unit_values_cols <- rlang::quos(
+  conc_original, conc,
+  conc_units_original, conc_units_normalized,
+  conc_sd_original, conc_sd,
+  loq, loq_units,
+  dose_level_original, dose_level_normalized,
+  dose_level_units_original, dose_volume_units,
+  dose_volume, weight_kg
+)
 
@@
 # from previous 'cvt' objects
-devtools::load_all() # So this loads the previous cvt object
 diff_log_cvt <- function(new_cvt,
                          key_id = "conc_time_id",
-                         grp_ids = c("analyte_dtxsid",
-                                     "species"),
+                         grp_ids = c(
+                           "analyzed_chem_dtxsid",
+                           "species"
+                         ),
                          notes = character(0L)) {
@@
     msg_to_write <- paste(msg_to_write, "No changes.", sep = "\t")
-    message("There are no changes from previous `cvt` data.frame, ",
-            "are you sure you want to save this?")
+    message(
+      "There are no changes from previous `cvt` data.frame, ",
+      "are you sure you want to save this?"
+    )
   } else {
@@
 
-    ###---- Check key_id changes (usually conc_time_id)
+    ### ---- Check key_id changes (usually conc_time_id)
     diff_row_add <- setdiff(new_cvt[[key_id]], cvt[[key_id]])
@@
     added_grps <- unique(
-      do.call("paste",
+      do.call(
+        "paste",
         new_cvt[which(new_cvt[[key_id]] %in% diff_row_add), grp_ids]
@@
     removed_grps <- unique(
-      do.call("paste",
+      do.call(
+        "paste",
         cvt[which(cvt[[key_id]] %in% diff_row_sub), grp_ids]
@@
         if (length(grp_vector) > 6) {
-          grp_vector <- c(grp_vector[c(1,2)],
-                              paste0("... [",
+          grp_vector <- c(
+            grp_vector[c(1, 2)],
+            paste0(
+              "... [",
               length(grp_vector) - 3,
-                                     "] more!"),
+              "] more!"
+            ),
             grp_vector[c(length(grp_vector) - 1)]
@@
       }
-      msg_to_write <- c(msg_to_write,
+      msg_to_write <- c(
+        msg_to_write,
         "New Groups added (not in previous data):",
@@
     if (length(c(diff_col_add, diff_col_sub)) == 0) {
-      msg_to_write <- c(msg_to_write,
-                        "No changes in column names.")
+      msg_to_write <- c(
+        msg_to_write,
+        "No changes in column names."
+      )
     } else if (length(diff_col_add) > 0 && length(diff_col_sub) > 0) {
@@
           for (iy in setdiff(names(y), key_id)) {
-            tmp <- merge(x[c(key_id,ix)], y[c(key_id, iy)], by=key_id)
+            tmp <- merge(x[c(key_id, ix)], y[c(key_id, iy)], by = key_id)
             if (identical(tmp[[2]], tmp[[3]])) {
@@
 
-      renamed_cols <- diff_columns(common_row_cvt[c(key_id,diff_col_sub)],
-                                   common_row_new[c(key_id, diff_col_add)])
+      renamed_cols <- diff_columns(
+        common_row_cvt[c(key_id, diff_col_sub)],
+        common_row_new[c(key_id, diff_col_add)]
+      )
       if (length(renamed_cols) > 0) {
-        msg_to_write <- c(msg_to_write,
+        msg_to_write <- c(
+          msg_to_write,
           "Renamed columns (non-exhaustive):",
-                          renamed_cols)
+          renamed_cols
+        )
       } else {
-        msg_to_write <- c(msg_to_write,
-                          "No renamed columns found.")
+        msg_to_write <- c(
+          msg_to_write,
+          "No renamed columns found."
+        )
       }
@@
     if (length(diff_col_add) > 0) {
-      msg_to_write <- c(msg_to_write,
+      msg_to_write <- c(
+        msg_to_write,
         "--------------",
         "Columns added:",
-                        diff_col_add)
+        diff_col_add
+      )
     }
     if (length(diff_col_sub) > 0) {
-      msg_to_write <- c(msg_to_write,
+      msg_to_write <- c(
+        msg_to_write,
         "______________",
         "Columns removed (from previous data):",
-                        diff_col_sub)
+        diff_col_sub
+      )
     }
@@
         common_row_cvt[diff_col_common], common_row_new[diff_col_common]
-      )) > 0
+      )
+    ) > 0
     ) || (NROW(
@@
         common_row_new[diff_col_common], common_row_cvt[diff_col_common]
-      )) > 0
+      )
+    ) > 0
     )) {
-      msg_to_write <- c(msg_to_write,
-                        "Data for same observation key_ids have changed.")
+      msg_to_write <- c(
+        msg_to_write,
+        "Data for same observation key_ids have changed."
+      )
 
@@
       for (i in test_cols) {
-        this_diff <- setdiff(common_row_new[c(key_id, i)],
-                             common_row_cvt[c(key_id, i)])
-        that_diff <- setdiff(common_row_cvt[c(key_id, i)],
-                             common_row_new[c(key_id, i)])
+        this_diff <- setdiff(
+          common_row_new[c(key_id, i)],
+          common_row_cvt[c(key_id, i)]
+        )
+        that_diff <- setdiff(
+          common_row_cvt[c(key_id, i)],
+          common_row_new[c(key_id, i)]
+        )
 
@@
           ])
-          this_grp <- paste0(this_grp[1,1:2], collapse = " ")
+          this_grp <- paste0(this_grp[1, 1:2], collapse = " ")
 
@@
             ),
-            paste0(c(i, "\t new:", this_diff[1,2], "<--\t old:", that_diff[1,2]),
-                   collapse = " "), "\n"
-          )
-        }
-      }
-    }
-    msg_to_write <- c(msg_to_write,
+            paste0(c(i, "\t new:", this_diff[1, 2], "<--\t old:", that_diff[1, 2]),
+              collapse = " "
+            ), "\n"
+          )
+        }
+      }
+    }
+    msg_to_write <- c(
+      msg_to_write,
       notes,
-                      "================================\n")
+      "================================\n"
+    )
   }
@@
 
-## Suggestions for CvTdb
-
-Repairing duplication in the chemicals table should be a priority
-that would benefit all current and future users of _CvTdb_. It would repair other
-missing identifying chemical information as well as truly have unique rows per chemical.
-Here this repair is done by making names lowercase to avoid capitalization, but there
-may be other issues arise with spaces that should be parsed prior to input into 
-the database record.
-
-The other suggestion would be to have a filled out `conc_units_normalized` column in
-the `series` table. Although it is assumed to be _mg/kg_, it would be nice to have this
-confirmed. Here `conc_units_original` is compared with the ratio of `conc` to `conc_original`
-to get a sense of whether the units for `conc` were reasonably converted to
-_mg/kg_. This seems like it could reasonably be a part of the QA process.
-
-Besides these two suggestions, there are only a couple other changes in the data that 
-are made throughout this document but these pertain to specific records rather than
-the entire database, so I think they are a little bit lower on the priority list.
-
 ```{r SQL_queries, warning=FALSE}
@@
 # Note that this uses an ALIAS for each table which is later specified in
-# the FROM and LEFT JOIN statments
+# the FROM and LEFT JOIN statements
+series_chems <- paste0(
+  "SELECT DISTINCT a.id, a.fk_analyzed_chemical_id, ",
+  "b.analyzed_chem_dtxsid, b.analyzed_chem_name_original, ",
+  "b.analyzed_chem_name_secondary_original, ",
+  "b.analyzed_chem_casrn, b.analyzed_chem_name, ",
+  "a.time_units_original, a.conc_units_original, ",
+  "a.conc_units_normalized, a.loq, a.loq_units, ",
+  "a.n_subjects_in_series, a.radiolabeled, a.fk_study_id, ",
+  "a.qc_notes, a.qc_status, a.qc_flags, c.conc_medium_normalized ",
+  "FROM series a ",
+  "LEFT JOIN (SELECT id, dsstox_substance_id AS analyzed_chem_dtxsid, ",
+  "chemical_name_original AS analyzed_chem_name_original, ",
+  "chemical_name_secondary_original AS analyzed_chem_name_secondary_original, ",
+  "dsstox_casrn as analyzed_chem_casrn, preferred_name AS analyzed_chem_name ",
+  "FROM chemicals) AS b ON a.fk_analyzed_chemical_id = b.id ",
+  "LEFT JOIN conc_medium_dict AS c ON a.fk_conc_medium_id = c.id"
+)
+
+study_docs <- paste0(
+  "SELECT a.id, a.fk_extraction_document_id, a.fk_dosed_chemical_id, ",
+  "b.pmid, b.doi, b.year, b.other_study_identifier, ",
+  "b.url, b.extracted, b.curation_set_tag ",
+  "FROM studies a ",
+  "LEFT JOIN documents b ON a.fk_extraction_document_id = b.id"
+)
+
+audit_query <- query_db(
+  paste0(
+    "SELECT DISTINCT * FROM cvt_audit ",
+    "WHERE fk_table_name IN ('documents', 'series', 'studies')"
+  ),
+  "cvt"
+)
+study_query <- query_db(study_docs, "cvt")
+series_query <- query_db(series_chems, "cvt")
+dtxsid_query <- query_db("SELECT DISTINCT * FROM chemicals", "cvt") %>%
+  mutate(
+    across(ends_with("_id"), as.character),
+    across(contains("_name"), \(x) {
+      stringr::str_to_lower(x) |>
+        force_ascii_quotes() |>
+        # trim whitespace around hyphens
+        stringr::str_replace_all("\\s*-\\s*", "-") |>
+        # comma-separate forms like 3'6 into 3',6
+        stringr::str_replace_all("(?<=\\d)'(?=\\d)", "',") |>
+        # fix some bracket cases
+        stringr::str_replace_all("\\[3\\]h", "[3h]") |>
+        stringr::str_replace_all("benzo\\[a\\]", "benzo(a)") |>
+        # adds a space after square bracket separator
+        stringr::str_replace_all("](?!\\s|-)", "] ")
+    })
+  )
+
+select_chems <- subset(
+  dtxsid_query,
+  select = c(
+    "id",
+    "dsstox_substance_id",
+    "dsstox_casrn",
+    "preferred_name",
+    "chemical_name_original",
+    "chemical_name_secondary_original"
+  )
+)
+
+# Surveying the non-equal chemical id landscape:
+series_query |>
+  inner_join(study_query, by = join_by(fk_study_id == id)) |>
+  distinct(fk_analyzed_chemical_id, fk_dosed_chemical_id, curation_set_tag) |>
+  count(fk_analyzed_chemical_id == fk_dosed_chemical_id)
+
+unequal_chem_ids <- series_query |>
+  inner_join(study_query, by = join_by(fk_study_id == id)) |>
+  distinct(fk_analyzed_chemical_id, fk_dosed_chemical_id, curation_set_tag) |>
+  filter(fk_analyzed_chemical_id != fk_dosed_chemical_id) |>
+  left_join(
+    rename_with(select_chems, ~ paste0("analyzed_", .x)),
+    by = join_by(fk_analyzed_chemical_id == analyzed_id)
+  ) |>
+  left_join(
+    rename_with(select_chems, ~ paste0("dosed_", .x)),
+    by = join_by(fk_dosed_chemical_id == dosed_id)
+  ) |>
+  glimpse()
+
+count(
+  unequal_chem_ids,
+  analyzed_dsstox_substance_id == dosed_dsstox_substance_id,
+  analyzed_dsstox_casrn == dosed_dsstox_casrn,
+  analyzed_preferred_name == dosed_preferred_name,
+  analyzed_chemical_name_original == dosed_chemical_name_original,
+  analyzed_chemical_name_secondary_original == dosed_chemical_name_secondary_original
+) |>
+  rename(
+    "Equal DTXSID" = 1, "Equal CASRN" = 2, "Equal Preffered Name" = 3,
+    "Equal Recorded Name" = 4, "Equal Secondary Recorded Name" = 5, "N" = 6
+  )
+
+# Are any names equal???
+count(
+  unequal_chem_ids,
+  analyzed_dsstox_substance_id == dosed_dsstox_substance_id |
+    analyzed_dsstox_casrn == dosed_dsstox_casrn |
+    analyzed_preferred_name == dosed_preferred_name |
+    analyzed_chemical_name_original == dosed_chemical_name_original |
+    analyzed_chemical_name_secondary_original == dosed_chemical_name_secondary_original
+) |>
+  rename(
+    "Any" = 1, "N" = 2
+  ) |>
+  mutate(
+    Any = ifelse(Any %in% TRUE, "Some Identical", "None Identical")
+  ) |>
+  group_by(Any) |>
+  summarize(N = sum(N)) |>
+  pivot_wider(names_from = Any, values_from = N)
+
+# Let's parse through with those "Some Identical" identifiers first
+unequal_chem_ids |>
+  filter(
+    analyzed_dsstox_substance_id == dosed_dsstox_substance_id |
+      analyzed_dsstox_casrn == dosed_dsstox_casrn |
+      analyzed_preferred_name == dosed_preferred_name |
+      analyzed_chemical_name_original == dosed_chemical_name_original |
+      analyzed_chemical_name_secondary_original == dosed_chemical_name_secondary_original
+  ) |>
+  group_by(fk_analyzed_chemical_id, fk_dosed_chemical_id) |>
+  summarize(
+    same_dtxsid = if_else(
+      analyzed_dsstox_substance_id == dosed_dsstox_substance_id,
+      analyzed_dsstox_substance_id, NA_character_, missing = NA_character_
+    ),
+    same_casrn = if_else(
+      analyzed_dsstox_casrn == dosed_dsstox_casrn,
+      analyzed_dsstox_casrn, NA_character_, NA_character_
+    ),
+    same_preferred_name = if_else(
+      analyzed_preferred_name == dosed_preferred_name,
+      analyzed_preferred_name, NA_character_, NA_character_
+    ),
+    same_chem_name = if_else(
+      analyzed_chemical_name_original == dosed_chemical_name_original,
+      analyzed_chemical_name_original, NA_character_, NA_character_
+    ),
+    same_chem_name_secondary = if_else(
+      analyzed_chemical_name_secondary_original == dosed_chemical_name_secondary_original,
+      analyzed_chemical_name_secondary_original, NA_character_, NA_character_
+    )
+  ) |>
+  rowwise() |>
+  mutate(
+    likely_same = sum(!is.na(c_across(starts_with("same_"))))
+  ) |>
+  ungroup() |>
+  arrange(same_dtxsid, same_casrn, same_preferred_name, same_chem_name,
+          same_chem_name_secondary) |>
+  View("Similar IDs")
+# There are two ways the identifiers may be duplicated,
+# shown here between rows and columns
+
+# There are a lot of duplicate DTXSIDs
 query <- paste0(
@@
   "l.analyzed_chem_casrn, l.analyzed_chem_name, ",
-
+  "l.analyzed_chem_name_secondary_original, ",
   "b.time_units_original, b.conc_units_original, ",
@@
   "k.dosed_chem_casrn, k.dosed_chem_name, ",
-
+  "k.dosed_chem_name_secondary_original, ",
   "c.dose_volume, c.dose_volume_units, c.dose_vehicle, ",
@@
   "c.fasting_period, ",
-  "c.dose_level_normalized, c.dose_level_original, c.dose_level_units_original, ",
+  "c.dose_level_normalized, c.dose_level_original, ",
+  "c.dose_level_units_original, c.dose_level_units_normalized, ",
   ## conc_medium dictionary fields
@@
   # Rename chemical fields for dosed vs. analyzed chemical record foreign keys
-  "LEFT JOIN (SELECT id, dsstox_substance_id as dosed_chem_dtxsid, ",
-  "chemical_name_original as dosed_chem_name_original, ", 
-  "dsstox_casrn as dosed_chem_casrn, preferred_name as dosed_chem_name ",
-  "FROM chemicals) as k ON c.fk_dosed_chemical_id = k.id ",
-  "LEFT JOIN (SELECT id, dsstox_substance_id as analyzed_chem_dtxsid, ",
-  "chemical_name_original as analyzed_chem_name_original, ",
-  "dsstox_casrn as analyzed_chem_casrn, preferred_name as analyzed_chem_name ",
-  "FROM chemicals) as l ON b.fk_analyzed_chemical_id = l.id ",
+  "LEFT JOIN (SELECT id, dsstox_substance_id AS dosed_chem_dtxsid, ",
+  "chemical_name_original AS dosed_chem_name_original, ",
+  "chemical_name_secondary_original AS dosed_chem_name_secondary_original, ",
+  "dsstox_casrn AS dosed_chem_casrn, preferred_name AS dosed_chem_name ",
+  "FROM chemicals) AS k ON c.fk_dosed_chemical_id = k.id ",
+  "LEFT JOIN (SELECT id, dsstox_substance_id AS analyzed_chem_dtxsid, ",
+  "chemical_name_original AS analyzed_chem_name_original, ",
+  "chemical_name_secondary_original AS analyzed_chem_name_secondary_original, ",
+  "dsstox_casrn AS analyzed_chem_casrn, preferred_name AS analyzed_chem_name ",
+  "FROM chemicals) AS l ON b.fk_analyzed_chemical_id = l.id ",
 
@@
   "WHERE h.administration_route_normalized IN ('iv', 'oral') AND ",
-  "(i.conc_medium_normalized IN ('blood', 'plasma', 'excreta') OR ",
-  "i.conc_medium_original IN ('blood', 'plasma', 'excreta'))"
-)
-
-sql_query <- query_db(query = query,
-         schema = "cvt")
-
-# Need to change column names for this
-{
+  "(i.conc_medium_normalized IN ('blood', 'plasma') OR ",
+  "i.conc_medium_original IN ('blood', 'plasma')) AND ",
+  "(j.dose_frequency_normalized IN ('Once') OR e.curation_set_tag IN ('CVT_Showa'))"
+)
+
+sql_query <- query_db(query = query, schema = "cvt")
+
+# Need to change the column name for this
 names(sql_query)[1] <- "conc_time_id"
-}
-
-# Unfortunately, there are some "fancy" or curly quotes that need to be replaced
-# with "straight" quotes to be more machine read-able
-force_straight_quotes <- function(x) {
-  temp <- gsub("(’|′)", "'", x)
-  temp <- gsub("(, | ,)", ",", temp)
-  return(temp)
-}
-force_straight_quotes("3,3’,4,4’-tetrachloro-5-biphenylol")
+
+cvtdb_original <- sql_query
+save(cvtdb_original, file = "data/cvtdb_original.rda", compress = "bzip2")
+```
+
+```{r harmonizing}
+load("data/cvtdb_original.rda")
+sql_query <- cvtdb_original
+rm(cvtdb_original)
 
@@
   mutate(
-    across(ends_with("id"), as.character),
     # Note that sometimes fk_test_chemical_id is NA
-    across(all_of(c("time_original",
+    across(all_of(c(
+      "time_original",
       "time_hr",
@@
       "dose_level_normalized",
-                    "loq")), as.numeric),
+      "loq"
+    )), as.numeric),
     # conc, conc_sd_original, and conc_original
@@
     sex = tolower(sex),
-    analyte_name_original = force_straight_quotes(tolower(analyte_name_original)),
-    analyte_name_secondary_original = force_straight_quotes(tolower(
-      analyte_name_secondary_original
+    across(contains("chem_name"), \(x) {
+      stringr::str_to_lower(x) |>
+        force_ascii_quotes() |>
+        # trim whitespace around hyphens
+        stringr::str_replace_all("\\s*-\\s*", "-") |>
+        # comma-separate forms like 3'6 into 3',6
+        stringr::str_replace_all("(?<=\\d)'(?=\\d)", "',") |>
+        # fix some bracket cases
+        stringr::str_replace_all("\\[3\\]h", "[3h]") |>
+        stringr::str_replace_all("\\[a\\]pyr", "(a)pyr") |>
+        stringr::str_remove_all(" \\(aids\\)$") |>
+        # adds a space after square bracket separator
+        stringr::str_replace_all("](?!\\s|-)", "] ")
+    }),
+    dose_volume_units = ifelse(
+      dose_volume_units %in% c("NR", "ND"),
+      NA_character_,
+      gsub(" / ", "/", gsub("ml", "mL", dose_volume_units))
+    ),
+    dose_volume = signif(as.numeric(dose_volume), digits = 7),
+    dose_duration_units = trimws(dose_duration_units),
+    dose_duration = as.numeric(stringr::str_extract(dose_duration,
+      pattern = "^\\d+"
     )),
-    dose_volume_units = stringr::str_extract(dose_volume,
-                                    pattern = "(?<=[:space:]).+"),
-    dose_volume = as.numeric(stringr::str_extract(dose_volume,
-                                         pattern = "^(\\d|\\.)*")),
-    dose_duration_units = stringr::str_extract(dose_duration,
-                                      pattern = "(?<=[space]).+"),
-    dose_duration = as.numeric(stringr::str_extract(dose_duration,
-                                pattern = "^\\d")),
+    dose_frequency_normalized = "Once", # Showa is not annotated
     radiolabeled = ifelse(is.na(radiolabeled), FALSE, as.logical(radiolabeled)),
-    n_subjects_normalized = ifelse(n_subjects_in_series %in% "NR", NA_real_,
-      as.numeric(stringr::str_extract(n_subjects_in_series,
-                                                 pattern = "\\d+")))
-  )
+    # for n_subject ranges, take integer value of median
+    # otherwise pull number or NA
+    n_subjects_normalized = case_when(
+      n_subjects_in_series %in% "NR" ~ NA_real_,
+      grepl("-", n_subjects_in_series) ~ floor(mean(
+        as.numeric(unlist(strsplit(n_subjects_in_series, split = "-"))),
+        na.rm = TRUE
+      )),
+      .default = as.numeric(
+        stringr::str_extract(n_subjects_in_series, pattern = "\\d+")
+      )
+    )
+  )
+```
+
+## Some data malformations
+
+There are some duplications in chemical entries such that not all unique chemical ids
+represent a unique DTXSID, but rather a unique original name entry.
+To fix this, when DTXSIDs for dosed and analyzed chemicals match, I will
+be setting `fk_dosed_chemical_id` to `fk_analyzed_chemical_id`.
+
+Note that we can "de-duplicate" these in two ways. Take for instance:
+
+|analyzed_chem_id|dosed_chem_id|analyzed_dtxsid|dosed_dtxsid  |
+|---------------:|:------------|--------------:|:-------------|
+| 893            | 892         | DTXSID0021383 | DTXSID0021383|
+| 929            | 893         | DTXSID0021383 | DTXSID0021383|
+
+This is duplicated across rows and between rows! Ideally, we would take the
+"most complete" record if we are convinced that these are the same chemical.
+
+There is also some radiolabeling experiments that aren't described as such.
+We can use `stringr::str_detect(x,"(13|14)c")` to recode `radiolabeled = TRUE`
+for these.
+
+Then we should address the fact that the `invivoPKfit_2.0.0` version of the `cvt`
+object has 228 chemicals, while the recent query only has 145. This is a
+difference of 83.
+
+By hand, I can add back the DTXSIDs for about 15 chemicals. Some of these will
+be ChEMBLIDs actually.
+
+```{r malformed_data}
+# First quick check to see if any chemical_ids are NA
+# Should be FALSE for both of these!
+any(is.na(cvt_df$fk_analyzed_chemical_id))
+any(is.na(cvt_df$fk_dosed_chemical_id))
+
+cli::cli_inform(
+  "{length(unique(cvt_df$analyzed_chem_dtxsid))} unique analyzed_dtxsids"
+)
+
+cli::cli_inform(
+  "{length(unique(cvt_df$dosed_chem_dtxsid))} unique dosed dtxsids"
+)
+
+# Fix Radiolabeled ones!
+cvt_df %>%
+  distinct(analyzed_chem_name_original, dosed_chem_name_original, radiolabeled) %>%
+  filter(!radiolabeled) %>%
+  filter(stringr::str_detect(dosed_chem_name_original, "((13|14)c|3h)"))
+cvt_df %>%
+  distinct(analyzed_chem_name_original, dosed_chem_name_original, radiolabeled) %>%
+  filter(!radiolabeled) %>%
+  filter(stringr::str_detect(analyzed_chem_name_original, "((13|14)c|3h)"))
 
 cvt_df <- cvt_df %>%
-  mutate(conc_medium_normalized = ifelse(is.na(conc_medium_normalized),
-                                         conc_medium_original,
-                                         conc_medium_normalized))
-
-# There are some missing DTXSIDs that we need to fix
+  mutate(
+    radiolabeled = ifelse(
+      stringr::str_detect(dosed_chem_name_original, "((13|14)c|3h)") |
+        stringr::str_detect(analyzed_chem_name_original, "((13|14)c|3h)"),
+      TRUE,
+      radiolabeled
+    )
+  )
+# There is a distinct challenge when handling radiolabelled data but these will be
+# filtered out later for our purposes.
+# Pre-emptive filtering to cut down workload
+cvt_df <- filter(cvt_df, !(radiolabeled %in% TRUE))
+
+cvt_df$analyzed_chem_name_original[
+  grepl("\\[\\w\\]", cvt_df$analyzed_chem_name_original)
+] |> unique()
+
+cvt_df$dosed_chem_name_original[
+  grepl("\\[\\w\\]", cvt_df$dosed_chem_name_original)
+] |> unique()
+
+cvt_df |> 
+  distinct(!!!chem_id_cols) |> 
+  count(is.na(analyzed_chem_dtxsid), is.na(dosed_chem_dtxsid))
+# Most have both dosed and chemical dtxsid
+# Are the 'NA' values for analyzed_chem_dtxsid that have dosed_chem_dtxsid the same?
+
+cvt_df <- cvt_df |>
+  mutate(
+    # fix misspellings
+    analyzed_chem_name_original = str_replace_lst(
+      analyzed_chem_name_original,
+      c(
+        "paracetmol" = "paracetamol",
+        "deacetyl diltiazem" = "desacetyl diltaiazem",
+        "deacetyl n-monodesmethyl diltiazem" = "desacetyl n-monodesmethyl diltiazem",
+        "2,2',4,4',5,5'-hexachlorobiphenyl" = "2,4,5,2',4',5'-hexachlorobiphenyl",
+        "valproate \\(vpa\\)" = "valproic acid",
+        "clotiapine" = "clothiapine"
+      )
+    ),
+    dosed_chem_name_original = str_replace_lst(
+      dosed_chem_name_original,
+      c(
+        "paracetmol" = "paracetamol",
+        "deacetyl diltiazem" = "desacetyl diltaiazem",
+        "deacetyl n-monodesmethyl diltiazem" = "desacetyl n-monodesmethyl diltiazem",
+        "2,2',4,4',5,5'-hexachlorobiphenyl" = "2,4,5,2',4',5'-hexachlorobiphenyl",
+        "clotiapine" = "clothiapine"
+      )
+    ),
+    # Missing DTXSIDs I found
+    dosed_chem_dtxsid = case_match_lst(
+      dosed_chem_name_original,
+      c(
+        "4,4'-sulfonylbisphenol-d8" = "DTXSID3022409",
+        "(+-)-metoprolol tartrate" = "DTXSID9037248",
+        "antipyrene" = "DTXSID6021117",
+        "3'-azido-3'-deoxythymidine" = "DTXSID8020127",
+        "2,4,5,2',4',5'-hexachlorobiphenyl" = "DTXSID2032180"
+      ),
+      dosed_chem_dtxsid
+    ),
+    analyzed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name_original,
+      c(
+        "fluorotelomer acid 7+3" = "DTXSID20874028",
+        "valproic acid" = "DTXSID6023733",
+        "s-(-)-metoprolol" = "DTXSID60230861",
+        "r-(+)-metoprolol" = "DTXSID20230862",
+        "paracetamol" = "DTXSID2020006"
+      ),
+      analyzed_chem_dtxsid
+    ),
+    # check name matches
+    analyzed_chem_dtxsid = ifelse(
+      is.na(analyzed_chem_dtxsid) &
+        analyzed_chem_name_original == dosed_chem_name_original,
+      dosed_chem_dtxsid,
+      analyzed_chem_dtxsid
+    )
+  )
+
+quick_stats(cvt_df)
+# quick_stats(cvt_2.0.0, old_version = FALSE)
+# Note unique chemical counts
+
+cvt_df |>
+  distinct(!!!chem_id_cols) |> 
+  filter(is.na(analyzed_chem_dtxsid)) |>
+  View("ID-less")
+# Anything without an ID for analyzed_chemical is likely a metabolite/control of sorts
+# So... I filter it out.
+cvt_df <- cvt_df |> 
+  filter(!is.na(analyzed_chem_dtxsid))
+
+quick_stats(cvt_df)
+
+# Now we need to pre-emptively address the chemicals that have different
+# IDs but are actually the same chemical or represent the same chemical during the experiment
+# This includes primarily: SALTS and ENANTIOMERS
 cvt_df %>%
-    filter(is.na(analyte_dtxsid),
-           !(radiolabeled %in% TRUE)) %>%
-  distinct(fk_analyzed_chemical_id,fk_dosed_chemical_id,
-           analyte_dtxsid, analyte_name_original,
-           analyte_name_secondary_original) %>%
-  View("NA_dtxsid")
-
-dtxsid_query <- paste0(
-  "SELECT distinct * FROM chemicals"
-)
-
-dtxsid_query <- query_db(query = dtxsid_query,
-         schema = "cvt")
-
-dtxsid_query <- dtxsid_query %>%
-  filter(id %in% as.numeric(
-    union(cvt_df$fk_analyzed_chemical_id, cvt_df$fk_dosed_chemical_id))
+  filter(
+    fk_analyzed_chemical_id != fk_dosed_chemical_id,
+    analyzed_chem_dtxsid != dosed_chem_dtxsid
   ) %>%
-  mutate(id = as.character(id),
-         chemical_name_original = force_straight_quotes(tolower(
-           chemical_name_original
-         )),
-         chemical_name_secondary_original = force_straight_quotes(tolower(
-           chemical_name_secondary_original
-         ))
-  )
-
-cvt_df %>% 
-  filter(fk_analyzed_chemical_id != fk_dosed_chemical_id,
-         !(radiolabeled %in% TRUE)) %>%
-  distinct(fk_analyzed_chemical_id,fk_dosed_chemical_id,fk_test_chemical_id) %>%
-  left_join(dtxsid_query %>%
-              select("fk_analyzed_chemical_id" = "id",
-                     "analyzed_chemical_name" = "chemical_name_original")) %>%
-  left_join(dtxsid_query %>%
-              select("fk_dosed_chemical_id" = "id",
-                     "dosed_chemical_name" = "chemical_name_original")) %>%
-  View("errors")
-
-# Rather than hope most of these chemicals have dtxsids within CvTdb,
-# I cross-referenced it with the CompTox database batch search.
-dtxsid_batch_idless <- readr::read_csv(
-  "data-raw/CCD-Batch-Search_2025-04-17_DTXSIDless.csv",
-  na = "N/A"
-) %>% filter(!is.na(DTXSID)) %>%
-  select("dsstox_substance_id" = "DTXSID",
-         "chemical_name_original" = "INPUT") %>%
-  distinct()
-
-quick_message(c(
-  "Erroneous DTXSID assignments (identified via duplication):",
-  "perfluorohexanesulfonate == DTXSID80873012",
-  "tacrolimus == DTXSID5046354",
-  "hippuric acid == DTXSID9046073"
-))
-
-dtxsid_batch_idless <- dtxsid_batch_idless %>%
-  mutate(dsstox_substance_id = case_when(
-    chemical_name_original == "perfluorohexanesulfonate" ~ "DTXSID80873012",
-    chemical_name_original == "tacrolimus" ~ "DTXSID5046354",
-    chemical_name_original == "hippuric acid" ~ "DTXSID9046073",
-    .default = dsstox_substance_id
-  )) %>% distinct()
-
-# Fixing the missing DTXSID to prevent premature filtering
-cvt_df <- cvt_df %>%
-  left_join(
-    dtxsid_batch_idless,
-    by = join_by(analyte_name_original == chemical_name_original)
+  distinct(
+    analyzed_chem_name_original, dosed_chem_name_original,
+    fk_analyzed_chemical_id, fk_dosed_chemical_id,
+    analyzed_chem_dtxsid, dosed_chem_dtxsid
   ) %>%
-  mutate(analyte_dtxsid = coalesce(analyte_dtxsid, dsstox_substance_id)) %>%
-  select(!dsstox_substance_id)
-
-quick_stats(cvt_df)
-
-# Now we need to pre-emptively address the chemicals that have different
-# dosed_id and analyzed_ids but are actually the same chemical
-quick_message(c(
-  "The following have resolvable errors:",
-  "If dosed chemical id is 47, change this to 46 to match analyte id. tamoxifen, salt dosed.",
-  "If dosed chemical id is 893, change this to 929 to match analyte id. trichloroethylene, duplicate.",
-  "If dosed chemical id is 671, change to 672 to match analyte id. PFHS, salt dosed.",
-  "If dosed chemical id is 673, change to 675 to match analyte id. PFNA, capitalization.",
-  "If dosed chemical id is 674, change to 676 to match analyte id, PFDA, capitalization."
-))
-
+  arrange(analyzed_chem_name_original) %>%
+  # head()
+View()
+
+# The other issue with salts is sometimes they will appear in analyzed chemical names!
+# Compose regular expressions looking for possible salts.
+mcations <- paste(
+  c("(hydrogen", "lithium", "sodium", "potassium", "rubidium", "cesium",
+    "silver", "beryllium", "magnesium", "strontium", "barium", "radium",
+    "zinc", "calcium", "aluminum)"),
+  collapse = "|"
+)
+manions <-  paste(
+  c("(hydride", "fluoride", "chloride", "bromide", "iodide", "oxide",
+    "sulfide", "selenide", "telluride", "nitride", "phosphiide",
+    "arsenide)"),
+  collapse = "|"
+)
+
+pa_ions <- paste(
+  c(
+    "(ammonium", "nitrate", "nitrite", "chromate", "dichromate", "cyanide",
+    "permanganate", "hydroxide", "peroxide", " amide", "carbonate", "sulfate",
+    "sulfite", "oxalate", "phosphate", "phosphite", "thiosulfate",
+    "arsenate", "selenate", "silicate", "tartrate", "perchlorate", "acetate",
+    "chlorate", "chlorite", "hypochlorite", "periodate", "iodate", "hypoiodite",
+    "bromate", "hypobromite", "binoxolate", "borate", "hydrochloride", "thiocyanate)"
+  ),
+  collapse = "|"
+)
+
+cvt_df |>
+  distinct(!!!chem_id_cols) |>
+  filter(
+    stringr::str_detect(analyzed_chem_name_original, pattern = mcations) |
+      stringr::str_detect(analyzed_chem_name_original, pattern = manions) |
+      stringr::str_detect(analyzed_chem_name_original, pattern = pa_ions) |
+      stringr::str_detect(analyzed_chem_name, pattern = mcations) |
+      stringr::str_detect(analyzed_chem_name, pattern = manions) |
+      stringr::str_detect(analyzed_chem_name, pattern = pa_ions) |
+      stringr::str_detect(dosed_chem_name_original, pattern = mcations) |
+      stringr::str_detect(dosed_chem_name_original, pattern = manions) |
+      stringr::str_detect(dosed_chem_name_original, pattern = pa_ions) |
+      stringr::str_detect(dosed_chem_name, pattern = mcations) |
+      stringr::str_detect(dosed_chem_name, pattern = manions) |
+      stringr::str_detect(dosed_chem_name, pattern = pa_ions)
+  ) |>
+  View("Potential salt errors")
+
+# Method: To make DTXSID == DTXSID, salt DTXSIDs will be replaced with
+# non-salt DTXSIDs.
+cvt_df <- cvt_df |> 
+  mutate(
+    analyzed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name,
+      c(
+        "methadone hydrochloride" = "DTXSID7023273",
+        "ammonium perfluorooctanoate" = "DTXSID40892486",
+        "sodium nitrite" = "DTXSID5024219",
+        "potassium perfluorobutanesulfonate" = "DTXSID5030030", # acid is more stable
+        "potassium perfluorohexanesulfonate" = "DTXSID80873012"
+      ),
+      analyzed_chem_dtxsid
+    ),
+    dosed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name,
+      c(
+        "methadone hydrochloride" = "DTXSID7023273",
+        "ammonium perfluorooctanoate" = "DTXSID40892486",
+        "sodium nitrite" = "DTXSID5024219",
+        "potassium perfluorobutanesulfonate" = "DTXSID5030030", # acid is more stable
+        "potassium perfluorohexanesulfonate" = "DTXSID80873012",
+        "bosentan" = "DTXSID7046627",
+        "hexobarbital" = "DTXSID9023122",
+        "quinidine" = "DTXSID4023549"
+      ),
+      dosed_chem_dtxsid
+    ),
+    dosed_chem_dtxsid = case_match_lst(
+      dosed_chem_name,
+      c(
+        "imipramine hydrochloride" = "DTXSID1043881",
+        "ondansetron hydrochloride dihydrate" = "DTXSID8023393",
+        "thiopental sodium" = "DTXSID1023653",
+        "phenobarbital" = "DTXSID5021122",
+        "phenobarbital sodium" = "DTXSID5021122",
+        "potassium perfluorohexanesulfonate" = "DTXSID80873012",
+        "tamoxifen citrate" = "DTXSID1034187",
+        "sodium nitrite" = "DTXSID5024219"
+      ),
+      dosed_chem_dtxsid
+    ),
+    analyzed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name_original,
+      c(
+        "formetanate hydrochloride" = "DTXSID9041990",
+        "propamocarb hydrochloride" = "DTXSID1040295",
+        "pyrithiobac sodium" = "DTXSID3037703",
+        "tamoxifen citrate" = "DTXSID1034187"
+      ),
+      analyzed_chem_dtxsid
+    ),
+    dosed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name_original,
+      c(
+        "formetanate hydrochloride" = "DTXSID9041990",
+        "propamocarb hydrochloride" = "DTXSID1040295",
+        "pyrithiobac sodium" = "DTXSID3037703",
+        "valproic acid" = "DTXSID6023733",
+        # add the enantiomers of metoprolol here
+        "r-(+)-metoprolol" = "DTXSID20230862",
+        "s-(-)-metoprolol" = "DTXSID60230861"
+      ),
+      dosed_chem_dtxsid
+    )
+  ) # This is imperfect but will do.
+
+cvt_df |> 
+  distinct(analyzed_chem_dtxsid, dosed_chem_dtxsid) |> 
+  count(analyzed_chem_dtxsid == dosed_chem_dtxsid)
+cvt_df |>
+  distinct(!!!chem_id_cols) |> 
+  filter(analyzed_chem_dtxsid != dosed_chem_dtxsid) |> 
+  View()
+
+## Now that we've added some missing DTXSIDs, redo the chemical id
 cvt_df <- cvt_df %>%
   rowwise() %>%
-  mutate(fk_dosed_chemical_id = case_when(
-    fk_dosed_chemical_id == "47" &&
-      fk_analyzed_chemical_id == "46" ~ "46",
-    fk_dosed_chemical_id == "893" &&
-      fk_analyzed_chemical_id == "929" ~ "929",
-    fk_dosed_chemical_id == "671" &&
-      fk_analyzed_chemical_id == "672" ~ "672",
-    fk_dosed_chemical_id == "673" &&
-      fk_analyzed_chemical_id == "673" ~ "673",
-    fk_dosed_chemical_id == "674" &&
-      fk_analyzed_chemical_id == "676" ~ "676",
-    .default = fk_dosed_chemical_id
+  mutate(fk_dosed_chemical_id = ifelse(
+    identical(analyzed_chem_dtxsid, dosed_chem_dtxsid),
+    fk_analyzed_chemical_id,
+    fk_dosed_chemical_id
   )) %>%
@@
 
-# glimpse(dq_cols)
-
-# names(cvt_df)
-
-# study_query <- query_db(query = "SELECT distinct * FROM studies",
-#          schema = "cvt")
+any(is.na(cvt_df$fk_analyzed_chemical_id))
+any(is.na(cvt_df$fk_dosed_chemical_id))
 
 quick_stats(cvt_df)
-
-# For figuring out whether there was a change from the original units to reported conc
-# And only keep non-radiolabeling experiments, where analyte_dtxsid is known
-# and where analyzed chemical is equivalent to the dosed chemical
-cvt_df <- cvt_df %>% mutate(conc_unit_norm_factor = signif(conc/conc_original, 1),
-                            .after = conc_units_normalized)
-
-cat("Current # chemicals: ", length(unique(cvt_df$analyte_dtxsid)), "\n")
-cat("Number of chemicals where analyte_dtxsid is NA: ",
-    sum(is.na(unique(cvt_df[c("fk_analyzed_chemical_id",
-                               "analyte_dtxsid")])$analyte_dtxsid)),
-    "\n")
-
-cat("Number of radiolabelling experiments: ",
-    sum(distinct(cvt_df, analyte_dtxsid, radiolabeled) %>% pull(radiolabeled) %>%
-          {. %in% TRUE}
-        )
-    )
-distinct(cvt_df, analyte_dtxsid, analyte_name_original, radiolabeled) %>%
-  filter(radiolabeled %in% TRUE, !is.na(analyte_dtxsid))
-
-cat("Number of chemicals with non-matching ids ",
-    cvt_df %>%
-      filter(!is.na(analyte_dtxsid),
-             !(radiolabeled %in% TRUE),
-             fk_analyzed_chemical_id != fk_dosed_chemical_id) %>%
-      distinct(analyte_dtxsid) %>%
-      NROW()
-)
-
-cvt_df <- cvt_df %>%
-  filter(!(radiolabeled %in% TRUE),
-         !is.na(analyte_dtxsid),
-         (fk_analyzed_chemical_id == fk_dosed_chemical_id)) %>%
-  distinct()
-
-quick_message(text = c("Filtering out:",
-                       "Missing {.code analyte_dtxsid}",
-                       "Radiolabeling experiments",
-                       "Data where the analyzed chemicals and dosed chemicals are different"))
-quick_stats(cvt_df)
-diff_log_cvt(cvt_df)
 ```
@@
 ```{r preliminary_filtering}
+cvt_df <- cvt_df %>%
+  filter(
+    !is.na(analyzed_chem_dtxsid),
+    (fk_analyzed_chemical_id == fk_dosed_chemical_id)
+  ) %>%
+  distinct()
+
+quick_message(text = c(
+  "Filtering out:",
+  "Missing {.code analyzed_chem_dtxsid}",
+  "Data where the analyzed chemicals and dosed chemicals are different"
+))
+
+quick_stats(cvt_df)
+
+# Filtering out non-circulation mediums (these are retained in cvtdb_original)
+cvt_df <- cvt_df %>%
+  filter(conc_medium_normalized %in% c("blood", "plasma"))
+
+quick_message(text = c(
+  "Filtering out:",
+  "Non-plasma/blood medium collected."
+))
+
+# Filter out where all values in experiment are missing values/below LOQ
+# Also filter out observations where
+cvt_df <- cvt_df %>%
+  mutate(
+    conc = ifelse(conc < 0, NA_real_, conc),
+    conc_original = ifelse(conc_original < 0, NA_real_, conc_original)
+  ) %>%
+  group_by(
+    analyzed_chem_dtxsid, species, fk_extraction_document_id,
+    administration_route_normalized, conc_medium_normalized
+  ) %>%
+  filter(
+    !(if_all(conc, is.na) & if_all(conc_original, is.na))
+  ) %>%
+  ungroup() %>%
+  distinct()
+
+quick_message(text = c(
+  "Filtering out:",
+  "Experiments missing concentration values altogether."
+))
+
+quick_stats(cvt_df)
+
+# Need to see all the conc, conc_sd, dose, loq (original, values and units)
 # Dose Units: Need mg/kg... = ug/mg = ng/ug, and kg = L
@@
 cvt_df <- cvt_df %>% mutate(
+  conc_units_original = stringr::str_replace(
+    conc_units_original, 
+    pattern = "l$",
+    replacement = "L"
+  ),
+  conc_units_original = stringr::str_replace(
+    conc_units_original, 
+    pattern = "\u00B5",
+    replacement = "u"
+  ),
+  conc_units_normalized = stringr::str_replace(
+    conc_units_normalized, 
+    pattern = "l$",
+    replacement = "L"
+  ),
+  loq_units = stringr::str_replace(loq_units, "l$", "L"),
   invivPK_dose_level_units = "mg/kg",
-  invivPK_conc_units = "ug/mL",
-  invivPK_conc = NA_real_,
-  invivPK_dose_level = NA_real_
-  )
-# Set the equivalent units
-equiv_mgkg <- c("mg/kg", "ug/g", "ng/mg")
-equiv_mgL <- c("mg/L", "ug/mL", "ng/uL", "mg/kg", "mg/g", "ug/mg")
-
-# Filtering out entries with no concentration information available
-cvt_df <- cvt_df %>%
-  filter(!(is.na(conc) & is.na(conc_original))) %>%
-  group_by(fk_study_id) %>%
-  filter(n() > 1) %>%
-  ungroup()
-###
+  invivPK_conc_units = "ug/mL"
+)
+
+# Filtering out observations with no concentration information
+cvt_df <- cvt_df |> 
+  filter(!(is.na(conc_original) & is.na(conc)))
+
+```
+
+For the majority of compounds with a missing `conc` value, it is usually a 
+factor of converting `conc_units_original` to the standard `conc_units_normalized`.
+
+While I leave most of this curation work to the CvTdb team which have been working
+on this data since 2020 at least, I will try to wade through the data for
+the following 5 chemicals with large amounts of data that is missing.
+
+1. _tetralin/DTXSID1026118_: has `conc_units_original` in `ug/g` of plasma concentration.
+Blood plasma has a density of approximately `1.025 g/mL` which means that the values
+for `conc_original` and `loq` can be multiplied by this value to give the standard
+`ug/mL`.
+
+2. _PCB 136/DTXSID6073499_: has some `conc_units_original` in `ng/g` of whole blood
+concentration. Whole blood has a density of approximately `1.05 g/mL` which means
+we can multiply the concentrations by $1.05\frac{g}{mL}\times 10^{-3}\frac{\mu g}{ng}$.
+For simplicity, I will discard the observations where `conc_units_original` is
+given in `molar percentage`.
+
+3. _PFOA/DTXSID40892486_: has some `conc_units_original` in `ug/g` of plasma.
+I will apply the same formula as #1 above.
+
+4. _propyzamide/DTXSID2020420_: this, and all chemicals in `pmid == 29385628`
+have concentration over time values of `mg/kg`, but these are actually the
+`ug/mL`. This is apparent in the Supplementary Table 1 of this paper. The `loq`
+values are carefully calibrated, but should all be in `ng/mL` units.
+
+5. _carbon disulfide/DTXSID6023947_: similar to #2 the `conc_units_original` is
+in `ug/g` of whole blood, which means we can simply multiply `conc_original`
+by `1.05 g/mL` to supply `conc`.
+
+In general, if we have missing `conc` values, we are only interested in those
+that have a mass value (i.e. kg, g, ug) in the denominator, so I will begin
+by filtering out all other observations.
+
+```{r}
+# Densities in units: g/ml
+WB_DENSITY = 1.05 
+PL_DENSITY = 1.025
+
+# This removes around 100 observations!
+cvt_df <- cvt_df |>
+  filter(!is.na(conc) | stringr::str_detect(conc_units_original, "g$"))
+
+cvt_df <- cvt_df |>
+  mutate(
+    conc = case_when(
+      # Carry over values when pmid == 29385628
+      is.na(conc) & 
+        pmid == 29385628L & 
+        conc_units_original == "mg/kg" ~ conc_original,
+      is.na(conc) &
+        conc_medium_normalized == "plasma" &
+        conc_units_original == "ug/g" ~ conc_original * PL_DENSITY,
+      is.na(conc) &
+        conc_medium_normalized == "blood" &
+        conc_units_original == "ug/g" ~ conc_original * WB_DENSITY,
+      is.na(conc) &
+        conc_medium_normalized == "blood" &
+        conc_units_original == "ng/g" ~ conc_original * WB_DENSITY * 1E-3,
+      is.na(conc) &
+        conc_medium_normalized == "plasma" &
+        conc_units_original == "ng/g" ~ conc_original * PL_DENSITY * 1E-3,
+      .default = conc
+    )
+  )
+
+quick_stats(cvt_df)
+
+# When LOQ values are present, the units are always specified
+# There is one case that is at first glance not an easy conversion, nmol/mL,
+# but TAME has a mass of 102.104465 g/mol. LOQ value in ug/mL is approximately the
+# same and we will treat it as such
+# There is another case where loq_units is recorded as "ng". I will treat this as "ng/mL"
+
+cvt_df <- cvt_df |> 
+  mutate(
+    loq = case_when(
+      loq_units %in% c("ug/L", "ng/mL", "ng") ~ loq * 1E-3,
+      loq_units == "pg/mL" ~ loq * 1E-6,
+      loq_units == "ng/g" & conc_medium_normalized == "blood" ~ loq * WB_DENSITY * 1E-3,
+      loq_units == "ug/g" & conc_medium_normalized == "blood" ~ loq * WB_DENSITY,
+      loq_units == "ug/g" & conc_medium_normalized == "plasma" ~ loq * PL_DENSITY,
+      .default = loq
+    ),
+    loq_units = "ng/uL"
+  )
+
+quick_stats(cvt_df)
+
+```
+
+Per the CvTdb 2.0.0 release notes, Dose is normalized to `mg/kg BW`.
+However, there are some with missing values, representing 180 observations across
+3 chemicals (by DTXSIDs): quinidine, clothiapine, and padsevonil. I will simply 
+exclude these in this case.
+
+```{r handling_dose}
+cvt_df <- cvt_df |> filter(dose_level_units_normalized == "mg/kg BW")
+
 quick_stats(cvt_df)
@@
 
-## Specific Data Changes
-
-To summarize these changes:
-
-+  Convert original dose units for CEBS study _S0916_ to mg/kg.  
-+  Convert original dose units for CEBS study _S0624_ to mg/kg. Data got corrected in CEBS, trusting that.  
-+  Input the LOQ for studies _S0976_.  
-+  Infer the LOQ for study _S0328_ as 1, given the values near it deemed above and below LOQ.
-
-```{r specific_data_validation}
-# Looking for suspect dose levels
-quick_message(paste0("Looking at dose units not equivalent to mg/kg where ",
-                     "dose_level_original and dose_level_normalized ",
-                     "{.emph remain the same}"))
-
-cvt_df %>% filter(!(dose_level_units_original %in% equiv_mgkg),
-                  dose_level_normalized == dose_level_original) %>%
-  distinct(fk_study_id, 
-           dose_level_original, dose_level_normalized,
-           dose_level_units_original,
-           pmid,
-           other_study_identifier)
-
-cvt_df <- cvt_df %>%
-  mutate(invivPK_dose_level = dose_level_normalized,
-         invivPK_loq = loq,
-         invivPK_loq_units = loq_units,
-         invivPK_conc_sd = conc_sd,
-         invivPK_conc = conc)
-diff_log_cvt(cvt_df)
-
-# Checking other_study_identifier == S0916
-quick_message(text = c(
-  "Data Modification:",
-  paste("For study 1713 and 1714, tamoxifen was administered at 5mL/kg, ",
-        "meaning these doses are 5/1000th of current value to convert ug/mL -> mg/kg."
-),
- "This entry has since been removed from CvT as of April 2025"
-)
-)
-
-# In CEBS "S0916" the Dose is 300,100 ug/mL with 5mL/kg administered by gavage (the only data left)
-# Making it 5/1000 mg/kg x either doses in study_ids 1714,1713 (the latter was filtered out prior to this)
-# cvt_df <- cvt_df %>%
-#   mutate(
-#     invivPK_dose_level = if_else(
-#       fk_study_id %in% c("1714", "1713"),
-#       5/1000 * dose_level_normalized,
-#       dose_level_normalized
-#     )
-#   )
-
-# In CEBS "S0624" it was in ng/kg not mg/kg in the summary, but that has been deleted from CEBS
-# Assuming that was a error of record
-
-quick_message("CEBS datasets S0976 and S0328 contain data on LOQ or ELOQ")
-# For study S0976, Caffeine, L-ephedrine, and psuedoephedrine 
-quick_message(c(
-  "Data Modification:",
-  "Adjusting LOQ values for L-ephedrine to 3.39 as stated in CEBS study S0976.",
-  "Set LOQ units to ng/mL as detailed in the same CEBS study.",
-  "S0976 has been removed as of April 2025."
-))
-# Here I create new columns for loq and loq_units b/c I have modified them.
-# cvt_df <- cvt_df %>%
-#   mutate(invivPK_loq = if_else(
-#     other_study_identifier %in% "S0976",
-#     case_when(
-#       analyte_name_original %in% "caffeine" ~ 4.00,
-#       analyte_name_original %in% "l-ephedrine" ~ 3.39,
-#       analyte_name_original %in% "pseudoephedrine" ~ 4.43
-#     ),
-#     loq),
-#     invivPK_loq_units = if_else(
-#       other_study_identifier %in% "S0976",
-#       "ng/mL",
-#       loq_units
-#     ))
-
-# Some pentachlorophenol studies
-quick_message(c(
-  "Data Modification:",
-  "Looked at ELOQ in CEBS study S0328 and found it to be around 1",
-  "This only is relevant for {.code study_id} 1779.",
-  "This record is no longer present as of April 2025."
-))
-
-# cvt_df <- cvt_df %>%
-#   mutate(
-#   invivPK_loq = if_else(
-#     fk_study_id %in% "1779",
-#     1, invivPK_loq),
-#   invivPK_loq_units = if_else(
-#     other_study_identifier %in% "S0328",
-#     "ug/mL",
-#     invivPK_loq_units
-#   ))
-
-quick_stats(cvt_df)
-diff_log_cvt(cvt_df)
+```{r plot_by_dtxsid}
+cvt_df %>%
+  ggplot(aes(
+    x = time_hr, y = conc, group = analyzed_chem_dtxsid,
+    color = analyzed_chem_dtxsid
+  )) +
+  geom_point() +
+  geom_smooth(se = FALSE) +
+  theme_bw() +
+  scale_y_log10() +
+  theme(legend.position = "none")
 ```
 
-## Routine Unit Conversions and final filtering steps
-
-Here I converted units for concentration, concentration standard deviation,
-and LOQ to *ug/mL* and dose units to *mg/kg*. There is a special case for records
-in series 23340 and 23380 where the `conc_original` value is already in *mg/kg*
-but is somehow rounded in `conc`, which gives zero values for the final timepoints in this series
-even when these are not below LOQ.
-
- There are some final filtering steps as well:
-
-+  Filter out chemicals dosed multiple times throughout the experiment.  
-+  Filter out chemicals with very limited information.
-
-```{r general_unit_conversions}
-quick_message(c(
-  "Filtering data:",
-  "Only including data with a single dose.",
-  "{.code dose_frequency} of {.code NA} is assumed to be single bolus dose."
-))
-# Eliminate study that gave chemical each day, not single dose
-# This may be used in another type of model, but right now we deal with single bolus
-# Only include those that have NA or 1 for dose frequency
-cvt_df <- cvt_df %>%
-  filter(dose_frequency %in% c("1", NA))
-
-# quick_stats(cvt_df)
-quick_message("Uniqe LOQ units:")
-table(cvt_df$invivPK_loq_units)
-diff_log_cvt(cvt_df)
-quick_stats(cvt_df)
-
-quick_message(c(
-  "Modifying Data:",
-  "Converting loq units to concentration unit standard mg/L",
-  "Converting concentration units to standard mg/L",
-  "Converting concentration sd units to the standard mg/L",
-  "Keeping concentration values for series 23340 and 23380 to original records"
-))
-# Normalize LOQ units
-cvt_df <- cvt_df %>%
-  mutate(invivPK_loq = if_else(
-    invivPK_loq_units %in% c("ug/L", "ng/mL", "ng/g"),
-    invivPK_loq * 1E-3, invivPK_loq)) %>% 
-  mutate(ivivPK_loq_units = "ug/mL") # mg/L and ug/mL are same scale
-# Normalize conc_sd and conc units manually
-
-# Some concentrations are already normalized
-cvt_df <- cvt_df %>%
-  mutate(invivPK_conc_sd = case_when(
-    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
-                               "ng/g", "ng/g tissue", "ug/L") ~ conc_sd_original*1E-3,
-    conc_units_original %in% c("g/dL") ~ conc_sd_original*1E-4,
-    conc_units_original %in% c("pg/mL") ~ conc_sd_original*1E-6,
-    !is.na(conc_sd) ~ conc_sd, 
-    .default = conc_sd_original
-  ))
-# Need to normalize the ng-eq/mL sample, conc is generally already normalized
-# 
-cvt_df <- cvt_df %>%
-  mutate(invivPK_conc = case_when(
-    conc_units_original %in% c("ng-eq/mL", "ng/mL", "ng/ml",
-                               "ng/g", "ng/g tissue", "ug/L") ~ conc_original*1E-3,
-    conc_units_original %in% c("g/dL") ~ conc_original*1E-4,
-    conc_units_original %in% c("pg/mL") ~ conc_original*1E-6,
-    fk_series_id %in% c("23340", "23380") ~ conc_original, # Special case of rounding errors
-    .default = conc
-  ))
-
-quick_message("Are there chemicals with very few (less than 5) observations still?")
-cvt_df %>% count(analyte_dtxsid) %>% arrange(n) %>% head()
-# This has been resolved now
-# quick_message(c(
-#   "Filtering Data:",
-#   "Removing DTXSID6038299 due to insufficient data",
-#   "Removing all data points that still have recorded concentrations of zero"
-# ))
-# cvt_df <- cvt_df %>%
-#   dplyr::filter(!(analyte_dtxsid %in% "DTXSID6038299"))
-
-# This is the final filtering so that the dataset is most consistent with the
-# most current near future pull in the new year
-# This will include some zero values, but should work itself out during preprocessing
-cvt_df <- cvt_df %>%
-  filter(invivPK_conc >= 0)
-
-# More notes:
-# DTXSID6020438 & DTXSID0020868 rat is from water (top) and oil (bottom curve) gavage
-
-glimpse(cvt_df)
-quick_stats(cvt_df)
-
-diff_log_cvt(cvt_df, 
-             notes = c("Used CompTox name - DTXSID matching to fill in NAs.",
-                       "Fixed names that used non-standard single quotes.")
-)
+```{r final_checks}
+cvt_df %>%
+  count(
+    is.na(dose_level_normalized),
+    is.na(dose_level_original)
+  ) %>%
+  glimpse()
+
+cvt_df %>%
+  count(is.na(conc_sd) & n_subjects_normalized > 1)
+
+cvt_df %>%
+  count(is.na(n_subjects_normalized))
+
+cvt_df <- cvt_df |> select(!starts_with("invivPK_"))
+cvt_df <- cvt_df |> filter(time_hr >= 0)
 
@@
 
-Note the columns prefixed by _invivPK_. These are generated as a non-destructive form
-of modifying the data that we will use for _invivoPKfit_. The only column from the
-SQL query result of CvTdb that is actually changed is the `analyte_dtxsid` as 
-described earlier.
+### Changes to mapping!
+We now use `conc`, `conc_units_normalized`, `loq`, `loq_units`,
+`dose_level_units_normalized`, and `dose_level_normalized` directly.
 
@@
 cvt_date <- Sys.Date()
-cat(diff_log_cvt(cvt_df, 
-             notes = c("Used CompTox name - DTXSID matching to fill in NAs.",
-                       "Fixed names that used non-standard single quotes.")
-),
-    file = "data-raw/cvt_changelog.txt",
-    append = TRUE)
 
@@
 save(cvt_date, file = "data/cvt_date.rda")
-
 ```
+
+# QSAR Bakeoff Run
+
+```{r running}
+my_pk <- pk(
+  cvt,
+  mapping = ggplot2::aes(
+    Chemical = analyzed_chem_dtxsid,
+    Chemical_Name = analyzed_chem_name_original,
+    DTXSID = analyzed_chem_dtxsid,
+    CASRN = analyzed_chem_casrn,
+    Species = species,
+    Reference = fk_extraction_document_id,
+    Media = conc_medium_normalized,
+    Route = administration_route_normalized,
+    Dose = dose_level_normalized,
+    Dose.Units = "mg/kg",
+    Subject_ID = fk_subject_id,
+    Series_ID = fk_series_id,
+    Study_ID = fk_study_id,
+    ConcTime_ID = conc_time_id,
+    N_Subjects = n_subjects_normalized,
+    Weight = weight_kg,
+    Weight.Units = "kg",
+    Time = time_hr,
+    Time.Units = "hours",
+    Value = conc,
+    Value.Units = "mg/L",
+    Value_SD = conc_sd,
+    LOQ = loq
+  )
+)
+
+my_pk <- my_pk +
+  stat_error_model(Chemical, Species) +
+  settings_optimx(method = "bobyqa") +
+  facet_data(Chemical, Species) +
+  settings_preprocess(
+    keep_data_original = TRUE,
+    suppress.messages = TRUE
+  ) +
+  scale_conc(dose_norm = TRUE, log10_trans = TRUE)
+
+my_pk <- do_preprocess(my_pk)
+apply(my_pk$data, 2, \(x) {
+  any(is.na(x))
+})
+
+my_pk <- do_data_info(my_pk)
+my_pk <- do_prefit(my_pk)
+
+mirai::daemons(8)
+mirai::everywhere(devtools::load_all())
+my_pk <- do_fit(my_pk, async = TRUE)
+mirai::daemons(0)
+
+fit_pl <- plot(my_pk, use_scale_conc = FALSE)
+
+fit_pl %>%
+  filter(Chemical %in% "DTXSID1021116", Species %in% "human") %>%
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID9025617", Species %in% "mouse") %>%
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID9025617", Species %in% "rat") %>%
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID2021781", Species %in% "mouse") %>%
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID1034187") %>% # Tamoxifen sanity check
+  pull(final_plot) %>%
+  .[[1]]
+
+fit_pl %>%
+  filter(Chemical %in% "DTXSID1043881") %>% # Imipramine sanity check
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID1023653") %>% # Thiopental sanity check
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID5021122") %>% # Phenobarbital sanity check
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID80873012") %>% # PFHS sanity check
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID20230862") %>% # Metoprolol sanity check
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID60230861") %>% # Metoprolol sanity check
+  pull(final_plot) %>%
+  .[[1]]
+fit_pl %>%
+  filter(Chemical %in% "DTXSID8031865") %>% # Metoprolol sanity check
+  pull(final_plot) %>%
+  .[[1]]
+
+get_winning_model(my_pk) %>% filter(Chemical %in% "DTXSID1034187")
+get_fit(my_pk) |>
+  distinct(Chemical, Species, model, convergence) |> 
+  count(model, convergence)
+
+eval_tkstats(my_pk) |> glimpse(80)
+eval_tkstats(my_pk) |> pull(DATA_GROUP_ID) |> unique() |> length()
+
+save(my_pk, file = "data-raw/temp_pk.rda")
+
+write_csv(
+  eval_tkstats(my_pk),
+  file = paste0(
+    Sys.getenv("FIG_DIR"),
+    "2025_07_31_eval_tkstats.csv"
+  )
+)
+
+```

### 2025-08-05 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Update to cvt fitting options and tkstats + parameter table generation for dashboard.

@@
   ) +
-  scale_conc(dose_norm = TRUE, log10_trans = TRUE)
+  scale_conc(dose_norm = FALSE, log10_trans = FALSE)
 
@@
 
-mirai::daemons(8)
+mirai::daemons(8L)
 mirai::everywhere(devtools::load_all())
 my_pk <- do_fit(my_pk, async = TRUE)
-mirai::daemons(0)
+mirai::daemons(0L)
 
@@
 
-write_csv(
-  eval_tkstats(my_pk),
+my_tkstats <- eval_tkstats(my_pk, dose_norm = TRUE)
+my_fit <- get_fit(my_pk)
+my_wm <- get_winning_model(my_pk)
+
+my_fit |>
+  select(DATA_GROUP_ID:param_name, estimate) |>
+  inner_join(my_wm, by = c("Chemical", "Species", "method", "model")) |>
+  select(-c(near_flat, preds_below_loq)) |>
+  filter(stringr::str_detect(param_name, "sigma_", negate = TRUE)) |>
+  mutate(
+    estimate = purrr::map_dbl(
+      estimate,
+      \(x) ifelse(is.null(x), NA_real_, as.numeric(x))
+    )
+  ) |> 
+  tidyr::pivot_wider(names_from = param_name, values_from = estimate) |> 
+  inner_join(my_tkstats,
+             by = join_by(DATA_GROUP_ID, model, method, Chemical, Species)) |>
+  readr::write_csv(
     file = paste0(
       Sys.getenv("FIG_DIR"),
-    "2025_07_31_eval_tkstats.csv"
+      "20250805_pk000_evalTKstats.csv"
     )

### 2025-08-12 data-raw/pulling_oral_iv_data_cvtdb.Rmd
Moved helper functions to CvTdb query report.

@@
 library(readr)
+library(stringr)
+library(cli)
 ```
@@
 ```{r quick_message_funtion}
-quick_message <- function(text = character()) {
+quick_message <- function(text = character(0L)) {
   stopifnot(length(text) > 0)
 
-  cli::cli_par()
-  cli::cli_text(paste("{.strong [i]}  ", text[1], sep = "\t"))
+  this_par <- cli_par()
+  cli_text(text[1])
   text <- text[-1]
 
-  for (this_text in seq_along(text)) {
-    cli::cli_li(text[this_text])
+  ul <- cli_ul()
+  for (this_text in text) {
+    cli_li(this_text)
   }
-  cli::cli_end()
+  cli_end(ul)
+  cli_end(this_par)
 }
 
-quick_stats <- function(.data, old_version = FALSE) {
+cli_print <- function(x, file = "", append = FALSE) {
+  cat(x, file = file, sep = "\n", append = append)
+}
+
+# Wrapper for qcount())
+qcount <- function(x) length(unique(x))
+
+quick_stats <- function(.data) {
   stopifnot(is.data.frame(.data))
 
-  cli::cli_h2("Statistics on the current data")
-  message(paste0("Total number of data points: ", nrow(.data)))
-  message("Unique Species and data counts:")
-  print(table(.data$species))
-
-  message(
-    "Number of unique studies: ",
-    length(unique(.data$fk_study_id))
-  )
-  message(
-    "Number of unique series: ",
-    length(unique(.data$fk_series_id))
-  )
-
-  if (old_version) {
-    message(
-      "Number of unique chemicals: ",
-      length(unique(.data$analyte_dtxsid)),
-      "\n"
-    )
-    chem_by_medium <- .data[c("conc_medium_normalized", "analyte_dtxsid")] %>%
-      filter(!is.na(analyte_dtxsid)) %>%
-      distinct()
-    chem_by_curset <- .data[c("curation_set_tag", "analyte_dtxsid")] %>%
-      filter(!is.na(analyte_dtxsid)) %>%
-      distinct()
-  } else {
-    message(
-      "Number of unique chemicals: ",
-      length(unique(.data$analyzed_chem_dtxsid)),
-      "\n"
-    )
-    chem_by_medium <- .data[c("conc_medium_normalized", "analyzed_chem_dtxsid")] %>%
-      filter(!is.na(analyzed_chem_dtxsid)) %>%
-      distinct()
-    chem_by_curset <- .data[c("curation_set_tag", "analyzed_chem_dtxsid")] %>%
-      filter(!is.na(analyzed_chem_dtxsid)) %>%
-      distinct()
+  .data <- subset(.data, !is.na(analyzed_chem_dtxsid))
+  cli_text(c(
+    "!" = "Only data with analyzed chemical dtxsid will be considered."
+  ))
+  cli_text("---- Statistics on the current data ----")
+  cli_text("Total number of data points: {nrow(.data)}")
+  cli_text("Unique Species and data counts:")
+  cli_dl(table(.data$species))
+
+  this_par <- cli_par()
+  cli_text("Number of unique studies: {qcount(.data$fk_study_id)}")
+  cli_text("Number of unique series: {qcount(.data$fk_series_id)}")
+  cli_text("Number of unique chemicals: {qcount(.data$analyzed_chem_dtxsid)}")
+  cli_end(this_par)
+
+  that_par <- cli_par()
+  cli_text("Original Dose Units: {qcount(.data$dose_level_units_original)}")
+  cli_text("Normalized Dose Units: {qcount(.data$dose_level_units_normalized)}")
+  cli_text("Original Conc Units: {qcount(.data$conc_units_original)}")
+  cli_text("Normalized Conc Units: {qcount(.data$conc_units_normalized)}")
+  cli_end(that_par)
+
+  cli_par()
+  cli_text("Data by unique route of administration:")
+  cli_dl(table(.data$administration_route_normalized))
+  cli_end()
+  cli_par()
+  cli_text("Data by unique medium collected:")
+  cli_dl(table(.data$conc_medium_normalized))
+  cli_end()
+  cli_par()
+  cli_text("Data by unique curation set:")
+  cli_dl(table(.data$curation_set_tag))
+  cli_end()
 }
 
-  message(
-    "Unique Dose units: ",
-    toString(unique(.data$dose_level_units_original)),
-    "\n"
-  )
-  if (all(is.na(.data$conc_units_normalized))) {
-    message(
-      "Unique Concentration units: ",
-      toString(unique(.data$conc_units_original)),
-      "\n"
-    )
-  } else {
-    message(
-      "Unique Concentration units: ",
-      toString(unique(.data$conc_units_normalized)),
-      "\n"
+#' Wrapper for [dplyr::case_match()] that accepts named lists as arguments
+#' @param .x A vector to match against. In a data context, a column.
+#' @param .lst A named list in the form `old_value = new_value`.
+#' @param .default Value to be used when there are no values. Suggest setting it to `.x`
+#' @return A vector of replaced values
+case_match_lst <- function(.x, .lst, .default = NULL) {
+  stopifnot(rlang::is_named(.lst))
+
+  dplyr::case_match(
+    .x,
+    !!!lapply(paste0("\"", names(.lst), "\"~\"", .lst, "\""), stats::as.formula),
+    .default = .default
   )
 }
-  message("Data by unique route of administration:")
-  print(table(.data$administration_route_normalized))
-  message("Data by medium collected:")
-  print(table(.data$conc_medium_normalized))
-  message("Data by curation set:")
-  print(table(.data$curation_set_tag))
-  message("\n\nUnique chemicals per medium:")
-  print(table(chem_by_medium$conc_medium_normalized))
-  message("Unique chemicals per curation set:")
-  print(table(chem_by_curset$curation_set_tag))
+
+#' Wrapper for [str_replace_all()] which replaces whole words.
+#' @param .x A vector to match against.
+#' @param .lst A named vector in the form `old_value = new_value`.
+#' @return A character vector with values substituted in.
+str_replace_lst <- function(.x, .lst) {
+  stopifnot(rlang::is_named(.lst))
+
+  str_replace_all(.x, setNames(.lst, paste0("^", names(.lst), "$")))
 }
@@
 )
-
-```
-
-```{r diff_log_function}
-# Now I want to write a quick function that will log relevant changes
-# from previous 'cvt' objects
-diff_log_cvt <- function(new_cvt,
-                         key_id = "conc_time_id",
-                         grp_ids = c(
-                           "analyzed_chem_dtxsid",
-                           "species"
-                         ),
-                         notes = character(0L)) {
-  stopifnot(
-    key_id %in% colnames(cvt),
-    key_id %in% colnames(new_cvt),
-    all(grp_ids %in% colnames(cvt)),
-    all(grp_ids %in% colnames(new_cvt))
-  )
-  if (length(unique(new_cvt[[key_id]])) != NROW(new_cvt)) {
-    stop("key_id is not not a column that uniquely identifies this data.")
-  }
-
-  # Prepare some vectors:
-  grp_strings_new <- unique(do.call("paste", new_cvt[grp_ids]))
-  grp_strings_old <- unique(do.call("paste", cvt[grp_ids]))
-
-  msg_to_write <- paste0("\n\n======== ", round(Sys.time()))
-
-  if (identical(new_cvt, cvt)) {
-    msg_to_write <- paste(msg_to_write, "No changes.", sep = "\t")
-    message(
-      "There are no changes from previous `cvt` data.frame, ",
-      "are you sure you want to save this?"
-    )
-  } else {
-    msg_to_write <- paste(msg_to_write, "Changes detected.", sep = "\t")
-
-    ### ---- Check key_id changes (usually conc_time_id)
-    diff_row_add <- setdiff(new_cvt[[key_id]], cvt[[key_id]])
-    diff_row_sub <- setdiff(cvt[[key_id]], new_cvt[[key_id]])
-    diff_row_common <- intersect(cvt[[key_id]], new_cvt[[key_id]])
-    # Nature of data changes:
-    added_grps <- unique(
-      do.call(
-        "paste",
-        new_cvt[which(new_cvt[[key_id]] %in% diff_row_add), grp_ids]
-      )
-    )
-    removed_grps <- unique(
-      do.call(
-        "paste",
-        cvt[which(cvt[[key_id]] %in% diff_row_sub), grp_ids]
-      )
-    )
-
-    added_new_grps <- setdiff(added_grps, grp_strings_old)
-    added_existing_grps <- intersect(added_grps, grp_strings_old)
-    removed_new_grps <- setdiff(removed_grps, grp_strings_new)
-    removed_existing_grps <- intersect(removed_grps, grp_strings_new)
-
-    msg_to_write <- c(
-      msg_to_write,
-      paste("Rows added:", length(diff_row_add)),
-      paste("Rows removed:", length(diff_row_sub))
-    )
-
-    limit_grp_output <- function(grp_vector) {
-      if (length(grp_vector) > 0) {
-        if (length(grp_vector) > 6) {
-          grp_vector <- c(
-            grp_vector[c(1, 2)],
-            paste0(
-              "... [",
-              length(grp_vector) - 3,
-              "] more!"
-            ),
-            grp_vector[c(length(grp_vector) - 1)]
-          )
-        }
-        return(grp_vector)
-      }
-      msg_to_write <- c(
-        msg_to_write,
-        "New Groups added (not in previous data):",
-        paste0("\t", limit_grp_output(added_new_grps)),
-        "Groups with new observations (group present in previous data)",
-        paste0("\t", limit_grp_output(added_existing_grps)),
-        "Groups removed that no longer have data present:",
-        paste0("\t", limit_grp_output(removed_new_grps)),
-        "Groups removed that still have some data present:",
-        paste0("\t", limit_grp_output(removed_existing_grps)),
-        "-----------------------------------"
-      )
-    }
-
-    ### -----Checking columns
-    diff_col_add <- setdiff(names(new_cvt), names(cvt)) # Columns added in new_cvt
-    diff_col_sub <- setdiff(names(cvt), names(new_cvt)) # Columns removed in new_cvt
-    diff_col_common <- intersect(names(cvt), names(new_cvt))
-    common_row_cvt <- cvt[cvt[[key_id]] %in% diff_row_common, ]
-
-    common_row_cvt <- common_row_cvt[order(common_row_cvt[[key_id]]), ]
-
-    common_row_new <- new_cvt[new_cvt[[key_id]] %in% diff_row_common, ]
-    common_row_new <- common_row_new[order(common_row_new[[key_id]]), ]
-
-    if (length(c(diff_col_add, diff_col_sub)) == 0) {
-      msg_to_write <- c(
-        msg_to_write,
-        "No changes in column names."
-      )
-    } else if (length(diff_col_add) > 0 && length(diff_col_sub) > 0) {
-      # Check renaming
-
-      diff_columns <- function(x, y) {
-        out_list <- character()
-        for (ix in setdiff(names(x), key_id)) {
-          for (iy in setdiff(names(y), key_id)) {
-            tmp <- merge(x[c(key_id, ix)], y[c(key_id, iy)], by = key_id)
-            if (identical(tmp[[2]], tmp[[3]])) {
-              out_list <- c(out_list, paste0(ix, " -> ", iy))
-            }
-          }
-        }
-        return(out_list)
-      }
-
-      renamed_cols <- diff_columns(
-        common_row_cvt[c(key_id, diff_col_sub)],
-        common_row_new[c(key_id, diff_col_add)]
-      )
-      if (length(renamed_cols) > 0) {
-        msg_to_write <- c(
-          msg_to_write,
-          "Renamed columns (non-exhaustive):",
-          renamed_cols
-        )
-      } else {
-        msg_to_write <- c(
-          msg_to_write,
-          "No renamed columns found."
-        )
-      }
-    }
-    if (length(diff_col_add) > 0) {
-      msg_to_write <- c(
-        msg_to_write,
-        "--------------",
-        "Columns added:",
-        diff_col_add
-      )
-    }
-    if (length(diff_col_sub) > 0) {
-      msg_to_write <- c(
-        msg_to_write,
-        "______________",
-        "Columns removed (from previous data):",
-        diff_col_sub
-      )
-    }
-
-    if ((NROW(
-      setdiff(
-        common_row_cvt[diff_col_common], common_row_new[diff_col_common]
-      )
-    ) > 0
-    ) || (NROW(
-      setdiff(
-        common_row_new[diff_col_common], common_row_cvt[diff_col_common]
-      )
-    ) > 0
-    )) {
-      msg_to_write <- c(
-        msg_to_write,
-        "Data for same observation key_ids have changed."
-      )
-
-      # Which columns have different data?
-      test_cols <- setdiff(diff_col_common, key_id)
-      for (i in test_cols) {
-        this_diff <- setdiff(
-          common_row_new[c(key_id, i)],
-          common_row_cvt[c(key_id, i)]
-        )
-        that_diff <- setdiff(
-          common_row_cvt[c(key_id, i)],
-          common_row_new[c(key_id, i)]
-        )
-
-        if (NROW(this_diff) > 0) {
-          msg_to_write <- c(
-            msg_to_write,
-            paste0(c(i, "had", NROW(this_diff), "differences."), collapse = " ")
-          )
-
-          this_grp <- dplyr::distinct(common_row_new[
-            common_row_new[[key_id]] %in% this_diff[[key_id]],
-            grp_ids
-          ])
-          this_grp <- paste0(this_grp[1, 1:2], collapse = " ")
-
-          # Print the differences (if below a certain number of rows)
-          msg_to_write <- c(
-            msg_to_write,
-            paste0(
-              "Example:",
-              paste(this_grp, collapse = " "),
-              collapse = " "
-            ),
-            paste0(c(i, "\t new:", this_diff[1, 2], "<--\t old:", that_diff[1, 2]),
-              collapse = " "
-            ), "\n"
-          )
-        }
-      }
-    }
-    msg_to_write <- c(
-      msg_to_write,
-      notes,
-      "================================\n"
-    )
-  }
-  return(cat(msg_to_write, sep = "\n"))
-}
 ```
@@
 )
-study_query <- query_db(study_docs, "cvt")
+study_query <- query_dib(study_docs, "cvt")
 series_query <- query_db(series_chems, "cvt")
@@
     across(contains("_name"), \(x) {
-      stringr::str_to_lower(x) |>
+      str_to_lower(x) |>
         force_ascii_quotes() |>
         # trim whitespace around hyphens
-        stringr::str_replace_all("\\s*-\\s*", "-") |>
+        str_replace_all("\\s*-\\s*", "-") |>
         # comma-separate forms like 3'6 into 3',6
-        stringr::str_replace_all("(?<=\\d)'(?=\\d)", "',") |>
+        str_replace_all("(?<=\\d)'(?=\\d)", "',") |>
         # fix some bracket cases
-        stringr::str_replace_all("\\[3\\]h", "[3h]") |>
-        stringr::str_replace_all("benzo\\[a\\]", "benzo(a)") |>
+        str_replace_all("\\[3\\]h", "[3h]") |>
+        str_replace_all("benzo\\[a\\]", "benzo(a)") |>
         # adds a space after square bracket separator
-        stringr::str_replace_all("](?!\\s|-)", "] ")
+        str_replace_all("](?!\\s|-)", "] ")
     })
@@
   ungroup() |>
-  arrange(same_dtxsid, same_casrn, same_preferred_name, same_chem_name,
-          same_chem_name_secondary) |>
+  arrange(
+    same_dtxsid, same_casrn, same_preferred_name, same_chem_name,
+    same_chem_name_secondary
+  ) |>
   View("Similar IDs")
@@
 ```{r harmonizing}
+log_file <- "data-raw/creating_cvt_object.txt"
+cli_print(
+  "Creating the `cvt` data object for invivoPKfit, after SQL query.",
+  file = log_file,
+  append = FALSE # Overwrite file
+)
+
 load("data/cvtdb_original.rda")
@@
 
-# Harmonize values for easier analysis
-cvt_df <- sql_query %>%
-  mutate(
-    # Note that sometimes fk_test_chemical_id is NA
-    across(all_of(c(
+columns_to_numeric <- c(
   "time_original",
@@
   "loq"
-    )), as.numeric),
+)
+
+# Harmonize values for easier analysis
+cvt_df <- sql_query %>%
+  mutate(
+    # Note that sometimes fk_test_chemical_id is NA
+    across(all_of(columns_to_numeric), as.numeric),
     # conc, conc_sd_original, and conc_original
@@
     across(contains("chem_name"), \(x) {
-      stringr::str_to_lower(x) |>
+      str_to_lower(x) |>
         force_ascii_quotes() |>
         # trim whitespace around hyphens
-        stringr::str_replace_all("\\s*-\\s*", "-") |>
+        str_replace_all("\\s*-\\s*", "-") |>
         # comma-separate forms like 3'6 into 3',6
-        stringr::str_replace_all("(?<=\\d)'(?=\\d)", "',") |>
+        str_replace_all("(?<=\\d)'(?=\\d)", "',") |>
         # fix some bracket cases
-        stringr::str_replace_all("\\[3\\]h", "[3h]") |>
-        stringr::str_replace_all("\\[a\\]pyr", "(a)pyr") |>
-        stringr::str_remove_all(" \\(aids\\)$") |>
+        str_replace_all("\\[3\\]h", "[3h]") |>
+        str_replace_all("\\[a\\]pyr", "(a)pyr") |>
+        str_remove_all(" \\(aids\\)$") |>
         # adds a space after square bracket separator
-        stringr::str_replace_all("](?!\\s|-)", "] ")
+        str_replace_all("](?!\\s|-)", "] ")
     }),
@@
     dose_duration_units = trimws(dose_duration_units),
-    dose_duration = as.numeric(stringr::str_extract(dose_duration,
+    dose_duration = as.numeric(str_extract(dose_duration,
       pattern = "^\\d+"
@@
       .default = as.numeric(
-        stringr::str_extract(n_subjects_in_series, pattern = "\\d+")
-      )
-    )
-  )
+        str_extract(n_subjects_in_series, pattern = "\\d+")
+      )
+    )
+  )
+
+qm <- quick_message(c(
+  "Column changes:",
+  "Set {.var {columns_to_numeric}} to numeric type.",
+  "Set {.var year} to character type.",
+  "Set {.var {c('species', 'sex')}} to lowercase.",
+  "Set {.var radiolabeled} to logical.",
+  "Normalized some chemicals names. (See code for details)",
+  "If `dose_volume_units` was 'NR' or 'ND' set this to {NA_character_}.",
+  "Replaced ' / ', with '/' and 'ml' with 'mL' for `dose_volume_units`.",
+  "Set `dose_duration` to first number and converted to numeric.",
+  "Trimmed whitespace around `dose_duration_units`.",
+  "Extracted integer average from `n_subjects_in_series` and set 'NR' to NA."
+)) |> cli_fmt()
+
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 ```
@@
 There is also some radiolabeling experiments that aren't described as such.
-We can use `stringr::str_detect(x,"(13|14)c")` to recode `radiolabeled = TRUE`
-for these.
-
-Then we should address the fact that the `invivoPKfit_2.0.0` version of the `cvt`
-object has 228 chemicals, while the recent query only has 145. This is a
-difference of 83.
+We can use `str_detect(x,"(13|14)c")` to recode `radiolabeled = TRUE`
+for these. Then I filter out radiolabeled data because currently _invivoPKfit_
+does not handle these.
 
@@
 
-cli::cli_inform(
-  "{length(unique(cvt_df$analyzed_chem_dtxsid))} unique analyzed_dtxsids"
-)
-
-cli::cli_inform(
-  "{length(unique(cvt_df$dosed_chem_dtxsid))} unique dosed dtxsids"
-)
+cli_text("{qcount(cvt_df$analyzed_chem_dtxsid)} unique analyzed_dtxsids")
+
+cli_text("{qcount(cvt_df$dosed_chem_dtxsid)} unique dosed dtxsids")
 
@@
 cvt_df %>%
-  distinct(analyzed_chem_name_original, dosed_chem_name_original, radiolabeled) %>%
-  filter(!radiolabeled) %>%
-  filter(stringr::str_detect(dosed_chem_name_original, "((13|14)c|3h)"))
-cvt_df %>%
-  distinct(analyzed_chem_name_original, dosed_chem_name_original, radiolabeled) %>%
-  filter(!radiolabeled) %>%
-  filter(stringr::str_detect(analyzed_chem_name_original, "((13|14)c|3h)"))
+  distinct(
+    fk_dosed_chemical_id,
+    analyzed_chem_name_original,
+    dosed_chem_name_original,
+    radiolabeled
+  ) %>%
+  filter(
+    !radiolabeled,
+    str_detect(dosed_chem_name_original, "((13|14)c|3h)") |
+      str_detect(analyzed_chem_name_original, "((13|14)c|3h)")
+  )
 
@@
     radiolabeled = ifelse(
-      stringr::str_detect(dosed_chem_name_original, "((13|14)c|3h)") |
-        stringr::str_detect(analyzed_chem_name_original, "((13|14)c|3h)"),
+      str_detect(dosed_chem_name_original, "((13|14)c|3h)") |
+        str_detect(analyzed_chem_name_original, "((13|14)c|3h)"),
       TRUE,
@@
 
-cvt_df$analyzed_chem_name_original[
-  grepl("\\[\\w\\]", cvt_df$analyzed_chem_name_original)
-] |> unique()
-
-cvt_df$dosed_chem_name_original[
-  grepl("\\[\\w\\]", cvt_df$dosed_chem_name_original)
-] |> unique()
+qm <- quick_message(c(
+  "Found chemicals that were missidentified as not radiolabeled.",
+  "Dosed Chemical IDs = (710, 1108)",
+  "Filtered out radiolabeled data."
+)) |> cli_fmt()
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 
@@
 
-cvt_df <- cvt_df |>
-  mutate(
-    # fix misspellings
-    analyzed_chem_name_original = str_replace_lst(
-      analyzed_chem_name_original,
-      c(
+name_misspellings <- c(
   "paracetmol" = "paracetamol",
@@
 )
-    ),
-    dosed_chem_name_original = str_replace_lst(
-      dosed_chem_name_original,
-      c(
-        "paracetmol" = "paracetamol",
-        "deacetyl diltiazem" = "desacetyl diltaiazem",
-        "deacetyl n-monodesmethyl diltiazem" = "desacetyl n-monodesmethyl diltiazem",
-        "2,2',4,4',5,5'-hexachlorobiphenyl" = "2,4,5,2',4',5'-hexachlorobiphenyl",
-        "clotiapine" = "clothiapine"
-      )
-    ),
-    # Missing DTXSIDs I found
-    dosed_chem_dtxsid = case_match_lst(
-      dosed_chem_name_original,
-      c(
+
+found_dtxsids <- c(
   "4,4'-sulfonylbisphenol-d8" = "DTXSID3022409",
@@
   "3'-azido-3'-deoxythymidine" = "DTXSID8020127",
-        "2,4,5,2',4',5'-hexachlorobiphenyl" = "DTXSID2032180"
-      ),
-      dosed_chem_dtxsid
-    ),
-    analyzed_chem_dtxsid = case_match_lst(
-      analyzed_chem_name_original,
-      c(
+  "2,4,5,2',4',5'-hexachlorobiphenyl" = "DTXSID2032180",
   "fluorotelomer acid 7+3" = "DTXSID20874028",
@@
   "paracetamol" = "DTXSID2020006"
-      ),
+)
+
+cvt_df <- cvt_df |>
+  mutate(
+    # fix misspellings
+    analyzed_chem_name_original = str_replace_lst(
+      analyzed_chem_name_original,
+      name_misspellings
+    ),
+    dosed_chem_name_original = str_replace_lst(
+      dosed_chem_name_original,
+      name_misspellings
+    ),
+    # Missing DTXSIDs I found
+    dosed_chem_dtxsid = case_match_lst(
+      dosed_chem_name_original,
+      found_dtxsids,
+      dosed_chem_dtxsid
+    ),
+    analyzed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name_original,
+      found_dtxsids,
       analyzed_chem_dtxsid
@@
 
+qm <- cli_fmt({
+  cli_par()
+  cli_text("Fixed the following misspellings [old: new] :")
+  cli_dl(name_misspellings)
+  cli_par()
+  cli_text("Added missing DTXSIDs:")
+  cli_dl(found_dtxsids)
+  cli_end()
+})
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
+
 quick_stats(cvt_df)
-# quick_stats(cvt_2.0.0, old_version = FALSE)
-# Note unique chemical counts
+# Note unique chemical counts are
 
@@
   View("ID-less")
+
 # Anything without an ID for analyzed_chemical is likely a metabolite/control of sorts
+# Or justifiably undetermined...
 # So... I filter it out.
@@
 
+cli_print(
+  cli_fmt({
+    quick_message("Filtered out observations where `analyzed_chem_dtxsid` is still NA.")
+  }),
+  file = log_file,
+  append = TRUE
+)
+
 quick_stats(cvt_df)
-
-# Now we need to pre-emptively address the chemicals that have different
-# IDs but are actually the same chemical or represent the same chemical during the experiment
-# This includes primarily: SALTS and ENANTIOMERS
+```
+
+Now we need to preemptively address the chemicals that have different
+IDs but actually represent the same chemical during the experiment
+This includes primarily: SALTS and stereoisomers
+
+**Small note about stereoisomers:**  
+Here I give an un-elaborate treatment to racemic mixtures,
+both stereoisomers/enantiomers are assumed to be 100% of the dose.
+This isn't physically possible but the assumption would be that for each 
+analyzed stereoisomer, the dose is representing the maximum possible dose in those
+cases. For the purposes of _invivoPKfit_ the complication lies in possible
+overestimation of elimination or underestimation of absorption.
+Since this is rare in the data, I note this caveat but keep the data.
+
+```{r salts-enantiomers}
 cvt_df %>%
@@
 mcations <- paste(
-  c("(hydrogen", "lithium", "sodium", "potassium", "rubidium", "cesium",
+  c(
+    "(hydrogen", "lithium", "sodium", "potassium", "rubidium", "cesium",
     "silver", "beryllium", "magnesium", "strontium", "barium", "radium",
-    "zinc", "calcium", "aluminum)"),
+    "zinc", "calcium", "aluminum)"
+  ),
   collapse = "|"
@@
 manions <- paste(
-  c("(hydride", "fluoride", "chloride", "bromide", "iodide", "oxide",
+  c(
+    "(hydride", "fluoride", "chloride", "bromide", "iodide", "oxide",
     "sulfide", "selenide", "telluride", "nitride", "phosphiide",
-    "arsenide)"),
+    "arsenide)"
+  ),
   collapse = "|"
@@
   filter(
-    stringr::str_detect(analyzed_chem_name_original, pattern = mcations) |
-      stringr::str_detect(analyzed_chem_name_original, pattern = manions) |
-      stringr::str_detect(analyzed_chem_name_original, pattern = pa_ions) |
-      stringr::str_detect(analyzed_chem_name, pattern = mcations) |
-      stringr::str_detect(analyzed_chem_name, pattern = manions) |
-      stringr::str_detect(analyzed_chem_name, pattern = pa_ions) |
-      stringr::str_detect(dosed_chem_name_original, pattern = mcations) |
-      stringr::str_detect(dosed_chem_name_original, pattern = manions) |
-      stringr::str_detect(dosed_chem_name_original, pattern = pa_ions) |
-      stringr::str_detect(dosed_chem_name, pattern = mcations) |
-      stringr::str_detect(dosed_chem_name, pattern = manions) |
-      stringr::str_detect(dosed_chem_name, pattern = pa_ions)
+    str_detect(analyzed_chem_name_original, pattern = mcations) |
+      str_detect(analyzed_chem_name_original, pattern = manions) |
+      str_detect(analyzed_chem_name_original, pattern = pa_ions) |
+      str_detect(analyzed_chem_name, pattern = mcations) |
+      str_detect(analyzed_chem_name, pattern = manions) |
+      str_detect(analyzed_chem_name, pattern = pa_ions) |
+      str_detect(dosed_chem_name_original, pattern = mcations) |
+      str_detect(dosed_chem_name_original, pattern = manions) |
+      str_detect(dosed_chem_name_original, pattern = pa_ions) |
+      str_detect(dosed_chem_name, pattern = mcations) |
+      str_detect(dosed_chem_name, pattern = manions) |
+      str_detect(dosed_chem_name, pattern = pa_ions)
   ) |>
@@
 
-# Method: To make DTXSID == DTXSID, salt DTXSIDs will be replaced with
-# non-salt DTXSIDs.
-cvt_df <- cvt_df |> 
-  mutate(
-    analyzed_chem_dtxsid = case_match_lst(
-      analyzed_chem_name,
-      c(
-        "methadone hydrochloride" = "DTXSID7023273",
-        "ammonium perfluorooctanoate" = "DTXSID40892486",
-        "sodium nitrite" = "DTXSID5024219",
-        "potassium perfluorobutanesulfonate" = "DTXSID5030030", # acid is more stable
-        "potassium perfluorohexanesulfonate" = "DTXSID80873012"
-      ),
-      analyzed_chem_dtxsid
-    ),
-    dosed_chem_dtxsid = case_match_lst(
-      analyzed_chem_name,
-      c(
+name_change_dtxsid <- c(
   "methadone hydrochloride" = "DTXSID7023273",
@@
   "hexobarbital" = "DTXSID9023122",
-        "quinidine" = "DTXSID4023549"
-      ),
-      dosed_chem_dtxsid
-    ),
-    dosed_chem_dtxsid = case_match_lst(
-      dosed_chem_name,
-      c(
+  "quinidine" = "DTXSID4023549",
+  "tamoxifen citrate" = "DTXSID1034187",
+  "sodium nitrite" = "DTXSID5024219",
   "imipramine hydrochloride" = "DTXSID1043881",
@@
   "phenobarbital" = "DTXSID5021122",
-        "phenobarbital sodium" = "DTXSID5021122",
-        "potassium perfluorohexanesulfonate" = "DTXSID80873012",
-        "tamoxifen citrate" = "DTXSID1034187",
-        "sodium nitrite" = "DTXSID5024219"
-      ),
-      dosed_chem_dtxsid
-    ),
-    analyzed_chem_dtxsid = case_match_lst(
-      analyzed_chem_name_original,
-      c(
+  "phenobarbital sodium" = "DTXSID5021122"
+)
+
+original_name_change_dtxsid <- c(
   "formetanate hydrochloride" = "DTXSID9041990",
@@
   "pyrithiobac sodium" = "DTXSID3037703",
-        "tamoxifen citrate" = "DTXSID1034187"
-      ),
+  "tamoxifen citrate" = "DTXSID1034187",
+  "valproic acid" = "DTXSID6023733",
+  "r-(+)-metoprolol" = "DTXSID20230862",
+  "s-(-)-metoprolol" = "DTXSID60230861"
+)
+
+# Method: To make DTXSID == DTXSID, salt DTXSIDs will be replaced with
+# non-salt DTXSIDs.
+cvt_df <- cvt_df |>
+  mutate(
+    analyzed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name,
+      name_change_dtxsid,
+      analyzed_chem_dtxsid
+    ),
+    dosed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name,
+      name_change_dtxsid,
+      dosed_chem_dtxsid
+    ),
+    dosed_chem_dtxsid = case_match_lst(
+      dosed_chem_name,
+      name_change_dtxsid,
+      dosed_chem_dtxsid
+    ),
+    analyzed_chem_dtxsid = case_match_lst(
+      analyzed_chem_name_original,
+      original_name_change_dtxsid,
       analyzed_chem_dtxsid
@@
       analyzed_chem_name_original,
-      c(
-        "formetanate hydrochloride" = "DTXSID9041990",
-        "propamocarb hydrochloride" = "DTXSID1040295",
-        "pyrithiobac sodium" = "DTXSID3037703",
-        "valproic acid" = "DTXSID6023733",
-        # add the enantiomers of metoprolol here
-        "r-(+)-metoprolol" = "DTXSID20230862",
-        "s-(-)-metoprolol" = "DTXSID60230861"
-      ),
+      original_name_change_dtxsid,
       dosed_chem_dtxsid
@@
   ) # This is imperfect but will do.
+
+qm <- cli_fmt({
+  this_par <- cli_par()
+  cli_text("Changed DTXSIDs based on chemical names to match unsalted chemical:")
+  cli_dl(name_change_dtxsid)
+  cli_end(this_par)
+  that_par <- cli_par()
+  cli_text("Changed DTXSID based on original chemical name to match unsalted chemical:")
+  cli_dl(original_name_change_dtxsid)
+  cli_end(that_par)
+})
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 
@@
   count(analyzed_chem_dtxsid == dosed_chem_dtxsid)
-cvt_df |>
-  distinct(!!!chem_id_cols) |> 
-  filter(analyzed_chem_dtxsid != dosed_chem_dtxsid) |> 
-  View()
 
@@
 
+qm <- quick_message(
+  "Now, when dosed and analyzed chemical DTXSIDs are identical, replace fk_dosed_chemical_id with fk_analyzed_chemical_id."
+) |> cli_fmt()
+cli_print(qm, file = log_file, append = TRUE)
+
 any(is.na(cvt_df$fk_analyzed_chemical_id))
@@
 
-quick_message(text = c(
+qm <- quick_message(text = c(
   "Filtering out:",
-  "Missing {.code analyzed_chem_dtxsid}",
+  "Missing {.var analyzed_chem_dtxsid}",
   "Data where the analyzed chemicals and dosed chemicals are different"
-))
-
-quick_stats(cvt_df)
+)) |>
+  cli_fmt()
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 
 # Filtering out non-circulation mediums (these are retained in cvtdb_original)
-cvt_df <- cvt_df %>%
-  filter(conc_medium_normalized %in% c("blood", "plasma"))
-
-quick_message(text = c(
-  "Filtering out:",
-  "Non-plasma/blood medium collected."
-))
+cvt_df <- filter(cvt_df, conc_medium_normalized %in% c("blood", "plasma"))
+
+qm <- quick_message(text = c(
+  "Only keeping:",
+  "Plasma or blood medium collected."
+)) |>
+  cli_fmt()
+
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 
@@
 
-quick_message(text = c(
+qm <- quick_message(text = c(
   "Filtering out:",
   "Experiments missing concentration values altogether."
-))
+)) |>
+  cli_fmt()
+
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 
@@
 cvt_df <- cvt_df %>% mutate(
-  conc_units_original = stringr::str_replace(
+  conc_units_original = str_replace(
     conc_units_original,
@@
   ),
-  conc_units_original = stringr::str_replace(
+  conc_units_original = str_replace(
     conc_units_original,
@@
   ),
-  conc_units_normalized = stringr::str_replace(
+  conc_units_normalized = str_replace(
     conc_units_normalized,
@@
   ),
-  loq_units = stringr::str_replace(loq_units, "l$", "L"),
+  loq_units = str_replace(loq_units, "l$", "L"),
   invivPK_dose_level_units = "mg/kg",
@@
 
+qm <- quick_message(c(
+  "Preparing concentration (and LOQ) units for validation:",
+  "Replacing lowercase 'l' at end of unit into upper case 'L' for liters.",
+  "Replacing '{'\u00B5'}' character with 'u' to standardize unit labels.",
+  "Filtering out any observations with NA values in both `conc` and `conc_original`."
+)) |>
+  cli_fmt()
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 ```
@@
 # Densities in units: g/ml
-WB_DENSITY = 1.05 
-PL_DENSITY = 1.025
+WB_DENSITY <- 1.05
+PL_DENSITY <- 1.025
 
@@
 cvt_df <- cvt_df |>
-  filter(!is.na(conc) | stringr::str_detect(conc_units_original, "g$"))
+  filter(!is.na(conc) | str_detect(conc_units_original, "g$"))
+qm <- quick_message(c(
+  "Only keeping:",
+  "Observations with non-NA `conc` values.",
+  "Observations with `conc_units_original` ends with 'g'."
+)) |>
+  cli_fmt()
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 
@@
 
+qm <- quick_message(c(
+  "Calculating missing concentrations when `conc_units_original` is per *grams:",
+  "When blood is measured, multiply by {WB_DENSITY} and metric scaling factor.",
+  "When plasma is measured, multiply by {PL_DENSITY} and metric scaling factor."
+)) |>
+  cli_fmt()
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
+
 quick_stats(cvt_df)
@@
 cvt_df <- cvt_df |>
+  mutate(
+    loq_units = case_match(
+      other_study_identifier,
+      "K02922" ~ "ng/mL",
+      .default = loq_units
+    )
+  ) |> 
   mutate(
@@
 
+qm <- quick_message(c(
+  "Calculating missing LOQs:",
+  "For NTP study 'K02922', loq units are actually 'ng/mL'",
+  "When units are in 'pg/mL', multiply by 10^-6",
+  "When units are in 'ug/L', 'ng/mL', or 'ng', multiply by 10^-3",
+  "When blood is measured and `loq_units` are per gram, multiply by {WB_DENSITY} and metric scaling factor.",
+  "When plasma is measured and `loq_units` are per gram, multiply by {PL_DENSITY} and metric scaling factor."
+)) |>
+  cli_fmt()
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
+
 quick_stats(cvt_df)
-
 ```
@@
 ```{r handling_dose}
-cvt_df <- cvt_df |> filter(dose_level_units_normalized == "mg/kg BW")
+cvt_df <- filter(cvt_df, dose_level_units_normalized == "mg/kg BW")
+cli_print(
+  cli_fmt({
+    quick_message("Removing observations with missing dose values.")
+  }),
+  file = log_file,
+  append = TRUE
+)
 
@@
 cvt_df <- cvt_df |> filter(time_hr >= 0)
+qm <- quick_message("Filtering out all non-positive or non-zero timepoints.") |> 
+  cli_fmt()
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
+
+# Eliminate all observations with unique timepoints below 5
+low_observation_chem_names <- cvt_df |> 
+  group_by(analyzed_chem_name_original) |> 
+  summarize(observation_count = qcount(time_hr)) |>
+  arrange(observation_count) |> 
+  filter(observation_count < 5) |> 
+  pull(analyzed_chem_name_original)
+
+cvt_df <- cvt_df |> 
+  filter(!analyzed_chem_name_original %in% low_observation_chem_names)
+
+qm <- cli_fmt({
+  cli_par()
+  cli_text("Removing chemical entries with less than 5 unique timepoints.")
+  cli_text("This eliminates the following chemicals:")
+  cli_ul(low_observation_chem_names)
+  cli_end()
+})
+cli_print(qm)
+cli_print(qm, file = log_file, append = TRUE)
 
@@
 save(cvt_date, file = "data/cvt_date.rda")
+cli_print(
+  cli_fmt({quick_stats(cvt)}),
+  file = log_file,
+  append = TRUE
+)
+
+cli_print(
+  paste0("Created: ", cvt_date),
+  file = log_file,
+  append = TRUE
+)
+
 ```
@@
 
-mirai::daemons(8L)
+mirai::daemons(10L)
 mirai::everywhere(devtools::load_all())
@@
   .[[1]]
-fit_pl %>%
-  filter(Chemical %in% "DTXSID1034187") %>% # Tamoxifen sanity check
-  pull(final_plot) %>%
-  .[[1]]
-
 fit_pl %>%
@@
 fit_pl %>%
-  filter(Chemical %in% "DTXSID8031865") %>% # Metoprolol sanity check
+  filter(Chemical %in% "DTXSID8031865") %>% # PFOS sanity check
   pull(final_plot) %>%
   .[[1]]
+
+final_plot <- fit_pl |> pull(final_plot)
+pdf(paste0(Sys.getenv("FIG_DIR"), "20250812_plots.pdf"))
+for (this_plot in seq_len(length(final_plot))) {
+  print(final_plot[[this_plot]])
+}
+dev.off()
 
@@
 eval_tkstats(my_pk) |> glimpse(80)
-eval_tkstats(my_pk) |> pull(DATA_GROUP_ID) |> unique() |> length()
+eval_tkstats(my_pk) |>
+  pull(DATA_GROUP_ID) |>
+  unique() |>
+  length()
 
@@
   select(-c(near_flat, preds_below_loq)) |>
-  filter(stringr::str_detect(param_name, "sigma_", negate = TRUE)) |>
+  filter(str_detect(param_name, "sigma_", negate = TRUE)) |>
   mutate(
@@
   inner_join(my_tkstats,
-             by = join_by(DATA_GROUP_ID, model, method, Chemical, Species)) |>
+    by = join_by(DATA_GROUP_ID, model, method, Chemical, Species)
+  ) |>
   readr::write_csv(
@@
   )
-
-```
+```

### 2025-08-22 data-raw/ClearanceProject-0-Distinguishability.Rmd
Updates project file organization. Moves common functions to a common, sourced file.

@@
 ```{r library_loading}
-# June 6, 2025 8AM: Using httk-dev/HTTK-293 branch
-# June 6, 2025 3PM: Using httk-dev/dev branch
 source("data-raw/RC_comparison_bkgd.R")
@@
 
+Here I want to understand whether selecting the restrictive or nonrestrictive
+mode of clearance makes *distinguishable* differences in the predictions. This
+is somewhat similar to discerning whether this parameter is structurally 
+identifiable. The way I will do this is to take a sampled distribution for
+Clint and Funbound.plasma then compare the 95% confidence intervals between the
+estimates, labeling these parameters **Distinguishable** when there is
+a *10%* (or lower) chance a sampled prediction would overlap between the
+restrictive and nonrestrictive.
+There are two reasons why this is quite strict threshold:
+for a single bolus exposure/treatment, the differences over time collapse to
+zero (or realistically, the limit of detection) and when determining distinguishability I would like to ensure that it is as clearly distinguishable as
+possible.
+The latter reasoning does pose a risk of false negatives (calling something
+non-distinguishable in error) but this is partly assuaged by the motivation to
+find a robust training set for a QSAR or QSAR-like model of clearance.
+The non-distinguishable set will also play a role in the model.
+
 ```{r set_parameters}
@@
 CENSORPARS = list(Funbound.plasma = list(cv = 0.1, lod = 1E-5))
-HUMAN_CLINT_FUP = TRUE
+HUMAN_CLINT_FUP = FALSE
 SPECIES_TEXT <- ifelse(SPECIES != "Human" && HUMAN_CLINT_FUP,
@@
                                 model = "gas_pbtk", suppress.messages = TRUE)
-```
-
-```{r helper_functions}
-# Get all simulations (restrictive and nonrestrictive)
-conc_fun_wsamples <- function(
-    # Parameterizing args
-    dtxsid,
-    species = "Human",
-    default_to_human = FALSE,
-    force_human = FALSE,
-    # Solving args
-    dose = 20, 
-    route = "iv",
-    times = seq(0, 48, by = 1)/24,
-    # MC sampler args
-    vary.params = NULL,
-    censored.params = NULL,
-    samples = 1000
-) {
-  # Decided to do both Clearances in one go
-  # parameterization to be able to explicitly force human clint and fup
-
-  # Parameterize
-  gas_pars <- standard_parameterization(
-    dtxsid = dtxsid,
-    species = species,
-    default_to_human = default_to_human,
-    force_human = force_human
-  )
-
-  # SOLVE NUMERICALLY
-  numerical_solution <- standard_httk_preds(parameters = gas_pars,
-                                            species = species,
-                                            default_to_human = default_to_human,
-                                            force_human = force_human,
-                                            dose = dose,
-                                            route = route,
-                                            times = times)
-
-  mc_solutions <- standard_httk_mc(parameters = gas_pars,
-                                   species = species,
-                                   default_to_human = default_to_human,
-                                   force_human = force_human,
-                                   dose = dose,
-                                   route = route,
-                                   times = times,
-                                   vary.params = vary.params,
-                                   censored.params = censored.params,
-                                   samples = samples)
-
-  # Merge the solutions
-  tmp <- merge(numerical_solution, mc_solutions)
-  tmp <- subset(tmp, Time %in% times)
-
-  # Time from days to hours
-  tmp$Time <- janitor::round_to_fraction(tmp$Time * 24, denominator = 60)
-
-  return(tmp)
-}
-
 ```
@@
 }
-
 ```
 
-#### Set-up assessment functions
+#### Assesing all chemicals
 
@@
 of variation for `Clint` and `Funbound.plasma`. However, there may be specific
-doses and CVs for which we want to test. Note that there are
+doses and CVs for which we want to test.
 
-```{r all_chems_fun}
-
+```{r helper_functions}
+# Function for standardized assessment of restrictive and non-restrictive
 assessment_fun <- function(
@@
 # Parallelized simulation assessment
-detectCores() # 16 cores, use 12
+detectCores() # 16 cores, use 10
 gc()
 
-clust <- makeCluster(14L)
+clust <- makeCluster(12L)
 clusterEvalQ(clust, library("httk"))
@@
 
+# low, hi, mid refer to the hepatic extraction coefficient.
 table(sim_bins)
@@
 saveRDS(bindf,
-        paste0("data-raw/", SPECIES_TEXT, "_", ROUTE, INVITROUV_TEXT,
+        paste0("data-raw/RCdata/",
+               SPECIES_TEXT, "_",
+               ROUTE,
+               INVITROUV_TEXT,
                "_simulation_bins.rds")
@@
 ```{r plot_all_chems}
-# Parallelized simulation assessment
+# Parallelize simulation assessment
 clust <- makeCluster(12L)
@@
 
-pdf(file = paste0(Sys.getenv("FIG_DIR"), "RestNonRest_",SPECIES_TEXT,
+pdf(file = paste0(Sys.getenv("FIG_DIR"),
+                  "RestrictiveClearance_Analysis/RestNonRest_",
+                  SPECIES_TEXT,
                   ROUTE,"_Comparison_gasPBTK.pdf"),
     paper = "usr", bg = "white")
-for (i in seq_along(sim_pls)) {
+
+for (i in cli::cli_progress_along(sim_pls)) {
   print(sim_pls[[i]])
@@
 rm(sim_pls)
+rm(clust)
 gc()
@@
 ```{r lombardo_sipes}
-
+# Run the `external-data` chunk in ClearanceProject-1-Data.Rmd
 load(file = "data-raw/CYP_Sipes2017.Rdata")
@@
 
-```{r data-specific-parameterization}
-# Each x is a grouped split of a data.frame
-# Using a factor of DTXSID, Species, Media, Route, Dose
-invivo_prediction <- function(
-    x,
-    vary.params = VARPARS,
-    censored.params = CENSORPARS,
-    force_human = HUMAN_CLINT_FUP
-) {
-  dtxsid <- unique(x[["DTXSID"]])
-  species <- tools::toTitleCase(unique(x[['Species']]))
-  media <- unique(x[['Media']])
-  route <- unique(x[['Route']])
-  dose <- unique(x[['Dose']])
-  times <- unique(x[['Time']])/24 # Multiple values (in hours)
-
-  invivo_preds <- conc_fun_wsamples(
-    dtxsid = dtxsid,
-    species = species,
-    dose = dose,
-    route = route,
-    times = times,
-    samples = 1000,
-    force_human = force_human,
-    vary.params = vary.params,
-    censored.params = censored.params
-  ) |> try()
-
-  if (inherits(invivo_preds, "try-error")) return(NULL)
-
-  # If measured media is blood need to divide CPLASMA results by Rblood2plasma
-  if (media == "blood") {
-    Rb2p <- standard_parameterization(
-      dtxsid = dtxsid, 
-      species = species,
-      force_human = force_human
-    )[['par_rest']][['Rblood2plasma']]
-
-    browser()
-    cols2convert <- apply(
-      expand.grid(c("Sol", "l95", "MED", "u95"), c("_R", "_N")),
-      MARGIN = 1,
-      paste0, collapse = ""
-      )
-
-    invivo_preds <- invivo_preds |>
-      dplyr::mutate(dplyr::across(dplyr::all_of(cols2convert), function(x) x / Rb2p))
-  }
-
-  cbind(
-    data.frame(
-    DTXSID = dtxsid,
-    Species = tolower(species),
-    Dose = dose,
-    Route = route,
-    Media = media
-    ),
-    as.data.frame(censored.params),
-    as.data.frame(vary.params),
-    invivo_preds
-  )
-}
-
-```
-
 ```{r run_invivo_preds}
@@
 system.time(
-  temp_lst <- parLapply(clust, temp_lst, invivo_prediction)
+  temp_lst <- parLapply(clust, temp_lst, cvt_httk_predictions)
 )
@@
 fit_tree_rat <- rpart::rpart(Bin ~ ., data = tree_rat)
+
+png(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
+    "RestrictiveClearance_Analysis/Rat_Tree.png"
+  ),
+  width = 4, height = 3, units = "in", bg = "white",
+  res = 200
+)
 rpart.plot::rpart.plot(fit_tree_rat)
+dev.off()
+
 preds_tree <- predict(fit_tree_rat, tree_rat, type = "class")
 caret::confusionMatrix(preds_tree, tree_rat$Bin, positive = 'Distinguished')
+
+saveRDS(fit_tree_rat, file = "data-raw/RCdata/fit_tree_rat.rds")
 

### 2025-08-22 data-raw/ClearanceProject-1-Data.Rmd
Updates project file organization. Moves common functions to a common, sourced file.

---
title: "Clearance Project - 1 - Data Generation"
author: "Gilberto Padilla Mercado"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

This vignette creates and describes data for downstream analysis.

```{r library_loading}
today <- format(Sys.Date(), "%d%b%Y")
devtools::load_all()
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ctxR)
library(ComplexHeatmap, quietly = TRUE)
library(ggalluvial)
library(flextable)
library(reticulate)
library(patchwork)
source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
```

This code chunk creates and `.RData` file that contains character vectors
of DTXSIDs for:

1. All chemicals with human parameterization available for a 3-compartment model w/ inhalation.  
2. All chemicals with rat parameterization available for a 3-compartment model w/ inhalation.  
3. All chemicals with human and rat plasma concentration over time data.

```{r chemical-lists}
human_chems <- unique(get_cheminfo(
  info = "DTXSID",
  species = "human",
  model = "gas_pbtk",
  physchem.exclude = TRUE,
  suppress.messages = TRUE
)) %>%
  suppressWarnings()

rat_chems <- unique(get_cheminfo(
  info = "DTXSID",
  species = "rat",
  model = "gas_pbtk",
  physchem.exclude = TRUE,
  suppress.messages = TRUE
)) %>%
  suppressWarnings()

cvt_plasma_chems <- cvt %>%
  filter(
    species %in% c("human", "rat"),
    conc_medium_normalized == "plasma"
  ) %>%
  pull(analyzed_chem_dtxsid) %>%
  unique()

# These are the chemicals we can evaluate!
target_chems_human <- intersect(
  cvt_plasma_chems,
  human_chems
)
target_chems_rat <- intersect(
  cvt_plasma_chems,
  rat_chems
)

# save in an .Rdata file
save(target_chems_human, target_chems_rat,
  human_chems, rat_chems,
  cvt_plasma_chems,
  file = "data-raw/chem_lists.RData"
)
```

Below read in some external data which is publicly available already.

- `red_assay_res` is the named object that contains the data from the RED assay
including the dissociation constant $K_d$ for plasma protein binding.  
- `chem_info` is a combined data.frame from calls to `get_chemical_details_batch`
and `get_chem_info_batch`. This uses the `ctxR` API to fetch chemical information
such as physio-chemical properties and SMILES from the CompTox dashboard.  
- `cyp_data` is data from Sipes 2017 predicting the CLint fraction for each CYP enzyme.
- `functional_uses_all` is a list of functional use categories for each chemical
from the Chemical and Products Database.

```{r external_data}
# Here we load Kd/binding affinity data
red_assay_res <- readRDS("data-raw/2019-05-06-REDassay_HTTK.rds")

# ctxR download of all chemicals in gas_pbtk model
# Chemical info and properties (averaging the latter by chemical and experimental/predicted)
chem_info <- get_chemical_details_batch(
  DTXSID = human_chems,
  rate_limit = 0L
) %>%
  filter(!is.na(smiles))
# 9086 total unique chemicals with SMILES data

chem_properties <- get_chem_info_batch(
  DTXSID = chem_info$dtxsid,
  type = "",
  rate_limit = 0L,
  verbose = TRUE
)
# This takes a minute or so... save a reference RDS file to load
# Also get rid of any that don't have SMILES
chem_info %>%
  distinct(
    dtxsid, preferredName,
    qsarReadySmiles, monoisotopicMass
  ) %>%
  right_join(chem_properties) %>%
  filter(!is.na(qsarReadySmiles)) %>%
  saveRDS(file = "data-raw/RCdata/ctxR_3comp2_cheminfo.rds")

# Sipes 2017 data
cyp_data <- readr::read_csv(paste0(
  Sys.getenv("FIG_DIR"),
  "RestrictiveClearance_Analysis/",
  "CLint_CYP_Sipes2017.csv"
)) %>%
  left_join(
    chem.physical_and_invitro.data %>%
      select(CAS = CAS, Chemical = DTXSID) %>%
      distinct()
  ) %>%
  select(Chemical, CAS, starts_with("MET_")) %>%
  filter(!is.na(Chemical))
names(cyp_data) <- c(
  "Chemical", "CAS", "CYP1A2",
  "CYP2C9", "CYP2C19", "CYP2D6", "CYP3A4"
)
# Functional use categories from CPdat
functional_uses_all <- readr::read_csv(paste0(
  Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
  "ChemExpo_bulk_functional_uses_20250304.csv"
))

save(cyp_data,
  file = "data-raw/CYP_Sipes2017.Rdata"
)
```

Next we fit the plasma data from CvTdb, which we already have in the `invivoPKfit`
package using `cvt` object. We also get a few downstream statistics and save them
in an `.RData` file.

```{r inivopkfit}
# Here we fit CvTdb data that has plasma measurements
# Only use plasma for simplicity
this_pk <- pk(cvt %>%
  dplyr::filter(conc_medium_normalized == "plasma")) +
  settings_optimx(method = "bobyqa") +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = FALSE
  ) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  stat_error_model(error_group = vars(Chemical, Species))

this_pk <- do_prefit(this_pk)
this_pk <- do_fit(this_pk, n_cores = 14)
saveRDS(this_pk, "data-raw/plasma_CvTfits.rds")

# Related files for pre-calculated:
# tkstats, winning model, AIC, coef_sd, predictions, etc...
this_winmodel <- get_winning_model(this_pk)

this_tkstats <- eval_tkstats(this_pk,
  model = c("model_1comp", "model_2comp"),
  finite_only = TRUE,
  dose_norm = TRUE
) %>%
  inner_join(this_winmodel)
colnames(this_tkstats) <- gsub("/", "_", colnames(this_tkstats))

winning_preds <- predict(this_pk) %>%
  semi_join(this_winmodel) %>%
  distinct(
    Chemical, Species, Chemical_Name,
    model, method, Dose, Media, Route, Reference, pLOQ, Time,
    N_Subjects, Conc, Conc_est
  )
this_AIC <- AIC(this_pk)
this_coef_win <- coef(this_pk) %>% semi_join(this_winmodel)
this_coef_fit <- this_pk$fit %>% semi_join(this_winmodel)
this_coef_sd_win <- coef_sd(this_pk) %>% semi_join(this_winmodel)

save(this_winmodel, this_tkstats, winning_preds,
  this_AIC, this_coef_win, this_coef_fit, this_coef_sd_win,
  file = "data-raw/plasma_CvTfits_data.RData"
)
```

 We already have the fits from the previous vignette!

### 2025-08-22 data-raw/ClearanceProject-2-RelativeLikelihood.Rmd
Updates project file organization. Moves common functions to a common, sourced file.

@@
 library(ctxR)
-library(ggvenn)
+library(ComplexHeatmap)
 library(ggalluvial)
@@
 ```{r data_loading}
+# TODO: Adjust this to load in new prediction files
+# Adjust rest of document as well!
 this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
@@
 ```{r venn_diagrams}
-member_list <- list(cvt = cvt_plasma_chems,
-                    httk_3comp2 = human_3compchems)
-
-ggvenn(member_list, fill_color = c("white", "white"), auto_scale = FALSE)
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+member_list <- list_to_matrix(list(
+  CvTdb = cvt_plasma_chems,
+  httk_human = human_chems,
+  httk_rat = rat_chems
+)) |> make_comb_mat()
+
+png(
+  paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "httk_vs_CvT_VennDiagram_human.png"),
+    "CURRENT_", "httk_vs_CvT_UpsetPlot.png"
+  ),
   bg = "white",
-       height = 3, width = 5
-)
-
+  height = 4, width = 4, units = "in",
+  res = 200
+)
+
+ComplexHeatmap::UpSet(
+  member_list,
+  set_order = c("CvTdb", "httk_rat", "httk_human"),
+  comb_order = order(comb_size(member_list), decreasing = TRUE),
+  top_annotation = upset_top_annotation(
+    show_annotation_name = FALSE,
+    member_list,
+    axis = FALSE,
+    add_numbers = TRUE,
+    numbers_rot = 0,
+    numbers_gp = gpar(fontsize = 10)
+  ),
+  right_annotation = upset_right_annotation(
+    show_annotation_name = FALSE,
+    member_list,
+    axis = FALSE,
+    add_numbers = TRUE,
+    numbers_rot = 0,
+    numbers_gp = gpar(fontsize = 10)
+  ),
+  pt_size = unit(5, "mm")
+)
+dev.off()
 ```
@@
 ```{r httk_pr_rmsle}
-
 # RMSLE formula
@@
   group_by(Chemical, Species, Route) %>%
-  summarize(RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
+  summarize(
+    RMSLE_restrictive = sqrt(mean(restrictive_SLE, na.rm = TRUE)),
     RMSLE_nonrestrictive = sqrt(mean(nonrestrictive_SLE, na.rm = TRUE)),
-            RMSLE_invivoPKfit = sqrt(mean(invivoPK_SLE, na.rm = TRUE))) %>%
+    RMSLE_invivoPKfit = sqrt(mean(invivoPK_SLE, na.rm = TRUE))
+  ) %>%
   ungroup() %>%
@@
     RMSLE_invivoPKfit > RMSLE_restrictive &
-      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
+      RMSLE_invivoPKfit > RMSLE_nonrestrictive ~ "More than"
   ))
@@
   ungroup() %>%
-  pivot_longer(cols = starts_with("RMSLE_"),
+  pivot_longer(
+    cols = starts_with("RMSLE_"),
     names_to = "Source",
-               values_to = "RMSLE") %>%
+    values_to = "RMSLE"
+  ) %>%
   mutate(Source = factor(Source,
-                         levels = c("RMSLE_nonrestrictive",
+    levels = c(
+      "RMSLE_nonrestrictive",
       "RMSLE_invivoPKfit",
-                                    "RMSLE_restrictive")
+      "RMSLE_restrictive"
+    )
   )) %>%
@@
   geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
-  facet_grid(~factor(comparison_group,
-                     levels = c("Less than", "Between", "More than")),
-             scales = "free_x", space = "free_x") +
+  facet_grid(
+    ~ factor(comparison_group,
+      levels = c("Less than", "Between", "More than")
+    ),
+    scales = "free_x", space = "free_x"
+  ) +
   labs(y = "RMSLE") +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
@@
     axis.title = element_text(size = 14),
-        strip.text = element_text(size = 12))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+    strip.text = element_text(size = 12)
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "RMSLE_comparison_fullChart.png"),
+    "CURRENT_", "RMSLE_comparison_fullChart.png"
+  ),
   bg = "white",
@@
 # Number of chemicals we have RMSLE's for
-combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()
-
+combined_RMSLE %>%
+  pull(Chemical) %>%
+  unique() %>%
+  length()
 ```
@@
 ```{r relative-likelihood}
-
 # AIC and relative likelihood
 # LL from pre-calculated httk predictions
-this_pk <- this_pk %>% fit_sigma.pk(preds = rpr_httk_preds,
-                                    pred_col = "httk_Preds_restrictive")
-this_pk <- this_pk %>% fit_sigma.pk(preds = rpr_httk_preds,
-                                    pred_col = "httk_Preds_nonrestrictive")
+this_pk <- this_pk %>% fit_sigma.pk(
+  preds = rpr_httk_preds,
+  pred_col = "httk_Preds_restrictive"
+)
+this_pk <- this_pk %>% fit_sigma.pk(
+  preds = rpr_httk_preds,
+  pred_col = "httk_Preds_nonrestrictive"
+)
 
@@
   mutate(minAIC = min(c_across(starts_with("model_")),
-                      na.rm = TRUE)) %>%
+    na.rm = TRUE
+  )) %>%
   ungroup() %>%
   mutate(across(starts_with("model_"), \(x) {
-    signif(exp((minAIC - x)/2) * 100, 4)
+    signif(exp((minAIC - x) / 2) * 100, 4)
   })) %>%
@@
   mutate(ll_label = factor(
-    case_when(model_flat > 95 ~ "Undetermined",
+    case_when(
+      model_flat > 95 ~ "Undetermined",
       model_3comp2_nonrestrictive > 50 &
@@
       model_3comp2_nonrestrictive > 50 ~ "Nonrestrictive",
-              model_3comp2_restrictive > 50 ~ "Restrictive")
+      model_3comp2_restrictive > 50 ~ "Restrictive"
+    )
   ))
@@
   select(Chemical, Species, starts_with("model_"), minAIC) %>%
-  mutate(Chemical = forcats::fct_reorder2(Chemical,
+  mutate(Chemical = forcats::fct_reorder2(
+    Chemical,
     model_flat,
     minAIC,
-                                         mean)
-         ) %>%
-  pivot_longer(cols = starts_with("model_"),
-               names_to = "model", values_to = "relative_ll") %>%
+    mean
+  )) %>%
+  pivot_longer(
+    cols = starts_with("model_"),
+    names_to = "model", values_to = "relative_ll"
+  ) %>%
   mutate(
@@
   scale_color_manual(
-    values = c('#33a02c', '#cc88ff', '#7b3294', 'orange'),
-    breaks = c('model_empirical',
-               'model_3comp2_restrictive',
-               'model_3comp2_nonrestrictive',
-               'model_flat')
+    values = c("#33a02c", "#cc88ff", "#7b3294", "orange"),
+    breaks = c(
+      "model_empirical",
+      "model_3comp2_restrictive",
+      "model_3comp2_nonrestrictive",
+      "model_flat"
+    )
   ) +
@@
     y = "More Likely Model >>>",
-    color = ''
+    color = ""
   ) +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
@@
     plot.title = element_text(hjust = 0.5),
-        plot.subtitle = element_text(hjust = 0.5))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+    plot.subtitle = element_text(hjust = 0.5)
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "AIC_comparisons.png"),
+    "CURRENT_", "AIC_comparisons.png"
+  ),
   bg = "white",
@@
   inner_join(rph_param_df %>%
-               distinct(Chemical,
+    distinct(
+      Chemical,
       forced_human_values,
@@
       Fabsgut.nonrestrictive,
-                        CLint)) %>%
+      CLint
+    )) %>%
   mutate(Chemical = forcats::fct_reorder(Chemical, halflife_restrictive)) %>%
@@
 halflife_pl <- this_rel_evaluated_df %>%
-  distinct(Chemical, Species, Css_httk_r,
+  distinct(
+    Chemical, Species, Css_httk_r,
     halflife.tkstats, halflife_restrictive,
     halflife_nonrestrictive,
-           ll_label) %>%
+    ll_label
+  ) %>%
   ggplot(aes(x = Chemical)) +
-  geom_pointrange(aes(y = halflife.tkstats, 
+  geom_pointrange(
+    aes(
+      y = halflife.tkstats,
       ymin = halflife_nonrestrictive,
-                      ymax = halflife_restrictive),
-                  size = 0.1, shape = 23) +
+      ymax = halflife_restrictive
+    ),
+    size = 0.1, shape = 23
+  ) +
   facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
@@
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
@@
     axis.text.y = element_text(color = "black", size = 10),
-        axis.title = element_text(size = 10))
-
-ggsave(halflife_pl, filename = paste0(Sys.getenv("FIG_DIR"),
+    axis.title = element_text(size = 10)
+  )
+
+ggsave(halflife_pl,
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "halflife_fullChart.png"),
+    "CURRENT_", "halflife_fullChart.png"
+  ),
   bg = "white",
@@
 css_pl <- this_rel_evaluated_df %>%
-  distinct(Chemical, Species, Css.tkstats, Css_httk_nr, Css_httk_r,
-         ll_label) %>%
+  distinct(
+    Chemical, Species, Css.tkstats, Css_httk_nr, Css_httk_r,
+    ll_label
+  ) %>%
   ggplot(aes(x = Chemical)) +
   geom_pointrange(aes(y = Css.tkstats, ymin = Css_httk_nr, ymax = Css_httk_r),
-                  size = 0.1, shape = 23) +
+    size = 0.1, shape = 23
+  ) +
   facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
   scale_y_log10() +
-  labs(x = 'Chemicals', y = "Css") +
+  labs(x = "Chemicals", y = "Css") +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
@@
     axis.text.y = element_text(color = "black", size = 10),
-        axis.title = element_text(size = 10))
+    axis.title = element_text(size = 10)
+  )
 
 cltot_pl <- this_rel_evaluated_df %>%
-  distinct(Chemical, Species, CLtot_Fgutabs.tkstats,
+  distinct(
+    Chemical, Species, CLtot_Fgutabs.tkstats,
     CLtot_restrictive, CLtot_nonrestrictive,
     Fabsgut.restrictive, Fabsgut.nonrestrictive,
-         ll_label) %>%
+    ll_label
+  ) %>%
   ggplot(aes(x = Chemical)) +
-  geom_pointrange(aes(y = CLtot_Fgutabs.tkstats,
-                      ymin = CLtot_restrictive/Fabsgut.restrictive,
-                      ymax = CLtot_nonrestrictive/Fabsgut.nonrestrictive),
-                  size = 0.1, shape = 23) +
+  geom_pointrange(
+    aes(
+      y = CLtot_Fgutabs.tkstats,
+      ymin = CLtot_restrictive / Fabsgut.restrictive,
+      ymax = CLtot_nonrestrictive / Fabsgut.nonrestrictive
+    ),
+    size = 0.1, shape = 23
+  ) +
   facet_grid(cols = vars(ll_label), space = "free_x", scales = "free_x") +
   scale_y_log10() +
-  labs(x = 'Chemicals', y = "CLtot/Fabsgut") +
+  labs(x = "Chemicals", y = "CLtot/Fabsgut") +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
@@
     axis.text.y = element_text(color = "black", size = 10),
-        axis.title = element_text(size = 10))
+    axis.title = element_text(size = 10)
+  )
 
 (halflife_pl + theme(axis.title.x = element_blank())) /
-  (css_pl+ theme(axis.title.x = element_blank())) /
+  (css_pl + theme(axis.title.x = element_blank())) /
   cltot_pl
 
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "tkcomparisons_fullChart.png"),
+    "CURRENT_", "tkcomparisons_fullChart.png"
+  ),
   bg = "white",
@@
   group_by(`Harmonized Functional Use`) %>%
-  count() %>% arrange(-n) %>% head(20) %>% pull(1)
+  count() %>%
+  arrange(-n) %>%
+  head(20) %>%
+  pull(1)
 target_chem_functions <- functional_uses_all %>%
@@
   group_by(`Harmonized Functional Use`) %>%
-  count() %>% arrange(-n) %>% head(20) %>% pull(1)
-
-combined_function_list <- union(all_chem_functions,
-                                target_chem_functions) # 25 total
+  count() %>%
+  arrange(-n) %>%
+  head(20) %>%
+  pull(1)
+
+combined_function_list <- union(
+  all_chem_functions,
+  target_chem_functions
+) # 25 total
 
@@
   janitor::clean_names() %>%
-  mutate(n_total_targets = length(target_chems_human),
+  mutate(
+    n_total_targets = length(target_chems_human),
     n_total_nontargets = length(human_3compchems) - n_total_targets,
     n_nontargets_out = n_total_nontargets - n_nontargets,
-         n_targets_out = n_total_targets - n_targets) %>%
+    n_targets_out = n_total_targets - n_targets
+  ) %>%
   select(!c(n_total_nontargets, n_total_targets))
@@
   rowwise() %>%
-  mutate(odds_ratio = fisher.test(
-    matrix(c(n_targets, n_nontargets,
-             n_targets_out, n_nontargets_out),
-           nrow = 2),
-    alternative = "greater")$estimate,
+  mutate(
+    odds_ratio = fisher.test(
+      matrix(
+        c(
+          n_targets, n_nontargets,
+          n_targets_out, n_nontargets_out
+        ),
+        nrow = 2
+      ),
+      alternative = "greater"
+    )$estimate,
     pval = fisher.test(
-    matrix(c(n_targets, n_nontargets,
-             n_targets_out, n_nontargets_out),
-           nrow = 2),
-    alternative = "greater")$p.value
+      matrix(
+        c(
+          n_targets, n_nontargets,
+          n_targets_out, n_nontargets_out
+        ),
+        nrow = 2
+      ),
+      alternative = "greater"
+    )$p.value
   ) %>%
   ungroup() %>%
-  mutate(padj = 0.05/n()) %>%
+  mutate(padj = 0.05 / n()) %>%
   arrange(pval)
@@
 upset_pl <- this_rel_evaluated_df %>%
-  distinct(Chemical, Species, Css_httk_r,
+  distinct(
+    Chemical, Species, Css_httk_r,
     halflife.tkstats, halflife_restrictive,
     halflife_nonrestrictive,
-           ll_label) %>%
+    ll_label
+  ) %>%
   left_join(functional_uses_all %>%
@@
       "Pharmaceutical (EPA)",
-              "Degradant/impurity (EPA)"))
-          ) %>%
+      "Degradant/impurity (EPA)"
+    ))) %>%
   # filter(!is.na(`Harmonized Functional Use`)) %>%
@@
   theme_minimal() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     panel.grid.minor = element_blank(),
@@
     strip.text = element_blank(),
-        legend.title = element_blank(), axis.title.y = element_blank())
+    legend.title = element_blank(), axis.title.y = element_blank()
+  )
 
@@
 
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "tkcomparisons_withUpset.png"),
+    "CURRENT_", "tkcomparisons_withUpset.png"
+  ),
   bg = "white",
@@
     harmonized_functional_use = forcats::fct_reorder(
-      harmonized_functional_use, odds_ratio)
+      harmonized_functional_use, odds_ratio
+    )
   ) %>%
@@
   ggplot() +
-  geom_col(aes(x = odds_ratio, 
+  geom_col(
+    aes(
+      x = odds_ratio,
       y = harmonized_functional_use,
-                fill = padj_val),
+      fill = padj_val
+    ),
     color = "black", linewidth = 0.2,
-           width = 0.75) +
-  scale_fill_viridis_b(option = "viridis", direction = -1,
+    width = 0.75
+  ) +
+  scale_fill_viridis_b(
+    option = "viridis", direction = -1,
     breaks = c(0, 0.05, 0.1, 0.5),
@@
   ) +
-  scale_x_continuous(limits = c(0, 12),
-                     expand = expansion()) +
-  labs(x = "Enrichment Score", y = "",
+  scale_x_continuous(
+    limits = c(0, 12),
+    expand = expansion()
+  ) +
+  labs(
+    x = "Enrichment Score", y = "",
     title = "Enrichment of Functional Use Categories",
-       fill = "adjusted p-value") +
+    fill = "adjusted p-value"
+  ) +
   theme_bw() +
-  theme(legend.title = element_text(hjust = 0.5),
+  theme(
+    legend.title = element_text(hjust = 0.5),
     axis.text = element_text(color = "black"),
     axis.text.y = element_text(face = "bold", size = 10),
-        plot.title = element_text(hjust = 0.5))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+    plot.title = element_text(hjust = 0.5)
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "FunctionalUse_Enrichment.png"),
+    "CURRENT_", "FunctionalUse_Enrichment.png"
+  ),
   bg = "white",
@@
 ```{r selecting_chemical_params}
-
 # Testing to make sure there are some chemicals that have different clearances
@@
 # The majority (140) do!
-
 ```
@@
 red_assay_res %>%
-  distinct(DTXSID, Affinity.Kd.Med, Affinity.Kd.Low, Affinity.Kd.High,
-           Fit) %>%
+  distinct(
+    DTXSID, Affinity.Kd.Med, Affinity.Kd.Low, Affinity.Kd.High,
+    Fit
+  ) %>%
   na.omit() %>%
   mutate(Target_Chemical = (DTXSID %in% target_chems_human)) %>%
-
   ggplot(
@@
       x = forcats::fct_reorder(DTXSID, Affinity.Kd.Low)
-         )) +
+    )
+  ) +
   geom_linerange(aes(
@@
     plot.title = element_text(hjust = 0.5, face = "bold"),
-        legend.position = "bottom") +
+    legend.position = "bottom"
+  ) +
   labs(title = "Kd estimates across chemicals", x = NULL)
 
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Kd_estimates_initialsummary.png"),
+    "CURRENT_", "Kd_estimates_initialsummary.png"
+  ),
   bg = "white",
@@
   select(DTXSID, Human.Funbound.plasma, Rat.Funbound.plasma) %>%
-  mutate(Rat.Funbound.plasma = as.numeric(str_extract(Rat.Funbound.plasma,
-                                                      "^([^,]+)")),
-         Human.Funbound.plasma = as.numeric(str_extract(Human.Funbound.plasma,
-                                                        "^([^,]+)"))
+  mutate(
+    Rat.Funbound.plasma = as.numeric(str_extract(
+      Rat.Funbound.plasma,
+      "^([^,]+)"
+    )),
+    Human.Funbound.plasma = as.numeric(str_extract(
+      Human.Funbound.plasma,
+      "^([^,]+)"
+    ))
   )
@@
   inner_join(all_hum_rat_fups) %>%
-  pivot_longer(cols = Human.Funbound.plasma:Rat.Funbound.plasma,
-               names_to = "Species", values_to = "httk_fup_med") %>%
+  pivot_longer(
+    cols = Human.Funbound.plasma:Rat.Funbound.plasma,
+    names_to = "Species", values_to = "httk_fup_med"
+  ) %>%
   ggplot(aes(x = Affinity.Kd.Med, y = httk_fup_med, color = Species)) +
   geom_point(alpha = 0.5) +
-  scale_color_manual(values = c("green4", "purple2"),
-                     labels = c("Human", "Rat")) +
+  scale_color_manual(
+    values = c("green4", "purple2"),
+    labels = c("Human", "Rat")
+  ) +
   scale_x_log10(labels = scales::label_log(digits = 2)) +
-  labs(x = "Dissociation constant Kd\n(uM, from in vitro RED assay)",
-       y = "Fraction unbound\nin plasma") +
+  labs(
+    x = "Dissociation constant Kd\n(uM, from in vitro RED assay)",
+    y = "Fraction unbound\nin plasma"
+  ) +
   theme_bw() +
-  theme(legend.position = "left",
+  theme(
+    legend.position = "left",
     legend.text = element_text(size = 8),
@@
     axis.title = element_text(size = 10),
-        axis.text = element_text(size = 8, color = "black"))
+    axis.text = element_text(size = 8, color = "black")
+  )
 
@@
 
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Kd_estimates_vs_fup_multispecies.png"),
+    "CURRENT_", "Kd_estimates_vs_fup_multispecies.png"
+  ),
   bg = "white",
@@
   ungroup() %>%
-  pivot_longer(cols = starts_with("model_"),
+  pivot_longer(
+    cols = starts_with("model_"),
     names_to = "all_models",
-               values_to = "relative_likelihood") %>% 
+    values_to = "relative_likelihood"
+  ) %>%
   ungroup() %>%
-  mutate(gamma_weight = 100 * RMSLE_invivoPKfit / relative_likelihood,
+  mutate(
+    gamma_weight = 100 * RMSLE_invivoPKfit / relative_likelihood,
     rmsle_comparison_group = case_when(
@@
       RMSLE_invivoPKfit > RMSLE_restrictive &
-      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than")
+        RMSLE_invivoPKfit > RMSLE_nonrestrictive ~ "More than"
+    )
   ) %>%
   mutate(rmsle_comparison_group = factor(rmsle_comparison_group,
-                                         levels = c("Less than", "Between",
-                                                    "More than"))) %>%
-  select(-all_models) %>% distinct()
+    levels = c(
+      "Less than", "Between",
+      "More than"
+    )
+  )) %>%
+  select(-all_models) %>%
+  distinct()
 
@@
   geom_freqpoly() +
-  labs(x = "Inverse Confidence",
-       color = "RMSLE relative to httk predictions") +
+  labs(
+    x = "Inverse Confidence",
+    color = "RMSLE relative to httk predictions"
+  ) +
   facet_grid(rows = vars(rmsle_comparison_group)) +
   theme_bw()
-
 ```
@@
   !is.na(halflife.tkstats)
-) %>% flextable() %>%
+) %>%
+  flextable() %>%
   set_header_labels(
@@
 count(this_tkstats %>% filter_targets(), is.na(Css.tkstats))
-
 ```
@@
 ```{r Css_assessment}
-
 # Table
 rph_httk_clearance_df %>%
-  count(Css_httk_r == Css_httk_nr,
+  count(
+    Css_httk_r == Css_httk_nr,
     Css_httk_r - Css_httk_nr < 0.1 & Css_httk_r - Css_httk_nr > 0,
-        Css_httk_r - Css_httk_nr >= 0.1) %>%
-  rename("No difference" = "Css_httk_r == Css_httk_nr",
+    Css_httk_r - Css_httk_nr >= 0.1
+  ) %>%
+  rename(
+    "No difference" = "Css_httk_r == Css_httk_nr",
     "Less than 0.1" = "Css_httk_r - Css_httk_nr < 0.1 & Css_httk_r - Css_httk_nr > 0",
-         "At least 0.1" = "Css_httk_r - Css_httk_nr >= 0.1")
+    "At least 0.1" = "Css_httk_r - Css_httk_nr >= 0.1"
+  )
 
@@
 rph_httk_clearance_df %>%
-  mutate(relative_difference = (Css_httk_r - Css_httk_nr)/Css_httk_nr) %>%
+  mutate(relative_difference = (Css_httk_r - Css_httk_nr) / Css_httk_nr) %>%
   count(relative_difference == 0, Css_httk_r == 0) # 31 Chemicals have zero difference
@@
 rph_httk_clearance_df %>%
-  mutate(relative_difference = (Css_httk_r - Css_httk_nr)/Css_httk_nr) %>%
+  mutate(relative_difference = (Css_httk_r - Css_httk_nr) / Css_httk_nr) %>%
   filter(relative_difference > 0) %>%
@@
     max,
-                                      .desc = FALSE))) +
+    .desc = FALSE
+  ))) +
   geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r),
-                 linewidth = 1.25) +
-  labs(title = "Css differences between restrictive & nonrestrictive clearance",
-       y = "Css\n(mg/L)", x = "Chemicals") +
+    linewidth = 1.25
+  ) +
+  labs(
+    title = "Css differences between restrictive & nonrestrictive clearance",
+    y = "Css\n(mg/L)", x = "Chemicals"
+  ) +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks = element_blank(),
@@
     axis.title = element_text(size = 10),
-        axis.text.y = element_text(size = 8, color = "black"))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+    axis.text.y = element_text(size = 8, color = "black")
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_difference_httk_lineplot.png"),
+    "CURRENT_", "Css_difference_httk_lineplot.png"
+  ),
   bg = "white",
-       height = 3, width = 8)
+  height = 3, width = 8
+)
 
 rph_httk_clearance_df %>%
-  mutate(relative_difference = log1p((Css_httk_r - Css_httk_nr)/Css_httk_nr)) %>%
+  mutate(relative_difference = log1p((Css_httk_r - Css_httk_nr) / Css_httk_nr)) %>%
   filter(relative_difference > 0) %>%
@@
     max,
-                                      .desc = FALSE))) +
-  geom_linerange(aes(ymin = 0,
-                     ymax = 0 + relative_difference),
-                 linewidth = 1) +
+    .desc = FALSE
+  ))) +
+  geom_linerange(
+    aes(
+      ymin = 0,
+      ymax = 0 + relative_difference
+    ),
+    linewidth = 1
+  ) +
   labs(
-    title = paste0("Relative Css differences between\n",
-                   "restrictive & nonrestrictive clearance"),
-       y = "log10 Css\n(relative difference, mg/L)", x = "Chemicals") +
+    title = paste0(
+      "Relative Css differences between\n",
+      "restrictive & nonrestrictive clearance"
+    ),
+    y = "log10 Css\n(relative difference, mg/L)", x = "Chemicals"
+  ) +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks = element_blank(),
@@
     axis.title = element_text(size = 10),
-        axis.text.y = element_text(size = 8, color = "black"))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+    axis.text.y = element_text(size = 8, color = "black")
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_relativedifference_httk_lineplot.png"),
+    "CURRENT_", "Css_relativedifference_httk_lineplot.png"
+  ),
   bg = "white",
-       height = 3, width = 5.75)
+  height = 3, width = 5.75
+)
 
@@
   filter(relative_difference > 0) %>%
-  ggplot(aes(x = forcats::fct_reorder(Chemical,
-                                      relative_difference))) +
+  ggplot(aes(x = forcats::fct_reorder(
+    Chemical,
+    relative_difference
+  ))) +
   geom_point(aes(size = relative_difference), y = 0, alpha = 0.2, shape = 16) +
-  annotate(x = 1, y = 150 ,label = "Min: 0 mg/L\n31 Chemicals", geom = "text") +
-  annotate(x = 140, y = 150 ,label = "Max: 30 mg/L\n", geom = "text") +
-  scale_y_continuous(limits = c(-150,150)) +
+  annotate(x = 1, y = 150, label = "Min: 0 mg/L\n31 Chemicals", geom = "text") +
+  annotate(x = 140, y = 150, label = "Max: 30 mg/L\n", geom = "text") +
+  scale_y_continuous(limits = c(-150, 150)) +
   scale_size_area(max_size = 40) +
@@
   theme_void() +
-  theme(legend.position = "none",
-        plot.margin = unit(c(2,2,1,2), units = "inches"))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+  theme(
+    legend.position = "none",
+    plot.margin = unit(c(2, 2, 1, 2), units = "inches")
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "Css_difference_httk_inkblot.png"),
+    "CURRENT_", "Css_difference_httk_inkblot.png"
+  ),
   bg = "white",
-       height = 5, width = 7)
+  height = 5, width = 7
+)
 ###
@@
     case_when(
-    between(log2(CLtot.tkstats), 
-            log2(CLtot_restrictive)-1,
-            log2(CLtot_restrictive)+1) ~ "Restrictive",
-    between(log2(CLtot.tkstats), 
-            log2(CLtot_nonrestrictive)-1,
-            log2(CLtot_nonrestrictive)+1) ~ "Nonrestrictive",
-    between(CLtot.tkstats,
-            CLtot_restrictive, CLtot_nonrestrictive) ~ "Between",
+      between(
+        log2(CLtot.tkstats),
+        log2(CLtot_restrictive) - 1,
+        log2(CLtot_restrictive) + 1
+      ) ~ "Restrictive",
+      between(
+        log2(CLtot.tkstats),
+        log2(CLtot_nonrestrictive) - 1,
+        log2(CLtot_nonrestrictive) + 1
+      ) ~ "Nonrestrictive",
+      between(
+        CLtot.tkstats,
+        CLtot_restrictive, CLtot_nonrestrictive
+      ) ~ "Between",
       .default = "Out of Range"
-  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of Range")
+    ),
+    levels = c("Nonrestrictive", "Between", "Restrictive", "Out of Range")
   ))
 enhanced_tkstats %>%
-  ggplot(aes(forcats::fct_reorder(Chemical,
-                          gamma_weight))) +
+  ggplot(aes(forcats::fct_reorder(
+    Chemical,
+    gamma_weight
+  ))) +
   geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
-             shape = 21) +
-  geom_linerange(aes(ymin = CLtot_restrictive, 
-                     ymax = CLtot_nonrestrictive)) +
+    shape = 21
+  ) +
+  geom_linerange(aes(
+    ymin = CLtot_restrictive,
+    ymax = CLtot_nonrestrictive
+  )) +
   geom_point(aes(y = CLtot_restrictive),
-             shape = 2, size = 0.8) + # Note that this is the lower value
+    shape = 2, size = 0.8
+  ) + # Note that this is the lower value
   geom_point(aes(y = CLtot_nonrestrictive),
-             shape = 6, size = 0.8) +
-  scale_fill_viridis_b(option = "viridis", 
+    shape = 6, size = 0.8
+  ) +
+  scale_fill_viridis_b(
+    option = "viridis",
     guide = guide_colorbar(position = "bottom"),
-                       limits = c(0,1.5)) +
+    limits = c(0, 1.5)
+  ) +
   scale_y_log10() +
-  facet_grid(cols = vars(comparison_CLtot),
+  facet_grid(
+    cols = vars(comparison_CLtot),
     scales = "free_x",
-             space = "free_x") +
+    space = "free_x"
+  ) +
   labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence") +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
     plot.subtitle = element_text(hjust = 0.5),
-        legend.title = element_text(vjust = 0.8))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+    legend.title = element_text(vjust = 0.8)
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
+    "CURRENT_", "TotalClearance_withRMSLEweights.png"
+  ),
   bg = "white",
@@
 ```{r CLtot_subset_withCss}
-
 this_tkstats %>%
@@
     case_when(
-      between(log2(CLtot.tkstats),log2(CLtot_restrictive)-1,
-              log2(CLtot_restrictive)+1) ~ "Restrictive",
-      between(log2(CLtot.tkstats),log2(CLtot_nonrestrictive)-1,
-              log2(CLtot_nonrestrictive)+1) ~ "Nonrestrictive",
-      between(CLtot.tkstats,
-              CLtot_restrictive, CLtot_nonrestrictive) ~ "Between",
+      between(
+        log2(CLtot.tkstats), log2(CLtot_restrictive) - 1,
+        log2(CLtot_restrictive) + 1
+      ) ~ "Restrictive",
+      between(
+        log2(CLtot.tkstats), log2(CLtot_nonrestrictive) - 1,
+        log2(CLtot_nonrestrictive) + 1
+      ) ~ "Nonrestrictive",
+      between(
+        CLtot.tkstats,
+        CLtot_restrictive, CLtot_nonrestrictive
+      ) ~ "Between",
       .default = "Out of range"
-  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of range"))) %>%
-  ggplot(aes(forcats::fct_reorder(Chemical,
-                          gamma_weight))) +
+    ),
+    levels = c("Nonrestrictive", "Between", "Restrictive", "Out of range")
+  )) %>%
+  ggplot(aes(forcats::fct_reorder(
+    Chemical,
+    gamma_weight
+  ))) +
   geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
-             shape = 21) +
-  geom_linerange(aes(ymin = CLtot_restrictive, 
-                     ymax = CLtot_nonrestrictive)) +
+    shape = 21
+  ) +
+  geom_linerange(aes(
+    ymin = CLtot_restrictive,
+    ymax = CLtot_nonrestrictive
+  )) +
   geom_point(aes(y = CLtot_restrictive),
-             shape = 4, size = 0.8) + # Note that this is the lower value
+    shape = 4, size = 0.8
+  ) + # Note that this is the lower value
   geom_point(aes(y = CLtot_nonrestrictive),
-             shape = 4, size = 0.8) +
-  scale_fill_viridis_b(option = "viridis", 
-                        guide = guide_colorbar(position = "bottom")) +
+    shape = 4, size = 0.8
+  ) +
+  scale_fill_viridis_b(
+    option = "viridis",
+    guide = guide_colorbar(position = "bottom")
+  ) +
   scale_y_log10() +
-  facet_grid(cols = vars(comparison_CLtot),
-             scales = "free_x") +
-  labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence",
-       subtitle = "Estimates within 2-fold of in vitro modelled predictions") +
+  facet_grid(
+    cols = vars(comparison_CLtot),
+    scales = "free_x"
+  ) +
+  labs(
+    y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence",
+    subtitle = "Estimates within 2-fold of in vitro modelled predictions"
+  ) +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
+  theme(
+    axis.text.x = element_blank(),
     axis.ticks.x = element_blank(),
     plot.subtitle = element_text(hjust = 0.5),
-        legend.title = element_text(vjust = 0.8))
-
-ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+    legend.title = element_text(vjust = 0.8)
+  )
+
+ggsave(
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
     "RestrictiveClearance_Analysis/",
-                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
+    "CURRENT_", "TotalClearance_withRMSLEweights.png"
+  ),
   bg = "white",
@@
 ```{r rudimentary_clustering}
-
 # Set up a data.frame that has chemical, Css difference, Funbound z-score,
 # nearest_clearance (using Css), and model weight
-this_fupZ_df <- rph_param_df %>% select(Chemical, Funbound.plasma) %>%
-  mutate(Fup_Z = as.vector(scale(sqrt(Funbound.plasma))),
-         .keep = "unused")
-
+this_fupZ_df <- rph_param_df %>%
+  select(Chemical, Funbound.plasma) %>%
+  mutate(
+    Fup_Z = as.vector(scale(sqrt(Funbound.plasma))),
+    .keep = "unused"
+  )
 ```
@@
 
-ggplot(data = rph_httk_clearance_df,
-       aes(x = Chemical)) +
+ggplot(
+  data = rph_httk_clearance_df,
+  aes(x = Chemical)
+) +
   geom_point(aes(y = CLtot_restrictive), color = "green4") +
   geom_point(aes(y = CLtot_nonrestrictive), color = "orange2") +
-  geom_point(data = this_tkstats2,
-             aes(y = CLtot_calc)) +
+  geom_point(
+    data = this_tkstats2,
+    aes(y = CLtot_calc)
+  ) +
   scale_y_log10() +
   theme_bw() +
-  theme(axis.text.x = element_blank(),
-        axis.ticks.x = element_blank())
+  theme(
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank()
+  )
 
@@
   geom_line(aes(y = Cliver), color = "darkgreen")
-
 ```
@@
   dplyr::select(-c(log_likelihood, npar)) %>%
-  pivot_wider(names_from = model,
-              values_from = AIC) %>% 
+  pivot_wider(
+    names_from = model,
+    values_from = AIC
+  ) %>%
   rowwise() %>%
@@
   mutate(across(starts_with("model_"), \(x) {
-    signif(exp((minAIC - x)/2) * 100, 4)
+    signif(exp((minAIC - x) / 2) * 100, 4)
   }))
@@
 # We can inspect this visually
-rel_ll %>% arrange(desc(model_flat)) %>% head()
+rel_ll %>%
+  arrange(desc(model_flat)) %>%
+  head()
 rel_ll %>%
@@
   rowwise() %>%
-  mutate(across(contains("_1comp"),
+  mutate(across(
+    contains("_1comp"),
     \(x) {
@@
       )
-                })) %>% 
+    }
+  )) %>%
   filter(!if_all(contains("_1comp_"), is.na)) %>%
@@
       )
-                })) %>% 
+    }
+  )) %>%
   count(is.na(model_1comp_fup))
@@
 new_pk$fit %>%
-  filter(param_name %in% "Fup",
-         model %in% "model_1comp_fup") %>%
+  filter(
+    param_name %in% "Fup",
+    model %in% "model_1comp_fup"
+  ) %>%
   ggplot(aes(x = estimate, y = start)) +
@@
   theme_bw() +
-  coord_equal(xlim = c(0,1), ylim = c(0,1),
-              expand = TRUE) +
+  coord_equal(
+    xlim = c(0, 1), ylim = c(0, 1),
+    expand = TRUE
+  ) +
   coord_flip()
 
-ggsave(filename = paste0(
+ggsave(
+  filename = paste0(
     Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
-  today, "fup_optimization_allowingHuman.png"),
-  height = 5, width = 5)
+    today, "fup_optimization_allowingHuman.png"
+  ),
+  height = 5, width = 5
+)
 
 new_pk$fit %>%
-  filter(param_name %in% "Fup",
-         model %in% "model_1comp_fup") %>%
-  distinct(Chemical, Species, method, model,
-           param_name, estimate, start) %>%
+  filter(
+    param_name %in% "Fup",
+    model %in% "model_1comp_fup"
+  ) %>%
+  distinct(
+    Chemical, Species, method, model,
+    param_name, estimate, start
+  ) %>%
   mutate(direction = ifelse(abs(estimate - start) < 0.1,
@@
       "increase",
-                                   "decrease"))) %>%
+      "decrease"
+    )
+  )) %>%
   # filter(direction %in% "similar (less than 10% difference)") %>%
-  pivot_longer(cols = c(estimate, start),
+  pivot_longer(
+    cols = c(estimate, start),
     names_to = "parameterization",
-               values_to = "value") %>%
+    values_to = "value"
+  ) %>%
   mutate(parameterization = factor(parameterization,
-                                   levels = c("start", "estimate"))) %>%
+    levels = c("start", "estimate")
+  )) %>%
   ggplot(aes(x = parameterization, y = value)) +
@@
 
-ggsave(filename = paste0(
+ggsave(
+  filename = paste0(
     Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
-  today, "fup_optimization_generalFits_allowingHuman.png"),
-  height = 5, width = 7)
-
+    today, "fup_optimization_generalFits_allowingHuman.png"
+  ),
+  height = 5, width = 7
+)
 ```
@@
   geom_point(aes(y = CLtot.httk_rest),
-             shape = 19, size = 2, color = "green4") +
+    shape = 19, size = 2, color = "green4"
+  ) +
   geom_point(aes(y = CLtot.httk_nonrest),
-             shape = 19, size = 2, color = "orange2") +
-  geom_point(aes(y = CLtot.tkstats,
-                 shape = Species), size = 3, color = "black", stroke = 1) +
+    shape = 19, size = 2, color = "orange2"
+  ) +
+  geom_point(aes(
+    y = CLtot.tkstats,
+    shape = Species
+  ), size = 3, color = "black", stroke = 1) +
   scale_y_log10(labels = scales::label_math(format = log10)) +
@@
 ggsave(
-  filename = paste0(Sys.getenv("FIG_DIR"),
-                    "Cltot_backcompare_wDawson_2024_0416.png"),
+  filename = paste0(
+    Sys.getenv("FIG_DIR"),
+    "Cltot_backcompare_wDawson_2024_0416.png"
+  ),
   height = 8,
@@
 
-this_coefsd %>% filter(param_name == "Clint", Chemical %in% clear_chem_levels) %>%
-  ggplot(aes(x = factor(Chemical, levels = clear_chem_levels), 
+this_coefsd %>%
+  filter(param_name == "Clint", Chemical %in% clear_chem_levels) %>%
+  ggplot(aes(
+    x = factor(Chemical, levels = clear_chem_levels),
     y = param_value,
-             color = model)) +
+    color = model
+  )) +
   geom_point(alpha = 0.5) +
-  geom_linerange(aes(ymin = param_value-param_sd,
-                    ymax = param_value+param_sd),
-                 alpha = 0.5) +
+  geom_linerange(
+    aes(
+      ymin = param_value - param_sd,
+      ymax = param_value + param_sd
+    ),
+    alpha = 0.5
+  ) +
   theme_bw() +
@@
   filename = paste0(
-    Sys.getenv("FIG_DIR"),"RestrictiveClearance_Analysis/",
+    Sys.getenv("FIG_DIR"), "RestrictiveClearance_Analysis/",
     today,
@@
 # particular way
-
 ```
@@
 ```{r slow_pbpk_optimizations}
-
 ```

### 2025-08-22 data-raw/ClearanceProject-4-PhysChemClustering.Rmd

@@
 
+```{r library-loading}
+today <- format(Sys.Date(), "%d%b%Y")
+devtools::load_all()
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(ctxR)
+library(ggdist)
+library(patchwork)
+library(httk)
+load_dawson2021()
+```
+
 ```{r data_loading}
@@
 load("data-raw/CYP_Sipes2017.RData")
+```
+
+# Binding kinetics
+
+Here what I want to do is understand the binding kinetics for available chemicals.
+These don't all 
+```{r Kd}
+kd_halfway <- red_assay_res %>%
+  select(DTXSID, Name, CAS, starts_with("Affinity.Kd.")) %>%
+  distinct()
+kd_halfway <- kd_halfway[apply(!is.na(kd_halfway[4:6]), MARGIN = 1, any), ]
+
+t1.2_halfway <- kd_halfway %>%
+  mutate(across(.cols = starts_with("Affinity"),
+                \(x) {log(2)/(x*7E9)},
+                .names = "t1.2min_{col}"),
+         across(.cols = starts_with("Affinity"),
+                \(x) {log(2)/(x*3.5E4)},
+                .names = "t1.2max_{col}"),
+         across(.cols = starts_with("Affinity"),
+                \(x) {log(100)/(x*7E9)},
+                .names = "t99min_{col}"),
+         across(.cols = starts_with("Affinity"),
+                \(x) {log(100)/(x*3.5E4)},
+                .names = "t99max_{col}"))
+
+t50_pl <- t1.2_halfway %>%
+  ggplot(aes(x = forcats::fct_reorder(DTXSID, t1.2min_Affinity.Kd.Low))) +
+  geom_pointinterval(aes(y = t1.2min_Affinity.Kd.Med,
+                         ymin = t1.2min_Affinity.Kd.High,
+                         ymax = t1.2min_Affinity.Kd.Low),
+                     alpha = 0.5, shape = 20) +
+  geom_pointinterval(aes(y = t1.2max_Affinity.Kd.Med,
+                         ymin = t1.2max_Affinity.Kd.High, 
+                         ymax = t1.2max_Affinity.Kd.Low), 
+                     alpha = 0.5, shape = 20, color = "purple3") +
+  scale_y_log10(labels = scales::label_math(format = log10)) + 
+  labs(x = "Chemicals",y = "Binding t<sub>1/2</sub>",
+       title = "t<sub>1/2</sub> = ln(2)/(K<sub>D</sub>*k<sub>on</sub>)") +
+  ggtext::geom_richtext(
+    x = 200, y = 1, vjust = 0,
+    label = "k<sub>on,max</sub> = 7E9 M<sup>-1</sup>s<sup>-1</sup>") +
+  ggtext::geom_richtext(
+    x = 100, y = 1, vjust = 0,
+    label = "k<sub>on,min</sub> = 3.5E4 M<sup>-1</sup>s<sup>-1</sup>", 
+    color = "purple4") +
+  geom_hline(yintercept = median(t1.2_halfway$t1.2min_Affinity.Kd.Med), 
+             linetype = "dotted", color = "grey10") +
+  geom_hline(yintercept = median(t1.2_halfway$t1.2max_Affinity.Kd.Med), 
+             linetype = "dotted", color = "purple3") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.title = ggtext::element_markdown(), 
+        plot.title = ggtext::element_markdown(hjust = 0.5),
+        panel.grid.major.x = element_blank())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Binding_halflife_toEquilibrium.png"),
+       bg = "white",
+       height = 5, width = 10
+)
+
+# What about 99% time
+t99_pl <- t1.2_halfway %>%
+  ggplot(aes(x = forcats::fct_reorder(DTXSID, t99min_Affinity.Kd.Low))) +
+  geom_pointinterval(aes(y = t99min_Affinity.Kd.Med,
+                         ymin = t99min_Affinity.Kd.High,
+                         ymax = t99min_Affinity.Kd.Low),
+                     alpha = 0.5, shape = 20) +
+  geom_pointinterval(aes(y = t99max_Affinity.Kd.Med,
+                         ymin = t99max_Affinity.Kd.High, 
+                         ymax = t99max_Affinity.Kd.Low), 
+                     alpha = 0.5, shape = 20, color = "purple3") +
+  scale_y_log10(labels = scales::label_math(format = log10)) + 
+  labs(x = "Chemicals",y = "Binding t<sub>0.99</sub>",
+       title = "t<sub>0.99</sub> = ln(100)/(K<sub>D</sub>*k<sub>on</sub>)") +
+  ggtext::geom_richtext(
+    x = 200, y = 1, vjust = 0,
+    label = "k<sub>on,max</sub> = 7E9 M<sup>-1</sup>s<sup>-1</sup>") +
+  ggtext::geom_richtext(
+    x = 100, y = 1, vjust = 0,
+    label = "k<sub>on,min</sub> = 3.5E4 M<sup>-1</sup>s<sup>-1</sup>", 
+    color = "purple4") +
+  geom_hline(yintercept = median(t1.2_halfway$t99min_Affinity.Kd.Med), 
+             linetype = "dotted", color = "grey10") +
+  geom_hline(yintercept = median(t1.2_halfway$t99max_Affinity.Kd.Med), 
+             linetype = "dotted", color = "purple3") +
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.title = ggtext::element_markdown(), 
+        plot.title = ggtext::element_markdown(hjust = 0.5),
+        panel.grid.major.x = element_blank())
+
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Binding_99percent_toEquilibrium.png"),
+       bg = "white",
+       height = 5, width = 10
+)
+
+t50_pl/t99_pl
+ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
+                         "RestrictiveClearance_Analysis/",
+                         "CURRENT_", "Binding_time_toEquilibrium.png"),
+       bg = "white",
+       height = 10, width = 10
+)
 ```
